\begin{register}{H}{MB\_MASSEGE\_0\_REG}{0x0000}\label{regdesc:MBMESSAGE0REG}
\regfield{MB\_MASSEGE\_0}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBMESSAGE0}\item [MB\_MASSEGE\_0] 信息寄存器 0。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_MASSEGE\_1\_REG}{0x0004}\label{regdesc:MBMESSAGE1REG}
\regfield{MB\_MASSEGE\_1}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBMESSAGE1}\item [MB\_MASSEGE\_1] 信息寄存器 1。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_MASSEGE\_2\_REG}{0x0008}\label{regdesc:MBMESSAGE2REG}
\regfield{MB\_MASSEGE\_2}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBMESSAGE2}\item [MB\_MASSEGE\_2] 信息寄存器 2。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_MASSEGE\_3\_REG}{0x000C}\label{regdesc:MBMESSAGE3REG}
\regfield{MB\_MASSEGE\_3}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBMESSAGE3}\item [MB\_MASSEGE\_3] 信息寄存器 3。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_MASSEGE\_4\_REG}{0x0010}\label{regdesc:MBMESSAGE4REG}
\regfield{MB\_MASSEGE\_4}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBMESSAGE4}\item [MB\_MASSEGE\_4] 信息寄存器 4。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_MASSEGE\_5\_REG}{0x0014}\label{regdesc:MBMESSAGE5REG}
\regfield{MB\_MASSEGE\_5}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBMESSAGE5}\item [MB\_MASSEGE\_5] 信息寄存器 5。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_MASSEGE\_6\_REG}{0x0018}\label{regdesc:MBMESSAGE6REG}
\regfield{MB\_MASSEGE\_6}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBMESSAGE6}\item [MB\_MASSEGE\_6] 信息寄存器 6。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_MASSEGE\_7\_REG}{0x001C}\label{regdesc:MBMESSAGE7REG}
\regfield{MB\_MASSEGE\_7}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBMESSAGE7}\item [MB\_MASSEGE\_7] 信息寄存器 7。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_MASSEGE\_8\_REG}{0x0020}\label{regdesc:MBMESSAGE8REG}
\regfield{MB\_MASSEGE\_8}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBMESSAGE8}\item [MB\_MASSEGE\_8] 信息寄存器 8。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_MASSEGE\_9\_REG}{0x0024}\label{regdesc:MBMESSAGE9REG}
\regfield{MB\_MASSEGE\_9}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBMESSAGE9}\item [MB\_MASSEGE\_9] 信息寄存器 9。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_MASSEGE\_10\_REG}{0x0028}\label{regdesc:MBMESSAGE10REG}
\regfield{MB\_MASSEGE\_10}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBMESSAGE10}\item [MB\_MASSEGE\_10] 信息寄存器 10。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_MASSEGE\_11\_REG}{0x002C}\label{regdesc:MBMESSAGE11REG}
\regfield{MB\_MASSEGE\_11}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBMESSAGE11}\item [MB\_MASSEGE\_11] 信息寄存器 11。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_MASSEGE\_12\_REG}{0x0030}\label{regdesc:MBMESSAGE12REG}
\regfield{MB\_MASSEGE\_12}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBMESSAGE12}\item [MB\_MASSEGE\_12] 信息寄存器 12。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_MASSEGE\_13\_REG}{0x0034}\label{regdesc:MBMESSAGE13REG}
\regfield{MB\_MASSEGE\_13}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBMESSAGE13}\item [MB\_MASSEGE\_13] 信息寄存器 13。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_MASSEGE\_14\_REG}{0x0038}\label{regdesc:MBMESSAGE14REG}
\regfield{MB\_MASSEGE\_14}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBMESSAGE14}\item [MB\_MASSEGE\_14] 信息寄存器 14。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_MASSEGE\_15\_REG}{0x003C}\label{regdesc:MBMESSAGE15REG}
\regfield{MB\_MASSEGE\_15}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBMESSAGE15}\item [MB\_MASSEGE\_15] 信息寄存器 15。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_REG\_CLK\_EN\_REG}{0x0060}\label{regdesc:MBREGCLKENREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{MB\_REG\_CLK\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBREGCLKEN}\item [MB\_REG\_CLK\_EN] 配置寄存器时钟门控。\\
1：读写寄存器时，始终开启时钟。\\
0：仅在读写寄存器操作时，使能时钟。\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_LP\_INT\_RAW\_REG}{0x0040}\label{regdesc:MBLPINTRAWREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{MB\_LP\_15\_INT\_RAW}{1}{15}{{0}}%
\regfield{MB\_LP\_14\_INT\_RAW}{1}{14}{{0}}%
\regfield{MB\_LP\_13\_INT\_RAW}{1}{13}{{0}}%
\regfield{MB\_LP\_12\_INT\_RAW}{1}{12}{{0}}%
\regfield{MB\_LP\_11\_INT\_RAW}{1}{11}{{0}}%
\regfield{MB\_LP\_10\_INT\_RAW}{1}{10}{{0}}%
\regfield{MB\_LP\_9\_INT\_RAW}{1}{9}{{0}}%
\regfield{MB\_LP\_8\_INT\_RAW}{1}{8}{{0}}%
\regfield{MB\_LP\_7\_INT\_RAW}{1}{7}{{0}}%
\regfield{MB\_LP\_6\_INT\_RAW}{1}{6}{{0}}%
\regfield{MB\_LP\_5\_INT\_RAW}{1}{5}{{0}}%
\regfield{MB\_LP\_4\_INT\_RAW}{1}{4}{{0}}%
\regfield{MB\_LP\_3\_INT\_RAW}{1}{3}{{0}}%
\regfield{MB\_LP\_2\_INT\_RAW}{1}{2}{{0}}%
\regfield{MB\_LP\_1\_INT\_RAW}{1}{1}{{0}}%
\regfield{MB\_LP\_0\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBLP0INTRAW}\item [MB\_LP\_0\_INT\_RAW] MB\_LP\_0\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBLP1INTRAW}\item [MB\_LP\_1\_INT\_RAW] MB\_LP\_1\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBLP2INTRAW}\item [MB\_LP\_2\_INT\_RAW] MB\_LP\_2\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBLP3INTRAW}\item [MB\_LP\_3\_INT\_RAW] MB\_LP\_3\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBLP4INTRAW}\item [MB\_LP\_4\_INT\_RAW] MB\_LP\_4\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBLP5INTRAW}\item [MB\_LP\_5\_INT\_RAW] MB\_LP\_5\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBLP6INTRAW}\item [MB\_LP\_6\_INT\_RAW] MB\_LP\_6\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBLP7INTRAW}\item [MB\_LP\_7\_INT\_RAW] MB\_LP\_7\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBLP8INTRAW}\item [MB\_LP\_8\_INT\_RAW] MB\_LP\_8\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBLP9INTRAW}\item [MB\_LP\_9\_INT\_RAW] MB\_LP\_9\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBLP10INTRAW}\item [MB\_LP\_10\_INT\_RAW] MB\_LP\_10\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBLP11INTRAW}\item [MB\_LP\_11\_INT\_RAW] MB\_LP\_11\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBLP12INTRAW}\item [MB\_LP\_12\_INT\_RAW] MB\_LP\_12\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBLP13INTRAW}\item [MB\_LP\_13\_INT\_RAW] MB\_LP\_13\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBLP14INTRAW}\item [MB\_LP\_14\_INT\_RAW] MB\_LP\_14\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBLP15INTRAW}\item [MB\_LP\_15\_INT\_RAW] MB\_LP\_15\_INT 的原始中断状态。 (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_LP\_INT\_ST\_REG}{0x0044}\label{regdesc:MBLPINTSTREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{MB\_LP\_15\_INT\_ST}{1}{15}{{0}}%
\regfield{MB\_LP\_14\_INT\_ST}{1}{14}{{0}}%
\regfield{MB\_LP\_13\_INT\_ST}{1}{13}{{0}}%
\regfield{MB\_LP\_12\_INT\_ST}{1}{12}{{0}}%
\regfield{MB\_LP\_11\_INT\_ST}{1}{11}{{0}}%
\regfield{MB\_LP\_10\_INT\_ST}{1}{10}{{0}}%
\regfield{MB\_LP\_9\_INT\_ST}{1}{9}{{0}}%
\regfield{MB\_LP\_8\_INT\_ST}{1}{8}{{0}}%
\regfield{MB\_LP\_7\_INT\_ST}{1}{7}{{0}}%
\regfield{MB\_LP\_6\_INT\_ST}{1}{6}{{0}}%
\regfield{MB\_LP\_5\_INT\_ST}{1}{5}{{0}}%
\regfield{MB\_LP\_4\_INT\_ST}{1}{4}{{0}}%
\regfield{MB\_LP\_3\_INT\_ST}{1}{3}{{0}}%
\regfield{MB\_LP\_2\_INT\_ST}{1}{2}{{0}}%
\regfield{MB\_LP\_1\_INT\_ST}{1}{1}{{0}}%
\regfield{MB\_LP\_0\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBLP0INTST}\item [MB\_LP\_0\_INT\_ST] MB\_LP\_0\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBLP1INTST}\item [MB\_LP\_1\_INT\_ST] MB\_LP\_1\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBLP2INTST}\item [MB\_LP\_2\_INT\_ST] MB\_LP\_2\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBLP3INTST}\item [MB\_LP\_3\_INT\_ST] MB\_LP\_3\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBLP4INTST}\item [MB\_LP\_4\_INT\_ST] MB\_LP\_4\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBLP5INTST}\item [MB\_LP\_5\_INT\_ST] MB\_LP\_5\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBLP6INTST}\item [MB\_LP\_6\_INT\_ST] MB\_LP\_6\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBLP7INTST}\item [MB\_LP\_7\_INT\_ST] MB\_LP\_7\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBLP8INTST}\item [MB\_LP\_8\_INT\_ST] MB\_LP\_8\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBLP9INTST}\item [MB\_LP\_9\_INT\_ST] MB\_LP\_9\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBLP10INTST}\item [MB\_LP\_10\_INT\_ST] MB\_LP\_10\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBLP11INTST}\item [MB\_LP\_11\_INT\_ST] MB\_LP\_11\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBLP12INTST}\item [MB\_LP\_12\_INT\_ST] MB\_LP\_12\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBLP13INTST}\item [MB\_LP\_13\_INT\_ST] MB\_LP\_13\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBLP14INTST}\item [MB\_LP\_14\_INT\_ST] MB\_LP\_14\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBLP15INTST}\item [MB\_LP\_15\_INT\_ST] MB\_LP\_15\_INT 的屏蔽中断状态。 (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_LP\_INT\_ENA\_REG}{0x0048}\label{regdesc:MBLPINTENAREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{MB\_LP\_15\_INT\_ENA}{1}{15}{{0}}%
\regfield{MB\_LP\_14\_INT\_ENA}{1}{14}{{0}}%
\regfield{MB\_LP\_13\_INT\_ENA}{1}{13}{{0}}%
\regfield{MB\_LP\_12\_INT\_ENA}{1}{12}{{0}}%
\regfield{MB\_LP\_11\_INT\_ENA}{1}{11}{{0}}%
\regfield{MB\_LP\_10\_INT\_ENA}{1}{10}{{0}}%
\regfield{MB\_LP\_9\_INT\_ENA}{1}{9}{{0}}%
\regfield{MB\_LP\_8\_INT\_ENA}{1}{8}{{0}}%
\regfield{MB\_LP\_7\_INT\_ENA}{1}{7}{{1}}%
\regfield{MB\_LP\_6\_INT\_ENA}{1}{6}{{1}}%
\regfield{MB\_LP\_5\_INT\_ENA}{1}{5}{{1}}%
\regfield{MB\_LP\_4\_INT\_ENA}{1}{4}{{1}}%
\regfield{MB\_LP\_3\_INT\_ENA}{1}{3}{{1}}%
\regfield{MB\_LP\_2\_INT\_ENA}{1}{2}{{1}}%
\regfield{MB\_LP\_1\_INT\_ENA}{1}{1}{{1}}%
\regfield{MB\_LP\_0\_INT\_ENA}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBLP0INTENA}\item [MB\_LP\_0\_INT\_ENA] 写 1 使能 MB\_LP\_0\_INT 中断。 (R/W)
\label{fielddesc:MBLP1INTENA}\item [MB\_LP\_1\_INT\_ENA] 写 1 使能 MB\_LP\_1\_INT 中断。 (R/W)
\label{fielddesc:MBLP2INTENA}\item [MB\_LP\_2\_INT\_ENA] 写 1 使能 MB\_LP\_2\_INT 中断。 (R/W)
\label{fielddesc:MBLP3INTENA}\item [MB\_LP\_3\_INT\_ENA] 写 1 使能 MB\_LP\_3\_INT 中断。 (R/W)
\label{fielddesc:MBLP4INTENA}\item [MB\_LP\_4\_INT\_ENA] 写 1 使能 MB\_LP\_4\_INT 中断。 (R/W)
\label{fielddesc:MBLP5INTENA}\item [MB\_LP\_5\_INT\_ENA] 写 1 使能 MB\_LP\_5\_INT 中断。 (R/W)
\label{fielddesc:MBLP6INTENA}\item [MB\_LP\_6\_INT\_ENA] 写 1 使能 MB\_LP\_6\_INT 中断。 (R/W)
\label{fielddesc:MBLP7INTENA}\item [MB\_LP\_7\_INT\_ENA] 写 1 使能 MB\_LP\_7\_INT 中断。 (R/W)
\label{fielddesc:MBLP8INTENA}\item [MB\_LP\_8\_INT\_ENA] 写 1 使能 MB\_LP\_8\_INT 中断。 (R/W)
\label{fielddesc:MBLP9INTENA}\item [MB\_LP\_9\_INT\_ENA] 写 1 使能 MB\_LP\_9\_INT 中断。 (R/W)
\label{fielddesc:MBLP10INTENA}\item [MB\_LP\_10\_INT\_ENA] 写 1 使能 MB\_LP\_10\_INT 中断。 (R/W)
\label{fielddesc:MBLP11INTENA}\item [MB\_LP\_11\_INT\_ENA] 写 1 使能 MB\_LP\_11\_INT 中断。 (R/W)
\label{fielddesc:MBLP12INTENA}\item [MB\_LP\_12\_INT\_ENA] 写 1 使能 MB\_LP\_12\_INT 中断。 (R/W)
\label{fielddesc:MBLP13INTENA}\item [MB\_LP\_13\_INT\_ENA] 写 1 使能 MB\_LP\_13\_INT 中断。 (R/W)
\label{fielddesc:MBLP14INTENA}\item [MB\_LP\_14\_INT\_ENA] 写 1 使能 MB\_LP\_14\_INT 中断。 (R/W)
\label{fielddesc:MBLP15INTENA}\item [MB\_LP\_15\_INT\_ENA] 写 1 使能 MB\_LP\_15\_INT 中断。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_LP\_INT\_CLR\_REG}{0x004C}\label{regdesc:MBLPINTCLRREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{MB\_LP\_15\_INT\_CLR}{1}{15}{{0}}%
\regfield{MB\_LP\_14\_INT\_CLR}{1}{14}{{0}}%
\regfield{MB\_LP\_13\_INT\_CLR}{1}{13}{{0}}%
\regfield{MB\_LP\_12\_INT\_CLR}{1}{12}{{0}}%
\regfield{MB\_LP\_11\_INT\_CLR}{1}{11}{{0}}%
\regfield{MB\_LP\_10\_INT\_CLR}{1}{10}{{0}}%
\regfield{MB\_LP\_9\_INT\_CLR}{1}{9}{{0}}%
\regfield{MB\_LP\_8\_INT\_CLR}{1}{8}{{0}}%
\regfield{MB\_LP\_7\_INT\_CLR}{1}{7}{{0}}%
\regfield{MB\_LP\_6\_INT\_CLR}{1}{6}{{0}}%
\regfield{MB\_LP\_5\_INT\_CLR}{1}{5}{{0}}%
\regfield{MB\_LP\_4\_INT\_CLR}{1}{4}{{0}}%
\regfield{MB\_LP\_3\_INT\_CLR}{1}{3}{{0}}%
\regfield{MB\_LP\_2\_INT\_CLR}{1}{2}{{0}}%
\regfield{MB\_LP\_1\_INT\_CLR}{1}{1}{{0}}%
\regfield{MB\_LP\_0\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBLP0INTCLR}\item [MB\_LP\_0\_INT\_CLR] 写 1 清除 MB\_LP\_0\_INT 中断。 (WO)
\label{fielddesc:MBLP1INTCLR}\item [MB\_LP\_1\_INT\_CLR] 写 1 清除 MB\_LP\_1\_INT 中断。 (WO)
\label{fielddesc:MBLP2INTCLR}\item [MB\_LP\_2\_INT\_CLR] 写 1 清除 MB\_LP\_2\_INT 中断。 (WO)
\label{fielddesc:MBLP3INTCLR}\item [MB\_LP\_3\_INT\_CLR] 写 1 清除 MB\_LP\_3\_INT 中断。 (WO)
\label{fielddesc:MBLP4INTCLR}\item [MB\_LP\_4\_INT\_CLR] 写 1 清除 MB\_LP\_4\_INT 中断。 (WO)
\label{fielddesc:MBLP5INTCLR}\item [MB\_LP\_5\_INT\_CLR] 写 1 清除 MB\_LP\_5\_INT 中断。 (WO)
\label{fielddesc:MBLP6INTCLR}\item [MB\_LP\_6\_INT\_CLR] 写 1 清除 MB\_LP\_6\_INT 中断。 (WO)
\label{fielddesc:MBLP7INTCLR}\item [MB\_LP\_7\_INT\_CLR] 写 1 清除 MB\_LP\_7\_INT 中断。 (WO)
\label{fielddesc:MBLP8INTCLR}\item [MB\_LP\_8\_INT\_CLR] 写 1 清除 MB\_LP\_8\_INT 中断。 (WO)
\label{fielddesc:MBLP9INTCLR}\item [MB\_LP\_9\_INT\_CLR] 写 1 清除 MB\_LP\_9\_INT 中断。 (WO)
\label{fielddesc:MBLP10INTCLR}\item [MB\_LP\_10\_INT\_CLR] 写 1 清除 MB\_LP\_10\_INT 中断。 (WO)
\label{fielddesc:MBLP11INTCLR}\item [MB\_LP\_11\_INT\_CLR] 写 1 清除 MB\_LP\_11\_INT 中断。 (WO)
\label{fielddesc:MBLP12INTCLR}\item [MB\_LP\_12\_INT\_CLR] 写 1 清除 MB\_LP\_12\_INT 中断。 (WO)
\label{fielddesc:MBLP13INTCLR}\item [MB\_LP\_13\_INT\_CLR] 写 1 清除 MB\_LP\_13\_INT 中断。 (WO)
\label{fielddesc:MBLP14INTCLR}\item [MB\_LP\_14\_INT\_CLR] 写 1 清除 MB\_LP\_14\_INT 中断。 (WO)
\label{fielddesc:MBLP15INTCLR}\item [MB\_LP\_15\_INT\_CLR] 写 1 清除 MB\_LP\_15\_INT 中断。 (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_HP\_INT\_RAW\_REG}{0x0050}\label{regdesc:MBHPINTRAWREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{MB\_HP\_15\_INT\_RAW}{1}{15}{{0}}%
\regfield{MB\_HP\_14\_INT\_RAW}{1}{14}{{0}}%
\regfield{MB\_HP\_13\_INT\_RAW}{1}{13}{{0}}%
\regfield{MB\_HP\_12\_INT\_RAW}{1}{12}{{0}}%
\regfield{MB\_HP\_11\_INT\_RAW}{1}{11}{{0}}%
\regfield{MB\_HP\_10\_INT\_RAW}{1}{10}{{0}}%
\regfield{MB\_HP\_9\_INT\_RAW}{1}{9}{{0}}%
\regfield{MB\_HP\_8\_INT\_RAW}{1}{8}{{0}}%
\regfield{MB\_HP\_7\_INT\_RAW}{1}{7}{{0}}%
\regfield{MB\_HP\_6\_INT\_RAW}{1}{6}{{0}}%
\regfield{MB\_HP\_5\_INT\_RAW}{1}{5}{{0}}%
\regfield{MB\_HP\_4\_INT\_RAW}{1}{4}{{0}}%
\regfield{MB\_HP\_3\_INT\_RAW}{1}{3}{{0}}%
\regfield{MB\_HP\_2\_INT\_RAW}{1}{2}{{0}}%
\regfield{MB\_HP\_1\_INT\_RAW}{1}{1}{{0}}%
\regfield{MB\_HP\_0\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBHP0INTRAW}\item [MB\_HP\_0\_INT\_RAW] MB\_HP\_0\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBHP1INTRAW}\item [MB\_HP\_1\_INT\_RAW] MB\_HP\_1\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBHP2INTRAW}\item [MB\_HP\_2\_INT\_RAW] MB\_HP\_2\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBHP3INTRAW}\item [MB\_HP\_3\_INT\_RAW] MB\_HP\_3\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBHP4INTRAW}\item [MB\_HP\_4\_INT\_RAW] MB\_HP\_4\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBHP5INTRAW}\item [MB\_HP\_5\_INT\_RAW] MB\_HP\_5\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBHP6INTRAW}\item [MB\_HP\_6\_INT\_RAW] MB\_HP\_6\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBHP7INTRAW}\item [MB\_HP\_7\_INT\_RAW] MB\_HP\_7\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBHP8INTRAW}\item [MB\_HP\_8\_INT\_RAW] MB\_HP\_8\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBHP9INTRAW}\item [MB\_HP\_9\_INT\_RAW] MB\_HP\_9\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBHP10INTRAW}\item [MB\_HP\_10\_INT\_RAW] MB\_HP\_10\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBHP11INTRAW}\item [MB\_HP\_11\_INT\_RAW] MB\_HP\_11\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBHP12INTRAW}\item [MB\_HP\_12\_INT\_RAW] MB\_HP\_12\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBHP13INTRAW}\item [MB\_HP\_13\_INT\_RAW] MB\_HP\_13\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBHP14INTRAW}\item [MB\_HP\_14\_INT\_RAW] MB\_HP\_14\_INT 的原始中断状态。 (RO)
\label{fielddesc:MBHP15INTRAW}\item [MB\_HP\_15\_INT\_RAW] MB\_HP\_15\_INT 的原始中断状态。 (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_HP\_INT\_ST\_REG}{0x0054}\label{regdesc:MBHPINTSTREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{MB\_HP\_15\_INT\_ST}{1}{15}{{0}}%
\regfield{MB\_HP\_14\_INT\_ST}{1}{14}{{0}}%
\regfield{MB\_HP\_13\_INT\_ST}{1}{13}{{0}}%
\regfield{MB\_HP\_12\_INT\_ST}{1}{12}{{0}}%
\regfield{MB\_HP\_11\_INT\_ST}{1}{11}{{0}}%
\regfield{MB\_HP\_10\_INT\_ST}{1}{10}{{0}}%
\regfield{MB\_HP\_9\_INT\_ST}{1}{9}{{0}}%
\regfield{MB\_HP\_8\_INT\_ST}{1}{8}{{0}}%
\regfield{MB\_HP\_7\_INT\_ST}{1}{7}{{0}}%
\regfield{MB\_HP\_6\_INT\_ST}{1}{6}{{0}}%
\regfield{MB\_HP\_5\_INT\_ST}{1}{5}{{0}}%
\regfield{MB\_HP\_4\_INT\_ST}{1}{4}{{0}}%
\regfield{MB\_HP\_3\_INT\_ST}{1}{3}{{0}}%
\regfield{MB\_HP\_2\_INT\_ST}{1}{2}{{0}}%
\regfield{MB\_HP\_1\_INT\_ST}{1}{1}{{0}}%
\regfield{MB\_HP\_0\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBHP0INTST}\item [MB\_HP\_0\_INT\_ST] MB\_HP\_0\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBHP1INTST}\item [MB\_HP\_1\_INT\_ST] MB\_HP\_1\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBHP2INTST}\item [MB\_HP\_2\_INT\_ST] MB\_HP\_2\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBHP3INTST}\item [MB\_HP\_3\_INT\_ST] MB\_HP\_3\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBHP4INTST}\item [MB\_HP\_4\_INT\_ST] MB\_HP\_4\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBHP5INTST}\item [MB\_HP\_5\_INT\_ST] MB\_HP\_5\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBHP6INTST}\item [MB\_HP\_6\_INT\_ST] MB\_HP\_6\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBHP7INTST}\item [MB\_HP\_7\_INT\_ST] MB\_HP\_7\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBHP8INTST}\item [MB\_HP\_8\_INT\_ST] MB\_HP\_8\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBHP9INTST}\item [MB\_HP\_9\_INT\_ST] MB\_HP\_9\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBHP10INTST}\item [MB\_HP\_10\_INT\_ST] MB\_HP\_10\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBHP11INTST}\item [MB\_HP\_11\_INT\_ST] MB\_HP\_11\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBHP12INTST}\item [MB\_HP\_12\_INT\_ST] MB\_HP\_12\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBHP13INTST}\item [MB\_HP\_13\_INT\_ST] MB\_HP\_13\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBHP14INTST}\item [MB\_HP\_14\_INT\_ST] MB\_HP\_14\_INT 的屏蔽中断状态。 (RO)
\label{fielddesc:MBHP15INTST}\item [MB\_HP\_15\_INT\_ST] MB\_HP\_15\_INT 的屏蔽中断状态。 (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_HP\_INT\_ENA\_REG}{0x0058}\label{regdesc:MBHPINTENAREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{MB\_HP\_15\_INT\_ENA}{1}{15}{{0}}%
\regfield{MB\_HP\_14\_INT\_ENA}{1}{14}{{0}}%
\regfield{MB\_HP\_13\_INT\_ENA}{1}{13}{{0}}%
\regfield{MB\_HP\_12\_INT\_ENA}{1}{12}{{0}}%
\regfield{MB\_HP\_11\_INT\_ENA}{1}{11}{{0}}%
\regfield{MB\_HP\_10\_INT\_ENA}{1}{10}{{0}}%
\regfield{MB\_HP\_9\_INT\_ENA}{1}{9}{{0}}%
\regfield{MB\_HP\_8\_INT\_ENA}{1}{8}{{0}}%
\regfield{MB\_HP\_7\_INT\_ENA}{1}{7}{{1}}%
\regfield{MB\_HP\_6\_INT\_ENA}{1}{6}{{1}}%
\regfield{MB\_HP\_5\_INT\_ENA}{1}{5}{{1}}%
\regfield{MB\_HP\_4\_INT\_ENA}{1}{4}{{1}}%
\regfield{MB\_HP\_3\_INT\_ENA}{1}{3}{{1}}%
\regfield{MB\_HP\_2\_INT\_ENA}{1}{2}{{1}}%
\regfield{MB\_HP\_1\_INT\_ENA}{1}{1}{{1}}%
\regfield{MB\_HP\_0\_INT\_ENA}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBHP0INTENA}\item [MB\_HP\_0\_INT\_ENA] 写 1 使能 MB\_HP\_0\_INT 中断。 (R/W)
\label{fielddesc:MBHP1INTENA}\item [MB\_HP\_1\_INT\_ENA] 写 1 使能 MB\_HP\_1\_INT 中断。 (R/W)
\label{fielddesc:MBHP2INTENA}\item [MB\_HP\_2\_INT\_ENA] 写 1 使能 MB\_HP\_2\_INT 中断。 (R/W)
\label{fielddesc:MBHP3INTENA}\item [MB\_HP\_3\_INT\_ENA] 写 1 使能 MB\_HP\_3\_INT 中断。 (R/W)
\label{fielddesc:MBHP4INTENA}\item [MB\_HP\_4\_INT\_ENA] 写 1 使能 MB\_HP\_4\_INT 中断。 (R/W)
\label{fielddesc:MBHP5INTENA}\item [MB\_HP\_5\_INT\_ENA] 写 1 使能 MB\_HP\_5\_INT 中断。 (R/W)
\label{fielddesc:MBHP6INTENA}\item [MB\_HP\_6\_INT\_ENA] 写 1 使能 MB\_HP\_6\_INT 中断。 (R/W)
\label{fielddesc:MBHP7INTENA}\item [MB\_HP\_7\_INT\_ENA] 写 1 使能 MB\_HP\_7\_INT 中断。 (R/W)
\label{fielddesc:MBHP8INTENA}\item [MB\_HP\_8\_INT\_ENA] 写 1 使能 MB\_HP\_8\_INT 中断。 (R/W)
\label{fielddesc:MBHP9INTENA}\item [MB\_HP\_9\_INT\_ENA] 写 1 使能 MB\_HP\_9\_INT 中断。 (R/W)
\label{fielddesc:MBHP10INTENA}\item [MB\_HP\_10\_INT\_ENA] 写 1 使能 MB\_HP\_10\_INT 中断。 (R/W)
\label{fielddesc:MBHP11INTENA}\item [MB\_HP\_11\_INT\_ENA] 写 1 使能 MB\_HP\_11\_INT 中断。 (R/W)
\label{fielddesc:MBHP12INTENA}\item [MB\_HP\_12\_INT\_ENA] 写 1 使能 MB\_HP\_12\_INT 中断。 (R/W)
\label{fielddesc:MBHP13INTENA}\item [MB\_HP\_13\_INT\_ENA] 写 1 使能 MB\_HP\_13\_INT 中断。 (R/W)
\label{fielddesc:MBHP14INTENA}\item [MB\_HP\_14\_INT\_ENA] 写 1 使能 MB\_HP\_14\_INT 中断。 (R/W)
\label{fielddesc:MBHP15INTENA}\item [MB\_HP\_15\_INT\_ENA] 写 1 使能 MB\_HP\_15\_INT 中断。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{MB\_HP\_INT\_CLR\_REG}{0x005C}\label{regdesc:MBHPINTCLRREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{MB\_HP\_15\_INT\_CLR}{1}{15}{{0}}%
\regfield{MB\_HP\_14\_INT\_CLR}{1}{14}{{0}}%
\regfield{MB\_HP\_13\_INT\_CLR}{1}{13}{{0}}%
\regfield{MB\_HP\_12\_INT\_CLR}{1}{12}{{0}}%
\regfield{MB\_HP\_11\_INT\_CLR}{1}{11}{{0}}%
\regfield{MB\_HP\_10\_INT\_CLR}{1}{10}{{0}}%
\regfield{MB\_HP\_9\_INT\_CLR}{1}{9}{{0}}%
\regfield{MB\_HP\_8\_INT\_CLR}{1}{8}{{0}}%
\regfield{MB\_HP\_7\_INT\_CLR}{1}{7}{{0}}%
\regfield{MB\_HP\_6\_INT\_CLR}{1}{6}{{0}}%
\regfield{MB\_HP\_5\_INT\_CLR}{1}{5}{{0}}%
\regfield{MB\_HP\_4\_INT\_CLR}{1}{4}{{0}}%
\regfield{MB\_HP\_3\_INT\_CLR}{1}{3}{{0}}%
\regfield{MB\_HP\_2\_INT\_CLR}{1}{2}{{0}}%
\regfield{MB\_HP\_1\_INT\_CLR}{1}{1}{{0}}%
\regfield{MB\_HP\_0\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MBHP0INTCLR}\item [MB\_HP\_0\_INT\_CLR] 写 1 清除 MB\_HP\_0\_INT 中断。 (WO)
\label{fielddesc:MBHP1INTCLR}\item [MB\_HP\_1\_INT\_CLR] 写 1 清除 MB\_HP\_1\_INT 中断。 (WO)
\label{fielddesc:MBHP2INTCLR}\item [MB\_HP\_2\_INT\_CLR] 写 1 清除 MB\_HP\_2\_INT 中断。 (WO)
\label{fielddesc:MBHP3INTCLR}\item [MB\_HP\_3\_INT\_CLR] 写 1 清除 MB\_HP\_3\_INT 中断。 (WO)
\label{fielddesc:MBHP4INTCLR}\item [MB\_HP\_4\_INT\_CLR] 写 1 清除 MB\_HP\_4\_INT 中断。 (WO)
\label{fielddesc:MBHP5INTCLR}\item [MB\_HP\_5\_INT\_CLR] 写 1 清除 MB\_HP\_5\_INT 中断。 (WO)
\label{fielddesc:MBHP6INTCLR}\item [MB\_HP\_6\_INT\_CLR] 写 1 清除 MB\_HP\_6\_INT 中断。 (WO)
\label{fielddesc:MBHP7INTCLR}\item [MB\_HP\_7\_INT\_CLR] 写 1 清除 MB\_HP\_7\_INT 中断。 (WO)
\label{fielddesc:MBHP8INTCLR}\item [MB\_HP\_8\_INT\_CLR] 写 1 清除 MB\_HP\_8\_INT 中断。 (WO)
\label{fielddesc:MBHP9INTCLR}\item [MB\_HP\_9\_INT\_CLR] 写 1 清除 MB\_HP\_9\_INT 中断。 (WO)
\label{fielddesc:MBHP10INTCLR}\item [MB\_HP\_10\_INT\_CLR] 写 1 清除 MB\_HP\_10\_INT 中断。 (WO)
\label{fielddesc:MBHP11INTCLR}\item [MB\_HP\_11\_INT\_CLR] 写 1 清除 MB\_HP\_11\_INT 中断。 (WO)
\label{fielddesc:MBHP12INTCLR}\item [MB\_HP\_12\_INT\_CLR] 写 1 清除 MB\_HP\_12\_INT 中断。 (WO)
\label{fielddesc:MBHP13INTCLR}\item [MB\_HP\_13\_INT\_CLR] 写 1 清除 MB\_HP\_13\_INT 中断。 (WO)
\label{fielddesc:MBHP14INTCLR}\item [MB\_HP\_14\_INT\_CLR] 写 1 清除 MB\_HP\_14\_INT 中断。 (WO)
\label{fielddesc:MBHP15INTCLR}\item [MB\_HP\_15\_INT\_CLR] 写 1 清除 MB\_HP\_15\_INT 中断。 (WO)
\end{reglist}\end{regdesc}
\end{register}


