\begin{enumerate}
    \item \label{others:sha-sel-algorithm2} Select a hash algorithm.
    \begin{itemize}
        \item Configure the \hyperref[regdesc:SHAMODEREG]{SHA\_MODE\_REG} register to 7 for SHA-512/{\it{t}}.
    \end{itemize}
    \item Calculate the initial hash value.
        \begin{enumerate}
            \item Calculate t\_stiring and t\_length and initialize \hyperref[regdesc:SHATSTRINGREG]{SHA\_T\_STRING\_REG} and  \hyperref[regdesc:SHATLENGTHREG]{SHA\_T\_LENGTH\_REG} with the generated t\_string and t\_length. For details, please refer to Section \ref{others:sha-512/t}.
            \item Set the \hyperref[regdesc:SHASTARTREG]{SHA\_START\_REG} register to 1 to start the SHA accelerator.
            \item Poll register \hyperref[regdesc:SHABUSYREG]{SHA\_BUSY\_REG} until the content of this register becomes 0, indicating the calculation of initial hash value is completed.
        \end{enumerate}
    
    \item \label{others:sha-current-block1} Process the current message block\hyperref[others:sha-note-typical-sha]{$^1$}.
    \begin{itemize}
        \item Write the message block in registers \hyperref[regdesc:SHAMNREG]{SHA\_M\_\regindex{n}\_REG}.
    \end{itemize}
    \item Start the SHA accelerator 
    \begin{itemize}
        \item Set the \hyperref[regdesc:SHACONTINUEREG]{SHA\_CONTINUE\_REG} register to 1. In this case, the accelerator uses the hash value stored in the \hyperref[regdesc:SHAHNREG]{SHA\_H\_\regindex{n}\_REG} register to start calculation.
    \end{itemize}
    
    \item Check the progress of the calculation.
    \begin{itemize}
        \item Poll register \hyperref[regdesc:SHABUSYREG]{SHA\_BUSY\_REG} until the content of this register becomes 0, indicating the accelerator has completed the calculation for the current message block and now is in the ``idle" status\hyperref[others:sha-note-typical-sha]{$^3$}. 
    \end{itemize}
    
    \item Decide if you have more message blocks to process:
    \begin{itemize}
        \item If yes, please go back to Step \ref{others:sha-current-block1}.
        \item Otherwise, please continue.
    \end{itemize}
    
    \item Obtain the message digest.
    \begin{itemize}
        \item Read the message digest from registers \hyperref[regdesc:SHAHNREG]{SHA\_H\_\regindex{n}\_REG}.
    \end{itemize}
\end{enumerate}
