\begin{enumerate}
    \item Select a hash algorithm.
    \begin{itemize}
        \item Select a hash algorithm by configuring the \hyperref[regdesc:SHAMODEREG]{SHA\_MODE\_REG} register. For details, please refer to Table \ref{tab:sha-hash-algo-select}.
    \end{itemize}
    \item Configure the \hyperref[regdesc:SHAINTENAREG]{SHA\_INT\_ENA\_REG} register to enable or disable interrupt (Set 1 to enable).
    \item Configure the number of message blocks.
    \begin{itemize}
        \item  Write the number of message blocks \begin{math}M\end{math} to the  \hyperref[regdesc:SHADMABLOCKNUMREG]{SHA\_DMA\_BLOCK\_NUM\_REG} register.
    \end{itemize}
    \item Start the DMA-SHA calculation.
        \begin{itemize}
            \item If the current DMA-SHA calculation follows a previous calculation, firstly write the message digest from the previous calculation to registers \hyperref[regdesc:SHAHNREG]{SHA\_H\_\regindex{n}\_REG}, then write 1 to register \hyperref[regdesc:SHADMACONTINUEREG]{SHA\_DMA\_CONTINUE\_REG} to start SHA accelerator;
            \item Otherwise, write 1 to register \hyperref[regdesc:SHADMASTARTREG]{SHA\_DMA\_START\_REG} to start the accelerator.
        \end{itemize}
    \item Wait till the completion of the DMA-SHA calculation, which happens when:
        \begin{itemize}
            \item The content of \hyperref[regdesc:SHABUSYREG]{SHA\_BUSY\_REG} register becomes 0, or
            \item An SHA interrupt occurs. In this case, please clear interrupt by writing 1 to the \hyperref[regdesc:SHAINTCLEARREG]{SHA\_INT\_CLEAR\_REG} register.
        \end{itemize}
    
    \item Obtain the message digest:
    \begin{itemize}
        \item Read the message digest from registers \hyperref[regdesc:SHAHNREG]{SHA\_H\_\regindex{n}\_REG}.
    \end{itemize}
\end{enumerate}