\begin{enumerate}
    \item \label{others:sha-sel-algorithm} Select a hash algorithm.
    \begin{itemize}
        \item Configure the \hyperref[regdesc:SHAMODEREG]{SHA\_MODE\_REG} register based on Table \ref{tab:sha-hash-algo-select}.
    \end{itemize}
    \item \label{others:sha-current-block} Process the current message block \hyperref[others:sha-note-typical-sha]{$^1$}.
    \begin{itemize}
        \item Write the message block in registers \hyperref[regdesc:SHAMNREG]{SHA\_M\_\regindex{n}\_REG}.
    \end{itemize}
    \item Start the SHA accelerator.
    \begin{itemize}
        \item If this is the first time to execute this step, set the \hyperref[regdesc:SHASTARTREG]{SHA\_START\_REG} register to 1 to start the SHA accelerator. In this case, the accelerator uses the initial hash value stored in hardware for a given algorithm configured in Step \ref{others:sha-sel-algorithm} to start the calculation;
        \item If this is not the first time to execute this step\hyperref[others:sha-note-typical-sha]{$^2$}, set the \hyperref[regdesc:SHACONTINUEREG]{SHA\_CONTINUE\_REG} register to 1 to start the SHA accelerator. In this case, the accelerator uses the hash value stored in the \hyperref[regdesc:SHAHNREG]{SHA\_H\_\regindex{n}\_REG} register to start calculation.
    \end{itemize}
    \item Check the progress of the current message block.
    \begin{itemize}
        \item Poll register \hyperref[regdesc:SHABUSYREG]{SHA\_BUSY\_REG} until the content of this register becomes 0, indicating the accelerator has completed the calculation for the current message block and now is in the ``idle" status \hyperref[others:sha-note-typical-sha]{$^3$}. 
    \end{itemize}
        
    \item Decide if you have more message blocks to process:
    \begin{itemize}
        \item If yes, please go back to Step \ref{others:sha-current-block}.
        \item Otherwise, please continue.
    \end{itemize}

    \item Obtain the message digest.
    \begin{itemize}
        \item Read the message digest from registers \hyperref[regdesc:SHAHNREG]{SHA\_H\_\regindex{n}\_REG}.
    \end{itemize}
\end{enumerate}
