\begin{enumerate}
    \item Select a hash algorithm.
    \begin{itemize}
        \item Select SHA-512/{\it{t}} algorithm by configuring the \hyperref[regdesc:SHAMODEREG]{SHA\_MODE\_REG} register to 7.
    \end{itemize}
    
    \item Configure the \hyperref[regdesc:SHAINTENAREG]{SHA\_INT\_ENA\_REG} register to enable or disable interrupt (Set 1 to enable).
    
    \item Calculate the initial hash value.    
        \begin{enumerate}
            \item Calculate t\_string and t\_length and initialize \hyperref[regdesc:SHATSTRINGREG]{SHA\_T\_STRING\_REG} and  \hyperref[regdesc:SHATLENGTHREG]{SHA\_T\_LENGTH\_REG} with the generated t\_string and t\_length. For details, please refer to Section \ref{others:sha-512/t}.
            \item Set the \hyperref[regdesc:SHASTARTREG]{SHA\_START\_REG} register to 1 to start the SHA accelerator.
            \item Poll register \hyperref[regdesc:SHABUSYREG]{SHA\_BUSY\_REG} until the content of this register becomes 0, indicating the calculation of initial hash value is completed.
        \end{enumerate}
    
    \item Configure the number of message blocks.
    \begin{itemize}
        \item  Write the number of message blocks \begin{math}M\end{math} to the  \hyperref[regdesc:SHADMABLOCKNUMREG]{SHA\_DMA\_BLOCK\_NUM\_REG} register.
    \end{itemize}
    
    \item Start the DMA-SHA calculation.
        \begin{itemize}
            \item Write 1 to register \hyperref[regdesc:SHADMACONTINUEREG]{SHA\_DMA\_CONTINUE\_REG} to start the accelerator.
        \end{itemize}
    
    \item Wait till the completion of the DMA-SHA calculation, which happens when:
        \begin{itemize}
            \item The content of \hyperref[regdesc:SHABUSYREG]{SHA\_BUSY\_REG} register becomes 0, or
            \item An SHA interrupt occurs. In this case, please clear interrupt by writing 1 to the \hyperref[regdesc:SHAINTCLEARREG]{SHA\_INT\_CLEAR\_REG} register.
        \end{itemize}
    
    \item Obtain the message digest:
    \begin{itemize}
        \item Read the message digest from registers \hyperref[regdesc:SHAHNREG]{SHA\_H\_\regindex{n}\_REG}.
    \end{itemize}
\end{enumerate}
