\begin{register}{H}{SPI\_CMD\_REG}{\hexprefix{}0000}\label{regdesc:SPICMDREG}
\regfield{(reserved)}{7}{25}{0000000}%
\regfield{SPI\_USR}{1}{24}{{0}}%
\regfield{(reserved)}{1}{23}{0}%
\regfield{SPI\_CONF\_BITLEN}{23}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPICONFBITLEN}\item [SPI\_CONF\_BITLEN] Define the SPI\_CLK cycles of  SPI\_CONF state. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSR}\item [SPI\_USR] User-defined command enable. An operation will be triggered when the bit is set. The bit will be cleared once the operation is done. 1: enable, 0: disable. Can not be changed by CONF\_buf. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_ADDR\_REG}{\hexprefix{}0004}\label{regdesc:SPIADDRREG}
\regfield{SPI\_USR\_ADDR\_VALUE}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIUSRADDRVALUE}\item [SPI\_USR\_ADDR\_VALUE] [31:8]: the address to slave, [7:0]: Reserved. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_USER\_REG}{\hexprefix{}0018}\label{regdesc:SPIUSERREG}
\regfield{SPI\_USR\_COMMAND}{1}{31}{{1}}%
\regfield{SPI\_USR\_ADDR}{1}{30}{{0}}%
\regfield{SPI\_USR\_DUMMY}{1}{29}{{0}}%
\regfield{SPI\_USR\_MISO}{1}{28}{{0}}%
\regfield{SPI\_USR\_MOSI}{1}{27}{{0}}%
\regfield{SPI\_USR\_DUMMY\_IDLE}{1}{26}{{0}}%
\regfield{SPI\_USR\_MOSI\_HIGHPART}{1}{25}{{0}}%
\regfield{SPI\_USR\_MISO\_HIGHPART}{1}{24}{{0}}%
\regfield{(reserved)}{6}{18}{000000}%
\regfield{SPI\_USR\_HOLD\_POL}{1}{17}{{0}}%
\regfield{SPI\_SIO}{1}{16}{{0}}%
\regfield{SPI\_USR\_CONF\_NXT}{1}{15}{{0}}%
\regfield{SPI\_FWRITE\_OCT}{1}{14}{{0}}%
\regfield{SPI\_FWRITE\_QUAD}{1}{13}{{0}}%
\regfield{SPI\_FWRITE\_DUAL}{1}{12}{{0}}%
\regfield{SPI\_WR\_BYTE\_ORDER}{1}{11}{{0}}%
\regfield{SPI\_RD\_BYTE\_ORDER}{1}{10}{{0}}%
\regfield{SPI\_CK\_OUT\_EDGE}{1}{9}{{0}}%
\regfield{SPI\_RSCK\_I\_EDGE}{1}{8}{{0}}%
\regfield{SPI\_CS\_SETUP}{1}{7}{{1}}%
\regfield{SPI\_CS\_HOLD}{1}{6}{{1}}%
\regfield{SPI\_TSCK\_I\_EDGE}{1}{5}{{0}}%
\regfield{SPI\_OPI\_MODE}{1}{4}{{0}}%
\regfield{SPI\_QPI\_MODE}{1}{3}{{0}}%
\regfield{(reserved)}{2}{1}{00}%
\regfield{SPI\_DOUTDIN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDOUTDIN}\item [SPI\_DOUTDIN] Set the bit to enable full-duplex communication. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIQPIMODE}\item [SPI\_QPI\_MODE] Both for master mode and slave mode. 1: SPI controller is in QPI mode. 0: other modes. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIOPIMODE}\item [SPI\_OPI\_MODE] Just for master mode. 1: SPI controller is in OPI mode (all in 8-bit mode). 0: other modes. Can be configured in CONF state. (R/W)
\label{fielddesc:SPITSCKIEDGE}\item [SPI\_TSCK\_I\_EDGE] In slave mode, this bit can be used to change the polarity of tsck. 0: TSCK = SPI\_CK\_I. 1: TSCK = !SPI\_CK\_I. (R/W)
\label{fielddesc:SPICSHOLD}\item [SPI\_CS\_HOLD] Keep SPI CS low when SPI is in DONE phase. 1: enable. 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICSSETUP}\item [SPI\_CS\_SETUP] Enable SPI CS when SPI is in (PREP) prepare phase. 1: enable. 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIRSCKIEDGE}\item [SPI\_RSCK\_I\_EDGE] In slave mode, this bit can be used to change the polarity of rsck. 0: RSCK = !SPI\_CK\_I. 1: RSCK = SPI\_CK\_I. (R/W)
\label{fielddesc:SPICKOUTEDGE}\item [SPI\_CK\_OUT\_EDGE] This bit together with SPI\_DOUT\_MODE is used to set MOSI signal delay mode. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIRDBYTEORDER}\item [SPI\_RD\_BYTE\_ORDER] In read-data (MISO) phase, 1: big-endian, 0: little-endian. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIWRBYTEORDER}\item [SPI\_WR\_BYTE\_ORDER] In CMD (command), ADDR (address), and write-data (MOSI) phases, 1: big-endian, 0: litte-endian. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFWRITEDUAL}\item [SPI\_FWRITE\_DUAL] In write operations, read-data phase is in 2-bit mode. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFWRITEQUAD}\item [SPI\_FWRITE\_QUAD] In write operations, read-data phase is in 4-bit mode. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFWRITEOCT}\item [SPI\_FWRITE\_OCT] In write operations, read-data phase is in 8-bit mode. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRCONFNXT}\item [SPI\_USR\_CONF\_NXT] 1: Enable the DMA CONF phase of next seg-trans operation, which means seg-trans will continue. 0: The segmented-transfer will end after the current SPI segmented-transfer or this is not segmented-transfer mode. Can be configured in CONF state. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{SPI\_USER\_REG}{\hexprefix{}0018}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:SPISIO}\item [SPI\_SIO] Set the bit to enable 3-line half-duplex communication, where MOSI and MISO signals share the same pin. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRHOLDPOL}\item [SPI\_USR\_HOLD\_POL] This bit together with the hold bits is used to set the polarity of SPI hold line. 1: SPI will be held when SPI hold line is high. 0: SPI will be held when SPI hold line is low. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRMISOHIGHPART}\item [SPI\_USR\_MISO\_HIGHPART] In read-data phase, access only to high-part of the buffer SPI\_BUF8 \verb+~+ SPI\_BUF17. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRMOSIHIGHPART}\item [SPI\_USR\_MOSI\_HIGHPART] In write-data phase, access only to high-part of the buffer SPI\_BUF8 \verb+~+ SPI\_BUF17. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRDUMMYIDLE}\item [SPI\_USR\_DUMMY\_IDLE] When this bit is enabled, the SPI clock is disabled in DUMMY phase. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRMOSI}\item [SPI\_USR\_MOSI] This bit enables the write-data phase of an operation. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRMISO}\item [SPI\_USR\_MISO] This bit enables the read-data phase of an operation. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRDUMMY}\item [SPI\_USR\_DUMMY] This bit enables the DUMMY phase of an operation. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRADDR}\item [SPI\_USR\_ADDR] This bit enables the address phase of an operation. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRCOMMAND}\item [SPI\_USR\_COMMAND] This bit enables the command phase of an operation. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_USER1\_REG}{\hexprefix{}001C}\label{regdesc:SPIUSER1REG}
\regfield{SPI\_USR\_ADDR\_BITLEN}{5}{27}{{23}}%
\regfield{(reserved)}{19}{8}{0000000000000000000}%
\regfield{SPI\_USR\_DUMMY\_CYCLELEN}{8}{0}{{7}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIUSRDUMMYCYCLELEN}\item [SPI\_USR\_DUMMY\_CYCLELEN] The length in SPI\_CLK cycles of dummy phase. The register value shall be (cycle\_num-1). Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRADDRBITLEN}\item [SPI\_USR\_ADDR\_BITLEN] The length in bits of address phase. The register value shall be (bit\_num-1). Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_USER2\_REG}{\hexprefix{}0020}\label{regdesc:SPIUSER2REG}
\regfield{SPI\_USR\_COMMAND\_BITLEN}{4}{28}{{7}}%
\regfield{(reserved)}{12}{16}{000000000000}%
\regfield{SPI\_USR\_COMMAND\_VALUE}{16}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIUSRCOMMANDVALUE}\item [SPI\_USR\_COMMAND\_VALUE] The value of command. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRCOMMANDBITLEN}\item [SPI\_USR\_COMMAND\_BITLEN] The length in bits of command phase. The register value shall be (bit\_num-1). Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_MOSI\_DLEN\_REG}{\hexprefix{}0024}\label{regdesc:SPIMOSIDLENREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{SPI\_USR\_MOSI\_DBITLEN}{23}{0}{{\hexprefix{}0000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIUSRMOSIDBITLEN}\item [SPI\_USR\_MOSI\_DBITLEN] The length in bits of write-data phase. The register value shall be (bit\_num-1). Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_MISO\_DLEN\_REG}{\hexprefix{}0028}\label{regdesc:SPIMISODLENREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{SPI\_USR\_MISO\_DBITLEN}{23}{0}{{\hexprefix{}0000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIUSRMISODBITLEN}\item [SPI\_USR\_MISO\_DBITLEN] The length in bits of read-data phase. The register value shall be (bit\_num-1). Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_CTRL\_REG}{\hexprefix{}0008}\label{regdesc:SPICTRLREG}
\regfield{(reserved)}{5}{27}{00000}%
\regfield{SPI\_WR\_BIT\_ORDER}{1}{26}{{0}}%
\regfield{SPI\_RD\_BIT\_ORDER}{1}{25}{{0}}%
\regfield{(reserved)}{3}{22}{000}%
\regfield{SPI\_WP\_REG}{1}{21}{{1}}%
\regfield{(reserved)}{1}{20}{0}%
\regfield{SPI\_D\_POL}{1}{19}{{1}}%
\regfield{SPI\_Q\_POL}{1}{18}{{1}}%
\regfield{(reserved)}{1}{17}{0}%
\regfield{SPI\_FREAD\_OCT}{1}{16}{{0}}%
\regfield{SPI\_FREAD\_QUAD}{1}{15}{{0}}%
\regfield{SPI\_FREAD\_DUAL}{1}{14}{{0}}%
\regfield{(reserved)}{3}{11}{000}%
\regfield{SPI\_FCMD\_OCT}{1}{10}{{0}}%
\regfield{SPI\_FCMD\_QUAD}{1}{9}{{0}}%
\regfield{SPI\_FCMD\_DUAL}{1}{8}{{0}}%
\regfield{SPI\_FADDR\_OCT}{1}{7}{{0}}%
\regfield{SPI\_FADDR\_QUAD}{1}{6}{{0}}%
\regfield{SPI\_FADDR\_DUAL}{1}{5}{{0}}%
\regfield{(reserved)}{1}{4}{0}%
\regfield{SPI\_DUMMY\_OUT}{1}{3}{{0}}%
\regfield{(reserved)}{3}{0}{000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDUMMYOUT}\item [SPI\_DUMMY\_OUT] The signal level output by the SPI controller in the dummy phase. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFADDRDUAL}\item [SPI\_FADDR\_DUAL] Apply 2-bit mode during address phase. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFADDRQUAD}\item [SPI\_FADDR\_QUAD] Apply 4-bit mode during address phase. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFADDROCT}\item [SPI\_FADDR\_OCT] Apply 8-bit mode during address phase. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFCMDDUAL}\item [SPI\_FCMD\_DUAL] Apply 2-bit mode during command phase. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFCMDQUAD}\item [SPI\_FCMD\_QUAD] Apply 4-bit mode during command phase. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFCMDOCT}\item [SPI\_FCMD\_OCT] Apply 8-bit mode during command phase. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFREADDUAL}\item [SPI\_FREAD\_DUAL] In the read operations, read-data phase is in 2-bit mode. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFREADQUAD}\item [SPI\_FREAD\_QUAD] In the read operations, read-data phase is in 4-bit mode. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFREADOCT}\item [SPI\_FREAD\_OCT] In the read operations, read-data phase is in 8-bit mode. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIQPOL}\item [SPI\_Q\_POL] The bit is used to set MISO line polarity. 1: high, 0: low. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDPOL}\item [SPI\_D\_POL] The bit is used to set MOSI line polarity. 1: high, 0: low. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIWPREG}\item [SPI\_WP\_REG] Write protect signal output when SPI is idle. 1: output high, 0: output low. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIRDBITORDER}\item [SPI\_RD\_BIT\_ORDER] In read-data (MISO) phase, 1: LSB first, 0: MSB first. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIWRBITORDER}\item [SPI\_WR\_BIT\_ORDER] In command, address, and write-data (MOSI) phases, 1: LSB first, 0: MSB first. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_CTRL1\_REG}{\hexprefix{}000C}\label{regdesc:SPICTRL1REG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{SPI\_CS\_HOLD\_DELAY}{6}{14}{{\hexprefix{}1}}%
\regfield{(reserved)}{9}{5}{000000000}%
\regfield{SPI\_W16\_17\_WR\_ENA}{1}{4}{{1}}%
\regfield{SPI\_RSCK\_DATA\_OUT}{1}{3}{{0}}%
\regfield{SPI\_CLK\_MODE\_13}{1}{2}{{0}}%
\regfield{SPI\_CLK\_MODE}{2}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPICLKMODE}\item [SPI\_CLK\_MODE] SPI clock mode bits. 0: SPI clock is off when CS inactive. 1: SPI clock is delayed one cycle after CS inactive. 2: SPI clock is delayed two cycles after CS inactive. 3: SPI clock is always on. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICLKMODE13}\item [SPI\_CLK\_MODE\_13] {CPOL, CPHA}, 1: support SPI CLK mode 1 and 3, and output data B[0]/B[7] at first edge. 0: support SPI CLK mode 0 and 2, and output data B[1]/B[6] at first edge. (R/W)
\label{fielddesc:SPIRSCKDATAOUT}\item [SPI\_RSCK\_DATA\_OUT] Save half a cycle when tsck is the same as rsck. 1: output data at rsck positive edge. 0: output data at tsck positive edge. (R/W)
\label{fielddesc:SPIW1617WRENA}\item [SPI\_W16\_17\_WR\_ENA] 1: SPI\_BUF16 \verb+~+ SPI\_BUF17 can be written. 0: SPI\_BUF16 \verb+~+ SPI\_BUF17 can not  be written. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICSHOLDDELAY}\item [SPI\_CS\_HOLD\_DELAY] SPI CS signal is delayed by SPI clock cycles. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_CTRL2\_REG}{\hexprefix{}0010}\label{regdesc:SPICTRL2REG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{SPI\_CS\_DELAY\_NUM}{2}{29}{{\hexprefix{}0}}%
\regfield{SPI\_CS\_DELAY\_MODE}{3}{26}{{\hexprefix{}0}}%
\regfield{SPI\_CS\_HOLD\_TIME}{13}{13}{{\hexprefix{}01}}%
\regfield{SPI\_CS\_SETUP\_TIME}{13}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPICSSETUPTIME}\item [SPI\_CS\_SETUP\_TIME] (cycles+1) of prepare phase by SPI clock. These bits are used together with SPI\_CS\_SETUP bit. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICSHOLDTIME}\item [SPI\_CS\_HOLD\_TIME] Delay cycles of CS pin by SPI clock. These bits are used together with SPI\_CS\_HOLD bit. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICSDELAYMODE}\item [SPI\_CS\_DELAY\_MODE] SPI\_CS signal is delayed by SPI\_CLK. 0: zero cycle. 1: if SPI\_CK\_OUT\_EDGE or SPI\_CK\_IDLE\_EDGE is set to 1, SPI\_CLK will be delayed by half cycle, else delayed by one cycle. 2: if SPI\_CK\_OUT\_EDGE or SPI\_CK\_IDLE\_EDGE is set to 1, SPI\_CLK will be delayed by one cycle, else delayed by half cycle. 3: delay one cycle. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICSDELAYNUM}\item [SPI\_CS\_DELAY\_NUM] SPI\_CS signal is delayed by system clock cycles. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_CLOCK\_REG}{\hexprefix{}0014}\label{regdesc:SPICLOCKREG}
\regfield{SPI\_CLK\_EQU\_SYSCLK}{1}{31}{{1}}%
\regfield{SPI\_CLKDIV\_PRE}{13}{18}{{0}}%
\regfield{SPI\_CLKCNT\_N}{6}{12}{{\hexprefix{}3}}%
\regfield{SPI\_CLKCNT\_H}{6}{6}{{\hexprefix{}1}}%
\regfield{SPI\_CLKCNT\_L}{6}{0}{{\hexprefix{}3}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPICLKCNTL}\item [SPI\_CLKCNT\_L] In the master mode it must be equal to SPI\_CLKCNT\_N. In the slave mode it must be 0. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICLKCNTH}\item [SPI\_CLKCNT\_H] In the master mode it must be floor((SPI\_CLKCNT\_N+1)/2-1). floor() here is to down round a number, floor(2.2) = 2. In the slave mode it must be 0. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICLKCNTN}\item [SPI\_CLKCNT\_N] In the master mode it is the divider of SPI\_CLK. So SPI\_CLK frequency is $f_{\textrm{apb}}$/(SPI\_CLKDIV\_PRE+1)/(SPI\_CLKCNT\_N+1). Can be configured in CONF state. (R/W)
\label{fielddesc:SPICLKDIVPRE}\item [SPI\_CLKDIV\_PRE] In the master mode it is pre-divider of SPI\_CLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICLKEQUSYSCLK}\item [SPI\_CLK\_EQU\_SYSCLK] In the master mode, 1: SPI\_CLK is equal to APB clock. 0: SPI\_CLK is obtained by dividing from APB clock. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_MISC\_REG}{\hexprefix{}002C}\label{regdesc:SPIMISCREG}
\regfield{SPI\_QUAD\_DIN\_PIN\_SWAP}{1}{31}{{0}}%
\regfield{SPI\_CS\_KEEP\_ACTIVE}{1}{30}{{0}}%
\regfield{SPI\_CK\_IDLE\_EDGE}{1}{29}{{0}}%
\regfield{(reserved)}{2}{27}{00}%
\regfield{SPI\_CD\_IDLE\_EDGE}{1}{26}{{0}}%
\regfield{SPI\_CD\_CMD\_SET}{1}{25}{{0}}%
\regfield{SPI\_DQS\_IDLE\_EDGE}{1}{24}{{0}}%
\regfield{SPI\_SLAVE\_CS\_POL}{1}{23}{{0}}%
\regfield{SPI\_CD\_ADDR\_SET}{1}{22}{{0}}%
\regfield{SPI\_CD\_DUMMY\_SET}{1}{21}{{0}}%
\regfield{SPI\_CD\_DATA\_SET}{1}{20}{{0}}%
\regfield{SPI\_CMD\_DTR\_EN}{1}{19}{{0}}%
\regfield{SPI\_ADDR\_DTR\_EN}{1}{18}{{0}}%
\regfield{SPI\_DATA\_DTR\_EN}{1}{17}{{0}}%
\regfield{SPI\_CLK\_DATA\_DTR\_EN}{1}{16}{{0}}%
\regfield{(reserved)}{3}{13}{000}%
\regfield{SPI\_MASTER\_CS\_POL}{6}{7}{{0}}%
\regfield{SPI\_CK\_DIS}{1}{6}{{0}}%
\regfield{SPI\_CS5\_DIS}{1}{5}{{1}}%
\regfield{SPI\_CS4\_DIS}{1}{4}{{1}}%
\regfield{SPI\_CS3\_DIS}{1}{3}{{1}}%
\regfield{SPI\_CS2\_DIS}{1}{2}{{1}}%
\regfield{SPI\_CS1\_DIS}{1}{1}{{1}}%
\regfield{SPI\_CS0\_DIS}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPICS0DIS}\item [SPI\_CS0\_DIS] SPI CS0 pin disable bit. 1: disable CS0, 0: SPI\_CS0 signal is from/to CS0 pin. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICS1DIS}\item [SPI\_CS1\_DIS] SPI CS1 pin disable bit. 1: disable CS1, 0: SPI\_CS1 signal is from/to CS1 pin. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICS2DIS}\item [SPI\_CS2\_DIS] SPI CS2 pin disable bit. 1: disable CS2, 0: SPI\_CS2 signal is from/to CS2 pin. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICS3DIS}\item [SPI\_CS3\_DIS] SPI CS3 pin disable bit. 1: disable CS3, 0: SPI\_CS3 signal is from/to CS3 pin. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICS4DIS}\item [SPI\_CS4\_DIS] SPI CS4 pin disable bit. 1: disable CS4, 0: SPI\_CS4 signal is from/to CS4 pin. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICS5DIS}\item [SPI\_CS5\_DIS] SPI CS5 pin disable bit. 1: disable CS5, 0: SPI\_CS5 signal is from/to CS5 pin. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICKDIS}\item [SPI\_CK\_DIS] 1: SPI CLK output disable, 0: SPI CLK output enable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIMASTERCSPOL}\item [SPI\_MASTER\_CS\_POL] In master mode, the bits are the polarity of SPI CS line. The value is equivalent to SPI\_CS \^{} SPI\_MASTER\_CS\_POL. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICLKDATADTREN}\item [SPI\_CLK\_DATA\_DTR\_EN] 1: SPI master DTR mode is applied to SPI CLK, data and SPI\_DQS. 0: SPI master DTR mode is only applied to SPI\_DQS. This bit should be used with bit 17/18/19. (R/W)
\label{fielddesc:SPIDATADTREN}\item [SPI\_DATA\_DTR\_EN] 1: SPI CLK and data of SPI\_DOUT and SPI\_DIN states are in DTR mode, including master 1/2/4/8-bit mode. 0: SPI CLK and DATA of SPI\_DOUT and SPI\_DIN states are in STR mode. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIADDRDTREN}\item [SPI\_ADDR\_DTR\_EN] 1: SPI CLK and data of SPI\_SEND\_ADDR state are in DTR mode, including master 1/2/4/8-bit mode. 0:  SPI CLK and data of SPI\_SEND\_ADDR state are in STR mode. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICMDDTREN}\item [SPI\_CMD\_DTR\_EN] 1: SPI CLK and data of SPI\_SEND\_CMD state are in DTR mode, including master 1/2/4/8-bit mode. 0: SPI CLK and data of SPI\_SEND\_CMD state are in STR mode. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICDDATASET}\item [SPI\_CD\_DATA\_SET] 1: SPI\_CD = !SPI\_CD\_IDLE\_EDGE when SPI\_ST[3:0] is in SPI\_DOUT or SPI\_DIN state. 0: SPI\_CD = SPI\_CD\_IDLE\_EDGE. Can be configured in CONF state. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{SPI\_MISC\_REG}{\hexprefix{}002C}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:SPICDDUMMYSET}\item [SPI\_CD\_DUMMY\_SET] 1: SPI\_CD = !SPI\_CD\_IDLE\_EDGE when SPI\_ST[3:0] is in SPI\_DUMMY state. 0: SPI\_CD = SPI\_CD\_IDLE\_EDGE. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICDADDRSET}\item [SPI\_CD\_ADDR\_SET] 1: SPI\_CD = !SPI\_CD\_IDLE\_EDGE when SPI\_ST[3:0] is in SPI\_SEND\_ADDR state. 0: SPI\_CD = SPI\_CD\_IDLE\_EDGE. Can be configured in CONF state. (R/W)
\label{fielddesc:SPISLAVECSPOL}\item [SPI\_SLAVE\_CS\_POL] Select polarity of SPI slave input CS. 1: inverted, 0: not change. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDQSIDLEEDGE}\item [SPI\_DQS\_IDLE\_EDGE] The default value of SPI\_DQS. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICDCMDSET}\item [SPI\_CD\_CMD\_SET] 1: SPI\_CD = !SPI\_CD\_IDLE\_EDGE when SPI\_ST[3:0] is in SPI\_SEND\_CMD state. 0: SPI\_CD = SPI\_CD\_IDLE\_EDGE. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICDIDLEEDGE}\item [SPI\_CD\_IDLE\_EDGE] The default value of SPI\_CD. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICKIDLEEDGE}\item [SPI\_CK\_IDLE\_EDGE] 1: SPI CLK line is high when idle. 0: SPI CLK line is low when idle. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICSKEEPACTIVE}\item [SPI\_CS\_KEEP\_ACTIVE] Set this bit to keep the SPI CS line low. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIQUADDINPINSWAP}\item [SPI\_QUAD\_DIN\_PIN\_SWAP] 1: SPI quad input swap enable. 0: SPI quad input swap disable. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_FSM\_REG}{\hexprefix{}0044}\label{regdesc:SPIFSMREG}
\regfield{SPI\_MST\_DMA\_RD\_BYTELEN}{20}{12}{{\hexprefix{}000}}%
\regfield{(reserved)}{8}{4}{00000000}%
\regfield{SPI\_ST}{4}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIST}\item [SPI\_ST] The status of SPI state machine. 0: idle state, 1: preparation state, 2: send command state, 3: send data state, 4: read data state, 5: write data state, 6: wait state, 7: done state. (RO)
\label{fielddesc:SPIMSTDMARDBYTELEN}\item [SPI\_MST\_DMA\_RD\_BYTELEN] Define the master DMA read byte length in segmented-configure-transfer mode or in other modes. Invalid when SPI\_RX\_EOF\_EN is 0. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_HOLD\_REG}{\hexprefix{}0048}\label{regdesc:SPIHOLDREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{SPI\_DMA\_SEG\_TRANS\_DONE}{1}{7}{{0}}%
\regfield{SPI\_HOLD\_OUT\_TIME}{3}{4}{{0}}%
\regfield{SPI\_HOLD\_OUT\_EN}{1}{3}{{0}}%
\regfield{SPI\_HOLD\_VAL\_REG}{1}{2}{{0}}%
\regfield{(reserved)}{2}{0}{00}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIHOLDVALREG}\item [SPI\_HOLD\_VAL\_REG] SPI output hold value, which should be used with SPI\_HOLD\_OUT\_EN. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIHOLDOUTEN}\item [SPI\_HOLD\_OUT\_EN] Enable set SPI output hold value to SPI\_HOLD\_REG. It can be used to hold SPI state machine with SPI\_EXT\_HOLD\_EN and other user hold signals. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIHOLDOUTTIME}\item [SPI\_HOLD\_OUT\_TIME] Set the hold cycles of output SPI\_HOLD signal when SPI\_HOLD\_OUT\_EN is enabled. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDMASEGTRANSDONE}\item [SPI\_DMA\_SEG\_TRANS\_DONE] 1: SPI master DMA full-duplex/half-duplex segmented-configure-transfer ends or slave half-duplex segmented-transfer ends. And data has been pushed to corresponding memory. 0: segmented-transfer or segmented-configure-transfer is not ended or not occurred. Can not be changed by CONF\_buf. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_SLAVE\_REG}{\hexprefix{}0030}\label{regdesc:SPISLAVEREG}
\regfield{SPI\_SOFT\_RESET}{1}{31}{{0}}%
\regfield{SPI\_SLAVE\_MODE}{1}{30}{{0}}%
\regfield{SPI\_TRANS\_DONE\_AUTO\_CLR\_EN}{1}{29}{{0}}%
\regfield{(reserved)}{2}{27}{00}%
\regfield{SPI\_TRANS\_CNT}{4}{23}{{0}}%
\regfield{(reserved)}{11}{12}{00000000000}%
\regfield{SPI\_SEG\_MAGIC\_ERR\_INT\_EN}{1}{11}{{0}}%
\regfield{SPI\_INT\_DMA\_SEG\_TRANS\_EN}{1}{10}{{0}}%
\regfield{SPI\_INT\_TRANS\_DONE\_EN}{1}{9}{{1}}%
\regfield{SPI\_INT\_WR\_DMA\_DONE\_EN}{1}{8}{{0}}%
\regfield{SPI\_INT\_RD\_DMA\_DONE\_EN}{1}{7}{{0}}%
\regfield{SPI\_INT\_WR\_BUF\_DONE\_EN}{1}{6}{{0}}%
\regfield{SPI\_INT\_RD\_BUF\_DONE\_EN}{1}{5}{{0}}%
\regfield{SPI\_TRANS\_DONE}{1}{4}{{0}}%
\regfield{(reserved)}{4}{0}{0000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPITRANSDONE}\item [SPI\_TRANS\_DONE] The interrupt raw bit for the completion of any operation in both the master mode and the slave mode. Can not be changed by CONF\_buf. (R/W)
\label{fielddesc:SPIINTRDBUFDONEEN}\item [SPI\_INT\_RD\_BUF\_DONE\_EN] SPI\_SLV\_RD\_BUF\_DONE interrupt enable. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIINTWRBUFDONEEN}\item [SPI\_INT\_WR\_BUF\_DONE\_EN] SPI\_SLV\_WR\_BUF\_DONE interrupt enable. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIINTRDDMADONEEN}\item [SPI\_INT\_RD\_DMA\_DONE\_EN] SPI\_SLV\_RD\_DMA\_DONE interrupt enable. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIINTWRDMADONEEN}\item [SPI\_INT\_WR\_DMA\_DONE\_EN] SPI\_SLV\_WR\_DMA\_DONE interrupt enable. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIINTTRANSDONEEN}\item [SPI\_INT\_TRANS\_DONE\_EN] SPI\_TRANS\_DONE interrupt enable. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIINTDMASEGTRANSEN}\item [SPI\_INT\_DMA\_SEG\_TRANS\_EN] SPI\_DMA\_SEG\_TRANS\_DONE interrupt enable. 1: enable, 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPISEGMAGICERRINTEN}\item [SPI\_SEG\_MAGIC\_ERR\_INT\_EN] 1: Enable magic value error interrupt. 0: Others. Can be configured in CONF state. (R/W)
\label{fielddesc:SPITRANSCNT}\item [SPI\_TRANS\_CNT] The operations counter in both the master mode and the slave mode. (RO)
\label{fielddesc:SPITRANSDONEAUTOCLREN}\item [SPI\_TRANS\_DONE\_AUTO\_CLR\_EN] SPI\_TRANS\_DONE auto clear enable, clear it 3 APB cycles after the positive edge of SPI\_TRANS\_DONE. 0: disable. 1: enable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPISLAVEMODE}\item [SPI\_SLAVE\_MODE] Set SPI work mode. 1: slave mode, 0: master mode. (R/W)
\label{fielddesc:SPISOFTRESET}\item [SPI\_SOFT\_RESET] Software reset enable, to reset the SPI clock line, CS line and data lines. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_SLAVE1\_REG}{\hexprefix{}0034}\label{regdesc:SPISLAVE1REG}
\regfield{SPI\_SLV\_LAST\_ADDR}{8}{24}{{0}}%
\regfield{SPI\_SLV\_LAST\_COMMAND}{8}{16}{{0}}%
\regfield{SPI\_SLV\_WR\_DMA\_DONE}{1}{15}{{0}}%
\regfield{SPI\_SLV\_CMD\_ERR}{1}{14}{{0}}%
\regfield{SPI\_SLV\_ADDR\_ERR}{1}{13}{{0}}%
\regfield{SPI\_SLV\_NO\_QPI\_EN}{1}{12}{{0}}%
\regfield{SPI\_SLV\_CMD\_ERR\_CLR}{1}{11}{{0}}%
\regfield{SPI\_SLV\_ADDR\_ERR\_CLR}{1}{10}{{0}}%
\regfield{(reserved)}{10}{0}{0000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPISLVADDRERRCLR}\item [SPI\_SLV\_ADDR\_ERR\_CLR] 1: Clear SPI\_SLV\_ADDR\_ERR. 0: not valid. Can be changed by CONF\_buf. (R/W)
\label{fielddesc:SPISLVCMDERRCLR}\item [SPI\_SLV\_CMD\_ERR\_CLR] 1: Clear SPI\_SLV\_CMD\_ERR. 0: not valid. Can be changed by CONF\_buf. (R/W)
\label{fielddesc:SPISLVNOQPIEN}\item [SPI\_SLV\_NO\_QPI\_EN] 1: SPI slave QPI mode is not supported. 0: SPI slave QPI mode is supported. (R/W)
\label{fielddesc:SPISLVADDRERR}\item [SPI\_SLV\_ADDR\_ERR] 1: The address value of the last SPI transfer is not supported by SPI slave. 0: The address value is supported or no address value is received. (RO)
\label{fielddesc:SPISLVCMDERR}\item [SPI\_SLV\_CMD\_ERR] 1: The command value of the last SPI transfer is not supported by SPI slave. 0: The command value is supported or no command value is received. (RO)
\label{fielddesc:SPISLVWRDMADONE}\item [SPI\_SLV\_WR\_DMA\_DONE] The interrupt raw bit for the completion of DMA write operation in slave mode. Can not be changed by CONF\_buf. (R/W)
\label{fielddesc:SPISLVLASTCOMMAND}\item [SPI\_SLV\_LAST\_COMMAND] In slave mode, it is the value of command. (R/W)
\label{fielddesc:SPISLVLASTADDR}\item [SPI\_SLV\_LAST\_ADDR] In slave mode, it is the value of address. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_SLV\_WRBUF\_DLEN\_REG}{\hexprefix{}0038}\label{regdesc:SPISLVWRBUFDLENREG}
\regfield{SPI\_CONF\_BASE\_BITLEN}{7}{25}{{108}}%
\regfield{SPI\_SLV\_WR\_BUF\_DONE}{1}{24}{{0}}%
\regfield{(reserved)}{24}{0}{000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPISLVWRBUFDONE}\item [SPI\_SLV\_WR\_BUF\_DONE] The interrupt raw bit for the completion of write-buffer operation in slave mode. Can not be changed by CONF\_buf. (R/W)
\label{fielddesc:SPICONFBASEBITLEN}\item [SPI\_CONF\_BASE\_BITLEN] The basic SPI\_CLK cycles of CONF state. The real cycle length of CONF state, if SPI\_USR\_CONF is enabled, is SPI\_CONF\_BASE\_BITLEN[6:0] + SPI\_CONF\_BITLEN[23:0]. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_SLV\_RDBUF\_DLEN\_REG}{\hexprefix{}003C}\label{regdesc:SPISLVRDBUFDLENREG}
\regfield{(reserved)}{6}{26}{000000}%
\regfield{SPI\_SEG\_MAGIC\_ERR}{1}{25}{{0}}%
\regfield{SPI\_SLV\_RD\_BUF\_DONE}{1}{24}{{0}}%
\regfield{(reserved)}{4}{20}{0000}%
\regfield{SPI\_SLV\_DMA\_RD\_BYTELEN}{20}{0}{{\hexprefix{}000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPISLVDMARDBYTELEN}\item [SPI\_SLV\_DMA\_RD\_BYTELEN] In slave mode, it is the length in bytes for read operations. The register value shall be byte\_num. (R/W)
\label{fielddesc:SPISLVRDBUFDONE}\item [SPI\_SLV\_RD\_BUF\_DONE] The interrupt raw bit for the completion of read-buffer operation in slave mode. Can not be changed by CONF\_buf. (R/W)
\label{fielddesc:SPISEGMAGICERR}\item [SPI\_SEG\_MAGIC\_ERR] 1: The recent magic value in CONF buffer is not right in master DMA segmented-configure-transfer mode. 0: others. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_SLV\_RD\_BYTE\_REG}{\hexprefix{}0040}\label{regdesc:SPISLVRDBYTEREG}
\regfield{SPI\_USR\_CONF}{1}{31}{{0}}%
\regfield{SPI\_SLV\_RD\_DMA\_DONE}{1}{30}{{0}}%
\regfield{(reserved)}{2}{28}{00}%
\regfield{SPI\_DMA\_SEG\_MAGIC\_VALUE}{4}{24}{{10}}%
\regfield{SPI\_SLV\_WRBUF\_BYTELEN\_EN}{1}{23}{{0}}%
\regfield{SPI\_SLV\_RDBUF\_BYTELEN\_EN}{1}{22}{{0}}%
\regfield{SPI\_SLV\_WRDMA\_BYTELEN\_EN}{1}{21}{{0}}%
\regfield{SPI\_SLV\_RDDMA\_BYTELEN\_EN}{1}{20}{{0}}%
\regfield{SPI\_SLV\_DATA\_BYTELEN}{20}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPISLVDATABYTELEN}\item [SPI\_SLV\_DATA\_BYTELEN] The full-duplex or half-duplex data byte length of the last SPI transfer in slave mode. In half-duplex mode, this value is controlled by bits [23:20]. (R/W)
\label{fielddesc:SPISLVRDDMABYTELENEN}\item [SPI\_SLV\_RDDMA\_BYTELEN\_EN] 1: SPI\_SLV\_DATA\_BYTELEN stores data byte length of master-read-slave data length in DMA controlled mode (Rd\_DMA). 0: others (R/W)
\label{fielddesc:SPISLVWRDMABYTELENEN}\item [SPI\_SLV\_WRDMA\_BYTELEN\_EN] 1: SPI\_SLV\_DATA\_BYTELEN stores data byte length of master-write-to-slave data length in DMA controlled mode (Wr\_DMA). 0: others (R/W)
\label{fielddesc:SPISLVRDBUFBYTELENEN}\item [SPI\_SLV\_RDBUF\_BYTELEN\_EN] 1: SPI\_SLV\_DATA\_BYTELEN stores data byte length of master-read-slave data length in CPU controlled mode (Rd\_BUF). 0: others (R/W)
\label{fielddesc:SPISLVWRBUFBYTELENEN}\item [SPI\_SLV\_WRBUF\_BYTELEN\_EN] 1: SPI\_SLV\_DATA\_BYTELEN stores data byte length of master-write-to-slave data length in CPU controlled mode (Wr\_BUF). 0: others (R/W)
\label{fielddesc:SPIDMASEGMAGICVALUE}\item [SPI\_DMA\_SEG\_MAGIC\_VALUE] The magic value of BM table in master DMA segmented-configure-transfer. (R/W)
\label{fielddesc:SPISLVRDDMADONE}\item [SPI\_SLV\_RD\_DMA\_DONE] The interrupt raw bit for the completion of Rd\_DMA operation in slave mode. Can not be changed by CONF\_buf. (R/W)
\label{fielddesc:SPIUSRCONF}\item [SPI\_USR\_CONF] 1: Enable the DMA CONF phase of current segmented-configure-transfer operation, which means segmented-configure-transfer will start. 0: This is not segmented-configure-transfer mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_CONF\_REG}{\hexprefix{}004C}\label{regdesc:SPIDMACONFREG}
\regfield{(reserved)}{3}{29}{000}%
\regfield{SPI\_DMA\_SEG\_TRANS\_CLR}{1}{28}{{0}}%
\regfield{SPI\_EXT\_MEM\_BK\_SIZE}{2}{26}{{0}}%
\regfield{(reserved)}{2}{24}{00}%
\regfield{SPI\_DMA\_OUTFIFO\_EMPTY\_CLR}{1}{23}{{0}}%
\regfield{SPI\_DMA\_INFIFO\_FULL\_CLR}{1}{22}{{0}}%
\regfield{SPI\_RX\_EOF\_EN}{1}{21}{{0}}%
\regfield{SPI\_SLV\_TX\_SEG\_TRANS\_CLR\_EN}{1}{20}{{0}}%
\regfield{SPI\_SLV\_RX\_SEG\_TRANS\_CLR\_EN}{1}{19}{{0}}%
\regfield{SPI\_DMA\_SLV\_SEG\_TRANS\_EN}{1}{18}{{0}}%
\regfield{SPI\_SLV\_LAST\_SEG\_POP\_CLR}{1}{17}{{0}}%
\regfield{SPI\_DMA\_CONTINUE}{1}{16}{{0}}%
\regfield{SPI\_DMA\_TX\_STOP}{1}{15}{{0}}%
\regfield{SPI\_DMA\_RX\_STOP}{1}{14}{{0}}%
\regfield{SPI\_MEM\_TRANS\_EN}{1}{13}{{0}}%
\regfield{SPI\_OUT\_DATA\_BURST\_EN}{1}{12}{{0}}%
\regfield{SPI\_INDSCR\_BURST\_EN}{1}{11}{{0}}%
\regfield{SPI\_OUTDSCR\_BURST\_EN}{1}{10}{{0}}%
\regfield{SPI\_OUT\_EOF\_MODE}{1}{9}{{1}}%
\regfield{(reserved)}{3}{6}{000}%
\regfield{SPI\_AHBM\_RST}{1}{5}{{0}}%
\regfield{SPI\_AHBM\_FIFO\_RST}{1}{4}{{0}}%
\regfield{SPI\_OUT\_RST}{1}{3}{{0}}%
\regfield{SPI\_IN\_RST}{1}{2}{{0}}%
\regfield{(reserved)}{2}{0}{00}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIINRST}\item [SPI\_IN\_RST] The bit is used to reset in\_DMA FSM and in\_data FIFO pointer. (R/W)
\label{fielddesc:SPIOUTRST}\item [SPI\_OUT\_RST] The bit is used to reset out\_DMA FSM and out\_data FIFO pointer. (R/W)
\label{fielddesc:SPIAHBMFIFORST}\item [SPI\_AHBM\_FIFO\_RST] Reset SPI DMA AHB master FIFO pointer. (R/W)
\label{fielddesc:SPIAHBMRST}\item [SPI\_AHBM\_RST] Reset SPI DMA AHB master. (R/W)
\label{fielddesc:SPIOUTEOFMODE}\item [SPI\_OUT\_EOF\_MODE] out\_EOF flag generation mode. 1: when DMA pops all data from FIFO. 0: when AHB pushes all data to FIFO. (R/W)
\label{fielddesc:SPIOUTDSCRBURSTEN}\item [SPI\_OUTDSCR\_BURST\_EN] Read descriptor uses burst mode when read data from memory. (R/W)
\label{fielddesc:SPIINDSCRBURSTEN}\item [SPI\_INDSCR\_BURST\_EN] Read descriptor uses burst mode when write data to memory. (R/W)
\label{fielddesc:SPIOUTDATABURSTEN}\item [SPI\_OUT\_DATA\_BURST\_EN] SPI DMA reads data from memory in burst mode. (R/W)
\label{fielddesc:SPIMEMTRANSEN}\item [SPI\_MEM\_TRANS\_EN] 1: Internal memory data transfer enable bit. Send SPI DMA RX buffer data to SPI DMA TX buffer. 0: Disable this function. (R/W)
\label{fielddesc:SPIDMARXSTOP}\item [SPI\_DMA\_RX\_STOP] SPI DMA read data stops when in continuous tx/rx mode. (R/W)
\label{fielddesc:SPIDMATXSTOP}\item [SPI\_DMA\_TX\_STOP] SPI DMA write data stops when in continuous tx/rx mode. (R/W)
\label{fielddesc:SPIDMACONTINUE}\item [SPI\_DMA\_CONTINUE] SPI DMA continues sending/receiving data. (R/W)
\label{fielddesc:SPISLVLASTSEGPOPCLR}\item [SPI\_SLV\_LAST\_SEG\_POP\_CLR] Before slave segmented-transfer starts, set first and then clear this bit, to clear the data not used in last transfer. (R/W)
\label{fielddesc:SPIDMASLVSEGTRANSEN}\item [SPI\_DMA\_SLV\_SEG\_TRANS\_EN] Enable DMA segment transfer in SPI DMA half slave mode. 1: enable. 0: disable. (R/W)
\label{fielddesc:SPISLVRXSEGTRANSCLREN}\item [SPI\_SLV\_RX\_SEG\_TRANS\_CLR\_EN] In DMA-controlled half-duplex slave transfer, if the size of DMA RX buffer is smaller than the size of the received data, 1: the data in next transfer will not be received; 0: the transferred data this time will not be received, but in the next transfer, if the size of DMA RX buffer is not 0, the following transferred data will be received, otherwise not. (R/W)
\label{fielddesc:SPISLVTXSEGTRANSCLREN}\item [SPI\_SLV\_TX\_SEG\_TRANS\_CLR\_EN]  In DMA-controlled half-duplex slave transfer, if the size of DMA TX buffer is smaller than the size of the transferred data, 1: the data in next transfer will not be updated, i.e. the old data is transferred repeatedly; 0: the data in this transfer will not be updated. But in next transfer, if new data is filled in DMA TX FIFO, new data will be transferred, otherwise not. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{SPI\_DMA\_CONF\_REG}{\hexprefix{}004C}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\label{fielddesc:SPIRXEOFEN}\item [SPI\_RX\_EOF\_EN] 1: SPI\_IN\_SUC\_EOF\_INT\_RAW is set when the number of DMA pushed data bytes is equal to the value of SPI\_SLV\_DMA\_RD\_BYTELEN[19:0]/ SPI\_MST\_DMA\_RD\_BYTELEN[19:0] in SPI DMA transition. 0: SPI\_IN\_SUC\_EOF\_INT\_RAW is set by SPI\_TRANS\_DONE in non-segment-transfer or SPI\_DMA\_SEG\_TRANS\_DONE in segment-transfer. (R/W)
\label{fielddesc:SPIDMAINFIFOFULLCLR}\item [SPI\_DMA\_INFIFO\_FULL\_CLR]
In DMA-controlled half-duplex slave transfer, if the bit SPI\_SLV\_RX\_SEG\_TRANS\_CLR\_EN is set and the size of DMA RX buffer is smaller than the size of the transferred data, the bit SPI\_DMA\_INFIFO\_FULL\_CLR should be set first and then cleared, to avoid affecting next transfer. (R/W)
\label{fielddesc:SPIDMAOUTFIFOEMPTYCLR}\item [SPI\_DMA\_OUTFIFO\_EMPTY\_CLR]
In DMA-controlled half-duplex slave transfer, if the bit SPI\_SLV\_TX\_SEG\_TRANS\_CLR\_EN is set and the size of DMA TX buffer is smaller than the size of the transferred data, this bit SPI\_DMA\_OUTFIFO\_EMPTY\_CLR should be set first and then cleared, to avoid affecting next transfer. (R/W)
\label{fielddesc:SPIEXTMEMBKSIZE}\item [SPI\_EXT\_MEM\_BK\_SIZE] Select the external memory block size. (R/W)
\label{fielddesc:SPIDMASEGTRANSCLR}\item [SPI\_DMA\_SEG\_TRANS\_CLR] 1: End slave segment-transfer, which acts as \hexprefix{}05 command. 2 or more: end segment-transfer signals will induce error in DMA RX. 0: others. This bit will be cleared in 1 APB CLK cycle by hardware. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_OUT\_LINK\_REG}{\hexprefix{}0050}\label{regdesc:SPIDMAOUTLINKREG}
\regfield{SPI\_DMA\_TX\_ENA}{1}{31}{{0}}%
\regfield{SPI\_OUTLINK\_RESTART}{1}{30}{{0}}%
\regfield{SPI\_OUTLINK\_START}{1}{29}{{0}}%
\regfield{SPI\_OUTLINK\_STOP}{1}{28}{{0}}%
\regfield{(reserved)}{8}{20}{00000000}%
\regfield{SPI\_OUTLINK\_ADDR}{20}{0}{{\hexprefix{}000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIOUTLINKADDR}\item [SPI\_OUTLINK\_ADDR] The address of the first outlink descriptor. (R/W)
\label{fielddesc:SPIOUTLINKSTOP}\item [SPI\_OUTLINK\_STOP] Set the bit to stop using outlink descriptor. (R/W)
\label{fielddesc:SPIOUTLINKSTART}\item [SPI\_OUTLINK\_START] Set the bit to start using outlink descriptor. (R/W)
\label{fielddesc:SPIOUTLINKRESTART}\item [SPI\_OUTLINK\_RESTART] Set the bit to mount on new outlink descriptors. (R/W)
\label{fielddesc:SPIDMATXENA}\item [SPI\_DMA\_TX\_ENA] 1: enable DMA controlled TX mode. 0: enable CPU controlled TX mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_IN\_ERR\_EOF\_DES\_ADDR\_REG}{\hexprefix{}0068}\label{regdesc:SPIINERREOFDESADDRREG}
\regfield{SPI\_DMA\_IN\_ERR\_EOF\_DES\_ADDR}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDMAINERREOFDESADDR}\item [SPI\_DMA\_IN\_ERR\_EOF\_DES\_ADDR] The inlink descriptor address when SPI DMA generates receiving error. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_IN\_SUC\_EOF\_DES\_ADDR\_REG}{\hexprefix{}006C}\label{regdesc:SPIINSUCEOFDESADDRREG}
\regfield{SPI\_DMA\_IN\_SUC\_EOF\_DES\_ADDR}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDMAINSUCEOFDESADDR}\item [SPI\_DMA\_IN\_SUC\_EOF\_DES\_ADDR] The last inlink descriptor address when SPI DMA generates FROM\_SUC\_EOF. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_INLINK\_DSCR\_REG}{\hexprefix{}0070}\label{regdesc:SPIINLINKDSCRREG}
\regfield{SPI\_DMA\_INLINK\_DSCR}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDMAINLINKDSCR}\item [SPI\_DMA\_INLINK\_DSCR] The content of current inlink descriptor pointer. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_INLINK\_DSCR\_BF0\_REG}{\hexprefix{}0074}\label{regdesc:SPIINLINKDSCRBF0REG}
\regfield{SPI\_DMA\_INLINK\_DSCR\_BF0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDMAINLINKDSCRBF0}\item [SPI\_DMA\_INLINK\_DSCR\_BF0] The content of next inlink descriptor pointer. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_OUT\_EOF\_BFR\_DES\_ADDR\_REG}{\hexprefix{}007C}\label{regdesc:SPIOUTEOFBFRDESADDRREG}
\regfield{SPI\_DMA\_OUT\_EOF\_BFR\_DES\_ADDR}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDMAOUTEOFBFRDESADDR}\item [SPI\_DMA\_OUT\_EOF\_BFR\_DES\_ADDR] The address of buffer relative to the outlink descriptor that generates EOF. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_OUT\_EOF\_DES\_ADDR\_REG}{\hexprefix{}0080}\label{regdesc:SPIOUTEOFDESADDRREG}
\regfield{SPI\_DMA\_OUT\_EOF\_DES\_ADDR}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDMAOUTEOFDESADDR}\item [SPI\_DMA\_OUT\_EOF\_DES\_ADDR] The last outlink descriptor address when SPI DMA generates TO\_EOF. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_OUTLINK\_DSCR\_REG}{\hexprefix{}0084}\label{regdesc:SPIOUTLINKDSCRREG}
\regfield{SPI\_DMA\_OUTLINK\_DSCR}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDMAOUTLINKDSCR}\item [SPI\_DMA\_OUTLINK\_DSCR] The content of current outlink descriptor pointer. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_OUTLINK\_DSCR\_BF0\_REG}{\hexprefix{}0088}\label{regdesc:SPIOUTLINKDSCRBF0REG}
\regfield{SPI\_DMA\_OUTLINK\_DSCR\_BF0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDMAOUTLINKDSCRBF0}\item [SPI\_DMA\_OUTLINK\_DSCR\_BF0] The content of next outlink descriptor pointer. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_OUTSTATUS\_REG}{\hexprefix{}0090}\label{regdesc:SPIDMAOUTSTATUSREG}
\regfield{SPI\_DMA\_OUTFIFO\_EMPTY}{1}{31}{{1}}%
\regfield{SPI\_DMA\_OUTFIFO\_FULL}{1}{30}{{0}}%
\regfield{SPI\_DMA\_OUTFIFO\_CNT}{7}{23}{{0}}%
\regfield{SPI\_DMA\_OUT\_STATE}{3}{20}{{0}}%
\regfield{SPI\_DMA\_OUTDSCR\_STATE}{2}{18}{{0}}%
\regfield{SPI\_DMA\_OUTDSCR\_ADDR}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDMAOUTDSCRADDR}\item [SPI\_DMA\_OUTDSCR\_ADDR] SPI DMA out descriptor address. (RO)
\label{fielddesc:SPIDMAOUTDSCRSTATE}\item [SPI\_DMA\_OUTDSCR\_STATE] SPI DMA out descriptor state. (RO)
\label{fielddesc:SPIDMAOUTSTATE}\item [SPI\_DMA\_OUT\_STATE] SPI DMA out data state. (RO)
\label{fielddesc:SPIDMAOUTFIFOCNT}\item [SPI\_DMA\_OUTFIFO\_CNT] The remaining part of SPI DMA out\_FIFO data. (RO)
\label{fielddesc:SPIDMAOUTFIFOFULL}\item [SPI\_DMA\_OUTFIFO\_FULL] SPI DMA out\_FIFO is full. (RO)
\label{fielddesc:SPIDMAOUTFIFOEMPTY}\item [SPI\_DMA\_OUTFIFO\_EMPTY] SPI DMA out\_FIFO is empty. (RO)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{SPI\_DMA\_INSTATUS\_REG}{\hexprefix{}0094}\label{regdesc:SPIDMAINSTATUSREG}
\regfield{SPI\_DMA\_INFIFO\_EMPTY}{1}{31}{{1}}%
\regfield{SPI\_DMA\_INFIFO\_FULL}{1}{30}{{0}}%
\regfield{SPI\_DMA\_INFIFO\_CNT}{7}{23}{{0}}%
\regfield{SPI\_DMA\_IN\_STATE}{3}{20}{{0}}%
\regfield{SPI\_DMA\_INDSCR\_STATE}{2}{18}{{0}}%
\regfield{SPI\_DMA\_INDSCR\_ADDR}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDMAINDSCRADDR}\item [SPI\_DMA\_INDSCR\_ADDR] SPI DMA in descriptor address. (RO)
\label{fielddesc:SPIDMAINDSCRSTATE}\item [SPI\_DMA\_INDSCR\_STATE] SPI DMA in descriptor state. (RO)
\label{fielddesc:SPIDMAINSTATE}\item [SPI\_DMA\_IN\_STATE] SPI DMA in data state. (RO)
\label{fielddesc:SPIDMAINFIFOCNT}\item [SPI\_DMA\_INFIFO\_CNT] The remaining part of SPI DMA inFIFO data. (RO)
\label{fielddesc:SPIDMAINFIFOFULL}\item [SPI\_DMA\_INFIFO\_FULL] SPI DMA inFIFO is full. (RO)
\label{fielddesc:SPIDMAINFIFOEMPTY}\item [SPI\_DMA\_INFIFO\_EMPTY] SPI DMA inFIFO is empty. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_IN\_LINK\_REG}{\hexprefix{}0054}\label{regdesc:SPIDMAINLINKREG}
\regfield{SPI\_DMA\_RX\_ENA}{1}{31}{{0}}%
\regfield{SPI\_INLINK\_RESTART}{1}{30}{{0}}%
\regfield{SPI\_INLINK\_START}{1}{29}{{0}}%
\regfield{SPI\_INLINK\_STOP}{1}{28}{{0}}%
\regfield{(reserved)}{7}{21}{0000000}%
\regfield{SPI\_INLINK\_AUTO\_RET}{1}{20}{{0}}%
\regfield{SPI\_INLINK\_ADDR}{20}{0}{{\hexprefix{}000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIINLINKADDR}\item [SPI\_INLINK\_ADDR] The address of the first inlink descriptor. (R/W)
\label{fielddesc:SPIINLINKAUTORET}\item [SPI\_INLINK\_AUTO\_RET] When the bit is set, the inlink descriptor returns to the first link node when a packet is in error. (R/W)
\label{fielddesc:SPIINLINKSTOP}\item [SPI\_INLINK\_STOP] Set the bit to stop using inlink descriptor. (R/W)
\label{fielddesc:SPIINLINKSTART}\item [SPI\_INLINK\_START] Set the bit to start using inlink descriptor. (R/W)
\label{fielddesc:SPIINLINKRESTART}\item [SPI\_INLINK\_RESTART] Set the bit to mount on new inlink descriptors. (R/W)
\label{fielddesc:SPIDMARXENA}\item [SPI\_DMA\_RX\_ENA] 1: enable DMA controlled RX mode. 0: enable CPU controlled RX mode. (R/W) (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_INT\_ENA\_REG}{\hexprefix{}0058}\label{regdesc:SPIDMAINTENAREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{SPI\_SLV\_CMDA\_INT\_ENA}{1}{15}{{0}}%
\regfield{SPI\_SLV\_CMD9\_INT\_ENA}{1}{14}{{0}}%
\regfield{SPI\_SLV\_CMD8\_INT\_ENA}{1}{13}{{0}}%
\regfield{SPI\_SLV\_CMD7\_INT\_ENA}{1}{12}{{0}}%
\regfield{SPI\_SLV\_CMD6\_INT\_ENA}{1}{11}{{0}}%
\regfield{SPI\_OUTFIFO\_EMPTY\_ERR\_INT\_ENA}{1}{10}{{0}}%
\regfield{SPI\_INFIFO\_FULL\_ERR\_INT\_ENA}{1}{9}{{0}}%
\regfield{SPI\_OUT\_TOTAL\_EOF\_INT\_ENA}{1}{8}{{0}}%
\regfield{SPI\_OUT\_EOF\_INT\_ENA}{1}{7}{{0}}%
\regfield{SPI\_OUT\_DONE\_INT\_ENA}{1}{6}{{0}}%
\regfield{SPI\_IN\_SUC\_EOF\_INT\_ENA}{1}{5}{{0}}%
\regfield{SPI\_IN\_ERR\_EOF\_INT\_ENA}{1}{4}{{0}}%
\regfield{SPI\_IN\_DONE\_INT\_ENA}{1}{3}{{0}}%
\regfield{SPI\_INLINK\_DSCR\_ERROR\_INT\_ENA}{1}{2}{{0}}%
\regfield{SPI\_OUTLINK\_DSCR\_ERROR\_INT\_ENA}{1}{1}{{0}}%
\regfield{SPI\_INLINK\_DSCR\_EMPTY\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIINLINKDSCREMPTYINTENA}\item [SPI\_INLINK\_DSCR\_EMPTY\_INT\_ENA] The enable bit for not enough inlink descriptors. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIOUTLINKDSCRERRORINTENA}\item [SPI\_OUTLINK\_DSCR\_ERROR\_INT\_ENA] The enable bit for outlink descriptor error. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIINLINKDSCRERRORINTENA}\item [SPI\_INLINK\_DSCR\_ERROR\_INT\_ENA] The enable bit for inlink descriptor error. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIINDONEINTENA}\item [SPI\_IN\_DONE\_INT\_ENA] The enable bit for completing usage of an inlink descriptor. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIINERREOFINTENA}\item [SPI\_IN\_ERR\_EOF\_INT\_ENA] The enable bit for receiving error. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIINSUCEOFINTENA}\item [SPI\_IN\_SUC\_EOF\_INT\_ENA] The enable bit for completing receiving all the packets from host. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIOUTDONEINTENA}\item [SPI\_OUT\_DONE\_INT\_ENA] The enable bit for completing usage of an outlink descriptor. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIOUTEOFINTENA}\item [SPI\_OUT\_EOF\_INT\_ENA] The enable bit for sending a packet to host done. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIOUTTOTALEOFINTENA}\item [SPI\_OUT\_TOTAL\_EOF\_INT\_ENA] The enable bit for sending all the packets to host done. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIINFIFOFULLERRINTENA}\item [SPI\_INFIFO\_FULL\_ERR\_INT\_ENA] The enable bit for inFIFO full error interrupt. (R/W)
\label{fielddesc:SPIOUTFIFOEMPTYERRINTENA}\item [SPI\_OUTFIFO\_EMPTY\_ERR\_INT\_ENA] The enable bit for outFIFO empty error interrupt. (R/W)
\label{fielddesc:SPISLVCMD6INTENA}\item [SPI\_SLV\_CMD6\_INT\_ENA] The enable bit for SPI slave CMD6 interrupt. (R/W)
\label{fielddesc:SPISLVCMD7INTENA}\item [SPI\_SLV\_CMD7\_INT\_ENA] The enable bit for SPI slave CMD7 interrupt. (R/W)
\label{fielddesc:SPISLVCMD8INTENA}\item [SPI\_SLV\_CMD8\_INT\_ENA] The enable bit for SPI slave CMD8 interrupt. (R/W)
\label{fielddesc:SPISLVCMD9INTENA}\item [SPI\_SLV\_CMD9\_INT\_ENA] The enable bit for SPI slave CMD9 interrupt. (R/W)
\label{fielddesc:SPISLVCMDAINTENA}\item [SPI\_SLV\_CMDA\_INT\_ENA] The enable bit for SPI slave CMDA interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_INT\_RAW\_REG}{\hexprefix{}005C}\label{regdesc:SPIDMAINTRAWREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{SPI\_SLV\_CMDA\_INT\_RAW}{1}{15}{{0}}%
\regfield{SPI\_SLV\_CMD9\_INT\_RAW}{1}{14}{{0}}%
\regfield{SPI\_SLV\_CMD8\_INT\_RAW}{1}{13}{{0}}%
\regfield{SPI\_SLV\_CMD7\_INT\_RAW}{1}{12}{{0}}%
\regfield{SPI\_SLV\_CMD6\_INT\_RAW}{1}{11}{{0}}%
\regfield{SPI\_OUTFIFO\_EMPTY\_ERR\_INT\_RAW}{1}{10}{{0}}%
\regfield{SPI\_INFIFO\_FULL\_ERR\_INT\_RAW}{1}{9}{{0}}%
\regfield{SPI\_OUT\_TOTAL\_EOF\_INT\_RAW}{1}{8}{{0}}%
\regfield{SPI\_OUT\_EOF\_INT\_RAW}{1}{7}{{0}}%
\regfield{SPI\_OUT\_DONE\_INT\_RAW}{1}{6}{{0}}%
\regfield{SPI\_IN\_SUC\_EOF\_INT\_RAW}{1}{5}{{0}}%
\regfield{SPI\_IN\_ERR\_EOF\_INT\_RAW}{1}{4}{{0}}%
\regfield{SPI\_IN\_DONE\_INT\_RAW}{1}{3}{{0}}%
\regfield{SPI\_INLINK\_DSCR\_ERROR\_INT\_RAW}{1}{2}{{0}}%
\regfield{SPI\_OUTLINK\_DSCR\_ERROR\_INT\_RAW}{1}{1}{{0}}%
\regfield{SPI\_INLINK\_DSCR\_EMPTY\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIINLINKDSCREMPTYINTRAW}\item [SPI\_INLINK\_DSCR\_EMPTY\_INT\_RAW] The raw bit for not enough inlink descriptors. Can be configured in CONF state. (RO)
\label{fielddesc:SPIOUTLINKDSCRERRORINTRAW}\item [SPI\_OUTLINK\_DSCR\_ERROR\_INT\_RAW] The raw bit for outlink descriptor error. Can be configured in CONF state. (RO)
\label{fielddesc:SPIINLINKDSCRERRORINTRAW}\item [SPI\_INLINK\_DSCR\_ERROR\_INT\_RAW] The raw bit for inlink descriptor error. Can be configured in CONF state. (RO)
\label{fielddesc:SPIINDONEINTRAW}\item [SPI\_IN\_DONE\_INT\_RAW] The raw bit for completing usage of an inlink descriptor. Can be configured in CONF state. (RO)
\label{fielddesc:SPIINERREOFINTRAW}\item [SPI\_IN\_ERR\_EOF\_INT\_RAW] The raw bit for receiving error. Can be configured in CONF state. (RO)
\label{fielddesc:SPIINSUCEOFINTRAW}\item [SPI\_IN\_SUC\_EOF\_INT\_RAW] The raw bit for completing receiving all the packets from host. Can be configured in CONF state. (RO)
\label{fielddesc:SPIOUTDONEINTRAW}\item [SPI\_OUT\_DONE\_INT\_RAW] The raw bit for completing usage of an outlink descriptor. Can be configured in CONF state. (RO)
\label{fielddesc:SPIOUTEOFINTRAW}\item [SPI\_OUT\_EOF\_INT\_RAW] The raw bit for sending a packet to host done. Can be configured in CONF state. (RO)
\label{fielddesc:SPIOUTTOTALEOFINTRAW}\item [SPI\_OUT\_TOTAL\_EOF\_INT\_RAW] The raw bit for sending all the packets to host done. Can be configured in CONF state. (RO)
\label{fielddesc:SPIINFIFOFULLERRINTRAW}\item [SPI\_INFIFO\_FULL\_ERR\_INT\_RAW]
If the size of the DMA RX buffer is smaller than the size of the transferred data, the interrupt SPI\_INFIFO\_FULL\_ERR\_INT will be triggered. Can not be configured in CONF phase. (RO)
\label{fielddesc:SPIOUTFIFOEMPTYERRINTRAW}\item [SPI\_OUTFIFO\_EMPTY\_ERR\_INT\_RAW]
当 DMA TX buffer 的大小小于传输数据长度时，触发此中断。 不可在 CONF 阶段配置。
If the size of the DMA TX buffer is smaller than the size of the transferred data, the interrupt SPI\_OUTFIFO\_EMPTY\_ERR\_INT will be triggered. Can not be configured in CONF phase. (RO)
\label{fielddesc:SPISLVCMD6INTRAW}\item [SPI\_SLV\_CMD6\_INT\_RAW] The raw bit for SPI slave CMD6 interrupt. (R/W)
\label{fielddesc:SPISLVCMD7INTRAW}\item [SPI\_SLV\_CMD7\_INT\_RAW] The raw bit for SPI slave CMD7 interrupt. (R/W)
\label{fielddesc:SPISLVCMD8INTRAW}\item [SPI\_SLV\_CMD8\_INT\_RAW] The raw bit for SPI slave CMD8 interrupt. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{SPI\_DMA\_INT\_RAW\_REG}{\hexprefix{}005C}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:SPISLVCMD9INTRAW}\item [SPI\_SLV\_CMD9\_INT\_RAW] The raw bit for SPI slave CMD9 interrupt. (R/W)
\label{fielddesc:SPISLVCMDAINTRAW}\item [SPI\_SLV\_CMDA\_INT\_RAW] The raw bit for SPI slave CMDA interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_INT\_ST\_REG}{\hexprefix{}0060}\label{regdesc:SPIDMAINTSTREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{SPI\_SLV\_CMDA\_INT\_ST}{1}{15}{{0}}%
\regfield{SPI\_SLV\_CMD9\_INT\_ST}{1}{14}{{0}}%
\regfield{SPI\_SLV\_CMD8\_INT\_ST}{1}{13}{{0}}%
\regfield{SPI\_SLV\_CMD7\_INT\_ST}{1}{12}{{0}}%
\regfield{SPI\_SLV\_CMD6\_INT\_ST}{1}{11}{{0}}%
\regfield{SPI\_OUTFIFO\_EMPTY\_ERR\_INT\_ST}{1}{10}{{0}}%
\regfield{SPI\_INFIFO\_FULL\_ERR\_INT\_ST}{1}{9}{{0}}%
\regfield{SPI\_OUT\_TOTAL\_EOF\_INT\_ST}{1}{8}{{0}}%
\regfield{SPI\_OUT\_EOF\_INT\_ST}{1}{7}{{0}}%
\regfield{SPI\_OUT\_DONE\_INT\_ST}{1}{6}{{0}}%
\regfield{SPI\_IN\_SUC\_EOF\_INT\_ST}{1}{5}{{0}}%
\regfield{SPI\_IN\_ERR\_EOF\_INT\_ST}{1}{4}{{0}}%
\regfield{SPI\_IN\_DONE\_INT\_ST}{1}{3}{{0}}%
\regfield{SPI\_INLINK\_DSCR\_ERROR\_INT\_ST}{1}{2}{{0}}%
\regfield{SPI\_OUTLINK\_DSCR\_ERROR\_INT\_ST}{1}{1}{{0}}%
\regfield{SPI\_INLINK\_DSCR\_EMPTY\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIINLINKDSCREMPTYINTST}\item [SPI\_INLINK\_DSCR\_EMPTY\_INT\_ST] The status bit for not enough inlink descriptors. (RO)
\label{fielddesc:SPIOUTLINKDSCRERRORINTST}\item [SPI\_OUTLINK\_DSCR\_ERROR\_INT\_ST] The status bit for outlink descriptor error. (RO)
\label{fielddesc:SPIINLINKDSCRERRORINTST}\item [SPI\_INLINK\_DSCR\_ERROR\_INT\_ST] The status bit for inlink descriptor error. (RO)
\label{fielddesc:SPIINDONEINTST}\item [SPI\_IN\_DONE\_INT\_ST] The status bit for completing usage of a inlink descriptor. (RO)
\label{fielddesc:SPIINERREOFINTST}\item [SPI\_IN\_ERR\_EOF\_INT\_ST] The status bit for receiving error. (RO)
\label{fielddesc:SPIINSUCEOFINTST}\item [SPI\_IN\_SUC\_EOF\_INT\_ST] The status bit for completing receiving all the packets from host. (RO)
\label{fielddesc:SPIOUTDONEINTST}\item [SPI\_OUT\_DONE\_INT\_ST] The status bit for completing usage of a outlink descriptor. (RO)
\label{fielddesc:SPIOUTEOFINTST}\item [SPI\_OUT\_EOF\_INT\_ST] The status bit for sending a packet to host done. (RO)
\label{fielddesc:SPIOUTTOTALEOFINTST}\item [SPI\_OUT\_TOTAL\_EOF\_INT\_ST] The status bit for sending all the packets to host done. (RO)
\label{fielddesc:SPIINFIFOFULLERRINTST}\item [SPI\_INFIFO\_FULL\_ERR\_INT\_ST] The status bit for inFIFO full error. (RO)
\label{fielddesc:SPIOUTFIFOEMPTYERRINTST}\item [SPI\_OUTFIFO\_EMPTY\_ERR\_INT\_ST] The status bit for outFIFO empty error. (RO)
\label{fielddesc:SPISLVCMD6INTST}\item [SPI\_SLV\_CMD6\_INT\_ST] The status bit for SPI slave CMD6 interrupt. (R/W)
\label{fielddesc:SPISLVCMD7INTST}\item [SPI\_SLV\_CMD7\_INT\_ST] The status bit for SPI slave CMD7 interrupt. (R/W)
\label{fielddesc:SPISLVCMD8INTST}\item [SPI\_SLV\_CMD8\_INT\_ST] The status bit for SPI slave CMD8 interrupt. (R/W)
\label{fielddesc:SPISLVCMD9INTST}\item [SPI\_SLV\_CMD9\_INT\_ST] The status bit for SPI slave CMD9 interrupt. (R/W)
\label{fielddesc:SPISLVCMDAINTST}\item [SPI\_SLV\_CMDA\_INT\_ST] The status bit for SPI slave CMDA interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_INT\_CLR\_REG}{\hexprefix{}0064}\label{regdesc:SPIDMAINTCLRREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{SPI\_SLV\_CMDA\_INT\_CLR}{1}{15}{{0}}%
\regfield{SPI\_SLV\_CMD9\_INT\_CLR}{1}{14}{{0}}%
\regfield{SPI\_SLV\_CMD8\_INT\_CLR}{1}{13}{{0}}%
\regfield{SPI\_SLV\_CMD7\_INT\_CLR}{1}{12}{{0}}%
\regfield{SPI\_SLV\_CMD6\_INT\_CLR}{1}{11}{{0}}%
\regfield{SPI\_OUTFIFO\_EMPTY\_ERR\_INT\_CLR}{1}{10}{{0}}%
\regfield{SPI\_INFIFO\_FULL\_ERR\_INT\_CLR}{1}{9}{{0}}%
\regfield{SPI\_OUT\_TOTAL\_EOF\_INT\_CLR}{1}{8}{{0}}%
\regfield{SPI\_OUT\_EOF\_INT\_CLR}{1}{7}{{0}}%
\regfield{SPI\_OUT\_DONE\_INT\_CLR}{1}{6}{{0}}%
\regfield{SPI\_IN\_SUC\_EOF\_INT\_CLR}{1}{5}{{0}}%
\regfield{SPI\_IN\_ERR\_EOF\_INT\_CLR}{1}{4}{{0}}%
\regfield{SPI\_IN\_DONE\_INT\_CLR}{1}{3}{{0}}%
\regfield{SPI\_INLINK\_DSCR\_ERROR\_INT\_CLR}{1}{2}{{0}}%
\regfield{SPI\_OUTLINK\_DSCR\_ERROR\_INT\_CLR}{1}{1}{{0}}%
\regfield{SPI\_INLINK\_DSCR\_EMPTY\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIINLINKDSCREMPTYINTCLR}\item [SPI\_INLINK\_DSCR\_EMPTY\_INT\_CLR] The clear bit for lack of enough inlink descriptors. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIOUTLINKDSCRERRORINTCLR}\item [SPI\_OUTLINK\_DSCR\_ERROR\_INT\_CLR] The clear bit for outlink descriptor error. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIINLINKDSCRERRORINTCLR}\item [SPI\_INLINK\_DSCR\_ERROR\_INT\_CLR] The clear bit for inlink descriptor error. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIINDONEINTCLR}\item [SPI\_IN\_DONE\_INT\_CLR] The clear bit for completing usage of a inlink descriptor. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIINERREOFINTCLR}\item [SPI\_IN\_ERR\_EOF\_INT\_CLR] The clear bit for receiving error. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIINSUCEOFINTCLR}\item [SPI\_IN\_SUC\_EOF\_INT\_CLR] The clear bit for completing receiving all the packets from host. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIOUTDONEINTCLR}\item [SPI\_OUT\_DONE\_INT\_CLR] The clear bit for completing usage of a outlink descriptor. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIOUTEOFINTCLR}\item [SPI\_OUT\_EOF\_INT\_CLR] The clear bit for sending a packet to host done. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIOUTTOTALEOFINTCLR}\item [SPI\_OUT\_TOTAL\_EOF\_INT\_CLR] The clear bit for sending all the packets to host done. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIINFIFOFULLERRINTCLR}\item [SPI\_INFIFO\_FULL\_ERR\_INT\_CLR] 1: Clear SPI\_INFIFO\_FULL\_ERR\_INT\_RAW. 0: not valid. Can be changed by CONF\_buf. (R/W)
\label{fielddesc:SPIOUTFIFOEMPTYERRINTCLR}\item [SPI\_OUTFIFO\_EMPTY\_ERR\_INT\_CLR] 1: Clear SPI\_OUTFIFO\_EMPTY\_ERR\_INT\_RAW signal. 0: not valid. Can be changed by CONF\_buf. (R/W)
\label{fielddesc:SPISLVCMD6INTCLR}\item [SPI\_SLV\_CMD6\_INT\_CLR] The clear bit for SPI slave CMD6 interrupt. (R/W)
\label{fielddesc:SPISLVCMD7INTCLR}\item [SPI\_SLV\_CMD7\_INT\_CLR] The clear bit for SPI slave CMD7 interrupt. (R/W)
\label{fielddesc:SPISLVCMD8INTCLR}\item [SPI\_SLV\_CMD8\_INT\_CLR] The clear bit for SPI slave CMD8 interrupt. (R/W)
\label{fielddesc:SPISLVCMD9INTCLR}\item [SPI\_SLV\_CMD9\_INT\_CLR] The clear bit for SPI slave CMD9 interrupt. (R/W)
\label{fielddesc:SPISLVCMDAINTCLR}\item [SPI\_SLV\_CMDA\_INT\_CLR] The clear bit for SPI slave CMDA interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W0\_REG}{\hexprefix{}0098}\label{regdesc:SPIW0REG}
\regfield{SPI\_BUF0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF0}\item [SPI\_BUF0] 32 bits data buffer 0, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W1\_REG}{\hexprefix{}009C}\label{regdesc:SPIW1REG}
\regfield{SPI\_BUF1}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF1}\item [SPI\_BUF1] 32 bits data buffer 1, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W2\_REG}{\hexprefix{}00A0}\label{regdesc:SPIW2REG}
\regfield{SPI\_BUF2}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF2}\item [SPI\_BUF2] 32 bits data buffer 2, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W3\_REG}{\hexprefix{}00A4}\label{regdesc:SPIW3REG}
\regfield{SPI\_BUF3}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF3}\item [SPI\_BUF3] 32 bits data buffer 3, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W4\_REG}{\hexprefix{}00A8}\label{regdesc:SPIW4REG}
\regfield{SPI\_BUF4}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF4}\item [SPI\_BUF4] 32 bits data buffer 4, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W5\_REG}{\hexprefix{}00AC}\label{regdesc:SPIW5REG}
\regfield{SPI\_BUF5}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF5}\item [SPI\_BUF5] 32 bits data buffer 5, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W6\_REG}{\hexprefix{}00B0}\label{regdesc:SPIW6REG}
\regfield{SPI\_BUF6}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF6}\item [SPI\_BUF6] 32 bits data buffer 6, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W7\_REG}{\hexprefix{}00B4}\label{regdesc:SPIW7REG}
\regfield{SPI\_BUF7}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF7}\item [SPI\_BUF7] 32 bits data buffer 7, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W8\_REG}{\hexprefix{}00B8}\label{regdesc:SPIW8REG}
\regfield{SPI\_BUF8}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF8}\item [SPI\_BUF8] 32 bits data buffer 8, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W9\_REG}{\hexprefix{}00BC}\label{regdesc:SPIW9REG}
\regfield{SPI\_BUF9}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF9}\item [SPI\_BUF9] 32 bits data buffer 9, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W10\_REG}{\hexprefix{}00C0}\label{regdesc:SPIW10REG}
\regfield{SPI\_BUF10}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF10}\item [SPI\_BUF10] 32 bits data buffer 10, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W11\_REG}{\hexprefix{}00C4}\label{regdesc:SPIW11REG}
\regfield{SPI\_BUF11}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF11}\item [SPI\_BUF11] 32 bits data buffer 11, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W12\_REG}{\hexprefix{}00C8}\label{regdesc:SPIW12REG}
\regfield{SPI\_BUF12}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF12}\item [SPI\_BUF12] 32 bits data buffer 12, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W13\_REG}{\hexprefix{}00CC}\label{regdesc:SPIW13REG}
\regfield{SPI\_BUF13}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF13}\item [SPI\_BUF13] 32 bits data buffer 13, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W14\_REG}{\hexprefix{}00D0}\label{regdesc:SPIW14REG}
\regfield{SPI\_BUF14}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF14}\item [SPI\_BUF14] 32 bits data buffer 14, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W15\_REG}{\hexprefix{}00D4}\label{regdesc:SPIW15REG}
\regfield{SPI\_BUF15}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF15}\item [SPI\_BUF15] 32 bits data buffer 15, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W16\_REG}{\hexprefix{}00D8}\label{regdesc:SPIW16REG}
\regfield{SPI\_BUF16}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF16}\item [SPI\_BUF16] 32 bits data buffer 16, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W17\_REG}{\hexprefix{}00DC}\label{regdesc:SPIW17REG}
\regfield{SPI\_BUF17}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF17}\item [SPI\_BUF17] 32 bits data buffer 17, transferred in the unit of byte. Byte addressable in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DIN\_MODE\_REG}{\hexprefix{}00E0}\label{regdesc:SPIDINMODEREG}
\regfield{(reserved)}{7}{25}{0000000}%
\regfield{SPI\_TIMING\_CLK\_ENA}{1}{24}{{0}}%
\regfield{SPI\_DIN7\_MODE}{3}{21}{{\hexprefix{}0}}%
\regfield{SPI\_DIN6\_MODE}{3}{18}{{\hexprefix{}0}}%
\regfield{SPI\_DIN5\_MODE}{3}{15}{{\hexprefix{}0}}%
\regfield{SPI\_DIN4\_MODE}{3}{12}{{\hexprefix{}0}}%
\regfield{SPI\_DIN3\_MODE}{3}{9}{{\hexprefix{}0}}%
\regfield{SPI\_DIN2\_MODE}{3}{6}{{\hexprefix{}0}}%
\regfield{SPI\_DIN1\_MODE}{3}{3}{{\hexprefix{}0}}%
\regfield{SPI\_DIN0\_MODE}{3}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDIN0MODE}\item [SPI\_DIN0\_MODE]
Select clock source, and sample input signal FSPID from the master with delays. 0: input without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDIN1MODE}\item [SPI\_DIN1\_MODE] Select clock source, and sample input signal FSPIQ from the master with delays. 0: input without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDIN2MODE}\item [SPI\_DIN2\_MODE] Select clock source, and sample input signal FSPIWP from the master with delays. 0: input without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDIN3MODE}\item [SPI\_DIN3\_MODE] Select clock source, and sample input signal FSPIHD from the master with delays. 0: input without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDIN4MODE}\item [SPI\_DIN4\_MODE] Select clock source, and sample input signal FSPIIO4 from the master with delays. 0: input without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDIN5MODE}\item [SPI\_DIN5\_MODE] Select clock source, and sample input signal FSPIIO5 from the master with delays. 0: input without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDIN6MODE}\item [SPI\_DIN6\_MODE] Select clock source, and sample input signal FSPIIO6 from the master with delays. 0: input without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDIN7MODE}\item [SPI\_DIN7\_MODE] Select clock source, and sample input signal FSPIIO7 from the master with delays. 0: input without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPITIMINGCLKENA}\item [SPI\_TIMING\_CLK\_ENA] 1: enable high-frequency clock: HCLK 160 MHz. 0: disable. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DIN\_NUM\_REG}{\hexprefix{}00E4}\label{regdesc:SPIDINNUMREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{SPI\_DIN7\_NUM}{2}{14}{{\hexprefix{}0}}%
\regfield{SPI\_DIN6\_NUM}{2}{12}{{\hexprefix{}0}}%
\regfield{SPI\_DIN5\_NUM}{2}{10}{{\hexprefix{}0}}%
\regfield{SPI\_DIN4\_NUM}{2}{8}{{\hexprefix{}0}}%
\regfield{SPI\_DIN3\_NUM}{2}{6}{{\hexprefix{}0}}%
\regfield{SPI\_DIN2\_NUM}{2}{4}{{\hexprefix{}0}}%
\regfield{SPI\_DIN1\_NUM}{2}{2}{{\hexprefix{}0}}%
\regfield{SPI\_DIN0\_NUM}{2}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDIN0NUM}\item [SPI\_DIN0\_NUM]
Configure the delays to input signal FSPID based on the setting of SPI\_DIN0\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDIN1NUM}\item [SPI\_DIN1\_NUM] The Configure the delays to input signal FSPIQ based on the setting of SPI\_DIN1\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDIN2NUM}\item [SPI\_DIN2\_NUM] Configure the delays to input signal FSPIWP based on the setting of SPI\_DIN2\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDIN3NUM}\item [SPI\_DIN3\_NUM] Configure the delays to input signal FSPIHD based on the setting of SPI\_DIN3\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDIN4NUM}\item [SPI\_DIN4\_NUM] Configure the delays to input signal FSPIIO4 based on the setting of SPI\_DIN4\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDIN5NUM}\item [SPI\_DIN5\_NUM] Configure the delays to input signal FSPIIO5 based on the setting of SPI\_DIN5\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDIN6NUM}\item [SPI\_DIN6\_NUM] Configure the delays to input signal FSPIIO6 based on the setting of SPI\_DIN6\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDIN7NUM}\item [SPI\_DIN7\_NUM] Configure the delays to input signal FSPIIO7 based on the setting of SPI\_DIN7\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DOUT\_MODE\_REG}{\hexprefix{}00E8}\label{regdesc:SPIDOUTMODEREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{SPI\_DOUT7\_MODE}{3}{21}{{\hexprefix{}0}}%
\regfield{SPI\_DOUT6\_MODE}{3}{18}{{\hexprefix{}0}}%
\regfield{SPI\_DOUT5\_MODE}{3}{15}{{\hexprefix{}0}}%
\regfield{SPI\_DOUT4\_MODE}{3}{12}{{\hexprefix{}0}}%
\regfield{SPI\_DOUT3\_MODE}{3}{9}{{\hexprefix{}0}}%
\regfield{SPI\_DOUT2\_MODE}{3}{6}{{\hexprefix{}0}}%
\regfield{SPI\_DOUT1\_MODE}{3}{3}{{\hexprefix{}0}}%
\regfield{SPI\_DOUT0\_MODE}{3}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDOUT0MODE}\item [SPI\_DOUT0\_MODE]
Select clock source, and sample output signal FSPID from the master with delays. 0: output without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDOUT1MODE}\item [SPI\_DOUT1\_MODE]
Select clock source, and sample output signal FSPIQ from the master with delays. 0: output without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDOUT2MODE}\item [SPI\_DOUT2\_MODE] Select clock source, and sample output signal FSPIWP from the master with delays. 0: output without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDOUT3MODE}\item [SPI\_DOUT3\_MODE] Select clock source, and sample output signal FSPIHD from the master with delays. 0: output without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDOUT4MODE}\item [SPI\_DOUT4\_MODE] Select clock source, and sample output signal FSPIIO4 from the master with delays. 0: output without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDOUT5MODE}\item [SPI\_DOUT5\_MODE] Select clock source, and sample output signal FSPIIO5 from the master with delays. 0: output without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDOUT6MODE}\item [SPI\_DOUT6\_MODE] Select clock source, and sample output signal FSPIIO6 from the master with delays. 0: output without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDOUT7MODE}\item [SPI\_DOUT7\_MODE] Select clock source, and sample output signal FSPIIO7 from the master with delays. 0: output without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DOUT\_NUM\_REG}{\hexprefix{}00EC}\label{regdesc:SPIDOUTNUMREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{SPI\_DOUT7\_NUM}{2}{14}{{\hexprefix{}0}}%
\regfield{SPI\_DOUT6\_NUM}{2}{12}{{\hexprefix{}0}}%
\regfield{SPI\_DOUT5\_NUM}{2}{10}{{\hexprefix{}0}}%
\regfield{SPI\_DOUT4\_NUM}{2}{8}{{\hexprefix{}0}}%
\regfield{SPI\_DOUT3\_NUM}{2}{6}{{\hexprefix{}0}}%
\regfield{SPI\_DOUT2\_NUM}{2}{4}{{\hexprefix{}0}}%
\regfield{SPI\_DOUT1\_NUM}{2}{2}{{\hexprefix{}0}}%
\regfield{SPI\_DOUT0\_NUM}{2}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDOUT0NUM}\item [SPI\_DOUT0\_NUM] Configure the delays to output signal FSPID based on the setting of SPI\_DOUT0\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDOUT1NUM}\item [SPI\_DOUT1\_NUM] Configure the delays to output signal FSPIQ based on the setting of SPI\_DOUT1\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDOUT2NUM}\item [SPI\_DOUT2\_NUM] Configure the delays to output signal FSPIWP based on the setting of SPI\_DOUT2\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDOUT3NUM}\item [SPI\_DOUT3\_NUM] Configure the delays to output signal FSPIHD based on the setting of SPI\_DOUT3\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDOUT4NUM}\item [SPI\_DOUT4\_NUM] Configure the delays to output signal FSPIIO4 based on the setting of SPI\_DOUT4\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDOUT5NUM}\item [SPI\_DOUT5\_NUM] Configure the delays to output signal FSPIIO5 based on the setting of SPI\_DOUT5\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDOUT6NUM}\item [SPI\_DOUT6\_NUM] Configure the delays to output signal FSPIIO6 based on the setting of SPI\_DOUT6\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDOUT7NUM}\item [SPI\_DOUT7\_NUM] Configure the delays to output signal FSPIIO7 based on the setting of SPI\_DOUT7\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_LCD\_CTRL\_REG}{\hexprefix{}00F0}\label{regdesc:SPILCDCTRLREG}
\regfield{SPI\_LCD\_MODE\_EN}{1}{31}{{0}}%
\regfield{SPI\_LCD\_VT\_HEIGHT}{10}{21}{{0}}%
\regfield{SPI\_LCD\_VA\_HEIGHT}{10}{11}{{0}}%
\regfield{SPI\_LCD\_HB\_FRONT}{11}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPILCDHBFRONT}\item [SPI\_LCD\_HB\_FRONT] Configures the value of (\hyperref[fielddesc:SPILCDHSYNCPOSITION]{HSYNC\_POSITION} + \hyperref[fielddesc:SPILCDHSYNCWIDTH]{HSYNC\_WIDTH} + horizontal back porch). It can be configured in CONF state. (R/W)
\label{fielddesc:SPILCDVAHEIGHT}\item [SPI\_LCD\_VA\_HEIGHT] It is the vertical active height of a frame. Can be configured in CONF state. (R/W)
\label{fielddesc:SPILCDVTHEIGHT}\item [SPI\_LCD\_VT\_HEIGHT] It is the vertical total height of a frame. Can be configured in CONF state. (R/W)
\label{fielddesc:SPILCDMODEEN}\item [SPI\_LCD\_MODE\_EN] 1: Enable LCD mode output vsync, hsync, de. 0: Disable. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_LCD\_CTRL1\_REG}{\hexprefix{}00F4}\label{regdesc:SPILCDCTRL1REG}
\regfield{SPI\_LCD\_HT\_WIDTH}{12}{20}{{0}}%
\regfield{SPI\_LCD\_HA\_WIDTH}{12}{8}{{0}}%
\regfield{SPI\_LCD\_VB\_FRONT}{8}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPILCDVBFRONT}\item [SPI\_LCD\_VB\_FRONT] Configures the value of (\hyperref[fielddesc:SPILCDVSYNCWIDTH]{VSYNC\_WIDTH} + vertical back porch). It can be configured in CONF state. (R/W)
\label{fielddesc:SPILCDHAWIDTH}\item [SPI\_LCD\_HA\_WIDTH] It is the horizontal active width of a frame. Can be configured in CONF state. (R/W)
\label{fielddesc:SPILCDHTWIDTH}\item [SPI\_LCD\_HT\_WIDTH] It is the horizontal total width of a frame. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_LCD\_CTRL2\_REG}{\hexprefix{}00F8}\label{regdesc:SPILCDCTRL2REG}
\regfield{SPI\_LCD\_HSYNC\_POSITION}{8}{24}{{0}}%
\regfield{SPI\_HSYNC\_IDLE\_POL}{1}{23}{{0}}%
\regfield{SPI\_LCD\_HSYNC\_WIDTH}{7}{16}{{1}}%
\regfield{(reserved)}{8}{8}{00000000}%
\regfield{SPI\_VSYNC\_IDLE\_POL}{1}{7}{{0}}%
\regfield{SPI\_LCD\_VSYNC\_WIDTH}{7}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPILCDVSYNCWIDTH}\item [SPI\_LCD\_VSYNC\_WIDTH] Configures the width of SPI\_VSYNC active pulse. It can be configured in CONF state. (R/W)
\label{fielddesc:SPIVSYNCIDLEPOL}\item [SPI\_VSYNC\_IDLE\_POL] It is the idle value of spi\_vsync. Can be configured in CONF state. (R/W)
\label{fielddesc:SPILCDHSYNCWIDTH}\item [SPI\_LCD\_HSYNC\_WIDTH] Configures the width of SPI\_HSYNC active pulse. Expected width = this value +1. It can be configured in CONF state. (R/W)
\label{fielddesc:SPIHSYNCIDLEPOL}\item [SPI\_HSYNC\_IDLE\_POL] It is the idle value of spi\_hsync. Can be configured in CONF state. (R/W)
\label{fielddesc:SPILCDHSYNCPOSITION}\item [SPI\_LCD\_HSYNC\_POSITION] Configures the position of SPI\_HSYNC active pulse. Expected position = this value + 1. Unit is a pixel. It can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_LCD\_D\_MODE\_REG}{\hexprefix{}00FC}\label{regdesc:SPILCDDMODEREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{SPI\_HS\_BLANK\_EN}{1}{16}{{0}}%
\regfield{SPI\_DE\_IDLE\_POL}{1}{15}{{0}}%
\regfield{SPI\_D\_VSYNC\_MODE}{3}{12}{{\hexprefix{}0}}%
\regfield{SPI\_D\_HSYNC\_MODE}{3}{9}{{\hexprefix{}0}}%
\regfield{SPI\_D\_DE\_MODE}{3}{6}{{\hexprefix{}0}}%
\regfield{SPI\_D\_CD\_MODE}{3}{3}{{\hexprefix{}0}}%
\regfield{SPI\_D\_DQS\_MODE}{3}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDDQSMODE}\item [SPI\_D\_DQS\_MODE]
Select clock source, and sample output signal FSPIDQS from the master with delays. 0: output without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDCDMODE}\item [SPI\_D\_CD\_MODE]
Select clock source, and sample output signal FSPICD from the master with delays. 0: output without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDDEMODE}\item [SPI\_D\_DE\_MODE] Select clock source, and sample output signal FSPI\_DE from the master with delays. 0: output without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDHSYNCMODE}\item [SPI\_D\_HSYNC\_MODE] SPI\_HSYNC output mode. 0: output Select clock source, and sample output signal FSPI\_HSYNC from the master with delays. 0: output without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDVSYNCMODE}\item [SPI\_D\_VSYNC\_MODE] Select clock source, and sample output signal FSPI\_VSYNC from the master with delays. 0: output without delay. 1: sample at the rising edge of APB\_CLK. 2: sample at the falling edge of APB\_CLK. 3: sample at the rising edge of HCLK. 4: sample at the falling edge of HCLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDEIDLEPOL}\item [SPI\_DE\_IDLE\_POL] It is the idle value of SPI\_DE. (R/W)
\label{fielddesc:SPIHSBLANKEN}\item [SPI\_HS\_BLANK\_EN] 1: The pulse of SPI\_HSYNC is out in vertical blanking lines in seg-trans or one trans. 0: SPI\_HSYNC pulse is valid only in active region lines in segment transfer. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_LCD\_D\_NUM\_REG}{\hexprefix{}0100}\label{regdesc:SPILCDDNUMREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{SPI\_D\_VSYNC\_NUM}{2}{8}{{\hexprefix{}0}}%
\regfield{SPI\_D\_HSYNC\_NUM}{2}{6}{{\hexprefix{}0}}%
\regfield{SPI\_D\_DE\_NUM}{2}{4}{{\hexprefix{}0}}%
\regfield{SPI\_D\_CD\_NUM}{2}{2}{{\hexprefix{}0}}%
\regfield{SPI\_D\_DQS\_NUM}{2}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDDQSNUM}\item [SPI\_D\_DQS\_NUM]
Configure the delays to output signal FSPIDQS based on the setting of SPI\_D\_DQS\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDCDNUM}\item [SPI\_D\_CD\_NUM] Configure the delays to output signal FSPI\_CD based on the setting of SPI\_D\_CD\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDDENUM}\item [SPI\_D\_DE\_NUM] Configure the delays to output signal FSPI\_DE based on the setting of SPI\_D\_DE\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDHSYNCNUM}\item [SPI\_D\_HSYNC\_NUM] Configure the delays to output signal FSPI\_HSYNC based on the setting of SPI\_D\_HSYNC\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDVSYNCNUM}\item [SPI\_D\_VSYNC\_NUM] Configure the delays to output signal FSPI\_VSYNC based on the setting of SPI\_D\_VSYNC\_MODE. 0: delayed by 1 clock cycle, 1: delayed by 2 clock cycles,...  Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DATE\_REG}{\hexprefix{}03FC}\label{regdesc:SPIDATEREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{SPI\_DATE}{28}{0}{{\hexprefix{}1907240}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDATE}\item [SPI\_DATE] Version control register (R/W)
\end{reglist}\end{regdesc}
\end{register}
