\begin{longtable}{ | L{6cm} | L{6cm} | p{1.3cm} | p{2cm} | }
\hline\rowcolor{lightgray}
\textbf{Name} & \textbf{Description} &  \textbf{Address} & \textbf{Access} \\ \hline
\endhead
\multicolumn{4}{|l|}{\textbf{LP ADC Configuration Registers}} \\ \hline
\hyperref[regdesc:LPADCREADER1CTRLREG]{LPADC\_READER1\_CTRL\_REG} & LP ADC1 Reader control register. & 0x0000 & R/W \\ \hline
\hyperref[regdesc:LPADCMEAS1CTRL2REG]{LPADC\_MEAS1\_CTRL2\_REG} & LP ADC1 configuration registers. & 0x000C & varies \\ \hline
\hyperref[regdesc:LPADCMEAS1MUXREG]{LPADC\_MEAS1\_MUX\_REG} & LP or HP ADC controller selection register for SAR ADC1. & 0x0010 & R/W \\ \hline
\hyperref[regdesc:LPADCATTEN1REG]{LPADC\_ATTEN1\_REG} & LP ADC1 attenuation registers. & 0x0014 & R/W \\ \hline
\hyperref[regdesc:LPADCREADER2CTRLREG]{LPADC\_READER2\_CTRL\_REG} & LP ADC2 Reader control register. & 0x0024 & R/W \\ \hline
\hyperref[regdesc:LPADCMEAS2CTRL2REG]{LPADC\_MEAS2\_CTRL2\_REG} & LP ADC2 configuration registers. & 0x0030 & varies \\ \hline
\hyperref[regdesc:LPADCMEAS2MUXREG]{LPADC\_MEAS2\_MUX\_REG} & LP or HP controller selection register for SAR ADC2. & 0x0034 & R/W \\ \hline
\hyperref[regdesc:LPADCATTEN2REG]{LPADC\_ATTEN2\_REG} & LP ADC2 attenuation registers. & 0x0038 & R/W \\ \hline
\multicolumn{4}{|l|}{\textbf{LP ADC Power Control Registers}} \\ \hline
\hyperref[regdesc:LPADCFORCEWPDSARREG]{LPADC\_FORCE\_WPD\_SAR\_REG} & LP ADC Controllers power control registers. & 0x003C & R/W \\ \hline
\multicolumn{4}{|l|}{\textbf{LP ADC Interrupt Registers}} \\ \hline
\hyperref[regdesc:LPADCCOCPUINTRAWREG]{LPADC\_COCPU\_INT\_RAW\_REG} & Raw register of LP ADC interrupts. & 0x0048 & R/WTC/SS \\ \hline
\hyperref[regdesc:LPADCINTENAREG]{LPADC\_INT\_ENA\_REG} & Enable register of LP ADC interrupts. & 0x004C & R/WTC \\ \hline
\hyperref[regdesc:LPADCINTSTREG]{LPADC\_INT\_ST\_REG} & Status register of LP ADC interrupts. & 0x0050 & RO \\ \hline
\hyperref[regdesc:LPADCINTCLRREG]{LPADC\_INT\_CLR\_REG} & Clear register of LP ADC interrupts. & 0x0054 & WT \\ \hline
\hyperref[regdesc:LPADCINTENAW1TSREG]{LPADC\_INT\_ENA\_W1TS\_REG} & \hyperref[regdesc:LPADCINTENAREG]{LPADC\_INT\_ENA\_REG} configuration register. & 0x0058 & WT \\ \hline
\hyperref[regdesc:LPADCINTENAW1TCREG]{LPADC\_INT\_ENA\_W1TC\_REG} & \hyperref[regdesc:LPADCINTENAW1TCREG]{LPADC\_INT\_ENA\_REG} configuration register. & 0x005C & WT \\ \hline
\multicolumn{4}{|l|}{\textbf{LP ADC Wake-up Control Registers}} \\ \hline
\hyperref[regdesc:LPADCWAKEUP1REG]{LPADC\_WAKEUP1\_REG} & LP ADC1 wake-up configuration registers. & 0x0060 & varies \\ \hline
\hyperref[regdesc:LPADCWAKEUP2REG]{LPADC\_WAKEUP2\_REG} & LP ADC2 wake-up configuration registers. & 0x0064 & varies \\ \hline
\hyperref[regdesc:LPADCWAKEUPSELREG]{LPADC\_WAKEUP\_SEL\_REG} & Wake-up source selection register. & 0x0068 & R/W \\ \hline
\hyperref[regdesc:LPADCSAR1HWWAKEUPREG]{LPADC\_SAR1\_HW\_WAKEUP\_REG} & LP ADC1 automatic monitoring configuration registers. & 0x006C & R/W \\ \hline
\hyperref[regdesc:LPADCSAR2HWWAKEUPREG]{LPADC\_SAR2\_HW\_WAKEUP\_REG} & LP ADC2 automatic monitoring configuration registers. & 0x0070 & R/W \\ \hline
\end{longtable}


