\begin{register}{H}{SYSTEM\_CORE\_1\_CONTROL\_0\_REG}{0x{}0000}\label{regdesc:SYSTEMCORE1CONTROL0REG}
\regfield{(reserved)}{29}{3}{00000000000000000000000000000}%
\regfield{SYSTEM\_CONTROL\_CORE\_1\_RESETING}{1}{2}{{1}}%
\regfield{\tiny{SYSTEM\_CONTROL\_CORE\_1\_CLKGATE\_EN}}{1}{1}{{0}}%
\regfield{\tiny{SYSTEM\_CONTROL\_CORE\_1\_RUNSTALL}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMCONTROLCORE1RUNSTALL}\item [SYSTEM\_CONTROL\_CORE\_1\_RUNSTALL] Set this bit to stall Core 1. (R/W)
\label{fielddesc:SYSTEMCONTROLCORE1CLKGATEEN}\item [SYSTEM\_CONTROL\_CORE\_1\_CLKGATE\_EN] Set this bit to enable Core 1 clock. (R/W)
\label{fielddesc:SYSTEMCONTROLCORE1RESETING}\item [SYSTEM\_CONTROL\_CORE\_1\_RESETING] Set this bit to reset Core 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_CORE\_1\_CONTROL\_1\_REG}{0x{}0004}\label{regdesc:SYSTEMCORE1CONTROL1REG}
\regfield{SYSTEM\_CONTROL\_CORE\_1\_MESSAGE}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMCONTROLCORE1MESSAGE}\item [SYSTEM\_CONTROL\_CORE\_1\_MESSAGE] Sets the boot address for CPU1. Please note that this field is only effective during the first boot of CPU1; afterwards, users can configure it for other purposes as needed. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_CPU\_PER\_CONF\_REG}{0x{}0010}\label{regdesc:SYSTEMCPUPERCONFREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{SYSTEM\_CPU\_WAITI\_DELAY\_NUM}{4}{4}{{0x{}0}}%
\regfield{SYSTEM\_CPU\_WAIT\_MODE\_FORCE\_ON}{1}{3}{{1}}%
\regfield{SYSTEM\_PLL\_FREQ\_SEL}{1}{2}{{1}}%
\regfield{SYSTEM\_CPUPERIOD\_SEL}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMCPUPERIODSEL}\item [SYSTEM\_CPUPERIOD\_SEL] Set this field to select the CPU clock frequency. (R/W)
\label{fielddesc:SYSTEMPLLFREQSEL}\item [SYSTEM\_PLL\_FREQ\_SEL] Set this bit to select the PLL clock frequency. (R/W)
\label{fielddesc:SYSTEMCPUWAITMODEFORCEON}\item [SYSTEM\_CPU\_WAIT\_MODE\_FORCE\_ON] Set this bit to force on the clock gate of CPU wait mode. Usually, after executing the WAITI instruction, CPU enters the wait mode, during which the clock gate of CPU is turned off until any interrupts occur. In this way, power consumption is reduced. However, if this bit is set, the clock gate of CPU is always on and will not be turned off by the WAITI instruction. (R/W)
\label{fielddesc:SYSTEMCPUWAITIDELAYNUM}\item [SYSTEM\_CPU\_WAITI\_DELAY\_NUM] Sets the number of delay cycles to turn off the CPU clock gate after the CPU enters the wait mode because of a WAITI instruction. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_PERIP\_CLK\_EN0\_REG}{0x{}0018}\label{regdesc:SYSTEMPERIPCLKEN0REG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{SYSTEM\_ADC2\_ARB\_CLK\_EN}{1}{30}{{1}}%
\regfield{SYSTEM\_SYSTIMER\_CLK\_EN}{1}{29}{{1}}%
\regfield{SYSTEM\_APB\_SARADC\_CLK\_EN}{1}{28}{{0}}
\regfield{(reserved)}{3}{25}{000}%
\regfield{SYSTEM\_UART\_MEM\_CLK\_EN}{1}{24}{{1}}%
\regfield{SYSTEM\_USB\_CLK\_EN}{1}{23}{{1}}%
\regfield{(reserved)}{1}{22}{0}%
\regfield{SYSTEM\_I2S1\_CLK\_EN}{1}{21}{{0}}%
\regfield{SYSTEM\_PWM1\_CLK\_EN}{1}{20}{{0}}%
\regfield{SYSTEM\_CAN\_CLK\_EN}{1}{19}{{0}}%
\regfield{SYSTEM\_I2C\_EXT1\_CLK\_EN}{1}{18}{{0}}%
\regfield{SYSTEM\_PWM0\_CLK\_EN}{1}{17}{{0}}%
\regfield{SYSTEM\_SPI3\_CLK\_EN}{1}{16}{{1}}%
\regfield{SYSTEM\_TIMERGROUP1\_CLK\_EN}{1}{15}{{1}}%
\regfield{(reserved)}{1}{14}{0}%
\regfield{SYSTEM\_TIMERGROUP\_CLK\_EN}{1}{13}{{1}}%
\regfield{(reserved)}{1}{12}{0}%
\regfield{SYSTEM\_LEDC\_CLK\_EN}{1}{11}{{0}}%
\regfield{SYSTEM\_PCNT\_CLK\_EN}{1}{10}{{0}}%
\regfield{SYSTEM\_RMT\_CLK\_EN}{1}{9}{{0}}%
\regfield{SYSTEM\_UHCI0\_CLK\_EN}{1}{8}{{0}}%
\regfield{SYSTEM\_I2C\_EXT0\_CLK\_EN}{1}{7}{{0}}%
\regfield{SYSTEM\_SPI2\_CLK\_EN}{1}{6}{{1}}%
\regfield{SYSTEM\_UART1\_CLK\_EN}{1}{5}{{1}}%
\regfield{SYSTEM\_I2S0\_CLK\_EN}{1}{4}{{0}}%
\regfield{(reserved)}{1}{3}{0}%
\regfield{SYSTEM\_UART\_CLK\_EN}{1}{2}{{1}}%
\regfield{SYSTEM\_SPI01\_CLK\_EN}{1}{1}{{1}}%
\regfield{(reserved)}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMSPI01CLKEN}\item [SYSTEM\_SPI01\_CLK\_EN] Set this bit to enable SPI01 clock. (R/W)
\label{fielddesc:SYSTEMUARTCLKEN}\item [SYSTEM\_UART\_CLK\_EN] Set this bit to enable UART clock. (R/W)
\label{fielddesc:SYSTEMI2S0CLKEN}\item [SYSTEM\_I2S0\_CLK\_EN] Set this bit to enable I2S0 clock. (R/W)
\label{fielddesc:SYSTEMUART1CLKEN}\item [SYSTEM\_UART1\_CLK\_EN] Set this bit to enable UART1 clock. (R/W)
\label{fielddesc:SYSTEMSPI2CLKEN}\item [SYSTEM\_SPI2\_CLK\_EN] Set this bit to enable SPI2 clock. (R/W)
\label{fielddesc:SYSTEMI2CEXT0CLKEN}\item [SYSTEM\_I2C\_EXT0\_CLK\_EN] Set this bit to enable I2C\_EXT0 clock. (R/W)
\label{fielddesc:SYSTEMUHCI0CLKEN}\item [SYSTEM\_UHCI0\_CLK\_EN] Set this bit to enable UHCI0 clock. (R/W)
\label{fielddesc:SYSTEMRMTCLKEN}\item [SYSTEM\_RMT\_CLK\_EN] Set this bit to enable RMT clock. (R/W)
\label{fielddesc:SYSTEMPCNTCLKEN}\item [SYSTEM\_PCNT\_CLK\_EN] Set this bit to enable PCNT clock. (R/W)
\label{fielddesc:SYSTEMLEDCCLKEN}\item [SYSTEM\_LEDC\_CLK\_EN] Set this bit to enable LEDC clock. (R/W)
\label{fielddesc:SYSTEMTIMERGROUPCLKEN}\item [SYSTEM\_TIMERGROUP\_CLK\_EN] Set this bit to enable TIMERGROUP0 clock. (R/W)
\label{fielddesc:SYSTEMTIMERGROUP1CLKEN}\item [SYSTEM\_TIMERGROUP1\_CLK\_EN] Set this bit to enable TIMERGROUP1 clock. (R/W)
\label{fielddesc:SYSTEMSPI3CLKEN}\item [SYSTEM\_SPI3\_CLK\_EN] Set this bit to enable SPI3 clock. (R/W)
\label{fielddesc:SYSTEMPWM0CLKEN}\item [SYSTEM\_PWM0\_CLK\_EN] Set this bit to enable PWM0 clock. (R/W)
\label{fielddesc:SYSTEMI2CEXT1CLKEN}\item [SYSTEM\_I2C\_EXT1\_CLK\_EN] Set this bit to enable I2C\_EXT1 clock. (R/W)
\label{fielddesc:SYSTEMCANCLKEN}\item [SYSTEM\_CAN\_CLK\_EN] Set this bit to enable CAN clock. (R/W)
\label{fielddesc:SYSTEMPWM1CLKEN}\item [SYSTEM\_PWM1\_CLK\_EN] Set this bit to enable PWM1 clock. (R/W)
\label{fielddesc:SYSTEMI2S1CLKEN}\item [SYSTEM\_I2S1\_CLK\_EN] Set this bit to enable I2S1 clock. (R/W)
\label{fielddesc:SYSTEMUSBCLKEN}\item [SYSTEM\_USB\_CLK\_EN] Set this bit to enable USB clock. (R/W)
\label{fielddesc:SYSTEMUARTMEMCLKEN}\item [SYSTEM\_UART\_MEM\_CLK\_EN] Set this bit to enable UART\_MEM clock. (R/W)
\label{fielddesc:SYSTEMAPBSARADCCLKEN}\item [SYSTEM\_APB\_SARADC\_CLK\_EN] Set this bit to enable ADC controller clock. (R/W)
\label{fielddesc:SYSTEMSYSTIMERCLKEN}\item [SYSTEM\_SYSTIMER\_CLK\_EN] Set this bit to enable SYSTEM TIMER clock. (R/W)
\label{fielddesc:SYSTEMADC2ARBCLKEN}\item [SYSTEM\_ADC2\_ARB\_CLK\_EN] Set this bit to enable ADC2\_ARB clock. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_PERIP\_CLK\_EN1\_REG}{0x{}001C}\label{regdesc:SYSTEMPERIPCLKEN1REG}
\regfield{(reserved)}{21}{11}{000000000000000000000}%
\regfield{SYSTEM\_USB\_DEVICE\_CLK\_EN}{1}{10}{{1}}%
\regfield{SYSTEM\_UART2\_CLK\_EN}{1}{9}{{1}}%
\regfield{SYSTEM\_LCD\_CAM\_CLK\_EN}{1}{8}{{0}}%
\regfield{SYSTEM\_SDIO\_HOST\_CLK\_EN}{1}{7}{{0}}%
\regfield{SYSTEM\_DMA\_CLK\_EN}{1}{6}{{0}}%
\regfield{SYSTEM\_CRYPTO\_HMAC\_CLK\_EN}{1}{5}{{0}}%
\regfield{SYSTEM\_CRYPTO\_DS\_CLK\_EN}{1}{4}{{0}}%
\regfield{SYSTEM\_CRYPTO\_RSA\_CLK\_EN}{1}{3}{{0}}%
\regfield{SYSTEM\_CRYPTO\_SHA\_CLK\_EN}{1}{2}{{0}}%
\regfield{SYSTEM\_CRYPTO\_AES\_CLK\_EN}{1}{1}{{0}}%
\regfield{SYSTEM\_PERI\_BACKUP\_CLK\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMPERIBACKUPCLKEN}\item [SYSTEM\_PERI\_BACKUP\_CLK\_EN] Set this bit to enable peri backup clock. (R/W)
\label{fielddesc:SYSTEMCRYPTOAESCLKEN}\item [SYSTEM\_CRYPTO\_AES\_CLK\_EN] Set this bit to enable AES clock. (R/W)
\label{fielddesc:SYSTEMCRYPTOSHACLKEN}\item [SYSTEM\_CRYPTO\_SHA\_CLK\_EN] Set this bit to enable SHA clock. (R/W)
\label{fielddesc:SYSTEMCRYPTORSACLKEN}\item [SYSTEM\_CRYPTO\_RSA\_CLK\_EN] Set this bit to enable RSA clock. (R/W)
\label{fielddesc:SYSTEMCRYPTODSCLKEN}\item [SYSTEM\_CRYPTO\_DS\_CLK\_EN] Set this bit to enable the RSA\_DS clock. (R/W)
\label{fielddesc:SYSTEMCRYPTOHMACCLKEN}\item [SYSTEM\_CRYPTO\_HMAC\_CLK\_EN] Set this bit to enable HMAC clock. (R/W)
\label{fielddesc:SYSTEMDMACLKEN}\item [SYSTEM\_DMA\_CLK\_EN] Set this bit to enable DMA clock. (R/W)
\label{fielddesc:SYSTEMSDIOHOSTCLKEN}\item [SYSTEM\_SDIO\_HOST\_CLK\_EN] Set this bit to enable SDIO\_HOST clock. (R/W)
\label{fielddesc:SYSTEMLCDCAMCLKEN}\item [SYSTEM\_LCD\_CAM\_CLK\_EN] Set this bit to enable LCD\_CAM clock. (R/W)
\label{fielddesc:SYSTEMUART2CLKEN}\item [SYSTEM\_UART2\_CLK\_EN] Set this bit to enable UART2 clock. (R/W)
\label{fielddesc:SYSTEMUSBDEVICECLKEN}\item [SYSTEM\_USB\_DEVICE\_CLK\_EN] Set this bit to enable USB\_DEVICE clock. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_PERIP\_RST\_EN0\_REG}{0x{}0020}\label{regdesc:SYSTEMPERIPRSTEN0REG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{SYSTEM\_ADC2\_ARB\_RST}{1}{30}{{0}}%
\regfield{SYSTEM\_SYSTIMER\_RST}{1}{29}{{0}}%
\regfield{SYSTEM\_APB\_SARADC\_RST}{1}{28}{{0}}
\regfield{(reserved)}{3}{25}{000}%
\regfield{SYSTEM\_UART\_MEM\_RST}{1}{24}{{0}}%
\regfield{SYSTEM\_USB\_RST}{1}{23}{{0}}%
\regfield{(reserved)}{1}{22}{0}%
\regfield{SYSTEM\_I2S1\_RST}{1}{21}{{0}}%
\regfield{SYSTEM\_PWM1\_RST}{1}{20}{{0}}%
\regfield{SYSTEM\_CAN\_RST}{1}{19}{{0}}%
\regfield{SYSTEM\_I2C\_EXT1\_RST}{1}{18}{{0}}%
\regfield{SYSTEM\_PWM0\_RST}{1}{17}{{0}}%
\regfield{SYSTEM\_SPI3\_RST}{1}{16}{{0}}%
\regfield{SYSTEM\_TIMERGROUP1\_RST}{1}{15}{{0}}%
\regfield{(reserved)}{1}{14}{0}%
\regfield{SYSTEM\_TIMERGROUP\_RST}{1}{13}{{0}}%
\regfield{(reserved)}{1}{12}{0}%
\regfield{SYSTEM\_LEDC\_RST}{1}{11}{{0}}%
\regfield{SYSTEM\_PCNT\_RST}{1}{10}{{0}}%
\regfield{SYSTEM\_RMT\_RST}{1}{9}{{0}}%
\regfield{SYSTEM\_UHCI0\_RST}{1}{8}{{0}}%
\regfield{SYSTEM\_I2C\_EXT0\_RST}{1}{7}{{0}}%
\regfield{SYSTEM\_SPI2\_RST}{1}{6}{{0}}%
\regfield{SYSTEM\_UART1\_RST}{1}{5}{{0}}%
\regfield{SYSTEM\_I2S0\_RST}{1}{4}{{0}}%
\regfield{(reserved)}{1}{3}{0}%
\regfield{SYSTEM\_UART\_RST}{1}{2}{{0}}%
\regfield{SYSTEM\_SPI01\_RST}{1}{1}{{0}}%
\regfield{(reserved)}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMSPI01RST}\item [SYSTEM\_SPI01\_RST] Set this bit to reset SPI01. (R/W)
\label{fielddesc:SYSTEMUARTRST}\item [SYSTEM\_UART\_RST] Set this bit to reset UART. (R/W)
\label{fielddesc:SYSTEMI2S0RST}\item [SYSTEM\_I2S0\_RST] Set this bit to reset I2S0. (R/W)
\label{fielddesc:SYSTEMUART1RST}\item [SYSTEM\_UART1\_RST] Set this bit to reset UART1. (R/W)
\label{fielddesc:SYSTEMSPI2RST}\item [SYSTEM\_SPI2\_RST] Set this bit to reset SPI2. (R/W)
\label{fielddesc:SYSTEMI2CEXT0RST}\item [SYSTEM\_I2C\_EXT0\_RST] Set this bit to reset I2C\_EXT0. (R/W)
\label{fielddesc:SYSTEMUHCI0RST}\item [SYSTEM\_UHCI0\_RST] Set this bit to reset UHCI0. (R/W)
\label{fielddesc:SYSTEMRMTRST}\item [SYSTEM\_RMT\_RST] Set this bit to reset RMT. (R/W)
\label{fielddesc:SYSTEMPCNTRST}\item [SYSTEM\_PCNT\_RST] Set this bit to reset PCNT. (R/W)
\label{fielddesc:SYSTEMLEDCRST}\item [SYSTEM\_LEDC\_RST] Set this bit to reset LEDC. (R/W)
\label{fielddesc:SYSTEMTIMERGROUPRST}\item [SYSTEM\_TIMERGROUP\_RST] Set this bit to reset TIMERGROUP0. (R/W)
\label{fielddesc:SYSTEMTIMERGROUP1RST}\item [SYSTEM\_TIMERGROUP1\_RST] Set this bit to reset TIMERGROUP1. (R/W)
\label{fielddesc:SYSTEMSPI3RST}\item [SYSTEM\_SPI3\_RST] Set this bit to reset SPI3. (R/W)
\label{fielddesc:SYSTEMPWM0RST}\item [SYSTEM\_PWM0\_RST] Set this bit to reset PWM0. (R/W)
\label{fielddesc:SYSTEMI2CEXT1RST}\item [SYSTEM\_I2C\_EXT1\_RST] Set this bit to reset I2C\_EXT1. (R/W)
\label{fielddesc:SYSTEMCANRST}\item [SYSTEM\_CAN\_RST] Set this bit to reset CAN. (R/W)
\label{fielddesc:SYSTEMPWM1RST}\item [SYSTEM\_PWM1\_RST] Set this bit to reset PWM1. (R/W)
\label{fielddesc:SYSTEMI2S1RST}\item [SYSTEM\_I2S1\_RST] Set this bit to reset I2S1. (R/W)
\label{fielddesc:SYSTEMUSBRST}\item [SYSTEM\_USB\_RST] Set this bit to reset USB. (R/W)
\label{fielddesc:SYSTEMUARTMEMRST}\item [SYSTEM\_UART\_MEM\_RST] Set this bit to reset UART\_MEM. (R/W)
\label{fielddesc:SYSTEMAPBSARADCRST}\item [SYSTEM\_APB\_SARADC\_RST] Set this bit to reset ADC controller. (R/W)
\label{fielddesc:SYSTEMSYSTIMERRST}\item [SYSTEM\_SYSTIMER\_RST] Set this bit to reset SYSTIMER. (R/W)
\label{fielddesc:SYSTEMADC2ARBRST}\item [SYSTEM\_ADC2\_ARB\_RST] Set this bit to reset ADC2\_ARB. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_PERIP\_RST\_EN1\_REG}{0x{}0024}\label{regdesc:SYSTEMPERIPRSTEN1REG}
\regfield{(reserved)}{21}{11}{000000000000000000000}%
\regfield{SYSTEM\_USB\_DEVICE\_RST}{1}{10}{{0}}%
\regfield{SYSTEM\_UART2\_RST}{1}{9}{{0}}%
\regfield{SYSTEM\_LCD\_CAM\_RST}{1}{8}{{1}}%
\regfield{SYSTEM\_SDIO\_HOST\_RST}{1}{7}{{1}}%
\regfield{SYSTEM\_DMA\_RST}{1}{6}{{1}}%
\regfield{SYSTEM\_CRYPTO\_HMAC\_RST}{1}{5}{{1}}%
\regfield{SYSTEM\_CRYPTO\_DS\_RST}{1}{4}{{1}}%
\regfield{SYSTEM\_CRYPTO\_RSA\_RST}{1}{3}{{1}}%
\regfield{SYSTEM\_CRYPTO\_SHA\_RST}{1}{2}{{1}}%
\regfield{SYSTEM\_CRYPTO\_AES\_RST}{1}{1}{{1}}%
\regfield{SYSTEM\_PERI\_BACKUP\_RST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMPERIBACKUPRST}\item [SYSTEM\_PERI\_BACKUP\_RST] Set this bit to reset BACKUP. (R/W)
\label{fielddesc:SYSTEMCRYPTOAESRST}\item [SYSTEM\_CRYPTO\_AES\_RST] Set this bit to reset CRYPTO\_AES. (R/W)
\label{fielddesc:SYSTEMCRYPTOSHARST}\item [SYSTEM\_CRYPTO\_SHA\_RST] Set this bit to reset CRYPTO\_SHA. (R/W)
\label{fielddesc:SYSTEMCRYPTORSARST}\item [SYSTEM\_CRYPTO\_RSA\_RST] Set this bit to reset CRYPTO\_RSA. (R/W)
\label{fielddesc:SYSTEMCRYPTODSRST}\item [SYSTEM\_CRYPTO\_DS\_RST] Set this bit to reset CRYPTO\_DS. (R/W)
\label{fielddesc:SYSTEMCRYPTOHMACRST}\item [SYSTEM\_CRYPTO\_HMAC\_RST] Set this bit to reset CRYPTO\_HMAC. (R/W)
\label{fielddesc:SYSTEMDMARST}\item [SYSTEM\_DMA\_RST] Set this bit to reset DMA. (R/W)
\label{fielddesc:SYSTEMSDIOHOSTRST}\item [SYSTEM\_SDIO\_HOST\_RST] Set this bit to reset SDIO\_HOST. (R/W)
\label{fielddesc:SYSTEMLCDCAMRST}\item [SYSTEM\_LCD\_CAM\_RST] Set this bit to reset LCD\_CAM. (R/W)
\label{fielddesc:SYSTEMUART2RST}\item [SYSTEM\_UART2\_RST] Set this bit to reset UART2. (R/W)
\label{fielddesc:SYSTEMUSBDEVICERST}\item [SYSTEM\_USB\_DEVICE\_RST] Set this bit to reset USB\_DEVICE. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_BT\_LPCK\_DIV\_FRAC\_REG}{0x{}002C}\label{regdesc:SYSTEMBTLPCKDIVFRACREG}
\regfield{(reserved)}{3}{29}{000}%
\regfield{SYSTEM\_LPCLK\_RTC\_EN}{1}{28}{{0}}%
\regfield{SYSTEM\_LPCLK\_SEL\_XTAL32K}{1}{27}{{0}}%
\regfield{SYSTEM\_LPCLK\_SEL\_XTAL}{1}{26}{{0}}%
\regfield{SYSTEM\_LPCLK\_SEL\_8M}{1}{25}{{1}}%
\regfield{SYSTEM\_LPCLK\_SEL\_RTC\_SLOW}{1}{24}{{0}}%
\regfield{(reserved)}{24}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMLPCLKSELRTCSLOW}\item [SYSTEM\_LPCLK\_SEL\_RTC\_SLOW] Set this bit to select RTC\_SLOW\_CLK as the low-power clock. (R/W)
\label{fielddesc:SYSTEMLPCLKSEL8M}\item [SYSTEM\_LPCLK\_SEL\_8M] Set this bit to select RC\_FAST\_CLK div n as the low-power clock. (R/W)
\label{fielddesc:SYSTEMLPCLKSELXTAL}\item [SYSTEM\_LPCLK\_SEL\_XTAL] Set this bit to select XTAL\_CLKL clock as the low-power clock. (R/W)
\label{fielddesc:SYSTEMLPCLKSELXTAL32K}\item [SYSTEM\_LPCLK\_SEL\_XTAL32K] Set this bit to select XTAL32K\_CLK clock as the low-power clock. (R/W)
\label{fielddesc:SYSTEMLPCLKRTCEN}\item [SYSTEM\_LPCLK\_RTC\_EN] Set this bit to enable the LOW\_POWER\_CLK clock. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_CPU\_INTR\_FROM\_CPU\_0\_REG}{0x{}0030}\label{regdesc:SYSTEMCPUINTRFROMCPU0REG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{SYSTEM\_CPU\_INTR\_FROM\_CPU\_0}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMCPUINTRFROMCPU0}\item [SYSTEM\_CPU\_INTR\_FROM\_CPU\_0] Set this bit to generate CPU interrupt 0. This bit needs to be reset by software in the ISR process. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_CPU\_INTR\_FROM\_CPU\_1\_REG}{0x{}0034}\label{regdesc:SYSTEMCPUINTRFROMCPU1REG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{SYSTEM\_CPU\_INTR\_FROM\_CPU\_1}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMCPUINTRFROMCPU1}\item [SYSTEM\_CPU\_INTR\_FROM\_CPU\_1] Set this bit to generate CPU interrupt 1. This bit needs to be reset by software in the ISR process. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_CPU\_INTR\_FROM\_CPU\_2\_REG}{0x{}0038}\label{regdesc:SYSTEMCPUINTRFROMCPU2REG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{SYSTEM\_CPU\_INTR\_FROM\_CPU\_2}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMCPUINTRFROMCPU2}\item [SYSTEM\_CPU\_INTR\_FROM\_CPU\_2] Set this bit to generate CPU interrupt 2. This bit needs to be reset by software in the ISR process. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_CPU\_INTR\_FROM\_CPU\_3\_REG}{0x{}003C}\label{regdesc:SYSTEMCPUINTRFROMCPU3REG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{SYSTEM\_CPU\_INTR\_FROM\_CPU\_3}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMCPUINTRFROMCPU3}\item [SYSTEM\_CPU\_INTR\_FROM\_CPU\_3] Set this bit to generate CPU interrupt 3. This bit needs to be reset by software in the ISR process. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_RSA\_PD\_CTRL\_REG}{0x{}0040}\label{regdesc:SYSTEMRSAPDCTRLREG}
\regfield{(reserved)}{29}{3}{00000000000000000000000000000}%
\regfield{SYSTEM\_RSA\_MEM\_FORCE\_PD}{1}{2}{{0}}%
\regfield{SYSTEM\_RSA\_MEM\_FORCE\_PU}{1}{1}{{0}}%
\regfield{SYSTEM\_RSA\_MEM\_PD}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMRSAMEMPD}\item [SYSTEM\_RSA\_MEM\_PD] Set this bit to send the RSA memory into retention state. This bit has the lowest priority, meaning it can be masked by the \hyperref[fielddesc:SYSTEMRSAMEMFORCEPU]{SYSTEM\_RSA\_MEM\_FORCE\_PU} field. When Digital Signature occupies the RSA, this bit is invalid. (R/W)
\label{fielddesc:SYSTEMRSAMEMFORCEPU}\item [SYSTEM\_RSA\_MEM\_FORCE\_PU] Set this bit to force the RSA memory to work as normal when the chip enters light sleep. This bit has the second highest priority, meaning it overrides the \hyperref[fielddesc:SYSTEMRSAMEMPD]{SYSTEM\_RSA\_MEM\_PD} field. (R/W)
\label{fielddesc:SYSTEMRSAMEMFORCEPD}\item [SYSTEM\_RSA\_MEM\_FORCE\_PD] Set this bit to send the RSA memory into retention state. This bit has the highest priority, meaning it sends the RSA memory into retention state regardless of the \hyperref[fielddesc:SYSTEMRSAMEMFORCEPU]{SYSTEM\_RSA\_MEM\_FORCE\_PU} field. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_EDMA\_CTRL\_REG}{0x{}0044}\label{regdesc:SYSTEMEDMACTRLREG}
\regfield{(reserved)}{30}{2}{000000000000000000000000000000}%
\regfield{SYSTEM\_EDMA\_RESET}{1}{1}{{0}}%
\regfield{SYSTEM\_EDMA\_CLK\_ON}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMEDMACLKON}\item [SYSTEM\_EDMA\_CLK\_ON] Set this bit to enable EDMA clock. (R/W)
\label{fielddesc:SYSTEMEDMARESET}\item [SYSTEM\_EDMA\_RESET] Set this bit to reset EDMA. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_CACHE\_CONTROL\_REG}{0x{}0048}\label{regdesc:SYSTEMCACHECONTROLREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{SYSTEM\_DCACHE\_RESET}{1}{3}{{0}}%
\regfield{SYSTEM\_DCACHE\_CLK\_ON}{1}{2}{{1}}%
\regfield{SYSTEM\_ICACHE\_RESET}{1}{1}{{0}}%
\regfield{SYSTEM\_ICACHE\_CLK\_ON}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMICACHECLKON}\item [SYSTEM\_ICACHE\_CLK\_ON] Set this bit to enable i-cache clock. (R/W)
\label{fielddesc:SYSTEMICACHERESET}\item [SYSTEM\_ICACHE\_RESET] Set this bit to reset i-cache. (R/W)
\label{fielddesc:SYSTEMDCACHECLKON}\item [SYSTEM\_DCACHE\_CLK\_ON] Set this bit to enable d-cache clock. (R/W)
\label{fielddesc:SYSTEMDCACHERESET}\item [SYSTEM\_DCACHE\_RESET] Set this bit to reset d-cache. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_EXTERNAL\_DEVICE\_ENCRYPT\_DECRYPT\_CONTROL\_REG}{0x{}004C}\label{regdesc:SYSTEMEXTERNALDEVICEENCRYPTDECRYPTCONTROLREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{\tiny{SYSTEM\_ENABLE\_DOWNLOAD\_MANUAL\_ENCRYPT}}{1}{3}{{0}}%
\regfield{\tiny{SYSTEM\_ENABLE\_DOWNLOAD\_G0CB\_DECRYPT}}{1}{2}{{0}}%
\regfield{\tiny{SYSTEM\_ENABLE\_DOWNLOAD\_DB\_ENCRYPT}}{1}{1}{{0}}%
\regfield{\tiny{SYSTEM\_ENABLE\_SPI\_MANUAL\_ENCRYPT}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMENABLESPIMANUALENCRYPT}\item [SYSTEM\_ENABLE\_SPI\_MANUAL\_ENCRYPT] Set this bit to enable Manual Encryption under SPI Boot mode. (R/W)
\label{fielddesc:SYSTEMENABLEDOWNLOADDBENCRYPT}\item [SYSTEM\_ENABLE\_DOWNLOAD\_DB\_ENCRYPT] Set this bit to enable Auto Encryption under Download Boot mode. (R/W)
\label{fielddesc:SYSTEMENABLEDOWNLOADG0CBDECRYPT}\item [SYSTEM\_ENABLE\_DOWNLOAD\_G0CB\_DECRYPT] Set this bit to enable Auto Decryption under Download Boot mode. (R/W)
\label{fielddesc:SYSTEMENABLEDOWNLOADMANUALENCRYPT}\item [SYSTEM\_ENABLE\_DOWNLOAD\_MANUAL\_ENCRYPT] Set this bit to enable Manual Encryption under Download Boot mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_RTC\_FASTMEM\_CONFIG\_REG}{0x{}0050}\label{regdesc:SYSTEMRTCFASTMEMCONFIGREG}
\regfield{SYSTEM\_RTC\_MEM\_CRC\_FINISH}{1}{31}{{0}}%
\regfield{SYSTEM\_RTC\_MEM\_CRC\_LEN}{11}{20}{{0x{}7ff}}%
\regfield{SYSTEM\_RTC\_MEM\_CRC\_ADDR}{11}{9}{{0x{}0}}%
\regfield{SYSTEM\_RTC\_MEM\_CRC\_START}{1}{8}{{0}}%
\regfield{(reserved)}{8}{0}{00000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMRTCMEMCRCSTART}\item [SYSTEM\_RTC\_MEM\_CRC\_START] Set this bit to start the CRC of RTC memory (R/W)
\label{fielddesc:SYSTEMRTCMEMCRCADDR}\item [SYSTEM\_RTC\_MEM\_CRC\_ADDR] This field is used to set address of RTC memory for CRC. (R/W)
\label{fielddesc:SYSTEMRTCMEMCRCLEN}\item [SYSTEM\_RTC\_MEM\_CRC\_LEN] This field is used to set length of RTC memory for CRC based on start address. (R/W)
\label{fielddesc:SYSTEMRTCMEMCRCFINISH}\item [SYSTEM\_RTC\_MEM\_CRC\_FINISH] This bit stores the status of RTC memory CRC. High level means finished while low level means not finished. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_RTC\_FASTMEM\_CRC\_REG}{0x{}0054}\label{regdesc:SYSTEMRTCFASTMEMCRCREG}
\regfield{SYSTEM\_RTC\_MEM\_CRC\_RES}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMRTCMEMCRCRES}\item [SYSTEM\_RTC\_MEM\_CRC\_RES] This field stores the CRC result of RTC memory. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_CLOCK\_GATE\_REG}{0x{}005C}\label{regdesc:SYSTEMCLOCKGATEREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{SYSTEM\_CLK\_EN}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMCLKEN}\item [SYSTEM\_CLK\_EN] Set this bit to enable the system clock. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_SYSCLK\_CONF\_REG}{0x{}0060}\label{regdesc:SYSTEMSYSCLKCONFREG}
\regfield{(reserved)}{13}{19}{0000000000000}%
\regfield{SYSTEM\_CLK\_XTAL\_FREQ}{7}{12}{{0}}%
\regfield{SYSTEM\_SOC\_CLK\_SEL}{2}{10}{{0}}%
\regfield{SYSTEM\_PRE\_DIV\_CNT}{10}{0}{{0x{}1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMPREDIVCNT}\item [SYSTEM\_PRE\_DIV\_CNT] This field is used to set the count of prescaler of XTAL\_CLK. For details, please refer to Table \ref{tab:resclk-periph-clks} in Chapter \ref{mod:resclk} \textit{\nameref{mod:resclk}}. (R/W)
\label{fielddesc:SYSTEMSOCCLKSEL}\item [SYSTEM\_SOC\_CLK\_SEL] This field is used to select SOC clock. For details, please refer to Table \ref{tab:resclk-cpu-clk-src} in Chapter \ref{mod:resclk} \textit{\nameref{mod:resclk}}. (R/W)
\label{fielddesc:SYSTEMCLKXTALFREQ}\item [SYSTEM\_CLK\_XTAL\_FREQ] This field is used to read XTAL frequency in MHz. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_DATE\_REG}{0x{}0FFC}\label{regdesc:SYSTEMDATEREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{SYSTEM\_DATE}{28}{0}{{0x{}2101220}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMDATE}\item [SYSTEM\_DATE] Version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}
