\documentclass[openany, 10pt]{book}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Find  10-readme-for-trm-repo.tex at:        %%%
%%% https://www.overleaf.com/read/bwdjvfjksvjy/ %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% >>> R?: marks a repo project setting number or important notice

% >>> R1: Configure chip-specific settings <<<
\usepackage{chip-spec-settings}

% Imports packages and global formatting settings
\usepackage{preamble-trm-repo}

% >>> R2: In file below, comment out the modules already included into
% this project to avoid warnings for multiple label definitions <<<
\myexternaldocument{temp-labels-en}

% Make text left-aligned and allow latex to break pages naturally, comment out for full justification
\raggedright
\raggedbottom

% Keep commented out!
% >>> Only uncomment to generate the list of added hypertargets <<<
%\toggletrue{addedhypertargets}


\begin{document}

\selectlanguage{english}
\setenglishformatting

% Initial checks make sure that all variables for cross-project shared
% content are configured correctly. If not, guidance will be provided.
\input{initial-checks}

\input{titlepage}
\clearpage
\input{preface__EN}
\clearpage
\input{glance__EN}

\tableofcontents
\clearpage
\listoftables
\clearpage
\listoffigures

% >>> R3: List all todo notes from the current project? <<<
% 'Yes' - uncomment the lines below; 'No' - comment out
% Don't forget to deactivate before publishing
%\todototoc
%\listoftodos
%{\let\clearpage\relax \listofdonetodos}


% Included modules
% Uncomment to include

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Module Group: System %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\part{Microprocessor and Master}

% Note: Updates may be necessary based on the specific SoC. For instance, Xtensa-based SoCs lack CPU descriptions, and certain SoCs may omit processor instruction extensions.

This part covers the essential processing elements of the system, diving into the microprocessor architecture with both high-performance and low-power CPUs. Details include trace encoding for debugging purposes and controllers for Direct Memory Access (DMA).

\subfileinclude{00-BUSARCH__EN}
\subfileinclude{01-RISCVCPU__EN}
\subfileinclude{02-RISCVTRACENC__EN}
\subfileinclude{03-ULP__EN}
\subfileinclude{04-DMA__EN}

\part{Memory Organization}

This part provides insights into the system's memory structure, discussing the organization and mapping of RAM, ROM, eFuse, and external memories, offering a framework for understanding memory-related subsystems.

\subfileinclude{05-SYSMEM__EN}
\subfileinclude{06-EFUSE__EN}

\part{System Component}

% Note: Tailor the description based on the specific components present in the SoC.

Encompassing a range of system-level functionalities, this part describes components related to system boot, clocks, GPIO, timers, watchdogs, debug assistance, event and interrupt handling, low-power management, and various system registers.

\subfileinclude{08-IOMUXGPIO__EN}
\subfileinclude{09-RESCLK__EN}
\subfileinclude{10-BOOTCTRL__EN}
\subfileinclude{11-INTMTRX__EN}
\subfileinclude{12-EVNTASKMATRIX__EN}
\subfileinclude{13-LOWPOWM__EN}
\subfileinclude{14-SYSTIMER__EN}
\subfileinclude{15-TIMG__EN}
\subfileinclude{16-WDT__EN}
\subfileinclude{17-RTCTIMER__EN}
\subfileinclude{18-PERMCTRL__EN}
\subfileinclude{19-SYSREG__EN}
\subfileinclude{20-DBGASSIST__EN}
\subfileinclude{21-PSDET__EN}

\part{Cryptography/Security Component}

Dedicated to security features, this part explores cryptographic accelerators like AES and ECC. It also covers digital signatures, random number generation, key management, and encryption/decryption algorithms, showcasing the SoC’s capabilities in cryptography and secure data processing.

\subfileinclude{22-AES__EN}
\subfileinclude{23-ECC__EN}
\subfileinclude{24-HMAC__EN}
\subfileinclude{25-RSA__EN}
\subfileinclude{26-SHA__EN}
\subfileinclude{27-DIGSIG__EN}
\subfileinclude{28-ECDSA__EN}
\subfileinclude{29-EXTMEMENCR__EN}
\subfileinclude{30-RNG__EN}
\subfileinclude{31-KEYMNG__EN}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Module Group: Peripherals %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\part{Connectivity Interface}

% Note: Update the description based on the actual components implemented in the SoC, e.g., some SoCs do not have RMT.

This part addresses the connectivity aspects of the system, describing components related to various communication interfaces like I2C, I2S, SPI, UART, USB, and more. The part also covers interfaces to generate signals used in remote control, motor control, LED control, etc.

\subfileinclude{32-UART__EN}
\subfileinclude{33-SPI__EN}
\subfileinclude{34-I2C__EN}
\subfileinclude{35-I2S__EN}
\subfileinclude{36-PCNT__EN}
\subfileinclude{37-USBSERIALJTAG__EN}
\subfileinclude{38-TWAI__EN}
\subfileinclude{47-SDIOSLAVE__EN}
\subfileinclude{39-LEDPWM__EN}
\subfileinclude{40-MCPWM__EN}
\subfileinclude{41-RMT__EN}
\subfileinclude{42-PARLIO__EN}
\subfileinclude{43-BITSCRM__EN}

\part{Analog Signal Processing}

% Note: Tailor the description based on the actual components implemented in the SoC.

This part describes components related to analog-to-digital conversion, voltage comparison, on-chip sensors, and features such as temperature sensing, demonstrating the system's capabilities in handling analog signals.

\subfileinclude{44-TMPSEN__EN}
\subfileinclude{45-ADC__EN}
\subfileinclude{46-ANACOM__EN}


%%%%%%%%%%%%%%%%
%%% Appendix %%%
%%%%%%%%%%%%%%%%

\part{Appendix}\label{appendix}

This part contains the following information starting from the next page:

\begin{itemize}
    \item \hyperref[sec:resources]{\textit{Related Documentation and Resources}}
    \item \hyperref[glossary]{\textit{Glossary}}
    \item \hyperref[programming-reserved-field]{\textit{Programming Reserved Register Field}}
    \item \hyperref[interrupt-config-registers]{\textit{Interrupt Configuration Registers}}
    \item \hyperref[revision-history]{\textit{Revision History}}
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Related Documentation and Resources %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\input{resources__EN}

\clearpage
\input{glossary__EN}

\clearpage
\input{programming-reserved-field__EN}

\clearpage
\input{interrupt_config_registers__EN}

\clearpage
\input{revision-history__EN}

\clearpage
\input{disclaimer-copyright__EN}

\end{document}
