
\begin{longtable}{ | p{4.0cm} | p{8.4cm} | c | c| }
\hline\rowcolor{lightgray}
Name & Description & Address & Access \\ \hline
\endfirsthead
\hline
\rowcolor{lightgray}
Name & Description & Address & Access  \\
\hline
\endhead
\endfoot

\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpcfg0} & Physical memory protection configuration. & 0x3A0 & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpcfg1} & Physical memory protection configuration. & 0x3A1 & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpcfg2} & Physical memory protection configuration. & 0x3A2 & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpcfg3} & Physical memory protection configuration. & 0x3A3 & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpaddr0} & Physical memory protection address register. & 0x3B0 & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpaddr1} & Physical memory protection address register. & 0x3B1 & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpaddr2} & Physical memory protection address register. & 0x3B2 & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpaddr3} & Physical memory protection address register. & 0x3B3 & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpaddr4} & Physical memory protection address register. & 0x3B4 & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpaddr5} & Physical memory protection address register. & 0x3B5 & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpaddr6} & Physical memory protection address register. & 0x3B6 & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpaddr7} & Physical memory protection address register. & 0x3B7 & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpaddr8} & Physical memory protection address register. & 0x3B8 & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpaddr9} & Physical memory protection address register. & 0x3B9 & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpaddr10} & Physical memory protection address register. & 0x3BA & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpaddr11} & Physical memory protection address register. & 0x3BB & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpaddr12} & Physical memory protection address register. & 0x3BC & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpaddr13} & Physical memory protection address register. & 0x3BD & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpaddr14} & Physical memory protection address register. & 0x3BE & R/W \\\hline
\hyperref[sec:riscvcpu-pmp-reg-desc]{pmpaddr15} & Physical memory protection address register. & 0x3BF & R/W \\\hline

\end{longtable}
