\begin{register}{H}{RTC\_CNTL\_TOUCH\_CTRL1\_REG}{0x{}0108}\label{regdesc:RTCCNTLRTCTOUCHCTRL1REG}
\regfield{RTC\_CNTL\_TOUCH\_MEAS\_NUM}{16}{16}{{0x{}1000}}%
\regfield{RTC\_CNTL\_TOUCH\_SLEEP\_CYCLES}{16}{0}{{0x{}100}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHSLEEPCYCLES}\item [RTC\_CNTL\_TOUCH\_SLEEP\_CYCLES] Set sleep cycles for touch timer. Clock: RTC\_SLOW\_CLK. (R/W)
\label{fielddesc:RTCCNTLTOUCHMEASNUM}\item [RTC\_CNTL\_TOUCH\_MEAS\_NUM] Configure measurement duration expressed in number of charge/discharge cycles. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TOUCH\_CTRL2\_REG}{0x{}010C}\label{regdesc:RTCCNTLRTCTOUCHCTRL2REG}
\regfield{RTC\_CNTL\_TOUCH\_CLKGATE\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_CLK\_FO}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_RESET}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_TIMER\_FORCE\_DONE}{2}{27}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_SLP\_CYC\_DIV}{2}{25}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_XPD\_WAIT}{8}{17}{{0x{}4}}%
\regfield{RTC\_CNTL\_TOUCH\_START\_FORCE}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_START\_EN}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_START\_FSM\_EN}{1}{14}{{1}}%
\regfield{RTC\_CNTL\_TOUCH\_SLP\_TIMER\_EN}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_DBIAS}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_REFC}{3}{9}{{0x{}0}}%
\regfield{RTC\_CNTL\_TOUCH\_XPD\_BIAS}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_DREFH}{2}{6}{{3}}%
\regfield{RTC\_CNTL\_TOUCH\_DREFL}{2}{4}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_DRANGE}{2}{2}{{3}}%
\regfield{(reserved)}{2}{0}{00}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHDRANGE}\item [RTC\_CNTL\_TOUCH\_DRANGE] Touch attenuation. (R/W)
\label{fielddesc:RTCCNTLTOUCHDREFL}\item [RTC\_CNTL\_TOUCH\_DREFL] Touch reference voltage low. (R/W)
\begin{itemize}
    \item 0: 0.5 V
    \item 1: 0.6 V
    \item 2: 0.7 V
    \item 3: 0.8 V
\end{itemize}

\label{fielddesc:RTCCNTLTOUCHDREFH}\item [RTC\_CNTL\_TOUCH\_DREFH] Touch reference voltage high. (R/W)
\begin{itemize}
    \item 0: 2.4 V
    \item 1: 2.5 V
    \item 2: 2.6 V
    \item 3: 2.7 V
\end{itemize}

\label{fielddesc:RTCCNTLTOUCHXPDBIAS}\item [RTC\_CNTL\_TOUCH\_XPD\_BIAS] Touch bias power switch. (R/W)
\label{fielddesc:RTCCNTLTOUCHREFC}\item [RTC\_CNTL\_TOUCH\_REFC] Touch pin 0 reference capacitance. (R/W)
\label{fielddesc:RTCCNTLTOUCHDBIAS}\item [RTC\_CNTL\_TOUCH\_DBIAS] 1: Use self bias. 0: Use bandgap bias. (R/W)
\label{fielddesc:RTCCNTLTOUCHSLPTIMEREN}\item [RTC\_CNTL\_TOUCH\_SLP\_TIMER\_EN] Touch timer enable bit. (R/W)
\label{fielddesc:RTCCNTLTOUCHSTARTFSMEN}\item [RTC\_CNTL\_TOUCH\_START\_FSM\_EN] 1: TOUCH\_START and TOUCH\_XPD are controlled by touch FSM. 0: TOUCH\_START and TOUCH\_XPD are controlled by software. (R/W)
\label{fielddesc:RTCCNTLTOUCHSTARTEN}\item [RTC\_CNTL\_TOUCH\_START\_EN] 1: Start touch FSM, only valid when RTC\_CNTL\_TOUCH\_START\_FORCE = 1. (R/W)
\label{fielddesc:RTCCNTLTOUCHSTARTFORCE}\item [RTC\_CNTL\_TOUCH\_START\_FORCE] 1: Start touch FSM by software. 0: Start touch FSM by timer. (R/W)
\label{fielddesc:RTCCNTLTOUCHXPDWAIT}\item [RTC\_CNTL\_TOUCH\_XPD\_WAIT] The waiting cycles between TOUCH\_START and TOUCH\_XPD. Clock: RTC\_FAST\_CLK. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_TOUCH\_CTRL2\_REG}{0x{}010C}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:RTCCNTLTOUCHSLPCYCDIV}\item [RTC\_CNTL\_TOUCH\_SLP\_CYC\_DIV] When a touch pin is active, sleep cycle could be divided by this number. (R/W)
\label{fielddesc:RTCCNTLTOUCHTIMERFORCEDONE}\item [RTC\_CNTL\_TOUCH\_TIMER\_FORCE\_DONE] Force touch timer done. (R/W)
\label{fielddesc:RTCCNTLTOUCHRESET}\item [RTC\_CNTL\_TOUCH\_RESET] Reset touch FSM via software. (R/W)
\label{fielddesc:RTCCNTLTOUCHCLKFO}\item [RTC\_CNTL\_TOUCH\_CLK\_FO] Touch clock force on. (R/W)
\label{fielddesc:RTCCNTLTOUCHCLKGATEEN}\item [RTC\_CNTL\_TOUCH\_CLKGATE\_EN] Touch clock enable bit. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TOUCH\_SCAN\_CTRL\_REG}{0x{}0110}\label{regdesc:RTCCNTLRTCTOUCHSCANCTRLREG}
\regfield{RTC\_CNTL\_TOUCH\_OUT\_RING}{4}{28}{{0x{}f}}%
\regfield{RTC\_CNTL\_TOUCH\_BUFDRV}{3}{25}{{0x{}0}}%
\regfield{RTC\_CNTL\_TOUCH\_SCAN\_PAD\_MAP}{15}{10}{{0x{}00}}%
\regfield{RTC\_CNTL\_TOUCH\_SHIELD\_PAD\_EN}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_INACTIVE\_CONNECTION}{1}{8}{{1}}%
\regfield{(reserved)}{5}{3}{00000}%
\regfield{RTC\_CNTL\_TOUCH\_DENOISE\_EN}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_DENOISE\_RES}{2}{0}{{2}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHDENOISERES}\item [RTC\_CNTL\_TOUCH\_DENOISE\_RES] De-noise resolution. (R/W)
\begin{itemize}
    \item 0: 12-bit
    \item 1: 10-bit
    \item 2: 8-bit
    \item 3: 4-bit
\end{itemize}
\label{fielddesc:RTCCNTLTOUCHDENOISEEN}\item [RTC\_CNTL\_TOUCH\_DENOISE\_EN] Touch pin 0 will be used to de-noise. (R/W)
\label{fielddesc:RTCCNTLTOUCHINACTIVECONNECTION}\item [RTC\_CNTL\_TOUCH\_INACTIVE\_CONNECTION] Inactive touch pins connect to, 1: GND, 0: HighZ. (R/W)
\label{fielddesc:RTCCNTLTOUCHSHIELDPADEN}\item [RTC\_CNTL\_TOUCH\_SHIELD\_PAD\_EN] Touch pin 14 will be used as shield\_pin. (R/W)
\label{fielddesc:RTCCNTLTOUCHSCANPADMAP}\item [RTC\_CNTL\_TOUCH\_SCAN\_PAD\_MAP] Pin enable map for touch scan mode. (R/W)
\label{fielddesc:RTCCNTLTOUCHBUFDRV}\item [RTC\_CNTL\_TOUCH\_BUFDRV] Touch 14 buffer driver strength. (R/W)
\label{fielddesc:RTCCNTLTOUCHOUTRING}\item [RTC\_CNTL\_TOUCH\_OUT\_RING] Select out one pin as guard\_ring. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TOUCH\_SLP\_THRES\_REG}{0x{}0114}\label{regdesc:RTCCNTLRTCTOUCHSLPTHRESREG}
\regfield{RTC\_CNTL\_TOUCH\_SLP\_PAD}{5}{27}{{0x{}f}}%
\regfield{RTC\_CNTL\_TOUCH\_SLP\_APPROACH\_EN}{1}{26}{{0}}%
\regfield{(reserved)}{4}{22}{0000}%
\regfield{RTC\_CNTL\_TOUCH\_SLP\_TH}{22}{0}{{0x{}0000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHSLPTH}\item [RTC\_CNTL\_TOUCH\_SLP\_TH] Set the threshold for sleep touch pin. (R/W)
\label{fielddesc:RTCCNTLTOUCHSLPAPPROACHEN}\item [RTC\_CNTL\_TOUCH\_SLP\_APPROACH\_EN] Enable the proximity mode of touch sleep pin. (R/W)
\label{fielddesc:RTCCNTLTOUCHSLPPAD}\item [RTC\_CNTL\_TOUCH\_SLP\_PAD] Select sleep pin. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TOUCH\_APPROACH\_REG}{0x{}0118}\label{regdesc:RTCCNTLRTCTOUCHAPPROACHREG}
\regfield{RTC\_CNTL\_TOUCH\_APPROACH\_MEAS\_TIME}{8}{24}{{80}}%
\regfield{RTC\_CNTL\_TOUCH\_SLP\_CHANNEL\_CLR}{1}{23}{{0}}%
\regfield{(reserved)}{23}{0}{00000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHSLPCHANNELCLR}\item [RTC\_CNTL\_TOUCH\_SLP\_CHANNEL\_CLR] Clear touch sleep channel. (WO)
\label{fielddesc:RTCCNTLTOUCHAPPROACHMEASTIME}\item [RTC\_CNTL\_TOUCH\_APPROACH\_MEAS\_TIME] Set the total measurement times for the pins in proximity mode. Range: 0 \verb+~+ 255. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TOUCH\_FILTER\_CTRL\_REG}{0x{}011C}\label{regdesc:RTCCNTLRTCTOUCHFILTERCTRLREG}
\regfield{RTC\_CNTL\_TOUCH\_FILTER\_EN}{1}{31}{{1}}%
\regfield{RTC\_CNTL\_TOUCH\_FILTER\_MODE}{3}{28}{{1}}%
\regfield{(reserved)}{3}{25}{{3}}%
\regfield{RTC\_CNTL\_TOUCH\_CONFIG3}{2}{23}{{1}}%
\regfield{RTC\_CNTL\_TOUCH\_NOISE\_THRES}{2}{21}{{1}}%
\regfield{RTC\_CNTL\_TOUCH\_CONFIG2}{2}{19}{{1}}%
\regfield{RTC\_CNTL\_TOUCH\_CONFIG1}{4}{15}{{5}}%
\regfield{RTC\_CNTL\_TOUCH\_JITTER\_STEP}{4}{11}{{1}}%
\regfield{RTC\_CNTL\_TOUCH\_SMOOTH\_LVL}{2}{9}{{0}}%
\regfield{(reserved)}{9}{0}{0000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHSMOOTHLVL}\item [RTC\_CNTL\_TOUCH\_SMOOTH\_LVL] Smooth filter factor. 0: Raw data. 1: IIR1/2. 2: IIR1/4. 3: IIR1/8. (R/W)
\label{fielddesc:RTCCNTLTOUCHJITTERSTEP}\item [RTC\_CNTL\_TOUCH\_JITTER\_STEP] Touch jitter step. Range: 0 \verb+~+ 15. (R/W)
\label{fielddesc:RTCCNTLTOUCHNEGNOISELIMIT}\item [RTC\_CNTL\_TOUCH\_CONFIG1] Internal configuration field. (R/W)
\label{fielddesc:RTCCNTLTOUCHNEGNOISETHRES}\item [RTC\_CNTL\_TOUCH\_CONFIG2] Internal configuration field. (R/W)
\label{fielddesc:RTCCNTLTOUCHNOISETHRES}\item [RTC\_CNTL\_TOUCH\_NOISE\_THRES] Active noise threshold. (R/W)
\label{fielddesc:RTCCNTLTOUCHHYSTERESIS}\item [RTC\_CNTL\_TOUCH\_CONFIG3] Internal configuration field. (R/W)
\label{fielddesc:RTCCNTLTOUCHFILTERMODE}\item [RTC\_CNTL\_TOUCH\_FILTER\_MODE] Set filter mode. (R/W)
\begin{itemize}
    \item 0: IIR 1/2
    \item 1: IIR 1/4
    \item 2: IIR 1/8
    \item 3: IIR 1/16
    \item 4: IIR 1/32
    \item 5: IIR 1/64
    \item 6: IIR 1/128
    \item 7: Jitter
\end{itemize}
\label{fielddesc:RTCCNTLTOUCHFILTEREN}\item [RTC\_CNTL\_TOUCH\_FILTER\_EN] Enable touch filter. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_TOUCH\_TIMEOUT\_CTRL\_REG}{0x{}0124}\label{regdesc:RTCCNTLRTCTOUCHTIMEOUTCTRLREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{RTC\_CNTL\_TOUCH\_TIMEOUT\_EN}{1}{22}{{1}}%
\regfield{RTC\_CNTL\_TOUCH\_TIMEOUT\_NUM}{22}{0}{{0x{}3fffff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHTIMEOUTNUM}\item [RTC\_CNTL\_TOUCH\_TIMEOUT\_NUM] Set touch timeout threshold. (R/W)
\label{fielddesc:RTCCNTLTOUCHTIMEOUTEN}\item [RTC\_CNTL\_TOUCH\_TIMEOUT\_EN] Enable touch timeout. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_TOUCH\_DAC\_REG}{0x{}014C}\label{regdesc:RTCCNTLTOUCHDACREG}
\regfield{RTC\_CNTL\_TOUCH\_PAD0\_DAC}{3}{29}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD1\_DAC}{3}{26}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD2\_DAC}{3}{23}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD3\_DAC}{3}{20}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD4\_DAC}{3}{17}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD5\_DAC}{3}{14}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD6\_DAC}{3}{11}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD7\_DAC}{3}{8}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD8\_DAC}{3}{5}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD9\_DAC}{3}{2}{{0}}%
\regfield{(reserved)}{2}{0}{00}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHPAD9DAC}\item [RTC\_CNTL\_TOUCH\_PAD9\_DAC] Configure the charge/discharge speed (slope) for touch sensor 9. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD8DAC}\item [RTC\_CNTL\_TOUCH\_PAD8\_DAC] Configure the charge/discharge speed (slope) for touch sensor 8. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD7DAC}\item [RTC\_CNTL\_TOUCH\_PAD7\_DAC] Configure the charge/discharge speed (slope) for touch sensor 7. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD6DAC}\item [RTC\_CNTL\_TOUCH\_PAD6\_DAC] Configure the charge/discharge speed (slope) for touch sensor 6. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD5DAC}\item [RTC\_CNTL\_TOUCH\_PAD5\_DAC] Configure the charge/discharge speed (slope) for touch sensor 5. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD4DAC}\item [RTC\_CNTL\_TOUCH\_PAD4\_DAC] Configure the charge/discharge speed (slope) for touch sensor 4. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD3DAC}\item [RTC\_CNTL\_TOUCH\_PAD3\_DAC] Configure the charge/discharge speed (slope) for touch sensor 3. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD2DAC}\item [RTC\_CNTL\_TOUCH\_PAD2\_DAC] Configure the charge/discharge speed (slope) for touch sensor 2. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD1DAC}\item [RTC\_CNTL\_TOUCH\_PAD1\_DAC] Configure the charge/discharge speed (slope) for touch sensor 1. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD0DAC}\item [RTC\_CNTL\_TOUCH\_PAD0\_DAC] Configure the charge/discharge speed (slope) for touch sensor 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TOUCH\_DAC1\_REG}{0x{}0150}\label{regdesc:RTCCNTLTOUCHDAC1REG}
\regfield{RTC\_CNTL\_TOUCH\_PAD10\_DAC}{3}{29}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD11\_DAC}{3}{26}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD12\_DAC}{3}{23}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD13\_DAC}{3}{20}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD14\_DAC}{3}{17}{{0}}%
\regfield{(reserved)}{17}{0}{00000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHPAD14DAC}\item [RTC\_CNTL\_TOUCH\_PAD14\_DAC] Configure the charge/discharge speed (slope) for touch sensor 14. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD13DAC}\item [RTC\_CNTL\_TOUCH\_PAD13\_DAC] Configure the charge/discharge speed (slope) for touch sensor 13. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD12DAC}\item [RTC\_CNTL\_TOUCH\_PAD12\_DAC] Configure the charge/discharge speed (slope) for touch sensor 12. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD11DAC}\item [RTC\_CNTL\_TOUCH\_PAD11\_DAC] Configure the charge/discharge speed (slope) for touch sensor 11. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD10DAC}\item [RTC\_CNTL\_TOUCH\_PAD10\_DAC] Configure the charge/discharge speed (slope) for touch sensor 10. (R/W)
\end{reglist}\end{regdesc}
\end{register}


