\begin{register}{H}{RTC\_CNTL\_TOUCH\_CTRL1\_REG}{0x{}0108}\label{regdesc:RTCCNTLRTCTOUCHCTRL1REG}
\regfield{RTC\_CNTL\_TOUCH\_MEAS\_NUM}{16}{16}{{0x{}1000}}%
\regfield{RTC\_CNTL\_TOUCH\_SLEEP\_CYCLES}{16}{0}{{0x{}100}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHSLEEPCYCLES}\item [RTC\_CNTL\_TOUCH\_SLEEP\_CYCLES] 设置触摸定时器的睡眠周期。时钟：RTC\_SLOW\_CLK。 (R/W)
\label{fielddesc:RTCCNTLTOUCHMEASNUM}\item [RTC\_CNTL\_TOUCH\_MEAS\_NUM] 设置测量阈值，即充放电的次数。(R/W) 
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TOUCH\_CTRL2\_REG}{0x{}010C}\label{regdesc:RTCCNTLRTCTOUCHCTRL2REG}
\regfield{RTC\_CNTL\_TOUCH\_CLKGATE\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_CLK\_FO}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_RESET}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_TIMER\_FORCE\_DONE}{2}{27}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_SLP\_CYC\_DIV}{2}{25}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_XPD\_WAIT}{8}{17}{{0x{}4}}%
\regfield{RTC\_CNTL\_TOUCH\_START\_FORCE}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_START\_EN}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_START\_FSM\_EN}{1}{14}{{1}}%
\regfield{RTC\_CNTL\_TOUCH\_SLP\_TIMER\_EN}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_DBIAS}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_REFC}{3}{9}{{0x{}0}}%
\regfield{RTC\_CNTL\_TOUCH\_XPD\_BIAS}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_DREFH}{2}{6}{{3}}%
\regfield{RTC\_CNTL\_TOUCH\_DREFL}{2}{4}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_DRANGE}{2}{2}{{3}}%
\regfield{(reserved)}{2}{0}{00}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHDRANGE}\item [RTC\_CNTL\_TOUCH\_DRANGE] 触摸传感器充放电衰减。 (R/W)
\label{fielddesc:RTCCNTLTOUCHDREFL}\item [RTC\_CNTL\_TOUCH\_DREFL] 触摸传感器充放电低阈值。 (R/W)
\begin{itemize}
    \item 0: 0.5 V
    \item 1: 0.6 V
    \item 2: 0.7 V
    \item 3: 0.8 V
\end{itemize}

\label{fielddesc:RTCCNTLTOUCHDREFH}\item [RTC\_CNTL\_TOUCH\_DREFH] 触摸传感器充放电高阈值。 (R/W)
\begin{itemize}
    \item 0: 2.4 V
    \item 1: 2.5 V
    \item 2: 2.6 V
    \item 3: 2.7 V
\end{itemize}

\label{fielddesc:RTCCNTLTOUCHXPDBIAS}\item [RTC\_CNTL\_TOUCH\_XPD\_BIAS] 触摸传感器的偏置电源开关。 (R/W)
\label{fielddesc:RTCCNTLTOUCHREFC}\item [RTC\_CNTL\_TOUCH\_REFC] 触摸管脚 0 的参考电容。(R/W)
\label{fielddesc:RTCCNTLTOUCHDBIAS}\item [RTC\_CNTL\_TOUCH\_DBIAS] 0：选择使用自身偏置。1：选择使用带隙偏置。 (R/W)
\label{fielddesc:RTCCNTLTOUCHSLPTIMEREN}\item [RTC\_CNTL\_TOUCH\_SLP\_TIMER\_EN] 触摸传感器的定时器使能位。 (R/W)
\label{fielddesc:RTCCNTLTOUCHSTARTFSMEN}\item [RTC\_CNTL\_TOUCH\_START\_FSM\_EN] 1：TOUCH\_START 和 TOUCH\_XPD 信号由 Touch FSM 控制；0：TOUCH\_START 和 TOUCH\_XPD 信号由软件控制。 (R/W)
\label{fielddesc:RTCCNTLTOUCHSTARTEN}\item [RTC\_CNTL\_TOUCH\_START\_EN] 1：启动 Touch FSM，仅当 RTC\_CNTL\_TOUCH\_START\_FORCE = 1 时有效。 (R/W)
\label{fielddesc:RTCCNTLTOUCHSTARTFORCE}\item [RTC\_CNTL\_TOUCH\_START\_FORCE] 1：Touch FSM 由软件启动；0：Touch FSM 由定时器启动。 (R/W)
\label{fielddesc:RTCCNTLTOUCHXPDWAIT}\item [RTC\_CNTL\_TOUCH\_XPD\_WAIT] 从 TOUCH\_START 到 TOUCH\_XPD 需等待的时钟周期。时钟：RTC\_FAST\_CLK。 (R/W)

\item [见下页]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_TOUCH\_CTRL2\_REG}{0x{}010C}
\begin{regdesc}\begin{reglist}
\item [接上页]

\label{fielddesc:RTCCNTLTOUCHSLPCYCDIV}\item [RTC\_CNTL\_TOUCH\_SLP\_CYC\_DIV] 触摸管脚处于活动状态时，睡眠周期可以除以此处设置的数值。 (R/W)
\label{fielddesc:RTCCNTLTOUCHTIMERFORCEDONE}\item [RTC\_CNTL\_TOUCH\_TIMER\_FORCE\_DONE] 强制结束 Touch 定时器。 (R/W)
\label{fielddesc:RTCCNTLTOUCHRESET}\item [RTC\_CNTL\_TOUCH\_RESET] 软件复位 Touch FSM。 (R/W)
\label{fielddesc:RTCCNTLTOUCHCLKFO}\item [RTC\_CNTL\_TOUCH\_CLK\_FO] 强制开启触摸传感器的时钟。 (R/W)
\label{fielddesc:RTCCNTLTOUCHCLKGATEEN}\item [RTC\_CNTL\_TOUCH\_CLKGATE\_EN] 触摸传感器时钟的使能位。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TOUCH\_SCAN\_CTRL\_REG}{0x{}0110}\label{regdesc:RTCCNTLRTCTOUCHSCANCTRLREG}
\regfield{RTC\_CNTL\_TOUCH\_OUT\_RING}{4}{28}{{0x{}f}}%
\regfield{RTC\_CNTL\_TOUCH\_BUFDRV}{3}{25}{{0x{}0}}%
\regfield{RTC\_CNTL\_TOUCH\_SCAN\_PAD\_MAP}{15}{10}{{0x{}00}}%
\regfield{RTC\_CNTL\_TOUCH\_SHIELD\_PAD\_EN}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_INACTIVE\_CONNECTION}{1}{8}{{1}}%
\regfield{(reserved)}{5}{3}{00000}%
\regfield{RTC\_CNTL\_TOUCH\_DENOISE\_EN}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_DENOISE\_RES}{2}{0}{{2}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHDENOISERES}\item [RTC\_CNTL\_TOUCH\_DENOISE\_RES] 设置去噪分辨率。 (R/W)
\begin{itemize}
    \item 0: 12-bit
    \item 1: 10-bit
    \item 2: 8-bit
    \item 3: 4-bit
\end{itemize}
\label{fielddesc:RTCCNTLTOUCHDENOISEEN}\item [RTC\_CNTL\_TOUCH\_DENOISE\_EN] 触摸管脚 0 将用于去噪。 (R/W)
\label{fielddesc:RTCCNTLTOUCHINACTIVECONNECTION}\item [RTC\_CNTL\_TOUCH\_INACTIVE\_CONNECTION] 配置非活动状态的触摸管脚的连接方式。0：连接至 HighZ。1：连接至 GND。 (R/W)
\label{fielddesc:RTCCNTLTOUCHSHIELDPADEN}\item [RTC\_CNTL\_TOUCH\_SHIELD\_PAD\_EN] 配置触摸管脚 14 用作屏蔽垫。 (R/W)
\label{fielddesc:RTCCNTLTOUCHSCANPADMAP}\item [RTC\_CNTL\_TOUCH\_SCAN\_PAD\_MAP] 触摸扫描模式下触摸管脚的使能位图。 (R/W)
\label{fielddesc:RTCCNTLTOUCHBUFDRV}\item [RTC\_CNTL\_TOUCH\_BUFDRV] 设置触摸管脚 14 的驱动强度。 (R/W)
\label{fielddesc:RTCCNTLTOUCHOUTRING}\item [RTC\_CNTL\_TOUCH\_OUT\_RING] 选择一个触摸管脚用作保护环。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TOUCH\_SLP\_THRES\_REG}{0x{}0114}\label{regdesc:RTCCNTLRTCTOUCHSLPTHRESREG}
\regfield{RTC\_CNTL\_TOUCH\_SLP\_PAD}{5}{27}{{0x{}f}}%
\regfield{RTC\_CNTL\_TOUCH\_SLP\_APPROACH\_EN}{1}{26}{{0}}%
\regfield{(reserved)}{4}{22}{0000}%
\regfield{RTC\_CNTL\_TOUCH\_SLP\_TH}{22}{0}{{0x{}0000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHSLPTH}\item [RTC\_CNTL\_TOUCH\_SLP\_TH] 设置睡眠管脚的阈值。 (R/W)
\label{fielddesc:RTCCNTLTOUCHSLPAPPROACHEN}\item [RTC\_CNTL\_TOUCH\_SLP\_APPROACH\_EN] 使能睡眠管脚的接近模式。 (R/W)
\label{fielddesc:RTCCNTLTOUCHSLPPAD}\item [RTC\_CNTL\_TOUCH\_SLP\_PAD] 选择一个触摸管脚用作睡眠管脚。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TOUCH\_APPROACH\_REG}{0x{}0118}\label{regdesc:RTCCNTLRTCTOUCHAPPROACHREG}
\regfield{RTC\_CNTL\_TOUCH\_APPROACH\_MEAS\_TIME}{8}{24}{{80}}%
\regfield{RTC\_CNTL\_TOUCH\_SLP\_CHANNEL\_CLR}{1}{23}{{0}}%
\regfield{(reserved)}{23}{0}{00000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHSLPCHANNELCLR}\item [RTC\_CNTL\_TOUCH\_SLP\_CHANNEL\_CLR] 清除睡眠通道。 (WO)
\label{fielddesc:RTCCNTLTOUCHAPPROACHMEASTIME}\item [RTC\_CNTL\_TOUCH\_APPROACH\_MEAS\_TIME] 设置成接近模式的管脚执行的所有测量次数。范围：0 \verb+~+ 255。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TOUCH\_FILTER\_CTRL\_REG}{0x{}011C}\label{regdesc:RTCCNTLRTCTOUCHFILTERCTRLREG}
\regfield{RTC\_CNTL\_TOUCH\_FILTER\_EN}{1}{31}{{1}}%
\regfield{RTC\_CNTL\_TOUCH\_FILTER\_MODE}{3}{28}{{1}}%
\regfield{(reserved)}{3}{25}{{3}}%
\regfield{RTC\_CNTL\_TOUCH\_CONFIG3}{2}{23}{{1}}%
\regfield{RTC\_CNTL\_TOUCH\_NOISE\_THRES}{2}{21}{{1}}%
\regfield{RTC\_CNTL\_TOUCH\_CONFIG2}{2}{19}{{1}}%
\regfield{RTC\_CNTL\_TOUCH\_CONFIG1}{4}{15}{{5}}%
\regfield{RTC\_CNTL\_TOUCH\_JITTER\_STEP}{4}{11}{{1}}%
\regfield{RTC\_CNTL\_TOUCH\_SMOOTH\_LVL}{2}{9}{{0}}%
\regfield{(reserved)}{9}{0}{0000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHSMOOTHLVL}\item [RTC\_CNTL\_TOUCH\_SMOOTH\_LVL] 配置平滑过滤系数。0：原始数据；1：IIR1/2；2：IIR1/4；3：IIR1/8。 (R/W)
\label{fielddesc:RTCCNTLTOUCHJITTERSTEP}\item [RTC\_CNTL\_TOUCH\_JITTER\_STEP] 配置抖动幅度。范围：0 \verb+~+ 15。 (R/W)
\label{fielddesc:RTCCNTLTOUCHNEGNOISELIMIT}\item [RTC\_CNTL\_TOUCH\_CONFIG1] 内部配置。 (R/W) 
\label{fielddesc:RTCCNTLTOUCHNEGNOISETHRES}\item [RTC\_CNTL\_TOUCH\_CONFIG2] 内部配置。 (R/W) 
\label{fielddesc:RTCCNTLTOUCHNOISETHRES}\item [RTC\_CNTL\_TOUCH\_NOISE\_THRES] 正噪声阈值。 (R/W)
\label{fielddesc:RTCCNTLTOUCHHYSTERESIS}\item [RTC\_CNTL\_TOUCH\_CONFIG3] 触摸迟滞。 (R/W)
\label{fielddesc:RTCCNTLTOUCHFILTERMODE}\item [RTC\_CNTL\_TOUCH\_FILTER\_MODE] 滤波模式选择。(R/W)
\begin{itemize}
    \item 0: IIR 1/2
    \item 1: IIR 1/4
    \item 2: IIR 1/8
    \item 3: IIR 1/16
    \item 4: IIR 1/32
    \item 5: IIR 1/64
    \item 6: IIR 1/128
    \item 7: Jitter
\end{itemize}
\label{fielddesc:RTCCNTLTOUCHFILTEREN}\item [RTC\_CNTL\_TOUCH\_FILTER\_EN] 使能噪声过滤功能。 (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_TOUCH\_TIMEOUT\_CTRL\_REG}{0x{}0124}\label{regdesc:RTCCNTLRTCTOUCHTIMEOUTCTRLREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{RTC\_CNTL\_TOUCH\_TIMEOUT\_EN}{1}{22}{{1}}%
\regfield{RTC\_CNTL\_TOUCH\_TIMEOUT\_NUM}{22}{0}{{0x{}3fffff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHTIMEOUTNUM}\item [RTC\_CNTL\_TOUCH\_TIMEOUT\_NUM] 设置触摸超时阈值。 (R/W)
\label{fielddesc:RTCCNTLTOUCHTIMEOUTEN}\item [RTC\_CNTL\_TOUCH\_TIMEOUT\_EN] 使能触摸超时。 (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_TOUCH\_DAC\_REG}{0x{}014C}\label{regdesc:RTCCNTLTOUCHDACREG}
\regfield{RTC\_CNTL\_TOUCH\_PAD0\_DAC}{3}{29}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD1\_DAC}{3}{26}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD2\_DAC}{3}{23}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD3\_DAC}{3}{20}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD4\_DAC}{3}{17}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD5\_DAC}{3}{14}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD6\_DAC}{3}{11}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD7\_DAC}{3}{8}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD8\_DAC}{3}{5}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD9\_DAC}{3}{2}{{0}}%
\regfield{(reserved)}{2}{0}{00}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHPAD9DAC}\item [RTC\_CNTL\_TOUCH\_PAD9\_DAC] 配置触摸传感器 9 的斜率。 (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD8DAC}\item [RTC\_CNTL\_TOUCH\_PAD8\_DAC] 配置触摸传感器 8 的斜率。 (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD7DAC}\item [RTC\_CNTL\_TOUCH\_PAD7\_DAC] 配置触摸传感器 7 的斜率。 (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD6DAC}\item [RTC\_CNTL\_TOUCH\_PAD6\_DAC] 配置触摸传感器 6 的斜率。 (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD5DAC}\item [RTC\_CNTL\_TOUCH\_PAD5\_DAC] 配置触摸传感器 5 的斜率。 (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD4DAC}\item [RTC\_CNTL\_TOUCH\_PAD4\_DAC] 配置触摸传感器 4 的斜率。 (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD3DAC}\item [RTC\_CNTL\_TOUCH\_PAD3\_DAC] 配置触摸传感器 3 的斜率。 (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD2DAC}\item [RTC\_CNTL\_TOUCH\_PAD2\_DAC] 配置触摸传感器 2 的斜率。 (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD1DAC}\item [RTC\_CNTL\_TOUCH\_PAD1\_DAC] 配置触摸传感器 1 的斜率。 (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD0DAC}\item [RTC\_CNTL\_TOUCH\_PAD0\_DAC] 配置触摸传感器 0 的斜率。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TOUCH\_DAC1\_REG}{0x{}0150}\label{regdesc:RTCCNTLTOUCHDAC1REG}
\regfield{RTC\_CNTL\_TOUCH\_PAD10\_DAC}{3}{29}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD11\_DAC}{3}{26}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD12\_DAC}{3}{23}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD13\_DAC}{3}{20}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD14\_DAC}{3}{17}{{0}}%
\regfield{(reserved)}{17}{0}{00000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHPAD14DAC}\item [RTC\_CNTL\_TOUCH\_PAD14\_DAC] 配置触摸传感器 14 的斜率。 (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD13DAC}\item [RTC\_CNTL\_TOUCH\_PAD13\_DAC] 配置触摸传感器 13 的斜率。 (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD12DAC}\item [RTC\_CNTL\_TOUCH\_PAD12\_DAC] 配置触摸传感器 12 的斜率。 (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD11DAC}\item [RTC\_CNTL\_TOUCH\_PAD11\_DAC] 配置触摸传感器 11 的斜率。 (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD10DAC}\item [RTC\_CNTL\_TOUCH\_PAD10\_DAC] 配置触摸传感器 10 的斜率。 (R/W)
\end{reglist}\end{regdesc}
\end{register}


