\begin{register}{H}{RTCIO\_RTC\_GPIO\_OUT\_REG}{0x0000}\label{regdesc:RTCIORTCGPIOOUTREG}
\regfield{RTCIO\_RTC\_GPIO\_OUT\_DATA}{18}{14}{xxxxxxxxxxxxxxxxxx}%
\regfield{(reserved)}{14}{0}{00000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_RTC\_GPIO\_OUT\_DATA]GPIO0-17 output register. Bit14 is GPIO[0], bit15 is GPIO[1], etc. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_RTC\_GPIO\_OUT\_W1TS\_REG}{0x0004}\label{regdesc:RTCIORTCGPIOOUTW1TSREG}
\regfield{RTCIO\_RTC\_GPIO\_OUT\_DATA\_W1TS}{18}{14}{xxxxxxxxxxxxxxxxxx}%
\regfield{(reserved)}{14}{0}{00000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_RTC\_GPIO\_OUT\_DATA\_W1TS]GPIO0-17 output set register. For every bit that is 1 in the value written here, the corresponding bit in RTCIO\_RTC\_GPIO\_OUT will be set. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_RTC\_GPIO\_OUT\_W1TC\_REG}{0x0008}\label{regdesc:RTCIORTCGPIOOUTW1TCREG}
\regfield{RTCIO\_RTC\_GPIO\_OUT\_DATA\_W1TC}{18}{14}{xxxxxxxxxxxxxxxxxx}%
\regfield{(reserved)}{14}{0}{00000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_RTC\_GPIO\_OUT\_DATA\_W1TC]GPIO0-17 output clear register. For every bit that is 1 in the value written here, the corresponding bit in RTCIO\_RTC\_GPIO\_OUT will be cleared. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_RTC\_GPIO\_ENABLE\_REG}{0x000C}\label{regdesc:RTCIORTCGPIOENABLEREG}
\regfield{RTCIO\_RTC\_GPIO\_ENABLE}{18}{14}{xxxxxxxxxxxxxxxxxx}%
\regfield{(reserved)}{14}{0}{00000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_RTC\_GPIO\_ENABLE]GPIO0-17 output enable. Bit14 is GPIO[0], bit15 is GPIO[1], etc. 1 means this GPIO pin is output. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_RTC\_GPIO\_ENABLE\_W1TS\_REG}{0x0010}\label{regdesc:RTCIORTCGPIOENABLEW1TSREG}
\regfield{RTCIO\_RTC\_GPIO\_ENABLE\_W1TS}{18}{14}{xxxxxxxxxxxxxxxxxx}%
\regfield{(reserved)}{14}{0}{00000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_RTC\_GPIO\_ENABLE\_W1TS]GPIO0-17 output enable set register. For every bit that is 1 in the value written here, the corresponding bit in RTCIO\_RTC\_GPIO\_ENABLE will be set. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_RTC\_GPIO\_ENABLE\_W1TC\_REG}{0x0014}\label{regdesc:RTCIORTCGPIOENABLEW1TCREG}
\regfield{RTCIO\_RTC\_GPIO\_ENABLE\_W1TC}{18}{14}{xxxxxxxxxxxxxxxxxx}%
\regfield{(reserved)}{14}{0}{00000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_RTC\_GPIO\_ENABLE\_W1TC]GPIO0-17 output enable clear register. For every bit that is 1 in the value written here, the corresponding bit in RTCIO\_RTC\_GPIO\_ENABLE will be cleared. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_RTC\_GPIO\_STATUS\_REG}{0x0018}\label{regdesc:RTCIORTCGPIOSTATUSREG}
\regfield{RTCIO\_RTC\_GPIO\_STATUS\_INT}{18}{14}{xxxxxxxxxxxxxxxxxx}%
\regfield{(reserved)}{14}{0}{00000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_RTC\_GPIO\_STATUS\_INT]GPIO0-17 interrupt status. Bit14 is GPIO[0], bit15 is GPIO[1], etc. This register should be used together with RTCIO\_RTC\_GPIO\_PIN\textcolor{red}{\it{n}}\_INT\_TYPE in RTCIO\_RTC\_GPIO\_PIN\textcolor{red}{\it{n}}\_REG. 1: corresponding interrupt; 0: no interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_RTC\_GPIO\_STATUS\_W1TS\_REG}{0x001C}\label{regdesc:RTCIORTCGPIOSTATUSW1TSREG}
\regfield{RTCIO\_RTC\_GPIO\_STATUS\_INT\_W1TS}{18}{14}{xxxxxxxxxxxxxxxxxx}%
\regfield{(reserved)}{14}{0}{00000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_RTC\_GPIO\_STATUS\_INT\_W1TS]GPIO0-17 interrupt set register. For every bit that is 1 in the value written here, the corresponding bit in RTCIO\_RTC\_GPIO\_STATUS\_INT will be set. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_RTC\_GPIO\_STATUS\_W1TC\_REG}{0x0020}\label{regdesc:RTCIORTCGPIOSTATUSW1TCREG}
\regfield{RTCIO\_RTC\_GPIO\_STATUS\_INT\_W1TC}{18}{14}{xxxxxxxxxxxxxxxxxx}%
\regfield{(reserved)}{14}{0}{00000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_RTC\_GPIO\_STATUS\_INT\_W1TC]GPIO0-17 interrupt clear register. For every bit that is 1 in the value written here, the corresponding bit in RTCIO\_RTC\_GPIO\_STATUS\_INT will be cleared. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_RTC\_GPIO\_IN\_REG}{0x0024}\label{regdesc:RTCIORTCGPIOINREG}
\regfield{RTCIO\_RTC\_GPIO\_IN\_NEXT}{18}{14}{xxxxxxxxxxxxxxxxxx}%
\regfield{(reserved)}{14}{0}{00000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_RTC\_GPIO\_IN\_NEXT]GPIO0-17 input value. Bit14 is GPIO[0], bit15 is GPIO[1], etc. Each bit represents a pin input value, 1 for high level, and 0 for low level. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_RTC\_GPIO\_PIN\textcolor{red}{\it{n}}\_REG (\textcolor{red}{\it{n}}: 0-17)}{0x28+4*\textcolor{red}{\it{n}}}\label{regdesc:RTCIORTCGPIOPINnREG}
\regfield{(reserved)}{21}{11}{000000000000000000000}%
\regfield{RTCIO\_RTC\_GPIO\_PIN\textcolor{red}{\it{n}}\_WAKEUP\_ENABLE}{1}{10}{x}%
\regfield{RTCIO\_RTC\_GPIO\_PIN\textcolor{red}{\it{n}}\_INT\_TYPE}{3}{7}{xxx}%
\regfield{(reserved)}{4}{3}{0000}%
\regfield{RTCIO\_RTC\_GPIO\_PIN\textcolor{red}{\it{n}}\_PAD\_DRIVER}{1}{2}{x}%
\regfield{(reserved)}{2}{0}{00}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_RTC\_GPIO\_PIN\textcolor{red}{\it{n}}\_WAKEUP\_ENABLE]GPIO wake-up enable. This will only wake up the ESP32 from Light-sleep. (R/W)
\item [RTCIO\_RTC\_GPIO\_PIN\textcolor{red}{\it{n}}\_INT\_TYPE]GPIO interrupt type selection. (R/W) \\0: GPIO interrupt disable; \\1: rising edge trigger; \\2: falling edge trigger; \\3: any edge trigger; \\4: low level trigger; \\5: high level trigger.
\item [RTCIO\_RTC\_GPIO\_PIN\textcolor{red}{\it{n}}\_PAD\_DRIVER]Pin driver selection. 0: normal output; 1: open drain. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\clearpage
\begin{register}{H}{RTCIO\_DIG\_PAD\_HOLD\_REG}{0x0074}\label{regdesc:RTCIODIGPADHOLDREG}
\regfield{}{32}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_DIG\_PAD\_HOLD\_REG]Selects the digital pins which should be put on hold. While 0 allows normal operation, 1 puts the pin on hold. (R/W)
\end{reglist}\end{regdesc}
\end{register}
\begin{longtable}[c]{ | p{5.5cm} | p{7.5cm} | }
\caption{Mapping of Bits to Pins}\label{tab:hold-bit-mapping}
\\\hline
\rowcolor{lightgray}
\textbf{Name} & \textbf{Description} \\ \hline
\endhead
Bit[0] & Set to 1 to enable the Hold function of pin U0RXD\\\hline
Bit[1] & Set to 1 to enable the Hold function of pin U0TXD\\\hline
Bit[2] & Set to 1 to enable the Hold function of pin SD\_CLK\\\hline
Bit[3] & Set to 1 to enable the Hold function of pin SD\_DATA0\\\hline
Bit[4] & Set to 1 to enable the Hold function of pin SD\_DATA1\\\hline
Bit[5] & Set to 1 to enable the Hold function of pin SD\_DATA2\\\hline
Bit[6] & Set to 1 to enable the Hold function of pin SD\_DATA3\\\hline
Bit[7] & Set to 1 to enable the Hold function of pin SD\_CMD\\\hline
Bit[8] & Set to 1 to enable the Hold function of pin GPIO5\\\hline
Bit[9] & Set to 1 to enable the Hold function of pin GPIO16\\\hline
Bit[10] & Set to 1 to enable the Hold function of pin GPIO17\\\hline
Bit[11] & Set to 1 to enable the Hold function of pin GPIO18\\\hline
Bit[12] & Set to 1 to enable the Hold function of pin GPIO19\\\hline
Bit[13] & Set to 1 to enable the Hold function of pin GPIO20$^1$\\\hline
Bit[14] & Set to 1 to enable the Hold function of pin GPIO21\\\hline
Bit[15] & Set to 1 to enable the Hold function of pin GPIO22\\\hline
Bit[16] & Set to 1 to enable the Hold function of pin GPIO23\\\hline
\end{longtable}

\vspace {-1em}
\begin{small}
\begin{enumerate}
  \item GPIO20 is only available for ESP32-PICO-V3 and ESP32-PICO-V3-02. Please refer to \href{https://www.espressif.com/sites/default/files/documentation/esp32-pico_series_datasheet_en.pdf}{\textit{ESP32-PICO Series Datasheet}} for more information.\\
\end{enumerate}
\end{small}


\begin{register}{H}{RTCIO\_SENSOR\_PADS\_REG}{0x007C}\label{regdesc:RTCIOSENSORPADSREG}
\regfield{RTCIO\_SENSOR\_SENSE1\_HOLD}{1}{31}{0}%
\regfield{RTCIO\_SENSOR\_SENSE2\_HOLD}{1}{30}{0}%
\regfield{RTCIO\_SENSOR\_SENSE3\_HOLD}{1}{29}{0}%
\regfield{RTCIO\_SENSOR\_SENSE4\_HOLD}{1}{28}{0}%
\regfield{RTCIO\_SENSOR\_SENSE1\_MUX\_SEL}{1}{27}{0}%
\regfield{RTCIO\_SENSOR\_SENSE2\_MUX\_SEL}{1}{26}{0}%
\regfield{RTCIO\_SENSOR\_SENSE3\_MUX\_SEL}{1}{25}{0}%
\regfield{RTCIO\_SENSOR\_SENSE4\_MUX\_SEL}{1}{24}{0}%
\regfield{RTCIO\_SENSOR\_SENSE1\_FUN\_SEL}{2}{22}{{0}}%
\regfield{RTCIO\_SENSOR\_SENSE1\_SLP\_SEL}{1}{21}{0}%
\regfield{RTCIO\_SENSOR\_SENSE1\_SLP\_IE}{1}{20}{0}%
\regfield{RTCIO\_SENSOR\_SENSE1\_FUN\_IE}{1}{19}{0}%
\regfield{RTCIO\_SENSOR\_SENSE2\_FUN\_SEL}{2}{17}{{0}}%
\regfield{RTCIO\_SENSOR\_SENSE2\_SLP\_SEL}{1}{16}{0}%
\regfield{RTCIO\_SENSOR\_SENSE2\_SLP\_IE}{1}{15}{0}%
\regfield{RTCIO\_SENSOR\_SENSE2\_FUN\_IE}{1}{14}{0}%
\regfield{RTCIO\_SENSOR\_SENSE3\_FUN\_SEL}{2}{12}{{0}}%
\regfield{RTCIO\_SENSOR\_SENSE3\_SLP\_SEL}{1}{11}{0}%
\regfield{RTCIO\_SENSOR\_SENSE3\_SLP\_IE}{1}{10}{0}%
\regfield{RTCIO\_SENSOR\_SENSE3\_FUN\_IE}{1}{9}{0}%
\regfield{RTCIO\_SENSOR\_SENSE4\_FUN\_SEL}{2}{7}{{0}}%
\regfield{RTCIO\_SENSOR\_SENSE4\_SLP\_SEL}{1}{6}{0}%
\regfield{RTCIO\_SENSOR\_SENSE4\_SLP\_IE}{1}{5}{0}%
\regfield{RTCIO\_SENSOR\_SENSE4\_FUN\_IE}{1}{4}{0}%
\regfield{(reserved)}{4}{0}{0000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_SENSOR\_SENSE\textcolor{red}{\it{n}}\_HOLD]Set to 1 to hold the output value on sense\textcolor{red}{\it{n}}; 0 is for normal operation. (R/W)
\item [RTCIO\_SENSOR\_SENSE\textcolor{red}{\it{n}}\_MUX\_SEL]1: route sense\textcolor{red}{\it{n}} to the RTC block; 0: route sense\textcolor{red}{\it{n}} to the digital IO\_MUX. (R/W) 
\item [RTCIO\_SENSOR\_SENSE\textcolor{red}{\it{n}}\_FUN\_SEL]Select the RTC IO\_MUX function for this pin. 0:  select Function 0. (R/W)
\item [RTCIO\_SENSOR\_SENSE\textcolor{red}{\it{n}}\_SLP\_SEL]Selection of sleep mode for the pin: set to 1 to put the pin in sleep mode. (R/W)
\item [RTCIO\_SENSOR\_SENSE\textcolor{red}{\it{n}}\_SLP\_IE]Input enable of the pin in sleep mode. 1: enabled; 0: disabled. (R/W)
\item [RTCIO\_SENSOR\_SENSE\textcolor{red}{\it{n}}\_FUN\_IE]Input enable of the pin. 1: enabled; 0: disabled. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_ADC\_PAD\_REG}{0x0080}\label{regdesc:RTCIOADCPADREG}
\regfield{RTCIO\_ADC\_ADC1\_HOLD}{1}{31}{0}%
\regfield{RTCIO\_ADC\_ADC2\_HOLD}{1}{30}{0}%
\regfield{RTCIO\_ADC\_ADC1\_MUX\_SEL}{1}{29}{0}%
\regfield{RTCIO\_ADC\_ADC2\_MUX\_SEL}{1}{28}{0}%
\regfield{RTCIO\_ADC\_ADC1\_FUN\_SEL}{2}{26}{{0}}%
\regfield{RTCIO\_ADC\_ADC1\_SLP\_SEL}{1}{25}{0}%
\regfield{RTCIO\_ADC\_ADC1\_SLP\_IE}{1}{24}{0}%
\regfield{RTCIO\_ADC\_ADC1\_FUN\_IE}{1}{23}{0}%
\regfield{RTCIO\_ADC\_ADC2\_FUN\_SEL}{2}{21}{{0}}%
\regfield{RTCIO\_ADC\_ADC2\_SLP\_SEL}{1}{20}{0}%
\regfield{RTCIO\_ADC\_ADC2\_SLP\_IE}{1}{19}{0}%
\regfield{RTCIO\_ADC\_ADC2\_FUN\_IE}{1}{18}{0}%
\regfield{(reserved)}{18}{0}{000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_ADC\_ADC\textcolor{red}{\it{n}}\_HOLD]Set to 1 to hold the output value on the pin; 0 is for normal operation. (R/W)
\item [RTCIO\_ADC\_ADC\textcolor{red}{\it{n}}\_MUX\_SEL]0: route pin to the digital IO\_MUX; (R/W) \\1: route pin to the RTC block.
\item [RTCIO\_ADC\_ADC\textcolor{red}{\it{n}}\_FUN\_SEL]Select the RTC function for this pin. 0: select Function 0; 3: select Function 1.  (R/W)
\item [RTCIO\_ADC\_ADC\textcolor{red}{\it{n}}\_SLP\_SEL]Signal selection of pin's sleep mode. Set this bit to 1 to put the pin to sleep. (R/W)
\item [RTCIO\_ADC\_ADC\textcolor{red}{\it{n}}\_SLP\_IE]Input enable of the pin in sleep mode. 1 enabled; 0 disabled. (R/W)
\item [RTCIO\_ADC\_ADC\textcolor{red}{\it{n}}\_FUN\_IE]Input enable of the pin. 1 enabled; 0 disabled. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_PAD\_DAC1\_REG}{0x0084}\label{regdesc:RTCIOPADDAC1REG}
\regfield{RTCIO\_PAD\_PDAC1\_DRV}{2}{30}{{2}}%
\regfield{RTCIO\_PAD\_PDAC1\_HOLD}{1}{29}{0}%
\regfield{RTCIO\_PAD\_PDAC1\_RDE}{1}{28}{0}%
\regfield{RTCIO\_PAD\_PDAC1\_RUE}{1}{27}{0}%
\regfield{RTCIO\_PAD\_PDAC1\_DAC}{8}{19}{{0}}%
\regfield{RTCIO\_PAD\_PDAC1\_XPD\_DAC}{1}{18}{0}%
\regfield{RTCIO\_PAD\_PDAC1\_MUX\_SEL}{1}{17}{0}%
\regfield{RTCIO\_PAD\_PDAC1\_FUN\_SEL}{2}{15}{{0}}%
\regfield{RTCIO\_PAD\_PDAC1\_SLP\_SEL}{1}{14}{0}%
\regfield{RTCIO\_PAD\_PDAC1\_SLP\_IE}{1}{13}{0}%
\regfield{RTCIO\_PAD\_PDAC1\_SLP\_OE}{1}{12}{0}%
\regfield{RTCIO\_PAD\_PDAC1\_FUN\_IE}{1}{11}{0}%
\regfield{RTCIO\_PAD\_PDAC1\_DAC\_XPD\_FORCE}{1}{10}{0}%
\regfield{(reserved)}{10}{0}{0000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_PAD\_PDAC1\_DRV]Select the drive strength of the pin. (R/W)
\item [RTCIO\_PAD\_PDAC1\_HOLD]Set to 1 to hold the output value on the pin; set to 0 for normal operation. (R/W)
\item [RTCIO\_PAD\_PDAC1\_RDE]1: Pull-down on pin enabled; 0: Pull-down disabled. (R/W)
\item [RTCIO\_PAD\_PDAC1\_RUE]1: Pull-up on pin enabled; 0: Pull-up disabled. (R/W)
\item [RTCIO\_PAD\_PDAC1\_DAC]Pin DAC1 output value.  (R/W)
\item [RTCIO\_PAD\_PDAC1\_XPD\_DAC]Power on DAC1. Usually, PDAC1 needs to be tristated if we power on the DAC, i.e. IE=0, OE=0, RDE=0, RUE=0. (R/W)
\item [RTCIO\_PAD\_PDAC1\_MUX\_SEL]0: route pin to the digital IO\_MUX; (R/W) \\1: route to the RTC block.
\item [RTCIO\_PAD\_PDAC1\_FUN\_SEL]the functional selection signal of the pin. (R/W)
\item [RTCIO\_PAD\_PDAC1\_SLP\_SEL]Sleep mode selection signal of the pin. Set this bit to 1 to put the pin to sleep. (R/W)
\item [RTCIO\_PAD\_PDAC1\_SLP\_IE]Input enable of the pin in sleep mode. 1: enabled; 0: disabled. (R/W)
\item [RTCIO\_PAD\_PDAC1\_SLP\_OE]Output enable of the pin. 1: enabled ; 0: disabled. (R/W)
\item [RTCIO\_PAD\_PDAC1\_FUN\_IE]Input enable of the pin. 1: enabled it; 0: disabled. (R/W)
\item [RTCIO\_PAD\_PDAC1\_DAC\_XPD\_FORCE]Power on DAC1. Usually, we need to tristate PDAC1 if we power on the DAC, i.e. IE=0, OE=0, RDE=0, RUE=0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_PAD\_DAC2\_REG}{0x0088}\label{regdesc:RTCIOPADDAC2REG}
\regfield{RTCIO\_PAD\_PDAC2\_DRV}{2}{30}{{2}}%
\regfield{RTCIO\_PAD\_PDAC2\_HOLD}{1}{29}{0}%
\regfield{RTCIO\_PAD\_PDAC2\_RDE}{1}{28}{0}%
\regfield{RTCIO\_PAD\_PDAC2\_RUE}{1}{27}{0}%
\regfield{RTCIO\_PAD\_PDAC2\_DAC}{8}{19}{{0}}%
\regfield{RTCIO\_PAD\_PDAC2\_XPD\_DAC}{1}{18}{0}%
\regfield{RTCIO\_PAD\_PDAC2\_MUX\_SEL}{1}{17}{0}%
\regfield{RTCIO\_PAD\_PDAC2\_FUN\_SEL}{2}{15}{{0}}%
\regfield{RTCIO\_PAD\_PDAC2\_SLP\_SEL}{1}{14}{0}%
\regfield{RTCIO\_PAD\_PDAC2\_SLP\_IE}{1}{13}{0}%
\regfield{RTCIO\_PAD\_PDAC2\_SLP\_OE}{1}{12}{0}%
\regfield{RTCIO\_PAD\_PDAC2\_FUN\_IE}{1}{11}{0}%
\regfield{RTCIO\_PAD\_PDAC2\_DAC\_XPD\_FORCE}{1}{10}{0}%
\regfield{(reserved)}{10}{0}{0000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_PAD\_PDAC2\_DRV]Select the drive strength of the pin. (R/W)
\item [RTCIO\_PAD\_PDAC2\_HOLD]Set to 1 to hold the output value on the pin; 0 is for normal operation. (R/W)
\item [RTCIO\_PAD\_PDAC2\_RDE]1: Pull-down on pin enabled; 0: Pull-down disabled. (R/W)
\item [RTCIO\_PAD\_PDAC2\_RUE]1: Pull-up on pin enabled; 0: Pull-up disabled. (R/W)
\item [RTCIO\_PAD\_PDAC2\_DAC]Pin DAC2 output value.  (R/W)
\item [RTCIO\_PAD\_PDAC2\_XPD\_DAC]Power on DAC2. PDAC2 needs to be tristated if we power on the DAC, i.e. IE=0, OE=0, RDE=0, RUE=0. (R/W)
\item [RTCIO\_PAD\_PDAC2\_MUX\_SEL]0: route pin to the digital IO\_MUX; (R/W) \\1: route to the RTC block.
\item [RTCIO\_PAD\_PDAC2\_FUN\_SEL]Select the RTC function for this pin. 0: select Function 0.  (R/W)
\item [RTCIO\_PAD\_PDAC2\_SLP\_SEL]Sleep mode selection signal of the pin. Set this bit to 1 to put the pin to sleep. (R/W)
\item [RTCIO\_PAD\_PDAC2\_SLP\_IE]Input enable of the pin in sleep mode. 1: enabled; 0: disabled. (R/W)
\item [RTCIO\_PAD\_PDAC2\_SLP\_OE]Output enable of the pin. 1: enabled; 0: disabled. (R/W)
\item [RTCIO\_PAD\_PDAC2\_FUN\_IE]Input  enable of the pin. 1: enabled; 0: disabled. (R/W)
\item [RTCIO\_PAD\_PDAC2\_DAC\_XPD\_FORCE]Power on DAC2. Usually, we need to tristate PDAC2 if we power on the DAC, i.e. IE=0, OE=0, RDE=0, RUE=0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_XTAL\_32K\_PAD\_REG}{0x008C}\label{regdesc:RTCIOXTAL32KPADREG}
\regfield{RTCIO\_XTAL\_X32N\_DRV}{2}{30}{{2}}%
\regfield{RTCIO\_XTAL\_X32N\_HOLD}{1}{29}{0}%
\regfield{RTCIO\_XTAL\_X32N\_RDE}{1}{28}{0}%
\regfield{RTCIO\_XTAL\_X32N\_RUE}{1}{27}{0}%
\regfield{RTCIO\_XTAL\_X32P\_DRV}{2}{25}{{2}}%
\regfield{RTCIO\_XTAL\_X32P\_HOLD}{1}{24}{0}%
\regfield{RTCIO\_XTAL\_X32P\_RDE}{1}{23}{0}%
\regfield{RTCIO\_XTAL\_X32P\_RUE}{1}{22}{0}%
\regfield{RTCIO\_XTAL\_DAC\_XTAL\_32K}{2}{20}{01}%
\regfield{RTCIO\_XTAL\_XPD\_XTAL\_32K}{1}{19}{0}%
\regfield{RTCIO\_XTAL\_X32N\_MUX\_SEL}{1}{18}{0}%
\regfield{RTCIO\_XTAL\_X32P\_MUX\_SEL}{1}{17}{0}%
\regfield{RTCIO\_XTAL\_X32N\_FUN\_SEL}{2}{15}{{0}}%
\regfield{RTCIO\_XTAL\_X32N\_SLP\_SEL}{1}{14}{0}%
\regfield{RTCIO\_XTAL\_X32N\_SLP\_IE}{1}{13}{0}%
\regfield{RTCIO\_XTAL\_X32N\_SLP\_OE}{1}{12}{0}%
\regfield{RTCIO\_XTAL\_X32N\_FUN\_IE}{1}{11}{0}%
\regfield{RTCIO\_XTAL\_X32P\_FUN\_SEL}{2}{9}{{0}}%
\regfield{RTCIO\_XTAL\_X32P\_SLP\_SEL}{1}{8}{0}%
\regfield{RTCIO\_XTAL\_X32P\_SLP\_IE}{1}{7}{0}%
\regfield{RTCIO\_XTAL\_X32P\_SLP\_OE}{1}{6}{0}%
\regfield{RTCIO\_XTAL\_X32P\_FUN\_IE}{1}{5}{0}%
\regfield{RTCIO\_XTAL\_DRES\_XTAL\_32K}{2}{3}{10}%
\regfield{RTCIO\_XTAL\_DBIAS\_XTAL\_32K}{2}{1}{00}%
\regfield{(reserved)}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_XTAL\_X32N\_DRV]Select the drive strength of the pin. (R/W)
\item [RTCIO\_XTAL\_X32N\_HOLD]Set to 1 to hold the output value on the pin; 0 is for normal operation. (R/W)
\item [RTCIO\_XTAL\_X32N\_RDE]1: Pull-down on pin enabled; 0: Pull-down disabled. (R/W)
\item [RTCIO\_XTAL\_X32N\_RUE]1: Pull-up on pin enabled; 0: Pull-up disabled. (R/W)
\item [RTCIO\_XTAL\_X32P\_DRV]Select the drive strength of the pin. (R/W)
\item [RTCIO\_XTAL\_X32P\_HOLD]Set to 1 to hold the output value on the pin, 0 is for normal operation. (R/W)
\item [RTCIO\_XTAL\_X32P\_RDE]1: Pull-down on pin enabled; 0: Pull-down disabled. (R/W)
\item [RTCIO\_XTAL\_X32P\_RUE]1: Pull-up on pin enabled; 0: Pull-up disabled. (R/W)
\item [RTCIO\_XTAL\_DAC\_XTAL\_32K]32K XTAL bias current DAC value. (R/W)
\item [RTCIO\_XTAL\_XPD\_XTAL\_32K]Power up 32 KHz crystal oscillator. (R/W)
\item [RTCIO\_XTAL\_X32N\_MUX\_SEL]0: route X32N pin to the digital IO\_MUX; 1: route to RTC block. (R/W)
\item [RTCIO\_XTAL\_X32P\_MUX\_SEL]0: route X32P pin to the digital IO\_MUX; 1: route to RTC block. (R/W)
\item [RTCIO\_XTAL\_X32N\_FUN\_SEL]Select the RTC function. 0: select function 0. (R/W)
\item [RTCIO\_XTAL\_X32N\_SLP\_SEL]Sleep mode selection. Set this bit to 1 to put the pin to sleep. (R/W)
\item [RTCIO\_XTAL\_X32N\_SLP\_IE]Input enable of the pin in sleep mode. 1: enabled; 0: disabled. (R/W)
\item [RTCIO\_XTAL\_X32N\_SLP\_OE]Output enable of the pin. 1: enabled; 0; disabled. (R/W)
\item [RTCIO\_XTAL\_X32N\_FUN\_IE]Input enable of the pin.  1: enabled; 0: disabled. (R/W)
\item [RTCIO\_XTAL\_X32P\_FUN\_SEL]Select the RTC function. 0: select function 0; 1: select function 1.   (R/W)
\item [RTCIO\_XTAL\_X32P\_SLP\_SEL]Sleep mode selection. Set this bit to 1 to put the pin to sleep. (R/W)
\item [RTCIO\_XTAL\_X32P\_SLP\_IE]Input enable of the pin in sleep mode. 1: enabled; 0: disabled. (R/W)
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTCIO\_XTAL\_32K\_PAD\_REG}{0x008C}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\item [RTCIO\_XTAL\_X32P\_SLP\_OE]Output enable of the pin in sleep mode. 1: enabled; 0: disabled. (R/W)
\item [RTCIO\_XTAL\_X32P\_FUN\_IE]Input enable of the pin. 1: enabled; 0: disabled. (R/W)
\item [RTCIO\_XTAL\_DRES\_XTAL\_32K]32K XTAL resistor bias control.  (R/W)
\item [RTCIO\_XTAL\_DBIAS\_XTAL\_32K]32K XTAL self-bias reference control. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTCIO\_TOUCH\_CFG\_REG}{0x0090}\label{regdesc:RTCIOTOUCHCFGREG}
\regfield{RTCIO\_TOUCH\_XPD\_BIAS}{1}{31}{0}%
\regfield{RTCIO\_TOUCH\_DREFH}{2}{29}{11}%
\regfield{RTCIO\_TOUCH\_DREFL}{2}{27}{00}%
\regfield{RTCIO\_TOUCH\_DRANGE}{2}{25}{11}%
\regfield{RTCIO\_TOUCH\_DCUR}{2}{23}{00}%
\regfield{(reserved)}{23}{0}{00000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_TOUCH\_XPD\_BIAS]Touch sensor bias power on bit. 1: power on; 0: disabled.  (R/W)
\item [RTCIO\_TOUCH\_DREFH]Touch sensor saw wave top voltage.  (R/W)
\item [RTCIO\_TOUCH\_DREFL]Touch sensor saw wave bottom voltage.  (R/W)
\item [RTCIO\_TOUCH\_DRANGE]Touch sensor saw wave voltage range.  (R/W)
\item [RTCIO\_TOUCH\_DCUR]Touch sensor bias current. When BIAS\_SLEEP is enabled, this setting is available. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_REG (\textcolor{red}{\it{n}}: 0-7)}{0x94+4*\textcolor{red}{\it{n}}}\label{regdesc:RTCIOTOUCHPADnREG} 
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_HOLD}{1}{31}{0}%
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_DRV}{2}{29}{10}%
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_RDE}{1}{28}{1}%
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_RUE}{1}{27}{0}%
\regfield{(reserved)}{1}{26}{0}%
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_DAC}{3}{23}{100}
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_START}{1}{22}{0}%
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_TIE\_OPT}{1}{21}{0}%
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_XPD}{1}{20}{0}%
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_MUX\_SEL}{1}{19}{0}%
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_FUN\_SEL}{2}{17}{00}%
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_SLP\_SEL}{1}{16}{0}%
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_SLP\_IE}{1}{15}{0}%
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_SLP\_OE}{1}{14}{0}%
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_FUN\_IE}{1}{13}{0}%
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_TO\_GPIO}{1}{12}{0}%
\regfield{(reserved)}{12}{0}{000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item[RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_HOLD] Write 1 to hold the current value of the output. (R/W)
\item[RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_DRV] Selects the drive strength of the pin. A higher value corresponds with a higher strength.
For detailed drive strength, please see \href{https://www.espressif.com/sites/default/files/documentation/esp32_datasheet_en.pdf}{\textit{ESP32 Datasheet}} > Appendix A.1 \textit{Notes on ESP32 Pin Lists} > Note 8. (R/W)\\
\item[RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_RDE] 1: Pull-down on pin enabled; 
0: Pull-down disabled.
(R/W)
\item[RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_RUE] 1: Pull-up on pin enabled;
0: Pull-up disabled.
(R/W)
\item [RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_DAC]Touch sensor slope control. 3-bit for each touch pin. Default is b'100.  (R/W) 
\item [RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_START] Write 1 to start touch sensor. (R/W)
\item [RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_TIE\_OPT] Default touch sensor tie option. \\
0: Tied to 0 V\\
1: Tied to VDD\_RTC voltage\\
(R/W) 
\item [RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_XPD] Write 1 to power on the touch sensor. (R/W)
\item [RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_MUX\_SEL] Selects RTC IO\_MUX or IO\_MUX to control the IE/OE/RUE/RDE statues of RTC pin.\\
1: Selects RTC IO\_MUX\\
0: Selects IO\_MUX \\
(R/W)
\item [RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_FUN\_SEL] Selects the function of the RTC.\\
0: RTC Function 0\\
1: Reserved\\
2: Reserved\\
3: RTC Function 1\\
(R/W)
\item[RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_SLP\_SEL] Sleep mode selection signal of the pin. Set this bit to 1 to put the pin to sleep. (R/W)
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_REG (\textcolor{red}{\it{n}}: 0-7)}{0x94+4*\textcolor{red}{\it{n}}}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\item[RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_SLP\_IE] Input enable of the pin in sleep mode (SLP\_SEL = 1). \\
1: Enabled \\
0: Disabled \\
(R/W)
\item[RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_SLP\_OE] Output enable of the pin in sleep mode (SLP\_SEL = 1). \\
1: Enabled\\
0: Disabled\\
(R/W)
\item[RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_FUN\_IE] Input enable of the pin in normal working mode (SLP\_SEL = 0).\\
1: Enabled \\
0: Disabled \\
(R/W)
\item[RTCIO\_TOUCH\_PAD\textcolor{red}{\it{n}}\_TO\_GPIO] Controls the routing of touch pin input signals to IO\_MUX. \\
1: The input signal from the touch pin is routed to IO\_MUX through analog function.\\
0: The input signal from the touch pin is routed to IO\_MUX through digital function. \\
(R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{m}}\_REG (\textcolor{red}{\it{m}} = 8, 9)}{0x00B4, 0x00B8}\label{regdesc:RTCIOTOUCHPADmREG} 
\regfield{(reserved)}{6}{26}{000000}%
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{m}}\_DAC}{3}{23}{100}
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{m}}\_START}{1}{22}{0}%
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{m}}\_TIE\_OPT}{1}{21}{0}%
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{m}}\_XPD}{1}{20}{0}%
\regfield{RTCIO\_TOUCH\_PAD\textcolor{red}{\it{m}}\_TO\_GPIO}{1}{19}{0}%
\regfield{(reserved)}{17}{0}{0000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_TOUCH\_PAD\textcolor{red}{\it{m}}\_DAC]Touch sensor slope control. 3-bit for each touch pin. Default b'100.  (R/W) 
\item [RTCIO\_TOUCH\_PAD\textcolor{red}{\it{m}}\_START] Write 1 to start touch sensor. (R/W)
\item [RTCIO\_TOUCH\_PAD\textcolor{red}{\it{m}}\_TIE\_OPT] Default touch sensor tie option. \\
0: Tied to 0 V\\
1: Tied to VDD\_RTC voltage\\
(R/W) 
\item [RTCIO\_TOUCH\_PAD\textcolor{red}{\it{m}}\_XPD] Write 1 to power on the touch sensor. (R/W)
\item [RTCIO\_TOUCH\_PAD\textcolor{red}{\it{m}}\_TO\_GPIO] Controls the routing of touch pin input signals to IO\_MUX. \\
1: The input signal from the touch pin is routed to IO\_MUX through analog function.\\
0: The input signal from the touch pin is routed to IO\_MUX through digital function. \\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_EXT\_WAKEUP0\_REG}{0x00BC}\label{regdesc:RTCIOEXTWAKEUP0REG}
\regfield{RTCIO\_EXT\_WAKEUP0\_SEL}{5}{27}{{0}}%
\regfield{(reserved)}{27}{0}{000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_EXT\_WAKEUP0\_SEL]GPIO[0-17] can be used to wake up the chip when the chip is in the sleep mode. This register prompts the pin source to wake up the chip when the latter is in deep/light sleep mode. 0: select GPIO0; 1: select GPIO2, etc. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_XTL\_EXT\_CTR\_REG}{0x00C0}\label{regdesc:RTCIOXTLEXTCTRREG}
\regfield{RTCIO\_XTL\_EXT\_CTR\_SEL}{5}{27}{{0}}%
\regfield{(reserved)}{27}{0}{000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_XTL\_EXT\_CTR\_SEL]Select the external crystal power down enable source to get into sleep mode. 0: select GPIO0; 1: select GPIO2, etc. The input value on this pin XOR \hyperref[regdesc:RTCCNTLXTEXTCTRLV]{RTC\_CNTL\_XTL\_EXT\_CTR\_LV} is the crystal power down enable signal. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTCIO\_SAR\_I2C\_IO\_REG}{0x00C4}\label{regdesc:RTCIOSARI2CIOREG}
\regfield{RTCIO\_SAR\_I2C\_SDA\_SEL}{2}{30}{{0}}%
\regfield{RTCIO\_SAR\_I2C\_SCL\_SEL}{2}{28}{{0}}%
\regfield{(reserved)}{28}{0}{0000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTCIO\_SAR\_I2C\_SDA\_SEL]Selects the other pin as the RTC I2C SDA signal. 0: pin TOUCH\_PAD[1]; 1: pin TOUCH\_PAD[3]. Default value is 0. (R/W)
\item [RTCIO\_SAR\_I2C\_SCL\_SEL]Selects the other pin as the RTC I2C SCL signal. 0: pin TOUCH\_PAD[0]; 1: pin TOUCH\_PAD[2]. Default value is 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}
