\begin{longtable}[l]{ |m{8.2cm}|r|c|r|m{9cm}| }    
\caption{Parameters in eFuse BLOCK0}
    \label{tab:efuse-block0-para} \\\hline
    
    \rowcolor{lightgray}
    \textbf{Parameters} & \textbf{\thead{Bit \\Width}} & \textbf{\thead{Accessible \\by Hardware}} & \textbf{\thead{Programming-Protection \\by \hyperref[fielddesc:EFUSEWRDIS]{EFUSE\_WR\_DIS}\\ Bit Number}}
    & \textbf{Description} \\
    \endfirsthead
    
    \multicolumn{5}{c}{\bfseries \tablename\ \thetable{} -- cont'd from previous page}\\\hline
    \rowcolor{lightgray}
    \textbf{Parameters} & \textbf{\thead{Bit \\Width}} & \textbf{\thead{Accessible \\by Hardware}} & \textbf{\thead{Programming-Protection \\by \hyperref[fielddesc:EFUSEWRDIS]{EFUSE\_WR\_DIS}\\ Bit Number}}
    & \textbf{Description} \\
    \endhead 
    \multicolumn{5}{r}{\textbf{Cont'd on next page}} \\
    \endfoot
    \endlastfoot
    \hline   
    \hyperref[fielddesc:EFUSEWRDIS]{\textbf{EFUSE\_WR\_DIS}} & 32 & Y & N/A & Represents whether writing of individual eFuses is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSERDDIS]{\textbf{EFUSE\_RD\_DIS}} & 7 & Y & 0  & Represents whether users' reading from BLOCK4 \verb+~+ 10 is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEDISICACHE]{EFUSE\_DIS\_ICACHE} &  1 & Y & 2  & Represents whether iCache is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEDISDCACHE]{EFUSE\_DIS\_DCACHE} & 1 & Y & 2  & Represents whether dCache is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEDISDOWNLOADICACHE]{EFUSE\_DIS\_DOWNLOAD\_ICACHE} & 1 & Y & 2 & Represents whether iCache is disabled in Download mode. \\   
    \hline
    \hyperref[fielddesc:EFUSEDISDOWNLOADDCACHE]{EFUSE\_DIS\_DOWNLOAD\_DCACHE} & 1 & Y & 2 & Represents whether dCache is disabled in Download mode. \\      
    \hline    
    \hyperref[fielddesc:EFUSEDISFORCEDOWNLOAD]{EFUSE\_DIS\_FORCE\_DOWNLOAD} & 1 & Y & 2 & Represents whether the function that forces chip into download mode is disabled. \\   
    \hline
    \hyperref[fielddesc:EFUSEDISUSBOTG]{EFUSE\_DIS\_USB\_OTG} &1 & Y & 2 & Represents whether USB OTG function is disabled. \\     
    \hline
    \hyperref[fielddesc:EFUSEDISTWAI]{EFUSE\_DIS\_TWAI} & 1 & Y & 2 & Represents whether TWAI Controller is disable. \\  
    \hline
    \hyperref[fielddesc:EFUSEDISAPPCPU]{EFUSE\_DIS\_APP\_CPU} & 1 & Y & 2 & Represents whether app CPU is disable. \\   
    \hline
    \hyperref[fielddesc:EFUSESOFTDISJTAG]{EFUSE\_SOFT\_DIS\_JTAG} & 3 & Y & 31 & Represents whether JTAG with soft-disable is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEDISPADJTAG]{EFUSE\_DIS\_PAD\_JTAG} & 1 & Y & 2 & Represents whether pad JTAG is permanently disabled. \\   
    \hline
    \hyperref[fielddesc:EFUSEDISDOWNLOADMANUALENCRYPT]{EFUSE\_DIS\_DOWNLOAD\_
    MANUAL\_ENCRYPT} &  1 & Y & 2 & Represents whether flash encryption is disabled in Download boot modes.\\ 
    \hline
    \hyperref[fielddesc:EFUSEUSBEXCHGPINS]{EFUSE\_USB\_EXCHG\_PINS} & 1 & Y & 30 & Represents whether USB D+ and D- pins are swapped. \\
    \hline
    \hyperref[fielddesc:EFUSEEXTPHYENABLE]{EFUSE\_EXT\_PHY\_ENABLE} & 1 & N & 30 & Represents whether external USB PHY is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEVDDSPIXPD]{EFUSE\_VDD\_SPI\_XPD} & 1 & Y & 3 & Represents whether Flash Voltage Regulator is powered up. \\        
    \hline
    \hyperref[fielddesc:EFUSEVDDSPITIEH]{EFUSE\_VDD\_SPI\_TIEH} & 1 & Y & 3 & Represents whether Flash Voltage Regulator output is short connected to VDD3P3\_RTC\_IO. \\   
    \hline
    \hyperref[fielddesc:EFUSEVDDSPIFORCE]{EFUSE\_VDD\_SPI\_FORCE} & 1 & Y & 3 & Represents whether to force using EFUSE\_VDD\_SPI\_XPD and EFUSE\_VDD\_SPI\_TIEH to configure flash voltage LDO. \\ 
    \hline
    \hyperref[fielddesc:EFUSEWDTDELAYSEL]{EFUSE\_WDT\_DELAY\_SEL} & 2 & Y & 3 & Represents RTC watchdog timeout threshold. \\
    \hline
    \hyperref[fielddesc:EFUSESPIBOOTCRYPTCNT]{EFUSE\_SPI\_BOOT\_CRYPT\_CNT} & 3 & Y & 4 & Represents whether SPI boot encrypt/decrypt is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE0]{EFUSE\_SECURE\_BOOT\_KEY\_
    REVOKE0} & 1 & N & 5 & Represents whether the first secure boot key is revoked. \\
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE1]{EFUSE\_SECURE\_BOOT\_KEY\_
    REVOKE1} & 1 & N & 6 & Represents whether the second secure boot key is revoked. \\
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE2]{EFUSE\_SECURE\_BOOT\_KEY\_
    REVOKE2} & 1 & N & 7 & Represents whether the third secure boot key is revoked. \\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE0]{EFUSE\_KEY\_PURPOSE\_0} & 4 & Y & 8 & Represents Key0 purpose, see Table \ref{tab:efuse-key-purpose}. \\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE1]{EFUSE\_KEY\_PURPOSE\_1} & 4 & Y & 9 & Represents Key1 purpose, see Table \ref{tab:efuse-key-purpose}.\\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE2]{EFUSE\_KEY\_PURPOSE\_2} & 4 & Y & 10 & Represents Key2 purpose, see Table  \ref{tab:efuse-key-purpose}. \\ 
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE3]{EFUSE\_KEY\_PURPOSE\_3} & 4 & Y & 11 & Represents Key3 purpose, see Table \ref{tab:efuse-key-purpose}. \\    
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE4]{EFUSE\_KEY\_PURPOSE\_4} & 4 & Y & 12 & Represents Key4 purpose, see Table \ref{tab:efuse-key-purpose}.\\    
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE5]{EFUSE\_KEY\_PURPOSE\_5} & 4 & Y & 13 & Represents Key5 purpose, see Table \ref{tab:efuse-key-purpose}. \\  
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTEN]{EFUSE\_SECURE\_BOOT\_EN} & 1 & N & 15 & Represents whether secure boot is enabled. \\ 
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTAGGRESSIVEREVOKE]{EFUSE\_SECURE\_BOOT\_AGG
    RESSIVE\_REVOKE} & 1 & N & 16 & Represents whether aggressive revoke of secure boot keys is enabled. \\
    \hline
    \hyperref[fielddesc:EFUSEDISUSBJTAG]{EFUSE\_DIS\_USB\_JTAG} & 1 & Y & 2 & Represents whether the function of usb\_serial\_jtag that switch usb to jtag is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEDISUSBSERIALJTAG]{EFUSE\_DIS\_USB\_SERIAL\_JTAG} & 1 & Y & 2 & Represents whether usb\_serial\_jtag function is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSESTRAPJTAGSEL]{EFUSE\_STRAP\_JTAG\_SEL} & 1 & Y & 2 & Represents whether to enable selection between usb\_to\_jtag or pad\_to\_jtag through GPIO3. 0: pad\_to\_jtag; 1: usb\_to\_jtag. \\
    \hline
    \hyperref[fielddesc:EFUSEUSBPHYSEL]{EFUSE\_USB\_PHY\_SEL} & 1 & Y & 2 & Represents the connection relationship between internal PHY, external PHY, and USB OTG, USB Serial/JTAG. \\
    \hline
    \hyperref[fielddesc:EFUSEFLASHTPUW]{EFUSE\_FLASH\_TPUW} & 4 & N & 18 & Represents flash waiting time after power-up. \\    
    \hline    
    \hyperref[fielddesc:EFUSEDISDOWNLOADMODE]{EFUSE\_DIS\_DOWNLOAD\_MODE} & 1 & N & 18 & Represents whether all download modes are disabled.\\       
    \hline
    \hyperref[fielddesc:EFUSEDISLEGACYSPIBOOT]{EFUSE\_DIS\_LEGACY\_SPI\_BOOT} & 1 & N & 18 & Represents whether Legacy SPI is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEDISUSBPRINT]{EFUSE\_DIS\_USB\_PRINT} & 1 & N & 18 & Represents whether USB printing is disabled. \\
    \hline  
    \hyperref[fielddesc:EFUSEFLASHECCMODE]{EFUSE\_FLASH\_ECC\_MODE} & 1 & N & 18 & Represents the flash ECC mode in ROM. \\
    \hline
    \hyperref[fielddesc:EFUSEDISUSBSERIALJTAGDOWNLOADMODE]{EFUSE\_DIS\_USB\_SERIAL\_JTAG\_DOWNLOAD\_MODE} & 1 & N & 18 & Represents whether download through USB-Serial-JTAG is disabled. \\
    \hline 
    \hyperref[fielddesc:EFUSEENABLESECURITYDOWNLOAD]{EFUSE\_ENABLE\_SECURITY\_
    DOWNLOAD} & 1 & N & 18 & Represents whether secure UART download mode is enabled. \\
    \hline
    \hyperref[fielddesc:EFUSEUARTPRINTCONTROL]{EFUSE\_UART\_PRINT\_CONTROL} & 2 & N & 18 & Represents the default UART boot message output mode. \\
    \hline
    \hyperref[fielddesc:EFUSEPINPOWERSELECTION]{EFUSE\_PIN\_POWER\_SELECTION} & 1 & N & 18 & Represents the power supply for GPIO33 \verb+~+ GPIO37, GPIO47, and GPIO48. \\
    \hline
    \hyperref[fielddesc:EFUSEFLASHTYPE]{EFUSE\_FLASH\_TYPE} & 1 & N & 18 & Represents the maximum data lines of SPI flash. \\
    \hline
    \hyperref[fielddesc:EFUSEFLASHPAGESIZE]{EFUSE\_FLASH\_PAGE\_SIZE} & 2 & N & 18 & Represents the page size of flash.\\
    \hline
    \hyperref[fielddesc:EFUSEFLASHECCEN]{EFUSE\_FLASH\_ECC\_EN} & 1 & N & 18 & Represents whether ECC for flash boot is enabled. \\
    \hline
    \hyperref[fielddesc:EFUSEFORCESENDRESUME]{EFUSE\_FORCE\_SEND\_RESUME} & 1 & N & 18 & Represents whether to force ROM code to send a resume command during SPI boot. \\  
    \hline
    \hyperref[fielddesc:EFUSESECUREVERSION]{EFUSE\_SECURE\_VERSION} & 16 & N & 18 & Represents IDF secure version. \\\hline
    \hyperref[fielddesc:EFUSEDISUSBOTGDOWNLOADMODE]{EFUSE\_DIS\_USB\_OTG\_DOWNLOAD\_MODE} & 1 & N & 19 & Represents whether download through USB-OTG is disabled. \\\hline
\end{longtable}
