\begin{register}{H}{\textcolor{red}{SPI\_CMD\_REG}}{0x{}0000}\label{regdesc:SPICMDREG}
\regfield{(reserved)}{7}{25}{0000000}%
\regfield{SPI\_USR}{1}{24}{{0}}%
\regfield{SPI\_UPDATE}{1}{23}{{0}}%
\regfield{(reserved)}{5}{18}{00000}%
\regfield{(reserved)|\textcolor{red}{SPI\_CONF\_BITLEN}}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPICONFBITLEN}\item [\textcolor{red}{SPI\_CONF\_BITLEN (for SPI2 only)}] Define the cycles of \hyperref[clk:APBCLK]{APB\_CLK} in CONF state. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUPDATE}\item [SPI\_UPDATE] Set this bit to synchronize SPI registers from APB clock domain into SPI module clock domain. This bit is only used in SPI master mode. (WT)
\label{fielddesc:SPIUSR}\item [SPI\_USR] User-defined command enable. An SPI operation will be triggered when the bit is set. The bit will be cleared once the operation is done. 1: enable. 0: disable. Can not be changed by CONF\_buf. (R/W/SC)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_ADDR\_REG}{0x{}0004}\label{regdesc:SPIADDRREG}
\regfield{SPI\_USR\_ADDR\_VALUE}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIUSRADDRVALUE}\item [SPI\_USR\_ADDR\_VALUE] Address to slave. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{\textcolor{red}{SPI\_USER\_REG}}{0x{}0010}\label{regdesc:SPIUSERREG}
\regfield{SPI\_USR\_COMMAND}{1}{31}{{1}}%
\regfield{SPI\_USR\_ADDR}{1}{30}{{0}}%
\regfield{SPI\_USR\_DUMMY}{1}{29}{{0}}%
\regfield{SPI\_USR\_MISO}{1}{28}{{0}}%
\regfield{SPI\_USR\_MOSI}{1}{27}{{0}}%
\regfield{SPI\_USR\_DUMMY\_IDLE}{1}{26}{{0}}%
\regfield{SPI\_USR\_MOSI\_HIGHPART}{1}{25}{{0}}%
\regfield{SPI\_USR\_MISO\_HIGHPART}{1}{24}{{0}}%
\regfield{(reserved)}{6}{18}{000000}%
\regfield{SPI\_SIO}{1}{17}{{0}}%
\regfield{(reserved)}{1}{16}{0}%
\regfield{(reserved)|\textcolor{red}{SPI\_USR\_CONF\_NXT}}{1}{15}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_FWRITE\_OCT}}{1}{14}{{0}}%
\regfield{SPI\_FWRITE\_QUAD}{1}{13}{{0}}%
\regfield{SPI\_FWRITE\_DUAL}{1}{12}{{0}}%
\regfield{(reserved)}{2}{10}{00}%
\regfield{SPI\_CK\_OUT\_EDGE}{1}{9}{{0}}%
\regfield{SPI\_RSCK\_I\_EDGE}{1}{8}{{0}}%
\regfield{SPI\_CS\_SETUP}{1}{7}{{1}}%
\regfield{SPI\_CS\_HOLD}{1}{6}{{1}}%
\regfield{SPI\_TSCK\_I\_EDGE}{1}{5}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_OPI\_MODE}}{1}{4}{{0}}%
\regfield{SPI\_QPI\_MODE}{1}{3}{{0}}%
\regfield{(reserved)}{2}{1}{00}%
\regfield{SPI\_DOUTDIN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDOUTDIN}\item [SPI\_DOUTDIN] Set the bit to enable full-duplex communication. 1: enable. 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIQPIMODE}\item [SPI\_QPI\_MODE] 1: Enable QPI mode. 0: Disable QPI mode. This configuration is applicable when the SPI controller works as master or slave. Can be configured in CONF state. (R/W/SS/SC)
\label{fielddesc:SPIOPIMODE}\item [\textcolor{red}{SPI\_OPI\_MODE (for SPI2 only)}] 1: Enable OPI mode (all in 8-bit mode). 0: Disable OPI mode. This configuration is applicable when the SPI controller works as master. Can be configured in CONF state. (R/W)
\label{fielddesc:SPITSCKIEDGE}\item [SPI\_TSCK\_I\_EDGE] In slave mode, this bit can be used to support four SPI clock modes, which is described in Subsection \ref{GP-SPI slave clock control}.  (R/W)
\label{fielddesc:SPICSHOLD}\item [SPI\_CS\_HOLD] Keep SPI CS low when SPI is in DONE state. 1: enable. 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICSSETUP}\item [SPI\_CS\_SETUP] Enable SPI CS when SPI is in prepare (PREP) state. 1: enable; 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIRSCKIEDGE}\item [SPI\_RSCK\_I\_EDGE] In slave mode, this bit can be used to support four SPI clock modes, which is described in Subsection \ref{GP-SPI slave clock control}.  (R/W)
\label{fielddesc:SPICKOUTEDGE}\item [SPI\_CK\_OUT\_EDGE] This bit together with SPI\_MOSI\_DELAY\_MODE is used to set MOSI signal delay mode. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFWRITEDUAL}\item [SPI\_FWRITE\_DUAL] In write operations, read-data phase is in 2-bit mode. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFWRITEQUAD}\item [SPI\_FWRITE\_QUAD] In write operations, read-data phase is in 4-bit mode. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFWRITEOCT}\item [\textcolor{red}{SPI\_FWRITE\_OCT (for SPI2 only)}] In write operations, read-data phase is in 8-bit mode. Can be configured in CONF state. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{\textcolor{red}{SPI\_USER\_REG}}{0x{}0010}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:SPIUSRCONFNXT}\item [\textcolor{red}{SPI\_USR\_CONF\_NXT (for SPI2 only)}]
Enable the CONF state for the next transaction (segment) in a configurable segmented transfer. Can be configured in CONF state. (R/W)
\begin{itemize}
    \item If this bit is set, it means this configurable segmented transfer will continue its next transaction (segment).
    \item If this bit is cleared, it means this transfer will end after the current transaction (segment) is finished. Or this is not a configurable segmented transfer.
\end{itemize}
\label{fielddesc:SPISIO}\item [SPI\_SIO] Set the bit to enable 3-line half-duplex communication, where MOSI and MISO signals share the same pin. 1: enable. 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRMISOHIGHPART}\item [SPI\_USR\_MISO\_HIGHPART] In read-data phase, only access to high-part of the buffers \hyperref[regdesc:SPIW8REG]{SPI\_W8\_REG} \verb+~+ \hyperref[regdesc:SPIW15REG]{SPI\_W15\_REG}. 1: enable. 0: disable. Can be configured in CONF state. (R/W)

\label{fielddesc:SPIUSRMOSIHIGHPART}\item [SPI\_USR\_MOSI\_HIGHPART] In write-data phase, only access to high-part of the buffers \hyperref[regdesc:SPIW8REG]{SPI\_W8\_REG} \verb+~+ \hyperref[regdesc:SPIW15REG]{SPI\_W15\_REG}. 1: enable. 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRDUMMYIDLE}\item [SPI\_USR\_DUMMY\_IDLE] If this bit is set, SPI clock is disable in DUMMY state. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRMOSI}\item [SPI\_USR\_MOSI] Set this bit to enable the write-data (DOUT) state of an operation. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRMISO}\item [SPI\_USR\_MISO] Set this bit to enable the read-data (DIN) state of an operation. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRDUMMY}\item [SPI\_USR\_DUMMY] Set this bit to enable the DUMMY state of an operation. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRADDR}\item [SPI\_USR\_ADDR] Set this bit to enable the address (ADDR) state of an operation. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRCOMMAND}\item [SPI\_USR\_COMMAND] Set this bit to enable the command (CMD) state of an operation. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_USER1\_REG}{0x{}0014}\label{regdesc:SPIUSER1REG}
\regfield{SPI\_USR\_ADDR\_BITLEN}{5}{27}{{23}}%
\regfield{SPI\_CS\_HOLD\_TIME}{5}{22}{{0x{}1}}%
\regfield{SPI\_CS\_SETUP\_TIME}{5}{17}{{0}}%
\regfield{SPI\_MST\_WFULL\_ERR\_END\_EN}{1}{16}{{1}}%
\regfield{(reserved)}{8}{8}{00000000}%
\regfield{SPI\_USR\_DUMMY\_CYCLELEN}{8}{0}{{7}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIUSRDUMMYCYCLELEN}\item [SPI\_USR\_DUMMY\_CYCLELEN] The length of DUMMY state, in unit of SPI\_CLK cycles. The value is (the expected cycle number - 1). Can be configured in CONF state. (R/W)
\label{fielddesc:SPIMSTWFULLERRENDEN}\item [SPI\_MST\_WFULL\_ERR\_END\_EN] 1: SPI transfer is ended when SPI RX AFIFO wfull error occurs in GP-SPI master full-/half-duplex modes. 0: SPI transfer is not ended when SPI RX AFIFO wfull error occurs in GP-SPI master full-/half-duplex modes. (R/W)
\label{fielddesc:SPICSSETUPTIME}\item [SPI\_CS\_SETUP\_TIME] The length of prepare (PREP) state, in unit of SPI\_CLK cycles. This value is equal to the expected cycles -1. This field is used together with \hyperref[fielddesc:SPICSSETUP]{SPI\_CS\_SETUP}. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICSHOLDTIME}\item [SPI\_CS\_HOLD\_TIME] Delay cycles of CS pin, in units of SPI\_CLK cycles. This field is used together with \hyperref[fielddesc:SPICSHOLD]{SPI\_CS\_HOLD}. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIUSRADDRBITLEN}\item [SPI\_USR\_ADDR\_BITLEN] The bit length in address state. This value is (expected bit number - 1). Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_USER2\_REG}{0x{}0018}\label{regdesc:SPIUSER2REG}
\regfield{SPI\_USR\_COMMAND\_BITLEN}{4}{28}{{7}}%
\regfield{SPI\_MST\_REMPTY\_ERR\_END\_EN}{1}{27}{{1}}%
\regfield{(reserved)}{11}{16}{00000000000}%
\regfield{SPI\_USR\_COMMAND\_VALUE}{16}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIUSRCOMMANDVALUE}\item [SPI\_USR\_COMMAND\_VALUE] The value of command. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIMSTREMPTYERRENDEN}\item [SPI\_MST\_REMPTY\_ERR\_END\_EN] 1: SPI transfer is ended when SPI TX AFIFO read empty error occurs in GP-SPI master full-/half-duplex modes. 0: SPI transfer is not ended when SPI TX AFIFO read empty error occurs in GP-SPI master full-/half-duplex modes. (R/W)
\label{fielddesc:SPIUSRCOMMANDBITLEN}\item [SPI\_USR\_COMMAND\_BITLEN] The bit length of command state. This value is (expected bit number - 1). Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{\textcolor{red}{SPI\_CTRL\_REG}}{0x{}0008}\label{regdesc:SPICTRLREG}
\regfield{(reserved)}{5}{27}{00000}%
\regfield{SPI\_WR\_BIT\_ORDER}{2}{25}{{0}}%
\regfield{SPI\_RD\_BIT\_ORDER}{2}{23}{{0}}%
\regfield{(reserved)}{1}{22}{0}%
\regfield{SPI\_WP\_POL}{1}{21}{{1}}%
\regfield{SPI\_HOLD\_POL}{1}{20}{{1}}%
\regfield{SPI\_D\_POL}{1}{19}{{1}}%
\regfield{SPI\_Q\_POL}{1}{18}{{1}}%
\regfield{(reserved)}{1}{17}{0}%
\regfield{(reserved)|\textcolor{red}{SPI\_FREAD\_OCT}}{1}{16}{{0}}%
\regfield{SPI\_FREAD\_QUAD}{1}{15}{{0}}%
\regfield{SPI\_FREAD\_DUAL}{1}{14}{{0}}%
\regfield{(reserved)}{3}{11}{000}%
\regfield{(reserved)|\textcolor{red}{SPI\_FCMD\_OCT}}{1}{10}{{0}}%
\regfield{SPI\_FCMD\_QUAD}{1}{9}{{0}}%
\regfield{SPI\_FCMD\_DUAL}{1}{8}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_FADDR\_OCT}}{1}{7}{{0}}%
\regfield{SPI\_FADDR\_QUAD}{1}{6}{{0}}%
\regfield{SPI\_FADDR\_DUAL}{1}{5}{{0}}%
\regfield{(reserved)}{1}{4}{0}%
\regfield{SPI\_DUMMY\_OUT}{1}{3}{{0}}%
\regfield{(reserved)}{3}{0}{000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDUMMYOUT}\item [SPI\_DUMMY\_OUT] Can be configured in CONF state. (R/W)
\begin{itemize}
    \item For SPI2:
    \begin{itemize}
        \item 0: In DUMMY state, the FSPI bus signals are not output.
        \item 1: In DUMMY state, the FSPI bus signals are output.
    \end{itemize}
    \item For SPI3: In DUMMY state, the signal level of SPI is output by the SPI controller.
\end{itemize}

\label{fielddesc:SPIFADDRDUAL}\item [SPI\_FADDR\_DUAL] Apply 2-bit mode during address (ADDR) state. 1: enable. 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFADDRQUAD}\item [SPI\_FADDR\_QUAD] Apply 4-bit mode during address (ADDR) state. 1: enable. 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFADDROCT}\item [\textcolor{red}{SPI\_FADDR\_OCT (for SPI2 only)}] Apply 8-bit mode during address (ADDR) state. 1: enable. 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFCMDDUAL}\item [SPI\_FCMD\_DUAL] Apply 2-bit mode during command (CMD) state. 1: enable. 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFCMDQUAD}\item [SPI\_FCMD\_QUAD] Apply 4-bit mode during command (CMD) state. 1: enable. 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFCMDOCT}\item [\textcolor{red}{SPI\_FCMD\_OCT (for SP2 only)}] Apply 8-bit mode during command (CMD) state. 1: enable. 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFREADDUAL}\item [SPI\_FREAD\_DUAL] In read operations, read-data (DIN) state is in 2-bit mode. 1: enable. 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFREADQUAD}\item [SPI\_FREAD\_QUAD] In read operations, read-data (DIN) state is in 4-bit mode. 1: enable. 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIFREADOCT}\item [\textcolor{red}{SPI\_FREAD\_OCT (for SP2 only)}] In read operations, read-data (DIN) state is in 8-bit mode. 1: enable. 0: disable. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIQPOL}\item [SPI\_Q\_POL] The bit is used to set MISO line polarity. 1: high. 0: low. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIDPOL}\item [SPI\_D\_POL] The bit is used to set MOSI line polarity, 1: high. 0, low. Can be configured in CONF state. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{\textcolor{red}{SPI\_CTRL\_REG}}{0x{}0008}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:SPIHOLDPOL}\item [SPI\_HOLD\_POL] This bit is used to set SPI\_HOLD output value when SPI is in idle. 1: output high. 0: output low. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIWPPOL}\item [SPI\_WP\_POL] This bit is used to set the output value of write-protect signal when SPI is in idle. 1: output high. 0: output low. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIRDBITORDER}\item [SPI\_RD\_BIT\_ORDER] In read-data (MISO) state, 1: LSB first. 0: MSB first. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIWRBITORDER}\item [SPI\_WR\_BIT\_ORDER] In command (CMD), address (ADDR), and write-data (MOSI) states, 1: LSB first. 0: MSB first. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_MS\_DLEN\_REG}{0x{}001C}\label{regdesc:SPIMSDLENREG}
\regfield{(reserved)}{14}{18}{00000000000000}%
\regfield{SPI\_MS\_DATA\_BITLEN}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIMSDATABITLEN}\item [SPI\_MS\_DATA\_BITLEN] The value of this field is the configured SPI transmission data bit length in master mode DMA-controlled transfer or CPU-controlled transfer. The value is also the configured bit length in slave mode DMA RX controlled transfer. The register value shall be (expected bit number - 1). Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{\textcolor{red}{SPI\_MISC\_REG (For SPI2 Only)}}{0x{}0020}\label{regdesc:SPIMISCREG}
\regfield{SPI\_QUAD\_DIN\_PIN\_SWAP}{1}{31}{{0}}%
\regfield{SPI\_CS\_KEEP\_ACTIVE}{1}{30}{{0}}%
\regfield{SPI\_CK\_IDLE\_EDGE}{1}{29}{{0}}%
\regfield{(reserved)}{4}{25}{0000}%
\regfield{SPI\_DQS\_IDLE\_EDGE}{1}{24}{{0}}%
\regfield{SPI\_SLAVE\_CS\_POL}{1}{23}{{0}}%
\regfield{(reserved)}{3}{20}{000}%
\regfield{SPI\_CMD\_DTR\_EN}{1}{19}{{0}}%
\regfield{SPI\_ADDR\_DTR\_EN}{1}{18}{{0}}%
\regfield{SPI\_DATA\_DTR\_EN}{1}{17}{{0}}%
\regfield{SPI\_CLK\_DATA\_DTR\_EN}{1}{16}{{0}}%
\regfield{(reserved)}{3}{13}{000}%
\regfield{SPI\_MASTER\_CS\_POL}{6}{7}{{0}}%
\regfield{SPI\_CK\_DIS}{1}{6}{{0}}%
\regfield{SPI\_CS5\_DIS}{1}{5}{{1}}%
\regfield{SPI\_CS4\_DIS}{1}{4}{{1}}%
\regfield{SPI\_CS3\_DIS}{1}{3}{{1}}%
\regfield{SPI\_CS2\_DIS}{1}{2}{{1}}%
\regfield{SPI\_CS1\_DIS}{1}{1}{{1}}%
\regfield{SPI\_CS0\_DIS}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPICS0DIS}\item [SPI\_CS0\_DIS] SPI CS0 pin enable bit. 1: disable CS0. 0: SPI\_CS0 signal is from/to CS0 pin. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICS1DIS}\item [SPI\_CS1\_DIS] SPI CS1 pin enable bit. 1: disable CS1. 0: SPI\_CS1 signal is from/to CS1 pin. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICS2DIS}\item [SPI\_CS2\_DIS] SPI CS2 pin enable bit. 1: disable CS2. 0: SPI\_CS2 signal is from/to CS2 pin. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICS3DIS}\item [SPI\_CS3\_DIS] SPI CS3 pin enable bit. 1: disable CS3. 0: SPI\_CS3 signal is from/to CS3 pin. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICS4DIS}\item [SPI\_CS4\_DIS] SPI CS4 pin enable bit. 1: disable CS4. 0: SPI\_CS4 signal is from/to CS4 pin. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICS5DIS}\item [SPI\_CS5\_DIS] SPI CS5 pin enable bit. 1: disable CS5 0: SPI\_CS5 signal is from/to CS5 pin. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICKDIS}\item [SPI\_CK\_DIS] 1: Disable SPI\_CLK output. 0: Enable SPI\_CLK output. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIMASTERCSPOL}\item [SPI\_MASTER\_CS\_POL] SPI\_MASTER\_CS\_POL[\regindex{i}] configures the polarity of SPI CS\regindex{i} (\regindex{i} is from 0 \verb+~+ 2) line in master mode.
0: CS\regindex{i} is low active. 1: CS\regindex{i} is high active. Can be configured in CONF state. (R/W)

\label{fielddesc:SPICLKDATADTREN}\item [SPI\_CLK\_DATA\_DTR\_EN] 1: SPI master DDR mode is applied to SPI clock, data, and SPI\_DQS. 0: SPI master DDR mode is only applied to SPI\_DQS. This bit should be used with bit 17/18/19. (R/W)
\label{fielddesc:SPIDATADTREN}\item [SPI\_DATA\_DTR\_EN] 1: SPI clock and data of DOUT and DIN states are in DDR mode, including master 1/2/4/8-bit mode. 0: SPI clock and data of DOUT and DIN states are in SDR mode. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIADDRDTREN}\item [SPI\_ADDR\_DTR\_EN] 1: SPI clock and data of SPI\_SEND\_ADDR state are in DDR mode, including master 1/2/4/8-bit mode. 0: SPI clock and data of SPI\_SEND\_ADDR state are in SDR mode. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICMDDTREN}\item [SPI\_CMD\_DTR\_EN] 1: SPI clock and data of SPI\_SEND\_CMD state are in DDR mode, including master 1/2/4/8-bit mode. 0: SPI clock and data of SPI\_SEND\_CMD state are in SDR mode. Can be configured in CONF state. (R/W)
\label{fielddesc:SPISLAVECSPOL}\item [SPI\_SLAVE\_CS\_POL] Configure SPI slave input CS polarity. 1: invert. 0: not change. Can be configured in CONF state. (R/W)
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{\textcolor{red}{SPI\_MISC\_REG (For SPI2 Only)}}{0x{}0020}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:SPIDQSIDLEEDGE}\item [SPI\_DQS\_IDLE\_EDGE] The default value of SPI\_DQS. 0: low voltage level; 1: high voltage level. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICKIDLEEDGE}\item [SPI\_CK\_IDLE\_EDGE] 1: SPI\_CLK line is high when GP-SPI2 is in idle. 0: SPI\_CLK line is low when GP-SPI2 is in idle. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICSKEEPACTIVE}\item [SPI\_CS\_KEEP\_ACTIVE] SPI CS line keeps low when the bit is set. Can be configured in CONF state. (R/W)
\label{fielddesc:SPIQUADDINPINSWAP}\item [SPI\_QUAD\_DIN\_PIN\_SWAP] SPI quad input swap enable. 1: swap FSPID with FSPIQ, swap FSPIWP with FSPIHD. 0: SPI quad input swap disable. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{\textcolor{red}{SPI\_MISC\_REG (For SPI3 Only)}}{0x{}0020}\label{regdesc:SPI3MISCREG}
\regfield{SPI\_QUAD\_DIN\_PIN\_SWAP}{1}{31}{{0}}%
\regfield{SPI\_CS\_KEEP\_ACTIVE}{1}{30}{{0}}%
\regfield{SPI\_CK\_IDLE\_EDGE}{1}{29}{{0}}%
\regfield{(reserved)}{5}{24}{00000}%
\regfield{SPI\_SLAVE\_CS\_POL}{1}{23}{{0}}%
\regfield{(reserved)}{13}{10}{0000000000000}%
\regfield{SPI\_MASTER\_CS\_POL}{3}{7}{{0}}%
\regfield{SPI\_CK\_DIS}{1}{6}{{0}}%
\regfield{(reserved)}{3}{3}{000}%
\regfield{SPI\_CS2\_DIS}{1}{2}{{1}}%
\regfield{SPI\_CS1\_DIS}{1}{1}{{1}}%
\regfield{SPI\_CS0\_DIS}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPI3CS0DIS}\item [SPI\_CS0\_DIS] SPI CS0 pin enable bit. 1: disable CS0. 0: SPI\_CS0 signal is from/to CS0 pin. Can be configured in CONF state. (R/W)
\label{fielddesc:SPI3CS1DIS}\item [SPI\_CS1\_DIS] SPI CS1 pin enable bit. 1: disable CS1. 0: SPI\_CS1 signal is from/to CS1 pin. Can be configured in CONF state. (R/W)
\label{fielddesc:SPI3CS2DIS}\item [SPI\_CS2\_DIS] SPI CS2 pin enable bit. 1: disable CS2. 0: SPI\_CS2 signal is from/to CS2 pin. Can be configured in CONF state. (R/W)
\label{fielddesc:SPI3CKDIS}\item [SPI\_CK\_DIS] 1: Disable SPI\_CLK output. 0: Enable SPI\_CLK output. Can be configured in CONF state. (R/W)
\label{fielddesc:SPI3MASTERCSPOL}\item [SPI\_MASTER\_CS\_POL] SPI\_MASTER\_CS\_POL[\regindex{i}] configures the polarity of SPI CS\regindex{i} (\regindex{i} is from 0 \verb+~+ 5) line in master mode.
0: CS\regindex{i} is low active. 1: CS\regindex{i} is high active. Can be configured in CONF state. (R/W)
\label{fielddesc:SPI3SLAVECSPOL}\item [SPI\_SLAVE\_CS\_POL] Configure SPI slave input CS polarity. 1: invert. 0: not change. Can be configured in CONF state. (R/W)
\label{fielddesc:SPI3CKIDLEEDGE}\item [SPI\_CK\_IDLE\_EDGE] 1: SPI\_CLK line is high when GP-SPI3 is in idle. 0: SPI\_CLK line is low when GP-SPI3 is in idle. Can be configured in CONF state. (R/W)
\label{fielddesc:SPI3CSKEEPACTIVE}\item [SPI\_CS\_KEEP\_ACTIVE] SPI CS line keeps low when the bit is set. Can be configured in CONF state. (R/W)
\label{fielddesc:SPI3QUADDINPINSWAP}\item [SPI\_QUAD\_DIN\_PIN\_SWAP] 1: SPI quad input swap enable. 0: SPI quad input swap disable. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_CONF\_REG}{0x{}0030}\label{regdesc:SPIDMACONFREG}
\regfield{SPI\_DMA\_AFIFO\_RST}{1}{31}{{0}}%
\regfield{SPI\_BUF\_AFIFO\_RST}{1}{30}{{0}}%
\regfield{SPI\_RX\_AFIFO\_RST}{1}{29}{{0}}%
\regfield{SPI\_DMA\_TX\_ENA}{1}{28}{{0}}%
\regfield{SPI\_DMA\_RX\_ENA}{1}{27}{{0}}%
\regfield{(reserved)}{5}{22}{00000}%
\regfield{SPI\_RX\_EOF\_EN}{1}{21}{{0}}%
\regfield{SPI\_SLV\_TX\_SEG\_TRANS\_CLR\_EN}{1}{20}{{0}}%
\regfield{SPI\_SLV\_RX\_SEG\_TRANS\_CLR\_EN}{1}{19}{{0}}%
\regfield{SPI\_DMA\_SLV\_SEG\_TRANS\_EN}{1}{18}{{0}}%
\regfield{(reserved)}{16}{2}{0000000000000000}%
\regfield{SPI\_DMA\_INFIFO\_FULL}{1}{1}{{1}}%
\regfield{SPI\_DMA\_OUTFIFO\_EMPTY}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDMAOUTFIFOEMPTY}\item [SPI\_DMA\_OUTFIFO\_EMPTY] Records the status of DMA TX FIFO. 1: DMA TX FIFO is not ready for sending data. 0: DMA TX FIFO is ready for sending data. (RO)
\label{fielddesc:SPIDMAINFIFOFULL}\item [SPI\_DMA\_INFIFO\_FULL] Records the status of DMA RX FIFO. 1: DMA RX FIFO is not ready for receiving data. 0: DMA RX FIFO is ready for receiving data. (RO)
\label{fielddesc:SPIDMASLVSEGTRANSEN}\item [SPI\_DMA\_SLV\_SEG\_TRANS\_EN] 1: Enable DMA-controlled segmented transfer in slave half-duplex mode. 0: disable. (R/W)
\label{fielddesc:SPISLVRXSEGTRANSCLREN}\item [SPI\_SLV\_RX\_SEG\_TRANS\_CLR\_EN] In DMA-controlled half-duplex slave mode, if the size of DMA RX buffer is smaller than the size of the received data, 1: the data in following transfers will not be received. 0: the data in this transfer will not be received, but in the following transfers, if the size of DMA RX buffer is not 0, the data in following transfers will be received, otherwise not. (R/W)
\label{fielddesc:SPISLVTXSEGTRANSCLREN}\item [SPI\_SLV\_TX\_SEG\_TRANS\_CLR\_EN] In DMA-controlled half-duplex slave mode, if the size of DMA TX buffer is smaller than the size of the transmitted data, 1: the data in the following transfers will not be updated, i.e., the old data is transmitted repeatedly. 0: the data in this transfer will not be updated. But in the following transfers, if new data is filled in DMA TX FIFO, new data will be transmitted, otherwise not. (R/W)
\label{fielddesc:SPIRXEOFEN}\item [SPI\_RX\_EOF\_EN] 1: In a DAM-controlled transfer, if the bit number of
transferred data is equal to (\hyperref[fielddesc:SPIMSDATABITLEN]{SPI\_MS\_DATA\_BITLEN} + 1), then GDMA\_IN\_SUC\_EOF\_CH\textcolor{red}{\it{n}}\_INT\_RAW will be set by hardware. 0: GDMA\_IN\_SUC\_EOF\_CH\textcolor{red}{\it{n}}\_INT\_RAW is set by \hyperref[int:SPITRANSDONEINT]{SPI\_TRANS\_DONE\_INT} event in a non-segmented transfer, or by a \hyperref[int:SPIDMASEGTRANSDONEINT]{SPI\_DMA\_SEG\_TRANS\_DONE\_INT} event in a segmented transfer. (R/W)

\label{fielddesc:SPIDMARXENA}\item [SPI\_DMA\_RX\_ENA] Set this bit to enable DMA-controlled receive data mode. (R/W)
\label{fielddesc:SPIDMATXENA}\item [SPI\_DMA\_TX\_ENA] Set this bit to enable DMA-controlled send data mode. (R/W)
\label{fielddesc:SPIRXAFIFORST}\item [SPI\_RX\_AFIFO\_RST] Set this bit to reset spi\_rx\_afifo as shown in Figure \ref{fig:spi-master-data-flow-control} and in Figure  \ref{fig:spi-slave-data-flow-control}. spi\_rx\_afifo is used to receive data in SPI master and slave transfer. (WT)

\label{fielddesc:SPIBUFAFIFORST}\item [SPI\_BUF\_AFIFO\_RST] Set this bit to reset buf\_tx\_afifo as shown in Figure \ref{fig:spi-master-data-flow-control} and in Figure  \ref{fig:spi-slave-data-flow-control}. buf\_tx\_afifo is used to send data out in CPU-controlled master and slave transfer. (WT)

\label{fielddesc:SPIDMAAFIFORST}\item [SPI\_DMA\_AFIFO\_RST] Set this bit to reset dma\_tx\_afifo as shown in Figure \ref{fig:spi-master-data-flow-control} and in Figure  \ref{fig:spi-slave-data-flow-control}. dma\_tx\_afifo is used to send data out in DMA-controlled slave transfer. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{\textcolor{red}{SPI\_SLAVE\_REG}}{0x{}00E0}\label{regdesc:SPISLAVEREG}
\regfield{(reserved)}{3}{29}{000}%
\regfield{(reserved)|\textcolor{red}{SPI\_USR\_CONF}}{1}{28}{{0}}%
\regfield{SPI\_SOFT\_RESET}{1}{27}{{0}}%
\regfield{SPI\_SLAVE\_MODE}{1}{26}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_DMA\_SEG\_MAGIC\_VALUE}}{4}{22}{{10}}%
\regfield{(reserved)}{10}{12}{0000000000}%
\regfield{SPI\_SLV\_WRBUF\_BITLEN\_EN}{1}{11}{{0}}%
\regfield{SPI\_SLV\_RDBUF\_BITLEN\_EN}{1}{10}{{0}}%
\regfield{SPI\_SLV\_WRDMA\_BITLEN\_EN}{1}{9}{{0}}%
\regfield{SPI\_SLV\_RDDMA\_BITLEN\_EN}{1}{8}{{0}}%
\regfield{(reserved)}{4}{4}{0000}%
\regfield{SPI\_RSCK\_DATA\_OUT}{1}{3}{{0}}%
\regfield{SPI\_CLK\_MODE\_13}{1}{2}{{0}}%
\regfield{SPI\_CLK\_MODE}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPICLKMODE}\item [SPI\_CLK\_MODE] SPI clock mode control bits. Can be configured in CONF state. (R/W)
\begin{itemize}
    \item 0: SPI clock is off when CS becomes inactive.
    \item 1: SPI clock is delayed one cycle after CS becomes inactive.
    \item 2: SPI clock is delayed two cycles after CS becomes inactive.
    \item 3: SPI clock is always on.
\end{itemize}
\label{fielddesc:SPICLKMODE13}\item [SPI\_CLK\_MODE\_13] Configure clock mode. (R/W)
\begin{itemize}
    \item 1: support SPI clock mode 1 and 3. Output data B[0]/B[7] at the first edge.
    \item 0: support SPI clock mode 0 and 2. Output data B[1]/B[6] at the first edge.
\end{itemize}
\label{fielddesc:SPIRSCKDATAOUT}\item [SPI\_RSCK\_DATA\_OUT] Save half a cycle when TSCK is the same as RSCK. 1: output data at RSCK rising edge. 0: output data at TSCK rising edge. (R/W)
\label{fielddesc:SPISLVRDDMABITLENEN}\item [SPI\_SLV\_RDDMA\_BITLEN\_EN] If this bit is set, \hyperref[fielddesc:SPISLVDATABITLEN]{SPI\_SLV\_DATA\_BITLEN} is used to store the data bit length of Rd\_DMA transfer. (R/W)
\label{fielddesc:SPISLVWRDMABITLENEN}\item [SPI\_SLV\_WRDMA\_BITLEN\_EN] If this bit is set, \hyperref[fielddesc:SPISLVDATABITLEN]{SPI\_SLV\_DATA\_BITLEN} is used to store the data bit length of Wr\_DMA transfer. (R/W)
\label{fielddesc:SPISLVRDBUFBITLENEN}\item [SPI\_SLV\_RDBUF\_BITLEN\_EN] If this bit is set, \hyperref[fielddesc:SPISLVDATABITLEN]{SPI\_SLV\_DATA\_BITLEN} is used to store data bit length of Rd\_BUF transfer. (R/W)
\label{fielddesc:SPISLVWRBUFBITLENEN}\item [SPI\_SLV\_WRBUF\_BITLEN\_EN] If this bit is set, \hyperref[fielddesc:SPISLVDATABITLEN]{SPI\_SLV\_DATA\_BITLEN} is used to store data bit length of Wr\_BUF transfer. (R/W)
\label{fielddesc:SPIDMASEGMAGICVALUE}\item [\textcolor{red}{SPI\_DMA\_SEG\_MAGIC\_VALUE (for SPI2 only)}] Configure the magic value of BM table in DMA-controlled configurable segmented transfer. (R/W)
\label{fielddesc:SPISLAVEMODE}\item [SPI\_SLAVE\_MODE] Set SPI work mode. 1: slave mode. 0: master mode. (R/W)
\label{fielddesc:SPISOFTRESET}\item [SPI\_SOFT\_RESET] Software reset enable bit. If this bit is set, the SPI clock line, CS line, and data line are reset. Can be configured in CONF state. (WT)
\label{fielddesc:SPIUSRCONF}\item [\textcolor{red}{SPI\_USR\_CONF (for SPI2 only)}] 1: Enable the CONF state of current DMA-controlled configurable segmented transfer, which means the configurable segmented transfer is started. 0: This is not a configurable segmented transfer. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_SLAVE1\_REG}{0x{}00E4}\label{regdesc:SPISLAVE1REG}
\regfield{SPI\_SLV\_LAST\_ADDR}{6}{26}{{0}}%
\regfield{SPI\_SLV\_LAST\_COMMAND}{8}{18}{{0}}%
\regfield{SPI\_SLV\_DATA\_BITLEN}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPISLVDATABITLEN}\item [SPI\_SLV\_DATA\_BITLEN] Configure the transferred data bit length in SPI slave full-/half-duplex modes. (R/W/SS)
\label{fielddesc:SPISLVLASTCOMMAND}\item [SPI\_SLV\_LAST\_COMMAND] In slave mode, it is the value of command. (R/W/SS)
\label{fielddesc:SPISLVLASTADDR}\item [SPI\_SLV\_LAST\_ADDR] In slave mode, it is the value of address. (R/W/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_CLOCK\_REG}{0x{}000C}\label{regdesc:SPICLOCKREG}
\regfield{SPI\_CLK\_EQU\_SYSCLK}{1}{31}{{1}}%
\regfield{(reserved)}{9}{22}{000000000}%
\regfield{SPI\_CLKDIV\_PRE}{4}{18}{{0}}%
\regfield{SPI\_CLKCNT\_N}{6}{12}{{0x{}3}}%
\regfield{SPI\_CLKCNT\_H}{6}{6}{{0x{}1}}%
\regfield{SPI\_CLKCNT\_L}{6}{0}{{0x{}3}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPICLKCNTL}\item [SPI\_CLKCNT\_L] In master mode, this field must be equal to SPI\_CLKCNT\_N. In slave mode, it must be 0. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICLKCNTH}\item [SPI\_CLKCNT\_H] In master mode, this field must be floor((SPI\_CLKCNT\_N + 1)/2 - 1). floor() here is to down round a number, floor(2.2) = 2. In slave mode, it must be 0. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICLKCNTN}\item [SPI\_CLKCNT\_N] In master mode, this is the divider of SPI\_CLK. So SPI\_CLK frequency is $f_{\textrm{apb\_clk}}$/(SPI\_CLKDIV\_PRE + 1)/(SPI\_CLKCNT\_N + 1). Can be configured in CONF state. (R/W)
\label{fielddesc:SPICLKDIVPRE}\item [SPI\_CLKDIV\_PRE] In master mode, this is pre-divider of SPI\_CLK. Can be configured in CONF state. (R/W)
\label{fielddesc:SPICLKEQUSYSCLK}\item [SPI\_CLK\_EQU\_SYSCLK] In master mode, 1: SPI\_CLK is equal to APB\_CLK. 0: SPI\_CLK is divided from APB\_CLK. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_CLK\_GATE\_REG}{0x{}00E8}\label{regdesc:SPICLKGATEREG}
\regfield{(reserved)}{29}{3}{00000000000000000000000000000}%
\regfield{SPI\_MST\_CLK\_SEL}{1}{2}{{0}}%
\regfield{SPI\_MST\_CLK\_ACTIVE}{1}{1}{{0}}%
\regfield{SPI\_CLK\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPICLKEN}\item [SPI\_CLK\_EN] Set this bit to enable clock gate. (R/W)
\label{fielddesc:SPIMSTCLKACTIVE}\item [SPI\_MST\_CLK\_ACTIVE] Set this bit to power on the SPI module clock. (R/W)
\label{fielddesc:SPIMSTCLKSEL}\item [SPI\_MST\_CLK\_SEL] This bit is used to select SPI module clock source in master mode.\\
1: PLL\_F80M\_CLK\\
0: XTAL\_CLK \\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{\textcolor{red}{SPI\_DIN\_MODE\_REG}}{0x{}0024}\label{regdesc:SPIDINMODEREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{SPI\_TIMING\_HCLK\_ACTIVE}{1}{16}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_DIN7\_MODE}}{2}{14}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_DIN6\_MODE}}{2}{12}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_DIN5\_MODE}}{2}{10}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_DIN4\_MODE}}{2}{8}{{0}}%
\regfield{SPI\_DIN3\_MODE}{2}{6}{{0}}%
\regfield{SPI\_DIN2\_MODE}{2}{4}{{0}}%
\regfield{SPI\_DIN1\_MODE}{2}{2}{{0}}%
\regfield{SPI\_DIN0\_MODE}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDIN0MODE}\item [SPI\_DIN0\_MODE] Configure the input mode for input data bit0 signal. Can be configured in CONF state. (R/W)

\begin{itemize}
    \item 0: input without delay
    \item 1: input data is delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for (\hyperref[fielddesc:SPIDIN0NUM]{SPI\_DIN0\_NUM} + 1) cycles
    \item 2: input data is delayed by the rising edge of \hyperref[clk:clkhclk]{clk\_hclk} for (\hyperref[fielddesc:SPIDIN0NUM]{SPI\_DIN0\_NUM} + 1) cycles, and then delayed by the rising edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
    \item 3: input data is delayed by the rising edge of \hyperref[clk:clkhclk]{clk\_hclk} for (\hyperref[fielddesc:SPIDIN0NUM]{SPI\_DIN0\_NUM} + 1) cycles, and then delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
\end{itemize}

\label{fielddesc:SPIDIN1MODE}\item [SPI\_DIN1\_MODE] Configure the input mode for input data bit1 signal. Can be configured in CONF state. (R/W)

\begin{itemize}
    \item 0: input without delay
    \item 1: input data is delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for (\hyperref[fielddesc:SPIDIN1NUM]{SPI\_DIN1\_NUM} +1) cycles

    \item 2: input data is delayed by the rising edge of \hyperref[clk:clkhclk]{clk\_hclk} for (\hyperref[fielddesc:SPIDIN1NUM]{SPI\_DIN1\_NUM} +1) cycles, and then delayed by the rising edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle

    \item 3: input data is delayed by the rising edge of \hyperref[clk:clkhclk]{clk\_hclk} for (\hyperref[fielddesc:SPIDIN1NUM]{SPI\_DIN1\_NUM} +1) cycles, and then delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
\end{itemize}

\label{fielddesc:SPIDIN2MODE}\item [SPI\_DIN2\_MODE] Configure the input mode for input data bit2 signal. Can be configured in CONF state. (R/W)

\begin{itemize}
    \item 0: input without delay
    \item 1: input data is delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for (\hyperref[fielddesc:SPIDIN2NUM]{SPI\_DIN2\_NUM} +1) cycles

    \item 2: input data is delayed by the rising edge of \hyperref[clk:clkhclk]{clk\_hclk} for (\hyperref[fielddesc:SPIDIN2NUM]{SPI\_DIN2\_NUM} +1) cycles, and then delayed by the rising edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle

    \item 3: input data is delayed by the rising edge of \hyperref[clk:clkhclk]{clk\_hclk} for (\hyperref[fielddesc:SPIDIN2NUM]{SPI\_DIN2\_NUM} +1) cycles, and then delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
\end{itemize}

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{\textcolor{red}{SPI\_DIN\_MODE\_REG}}{0x{}0024}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:SPIDIN3MODE}\item [SPI\_DIN3\_MODE] Configure the input mode for input data bit3 signal. Can be configured in CONF state. (R/W)

\begin{itemize}
    \item 0: input without delay
    \item 1: input data is delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for (\hyperref[fielddesc:SPIDIN3NUM]{SPI\_DIN3\_NUM} +1) cycles

    \item 2: input data is delayed by the rising edge of \hyperref[clk:clkhclk]{clk\_hclk} for (\hyperref[fielddesc:SPIDIN3NUM]{SPI\_DIN3\_NUM} +1) cycles, and then delayed by the rising edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle

    \item 3: input data is delayed by the rising edge of \hyperref[clk:clkhclk]{clk\_hclk} for (\hyperref[fielddesc:SPIDIN3NUM]{SPI\_DIN3\_NUM} +1) cycles, and then delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
\end{itemize}

\label{fielddesc:SPIDIN4MODE}\item [\textcolor{red}{SPI\_DIN4\_MODE (for SPI2 only)}] Configure the input mode for input data bit4 signal. Can be configured in CONF state. (R/W)

\begin{itemize}
    \item 0: input without delay
    \item 1: input data is delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for (\hyperref[fielddesc:SPIDIN4NUM]{SPI\_DIN4\_NUM} +1) cycles

    \item 2: input data is delayed by the rising edge of \hyperref[clk:clkhclk]{clk\_hclk} for (\hyperref[fielddesc:SPIDIN4NUM]{SPI\_DIN4\_NUM} +1) cycles, and then delayed by the rising edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle

    \item 3: input data is delayed by the rising edge of \hyperref[clk:clkhclk]{clk\_hclk} for (\hyperref[fielddesc:SPIDIN4NUM]{SPI\_DIN4\_NUM} +1) cycles, and then delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
\end{itemize}

\label{fielddesc:SPIDIN5MODE}\item [\textcolor{red}{SPI\_DIN5\_MODE (for SPI2 only)}] Configure the input mode for input data bit5 signal. Can be configured in CONF state. (R/W)

\begin{itemize}
    \item 0: input without delay
    \item 1: input data is delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for (\hyperref[fielddesc:SPIDIN5NUM]{SPI\_DIN5\_NUM} +1) cycles

    \item 2: input data is delayed by the rising edge of \hyperref[clk:clkhclk]{clk\_hclk} for (\hyperref[fielddesc:SPIDIN5NUM]{SPI\_DIN5\_NUM} +1) cycles, and then delayed by the rising edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle

    \item 3: input data is delayed by the rising edge of \hyperref[clk:clkhclk]{clk\_hclk} for (\hyperref[fielddesc:SPIDIN5NUM]{SPI\_DIN5\_NUM} + 1) cycles, and then delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
\end{itemize}

\label{fielddesc:SPIDIN6MODE}\item [\textcolor{red}{SPI\_DIN6\_MODE (for SPI2 only)}] Configure the input mode for input data bit6 signal. Can be configured in CONF state. (R/W)

\begin{itemize}
    \item 0: input without delay
    \item 1: input data is delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for (\hyperref[fielddesc:SPIDIN6NUM]{SPI\_DIN6\_NUM} +1) cycles

    \item 2: input data is delayed by the rising edge of \hyperref[clk:clkhclk]{clk\_hclk} for (\hyperref[fielddesc:SPIDIN6NUM]{SPI\_DIN6\_NUM} +1) cycles, and then delayed by the rising edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle

    \item 3: input data is delayed by the rising edge of \hyperref[clk:clkhclk]{clk\_hclk} for (\hyperref[fielddesc:SPIDIN6NUM]{SPI\_DIN6\_NUM} +1) cycles, and then delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
\end{itemize}

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{\textcolor{red}{SPI\_DIN\_MODE\_REG}}{0x{}0024}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:SPIDIN7MODE}\item [\textcolor{red}{SPI\_DIN7\_MODE (for SPI2 only)}]Configure the input mode for input data bit7 signal. Can be configured in CONF state. (R/W)

\begin{itemize}
    \item 0: input without delay
    \item 1: input data is delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for (\hyperref[fielddesc:SPIDIN7NUM]{SPI\_DIN7\_NUM} +1) cycles

    \item 2: input data is delayed by the rising edge of \hyperref[clk:clkhclk]{clk\_hclk} for (\hyperref[fielddesc:SPIDIN7NUM]{SPI\_DIN7\_NUM} +1) cycles, and then delayed by the rising edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle

    \item 3: input data is delayed by the rising edge of \hyperref[clk:clkhclk]{clk\_hclk} for (\hyperref[fielddesc:SPIDIN7NUM]{SPI\_DIN7\_NUM} +1) cycles, and then delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
\end{itemize}

\label{fielddesc:SPITIMINGHCLKACTIVE}\item [SPI\_TIMING\_HCLK\_ACTIVE] 1: Enable clk\_hclk (high-frequency clock) in SPI input timing module. 0: disable clk\_hclk. Can be configured in CONF state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{\textcolor{red}{SPI\_DIN\_NUM\_REG}}{0x{}0028}\label{regdesc:SPIDINNUMREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{(reserved)|\textcolor{red}{SPI\_DIN7\_NUM}}{2}{14}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_DIN6\_NUM}}{2}{12}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_DIN5\_NUM}}{2}{10}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_DIN4\_NUM}}{2}{8}{{0}}%
\regfield{SPI\_DIN3\_NUM}{2}{6}{{0}}%
\regfield{SPI\_DIN2\_NUM}{2}{4}{{0}}%
\regfield{SPI\_DIN1\_NUM}{2}{2}{{0}}%
\regfield{SPI\_DIN0\_NUM}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDIN0NUM}\item [SPI\_DIN0\_NUM] Configure the delays to input data bit0 signal based on the setting of \hyperref[fielddesc:SPIDIN0MODE]{SPI\_DIN0\_MODE}. Can be configured in CONF state. (R/W)

\label{fielddesc:SPIDIN1NUM}\item [SPI\_DIN1\_NUM] Configure the delays to input data bit1 signal based on the setting of \hyperref[fielddesc:SPIDIN1MODE]{SPI\_DIN1\_MODE}. Can be configured in CONF state. (R/W)

\label{fielddesc:SPIDIN2NUM}\item [SPI\_DIN2\_NUM] Configure the delays to input data bit2 signal based on the setting of \hyperref[fielddesc:SPIDIN2MODE]{SPI\_DIN2\_MODE}. Can be configured in CONF state. (R/W)

\label{fielddesc:SPIDIN3NUM}\item [SPI\_DIN3\_NUM] Configure the delays to input data bit3 signal based on the setting of \hyperref[fielddesc:SPIDIN3MODE]{SPI\_DIN3\_MODE}. Can be configured in CONF state. (R/W)

\label{fielddesc:SPIDIN4NUM}\item [\textcolor{red}{SPI\_DIN4\_NUM (for SPI2 only))}] Configure the delays to input data bit4 signal based on the setting of \hyperref[fielddesc:SPIDIN4MODE]{SPI\_DIN4\_MODE}. Can be configured in CONF state. (R/W)

\label{fielddesc:SPIDIN5NUM}\item [\textcolor{red}{SPI\_DIN5\_NUM (for SPI2 only)}] Configure the delays to input data bit5 signal based on the setting of \hyperref[fielddesc:SPIDIN5MODE]{SPI\_DIN5\_MODE}. Can be configured in CONF state. (R/W)

\label{fielddesc:SPIDIN6NUM}\item [\textcolor{red}{SPI\_DIN6\_NUM (for SPI2 only)}] Configure the delays to input data bit6 signal based on the setting of \hyperref[fielddesc:SPIDIN6MODE]{SPI\_DIN6\_MODE}. Can be configured in CONF state. (R/W)

\label{fielddesc:SPIDIN7NUM}\item [\textcolor{red}{SPI\_DIN7\_NUM (for SPI2 only)}] Configure the delays to input data bit7 signal based on the setting of \hyperref[fielddesc:SPIDIN7MODE]{SPI\_DIN7\_MODE}. Can be configured in CONF state. (R/W)

\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{\textcolor{red}{SPI\_DOUT\_MODE\_REG}}{0x{}002C}\label{regdesc:SPIDOUTMODEREG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{(reserved)|\textcolor{red}{SPI\_D\_DQS\_MODE}}{1}{8}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_DOUT7\_MODE}}{1}{7}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_DOUT6\_MODE}}{1}{6}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_DOUT5\_MODE}}{1}{5}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_DOUT4\_MODE}}{1}{4}{{0}}%
\regfield{SPI\_DOUT3\_MODE}{1}{3}{{0}}%
\regfield{SPI\_DOUT2\_MODE}{1}{2}{{0}}%
\regfield{SPI\_DOUT1\_MODE}{1}{1}{{0}}%
\regfield{SPI\_DOUT0\_MODE}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDOUT0MODE}\item [SPI\_DOUT0\_MODE] Configure the output mode for output data bit0 signal. Can be configured in CONF state. (R/W)

\begin{itemize}
    \item 0: output without delay
    \item 1: output data is delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
\end{itemize}

\label{fielddesc:SPIDOUT1MODE}\item [SPI\_DOUT1\_MODE] Configure the output mode for output data bit1 signal. Can be configured in CONF state. (R/W)

\begin{itemize}
    \item 0: output without delay
    \item 1: output data is delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
\end{itemize}

\label{fielddesc:SPIDOUT2MODE}\item [SPI\_DOUT2\_MODE] Configure the output mode for output data bit2 signal. Can be configured in CONF state. (R/W)

\begin{itemize}
    \item 0: output without delay
    \item 1: output data is delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
\end{itemize}

\label{fielddesc:SPIDOUT3MODE}\item [SPI\_DOUT3\_MODE] Configure the output mode for output data bit3 signal. Can be configured in CONF state. (R/W)

\begin{itemize}
    \item 0: output without delay
    \item 1: output data is delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
\end{itemize}

\label{fielddesc:SPIDOUT4MODE}\item [\textcolor{red}{SPI\_DOUT4\_MODE (for SPI2 only)}] Configure the output mode for output data bit4 signal. Can be configured in CONF state. (R/W)

\begin{itemize}
    \item 0: output without delay
    \item 1: output data is delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
\end{itemize}

\label{fielddesc:SPIDOUT5MODE}\item [\textcolor{red}{SPI\_DOUT5\_MODE  (for SPI2 only)}] Configure the output mode for output data bit5 signal. Can be configured in CONF state. (R/W)

\begin{itemize}
    \item 0: output without delay
    \item 1: output data is delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
\end{itemize}

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{\textcolor{red}{SPI\_DOUT\_MODE\_REG}}{0x{}002C}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:SPIDOUT6MODE}\item [\textcolor{red}{SPI\_DOUT6\_MODE  (for SPI2 only)}] Configure the output mode for output data bit6 signal. Can be configured in CONF state. (R/W)

\begin{itemize}
    \item 0: output without delay
    \item 1: output data is delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
\end{itemize}

\label{fielddesc:SPIDOUT7MODE}\item [\textcolor{red}{SPI\_DOUT7\_MODE  (for SPI2 only)}] Configure the output mode for output data bit7 signal. Can be configured in CONF state. (R/W)

\begin{itemize}
    \item 0: output without delay
    \item 1: output data is delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
\end{itemize}

\label{fielddesc:SPIDDQSMODE}\item [\textcolor{red}{SPI\_D\_DQS\_MODE  (for SPI2 only)}]
Configure the output mode for output SPI\_DQS signal. Can be configured in CONF state. (R/W)

\begin{itemize}
    \item 0: output without delay
    \item 1: output data is delayed by the falling edge of \hyperref[clk:SPICLK]{SPI\_CLK} for one cycle
\end{itemize}

\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{\textcolor{red}{SPI\_DMA\_INT\_ENA\_REG}}{0x{}0034}\label{regdesc:SPIDMAINTENAREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{SPI\_APP1\_INT\_ENA}{1}{20}{{0}}%
\regfield{SPI\_APP2\_INT\_ENA}{1}{19}{{0}}%
\regfield{SPI\_MST\_TX\_AFIFO\_REMPTY\_ERR\_INT\_ENA}{1}{18}{{0}}%
\regfield{SPI\_MST\_RX\_AFIFO\_WFULL\_ERR\_INT\_ENA}{1}{17}{{0}}%
\regfield{SPI\_SLV\_CMD\_ERR\_INT\_ENA}{1}{16}{{0}}%
\regfield{(reserved)}{1}{15}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_SEG\_MAGIC\_ERR\_INT\_ENA}}{1}{14}{{0}}%
\regfield{SPI\_DMA\_SEG\_TRANS\_DONE\_INT\_ENA}{1}{13}{{0}}%
\regfield{SPI\_TRANS\_DONE\_INT\_ENA}{1}{12}{{0}}%
\regfield{SPI\_SLV\_WR\_BUF\_DONE\_INT\_ENA}{1}{11}{{0}}%
\regfield{SPI\_SLV\_RD\_BUF\_DONE\_INT\_ENA}{1}{10}{{0}}%
\regfield{SPI\_SLV\_WR\_DMA\_DONE\_INT\_ENA}{1}{9}{{0}}%
\regfield{SPI\_SLV\_RD\_DMA\_DONE\_INT\_ENA}{1}{8}{{0}}%
\regfield{SPI\_SLV\_CMDA\_INT\_ENA}{1}{7}{{0}}%
\regfield{SPI\_SLV\_CMD9\_INT\_ENA}{1}{6}{{0}}%
\regfield{SPI\_SLV\_CMD8\_INT\_ENA}{1}{5}{{0}}%
\regfield{SPI\_SLV\_CMD7\_INT\_ENA}{1}{4}{{0}}%
\regfield{SPI\_SLV\_EN\_QPI\_INT\_ENA}{1}{3}{{0}}%
\regfield{SPI\_SLV\_EX\_QPI\_INT\_ENA}{1}{2}{{0}}%
\regfield{SPI\_DMA\_OUTFIFO\_EMPTY\_ERR\_INT\_ENA}{1}{1}{{0}}%
\regfield{SPI\_DMA\_INFIFO\_FULL\_ERR\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDMAINFIFOFULLERRINTENA}\item [SPI\_DMA\_INFIFO\_FULL\_ERR\_INT\_ENA] The enable bit for \hyperref[int:SPIINFIFOFULLERRINT]{SPI\_DMA\_INFIFO\_FULL\_ERR\_INT} interrupt. (R/W)
\label{fielddesc:SPIDMAOUTFIFOEMPTYERRINTENA}\item [SPI\_DMA\_OUTFIFO\_EMPTY\_ERR\_INT\_ENA] The enable bit for \hyperref[int:SPIOUTFIFOEMPTYERRINT]{SPI\_DMA\_OUTFIFO\_EMPTY\_ERR\_INT} interrupt. (R/W)
\label{fielddesc:SPISLVEXQPIINTENA}\item [SPI\_SLV\_EX\_QPI\_INT\_ENA] The enable bit for \hyperref[int:SPISLVEXQPIINT]{SPI\_SLV\_EX\_QPI\_INT} interrupt. (R/W)
\label{fielddesc:SPISLVENQPIINTENA}\item [SPI\_SLV\_EN\_QPI\_INT\_ENA] The enable bit for \hyperref[int:SPISLVENQPIINT]{SPI\_SLV\_EN\_QPI\_INT} interrupt. (R/W)
\label{fielddesc:SPISLVCMD7INTENA}\item [SPI\_SLV\_CMD7\_INT\_ENA] The enable bit for \hyperref[int:SPISLVCMD7INT]{SPI\_SLV\_CMD7\_INT} interrupt. (R/W)
\label{fielddesc:SPISLVCMD8INTENA}\item [SPI\_SLV\_CMD8\_INT\_ENA] The enable bit for \hyperref[int:SPISLVCMD8INT]{SPI\_SLV\_CMD8\_INT} interrupt. (R/W)
\label{fielddesc:SPISLVCMD9INTENA}\item [SPI\_SLV\_CMD9\_INT\_ENA] The enable bit for \hyperref[int:SPISLVCMD9INT]{SPI\_SLV\_CMD9\_INT} interrupt. (R/W)
\label{fielddesc:SPISLVCMDAINTENA}\item [SPI\_SLV\_CMDA\_INT\_ENA] The enable bit for \hyperref[int:SPISLVCMDAINT]{SPI\_SLV\_CMDA\_INT} interrupt. (R/W)
\label{fielddesc:SPISLVRDDMADONEINTENA}\item [SPI\_SLV\_RD\_DMA\_DONE\_INT\_ENA] The enable bit for \hyperref[int:SPISLVRDDMADONEINT]{SPI\_SLV\_RD\_DMA\_DONE\_INT} interrupt. (R/W)
\label{fielddesc:SPISLVWRDMADONEINTENA}\item [SPI\_SLV\_WR\_DMA\_DONE\_INT\_ENA] The enable bit for \hyperref[int:SPISLVWRDMADONEINT]{SPI\_SLV\_WR\_DMA\_DONE\_INT} interrupt. (R/W)
\label{fielddesc:SPISLVRDBUFDONEINTENA}\item [SPI\_SLV\_RD\_BUF\_DONE\_INT\_ENA] The enable bit for \hyperref[int:SPISLVRDBUFDONEINT]{SPI\_SLV\_RD\_BUF\_DONE\_INT} interrupt. (R/W)
\label{fielddesc:SPISLVWRBUFDONEINTENA}\item [SPI\_SLV\_WR\_BUF\_DONE\_INT\_ENA] The enable bit for \hyperref[int:SPISLVWRBUFDONEINT]{SPI\_SLV\_WR\_BUF\_DONE\_INT} interrupt. (R/W)
\label{fielddesc:SPITRANSDONEINTENA}\item [SPI\_TRANS\_DONE\_INT\_ENA] The enable bit for \hyperref[int:SPITRANSDONEINT]{SPI\_TRANS\_DONE\_INT} interrupt. (R/W)
\label{fielddesc:SPIDMASEGTRANSDONEINTENA}\item [SPI\_DMA\_SEG\_TRANS\_DONE\_INT\_ENA] The enable bit for \hyperref[int:SPIDMASEGTRANSDONEINT]{SPI\_DMA\_SEG\_TRANS\_DONE\_INT} interrupt. (R/W)
\label{fielddesc:SPISEGMAGICERRINTENA}\item [\textcolor{red}{SPI\_SEG\_MAGIC\_ERR\_INT\_ENA (for SPI2 only)}] The enable bit for \hyperref[int:SPISEGMAGICERRINT]{SPI\_SEG\_MAGIC\_ERR\_INT} interrupt. (R/W)
\label{fielddesc:SPISLVCMDERRINTENA}\item [SPI\_SLV\_CMD\_ERR\_INT\_ENA] The enable bit for \hyperref[int:SPISLVCMDERRINT]{SPI\_SLV\_CMD\_ERR\_INT} interrupt. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{\textcolor{red}{SPI\_DMA\_INT\_ENA\_REG}}{0x{}0034}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\label{fielddesc:SPIMSTRXAFIFOWFULLERRINTENA}\item [SPI\_MST\_RX\_AFIFO\_WFULL\_ERR\_INT\_ENA] The enable bit for \hyperref[int:SPIMSTRXAFIFOWFULLERRINT]{SPI\_MST\_RX\_AFIFO\_WFULL\_ERR\_INT} interrupt. (R/W)
\label{fielddesc:SPIMSTTXAFIFOREMPTYERRINTENA}\item [SPI\_MST\_TX\_AFIFO\_REMPTY\_ERR\_INT\_ENA] The enable bit for \hyperref[int:SPIMSTTXAFIFOREMPTYERRINT]{SPI\_MST\_TX\_AFIFO\_REMPTY\_ERR\_INT} interrupt. (R/W)
\label{fielddesc:SPIAPP2INTENA}\item [SPI\_APP2\_INT\_ENA] The enable bit for \hyperref[int:SPIAPP2INT]{SPI\_APP2\_INT} interrupt. (R/W)
\label{fielddesc:SPIAPP1INTENA}\item [SPI\_APP1\_INT\_ENA] The enable bit for \hyperref[int:SPIAPP1INT]{SPI\_APP1\_INT} interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{\textcolor{red}{SPI\_DMA\_INT\_CLR\_REG}}{0x{}0038}\label{regdesc:SPIDMAINTCLRREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{SPI\_APP1\_INT\_CLR}{1}{20}{{0}}%
\regfield{SPI\_APP2\_INT\_CLR}{1}{19}{{0}}%
\regfield{SPI\_MST\_TX\_AFIFO\_REMPTY\_ERR\_INT\_CLR}{1}{18}{{0}}%
\regfield{SPI\_MST\_RX\_AFIFO\_WFULL\_ERR\_INT\_CLR}{1}{17}{{0}}%
\regfield{SPI\_SLV\_CMD\_ERR\_INT\_CLR}{1}{16}{{0}}%
\regfield{(reserved)}{1}{15}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_SEG\_MAGIC\_ERR\_INT\_CLR}}{1}{14}{{0}}%
\regfield{SPI\_DMA\_SEG\_TRANS\_DONE\_INT\_CLR}{1}{13}{{0}}%
\regfield{SPI\_TRANS\_DONE\_INT\_CLR}{1}{12}{{0}}%
\regfield{SPI\_SLV\_WR\_BUF\_DONE\_INT\_CLR}{1}{11}{{0}}%
\regfield{SPI\_SLV\_RD\_BUF\_DONE\_INT\_CLR}{1}{10}{{0}}%
\regfield{SPI\_SLV\_WR\_DMA\_DONE\_INT\_CLR}{1}{9}{{0}}%
\regfield{SPI\_SLV\_RD\_DMA\_DONE\_INT\_CLR}{1}{8}{{0}}%
\regfield{SPI\_SLV\_CMDA\_INT\_CLR}{1}{7}{{0}}%
\regfield{SPI\_SLV\_CMD9\_INT\_CLR}{1}{6}{{0}}%
\regfield{SPI\_SLV\_CMD8\_INT\_CLR}{1}{5}{{0}}%
\regfield{SPI\_SLV\_CMD7\_INT\_CLR}{1}{4}{{0}}%
\regfield{SPI\_SLV\_EN\_QPI\_INT\_CLR}{1}{3}{{0}}%
\regfield{SPI\_SLV\_EX\_QPI\_INT\_CLR}{1}{2}{{0}}%
\regfield{SPI\_DMA\_OUTFIFO\_EMPTY\_ERR\_INT\_CLR}{1}{1}{{0}}%
\regfield{SPI\_DMA\_INFIFO\_FULL\_ERR\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDMAINFIFOFULLERRINTCLR}\item [SPI\_DMA\_INFIFO\_FULL\_ERR\_INT\_CLR] The clear bit for \hyperref[int:SPIINFIFOFULLERRINT]{SPI\_DMA\_INFIFO\_FULL\_ERR\_INT} interrupt. (WT)
\label{fielddesc:SPIDMAOUTFIFOEMPTYERRINTCLR}\item [SPI\_DMA\_OUTFIFO\_EMPTY\_ERR\_INT\_CLR] The clear bit for \hyperref[int:SPIOUTFIFOEMPTYERRINT]{SPI\_DMA\_OUTFIFO\_EMPTY\_ERR\_INT}interrupt. (WT)
\label{fielddesc:SPISLVEXQPIINTCLR}\item [SPI\_SLV\_EX\_QPI\_INT\_CLR] The clear bit for \hyperref[int:SPISLVEXQPIINT]{SPI\_SLV\_EX\_QPI\_INT} interrupt. (WT)
\label{fielddesc:SPISLVENQPIINTCLR}\item [SPI\_SLV\_EN\_QPI\_INT\_CLR] The clear bit for \hyperref[int:SPISLVENQPIINT]{SPI\_SLV\_EN\_QPI\_INT} interrupt. (WT)
\label{fielddesc:SPISLVCMD7INTCLR}\item [SPI\_SLV\_CMD7\_INT\_CLR] The clear bit for \hyperref[int:SPISLVCMD7INT]{SPI\_SLV\_CMD7\_INT} interrupt. (WT)
\label{fielddesc:SPISLVCMD8INTCLR}\item [SPI\_SLV\_CMD8\_INT\_CLR] The clear bit for \hyperref[int:SPISLVCMD8INT]{SPI\_SLV\_CMD8\_INT} interrupt. (WT)
\label{fielddesc:SPISLVCMD9INTCLR}\item [SPI\_SLV\_CMD9\_INT\_CLR] The clear bit for \hyperref[int:SPISLVCMD9INT]{SPI\_SLV\_CMD9\_INT} interrupt. (WT)
\label{fielddesc:SPISLVCMDAINTCLR}\item [SPI\_SLV\_CMDA\_INT\_CLR] The clear bit for \hyperref[int:SPISLVCMDAINT]{SPI\_SLV\_CMDA\_INT} interrupt. (WT)
\label{fielddesc:SPISLVRDDMADONEINTCLR}\item [SPI\_SLV\_RD\_DMA\_DONE\_INT\_CLR] The clear bit for \hyperref[int:SPISLVRDDMADONEINT]{SPI\_SLV\_RD\_DMA\_DONE\_INT} interrupt. (WT)
\label{fielddesc:SPISLVWRDMADONEINTCLR}\item [SPI\_SLV\_WR\_DMA\_DONE\_INT\_CLR] The clear bit for \hyperref[int:SPISLVWRDMADONEINT]{SPI\_SLV\_WR\_DMA\_DONE\_INT} interrupt. (WT)
\label{fielddesc:SPISLVRDBUFDONEINTCLR}\item [SPI\_SLV\_RD\_BUF\_DONE\_INT\_CLR] The clear bit for \hyperref[int:SPISLVRDBUFDONEINT]{SPI\_SLV\_RD\_BUF\_DONE\_INT} interrupt. (WT)
\label{fielddesc:SPISLVWRBUFDONEINTCLR}\item [SPI\_SLV\_WR\_BUF\_DONE\_INT\_CLR] The clear bit for \hyperref[int:SPISLVWRBUFDONEINT]{SPI\_SLV\_WR\_BUF\_DONE\_INT} interrupt. (WT)
\label{fielddesc:SPITRANSDONEINTCLR}\item [SPI\_TRANS\_DONE\_INT\_CLR] The clear bit for \hyperref[int:SPITRANSDONEINT]{SPI\_TRANS\_DONE\_INT} interrupt. (WT)
\label{fielddesc:SPIDMASEGTRANSDONEINTCLR}\item [SPI\_DMA\_SEG\_TRANS\_DONE\_INT\_CLR] The clear bit for \hyperref[int:SPIDMASEGTRANSDONEINT]{SPI\_DMA\_SEG\_TRANS\_DONE\_INT} interrupt. (WT)
\label{fielddesc:SPISEGMAGICERRINTCLR}\item [\textcolor{red}{SPI\_SEG\_MAGIC\_ERR\_INT\_CLR (for SPI2 only)}] The clear bit for \hyperref[int:SPISEGMAGICERRINT]{SPI\_SEG\_MAGIC\_ERR\_INT} interrupt. (WT)
\label{fielddesc:SPISLVCMDERRINTCLR}\item [SPI\_SLV\_CMD\_ERR\_INT\_CLR] The clear bit for \hyperref[int:SPISLVCMDERRINT]{SPI\_SLV\_CMD\_ERR\_INT} interrupt. (WT)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{\textcolor{red}{SPI\_DMA\_INT\_CLR\_REG}}{0x{}0038}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\label{fielddesc:SPIMSTRXAFIFOWFULLERRINTCLR}\item [SPI\_MST\_RX\_AFIFO\_WFULL\_ERR\_INT\_CLR] The clear bit for \hyperref[int:SPIMSTRXAFIFOWFULLERRINT]{SPI\_MST\_RX\_AFIFO\_WFULL\_ERR\_INT} interrupt. (WT)
\label{fielddesc:SPIMSTTXAFIFOREMPTYERRINTCLR}\item [SPI\_MST\_TX\_AFIFO\_REMPTY\_ERR\_INT\_CLR] The clear bit for \hyperref[int:SPIMSTTXAFIFOREMPTYERRINT]{SPI\_MST\_TX\_AFIFO\_REMPTY\_ERR\_INT} interrupt. (WT)
\label{fielddesc:SPIAPP2INTCLR}\item [SPI\_APP2\_INT\_CLR] The clear bit for \hyperref[int:SPIAPP2INT]{SPI\_APP2\_INT} interrupt. (WT)
\label{fielddesc:SPIAPP1INTCLR}\item [SPI\_APP1\_INT\_CLR] The clear bit for \hyperref[int:SPIAPP1INT]{SPI\_APP1\_INT} interrupt. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{\textcolor{red}{SPI\_DMA\_INT\_RAW\_REG}}{0x{}003C}\label{regdesc:SPIDMAINTRAWREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{SPI\_APP1\_INT\_RAW}{1}{20}{{0}}%
\regfield{SPI\_APP2\_INT\_RAW}{1}{19}{{0}}%
\regfield{SPI\_MST\_TX\_AFIFO\_REMPTY\_ERR\_INT\_RAW}{1}{18}{{0}}%
\regfield{SPI\_MST\_RX\_AFIFO\_WFULL\_ERR\_INT\_RAW}{1}{17}{{0}}%
\regfield{SPI\_SLV\_CMD\_ERR\_INT\_RAW}{1}{16}{{0}}%
\regfield{(reserved)}{1}{15}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_SEG\_MAGIC\_ERR\_INT\_RAW}}{1}{14}{{0}}%
\regfield{SPI\_DMA\_SEG\_TRANS\_DONE\_INT\_RAW}{1}{13}{{0}}%
\regfield{SPI\_TRANS\_DONE\_INT\_RAW}{1}{12}{{0}}%
\regfield{SPI\_SLV\_WR\_BUF\_DONE\_INT\_RAW}{1}{11}{{0}}%
\regfield{SPI\_SLV\_RD\_BUF\_DONE\_INT\_RAW}{1}{10}{{0}}%
\regfield{SPI\_SLV\_WR\_DMA\_DONE\_INT\_RAW}{1}{9}{{0}}%
\regfield{SPI\_SLV\_RD\_DMA\_DONE\_INT\_RAW}{1}{8}{{0}}%
\regfield{SPI\_SLV\_CMDA\_INT\_RAW}{1}{7}{{0}}%
\regfield{SPI\_SLV\_CMD9\_INT\_RAW}{1}{6}{{0}}%
\regfield{SPI\_SLV\_CMD8\_INT\_RAW}{1}{5}{{0}}%
\regfield{SPI\_SLV\_CMD7\_INT\_RAW}{1}{4}{{0}}%
\regfield{SPI\_SLV\_EN\_QPI\_INT\_RAW}{1}{3}{{0}}%
\regfield{SPI\_SLV\_EX\_QPI\_INT\_RAW}{1}{2}{{0}}%
\regfield{SPI\_DMA\_OUTFIFO\_EMPTY\_ERR\_INT\_RAW}{1}{1}{{0}}%
\regfield{SPI\_DMA\_INFIFO\_FULL\_ERR\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDMAINFIFOFULLERRINTRAW}\item [SPI\_DMA\_INFIFO\_FULL\_ERR\_INT\_RAW] The raw bit for \hyperref[int:SPIINFIFOFULLERRINT]{SPI\_DMA\_INFIFO\_FULL\_ERR\_INT} interrupt. (R/WTC/SS)
\label{fielddesc:SPIDMAOUTFIFOEMPTYERRINTRAW}\item [SPI\_DMA\_OUTFIFO\_EMPTY\_ERR\_INT\_RAW] The raw bit for \hyperref[int:SPIOUTFIFOEMPTYERRINT]{SPI\_DMA\_OUTFIFO\_EMPTY\_ERR\_INT}interrupt. (R/WTC/SS)
\label{fielddesc:SPISLVEXQPIINTRAW}\item [SPI\_SLV\_EX\_QPI\_INT\_RAW] The raw bit for \hyperref[int:SPISLVEXQPIINT]{SPI\_SLV\_EX\_QPI\_INT} interrupt. (R/WTC/SS)
\label{fielddesc:SPISLVENQPIINTRAW}\item [SPI\_SLV\_EN\_QPI\_INT\_RAW] The raw bit for \hyperref[int:SPISLVENQPIINT]{SPI\_SLV\_EN\_QPI\_INT} interrupt. (R/WTC/SS)
\label{fielddesc:SPISLVCMD7INTRAW}\item [SPI\_SLV\_CMD7\_INT\_RAW] The raw bit for \hyperref[int:SPISLVCMD7INT]{SPI\_SLV\_CMD7\_INT} interrupt. (R/WTC/SS)
\label{fielddesc:SPISLVCMD8INTRAW}\item [SPI\_SLV\_CMD8\_INT\_RAW] The raw bit for \hyperref[int:SPISLVCMD8INT]{SPI\_SLV\_CMD8\_INT} interrupt. (R/WTC/SS)
\label{fielddesc:SPISLVCMD9INTRAW}\item [SPI\_SLV\_CMD9\_INT\_RAW] The raw bit for \hyperref[int:SPISLVCMD9INT]{SPI\_SLV\_CMD9\_INT} interrupt. (R/WTC/SS)
\label{fielddesc:SPISLVCMDAINTRAW}\item [SPI\_SLV\_CMDA\_INT\_RAW] The raw bit for \hyperref[int:SPISLVCMDAINT]{SPI\_SLV\_CMDA\_INT} interrupt. (R/WTC/SS)
\label{fielddesc:SPISLVRDDMADONEINTRAW}\item [SPI\_SLV\_RD\_DMA\_DONE\_INT\_RAW] The raw bit for \hyperref[int:SPISLVRDDMADONEINT]{SPI\_SLV\_RD\_DMA\_DONE\_INT} interrupt. (R/WTC/SS)
\label{fielddesc:SPISLVWRDMADONEINTRAW}\item [SPI\_SLV\_WR\_DMA\_DONE\_INT\_RAW] The raw bit for \hyperref[int:SPISLVWRDMADONEINT]{SPI\_SLV\_WR\_DMA\_DONE\_INT} interrupt. (R/WTC/SS)
\label{fielddesc:SPISLVRDBUFDONEINTRAW}\item [SPI\_SLV\_RD\_BUF\_DONE\_INT\_RAW] The raw bit for \hyperref[int:SPISLVRDBUFDONEINT]{SPI\_SLV\_RD\_BUF\_DONE\_INT} interrupt. (R/WTC/SS)
\label{fielddesc:SPISLVWRBUFDONEINTRAW}\item [SPI\_SLV\_WR\_BUF\_DONE\_INT\_RAW] The raw bit for \hyperref[int:SPISLVWRBUFDONEINT]{SPI\_SLV\_WR\_BUF\_DONE\_INT} interrupt. (R/WTC/SS)
\label{fielddesc:SPITRANSDONEINTRAW}\item [SPI\_TRANS\_DONE\_INT\_RAW] The raw bit for \hyperref[int:SPITRANSDONEINT]{SPI\_TRANS\_DONE\_INT} interrupt. (R/WTC/SS)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{\textcolor{red}{SPI\_DMA\_INT\_RAW\_REG}}{0x{}003C}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\label{fielddesc:SPIDMASEGTRANSDONEINTRAW}\item [SPI\_DMA\_SEG\_TRANS\_DONE\_INT\_RAW] The raw bit for \hyperref[int:SPIDMASEGTRANSDONEINT]{SPI\_DMA\_SEG\_TRANS\_DONE\_INT} interrupt. (R/WTC/SS)
\label{fielddesc:SPISEGMAGICERRINTRAW}\item [\textcolor{red}{SPI\_SEG\_MAGIC\_ERR\_INT\_RAW (for SPI2 only)}] The raw bit for \hyperref[int:SPISEGMAGICERRINT]{SPI\_SEG\_MAGIC\_ERR\_INT} interrupt. (R/WTC/SS)
\label{fielddesc:SPISLVCMDERRINTRAW}\item [SPI\_SLV\_CMD\_ERR\_INT\_RAW] The raw bit for \hyperref[int:SPISLVCMDERRINT]{SPI\_SLV\_CMD\_ERR\_INT} interrupt. (R/WTC/SS)
\label{fielddesc:SPIMSTRXAFIFOWFULLERRINTRAW}\item [SPI\_MST\_RX\_AFIFO\_WFULL\_ERR\_INT\_RAW] The raw bit for \hyperref[int:SPIMSTRXAFIFOWFULLERRINT]{SPI\_MST\_RX\_AFIFO\_WFULL\_ERR\_INT} interrupt. (R/WTC/SS)
\label{fielddesc:SPIMSTTXAFIFOREMPTYERRINTRAW}\item [SPI\_MST\_TX\_AFIFO\_REMPTY\_ERR\_INT\_RAW] The raw bit for \hyperref[int:SPIMSTTXAFIFOREMPTYERRINT]{SPI\_MST\_TX\_AFIFO\_REMPTY\_ERR\_INT} interrupt. (R/WTC/SS)
\label{fielddesc:SPIAPP2INTRAW}\item [SPI\_APP2\_INT\_RAW] The raw bit for \hyperref[int:SPIAPP2INT]{SPI\_APP2\_INT} interrupt. The value is only controlled by software. (R/WTC/SS)
\label{fielddesc:SPIAPP1INTRAW}\item [SPI\_APP1\_INT\_RAW] The raw bit for \hyperref[int:SPIAPP1INT]{SPI\_APP1\_INT} interrupt. The value is only controlled by software. (R/WTC/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{\textcolor{red}{SPI\_DMA\_INT\_ST\_REG}}{0x{}0040}\label{regdesc:SPIDMAINTSTREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{SPI\_APP1\_INT\_ST}{1}{20}{{0}}%
\regfield{SPI\_APP2\_INT\_ST}{1}{19}{{0}}%
\regfield{SPI\_MST\_TX\_AFIFO\_REMPTY\_ERR\_INT\_ST}{1}{18}{{0}}%
\regfield{SPI\_MST\_RX\_AFIFO\_WFULL\_ERR\_INT\_ST}{1}{17}{{0}}%
\regfield{SPI\_SLV\_CMD\_ERR\_INT\_ST}{1}{16}{{0}}%
\regfield{(reserved)}{1}{15}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_SEG\_MAGIC\_ERR\_INT\_ST}}{1}{14}{{0}}%
\regfield{SPI\_DMA\_SEG\_TRANS\_DONE\_INT\_ST}{1}{13}{{0}}%
\regfield{SPI\_TRANS\_DONE\_INT\_ST}{1}{12}{{0}}%
\regfield{SPI\_SLV\_WR\_BUF\_DONE\_INT\_ST}{1}{11}{{0}}%
\regfield{SPI\_SLV\_RD\_BUF\_DONE\_INT\_ST}{1}{10}{{0}}%
\regfield{SPI\_SLV\_WR\_DMA\_DONE\_INT\_ST}{1}{9}{{0}}%
\regfield{SPI\_SLV\_RD\_DMA\_DONE\_INT\_ST}{1}{8}{{0}}%
\regfield{SPI\_SLV\_CMDA\_INT\_ST}{1}{7}{{0}}%
\regfield{SPI\_SLV\_CMD9\_INT\_ST}{1}{6}{{0}}%
\regfield{SPI\_SLV\_CMD8\_INT\_ST}{1}{5}{{0}}%
\regfield{SPI\_SLV\_CMD7\_INT\_ST}{1}{4}{{0}}%
\regfield{SPI\_SLV\_EN\_QPI\_INT\_ST}{1}{3}{{0}}%
\regfield{SPI\_SLV\_EX\_QPI\_INT\_ST}{1}{2}{{0}}%
\regfield{SPI\_DMA\_OUTFIFO\_EMPTY\_ERR\_INT\_ST}{1}{1}{{0}}%
\regfield{SPI\_DMA\_INFIFO\_FULL\_ERR\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDMAINFIFOFULLERRINTST}\item [SPI\_DMA\_INFIFO\_FULL\_ERR\_INT\_ST] The status bit for \hyperref[int:SPIINFIFOFULLERRINT]{SPI\_DMA\_INFIFO\_FULL\_ERR\_INT} interrupt. (RO)
\label{fielddesc:SPIDMAOUTFIFOEMPTYERRINTST}\item [SPI\_DMA\_OUTFIFO\_EMPTY\_ERR\_INT\_ST] The status bit for \hyperref[int:SPIOUTFIFOEMPTYERRINT]{SPI\_DMA\_OUTFIFO\_EMPTY\_ERR\_INT} interrupt. (RO)
\label{fielddesc:SPISLVEXQPIINTST}\item [SPI\_SLV\_EX\_QPI\_INT\_ST] The status bit for \hyperref[int:SPISLVEXQPIINT]{SPI\_SLV\_EX\_QPI\_INT} interrupt. (RO)
\label{fielddesc:SPISLVENQPIINTST}\item [SPI\_SLV\_EN\_QPI\_INT\_ST] The status bit for \hyperref[int:SPISLVENQPIINT]{SPI\_SLV\_EN\_QPI\_INT} interrupt. (RO)
\label{fielddesc:SPISLVCMD7INTST}\item [SPI\_SLV\_CMD7\_INT\_ST] The status bit for \hyperref[int:SPISLVCMD7INT]{SPI\_SLV\_CMD7\_INT} interrupt. (RO)
\label{fielddesc:SPISLVCMD8INTST}\item [SPI\_SLV\_CMD8\_INT\_ST] The status bit for \hyperref[int:SPISLVCMD8INT]{SPI\_SLV\_CMD8\_INT} interrupt. (RO)
\label{fielddesc:SPISLVCMD9INTST}\item [SPI\_SLV\_CMD9\_INT\_ST] The status bit for \hyperref[int:SPISLVCMD9INT]{SPI\_SLV\_CMD9\_INT} interrupt. (RO)
\label{fielddesc:SPISLVCMDAINTST}\item [SPI\_SLV\_CMDA\_INT\_ST] The status bit for \hyperref[int:SPISLVCMDAINT]{SPI\_SLV\_CMDA\_INT} interrupt. (RO)
\label{fielddesc:SPISLVRDDMADONEINTST}\item [SPI\_SLV\_RD\_DMA\_DONE\_INT\_ST] The status bit for \hyperref[int:SPISLVRDDMADONEINT]{SPI\_SLV\_RD\_DMA\_DONE\_INT} interrupt. (RO)
\label{fielddesc:SPISLVWRDMADONEINTST}\item [SPI\_SLV\_WR\_DMA\_DONE\_INT\_ST] The status bit for \hyperref[int:SPISLVWRDMADONEINT]{SPI\_SLV\_WR\_DMA\_DONE\_INT} interrupt. (RO)
\label{fielddesc:SPISLVRDBUFDONEINTST}\item [SPI\_SLV\_RD\_BUF\_DONE\_INT\_ST] The status bit for \hyperref[int:SPISLVRDBUFDONEINT]{SPI\_SLV\_RD\_BUF\_DONE\_INT} interrupt. (RO)
\label{fielddesc:SPISLVWRBUFDONEINTST}\item [SPI\_SLV\_WR\_BUF\_DONE\_INT\_ST] The status bit for \hyperref[int:SPISLVWRBUFDONEINT]{SPI\_SLV\_WR\_BUF\_DONE\_INT} interrupt. (RO)
\label{fielddesc:SPITRANSDONEINTST}\item [SPI\_TRANS\_DONE\_INT\_ST] The status bit for \hyperref[int:SPITRANSDONEINT]{SPI\_TRANS\_DONE\_INT} interrupt. (RO)
\label{fielddesc:SPIDMASEGTRANSDONEINTST}\item [SPI\_DMA\_SEG\_TRANS\_DONE\_INT\_ST] The status bit for \hyperref[int:SPIDMASEGTRANSDONEINT]{SPI\_DMA\_SEG\_TRANS\_DONE\_INT} interrupt. (RO)
\label{fielddesc:SPISEGMAGICERRINTST}\item [\textcolor{red}{SPI\_SEG\_MAGIC\_ERR\_INT\_ST (for SPI2 only)}] The status bit for \hyperref[int:SPISEGMAGICERRINT]{SPI\_SEG\_MAGIC\_ERR\_INT} interrupt. (RO)
\label{fielddesc:SPISLVCMDERRINTST}\item [SPI\_SLV\_CMD\_ERR\_INT\_ST] The status bit for \hyperref[int:SPISLVCMDERRINT]{SPI\_SLV\_CMD\_ERR\_INT} interrupt. (RO)
\label{fielddesc:SPIMSTRXAFIFOWFULLERRINTST}\item [SPI\_MST\_RX\_AFIFO\_WFULL\_ERR\_INT\_ST] The status bit for \hyperref[int:SPIMSTRXAFIFOWFULLERRINT]{SPI\_MST\_RX\_AFIFO\_WFULL\_ERR\_INT} interrupt. (RO)


\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{\textcolor{red}{SPI\_DMA\_INT\_ST\_REG}}{0x{}0040}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\label{fielddesc:SPIMSTTXAFIFOREMPTYERRINTST}\item [SPI\_MST\_TX\_AFIFO\_REMPTY\_ERR\_INT\_ST] The status bit for \hyperref[int:SPIMSTTXAFIFOREMPTYERRINT]{SPI\_MST\_TX\_AFIFO\_REMPTY\_ERR\_INT} interrupt. (RO)
\label{fielddesc:SPIAPP2INTST}\item [SPI\_APP2\_INT\_ST] The status bit for \hyperref[int:SPIAPP2INT]{SPI\_APP2\_INT} interrupt. (RO)
\label{fielddesc:SPIAPP1INTST}\item [SPI\_APP1\_INT\_ST] The status bit for \hyperref[int:SPIAPP1INT]{SPI\_APP1\_INT} interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{\textcolor{red}{SPI\_DMA\_INT\_SET\_REG}}{0x{}0044}\label{regdesc:SPIDMAINTSETREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{SPI\_APP1\_INT\_SET}{1}{20}{{0}}%
\regfield{SPI\_APP2\_INT\_SET}{1}{19}{{0}}%
\regfield{SPI\_MST\_TX\_AFIFO\_REMPTY\_ERR\_INT\_SET}{1}{18}{{0}}%
\regfield{SPI\_MST\_RX\_AFIFO\_WFULL\_ERR\_INT\_SET}{1}{17}{{0}}%
\regfield{SPI\_SLV\_CMD\_ERR\_INT\_SET}{1}{16}{{0}}%
\regfield{(reserved)}{1}{15}{{0}}%
\regfield{(reserved)|\textcolor{red}{SPI\_SEG\_MAGIC\_ERR\_INT\_SET}}{1}{14}{{0}}%
\regfield{SPI\_DMA\_SEG\_TRANS\_DONE\_INT\_SET}{1}{13}{{0}}%
\regfield{SPI\_TRANS\_DONE\_INT\_SET}{1}{12}{{0}}%
\regfield{SPI\_SLV\_WR\_BUF\_DONE\_INT\_SET}{1}{11}{{0}}%
\regfield{SPI\_SLV\_RD\_BUF\_DONE\_INT\_SET}{1}{10}{{0}}%
\regfield{SPI\_SLV\_WR\_DMA\_DONE\_INT\_SET}{1}{9}{{0}}%
\regfield{SPI\_SLV\_RD\_DMA\_DONE\_INT\_SET}{1}{8}{{0}}%
\regfield{SPI\_SLV\_CMDA\_INT\_SET}{1}{7}{{0}}%
\regfield{SPI\_SLV\_CMD9\_INT\_SET}{1}{6}{{0}}%
\regfield{SPI\_SLV\_CMD8\_INT\_SET}{1}{5}{{0}}%
\regfield{SPI\_SLV\_CMD7\_INT\_SET}{1}{4}{{0}}%
\regfield{SPI\_SLV\_EN\_QPI\_INT\_SET}{1}{3}{{0}}%
\regfield{SPI\_SLV\_EX\_QPI\_INT\_SET}{1}{2}{{0}}%
\regfield{SPI\_DMA\_OUTFIFO\_EMPTY\_ERR\_INT\_SET}{1}{1}{{0}}%
\regfield{SPI\_DMA\_INFIFO\_FULL\_ERR\_INT\_SET}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDMAINFIFOFULLERRINTSET}\item [SPI\_DMA\_INFIFO\_FULL\_ERR\_INT\_SET] The software set bit for \hyperref[int:SPIINFIFOFULLERRINT]{SPI\_DMA\_INFIFO\_FULL\_ERR\_INT} interrupt. (WT)
\label{fielddesc:SPIDMAOUTFIFOEMPTYERRINTSET}\item [SPI\_DMA\_OUTFIFO\_EMPTY\_ERR\_INT\_SET] The software set bit for \hyperref[int:SPIOUTFIFOEMPTYERRINT]{SPI\_DMA\_OUTFIFO\_EMPTY\_ERR\_INT} interrupt. (WT)
\label{fielddesc:SPISLVEXQPIINTSET}\item [SPI\_SLV\_EX\_QPI\_INT\_SET] The software set bit for \hyperref[int:SPISLVEXQPIINT]{SPI\_SLV\_EX\_QPI\_INT} interrupt. (WT)
\label{fielddesc:SPISLVENQPIINTSET}\item [SPI\_SLV\_EN\_QPI\_INT\_SET] The software set bit for \hyperref[int:SPISLVENQPIINT]{SPI\_SLV\_EN\_QPI\_INT} interrupt. (WT)
\label{fielddesc:SPISLVCMD7INTSET}\item [SPI\_SLV\_CMD7\_INT\_SET] The software set bit for \hyperref[int:SPISLVCMD7INT]{SPI\_SLV\_CMD7\_INT} interrupt. (WT)
\label{fielddesc:SPISLVCMD8INTSET}\item [SPI\_SLV\_CMD8\_INT\_SET] The software set bit for \hyperref[int:SPISLVCMD8INT]{SPI\_SLV\_CMD8\_INT} interrupt. (WT)
\label{fielddesc:SPISLVCMD9INTSET}\item [SPI\_SLV\_CMD9\_INT\_SET] The software set bit for \hyperref[int:SPISLVCMD9INT]{SPI\_SLV\_CMD9\_INT} interrupt. (WT)
\label{fielddesc:SPISLVCMDAINTSET}\item [SPI\_SLV\_CMDA\_INT\_SET] The software set bit for \hyperref[int:SPISLVCMDAINT]{SPI\_SLV\_CMDA\_INT} interrupt. (WT)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{\textcolor{red}{SPI\_DMA\_INT\_SET\_REG}}{0x{}0044}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\label{fielddesc:SPISLVRDDMADONEINTSET}\item [SPI\_SLV\_RD\_DMA\_DONE\_INT\_SET] The software set bit for \hyperref[int:SPISLVRDDMADONEINT]{SPI\_SLV\_RD\_DMA\_DONE\_INT} interrupt. (WT)
\label{fielddesc:SPISLVWRDMADONEINTSET}\item [SPI\_SLV\_WR\_DMA\_DONE\_INT\_SET] The software set bit for \hyperref[int:SPISLVWRDMADONEINT]{SPI\_SLV\_WR\_DMA\_DONE\_INT} interrupt. (WT)
\label{fielddesc:SPISLVRDBUFDONEINTSET}\item [SPI\_SLV\_RD\_BUF\_DONE\_INT\_SET] The software set bit for \hyperref[int:SPISLVRDBUFDONEINT]{SPI\_SLV\_RD\_BUF\_DONE\_INT} interrupt. (WT)
\label{fielddesc:SPISLVWRBUFDONEINTSET}\item [SPI\_SLV\_WR\_BUF\_DONE\_INT\_SET] The software set bit for \hyperref[int:SPISLVWRBUFDONEINT]{SPI\_SLV\_WR\_BUF\_DONE\_INT} interrupt. (WT)
\label{fielddesc:SPITRANSDONEINTSET}\item [SPI\_TRANS\_DONE\_INT\_SET] The software set bit for \hyperref[int:SPITRANSDONEINT]{SPI\_TRANS\_DONE\_INT} interrupt. (WT)
\label{fielddesc:SPIDMASEGTRANSDONEINTSET}\item [SPI\_DMA\_SEG\_TRANS\_DONE\_INT\_SET] The software set bit for \hyperref[int:SPIDMASEGTRANSDONEINT]{SPI\_DMA\_SEG\_TRANS\_DONE\_INT} interrupt. (WT)
\label{fielddesc:SPISEGMAGICERRINTSET}\item [\textcolor{red}{SPI\_SEG\_MAGIC\_ERR\_INT\_SET (for SPI2 only)}] The software set bit for \hyperref[int:SPISEGMAGICERRINT]{SPI\_SEG\_MAGIC\_ERR\_INT} interrupt. (WT)
\label{fielddesc:SPISLVCMDERRINTSET}\item [SPI\_SLV\_CMD\_ERR\_INT\_SET] The software set bit for \hyperref[int:SPISLVCMDERRINT]{SPI\_SLV\_CMD\_ERR\_INT} interrupt. (WT)
\label{fielddesc:SPIMSTRXAFIFOWFULLERRINTSET}\item [SPI\_MST\_RX\_AFIFO\_WFULL\_ERR\_INT\_SET] The software set bit for \hyperref[int:SPIMSTRXAFIFOWFULLERRINT]{SPI\_MST\_RX\_AFIFO\_WFULL\_ERR\_INT} interrupt. (WT)
\label{fielddesc:SPIMSTTXAFIFOREMPTYERRINTSET}\item [SPI\_MST\_TX\_AFIFO\_REMPTY\_ERR\_INT\_SET] The software set bit for \hyperref[int:SPIMSTTXAFIFOREMPTYERRINT]{SPI\_MST\_TX\_AFIFO\_REMPTY\_ERR\_INT} interrupt. (WT)
\label{fielddesc:SPIAPP2INTSET}\item [SPI\_APP2\_INT\_SET] The software set bit for \hyperref[int:SPIAPP2INT]{SPI\_APP2\_INT} interrupt. (WT)
\label{fielddesc:SPIAPP1INTSET}\item [SPI\_APP1\_INT\_SET] The software set bit for \hyperref[int:SPIAPP1INT]{SPI\_APP1\_INT} interrupt. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W0\_REG}{0x{}0098}\label{regdesc:SPIW0REG}
\regfield{SPI\_BUF0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF0}\item [SPI\_BUF0] 32-bit data buffer 0. (R/W/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W1\_REG}{0x{}009C}\label{regdesc:SPIW1REG}
\regfield{SPI\_BUF1}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF1}\item [SPI\_BUF1] 32-bit data buffer 1. (R/W/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W2\_REG}{0x{}00A0}\label{regdesc:SPIW2REG}
\regfield{SPI\_BUF2}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF2}\item [SPI\_BUF2] 32-bit data buffer 2. (R/W/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W3\_REG}{0x{}00A4}\label{regdesc:SPIW3REG}
\regfield{SPI\_BUF3}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF3}\item [SPI\_BUF3] 32-bit data buffer 3. (R/W/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W4\_REG}{0x{}00A8}\label{regdesc:SPIW4REG}
\regfield{SPI\_BUF4}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF4}\item [SPI\_BUF4] 32-bit data buffer 4. (R/W/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W5\_REG}{0x{}00AC}\label{regdesc:SPIW5REG}
\regfield{SPI\_BUF5}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF5}\item [SPI\_BUF5] 32-bit data buffer 5. (R/W/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W6\_REG}{0x{}00B0}\label{regdesc:SPIW6REG}
\regfield{SPI\_BUF6}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF6}\item [SPI\_BUF6] 32-bit data buffer 6. (R/W/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W7\_REG}{0x{}00B4}\label{regdesc:SPIW7REG}
\regfield{SPI\_BUF7}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF7}\item [SPI\_BUF7] 32-bit data buffer 7. (R/W/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W8\_REG}{0x{}00B8}\label{regdesc:SPIW8REG}
\regfield{SPI\_BUF8}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF8}\item [SPI\_BUF8] 32-bit data buffer 8. (R/W/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W9\_REG}{0x{}00BC}\label{regdesc:SPIW9REG}
\regfield{SPI\_BUF9}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF9}\item [SPI\_BUF9] 32-bit data buffer 9. (R/W/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W10\_REG}{0x{}00C0}\label{regdesc:SPIW10REG}
\regfield{SPI\_BUF10}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF10}\item [SPI\_BUF10] 32-bit data buffer 10. (R/W/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W11\_REG}{0x{}00C4}\label{regdesc:SPIW11REG}
\regfield{SPI\_BUF11}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF11}\item [SPI\_BUF11] 32-bit data buffer 11. (R/W/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W12\_REG}{0x{}00C8}\label{regdesc:SPIW12REG}
\regfield{SPI\_BUF12}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF12}\item [SPI\_BUF12] 32-bit data buffer 12. (R/W/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W13\_REG}{0x{}00CC}\label{regdesc:SPIW13REG}
\regfield{SPI\_BUF13}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF13}\item [SPI\_BUF13] 32-bit data buffer 13. (R/W/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W14\_REG}{0x{}00D0}\label{regdesc:SPIW14REG}
\regfield{SPI\_BUF14}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF14}\item [SPI\_BUF14] 32-bit data buffer 14. (R/W/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W15\_REG}{0x{}00D4}\label{regdesc:SPIW15REG}
\regfield{SPI\_BUF15}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIBUF15}\item [SPI\_BUF15] 32-bit data buffer 15. (R/W/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DATE\_REG}{0x{}00F0}\label{regdesc:SPIDATEREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{SPI\_DATE}{28}{0}{{0x{}2101190}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SPIDATE}\item [SPI\_DATE] Version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}


