\subsubsection{External Memory}\label{para:external_Memory}

Accesses to the external flash and external SPI RAM are done through a cache and are also handled by an MMU. This Cache MMU can apply different mappings, depending on the PID of the process as well as the CPU the process is running on. The MMU does this in a way that is similar to the internal memory MMU, that is, for every page of virtual memory, it has a register detailing which physical page this virtual page should map to. There are differences between the MMUs governing the internal memory and the Cache MMU, though. First of all, the Cache MMU has a fixed page size (which is 64 KB for external flash and 32 KB for external RAM) and secondly, instead of specifying access rights in the MMU entries, the Cache MMU has explicit mapping tables for each PID and processor core. The MMU mapping configuration registers will be referred to as 'entries' in the rest of this chapter. These registers are only accessible from processes with a PID of 0 or 1; processes with a PID of 2 to 7 will have to delegate to one of the above-mentioned processes to change their MMU settings.

The MMU entries, as stated before, are used for mapping a virtual memory page access to a physical memory page access. The MMU controls five regions of virtual address space, detailed in Table \ref{table:Virtual_Address_for_External_Memory}. $VAddr_1$ to $VAddr_4$ are used for accessing external flash, whereas $VAddr_{\mathrm{RAM}}$ is used for accessing external RAM. Note that $VAddr_4$ is a subset of $VAddr_0$.

\begin{table}[H]
    \caption{Virtual Address for External Memory}
    \label{table:Virtual_Address_for_External_Memory}
     \begin{tabular}[h]{ |p{3cm}|p{2cm}|p{3.5cm}|p{3.5cm}|p{3cm}|}
        \hline
        \rowcolor{lightgray}
        & & \multicolumn{2}{c|}{Boundary address} & \\
        \cline{3-4}
        \rowcolor{lightgray}
        \multirow{-2}*{Name} & \multirow{-2}*{Size} & Low & High & \multirow{-2}*{Page quantity} \\
        \hline
        $\mathrm{VAddr}_{0}$ & 4 MB & 0x3F40\_0000 & 0x3F7F\_FFFF & 64 \\
        \hline
        $\mathrm{VAddr}_{1}$ & 4 MB & 0x4000\_0000 & 0x403F\_FFFF & 64* \\
        \hline
        $\mathrm{VAddr}_{2}$ & 4 MB & 0x4040\_0000 & 0x407F\_FFFF & 64 \\
        \hline
        $\mathrm{VAddr}_{3}$ & 4 MB & 0x4080\_0000 & 0x40BF\_FFFF & 64 \\
        \hline
        $\mathrm{VAddr}_{4}$ & 1 MB & 0x3F40\_0000 & 0x3F4F\_FFFF & 16 \\
        \hline
        $VAddr_{\mathrm{RAM}}$ & 4 MB & 0x3F80\_0000 & 0x3FBF\_FFFF & 128 \\
        \hline
    \end{tabular}\\
       \\
   {*} The configuration entries for address range 0x4000\_0000 \verb+~+ 0x403F\_FFFF are implemented and documented as if it were a full 4 MB address range, but it is not accessible as such. Instead, the address range 0x4000\_0000 \verb+~+ 0x400C\_1FFF accesses on-chip memory. This means that some of the configuration entries for $VAddr_1$ will not be used.
\end{table}



\subparagraph{External Flash}

For flash, the relationships among entry numbers, virtual memory ranges, and PIDs are detailed in Tables \ref{table:MMU_Entry_Numbers_PRO_CPU} and \ref{table:MMU_Entry_Numbers_APP_CPU}, which for every memory region and PID combination specify the first MMU entry governing the mapping. This number refers to the MMU entry governing the very first page; the entire region is described by the amount of pages specified in the 'count' column.

These two tables are essentially the same, with the sole difference being that the APP\_CPU entry numbers are 2048 higher than the corresponding PRO\_CPU numbers. Note that memory regions $VAddr_0$ and $VAddr_1$ are only accessible using PID 0 and 1, while $VAddr_1$ can only be accessed by PID 2 \verb+~+ 7.

\begin{table}[H]
    \centering
    \caption{MMU Entry Numbers for PRO\_CPU}
    \label{table:MMU_Entry_Numbers_PRO_CPU}
     \begin{tabular}[h]{|p{2.5cm}|p{1.5cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|}
        \hline
        \rowcolor{lightgray}
        & & \multicolumn{7}{c|}{First MMU entry for PID} \\
        \rowcolor{lightgray}
        \multirow{-2}*{VAddr} & \multirow{-2}*{Count} & 0/1 & 2 & 3 & 4 & 5 & 6 & 7 \\
        \hline
        $\mathrm{VAddr}_{0}$ & 64 & 0 & - & - & - & - & - & - \\
        \hline
        $\mathrm{VAddr}_{1}$ & 64 & 64 & - & - & - & - & - & - \\
        \hline
        $\mathrm{VAddr}_{2}$ & 64 & 128 & 256 & 384 & 512 & 640 & 768 & 896 \\
        \hline
        $\mathrm{VAddr}_{3}$ & 64 & 192 & 320 & 448 & 576 & 704 & 832 & 960 \\
        \hline
        $\mathrm{VAddr}_{4}$ & 16 & - & 1056 & 1072 & 1088 & 1104 & 1120 & 1136\\
        \hline
    \end{tabular}
\end{table}

\begin{table}[H]
    \centering
    \caption{MMU Entry Numbers for APP\_CPU}
    \label{table:MMU_Entry_Numbers_APP_CPU}
     \begin{tabular}[h]{|p{2.5cm}|p{1.5cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|}
        \hline
        \rowcolor{lightgray}
        & & \multicolumn{7}{c|}{First MMU entry for PID} \\
        \rowcolor{lightgray}
        \multirow{-2}*{VAddr} & \multirow{-2}*{Count} & 0/1 & 2 & 3 & 4 & 5 & 6 & 7 \\
        \hline
        $\mathrm{VAddr}_{0}$ & 64 & 2048 & - & - & - & - & - & - \\
        \hline
        $\mathrm{VAddr}_{1}$ & 64 & 2112 & - & - & - & - & - & - \\
        \hline
        $\mathrm{VAddr}_{2}$ & 64 & 2176 & 2304 & 2432 & 2560 & 2688 & 2816 & 2944 \\
        \hline
        $\mathrm{VAddr}_{3}$ & 64 & 2240 & 2368 & 2496 & 2624 & 2752 & 2880 & 3008 \\
        \hline
        $\mathrm{VAddr}_{4}$ & 16 & - & 3104 & 3120 & 3136 & 3152 & 3168 & 3184 \\
        \hline
    \end{tabular}
\end{table}


As these tables show, virtual address $\mathrm{VAddr}_{1}$ can only be used by processes with a PID of 0 or 1. There is a special mode to allow processes with a PID of 2 to 7 to read the External Flash via address $\mathrm{VAddr}_{1}$.
When the DPORT\_PRO\_SINGLE\_IRAM\_ENA bit of register DPORT\_PRO\_CACHE\_CTRL\_REG is 1, the MMU enters this special mode for PRO\_CPU memory accesses. Similarly, when the DPORT\_APP\_SINGLE\_IRAM\_ENA bit of register DPORT\_APP\_CACHE\_CTRL\_REG  is 1, the APP\_CPU accesses memory using this special mode. In this mode, the process and virtual address page supported by each configuration entry of MMU are different. For details please see Table \ref{table:MMU_Entry_Numbers_PRO_CPU_Special_Mode} and  \ref{table:MMU_Entry_Numbers_APP_CPU_Special_Mode}. As shown in these tables, in this special mode $\mathrm{VAddr}_{2}$ and $\mathrm{VAddr}_{3}$ cannot be used to access External Flash.

\begin{table}[H]
    \centering
    \caption{MMU Entry Numbers for PRO\_CPU (Special Mode)}
    \label{table:MMU_Entry_Numbers_PRO_CPU_Special_Mode}
       \begin{tabular}[h]{|p{2.5cm}|p{1.5cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|}
        \hline
        \rowcolor{lightgray}
        & & \multicolumn{7}{c|}{First MMU entry for PID} \\
        \rowcolor{lightgray}
        \multirow{-2}*{VAddr} & \multirow{-2}*{Count} & 0/1 & 2 & 3 & 4 & 5 & 6 & 7 \\
        \hline
        $\mathrm{VAddr}_{0}$ & 64 & 0 & - & - & - & - & - & -\\
        \hline
        $\mathrm{VAddr}_{1}$ & 64 & 64 & 256 & 384 & 512 & 640 & 768 & 896 \\
        \hline
        $\mathrm{VAddr}_{2}$ & 64 & - & - & - & - & - & - & -\\
        \hline
        $\mathrm{VAddr}_{3}$ & 64 & - & - & - & - & - & - & -\\
        \hline
        $\mathrm{VAddr}_{4}$ & 16 & - & 1056 & 1072 & 1088 & 1104 & 1120 & 1136\\
        \hline
    \end{tabular}
\end{table}

\begin{table}[H]
    \centering
    \caption{MMU Entry Numbers for APP\_CPU (Special Mode)}
    \label{table:MMU_Entry_Numbers_APP_CPU_Special_Mode}
     \begin{tabular}[h]{|p{2.5cm}|p{1.5cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|}
        \hline
        \rowcolor{lightgray}
        & & \multicolumn{7}{c|}{First MMU entry for PID} \\
        \rowcolor{lightgray}
        \multirow{-2}*{VAddr} & \multirow{-2}*{Count} & 0/1 & 2 & 3 & 4 & 5 & 6 & 7 \\
        \hline
        $\mathrm{VAddr}_{0}$ & 64 & 2048 & - & - & - & - & - & - \\
        \hline
        $\mathrm{VAddr}_{1}$ & 64 & 2112 & 2304 & 2432 & 2560 & 2688 & 2816 & 2944 \\
        \hline
        $\mathrm{VAddr}_{2}$ & 64 & - & - & - & - & - & - & - \\
        \hline
        $\mathrm{VAddr}_{3}$ & 64 & - & - & - & - & - & - & - \\
        \hline
        $\mathrm{VAddr}_{4}$ & 16 & - & 3104 & 3120 & 3136 & 3152 & 3168 & 3184 \\
        \hline
    \end{tabular}
\end{table}


Every configuration entry of MMU maps a virtual address page of a CPU process to a physical address page. An entry is 32 bits wide. Of these, bits 0\verb+~+7 indicate the physical page the virtual page is mapped to. Bit 8 should be cleared to indicate that the MMU entry is valid; entries with this bit set will not map any physical address to the virtual address. Bits 10 to 32 are unused and should be written as zero. Because there are eight address bits in an MMU entry, and the page size for external flash is 64 KB, a maximum of 256 × 64 KB = 16 MB of external flash is supported.

\subparagraph{Examples}


Example 1. A PRO\_CPU process, with a PID of 1, needs to read external flash address 0x07\_2375 via virtual address 0x3F70\_2375. The MMU is not in the special mode.
\begin{itemize}
\itemsep-0.5em
\item According to Table \ref{table:Virtual_Address_for_External_Memory}, virtual address 0x3F70\_2375 resides in the 0x30'th page of .$\mathrm{VAddr}_0$
\item According to Table \ref{table:MMU_Entry_Numbers_PRO_CPU}, the MMU entry for $\mathrm{VAddr}_0$ for PID 0/1 for the PRO\_CPU starts at 0.
\item The modified MMU entry is 0 + 0x30 = 0x30.
\item Address 0x07\_2375 resides in the 7'th 64 KB-sized page.
\item MMU entry 0x30 needs to be set to 7 and marked as valid by setting the 8'th bit to 0. Thus, 0x007 is written to MMU entry 0x30.
\end{itemize}


Example 2. An APP\_CPU process, with a PID of 4, needs to read external flash address 0x44\_048C via virtual address 0x4044\_048C. The MMU is not in special mode.
\begin{itemize}
\itemsep-0.5em
\item According to Table \ref{table:Virtual_Address_for_External_Memory}, virtual address 0x4044\_048C resides in the 0x4'th page of $\mathrm{VAddr}_{2}$.
\item According to Table \ref{table:MMU_Entry_Numbers_APP_CPU}, the MMU entry for $\mathrm{VAddr}_{2}$ for PID 4 for the APP\_CPU starts at 2560.
\item The modified MMU entry is 2560 + 0x4 = 2564.
\item Address 0x44\_048C resides in the 0x44'th 64 KB-sized page.
\item MMU entry 2564 needs to be set to 0x44 and marked as valid by setting the 8'th bit to 0. Thus, 0x044 is written to MMU entry 2564.
\end{itemize}

\subparagraph{External RAM}

Processes running on PRO\_CPU and APP\_CPU can read and write External SRAM via the Cache at virtual address range $VAddr_{\mathrm{RAM}}$, which is  0x3F80\_0000 \verb+~+ 0x3FBF\_FFFF. As with the flash MMU, the address space and the physical memory are divided into pages. For the External RAM MMU, the page size is 32 KB and the MMU is able to map 256 physical pages into the virtual address space, allowing for 32 KB × 256 = 8 MB of physical external RAM to be mapped.

The mapping of virtual pages into this memory range depends on the mode this MMU is in: Low-High mode, Even-Odd mode, or Normal mode. In all cases, the DPORT\_PRO\_DRAM\_HL bit and DPORT\_PRO\_DRAM\_SPLIT bit in register DPORT\_PRO\_CACHE\_CTRL\_REG, the DPORT\_APP\_DRAM\_HL bit and DPORT\_APP\_DRAM\_SPLIT bit in register DPORT\_APP\_CACHE\_CTRL\_REG determine the virtual address mode for External SRAM. For details, please see Table \ref{table:Virtual_Address_Mode_for_External_SRAM}. If a different mapping for the PRO\_CPU and APP\_CPU is required, the Normal Mode should be selected, as it is the only mode that can provide this. If it is allowable for the PRO\_CPU and the APP\_CPU to share the same mapping, using either High-Low or Even-Odd mode can give a speed gain when both CPUs access memory frequently.

In case the APP\_CPU cache is disabled, which renders the region of 0x4007\_8000 to 0x4007\_FFFF usable as normal internal RAM, the usability of the various cache modes changes. Normal mode will allow PRO\_CPU access to external RAM to keep functioning, but the APP\_CPU will be unable to access the external RAM. High-Low mode allows both CPUs to use external RAM, but only for the 2 MB virtual memory addresses from 0x3F80\_0000 to 0x3F9F\_FFFF. It is not advised to use Even-Odd mode with the APP\_CPU cache region disabled.


\begin{table}[H]
    \centering
    \caption{Virtual Address Mode for External SRAM}
    \label{table:Virtual_Address_Mode_for_External_SRAM}
    \begin{tabular}[h]{|p{4cm}|p{5.5cm}|p{5.5cm}|}
        \hline
        \rowcolor{lightgray}
        Mode &
        \makecell{DPORT\_PRO\_DRAM\_HL\\DPORT\_APP\_DRAM\_HL} &
        \makecell{DPORT\_PRO\_DRAM\_SPLIT\\DPORT\_APP\_DRAM\_SPLIT} \\
        \hline
        Low-High & 1 & 0 \\
        \hline
        Even-Odd & 0 & 1 \\
        \hline
        Normal & 0 & 0 \\
        \hline
    \end{tabular}
\end{table}

In normal mode, the virtual-to-physical page mapping can be different for both CPUs. Page mappings for PRO\_CPU are set using the MMU entries for $^{\mathrm{L}}\mathrm{VAddr}_{\mathrm{RAM}}$, and page mappings for the APP\_CPU can be configured using the MMU entries for $^{\mathrm{R}}\mathrm{VAddr}_{\mathrm{RAM}}$. In this mode, all 128 pages of both $^{\mathrm{L}}\mathrm{VAddr}$ and $^{\mathrm{R}}\mathrm{VAddr}$ are fully used, allowing a maximum of 8 MB of memory to be mapped; 4 MB into PRO\_CPU address space and a possibly different 4 MB into the APP\_CPU address space, as can be seen in Table \ref{table:Virtual_Address_for_External_SRAM_Normal_Mode}.


\begin{table}[H]
    \centering
    \caption{Virtual Address for External SRAM ( Normal Mode )}
    \label{table:Virtual_Address_for_External_SRAM_Normal_Mode}
     \begin{tabular}[h]{|p{3cm}|p{2cm}|p{5cm}|p{5cm}|}
        \hline
        \rowcolor{lightgray}
        & & \multicolumn{2}{c|}{PRO\_CPU address} \\
        \cline{3-4}
        \rowcolor{lightgray}
        \multirow{-2}*{Virtual address} & \multirow{-2}*{Size} & Low & High \\
        \hline
        $^{\mathrm{L}}\mathrm{VAddr}_{\mathrm{RAM}}$ &
        4 MB & 0x3F80\_0000 & 0x3FBF\_FFFF \\
        \hline
        \rowcolor{lightgray}
        & & \multicolumn{2}{c|}{APP\_CPU address} \\
        \cline{3-4}
        \rowcolor{lightgray}
        \multirow{-2}*{Virtual address} & \multirow{-2}*{Size} & Low & High \\
        \hline
        $^{\mathrm{R}}\mathrm{VAddr}_{\mathrm{RAM}}$ &
        4 MB & 0x3F80\_0000 & 0x3FBF\_FFFF \\
        \hline
    \end{tabular}
\end{table}


In Low-High mode, both the PRO\_CPU and the APP\_CPU use the same mapping entries. In this mode $^{\mathrm{L}}\mathrm{VAddr}_{\mathrm{RAM}}$ is used for the lower 2 MB of the virtual address space, while $^{\mathrm{R}}\mathrm{VAddr}_{\mathrm{RAM}}$ is used for the upper 2 MB. This also means that the upper 64 MMU entries for $^{\mathrm{L}}\mathrm{VAddr}_{\mathrm{RAM}}$, as well as the lower 64 entries for $^{\mathrm{R}}\mathrm{VAddr}_{\mathrm{RAM}}$, are unused. Table \ref{table:Virtual_Address_for_External_SRAM_Low_High_Mode} details these address ranges.


\begin{table}[H]
    \centering
    \caption{Virtual Address for External SRAM ( Low-High Mode )}
    \label{table:Virtual_Address_for_External_SRAM_Low_High_Mode}
       \begin{tabular}[h]{|p{3cm}|p{2cm}|p{5cm}|p{5cm}|}
        \hline
        \rowcolor{lightgray}
        & & \multicolumn{2}{c|}{PRO\_CPU/APP\_CPU address} \\
        \cline{3-4}
        \rowcolor{lightgray}
        \multirow{-2}*{Virtual address} & \multirow{-2}*{Size} & Low & High \\
        \hline
        $^{\mathrm{L}}\mathrm{VAddr}_{\mathrm{RAM}}$ &
        2 MB & 0x3F80\_0000 & 0x3F9F\_FFFF \\
        \hline
        $^{\mathrm{R}}\mathrm{VAddr}_{\mathrm{RAM}}$ &
        2 MB & 0x3FA0\_0000 & 0x3FBF\_FFFF \\
        \hline
    \end{tabular}
\end{table}



In Even-Odd memory, the VRAM is split into 32-byte chunks. The even chunks are resolved through the MMU entries for $^{\mathrm{L}}\mathrm{VAddr}_{\mathrm{RAM}}$, the odd chunks through the entries for $^{\mathrm{R}}\mathrm{VAddr}_{\mathrm{RAM}}$. Generally, the MMU entries for $^{\mathrm{L}}\mathrm{VAddr}_{\mathrm{RAM}}$ and $^{\mathrm{R}}\mathrm{VAddr}_{\mathrm{RAM}}$ are set to the same values, so that the virtual pages map to a contiguous region of physical memory. Table \ref{table:Virtual_Address_for_External_SRAM_Even_Odd_Mode} details this mode.


\begin{table}[H]
    \centering
    \caption{Virtual Address for External SRAM (Even–Odd Mode)}
    \label{table:Virtual_Address_for_External_SRAM_Even_Odd_Mode}
     \begin{tabular}[h]{|p{3cm}|p{2cm}|p{5cm}|p{5cm}|}
        \hline
        \rowcolor{lightgray}
        & & \multicolumn{2}{c|}{PRO\_CPU/APP\_CPU address} \\
        \cline{3-4}
        \rowcolor{lightgray}
        \multirow{-2}*{Virtual address} & \multirow{-2}*{Size} & Low & High \\
        \hline
        $^{\mathrm{L}}\mathrm{VAddr}_{\mathrm{RAM}}$ &
        32 Bytes & 0x3F80\_0000 & 0x3F80\_001F \\
        \hline
        $^{\mathrm{R}}\mathrm{VAddr}_{\mathrm{RAM}}$ &
        32 Bytes & 0x3F80\_0020 & 0x3F80\_003F \\
        \hline
        $^{\mathrm{L}}\mathrm{VAddr}_{\mathrm{RAM}}$ &
        32 Bytes & 0x3F80\_0040 & 0x3F80\_005F \\
        \hline
        $^{\mathrm{R}}\mathrm{VAddr}_{\mathrm{RAM}}$ &
        32 Bytes & 0x3F80\_0060 & 0x3F80\_007F \\
        \hline
        \multicolumn{4}{|c|}{...} \\
        \hline
        $^{\mathrm{L}}\mathrm{VAddr}_{\mathrm{RAM}}$ &
        32 Bytes & 0x3FBF\_FFC0 & 0x3FBF\_FFDF \\
        \hline
        $^{\mathrm{R}}\mathrm{VAddr}_{\mathrm{RAM}}$ &
        32 Bytes & 0x3FBF\_FFE0 & 0x3FBF\_FFFF \\
        \hline
    \end{tabular}
\end{table}



The bit configuration of the External RAM MMU entries is the same as for the flash memory: the entries are 32-bit registers, with the lower nine bits being used. Bits 0\verb+~+7 contain the physical page the entry should map its associate virtual page address to, while bit 8 is cleared when the entry is valid and set when it is not. Table \ref{table:MMU_Entry_Numbers_RAM} details the first MMU entry number for $^{\mathrm{L}}\mathrm{VAddr}_{\mathrm{RAM}}$ and $^{\mathrm{R}}\mathrm{VAddr}_{\mathrm{RAM}}$ for all PIDs.

\begin{table}[H]
    \centering
    \caption{MMU Entry Numbers for External RAM}
    \label{table:MMU_Entry_Numbers_RAM}
     \begin{tabular}[h]{|p{2.5cm}|p{1.5cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|p{1.25cm}|}
        \hline
        \rowcolor{lightgray}
        & & \multicolumn{7}{c|}{First MMU entry for PID} \\
        \rowcolor{lightgray}
        \multirow{-2}*{VAddr} & \multirow{-2}*{Count} & 0/1 & 2 & 3 & 4 & 5 & 6 & 7 \\
        \hline
        $^{\mathrm{L}}\mathrm{VAddr}_{\mathrm{RAM}}$ & 128 & 1152 & 1280 & 1408 & 1536 & 1664 & 1792 & 1920 \\
        \hline
        $^{\mathrm{R}}\mathrm{VAddr}_{\mathrm{RAM}}$ & 128 & 3200 & 3328 & 3456 & 3584 & 3712 & 3840 & 3968 \\
        \hline
    \end{tabular}
\end{table}


\subparagraph{Examples}


Example 1. A PRO\_CPU process, with a PID of 7, needs to read or write external RAM address 0x7F\_A375 via virtual address 0x3FA7\_2375. The MMU is in Low-High mode.
\begin{itemize}
\itemsep-0.5em
\item According to Table \ref{table:Virtual_Address_for_External_Memory}, virtual address 0x3FA7\_2375 resides in the 0x4E'th 32-KB-page of $\mathrm{VAddr}_{\mathrm{RAM}}$.
\item According to Table \ref{table:Virtual_Address_for_External_SRAM_Low_High_Mode}, virtual address 0x3FA7\_2375 is governed by  $^{\mathrm{R}}\mathrm{VAddr}_{\mathrm{RAM}}$.
\item According to Table \ref{table:MMU_Entry_Numbers_RAM}, the MMU entry for $^{\mathrm{R}}\mathrm{VAddr}_{\mathrm{RAM}}$ for PID 7 for the PRO\_CPU starts at 3968.
\item The modified MMU entry is 3968 + 0x4E = 4046. 
\item Address 0x7F\_A375 resides in the 255'th 32 KB-sized page.
\item MMU entry 4046 needs to be set to 255 and marked as valid by clearing the 8'th bit. Thus, 0x0FF is written to MMU entry 4046.
\end{itemize}

Example 2. An APP\_CPU process, with a PID of 5, needs to read or write external RAM address 0x55\_5805 up to 0x55\_5823 starting at virtual address 0x3F85\_5805. The MMU is in Even-Odd mode.
\begin{itemize}
\itemsep-0.5em
\item According to Table \ref{table:Virtual_Address_for_External_Memory}, virtual address 0x3F85\_5805 resides in the 0x0A'th 32-KB-page of $\mathrm{VAddr}_{\mathrm{RAM}}$.
\item According to Table \ref{table:Virtual_Address_for_External_SRAM_Even_Odd_Mode}, the range to be read/written spans both a 32-byte region in $^{\mathrm{R}}\mathrm{VAddr}_{\mathrm{RAM}}$ and $^{\mathrm{L}}\mathrm{VAddr}_{\mathrm{RAM}}$.
\item According to Table \ref{table:MMU_Entry_Numbers_RAM}, the MMU entry for $^{\mathrm{L}}\mathrm{VAddr}_{\mathrm{RAM}}$ for PID 5 starts at 1664.
\item According to Table \ref{table:MMU_Entry_Numbers_RAM}, the MMU entry for $^{\mathrm{R}}\mathrm{VAddr}_{\mathrm{RAM}}$ for PID 5 starts at 3712.
\item The modified MMU entries are 1664 + 0x0A = 1674 and 3712 + 0x0A = 3722. 
\item The addresses 0x55\_5805 to 0x55\_5823 reside in the 0xAA'th 32 KB-sized page.
\item MMU entries 1674 and 3722 need to be set to 0xAA and marked as valid by setting the 8'th bit to 0. Thus, 0x0AA is written to MMU entries 1674 and 3722. This mapping applies to both the PRO\_CPU and the APP\_CPU.
\end{itemize}

Example 3. A PRO\_CPU process, with a PID of 1, and an APP\_CPU process whose PID is also 1, need to read or write external RAM using virtual address 0x3F80\_0876. The PRO\_CPU needs this region to access physical address 0x10\_0876, while the APP\_CPU wants to access physical address 0x20\_0876 through this virtual address. The MMU is in Normal mode.
\begin{itemize}
\itemsep-0.5em
\item According to Table \ref{table:Virtual_Address_for_External_Memory}, virtual address 0x3F80\_0876 resides in the 0'th 32-KB-page of $\mathrm{VAddr}_{\mathrm{RAM}}$.
\item According to Table \ref{table:MMU_Entry_Numbers_RAM}, the MMU entry for PID 1 for the PRO\_CPU starts at 1152.
\item According to Table \ref{table:MMU_Entry_Numbers_RAM}, the MMU entry for PID 1 for the APP\_CPU starts at 3200.
\item The MMU entries that are modified are 1152 + 0 = 1152 for the PRO\_CPU and 3200 + 0 = 3200 for the APP\_CPU.
\item Address 0x10\_0876 resides in the 0x20'th 32 KB-sized page.
\item Address 0x20\_0876 resides in the 0x40'th 32 KB-sized page.
\item For the PRO\_CPU, MMU entry 1152 needs to be set to 0x20 and marked as valid by clearing the 8'th bit. Thus, 0x020 is written to MMU entry 1152.
\item For the APP\_CPU, MMU entry 3200 needs to be set to 0x40 and marked as valid by clearing the 8'th bit. Thus, 0x040 is written to MMU entry 3200.
\item Now, the PRO\_CPU and the APP\_CPU can access different physical memory regions through the same virtual address.
\end{itemize}