\begin{register}{H}{UHCI\_CONF0\_REG}{0x0}\label{regdesc:UHCICONF0REG}
\regfield{(reserved)}{10}{22}{0000000000}%
\regfield{UHCI\_ENCODE\_CRC\_EN}{1}{21}{1}%
\regfield{UHCI\_LEN\_EOF\_EN}{1}{20}{1}%
\regfield{UHCI\_UART\_IDLE\_EOF\_EN}{1}{19}{0}%
\regfield{UHCI\_CRC\_REC\_EN}{1}{18}{1}%
\regfield{UHCI\_HEAD\_EN}{1}{17}{1}%
\regfield{UHCI\_SEPER\_EN}{1}{16}{1}%
\regfield{(reserved)}{4}{12}{0000}%
\regfield{UHCI\_UART2\_CE}{1}{11}{0}%
\regfield{UHCI\_UART1\_CE}{1}{10}{0}%
\regfield{UHCI\_UART0\_CE}{1}{9}{0}%
\regfield{(reserved)}{9}{0}{000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_ENCODE\_CRC\_EN]Reserved. Please initialize it to 0. (R/W)
\item [UHCI\_LEN\_EOF\_EN]Reserved. Please initialize it to 0. (R/W)
\item [UHCI\_UART\_IDLE\_EOF\_EN]Reserved. Please initialize it to 0. (R/W)
\item [UHCI\_CRC\_REC\_EN]Reserved. Please initialize it to 0. (R/W)
\item [UHCI\_HEAD\_EN]Reserved. Please initialize it to 0. (R/W)
\item [UHCI\_SEPER\_EN]Set this bit to use a special char and separate the data frame. (R/W)
\item [UHCI\_UART2\_CE]Set this bit to use UART2 and transmit or receive data. (R/W)
\item [UHCI\_UART1\_CE]Set this bit to use UART1 and transmit or receive data. (R/W)
\item [UHCI\_UART0\_CE]Set this bit to use UART and transmit or receive data. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_INT\_RAW\_REG}{0x4}\label{regdesc:UHCIINTRAWREG}
\regfield{(reserved)}{18}{14}{000000000000000000}%
\regfield{UHCI\_OUT\_TOTAL\_EOF\_INT\_RAW}{1}{13}{0}%
\regfield{UHCI\_OUTLINK\_EOF\_ERR\_INT\_RAW}{1}{12}{0}%
\regfield{UHCI\_IN\_DSCR\_EMPTY\_INT\_RAW}{1}{11}{0}%
\regfield{UHCI\_OUT\_DSCR\_ERR\_INT\_RAW}{1}{10}{0}%
\regfield{UHCI\_IN\_DSCR\_ERR\_INT\_RAW}{1}{9}{0}%
\regfield{UHCI\_OUT\_EOF\_INT\_RAW}{1}{8}{0}%
\regfield{UHCI\_OUT\_DONE\_INT\_RAW}{1}{7}{0}%
\regfield{UHCI\_IN\_ERR\_EOF\_INT\_RAW}{1}{6}{0}%
\regfield{UHCI\_IN\_SUC\_EOF\_INT\_RAW}{1}{5}{0}%
\regfield{UHCI\_IN\_DONE\_INT\_RAW}{1}{4}{0}%
\regfield{UHCI\_TX\_HUNG\_INT\_RAW}{1}{3}{0}%
\regfield{UHCI\_RX\_HUNG\_INT\_RAW}{1}{2}{0}%
\regfield{UHCI\_TX\_START\_INT\_RAW}{1}{1}{0}%
\regfield{UHCI\_RX\_START\_INT\_RAW}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_OUT\_TOTAL\_EOF\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:UHCIOUTTOTALEOFINT]{UHCI\_OUT\_TOTAL\_EOF\_INT} interrupt. (RO)
\item [UHCI\_OUTLINK\_EOF\_ERR\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:UHCIOUTLINKEOFERRINT]{UHCI\_OUTLINK\_EOF\_ERR\_INT} interrupt. (RO)
\item [UHCI\_IN\_DSCR\_EMPTY\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:UHCIINDSCREMPTYINT]{UHCI\_IN\_DSCR\_EMPTY\_INT} interrupt. (RO)
\item [UHCI\_OUT\_DSCR\_ERR\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:UHCIOUTDSCRERRINT]{UHCI\_OUT\_DSCR\_ERR\_INT} interrupt. (RO)
\item [UHCI\_IN\_DSCR\_ERR\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:UHCIINDSCRERRINT]{UHCI\_IN\_DSCR\_ERR\_INT} interrupt. (RO)
\item [UHCI\_OUT\_EOF\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:UHCIOUTEOFINT]{UHCI\_OUT\_EOF\_INT} interrupt. (RO)
\item [UHCI\_OUT\_DONE\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:UHCIOUTDONEINT]{UHCI\_OUT\_DONE\_INT} interrupt. (RO)
\item [UHCI\_IN\_ERR\_EOF\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:UHCIINERREOFINT]{UHCI\_IN\_ERR\_EOF\_INT} interrupt. (RO)
\item [UHCI\_IN\_SUC\_EOF\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:UHCIINSUCEOFINT]{UHCI\_IN\_SUC\_EOF\_INT} interrupt. (RO)
\item [UHCI\_IN\_DONE\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:UHCIINDONEINT]{UHCI\_IN\_DONE\_INT} interrupt. (RO)
\item [UHCI\_TX\_HUNG\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:UHCITXHUNGINT]{UHCI\_TX\_HUNG\_INT} interrupt. (RO)
\item [UHCI\_RX\_HUNG\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:UHCIRXHUNGINT]{UHCI\_RX\_HUNG\_INT} interrupt. (RO)
\item [UHCI\_TX\_START\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:UHCITXSTARTINT]{UHCI\_TX\_START\_INT} interrupt. (RO)
\item [UHCI\_RX\_START\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:UHCIRXSTARTINT]{UHCI\_RX\_START\_INT} interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_INT\_ST\_REG}{0x8}\label{regdesc:UHCIINTSTREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{UHCI\_DMA\_INFIFO\_FULL\_WM\_INT\_ST}{1}{16}{0}%
\regfield{UHCI\_SEND\_A\_REG\_Q\_INT\_ST}{1}{15}{0}%
\regfield{UHCI\_SEND\_S\_REG\_Q\_INT\_ST}{1}{14}{0}%
\regfield{UHCI\_OUT\_TOTAL\_EOF\_INT\_ST}{1}{13}{0}%
\regfield{UHCI\_OUTLINK\_EOF\_ERR\_INT\_ST}{1}{12}{0}%
\regfield{UHCI\_IN\_DSCR\_EMPTY\_INT\_ST}{1}{11}{0}%
\regfield{UHCI\_OUT\_DSCR\_ERR\_INT\_ST}{1}{10}{0}%
\regfield{UHCI\_IN\_DSCR\_ERR\_INT\_ST}{1}{9}{0}%
\regfield{UHCI\_OUT\_EOF\_INT\_ST}{1}{8}{0}%
\regfield{UHCI\_OUT\_DONE\_INT\_ST}{1}{7}{0}%
\regfield{UHCI\_IN\_ERR\_EOF\_INT\_ST}{1}{6}{0}%
\regfield{UHCI\_IN\_SUC\_EOF\_INT\_ST}{1}{5}{0}%
\regfield{UHCI\_IN\_DONE\_INT\_ST}{1}{4}{0}%
\regfield{UHCI\_TX\_HUNG\_INT\_ST}{1}{3}{0}%
\regfield{UHCI\_RX\_HUNG\_INT\_ST}{1}{2}{0}%
\regfield{UHCI\_TX\_START\_INT\_ST}{1}{1}{0}%
\regfield{UHCI\_RX\_START\_INT\_ST}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}

\item [UHCI\_SEND\_A\_REG\_Q\_INT\_ST]The masked interrupt status bit for the \hyperref[int:UHCISENDAREGQINT]{UHCI\_SEND\_A\_REG\_Q\_INT} interrupt. (RO)
\item [UHCI\_SEND\_S\_REG\_Q\_INT\_ST]The masked interrupt status bit for the \hyperref[int:UHCISENDSREGQINT]{UHCI\_SEND\_S\_REG\_Q\_INT} interrupt. (RO)
\item [UHCI\_OUT\_TOTAL\_EOF\_INT\_ST]The masked interrupt status bit for the \hyperref[int:UHCIOUTTOTALEOFINT]{UHCI\_OUT\_TOTAL\_EOF\_INT} interrupt. (RO)
\item [UHCI\_OUTLINK\_EOF\_ERR\_INT\_ST]The masked interrupt status bit for the \hyperref[int:UHCIOUTLINKEOFERRINT]{UHCI\_OUTLINK\_EOF\_ERR\_INT} interrupt. (RO)
\item [UHCI\_IN\_DSCR\_EMPTY\_INT\_ST]The masked interrupt status bit for the \hyperref[int:UHCIINDSCREMPTYINT]{UHCI\_IN\_DSCR\_EMPTY\_INT} interrupt. (RO)
\item [UHCI\_OUT\_DSCR\_ERR\_INT\_ST]The masked interrupt status bit for the \hyperref[int:UHCIOUTDSCRERRINT]{UHCI\_OUT\_DSCR\_ERR\_INT} interrupt. (RO)
\item [UHCI\_IN\_DSCR\_ERR\_INT\_ST]The masked interrupt status bit for the \hyperref[int:UHCIINDSCRERRINT]{UHCI\_IN\_DSCR\_ERR\_INT} interrupt. (RO)
\item [UHCI\_OUT\_EOF\_INT\_ST]The masked interrupt status bit for the \hyperref[int:UHCIOUTEOFINT]{UHCI\_OUT\_EOF\_INT} interrupt. (RO)
\item [UHCI\_OUT\_DONE\_INT\_ST]The masked interrupt status bit for the \hyperref[int:UHCIOUTDONEINT]{UHCI\_OUT\_DONE\_INT} interrupt. (RO)
\item [UHCI\_IN\_ERR\_EOF\_INT\_ST]The masked interrupt status bit for the \hyperref[int:UHCIINERREOFINT]{UHCI\_IN\_ERR\_EOF\_INT} interrupt. (RO)
\item [UHCI\_IN\_SUC\_EOF\_INT\_ST]The masked interrupt status bit for the \hyperref[int:UHCIINSUCEOFINT]{UHCI\_IN\_SUC\_EOF\_INT} interrupt. (RO)
\item [UHCI\_IN\_DONE\_INT\_ST]The masked interrupt status bit for the \hyperref[int:UHCIINDONEINT]{UHCI\_IN\_DONE\_INT} interrupt. (RO)
\item [UHCI\_TX\_HUNG\_INT\_ST]The masked interrupt status bit for the \hyperref[int:UHCITXHUNGINT]{UHCI\_TX\_HUNG\_INT} interrupt. (RO)
\item [UHCI\_RX\_HUNG\_INT\_ST]The masked interrupt status bit for the \hyperref[int:UHCIRXHUNGINT]{UHCI\_RX\_HUNG\_INT} interrupt. (RO)
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{UHCI\_INT\_ST\_REG}{0x8}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\item [UHCI\_TX\_START\_INT\_ST]The masked interrupt status bit for the \hyperref[int:UHCITXSTARTINT]{UHCI\_TX\_START\_INT} interrupt. (RO)
\item [UHCI\_RX\_START\_INT\_ST]The masked interrupt status bit for the \hyperref[int:UHCIRXSTARTINT]{UHCI\_RX\_START\_INT} interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{UHCI\_INT\_ENA\_REG}{0xC}\label{regdesc:UHCIINTENAREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{UHCI\_DMA\_INFIFO\_FULL\_WM\_INT\_ENA}{1}{16}{0}%
\regfield{UHCI\_SEND\_A\_REG\_Q\_INT\_ENA}{1}{15}{0}%
\regfield{UHCI\_SEND\_S\_REG\_Q\_INT\_ENA}{1}{14}{0}%
\regfield{UHCI\_OUT\_TOTAL\_EOF\_INT\_ENA}{1}{13}{0}%
\regfield{UHCI\_OUTLINK\_EOF\_ERR\_INT\_ENA}{1}{12}{0}%
\regfield{UHCI\_IN\_DSCR\_EMPTY\_INT\_ENA}{1}{11}{0}%
\regfield{UHCI\_OUT\_DSCR\_ERR\_INT\_ENA}{1}{10}{0}%
\regfield{UHCI\_IN\_DSCR\_ERR\_INT\_ENA}{1}{9}{0}%
\regfield{UHCI\_OUT\_EOF\_INT\_ENA}{1}{8}{0}%
\regfield{UHCI\_OUT\_DONE\_INT\_ENA}{1}{7}{0}%
\regfield{UHCI\_IN\_ERR\_EOF\_INT\_ENA}{1}{6}{0}%
\regfield{UHCI\_IN\_SUC\_EOF\_INT\_ENA}{1}{5}{0}%
\regfield{UHCI\_IN\_DONE\_INT\_ENA}{1}{4}{0}%
\regfield{UHCI\_TX\_HUNG\_INT\_ENA}{1}{3}{0}%
\regfield{UHCI\_RX\_HUNG\_INT\_ENA}{1}{2}{0}%
\regfield{UHCI\_TX\_START\_INT\_ENA}{1}{1}{0}%
\regfield{UHCI\_RX\_START\_INT\_ENA}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}

\item [UHCI\_SEND\_A\_REG\_Q\_INT\_ENA]The interrupt enable bit for the \hyperref[int:UHCISENDAREGQINT]{UHCI\_SEND\_A\_REG\_Q\_INT} interrupt. (R/W)
\item [UHCI\_SEND\_S\_REG\_Q\_INT\_ENA]The interrupt enable bit for the \hyperref[int:UHCISENDSREGQINT]{UHCI\_SEND\_S\_REG\_Q\_INT} interrupt. (R/W)
\item [UHCI\_OUT\_TOTAL\_EOF\_INT\_ENA]The interrupt enable bit for the \hyperref[int:UHCIOUTTOTALEOFINT]{UHCI\_OUT\_TOTAL\_EOF\_INT} interrupt. (R/W)
\item [UHCI\_OUTLINK\_EOF\_ERR\_INT\_ENA]The interrupt enable bit for the \hyperref[int:UHCIOUTLINKEOFERRINT]{UHCI\_OUTLINK\_EOF\_ERR\_INT} interrupt. (R/W)
\item [UHCI\_IN\_DSCR\_EMPTY\_INT\_ENA]The interrupt enable bit for the \hyperref[int:UHCIINDSCREMPTYINT]{UHCI\_IN\_DSCR\_EMPTY\_INT} interrupt. (R/W)
\item [UHCI\_OUT\_DSCR\_ERR\_INT\_ENA]The interrupt enable bit for the \hyperref[int:UHCIOUTDSCRERRINT]{UHCI\_OUT\_DSCR\_ERR\_INT} interrupt. (R/W)
\item [UHCI\_IN\_DSCR\_ERR\_INT\_ENA]The interrupt enable bit for the \hyperref[int:UHCIINDSCRERRINT]{UHCI\_IN\_DSCR\_ERR\_INT} interrupt. (R/W)
\item [UHCI\_OUT\_EOF\_INT\_ENA]The interrupt enable bit for the \hyperref[int:UHCIOUTEOFINT]{UHCI\_OUT\_EOF\_INT} interrupt. (R/W)
\item [UHCI\_OUT\_DONE\_INT\_ENA]The interrupt enable bit for the \hyperref[int:UHCIOUTDONEINT]{UHCI\_OUT\_DONE\_INT} interrupt. (R/W)
\item [UHCI\_IN\_ERR\_EOF\_INT\_ENA]The interrupt enable bit for the \hyperref[int:UHCIINERREOFINT]{UHCI\_IN\_ERR\_EOF\_INT} interrupt. (R/W)
\item [UHCI\_IN\_SUC\_EOF\_INT\_ENA]The interrupt enable bit for the \hyperref[int:UHCIINSUCEOFINT]{UHCI\_IN\_SUC\_EOF\_INT} interrupt. (R/W)
\item [UHCI\_IN\_DONE\_INT\_ENA]The interrupt enable bit for the \hyperref[int:UHCIINDONEINT]{UHCI\_IN\_DONE\_INT} interrupt. (R/W)
\item [UHCI\_TX\_HUNG\_INT\_ENA]The interrupt enable bit for the \hyperref[int:UHCITXHUNGINT]{UHCI\_TX\_HUNG\_INT} interrupt. (R/W)
\item [UHCI\_RX\_HUNG\_INT\_ENA]The interrupt enable bit for the \hyperref[int:UHCIRXHUNGINT]{UHCI\_RX\_HUNG\_INT} interrupt. (R/W)
\item [UHCI\_TX\_START\_INT\_ENA]The interrupt enable bit for the \hyperref[int:UHCITXSTARTINT]{UHCI\_TX\_START\_INT} interrupt. (R/W)
\item [UHCI\_RX\_START\_INT\_ENA]The interrupt enable bit for the \hyperref[int:UHCIRXSTARTINT]{UHCI\_RX\_START\_INT} interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{UHCI\_INT\_CLR\_REG}{0x10}\label{regdesc:UHCIINTCLRREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{UHCI\_DMA\_INFIFO\_FULL\_WM\_INT\_CLR}{1}{16}{0}%
\regfield{UHCI\_SEND\_A\_REG\_Q\_INT\_CLR}{1}{15}{0}%
\regfield{UHCI\_SEND\_S\_REG\_Q\_INT\_CLR}{1}{14}{0}%
\regfield{UHCI\_OUT\_TOTAL\_EOF\_INT\_CLR}{1}{13}{0}%
\regfield{UHCI\_OUTLINK\_EOF\_ERR\_INT\_CLR}{1}{12}{0}%
\regfield{UHCI\_IN\_DSCR\_EMPTY\_INT\_CLR}{1}{11}{0}%
\regfield{UHCI\_OUT\_DSCR\_ERR\_INT\_CLR}{1}{10}{0}%
\regfield{UHCI\_IN\_DSCR\_ERR\_INT\_CLR}{1}{9}{0}%
\regfield{UHCI\_OUT\_EOF\_INT\_CLR}{1}{8}{0}%
\regfield{UHCI\_OUT\_DONE\_INT\_CLR}{1}{7}{0}%
\regfield{UHCI\_IN\_ERR\_EOF\_INT\_CLR}{1}{6}{0}%
\regfield{UHCI\_IN\_SUC\_EOF\_INT\_CLR}{1}{5}{0}%
\regfield{UHCI\_IN\_DONE\_INT\_CLR}{1}{4}{0}%
\regfield{UHCI\_TX\_HUNG\_INT\_CLR}{1}{3}{0}%
\regfield{UHCI\_RX\_HUNG\_INT\_CLR}{1}{2}{0}%
\regfield{UHCI\_TX\_START\_INT\_CLR}{1}{1}{0}%
\regfield{UHCI\_RX\_START\_INT\_CLR}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}

\item [UHCI\_SEND\_A\_REG\_Q\_INT\_CLR]Set this bit to clear the \hyperref[int:UHCISENDAREGQINT]{UHCI\_SEND\_A\_REG\_Q\_INT} interrupt. (WO)
\item [UHCI\_SEND\_S\_REG\_Q\_INT\_CLR]Set this bit to clear the \hyperref[int:UHCISENDSREGQINT]{UHCI\_SEND\_S\_REG\_Q\_INT} interrupt. (WO)
\item [UHCI\_OUT\_TOTAL\_EOF\_INT\_CLR]Set this bit to clear the \hyperref[int:UHCIOUTTOTALEOFINT]{UHCI\_OUT\_TOTAL\_EOF\_INT} interrupt. (WO)
\item [UHCI\_OUTLINK\_EOF\_ERR\_INT\_CLR]Set this bit to clear the \hyperref[int:UHCIOUTLINKEOFERRINT]{UHCI\_OUTLINK\_EOF\_ERR\_INT} interrupt. (WO)
\item [UHCI\_IN\_DSCR\_EMPTY\_INT\_CLR]Set this bit to clear the \hyperref[int:UHCIINDSCREMPTYINT]{UHCI\_IN\_DSCR\_EMPTY\_INT} interrupt. (WO)
\item [UHCI\_OUT\_DSCR\_ERR\_INT\_CLR]Set this bit to clear the \hyperref[int:UHCIOUTDSCRERRINT]{UHCI\_OUT\_DSCR\_ERR\_INT} interrupt. (WO)
\item [UHCI\_IN\_DSCR\_ERR\_INT\_CLR]Set this bit to clear the \hyperref[int:UHCIINDSCRERRINT]{UHCI\_IN\_DSCR\_ERR\_INT} interrupt. (WO)
\item [UHCI\_OUT\_EOF\_INT\_CLR]Set this bit to clear the \hyperref[int:UHCIOUTEOFINT]{UHCI\_OUT\_EOF\_INT} interrupt. (WO)
\item [UHCI\_OUT\_DONE\_INT\_CLR]Set this bit to clear the \hyperref[int:UHCIOUTDONEINT]{UHCI\_OUT\_DONE\_INT} interrupt. (WO)
\item [UHCI\_IN\_ERR\_EOF\_INT\_CLR]Set this bit to clear the \hyperref[int:UHCIINERREOFINT]{UHCI\_IN\_ERR\_EOF\_INT} interrupt. (WO)
\item [UHCI\_IN\_SUC\_EOF\_INT\_CLR]Set this bit to clear the \hyperref[int:UHCIINSUCEOFINT]{UHCI\_IN\_SUC\_EOF\_INT} interrupt. (WO)
\item [UHCI\_IN\_DONE\_INT\_CLR]Set this bit to clear the \hyperref[int:UHCIINDONEINT]{UHCI\_IN\_DONE\_INT} interrupt. (WO)
\item [UHCI\_TX\_HUNG\_INT\_CLR]Set this bit to clear the \hyperref[int:UHCITXHUNGINT]{UHCI\_TX\_HUNG\_INT} interrupt. (WO)
\item [UHCI\_RX\_HUNG\_INT\_CLR]Set this bit to clear the \hyperref[int:UHCIRXHUNGINT]{UHCI\_RX\_HUNG\_INT} interrupt. (WO)
\item [UHCI\_TX\_START\_INT\_CLR]Set this bit to clear the \hyperref[int:UHCITXSTARTINT]{UHCI\_TX\_START\_INT} interrupt. (WO)
\item [UHCI\_RX\_START\_INT\_CLR]Set this bit to clear the \hyperref[int:UHCIRXSTARTINT]{UHCI\_RX\_START\_INT} interrupt. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_DMA\_OUT\_STATUS\_REG}{0x14}\label{regdesc:UHCIDMAOUTSTATUSREG}
\regfield{(reserved)}{30}{2}{000000000000000000000000000000}%
\regfield{UHCI\_OUT\_EMPTY}{1}{1}{1}%
\regfield{UHCI\_OUT\_FULL}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_OUT\_EMPTY]1: DMA inlink descriptor's FIFO is empty. (RO)
\item [UHCI\_OUT\_FULL]1: DMA outlink descriptor's FIFO is full. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_DMA\_OUT\_PUSH\_REG}{0x18}\label{regdesc:UHCIDMAOUTPUSHREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{UHCI\_OUTFIFO\_PUSH}{1}{16}{0}%
\regfield{(reserved)}{7}{9}{0000000}%
\regfield{UHCI\_OUTFIFO\_WDATA}{9}{0}{{0x000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_OUTFIFO\_PUSH]Set this bit to push data into DMA FIFO. (R/W)
\item [UHCI\_OUTFIFO\_WDATA]This is the data that need to be pushed into DMA FIFO. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_DMA\_IN\_POP\_REG}{0x20}\label{regdesc:UHCIDMAINPOPREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{UHCI\_INFIFO\_POP}{1}{16}{0}%
\regfield{(reserved)}{4}{12}{0000}%
\regfield{UHCI\_INFIFO\_RDATA}{12}{0}{{0x0000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_INFIFO\_POP]Set this bit to pop data from DMA FIFO. (R/W)
\item [UHCI\_INFIFO\_RDATA]This register stores the data popping from DMA FIFO. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_DMA\_OUT\_LINK\_REG}{0x24}\label{regdesc:UHCIDMAOUTLINKREG}
\regfield{UHCI\_OUTLINK\_PARK}{1}{31}{0}%
\regfield{UHCI\_OUTLINK\_RESTART}{1}{30}{0}%
\regfield{UHCI\_OUTLINK\_START}{1}{29}{0}%
\regfield{UHCI\_OUTLINK\_STOP}{1}{28}{0}%
\regfield{(reserved)}{8}{20}{00000000}%
\regfield{UHCI\_OUTLINK\_ADDR}{20}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_OUTLINK\_PARK]1: the outlink descriptor's FSM is in idle state; 0: the outlink descriptor's FSM is working. (RO)
\item [UHCI\_OUTLINK\_RESTART]Set this bit to restart the outlink descriptor from the last address. (R/W)
\item [UHCI\_OUTLINK\_START]Set this bit to start a new outlink descriptor. (R/W)
\item [UHCI\_OUTLINK\_STOP]Set this bit to stop dealing with the outlink descriptor. (R/W)
\item [UHCI\_OUTLINK\_ADDR]This register stores the least significant 20 bits of the first outlink descriptor's address. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_DMA\_IN\_LINK\_REG}{0x28}\label{regdesc:UHCIDMAINLINKREG}
\regfield{UHCI\_INLINK\_PARK}{1}{31}{0}%
\regfield{UHCI\_INLINK\_RESTART}{1}{30}{0}%
\regfield{UHCI\_INLINK\_START}{1}{29}{0}%
\regfield{UHCI\_INLINK\_STOP}{1}{28}{0}%
\regfield{(reserved)}{8}{20}{00000000}%
\regfield{UHCI\_INLINK\_ADDR}{20}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_INLINK\_PARK]1: the inlink descriptor's FSM is in idle state; 0: the inlink descriptor's FSM is working. (RO)
\item [UHCI\_INLINK\_RESTART]Set this bit to mount new inlink descriptors. (R/W)
\item [UHCI\_INLINK\_START]Set this bit to start dealing with the inlink descriptors. (R/W)
\item [UHCI\_INLINK\_STOP]Set this bit to stop dealing with the inlink descriptors. (R/W)
\item [UHCI\_INLINK\_ADDR]This register stores the 20 least significant bits of the first inlink descriptor's address. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_CONF1\_REG}{0x2C}\label{regdesc:UHCICONF1REG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{UHCI\_TX\_ACK\_NUM\_RE}{1}{5}{1}%
\regfield{UHCI\_TX\_CHECK\_SUM\_RE}{1}{4}{1}%
\regfield{(reserved)}{2}{2}{00}%
\regfield{UHCI\_CHECK\_SEQ\_EN}{1}{1}{1}%
\regfield{UHCI\_CHECK\_SUM\_EN}{1}{0}{1}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_TX\_ACK\_NUM\_RE]Reserved. Please initialize to 0. (R/W)
\item [UHCI\_TX\_CHECK\_SUM\_RE]Reserved. Please initialize to 0. (R/W)
\item [UHCI\_CHECK\_SEQ\_EN]Reserved. Please initialize to 0. (R/W)
\item [UHCI\_CHECK\_SUM\_EN]Reserved. Please initialize to 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_DMA\_OUT\_EOF\_DES\_ADDR\_REG}{0x38}\label{regdesc:UHCIDMAOUTEOFDESADDRREG}
\regfield{}{32}{0}{{0x000000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_DMA\_OUT\_EOF\_DES\_ADDR\_REG]This register stores the address of the outlink descriptor when the EOF bit in this descriptor is 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_DMA\_IN\_SUC\_EOF\_DES\_ADDR\_REG}{0x3C}\label{regdesc:UHCIDMAINSUCEOFDESADDRREG}
\regfield{}{32}{0}{{0x000000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_DMA\_IN\_SUC\_EOF\_DES\_ADDR\_REG]This register stores the address of the inlink descriptor when the EOF bit in this descriptor is 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_DMA\_IN\_ERR\_EOF\_DES\_ADDR\_REG}{0x40}\label{regdesc:UHCIDMAINERREOFDESADDRREG}
\regfield{}{32}{0}{{0x000000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_DMA\_IN\_ERR\_EOF\_DES\_ADDR\_REG]This register stores the address of the inlink descriptor when there are some errors in this descriptor. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_DMA\_OUT\_EOF\_BFR\_DES\_ADDR\_REG}{0x44}\label{regdesc:UHCIDMAOUTEOFBFRDESADDRREG}
\regfield{}{32}{0}{{0x000000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_DMA\_OUT\_EOF\_BFR\_DES\_ADDR\_REG]This register stores the address of the outlink descriptor when there are some errors in this descriptor. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_DMA\_IN\_DSCR\_REG}{0x4C}\label{regdesc:UHCIDMAINDSCRREG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_DMA\_IN\_DSCR\_REG]The address of the current inlink descriptor \textcolor{red}{\it{x}}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_DMA\_IN\_DSCR\_BF0\_REG}{0x50}\label{regdesc:UHCIDMAINDSCRBF0REG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_DMA\_IN\_DSCR\_BF0\_REG]The address of the last inlink descriptor \textcolor{red}{\it{x-1}}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_DMA\_IN\_DSCR\_BF1\_REG}{0x54}\label{regdesc:UHCIDMAINDSCRBF1REG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_DMA\_IN\_DSCR\_BF1\_REG]The address of the second-to-last inlink descriptor \textcolor{red}{\it{x-2}}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_DMA\_OUT\_DSCR\_REG}{0x58}\label{regdesc:UHCIDMAOUTDSCRREG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_DMA\_OUT\_DSCR\_REG]The address of the current outlink descriptor \textcolor{red}{\it{y}}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_DMA\_OUT\_DSCR\_BF0\_REG}{0x5C}\label{regdesc:UHCIDMAOUTDSCRBF0REG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_DMA\_OUT\_DSCR\_BF0\_REG]The address of the last outlink descriptor \textcolor{red}{\it{y-1}}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_DMA\_OUT\_DSCR\_BF1\_REG}{0x60}\label{regdesc:UHCIDMAOUTDSCRBF1REG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_DMA\_OUT\_DSCR\_BF1\_REG]The address of the second-to-last outlink descriptor \textcolor{red}{\it{y-2}}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_ESCAPE\_CONF\_REG}{0x64}\label{regdesc:UHCIESCAPECONFREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{UHCI\_RX\_13\_ESC\_EN}{1}{7}{0}%
\regfield{UHCI\_RX\_11\_ESC\_EN}{1}{6}{0}%
\regfield{UHCI\_RX\_DB\_ESC\_EN}{1}{5}{1}%
\regfield{UHCI\_RX\_C0\_ESC\_EN}{1}{4}{1}%
\regfield{UHCI\_TX\_13\_ESC\_EN}{1}{3}{0}%
\regfield{UHCI\_TX\_11\_ESC\_EN}{1}{2}{0}%
\regfield{UHCI\_TX\_DB\_ESC\_EN}{1}{1}{1}%
\regfield{UHCI\_TX\_C0\_ESC\_EN}{1}{0}{1}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_RX\_13\_ESC\_EN]Set this bit to enable replacing flow control char 0x13, when DMA sends data. (R/W)
\item [UHCI\_RX\_11\_ESC\_EN]Set this bit to enable replacing flow control char 0x11, when DMA sends data. (R/W)
\item [UHCI\_RX\_DB\_ESC\_EN]Set this bit to enable replacing 0xdb char, when DMA sends data. (R/W)
\item [UHCI\_RX\_C0\_ESC\_EN]Set this bit to enable replacing 0xc0 char, when DMA sends data. (R/W)
\item [UHCI\_TX\_13\_ESC\_EN]Set this bit to enable decoding flow control char 0x13, when DMA receives data. (R/W)
\item [UHCI\_TX\_11\_ESC\_EN]Set this bit to enable decoding flow control char 0x11, when DMA receives data. (R/W)
\item [UHCI\_TX\_DB\_ESC\_EN]Set this bit to enable decoding 0xdb char, when DMA receives data. (R/W)
\item [UHCI\_TX\_C0\_ESC\_EN]Set this bit to enable decoding 0xc0 char, when DMA receives data. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_HUNG\_CONF\_REG}{0x68}\label{regdesc:UHCIHUNGCONFREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{UHCI\_RXFIFO\_TIMEOUT\_ENA}{1}{23}{1}%
\regfield{UHCI\_RXFIFO\_TIMEOUT\_SHIFT}{3}{20}{000}%
\regfield{UHCI\_RXFIFO\_TIMEOUT}{8}{12}{{0x010}}%
\regfield{UHCI\_TXFIFO\_TIMEOUT\_ENA}{1}{11}{1}%
\regfield{UHCI\_TXFIFO\_TIMEOUT\_SHIFT}{3}{8}{000}%
\regfield{UHCI\_TXFIFO\_TIMEOUT}{8}{0}{{0x010}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_RXFIFO\_TIMEOUT\_ENA]This is the enable bit for DMA send-data timeout. (R/W)
\item [UHCI\_RXFIFO\_TIMEOUT\_SHIFT]The tick count is cleared when its value is equal to or greater than  (17'd8000>>reg\_rxfifo\_timeout\_shift). (R/W)
\item [UHCI\_RXFIFO\_TIMEOUT]This register stores the timeout value. When DMA takes more time to read data from RAM than what this register indicates, it will produce the  UHCI\_RX\_HUNG\_INT interrupt. (R/W)
\item [UHCI\_TXFIFO\_TIMEOUT\_ENA]The enable bit for Tx FIFO receive-data  timeout (R/W)
\item [UHCI\_TXFIFO\_TIMEOUT\_SHIFT]The tick count is cleared when its value is equal to or greater than  (17'd8000>>reg\_txfifo\_timeout\_shift). (R/W)
\item [UHCI\_TXFIFO\_TIMEOUT]This register stores the timeout value. When DMA takes more time to receive data than what this register indicates, it will produce the UHCI\_TX\_HUNG\_INT interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UHCI\_ESC\_CONF\textcolor{red}{\it{n}}\_REG (\textcolor{red}{\it{n}}: 0-3)}{0xB0+4*\textcolor{red}{\it{n}}}\label{regdesc:UHCIESCCONFnREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{UHCI\_ESC\_SEQ2\_CHAR1}{8}{16}{{0x0DF}}%
\regfield{UHCI\_ESC\_SEQ2\_CHAR0}{8}{8}{{0x0DB}}%
\regfield{UHCI\_ESC\_SEQ2}{8}{0}{{0x013}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [UHCI\_ESC\_SEQ2\_CHAR1]This register stores  the second char used to replace the reg\_esc\_seq2 in data. (R/W)
\item [UHCI\_ESC\_SEQ2\_CHAR0]This register stores the first char used to replace the reg\_esc\_seq2 in data. (R/W)
\item [UHCI\_ESC\_SEQ2]This register stores the flow\_control char to turn off the flow\_control. (R/W)
\end{reglist}\end{regdesc}
\end{register}

