\begin{longtable}[l]{ |m{8.2cm}|r|c|r|m{9cm}| }
\caption{Parameters in eFuse BLOCK0}
    \label{tab:efuse-block0-para}
    \\\hline
    \rowcolor{lightgray}
    \textbf{Parameters} & \textbf{\thead{Bit \\Width}} & \textbf{\thead{Accessible \\by Hardware}} & \textbf{\thead{Write Protection \\by \hyperref[fielddesc:EFUSEWRDIS]{EFUSE\_WR\_DIS} \\Bit Number}}
    & \textbf{Description} \\
    \endfirsthead
    \multicolumn{5}{c}{\bfseries \tablename\ \thetable{} -- cont'd from previous page}\\\hline
    \rowcolor{lightgray}
    \textbf{Parameters} & \textbf{\thead{Bit \\Width}} & \textbf{\thead{Accessible \\by Hardware}} & \textbf{\thead{Write Protection \\by \hyperref[fielddesc:EFUSEWRDIS]{EFUSE\_WR\_DIS} \\Bit Number}}
    & \textbf{Description} \\
    \endhead
    \multicolumn{5}{r}{\textbf{Cont'd on next page}} \\
    \endfoot
    \endlastfoot
    \hline
    \hyperref[fielddesc:EFUSEWRDIS]{EFUSE\_WR\_DIS} & 32 & Y & N/A & Represents whether programming of individual eFuse memory bit is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSERDDIS]{EFUSE\_RD\_DIS} & 7 & Y & 0 & Represents whether reading of individual eFuse block (BLOCK4 \verb+~+ BLOCK10) is disabled. \\ \hline
    \hyperref[fielddesc:EFUSEBOOTLOADERANTIROLLBACKSECUREVERSIONHI]{EFUSE\_\-BOOTLOADER\_\-ANTI\_\-ROLLBACK\_\-SECURE\_\-VERSION\_\-HI} & 1 & N & N/A & Represents the anti-rollback secure version of the 2nd stage bootloader used by the ROM bootloader (the high part of the field).  \\ \hline
    \hyperref[fielddesc:EFUSEDISICACHE]{EFUSE\_DIS\_ICACHE} & 1 & Y & 2 & Represents whether cache is disabled. \\ \hline
    \hyperref[fielddesc:EFUSEDISUSBJTAG]{EFUSE\_DIS\_USB\_JTAG} & 1 & Y & 2 & Represents whether the USB-to-JTAG function in USB Serial/JTAG is disabled. \\ \hline
    \hyperref[fielddesc:EFUSEBOOTLOADERANTIROLLBACKEN]{EFUSE\_BOOTLOADER\_ANTI\_ROLLBACK\_EN} & 1 & N & N/A & Represents whether the ani-rollback check for the 2nd stage bootloader is enabled. \\ \hline
    \hyperref[fielddesc:EFUSEDISFORCEDOWNLOAD]{EFUSE\_DIS\_FORCE\_DOWNLOAD} & 1 & Y & 2 & Represents whether the function that forces chip into Download mode is disabled.  \\ \hline
    \hyperref[fielddesc:EFUSESPIDOWNLOADMSPIDIS]{EFUSE\_SPI\_DOWNLOAD\_MSPI\_DIS} & 1 & Y & 2 & Represents whether SPI0 controller during boot\_mode\_download is disabled. \\ \hline
    \hyperref[fielddesc:EFUSEDISTWAI]{EFUSE\_DIS\_TWAI} & 1 & Y & 2 & Represents whether TWAI$^®$ function is disabled. \\ \hline
    \hyperref[fielddesc:EFUSEJTAGSELENABLE]{EFUSE\_JTAG\_SEL\_ENABLE} & 1 & Y & 2 & Represents whether the selection of a JTAG signal source through the strapping pin value is enabled when all of \hyperref[fielddesc:EFUSEDISPADJTAG]{EFUSE\_DIS\_PAD\_JTAG} and \hyperref[fielddesc:EFUSEDISUSBJTAG]{EFUSE\_DIS\_USB\_JTAG} are configured to 0. For more information, please refer to Chapter \ref{mod:bootctrl} \textit{\nameref{mod:bootctrl}}. \\ \hline
    \hyperref[fielddesc:EFUSESOFTDISJTAG]{EFUSE\_SOFT\_DIS\_JTAG} & 3 & Y & 31 & Represents whether PAD JTAG is disabled in the soft way. It can be restarted via HMAC.  \\ \hline
    \hyperref[fielddesc:EFUSEDISPADJTAG]{EFUSE\_DIS\_PAD\_JTAG} & 1 & Y & 2 & Represents whether PAD JTAG is disabled in the hard way (permanently). \\ \hline
    \hyperref[fielddesc:EFUSEDISDOWNLOADMANUALENCRYPT]{EFUSE\_DIS\_DOWNLOAD\_MANUAL\_ENCRYPT} & 1 & Y & 2 & Represents whether flash encryption is disabled (except in SPI boot mode). \\ \hline
    \hyperref[fielddesc:EFUSEUSBEXCHGPINS]{EFUSE\_USB\_EXCHG\_PINS} & 1 & Y & 30 & Represents whether the D+ and D- pins is exchanged. \\ \hline
    \hyperref[fielddesc:EFUSEVDDSPIASGPIO]{EFUSE\_VDD\_SPI\_AS\_GPIO} & 1 & Y & 30 & Represents whether VDD SPI pin is functioned as GPIO. \\ \hline
    \hyperref[fielddesc:EFUSEWDTDELAYSEL]{EFUSE\_WDT\_DELAY\_SEL} & 2 & Y & 3 & Represents RTC watchdog timeout threshold. \\ \hline
    \hyperref[fielddesc:EFUSEBOOTLOADERANTIROLLBACKSECUREVERSIONLO]{EFUSE\_\-BOOTLOADER\_\-ANTI\_\-ROLLBACK\_\-SECURE\_\-VERSION\_\-LO} & 3 & N & N/A & Represents the anti-rollback secure version of the second stage bootloader used by the first stage (ROM bootloader (the low part of the field).  \\ \hline
    \hyperref[fielddesc:EFUSEKMDISABLEDEPLOYMODE]{EFUSE\_KM\_DISABLE\_DEPLOY\_MODE} & 4 & Y & 1 & Represents whether the new key deployment of key manager is disabled.  \\ \hline
    \hyperref[fielddesc:EFUSEKMRNDSWITCHCYCLE]{EFUSE\_KM\_RND\_SWITCH\_CYCLE} & 2 & Y & 1 & Represents the cycle at which the Key Manager switches random numbers. \\ \hline
    \hyperref[fielddesc:EFUSEKMDEPLOYONLYONCE]{EFUSE\_KM\_DEPLOY\_ONLY\_ONCE} & 4 & Y & 1 & Represents whether the corresponding key can be deployed only once. \\ \hline
    \hyperref[fielddesc:EFUSEFORCEUSEKEYMANAGERKEY]{EFUSE\_FORCE\_USE\_KEY\_MANAGER\_KEY} & 4 & Y & 1 & Represents whether the corresponding key must come from Key Manager.  \\ \hline
    \hyperref[fielddesc:EFUSEFORCEDISABLESWINITKEY]{EFUSE\_FORCE\_DISABLE\_SW\_INIT\_KEY} & 1 & Y & 1 & Represents whether to disable the use of the initialization key written by software and instead force use efuse\_init\_key. \\ \hline
    \hyperref[fielddesc:EFUSEBOOTLOADERANTIROLLBACKUPDATEINROM]{EFUSE\_\-BOOTLOADER\_\-ANTI\_\-ROLLBACK\_\-UPDATE\_\-IN\_\-ROM} & 1 & N & N/A & Represents whether the ani-rollback SECURE\_VERSION will be updated from the ROM bootloader. \\ \hline
    \hyperref[fielddesc:EFUSESPIBOOTCRYPTCNT]{EFUSE\_SPI\_BOOT\_CRYPT\_CNT} & 3 & Y & 4 & Represents whether SPI boot encryption/decryption is enabled.  \\ \hline
    \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE0]{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE0} & 1 & N & 5 & Represents whether revoking Secure Boot key digest 0 is enabled.  \\ \hline
    \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE1]{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE1} & 1 & N & 6 & Represents whether revoking Secure Boot key digest 1 is enabled. \\ \hline
    \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE2]{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE2} & 1 & N & 7 & Represents whether revoking Secure Boot key digest 2 is enabled. \\ \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE0]{EFUSE\_KEY\_PURPOSE\_0} & 5 & Y & 8 & Represents the purpose of Key0. See Table \ref{tab:efuse-key-purpose}. \\ \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE1]{EFUSE\_KEY\_PURPOSE\_1} & 5 & Y & 9 & Represents the purpose of Key1. See Table \ref{tab:efuse-key-purpose}. \\ \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE2]{EFUSE\_KEY\_PURPOSE\_2} & 5 & Y & 10 & Represents the purpose of Key2. See Table \ref{tab:efuse-key-purpose}. \\ \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE3]{EFUSE\_KEY\_PURPOSE\_3} & 5 & Y & 11 & Represents the purpose of Key3. See Table \ref{tab:efuse-key-purpose}. \\ \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE4]{EFUSE\_KEY\_PURPOSE\_4} & 5 & Y & 12 & Represents the purpose of Key4. See Table \ref{tab:efuse-key-purpose}. \\ \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE5]{EFUSE\_KEY\_PURPOSE\_5} & 5 & Y & 13 & Represents the purpose of Key5. See Table \ref{tab:efuse-key-purpose}. \\ \hline
    \hyperref[fielddesc:EFUSESECDPALEVEL]{EFUSE\_SEC\_DPA\_LEVEL} & 2 & Y & 14 & Represents the security level of anti-DPA attack. The level is adjusted by configuring the clock random frequency division mode. \\ \hline
    \hyperref[fielddesc:EFUSERECOVERYBOOTLOADERFLASHSECTORHI]{EFUSE\_RECOVERY\_BOOTLOADER\_FLASH\_SECTOR\_HI} & 3 & N & N/A & Represents the starting flash sector (flash sector size is 0x1000) of the recovery bootloader used by the ROM bootloader If the primary bootloader fails. 0 and 0xFFF - this feature is disabled. (The high part of the field). \\ \hline
    \hyperref[fielddesc:EFUSESECUREBOOTEN]{EFUSE\_SECURE\_BOOT\_EN} & 1 & N & 15 & Represents whether Secure Boot is enabled. \\ \hline
    \hyperref[fielddesc:EFUSESECUREBOOTAGGRESSIVEREVOKE]{EFUSE\_SECURE\_BOOT\_AGGRESSIVE\_REVOKE} & 1 & N & 16 & Represents whether aggressive revocation of Secure Boot is enabled. \\ \hline
    \hyperref[fielddesc:EFUSEKMXTSKEYLENGTH256]{EFUSE\_KM\_XTS\_KEY\_LENGTH\_256} & 1 & N & 1 & Represents which key flash encryption uses. \\ \hline
    \hyperref[fielddesc:EFUSEFLASHTPUW]{EFUSE\_FLASH\_TPUW} & 4 & N & 18 & Represents the flash waiting time after power-up. Measurement unit: ms. When the value is less than 15, the waiting time is the programmed value. Otherwise, the waiting time is a fixed value, i.e. 30 ms. \\ \hline
    \hyperref[fielddesc:EFUSEDISDOWNLOADMODE]{EFUSE\_DIS\_DOWNLOAD\_MODE} & 1 & N & 18 & Represents whether Download mode is disabled.\\ \hline
    \hyperref[fielddesc:EFUSEDISDIRECTBOOT]{EFUSE\_DIS\_DIRECT\_BOOT} & 1 & N & 18 & Represents whether direct boot mode is disabled. \\ \hline
    \hyperref[fielddesc:EFUSEDISUSBSERIALJTAGROMPRINT]{EFUSE\_DIS\_USB\_SERIAL\_JTAG\_ROM\_PRINT} & 1 & N & 18 & Represents whether print from USB-Serial-JTAG is disabled. \\ \hline
    \hyperref[fielddesc:EFUSELOCKKMKEY]{EFUSE\_LOCK\_KM\_KEY} & 1 & N & 1 & Represents whether the keys in the Key Manager are locked after deployment. \\ \hline
    \hyperref[fielddesc:EFUSEDISUSBSERIALJTAGDOWNLOADMODE]{EFUSE\_DIS\_USB\_SERIAL\_JTAG\_DOWNLOAD\_MODE} & 1 & N & 18 & Represents whether the USB-Serial-JTAG download function is disabled. \\ \hline
    \hyperref[fielddesc:EFUSEENABLESECURITYDOWNLOAD]{EFUSE\_ENABLE\_SECURITY\_DOWNLOAD} & 1 & N & 18 & Represents whether security download is enabled. Only downloading into flash is supported. Reading/writing RAM or registers is not supported (i.e. stub download is not supported). \\ \hline
    \hyperref[fielddesc:EFUSEUARTPRINTCONTROL]{EFUSE\_UART\_PRINT\_CONTROL} & 2 & N & 18 & Represents the type of UART printing.  \\ \hline
    \hyperref[fielddesc:EFUSEFORCESENDRESUME]{EFUSE\_FORCE\_SEND\_RESUME} & 1 & N & 18 & Represents whether ROM code is forced to send a resume command during SPI boot. \\ \hline
    \hyperref[fielddesc:EFUSESECUREVERSION]{EFUSE\_SECURE\_VERSION} & 9 & N & 18 & Represents the app security version used by ESP-IDF anti-rollback feature. \\ \hline
    \hyperref[fielddesc:EFUSESECUREBOOTDISABLEFASTWAKE]{EFUSE\_SECURE\_BOOT\_DISABLE\_FAST\_WAKE} & 1 & N & 18 & Represents whether FAST VERIFY ON WAKE is disabled when Secure Boot is enabled. \\ \hline
    \hyperref[fielddesc:EFUSEHYSENPAD]{EFUSE\_HYS\_EN\_PAD} & 1 & Y & 2 & Represents whether the hysteresis function of PAD0 – PAD27 is enabled. \\ \hline
    \hyperref[fielddesc:EFUSEXTSDPAPSEUDOLEVEL]{EFUSE\_XTS\_DPA\_PSEUDO\_LEVEL} & 2 & Y & 14 & Represents the pseudo round level of XTS-AES anti-DPA attack. \\ \hline
    \hyperref[fielddesc:EFUSEXTSDPACLKENABLE]{EFUSE\_XTS\_DPA\_CLK\_ENABLE} & 1 & Y & 14 & Represents whether XTS-AES anti-DPA attack clock is enabled. \\ \hline
    \hyperref[fielddesc:EFUSEECDSAP384ENABLE]{EFUSE\_ECDSA\_P384\_ENABLE} & 1 & N & 14 & Represents if the chip supports ECDSA\_DS P384 \\ \hline
    \hyperref[fielddesc:EFUSEHUKGENSTATE]{EFUSE\_HUK\_GEN\_STATE} & 9 & Y & 19 & Represents whether the HUK generate mode is valid. \\ \hline
    \hyperref[fielddesc:EFUSEECCFORCECONSTTIME]{EFUSE\_ECC\_FORCE\_CONST\_TIME} & 1 & Y & 14 & Represents whether to force ECC to use constant-time mode for point multiplication calculation.  \\ \hline
    \hyperref[fielddesc:EFUSERECOVERYBOOTLOADERFLASHSECTORLO]{EFUSE\_RECOVERY\_BOOTLOADER\_FLASH\_SECTOR\_LO} & 9 & N & N/A & Represents the starting flash sector (flash sector size is 0x1000) of the recovery bootloader used by the ROM bootloader If the primary bootloader fails. 0 and 0xFFF - this feature is disabled. (The low part of the field). \\ \hline
\end{longtable}
