\begin{longtable}[l]{ |m{8.2cm}|r|c|r|m{9cm}| }
\caption{Parameters in eFuse BLOCK0}
    \label{tab:efuse-block0-para}
    \\\hline
    \rowcolor{lightgray}
    \textbf{Parameters} & \textbf{\thead{Bit \\Width}} & \textbf{\thead{Accessible \\by Hardware}} & \textbf{\thead{Write Protection \\by \hyperref[fielddesc:EFUSEWRDIS]{EFUSE\_WR\_DIS} \\Bit Number}}
    & \textbf{Description} \\
    \endfirsthead
    \multicolumn{5}{c}{\bfseries \tablename\ \thetable{} -- cont'd from previous page}\\\hline
    \rowcolor{lightgray}
    \textbf{Parameters} & \textbf{\thead{Bit \\Width}} & \textbf{\thead{Accessible \\by Hardware}} & \textbf{\thead{Write Protection \\by \hyperref[fielddesc:EFUSEWRDIS]{EFUSE\_WR\_DIS} \\Bit Number}}
    & \textbf{Description} \\
    \endhead
    \multicolumn{5}{r}{\textbf{Cont'd on next page}} \\
    \endfoot
    \endlastfoot
    \hline
    \textbf{\hyperref[fielddesc:EFUSEWRDIS]{EFUSE\_WR\_DIS}}  & 32 & Y & N/A & Represents whether writing of eFuse bits by eFuse controller is disabled.\\
    \hline
    \textbf{\hyperref[fielddesc:EFUSERDDIS]{EFUSE\_RD\_DIS}}  & 7 & Y & 0  & Represents whether reading data from BLOCK4 \verb+~+ 10 in eFuse memory by users is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEUSBDEVICEEXCHGPINS]{EFUSE\_USB\_DEVICE\_EXCHG\_PINS} & 1 & Y & 30 & Represents whether the USB Serial/JTAG pins D+ and D- are exchanged. \\
    \hline
    \hyperref[fielddesc:EFUSEUSBOTG11EXCHGPINS]{EFUSE\_USB\_OTG11\_EXCHG\_PINS} & 1 & Y & 30 & Represents whether the USB FS pins D+ and D- are exchanged. \\
    \hline
    \hyperref[fielddesc:EFUSEDISUSBJTAG]{EFUSE\_DIS\_USB\_JTAG}  & 1 & Y & 2  & Represents whether the USB-to-JTAG function in USB Serial/JTAG module is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEPOWERGLITCHEN]{EFUSE\_POWERGLITCH\_EN}  & 1 & Y & 2  & Represents whether power glitch detection is enabled. \\
    \hline
    \hyperref[fielddesc:EFUSEDISFORCEDOWNLOAD]{EFUSE\_DIS\_FORCE\_DOWNLOAD} & 1 & Y & 2 & Represents whether the function to force the chip into Download mode is disabled.\\
    \hline
    \hyperref[fielddesc:EFUSESPIDOWNLOADMSPIDIS]{EFUSE\_SPI\_DOWNLOAD\_MSPI\_DIS} & 1 & Y & 2 & Represents accessing MSPI flash/MSPI RAM by SYS AXI matrix is disabled during boot\_mode\_download. \\
    \hline
    \hyperref[fielddesc:EFUSEDISTWAI]{EFUSE\_DIS\_TWAI} & 1 & Y & 2 & Represents whether the TWAI controller is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEJTAGSELENABLE]{EFUSE\_JTAG\_SEL\_ENABLE} & 1 & Y & 2 & Represents whether the selection of a JTAG signal source through the strapping value is enabled when both \hyperref[fielddesc:EFUSEDISPADJTAG]{EFUSE\_DIS\_PAD\_JTAG} and \hyperref[fielddesc:EFUSEDISUSBJTAG]{EFUSE\_DIS\_USB\_JTAG} are configured to 0.\\
    \hline
    \hyperref[fielddesc:EFUSESOFTDISJTAG]{EFUSE\_SOFT\_DIS\_JTAG} & 3 & Y & 31 & Represents whether PAD JTAG is disabled in the soft way.\\
    \hline
    \hyperref[fielddesc:EFUSEDISPADJTAG]{EFUSE\_DIS\_PAD\_JTAG} & 1 & Y & 2 & Represents whether PAD JTAG is disabled in the hard way (permanently). \\
    \hline
    \hyperref[fielddesc:EFUSEDISDOWNLOADMANUALENCRYPT]{EFUSE\_DIS\_DOWNLOAD\_MANUAL\_ENCRYPT} &  1 & Y & 2 & Represents whether flash encryption is disabled (except in SPI boot mode).\\
    \hline
    \hyperref[fielddesc:EFUSEUSBPHYSEL]{EFUSE\_USB\_PHY\_SEL} &  1 & Y & 30 & Represents the connection between USB Serial/JTAG Controller, OTG\_FS and FS\_PHY1, FS\_PHY2. \\
    \hline
    \hyperref[fielddesc:EFUSEXTSKEYLENGTH256]{EFUSE\_XTS\_KEY\_LENGTH\_256} &  1 & N & 1 & Represents which key is used for flash encryption.\\
    \hline
    \hyperref[fielddesc:EFUSEWDTDELAYSEL]{EFUSE\_WDT\_DELAY\_SEL} & 2 & Y & 2 & Represents RTC watchdog timeout threshold.\\
    \hline
    \hyperref[fielddesc:EFUSESPIBOOTCRYPTCNT]{EFUSE\_SPI\_BOOT\_CRYPT\_CNT} & 3 & Y & 4 & Represents whether SPI boot encryption/decryption is enabled.\\
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE0]{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE0} & 1 & N & 5 & Represents whether revoking the first Secure Boot key is enabled.\\
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE1]{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE1} & 1 & N & 6 & Represents whether revoking the second Secure Boot key is enabled.\\
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE2]{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE2} & 1 & N & 7 & Represents whether revoking the third Secure Boot key is enabled.\\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE0]{EFUSE\_KEY\_PURPOSE\_0} & 4 & Y & 8 & {Represents Key0 purpose. See Table \ref{tab:efuse-key-purpose}.} \\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE1]{EFUSE\_KEY\_PURPOSE\_1} & 4 & Y & 9 & {Represents Key1 purpose. See Table \ref{tab:efuse-key-purpose}.} \\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE2]{EFUSE\_KEY\_PURPOSE\_2} & 4 & Y & 10 & {Represents Key2 purpose. See Table \ref{tab:efuse-key-purpose}.} \\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE3]{EFUSE\_KEY\_PURPOSE\_3} & 4 & Y & 11 & {Represents Key3 purpose. See Table \ref{tab:efuse-key-purpose}.} \\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE4]{EFUSE\_KEY\_PURPOSE\_4} & 4 & Y & 12 & {Represents Key4 purpose. See Table \ref{tab:efuse-key-purpose}.} \\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE5]{EFUSE\_KEY\_PURPOSE\_5} & 4 & Y & 13 & {Represents Key5 purpose. See Table \ref{tab:efuse-key-purpose}.} \\
    \hline
    \hyperref[fielddesc:EFUSESECDPALEVEL]{EFUSE\_SEC\_DPA\_LEVEL} & 2 & Y & 14 & Represents the security level of anti-DPA (differential power analysis) attack. \\
    \hline
    \hyperref[fielddesc:EFUSECRYPTDPAENABLE]{EFUSE\_CRYPT\_DPA\_ENABLE} & 1 & Y & 14 & Represents whether defense against DPA attack is enabled. \\
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTEN]{EFUSE\_SECURE\_BOOT\_EN} & 1 & N & 15 & Represents whether Secure Boot is enabled. \\
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTAGGRESSIVEREVOKE]{EFUSE\_SECURE\_BOOT\_AGGRESSIVE\_REVOKE} & 1 & N & 16 & Represents whether aggressive revocation of Secure Boot is enabled. \\
    \hline
    \hyperref[fielddesc:EFUSEFLASHTYPE]{EFUSE\_FLASH\_TYPE} & 1 & N & 18 & Represents the type of the interfaced flash. \\
    \hline
    \hyperref[fielddesc:EFUSEFLASHPAGESIZE]{EFUSE\_FLASH\_PAGE\_SIZE} & 2 & N & 18 & Represents flash page size. \\
    \hline
    \hyperref[fielddesc:EFUSEFLASHECCEN]{EFUSE\_FLASH\_ECC\_EN} & 1 & N & 18 & Represents whether ECC is enabled during flash boot. \\
    \hline
    \hyperref[fielddesc:EFUSEDISUSBOTGDOWNLOADMODE]{EFUSE\_DIS\_USB\_OTG\_DOWNLOAD\_MODE} & 1 & N & 18 & Represents whether download via USB-OTG is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEFLASHTPUW]{EFUSE\_FLASH\_TPUW} & 4 & N & 18 & Represents the flash waiting time after power-up.\\
    \hline
    \hyperref[fielddesc:EFUSEDISDOWNLOADMODE]{EFUSE\_DIS\_DOWNLOAD\_MODE} & 1 & N & 18 & Represents whether all Download modes are disabled.\\
    \hline
    \hyperref[fielddesc:EFUSEDISDIRECTBOOT]{EFUSE\_DIS\_DIRECT\_BOOT} & 1 & N & 18 & Represents whether direct boot mode is disabled.\\
    \hline
    \hyperref[fielddesc:EFUSEDISUSBSERIALJTAGROMPRINT]{EFUSE\_DIS\_USB\_SERIAL\_JTAG\_ROM\_PRINT} & 1 & N & 18 & Represents whether print from USB-Serial-JTAG during ROM boot is disabled.\\
    \hline
    \hyperref[fielddesc:EFUSEDISUSBSERIALJTAGDOWNLOADMODE]{EFUSE\_DIS\_USB\_SERIAL\_JTAG\_DOWNLOAD\_MODE} & 1 & N & 18 & Represents whether the USB-Serial-JTAG download function is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEENABLESECURITYDOWNLOAD]{EFUSE\_ENABLE\_SECURITY\_DOWNLOAD} & 1 & N & 18 & Represents whether security download is enabled. \\
    \hline
    \hyperref[fielddesc:EFUSEUARTPRINTCONTROL]{EFUSE\_UART\_PRINT\_CONTROL} & 2 & N & 18 & Represents the type of UART printing.\\
    \hline
    \hyperref[fielddesc:EFUSEFORCESENDRESUME]{EFUSE\_FORCE\_SEND\_RESUME} & 1 & N & 18 & Represents whether ROM code is forced to send a resume command during SPI boot. \\
    \hline
    \hyperref[fielddesc:EFUSESECUREVERSION]{EFUSE\_SECURE\_VERSION} & 16 & N & 18 & Represents the version used by ESP-IDF anti-rollback feature. \\
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTDISABLEFASTWAKE]{EFUSE\_SECURE\_BOOT\_DISABLE\_FAST\_WAKE} & 1 & N & 19 & Represents whether FAST VERIFY ON WAKE is disabled or enabled when Secure Boot is enabled.\\
    \hline
    \hyperref[fielddesc:EFUSEHYSENPAD]{EFUSE\_HYS\_EN\_PAD} & 1 & Y & 2 & Represents whether the hysteresis function of PAD0 – PAD27 is enabled.\\
    \hline
    \hyperref[fielddesc:EFUSEDCDCVSET]{EFUSE\_DCDC\_VSET} & 5 & Y & N/A & Represents the default DCDC voltage.\\
    \hline
    \hyperref[fielddesc:EFUSE0PXATIEHSEL0]{EFUSE\_0PXA\_TIEH\_SEL0} & 2 & Y & 2 & Represents which output source is used for Extern Power (VO1).\\
    \hline
    \hyperref[fielddesc:EFUSE0PXATIEHSEL1]{EFUSE\_0PXA\_TIEH\_SEL1} & 2 & Y & 2 & Represents which output source is used for Extern Power (VO2).\\
    \hline
    \hyperref[fielddesc:EFUSE0PXATIEHSEL2]{EFUSE\_0PXA\_TIEH\_SEL2} & 2 & Y & 2 & Represents which output source is used for Extern Power (VO3).\\
    \hline
    \hyperref[fielddesc:EFUSE0PXATIEHSEL3]{EFUSE\_0PXA\_TIEH\_SEL3} & 2 & Y & 2 & Represents which output source is used for Extern Power (VO4).\\
    \hline
    \hyperref[fielddesc:EFUSEHPPWRSRCSEL]{EFUSE\_HP\_PWR\_SRC\_SEL} & 1 & Y & 3 & Represents the HP system power source.\\
    \hline
    \hyperref[fielddesc:EFUSEDCDCVSETEN]{EFUSE\_DCDC\_VSET\_EN} & 1 & Y & N/A & Represents whether to use the default voltage configured by \hyperref[fielddesc:EFUSEDCDCVSET]{EFUSE\_DCDC\_VSET}.\\
    \hline
    \hyperref[fielddesc:EFUSEDISWDT]{EFUSE\_DIS\_WDT} & 1 & Y & 2 & Represents whether to disable the watchdog.\\
    \hline
    \hyperref[fielddesc:EFUSEDISSWD]{EFUSE\_DIS\_SWD} & 1 & Y & 2 & Represents whether to disable the super watchdog.\\
    \hline
\end{longtable}
