\begin{register}{H}{I2C\_SCL\_LOW\_PERIOD\_REG}{\hexprefix{}0000}\label{regdesc:I2CSCLLOWPERIODREG}
\regfield{(reserved)}{18}{14}{000000000000000000}%
\regfield{I2C\_SCL\_LOW\_PERIOD}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CSCLLOWPERIOD}\item [I2C\_SCL\_LOW\_PERIOD] This register is used to configure for how long SCL remains low in master mode, in I2C module clock cycles. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_SDA\_HOLD\_REG}{\hexprefix{}0030}\label{regdesc:I2CSDAHOLDREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{I2C\_SDA\_HOLD\_TIME}{10}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CSDAHOLDTIME}\item [I2C\_SDA\_HOLD\_TIME] This register is used to configure the interval between changing the SDA output level and the falling edge of SCL, in I2C module clock cycles. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_SDA\_SAMPLE\_REG}{\hexprefix{}0034}\label{regdesc:I2CSDASAMPLEREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{I2C\_SDA\_SAMPLE\_TIME}{10}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CSDASAMPLETIME}\item [I2C\_SDA\_SAMPLE\_TIME] This register is used to configure the interval between the rising edge of SCL and the level sampling time of SDA, in I2C module clock cycles. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_SCL\_HIGH\_PERIOD\_REG}{\hexprefix{}0038}\label{regdesc:I2CSCLHIGHPERIODREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{I2C\_SCL\_WAIT\_HIGH\_PERIOD}{14}{14}{{\hexprefix{}00}}%
\regfield{I2C\_SCL\_HIGH\_PERIOD}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CSCLHIGHPERIOD}\item [I2C\_SCL\_HIGH\_PERIOD] This register is used to configure for how long SCL remains high in master mode, in I2C module clock cycles. (R/W)
\label{fielddesc:I2CSCLWAITHIGHPERIOD}\item [I2C\_SCL\_WAIT\_HIGH\_PERIOD] This register is used to configure for the SCL\_FSM's waiting period for SCL to go high in master mode, in I2C module clock cycles. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_SCL\_START\_HOLD\_REG}{\hexprefix{}0040}\label{regdesc:I2CSCLSTARTHOLDREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{I2C\_SCL\_START\_HOLD\_TIME}{10}{0}{{8}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CSCLSTARTHOLDTIME}\item [I2C\_SCL\_START\_HOLD\_TIME] This register is used to configure  interval between pulling SDA low and pulling SCL low when the master generates a START condition, in I2C module clock cycles. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_SCL\_RSTART\_SETUP\_REG}{\hexprefix{}0044}\label{regdesc:I2CSCLRSTARTSETUPREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{I2C\_SCL\_RSTART\_SETUP\_TIME}{10}{0}{{8}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CSCLRSTARTSETUPTIME}\item [I2C\_SCL\_RSTART\_SETUP\_TIME] This register is used to configure the interval between the positive edge of SCL and the negative edge of SDA for a RESTART condition, in I2C module clock cycles. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_SCL\_STOP\_HOLD\_REG}{\hexprefix{}0048}\label{regdesc:I2CSCLSTOPHOLDREG}
\regfield{(reserved)}{18}{14}{000000000000000000}%
\regfield{I2C\_SCL\_STOP\_HOLD\_TIME}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CSCLSTOPHOLDTIME}\item [I2C\_SCL\_STOP\_HOLD\_TIME] This register is used to configure the delay after the STOP condition, in I2C module clock cycles. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_SCL\_STOP\_SETUP\_REG}{\hexprefix{}004C}\label{regdesc:I2CSCLSTOPSETUPREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{I2C\_SCL\_STOP\_SETUP\_TIME}{10}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CSCLSTOPSETUPTIME}\item [I2C\_SCL\_STOP\_SETUP\_TIME] This register is used to configure the time between the positive edge of SCL and the positive edge of SDA, in I2C module clock cycles. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_SCL\_ST\_TIME\_OUT\_REG}{\hexprefix{}0098}\label{regdesc:I2CSCLSTTIMEOUTREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{I2C\_SCL\_ST\_TO}{24}{0}{{\hexprefix{}0100}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CSCLSTTO}\item [I2C\_SCL\_ST\_TO] The threshold value of SCL\_FSM state unchanged period. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_SCL\_MAIN\_ST\_TIME\_OUT\_REG}{\hexprefix{}009C}\label{regdesc:I2CSCLMAINSTTIMEOUTREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{I2C\_SCL\_MAIN\_ST\_TO}{24}{0}{{\hexprefix{}0100}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CSCLMAINSTTO}\item [I2C\_SCL\_MAIN\_ST\_TO] The threshold value of SCL\_MAIN\_FSM state unchanged period. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_CTR\_REG}{\hexprefix{}0004}\label{regdesc:I2CCTRREG}
\regfield{(reserved)}{20}{12}{00000000000000000000}%
\regfield{I2C\_REF\_ALWAYS\_ON}{1}{11}{{1}}%
\regfield{I2C\_FSM\_RST}{1}{10}{{0}}%
\regfield{I2C\_ARBITRATION\_EN}{1}{9}{{1}}%
\regfield{I2C\_CLK\_EN}{1}{8}{{0}}%
\regfield{I2C\_RX\_LSB\_FIRST}{1}{7}{{0}}%
\regfield{I2C\_TX\_LSB\_FIRST}{1}{6}{{0}}%
\regfield{I2C\_TRANS\_START}{1}{5}{{0}}%
\regfield{I2C\_MS\_MODE}{1}{4}{{0}}%
\regfield{I2C\_RX\_FULL\_ACK\_LEVEL}{1}{3}{{1}}%
\regfield{I2C\_SAMPLE\_SCL\_LEVEL}{1}{2}{{0}}%
\regfield{I2C\_SCL\_FORCE\_OUT}{1}{1}{{1}}%
\regfield{I2C\_SDA\_FORCE\_OUT}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CSDAFORCEOUT}\item [I2C\_SDA\_FORCE\_OUT] Configures the SDA output mode.\\
0: Open drain output \\
1: Direct output \\ (R/W)
\label{fielddesc:I2CSCLFORCEOUT}\item [I2C\_SCL\_FORCE\_OUT] Configures the SCL output mode.\\
0: Open drain output \\
1: Direct output \\ (R/W)
\label{fielddesc:I2CSAMPLESCLLEVEL}\item [I2C\_SAMPLE\_SCL\_LEVEL] This register is used to select the sample mode.
1: sample SDA data on the SCL low level.
0: sample SDA data on the SCL high level. (R/W)
\label{fielddesc:I2CRXFULLACKLEVEL}\item [I2C\_RX\_FULL\_ACK\_LEVEL] This register is used to configure the ACK value that need to sent by master when the rx\_fifo\_cnt has reached the threshold. (R/W)
\label{fielddesc:I2CMSMODE}\item [I2C\_MS\_MODE] Set this bit to configure the module as an I2C Master. Clear this bit to configure the
module as an I2C Slave. (R/W)
\label{fielddesc:I2CTRANSSTART}\item [I2C\_TRANS\_START] Set this bit to start sending the data in TX FIFO. (R/W)
\label{fielddesc:I2CTXLSBFIRST}\item [I2C\_TX\_LSB\_FIRST] This bit is used to control the sending mode for data needing to be sent.
1: send data from the least significant bit;
0: send data from the most significant bit. (R/W)
\label{fielddesc:I2CRXLSBFIRST}\item [I2C\_RX\_LSB\_FIRST] This bit is used to control the storage mode for received data.
1: receive data from the least significant bit;
0: receive data from the most significant bit. (R/W)
\label{fielddesc:I2CCLKEN}\item [I2C\_CLK\_EN] Reserved (R/W)
\label{fielddesc:I2CARBITRATIONEN}\item [I2C\_ARBITRATION\_EN] This is the enable bit for I2C bus arbitration function. (R/W)
\label{fielddesc:I2CFSMRST}\item [I2C\_FSM\_RST] This register is used to reset the SCL\_FSM. (R/W)
\label{fielddesc:I2CREFALWAYSON}\item [I2C\_REF\_ALWAYS\_ON] This register is used to control the REF\_TICK. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_TO\_REG}{\hexprefix{}000C}\label{regdesc:I2CTOREG}
\regfield{(reserved)}{7}{25}{0000000}%
\regfield{I2C\_TIME\_OUT\_EN}{1}{24}{{0}}%
\regfield{I2C\_TIME\_OUT\_VALUE}{24}{0}{{\hexprefix{}0000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CTIMEOUTVALUE}\item [I2C\_TIME\_OUT\_VALUE] This register is used to configure the timeout for receiving a data bit in APB clock cycles. (R/W)
\label{fielddesc:I2CTIMEOUTEN}\item [I2C\_TIME\_OUT\_EN] This is the enable bit for time out control. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_SLAVE\_ADDR\_REG}{\hexprefix{}0010}\label{regdesc:I2CSLAVEADDRREG}
\regfield{I2C\_ADDR\_10BIT\_EN}{1}{31}{{0}}%
\regfield{(reserved)}{16}{15}{0000000000000000}%
\regfield{I2C\_SLAVE\_ADDR}{15}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CSLAVEADDR}\item [I2C\_SLAVE\_ADDR] When configured as an I2C Slave, this field is used to configure the slave address. (R/W)
\label{fielddesc:I2CADDR10BITEN}\item [I2C\_ADDR\_10BIT\_EN] This field is used to enable the slave 10-bit addressing mode in master mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_FIFO\_CONF\_REG}{\hexprefix{}0018}\label{regdesc:I2CFIFOCONFREG}
\regfield{(reserved)}{5}{27}{00000}%
\regfield{I2C\_FIFO\_PRT\_EN}{1}{26}{{1}}%
\regfield{I2C\_NONFIFO\_TX\_THRES}{6}{20}{{\hexprefix{}15}}%
\regfield{I2C\_NONFIFO\_RX\_THRES}{6}{14}{{\hexprefix{}15}}%
\regfield{I2C\_TX\_FIFO\_RST}{1}{13}{{0}}%
\regfield{I2C\_RX\_FIFO\_RST}{1}{12}{{0}}%
\regfield{I2C\_FIFO\_ADDR\_CFG\_EN}{1}{11}{{0}}%
\regfield{I2C\_NONFIFO\_EN}{1}{10}{{0}}%
\regfield{I2C\_TXFIFO\_WM\_THRHD}{5}{5}{{\hexprefix{}4}}%
\regfield{I2C\_RXFIFO\_WM\_THRHD}{5}{0}{{\hexprefix{}b}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CRXFIFOWMTHRHD}\item [I2C\_RXFIFO\_WM\_THRHD] The water mark threshold of RX FIFO in non-FIFO mode. When I2C\_FIFO\_PRT\_EN is 1 and RX FIFO counter is bigger than I2C\_RXFIFO\_WM\_THRHD[4:0], I2C\_RXFIFO\_WM\_INT\_RAW bit will be valid. (R/W)
\label{fielddesc:I2CTXFIFOWMTHRHD}\item [I2C\_TXFIFO\_WM\_THRHD] The water mark threshold of TX FIFO in non-FIFO mode. When I2C\_FIFO\_PRT\_EN is 1 and TX FIFO counter is smaller than I2C\_TXFIFO\_WM\_THRHD[4:0], I2C\_TXFIFO\_WM\_INT\_RAW bit will be valid. (R/W)
\label{fielddesc:I2CNONFIFOEN}\item [I2C\_NONFIFO\_EN] Set this bit to enable APB non-FIFO mode. (R/W)
\label{fielddesc:I2CFIFOADDRCFGEN}\item [I2C\_FIFO\_ADDR\_CFG\_EN] When this bit is set to 1, the byte received after the I2C address byte represents the offset address in the I2C Slave RAM. (R/W)
\label{fielddesc:I2CRXFIFORST}\item [I2C\_RX\_FIFO\_RST] Set this bit to reset RX FIFO. (R/W)
\label{fielddesc:I2CTXFIFORST}\item [I2C\_TX\_FIFO\_RST] Set this bit to reset TX FIFO. (R/W)
\label{fielddesc:I2CNONFIFORXTHRES}\item [I2C\_NONFIFO\_RX\_THRES] When I2C receives more than I2C\_NONFIFO\_RX\_THRES bytes of data, it will generate an I2C\_RXFIFO\_UDF\_INT interrupt and update the current offset address of the received data. (R/W)
\label{fielddesc:I2CNONFIFOTXTHRES}\item [I2C\_NONFIFO\_TX\_THRES] When I2C sends more than I2C\_NONFIFO\_TX\_THRES bytes of data, it will generate
an I2C\_TXFIFO\_OVF\_INT interrupt and update the current offset address of the sent data. (R/W)
\label{fielddesc:I2CFIFOPRTEN}\item [I2C\_FIFO\_PRT\_EN] The control enable bit of FIFO pointer in non-FIFO mode. This bit controls the valid bits and the interrupts of TX/RX FIFO overflow, underflow, full and empty. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_SCL\_SP\_CONF\_REG}{\hexprefix{}00A0}\label{regdesc:I2CSCLSPCONFREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{I2C\_SDA\_PD\_EN}{1}{7}{{0}}%
\regfield{I2C\_SCL\_PD\_EN}{1}{6}{{0}}%
\regfield{I2C\_SCL\_RST\_SLV\_NUM}{5}{1}{{\hexprefix{}0}}%
\regfield{I2C\_SCL\_RST\_SLV\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CSCLRSTSLVEN}\item [I2C\_SCL\_RST\_SLV\_EN] When I2C master is IDLE, set this bit to send out SCL pulses. The number of pulses equals to I2C\_SCL\_RST\_SLV\_NUM[4:0]. (R/W)
\label{fielddesc:I2CSCLRSTSLVNUM}\item [I2C\_SCL\_RST\_SLV\_NUM] Configure the pulses of SCL generated in I2C master mode. Valid when I2C\_SCL\_RST\_SLV\_EN is 1. (R/W)
\label{fielddesc:I2CSCLPDEN}\item [I2C\_SCL\_PD\_EN] The power down enable bit for the I2C output SCL line. 1: Power down. 0: Not power down. Set I2C\_SCL\_FORCE\_OUT and I2C\_SCL\_PD\_EN to 1 to stretch SCL low. (R/W)
\label{fielddesc:I2CSDAPDEN}\item [I2C\_SDA\_PD\_EN] The power down enable bit for the I2C output SDA line. 1: Power down. 0: Not power down. Set I2C\_SDA\_FORCE\_OUT and I2C\_SDA\_PD\_EN to 1 to stretch SDA low. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_SCL\_STRETCH\_CONF\_REG}{\hexprefix{}00A4}\label{regdesc:I2CSCLSTRETCHCONFREG}
\regfield{(reserved)}{20}{12}{00000000000000000000}%
\regfield{I2C\_SLAVE\_SCL\_STRETCH\_CLR}{1}{11}{{0}}%
\regfield{I2C\_SLAVE\_SCL\_STRETCH\_EN}{1}{10}{{0}}%
\regfield{I2C\_STRETCH\_PROTECT\_NUM}{10}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CSTRETCHPROTECTNUM}\item [I2C\_STRETCH\_PROTECT\_NUM] Configure the period of I2C slave stretching SCL line. (R/W)
\label{fielddesc:I2CSLAVESCLSTRETCHEN}\item [I2C\_SLAVE\_SCL\_STRETCH\_EN] The enable bit for slave SCL stretch function. 1: Enable. 0: Disable. The SCL output line will be stretched low when I2C\_SLAVE\_SCL\_STRETCH\_EN is 1 and stretch event happens. The stretch cause can be seen in I2C\_STRETCH\_CAUSE. (R/W)
\label{fielddesc:I2CSLAVESCLSTRETCHCLR}\item [I2C\_SLAVE\_SCL\_STRETCH\_CLR] Set this bit to clear the I2C slave SCL stretch function. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_SR\_REG}{\hexprefix{}0008}\label{regdesc:I2CSRREG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{I2C\_SCL\_STATE\_LAST}{3}{28}{{\hexprefix{}0}}%
\regfield{(reserved)}{1}{27}{0}%
\regfield{I2C\_SCL\_MAIN\_STATE\_LAST}{3}{24}{{\hexprefix{}0}}%
\regfield{I2C\_TXFIFO\_CNT}{6}{18}{{\hexprefix{}0}}%
\regfield{(reserved)}{2}{16}{00}%
\regfield{I2C\_STRETCH\_CAUSE}{2}{14}{{\hexprefix{}0}}%
\regfield{I2C\_RXFIFO\_CNT}{6}{8}{{\hexprefix{}0}}%
\regfield{(reserved)}{1}{7}{0}%
\regfield{I2C\_BYTE\_TRANS}{1}{6}{{0}}%
\regfield{I2C\_SLAVE\_ADDRESSED}{1}{5}{{0}}%
\regfield{I2C\_BUS\_BUSY}{1}{4}{{0}}%
\regfield{I2C\_ARB\_LOST}{1}{3}{{0}}%
\regfield{I2C\_TIME\_OUT}{1}{2}{{0}}%
\regfield{I2C\_SLAVE\_RW}{1}{1}{{0}}%
\regfield{I2C\_RESP\_REC}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CRESPREC}\item [I2C\_RESP\_REC] The received ACK value in master mode or slave mode. 0: ACK; 1: NACK. (RO)
\label{fielddesc:I2CSLAVERW}\item [I2C\_SLAVE\_RW] When in slave mode, 1: master reads from slave; 0: master writes to slave. (RO)
\label{fielddesc:I2CTIMEOUT}\item [I2C\_TIME\_OUT] When the I2C controller takes more than I2C\_TIME\_OUT clocks to receive a data bit,
this field changes to 1. (RO)
\label{fielddesc:I2CARBLOST}\item [I2C\_ARB\_LOST] When the I2C controller loses control of SCL line, this register changes to 1. (RO)
\label{fielddesc:I2CBUSBUSY}\item [I2C\_BUS\_BUSY] 1: the I2C bus is busy transferring data; 0: the I2C bus is in idle state. (RO)
\label{fielddesc:I2CSLAVEADDRESSED}\item [I2C\_SLAVE\_ADDRESSED] When configured as an I2C Slave, and the address sent by the master is
equal to the address of the slave, then this bit will be of high level. (RO)
\label{fielddesc:I2CBYTETRANS}\item [I2C\_BYTE\_TRANS] This field changes to 1 when one byte is transferred. (RO)
\label{fielddesc:I2CRXFIFOCNT}\item [I2C\_RXFIFO\_CNT] This field represents the amount of data needed to be sent. (RO)
\label{fielddesc:I2CSTRETCHCAUSE}\item [I2C\_STRETCH\_CAUSE] The cause of stretching SCL low in slave mode. 0:  stretching SCL low at the beginning of I2C read data state. 1: stretching SCL low when I2C TX FIFO is empty in slave mode. 2: stretching SCL low when I2C RX FIFO is full in slave mode. (RO)
\label{fielddesc:I2CTXFIFOCNT}\item [I2C\_TXFIFO\_CNT] This field stores the amount of received data in RAM. (RO)
\label{fielddesc:I2CSCLMAINSTATELAST}\item [I2C\_SCL\_MAIN\_STATE\_LAST] This field indicates the states of the I2C module state machine.
0: Idle; 1: Address shift; 2: ACK address; 3: RX data; 4: TX data; 5: Send ACK; 6: Wait ACK. (RO)
\label{fielddesc:I2CSCLSTATELAST}\item [I2C\_SCL\_STATE\_LAST] This field indicates the states of the state machine used to produce SCL.
0: Idle; 1: Start; 2: Negative edge; 3: Low; 4: Positive edge; 5: High; 6: Stop. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_FIFO\_ST\_REG}{\hexprefix{}0014}\label{regdesc:I2CFIFOSTREG}
\regfield{(reserved)}{2}{30}{00}%
\regfield{I2C\_SLAVE\_RW\_POINT}{8}{22}{{\hexprefix{}0}}%
\regfield{I2C\_TX\_UPDATE}{1}{21}{{0}}%
\regfield{I2C\_RX\_UPDATE}{1}{20}{{0}}%
\regfield{I2C\_TXFIFO\_END\_ADDR}{5}{15}{{\hexprefix{}0}}%
\regfield{I2C\_TXFIFO\_START\_ADDR}{5}{10}{{\hexprefix{}0}}%
\regfield{I2C\_RXFIFO\_END\_ADDR}{5}{5}{{\hexprefix{}0}}%
\regfield{I2C\_RXFIFO\_START\_ADDR}{5}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CRXFIFOSTARTADDR}\item [I2C\_RXFIFO\_START\_ADDR] This is the offset address of the last received data, as described in I2C\_NONFIFO\_RX\_THRES. (RO)
\label{fielddesc:I2CRXFIFOENDADDR}\item [I2C\_RXFIFO\_END\_ADDR] This is the offset address of the last received data, as described in I2C\_NONFIFO\_RX\_THRES. This value refreshes when an I2C\_RXFIFO\_UDF\_INT or I2C\_TRANS\_COMPLETE\_INT interrupt is generated. (RO)
\label{fielddesc:I2CTXFIFOSTARTADDR}\item [I2C\_TXFIFO\_START\_ADDR] This is the offset address of the first sent data, as described in I2C\_NONFIFO\_TX\_THRES. (RO)
\label{fielddesc:I2CTXFIFOENDADDR}\item [I2C\_TXFIFO\_END\_ADDR] This is the offset address of the last sent data, as described in  I2C\_NONFIFO\_TX\_THRES.
The value refreshes when an I2C\_TXFIFO\_OVF\_INT or I2C\_TRANS\_COMPLETE\_INT interrupt is generated. (RO)
\label{fielddesc:I2CRXUPDATE}\item [I2C\_RX\_UPDATE] Write 0 or 1 to I2C\_RX\_UPDATE to update the value of I2C\_RXFIFO\_END\_ADDR and I2C\_RXFIFO\_START\_ADDR. (WO)
\label{fielddesc:I2CTXUPDATE}\item [I2C\_TX\_UPDATE] Write 0 or 1 to I2C\_TX\_UPDATE to update the value of I2C\_TXFIFO\_END\_ADDR and I2C\_TXFIFO\_START\_ADDR. (WO)
\label{fielddesc:I2CSLAVERWPOINT}\item [I2C\_SLAVE\_RW\_POINT] The received data in I2C slave mode. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_DATA\_REG}{\hexprefix{}001C}\label{regdesc:I2CDATAREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{I2C\_FIFO\_RDATA}{8}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CFIFORDATA}\item [I2C\_FIFO\_RDATA] This field is used to read data from RX FIFO, or write data to TX FIFO. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_INT\_RAW\_REG}{\hexprefix{}0020}\label{regdesc:I2CINTRAWREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{I2C\_SLAVE\_STRETCH\_INT\_RAW}{1}{16}{{0}}%
\regfield{I2C\_DET\_START\_INT\_RAW}{1}{15}{{0}}%
\regfield{I2C\_SCL\_MAIN\_ST\_TO\_INT\_RAW}{1}{14}{{0}}%
\regfield{I2C\_SCL\_ST\_TO\_INT\_RAW}{1}{13}{{0}}%
\regfield{I2C\_RXFIFO\_UDF\_INT\_RAW}{1}{12}{{0}}%
\regfield{I2C\_TXFIFO\_OVF\_INT\_RAW}{1}{11}{{0}}%
\regfield{I2C\_NACK\_INT\_RAW}{1}{10}{{0}}%
\regfield{I2C\_TRANS\_START\_INT\_RAW}{1}{9}{{0}}%
\regfield{I2C\_TIME\_OUT\_INT\_RAW}{1}{8}{{0}}%
\regfield{I2C\_TRANS\_COMPLETE\_INT\_RAW}{1}{7}{{0}}%
\regfield{I2C\_MST\_TXFIFO\_UDF\_INT\_RAW}{1}{6}{{0}}%
\regfield{I2C\_ARBITRATION\_LOST\_INT\_RAW}{1}{5}{{0}}%
\regfield{I2C\_BYTE\_TRANS\_DONE\_INT\_RAW}{1}{4}{{0}}%
\regfield{I2C\_END\_DETECT\_INT\_RAW}{1}{3}{{0}}%
\regfield{I2C\_RXFIFO\_OVF\_INT\_RAW}{1}{2}{{0}}%
\regfield{I2C\_TXFIFO\_WM\_INT\_RAW}{1}{1}{{0}}%
\regfield{I2C\_RXFIFO\_WM\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CRXFIFOWMINTRAW}\item [I2C\_RXFIFO\_WM\_INT\_RAW] The raw interrupt bit for I2C\_RXFIFO\_WM\_INT interrupt. (RO)
\label{fielddesc:I2CTXFIFOWMINTRAW}\item [I2C\_TXFIFO\_WM\_INT\_RAW] The raw interrupt bit for I2C\_TXFIFO\_WM\_INT interrupt. (RO)
\label{fielddesc:I2CRXFIFOOVFINTRAW}\item [I2C\_RXFIFO\_OVF\_INT\_RAW] The raw interrupt bit for I2C\_RXFIFO\_OVF\_INT interrupt. (RO)
\label{fielddesc:I2CENDDETECTINTRAW}\item [I2C\_END\_DETECT\_INT\_RAW] The raw interrupt bit for the I2C\_END\_DETECT\_INT interrupt. (RO)
\label{fielddesc:I2CBYTETRANSDONEINTRAW}\item [I2C\_BYTE\_TRANS\_DONE\_INT\_RAW] The raw interrupt bit for the I2C\_BYTE\_TRANS\_DONE\_INT interrupt. (RO)
\label{fielddesc:I2CARBITRATIONLOSTINTRAW}\item [I2C\_ARBITRATION\_LOST\_INT\_RAW] The raw interrupt bit for the I2C\_ARBITRATION\_LOST\_INT interrupt. (RO)
\label{fielddesc:I2CMSTTXFIFOUDFINTRAW}\item [I2C\_MST\_TXFIFO\_UDF\_INT\_RAW] The raw interrupt bit for I2C\_MST\_TXFIFO\_UDF\_INT interrupt. (RO)
\label{fielddesc:I2CTRANSCOMPLETEINTRAW}\item [I2C\_TRANS\_COMPLETE\_INT\_RAW] The raw interrupt bit for the I2C\_TRANS\_COMPLETE\_INT interrupt. (RO)
\label{fielddesc:I2CTIMEOUTINTRAW}\item [I2C\_TIME\_OUT\_INT\_RAW] The raw interrupt bit for the I2C\_TIME\_OUT\_INT interrupt. (RO)
\label{fielddesc:I2CTRANSSTARTINTRAW}\item [I2C\_TRANS\_START\_INT\_RAW] The raw interrupt bit for the I2C\_TRANS\_START\_INT interrupt. (RO)
\label{fielddesc:I2CNACKINTRAW}\item [I2C\_NACK\_INT\_RAW] The raw interrupt bit for I2C\_NACK\_INT interrupt. (RO)
\label{fielddesc:I2CTXFIFOOVFINTRAW}\item [I2C\_TXFIFO\_OVF\_INT\_RAW] The raw interrupt bit for I2C\_TXFIFO\_OVF\_INT interrupt. (RO)
\label{fielddesc:I2CRXFIFOUDFINTRAW}\item [I2C\_RXFIFO\_UDF\_INT\_RAW] The raw interrupt bit for I2C\_RXFIFO\_UDF\_INT  interrupt. (RO)
\label{fielddesc:I2CSCLSTTOINTRAW}\item [I2C\_SCL\_ST\_TO\_INT\_RAW] The raw interrupt bit for I2C\_SCL\_ST\_TO\_INT interrupt. (RO)
\label{fielddesc:I2CSCLMAINSTTOINTRAW}\item [I2C\_SCL\_MAIN\_ST\_TO\_INT\_RAW] The raw interrupt bit for I2C\_SCL\_MAIN\_ST\_TO\_INT interrupt. (RO)
\label{fielddesc:I2CDETSTARTINTRAW}\item [I2C\_DET\_START\_INT\_RAW] The raw interrupt bit for I2C\_DET\_START\_INT interrupt. (RO)
\label{fielddesc:I2CSLAVESTRETCHINTRAW}\item [I2C\_SLAVE\_STRETCH\_INT\_RAW] The raw interrupt bit for I2C\_SLAVE\_STRETCH\_INT interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_INT\_CLR\_REG}{\hexprefix{}0024}\label{regdesc:I2CINTCLRREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{I2C\_SLAVE\_STRETCH\_INT\_CLR}{1}{16}{{0}}%
\regfield{I2C\_DET\_START\_INT\_CLR}{1}{15}{{0}}%
\regfield{I2C\_SCL\_MAIN\_ST\_TO\_INT\_CLR}{1}{14}{{0}}%
\regfield{I2C\_SCL\_ST\_TO\_INT\_CLR}{1}{13}{{0}}%
\regfield{I2C\_RXFIFO\_UDF\_INT\_CLR}{1}{12}{{0}}%
\regfield{I2C\_TXFIFO\_OVF\_INT\_CLR}{1}{11}{{0}}%
\regfield{I2C\_NACK\_INT\_CLR}{1}{10}{{0}}%
\regfield{I2C\_TRANS\_START\_INT\_CLR}{1}{9}{{0}}%
\regfield{I2C\_TIME\_OUT\_INT\_CLR}{1}{8}{{0}}%
\regfield{I2C\_TRANS\_COMPLETE\_INT\_CLR}{1}{7}{{0}}%
\regfield{I2C\_MST\_TXFIFO\_UDF\_INT\_CLR}{1}{6}{{0}}%
\regfield{I2C\_ARBITRATION\_LOST\_INT\_CLR}{1}{5}{{0}}%
\regfield{I2C\_BYTE\_TRANS\_DONE\_INT\_CLR}{1}{4}{{0}}%
\regfield{I2C\_END\_DETECT\_INT\_CLR}{1}{3}{{0}}%
\regfield{I2C\_RXFIFO\_OVF\_INT\_CLR}{1}{2}{{0}}%
\regfield{I2C\_TXFIFO\_WM\_INT\_CLR}{1}{1}{{0}}%
\regfield{I2C\_RXFIFO\_WM\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CRXFIFOWMINTCLR}\item [I2C\_RXFIFO\_WM\_INT\_CLR] Set this bit to clear I2C\_RXFIFO\_WM\_INT interrupt. (WO)
\label{fielddesc:I2CTXFIFOWMINTCLR}\item [I2C\_TXFIFO\_WM\_INT\_CLR] Set this bit to clear I2C\_TXFIFO\_WM\_INT interrupt. (WO)
\label{fielddesc:I2CRXFIFOOVFINTCLR}\item [I2C\_RXFIFO\_OVF\_INT\_CLR] Set this bit to clear I2C\_RXFIFO\_OVF\_INT interrupt. (WO)
\label{fielddesc:I2CENDDETECTINTCLR}\item [I2C\_END\_DETECT\_INT\_CLR] Set this bit to clear the I2C\_END\_DETECT\_INT interrupt. (WO)
\label{fielddesc:I2CBYTETRANSDONEINTCLR}\item [I2C\_BYTE\_TRANS\_DONE\_INT\_CLR] Set this bit to clear the I2C\_BYTE\_TRANS\_DONE\_INT interrupt. (WO)
\label{fielddesc:I2CARBITRATIONLOSTINTCLR}\item [I2C\_ARBITRATION\_LOST\_INT\_CLR] Set this bit to clear the I2C\_ARBITRATION\_LOST\_INT interrupt. (WO)
\label{fielddesc:I2CMSTTXFIFOUDFINTCLR}\item [I2C\_MST\_TXFIFO\_UDF\_INT\_CLR] Set this bit to clear I2C\_MST\_TXFIFO\_UDF\_INT interrupt. (WO)
\label{fielddesc:I2CTRANSCOMPLETEINTCLR}\item [I2C\_TRANS\_COMPLETE\_INT\_CLR] Set this bit to clear the I2C\_TRANS\_COMPLETE\_INT interrupt. (WO)
\label{fielddesc:I2CTIMEOUTINTCLR}\item [I2C\_TIME\_OUT\_INT\_CLR] Set this bit to clear the I2C\_TIME\_OUT\_INT interrupt. (WO)
\label{fielddesc:I2CTRANSSTARTINTCLR}\item [I2C\_TRANS\_START\_INT\_CLR] Set this bit to clear the I2C\_TRANS\_START\_INT interrupt. (WO)
\label{fielddesc:I2CNACKINTCLR}\item [I2C\_NACK\_INT\_CLR] Set this bit to clear I2C\_NACK\_INT interrupt. (WO)
\label{fielddesc:I2CTXFIFOOVFINTCLR}\item [I2C\_TXFIFO\_OVF\_INT\_CLR] Set this bit to clear I2C\_TXFIFO\_OVF\_INT interrupt. (WO)
\label{fielddesc:I2CRXFIFOUDFINTCLR}\item [I2C\_RXFIFO\_UDF\_INT\_CLR] Set this bit to clear I2C\_RXFIFO\_UDF\_INT  interrupt. (WO)
\label{fielddesc:I2CSCLSTTOINTCLR}\item [I2C\_SCL\_ST\_TO\_INT\_CLR] Set this bit to clear I2C\_SCL\_ST\_TO\_INT interrupt. (WO)
\label{fielddesc:I2CSCLMAINSTTOINTCLR}\item [I2C\_SCL\_MAIN\_ST\_TO\_INT\_CLR] Set this bit to clear I2C\_SCL\_MAIN\_ST\_TO\_INT interrupt. (WO)
\label{fielddesc:I2CDETSTARTINTCLR}\item [I2C\_DET\_START\_INT\_CLR] Set this bit to clear I2C\_DET\_START\_INT interrupt. (WO)
\label{fielddesc:I2CSLAVESTRETCHINTCLR}\item [I2C\_SLAVE\_STRETCH\_INT\_CLR] Set this bit to clear I2C\_SLAVE\_STRETCH\_INT interrupt. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_INT\_ENA\_REG}{\hexprefix{}0028}\label{regdesc:I2CINTENAREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{I2C\_SLAVE\_STRETCH\_INT\_ENA}{1}{16}{{0}}%
\regfield{I2C\_DET\_START\_INT\_ENA}{1}{15}{{0}}%
\regfield{I2C\_SCL\_MAIN\_ST\_TO\_INT\_ENA}{1}{14}{{0}}%
\regfield{I2C\_SCL\_ST\_TO\_INT\_ENA}{1}{13}{{0}}%
\regfield{I2C\_RXFIFO\_UDF\_INT\_ENA}{1}{12}{{0}}%
\regfield{I2C\_TXFIFO\_OVF\_INT\_ENA}{1}{11}{{0}}%
\regfield{I2C\_NACK\_INT\_ENA}{1}{10}{{0}}%
\regfield{I2C\_TRANS\_START\_INT\_ENA}{1}{9}{{0}}%
\regfield{I2C\_TIME\_OUT\_INT\_ENA}{1}{8}{{0}}%
\regfield{I2C\_TRANS\_COMPLETE\_INT\_ENA}{1}{7}{{0}}%
\regfield{I2C\_MST\_TXFIFO\_UDF\_INT\_ENA}{1}{6}{{0}}%
\regfield{I2C\_ARBITRATION\_LOST\_INT\_ENA}{1}{5}{{0}}%
\regfield{I2C\_BYTE\_TRANS\_DONE\_INT\_ENA}{1}{4}{{0}}%
\regfield{I2C\_END\_DETECT\_INT\_ENA}{1}{3}{{0}}%
\regfield{I2C\_RXFIFO\_OVF\_INT\_ENA}{1}{2}{{0}}%
\regfield{I2C\_TXFIFO\_WM\_INT\_ENA}{1}{1}{{0}}%
\regfield{I2C\_RXFIFO\_WM\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CRXFIFOWMINTENA}\item [I2C\_RXFIFO\_WM\_INT\_ENA] The raw interrupt bit for I2C\_RXFIFO\_WM\_INT interrupt. (R/W)
\label{fielddesc:I2CTXFIFOWMINTENA}\item [I2C\_TXFIFO\_WM\_INT\_ENA] The raw interrupt bit for I2C\_TXFIFO\_WM\_INT interrupt. (R/W)
\label{fielddesc:I2CRXFIFOOVFINTENA}\item [I2C\_RXFIFO\_OVF\_INT\_ENA] The raw interrupt bit for I2C\_RXFIFO\_OVF\_INT interrupt. (R/W)
\label{fielddesc:I2CENDDETECTINTENA}\item [I2C\_END\_DETECT\_INT\_ENA] The raw interrupt bit for the I2C\_END\_DETECT\_INT interrupt. (R/W)
\label{fielddesc:I2CBYTETRANSDONEINTENA}\item [I2C\_BYTE\_TRANS\_DONE\_INT\_ENA] The raw interrupt bit for the I2C\_BYTE\_TRANS\_DONE\_INT interrupt. (R/W)
\label{fielddesc:I2CARBITRATIONLOSTINTENA}\item [I2C\_ARBITRATION\_LOST\_INT\_ENA] The raw interrupt bit for the I2C\_ARBITRATION\_LOST\_INT interrupt. (R/W)
\label{fielddesc:I2CMSTTXFIFOUDFINTENA}\item [I2C\_MST\_TXFIFO\_UDF\_INT\_ENA] The raw interrupt bit for I2C\_MST\_TXFIFO\_UDF\_INT interrupt. (R/W)
\label{fielddesc:I2CTRANSCOMPLETEINTENA}\item [I2C\_TRANS\_COMPLETE\_INT\_ENA] The raw interrupt bit for the I2C\_TRANS\_COMPLETE\_INT interrupt. (R/W)
\label{fielddesc:I2CTIMEOUTINTENA}\item [I2C\_TIME\_OUT\_INT\_ENA] The raw interrupt bit for the I2C\_TIME\_OUT\_INT interrupt. (R/W)
\label{fielddesc:I2CTRANSSTARTINTENA}\item [I2C\_TRANS\_START\_INT\_ENA] The raw interrupt bit for the I2C\_TRANS\_START\_INT interrupt. (R/W)
\label{fielddesc:I2CNACKINTENA}\item [I2C\_NACK\_INT\_ENA] The raw interrupt bit for I2C\_NACK\_INT interrupt. (R/W)
\label{fielddesc:I2CTXFIFOOVFINTENA}\item [I2C\_TXFIFO\_OVF\_INT\_ENA] The raw interrupt bit for I2C\_TXFIFO\_OVF\_INT interrupt. (R/W)
\label{fielddesc:I2CRXFIFOUDFINTENA}\item [I2C\_RXFIFO\_UDF\_INT\_ENA] The raw interrupt bit for I2C\_RXFIFO\_UDF\_INT  interrupt. (R/W)
\label{fielddesc:I2CSCLSTTOINTENA}\item [I2C\_SCL\_ST\_TO\_INT\_ENA] The raw interrupt bit for I2C\_SCL\_ST\_TO\_INT interrupt. (R/W)
\label{fielddesc:I2CSCLMAINSTTOINTENA}\item [I2C\_SCL\_MAIN\_ST\_TO\_INT\_ENA] The raw interrupt bit for I2C\_SCL\_MAIN\_ST\_TO\_INT interrupt. (R/W)
\label{fielddesc:I2CDETSTARTINTENA}\item [I2C\_DET\_START\_INT\_ENA] The raw interrupt bit for I2C\_DET\_START\_INT interrupt. (R/W)
\label{fielddesc:I2CSLAVESTRETCHINTENA}\item [I2C\_SLAVE\_STRETCH\_INT\_ENA] The raw interrupt bit for I2C\_SLAVE\_STRETCH\_INT interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_INT\_STATUS\_REG}{\hexprefix{}002C}\label{regdesc:I2CINTSTATUSREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{I2C\_SLAVE\_STRETCH\_INT\_ST}{1}{16}{{0}}%
\regfield{I2C\_DET\_START\_INT\_ST}{1}{15}{{0}}%
\regfield{I2C\_SCL\_MAIN\_ST\_TO\_INT\_ST}{1}{14}{{0}}%
\regfield{I2C\_SCL\_ST\_TO\_INT\_ST}{1}{13}{{0}}%
\regfield{I2C\_RXFIFO\_UDF\_INT\_ST}{1}{12}{{0}}%
\regfield{I2C\_TXFIFO\_OVF\_INT\_ST}{1}{11}{{0}}%
\regfield{I2C\_NACK\_INT\_ST}{1}{10}{{0}}%
\regfield{I2C\_TRANS\_START\_INT\_ST}{1}{9}{{0}}%
\regfield{I2C\_TIME\_OUT\_INT\_ST}{1}{8}{{0}}%
\regfield{I2C\_TRANS\_COMPLETE\_INT\_ST}{1}{7}{{0}}%
\regfield{I2C\_MST\_TXFIFO\_UDF\_INT\_ST}{1}{6}{{0}}%
\regfield{I2C\_ARBITRATION\_LOST\_INT\_ST}{1}{5}{{0}}%
\regfield{I2C\_BYTE\_TRANS\_DONE\_INT\_ST}{1}{4}{{0}}%
\regfield{I2C\_END\_DETECT\_INT\_ST}{1}{3}{{0}}%
\regfield{I2C\_RXFIFO\_OVF\_INT\_ST}{1}{2}{{0}}%
\regfield{I2C\_TXFIFO\_WM\_INT\_ST}{1}{1}{{0}}%
\regfield{I2C\_RXFIFO\_WM\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CRXFIFOWMINTST}\item [I2C\_RXFIFO\_WM\_INT\_ST] The masked interrupt status bit for I2C\_RXFIFO\_WM\_INT interrupt. (RO)
\label{fielddesc:I2CTXFIFOWMINTST}\item [I2C\_TXFIFO\_WM\_INT\_ST] The masked interrupt status bit for I2C\_TXFIFO\_WM\_INT interrupt. (RO)
\label{fielddesc:I2CRXFIFOOVFINTST}\item [I2C\_RXFIFO\_OVF\_INT\_ST] The masked interrupt status bit for I2C\_RXFIFO\_OVF\_INT interrupt. (RO)
\label{fielddesc:I2CENDDETECTINTST}\item [I2C\_END\_DETECT\_INT\_ST] The masked interrupt status bit for the I2C\_END\_DETECT\_INT interrupt. (RO)
\label{fielddesc:I2CBYTETRANSDONEINTST}\item [I2C\_BYTE\_TRANS\_DONE\_INT\_ST] The masked interrupt status bit for the I2C\_BYTE\_TRANS\_DONE\_INT interrupt. (RO)
\label{fielddesc:I2CARBITRATIONLOSTINTST}\item [I2C\_ARBITRATION\_LOST\_INT\_ST] The masked interrupt status bit for the I2C\_ARBITRATION\_LOST\_INT interrupt. (RO)
\label{fielddesc:I2CMSTTXFIFOUDFINTST}\item [I2C\_MST\_TXFIFO\_UDF\_INT\_ST] The masked interrupt status bit for I2C\_MST\_TXFIFO\_UDF\_INT interrupt. (RO)
\label{fielddesc:I2CTRANSCOMPLETEINTST}\item [I2C\_TRANS\_COMPLETE\_INT\_ST] The masked interrupt status bit for the I2C\_TRANS\_COMPLETE\_INT interrupt. (RO)
\label{fielddesc:I2CTIMEOUTINTST}\item [I2C\_TIME\_OUT\_INT\_ST] The masked interrupt status bit for the I2C\_TIME\_OUT\_INT interrupt. (RO)
\label{fielddesc:I2CTRANSSTARTINTST}\item [I2C\_TRANS\_START\_INT\_ST] The masked interrupt status bit for the I2C\_TRANS\_START\_INT interrupt. (RO)
\label{fielddesc:I2CNACKINTST}\item [I2C\_NACK\_INT\_ST] The masked interrupt status bit for I2C\_NACK\_INT interrupt. (RO)
\label{fielddesc:I2CTXFIFOOVFINTST}\item [I2C\_TXFIFO\_OVF\_INT\_ST] The masked interrupt status bit for I2C\_TXFIFO\_OVF\_INT interrupt. (RO)
\label{fielddesc:I2CRXFIFOUDFINTST}\item [I2C\_RXFIFO\_UDF\_INT\_ST] The masked interrupt status bit for I2C\_RXFIFO\_UDF\_INT  interrupt. (RO)
\label{fielddesc:I2CSCLSTTOINTST}\item [I2C\_SCL\_ST\_TO\_INT\_ST] The masked interrupt status bit for I2C\_SCL\_ST\_TO\_INT interrupt. (RO)
\label{fielddesc:I2CSCLMAINSTTOINTST}\item [I2C\_SCL\_MAIN\_ST\_TO\_INT\_ST] The masked interrupt status bit for I2C\_SCL\_MAIN\_ST\_TO\_INT interrupt. (RO)
\label{fielddesc:I2CDETSTARTINTST}\item [I2C\_DET\_START\_INT\_ST] The masked interrupt status bit for I2C\_DET\_START\_INT interrupt. (RO)
\label{fielddesc:I2CSLAVESTRETCHINTST}\item [I2C\_SLAVE\_STRETCH\_INT\_ST] The masked interrupt status bit for I2C\_SLAVE\_STRETCH\_INT interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_SCL\_FILTER\_CFG\_REG}{\hexprefix{}0050}\label{regdesc:I2CSCLFILTERCFGREG}
\regfield{(reserved)}{27}{5}{000000000000000000000000000}%
\regfield{I2C\_SCL\_FILTER\_EN}{1}{4}{{1}}%
\regfield{I2C\_SCL\_FILTER\_THRES}{4}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CSCLFILTERTHRES}\item [I2C\_SCL\_FILTER\_THRES] When a pulse on the SCL input has smaller width than this register value in I2C module clock cycles, the I2C controller will ignore that pulse. (R/W)
\label{fielddesc:I2CSCLFILTEREN}\item [I2C\_SCL\_FILTER\_EN] This is the filter enable bit for SCL. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_SDA\_FILTER\_CFG\_REG}{\hexprefix{}0054}\label{regdesc:I2CSDAFILTERCFGREG}
\regfield{(reserved)}{27}{5}{000000000000000000000000000}%
\regfield{I2C\_SDA\_FILTER\_EN}{1}{4}{{1}}%
\regfield{I2C\_SDA\_FILTER\_THRES}{4}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CSDAFILTERTHRES}\item [I2C\_SDA\_FILTER\_THRES] When a pulse on the SDA input has smaller width than this register value in I2C module clock cycles, the I2C controller will ignore that pulse. (R/W)
\label{fielddesc:I2CSDAFILTEREN}\item [I2C\_SDA\_FILTER\_EN] This is the filter enable bit for SDA. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_COMD0\_REG}{\hexprefix{}0058}\label{regdesc:I2CCOMD0REG}
\regfield{I2C\_COMMAND0\_DONE}{1}{31}{{0}}%
\regfield{(reserved)}{17}{14}{00000000000000000}%
\regfield{I2C\_COMMAND0}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CCOMMAND0}\item [I2C\_COMMAND0] This is the content of command 0. It consists of three parts:
op\_code is the command, 0: RSTART; 1: WRITE; 2: READ; 3: STOP; 4: END.
byte\_num represents the number of bytes that need to be sent or received.
ack\_check\_en, ack\_exp and ack are used to control the ACK bit. See I2C cmd structure for more information. (R/W)
\label{fielddesc:I2CCOMMAND0DONE}\item [I2C\_COMMAND0\_DONE] When command 0 is done in I2C Master mode, this bit changes to high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_COMD1\_REG}{\hexprefix{}005C}\label{regdesc:I2CCOMD1REG}
\regfield{I2C\_COMMAND1\_DONE}{1}{31}{{0}}%
\regfield{(reserved)}{17}{14}{00000000000000000}%
\regfield{I2C\_COMMAND1}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CCOMMAND1}\item [I2C\_COMMAND1] This is the content of command 1. It consists of three parts:
op\_code is the command, 0: RSTART; 1: WRITE; 2: READ; 3: STOP; 4: END.
byte\_num represents the number of bytes that need to be sent or received.
ack\_check\_en, ack\_exp and ack are used to control the ACK bit. See I2C cmd structure for more information. (R/W)
\label{fielddesc:I2CCOMMAND1DONE}\item [I2C\_COMMAND1\_DONE] When command 1 is done in I2C Master mode, this bit changes to high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_COMD2\_REG}{\hexprefix{}0060}\label{regdesc:I2CCOMD2REG}
\regfield{I2C\_COMMAND2\_DONE}{1}{31}{{0}}%
\regfield{(reserved)}{17}{14}{00000000000000000}%
\regfield{I2C\_COMMAND2}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CCOMMAND2}\item [I2C\_COMMAND2] This is the content of command 2. It consists of three parts:
op\_code is the command, 0: RSTART; 1: WRITE; 2: READ; 3: STOP; 4: END.
byte\_num represents the number of bytes that need to be sent or received.
ack\_check\_en, ack\_exp and ack are used to control the ACK bit. See I2C cmd structure for more information. (R/W)
\label{fielddesc:I2CCOMMAND2DONE}\item [I2C\_COMMAND2\_DONE] When command 2 is done in I2C Master mode, this bit changes to high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_COMD3\_REG}{\hexprefix{}0064}\label{regdesc:I2CCOMD3REG}
\regfield{I2C\_COMMAND3\_DONE}{1}{31}{{0}}%
\regfield{(reserved)}{17}{14}{00000000000000000}%
\regfield{I2C\_COMMAND3}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CCOMMAND3}\item [I2C\_COMMAND3] This is the content of command 3. It consists of three parts:
op\_code is the command, 0: RSTART; 1: WRITE; 2: READ; 3: STOP; 4: END.
byte\_num represents the number of bytes that need to be sent or received.
ack\_check\_en, ack\_exp and ack are used to control the ACK bit. See I2C cmd structure for more information. (R/W)
\label{fielddesc:I2CCOMMAND3DONE}\item [I2C\_COMMAND3\_DONE] When command 3 is done in I2C Master mode, this bit changes to high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_COMD4\_REG}{\hexprefix{}0068}\label{regdesc:I2CCOMD4REG}
\regfield{I2C\_COMMAND4\_DONE}{1}{31}{{0}}%
\regfield{(reserved)}{17}{14}{00000000000000000}%
\regfield{I2C\_COMMAND4}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CCOMMAND4}\item [I2C\_COMMAND4] This is the content of command 4. It consists of three parts:
op\_code is the command, 0: RSTART; 1: WRITE; 2: READ; 3: STOP; 4: END.
byte\_num represents the number of bytes that need to be sent or received.
ack\_check\_en, ack\_exp and ack are used to control the ACK bit. See I2C cmd structure for more information. (R/W)
\label{fielddesc:I2CCOMMAND4DONE}\item [I2C\_COMMAND4\_DONE] When command 4 is done in I2C Master mode, this bit changes to high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_COMD5\_REG}{\hexprefix{}006C}\label{regdesc:I2CCOMD5REG}
\regfield{I2C\_COMMAND5\_DONE}{1}{31}{{0}}%
\regfield{(reserved)}{17}{14}{00000000000000000}%
\regfield{I2C\_COMMAND5}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CCOMMAND5}\item [I2C\_COMMAND5] This is the content of command 5. It consists of three parts:
op\_code is the command, 0: RSTART; 1: WRITE; 2: READ; 3: STOP; 4: END.
byte\_num represents the number of bytes that need to be sent or received.
ack\_check\_en, ack\_exp and ack are used to control the ACK bit. See I2C cmd structure for more information. (R/W)
\label{fielddesc:I2CCOMMAND5DONE}\item [I2C\_COMMAND5\_DONE] When command 5 is done in I2C Master mode, this bit changes to high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_COMD6\_REG}{\hexprefix{}0070}\label{regdesc:I2CCOMD6REG}
\regfield{I2C\_COMMAND6\_DONE}{1}{31}{{0}}%
\regfield{(reserved)}{17}{14}{00000000000000000}%
\regfield{I2C\_COMMAND6}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CCOMMAND6}\item [I2C\_COMMAND6] This is the content of command 6. It consists of three parts:
op\_code is the command, 0: RSTART; 1: WRITE; 2: READ; 3: STOP; 4: END.
byte\_num represents the number of bytes that need to be sent or received.
ack\_check\_en, ack\_exp and ack are used to control the ACK bit. See I2C cmd structure for more information. (R/W)
\label{fielddesc:I2CCOMMAND6DONE}\item [I2C\_COMMAND6\_DONE] When command 6 is done in I2C Master mode, this bit changes to high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_COMD7\_REG}{\hexprefix{}0074}\label{regdesc:I2CCOMD7REG}
\regfield{I2C\_COMMAND7\_DONE}{1}{31}{{0}}%
\regfield{(reserved)}{17}{14}{00000000000000000}%
\regfield{I2C\_COMMAND7}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CCOMMAND7}\item [I2C\_COMMAND7] This is the content of command 7. It consists of three parts:
op\_code is the command, 0: RSTART; 1: WRITE; 2: READ; 3: STOP; 4: END.
byte\_num represents the number of bytes that need to be sent or received.
ack\_check\_en, ack\_exp and ack are used to control the ACK bit. See I2C cmd structure for more information. (R/W)
\label{fielddesc:I2CCOMMAND7DONE}\item [I2C\_COMMAND7\_DONE] When command 7 is done in I2C Master mode, this bit changes to high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_COMD8\_REG}{\hexprefix{}0078}\label{regdesc:I2CCOMD8REG}
\regfield{I2C\_COMMAND8\_DONE}{1}{31}{{0}}%
\regfield{(reserved)}{17}{14}{00000000000000000}%
\regfield{I2C\_COMMAND8}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CCOMMAND8}\item [I2C\_COMMAND8] This is the content of command 8. It consists of three parts:
op\_code is the command, 0: RSTART; 1: WRITE; 2: READ; 3: STOP; 4: END.
byte\_num represents the number of bytes that need to be sent or received.
ack\_check\_en, ack\_exp and ack are used to control the ACK bit. See I2C cmd structure for more information. (R/W)
\label{fielddesc:I2CCOMMAND8DONE}\item [I2C\_COMMAND8\_DONE] When command 8 is done in I2C Master mode, this bit changes to high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_COMD9\_REG}{\hexprefix{}007C}\label{regdesc:I2CCOMD9REG}
\regfield{I2C\_COMMAND9\_DONE}{1}{31}{{0}}%
\regfield{(reserved)}{17}{14}{00000000000000000}%
\regfield{I2C\_COMMAND9}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CCOMMAND9}\item [I2C\_COMMAND9] This is the content of command 9. It consists of three parts:
op\_code is the command, 0: RSTART; 1: WRITE; 2: READ; 3: STOP; 4: END.
byte\_num represents the number of bytes that need to be sent or received.
ack\_check\_en, ack\_exp and ack are used to control the ACK bit. See I2C cmd structure for more information. (R/W)
\label{fielddesc:I2CCOMMAND9DONE}\item [I2C\_COMMAND9\_DONE] When command 9 is done in I2C Master mode, this bit changes to high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_COMD10\_REG}{\hexprefix{}0080}\label{regdesc:I2CCOMD10REG}
\regfield{I2C\_COMMAND10\_DONE}{1}{31}{{0}}%
\regfield{(reserved)}{17}{14}{00000000000000000}%
\regfield{I2C\_COMMAND10}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CCOMMAND10}\item [I2C\_COMMAND10] This is the content of command 10. It consists of three parts:
op\_code is the command, 0: RSTART; 1: WRITE; 2: READ; 3: STOP; 4: END.
byte\_num represents the number of bytes that need to be sent or received.
ack\_check\_en, ack\_exp and ack are used to control the ACK bit. See I2C cmd structure for more information. (R/W)
\label{fielddesc:I2CCOMMAND10DONE}\item [I2C\_COMMAND10\_DONE] When command 10 is done in I2C Master mode, this bit changes to high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_COMD11\_REG}{\hexprefix{}0084}\label{regdesc:I2CCOMD11REG}
\regfield{I2C\_COMMAND11\_DONE}{1}{31}{{0}}%
\regfield{(reserved)}{17}{14}{00000000000000000}%
\regfield{I2C\_COMMAND11}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CCOMMAND11}\item [I2C\_COMMAND11] This is the content of command 11. It consists of three parts:
op\_code is the command, 0: RSTART; 1: WRITE; 2: READ; 3: STOP; 4: END.
byte\_num represents the number of bytes that need to be sent or received.
ack\_check\_en, ack\_exp and ack are used to control the ACK bit. See I2C cmd structure for more information. (R/W)
\label{fielddesc:I2CCOMMAND11DONE}\item [I2C\_COMMAND11\_DONE] When command 11 is done in I2C Master mode, this bit changes to high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_COMD12\_REG}{\hexprefix{}0088}\label{regdesc:I2CCOMD12REG}
\regfield{I2C\_COMMAND12\_DONE}{1}{31}{{0}}%
\regfield{(reserved)}{17}{14}{00000000000000000}%
\regfield{I2C\_COMMAND12}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CCOMMAND12}\item [I2C\_COMMAND12] This is the content of command 12. It consists of three parts:
op\_code is the command, 0: RSTART; 1: WRITE; 2: READ; 3: STOP; 4: END.
byte\_num represents the number of bytes that need to be sent or received.
ack\_check\_en, ack\_exp and ack are used to control the ACK bit. See I2C cmd structure for more information. (R/W)
\label{fielddesc:I2CCOMMAND12DONE}\item [I2C\_COMMAND12\_DONE] When command 12 is done in I2C Master mode, this bit changes to high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_COMD13\_REG}{\hexprefix{}008C}\label{regdesc:I2CCOMD13REG}
\regfield{I2C\_COMMAND13\_DONE}{1}{31}{{0}}%
\regfield{(reserved)}{17}{14}{00000000000000000}%
\regfield{I2C\_COMMAND13}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CCOMMAND13}\item [I2C\_COMMAND13] This is the content of command 13. It consists of three parts:
op\_code is the command, 0: RSTART; 1: WRITE; 2: READ; 3: STOP; 4: END.
byte\_num represents the number of bytes that need to be sent or received.
ack\_check\_en, ack\_exp and ack are used to control the ACK bit. See I2C cmd structure for more information. (R/W)
\label{fielddesc:I2CCOMMAND13DONE}\item [I2C\_COMMAND13\_DONE] When command 13 is done in I2C Master mode, this bit changes to high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_COMD14\_REG}{\hexprefix{}0090}\label{regdesc:I2CCOMD14REG}
\regfield{I2C\_COMMAND14\_DONE}{1}{31}{{0}}%
\regfield{(reserved)}{17}{14}{00000000000000000}%
\regfield{I2C\_COMMAND14}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CCOMMAND14}\item [I2C\_COMMAND14] This is the content of command 14. It consists of three parts:
op\_code is the command, 0: RSTART; 1: WRITE; 2: READ; 3: STOP; 4: END.
byte\_num represents the number of bytes that need to be sent or received.
ack\_check\_en, ack\_exp and ack are used to control the ACK bit. See I2C cmd structure for more information. (R/W)
\label{fielddesc:I2CCOMMAND14DONE}\item [I2C\_COMMAND14\_DONE] When command 14 is done in I2C Master mode, this bit changes to high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_COMD15\_REG}{\hexprefix{}0094}\label{regdesc:I2CCOMD15REG}
\regfield{I2C\_COMMAND15\_DONE}{1}{31}{{0}}%
\regfield{(reserved)}{17}{14}{00000000000000000}%
\regfield{I2C\_COMMAND15}{14}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CCOMMAND15}\item [I2C\_COMMAND15] This is the content of command 15. It consists of three parts:
op\_code is the command, 0: RSTART; 1: WRITE; 2: READ; 3: STOP; 4: END.
byte\_num represents the number of bytes that need to be sent or received.
ack\_check\_en, ack\_exp and ack are used to control the ACK bit. See I2C cmd structure for more information. (R/W)
\label{fielddesc:I2CCOMMAND15DONE}\item [I2C\_COMMAND15\_DONE] When command 15 is done in I2C Master mode, this bit changes to high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2C\_DATE\_REG}{\hexprefix{}00F8}\label{regdesc:I2CDATEREG}
\regfield{I2C\_DATE}{32}{0}{{\hexprefix{}19052000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2CDATE}\item [I2C\_DATE] This is the the version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}
