\begin{register}{H}{GDMA\_IN\_CONF0\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0000+192*\regindex{n}}\label{regdesc:DMAINCONF0CHNREG}
\regfield{(reserved)}{27}{5}{000000000000000000000000000}%
\regfield{GDMA\_MEM\_TRANS\_EN\_CH0}{1}{4}{{0}}%
\regfield{GDMA\_IN\_DATA\_BURST\_EN\_CH0}{1}{3}{{0}}%
\regfield{GDMA\_INDSCR\_BURST\_EN\_CH0}{1}{2}{{0}}%
\regfield{GDMA\_IN\_LOOP\_TEST\_CH0}{1}{1}{{0}}%
\regfield{GDMA\_IN\_RST\_CH0}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAINRSTCHN}\item [GDMA\_IN\_RST\_CH\regindex{n}] This bit is used to reset GDMA channel 0 RX FSM and RX FIFO pointer. (R/W)
\label{fielddesc:DMAINLOOPTESTCHN}\item [GDMA\_IN\_LOOP\_TEST\_CH\regindex{n}] Reserved. (R/W)
\label{fielddesc:DMAINDSCRBURSTENCHN}\item [GDMA\_INDSCR\_BURST\_EN\_CH\regindex{n}] Set this bit to 1 to enable INCR burst transfer for RX channel 0 reading descriptor when accessing internal RAM. (R/W)
\label{fielddesc:DMAINDATABURSTENCHN}\item [GDMA\_IN\_DATA\_BURST\_EN\_CH\regindex{n}] Set this bit to 1 to enable INCR burst transfer for RX channel 0 receiving data when accessing internal RAM. (R/W)
\label{fielddesc:DMAMEMTRANSENCHN}\item [GDMA\_MEM\_TRANS\_EN\_CH\regindex{n}] Set this bit 1 to enable automatic transmitting data from memory to memory via GDMA. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_CONF1\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0004+192*\regindex{n}}\label{regdesc:DMAINCONF1CHNREG}
\regfield{(reserved)}{17}{15}{00000000000000000}%
\regfield{GDMA\_IN\_EXT\_MEM\_BK\_SIZE\_CH0}{2}{13}{{0}}%
\regfield{GDMA\_IN\_CHECK\_OWNER\_CH0}{1}{12}{{0}}%
\regfield{GDMA\_DMA\_INFIFO\_FULL\_THRS\_CH0}{12}{0}{{0x{}c}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMADMAINFIFOFULLTHRSCHN}\item [GDMA\_DMA\_INFIFO\_FULL\_THRS\_CH\regindex{n}] This register is used to generate the GDMA\_INFIFO\_FULL\_WM\_INT interrupt when RX channel 0 received byte number in RX FIFO is up to the value of the register. (R/W)
\label{fielddesc:DMAINCHECKOWNERCHN}\item [GDMA\_IN\_CHECK\_OWNER\_CH\regindex{n}] Set this bit to enable checking the owner attribute of the descriptor. (R/W)
\label{fielddesc:DMAINEXTMEMBKSIZECHN}\item [GDMA\_IN\_EXT\_MEM\_BK\_SIZE\_CH\regindex{n}] Block size of RX channel 0 when GDMA access external RAM. 0: 16 bytes; 1: 32 bytes; 2: 64 bytes; 3: Reserved. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_POP\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}001C+192*\regindex{n}}\label{regdesc:DMAINPOPCHNREG}
\regfield{(reserved)}{19}{13}{0000000000000000000}%
\regfield{GDMA\_INFIFO\_POP\_CH0}{1}{12}{{0}}%
\regfield{GDMA\_INFIFO\_RDATA\_CH0}{12}{0}{{0x{}800}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAINFIFORDATACHN}\item [GDMA\_INFIFO\_RDATA\_CH\regindex{n}] This register stores the data popping from GDMA FIFO (intended for debugging). (RO)
\label{fielddesc:DMAINFIFOPOPCHN}\item [GDMA\_INFIFO\_POP\_CH\regindex{n}] Set this bit to pop data from GDMA FIFO (intended for debugging). (R/W/SC)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_LINK\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0020+192*\regindex{n}}\label{regdesc:DMAINLINKCHNREG}
\regfield{(reserved)}{7}{25}{0000000}%
\regfield{GDMA\_INLINK\_PARK\_CH0}{1}{24}{{1}}%
\regfield{GDMA\_INLINK\_RESTART\_CH0}{1}{23}{{0}}%
\regfield{GDMA\_INLINK\_START\_CH0}{1}{22}{{0}}%
\regfield{GDMA\_INLINK\_STOP\_CH0}{1}{21}{{0}}%
\regfield{GDMA\_INLINK\_AUTO\_RET\_CH0}{1}{20}{{1}}%
\regfield{GDMA\_INLINK\_ADDR\_CH0}{20}{0}{{0x{}000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAINLINKADDRCHN}\item [GDMA\_INLINK\_ADDR\_CH\regindex{n}] This register stores the 20 least significant bits of the first receive descriptor's address. (R/W)
\label{fielddesc:DMAINLINKAUTORETCHN}\item [GDMA\_INLINK\_AUTO\_RET\_CH\regindex{n}] Set this bit to return to current receive descriptor's address, when there are some errors in current receiving data. (R/W)
\label{fielddesc:DMAINLINKSTOPCHN}\item [GDMA\_INLINK\_STOP\_CH\regindex{n}] Set this bit to stop GDMA's receive channel from receiving data. (R/W/SC)
\label{fielddesc:DMAINLINKSTARTCHN}\item [GDMA\_INLINK\_START\_CH\regindex{n}] Set this bit to enable GDMA's receive channel for data transfer. (R/W/SC)
\label{fielddesc:DMAINLINKRESTARTCHN}\item [GDMA\_INLINK\_RESTART\_CH\regindex{n}] Set this bit to mount a new receive descriptor. (R/W/SC)
\label{fielddesc:DMAINLINKPARKCHN}\item [GDMA\_INLINK\_PARK\_CH\regindex{n}] 1: the receive descriptor's FSM is in idle state; 0: the receive descriptor's FSM is working. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_CONF0\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0060+192*\regindex{n}}\label{regdesc:DMAOUTCONF0CHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{GDMA\_OUT\_DATA\_BURST\_EN\_CH0}{1}{5}{{0}}%
\regfield{GDMA\_OUTDSCR\_BURST\_EN\_CH0}{1}{4}{{0}}%
\regfield{GDMA\_OUT\_EOF\_MODE\_CH0}{1}{3}{{1}}%
\regfield{GDMA\_OUT\_AUTO\_WRBACK\_CH0}{1}{2}{{0}}%
\regfield{GDMA\_OUT\_LOOP\_TEST\_CH0}{1}{1}{{0}}%
\regfield{GDMA\_OUT\_RST\_CH0}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAOUTRSTCHN}\item [GDMA\_OUT\_RST\_CH\regindex{n}] This bit is used to reset GDMA channel 0 TX FSM and TX FIFO pointer. (R/W)
\label{fielddesc:DMAOUTLOOPTESTCHN}\item [GDMA\_OUT\_LOOP\_TEST\_CH\regindex{n}] Reserved. (R/W)
\label{fielddesc:DMAOUTAUTOWRBACKCHN}\item [GDMA\_OUT\_AUTO\_WRBACK\_CH\regindex{n}] Set this bit to enable automatic outlink-writeback when all the data in TX FIFO has been transmitted. (R/W)
\label{fielddesc:DMAOUTEOFMODECHN}\item [GDMA\_OUT\_EOF\_MODE\_CH\regindex{n}] EOF flag generation mode when transmitting data. 1: EOF flag for TX channel 0 is generated when data need to transmit has been popped from FIFO in GDMA. (R/W)
\label{fielddesc:DMAOUTDSCRBURSTENCHN}\item [GDMA\_OUTDSCR\_BURST\_EN\_CH\regindex{n}] Set this bit to 1 to enable INCR burst transfer for TX channel 0 reading descriptor when accessing internal RAM. (R/W)
\label{fielddesc:DMAOUTDATABURSTENCHN}\item [GDMA\_OUT\_DATA\_BURST\_EN\_CH\regindex{n}] Set this bit to 1 to enable INCR burst transfer for TX channel 0 transmitting data when accessing internal RAM. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_CONF1\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0064+192*\regindex{n}}\label{regdesc:DMAOUTCONF1CHNREG}
\regfield{(reserved)}{17}{15}{00000000000000000}%
\regfield{GDMA\_OUT\_EXT\_MEM\_BK\_SIZE\_CH0}{2}{13}{{0}}%
\regfield{GDMA\_OUT\_CHECK\_OWNER\_CH0}{1}{12}{{0}}%
\regfield{(reserved)}{12}{0}{000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAOUTCHECKOWNERCHN}\item [GDMA\_OUT\_CHECK\_OWNER\_CH\regindex{n}] Set this bit to enable checking the owner attribute of the descriptor. (R/W)
\label{fielddesc:DMAOUTEXTMEMBKSIZECHN}\item [GDMA\_OUT\_EXT\_MEM\_BK\_SIZE\_CH\regindex{n}] Block size of TX channel 0 when GDMA access external RAM. 0: 16 bytes; 1: 32 bytes; 2: 64 bytes; 3: Reserved. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_PUSH\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}007C+192*\regindex{n}}\label{regdesc:DMAOUTPUSHCHNREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{GDMA\_OUTFIFO\_PUSH\_CH0}{1}{9}{{0}}%
\regfield{GDMA\_OUTFIFO\_WDATA\_CH0}{9}{0}{{0x{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAOUTFIFOWDATACHN}\item [GDMA\_OUTFIFO\_WDATA\_CH\regindex{n}] This register stores the data that need to be pushed into GDMA FIFO. (R/W)
\label{fielddesc:DMAOUTFIFOPUSHCHN}\item [GDMA\_OUTFIFO\_PUSH\_CH\regindex{n}] Set this bit to push data into GDMA FIFO. (R/W/SC)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_LINK\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0080+192*\regindex{n}}\label{regdesc:DMAOUTLINKCHNREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{GDMA\_OUTLINK\_PARK\_CH0}{1}{23}{{1}}%
\regfield{GDMA\_OUTLINK\_RESTART\_CH0}{1}{22}{{0}}%
\regfield{GDMA\_OUTLINK\_START\_CH0}{1}{21}{{0}}%
\regfield{GDMA\_OUTLINK\_STOP\_CH0}{1}{20}{{0}}%
\regfield{GDMA\_OUTLINK\_ADDR\_CH0}{20}{0}{{0x{}000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAOUTLINKADDRCHN}\item [GDMA\_OUTLINK\_ADDR\_CH\regindex{n}] This register stores the 20 least significant bits of the first transmit descriptor's address. (R/W)
\label{fielddesc:DMAOUTLINKSTOPCHN}\item [GDMA\_OUTLINK\_STOP\_CH\regindex{n}] Set this bit to stop GDMA's transmit channel from transferring data. (R/W/SC)
\label{fielddesc:DMAOUTLINKSTARTCHN}\item [GDMA\_OUTLINK\_START\_CH\regindex{n}] Set this bit to enable GDMA's transmit channel for data transfer. (R/W/SC)
\label{fielddesc:DMAOUTLINKRESTARTCHN}\item [GDMA\_OUTLINK\_RESTART\_CH\regindex{n}] Set this bit to restart a new outlink from the last address. (R/W/SC)
\label{fielddesc:DMAOUTLINKPARKCHN}\item [GDMA\_OUTLINK\_PARK\_CH\regindex{n}] 1: the transmit descriptor's FSM is in idle state; 0: the transmit descriptor's FSM is working. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_PD\_CONF\_REG}{0x{}03C4}\label{regdesc:DMAPDCONFREG}
\regfield{(reserved)}{25}{7}{0000000000000000000000000}%
\regfield{GDMA\_DMA\_RAM\_CLK\_FO}{1}{6}{{0}}%
\regfield{GDMA\_DMA\_RAM\_FORCE\_PU}{1}{5}{{1}}%
\regfield{GDMA\_DMA\_RAM\_FORCE\_PD}{1}{4}{{0}}%
\regfield{(reserved)}{4}{0}{0000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMADMARAMFORCEPD}\item [GDMA\_DMA\_RAM\_FORCE\_PD] Set this bit to force power down GDMA internal memory. (R/W)
\label{fielddesc:DMADMARAMFORCEPU}\item [GDMA\_DMA\_RAM\_FORCE\_PU] Set this bit to force power up GDMA internal memory. (R/W)
\label{fielddesc:DMADMARAMCLKFO}\item [GDMA\_DMA\_RAM\_CLK\_FO] 1: Force to open the clock and bypass the gate-clock when accessing the RAM in GDMA; 0: A gate-clock will be used when accessing the RAM in GDMA. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_MISC\_CONF\_REG}{0x{}03C8}\label{regdesc:DMAMISCCONFREG}
\regfield{(reserved)}{27}{5}{000000000000000000000000000}%
\regfield{GDMA\_CLK\_EN}{1}{4}{{0}}%
\regfield{(reserved)}{1}{3}{0}%
\regfield{GDMA\_ARB\_PRI\_DIS}{1}{2}{{0}}%
\regfield{GDMA\_AHBM\_RST\_EXTER}{1}{1}{{0}}%
\regfield{GDMA\_AHBM\_RST\_INTER}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAAHBMRSTINTER}\item [GDMA\_AHBM\_RST\_INTER] Set this bit, then clear this bit to reset the internal AHB FSM. (R/W)
\label{fielddesc:DMAAHBMRSTEXTER}\item [GDMA\_AHBM\_RST\_EXTER] Set this bit, then clear this bit to reset the external AHB FSM. (R/W)
\label{fielddesc:DMAARBPRIDIS}\item [GDMA\_ARB\_PRI\_DIS] Set this bit to disable priority arbitration function. (R/W)
\label{fielddesc:DMACLKEN}\item [GDMA\_CLK\_EN] 1: Force clock on for registers; 0: Support clock only when application writes registers. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_INT\_RAW\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0008+192*\regindex{n}}\label{regdesc:DMAININTRAWCHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{GDMA\_INFIFO\_FULL\_WM\_CH0\_INT\_RAW}{1}{5}{{0}}%
\regfield{GDMA\_IN\_DSCR\_EMPTY\_CH0\_INT\_RAW}{1}{4}{{0}}%
\regfield{GDMA\_IN\_DSCR\_ERR\_CH0\_INT\_RAW}{1}{3}{{0}}%
\regfield{GDMA\_IN\_ERR\_EOF\_CH0\_INT\_RAW}{1}{2}{{0}}%
\regfield{GDMA\_IN\_SUC\_EOF\_CH0\_INT\_RAW}{1}{1}{{0}}%
\regfield{GDMA\_IN\_DONE\_CH0\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAINDONECHNINTRAW}\item [GDMA\_IN\_DONE\_CH\regindex{n}\_INT\_RAW] The raw interrupt bit turns to high level when the last data pointed by one receive descriptor has been received for RX channel 0. (R/WTC/SS)
\label{fielddesc:DMAINSUCEOFCHNINTRAW}\item [GDMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_RAW] The raw interrupt bit turns to high level for RX channel 0 when the last data pointed by one receive descriptor has been received and the suc\_eof bit in this descriptor is 1. For UHCI0, the raw interrupt bit turns to high level when the last data pointed by one receive descriptor has been received and no data error is detected for RX channel 0. (R/WTC/SS)
\label{fielddesc:DMAINERREOFCHNINTRAW}\item [GDMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_RAW] The raw interrupt bit turns to high level when data error is detected only in the case that the peripheral is UHCI0 for RX channel 0. For other peripherals, this raw interrupt is reserved. (R/WTC/SS)
\label{fielddesc:DMAINDSCRERRCHNINTRAW}\item [GDMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_RAW] The raw interrupt bit turns to high level when detecting receive descriptor error, including owner error, the second and third word error of receive descriptor for RX channel 0. (R/WTC/SS)
\label{fielddesc:DMAINDSCREMPTYCHNINTRAW}\item [GDMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_RAW] The raw interrupt bit turns to high level when RX FIFO pointed by inlink is full and receiving data is not completed, but there is no more inlink for RX channel 0. (R/WTC/SS)
\label{fielddesc:DMAINFIFOFULLWMCHNINTRAW}\item [GDMA\_INFIFO\_FULL\_WM\_CH\regindex{n}\_INT\_RAW] The raw interrupt bit turns to high level when received data byte number is up to threshold configured by GDMA\_DMA\_INFIFO\_FULL\_THRS\_CH0 in RX FIFO of RX channel 0. (R/WTC/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_INT\_ST\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}000C+192*\regindex{n}}\label{regdesc:DMAININTSTCHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{GDMA\_INFIFO\_FULL\_WM\_CH0\_INT\_ST}{1}{5}{{0}}%
\regfield{GDMA\_IN\_DSCR\_EMPTY\_CH0\_INT\_ST}{1}{4}{{0}}%
\regfield{GDMA\_IN\_DSCR\_ERR\_CH0\_INT\_ST}{1}{3}{{0}}%
\regfield{GDMA\_IN\_ERR\_EOF\_CH0\_INT\_ST}{1}{2}{{0}}%
\regfield{GDMA\_IN\_SUC\_EOF\_CH0\_INT\_ST}{1}{1}{{0}}%
\regfield{GDMA\_IN\_DONE\_CH0\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAINDONECHNINTST}\item [GDMA\_IN\_DONE\_CH\regindex{n}\_INT\_ST] The raw interrupt status bit for the GDMA\_IN\_DONE\_CH\_INT interrupt. (RO)
\label{fielddesc:DMAINSUCEOFCHNINTST}\item [GDMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_ST] The raw interrupt status bit for the GDMA\_IN\_SUC\_EOF\_CH\_INT interrupt. (RO)
\label{fielddesc:DMAINERREOFCHNINTST}\item [GDMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_ST] The raw interrupt status bit for the GDMA\_IN\_ERR\_EOF\_CH\_INT interrupt. (RO)
\label{fielddesc:DMAINDSCRERRCHNINTST}\item [GDMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_ST] The raw interrupt status bit for the GDMA\_IN\_DSCR\_ERR\_CH\_INT interrupt. (RO)
\label{fielddesc:DMAINDSCREMPTYCHNINTST}\item [GDMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_ST] The raw interrupt status bit for the GDMA\_IN\_DSCR\_EMPTY\_CH\_INT interrupt. (RO)
\label{fielddesc:DMAINFIFOFULLWMCHNINTST}\item [GDMA\_INFIFO\_FULL\_WM\_CH\regindex{n}\_INT\_ST] The raw interrupt status bit for the GDMA\_INFIFO\_FULL\_WM\_CH\_INT interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_INT\_ENA\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0010+192*\regindex{n}}\label{regdesc:DMAININTENACHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{GDMA\_INFIFO\_FULL\_WM\_CH0\_INT\_ENA}{1}{5}{{0}}%
\regfield{GDMA\_IN\_DSCR\_EMPTY\_CH0\_INT\_ENA}{1}{4}{{0}}%
\regfield{GDMA\_IN\_DSCR\_ERR\_CH0\_INT\_ENA}{1}{3}{{0}}%
\regfield{GDMA\_IN\_ERR\_EOF\_CH0\_INT\_ENA}{1}{2}{{0}}%
\regfield{GDMA\_IN\_SUC\_EOF\_CH0\_INT\_ENA}{1}{1}{{0}}%
\regfield{GDMA\_IN\_DONE\_CH0\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAINDONECHNINTENA}\item [GDMA\_IN\_DONE\_CH\regindex{n}\_INT\_ENA] The interrupt enable bit for the GDMA\_IN\_DONE\_CH\_INT interrupt. (R/W)
\label{fielddesc:DMAINSUCEOFCHNINTENA}\item [GDMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_ENA] The interrupt enable bit for the GDMA\_IN\_SUC\_EOF\_CH\_INT interrupt. (R/W)
\label{fielddesc:DMAINERREOFCHNINTENA}\item [GDMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_ENA] The interrupt enable bit for the GDMA\_IN\_ERR\_EOF\_CH\_INT interrupt. (R/W)
\label{fielddesc:DMAINDSCRERRCHNINTENA}\item [GDMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_ENA] The interrupt enable bit for the GDMA\_IN\_DSCR\_ERR\_CH\_INT interrupt. (R/W)
\label{fielddesc:DMAINDSCREMPTYCHNINTENA}\item [GDMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_ENA] The interrupt enable bit for the GDMA\_IN\_DSCR\_EMPTY\_CH\_INT interrupt. (R/W)
\label{fielddesc:DMAINFIFOFULLWMCHNINTENA}\item [GDMA\_INFIFO\_FULL\_WM\_CH\regindex{n}\_INT\_ENA] The interrupt enable bit for the GDMA\_INFIFO\_FULL\_WM\_CH\_INT interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_INT\_CLR\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0014+192*\regindex{n}}\label{regdesc:DMAININTCLRCHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{GDMA\_DMA\_INFIFO\_FULL\_WM\_CH0\_INT\_CLR}{1}{5}{{0}}%
\regfield{GDMA\_IN\_DSCR\_EMPTY\_CH0\_INT\_CLR}{1}{4}{{0}}%
\regfield{GDMA\_IN\_DSCR\_ERR\_CH0\_INT\_CLR}{1}{3}{{0}}%
\regfield{GDMA\_IN\_ERR\_EOF\_CH0\_INT\_CLR}{1}{2}{{0}}%
\regfield{GDMA\_IN\_SUC\_EOF\_CH0\_INT\_CLR}{1}{1}{{0}}%
\regfield{GDMA\_IN\_DONE\_CH0\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAINDONECHNINTCLR}\item [GDMA\_IN\_DONE\_CH\regindex{n}\_INT\_CLR] Set this bit to clear the GDMA\_IN\_DONE\_CH\_INT interrupt. (WT)
\label{fielddesc:DMAINSUCEOFCHNINTCLR}\item [GDMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_CLR] Set this bit to clear the GDMA\_IN\_SUC\_EOF\_CH\_INT interrupt. (WT)
\label{fielddesc:DMAINERREOFCHNINTCLR}\item [GDMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_CLR] Set this bit to clear the GDMA\_IN\_ERR\_EOF\_CH\_INT interrupt. (WT)
\label{fielddesc:DMAINDSCRERRCHNINTCLR}\item [GDMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_CLR] Set this bit to clear the GDMA\_IN\_DSCR\_ERR\_CH\_INT interrupt. (WT)
\label{fielddesc:DMAINDSCREMPTYCHNINTCLR}\item [GDMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_CLR] Set this bit to clear the GDMA\_IN\_DSCR\_EMPTY\_CH\_INT interrupt. (WT)
\label{fielddesc:DMADMAINFIFOFULLWMCHNINTCLR}\item [GDMA\_DMA\_INFIFO\_FULL\_WM\_CH\regindex{n}\_INT\_CLR] Set this bit to clear the GDMA\_INFIFO\_FULL\_WM\_CH\_INT interrupt. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_INT\_RAW\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0068+192*\regindex{n}}\label{regdesc:DMAOUTINTRAWCHNREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{GDMA\_OUT\_TOTAL\_EOF\_CH0\_INT\_RAW}{1}{3}{{0}}%
\regfield{GDMA\_OUT\_DSCR\_ERR\_CH0\_INT\_RAW}{1}{2}{{0}}%
\regfield{GDMA\_OUT\_EOF\_CH0\_INT\_RAW}{1}{1}{{0}}%
\regfield{GDMA\_OUT\_DONE\_CH0\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAOUTDONECHNINTRAW}\item [GDMA\_OUT\_DONE\_CH\regindex{n}\_INT\_RAW] The raw interrupt bit turns to high level when the last data pointed by one transmit descriptor has been transmitted to peripherals for TX channel 0. (R/WTC/SS)
\label{fielddesc:DMAOUTEOFCHNINTRAW}\item [GDMA\_OUT\_EOF\_CH\regindex{n}\_INT\_RAW] The raw interrupt bit turns to high level when the last data pointed by one transmit descriptor has been read from memory for TX channel 0. (R/WTC/SS)
\label{fielddesc:DMAOUTDSCRERRCHNINTRAW}\item [GDMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_RAW] The raw interrupt bit turns to high level when detecting transmit descriptor error, including owner error, the second and third word error of transmit descriptor for TX channel 0. (R/WTC/SS)
\label{fielddesc:DMAOUTTOTALEOFCHNINTRAW}\item [GDMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_RAW] The raw interrupt bit turns to high level when data corresponding a outlink (includes one descriptor or few descriptors) is transmitted out for TX channel 0. (R/WTC/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_INT\_ST\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}006C+192*\regindex{n}}\label{regdesc:DMAOUTINTSTCHNREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{GDMA\_OUT\_TOTAL\_EOF\_CH0\_INT\_ST}{1}{3}{{0}}%
\regfield{GDMA\_OUT\_DSCR\_ERR\_CH0\_INT\_ST}{1}{2}{{0}}%
\regfield{GDMA\_OUT\_EOF\_CH0\_INT\_ST}{1}{1}{{0}}%
\regfield{GDMA\_OUT\_DONE\_CH0\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAOUTDONECHNINTST}\item [GDMA\_OUT\_DONE\_CH\regindex{n}\_INT\_ST] The raw interrupt status bit for the GDMA\_OUT\_DONE\_CH\_INT interrupt. (RO)
\label{fielddesc:DMAOUTEOFCHNINTST}\item [GDMA\_OUT\_EOF\_CH\regindex{n}\_INT\_ST] The raw interrupt status bit for the GDMA\_OUT\_EOF\_CH\_INT interrupt. (RO)
\label{fielddesc:DMAOUTDSCRERRCHNINTST}\item [GDMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_ST] The raw interrupt status bit for the GDMA\_OUT\_DSCR\_ERR\_CH\_INT interrupt. (RO)
\label{fielddesc:DMAOUTTOTALEOFCHNINTST}\item [GDMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_ST] The raw interrupt status bit for the GDMA\_OUT\_TOTAL\_EOF\_CH\_INT interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_INT\_ENA\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0070+192*\regindex{n}}\label{regdesc:DMAOUTINTENACHNREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{GDMA\_OUT\_TOTAL\_EOF\_CH0\_INT\_ENA}{1}{3}{{0}}%
\regfield{GDMA\_OUT\_DSCR\_ERR\_CH0\_INT\_ENA}{1}{2}{{0}}%
\regfield{GDMA\_OUT\_EOF\_CH0\_INT\_ENA}{1}{1}{{0}}%
\regfield{GDMA\_OUT\_DONE\_CH0\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAOUTDONECHNINTENA}\item [GDMA\_OUT\_DONE\_CH\regindex{n}\_INT\_ENA] The interrupt enable bit for the GDMA\_OUT\_DONE\_CH\_INT interrupt. (R/W)
\label{fielddesc:DMAOUTEOFCHNINTENA}\item [GDMA\_OUT\_EOF\_CH\regindex{n}\_INT\_ENA] The interrupt enable bit for the GDMA\_OUT\_EOF\_CH\_INT interrupt. (R/W)
\label{fielddesc:DMAOUTDSCRERRCHNINTENA}\item [GDMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_ENA] The interrupt enable bit for the GDMA\_OUT\_DSCR\_ERR\_CH\_INT interrupt. (R/W)
\label{fielddesc:DMAOUTTOTALEOFCHNINTENA}\item [GDMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_ENA] The interrupt enable bit for the GDMA\_OUT\_TOTAL\_EOF\_CH\_INT interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_INT\_CLR\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0074+192*\regindex{n}}\label{regdesc:DMAOUTINTCLRCHNREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{GDMA\_OUT\_TOTAL\_EOF\_CH0\_INT\_CLR}{1}{3}{{0}}%
\regfield{GDMA\_OUT\_DSCR\_ERR\_CH0\_INT\_CLR}{1}{2}{{0}}%
\regfield{GDMA\_OUT\_EOF\_CH0\_INT\_CLR}{1}{1}{{0}}%
\regfield{GDMA\_OUT\_DONE\_CH0\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAOUTDONECHNINTCLR}\item [GDMA\_OUT\_DONE\_CH\regindex{n}\_INT\_CLR] Set this bit to clear the GDMA\_OUT\_DONE\_CH\_INT interrupt. (WT)
\label{fielddesc:DMAOUTEOFCHNINTCLR}\item [GDMA\_OUT\_EOF\_CH\regindex{n}\_INT\_CLR] Set this bit to clear the GDMA\_OUT\_EOF\_CH\_INT interrupt. (WT)
\label{fielddesc:DMAOUTDSCRERRCHNINTCLR}\item [GDMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_CLR] Set this bit to clear the GDMA\_OUT\_DSCR\_ERR\_CH\_INT interrupt. (WT)
\label{fielddesc:DMAOUTTOTALEOFCHNINTCLR}\item [GDMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_CLR] Set this bit to clear the GDMA\_OUT\_TOTAL\_EOF\_CH\_INT interrupt. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_EXTMEM\_REJECT\_INT\_RAW\_REG}{0x{}03FC}\label{regdesc:DMAEXTMEMREJECTINTRAWREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{GDMA\_EXTMEM\_REJECT\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAEXTMEMREJECTINTRAW}\item [GDMA\_EXTMEM\_REJECT\_INT\_RAW] The raw interrupt bit turns to high level when accessing external RAM is rejected by permission control. (R/WTC/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_EXTMEM\_REJECT\_INT\_ST\_REG}{0x{}0400}\label{regdesc:DMAEXTMEMREJECTINTSTREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{GDMA\_EXTMEM\_REJECT\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAEXTMEMREJECTINTST}\item [GDMA\_EXTMEM\_REJECT\_INT\_ST] The raw interrupt status bit for the GDMA\_EXTMEM\_REJECT\_INT interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_EXTMEM\_REJECT\_INT\_ENA\_REG}{0x{}0404}\label{regdesc:DMAEXTMEMREJECTINTENAREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{GDMA\_EXTMEM\_REJECT\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAEXTMEMREJECTINTENA}\item [GDMA\_EXTMEM\_REJECT\_INT\_ENA] The interrupt enable bit for the GDMA\_EXTMEM\_REJECT\_INT interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_EXTMEM\_REJECT\_INT\_CLR\_REG}{0x{}0408}\label{regdesc:DMAEXTMEMREJECTINTCLRREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{GDMA\_EXTMEM\_REJECT\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAEXTMEMREJECTINTCLR}\item [GDMA\_EXTMEM\_REJECT\_INT\_CLR] Set this bit to clear the GDMA\_EXTMEM\_REJECT\_INT interrupt. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_INFIFO\_STATUS\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0018+192*\regindex{n}}\label{regdesc:DMAINFIFOSTATUSCHNREG}
\regfield{(reserved)}{3}{29}{000}%
\regfield{reserved}{1}{28}{{0}}%
\regfield{reserved}{1}{27}{{1}}%
\regfield{reserved}{1}{26}{{1}}%
\regfield{reserved}{1}{25}{{1}}%
\regfield{reserved}{1}{24}{{1}}%
\regfield{GDMA\_INFIFO\_CNT\_L3\_CH0}{5}{19}{{0}}%
\regfield{GDMA\_INFIFO\_CNT\_L2\_CH0}{7}{12}{{0}}%
\regfield{GDMA\_INFIFO\_CNT\_L1\_CH0}{6}{6}{{0}}%
\regfield{GDMA\_INFIFO\_EMPTY\_L3\_CH0}{1}{5}{{1}}%
\regfield{GDMA\_INFIFO\_FULL\_L3\_CH0}{1}{4}{{1}}%
\regfield{GDMA\_INFIFO\_EMPTY\_L2\_CH0}{1}{3}{{1}}%
\regfield{GDMA\_INFIFO\_FULL\_L2\_CH0}{1}{2}{{0}}%
\regfield{GDMA\_INFIFO\_EMPTY\_L1\_CH0}{1}{1}{{1}}%
\regfield{GDMA\_INFIFO\_FULL\_L1\_CH0}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAINFIFOFULLL1CHN}\item [GDMA\_INFIFO\_FULL\_L1\_CH\regindex{n}] L1 RX FIFO full signal for RX channel 0. (RO)
\label{fielddesc:DMAINFIFOEMPTYL1CHN}\item [GDMA\_INFIFO\_EMPTY\_L1\_CH\regindex{n}] L1 RX FIFO empty signal for RX channel 0. (RO)
\label{fielddesc:DMAINFIFOFULLL2CHN}\item [GDMA\_INFIFO\_FULL\_L2\_CH\regindex{n}] L2 RX FIFO full signal for RX channel 0. (RO)
\label{fielddesc:DMAINFIFOEMPTYL2CHN}\item [GDMA\_INFIFO\_EMPTY\_L2\_CH\regindex{n}] L2 RX FIFO empty signal for RX channel 0. (RO)
\label{fielddesc:DMAINFIFOFULLL3CHN}\item [GDMA\_INFIFO\_FULL\_L3\_CH\regindex{n}] L3 RX FIFO full signal for RX channel 0. (RO)
\label{fielddesc:DMAINFIFOEMPTYL3CHN}\item [GDMA\_INFIFO\_EMPTY\_L3\_CH\regindex{n}] L3 RX FIFO empty signal for RX channel 0. (RO)
\label{fielddesc:DMAINFIFOCNTL1CHN}\item [GDMA\_INFIFO\_CNT\_L1\_CH\regindex{n}] The register stores the byte number of the data in L1 RX FIFO for RX channel 0. (RO)
\label{fielddesc:DMAINFIFOCNTL2CHN}\item [GDMA\_INFIFO\_CNT\_L2\_CH\regindex{n}] The register stores the byte number of the data in L2 RX FIFO for RX channel 0. (RO)
\label{fielddesc:DMAINFIFOCNTL3CHN}\item [GDMA\_INFIFO\_CNT\_L3\_CH\regindex{n}] The register stores the byte number of the data in L3 RX FIFO for RX channel 0. (RO)

\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_STATE\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0024+192*\regindex{n}}\label{regdesc:DMAINSTATECHNREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{reserved}{3}{20}{{0}}%
\regfield{reserved}{2}{18}{{0}}%
\regfield{GDMA\_INLINK\_DSCR\_ADDR\_CH0}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAINLINKDSCRADDRCHN}\item [GDMA\_INLINK\_DSCR\_ADDR\_CH\regindex{n}] This register stores the lower 18 bits of the next receive descriptor address that is pre-read (but not processed yet). If the current receive descriptor is the last descriptor, then this field represents the address of the current receive descriptor. (RO)

\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_SUC\_EOF\_DES\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0028+192*\regindex{n}}\label{regdesc:DMAINSUCEOFDESADDRCHNREG}
\regfield{GDMA\_IN\_SUC\_EOF\_DES\_ADDR\_CH0}{32}{0}{{0x{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAINSUCEOFDESADDRCHN}\item [GDMA\_IN\_SUC\_EOF\_DES\_ADDR\_CH\regindex{n}] This register stores the address of the receive descriptor when the EOF bit in this descriptor is 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_ERR\_EOF\_DES\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}002C+192*\regindex{n}}\label{regdesc:DMAINERREOFDESADDRCHNREG}
\regfield{GDMA\_IN\_ERR\_EOF\_DES\_ADDR\_CH0}{32}{0}{{0x{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAINERREOFDESADDRCHN}\item [GDMA\_IN\_ERR\_EOF\_DES\_ADDR\_CH\regindex{n}] This register stores the address of the receive descriptor when there are some errors in current receiving data. Only used when peripheral is UHCI0. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_DSCR\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0030+192*\regindex{n}}\label{regdesc:DMAINDSCRCHNREG}
\regfield{GDMA\_INLINK\_DSCR\_CH0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAINLINKDSCRCHN}\item [GDMA\_INLINK\_DSCR\_CH\regindex{n}] Represents the address of the next receive descriptor x+1 pointed by the current receive descriptor that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_DSCR\_BF0\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0034+192*\regindex{n}}\label{regdesc:DMAINDSCRBF0CHNREG}
\regfield{GDMA\_INLINK\_DSCR\_BF0\_CH0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAINLINKDSCRBF0CHN}\item [GDMA\_INLINK\_DSCR\_BF0\_CH\regindex{n}] Represents the address of the current receive descriptor x that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_DSCR\_BF1\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0038+192*\regindex{n}}\label{regdesc:DMAINDSCRBF1CHNREG}
\regfield{GDMA\_INLINK\_DSCR\_BF1\_CH0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAINLINKDSCRBF1CHN}\item [GDMA\_INLINK\_DSCR\_BF1\_CH\regindex{n}] Represents the address of the previous receive descriptor x-1 that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUTFIFO\_STATUS\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0078+192*\regindex{n}}\label{regdesc:DMAOUTFIFOSTATUSCHNREG}
\regfield{(reserved)}{5}{27}{00000}%
\regfield{GDMA\_OUT\_REMAIN\_UNDER\_4B\_L3\_CH0}{1}{26}{{1}}%
\regfield{GDMA\_OUT\_REMAIN\_UNDER\_3B\_L3\_CH0}{1}{25}{{1}}%
\regfield{GDMA\_OUT\_REMAIN\_UNDER\_2B\_L3\_CH0}{1}{24}{{1}}%
\regfield{GDMA\_OUT\_REMAIN\_UNDER\_1B\_L3\_CH0}{1}{23}{{1}}%
\regfield{GDMA\_OUTFIFO\_CNT\_L3\_CH0}{5}{18}{{0}}%
\regfield{GDMA\_OUTFIFO\_CNT\_L2\_CH0}{7}{11}{{0}}%
\regfield{GDMA\_OUTFIFO\_CNT\_L1\_CH0}{5}{6}{{0}}%
\regfield{GDMA\_OUTFIFO\_EMPTY\_L3\_CH0}{1}{5}{{1}}%
\regfield{GDMA\_OUTFIFO\_FULL\_L3\_CH0}{1}{4}{{0}}%
\regfield{GDMA\_OUTFIFO\_EMPTY\_L2\_CH0}{1}{3}{{1}}%
\regfield{GDMA\_OUTFIFO\_FULL\_L2\_CH0}{1}{2}{{0}}%
\regfield{GDMA\_OUTFIFO\_EMPTY\_L1\_CH0}{1}{1}{{1}}%
\regfield{GDMA\_OUTFIFO\_FULL\_L1\_CH0}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAOUTFIFOFULLL1CHN}\item [GDMA\_OUTFIFO\_FULL\_L1\_CH\regindex{n}] L1 TX FIFO full signal for TX channel 0. (RO)
\label{fielddesc:DMAOUTFIFOEMPTYL1CHN}\item [GDMA\_OUTFIFO\_EMPTY\_L1\_CH\regindex{n}] L1 TX FIFO empty signal for TX channel 0. (RO)
\label{fielddesc:DMAOUTFIFOFULLL2CHN}\item [GDMA\_OUTFIFO\_FULL\_L2\_CH\regindex{n}] L2 TX FIFO full signal for TX channel 0. (RO)
\label{fielddesc:DMAOUTFIFOEMPTYL2CHN}\item [GDMA\_OUTFIFO\_EMPTY\_L2\_CH\regindex{n}] L2 TX FIFO empty signal for TX channel 0. (RO)
\label{fielddesc:DMAOUTFIFOFULLL3CHN}\item [GDMA\_OUTFIFO\_FULL\_L3\_CH\regindex{n}] L3 TX FIFO full signal for TX channel 0. (RO)
\label{fielddesc:DMAOUTFIFOEMPTYL3CHN}\item [GDMA\_OUTFIFO\_EMPTY\_L3\_CH\regindex{n}] L3 TX FIFO empty signal for TX channel 0. (RO)
\label{fielddesc:DMAOUTFIFOCNTL1CHN}\item [GDMA\_OUTFIFO\_CNT\_L1\_CH\regindex{n}] The register stores the byte number of the data in L1 TX FIFO for TX channel 0. (RO)
\label{fielddesc:DMAOUTFIFOCNTL2CHN}\item [GDMA\_OUTFIFO\_CNT\_L2\_CH\regindex{n}] The register stores the byte number of the data in L2 TX FIFO for TX channel 0. (RO)
\label{fielddesc:DMAOUTFIFOCNTL3CHN}\item [GDMA\_OUTFIFO\_CNT\_L3\_CH\regindex{n}] The register stores the byte number of the data in L3 TX FIFO for TX channel 0. (RO)
\label{fielddesc:DMAOUTREMAINUNDER1BL3CHN}\item [GDMA\_OUT\_REMAIN\_UNDER\_1B\_L3\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:DMAOUTREMAINUNDER2BL3CHN}\item [GDMA\_OUT\_REMAIN\_UNDER\_2B\_L3\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:DMAOUTREMAINUNDER3BL3CHN}\item [GDMA\_OUT\_REMAIN\_UNDER\_3B\_L3\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:DMAOUTREMAINUNDER4BL3CHN}\item [GDMA\_OUT\_REMAIN\_UNDER\_4B\_L3\_CH\regindex{n}] Reserved. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_STATE\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0084+192*\regindex{n}}\label{regdesc:DMAOUTSTATECHNREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{GDMA\_OUT\_STATE\_CH0}{3}{20}{{0}}%
\regfield{GDMA\_OUT\_DSCR\_STATE\_CH0}{2}{18}{{0}}%
\regfield{GDMA\_OUTLINK\_DSCR\_ADDR\_CH0}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAOUTLINKDSCRADDRCHN}\item [GDMA\_OUTLINK\_DSCR\_ADDR\_CH\regindex{n}] This register stores the lower 18 bits of the next receive descriptor address that is pre-read (but not processed yet). If the current receive descriptor is the last descriptor, then this field represents the address of the current receive descriptor. (RO)
\label{fielddesc:DMAOUTDSCRSTATECHN}\item [GDMA\_OUT\_DSCR\_STATE\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:DMAOUTSTATECHN}\item [GDMA\_OUT\_STATE\_CH\regindex{n}] Reserved. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_EOF\_DES\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0088+192*\regindex{n}}\label{regdesc:DMAOUTEOFDESADDRCHNREG}
\regfield{GDMA\_OUT\_EOF\_DES\_ADDR\_CH0}{32}{0}{{0x{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAOUTEOFDESADDRCHN}\item [GDMA\_OUT\_EOF\_DES\_ADDR\_CH\regindex{n}] This register stores the address of the transmit descriptor when the EOF bit in this descriptor is 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_EOF\_BFR\_DES\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}008C+192*\regindex{n}}\label{regdesc:DMAOUTEOFBFRDESADDRCHNREG}
\regfield{GDMA\_OUT\_EOF\_BFR\_DES\_ADDR\_CH0}{32}{0}{{0x{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAOUTEOFBFRDESADDRCHN}\item [GDMA\_OUT\_EOF\_BFR\_DES\_ADDR\_CH\regindex{n}] This register stores the address of the transmit descriptor before the last transmit descriptor. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_DSCR\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0090+192*\regindex{n}}\label{regdesc:DMAOUTDSCRCHNREG}
\regfield{GDMA\_OUTLINK\_DSCR\_CH0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAOUTLINKDSCRCHN}\item [GDMA\_OUTLINK\_DSCR\_CH\regindex{n}] Represents the address of the next transmit descriptor y+1 pointed by the current transmit descriptor that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_DSCR\_BF0\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0094+192*\regindex{n}}\label{regdesc:DMAOUTDSCRBF0CHNREG}
\regfield{GDMA\_OUTLINK\_DSCR\_BF0\_CH0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAOUTLINKDSCRBF0CHN}\item [GDMA\_OUTLINK\_DSCR\_BF0\_CH\regindex{n}] Represents the address of the current transmit descriptor y that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_DSCR\_BF1\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0098+192*\regindex{n}}\label{regdesc:DMAOUTDSCRBF1CHNREG}
\regfield{GDMA\_OUTLINK\_DSCR\_BF1\_CH0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAOUTLINKDSCRBF1CHN}\item [GDMA\_OUTLINK\_DSCR\_BF1\_CH\regindex{n}] Represents the address of the previous transmit descriptor y-1 that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_PRI\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0044+192*\regindex{n}}\label{regdesc:DMAINPRICHNREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{GDMA\_RX\_PRI\_CH0}{4}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMARXPRICHN}\item [GDMA\_RX\_PRI\_CH\regindex{n}] The priority of RX channel 0. The larger the value, the higher the priority. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_PRI\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}00A4+192*\regindex{n}}\label{regdesc:DMAOUTPRICHNREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{GDMA\_TX\_PRI\_CH0}{4}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMATXPRICHN}\item [GDMA\_TX\_PRI\_CH\regindex{n}] The priority of TX channel 0. The larger the value, the higher the priority. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_PERI\_SEL\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}0048+192*\regindex{n}}\label{regdesc:DMAINPERISELCHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{GDMA\_PERI\_IN\_SEL\_CH0}{6}{0}{{0x{}3f}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAPERIINSELCHN}\item [GDMA\_PERI\_IN\_SEL\_CH\regindex{n}] This register is used to select peripheral for RX channel 0. 0: SPI2; 1: SPI3; 2: UHCI0; 3: I2S0; 4: I2S1; 5: LCD\_CAM; 6: AES; 7: SHA; 8: ADC\_DAC; 9: RMT; 10 \verb+~+ 63: Invalid. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_PERI\_SEL\_CH\regindex{n}\_REG (\regindex{n}: 0-4)}{0x{}00A8+192*\regindex{n}}\label{regdesc:DMAOUTPERISELCHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{GDMA\_PERI\_OUT\_SEL\_CH0}{6}{0}{{0x{}3f}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAPERIOUTSELCHN}\item [GDMA\_PERI\_OUT\_SEL\_CH\regindex{n}] This register is used to select peripheral for TX channel 0. 0: SPI2; 1: SPI3; 2: UHCI0; 3: I2S0; 4: I2S1; 5: LCD\_CAM; 6: AES; 7: SHA; 8: ADC\_DAC; 9: RMT; 10 \verb+~+ 63: Invalid. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_EXTMEM\_REJECT\_ADDR\_REG}{0x{}03F4}\label{regdesc:DMAEXTMEMREJECTADDRREG}
\regfield{GDMA\_EXTMEM\_REJECT\_ADDR}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAEXTMEMREJECTADDR}\item [GDMA\_EXTMEM\_REJECT\_ADDR] This register store the first address rejected by permission control when accessing external RAM. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_EXTMEM\_REJECT\_ST\_REG}{0x{}03F8}\label{regdesc:DMAEXTMEMREJECTSTREG}
\regfield{(reserved)}{20}{12}{00000000000000000000}%
\regfield{GDMA\_EXTMEM\_REJECT\_PERI\_NUM}{6}{6}{{0}}%
\regfield{GDMA\_EXTMEM\_REJECT\_CHANNEL\_NUM}{4}{2}{{0}}%
\regfield{GDMA\_EXTMEM\_REJECT\_ATRR}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMAEXTMEMREJECTATRR}\item [GDMA\_EXTMEM\_REJECT\_ATRR] Read or write attribute of the rejected access. Bit 0: if this bit is 1, the rejected access is READ. Bit 1: if this bit is 1, the rejected access is WRITE. (RO)
\label{fielddesc:DMAEXTMEMREJECTCHANNELNUM}\item [GDMA\_EXTMEM\_REJECT\_CHANNEL\_NUM] This field indicates the channel used for the rejected access. (RO)
\label{fielddesc:DMAEXTMEMREJECTPERINUM}\item [GDMA\_EXTMEM\_REJECT\_PERI\_NUM] This bit indicates the peripheral whose access was rejected. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_DATE\_REG}{0x{}040C}\label{regdesc:DMADATEREG}
\regfield{GDMA\_DATE}{32}{0}{{0x{}2101180}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:DMADATE}\item [GDMA\_DATE] This is the version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}


