\begin{longtable}{ | m{6cm} | m{7.2cm} | r| r | }
\hline\rowcolor{lightgray}
Name & Description &  Address & Access \\ \hline
\endhead
\multicolumn{4}{|l|}{\textbf{PGM Data Registers}} \\ \hline
\hyperref[regdesc:EFUSEPGMDATANREG]{EFUSE\_PGM\_DATA0\_REG} & Register 0 that stores data to be programmed. & \hexprefix{}0000 & R/W \\ \hline
\hyperref[regdesc:EFUSEPGMDATANREG]{EFUSE\_PGM\_DATA1\_REG} & Register 1 that stores data to be programmed. & \hexprefix{}0004 & R/W \\ \hline
\hyperref[regdesc:EFUSEPGMDATANREG]{EFUSE\_PGM\_DATA2\_REG} & Register 2 that stores data to be programmed. & \hexprefix{}0008 & R/W \\ \hline
\hyperref[regdesc:EFUSEPGMDATANREG]{EFUSE\_PGM\_DATA3\_REG} & Register 3 that stores data to be programmed. & \hexprefix{}000C & R/W \\ \hline
\hyperref[regdesc:EFUSEPGMDATANREG]{EFUSE\_PGM\_DATA4\_REG} & Register 4 that stores data to be programmed. & \hexprefix{}0010 & R/W \\ \hline
\hyperref[regdesc:EFUSEPGMDATANREG]{EFUSE\_PGM\_DATA5\_REG} & Register 5 that stores data to be programmed. & \hexprefix{}0014 & R/W \\ \hline
\hyperref[regdesc:EFUSEPGMDATANREG]{EFUSE\_PGM\_DATA6\_REG} & Register 6 that stores data to be programmed. & \hexprefix{}0018 & R/W \\ \hline
\hyperref[regdesc:EFUSEPGMDATANREG]{EFUSE\_PGM\_DATA7\_REG} & Register 7 that stores data to be programmed. & \hexprefix{}001C & R/W \\ \hline
\hyperref[regdesc:EFUSEPGMCHECKVALUENREG]{EFUSE\_PGM\_CHECK\_VALUE0\_REG} & Register 0 that stores the RS code to be programmed. & \hexprefix{}0020 & R/W \\ \hline
\hyperref[regdesc:EFUSEPGMCHECKVALUENREG]{EFUSE\_PGM\_CHECK\_VALUE1\_REG} & Register 1 that stores the RS code to be programmed. & \hexprefix{}0024 & R/W \\ \hline
\hyperref[regdesc:EFUSEPGMCHECKVALUENREG]{EFUSE\_PGM\_CHECK\_VALUE2\_REG} & Register 2 that stores the RS code to be programmed. & \hexprefix{}0028 & R/W \\ \hline
\multicolumn{4}{|l|}{\textbf{Read Data Registers}} \\ \hline
\hyperref[regdesc:EFUSERDWRDISREG]{EFUSE\_RD\_WR\_DIS\_REG} & Register 0 of BLOCK0. & \hexprefix{}002C & RO \\ \hline
\hyperref[regdesc:EFUSERDREPEATDATA0REG]{EFUSE\_RD\_REPEAT\_DATA0\_REG} & Register 1 of BLOCK0. & \hexprefix{}0030 & RO \\ \hline
\hyperref[regdesc:EFUSERDREPEATDATA1REG]{EFUSE\_RD\_REPEAT\_DATA1\_REG} & Register 2 of BLOCK0. & \hexprefix{}0034 & RO \\ \hline
\hyperref[regdesc:EFUSERDREPEATDATA2REG]{EFUSE\_RD\_REPEAT\_DATA2\_REG} & Register 3 of BLOCK0. & \hexprefix{}0038 & RO \\ \hline
\hyperref[regdesc:EFUSERDREPEATDATA3REG]{EFUSE\_RD\_REPEAT\_DATA3\_REG} & Register 4 of BLOCK0. & \hexprefix{}003C & RO \\ \hline
\hyperref[regdesc:EFUSERDREPEATDATA4REG]{EFUSE\_RD\_REPEAT\_DATA4\_REG} & Register 5 of BLOCK0. & \hexprefix{}0040 & RO \\ \hline
\hyperref[regdesc:EFUSERDMACSPISYS0REG]{EFUSE\_RD\_MAC\_SPI\_SYS\_0\_REG} & Register 0 of BLOCK1. & \hexprefix{}0044 & RO \\ \hline
\hyperref[regdesc:EFUSERDMACSPISYS1REG]{EFUSE\_RD\_MAC\_SPI\_SYS\_1\_REG} & Register 1 of BLOCK1. & \hexprefix{}0048 & RO \\ \hline
\hyperref[regdesc:EFUSERDMACSPISYS2REG]{EFUSE\_RD\_MAC\_SPI\_SYS\_2\_REG} & Register 2 of BLOCK1. & \hexprefix{}004C & RO \\ \hline
\hyperref[regdesc:EFUSERDMACSPISYS3REG]{EFUSE\_RD\_MAC\_SPI\_SYS\_3\_REG} & Register 3 of BLOCK1. & \hexprefix{}0050 & RO \\ \hline
\hyperref[regdesc:EFUSERDMACSPISYS4REG]{EFUSE\_RD\_MAC\_SPI\_SYS\_4\_REG} & Register 4 of BLOCK1. & \hexprefix{}0054 & RO \\ \hline
\hyperref[regdesc:EFUSERDMACSPISYS5REG]{EFUSE\_RD\_MAC\_SPI\_SYS\_5\_REG} & Register 5 of BLOCK1. & \hexprefix{}0058 & RO \\ \hline
\hyperref[regdesc:EFUSERDSYSDATAPART1NREG]{EFUSE\_RD\_SYS\_DATA\_PART1\_0\_REG} & Register 0 of BLOCK2 (system). & \hexprefix{}005C & RO \\ \hline
\hyperref[regdesc:EFUSERDSYSDATAPART1NREG]{EFUSE\_RD\_SYS\_DATA\_PART1\_1\_REG} & Register 1 of BLOCK2 (system). & \hexprefix{}0060 & RO \\ \hline
\hyperref[regdesc:EFUSERDSYSDATAPART1NREG]{EFUSE\_RD\_SYS\_DATA\_PART1\_2\_REG} & Register 2 of BLOCK2 (system). & \hexprefix{}0064 & RO \\ \hline
\hyperref[regdesc:EFUSERDSYSDATAPART1NREG]{EFUSE\_RD\_SYS\_DATA\_PART1\_3\_REG} & Register 3 of BLOCK2 (system). & \hexprefix{}0068 & RO \\ \hline
\hyperref[regdesc:EFUSERDSYSDATAPART1NREG]{EFUSE\_RD\_SYS\_DATA\_PART1\_4\_REG} & Register 4 of BLOCK2 (system). & \hexprefix{}006C & RO \\ \hline
\hyperref[regdesc:EFUSERDSYSDATAPART1NREG]{EFUSE\_RD\_SYS\_DATA\_PART1\_5\_REG} & Register 5 of BLOCK2 (system). & \hexprefix{}0070 & RO \\ \hline
\hyperref[regdesc:EFUSERDSYSDATAPART1NREG]{EFUSE\_RD\_SYS\_DATA\_PART1\_6\_REG} & Register 6 of BLOCK2 (system). & \hexprefix{}0074 & RO \\ \hline
\hyperref[regdesc:EFUSERDSYSDATAPART1NREG]{EFUSE\_RD\_SYS\_DATA\_PART1\_7\_REG} & Register 7 of BLOCK2 (system). & \hexprefix{}0078 & RO \\ \hline
\hyperref[regdesc:EFUSERDUSRDATANREG]{EFUSE\_RD\_USR\_DATA0\_REG} & Register 0 of BLOCK3 (user). & \hexprefix{}007C & RO \\ \hline
\hyperref[regdesc:EFUSERDUSRDATANREG]{EFUSE\_RD\_USR\_DATA1\_REG} & Register 1 of BLOCK3 (user). & \hexprefix{}0080 & RO \\ \hline
\hyperref[regdesc:EFUSERDUSRDATANREG]{EFUSE\_RD\_USR\_DATA2\_REG} & Register 2 of BLOCK3 (user). & \hexprefix{}0084 & RO \\ \hline
\hyperref[regdesc:EFUSERDUSRDATANREG]{EFUSE\_RD\_USR\_DATA3\_REG} & Register 3 of BLOCK3 (user). & \hexprefix{}0088 & RO \\ \hline
\hyperref[regdesc:EFUSERDUSRDATANREG]{EFUSE\_RD\_USR\_DATA4\_REG} & Register 4 of BLOCK3 (user). & \hexprefix{}008C & RO \\ \hline
\hyperref[regdesc:EFUSERDUSRDATANREG]{EFUSE\_RD\_USR\_DATA5\_REG} & Register 5 of BLOCK3 (user). & \hexprefix{}0090 & RO \\ \hline
\hyperref[regdesc:EFUSERDUSRDATANREG]{EFUSE\_RD\_USR\_DATA6\_REG} & Register 6 of BLOCK3 (user). & \hexprefix{}0094 & RO \\ \hline
\hyperref[regdesc:EFUSERDUSRDATANREG]{EFUSE\_RD\_USR\_DATA7\_REG} & Register 7 of BLOCK3 (user). & \hexprefix{}0098 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY0DATANREG]{EFUSE\_RD\_KEY0\_DATA0\_REG} & Register 0 of BLOCK4 (KEY0). & \hexprefix{}009C & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY0DATANREG]{EFUSE\_RD\_KEY0\_DATA1\_REG} & Register 1 of BLOCK4 (KEY0). & \hexprefix{}00A0 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY0DATANREG]{EFUSE\_RD\_KEY0\_DATA2\_REG} & Register 2 of BLOCK4 (KEY0). & \hexprefix{}00A4 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY0DATANREG]{EFUSE\_RD\_KEY0\_DATA3\_REG} & Register 3 of BLOCK4 (KEY0). & \hexprefix{}00A8 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY0DATANREG]{EFUSE\_RD\_KEY0\_DATA4\_REG} & Register 4 of BLOCK4 (KEY0). & \hexprefix{}00AC & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY0DATANREG]{EFUSE\_RD\_KEY0\_DATA5\_REG} & Register 5 of BLOCK4 (KEY0). & \hexprefix{}00B0 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY0DATANREG]{EFUSE\_RD\_KEY0\_DATA6\_REG} & Register 6 of BLOCK4 (KEY0). & \hexprefix{}00B4 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY0DATANREG]{EFUSE\_RD\_KEY0\_DATA7\_REG} & Register 7 of BLOCK4 (KEY0). & \hexprefix{}00B8 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY1DATANREG]{EFUSE\_RD\_KEY1\_DATA0\_REG} & Register 0 of BLOCK5 (KEY1). & \hexprefix{}00BC & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY1DATANREG]{EFUSE\_RD\_KEY1\_DATA1\_REG} & Register 1 of BLOCK5 (KEY1). & \hexprefix{}00C0 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY1DATANREG]{EFUSE\_RD\_KEY1\_DATA2\_REG} & Register 2 of BLOCK5 (KEY1). & \hexprefix{}00C4 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY1DATANREG]{EFUSE\_RD\_KEY1\_DATA3\_REG} & Register 3 of BLOCK5 (KEY1). & \hexprefix{}00C8 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY1DATANREG]{EFUSE\_RD\_KEY1\_DATA4\_REG} & Register 4 of BLOCK5 (KEY1). & \hexprefix{}00CC & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY1DATANREG]{EFUSE\_RD\_KEY1\_DATA5\_REG} & Register 5 of BLOCK5 (KEY1). & \hexprefix{}00D0 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY1DATANREG]{EFUSE\_RD\_KEY1\_DATA6\_REG} & Register 6 of BLOCK5 (KEY1). & \hexprefix{}00D4 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY1DATANREG]{EFUSE\_RD\_KEY1\_DATA7\_REG} & Register 7 of BLOCK5 (KEY1). & \hexprefix{}00D8 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY2DATANREG]{EFUSE\_RD\_KEY2\_DATA0\_REG} & Register 0 of BLOCK6 (KEY2). & \hexprefix{}00DC & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY2DATANREG]{EFUSE\_RD\_KEY2\_DATA1\_REG} & Register 1 of BLOCK6 (KEY2). & \hexprefix{}00E0 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY2DATANREG]{EFUSE\_RD\_KEY2\_DATA2\_REG} & Register 2 of BLOCK6 (KEY2). & \hexprefix{}00E4 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY2DATANREG]{EFUSE\_RD\_KEY2\_DATA3\_REG} & Register 3 of BLOCK6 (KEY2). & \hexprefix{}00E8 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY2DATANREG]{EFUSE\_RD\_KEY2\_DATA4\_REG} & Register 4 of BLOCK6 (KEY2). & \hexprefix{}00EC & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY2DATANREG]{EFUSE\_RD\_KEY2\_DATA5\_REG} & Register 5 of BLOCK6 (KEY2). & \hexprefix{}00F0 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY2DATANREG]{EFUSE\_RD\_KEY2\_DATA6\_REG} & Register 6 of BLOCK6 (KEY2). & \hexprefix{}00F4 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY2DATANREG]{EFUSE\_RD\_KEY2\_DATA7\_REG} & Register 7 of BLOCK6 (KEY2). & \hexprefix{}00F8 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY3DATANREG]{EFUSE\_RD\_KEY3\_DATA0\_REG} & Register 0 of BLOCK7 (KEY3). & \hexprefix{}00FC & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY3DATANREG]{EFUSE\_RD\_KEY3\_DATA1\_REG} & Register 1 of BLOCK7 (KEY3). & \hexprefix{}0100 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY3DATANREG]{EFUSE\_RD\_KEY3\_DATA2\_REG} & Register 2 of BLOCK7 (KEY3). & \hexprefix{}0104 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY3DATANREG]{EFUSE\_RD\_KEY3\_DATA3\_REG} & Register 3 of BLOCK7 (KEY3). & \hexprefix{}0108 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY3DATANREG]{EFUSE\_RD\_KEY3\_DATA4\_REG} & Register 4 of BLOCK7 (KEY3). & \hexprefix{}010C & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY3DATANREG]{EFUSE\_RD\_KEY3\_DATA5\_REG} & Register 5 of BLOCK7 (KEY3). & \hexprefix{}0110 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY3DATANREG]{EFUSE\_RD\_KEY3\_DATA6\_REG} & Register 6 of BLOCK7 (KEY3). & \hexprefix{}0114 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY3DATANREG]{EFUSE\_RD\_KEY3\_DATA7\_REG} & Register 7 of BLOCK7 (KEY3). & \hexprefix{}0118 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY4DATANREG]{EFUSE\_RD\_KEY4\_DATA0\_REG} & Register 0 of BLOCK8 (KEY4). & \hexprefix{}011C & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY4DATANREG]{EFUSE\_RD\_KEY4\_DATA1\_REG} & Register 1 of BLOCK8 (KEY4). & \hexprefix{}0120 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY4DATANREG]{EFUSE\_RD\_KEY4\_DATA2\_REG} & Register 2 of BLOCK8 (KEY4). & \hexprefix{}0124 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY4DATANREG]{EFUSE\_RD\_KEY4\_DATA3\_REG} & Register 3 of BLOCK8 (KEY4). & \hexprefix{}0128 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY4DATANREG]{EFUSE\_RD\_KEY4\_DATA4\_REG} & Register 4 of BLOCK8 (KEY4). & \hexprefix{}012C & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY4DATANREG]{EFUSE\_RD\_KEY4\_DATA5\_REG} & Register 5 of BLOCK8 (KEY4). & \hexprefix{}0130 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY4DATANREG]{EFUSE\_RD\_KEY4\_DATA6\_REG} & Register 6 of BLOCK8 (KEY4). & \hexprefix{}0134 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY4DATANREG]{EFUSE\_RD\_KEY4\_DATA7\_REG} & Register 7 of BLOCK8 (KEY4). & \hexprefix{}0138 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY5DATANREG]{EFUSE\_RD\_KEY5\_DATA0\_REG} & Register 0 of BLOCK9 (KEY5). & \hexprefix{}013C & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY5DATANREG]{EFUSE\_RD\_KEY5\_DATA1\_REG} & Register 1 of BLOCK9 (KEY5). & \hexprefix{}0140 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY5DATANREG]{EFUSE\_RD\_KEY5\_DATA2\_REG} & Register 2 of BLOCK9 (KEY5). & \hexprefix{}0144 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY5DATANREG]{EFUSE\_RD\_KEY5\_DATA3\_REG} & Register 3 of BLOCK9 (KEY5). & \hexprefix{}0148 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY5DATANREG]{EFUSE\_RD\_KEY5\_DATA4\_REG} & Register 4 of BLOCK9 (KEY5). & \hexprefix{}014C & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY5DATANREG]{EFUSE\_RD\_KEY5\_DATA5\_REG} & Register 5 of BLOCK9 (KEY5). & \hexprefix{}0150 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY5DATANREG]{EFUSE\_RD\_KEY5\_DATA6\_REG} & Register 6 of BLOCK9 (KEY5). & \hexprefix{}0154 & RO \\ \hline
\hyperref[regdesc:EFUSERDKEY5DATANREG]{EFUSE\_RD\_KEY5\_DATA7\_REG} & Register 7 of BLOCK9 (KEY5). & \hexprefix{}0158 & RO \\ \hline
\hyperref[regdesc:EFUSERDSYSDATAPART2NREG]{EFUSE\_RD\_SYS\_DATA\_PART2\_0\_REG} & Register 0 of BLOCK10 (system). & \hexprefix{}015C & RO \\ \hline
\hyperref[regdesc:EFUSERDSYSDATAPART2NREG]{EFUSE\_RD\_SYS\_DATA\_PART2\_1\_REG} & Register 1 of BLOCK10 (system). & \hexprefix{}0160 & RO \\ \hline
\hyperref[regdesc:EFUSERDSYSDATAPART2NREG]{EFUSE\_RD\_SYS\_DATA\_PART2\_2\_REG} & Register 2 of BLOCK10 (system). & \hexprefix{}0164 & RO \\ \hline
\hyperref[regdesc:EFUSERDSYSDATAPART2NREG]{EFUSE\_RD\_SYS\_DATA\_PART2\_3\_REG} & Register 3 of BLOCK10 (system). & \hexprefix{}0168 & RO \\ \hline
\hyperref[regdesc:EFUSERDSYSDATAPART2NREG]{EFUSE\_RD\_SYS\_DATA\_PART2\_4\_REG} & Register 4 of BLOCK10 (system). & \hexprefix{}016C & RO \\ \hline
\hyperref[regdesc:EFUSERDSYSDATAPART2NREG]{EFUSE\_RD\_SYS\_DATA\_PART2\_5\_REG} & Register 5 of BLOCK10 (system). & \hexprefix{}0170 & RO \\ \hline
\hyperref[regdesc:EFUSERDSYSDATAPART2NREG]{EFUSE\_RD\_SYS\_DATA\_PART2\_6\_REG} & Register 6 of BLOCK10 (system). & \hexprefix{}0174 & RO \\ \hline
\hyperref[regdesc:EFUSERDSYSDATAPART2NREG]{EFUSE\_RD\_SYS\_DATA\_PART2\_7\_REG} & Register 7 of BLOCK10 (system). & \hexprefix{}0178 & RO \\ \hline
\multicolumn{4}{|l|}{\textbf{Error Status Registers}} \\ \hline
\hyperref[regdesc:EFUSERDREPEATERR0REG]{EFUSE\_RD\_REPEAT\_ERR0\_REG} & Programming error record register 0 of BLOCK0. & \hexprefix{}017C & RO \\ \hline
\hyperref[regdesc:EFUSERDREPEATERR1REG]{EFUSE\_RD\_REPEAT\_ERR1\_REG} & Programming error record register 1 of BLOCK0. & \hexprefix{}0180 & RO \\ \hline
\hyperref[regdesc:EFUSERDREPEATERR2REG]{EFUSE\_RD\_REPEAT\_ERR2\_REG} & Programming error record register 2 of BLOCK0. & \hexprefix{}0184 & RO \\ \hline
\hyperref[regdesc:EFUSERDREPEATERR3REG]{EFUSE\_RD\_REPEAT\_ERR3\_REG} & Programming error record register 3 of BLOCK0. & \hexprefix{}0188 & RO \\ \hline
\hyperref[regdesc:EFUSERDREPEATERR4REG]{EFUSE\_RD\_REPEAT\_ERR4\_REG} & Programming error record register 4 of BLOCK0. & \hexprefix{}0190 & RO \\ \hline
\hyperref[regdesc:EFUSERDRSERR0REG]{EFUSE\_RD\_RS\_ERR0\_REG} & Programming error record register 0 of BLOCK1-10. & \hexprefix{}01C0 & RO \\ \hline
\hyperref[regdesc:EFUSERDRSERR1REG]{EFUSE\_RD\_RS\_ERR1\_REG} & Programming error record register 1 of BLOCK1-10. & \hexprefix{}01C4 & RO \\ \hline
\multicolumn{4}{|l|}{\textbf{Control/Status Registers}} \\\hline
\hyperref[regdesc:EFUSECLKREG]{EFUSE\_CLK\_REG} & eFuse clock configuration register. & \hexprefix{}01C8 & R/W \\ \hline
\hyperref[regdesc:EFUSECONFREG]{EFUSE\_CONF\_REG} & eFuse operation mode configuration register. & \hexprefix{}01CC & R/W \\ \hline
\hyperref[regdesc:EFUSECMDREG]{EFUSE\_CMD\_REG} & eFuse command register. & \hexprefix{}01D4 & R/W \\ \hline
\hyperref[regdesc:EFUSEDACCONFREG]{EFUSE\_DAC\_CONF\_REG} & Controls the eFuse programming voltage. & \hexprefix{}01E8 & R/W \\ \hline
\hyperref[regdesc:EFUSESTATUSREG]{EFUSE\_STATUS\_REG} & eFuse status register. & \hexprefix{}01D0 & RO \\ \hline
\multicolumn{4}{|l|}{\textbf{Interrupt Registers}} \\ \hline
\hyperref[regdesc:EFUSEINTRAWREG]{EFUSE\_INT\_RAW\_REG} & eFuse raw interrupt register. & \hexprefix{}01D8 & RO \\ \hline
\hyperref[regdesc:EFUSEINTSTREG]{EFUSE\_INT\_ST\_REG} & eFuse interrupt status register. & \hexprefix{}01DC & RO \\ \hline
\hyperref[regdesc:EFUSEINTENAREG]{EFUSE\_INT\_ENA\_REG} & eFuse interrupt enable register. & \hexprefix{}01E0 & R/W \\ \hline
\hyperref[regdesc:EFUSEINTCLRREG]{EFUSE\_INT\_CLR\_REG} & eFuse interrupt clear register. & \hexprefix{}01E4 & WO \\ \hline
\multicolumn{4}{|l|}{\textbf{Configuration Registers}} \\ \hline
\hyperref[regdesc:EFUSERDTIMCONFREG]{EFUSE\_RD\_TIM\_CONF\_REG} & Configures read timing parameters. & \hexprefix{}01EC & R/W \\ \hline
\hyperref[regdesc:EFUSEWRTIMCONF0REG]{EFUSE\_WR\_TIM\_CONF0\_REG} & Configuration register 0 of eFuse programming timing parameters. & \hexprefix{}01F0 & R/W \\ \hline
\hyperref[regdesc:EFUSEWRTIMCONF1REG]{EFUSE\_WR\_TIM\_CONF1\_REG} & Configuration register 1 of eFuse programming timing parameters. & \hexprefix{}01F4 & R/W \\ \hline
\hyperref[regdesc:EFUSEWRTIMCONF2REG]{EFUSE\_WR\_TIM\_CONF2\_REG} & Configuration register 2 of eFuse programming timing parameters. & \hexprefix{}01F8 & R/W \\ \hline
\multicolumn{4}{|l|}{\textbf{Version Register}} \\ \hline
\hyperref[regdesc:EFUSEDATEREG]{EFUSE\_DATE\_REG} & Version control register. & \hexprefix{}01FC & R/W \\ \hline
\end{longtable}
