\begin{register}{H}{EFUSE\_PGM\_DATA\regindex{n}\_REG (\regindex{n}: 0-7)}{\hexprefix{}0000+4*\regindex{n}}\label{regdesc:EFUSEPGMDATANREG}
\regfield{EFUSE\_PGM\_DATA\_\regindex{n}}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEPGMDATAN}\item [EFUSE\_PGM\_DATA\_\regindex{n}] The content of the \regindex{n}th 32-bit data to be programmed. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_PGM\_CHECK\_VALUE\regindex{n}\_REG (\regindex{n}: 0-2)}{\hexprefix{}0020+4*\regindex{n}}\label{regdesc:EFUSEPGMCHECKVALUENREG}
\regfield{EFUSE\_PGM\_RS\_DATA\_\regindex{n}}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEPGMRSDATAN}\item [EFUSE\_PGM\_RS\_DATA\_\regindex{n}] The content of the \regindex{n}th 32-bit RS code to be programmed. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_WR\_DIS\_REG}{\hexprefix{}002C}\label{regdesc:EFUSERDWRDISREG}
\regfield{EFUSE\_WR\_DIS}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEWRDIS}\item [EFUSE\_WR\_DIS] Represents whether writing of individual eFuses is disabled. 1: Disabled. 0: Enabled. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_REPEAT\_DATA0\_REG}{\hexprefix{}0030}\label{regdesc:EFUSERDREPEATDATA0REG}
\regfield{(reserved)}{3}{29}{000}%
\regfield{EFUSE\_RPT4\_RESERVED0}{2}{27}{{\hexprefix{}0}}%
\regfield{EFUSE\_USB\_FORCE\_NOPERSIST}{1}{26}{{0}}%
\regfield{EFUSE\_EXT\_PHY\_ENABLE}{1}{25}{{0}}%
\regfield{EFUSE\_USB\_EXCHG\_PINS}{1}{24}{{0}}%
\regfield{(reserved)}{4}{20}{0000}%
\regfield{EFUSE\_DIS\_DOWNLOAD\_MANUAL\_ENCRYPT}{1}{19}{{0}}%
\regfield{EFUSE\_HARD\_DIS\_JTAG}{1}{18}{{0}}%
\regfield{EFUSE\_SOFT\_DIS\_JTAG}{1}{17}{{0}}%
\regfield{EFUSE\_RPT4\_RESERVED5}{1}{16}{{0}}%
\regfield{EFUSE\_DIS\_BOOT\_REMAP}{1}{15}{{0}}%
\regfield{EFUSE\_DIS\_CAN}{1}{14}{{0}}%
\regfield{EFUSE\_DIS\_USB}{1}{13}{{0}}%
\regfield{EFUSE\_DIS\_FORCE\_DOWNLOAD}{1}{12}{{0}}%
\regfield{EFUSE\_DIS\_DOWNLOAD\_DCACHE}{1}{11}{{0}}%
\regfield{EFUSE\_DIS\_DOWNLOAD\_ICACHE}{1}{10}{{0}}%
\regfield{EFUSE\_DIS\_DCACHE}{1}{9}{{0}}%
\regfield{EFUSE\_DIS\_ICACHE}{1}{8}{{0}}%
\regfield{EFUSE\_DIS\_RTC\_RAM\_BOOT}{1}{7}{{0}}%
\regfield{EFUSE\_RD\_DIS}{7}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSERDDIS}\item [EFUSE\_RD\_DIS] Represents whether users’ reading from BLOCK4 \verb+~+ 10 is disabled. 1: Disabled. 0: Enabled. (RO)
\label{fielddesc:EFUSEDISRTCRAMBOOT}\item [EFUSE\_DIS\_RTC\_RAM\_BOOT] Reserved. (RO)
\label{fielddesc:EFUSEDISICACHE}\item [EFUSE\_DIS\_ICACHE] Represents whether ICache is disabled or enabled. 1: Disabled. 0: Enabled. (RO)
\label{fielddesc:EFUSEDISDCACHE}\item [EFUSE\_DIS\_DCACHE] Represents whether DCache is disabled or enabled. 1: Disabled. 0: Enabled. (RO)
\label{fielddesc:EFUSEDISDOWNLOADICACHE}\item [EFUSE\_DIS\_DOWNLOAD\_ICACHE] Represents whether ICache is disabled in Download mode. 1: Disabled. 0: Enabled. (RO)
\label{fielddesc:EFUSEDISDOWNLOADDCACHE}\item [EFUSE\_DIS\_DOWNLOAD\_DCACHE] Represents whether Dcache is disabled in Download mode. 1: Disabled. 0: Enabled. (RO)
\label{fielddesc:EFUSEDISFORCEDOWNLOAD}\item [EFUSE\_DIS\_FORCE\_DOWNLOAD] Represents whether the function that forces chip into download mode is disabled. 1: Disabled. 0: Enabled. (RO)
\label{fielddesc:EFUSEDISUSB}\item [EFUSE\_DIS\_USB] Represents whether to disable USB OTG function. 1: Disabled. 0: Enabled. (RO)
\label{fielddesc:EFUSEDISCAN}\item [EFUSE\_DIS\_CAN] Represents whether to disable the TWAI Controller function. 1: Disabled. 0: Enabled. (RO)
\label{fielddesc:EFUSEDISBOOTREMAP}\item [EFUSE\_DIS\_BOOT\_REMAP] Represents whether to disable the capability to remap RAM to ROM address space. 1: Disabled. 0: Enabled. (RO)
\label{fielddesc:EFUSERPT4RESERVED5}\item [EFUSE\_RPT4\_RESERVED5] Reserved (used for four backups method). (RO)
\label{fielddesc:EFUSESOFTDISJTAG}\item
[EFUSE\_SOFT\_DIS\_JTAG] Represents whether JTAG is disabled in the soft way. 1: Disabled. It still can be restarted via HMAC. 0: Enabled. (RO)
\label{fielddesc:EFUSEHARDDISJTAG}\item [EFUSE\_HARD\_DIS\_JTAG] Represents whether JTAG is disabled in the hard way (permanently). 1: Disabled. 0: Enabled. (RO)
\label{fielddesc:EFUSEDISDOWNLOADMANUALENCRYPT}\item [EFUSE\_DIS\_DOWNLOAD\_MANUAL\_ENCRYPT] Represents whether flash encryption is disabled in Download boot mode. 1: Disabled. 0: Enabled. (RO)
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{EFUSE\_RD\_REPEAT\_DATA0\_REG}{\hexprefix{}0030}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\label{fielddesc:EFUSEUSBEXCHGPINS}\item [EFUSE\_USB\_EXCHG\_PINS] Represents whether or not USB D+ and D- pins are swapped. 1: Swapped. 0: Not swapped. (RO)
\label{fielddesc:EFUSEEXTPHYENABLE}\item [EFUSE\_EXT\_PHY\_ENABLE] Represents whether to enable external USB PHY. 1: Enabled. 0: Disabled. (RO)
\label{fielddesc:EFUSEUSBFORCENOPERSIST}\item [EFUSE\_USB\_FORCE\_NOPERSIST] Represents whether to force set USB BVALID to 1. 1: Set. 0: Not set. (RO)
\label{fielddesc:EFUSERPT4RESERVED0}\item [EFUSE\_RPT4\_RESERVED0] Reserved (used for four backups method). (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_REPEAT\_DATA1\_REG}{\hexprefix{}0034}\label{regdesc:EFUSERDREPEATDATA1REG}
\regfield{EFUSE\_KEY\_PURPOSE\_1}{4}{28}{{\hexprefix{}0}}%
\regfield{EFUSE\_KEY\_PURPOSE\_0}{4}{24}{{\hexprefix{}0}}%
\regfield{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE2}{1}{23}{{0}}%
\regfield{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE1}{1}{22}{{0}}%
\regfield{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE0}{1}{21}{{0}}%
\regfield{EFUSE\_SPI\_BOOT\_CRYPT\_CNT}{3}{18}{{\hexprefix{}0}}%
\regfield{EFUSE\_WDT\_DELAY\_SEL}{2}{16}{{\hexprefix{}0}}%
\regfield{(reserved)}{9}{7}{000000000}%
\regfield{EFUSE\_VDD\_SPI\_FORCE}{1}{6}{{0}}%
\regfield{EFUSE\_VDD\_SPI\_TIEH}{1}{5}{{0}}%
\regfield{EFUSE\_VDD\_SPI\_XPD}{1}{4}{{0}}%
\regfield{(reserved)}{4}{0}{0000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEVDDSPIXPD}\item [EFUSE\_VDD\_SPI\_XPD] Represents whether the VDD\_SPI regulator is powered on when VDD\_SPI\_FORCE is 1. 1: Powered on. 0: Not powered on. (RO)
\label{fielddesc:EFUSEVDDSPITIEH}\item [EFUSE\_VDD\_SPI\_TIEH] Represents the VDD\_SPI voltage when VDD\_SPI\_FORCE is 1. 1: VDD\_SPI connects to VDD\_RTC\_IO. 0: VDD\_SPI connects to 1.8 V LDO. (RO)
\label{fielddesc:EFUSEVDDSPIFORCE}\item [EFUSE\_VDD\_SPI\_FORCE] Represents whether to use XPD\_VDD\_PSI\_REG and VDD\_SPI\_TIEH to configure VDD\_SPI LDO. 1: Use. 0: Not use. (RO)
\label{fielddesc:EFUSEWDTDELAYSEL}\item [EFUSE\_WDT\_DELAY\_SEL] Represents RTC watchdog timeout threshold. Measurement unit: slow clock cycle. 00: 40000, 01: 80000, 10: 160000, 11:320000. (RO)
\label{fielddesc:EFUSESPIBOOTCRYPTCNT}\item [EFUSE\_SPI\_BOOT\_CRYPT\_CNT] Represents whether SPI boot encrypt/decrypt is disabled or enabled. Odd count of bits with a value of 1: Enabled. Even count of bits with a value of 1: Disabled. (RO)
\label{fielddesc:EFUSESECUREBOOTKEYREVOKE0}\item [EFUSE\_SECURE\_BOOT\_KEY\_REVOKE0] Represents whether or not the first secure boot key is revoked. 1: Revoked. 0: Not revoked. (RO)
\label{fielddesc:EFUSESECUREBOOTKEYREVOKE1}\item [EFUSE\_SECURE\_BOOT\_KEY\_REVOKE1] Represents whether or not the second secure boot key is revoked. 1: Revoked. 0: Not revoked. (RO)
\label{fielddesc:EFUSESECUREBOOTKEYREVOKE2}\item [EFUSE\_SECURE\_BOOT\_KEY\_REVOKE2] Represents whether or not the third secure boot key is revoked. 1: Revoked. 0: Not revoked. (RO)
\label{fielddesc:EFUSEKEYPURPOSE0}\item [EFUSE\_KEY\_PURPOSE\_0] Represents purpose of Key0. Refer to Table \ref{table: key_purpose}：\textit{Key Purpose Values}. (RO)
\label{fielddesc:EFUSEKEYPURPOSE1}\item [EFUSE\_KEY\_PURPOSE\_1] Represents purpose of Key1. Refer to Table \ref{table: key_purpose}：\textit{Key Purpose Values}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_REPEAT\_DATA2\_REG}{\hexprefix{}0038}\label{regdesc:EFUSERDREPEATDATA2REG}
\regfield{EFUSE\_FLASH\_TPUW}{4}{28}{{\hexprefix{}0}}%
\regfield{EFUSE\_RPT4\_RESERVED1}{6}{22}{{\hexprefix{}0}}%
\regfield{EFUSE\_SECURE\_BOOT\_AGGRESSIVE\_REVOKE}{1}{21}{{0}}%
\regfield{EFUSE\_SECURE\_BOOT\_EN}{1}{20}{{0}}%
\regfield{(reserved)}{4}{16}{0000}%
\regfield{EFUSE\_KEY\_PURPOSE\_5}{4}{12}{{\hexprefix{}0}}%
\regfield{EFUSE\_KEY\_PURPOSE\_4}{4}{8}{{\hexprefix{}0}}%
\regfield{EFUSE\_KEY\_PURPOSE\_3}{4}{4}{{\hexprefix{}0}}%
\regfield{EFUSE\_KEY\_PURPOSE\_2}{4}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEKEYPURPOSE2}\item [EFUSE\_KEY\_PURPOSE\_2] Represents purpose of Key2. Refer to Table \ref{table: key_purpose}：\textit{Key Purpose Values}. (RO)
\label{fielddesc:EFUSEKEYPURPOSE3}\item [EFUSE\_KEY\_PURPOSE\_3] Represents purpose of Key3. Refer to Table \ref{table: key_purpose}：\textit{Key Purpose Values}. (RO)
\label{fielddesc:EFUSEKEYPURPOSE4}\item [EFUSE\_KEY\_PURPOSE\_4] Represents purpose of Key4. Refer to Table \ref{table: key_purpose}：\textit{Key Purpose Values}. (RO)
\label{fielddesc:EFUSEKEYPURPOSE5}\item [EFUSE\_KEY\_PURPOSE\_5] Represents purpose of Key5. Refer to Table \ref{table: key_purpose}：\textit{Key Purpose Values}. (RO)
\label{fielddesc:EFUSESECUREBOOTEN}\item [EFUSE\_SECURE\_BOOT\_EN] Represents whether secure boot is enabled or disabled. 1: Enabled. 0: Disabled. (RO)
\label{fielddesc:EFUSESECUREBOOTAGGRESSIVEREVOKE}\item [EFUSE\_SECURE\_BOOT\_AGGRESSIVE\_REVOKE] Represents whether aggressive revoke of secure boot keys is enabled or disabled. 1: Enabled. 0: Disabled. (RO)
\label{fielddesc:EFUSERPT4RESERVED1}\item [EFUSE\_RPT4\_RESERVED1] Reserved (used for four backups method). (RO)
\label{fielddesc:EFUSEFLASHTPUW}\item [EFUSE\_FLASH\_TPUW] Represents flash waiting time after power-up. Measurement unit: ms. If the value is less than 15, the waiting time is the configurable value. Otherwise, the waiting time is always 30ms. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_REPEAT\_DATA3\_REG}{\hexprefix{}003C}\label{regdesc:EFUSERDREPEATDATA3REG}
\regfield{EFUSE\_RPT4\_RESERVED2}{5}{27}{{\hexprefix{}0}}%
\regfield{EFUSE\_SECURE\_VERSION}{16}{11}{{\hexprefix{}00}}%
\regfield{EFUSE\_FORCE\_SEND\_RESUME}{1}{10}{{0}}%
\regfield{EFUSE\_FLASH\_TYPE}{1}{9}{{0}}%
\regfield{EFUSE\_PIN\_POWER\_SELECTION}{1}{8}{{0}}%
\regfield{EFUSE\_UART\_PRINT\_CONTROL}{2}{6}{{\hexprefix{}0}}%
\regfield{EFUSE\_ENABLE\_SECURITY\_DOWNLOAD}{1}{5}{{0}}%
\regfield{EFUSE\_DIS\_USB\_DOWNLOAD\_MODE}{1}{4}{{0}}%
\regfield{EFUSE\_RPT4\_RESERVED3}{1}{3}{{0}}%
\regfield{EFUSE\_UART\_PRINT\_CHANNEL}{1}{2}{{0}}%
\regfield{EFUSE\_DIS\_LEGACY\_SPI\_BOOT}{1}{1}{{0}}%
\regfield{EFUSE\_DIS\_DOWNLOAD\_MODE}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEDISDOWNLOADMODE}\item [EFUSE\_DIS\_DOWNLOAD\_MODE] Represents whether download mode is disabled or enabled. 1: Disabled. 0: Enabled. (RO)
\label{fielddesc:EFUSEDISLEGACYSPIBOOT}\item [EFUSE\_DIS\_LEGACY\_SPI\_BOOT] Represents whether Legacy SPI boot mode is disabled. 1: Disabled. 0: Enabled. (RO)
\label{fielddesc:EFUSEUARTPRINTCHANNEL}\item [EFUSE\_UART\_PRINT\_CHANNEL] Represents the default UART for printing boot messages. 0: UART0; 1: UART1. (RO)
\label{fielddesc:EFUSERPT4RESERVED3}\item [EFUSE\_RPT4\_RESERVED3] Reserved (used for four backups method). (RO)
\label{fielddesc:EFUSEDISUSBDOWNLOADMODE}\item [EFUSE\_DIS\_USB\_DOWNLOAD\_MODE] Represents whether USB OTG is disabled in UART download boot mode. 1: Disabled. 0: Enabled. (RO)
\label{fielddesc:EFUSEENABLESECURITYDOWNLOAD}\item [EFUSE\_ENABLE\_SECURITY\_DOWNLOAD] Represents whether secure UART download mode is enabled (read/write flash only). 1: Enabled. 0: Disabled. (RO)
\label{fielddesc:EFUSEUARTPRINTCONTROL}\item [EFUSE\_UART\_PRINT\_CONTROL] Represents the default UART boot message output mode.
00: Enabled.
01: Enable when GPIO46 is low at reset.
10: Enable when GPIO46 is high at reset.
11: Disabled. (RO)
\label{fielddesc:EFUSEPINPOWERSELECTION}\item [EFUSE\_PIN\_POWER\_SELECTION] Represents the default power supply for GPIO33 \verb+~+ GPIO37 is set when SPI flash is initialized. 0: VDD3P3\_CPU. 1: VDD\_SPI. (RO)
\label{fielddesc:EFUSEFLASHTYPE}\item [EFUSE\_FLASH\_TYPE] Represents the SPI flash type. 0: Maximum four data lines. 1: Eight data lines. (RO)
\label{fielddesc:EFUSEFORCESENDRESUME}\item [EFUSE\_FORCE\_SEND\_RESUME] Represents whether or not to force ROM code to send a resume command during SPI boot. 1: Send. 0: Not send. (RO)
\label{fielddesc:EFUSESECUREVERSION}\item [EFUSE\_SECURE\_VERSION] Represents the values of version control register (used by ESP-IDF anti-rollback feature). (RO)
\label{fielddesc:EFUSERPT4RESERVED2}\item [EFUSE\_RPT4\_RESERVED2] Reserved (used for four backups method). (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_REPEAT\_DATA4\_REG}{\hexprefix{}0040}\label{regdesc:EFUSERDREPEATDATA4REG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{EFUSE\_RPT4\_RESERVED4}{24}{0}{{\hexprefix{}0000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSERPT4RESERVED4}\item [EFUSE\_RPT4\_RESERVED4] Reserved (used for four backups method). (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_MAC\_SPI\_SYS\_0\_REG}{\hexprefix{}0044}\label{regdesc:EFUSERDMACSPISYS0REG}
\regfield{EFUSE\_MAC\_0}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEMAC0}\item [EFUSE\_MAC\_0] Stores the low 32 bits of MAC address. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_MAC\_SPI\_SYS\_1\_REG}{\hexprefix{}0048}\label{regdesc:EFUSERDMACSPISYS1REG}
\regfield{EFUSE\_SPI\_PAD\_CONF\_0}{16}{16}{{\hexprefix{}00}}%
\regfield{EFUSE\_MAC\_1}{16}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEMAC1}\item [EFUSE\_MAC\_1] Stores the high 16 bits of MAC address. (RO)
\label{fielddesc:EFUSESPIPADCONF0}\item [EFUSE\_SPI\_PAD\_CONF\_0] Stores the zeroth part of SPI\_PAD\_CONF. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_MAC\_SPI\_SYS\_2\_REG}{\hexprefix{}004C}\label{regdesc:EFUSERDMACSPISYS2REG}
\regfield{EFUSE\_SPI\_PAD\_CONF\_1}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSESPIPADCONF1}\item [EFUSE\_SPI\_PAD\_CONF\_1] Stores the first part of SPI\_PAD\_CONF. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_MAC\_SPI\_SYS\_3\_REG}{\hexprefix{}0050}\label{regdesc:EFUSERDMACSPISYS3REG}
\regfield{EFUSE\_SYS\_DATA\_PART0\_0}{14}{18}{{\hexprefix{}00}}%
\regfield{EFUSE\_SPI\_PAD\_CONF\_2}{18}{0}{{\hexprefix{}000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSESPIPADCONF2}\item [EFUSE\_SPI\_PAD\_CONF\_2] Stores the second part of SPI\_PAD\_CONF. (RO)
\label{fielddesc:EFUSESYSDATAPART00}\item [EFUSE\_SYS\_DATA\_PART0\_0] Stores the zeroth part  of the zeroth part of system data. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_MAC\_SPI\_SYS\_4\_REG}{\hexprefix{}0054}\label{regdesc:EFUSERDMACSPISYS4REG}
\regfield{EFUSE\_SYS\_DATA\_PART0\_1}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSESYSDATAPART01}\item [EFUSE\_SYS\_DATA\_PART0\_1] Stores the fist part of the zeroth part of system data. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_MAC\_SPI\_SYS\_5\_REG}{\hexprefix{}0058}\label{regdesc:EFUSERDMACSPISYS5REG}
\regfield{EFUSE\_SYS\_DATA\_PART0\_2}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSESYSDATAPART02}\item [EFUSE\_SYS\_DATA\_PART0\_2] Stores the second part of the zeroth part of system data. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_SYS\_DATA\_PART1\_\regindex{n}\_REG (\regindex{n}: 0-7)}{\hexprefix{}005C+4*\regindex{n}}\label{regdesc:EFUSERDSYSDATAPART1NREG}
\regfield{EFUSE\_SYS\_DATA\_PART1\_\regindex{n}}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSESYSDATAPART1N}\item [EFUSE\_SYS\_DATA\_PART1\_\regindex{n}] Stores the \regindex{n}th 32 bits of the first part of system data. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_USR\_DATA\regindex{n}\_REG (\regindex{n}: 0-7)}{\hexprefix{}007C+4*\regindex{n}}\label{regdesc:EFUSERDUSRDATANREG}
\regfield{EFUSE\_USR\_DATA\regindex{n}}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEUSRDATAN}\item [EFUSE\_USR\_DATA\regindex{n}] Stores the \regindex{n}th 32 bits of BLOCK3 (user). (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_KEY0\_DATA\regindex{n}\_REG (\regindex{n}: 0-7)}{\hexprefix{}009C+4*\regindex{n}}\label{regdesc:EFUSERDKEY0DATANREG}
\regfield{EFUSE\_KEY0\_DATA\regindex{n}}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEKEY0DATAN}\item [EFUSE\_KEY0\_DATA\regindex{n}] Stores the \regindex{n}th 32 bits of KEY0. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_KEY1\_DATA\regindex{n}\_REG (\regindex{n}: 0-7)}{\hexprefix{}00BC+4*\regindex{n}}\label{regdesc:EFUSERDKEY1DATANREG}
\regfield{EFUSE\_KEY1\_DATA\regindex{n}}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEKEY1DATAN}\item [EFUSE\_KEY1\_DATA\regindex{n}] Stores the \regindex{n}th 32 bits of KEY1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_KEY2\_DATA\regindex{n}\_REG (\regindex{n}: 0-7)}{\hexprefix{}00DC+4*\regindex{n}}\label{regdesc:EFUSERDKEY2DATANREG}
\regfield{EFUSE\_KEY2\_DATA\regindex{n}}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEKEY2DATAN}\item [EFUSE\_KEY2\_DATA\regindex{n}] Stores the \regindex{n}th 32 bits of KEY2. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_KEY3\_DATA\regindex{n}\_REG (\regindex{n}: 0-7)}{\hexprefix{}00FC+4*\regindex{n}}\label{regdesc:EFUSERDKEY3DATANREG}
\regfield{EFUSE\_KEY3\_DATA\regindex{n}}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEKEY3DATAN}\item [EFUSE\_KEY3\_DATA\regindex{n}] Stores the \regindex{n}th 32 bits of KEY3. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_KEY4\_DATA\regindex{n}\_REG (\regindex{n}: 0-7)}{\hexprefix{}011C+4*\regindex{n}}\label{regdesc:EFUSERDKEY4DATANREG}
\regfield{EFUSE\_KEY4\_DATA\regindex{n}}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEKEY4DATAN}\item [EFUSE\_KEY4\_DATA\regindex{n}] Stores the \regindex{n}th 32 bits of KEY4. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_KEY5\_DATA\regindex{n}\_REG (\regindex{n}: 0-7)}{\hexprefix{}013C+4*\regindex{n}}\label{regdesc:EFUSERDKEY5DATANREG}
\regfield{EFUSE\_KEY5\_DATA\regindex{n}}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEKEY5DATAN}\item [EFUSE\_KEY5\_DATA\regindex{n}] Stores the \regindex{n}th 32 bits of KEY5. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_SYS\_DATA\_PART2\_\regindex{n}\_REG (\regindex{n}: 0-7)}{\hexprefix{}015C+4*\regindex{n}}\label{regdesc:EFUSERDSYSDATAPART2NREG}
\regfield{EFUSE\_SYS\_DATA\_PART2\_\regindex{n}}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSESYSDATAPART2N}\item [EFUSE\_SYS\_DATA\_PART2\_\regindex{n}] Stores the \regindex{n}th 32 bits of the 2nd part of system data. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_REPEAT\_ERR0\_REG}{\hexprefix{}017C}\label{regdesc:EFUSERDREPEATERR0REG}
\regfield{(reserved)}{3}{29}{000}%
\regfield{EFUSE\_RPT4\_RESERVED0\_ERR}{2}{27}{{\hexprefix{}0}}%
\regfield{EFUSE\_USB\_FORCE\_NOPERSIST\_ERR}{1}{26}{{0}}%
\regfield{EFUSE\_EXT\_PHY\_ENABLE\_ERR}{1}{25}{{0}}%
\regfield{EFUSE\_USB\_EXCHG\_PINS\_ERR}{1}{24}{{0}}%
\regfield{(reserved)}{4}{20}{0000}%
\regfield{EFUSE\_DIS\_DOWNLOAD\_MANUAL\_ENCRYPT\_ERR}{1}{19}{{0}}%
\regfield{EFUSE\_HARD\_DIS\_JTAG\_ERR}{1}{18}{{0}}%
\regfield{EFUSE\_SOFT\_DIS\_JTAG\_ERR}{1}{17}{{0}}%
\regfield{EFUSE\_RPT4\_RESERVED5\_ERR}{1}{16}{{0}}%
\regfield{EFUSE\_DIS\_BOOT\_REMAP\_ERR}{1}{15}{{0}}%
\regfield{EFUSE\_DIS\_CAN\_ERR}{1}{14}{{0}}%
\regfield{EFUSE\_DIS\_USB\_ERR}{1}{13}{{0}}%
\regfield{EFUSE\_DIS\_FORCE\_DOWNLOAD\_ERR}{1}{12}{{0}}%
\regfield{EFUSE\_DIS\_DOWNLOAD\_DCACHE\_ERR}{1}{11}{{0}}%
\regfield{EFUSE\_DIS\_DOWNLOAD\_ICACHE\_ERR}{1}{10}{{0}}%
\regfield{EFUSE\_DIS\_DCACHE\_ERR}{1}{9}{{0}}%
\regfield{EFUSE\_DIS\_ICACHE\_ERR}{1}{8}{{0}}%
\regfield{EFUSE\_DIS\_RTC\_RAM\_BOOT\_ERR}{1}{7}{{0}}%
\regfield{EFUSE\_RD\_DIS\_ERR}{7}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSERDDISERR}\item [EFUSE\_RD\_DIS\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSERDDIS]{EFUSE\_RD\_DIS}. (RO)
\label{fielddesc:EFUSEDISRTCRAMBOOTERR}\item [EFUSE\_DIS\_RTC\_RAM\_BOOT\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEDISRTCRAMBOOT]{EFUSE\_DIS\_RTC\_RAM\_BOOT}. (RO)
\label{fielddesc:EFUSEDISICACHEERR}\item [EFUSE\_DIS\_ICACHE\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEDISICACHE]{EFUSE\_DIS\_ICACHE}. (RO)
\label{fielddesc:EFUSEDISDCACHEERR}\item [EFUSE\_DIS\_DCACHE\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEDISDCACHE]{EFUSE\_DIS\_DCACHE}. (RO)
\label{fielddesc:EFUSEDISDOWNLOADICACHEERR}\item [EFUSE\_DIS\_DOWNLOAD\_ICACHE\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEDISDOWNLOADICACHE]{EFUSE\_DIS\_DOWNLOAD\_ICACHE}. (RO)
\label{fielddesc:EFUSEDISDOWNLOADDCACHEERR}\item [EFUSE\_DIS\_DOWNLOAD\_DCACHE\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEDISDOWNLOADDCACHE]{EFUSE\_DIS\_DOWNLOAD\_DCACHE}. (RO)
\label{fielddesc:EFUSEDISFORCEDOWNLOADERR}\item [EFUSE\_DIS\_FORCE\_DOWNLOAD\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEDISFORCEDOWNLOAD]{EFUSE\_DIS\_FORCE\_DOWNLOAD}. (RO)
\label{fielddesc:EFUSEDISUSBERR}\item [EFUSE\_DIS\_USB\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEDISUSB]{EFUSE\_DIS\_USB}. (RO)
\label{fielddesc:EFUSEDISCANERR}\item [EFUSE\_DIS\_CAN\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEDISCAN]{EFUSE\_DIS\_CAN}. (RO)
\label{fielddesc:EFUSEDISBOOTREMAPERR}\item [EFUSE\_DIS\_BOOT\_REMAP\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEDISBOOTREMAP]{EFUSE\_DIS\_BOOT\_REMAP}. (RO)
\label{fielddesc:EFUSERPT4RESERVED5ERR}\item [EFUSE\_RPT4\_RESERVED5\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSERPT4RESERVED5]{EFUSE\_RPT4\_RESERVED5}. (RO)
\label{fielddesc:EFUSESOFTDISJTAGERR}\item [EFUSE\_SOFT\_DIS\_JTAG\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSESOFTDISJTAG]{EFUSE\_SOFT\_DIS\_JTAG}. (RO)
\label{fielddesc:EFUSEHARDDISJTAGERR}\item
[EFUSE\_HARD\_DIS\_JTAG\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEHARDDISJTAG]{EFUSE\_HARD\_DIS\_JTAG}. (RO)
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{EFUSE\_RD\_REPEAT\_ERR0\_REG}{\hexprefix{}017C}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\label{fielddesc:EFUSEDISDOWNLOADMANUALENCRYPTERR}\item [EFUSE\_DIS\_DOWNLOAD\_MANUAL\_ENCRYPT\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEDISDOWNLOADMANUALENCRYPT]{EFUSE\_DIS\_DOWNLOAD\_MANUAL\_ENCRYPT}. (RO)
\label{fielddesc:EFUSEUSBEXCHGPINSERR}\item [EFUSE\_USB\_EXCHG\_PINS\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEUSBEXCHGPINS]{EFUSE\_USB\_EXCHG\_PINS}. (RO)
\label{fielddesc:EFUSEEXTPHYENABLEERR}\item [EFUSE\_EXT\_PHY\_ENABLE\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEEXTPHYENABLE]{EFUSE\_EXT\_PHY\_ENABLE}. (RO)
\label{fielddesc:EFUSEUSBFORCENOPERSISTERR}\item [EFUSE\_USB\_FORCE\_NOPERSIST\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEUSBFORCENOPERSIST]{EFUSE\_USB\_FORCE\_NOPERSIST}. (RO)
\label{fielddesc:EFUSERPT4RESERVED0ERR}\item [EFUSE\_RPT4\_RESERVED0\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSERPT4RESERVED0]{EFUSE\_RPT4\_RESERVED0}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_REPEAT\_ERR1\_REG}{\hexprefix{}0180}\label{regdesc:EFUSERDREPEATERR1REG}
\regfield{EFUSE\_KEY\_PURPOSE\_1\_ERR}{4}{28}{{\hexprefix{}0}}%
\regfield{EFUSE\_KEY\_PURPOSE\_0\_ERR}{4}{24}{{\hexprefix{}0}}%
\regfield{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE2\_ERR}{1}{23}{{0}}%
\regfield{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE1\_ERR}{1}{22}{{0}}%
\regfield{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE0\_ERR}{1}{21}{{0}}%
\regfield{EFUSE\_SPI\_BOOT\_CRYPT\_CNT\_ERR}{3}{18}{{\hexprefix{}0}}%
\regfield{EFUSE\_WDT\_DELAY\_SEL\_ERR}{2}{16}{{\hexprefix{}0}}%
\regfield{(reserved)}{9}{7}{000000000}%
\regfield{EFUSE\_VDD\_SPI\_FORCE\_ERR}{1}{6}{{0}}%
\regfield{EFUSE\_VDD\_SPI\_TIEH\_ERR}{1}{5}{{0}}%
\regfield{EFUSE\_VDD\_SPI\_XPD\_ERR}{1}{4}{{0}}%
\regfield{(reserved)}{4}{0}{0000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEVDDSPIXPDERR}\item [EFUSE\_VDD\_SPI\_XPD\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEVDDSPIXPD]{EFUSE\_VDD\_SPI\_XPD}. (RO)
\label{fielddesc:EFUSEVDDSPITIEHERR}\item [EFUSE\_VDD\_SPI\_TIEH\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEVDDSPITIEH]{EFUSE\_VDD\_SPI\_TIEH}. (RO)
\label{fielddesc:EFUSEVDDSPIFORCEERR}\item [EFUSE\_VDD\_SPI\_FORCE\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEVDDSPIFORCE]{EFUSE\_VDD\_SPI\_FORCE}. (RO)
\label{fielddesc:EFUSEWDTDELAYSELERR}\item [EFUSE\_WDT\_DELAY\_SEL\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEWDTDELAYSEL]{EFUSE\_WDT\_DELAY\_SEL}. (RO)
\label{fielddesc:EFUSESPIBOOTCRYPTCNTERR}\item [EFUSE\_SPI\_BOOT\_CRYPT\_CNT\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSESPIBOOTCRYPTCNT]{EFUSE\_SPI\_BOOT\_CRYPT\_CNT}. (RO)
\label{fielddesc:EFUSESECUREBOOTKEYREVOKE0ERR}\item [EFUSE\_SECURE\_BOOT\_KEY\_REVOKE0\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE0]{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE0}. (RO)
\label{fielddesc:EFUSESECUREBOOTKEYREVOKE1ERR}\item [EFUSE\_SECURE\_BOOT\_KEY\_REVOKE1\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE1]{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE1}. (RO)
\label{fielddesc:EFUSESECUREBOOTKEYREVOKE2ERR}\item [EFUSE\_SECURE\_BOOT\_KEY\_REVOKE2\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE2]{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE2}. (RO)
\label{fielddesc:EFUSEKEYPURPOSE0ERR}\item [EFUSE\_KEY\_PURPOSE\_0\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEKEYPURPOSE0]{EFUSE\_KEY\_PURPOSE\_0}. (RO)
\label{fielddesc:EFUSEKEYPURPOSE1ERR}\item [EFUSE\_KEY\_PURPOSE\_1\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEKEYPURPOSE1]{EFUSE\_KEY\_PURPOSE\_1}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_REPEAT\_ERR2\_REG}{\hexprefix{}0184}\label{regdesc:EFUSERDREPEATERR2REG}
\regfield{EFUSE\_FLASH\_TPUW\_ERR}{4}{28}{{\hexprefix{}0}}%
\regfield{EFUSE\_RPT4\_RESERVED1\_ERR}{6}{22}{{\hexprefix{}0}}%
\regfield{EFUSE\_SECURE\_BOOT\_AGGRESSIVE\_REVOKE\_ERR}{1}{21}{{0}}%
\regfield{EFUSE\_SECURE\_BOOT\_EN\_ERR}{1}{20}{{0}}%
\regfield{(reserved)}{4}{16}{0000}%
\regfield{EFUSE\_KEY\_PURPOSE\_5\_ERR}{4}{12}{{\hexprefix{}0}}%
\regfield{EFUSE\_KEY\_PURPOSE\_4\_ERR}{4}{8}{{\hexprefix{}0}}%
\regfield{EFUSE\_KEY\_PURPOSE\_3\_ERR}{4}{4}{{\hexprefix{}0}}%
\regfield{EFUSE\_KEY\_PURPOSE\_2\_ERR}{4}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEKEYPURPOSE2ERR}\item [EFUSE\_KEY\_PURPOSE\_2\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEKEYPURPOSE2]{EFUSE\_KEY\_PURPOSE\_2}. (RO)
\label{fielddesc:EFUSEKEYPURPOSE3ERR}\item [EFUSE\_KEY\_PURPOSE\_3\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEKEYPURPOSE3]{EFUSE\_KEY\_PURPOSE\_3}. (RO)
\label{fielddesc:EFUSEKEYPURPOSE4ERR}\item [EFUSE\_KEY\_PURPOSE\_4\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEKEYPURPOSE4]{EFUSE\_KEY\_PURPOSE\_4}. (RO)
\label{fielddesc:EFUSEKEYPURPOSE5ERR}\item [EFUSE\_KEY\_PURPOSE\_5\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEKEYPURPOSE5]{EFUSE\_KEY\_PURPOSE\_5}. (RO)
\label{fielddesc:EFUSESECUREBOOTENERR}\item [EFUSE\_SECURE\_BOOT\_EN\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSESECUREBOOTEN]{EFUSE\_SECURE\_BOOT\_EN}. (RO)
\label{fielddesc:EFUSESECUREBOOTAGGRESSIVEREVOKEERR}\item [EFUSE\_SECURE\_BOOT\_AGGRESSIVE\_REVOKE\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSESECUREBOOTAGGRESSIVEREVOKE]{EFUSE\_SECURE\_BOOT\_AGGRESSIVE\_REVOKE}. (RO)
\label{fielddesc:EFUSERPT4RESERVED1ERR}\item [EFUSE\_RPT4\_RESERVED1\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSERPT4RESERVED1]{EFUSE\_RPT4\_RESERVED1}. (RO)
\label{fielddesc:EFUSEFLASHTPUWERR}\item [EFUSE\_FLASH\_TPUW\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEFLASHTPUW]{EFUSE\_FLASH\_TPUW}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_REPEAT\_ERR3\_REG}{\hexprefix{}0188}\label{regdesc:EFUSERDREPEATERR3REG}
\regfield{EFUSE\_RPT4\_RESERVED2\_ERR}{5}{27}{{\hexprefix{}0}}%
\regfield{EFUSE\_SECURE\_VERSION\_ERR}{16}{11}{{\hexprefix{}00}}%
\regfield{EFUSE\_FORCE\_SEND\_RESUME\_ERR}{1}{10}{{0}}%
\regfield{EFUSE\_FLASH\_TYPE\_ERR}{1}{9}{{0}}%
\regfield{EFUSE\_PIN\_POWER\_SELECTION\_ERR}{1}{8}{{0}}%
\regfield{EFUSE\_UART\_PRINT\_CONTROL\_ERR}{2}{6}{{\hexprefix{}0}}%
\regfield{EFUSE\_ENABLE\_SECURITY\_DOWNLOAD\_ERR}{1}{5}{{0}}%
\regfield{EFUSE\_DIS\_USB\_DOWNLOAD\_MODE\_ERR}{1}{4}{{0}}%
\regfield{EFUSE\_RPT4\_RESERVED3\_ERR}{1}{3}{{0}}%
\regfield{EFUSE\_UART\_PRINT\_CHANNEL\_ERR}{1}{2}{{0}}%
\regfield{EFUSE\_DIS\_LEGACY\_SPI\_BOOT\_ERR}{1}{1}{{0}}%
\regfield{EFUSE\_DIS\_DOWNLOAD\_MODE\_ERR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEDISDOWNLOADMODEERR}\item [EFUSE\_DIS\_DOWNLOAD\_MODE\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEDISDOWNLOADMODE]{EFUSE\_DIS\_DOWNLOAD\_MODE}. (RO)
\label{fielddesc:EFUSEDISLEGACYSPIBOOTERR}\item [EFUSE\_DIS\_LEGACY\_SPI\_BOOT\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEDISLEGACYSPIBOOT]{EFUSE\_DIS\_LEGACY\_SPI\_BOOT}. (RO)
\label{fielddesc:EFUSEUARTPRINTCHANNELERR}\item [EFUSE\_UART\_PRINT\_CHANNEL\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEUARTPRINTCHANNEL]{EFUSE\_UART\_PRINT\_CHANNEL}. (RO)
\label{fielddesc:EFUSERPT4RESERVED3ERR}\item [EFUSE\_RPT4\_RESERVED3\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSERPT4RESERVED3]{EFUSE\_RPT4\_RESERVED3}. (RO)
\label{fielddesc:EFUSEDISUSBDOWNLOADMODEERR}\item [EFUSE\_DIS\_USB\_DOWNLOAD\_MODE\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEDISUSB]{EFUSE\_DIS\_USB}\_DOWNLOAD\_MODE. (RO)
\label{fielddesc:EFUSEENABLESECURITYDOWNLOADERR}\item [EFUSE\_ENABLE\_SECURITY\_DOWNLOAD\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEENABLESECURITYDOWNLOAD]{EFUSE\_ENABLE\_SECURITY\_DOWNLOAD}. (RO)
\label{fielddesc:EFUSEUARTPRINTCONTROLERR}\item [EFUSE\_UART\_PRINT\_CONTROL\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEUARTPRINTCONTROL]{EFUSE\_UART\_PRINT\_CONTROL}. (RO)
\label{fielddesc:EFUSEPINPOWERSELECTIONERR}\item [EFUSE\_PIN\_POWER\_SELECTION\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEPINPOWERSELECTION]{EFUSE\_PIN\_POWER\_SELECTION}. (RO)
\label{fielddesc:EFUSEFLASHTYPEERR}\item [EFUSE\_FLASH\_TYPE\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEFLASHTYPE]{EFUSE\_FLASH\_TYPE}. (RO)
\label{fielddesc:EFUSEFORCESENDRESUMEERR}\item [EFUSE\_FORCE\_SEND\_RESUME\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSEFORCESENDRESUME]{EFUSE\_FORCE\_SEND\_RESUME}. (RO)
\label{fielddesc:EFUSESECUREVERSIONERR}\item [EFUSE\_SECURE\_VERSION\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSESECUREVERSION]{EFUSE\_SECURE\_VERSION}. (RO)
\label{fielddesc:EFUSERPT4RESERVED2ERR}\item [EFUSE\_RPT4\_RESERVED2\_ERR] Any bit equal to 1 denotes a programming error in \hyperref[fielddesc:EFUSERPT4RESERVED2]{EFUSE\_RPT4\_RESERVED2}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_REPEAT\_ERR4\_REG}{\hexprefix{}0190}\label{regdesc:EFUSERDREPEATERR4REG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{EFUSE\_RPT4\_RESERVED4\_ERR}{24}{0}{{\hexprefix{}0000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSERPT4RESERVED4ERR}\item [EFUSE\_RPT4\_RESERVED4\_ERR] If any bit in RPT4\_RESERVED4 is 1, there is a programming error in \hyperref[fielddesc:EFUSERPT4RESERVED4]{EFUSE\_RPT4\_RESERVED4}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_RS\_ERR0\_REG}{\hexprefix{}01C0}\label{regdesc:EFUSERDRSERR0REG}
\regfield{EFUSE\_KEY4\_FAIL}{1}{31}{{0}}%
\regfield{EFUSE\_KEY4\_ERR\_NUM}{3}{28}{{\hexprefix{}0}}%
\regfield{EFUSE\_KEY3\_FAIL}{1}{27}{{0}}%
\regfield{EFUSE\_KEY3\_ERR\_NUM}{3}{24}{{\hexprefix{}0}}%
\regfield{EFUSE\_KEY2\_FAIL}{1}{23}{{0}}%
\regfield{EFUSE\_KEY2\_ERR\_NUM}{3}{20}{{\hexprefix{}0}}%
\regfield{EFUSE\_KEY1\_FAIL}{1}{19}{{0}}%
\regfield{EFUSE\_KEY1\_ERR\_NUM}{3}{16}{{\hexprefix{}0}}%
\regfield{EFUSE\_KEY0\_FAIL}{1}{15}{{0}}%
\regfield{EFUSE\_KEY0\_ERR\_NUM}{3}{12}{{\hexprefix{}0}}%
\regfield{EFUSE\_USR\_DATA\_FAIL}{1}{11}{{0}}%
\regfield{EFUSE\_USR\_DATA\_ERR\_NUM}{3}{8}{{\hexprefix{}0}}%
\regfield{EFUSE\_SYS\_PART1\_FAIL}{1}{7}{{0}}%
\regfield{EFUSE\_SYS\_PART1\_NUM}{3}{4}{{\hexprefix{}0}}%
\regfield{EFUSE\_MAC\_SPI\_8M\_FAIL}{1}{3}{{0}}%
\regfield{EFUSE\_MAC\_SPI\_8M\_ERR\_NUM}{3}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEMACSPI8MERRNUM}\item [EFUSE\_MAC\_SPI\_8M\_ERR\_NUM] The value of this signal means the number of error bytes in BLOCK1. (RO)
\label{fielddesc:EFUSEMACSPI8MFAIL}\item [EFUSE\_MAC\_SPI\_8M\_FAIL] 0: Means no failure and that the data of BLOCK1 is reliable; 1: Means that programming BLOCK1 data failed and the number of error bytes is over 5. (RO)
\label{fielddesc:EFUSESYSPART1NUM}\item [EFUSE\_SYS\_PART1\_NUM] The value of this signal means the number of error bytes in BLOCK2. (RO)
\label{fielddesc:EFUSESYSPART1FAIL}\item [EFUSE\_SYS\_PART1\_FAIL] 0: Means no failure and that the data of BLOCK2 is reliable; 1: Means that programming BLOCK2 data failed and the number of error bytes is over 5. (RO)
\label{fielddesc:EFUSEUSRDATAERRNUM}\item [EFUSE\_USR\_DATA\_ERR\_NUM] The value of this signal means the number of error bytes in BLOCK3. (RO)
\label{fielddesc:EFUSEUSRDATAFAIL}\item [EFUSE\_USR\_DATA\_FAIL] 0: Means no failure and that the data of BLOCK3 is reliable; 1: Means that programming BLOCK3 data failed and the number of error bytes is over 5. (RO)
\label{fielddesc:EFUSEKEYNERRNUM}\item [EFUSE\_KEY\regindex{n}\_ERR\_NUM] The value of this signal means the number of error bytes in KEY\regindex{n}. (RO)
\label{fielddesc:EFUSEKEYNFAIL}\item [EFUSE\_KEY\regindex{n}\_FAIL] 0: Means no failure and that the data of KEY\regindex{n} is reliable; 1: Means that programming KEY\regindex{n} failed and the number of error bytes is over 5. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_RS\_ERR1\_REG}{\hexprefix{}01C4}\label{regdesc:EFUSERDRSERR1REG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{EFUSE\_SYS\_PART2\_FAIL}{1}{7}{{0}}%
\regfield{EFUSE\_SYS\_PART2\_ERR\_NUM}{3}{4}{{\hexprefix{}0}}%
\regfield{EFUSE\_KEY5\_FAIL}{1}{3}{{0}}%
\regfield{EFUSE\_KEY5\_ERR\_NUM}{3}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEKEY5ERRNUM}\item [EFUSE\_KEY5\_ERR\_NUM] The value of this signal means the number of error bytes in KEY5. (RO)
\label{fielddesc:EFUSEKEY5FAIL}\item [EFUSE\_KEY5\_FAIL] 0: Means no failure and that the data of KEY5 is reliable; 1: Means that programming user data failed and the number of error bytes is over 5. (RO)
\label{fielddesc:EFUSESYSPART2ERRNUM}\item [EFUSE\_SYS\_PART2\_ERR\_NUM] The value of this signal means the number of error bytes in BLOCK10. (RO)
\label{fielddesc:EFUSESYSPART2FAIL}\item [EFUSE\_SYS\_PART2\_FAIL] 0: Means no failure and that the data of BLOCK10 is reliable; 1: Means that programming BLOCK10 data failed and the number of error bytes is over 5. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_CLK\_REG}{\hexprefix{}01C8}\label{regdesc:EFUSECLKREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{EFUSE\_CLK\_EN}{1}{16}{{0}}%
\regfield{(reserved)}{13}{3}{0000000000000}%
\regfield{EFUSE\_EFUSE\_MEM\_FORCE\_PU}{1}{2}{{0}}%
\regfield{EFUSE\_MEM\_CLK\_FORCE\_ON}{1}{1}{{1}}%
\regfield{EFUSE\_EFUSE\_MEM\_FORCE\_PD}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEEFUSEMEMFORCEPD}\item [EFUSE\_EFUSE\_MEM\_FORCE\_PD] If set, forces eFuse SRAM into power-saving mode. (R/W)
\label{fielddesc:EFUSEMEMCLKFORCEON}\item [EFUSE\_MEM\_CLK\_FORCE\_ON] If set, forces to activate clock signal of eFuse SRAM. (R/W)
\label{fielddesc:EFUSEEFUSEMEMFORCEPU}\item [EFUSE\_EFUSE\_MEM\_FORCE\_PU] If set, forces eFuse SRAM into working mode. (R/W)
\label{fielddesc:EFUSECLKEN}\item [EFUSE\_CLK\_EN] If set, forces to enable clock signal of eFuse memory. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_CONF\_REG}{\hexprefix{}01CC}\label{regdesc:EFUSECONFREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{EFUSE\_OP\_CODE}{16}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEOPCODE}\item [EFUSE\_OP\_CODE] \hexprefix{}5A5A: Operate programming command; \hexprefix{}5AA5: Operate read command. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_CMD\_REG}{\hexprefix{}01D4}\label{regdesc:EFUSECMDREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{EFUSE\_BLK\_NUM}{4}{2}{{\hexprefix{}0}}%
\regfield{EFUSE\_PGM\_CMD}{1}{1}{{0}}%
\regfield{EFUSE\_READ\_CMD}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEREADCMD}\item [EFUSE\_READ\_CMD] Set this bit to send read command. (R/W)
\label{fielddesc:EFUSEPGMCMD}\item [EFUSE\_PGM\_CMD] Set this bit to send programming command. (R/W)
\label{fielddesc:EFUSEBLKNUM}\item [EFUSE\_BLK\_NUM] The serial number of the block to be programmed. Value 0-10 corresponds to block number 0-10, respectively. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_DAC\_CONF\_REG}{\hexprefix{}01E8}\label{regdesc:EFUSEDACCONFREG}
\regfield{(reserved)}{14}{18}{00000000000000}%
\regfield{EFUSE\_OE\_CLR}{1}{17}{{0}}%
\regfield{EFUSE\_DAC\_NUM}{8}{9}{{255}}%
\regfield{EFUSE\_DAC\_CLK\_PAD\_SEL}{1}{8}{{0}}%
\regfield{EFUSE\_DAC\_CLK\_DIV}{8}{0}{{28}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEDACCLKDIV}\item [EFUSE\_DAC\_CLK\_DIV] Controls the division factor of the rising clock of the programming voltage. (R/W)
\label{fielddesc:EFUSEDACCLKPADSEL}\item [EFUSE\_DAC\_CLK\_PAD\_SEL] Don't care. (R/W)
\label{fielddesc:EFUSEDACNUM}\item [EFUSE\_DAC\_NUM] Controls the rising period of the programming voltage. (R/W)
\label{fielddesc:EFUSEOECLR}\item [EFUSE\_OE\_CLR] Reduces the power supply of the programming voltage. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_STATUS\_REG}{\hexprefix{}01D0}\label{regdesc:EFUSESTATUSREG}
\regfield{(reserved)}{14}{18}{00000000000000}%
\regfield{EFUSE\_REPEAT\_ERR\_CNT}{8}{10}{{\hexprefix{}0}}%
\regfield{(reserved)}{6}{4}{000000}%
\regfield{EFUSE\_STATE}{4}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSESTATE}\item [EFUSE\_STATE] Indicates the state of the eFuse state machine. (RO)
\label{fielddesc:EFUSEREPEATERRCNT}\item [EFUSE\_REPEAT\_ERR\_CNT] Indicates the number of error bits during programming BLOCK0. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_INT\_RAW\_REG}{\hexprefix{}01D8}\label{regdesc:EFUSEINTRAWREG}
\regfield{(reserved)}{30}{2}{000000000000000000000000000000}%
\regfield{EFUSE\_PGM\_DONE\_INT\_RAW}{1}{1}{{0}}%
\regfield{EFUSE\_READ\_DONE\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEREADDONEINTRAW}\item [EFUSE\_READ\_DONE\_INT\_RAW] The raw bit signal for read\_done interrupt. (RO)
\label{fielddesc:EFUSEPGMDONEINTRAW}\item [EFUSE\_PGM\_DONE\_INT\_RAW] The raw bit signal for pgm\_done interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_INT\_ST\_REG}{\hexprefix{}01DC}\label{regdesc:EFUSEINTSTREG}
\regfield{(reserved)}{30}{2}{000000000000000000000000000000}%
\regfield{EFUSE\_PGM\_DONE\_INT\_ST}{1}{1}{{0}}%
\regfield{EFUSE\_READ\_DONE\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEREADDONEINTST}\item [EFUSE\_READ\_DONE\_INT\_ST] The status signal for read\_done interrupt. (RO)
\label{fielddesc:EFUSEPGMDONEINTST}\item [EFUSE\_PGM\_DONE\_INT\_ST] The status signal for pgm\_done interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_INT\_ENA\_REG}{\hexprefix{}01E0}\label{regdesc:EFUSEINTENAREG}
\regfield{(reserved)}{30}{2}{000000000000000000000000000000}%
\regfield{EFUSE\_PGM\_DONE\_INT\_ENA}{1}{1}{{0}}%
\regfield{EFUSE\_READ\_DONE\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEREADDONEINTENA}\item [EFUSE\_READ\_DONE\_INT\_ENA] The enable signal for read\_done interrupt. (R/W)
\label{fielddesc:EFUSEPGMDONEINTENA}\item [EFUSE\_PGM\_DONE\_INT\_ENA] The enable signal for pgm\_done interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_INT\_CLR\_REG}{\hexprefix{}01E4}\label{regdesc:EFUSEINTCLRREG}
\regfield{(reserved)}{30}{2}{000000000000000000000000000000}%
\regfield{EFUSE\_PGM\_DONE\_INT\_CLR}{1}{1}{{0}}%
\regfield{EFUSE\_READ\_DONE\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEREADDONEINTCLR}\item [EFUSE\_READ\_DONE\_INT\_CLR] The clear signal for read\_done interrupt. (WO)
\label{fielddesc:EFUSEPGMDONEINTCLR}\item [EFUSE\_PGM\_DONE\_INT\_CLR] The clear signal for pgm\_done interrupt. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_RD\_TIM\_CONF\_REG}{\hexprefix{}01EC}\label{regdesc:EFUSERDTIMCONFREG}
\regfield{EFUSE\_READ\_INIT\_NUM}{8}{24}{{\hexprefix{}12}}%
\regfield{EFUSE\_TSUR\_A}{8}{16}{{\hexprefix{}1}}%
\regfield{EFUSE\_TRD}{8}{8}{{\hexprefix{}1}}%
\regfield{EFUSE\_THR\_A}{8}{0}{{\hexprefix{}1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSETHRA}\item [EFUSE\_THR\_A] Configures the hold time of read operation. (R/W)
\label{fielddesc:EFUSETRD}\item [EFUSE\_TRD] Configures the length of pulse of read operation. (R/W)
\label{fielddesc:EFUSETSURA}\item [EFUSE\_TSUR\_A] Configures the setup time of read operation. (R/W)
\label{fielddesc:EFUSEREADINITNUM}\item [EFUSE\_READ\_INIT\_NUM] Configures the initial read time of eFuse. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_WR\_TIM\_CONF0\_REG}{\hexprefix{}01F0}\label{regdesc:EFUSEWRTIMCONF0REG}
\regfield{EFUSE\_TPGM}{16}{16}{{\hexprefix{}c8}}%
\regfield{EFUSE\_TPGM\_INACTIVE}{8}{8}{{\hexprefix{}1}}%
\regfield{EFUSE\_THP\_A}{8}{0}{{\hexprefix{}1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSETHPA}\item [EFUSE\_THP\_A] Configures the hold time of programming operation. (R/W)
\label{fielddesc:EFUSETPGMINACTIVE}\item [EFUSE\_TPGM\_INACTIVE] Configures the length of pulse during programming 0 to eFuse. (R/W)
\label{fielddesc:EFUSETPGM}\item [EFUSE\_TPGM] Configures the length of pulse during programming 1 to eFuse. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_WR\_TIM\_CONF1\_REG}{\hexprefix{}01F4}\label{regdesc:EFUSEWRTIMCONF1REG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{EFUSE\_PWR\_ON\_NUM}{16}{8}{{\hexprefix{}2880}}%
\regfield{EFUSE\_TSUP\_A}{8}{0}{{\hexprefix{}1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSETSUPA}\item [EFUSE\_TSUP\_A] Configures the setup time of programming operation. (R/W)
\label{fielddesc:EFUSEPWRONNUM}\item [EFUSE\_PWR\_ON\_NUM] Configures the power up time for VDDQ. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_WR\_TIM\_CONF2\_REG}{\hexprefix{}01F8}\label{regdesc:EFUSEWRTIMCONF2REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{EFUSE\_PWR\_OFF\_NUM}{16}{0}{{\hexprefix{}190}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEPWROFFNUM}\item [EFUSE\_PWR\_OFF\_NUM] Configures the power outage time for VDDQ. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{EFUSE\_DATE\_REG}{\hexprefix{}01FC}\label{regdesc:EFUSEDATEREG}
\regfield{EFUSE\_DATE}{32}{0}{{\hexprefix{}19081100}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:EFUSEDATE}\item [EFUSE\_DATE] Version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}
