\begin{register}{H}{APB\_SARADC\_CTRL\_REG}{0x0000}\label{regdesc:APBSARADCCTRLREG}
\regfield{APB\_SARADC\_WAIT\_ARB\_CYCLE}{2}{30}{{1}}%
\regfield{(reserved)}{1}{29}{0}%
\regfield{APB\_SARADC\_XPD\_SAR\_FORCE}{2}{27}{{0}}%
\regfield{(reserved)}{3}{24}{000}%
\regfield{APB\_SARADC\_SAR\_PATT\_P\_CLEAR}{1}{23}{{0}}%
\regfield{(reserved)}{5}{18}{00000}%
\regfield{APB\_SARADC\_SAR\_PATT\_LEN}{3}{15}{{7}}%
\regfield{APB\_SARADC\_SAR\_CLK\_DIV}{8}{7}{{4}}%
\regfield{APB\_SARADC\_SAR\_CLK\_GATED}{1}{6}{{1}}%
\regfield{(reserved)}{4}{2}{0000}%
\regfield{APB\_SARADC\_START}{1}{1}{{0}}%
\regfield{APB\_SARADC\_START\_FORCE}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCSARADCSTARTFORCE}\item [APB\_SARADC\_START\_FORCE] 0: select FSM to start SAR ADC. 1: select software to start SAR ADC. (R/W)
\label{fielddesc:APBSARADCSARADCSTART}\item [APB\_SARADC\_START] Write 1 here to start the SAR ADC by software. Valid only when \hyperref[fielddesc:APBSARADCSARADCSTARTFORCE]{APB\_SARADC\_START\_FORCE} = 1. (R/W)
\label{fielddesc:APBSARADCSARADCSARCLKGATED}\item [APB\_SARADC\_SAR\_CLK\_GATED] SAR ADC clock gate enable bit. (R/W)
\label{fielddesc:APBSARADCSARADCSARCLKDIV}\item [APB\_SARADC\_SAR\_CLK\_DIV] SAR ADC clock divider. This value should be no less than 2. (R/W)
\label{fielddesc:APBSARADCSARADCSARPATTLEN}\item [APB\_SARADC\_SAR\_PATT\_LEN] Configure how many pattern table entries will be used. If this field is set to 1, then pattern table entries (cmd0) and (cmd1) will be used. (R/W)

\label{fielddesc:APBSARADCSARADCSARPATTPCLEAR}\item [APB\_SARADC\_SAR\_PATT\_P\_CLEAR] Clear the pointer of pattern table entry for DIG ADC controller. (R/W)
\label{fielddesc:APBSARADCSARADCXPDSARFORCE}\item [APB\_SARADC\_XPD\_SAR\_FORCE] Force select XPD SAR. (R/W)
\label{fielddesc:APBSARADCSARADCWAITARBCYCLE}\item [APB\_SARADC\_WAIT\_ARB\_CYCLE] The clock cycles of waiting arbitration signal stable after SAR\_DONE. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_CTRL2\_REG}{0x0004}\label{regdesc:APBSARADCCTRL2REG}
\regfield{(reserved)}{7}{25}{0000000}%
\regfield{APB\_SARADC\_TIMER\_EN}{1}{24}{{0}}%
\regfield{APB\_SARADC\_TIMER\_TARGET}{12}{12}{{10}}%
\regfield{(reserved)}{1}{11}{0}%
\regfield{APB\_SARADC\_SAR2\_INV}{1}{10}{{0}}%
\regfield{APB\_SARADC\_SAR1\_INV}{1}{9}{{0}}%
\regfield{APB\_SARADC\_MAX\_MEAS\_NUM}{8}{1}{{255}}%
\regfield{APB\_SARADC\_MEAS\_NUM\_LIMIT}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCSARADCMEASNUMLIMIT}\item [APB\_SARADC\_MEAS\_NUM\_LIMIT] Enable the limitation of SAR ADCs maximum conversion times. (R/W)
\label{fielddesc:APBSARADCSARADCMAXMEASNUM}\item [APB\_SARADC\_MAX\_MEAS\_NUM] The SAR ADCs maximum conversion times. (R/W)
\label{fielddesc:APBSARADCSARADCSAR1INV}\item [APB\_SARADC\_SAR1\_INV] Write 1 here to invert the data of SAR ADC1. (R/W)
\label{fielddesc:APBSARADCSARADCSAR2INV}\item [APB\_SARADC\_SAR2\_INV] Write 1 here to invert the data of SAR ADC2. (R/W)
\label{fielddesc:APBSARADCSARADCTIMERTARGET}\item [APB\_SARADC\_TIMER\_TARGET] Set SAR ADC timer target. (R/W)
\label{fielddesc:APBSARADCSARADCTIMEREN}\item [APB\_SARADC\_TIMER\_EN] Enable SAR ADC timer trigger. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_FILTER\_CTRL1\_REG}{0x0008}\label{regdesc:APBSARADCFILTERCTRL1REG}
\regfield{APB\_SARADC\_FILTER\_FACTOR0}{3}{29}{{0}}%
\regfield{APB\_SARADC\_FILTER\_FACTOR1}{3}{26}{{0}}%
\regfield{(reserved)}{26}{0}{00000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCAPBSARADCFILTERFACTOR1}\item [APB\_SARADC\_FILTER\_FACTOR1] The filter coefficient for SAR ADC filter 1. (R/W)
\label{fielddesc:APBSARADCAPBSARADCFILTERFACTOR0}\item [APB\_SARADC\_FILTER\_FACTOR0] The filter coefficient for SAR ADC filter 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_SAR\_PATT\_TAB1\_REG}{0x0018}\label{regdesc:APBSARADCSARPATTTAB1REG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{APB\_SARADC\_SAR\_PATT\_TAB1}{24}{0}{{0x0000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCSARADCSARPATTTAB1}\item [APB\_SARADC\_SAR\_PATT\_TAB1] Pattern table entries 0 \verb+~+ 3 (each entry is six bits). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_SAR\_PATT\_TAB2\_REG}{0x001C}\label{regdesc:APBSARADCSARPATTTAB2REG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{APB\_SARADC\_SAR\_PATT\_TAB2}{24}{0}{{0x0000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCSARADCSARPATTTAB2}\item [APB\_SARADC\_SAR\_PATT\_TAB2] Pattern table entries 4 \verb+~+ 7 (each entry is six bits). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_ONETIME\_SAMPLE\_REG}{0x0020}\label{regdesc:APBSARADCONETIMESAMPLEREG}
\regfield{APB\_SARADC1\_ONETIME\_SAMPLE}{1}{31}{{0}}%
\regfield{APB\_SARADC2\_ONETIME\_SAMPLE}{1}{30}{{0}}%
\regfield{APB\_SARADC\_ONETIME\_START}{1}{29}{{0}}%
\regfield{APB\_SARADC\_ONETIME\_CHANNEL}{4}{25}{{13}}%
\regfield{APB\_SARADC\_ONETIME\_ATTEN}{2}{23}{{0}}%
\regfield{(reserved)}{23}{0}{00000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCSARADCONETIMEATTEN}\item [APB\_SARADC\_ONETIME\_ATTEN] Configure the attenuation for a one-time sampling. (R/W)
\label{fielddesc:APBSARADCSARADCONETIMECHANNEL}\item [APB\_SARADC\_ONETIME\_CHANNEL] Configure the channel for a one-time sampling. (R/W)
\label{fielddesc:APBSARADCSARADCONETIMESTART}\item [APB\_SARADC\_ONETIME\_START] Start SAR ADC one-time sampling. (R/W)
\label{fielddesc:APBSARADCSARADC2ONETIMESAMPLE}\item [APB\_SARADC2\_ONETIME\_SAMPLE] Enable SAR ADC2 one-time sampling. (R/W)
\label{fielddesc:APBSARADCSARADC1ONETIMESAMPLE}\item [APB\_SARADC1\_ONETIME\_SAMPLE] Enable SAR ADC1 one-time sampling. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_APB\_ADC\_ARB\_CTRL\_REG}{0x0024}\label{regdesc:APBSARADCARBCTRLREG}
\regfield{(reserved)}{19}{13}{0000000000000000000}%
\regfield{APB\_SARADC\_ADC\_ARB\_FIX\_PRIORITY}{1}{12}{{0}}%
\regfield{APB\_SARADC\_ADC\_ARB\_WIFI\_PRIORITY}{2}{10}{{2}}%
\regfield{(reserved)}{2}{8}{{1}}%
\regfield{APB\_SARADC\_ADC\_ARB\_APB\_PRIORITY}{2}{6}{{0}}%
\regfield{APB\_SARADC\_ADC\_ARB\_GRANT\_FORCE}{1}{5}{{0}}%
\regfield{APB\_SARADC\_ADC\_ARB\_WIFI\_FORCE}{1}{4}{{0}}%
\regfield{(reserved)}{1}{3}{{0}}%
\regfield{APB\_SARADC\_ADC\_ARB\_APB\_FORCE}{1}{2}{{0}}%
\regfield{(reserved)}{2}{0}{00}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCADCARBAPBFORCE}\item [APB\_SARADC\_ADC\_ARB\_APB\_FORCE] SAR ADC2 arbiter forces to enable DIG ADC controller. (R/W)
\label{fielddesc:APBSARADCADCARBWIFIFORCE}\item [APB\_SARADC\_ADC\_ARB\_WIFI\_FORCE] SAR ADC2 arbiter forces to enable PWDET controller. (R/W)
\label{fielddesc:APBSARADCADCARBGRANTFORCE}\item [APB\_SARADC\_ADC\_ARB\_GRANT\_FORCE] ADC2 arbiter force grant. (R/W)
\label{fielddesc:APBSARADCADCARBAPBPRIORITY}\item [APB\_SARADC\_ADC\_ARB\_APB\_PRIORITY] Set DIG ADC controller priority. (R/W)
\label{fielddesc:APBSARADCADCARBWIFIPRIORITY}\item [APB\_SARADC\_ADC\_ARB\_WIFI\_PRIORITY] Set PWDET controller priority. (R/W)
\label{fielddesc:APBSARADCADCARBFIXPRIORITY}\item [APB\_SARADC\_ADC\_ARB\_FIX\_PRIORITY] ADC2 arbiter uses fixed priority. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_FILTER\_CTRL0\_REG}{0x0028}\label{regdesc:APBSARADCFILTERCTRL0REG}
\regfield{APB\_SARADC\_FILTER\_RESET}{1}{31}{{0}}%
\regfield{(reserved)}{5}{26}{00000}%
\regfield{APB\_SARADC\_FILTER\_CHANNEL0}{4}{22}{{13}}%
\regfield{APB\_SARADC\_FILTER\_CHANNEL1}{4}{18}{{13}}%
\regfield{(reserved)}{18}{0}{000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCAPBSARADCFILTERCHANNEL1}\item [APB\_SARADC\_FILTER\_CHANNEL1] The filter channel for SAR ADC filter 1. (R/W)
\label{fielddesc:APBSARADCAPBSARADCFILTERCHANNEL0}\item [APB\_SARADC\_FILTER\_CHANNEL0] The filter channel for SAR ADC filter 0. (R/W)
\label{fielddesc:APBSARADCAPBSARADCFILTERRESET}\item [APB\_SARADC\_FILTER\_RESET] Reset SAR ADC1 filter. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_1\_DATA\_STATUS\_REG}{0x002C}\label{regdesc:APBSARADCSAR1DATASTATUSREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{APB\_SARADC\_APB\_SARADC1\_DATA}{17}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCAPBSARADC1DATA}\item [APB\_SARADC\_ADC1\_DATA] SAR ADC1 conversion data. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_2\_DATA\_STATUS\_REG}{0x0030}\label{regdesc:APBSARADCSAR2DATASTATUSREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{APB\_SARADC\_ADC2\_DATA}{17}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCAPBSARADC2DATA}\item [APB\_SARADC\_ADC2\_DATA] SAR ADC2 conversion data. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_THRES0\_CTRL\_REG}{0x0034}\label{regdesc:APBSARADCTHRES0CTRLREG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{APB\_SARADC\_THRES0\_LOW}{13}{18}{{0}}%
\regfield{APB\_SARADC\_THRES0\_HIGH}{13}{5}{{0x1fff}}%
\regfield{(reserved)}{1}{4}{0}%
\regfield{APB\_SARADC\_THRES0\_CHANNEL}{4}{0}{{13}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCAPBSARADCTHRES0CHANNEL}\item [APB\_SARADC\_THRES0\_CHANNEL] The channel for SAR ADC monitor 0. (R/W)
\label{fielddesc:APBSARADCAPBSARADCTHRES0HIGH}\item [APB\_SARADC\_THRES0\_HIGH] The high threshold for SAR ADC monitor 0. (R/W)
\label{fielddesc:APBSARADCAPBSARADCTHRES0LOW}\item [APB\_SARADC\_THRES0\_LOW] The low threshold for SAR ADC monitor 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_THRES1\_CTRL\_REG}{0x0038}\label{regdesc:APBSARADCTHRES1CTRLREG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{APB\_SARADC\_THRES1\_LOW}{13}{18}{{0}}%
\regfield{APB\_SARADC\_THRES1\_HIGH}{13}{5}{{0x1fff}}%
\regfield{(reserved)}{1}{4}{0}%
\regfield{APB\_SARADC\_THRES1\_CHANNEL}{4}{0}{{13}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCAPBSARADCTHRES1CHANNEL}\item [APB\_SARADC\_THRES1\_CHANNEL] The channel for SAR ADC monitor 1. (R/W)
\label{fielddesc:APBSARADCAPBSARADCTHRES1HIGH}\item [APB\_SARADC\_THRES1\_HIGH] The high threshold for SAR ADC monitor 1. (R/W)
\label{fielddesc:APBSARADCAPBSARADCTHRES1LOW}\item [APB\_SARADC\_THRES1\_LOW] The low threshold for SAR ADC monitor 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_THRES\_CTRL\_REG}{0x003C}\label{regdesc:APBSARADCTHRESCTRLREG}
\regfield{APB\_SARADC\_THRES0\_EN}{1}{31}{{0}}%
\regfield{APB\_SARADC\_THRES1\_EN}{1}{30}{{0}}%
\regfield{(reserved)}{2}{28}{00}%
\regfield{APB\_SARADC\_THRES\_ALL\_EN}{1}{27}{{0}}%
\regfield{(reserved)}{27}{0}{000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCAPBSARADCTHRESALLEN}\item [APB\_SARADC\_THRES\_ALL\_EN] Enable the threshold monitoring for all configured channels. (R/W)
\label{fielddesc:APBSARADCAPBSARADCTHRES1EN}\item [APB\_SARADC\_THRES1\_EN] Enable threshold monitor 1. (R/W)
\label{fielddesc:APBSARADCAPBSARADCTHRES0EN}\item [APB\_SARADC\_THRES0\_EN] Enable threshold monitor 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_INT\_ENA\_REG}{0x0040}\label{regdesc:APBSARADCINTENAREG}
\regfield{APB\_SARADC\_ADC1\_DONE\_INT\_ENA}{1}{31}{{0}}%
\regfield{APB\_SARADC\_ADC2\_DONE\_INT\_ENA}{1}{30}{{0}}%
\regfield{APB\_SARADC\_THRES0\_HIGH\_INT\_ENA}{1}{29}{{0}}%
\regfield{APB\_SARADC\_THRES1\_HIGH\_INT\_ENA}{1}{28}{{0}}%
\regfield{APB\_SARADC\_THRES0\_LOW\_INT\_ENA}{1}{27}{{0}}%
\regfield{APB\_SARADC\_THRES1\_LOW\_INT\_ENA}{1}{26}{{0}}%
\regfield{(reserved)}{26}{0}{00000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCAPBSARADCTHRES1LOWINTENA}\item [APB\_SARADC\_THRES1\_LOW\_INT\_ENA] Enable bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_THRES1\_LOW\_INT} interrupt. (R/W)
\label{fielddesc:APBSARADCAPBSARADCTHRES0LOWINTENA}\item [APB\_SARADC\_THRES0\_LOW\_INT\_ENA] Enable bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_THRES0\_LOW\_INT} interrupt. (R/W)
\label{fielddesc:APBSARADCAPBSARADCTHRES1HIGHINTENA}\item [APB\_SARADC\_THRES1\_HIGH\_INT\_ENA] Enable bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_THRES1\_HIGH\_INT} interrupt. (R/W)
\label{fielddesc:APBSARADCAPBSARADCTHRES0HIGHINTENA}\item [APB\_SARADC\_THRES0\_HIGH\_INT\_ENA] Enable bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_THRES0\_HIGH\_INT} interrupt. (R/W)
\label{fielddesc:APBSARADCAPBSARADC2DONEINTENA}\item [APB\_SARADC\_ADC2\_DONE\_INT\_ENA] Enable bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_ADC2\_DONE\_INT} interrupt. (R/W)
\label{fielddesc:APBSARADCAPBSARADC1DONEINTENA}\item [APB\_SARADC\_ADC1\_DONE\_INT\_ENA] Enable bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_ADC1\_DONE\_INT} interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_INT\_RAW\_REG}{0x0044}\label{regdesc:APBSARADCINTRAWREG}
\regfield{APB\_SARADC\_ADC1\_DONE\_INT\_RAW}{1}{31}{{0}}%
\regfield{APB\_SARADC\_ADC2\_DONE\_INT\_RAW}{1}{30}{{0}}%
\regfield{APB\_SARADC\_THRES0\_HIGH\_INT\_RAW}{1}{29}{{0}}%
\regfield{APB\_SARADC\_THRES1\_HIGH\_INT\_RAW}{1}{28}{{0}}%
\regfield{APB\_SARADC\_THRES0\_LOW\_INT\_RAW}{1}{27}{{0}}%
\regfield{APB\_SARADC\_THRES1\_LOW\_INT\_RAW}{1}{26}{{0}}%
\regfield{(reserved)}{26}{0}{00000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCAPBSARADCTHRES1LOWINTRAW}\item [APB\_SARADC\_THRES1\_LOW\_INT\_RAW] Raw bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_THRES1\_LOW\_INT} interrupt. (RO)
\label{fielddesc:APBSARADCAPBSARADCTHRES0LOWINTRAW}\item [APB\_SARADC\_THRES0\_LOW\_INT\_RAW] Raw bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_THRES0\_LOW\_INT} interrupt. (RO)
\label{fielddesc:APBSARADCAPBSARADCTHRES1HIGHINTRAW}\item [APB\_SARADC\_THRES1\_HIGH\_INT\_RAW] Raw bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_THRES1\_HIGH\_INT} interrupt. (RO)
\label{fielddesc:APBSARADCAPBSARADCTHRES0HIGHINTRAW}\item [APB\_SARADC\_THRES0\_HIGH\_INT\_RAW] Raw bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_THRES0\_HIGH\_INT} interrupt. (RO)
\label{fielddesc:APBSARADCAPBSARADC2DONEINTRAW}\item [APB\_SARADC\_ADC2\_DONE\_INT\_RAW] Raw bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_ADC2\_DONE\_INT} interrupt. (RO)
\label{fielddesc:APBSARADCAPBSARADC1DONEINTRAW}\item [APB\_SARADC\_ADC1\_DONE\_INT\_RAW] Raw bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_ADC1\_DONE\_INT} interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_INT\_ST\_REG}{0x0048}\label{regdesc:APBSARADCINTSTREG}
\regfield{APB\_SARADC\_ADC1\_DONE\_INT\_ST}{1}{31}{{0}}%
\regfield{APB\_SARADC\_ADC2\_DONE\_INT\_ST}{1}{30}{{0}}%
\regfield{APB\_SARADC\_THRES0\_HIGH\_INT\_ST}{1}{29}{{0}}%
\regfield{APB\_SARADC\_THRES1\_HIGH\_INT\_ST}{1}{28}{{0}}%
\regfield{APB\_SARADC\_THRES0\_LOW\_INT\_ST}{1}{27}{{0}}%
\regfield{APB\_SARADC\_THRES1\_LOW\_INT\_ST}{1}{26}{{0}}%
\regfield{(reserved)}{26}{0}{00000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCAPBSARADCTHRES1LOWINTST}\item [APB\_SARADC\_THRES1\_LOW\_INT\_ST] Status of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_THRES1\_LOW\_INT} interrupt. (RO)
\label{fielddesc:APBSARADCAPBSARADCTHRES0LOWINTST}\item [APB\_SARADC\_THRES0\_LOW\_INT\_ST] Status of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_THRES0\_LOW\_INT} interrupt. (RO)
\label{fielddesc:APBSARADCAPBSARADCTHRES1HIGHINTST}\item [APB\_SARADC\_THRES1\_HIGH\_INT\_ST] Status of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_THRES1\_HIGH\_INT} interrupt. (RO)
\label{fielddesc:APBSARADCAPBSARADCTHRES0HIGHINTST}\item [APB\_SARADC\_THRES0\_HIGH\_INT\_ST] Status of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_THRES0\_HIGH\_INT} interrupt. (RO)
\label{fielddesc:APBSARADCAPBSARADC2DONEINTST}\item [APB\_SARADC\_ADC2\_DONE\_INT\_ST] Status of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_ADC2\_DONE\_INT} interrupt. (RO)
\label{fielddesc:APBSARADCAPBSARADC1DONEINTST}\item [APB\_SARADC\_ADC1\_DONE\_INT\_ST] Status of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_ADC1\_DONE\_INT} interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_INT\_CLR\_REG}{0x004C}\label{regdesc:APBSARADCINTCLRREG}
\regfield{APB\_SARADC\_ADC1\_DONE\_INT\_CLR}{1}{31}{{0}}%
\regfield{APB\_SARADC\_ADC2\_DONE\_INT\_CLR}{1}{30}{{0}}%
\regfield{APB\_SARADC\_THRES0\_HIGH\_INT\_CLR}{1}{29}{{0}}%
\regfield{APB\_SARADC\_THRES1\_HIGH\_INT\_CLR}{1}{28}{{0}}%
\regfield{APB\_SARADC\_THRES0\_LOW\_INT\_CLR}{1}{27}{{0}}%
\regfield{APB\_SARADC\_THRES1\_LOW\_INT\_CLR}{1}{26}{{0}}%
\regfield{(reserved)}{26}{0}{00000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCAPBSARADCTHRES1LOWINTCLR}\item [APB\_SARADC\_THRES1\_LOW\_INT\_CLR] Clear bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_THRES1\_LOW\_INT} interrupt. (WO)
\label{fielddesc:APBSARADCAPBSARADCTHRES0LOWINTCLR}\item [APB\_SARADC\_THRES0\_LOW\_INT\_CLR] Clear bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_THRES0\_LOW\_INT} interrupt. (WO)
\label{fielddesc:APBSARADCAPBSARADCTHRES1HIGHINTCLR}\item [APB\_SARADC\_THRES1\_HIGH\_INT\_CLR] Clear bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_THRES1\_HIGH\_INT} interrupt. (WO)
\label{fielddesc:APBSARADCAPBSARADCTHRES0HIGHINTCLR}\item [APB\_SARADC\_THRES0\_HIGH\_INT\_CLR] Clear bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_THRES0\_HIGH\_INT} interrupt. (WO)
\label{fielddesc:APBSARADCAPBSARADC2DONEINTCLR}\item [APB\_SARADC\_ADC2\_DONE\_INT\_CLR] Clear bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_ADC2\_DONE\_INT} interrupt. (WO)
\label{fielddesc:APBSARADCAPBSARADC1DONEINTCLR}\item [APB\_SARADC\_ADC1\_DONE\_INT\_CLR] Clear bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_ADC1\_DONE\_INT} interrupt. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_DMA\_CONF\_REG}{0x0050}\label{regdesc:APBSARADCDMACONFREG}
\regfield{APB\_SARADC\_APB\_ADC\_TRANS}{1}{31}{{0}}%
\regfield{APB\_SARADC\_APB\_ADC\_RESET\_FSM}{1}{30}{{0}}%
\regfield{(reserved)}{14}{16}{00000000000000}%
\regfield{APB\_SARADC\_APB\_ADC\_EOF\_NUM}{16}{0}{{255}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCAPBADCEOFNUM}\item [APB\_SARADC\_APB\_ADC\_EOF\_NUM] Generate dma\_in\_suc\_eof when sample cnt = eof\_num. (R/W)
\label{fielddesc:APBSARADCAPBADCRESETFSM}\item [APB\_SARADC\_APB\_ADC\_RESET\_FSM] Reset DIG ADC controller status. (R/W)
\label{fielddesc:APBSARADCAPBADCTRANS}\item [APB\_SARADC\_APB\_ADC\_TRANS] When this bit is set, DIG ADC controller uses DMA. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_APB\_ADC\_CLKM\_CONF\_REG}{0x0054}\label{regdesc:APBSARADCCLKMCONFREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{APB\_SARADC\_CLK\_SEL}{2}{21}{{0}}%
\regfield{APB\_SARADC\_CLK\_EN}{1}{20}{{0}}%
\regfield{APB\_SARADC\_CLKM\_DIV\_A}{6}{14}{{0x0}}%
\regfield{APB\_SARADC\_CLKM\_DIV\_B}{6}{8}{{0x0}}%
\regfield{APB\_SARADC\_CLKM\_DIV\_NUM}{8}{0}{{4}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCCLKMDIVNUM}\item [APB\_SARADC\_CLKM\_DIV\_NUM] The integer part of ADC clock divider.  Divider value = APB\_SARADC\_CLKM\_DIV\_NUM + APB\_SARADC\_CLKM\_DIV\_B/APB\_SARADC\_CLKM\_DIV\_A. (R/W)
\label{fielddesc:APBSARADCCLKMDIVB}\item [APB\_SARADC\_CLKM\_DIV\_B] The numerator value of fractional clock divider. (R/W)
\label{fielddesc:APBSARADCCLKMDIVA}\item [APB\_SARADC\_CLKM\_DIV\_A] The denominator value of fractional clock divider. (R/W)
\label{fielddesc:APBSARADCCLKEN}\item [APB\_SARADC\_CLK\_EN] Enable the SAR ADC register clock. (R/W)
\label{fielddesc:APBSARADCCLKSEL}\item [APB\_SARADC\_CLK\_SEL] 0: Use APB\_CLK as clock source, 1: use divided-down PLL\_240 as clock source. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_APB\_TSENS\_CTRL\_REG}{0x0058}\label{regdesc:APBSARADCAPBTSENSCTRLREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{APB\_SARADC\_TSENS\_PU}{1}{22}{{0}}%
\regfield{APB\_SARADC\_TSENS\_CLK\_DIV}{8}{14}{{6}}%
\regfield{APB\_SARADC\_TSENS\_IN\_INV}{1}{13}{{0}}%
\regfield{(reserved)}{5}{8}{00000}%
\regfield{APB\_SARADC\_TSENS\_OUT}{8}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCTSENSOUT}\item [APB\_SARADC\_TSENS\_OUT] Temperature sensor data out. (RO)
\label{fielddesc:APBSARADCTSENSININV}\item [APB\_SARADC\_TSENS\_IN\_INV] Invert temperature sensor input value. (R/W)
\label{fielddesc:APBSARADCTSENSCLKDIV}\item [APB\_SARADC\_TSENS\_CLK\_DIV] Temperature sensor clock divider. (R/W)
\label{fielddesc:APBSARADCTSENSPU}\item [APB\_SARADC\_TSENS\_PU] Temperature sensor power up. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{APB\_SARADC\_APB\_TSENS\_CTRL2\_REG}{0x005C}\label{regdesc:APBSARADCTSENSCTRL2REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{APB\_SARADC\_TSENS\_CLK\_SEL}{1}{15}{{0}}%
\regfield{(reserved)}{2}{12}{00}%
\regfield{APB\_SARADC\_TSENS\_XPD\_WAIT}{12}{0}{2}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCTSENSXPDWAIT}\item [APB\_SARADC\_TSENS\_XPD\_WAIT] The wait time before temperature sensor is powered up. (R/W)
\label{fielddesc:APBSARADCTSENSCLKSEL}\item [APB\_SARADC\_TSENS\_CLK\_SEL] Choose working clock for temperature sensor. 0: RC\_FAST\_CLK. 1: XTAL\_CLK. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{APB\_SARADC\_CALI\_REG}{0x0060}\label{regdesc:APBSARADCCALIREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{APB\_SARADC\_CALI\_CFG}{17}{0}{{0x8000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCAPBSARADCCALICFG}\item [APB\_SARADC\_CALI\_CFG] Configure the SAR ADC calibration factor. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_APB\_CTRL\_DATE\_REG}{0x03FC}\label{regdesc:APBSARADCCTRLDATEREG}
\regfield{APB\_SARADC\_DATE}{32}{0}{{0x2007171}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCDATE}\item [APB\_SARADC\_DATE] Version register. (R/W)
\end{reglist}\end{regdesc}
\end{register}
