
\begin{register}{H}{msip}{0x0000}\label{regdesc:CLINTMSIPREG}
\regfield{reserved}{31}{1}{{0x00000000}}%
\regfield{MSIP}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}
\begin{reglist}
\label{fielddesc:CLINTMSIP}\item[MSIP] Configures the pending status of the machine software interrupt.\\
0: Not pending\\
1: Pending\\
(R/W)
\end{reglist}
\end{regdesc}
\end{register}

\begin{register}{H}{mtimecmplo}{0x4000}\label{regdesc:CLINTMTIMECMPLOREG}
\regfield{MTIMECMPLO}{32}{0}{{0xFFFFFFFF}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}
\begin{reglist}
\label{fielddesc:CLINTMTIMECMPLO}\item [MTIMECMPLO] Represents the value to compare with the lower 32 bits of the system counter. (R/W)
\end{reglist}
\end{regdesc}
\end{register}

\begin{register}{H}{mtimecmphi}{0x4004}\label{regdesc:CLINTMTIMECMPHIREG}
\regfield{MTIMECMPHI}{32}{0}{{0xFFFFFFFF}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}
\begin{reglist}
\label{fielddesc:CLINTMTIMECMPHI}\item [MTIMECMPHI] Represents the value to compare with the higher 32 bits of the system counter. (R/W)
\end{reglist}
\end{regdesc}
\end{register}


\begin{register}{H}{mtimeloadlo}{0x4008}\label{regdesc:CLINTMTIMELOADLOREG}
\regfield{MTIMELOADLO}{32}{0}{{0x00000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}
\begin{reglist}
\label{fielddesc:CLINTMTIMELOADLO}\item [MTIME\_LOADLO] Represents the lower 32 bits to be loaded to the system counter. (R/W)
\end{reglist}
\end{regdesc}
\end{register}

\begin{register}{H}{mtimeloadhi}{0x400C}\label{regdesc:CLINTMTIMELOADHIREG}
\regfield{MTIMELOADHI}{32}{0}{{0x00000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}
\begin{reglist}
\label{fielddesc:CLINTMTIMELOADHI}\item [MTIME\_LOADHI] Represents the higher 32 bits to be loaded to the system counter. (R/W)
\end{reglist}
\end{regdesc}
\end{register}

\begin{register}{H}{mtimectl}{0x4010}\label{regdesc:CLINTMTIMECTLREG}
\regfield{reserved}{26}{6}{{0x0000000}}%
\regfield{MTIME\_SAM}{2}{4}{{0x0}}%
\regfield{MTIME\_OVF}{1}{3}{{0x0}}%
\regfield{MTIME\_EN}{1}{0}{{0x1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}
\begin{reglist}
\label{fielddesc:CLINTMTIMECTLEN}\item [MTIME\_EN] Configures whether to enable the system counter. \\
1: Enable\\
0: Disable\\
(R/W)
\label{fielddesc:CLINTMTIMECTLOVF}\item [MTIME\_OVF] Configures the overflow bit of the system counter. \\
1: Represents that system counter value is maximum, that is 0xFFFFFFFFFFFFFFFF\\
0: Otherwise\\
When the counter value is 0xFFFFFFFFFFFFFFFF, which is the maximum value, then this bit is set as 1 by hardware. Software can clear this bit by writing 0 to it. Writing 1 has no effect.
(R/W)
\label{fielddesc:CLINTMTIMECTLSAM}\item [MTIME\_SAM] Configures the sampling mode of MTIMELO and MTIMEHI registers to allow accurate reading of the 64-bit system count. For the 64-bit system count, only one half of the read can be performed atomically. Therefore, the sampling mode allows the value of the other half to be sampled and stored in a buffer, and upon the next read of the other half, the sampled value from this buffer is retrieved instead of the actual counter. \\
0x0: No sampling (Default)\\
0x1: Sample upper half of the system count on reading MTIMELO\\
0x2: Sample lower half of the system count on reading MTIMEHI\\
0x3: Sample the other half of the system count on reading MTIMELO or MTIMEHI\\
(R/W)
\end{reglist}
\end{regdesc}
\end{register}

\begin{register}{H}{mtimelo}{0xBFF8}\label{regdesc:CLINTMTIMELOREG}
\regfield{MTIMELO}{32}{0}{{0x00000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}
\begin{reglist}
\label{fielddesc:CLINTMTIMELO}\item [MTIMELO] Represents the current value of the lower 32 bits of the system counter. (RO)
\end{reglist}
\end{regdesc}
\end{register}

\begin{register}{H}{mtimehi}{0xBFFC}\label{regdesc:CLINTMTIMEHIREG}
\regfield{MTIMEHI}{32}{0}{{0x00000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}
\begin{reglist}
\label{fielddesc:CLINTMTIMEHI}\item [MTIMEHI] Represents the current value of the higher 32 bits of the system counter. (RO)
\end{reglist}
\end{regdesc}
\end{register}
