\begin{register}{H}{LP\_UART\_FIFO\_REG}{0x0000}\label{regdesc:LPUARTFIFOREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{LP\_UART\_RXFIFO\_RD\_BYTE}{8}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTRXFIFORDBYTE}\item [LP\_UART\_RXFIFO\_RD\_BYTE] Represents the data LP UART \regindex{n} read from FIFO.\\
Measurement unit: byte. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_TOUT\_CONF\_SYNC\_REG}{0x0064}\label{regdesc:LPUARTTOUTCONFSYNCREG}
\regfield{(reserved)}{20}{12}{00000000000000000000}%
\regfield{LP\_UART\_RX\_TOUT\_THRHD}{10}{2}{{0xa}}%
\regfield{LP\_UART\_RX\_TOUT\_FLOW\_DIS}{1}{1}{{0}}%
\regfield{LP\_UART\_RX\_TOUT\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTRXTOUTEN}\item [LP\_UART\_RX\_TOUT\_EN] Configures whether or not to enable LP UART receiver's timeout function.\\
0: Disable\\
1: Enable\\(R/W)
\label{fielddesc:LPUARTRXTOUTFLOWDIS}\item [LP\_UART\_RX\_TOUT\_FLOW\_DIS] Configures whether or not to disable the idle status counter when hardware flow control is enabled.\\
0: Invalid. No effect\\
1: Disable\\(R/W)
\label{fielddesc:LPUARTRXTOUTTHRHD}\item [LP\_UART\_RX\_TOUT\_THRHD] Configures the amount of time that the bus can remain idle before timeout.\\ Measurement unit: bit time (the time to transmit 1 bit). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_INT\_RAW\_REG}{0x0004}\label{regdesc:LPUARTINTRAWREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{LP\_UART\_WAKEUP\_INT\_RAW}{1}{19}{{0}}%
\regfield{LP\_UART\_AT\_CMD\_CHAR\_DET\_INT\_RAW}{1}{18}{{0}}%
\regfield{(reserved)}{3}{15}{000}%
\regfield{LP\_UART\_TX\_DONE\_INT\_RAW}{1}{14}{{0}}%
\regfield{LP\_UART\_TX\_BRK\_IDLE\_DONE\_INT\_RAW}{1}{13}{{0}}%
\regfield{LP\_UART\_TX\_BRK\_DONE\_INT\_RAW}{1}{12}{{0}}%
\regfield{LP\_UART\_GLITCH\_DET\_INT\_RAW}{1}{11}{{0}}%
\regfield{LP\_UART\_SW\_XOFF\_INT\_RAW}{1}{10}{{0}}%
\regfield{LP\_UART\_SW\_XON\_INT\_RAW}{1}{9}{{0}}%
\regfield{LP\_UART\_RXFIFO\_TOUT\_INT\_RAW}{1}{8}{{0}}%
\regfield{LP\_UART\_BRK\_DET\_INT\_RAW}{1}{7}{{0}}%
\regfield{LP\_UART\_CTS\_CHG\_INT\_RAW}{1}{6}{{0}}%
\regfield{LP\_UART\_DSR\_CHG\_INT\_RAW}{1}{5}{{0}}%
\regfield{LP\_UART\_RXFIFO\_OVF\_INT\_RAW}{1}{4}{{0}}%
\regfield{LP\_UART\_FRM\_ERR\_INT\_RAW}{1}{3}{{0}}%
\regfield{LP\_UART\_PARITY\_ERR\_INT\_RAW}{1}{2}{{0}}%
\regfield{LP\_UART\_TXFIFO\_EMPTY\_INT\_RAW}{1}{1}{{1}}%
\regfield{LP\_UART\_RXFIFO\_FULL\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTRXFIFOFULLINTRAW}\item [LP\_UART\_RXFIFO\_FULL\_INT\_RAW] The raw interrupt status of LP\_UART\_RXFIFO\_FULL\_INT. (R/WTC/SS)
\label{fielddesc:LPUARTTXFIFOEMPTYINTRAW}\item [LP\_UART\_TXFIFO\_EMPTY\_INT\_RAW] The raw interrupt status of LP\_UART\_TXFIFO\_EMPTY\_INT. (R/WTC/SS)
\label{fielddesc:LPUARTPARITYERRINTRAW}\item [LP\_UART\_PARITY\_ERR\_INT\_RAW] The raw interrupt status of LP\_UART\_PARITY\_ERR\_INT. (R/WTC/SS)
\label{fielddesc:LPUARTFRMERRINTRAW}\item [LP\_UART\_FRM\_ERR\_INT\_RAW] The raw interrupt status of LP\_UART\_FRM\_ERR\_INT. (R/WTC/SS)
\label{fielddesc:LPUARTRXFIFOOVFINTRAW}\item [LP\_UART\_RXFIFO\_OVF\_INT\_RAW] The raw interrupt status of LP\_UART\_RXFIFO\_OVF\_INT. (R/WTC/SS)
\label{fielddesc:LPUARTDSRCHGINTRAW}\item [LP\_UART\_DSR\_CHG\_INT\_RAW] The raw interrupt status of LP\_UART\_DSR\_CHG\_INT. (R/WTC/SS)
\label{fielddesc:LPUARTCTSCHGINTRAW}\item [LP\_UART\_CTS\_CHG\_INT\_RAW] The raw interrupt status of LP\_UART\_CTS\_CHG\_INT. (R/WTC/SS)
\label{fielddesc:LPUARTBRKDETINTRAW}\item [LP\_UART\_BRK\_DET\_INT\_RAW] The raw interrupt status of LP\_UART\_BRK\_DET\_INT. (R/WTC/SS)
\label{fielddesc:LPUARTRXFIFOTOUTINTRAW}\item [LP\_UART\_RXFIFO\_TOUT\_INT\_RAW] The raw interrupt status of LP\_UART\_RXFIFO\_TOUT\_INT. (R/WTC/SS)
\label{fielddesc:LPUARTSWXONINTRAW}\item [LP\_UART\_SW\_XON\_INT\_RAW] The raw interrupt status of LP\_UART\_SW\_XON\_INT. (R/WTC/SS)
\label{fielddesc:LPUARTSWXOFFINTRAW}\item [LP\_UART\_SW\_XOFF\_INT\_RAW] LP\_UART\_SW\_XOFF\_INT. (R/WTC/SS)
\label{fielddesc:LPUARTGLITCHDETINTRAW}\item [LP\_UART\_GLITCH\_DET\_INT\_RAW] The raw interrupt status of LP\_UART\_GLITCH\_DET\_INT. (R/WTC/SS)
\label{fielddesc:LPUARTTXBRKDONEINTRAW}\item [LP\_UART\_TX\_BRK\_DONE\_INT\_RAW] The raw interrupt status of LP\_UART\_TX\_BRK\_DONE\_INT. (R/WTC/SS)
\label{fielddesc:LPUARTTXBRKIDLEDONEINTRAW}\item [LP\_UART\_TX\_BRK\_IDLE\_DONE\_INT\_RAW] The raw interrupt status of LP\_UART\_TX\_BRK\_IDLE\_DONE\_INT. (R/WTC/SS)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{LP\_UART\_INT\_RAW\_REG}{0x0004}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:LPUARTTXDONEINTRAW}\item [LP\_UART\_TX\_DONE\_INT\_RAW] The raw interrupt status of LP\_UART\_TX\_DONE\_INT. (R/WTC/SS)
\label{fielddesc:LPUARTATCMDCHARDETINTRAW}\item [LP\_UART\_AT\_CMD\_CHAR\_DET\_INT\_RAW] The raw interrupt status of LP\_UART\_AT\_CMD\_CHAR\_DET\_INT. (R/WTC/SS)
\label{fielddesc:LPUARTWAKEUPINTRAW}\item [LP\_UART\_WAKEUP\_INT\_RAW] The raw interrupt status of LP\_UART\_WAKEUP\_INT. (R/WTC/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_INT\_ST\_REG}{0x0008}\label{regdesc:LPUARTINTSTREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{LP\_UART\_WAKEUP\_INT\_ST}{1}{19}{{0}}%
\regfield{LP\_UART\_AT\_CMD\_CHAR\_DET\_INT\_ST}{1}{18}{{0}}%
\regfield{(reserved)}{3}{15}{000}%
\regfield{LP\_UART\_TX\_DONE\_INT\_ST}{1}{14}{{0}}%
\regfield{LP\_UART\_TX\_BRK\_IDLE\_DONE\_INT\_ST}{1}{13}{{0}}%
\regfield{LP\_UART\_TX\_BRK\_DONE\_INT\_ST}{1}{12}{{0}}%
\regfield{LP\_UART\_GLITCH\_DET\_INT\_ST}{1}{11}{{0}}%
\regfield{LP\_UART\_SW\_XOFF\_INT\_ST}{1}{10}{{0}}%
\regfield{LP\_UART\_SW\_XON\_INT\_ST}{1}{9}{{0}}%
\regfield{LP\_UART\_RXFIFO\_TOUT\_INT\_ST}{1}{8}{{0}}%
\regfield{LP\_UART\_BRK\_DET\_INT\_ST}{1}{7}{{0}}%
\regfield{LP\_UART\_CTS\_CHG\_INT\_ST}{1}{6}{{0}}%
\regfield{LP\_UART\_DSR\_CHG\_INT\_ST}{1}{5}{{0}}%
\regfield{LP\_UART\_RXFIFO\_OVF\_INT\_ST}{1}{4}{{0}}%
\regfield{LP\_UART\_FRM\_ERR\_INT\_ST}{1}{3}{{0}}%
\regfield{LP\_UART\_PARITY\_ERR\_INT\_ST}{1}{2}{{0}}%
\regfield{LP\_UART\_TXFIFO\_EMPTY\_INT\_ST}{1}{1}{{0}}%
\regfield{LP\_UART\_RXFIFO\_FULL\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTRXFIFOFULLINTST}\item [LP\_UART\_RXFIFO\_FULL\_INT\_ST] The masked interrupt status of LP\_UART\_RXFIFO\_FULL\_INT.(RO)
\label{fielddesc:LPUARTTXFIFOEMPTYINTST}\item [LP\_UART\_TXFIFO\_EMPTY\_INT\_ST] The masked interrupt status of LP\_UART\_TXFIFO\_EMPTY\_INT. (RO)
\label{fielddesc:LPUARTPARITYERRINTST}\item [LP\_UART\_PARITY\_ERR\_INT\_ST] The masked interrupt status of LP\_UART\_PARITY\_ERR\_INT. (RO)
\label{fielddesc:LPUARTFRMERRINTST}\item [LP\_UART\_FRM\_ERR\_INT\_ST] The masked interrupt status of LP\_UART\_FRM\_ERR\_INT. (RO)
\label{fielddesc:LPUARTRXFIFOOVFINTST}\item [LP\_UART\_RXFIFO\_OVF\_INT\_ST] The masked interrupt status of LP\_UART\_RXFIFO\_OVF\_INT. (RO)
\label{fielddesc:LPUARTDSRCHGINTST}\item [LP\_UART\_DSR\_CHG\_INT\_ST] The masked interrupt status of LP\_UART\_DSR\_CHG\_INT. (RO)
\label{fielddesc:LPUARTCTSCHGINTST}\item [LP\_UART\_CTS\_CHG\_INT\_ST] The masked interrupt status of LP\_UART\_CTS\_CHG\_INT. (RO)
\label{fielddesc:LPUARTBRKDETINTST}\item [LP\_UART\_BRK\_DET\_INT\_ST] The masked interrupt status of LP\_UART\_BRK\_DET\_INT. (RO)
\label{fielddesc:LPUARTRXFIFOTOUTINTST}\item [LP\_UART\_RXFIFO\_TOUT\_INT\_ST] The masked interrupt status of LP\_UART\_RXFIFO\_TOUT\_INT. (RO)
\label{fielddesc:LPUARTSWXONINTST}\item [LP\_UART\_SW\_XON\_INT\_ST] The masked interrupt status of LP\_UART\_SW\_XON\_INT. (RO)
\label{fielddesc:LPUARTSWXOFFINTST}\item [LP\_UART\_SW\_XOFF\_INT\_ST] The masked interrupt status of LP\_UART\_SW\_XOFF\_INT. (RO)
\label{fielddesc:LPUARTGLITCHDETINTST}\item [LP\_UART\_GLITCH\_DET\_INT\_ST] The masked interrupt status of LP\_UART\_GLITCH\_DET\_INT. (RO)
\label{fielddesc:LPUARTTXBRKDONEINTST}\item [LP\_UART\_TX\_BRK\_DONE\_INT\_ST] The masked interrupt status of LP\_UART\_TX\_BRK\_DONE\_INT. (RO)
\label{fielddesc:LPUARTTXBRKIDLEDONEINTST}\item [LP\_UART\_TX\_BRK\_IDLE\_DONE\_INT\_ST] The masked interrupt status of LP\_UART\_TX\_BRK\_IDLE\_DONE\_INT. (RO)
\label{fielddesc:LPUARTTXDONEINTST}\item [LP\_UART\_TX\_DONE\_INT\_ST] The masked interrupt status of LP\_UART\_TX\_DONE\_INT. (RO)
\label{fielddesc:LPUARTATCMDCHARDETINTST}\item [LP\_UART\_AT\_CMD\_CHAR\_DET\_INT\_ST] The masked interrupt status of LP\_UART\_AT\_CMD\_CHAR\_DET\_INT. (RO)
\label{fielddesc:LPUARTWAKEUPINTST}\item [LP\_UART\_WAKEUP\_INT\_ST] The masked interrupt status of LP\_UART\_WAKEUP\_INT. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_INT\_ENA\_REG}{0x000C}\label{regdesc:LPUARTINTENAREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{LP\_UART\_WAKEUP\_INT\_ENA}{1}{19}{{0}}%
\regfield{LP\_UART\_AT\_CMD\_CHAR\_DET\_INT\_ENA}{1}{18}{{0}}%
\regfield{(reserved)}{3}{15}{000}%
\regfield{LP\_UART\_TX\_DONE\_INT\_ENA}{1}{14}{{0}}%
\regfield{LP\_UART\_TX\_BRK\_IDLE\_DONE\_INT\_ENA}{1}{13}{{0}}%
\regfield{LP\_UART\_TX\_BRK\_DONE\_INT\_ENA}{1}{12}{{0}}%
\regfield{LP\_UART\_GLITCH\_DET\_INT\_ENA}{1}{11}{{0}}%
\regfield{LP\_UART\_SW\_XOFF\_INT\_ENA}{1}{10}{{0}}%
\regfield{LP\_UART\_SW\_XON\_INT\_ENA}{1}{9}{{0}}%
\regfield{LP\_UART\_RXFIFO\_TOUT\_INT\_ENA}{1}{8}{{0}}%
\regfield{LP\_UART\_BRK\_DET\_INT\_ENA}{1}{7}{{0}}%
\regfield{LP\_UART\_CTS\_CHG\_INT\_ENA}{1}{6}{{0}}%
\regfield{LP\_UART\_DSR\_CHG\_INT\_ENA}{1}{5}{{0}}%
\regfield{LP\_UART\_RXFIFO\_OVF\_INT\_ENA}{1}{4}{{0}}%
\regfield{LP\_UART\_FRM\_ERR\_INT\_ENA}{1}{3}{{0}}%
\regfield{LP\_UART\_PARITY\_ERR\_INT\_ENA}{1}{2}{{0}}%
\regfield{LP\_UART\_TXFIFO\_EMPTY\_INT\_ENA}{1}{1}{{0}}%
\regfield{LP\_UART\_RXFIFO\_FULL\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTRXFIFOFULLINTENA}\item [LP\_UART\_RXFIFO\_FULL\_INT\_ENA] Write 1 to enable LP\_UART\_RXFIFO\_FULL\_INT. (R/W)
\label{fielddesc:LPUARTTXFIFOEMPTYINTENA}\item [LP\_UART\_TXFIFO\_EMPTY\_INT\_ENA] Write 1 to enable LP\_UART\_TXFIFO\_EMPTY\_INT.  (R/W)
\label{fielddesc:LPUARTPARITYERRINTENA}\item [LP\_UART\_PARITY\_ERR\_INT\_ENA] Write 1 to enable LP\_UART\_PARITY\_ERR\_INT. (R/W)
\label{fielddesc:LPUARTFRMERRINTENA}\item [LP\_UART\_FRM\_ERR\_INT\_ENA] Write 1 to enable LP\_UART\_FRM\_ERR\_INT. (R/W)
\label{fielddesc:LPUARTRXFIFOOVFINTENA}\item [LP\_UART\_RXFIFO\_OVF\_INT\_ENA] Write 1 to enable LP\_UART\_RXFIFO\_OVF\_INT. (R/W)
\label{fielddesc:LPUARTDSRCHGINTENA}\item [LP\_UART\_DSR\_CHG\_INT\_ENA] Write 1 to enable LP\_UART\_DSR\_CHG\_INT. (R/W)
\label{fielddesc:LPUARTCTSCHGINTENA}\item [LP\_UART\_CTS\_CHG\_INT\_ENA] Write 1 to enable LP\_UART\_CTS\_CHG\_INT. (R/W)
\label{fielddesc:LPUARTBRKDETINTENA}\item [LP\_UART\_BRK\_DET\_INT\_ENA] Write 1 to enable LP\_UART\_BRK\_DET\_INT. (R/W)
\label{fielddesc:LPUARTRXFIFOTOUTINTENA}\item [LP\_UART\_RXFIFO\_TOUT\_INT\_ENA] Write 1 to enable LP\_UART\_RXFIFO\_TOUT\_INT. (R/W)
\label{fielddesc:LPUARTSWXONINTENA}\item [LP\_UART\_SW\_XON\_INT\_ENA] Write 1 to enable LP\_UART\_SW\_XON\_INT.(R/W)
\label{fielddesc:LPUARTSWXOFFINTENA}\item [LP\_UART\_SW\_XOFF\_INT\_ENA] Write 1 to enable LP\_UART\_SW\_XOFF\_INT. (R/W)
\label{fielddesc:LPUARTGLITCHDETINTENA}\item [LP\_UART\_GLITCH\_DET\_INT\_ENA] Write 1 to enable LP\_UART\_GLITCH\_DET\_INT. (R/W)
\label{fielddesc:LPUARTTXBRKDONEINTENA}\item [LP\_UART\_TX\_BRK\_DONE\_INT\_ENA] Write 1 to enable LP\_UART\_TX\_BRK\_DONE\_INT. (R/W)
\label{fielddesc:LPUARTTXBRKIDLEDONEINTENA}\item [LP\_UART\_TX\_BRK\_IDLE\_DONE\_INT\_ENA] Write 1 to enable LP\_UART\_TX\_BRK\_IDLE\_DONE\_INT. (R/W)
\label{fielddesc:LPUARTTXDONEINTENA}\item [LP\_UART\_TX\_DONE\_INT\_ENA] Write 1 to enable LP\_UART\_TX\_DONE\_INT. (R/W)
\label{fielddesc:LPUARTATCMDCHARDETINTENA}\item [LP\_UART\_AT\_CMD\_CHAR\_DET\_INT\_ENA] Write 1 to enable LP\_UART\_AT\_CMD\_CHAR\_DET\_INT. (R/W)
\label{fielddesc:LPUARTWAKEUPINTENA}\item [LP\_UART\_WAKEUP\_INT\_ENA] Write 1 to enable LP\_UART\_WAKEUP\_INT. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_INT\_CLR\_REG}{0x0010}\label{regdesc:LPUARTINTCLRREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{LP\_UART\_WAKEUP\_INT\_CLR}{1}{19}{{0}}%
\regfield{LP\_UART\_AT\_CMD\_CHAR\_DET\_INT\_CLR}{1}{18}{{0}}%
\regfield{(reserved)}{3}{15}{000}%
\regfield{LP\_UART\_TX\_DONE\_INT\_CLR}{1}{14}{{0}}%
\regfield{LP\_UART\_TX\_BRK\_IDLE\_DONE\_INT\_CLR}{1}{13}{{0}}%
\regfield{LP\_UART\_TX\_BRK\_DONE\_INT\_CLR}{1}{12}{{0}}%
\regfield{LP\_UART\_GLITCH\_DET\_INT\_CLR}{1}{11}{{0}}%
\regfield{LP\_UART\_SW\_XOFF\_INT\_CLR}{1}{10}{{0}}%
\regfield{LP\_UART\_SW\_XON\_INT\_CLR}{1}{9}{{0}}%
\regfield{LP\_UART\_RXFIFO\_TOUT\_INT\_CLR}{1}{8}{{0}}%
\regfield{LP\_UART\_BRK\_DET\_INT\_CLR}{1}{7}{{0}}%
\regfield{LP\_UART\_CTS\_CHG\_INT\_CLR}{1}{6}{{0}}%
\regfield{LP\_UART\_DSR\_CHG\_INT\_CLR}{1}{5}{{0}}%
\regfield{LP\_UART\_RXFIFO\_OVF\_INT\_CLR}{1}{4}{{0}}%
\regfield{LP\_UART\_FRM\_ERR\_INT\_CLR}{1}{3}{{0}}%
\regfield{LP\_UART\_PARITY\_ERR\_INT\_CLR}{1}{2}{{0}}%
\regfield{LP\_UART\_TXFIFO\_EMPTY\_INT\_CLR}{1}{1}{{0}}%
\regfield{LP\_UART\_RXFIFO\_FULL\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTRXFIFOFULLINTCLR}\item [LP\_UART\_RXFIFO\_FULL\_INT\_CLR] Write 1 to clear LP\_UART\_RXFIFO\_FULL\_INT. (WT)
\label{fielddesc:LPUARTTXFIFOEMPTYINTCLR}\item [LP\_UART\_TXFIFO\_EMPTY\_INT\_CLR] Write 1 to clear LP\_UART\_TXFIFO\_EMPTY\_INT. (WT)
\label{fielddesc:LPUARTPARITYERRINTCLR}\item [LP\_UART\_PARITY\_ERR\_INT\_CLR] Write 1 to clear LP\_UART\_PARITY\_ERR\_INT. (WT)
\label{fielddesc:LPUARTFRMERRINTCLR}\item [LP\_UART\_FRM\_ERR\_INT\_CLR] Write 1 to clear LP\_UART\_FRM\_ERR\_INT. (WT)
\label{fielddesc:LPUARTRXFIFOOVFINTCLR}\item [LP\_UART\_RXFIFO\_OVF\_INT\_CLR] Write 1 to clear LP\_UART\_RXFIFO\_OVF\_INT. (WT)
\label{fielddesc:LPUARTDSRCHGINTCLR}\item [LP\_UART\_DSR\_CHG\_INT\_CLR] Write 1 to clear LP\_UART\_DSR\_CHG\_INT. (WT)
\label{fielddesc:LPUARTCTSCHGINTCLR}\item [LP\_UART\_CTS\_CHG\_INT\_CLR] Write 1 to clear LP\_UART\_CTS\_CHG\_INT. (WT)
\label{fielddesc:LPUARTBRKDETINTCLR}\item [LP\_UART\_BRK\_DET\_INT\_CLR] Write 1 to clear LP\_UART\_BRK\_DET\_INT. (WT)
\label{fielddesc:LPUARTRXFIFOTOUTINTCLR}\item [LP\_UART\_RXFIFO\_TOUT\_INT\_CLR] Write 1 to clear LP\_UART\_RXFIFO\_TOUT\_INT. (WT)
\label{fielddesc:LPUARTSWXONINTCLR}\item [LP\_UART\_SW\_XON\_INT\_CLR] Write 1 to clear LP\_UART\_SW\_XON\_INT. (WT)
\label{fielddesc:LPUARTSWXOFFINTCLR}\item [LP\_UART\_SW\_XOFF\_INT\_CLR] Write 1 to clear LP\_UART\_SW\_XOFF\_INT. (WT)
\label{fielddesc:LPUARTGLITCHDETINTCLR}\item [LP\_UART\_GLITCH\_DET\_INT\_CLR] Write 1 to clear LP\_UART\_GLITCH\_DET\_INT. (WT)
\label{fielddesc:LPUARTTXBRKDONEINTCLR}\item [LP\_UART\_TX\_BRK\_DONE\_INT\_CLR] Write 1 to clear LP\_UART\_TX\_BRK\_DONE\_INT. (WT)
\label{fielddesc:LPUARTTXBRKIDLEDONEINTCLR}\item [LP\_UART\_TX\_BRK\_IDLE\_DONE\_INT\_CLR] Write 1 to clear LP\_UART\_TX\_BRK\_IDLE\_DONE\_INT. (WT)
\label{fielddesc:LPUARTTXDONEINTCLR}\item [LP\_UART\_TX\_DONE\_INT\_CLR] Write 1 to clear LP\_UART\_TX\_DONE\_INT. (WT)
\label{fielddesc:LPUARTATCMDCHARDETINTCLR}\item [LP\_UART\_AT\_CMD\_CHAR\_DET\_INT\_CLR] Write 1 to clear LP\_UART\_AT\_CMD\_CHAR\_DET\_INT. (WT)
\label{fielddesc:LPUARTWAKEUPINTCLR}\item [LP\_UART\_WAKEUP\_INT\_CLR] Write 1 to clear LP\_UART\_WAKEUP\_INT. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_CLKDIV\_SYNC\_REG}{0x0014}\label{regdesc:LPUARTCLKDIVSYNCREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{LP\_UART\_CLKDIV\_FRAG}{4}{20}{{0x0}}%
\regfield{(reserved)}{8}{12}{00000000}%
\regfield{LP\_UART\_CLKDIV}{12}{0}{{0x2b6}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTCLKDIV}\item [LP\_UART\_CLKDIV] Configures the integral part of the divisor for baud rate generation. (R/W)
\label{fielddesc:LPUARTCLKDIVFRAG}\item [LP\_UART\_CLKDIV\_FRAG] Configures the fractional part of the divisor for baud rate generation. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_RX\_FILT\_REG}{0x0018}\label{regdesc:LPUARTRXFILTREG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{LP\_UART\_GLITCH\_FILT\_EN}{1}{8}{{0}}%
\regfield{LP\_UART\_GLITCH\_FILT}{8}{0}{{0x8}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTGLITCHFILT}\item [LP\_UART\_GLITCH\_FILT] Configures the width of a pulse to be filtered.\\Measurement unit: UART Core's clock cycle.\\Pulses whose width is lower than this value will be ignored. (R/W)
\label{fielddesc:LPUARTGLITCHFILTEN}\item [LP\_UART\_GLITCH\_FILT\_EN] Configures whether or not to enable RX signal filter.\\
0: Disable\\
1: Enable\\(R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_CONF0\_SYNC\_REG}{0x0020}\label{regdesc:LPUARTCONF0SYNCREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{LP\_UART\_TXFIFO\_RST}{1}{23}{{0}}%
\regfield{LP\_UART\_RXFIFO\_RST}{1}{22}{{0}}%
\regfield{LP\_UART\_SW\_RTS}{1}{21}{{0}}%
\regfield{LP\_UART\_MEM\_CLK\_EN}{1}{20}{{0}}%
\regfield{(reserved)}{1}{19}{{0}}%
\regfield{LP\_UART\_ERR\_WR\_MASK}{1}{18}{{0}}%
\regfield{LP\_UART\_DIS\_RX\_DAT\_OVF}{1}{17}{{0}}%
\regfield{LP\_UART\_TXD\_INV}{1}{16}{{0}}%
\regfield{LP\_UART\_RXD\_INV}{1}{15}{{0}}%
\regfield{(reserved)}{1}{14}{{0}}%
\regfield{LP\_UART\_TX\_FLOW\_EN}{1}{13}{{0}}%
\regfield{LP\_UART\_LOOPBACK}{1}{12}{{00000}}%
\regfield{(reserved)}{5}{7}{{0}}%
\regfield{LP\_UART\_TXD\_BRK}{1}{6}{{0}}%
\regfield{LP\_UART\_STOP\_BIT\_NUM}{2}{4}{{1}}%
\regfield{LP\_UART\_BIT\_NUM}{2}{2}{{3}}%
\regfield{LP\_UART\_PARITY\_EN}{1}{1}{{0}}%
\regfield{LP\_UART\_PARITY}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTPARITY}\item [LP\_UART\_PARITY] Configures the parity check mode.\\
0: Even parity\\
1: Odd parity\\(R/W)
\label{fielddesc:LPUARTPARITYEN}\item [LP\_UART\_PARITY\_EN] Configures whether or not to enable LP UART parity check.\\
0: Disable\\
1: Enable\\(R/W)
\label{fielddesc:LPUARTBITNUM}\item [LP\_UART\_BIT\_NUM] Configures the number of data bits.\\
0: 5 bits\\
1: 6 bits\\
2: 7 bits\\
3: 8 bits\\(R/W)
\label{fielddesc:LPUARTSTOPBITNUM}\item [LP\_UART\_STOP\_BIT\_NUM] Configures the number of stop bits.\\
0: Invalid. No effect\\
1: 1 bit\\
2: 1.5 bits\\
3: 2 bits\\(R/W)
\label{fielddesc:LPUARTTXDBRK}\item [LP\_UART\_TXD\_BRK] Configures whether or not to send NULL characters when finishing data transmission.\\
0: Not send\\
1: Send\\(R/W)
\label{fielddesc:LPUARTLOOPBACK}\item [LP\_UART\_LOOPBACK] Configures whether or not to enable LP UART loopback test.\\
0: Disable\\
1: Enable\\ (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{LP\_UART\_CONF0\_SYNC\_REG}{0x0020}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:LPUARTTXFLOWEN}\item [LP\_UART\_TX\_FLOW\_EN] Configures whether or not to enable flow control for the transmitter.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:LPUARTRXDINV}\item [LP\_UART\_RXD\_INV] Configures whether or not to invert the level of LP UART RXD signal.\\
0: Not invert\\
1: Invert\\ (R/W)
\label{fielddesc:LPUARTTXDINV}\item [LP\_UART\_TXD\_INV] Configures whether or not to invert the level of LP UART TXD signal.\\
0: Not invert\\
1: Invert\\ (R/W)
\label{fielddesc:LPUARTDISRXDATOVF}\item [LP\_UART\_DIS\_RX\_DAT\_OVF] Configures whether or not to disable data overflow detection for the LP UART receiver.\\
0: Enable\\
1: Disable\\(R/W)
\label{fielddesc:LPUARTERRWRMASK}\item [LP\_UART\_ERR\_WR\_MASK] Configures whether or not to store the received data with errors into FIFO.\\
0: Store\\
1: Not store\\(R/W)
\label{fielddesc:LPUARTMEMCLKEN}\item [LP\_UART\_MEM\_CLK\_EN] Configures whether or not to enable clock gating for LP UART memory.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:LPUARTSWRTS}\item [LP\_UART\_SW\_RTS] Configures the RTS signal used in software flow control.\\
0: The LP UART transmitter is not allowed to send data.\\
1: The LP UART transmitted is allowed to send data.\\(R/W)
\label{fielddesc:LPUARTRXFIFORST}\item [LP\_UART\_RXFIFO\_RST] Configures whether or not to reset the LP UART RX FIFO.\\
0: Not reset\\
1: Reset\\(R/W)
\label{fielddesc:LPUARTTXFIFORST}\item [LP\_UART\_TXFIFO\_RST] Configures whether or not to reset the LP UART TX FIFO.\\
0: Not reset\\
1: Reset\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_CONF1\_REG}{0x0024}\label{regdesc:LPUARTCONF1REG}
\regfield{(reserved)}{10}{22}{0000000000}%
\regfield{LP\_UART\_CLK\_EN}{1}{21}{{0}}%
\regfield{LP\_UART\_SW\_DTR}{1}{20}{{0}}%
\regfield{LP\_UART\_DTR\_INV}{1}{19}{{0}}%
\regfield{LP\_UART\_RTS\_INV}{1}{18}{{0}}%
\regfield{LP\_UART\_DSR\_INV}{1}{17}{{0}}%
\regfield{LP\_UART\_CTS\_INV}{1}{16}{{0}}%
\regfield{LP\_UART\_TXFIFO\_EMPTY\_THRHD}{5}{11}{{0xc}}%
\regfield{(reserved)}{3}{8}{000}%
\regfield{LP\_UART\_RXFIFO\_FULL\_THRHD}{5}{3}{{0xc}}%
\regfield{(reserved)}{3}{0}{000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTRXFIFOFULLTHRHD}\item [LP\_UART\_RXFIFO\_FULL\_THRHD] Configures the threshold for RX FIFO being full.\\Measurement unit: byte. (R/W)
\label{fielddesc:LPUARTTXFIFOEMPTYTHRHD}\item [LP\_UART\_TXFIFO\_EMPTY\_THRHD] Configures the threshold for TX FIFO being empty.\\Measurement unit: byte. (R/W)
\label{fielddesc:LPUARTCTSINV}\item [LP\_UART\_CTS\_INV] Configures whether or not to invert the level of LP UART CTS signal.\\
0: Not invert\\
1: Invert\\ (R/W)
\label{fielddesc:LPUARTDSRINV}\item [LP\_UART\_DSR\_INV] Configures whether or not to invert the level of LP UART DSR signal.\\
0: Not invert\\
1: Invert\\ (R/W)
\label{fielddesc:LPUARTRTSINV}\item [LP\_UART\_RTS\_INV] Configures whether or not to invert the level of LP UART RTS signal.\\
0: Not invert\\
1: Invert\\ (R/W)
\label{fielddesc:LPUARTDTRINV}\item [LP\_UART\_DTR\_INV] Configures whether or not to invert the level of LP UART DTR signal.\\
0: Not invert\\
1: Invert\\ (R/W)
\label{fielddesc:LPUARTSWDTR}\item [LP\_UART\_SW\_DTR] Configures the DTR signal used in software flow control.\\
0: Data to be transmitted is not ready.\\
1: Data to be transmitted is ready.\\(R/W)
\label{fielddesc:LPUARTCLKEN}\item [LP\_UART\_CLK\_EN] Configures clock gating.\\
0: Support clock only when the application writes registers.\\
1: Always force the clock on for registers.\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_HWFC\_CONF\_SYNC\_REG}{0x002C}\label{regdesc:LPUARTHWFCCONFSYNCREG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{LP\_UART\_RX\_FLOW\_EN}{1}{8}{{0}}%
\regfield{LP\_UART\_RX\_FLOW\_THRHD}{5}{3}{{0x0}}%
\regfield{(reserved)}{3}{0}{000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTRXFLOWTHRHD}\item [LP\_UART\_RX\_FLOW\_THRHD] Configures the maximum number of data bytes that can be received  during hardware flow control.\\Measurement unit: byte. (R/W)
\label{fielddesc:LPUARTRXFLOWEN}\item [LP\_UART\_RX\_FLOW\_EN] Configures whether or not to enable the LP UART receiver.\\
0: Disable\\
1: Enable\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_SLEEP\_CONF0\_REG}{0x0030}\label{regdesc:LPUARTSLEEPCONF0REG}
\regfield{LP\_UART\_WK\_CHAR4}{8}{24}{{0x0}}%
\regfield{LP\_UART\_WK\_CHAR3}{8}{16}{{0x0}}%
\regfield{LP\_UART\_WK\_CHAR2}{8}{8}{{0x0}}%
\regfield{LP\_UART\_WK\_CHAR1}{8}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTWKCHAR1}\item [LP\_UART\_WK\_CHAR1] Configures wakeup character 1. (R/W)
\label{fielddesc:LPUARTWKCHAR2}\item [LP\_UART\_WK\_CHAR2] Configures wakeup character 2. (R/W)
\label{fielddesc:LPUARTWKCHAR3}\item [LP\_UART\_WK\_CHAR3] Configures wakeup character 3. (R/W)
\label{fielddesc:LPUARTWKCHAR4}\item [LP\_UART\_WK\_CHAR4] Configures wakeup character 4. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_SLEEP\_CONF1\_REG}{0x0034}\label{regdesc:LPUARTSLEEPCONF1REG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{LP\_UART\_WK\_CHAR0}{8}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTWKCHAR0}\item [LP\_UART\_WK\_CHAR0] Configures wakeup character 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_SLEEP\_CONF2\_REG}{0x0038}\label{regdesc:LPUARTSLEEPCONF2REG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{LP\_UART\_WK\_MODE\_SEL}{2}{26}{{0}}%
\regfield{LP\_UART\_WK\_CHAR\_MASK}{5}{21}{{0x0}}%
\regfield{LP\_UART\_WK\_CHAR\_NUM}{3}{18}{{0x5}}%
\regfield{LP\_UART\_RX\_WAKE\_UP\_THRHD}{5}{13}{{1}}%
\regfield{(reserved)}{3}{10}{000}%
\regfield{LP\_UART\_ACTIVE\_THRESHOLD}{10}{0}{{0xf0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTACTIVETHRESHOLD}\item [LP\_UART\_ACTIVE\_THRESHOLD] Configures the number of RXD edge changes to wake up the chip in wakeup mode 0. (R/W)
\label{fielddesc:LPUARTRXWAKEUPTHRHD}\item [LP\_UART\_RX\_WAKE\_UP\_THRHD] Configures the number of received data bytes to wake up the chip in wakeup mode 1. (R/W)
\label{fielddesc:LPUARTWKCHARNUM}\item [LP\_UART\_WK\_CHAR\_NUM] Configures the number of wakeup characters. (R/W)
\label{fielddesc:LPUARTWKCHARMASK}\item [LP\_UART\_WK\_CHAR\_MASK] Configures whether or not to mask wakeup characters.\\
0: Not mask\\
1: Mask\\(R/W)
\label{fielddesc:LPUARTWKMODESEL}\item [LP\_UART\_WK\_MODE\_SEL] Configures which wakeup mode to select.\\
0: Mode 0\\
1: Mode 1\\
2: Mode 2\\
3: Mode 3\\(R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_SWFC\_CONF0\_SYNC\_REG}{0x003C}\label{regdesc:LPUARTSWFCCONF0SYNCREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{LP\_UART\_SEND\_XOFF}{1}{22}{{0}}%
\regfield{LP\_UART\_SEND\_XON}{1}{21}{{0}}%
\regfield{LP\_UART\_FORCE\_XOFF}{1}{20}{{0}}%
\regfield{LP\_UART\_FORCE\_XON}{1}{19}{{0}}%
\regfield{LP\_UART\_XONOFF\_DEL}{1}{18}{{0}}%
\regfield{LP\_UART\_SW\_FLOW\_CON\_EN}{1}{17}{{0}}%
\regfield{LP\_UART\_XON\_XOFF\_STILL\_SEND}{1}{16}{{0}}%
\regfield{LP\_UART\_XOFF\_CHAR}{8}{8}{{0x13}}%
\regfield{LP\_UART\_XON\_CHAR}{8}{0}{{0x11}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTXONCHAR}\item [LP\_UART\_XON\_CHAR] Configures the XON character for flow control. (R/W)
\label{fielddesc:LPUARTXOFFCHAR}\item [LP\_UART\_XOFF\_CHAR] Configures the XOFF character for flow control. (R/W)
\label{fielddesc:LPUARTXONXOFFSTILLSEND}\item [LP\_UART\_XON\_XOFF\_STILL\_SEND] Configures whether the LP UART transmitter can send XON or XOFF characters when it is disabled.\\
0: Cannot send\\
1: Can send\\ (R/W)
\label{fielddesc:LPUARTSWFLOWCONEN}\item [LP\_UART\_SW\_FLOW\_CON\_EN] Configures whether or not to enable software flow control.\\
0: Disable\\
1: Enable\\(R/W)
\label{fielddesc:LPUARTXONOFFDEL}\item [LP\_UART\_XONOFF\_DEL] Configures whether or not to remove flow control characters from the received data.\\
0: Not move\\
1: Move\\(R/W)
\label{fielddesc:LPUARTFORCEXON}\item [LP\_UART\_FORCE\_XON] Configures whether the transmitter continues to sending data.\\
0: Not send\\
1: Send\\(R/W)
\label{fielddesc:LPUARTFORCEXOFF}\item [LP\_UART\_FORCE\_XOFF] Configures whether or not to stop the transmitter from sending data.\\
0: Not stop\\
1: Stop\\(R/W)
\label{fielddesc:LPUARTSENDXON}\item [LP\_UART\_SEND\_XON] Configures whether or not to send XON characters.\\
0: Not send\\
1: Send\\(R/W/SS/SC)
\label{fielddesc:LPUARTSENDXOFF}\item [LP\_UART\_SEND\_XOFF] Configures whether or not to send XOFF characters.\\
0: Not send\\
1: Send\\(R/W/SS/SC)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_SWFC\_CONF1\_REG}{0x0040}\label{regdesc:LPUARTSWFCCONF1REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{LP\_UART\_XOFF\_THRESHOLD}{5}{11}{{0xc}}%
\regfield{(reserved)}{3}{8}{000}%
\regfield{LP\_UART\_XON\_THRESHOLD}{5}{3}{{0x0}}%
\regfield{(reserved)}{3}{0}{000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTXONTHRESHOLD}\item [LP\_UART\_XON\_THRESHOLD] Configures the threshold for data in RX FIFO to send XON characters in software flow control.\\Measurement unit: byte. (R/W)
\label{fielddesc:LPUARTXOFFTHRESHOLD}\item [LP\_UART\_XOFF\_THRESHOLD]  Configures the threshold for data in RX FIFO to send XOFF characters in software flow control.\\Measurement unit: byte. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_TXBRK\_CONF\_SYNC\_REG}{0x0044}\label{regdesc:LPUARTTXBRKCONFSYNCREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{LP\_UART\_TX\_BRK\_NUM}{8}{0}{{0xa}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTTXBRKNUM}\item [LP\_UART\_TX\_BRK\_NUM] Configures the number of NULL characters to be sent after finishing data transmission.\\Valid only when LP\_UART\_TXD\_BRK is 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_IDLE\_CONF\_SYNC\_REG}{0x0048}\label{regdesc:LPUARTIDLECONFSYNCREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{LP\_UART\_TX\_IDLE\_NUM}{10}{10}{{0x100}}%
\regfield{LP\_UART\_RX\_IDLE\_THRHD}{10}{0}{{0x100}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTRXIDLETHRHD}\item [LP\_UART\_RX\_IDLE\_THRHD] Configures the threshold to generate a frame end signal when the receiver takes more time to receive one data byte data.\\Measurement unit: bit time (the time to transmit 1 bit). (R/W)
\label{fielddesc:LPUARTTXIDLENUM}\item [LP\_UART\_TX\_IDLE\_NUM] Configures the interval between two data transfers.\\Measurement unit: bit time (the time to transmit 1 bit). (R/W)
\end{reglist}\end{regdesc}
\end{register}




\begin{register}{H}{LP\_UART\_CLK\_CONF\_REG}{0x0088}\label{regdesc:LPUARTCLKCONFREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{LP\_UART\_RX\_RST\_CORE}{1}{27}{{0}}%
\regfield{LP\_UART\_TX\_RST\_CORE}{1}{26}{{0}}%
\regfield{LP\_UART\_RX\_SCLK\_EN}{1}{25}{{1}}%
\regfield{LP\_UART\_TX\_SCLK\_EN}{1}{24}{{1}}%
\regfield{(reserved)}{24}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTTXSCLKEN}\item [LP\_UART\_TX\_SCLK\_EN] Configures whether or not to enable LP UART TX clock.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:LPUARTRXSCLKEN}\item [LP\_UART\_RX\_SCLK\_EN] Configures whether or not to enable LP UART RX clock.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:LPUARTTXRSTCORE}\item [LP\_UART\_TX\_RST\_CORE] Write 1 and then write 0 to reset LP UART TX. (R/W)
\label{fielddesc:LPUARTRXRSTCORE}\item [LP\_UART\_RX\_RST\_CORE] Write 1 and then write 0 to reset LP UART RX. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_STATUS\_REG}{0x001C}\label{regdesc:LPUARTSTATUSREG}
\regfield{LP\_UART\_TXD}{1}{31}{{1}}%
\regfield{LP\_UART\_RTSN}{1}{30}{{1}}%
\regfield{LP\_UART\_DTRN}{1}{29}{{1}}%
\regfield{(reserved)}{5}{24}{00000}%
\regfield{LP\_UART\_TXFIFO\_CNT}{5}{19}{{0}}%
\regfield{(reserved)}{3}{16}{000}%
\regfield{LP\_UART\_RXD}{1}{15}{{1}}%
\regfield{LP\_UART\_CTSN}{1}{14}{{1}}%
\regfield{LP\_UART\_DSRN}{1}{13}{{0}}%
\regfield{(reserved)}{5}{8}{00000}%
\regfield{LP\_UART\_RXFIFO\_CNT}{5}{3}{{0}}%
\regfield{(reserved)}{3}{0}{000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTRXFIFOCNT}\item [LP\_UART\_RXFIFO\_CNT] Represents the number of valid data bytes in RX FIFO. (RO)
\label{fielddesc:LPUARTDSRN}\item [LP\_UART\_DSRN] Represents the level of the internal LP UART DSR signal. (RO)
\label{fielddesc:LPUARTCTSN}\item [LP\_UART\_CTSN] Represents the level of the internal LP UART CTS signal. (RO)
\label{fielddesc:LPUARTRXD}\item [LP\_UART\_RXD] Represents the  level of the internal LP UART RXD signal. (RO)
\label{fielddesc:LPUARTTXFIFOCNT}\item [LP\_UART\_TXFIFO\_CNT] Represents the number of valid data bytes in RX FIFO. (RO)
\label{fielddesc:LPUARTDTRN}\item [LP\_UART\_DTRN] Represents the level of the internal LP UART DTR signal. (RO)
\label{fielddesc:LPUARTRTSN}\item [LP\_UART\_RTSN] Represents the level of the internal LP UART RTS signal. (RO)
\label{fielddesc:LPUARTTXD}\item [LP\_UART\_TXD] Represents the  level of the internal LP UART TXD signal. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_MEM\_TX\_STATUS\_REG}{0x0068}\label{regdesc:LPUARTMEMTXSTATUSREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{LP\_UART\_TX\_SRAM\_RADDR}{5}{12}{{0x0}}%
\regfield{(reserved)}{4}{8}{0000}%
\regfield{LP\_UART\_TX\_SRAM\_WADDR}{5}{3}{{0x0}}%
\regfield{(reserved)}{3}{0}{000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTTXSRAMWADDR}\item [LP\_UART\_TX\_SRAM\_WADDR] Represents the offset address to write TX FIFO. (RO)
\label{fielddesc:LPUARTTXSRAMRADDR}\item [LP\_UART\_TX\_SRAM\_RADDR] Represents the offset address to read TX FIFO. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_MEM\_RX\_STATUS\_REG}{0x006C}\label{regdesc:LPUARTMEMRXSTATUSREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{LP\_UART\_RX\_SRAM\_WADDR}{5}{12}{{0x10}}%
\regfield{(reserved)}{4}{8}{0000}%
\regfield{LP\_UART\_RX\_SRAM\_RADDR}{5}{3}{{0x10}}%
\regfield{(reserved)}{3}{0}{000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTRXSRAMRADDR}\item [LP\_UART\_RX\_SRAM\_RADDR] Represents the offset address to read RX FIFO. (RO)
\label{fielddesc:LPUARTRXSRAMWADDR}\item [LP\_UART\_RX\_SRAM\_WADDR] Represents the offset address to write RX FIFO. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_FSM\_STATUS\_REG}{0x0070}\label{regdesc:LPUARTFSMSTATUSREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{LP\_UART\_ST\_UTX\_OUT}{4}{4}{{0}}%
\regfield{LP\_UART\_ST\_URX\_OUT}{4}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTSTURXOUT}\item [LP\_UART\_ST\_URX\_OUT] Represents the status of the receiver. (RO)
\label{fielddesc:LPUARTSTUTXOUT}\item [LP\_UART\_ST\_UTX\_OUT] Represents the status of the transmitter. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_AFIFO\_STATUS\_REG}{0x0090}\label{regdesc:LPUARTAFIFOSTATUSREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{LP\_UART\_RX\_AFIFO\_EMPTY}{1}{3}{{1}}%
\regfield{LP\_UART\_RX\_AFIFO\_FULL}{1}{2}{{0}}%
\regfield{LP\_UART\_TX\_AFIFO\_EMPTY}{1}{1}{{1}}%
\regfield{LP\_UART\_TX\_AFIFO\_FULL}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTTXAFIFOFULL}\item [LP\_UART\_TX\_AFIFO\_FULL] Represents whether or not the APB TX asynchronous FIFO is full.\\
0: Not full\\
1: Full\\(RO)
\label{fielddesc:LPUARTTXAFIFOEMPTY}\item [LP\_UART\_TX\_AFIFO\_EMPTY] Represents whether or not the APB TX asynchronous FIFO is empty.\\
0: Not empty\\
1: Empty\\ (RO)
\label{fielddesc:LPUARTRXAFIFOFULL}\item [LP\_UART\_RX\_AFIFO\_FULL] Represents whether or not the APB RX asynchronous FIFO is full.\\
0: Not full\\
1: Full\\ (RO)
\label{fielddesc:LPUARTRXAFIFOEMPTY}\item [LP\_UART\_RX\_AFIFO\_EMPTY] Represents whether or not the APB RX asynchronous FIFO is empty.\\
0: Not empty\\
1: Empty\\ (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_AT\_CMD\_PRECNT\_SYNC\_REG}{0x0050}\label{regdesc:LPUARTATCMDPRECNTSYNCREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{LP\_UART\_PRE\_IDLE\_NUM}{16}{0}{{0x901}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTPREIDLENUM}\item [LP\_UART\_PRE\_IDLE\_NUM] Configures the idle time before the receiver receives the first AT\_CMD.\\Measurement unit: bit time (the time to transmit 1 bit). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_AT\_CMD\_POSTCNT\_SYNC\_REG}{0x0054}\label{regdesc:LPUARTATCMDPOSTCNTSYNCREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{LP\_UART\_POST\_IDLE\_NUM}{16}{0}{{0x901}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTPOSTIDLENUM}\item [LP\_UART\_POST\_IDLE\_NUM] Configures the interval between the last AT\_CMD and subsequent data.\\Measurement unit: bit time (the time to transmit 1 bit). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_AT\_CMD\_GAPTOUT\_SYNC\_REG}{0x0058}\label{regdesc:LPUARTATCMDGAPTOUTSYNCREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{LP\_UART\_RX\_GAP\_TOUT}{16}{0}{{11}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTRXGAPTOUT}\item [LP\_UART\_RX\_GAP\_TOUT] Configures the interval between two AT\_CMD characters.\\Measurement unit: bit time (the time to transmit 1 bit). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_AT\_CMD\_CHAR\_SYNC\_REG}{0x005C}\label{regdesc:LPUARTATCMDCHARSYNCREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{LP\_UART\_CHAR\_NUM}{8}{8}{{0x3}}%
\regfield{LP\_UART\_AT\_CMD\_CHAR}{8}{0}{{0x2b}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTATCMDCHAR}\item [LP\_UART\_AT\_CMD\_CHAR] Configures the AT\_CMD character. (R/W)
\label{fielddesc:LPUARTCHARNUM}\item [LP\_UART\_CHAR\_NUM] Configures the number of continuous AT\_CMD characters a receiver can receive. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_DATE\_REG}{0x008C}\label{regdesc:LPUARTDATEREG}
\regfield{LP\_UART\_DATE}{32}{0}{{0x2305050}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTDATE}\item [LP\_UART\_DATE] Version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_REG\_UPDATE\_REG}{0x0098}\label{regdesc:LPUARTREGUPDATEREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{LP\_UART\_REG\_UPDATE}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTREGUPDATE}\item [LP\_UART\_REG\_UPDATE] Configures whether or not to synchronize registers.\\
0: Not synchronize\\
1: Synchronize\\(R/W/SC)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_UART\_ID\_REG}{0x009C}\label{regdesc:LPUARTIDREG}
\regfield{LP\_UART\_ID}{32}{0}{{0x000500}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPUARTID}\item [LP\_UART\_ID] Configures the LP UART ID. (R/W)
\end{reglist}\end{regdesc}
\end{register}


