\begin{register}{H}{LEDC\_CH\regindex{n}\_CONF0\_REG (\regindex{n}: 0-5)}{0x0000+20*\regindex{n}}\label{regdesc:LEDCCHNCONF0REG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{LEDC\_OVF\_CNT\_RESET\_CH\regindex{n}}{1}{16}{{0}}%
\regfield{LEDC\_OVF\_CNT\_EN\_CH\regindex{n}}{1}{15}{{0}}%
\regfield{LEDC\_OVF\_NUM\_CH\regindex{n}}{10}{5}{{0}}%
\regfield{LEDC\_PARA\_UP\_CH\regindex{n}}{1}{4}{{0}}%
\regfield{LEDC\_IDLE\_LV\_CH\regindex{n}}{1}{3}{{0}}%
\regfield{LEDC\_SIG\_OUT\_EN\_CH\regindex{n}}{1}{2}{{0}}%
\regfield{LEDC\_TIMER\_SEL\_CH\regindex{n}}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LEDCTIMERSELCHN}\item [LEDC\_TIMER\_SEL\_CH\regindex{n}] This field is used to select one of the timers for channel \regindex{n}.

0: select Timer0; 1: select Timer1; 2: select Timer2; 3: select Timer3 (R/W)
\label{fielddesc:LEDCSIGOUTENCHN}\item [LEDC\_SIG\_OUT\_EN\_CH\regindex{n}] Set this bit to enable signal output on channel \regindex{n}. (R/W)
\label{fielddesc:LEDCIDLELVCHN}\item [LEDC\_IDLE\_LV\_CH\regindex{n}] This bit is used to control the output value when channel \regindex{n} is inactive (when LEDC\_SIG\_OUT\_EN\_CH\regindex{n} is 0). (R/W)
\label{fielddesc:LEDCPARAUPCHN}\item [LEDC\_PARA\_UP\_CH\regindex{n}] This bit is used to update the listed fields below for channel \regindex{n}, and will be automatically cleared by hardware. (WT)
\begin{itemize}
\item LEDC\_HPOINT\_CH\regindex{n}
\item LEDC\_DUTY\_START\_CH\regindex{n}
\item LEDC\_SIG\_OUT\_EN\_CH\regindex{n}
\item LEDC\_TIMER\_SEL\_CH\regindex{n}
\item LEDC\_DUTY\_NUM\_CH\regindex{n}
\item LEDC\_DUTY\_CYCLE\_CH\regindex{n}
\item LEDC\_DUTY\_SCALE\_CH\regindex{n}
\item LEDC\_DUTY\_INC\_CH\regindex{n}
\item LEDC\_OVF\_CNT\_EN\_CH\regindex{n}
\end{itemize}

\label{fielddesc:LEDCOVFNUMCHN}\item [LEDC\_OVF\_NUM\_CH\regindex{n}] This field is used to configure the maximum times of overflow minus 1.

The LEDC\_OVF\_CNT\_CH\regindex{n}\_INT interrupt will be triggered when channel \regindex{n} overflows for (LEDC\_OVF\_NUM\_CH\regindex{n} + 1) times. (R/W)
\label{fielddesc:LEDCOVFCNTENCHN}\item [LEDC\_OVF\_CNT\_EN\_CH\regindex{n}] This bit is used to count the number of times when the timer selected by channel \regindex{n} overflows. (R/W)
\label{fielddesc:LEDCOVFCNTRESETCHN}\item [LEDC\_OVF\_CNT\_RESET\_CH\regindex{n}] Set this bit to reset the timer-overflow counter of channel \regindex{n}. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LEDC\_CH\regindex{n}\_CONF1\_REG (\regindex{n}: 0-5)}{0x000C+20*\regindex{n}}\label{regdesc:LEDCCHNCONF1REG}
\regfield{LEDC\_DUTY\_START\_CH\regindex{n}}{1}{31}{{0}}%
\regfield{LEDC\_DUTY\_INC\_CH\regindex{n}}{1}{30}{{1}}%
\regfield{LEDC\_DUTY\_NUM\_CH\regindex{n}}{10}{20}{{0x0}}%
\regfield{LEDC\_DUTY\_CYCLE\_CH\regindex{n}}{10}{10}{{0x0}}%
\regfield{LEDC\_DUTY\_SCALE\_CH\regindex{n}}{10}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LEDCDUTYSCALECHN}\item [LEDC\_DUTY\_SCALE\_CH\regindex{n}] This field configures the step size of the duty cycle change during fading. (R/W)
\label{fielddesc:LEDCDUTYCYCLECHN}\item [LEDC\_DUTY\_CYCLE\_CH\regindex{n}] The duty will change every LEDC\_DUTY\_CYCLE\_CH\regindex{n} cycle on channel \regindex{n}. (R/W)
\label{fielddesc:LEDCDUTYNUMCHN}\item [LEDC\_DUTY\_NUM\_CH\regindex{n}] This field controls the number of times the duty cycle will be changed. (R/W)
\label{fielddesc:LEDCDUTYINCCHN}\item [LEDC\_DUTY\_INC\_CH\regindex{n}] This bit determines whether the duty cycle of the output signal on channel \regindex{n} increases or decreases. 1: Increase; 0: Decrease. (R/W)
\label{fielddesc:LEDCDUTYSTARTCHN}\item [LEDC\_DUTY\_START\_CH\regindex{n}] If this bit is set to 1, other configured fields in LEDC\_CH\regindex{n}\_CONF1\_REG will take effect upon the next timer overflow. (R/W/SC)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LEDC\_CONF\_REG}{0x00D0}\label{regdesc:LEDCCONFREG}
\regfield{LEDC\_CLK\_EN}{1}{31}{{0}}%
\regfield{(reserved)}{29}{2}{00000000000000000000000000000}%
\regfield{LEDC\_APB\_CLK\_SEL}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LEDCAPBCLKSEL}\item [LEDC\_APB\_CLK\_SEL] This field is used to select the common clock source for all the 4 timers.

1: APB\_CLK; 2: RC\_FAST\_CLK; 3: XTAL\_CLK. (R/W)
\label{fielddesc:LEDCCLKEN}\item [LEDC\_CLK\_EN] This bit is used to control the clock.

1: Force clock on for register. 0: Support clock only when application writes registers. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LEDC\_CH\regindex{n}\_HPOINT\_REG (\regindex{n}: 0-5)}{0x0004+20*\regindex{n}}\label{regdesc:LEDCCHNHPOINTREG}
\regfield{(reserved)}{18}{14}{000000000000000000}%
\regfield{LEDC\_HPOINT\_CH\regindex{n}}{14}{0}{{0x00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LEDCHPOINTCHN}\item [LEDC\_HPOINT\_CH\regindex{n}] The output value changes to high when the selected timer for this channel has reached the value specified by this field. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LEDC\_CH\regindex{n}\_DUTY\_REG (\regindex{n}: 0-5)}{0x0008+20*\regindex{n}}\label{regdesc:LEDCCHNDUTYREG}
\regfield{(reserved)}{13}{19}{0000000000000}%
\regfield{LEDC\_DUTY\_CH\regindex{n}}{19}{0}{{0x000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LEDCDUTYCHN}\item [LEDC\_DUTY\_CH\regindex{n}] This field is used to change the output duty by controlling the Lpoint. The output value turns to low when the selected timer for this channel has reached the Lpoint. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LEDC\_CH\regindex{n}\_DUTY\_R\_REG (\regindex{n}: 0-5)}{0x0010+20*\regindex{n}}\label{regdesc:LEDCCHNDUTYRREG}
\regfield{(reserved)}{13}{19}{0000000000000}%
\regfield{LEDC\_DUTY\_R\_CH\regindex{n}}{19}{0}{{0x000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LEDCDUTYRCHN}\item [LEDC\_DUTY\_R\_CH\regindex{n}] This field stores the current duty cycle of the output signal on channel \regindex{n}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LEDC\_TIMER\regindex{x}\_CONF\_REG (\regindex{x}: 0-3)}{0x00A0+8*\regindex{x}}\label{regdesc:LEDCTIMERXCONFREG}
\regfield{(reserved)}{6}{26}{000000}%
\regfield{LEDC\_TIMER\regindex{x}\_PARA\_UP}{1}{25}{{0}}%
\regfield{(reserved)}{1}{24}{0}%
\regfield{LEDC\_TIMER\regindex{x}\_RST}{1}{23}{{1}}%
\regfield{LEDC\_TIMER\regindex{x}\_PAUSE}{1}{22}{{0}}%
\regfield{LEDC\_CLK\_DIV\_TIMER\regindex{x}}{18}{4}{{0x000}}%
\regfield{LEDC\_TIMER\regindex{x}\_DUTY\_RES}{4}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LEDCTIMERXDUTYRES}\item [LEDC\_TIMER\regindex{x}\_DUTY\_RES] This field is used to control the range of the counter in timer \regindex{x}. (R/W)
\label{fielddesc:LEDCCLKDIVTIMERX}\item [LEDC\_CLK\_DIV\_TIMER\regindex{x}] This field is used to configure the divisor for the divider in timer \regindex{x}. The least significant eight bits represent the fractional part. (R/W)
\label{fielddesc:LEDCTIMERXPAUSE}\item [LEDC\_TIMER\regindex{x}\_PAUSE] This bit is used to suspend the counter in timer \regindex{x}. (R/W)
\label{fielddesc:LEDCTIMERXRST}\item [LEDC\_TIMER\regindex{x}\_RST] This bit is used to reset timer \regindex{x}. The counter will show 0 after reset. (R/W)
\label{fielddesc:LEDCTIMERXPARAUP}\item [LEDC\_TIMER\regindex{x}\_PARA\_UP] Set this bit to update LEDC\_CLK\_DIV\_TIMER\regindex{x} and LEDC\_TIMER\regindex{x}\_DUTY\_RES. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LEDC\_TIMER\regindex{x}\_VALUE\_REG (\regindex{x}: 0-3)}{0x00A4+8*\regindex{x}}\label{regdesc:LEDCTIMERXVALUEREG}
\regfield{(reserved)}{18}{14}{000000000000000000}%
\regfield{LEDC\_TIMER\regindex{x}\_CNT}{14}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LEDCTIMERXCNT}\item [LEDC\_TIMER\regindex{x}\_CNT] This field stores the current counter value of timer \regindex{x}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LEDC\_INT\_RAW\_REG}{0x00C0}\label{regdesc:LEDCINTRAWREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{LEDC\_OVF\_CNT\_CH5\_INT\_RAW}{1}{15}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH4\_INT\_RAW}{1}{14}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH3\_INT\_RAW}{1}{13}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH2\_INT\_RAW}{1}{12}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH1\_INT\_RAW}{1}{11}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH0\_INT\_RAW}{1}{10}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH5\_INT\_RAW}{1}{9}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH4\_INT\_RAW}{1}{8}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH3\_INT\_RAW}{1}{7}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH2\_INT\_RAW}{1}{6}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH1\_INT\_RAW}{1}{5}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH0\_INT\_RAW}{1}{4}{{0}}%
\regfield{LEDC\_TIMER3\_OVF\_INT\_RAW}{1}{3}{{0}}%
\regfield{LEDC\_TIMER2\_OVF\_INT\_RAW}{1}{2}{{0}}%
\regfield{LEDC\_TIMER1\_OVF\_INT\_RAW}{1}{1}{{0}}%
\regfield{LEDC\_TIMER0\_OVF\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LEDCTIMERXOVFINTRAW}\item [LEDC\_TIMER\regindex{x}\_OVF\_INT\_RAW] Triggered when the timer\regindex{x} has reached its maximum counter value. (R/WTC/SS)
\label{fielddesc:LEDCDUTYCHNGENDCHNINTRAW}\item [LEDC\_DUTY\_CHNG\_END\_CH\regindex{n}\_INT\_RAW] Interrupt raw bit for channel \regindex{n}. Triggered when the gradual change of duty has finished. (R/WTC/SS)
\label{fielddesc:LEDCOVFCNTCHNINTRAW}\item [LEDC\_OVF\_CNT\_CH\regindex{n}\_INT\_RAW] Interrupt raw bit for channel \regindex{n}. Triggered when the ovf\_cnt has reached the value specified by LEDC\_OVF\_NUM\_CH\regindex{n}. (R/WTC/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LEDC\_INT\_ST\_REG}{0x00C4}\label{regdesc:LEDCINTSTREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{LEDC\_OVF\_CNT\_CH5\_INT\_ST}{1}{15}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH4\_INT\_ST}{1}{14}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH3\_INT\_ST}{1}{13}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH2\_INT\_ST}{1}{12}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH1\_INT\_ST}{1}{11}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH0\_INT\_ST}{1}{10}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH5\_INT\_ST}{1}{9}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH4\_INT\_ST}{1}{8}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH3\_INT\_ST}{1}{7}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH2\_INT\_ST}{1}{6}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH1\_INT\_ST}{1}{5}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH0\_INT\_ST}{1}{4}{{0}}%
\regfield{LEDC\_TIMER3\_OVF\_INT\_ST}{1}{3}{{0}}%
\regfield{LEDC\_TIMER2\_OVF\_INT\_ST}{1}{2}{{0}}%
\regfield{LEDC\_TIMER1\_OVF\_INT\_ST}{1}{1}{{0}}%
\regfield{LEDC\_TIMER0\_OVF\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LEDCTIMERXOVFINTST}\item [LEDC\_TIMER\regindex{x}\_OVF\_INT\_ST] This is the masked interrupt status bit for the LEDC\_TIMER\regindex{x}\_OVF\_INT interrupt when LEDC\_TIMER\regindex{x}\_OVF\_INT\_ENA is set to 1. (RO)
\label{fielddesc:LEDCDUTYCHNGENDCHNINTST}\item [LEDC\_DUTY\_CHNG\_END\_CH\regindex{n}\_INT\_ST] This is the masked interrupt status bit for the LEDC\_DUTY\_CHNG\_END\_CH\regindex{n}\_INT interrupt when LEDC\_DUTY\_CHNG\_END\_CH\regindex{n}\_INT\_ENA is set to 1. (RO)
\label{fielddesc:LEDCOVFCNTCHNINTST}\item [LEDC\_OVF\_CNT\_CH\regindex{n}\_INT\_ST] This is the masked interrupt status bit for the LEDC\_OVF\_CNT\_CH\regindex{n}\_INT interrupt when LEDC\_OVF\_CNT\_CH\regindex{n}\_INT\_ENA is set to 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LEDC\_INT\_ENA\_REG}{0x00C8}\label{regdesc:LEDCINTENAREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{LEDC\_OVF\_CNT\_CH5\_INT\_ENA}{1}{15}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH4\_INT\_ENA}{1}{14}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH3\_INT\_ENA}{1}{13}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH2\_INT\_ENA}{1}{12}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH1\_INT\_ENA}{1}{11}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH0\_INT\_ENA}{1}{10}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH5\_INT\_ENA}{1}{9}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH4\_INT\_ENA}{1}{8}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH3\_INT\_ENA}{1}{7}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH2\_INT\_ENA}{1}{6}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH1\_INT\_ENA}{1}{5}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH0\_INT\_ENA}{1}{4}{{0}}%
\regfield{LEDC\_TIMER3\_OVF\_INT\_ENA}{1}{3}{{0}}%
\regfield{LEDC\_TIMER2\_OVF\_INT\_ENA}{1}{2}{{0}}%
\regfield{LEDC\_TIMER1\_OVF\_INT\_ENA}{1}{1}{{0}}%
\regfield{LEDC\_TIMER0\_OVF\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LEDCTIMERXOVFINTENA}\item [LEDC\_TIMER\regindex{x}\_OVF\_INT\_ENA] The interrupt enable bit for the LEDC\_TIMER\regindex{x}\_OVF\_INT interrupt. (R/W)
\label{fielddesc:LEDCDUTYCHNGENDCHNINTENA}\item [LEDC\_DUTY\_CHNG\_END\_CH\regindex{n}\_INT\_ENA] The interrupt enable bit for the LEDC\_DUTY\_CHNG\_END\_CH\regindex{n}\_INT interrupt. (R/W)
\label{fielddesc:LEDCOVFCNTCHNINTENA}\item [LEDC\_OVF\_CNT\_CH\regindex{n}\_INT\_ENA] The interrupt enable bit for the LEDC\_OVF\_CNT\_CH\regindex{n}\_INT interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LEDC\_INT\_CLR\_REG}{0x00CC}\label{regdesc:LEDCINTCLRREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{LEDC\_OVF\_CNT\_CH5\_INT\_CLR}{1}{15}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH4\_INT\_CLR}{1}{14}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH3\_INT\_CLR}{1}{13}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH2\_INT\_CLR}{1}{12}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH1\_INT\_CLR}{1}{11}{{0}}%
\regfield{LEDC\_OVF\_CNT\_CH0\_INT\_CLR}{1}{10}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH5\_INT\_CLR}{1}{9}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH4\_INT\_CLR}{1}{8}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH3\_INT\_CLR}{1}{7}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH2\_INT\_CLR}{1}{6}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH1\_INT\_CLR}{1}{5}{{0}}%
\regfield{LEDC\_DUTY\_CHNG\_END\_CH0\_INT\_CLR}{1}{4}{{0}}%
\regfield{LEDC\_TIMER3\_OVF\_INT\_CLR}{1}{3}{{0}}%
\regfield{LEDC\_TIMER2\_OVF\_INT\_CLR}{1}{2}{{0}}%
\regfield{LEDC\_TIMER1\_OVF\_INT\_CLR}{1}{1}{{0}}%
\regfield{LEDC\_TIMER0\_OVF\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LEDCTIMERXOVFINTCLR}\item [LEDC\_TIMER\regindex{x}\_OVF\_INT\_CLR] Set this bit to clear the LEDC\_TIMER\regindex{x}\_OVF\_INT interrupt. (WT)
\label{fielddesc:LEDCDUTYCHNGENDCHNINTCLR}\item [LEDC\_DUTY\_CHNG\_END\_CH\regindex{n}\_INT\_CLR] Set this bit to clear the LEDC\_DUTY\_CHNG\_END\_CH\regindex{n}\_INT interrupt. (WT)
\label{fielddesc:LEDCOVFCNTCHNINTCLR}\item [LEDC\_OVF\_CNT\_CH\regindex{n}\_INT\_CLR] Set this bit to clear the LEDC\_OVF\_CNT\_CH\regindex{n}\_INT interrupt. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LEDC\_DATE\_REG}{0x00FC}\label{regdesc:LEDCDATEREG}
\regfield{LEDC\_LEDC\_DATE}{32}{0}{{0x19061700}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LEDCLEDCDATE}\item [LEDC\_LEDC\_DATE] This is the version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}
