\begin{register}{H}{tselect}{0x7A0}\label{regdesc:TSELECT}
\regfield{(reserved)}{29}{2}{{0x00000000}}%
\regfield{tselect}{2}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:TSELECT}\item [tselect] Configures the index (0-3) of the selected trigger unit. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{tdata1}{0x7A1}\label{regdesc:TDATA1}
\regfield{type}{4}{28}{{0x2}}%
\regfield{dmode}{1}{27}{{0}}%
\regfield{data}{27}{0}{{0x3e00000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:TDATA1TYPE}\item [type] Represents the trigger type. This field is reserved since only match type (0x2) triggers are supported. (RO)
\label{fielddesc:TDATA1DMODE}\item [dmode] This is set to 1 if a trigger is being used by the debugger.\\
0: Both Debug and M mode can write the tdata1 and tdata2 registers at the selected tselect.\\
1: Only Debug Mode can write the tdata1 and tdata2 registers at the selected tselect. Writes from other modes are ignored.\\
Note: Only writable from debug mode.\\
(R/W)
\label{fielddesc:TDATA1DATA}\item [data] Configures the abstract tdata1 content. This will always be interpreted as fields of \hyperref[regdesc:MCONTROL]{mcontrol} since only match type (0x2) triggers are supported. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{tdata2}{0x7A2}\label{regdesc:TDATA2}
\regfield{tdata2}{32}{0}{{0x00000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:TDATA2}\item [tdata2] Configures the abstract tdata2 content. This will always be interpreted as \hyperref[regdesc:MADDRESS]{maddress} since only match type (0x2) triggers are supported. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{tdata3}{0x7A3}\label{regdesc:TDATA3}
\regfield{mvalue}{6}{26}{{0x0}}%
\regfield{mselect}{1}{25}{{0x0}}%
\regfield{Reserved}{25}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MVALUE}\item [mvalue] Data used together with mselect. (R/W)
\label{fielddesc:MSELECT}\item [mselect] 
0: Ignore mvalue. \\
1: This trigger will only match if the low bits of mcontext equal mvalue. \\
(R/W)
\label{fielddesc:tdata3_rsvd}\item [Reserved] Read as 0. (RO)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{tinfo}{0x7A4}\label{regdesc:TINFO}
\regfield{Reserved}{16}{16}{{0x0}}%
\regfield{info}{16}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:tinfo_rsvd}\item [Reserved] Read as 0. (RO)
\label{fielddesc:INFO}\item [info] One bit for each possible type enumerated in tdata1. Bit N corresponds to type N. If the bit is set, then that type is supported by the currently selected trigger. If the currently selected trigger does not exist, this field contains 1. If the type is not writable, this register may be unimplemented, in which case reading it causes an illegal instruction exception. In this case, the debugger can read the only supported type from tdata1. (RO)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{tcontrol}{0x7A5}\label{regdesc:TCONTROL}
\regfield{(reserved)}{24}{8}{{0x000000}}%
\regfield{mpte}{1}{7}{{0}}%
\regfield{(reserved)}{6}{1}{{0x00}}%
\regfield{mte}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:TCONTROLMPTE}\item [mpte] Configures whether to enable the machine mode previous trigger.\\
When CPU is taking a machine mode trap, the value of \hyperref[fielddesc:TCONTROLMTE]{mte} is automatically pushed into this.\\
When CPU is executing MRET, its value is popped back into \hyperref[fielddesc:TCONTROLMTE]{mte}, so this becomes 0.\\
(R/W)
\label{fielddesc:TCONTROLMTE}\item [mte] Configures whether to enable the machine mode trigger.\\
When CPU is taking a machine mode trap, its value is automatically pushed into \hyperref[fielddesc:TCONTROLMPTE]{mpte}, so this becomes 0 and triggers with \hyperref[fielddesc:MCONTROLACTION]{action}=0 are disabled globally.\\
When CPU is executing MRET, the value of \hyperref[fielddesc:TCONTROLMPTE]{mpte} is automatically popped back into this.\\
(R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{MCONTEXT}{0x7A8}\label{regdesc:MCONTEXT}
\regfield{Reserved}{26}{6}{{0x0}}%
\regfield{context}{6}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:monctext_rsvd}\item [Reserved] Read as 0. (RO)
\label{fielddesc:CONTEXT}\item [context] Writable in M mode and Debug Mode. Machine mode software can write a context number to this register, which can be used to set triggers that only fire in that specific context. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{mcontrol}{0x7A1}\label{regdesc:MCONTROL}
\regfield{(reserved)}{4}{28}{{0x2}}%
\regfield{dmode}{1}{27}{{0}}%
\regfield{maskmax}{6}{21}{{0x8}}%
\regfield{hit}{1}{20}{{0}}%
\regfield{(reserved)}{1}{19}{{0}}%
\regfield{(timing)}{1}{18}{{0}}%
\regfield{(sizelo)}{2}{16}{{0}}%
\regfield{action}{4}{12}{{0}}%
\regfield{(reserved)}{1}{11}{{0}}%
\regfield{match}{4}{7}{{0}}%
\regfield{m}{1}{6}{{0}}%
\regfield{(reserved)}{2}{4}{{0}}%
\regfield{u}{1}{3}{{0}}%
\regfield{execute}{1}{2}{{0}}%
\regfield{store}{1}{1}{{0}}%
\regfield{load}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MCONTROLDMODE}\item [dmode] Same as \hyperref[fielddesc:TDATA1DMODE]{dmode} in \hyperref[regdesc:TDATA1]{tdata1}. (RW*)
\label{fielddesc:MCONTROLMASKMAX}\item [maskmax] 
 Represents the largest natural power-of-two (NAPOT) range supported when \hyperref[fielddesc:MCONTROLMATCH]{match} is 1. It is always read as 0x8, which means only the lowest 8 bits can be masked. (RO)
\label{fielddesc:MCONTROLHIT}\item [hit] This is found to be 1 if the selected trigger had fired previously. This bit needs to be cleared manually. (R/W) 
\label{fielddesc:MCONTROLTIMING}\item [timing] Set this field to enable load/store trigger action timing.\\
0: Action for this trigger will be taken just before the instruction that triggered it is executed, but after all preceding instructions are committed.\\
1: Action for this trigger will be taken after the instruction that triggered it is executed. It should be taken before the next instruction is executed.\\
(R/W)
\label{fielddesc:MCONTROLSIZELO}\item [sizelo] This field contains the lowest two bits of access address.\\ 
0x0: The trigger will attempt to match against an access of any size\\
0x1: The trigger will attempt to match against 8-bit memory accesses\\
0x2: The trigger will attempt to match against 16-bit memory accesses\\
0x3: The trigger will attempt to match against 32-bit memory accesses\\
(R/W)
\label{fielddesc:MCONTROLACTION}\item [action] Configures the selected trigger to perform one of the available actions when firing. Valid options are:\\
0x0: cause breakpoint exception.\\
0x1: enter debug mode (only valid when dmode = 1)\\
0x2: Enable trace on trigger[0] hit\\
0x3: Enable trace on trigger[1] hit\\
0x4: Enable trace on trigger[2] hit\\
Note: Writing an invalid value will set this to the default value 0x0.\\
(R/W)
\label{fielddesc:MCONTROLMATCH}\item [match] Configures the selected trigger to perform one of the available matching operations on a data/instruction address. Valid options are:\\
0x0: exact byte match, i.e. address corresponding to one of the bytes in an access must match the value of \hyperref[regdesc:MADDRESS]{maddress} exactly.\\
0x1: NAPOT match, i.e. at least one of the bytes of an access must lie in the NAPOT region specified in \hyperref[regdesc:MADDRESS]{maddress}.\\
Note: Writing a larger value will clip it to the largest possible value 0x1.\\
(R/W)
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{mcontrol}{0x7A1}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\label{fielddesc:MCONTROLM}\item [m] Set this field to enable the selected trigger to operate in machine mode. (R/W)
\label{fielddesc:MCONTROLU}\item [u] Set this field to enable the selected trigger to operate in user mode. (R/W)
\label{fielddesc:MCONTROLEXECUTE}\item [execute] Set this field to enable the selected trigger to fire right before an instruction with the matching virtual address executed by the CPU. (R/W)
\label{fielddesc:MCONTROLSTORE}\item [store] Set this field to enable the selected trigger to fire right before a store operation with the matching data address executed by the CPU. (R/W)
\label{fielddesc:MCONTROLLOAD}\item [load] Set this field to enable the selected trigger to fire right before a load operation with the matching data address executed by the CPU. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{maddress}{0x7A2}\label{regdesc:MADDRESS}
\regfield{maddress}{32}{0}{{0x00000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MADDRESS}\item [maddress] Configures the address used by the selected trigger when performing a match operation. This is decoded as NAPOT when \hyperref[fielddesc:MCONTROLMATCH]{match}=1 in \hyperref[regdesc:MCONTROL]{mcontrol}. (R/W)
\end{reglist}\end{regdesc}
\end{register}

