\begin{register}{H}{pmpcfg0}{0x3A0}
\label{regdesc:pmpcfg0}%
\regfield{pmp3cfg}{8}{24}{{0}}%
\regfield{pmp2cfg}{8}{16}{{0}}%
\regfield{pmp1cfg}{8}{8}{{0}}%
\regfield{pmp0cfg}{8}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}
\begin{reglist}
\label{fielddesc:pmp3cfg}\item [pmp3cfg] Configuration register for PMP entry 3. (R/W)
\label{fielddesc:pmp2cfg}\item [pmp2cfg] Configuration register for PMP entry 2. (R/W)
\label{fielddesc:pmp1cfg}\item [pmp1cfg] Configuration register for PMP entry 1. (R/W)
\label{fielddesc:pmp0cfg}\item [pmp0cfg] Configuration register for PMP entry 0. (R/W)
\end{reglist}
\end{regdesc}
\end{register}

\begin{register}{H}{pmpcfg1}{0x3A1}
\label{regdesc:pmpcfg1}%
\regfield{pmp7cfg}{8}{24}{{0}}%
\regfield{pmp6cfg}{8}{16}{{0}}%
\regfield{pmp5cfg}{8}{8}{{0}}%
\regfield{pmp4cfg}{8}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}
\begin{reglist}
\label{fielddesc:pmp7cfg}\item [pmp7cfg] Configuration register for PMP entry 7. (R/W)
\label{fielddesc:pmp6cfg}\item [pmp6cfg] Configuration register for PMP entry 6. (R/W)
\label{fielddesc:pmp5cfg}\item [pmp5cfg] Configuration register for PMP entry 5. (R/W)
\label{fielddesc:pmp4cfg}\item [pmp4cfg] Configuration register for PMP entry 4. (R/W)
\end{reglist}
\end{regdesc}
\end{register}

\begin{register}{H}{pmpcfg2}{0x3A1}
\label{regdesc:pmpcfg2}%
\regfield{pmp11cfg}{8}{24}{{0}}%
\regfield{pmp10cfg}{8}{16}{{0}}%
\regfield{pmp9cfg}{8}{8}{{0}}%
\regfield{pmp8cfg}{8}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}
\begin{reglist}
\label{fielddesc:pmp11cfg}\item [pmp11cfg] Configuration register for PMP entry 11. (R/W)
\label{fielddesc:pmp10cfg}\item [pmp10cfg] Configuration register for PMP entry 10. (R/W)
\label{fielddesc:pmp9cfg}\item [pmp9cfg] Configuration register for PMP entry 9. (R/W)
\label{fielddesc:pmp8cfg}\item [pmp8cfg] Configuration register for PMP entry 8. (R/W)
\end{reglist}
\end{regdesc}
\end{register}
\begin{register}{H}{pmpcfg3}{0x3A2}
\label{regdesc:pmpcfg3}%
\regfield{pmp15cfg}{8}{24}{{0}}%
\regfield{pmp14cfg}{8}{16}{{0}}%
\regfield{pmp13cfg}{8}{8}{{0}}%
\regfield{pmp12cfg}{8}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}
\begin{reglist}
\label{fielddesc:pmp15cfg}\item [pmp15cfg] Configuration register for PMP entry 15. (R/W)
\label{fielddesc:pmp14cfg}\item [pmp14cfg] Configuration register for PMP entry 14. (R/W)
\label{fielddesc:pmp13cfg}\item [pmp13cfg] Configuration register for PMP entry 13. (R/W)
\label{fielddesc:pmp12cfg}\item [pmp12cfg] Configuration register for PMP entry 12. (R/W)
\end{reglist}
\end{regdesc}
\end{register}

The PMP configuration register format for any PMP entry is shown as follows.


\begin{register}{H}{pmpXcfg}{}
\label{regdesc:pmpXcfg}%
\regfield{L}{1}{7}{{0}}%
\regfield{Reserved}{1}{6}{{0}}%
\regfield{XL}{1}{5}{{0}}%
\regfield{A}{2}{3}{{0}}%
\regfield{X}{1}{2}{{0}}%
\regfield{W}{1}{1}{{0}}%
\regfield{R}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}
\begin{reglist}
\label{fielddesc:pmpXcfgL}\item [L] Configures lock bit. Once set, it can only be cleared through a core reset. (R/W)
\label{fielddesc:pmpXcfgXL}\item [XL] Configures custom-lock bit. Once set, it can only be cleared through a core reset.
0: PMP CSR accesses work normally \\
1: Respective pmpaddr and pmpcfg entry is locked and cannot be modified \\
(R/W)
\label{fielddesc:pmpXcfgA}\item [A] Configures address matching mode.\\
0: OFF \\
1: TOR (Top of range) \\
2: Not Supported \\
3: NAPOT (Natullary aligned power-of-two region >= 128 Bytes)\\
(R/W)
\label{fielddesc:pmpXcfgX}\item [X] Configures execute permission. When set, execution from the address range is allowed. (R/W)
\label{fielddesc:pmpXcfgW}\item [W] Configures write permission. When set, memory writes to the address range are allowed. (R/W)
\label{fielddesc:pmpXcfgR}\item [R] Configures execute permission. When set, memory reads from the address range are allowed. (R/W)
\end{reglist}
\end{regdesc}
\end{register}

\begin{register}{H}{pmpaddr\regindex{n} (\regindex{n}: 0-15)}{0x3B0+0x1*\regindex{n}}\label{regdesc:pmpaddrN}
\regfield{address}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:ADDR}\item [address] Configures the address for pmpaddr\regindex{n}. (R/W)
\end{reglist}\end{regdesc}
\end{register}

