\begin{register}{H}{tselect}{0x7A0}\label{regdesc:LPTSELECT}
\regfield{tselect}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPTSELECT}\item [tselect] Configures the index of the selected trigger unit. (R/W)
\end{reglist}\end{regdesc}
\end{register}

%%%%%%%%%
\begin{register}{H}{tdata1}{0x7A1}\label{regdesc:LPTDATA1}
\regfield{type}{4}{28}{0010}%
\regfield{dmode}{1}{27}{1}%
\regfield{data}{27}{0}{0x1040}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPTDATA1TYPE}\item [type] Represents the trigger type. This field is reserved since only match type (0x2) triggers are supported. (RO)
\label{fielddesc:LPTDATA1DMODE}\item [dmode] This is set to 1 if a trigger is being used by the debugger. This field is reserved since it is only supported in debug mode. (RO)
\label{fielddesc:LPTDATA1DATA}\item [data] Configures the abstract tdata1 content. This will always be interpreted as fields of \hyperref[regdesc:LPMCONTROL]{mcontrol} since only match type (0x2) triggers are supported. (R/W)
\end{reglist}\end{regdesc}
\end{register}


%%%%%%%%%
\begin{register}{H}{tdata2}{0x7A2}\label{regdesc:LPTDATA2}
\regfield{tdata2}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPTDATA2}\item [tdata2] Configures the abstract tdata2 content. This will always be interpreted as \hyperref[regdesc:LPMADDRESS]{maddress} since only match type (0x2) triggers are supported. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{mcontrol}{0x7A1}\label{regdesc:LPMCONTROL}
\regfield{(reserved)}{4}{28}{{0x2}}%
\regfield{dmode}{1}{27}{{0}}%
\regfield{maskmax}{6}{21}{{0x0}}%
\regfield{hit}{1}{20}{{0}}%
\regfield{select}{1}{19}{{0}}%
\regfield{timing}{1}{18}{{0}}%
\regfield{sizelo}{2}{16}{{0}}%
\regfield{action}{4}{12}{{0001}}%
\regfield{chain}{1}{11}{{0}}%
\regfield{match}{4}{7}{{0}}%
\regfield{m}{1}{6}{{0}}%
\regfield{(reserved)}{1}{5}{{0}}%
\regfield{s}{1}{4}{{0}}%
\regfield{u}{1}{3}{{0}}%
\regfield{execute}{1}{2}{{0}}%
\regfield{store}{1}{1}{{0}}%
\regfield{load}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPMCONTROLDMODE}\item [dmode] Same as \hyperref[fielddesc:LPTDATA1DMODE]{dmode} in \hyperref[regdesc:LPTDATA1]{tdata1}. (RO)
\label{fielddesc:LPMCONTROLMASKMAX}\item [maskmax] Represents the maximum NAPOT range. \\
0: A byte. Only exact match is supported.\\
Other values: Not supported.\\
(RO)
\label{fielddesc:LPMCONTROLHIT}\item [hit] Not implemented in hardware. This field remains 0. (RO)
\label{fielddesc:LPMCONTROLSELECT}\item [select] Configures to select between an address match or a data match.\\
0: Perform a match on the virtual address\\
1: Perform a match on the data value loaded or stored, or the instruction executed\\
Note: Only address match is implemented. This field remains 0.\\
(RO)
\label{fielddesc:LPMCONTROLTIMING}\item [timing] Configures when the trigger will take action.\\
0: Take action before the instruction is executed\\
1: Take action after the instruction is executed\\
Note: The field remains 0.\\
(RO)
\label{fielddesc:LPMCONTROLSIZELO}\item [sizelo] Only match of any size is supported. This field remains 0. (RO)
\label{fielddesc:LPMCONTROLACTION}\item [action] Configure action of the selected trigger after it is triggered.\\
0x0: Cause a breakpoint exception\\
0x1: Enter debug mode (Valid only when dmode = 1)\\
Note: Only entering debug mode is supported. This field remains 1.\\
(RO)
\label{fielddesc:LPMCONTROLCHAIN}\item [CHAIN] Not implemented in hardware. This field remains 0. (RO)
\label{fielddesc:LPMCONTROLMATCH}\item [match]
Configures the trigger to perform the matching operation of the lower data/instruction address. \\
0x0: Exact match. Namely, the address corresponding to a certain byte during the access must exactly match the value of \hyperref[regdesc:LPMADDRESS]{maddress}.\\
0x1: NAPOT match. Namely, at least one byte during the access is in the NAPOT region specified in \hyperref[regdesc:LPMADDRESS]{maddress}. \\
Note: Only exact byte match is supported. This field remains 0.\\
(R/W)
\label{fielddesc:LPMCONTROLM}\item [m] Set this field to make the selected trigger operate in machine mode. (RO)
\label{fielddesc:LPMCONTROLS}\item [s] Set this field to make the selected trigger operate in supervisor mode. Operation in supervisor mode is not supported. This field is always 0. (RO)
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{mcontrol}{0x7A1}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\label{fielddesc:LPMCONTROLU}\item [u] Set this field to make the selected trigger operate in user mode. Operation in user mode is not supported. This field is always 0. (RO)
\label{fielddesc:LPMCONTROLEXECUTE}\item [execute] Configures whether to enable the selected trigger to match the virtual address of instructions. \\
0: Not enable\\
1: Enable\\
(R/W)
\label{fielddesc:LPMCONTROLSTORE}\item [store]
Set this field to make the selected trigger match the virtual address of the memory write operation. Not supported by hardware. This field is always 0. (RO)
\label{fielddesc:LPMCONTROLLOAD}\item [load] Set this field to make the selected trigger match the virtual address of a memory read operation. Not supported by hardware. This field is always 0. (RO)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{maddress}{0x7A2}\label{regdesc:LPMADDRESS}
\regfield{maddress}{32}{0}{{0x00000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPMADDRESS}\item [maddress] Configures the address used by the selected trigger when performing match operation. (R/W)
\end{reglist}\end{regdesc}
\end{register}