\begin{register}{H}{I2S\_FIFO\_WR\_REG}{0x0000}\label{regdesc:I2SFIFOWRREG}
\regfield{I2S\_FIFO\_WR\_REG}{32}{0}{0000000000000}%
\begin{regdesc}\begin{reglist}
\item [I2S\_FIFO\_WR\_REG] Writes the data sent by I2S into FIFO. (WO)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{I2S\_FIFO\_RD\_REG}{0x0004}\label{regdesc:I2SFIFORDREG}
\regfield{I2S\_FIFO\_RD\_REG}{32}{0}{0000000000000}%
\begin{regdesc}\begin{reglist}
\item [I2S\_FIFO\_RD\_REG] Stores the data that I2S receives from FIFO. (RO)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{I2S\_CONF\_REG}{0x0008}\label{regdesc:I2SCONFREG}
\regfield{(reserved)}{13}{19}{0000000000000}%
\regfield{I2S\_SIG\_LOOPBACK}{1}{18}{0}%
\regfield{I2S\_RX\_MSB\_RIGHT}{1}{17}{0}%
\regfield{I2S\_TX\_MSB\_RIGHT}{1}{16}{0}%
\regfield{I2S\_RX\_MONO}{1}{15}{1}%
\regfield{I2S\_TX\_MONO}{1}{14}{1}%
\regfield{I2S\_RX\_SHORT\_SYNC}{1}{13}{1}%
\regfield{I2S\_TX\_SHORT\_SYNC}{1}{12}{1}%
\regfield{I2S\_RX\_MSB\_SHIFT}{1}{11}{0}%
\regfield{I2S\_TX\_MSB\_SHIFT}{1}{10}{0}%
\regfield{I2S\_RX\_RIGHT\_FIRST}{1}{9}{0}%
\regfield{I2S\_TX\_RIGHT\_FIRST}{1}{8}{0}%
\regfield{I2S\_RX\_SLAVE\_MOD}{1}{7}{0}%
\regfield{I2S\_TX\_SLAVE\_MOD}{1}{6}{0}%
\regfield{I2S\_RX\_START}{1}{5}{0}%
\regfield{I2S\_TX\_START}{1}{4}{0}%
\regfield{I2S\_RX\_FIFO\_RESET}{1}{3}{0}%
\regfield{I2S\_TX\_FIFO\_RESET}{1}{2}{0}%
\regfield{I2S\_RX\_RESET}{1}{1}{0}%
\regfield{I2S\_TX\_RESET}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_SIG\_LOOPBACK]Enable signal loopback mode, with transmitter module and receiver module sharing the same WS and BCK signals. (R/W)
\item [I2S\_RX\_MSB\_RIGHT]Set this to place right-channel data at the MSB in the receive FIFO. (R/W)
\item [I2S\_TX\_MSB\_RIGHT]\label{MSBRIGHT}Set this bit to place right-channel data at the MSB in the transmit FIFO. (R/W)
\item [I2S\_RX\_MONO]Set this bit to enable receiver's mono mode in PCM standard mode. (R/W)
\item [I2S\_TX\_MONO]Set this bit to enable transmitter's mono mode in PCM standard mode. (R/W)
\item [I2S\_RX\_SHORT\_SYNC]Set this bit to enable receiver in PCM standard mode. (R/W)
\item [I2S\_TX\_SHORT\_SYNC]Set this bit to enable transmitter in PCM standard mode. (R/W)
\item [I2S\_RX\_MSB\_SHIFT]Set this bit to enable receiver in Philips standard mode. (R/W)
\item [I2S\_TX\_MSB\_SHIFT]Set this bit to enable transmitter in Philips standard mode. (R/W)
\item [I2S\_RX\_RIGHT\_FIRST]Set this bit to receive right-channel data first. (R/W)
\item [I2S\_TX\_RIGHT\_FIRST]Set this bit to transmit right-channel data first. (R/W)
\item [I2S\_RX\_SLAVE\_MOD]Set this bit to enable slave receiver mode. (R/W)
\item [I2S\_TX\_SLAVE\_MOD]Set this bit to enable slave transmitter mode. (R/W)
\item [I2S\_RX\_START]Set this bit to start receiving data. (R/W)
\item [I2S\_TX\_START]Set this bit to start transmitting data. (R/W)
\item [I2S\_RX\_FIFO\_RESET]Set this bit to reset the receive FIFO. (R/W)
\item [I2S\_TX\_FIFO\_RESET]Set this bit to reset the transmit FIFO. (R/W)
\item [I2S\_RX\_RESET]Set this bit to reset the receiver. (R/W)
\item [I2S\_TX\_RESET]Set this bit to reset the transmitter. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_INT\_RAW\_REG}{0x000c}\label{regdesc:I2SINTRAWREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{I2S\_OUT\_TOTAL\_EOF\_INT\_RAW}{1}{16}{0}%
\regfield{I2S\_IN\_DSCR\_EMPTY\_INT\_RAW}{1}{15}{0}%
\regfield{I2S\_OUT\_DSCR\_ERR\_INT\_RAW}{1}{14}{0}%
\regfield{I2S\_IN\_DSCR\_ERR\_INT\_RAW}{1}{13}{0}%
\regfield{I2S\_OUT\_EOF\_INT\_RAW}{1}{12}{0}%
\regfield{I2S\_OUT\_DONE\_INT\_RAW}{1}{11}{0}%
\regfield{(reserved)}{1}{10}{0}%
\regfield{I2S\_IN\_SUC\_EOF\_INT\_RAW}{1}{9}{0}%
\regfield{I2S\_IN\_DONE\_INT\_RAW}{1}{8}{0}%
\regfield{I2S\_TX\_HUNG\_INT\_RAW}{1}{7}{0}%
\regfield{I2S\_RX\_HUNG\_INT\_RAW}{1}{6}{0}%
\regfield{I2S\_TX\_REMPTY\_INT\_RAW}{1}{5}{0}%
\regfield{I2S\_TX\_WFULL\_INT\_RAW}{1}{4}{0}%
\regfield{I2S\_RX\_REMPTY\_INT\_RAW}{1}{3}{0}%
\regfield{I2S\_RX\_WFULL\_INT\_RAW}{1}{2}{0}%
\regfield{I2S\_TX\_PUT\_DATA\_INT\_RAW}{1}{1}{0}%
\regfield{I2S\_RX\_TAKE\_DATA\_INT\_RAW}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_OUT\_TOTAL\_EOF\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:I2SOUTTOTALEOFINT]{I2S\_OUT\_TOTAL\_EOF\_INT} interrupt. (RO)
\item [I2S\_IN\_DSCR\_EMPTY\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:I2SINDSCREMPTYINT]{I2S\_IN\_DSCR\_EMPTY\_INT} interrupt. (RO)
\item [I2S\_OUT\_DSCR\_ERR\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:I2SOUTDSCRERRINT]{I2S\_OUT\_DSCR\_ERR\_INT} interrupt. (RO)
\item [I2S\_IN\_DSCR\_ERR\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:I2SINDSCRERRINT]{I2S\_IN\_DSCR\_ERR\_INT} interrupt. (RO)
\item [I2S\_OUT\_EOF\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:I2SOUTEOFINT]{I2S\_OUT\_EOF\_INT} interrupt. (RO)
\item [I2S\_OUT\_DONE\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:I2SOUTDONEINT]{I2S\_OUT\_DONE\_INT} interrupt. (RO)
\item [I2S\_IN\_SUC\_EOF\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:I2SINSUCEOFINT]{I2S\_IN\_SUC\_EOF\_INT} interrupt. (RO)
\item [I2S\_IN\_DONE\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:I2SINDONEINT]{I2S\_IN\_DONE\_INT} interrupt. (RO)
\item [I2S\_TX\_HUNG\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:I2STXHUNGINT]{I2S\_TX\_HUNG\_INT} interrupt. (RO)
\item [I2S\_RX\_HUNG\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:I2SRXHUNGINT]{I2S\_RX\_HUNG\_INT} interrupt. (RO)
\item [I2S\_TX\_REMPTY\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:I2STXREMPTYINT]{I2S\_TX\_REMPTY\_INT} interrupt. (RO)
\item [I2S\_TX\_WFULL\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:I2STXWFULLINT]{I2S\_TX\_WFULL\_INT} interrupt. (RO)
\item [I2S\_RX\_REMPTY\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:I2SRXREMPTYINT]{I2S\_RX\_REMPTY\_INT} interrupt. (RO)
\item [I2S\_RX\_WFULL\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:I2SRXWFULLINT]{I2S\_RX\_WFULL\_INT} interrupt. (RO)
\item [I2S\_TX\_PUT\_DATA\_INT\_RAW]The raw interrupt status bit for the I2S\_TX\_PUT\_DATA\_INT interrupt. (RO)
\item [I2S\_RX\_TAKE\_DATA\_INT\_RAW]The raw interrupt status bit for the I2S\_RX\_TAKE\_DATA\_INT interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_INT\_ST\_REG}{0x0010}\label{regdesc:I2SINTSTREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{I2S\_OUT\_TOTAL\_EOF\_INT\_ST}{1}{16}{0}%
\regfield{I2S\_IN\_DSCR\_EMPTY\_INT\_ST}{1}{15}{0}%
\regfield{I2S\_OUT\_DSCR\_ERR\_INT\_ST}{1}{14}{0}%
\regfield{I2S\_IN\_DSCR\_ERR\_INT\_ST}{1}{13}{0}%
\regfield{I2S\_OUT\_EOF\_INT\_ST}{1}{12}{0}%
\regfield{I2S\_OUT\_DONE\_INT\_ST}{1}{11}{0}%
\regfield{(reserved)}{1}{10}{0}%
\regfield{I2S\_IN\_SUC\_EOF\_INT\_ST}{1}{9}{0}%
\regfield{I2S\_TX\_DONE\_INT\_ST}{1}{8}{0}%
\regfield{I2S\_TX\_HUNG\_INT\_ST}{1}{7}{0}%
\regfield{I2S\_RX\_HUNG\_INT\_ST}{1}{6}{0}%
\regfield{I2S\_TX\_REMPTY\_INT\_ST}{1}{5}{0}%
\regfield{I2S\_TX\_WFULL\_INT\_ST}{1}{4}{0}%
\regfield{I2S\_RX\_REMPTY\_INT\_ST}{1}{3}{0}%
\regfield{I2S\_RX\_WFULL\_INT\_ST}{1}{2}{0}%
\regfield{I2S\_TX\_PUT\_DATA\_INT\_ST}{1}{1}{0}%
\regfield{I2S\_RX\_TAKE\_DATA\_INT\_ST}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_OUT\_TOTAL\_EOF\_INT\_ST]The masked interrupt status bit for the \hyperref[int:I2SOUTTOTALEOFINT]{I2S\_OUT\_TOTAL\_EOF\_INT} interrupt. (RO)
\item [I2S\_IN\_DSCR\_EMPTY\_INT\_ST]The masked interrupt status bit for the \hyperref[int:I2SINDSCREMPTYINT]{I2S\_IN\_DSCR\_EMPTY\_INT} interrupt. (RO)
\item [I2S\_OUT\_DSCR\_ERR\_INT\_ST]The masked interrupt status bit for the \hyperref[int:I2SOUTDSCRERRINT]{I2S\_OUT\_DSCR\_ERR\_INT} interrupt. (RO)
\item [I2S\_IN\_DSCR\_ERR\_INT\_ST]The masked interrupt status bit for the \hyperref[int:I2SINDSCRERRINT]{I2S\_IN\_DSCR\_ERR\_INT} interrupt. (RO)
\item [I2S\_OUT\_EOF\_INT\_ST]The masked interrupt status bit for the \hyperref[int:I2SOUTEOFINT]{I2S\_OUT\_EOF\_INT} interrupt. (RO)
\item [I2S\_OUT\_DONE\_INT\_ST]The masked interrupt status bit for the \hyperref[int:I2SOUTDONEINT]{I2S\_OUT\_DONE\_INT} interrupt. (RO)
\item [I2S\_IN\_SUC\_EOF\_INT\_ST]The masked interrupt status bit for the \hyperref[int:I2SINSUCEOFINT]{I2S\_IN\_SUC\_EOF\_INT} interrupt. (RO)
\item [I2S\_IN\_DONE\_INT\_ST]The masked interrupt status bit for the I2S\_IN\_DONE\_INT interrupt. (RO)
\item [I2S\_TX\_HUNG\_INT\_ST]The masked interrupt status bit for the \hyperref[int:I2STXHUNGINT]{I2S\_TX\_HUNG\_INT} interrupt. (RO)
\item [I2S\_RX\_HUNG\_INT\_ST]The masked interrupt status bit for the \hyperref[int:I2SRXHUNGINT]{I2S\_RX\_HUNG\_INT} interrupt. (RO)
\item [I2S\_TX\_REMPTY\_INT\_ST]The masked interrupt status bit for the \hyperref[int:I2STXREMPTYINT]{I2S\_TX\_REMPTY\_INT} interrupt. (RO)
\item [I2S\_TX\_WFULL\_INT\_ST]The masked interrupt status bit for the \hyperref[int:I2STXWFULLINT]{I2S\_TX\_WFULL\_INT} interrupt. (RO)
\item [I2S\_RX\_REMPTY\_INT\_ST]The masked interrupt status bit for the \hyperref[int:I2SRXREMPTYINT]{I2S\_RX\_REMPTY\_INT} interrupt. (RO)
\item [I2S\_RX\_WFULL\_INT\_ST]The masked interrupt status bit for the \hyperref[int:I2SRXWFULLINT]{I2S\_RX\_WFULL\_INT} interrupt. (RO)
\item [I2S\_TX\_PUT\_DATA\_INT\_ST]The masked interrupt status bit for the \hyperref[int:I2STXPUTDATAINT]{I2S\_TX\_PUT\_DATA\_INT} interrupt. (RO)
\item [I2S\_RX\_TAKE\_DATA\_INT\_ST]The masked interrupt status bit for the \hyperref[int:I2SRXTAKEDATAINT]{I2S\_RX\_TAKE\_DATA\_INT} interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_INT\_ENA\_REG}{0x0014}\label{regdesc:I2SINTENAREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{I2S\_OUT\_TOTAL\_EOF\_INT\_ENA}{1}{16}{0}%
\regfield{I2S\_IN\_DSCR\_EMPTY\_INT\_ENA}{1}{15}{0}%
\regfield{I2S\_OUT\_DSCR\_ERR\_INT\_ENA}{1}{14}{0}%
\regfield{I2S\_IN\_DSCR\_ERR\_INT\_ENA}{1}{13}{0}%
\regfield{I2S\_OUT\_EOF\_INT\_ENA}{1}{12}{0}%
\regfield{I2S\_OUT\_DONE\_INT\_ENA}{1}{11}{0}%
\regfield{(reserved)}{1}{10}{0}%
\regfield{I2S\_IN\_SUC\_EOF\_INT\_ENA}{1}{9}{0}%
\regfield{I2S\_IN\_DONE\_INT\_ENA}{1}{8}{0}%
\regfield{I2S\_TX\_HUNG\_INT\_ENA}{1}{7}{0}%
\regfield{I2S\_RX\_HUNG\_INT\_ENA}{1}{6}{0}%
\regfield{I2S\_TX\_REMPTY\_INT\_ENA}{1}{5}{0}%
\regfield{I2S\_TX\_WFULL\_INT\_ENA}{1}{4}{0}%
\regfield{I2S\_RX\_REMPTY\_INT\_ENA}{1}{3}{0}%
\regfield{I2S\_RX\_WFULL\_INT\_ENA}{1}{2}{0}%
\regfield{I2S\_TX\_PUT\_DATA\_INT\_ENA}{1}{1}{0}%
\regfield{I2S\_RX\_TAKE\_DATA\_INT\_ENA}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_OUT\_TOTAL\_EOF\_INT\_ENA]The interrupt enable bit for the \hyperref[int:I2SOUTTOTALEOFINT]{I2S\_OUT\_TOTAL\_EOF\_INT} interrupt. (R/W)
\item [I2S\_IN\_DSCR\_EMPTY\_INT\_ENA]The interrupt enable bit for the \hyperref[int:I2SINDSCREMPTYINT]{I2S\_IN\_DSCR\_EMPTY\_INT} interrupt. (R/W)
\item [I2S\_OUT\_DSCR\_ERR\_INT\_ENA]The interrupt enable bit for the \hyperref[int:I2SOUTDSCRERRINT]{I2S\_OUT\_DSCR\_ERR\_INT} interrupt. (R/W)
\item [I2S\_IN\_DSCR\_ERR\_INT\_ENA]The interrupt enable bit for the \hyperref[int:I2SINDSCRERRINT]{I2S\_IN\_DSCR\_ERR\_INT} interrupt. (R/W)
\item [I2S\_OUT\_EOF\_INT\_ENA]The interrupt enable bit for the \hyperref[int:I2SOUTEOFINT]{I2S\_OUT\_EOF\_INT} interrupt. (R/W)
\item [I2S\_OUT\_DONE\_INT\_ENA]The interrupt enable bit for the \hyperref[int:I2SOUTDONEINT]{I2S\_OUT\_DONE\_INT} interrupt. (R/W)
\item [I2S\_IN\_SUC\_EOF\_INT\_ENA]The interrupt enable bit for the \hyperref[int:I2SINSUCEOFINT]{I2S\_IN\_SUC\_EOF\_INT} interrupt. (R/W)
\item [I2S\_IN\_DONE\_INT\_ENA]The interrupt enable bit for the \hyperref[int:I2SINDONEINT]{I2S\_IN\_DONE\_INT} interrupt. (R/W)
\item [I2S\_TX\_HUNG\_INT\_ENA]The interrupt enable bit for the \hyperref[int:I2STXHUNGINT]{I2S\_TX\_HUNG\_INT} interrupt. (R/W)
\item [I2S\_RX\_HUNG\_INT\_ENA]The interrupt enable bit for the \hyperref[int:I2SRXHUNGINT]{I2S\_RX\_HUNG\_INT} interrupt. (R/W)
\item [I2S\_TX\_REMPTY\_INT\_ENA]The interrupt enable bit for the \hyperref[int:I2STXREMPTYINT]{I2S\_TX\_REMPTY\_INT} interrupt. (R/W)
\item [I2S\_TX\_WFULL\_INT\_ENA]The interrupt enable bit for the \hyperref[int:I2STXWFULLINT]{I2S\_TX\_WFULL\_INT} interrupt. (R/W)
\item [I2S\_RX\_REMPTY\_INT\_ENA]The interrupt enable bit for the \hyperref[int:I2SRXREMPTYINT]{I2S\_RX\_REMPTY\_INT} interrupt. (R/W)
\item [I2S\_RX\_WFULL\_INT\_ENA]The interrupt enable bit for the \hyperref[int:I2SRXWFULLINT]{I2S\_RX\_WFULL\_INT} interrupt. (R/W)
\item [I2S\_TX\_PUT\_DATA\_INT\_ENA]The interrupt enable bit for the \hyperref[int:I2STXPUTDATAINT]{I2S\_TX\_PUT\_DATA\_INT} interrupt. (R/W)
\item [I2S\_RX\_TAKE\_DATA\_INT\_ENA]The interrupt enable bit for the \hyperref[int:I2SRXTAKEDATAINT]{I2S\_RX\_TAKE\_DATA\_INT} interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_INT\_CLR\_REG}{0x0018}\label{regdesc:I2SINTCLRREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{I2S\_OUT\_TOTAL\_EOF\_INT\_CLR}{1}{16}{0}%
\regfield{I2S\_IN\_DSCR\_EMPTY\_INT\_CLR}{1}{15}{0}%
\regfield{I2S\_OUT\_DSCR\_ERR\_INT\_CLR}{1}{14}{0}%
\regfield{I2S\_IN\_DSCR\_ERR\_INT\_CLR}{1}{13}{0}%
\regfield{I2S\_OUT\_EOF\_INT\_CLR}{1}{12}{0}%
\regfield{I2S\_OUT\_DONE\_INT\_CLR}{1}{11}{0}%
\regfield{(reserved)}{1}{10}{0}%
\regfield{I2S\_IN\_SUC\_EOF\_INT\_CLR}{1}{9}{0}%
\regfield{I2S\_IN\_DONE\_INT\_CLR}{1}{8}{0}%
\regfield{I2S\_TX\_HUNG\_INT\_CLR}{1}{7}{0}%
\regfield{I2S\_RX\_HUNG\_INT\_CLR}{1}{6}{0}%
\regfield{I2S\_TX\_REMPTY\_INT\_CLR}{1}{5}{0}%
\regfield{I2S\_TX\_WFULL\_INT\_CLR}{1}{4}{0}%
\regfield{I2S\_RX\_REMPTY\_INT\_CLR}{1}{3}{0}%
\regfield{I2S\_RX\_WFULL\_INT\_CLR}{1}{2}{0}%
\regfield{I2S\_TX\_PUT\_DATA\_INT\_CLR}{1}{1}{0}%
\regfield{I2S\_RX\_TAKE\_DATA\_INT\_CLR}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_OUT\_TOTAL\_EOF\_INT\_CLR]Set this bit to clear the \hyperref[int:I2SOUTTOTALEOFINT]{I2S\_OUT\_TOTAL\_EOF\_INT} interrupt. (WO)
\item [I2S\_IN\_DSCR\_EMPTY\_INT\_CLR]Set this bit to clear the \hyperref[int:I2SINDSCREMPTYINT]{I2S\_IN\_DSCR\_EMPTY\_INT} interrupt. (WO)
\item [I2S\_OUT\_DSCR\_ERR\_INT\_CLR]Set this bit to clear the \hyperref[int:I2SOUTDSCRERRINT]{I2S\_OUT\_DSCR\_ERR\_INT} interrupt. (WO)
\item [I2S\_IN\_DSCR\_ERR\_INT\_CLR]Set this bit to clear the \hyperref[int:I2SINDSCRERRINT]{I2S\_IN\_DSCR\_ERR\_INT} interrupt. (WO)
\item [I2S\_OUT\_EOF\_INT\_CLR]Set this bit to clear the \hyperref[int:I2SOUTEOFINT]{I2S\_OUT\_EOF\_INT} interrupt. (WO)
\item [I2S\_OUT\_DONE\_INT\_CLR]Set this bit to clear the \hyperref[int:I2SOUTDONEINT]{I2S\_OUT\_DONE\_INT} interrupt. (WO)
\item [I2S\_IN\_SUC\_EOF\_INT\_CLR]Set this bit to clear the \hyperref[int:I2SINSUCEOFINT]{I2S\_IN\_SUC\_EOF\_INT} interrupt. (WO)
\item [I2S\_IN\_DONE\_INT\_CLR]Set this bit to clear the \hyperref[int:I2SINDONEINT]{I2S\_IN\_DONE\_INT} interrupt. (WO)
\item [I2S\_TX\_HUNG\_INT\_CLR]Set this bit to clear the \hyperref[int:I2STXHUNGINT]{I2S\_TX\_HUNG\_INT} interrupt. (WO)
\item [I2S\_RX\_HUNG\_INT\_CLR]Set this bit to clear the \hyperref[int:I2SRXHUNGINT]{I2S\_RX\_HUNG\_INT} interrupt. (WO)
\item [I2S\_TX\_REMPTY\_INT\_CLR]Set this bit to clear the \hyperref[int:I2STXREMPTYINT]{I2S\_TX\_REMPTY\_INT} interrupt. (WO)
\item [I2S\_TX\_WFULL\_INT\_CLR]Set this bit to clear the \hyperref[int:I2STXWFULLINT]{I2S\_TX\_WFULL\_INT} interrupt. (WO)
\item [I2S\_RX\_REMPTY\_INT\_CLR]Set this bit to clear the \hyperref[int:I2SRXREMPTYINT]{I2S\_RX\_REMPTY\_INT} interrupt. (WO)
\item [I2S\_RX\_WFULL\_INT\_CLR]Set this bit to clear the \hyperref[int:I2SRXWFULLINT]{I2S\_RX\_WFULL\_INT} interrupt. (WO)
\item [I2S\_TX\_PUT\_DATA\_INT\_CLR]Set this bit to clear the \hyperref[int:I2STXPUTDATAINT]{I2S\_TX\_PUT\_DATA\_INT} interrupt. (WO)
\item [I2S\_RX\_TAKE\_DATA\_INT\_CLR]Set this bit to clear the \hyperref[int:I2SRXTAKEDATAINT]{I2S\_RX\_TAKE\_DATA\_INT} interrupt. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_TIMING\_REG}{0x001c}\label{regdesc:I2STIMINGREG}
\regfield{(reserved)}{7}{25}{0000000}%
\regfield{I2S\_TX\_BCK\_IN\_INV}{1}{24}{0}%
\regfield{I2S\_DATA\_ENABLE\_DELAY}{2}{22}{00}%
\regfield{I2S\_RX\_DSYNC\_SW}{1}{21}{0}%
\regfield{I2S\_TX\_DSYNC\_SW}{1}{20}{0}%
\regfield{I2S\_RX\_BCK\_OUT\_DELAY}{2}{18}{00}%
\regfield{I2S\_RX\_WS\_OUT\_DELAY}{2}{16}{00}%
\regfield{I2S\_TX\_SD\_OUT\_DELAY}{2}{14}{00}%
\regfield{I2S\_TX\_WS\_OUT\_DELAY}{2}{12}{00}%
\regfield{I2S\_TX\_BCK\_OUT\_DELAY}{2}{10}{00}%
\regfield{I2S\_RX\_SD\_IN\_DELAY}{2}{8}{00}%
\regfield{I2S\_RX\_WS\_IN\_DELAY}{2}{6}{00}%
\regfield{I2S\_RX\_BCK\_IN\_DELAY}{2}{4}{00}%
\regfield{I2S\_TX\_WS\_IN\_DELAY}{2}{2}{00}%
\regfield{I2S\_TX\_BCK\_IN\_DELAY}{2}{0}{00}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_TX\_BCK\_IN\_INV]Set this bit to invert the BCK signal into the slave transmitter. (R/W)
\item [I2S\_DATA\_ENABLE\_DELAY]Number of delay cycles for data valid flag. (R/W)
\item [I2S\_RX\_DSYNC\_SW]Set this bit to synchronize signals into the receiver in double sync method. (R/W)
\item [I2S\_TX\_DSYNC\_SW]Set this bit to synchronize signals into the transmitter in double sync method. (R/W)
\item [I2S\_RX\_BCK\_OUT\_DELAY]Number of delay cycles for BCK signal out of the receiver. (R/W)
\item [I2S\_RX\_WS\_OUT\_DELAY]Number of delay cycles for WS signal out of the receiver. (R/W)
\item [I2S\_TX\_SD\_OUT\_DELAY]Number of delay cycles for SD signal out of the transmitter. (R/W)
\item [I2S\_TX\_WS\_OUT\_DELAY]Number of delay cycles for WS signal out of the transmitter. (R/W)
\item [I2S\_TX\_BCK\_OUT\_DELAY]Number of delay cycles for BCK signal out of the transmitter. (R/W)
\item [I2S\_RX\_SD\_IN\_DELAY]Number of delay cycles for SD signal into the receiver. (R/W)
\item [I2S\_RX\_WS\_IN\_DELAY]Number of delay cycles for WS signal into the receiver. (R/W)
\item [I2S\_RX\_BCK\_IN\_DELAY]Number of delay cycles for BCK signal into the receiver. (R/W)
\item [I2S\_TX\_WS\_IN\_DELAY]Number of delay cycles for WS signal into the transmitter. (R/W)
\item [I2S\_TX\_BCK\_IN\_DELAY]Number of delay cycles for BCK signal into the transmitter. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_FIFO\_CONF\_REG}{0x0020}\label{regdesc:I2SFIFOCONFREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{I2S\_RX\_FIFO\_MOD\_FORCE\_EN}{1}{20}{0}%
\regfield{I2S\_TX\_FIFO\_MOD\_FORCE\_EN}{1}{19}{0}%
\regfield{I2S\_RX\_FIFO\_MOD}{3}{16}{000}%
\regfield{I2S\_TX\_FIFO\_MOD}{3}{13}{000}%
\regfield{I2S\_DSCR\_EN}{1}{12}{1}%
\regfield{I2S\_TX\_DATA\_NUM}{6}{6}{{32}}%
\regfield{I2S\_RX\_DATA\_NUM}{6}{0}{{32}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_RX\_FIFO\_MOD\_FORCE\_EN]The bit should always be set to 1. (R/W)
\item [I2S\_TX\_FIFO\_MOD\_FORCE\_EN]The bit should always be set to 1. (R/W)
\item [I2S\_RX\_FIFO\_MOD]Receive FIFO mode configuration bit. (R/W)
\item [I2S\_TX\_FIFO\_MOD]Transmit FIFO mode configuration bit. (R/W)
\item [I2S\_DSCR\_EN]Set this bit to enable I2S DMA mode. (R/W)
\item [I2S\_TX\_DATA\_NUM]Threshold of data length in the transmit FIFO. (R/W)
\item [I2S\_RX\_DATA\_NUM]Threshold of data length in the receive FIFO. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_RXEOF\_NUM\_REG}{0x0024}\label{regdesc:I2SRXEOFNUMREG}
\regfield{}{32}{0}{{64}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_RXEOF\_NUM\_REG]The length of the data to be received. It will trigger \hyperref[int:I2SINSUCEOFINT]{I2S\_IN\_SUC\_EOF\_INT}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_CONF\_SINGLE\_DATA\_REG}{0x0028}\label{regdesc:I2SCONFSIGLEDATAREG}
\regfield{}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_CONF\_SINGLE\_DATA\_REG]The right channel or the left channel outputs constant values stored in this register according to \hyperref[TXCHANMOD]{TX\_CHAN\_MOD} and \hyperref[MSBRIGHT]{I2S\_TX\_MSB\_RIGHT}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_CONF\_CHAN\_REG}{0x002c}\label{regdesc:I2SCONFCHANREG}
\regfield{(reserved)}{27}{5}{000000000000000000000000000}%
\regfield{I2S\_RX\_CHAN\_MOD}{2}{3}{00}%
\regfield{I2S\_TX\_CHAN\_MOD}{3}{0}{000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_RX\_CHAN\_MOD]I2S receiver channel mode configuration bits. Please refer to Section \ref{RXCHAN} for further details. (R/W)
\item [I2S\_TX\_CHAN\_MOD]\label{TXCHANMOD}I2S transmitter channel mode configuration bits. Please refer to Section \ref{TXCHAN} for further details. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_OUT\_LINK\_REG}{0x0030}\label{regdesc:I2SOUTLINKREG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{I2S\_OUTLINK\_RESTART}{1}{30}{0}%
\regfield{I2S\_OUTLINK\_START}{1}{29}{0}%
\regfield{I2S\_OUTLINK\_STOP}{1}{28}{0}%
\regfield{(reserved)}{8}{20}{00000000}%
\regfield{I2S\_OUTLINK\_ADDR}{20}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_OUTLINK\_RESTART]Set this bit to restart outlink descriptor. (R/W)
\item [I2S\_OUTLINK\_START]Set this bit to start outlink descriptor. (R/W)
\item [I2S\_OUTLINK\_STOP]Set this bit to stop outlink descriptor. (R/W)
\item [I2S\_OUTLINK\_ADDR]The address of first outlink descriptor. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_IN\_LINK\_REG}{0x0034}\label{regdesc:I2SINLINKREG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{I2S\_INLINK\_RESTART}{1}{30}{0}%
\regfield{I2S\_INLINK\_START}{1}{29}{0}%
\regfield{I2S\_INLINK\_STOP}{1}{28}{0}%
\regfield{(reserved)}{8}{20}{00000000}%
\regfield{I2S\_INLINK\_ADDR}{20}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_INLINK\_RESTART]Set this bit to restart inlink descriptor. (R/W)
\item [I2S\_INLINK\_START]Set this bit to start inlink descriptor. (R/W)
\item [I2S\_INLINK\_STOP]Set this bit to stop inlink descriptor. (R/W)
\item [I2S\_INLINK\_ADDR]The address of first inlink descriptor. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_OUT\_EOF\_DES\_ADDR\_REG}{0x0038}\label{regdesc:I2SOUTEOFDESADDRREG}
\regfield{}{32}{0}{{0x000000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_OUT\_EOF\_DES\_ADDR\_REG]The address of outlink descriptor that produces EOF. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_IN\_EOF\_DES\_ADDR\_REG}{0x003c}\label{regdesc:I2SINEOFDESADDRREG}
\regfield{}{32}{0}{{0x000000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_IN\_EOF\_DES\_ADDR\_REG]The address of inlink descriptor that produces EOF. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_OUT\_EOF\_BFR\_DES\_ADDR\_REG}{0x0040}\label{regdesc:I2SOUTEOFBFRDESADDRREG}
\regfield{}{32}{0}{{0x000000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_OUT\_EOF\_BFR\_DES\_ADDR\_REG]The address of the buffer corresponding to the outlink descriptor that produces EOF. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_INLINK\_DSCR\_REG}{0x0048}\label{regdesc:I2SINLINKDSCRREG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_INLINK\_DSCR\_REG]The address of current inlink descriptor. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_INLINK\_DSCR\_BF0\_REG}{0x004c}\label{regdesc:I2SINLINKDSCRBF0REG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_INLINK\_DSCR\_BF0\_REG]The address of next inlink descriptor. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_INLINK\_DSCR\_BF1\_REG}{0x0050}\label{regdesc:I2SINLINKDSCRBF1REG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_INLINK\_DSCR\_BF1\_REG]The address of next inlink data buffer. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_OUTLINK\_DSCR\_REG}{0x0054}\label{regdesc:I2SOUTLINKDSCRREG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_OUTLINK\_DSCR\_REG]The address of current outlink descriptor. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_OUTLINK\_DSCR\_BF0\_REG}{0x0058}\label{regdesc:I2SOUTLINKDSCRBF0REG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_OUTLINK\_DSCR\_BF0\_REG]The address of next outlink descriptor. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_OUTLINK\_DSCR\_BF1\_REG}{0x005c}\label{regdesc:I2SOUTLINKDSCRBF1REG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_OUTLINK\_DSCR\_BF1\_REG]The address of next outlink data buffer. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_LC\_CONF\_REG}{0x0060}\label{regdesc:I2SLCCONFREG}
\regfield{(reserved)}{19}{13}{000000000000000000}%
\regfield{I2S\_CHECK\_OWNER}{1}{12}{0}%
\regfield{I2S\_OUT\_DATA\_BURST\_EN}{1}{11}{0}%
\regfield{I2S\_INDSCR\_BURST\_EN}{1}{10}{0}%
\regfield{I2S\_OUTDSCR\_BURST\_EN}{1}{9}{0}%
\regfield{I2S\_OUT\_EOF\_MODE}{1}{8}{1}%
\regfield{(reserved)}{1}{7}{0}%
\regfield{I2S\_OUT\_AUTO\_WRBACK}{1}{6}{0}%
\regfield{I2S\_OUT\_LOOP\_TEST}{1}{5}{0}%
\regfield{I2S\_IN\_LOOP\_TEST}{1}{4}{0}%
\regfield{I2S\_AHBM\_RST}{1}{3}{0}%
\regfield{I2S\_AHBM\_FIFO\_RST}{1}{2}{0}%
\regfield{I2S\_OUT\_RST}{1}{1}{0}%
\regfield{I2S\_IN\_RST}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_CHECK\_OWNER]Set this bit to check the owner bit by hardware. (R/W)
\item [I2S\_OUT\_DATA\_BURST\_EN]Transmitter data transfer mode configuration bit. (R/W)\\
1: Transmit data in burst mode;\\
0: Transmit data in byte mode.
\item [I2S\_INDSCR\_BURST\_EN]DMA inlink descriptor transfer mode configuration bit. (R/W)\\
1: Transfer inlink descriptor in burst mode;\\
0: Transfer inlink descriptor in byte mode.
\item [I2S\_OUTDSCR\_BURST\_EN]DMA outlink descriptor transfer mode configuration bit. (R/W)\\
1: Transfer outlink descriptor in burst mode;\\
0: Transfer outlink descriptor in byte mode.
\item [I2S\_OUT\_EOF\_MODE]DMA \hyperref[int:I2SOUTEOFINT]{I2S\_OUT\_EOF\_INT} generation mode. (R/W) \\1: When DMA has popped all data from the FIFO;\\
0: When AHB has pushed all data to the FIFO.
\item [I2S\_OUT\_AUTO\_WRBACK]Set this bit to enable automatic outlink-writeback when all the data in tx buffer has been transmitted. (R/W)
\item [I2S\_OUT\_LOOP\_TEST]Set this bit to loop test outlink. (R/W)
\item [I2S\_IN\_LOOP\_TEST]Set this bit to loop test inlink. (R/W)
\item [I2S\_AHBM\_RST]Set this bit to reset AHB interface of DMA. (R/W)
\item [I2S\_AHBM\_FIFO\_RST]Set this bit to reset AHB interface cmdFIFO of DMA. (R/W)
\item [I2S\_OUT\_RST]Set this bit to reset out DMA FSM. (R/W)
\item [I2S\_IN\_RST]Set this bit to reset in DMA FSM. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_LC\_STATE0\_REG}{0x006c}\label{regdesc:I2SLCSTATE0REG}
\regfield{}{32}{0}{{0x000000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_LC\_STATE0\_REG]Receiver DMA channel status register. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_LC\_STATE1\_REG}{0x0070}\label{regdesc:I2SLCSTATE1REG}
\regfield{}{32}{0}{{0x000000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_LC\_STATE1\_REG]Transmitter DMA channel status register. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_LC\_HUNG\_CONF\_REG}{0x0074}\label{regdesc:I2SLCHUNGCONFREG}
\regfield{(reserved)}{20}{12}{00000000000000000000}%
\regfield{I2S\_LC\_FIFO\_TIMEOUT\_ENA}{1}{11}{1}%
\regfield{I2S\_LC\_FIFO\_TIMEOUT\_SHIFT}{3}{8}{000}%
\regfield{I2S\_LC\_FIFO\_TIMEOUT}{8}{0}{{0x010}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_LC\_FIFO\_TIMEOUT\_ENA]The enable bit for FIFO timeout. (R/W)
\item [I2S\_LC\_FIFO\_TIMEOUT\_SHIFT]The bits are used to set the tick counter threshold. The tick counter is reset when the counter value >= 88000/\begin{math} 2^{\textrm{i2s\_lc\_fifo\_timeout\_shift}}\end{math}. (R/W)
\item [I2S\_LC\_FIFO\_TIMEOUT]When the value of FIFO hung counter is equal to this bit value, sending data-timeout interrupt or receiving data-timeout interrupt will be triggered. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_CONF1\_REG}{0x00a0}\label{regdesc:I2SCONF1REG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{I2S\_TX\_STOP\_EN}{1}{8}{0}%
\regfield{I2S\_RX\_PCM\_BYPASS}{1}{7}{1}%
\regfield{I2S\_RX\_PCM\_CONF}{3}{4}{{0x0}}%
\regfield{I2S\_TX\_PCM\_BYPASS}{1}{3}{1}%
\regfield{I2S\_TX\_PCM\_CONF}{3}{0}{{0x1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_TX\_STOP\_EN]Set this bit and the transmitter will stop transmitting BCK signal and WS signal when tx FIFO is empty. (R/W)
\item [I2S\_RX\_PCM\_BYPASS]Set this bit to bypass the Compress/Decompress module for the received data. (R/W)
\item [I2S\_RX\_PCM\_CONF]Compress/Decompress module configuration bit. (R/W)\\
0: Decompress received data;\\ 1: Compress received data.
\item [I2S\_TX\_PCM\_BYPASS]Set this bit to bypass the Compress/Decompress module for the transmitted data. (R/W)
\item [I2S\_TX\_PCM\_CONF]Compress/Decompress module configuration bit. (R/W)\\
0: Decompress transmitted data;\\
1: Compress transmitted data.
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_PD\_CONF\_REG}{0x00a4}\label{regdesc:I2SPDCONFREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{(reserved)}{1}{3}{1}%
\regfield{(reserved)}{1}{2}{0}%
\regfield{I2S\_FIFO\_FORCE\_PU}{1}{1}{1}%
\regfield{I2S\_FIFO\_FORCE\_PD}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_FIFO\_FORCE\_PU]Force FIFO power-up. (R/W)
\item [I2S\_FIFO\_FORCE\_PD]Force FIFO power-down. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_CONF2\_REG}{0x00a8}\label{regdesc:I2SCONF2REG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{I2S\_INTER\_VALID\_EN}{1}{7}{0}%
\regfield{I2S\_EXT\_ADC\_START\_EN}{1}{6}{0}%
\regfield{I2S\_LCD\_EN}{1}{5}{1}%
\regfield{(reserved)}{2}{3}{00}%
\regfield{I2S\_LCD\_TX\_SDX2\_EN}{1}{2}{0}%
\regfield{I2S\_LCD\_TX\_WRX2\_EN}{1}{1}{0}%
\regfield{I2S\_CAMERA\_EN}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_INTER\_VALID\_EN]Set this bit to enable camera's internal validation. (R/W)
\item [I2S\_EXT\_ADC\_START\_EN]Set this bit to enable the start of external ADC . (R/W)
\item [I2S\_LCD\_EN]Set this bit to enable LCD mode. (R/W)
\item [I2S\_LCD\_TX\_SDX2\_EN]Set this bit to duplicate data pairs (Data Frame, Form 2) in LCD mode. (R/W)
\item [I2S\_LCD\_TX\_WRX2\_EN]One datum will be written twice in LCD mode. (R/W)
\item [I2S\_CAMERA\_EN]Set this bit to enable camera mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_CLKM\_CONF\_REG}{0x00ac}\label{regdesc:I2SCLKMCONFREG}
\regfield{(reserved)}{10}{22}{00000000000000}%
\regfield{I2S\_CLKA\_ENA}{1}{21}{0}%
\regfield{(reserved)}{1}{20}{0}%
\regfield{I2S\_CLKM\_DIV\_A}{6}{14}{{0x00}}%
\regfield{I2S\_CLKM\_DIV\_B}{6}{8}{{0x00}}%
\regfield{I2S\_CLKM\_DIV\_NUM}{8}{0}{{4}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_CLKA\_ENA]Set this bit to enable APLL\_CLK. Default is PLL\_F160M\_CLK. (R/W)
\item [I2S\_CLKM\_DIV\_A]Fractional clock divider's denominator value. (R/W)
\item [I2S\_CLKM\_DIV\_B]Fractional clock divider's numerator value. (R/W)
\item [I2S\_CLKM\_DIV\_NUM]I2S clock divider's integral value. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_SAMPLE\_RATE\_CONF\_REG}{0x00b0}\label{regdesc:I2SSAMPLERATECONFREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{I2S\_RX\_BITS\_MOD}{6}{18}{{16}}%
\regfield{I2S\_TX\_BITS\_MOD}{6}{12}{{16}}%
\regfield{I2S\_RX\_BCK\_DIV\_NUM}{6}{6}{{6}}%
\regfield{I2S\_TX\_BCK\_DIV\_NUM}{6}{0}{{6}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_RX\_BITS\_MOD]Set the bits to configure the bit length of I2S receiver channel. (R/W)
\item [I2S\_TX\_BITS\_MOD]Set the bits to configure the bit length of I2S transmitter channel. (R/W)
\item [I2S\_RX\_BCK\_DIV\_NUM]Bit clock configuration bit in receiver mode.  (R/W)
\item [I2S\_TX\_BCK\_DIV\_NUM]Bit clock configuration bit in transmitter mode.  (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_PDM\_CONF\_REG}{0x00b4}\label{regdesc:I2SPDMCONFREG}
\regfield{(reserved)}{6}{26}{000000}%
\regfield{I2S\_TX\_PDM\_HP\_BYPASS}{1}{25}{0}%
\regfield{I2S\_RX\_PDM\_SINC\_DSR\_16\_EN}{1}{24}{1}%
\regfield{I2S\_TX\_PDM\_SIGMADELTA\_IN\_SHIFT}{2}{22}{{0x1}}%
\regfield{I2S\_TX\_PDM\_SINC\_IN\_SHIFT}{2}{20}{{0x1}}%
\regfield{I2S\_TX\_PDM\_LP\_IN\_SHIFT}{2}{18}{{0x1}}%
\regfield{I2S\_TX\_PDM\_HP\_IN\_SHIFT}{2}{16}{{0x1}}%
\regfield{(reserved)}{8}{8}{00000000}%
\regfield{I2S\_TX\_PDM\_SINC\_OSR2}{4}{4}{{0x02}}%
\regfield{I2S\_PDM2PCM\_CONV\_EN}{1}{3}{1}%
\regfield{I2S\_PCM2PDM\_CONV\_EN}{1}{2}{1}%
\regfield{I2S\_RX\_PDM\_EN}{1}{1}{0}%
\regfield{I2S\_TX\_PDM\_EN}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_TX\_PDM\_HP\_BYPASS]Set this bit to bypass the transmitter's PDM HP filter. (R/W)
\item [I2S\_RX\_PDM\_SINC\_DSR\_16\_EN]PDM downsampling rate for filter group 1 in receiver mode. (R/W)\\
1: downsampling rate = 128;\\
0: downsampling rate = 64.
\item [I2S\_TX\_PDM\_SIGMADELTA\_IN\_SHIFT]Adjust the size of the input signal into filter module. (R/W)\\
0: divided by 2;  1: multiplied by 1; 2: multiplied by 2;  3: multiplied by 4.
\item [I2S\_TX\_PDM\_SINC\_IN\_SHIFT]Adjust the size of the input signal into filter module. (R/W)\\
0: divided by 2;  1: multiplied by 1; 2: multiplied by 2;  3: multiplied by 4.
\item [I2S\_TX\_PDM\_LP\_IN\_SHIFT]Adjust the size of the input signal into filter module. (R/W)\\
0: divided by 2;  1: multiplied by 1; 2: multiplied by 2;  3: multiplied by 4.
\item [I2S\_TX\_PDM\_HP\_IN\_SHIFT]Adjust the size of the input signal into filter module. (R/W)\\
0: divided by 2;  1: multiplied by 1; 2: multiplied by 2;  3: multiplied by 4.
\item [I2S\_TX\_PDM\_SINC\_OSR2]Upsampling rate = 64×i2s\_tx\_pdm\_sinc\_osr2 (R/W)
\item [I2S\_PDM2PCM\_CONV\_EN]Set this bit to enable PDM-to-PCM converter. (R/W)
\item [I2S\_PCM2PDM\_CONV\_EN]Set this bit to enable PCM-to-PDM converter. (R/W)
\item [I2S\_RX\_PDM\_EN]Set this bit to enable receiver's PDM mode. (R/W)
\item [I2S\_TX\_PDM\_EN]Set this bit to enable transmitter's PDM mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_PDM\_FREQ\_CONF\_REG}{0x00b8}\label{regdesc:I2SPDMFREQCONFREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{I2S\_TX\_PDM\_FP}{10}{10}{{960}}%
\regfield{I2S\_TX\_PDM\_FS}{10}{0}{{441}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_TX\_PDM\_FP]PCM-to-PDM converter's PDM frequency parameter. (R/W)
\item [I2S\_TX\_PDM\_FS]PCM-to-PDM converter's PCM frequency parameter. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{I2S\_STATE\_REG}{0x00bc}\label{regdesc:I2SSTATEREG}
\regfield{(reserved)}{29}{3}{000000000000}%
\regfield{I2S\_RX\_FIFO\_RESET\_BACK}{1}{2}{{0}}%
\regfield{I2S\_TX\_FIFO\_RESET\_BACK}{1}{1}{{0}}%
\regfield{I2S\_TX\_IDLE}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [I2S\_RX\_FIFO\_RESET\_BACK]
This bit is used to confirm if the Rx FIFO reset is done. 1: reset is not ready; 0: reset is ready. (RO)
\item [I2S\_TX\_FIFO\_RESET\_BACK]This bit is used to confirm if the Tx FIFO reset is done. 1: reset is not ready; 0: reset is ready. (RO)
\item [I2S\_TX\_IDLE]The status bit of the transmitter. 1: the transmitter is idle; 0: the transmitter is busy. (RO)
\end{reglist}\end{regdesc}
\end{register}
