\begin{register}{H}{HP\_SYSTEM\_ICM\_VER\_DATE\_REG}{0x0000}\label{regdesc:HPSYSTEMICMVERDATEREG}
\regfield{HP\_SYSTEM\_ICM\_VER\_DATE}{32}{0}{{0x20230214}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:HPSYSTEMICMVERDATE}\item [HP\_SYSTEM\_ICM\_VER\_DATE] Version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{HP\_SYSTEM\_ICM\_CLK\_EN\_REG}{0x0004}\label{regdesc:HPSYSTEMICMCLKENREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{HP\_SYSTEM\_ICM\_CLK\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:HPSYSTEMICMCLKEN}\item [HP\_SYSTEM\_ICM\_CLK\_EN] Configures whether or not to force the clock on for the register.\\
0: Clock is supported only when application writes registers.\\
1: Force clock on for register.\\
(R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{HP\_SYSTEM\_ICM\_DLOCK\_STATUS\_REG}{0x0008}\label{regdesc:HPSYSTEMICMDLOCKSTATUSREG}
\regfield{(reserved)}{20}{12}{00000000000000000000}%
\regfield{HP\_SYSTEM\_ICM\_DLOCK\_WR}{1}{11}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_DLOCK\_ID}{4}{7}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_DLOCK\_SLV}{3}{4}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_DLOCK\_MST}{4}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:HPSYSTEMICMDLOCKMST}\item [HP\_SYSTEM\_ICM\_DLOCK\_MST] Records the lowest numbered master involved in a deadlock. (RO)
\label{fielddesc:HPSYSTEMICMDLOCKSLV}\item [HP\_SYSTEM\_ICM\_DLOCK\_SLV] Records the slave with which the deadlock has occurred. (RO)
\label{fielddesc:HPSYSTEMICMDLOCKID}\item [HP\_SYSTEM\_ICM\_DLOCK\_ID] Records the AXI ID of the transaction that is deadlocked. (RO)
\label{fielddesc:HPSYSTEMICMDLOCKWR}\item [HP\_SYSTEM\_ICM\_DLOCK\_WR] Indicates whether the deadlocked transaction is a write operation.\\
0: Not a write operation\\
1: Write operation\\
(RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_ADDR\_REG}{0x0038}\label{regdesc:HPSYSTEMICMSYSADDRHOLEADDRREG}
\regfield{HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_ADDR}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:HPSYSTEMICMSYSADDRHOLEADDR}\item [HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_ADDR] Records the address when \hyperref[tab:sysreg-int-sources]{ICM\_SYS\_ADDRHOLE\_INT} occurs. \\
When HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_SECURE is 0, it records the unauthorized access address.\\
When HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_SECURE is 1, it records the illegal access address.\\
(RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_INFO\_REG}{0x003C}\label{regdesc:HPSYSTEMICMSYSADDRHOLEINFOREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_SECURE}{1}{9}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_WR}{1}{8}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_ID}{8}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:HPSYSTEMICMSYSADDRHOLEID}\item [HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_ID] Records the master ID when \hyperref[tab:sysreg-int-sources]{ICM\_SYS\_ADDRHOLE\_INT} occurs. This ID consists of a 4-bit CID and a 4-bit UID (refer to the related IP for details). The CID is used for master verification in ICM. CID values correspond to the following masters:\\
1: CACHE\\
5: GDMA MST1\\
6: GDMA MST2\\
8: AXI GDMA\\
10: DMA2D\\
11: H264 MST1\\
12: H264 MST2\\
(RO)
\label{fielddesc:HPSYSTEMICMSYSADDRHOLEWR}\item [HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_WR] Records the type of transfer when \hyperref[tab:sysreg-int-sources]{ICM\_SYS\_ADDRHOLE\_INT} occurs.\\
0: Read transfer\\
1: Write transfer\\
(RO)
\label{fielddesc:HPSYSTEMICMSYSADDRHOLESECURE}\item [HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_SECURE] Records the type of access error when \hyperref[tab:sysreg-int-sources]{ICM\_SYS\_ADDRHOLE\_INT} occurs.\\
0: Unauthorized access\\
1: Illegal access\\
(RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_ADDR\_REG}{0x0040}\label{regdesc:HPSYSTEMICMCPUADDRHOLEADDRREG}
\regfield{HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_ADDR}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:HPSYSTEMICMCPUADDRHOLEADDR}\item [HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_ADDR] Records the address when \hyperref[tab:sysreg-int-sources]{ICM\_CPU\_ADDRHOLE\_INT} occurs.\\
When HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_SECURE is 0, it records the unauthorized access address.\\
When HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_SECURE is 1, it records the illegal access address.\\
(RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_INFO\_REG}{0x0044}\label{regdesc:HPSYSTEMICMCPUADDRHOLEINFOREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_SECURE}{1}{9}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_WR}{1}{8}{{0}}%
\regfield{(reserved)}{3}{5}{000}%
\regfield{HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_ID}{5}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:HPSYSTEMICMCPUADDRHOLEID}\item [HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_ID] Records the master ID when \hyperref[tab:sysreg-int-sources]{ICM\_CPU\_ADDRHOLE\_INT} occurs.\\
0: HP CPU0\\
1: HP CPU1\\
2: LP CPU\\
3: USBOTGFS\\
5: GMAC\\
6: SDMMC\\
7: USBOTGHS\\
8: TRACE0\\
9: TRACE1\\
10: SPM Monitor\\
11: L2MEM Monitor\\
16-31: AHB GDMA\\
(RO)
\label{fielddesc:HPSYSTEMICMCPUADDRHOLEWR}\item [HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_WR] Records the type of transfer when \hyperref[tab:sysreg-int-sources]{ICM\_CPU\_ADDRHOLE\_INT} occurs.\\
0: Read transfer\\
1: Write transfer\\
(RO)
\label{fielddesc:HPSYSTEMICMCPUADDRHOLESECURE}\item [HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_SECURE] Records the type of access error when \hyperref[tab:sysreg-int-sources]{ICM\_CPU\_ADDRHOLE\_INT} occurs.\\
0: Unauthorized access\\
1: Illegal access\\
(RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{HP\_SYSTEM\_ICM\_INT\_RAW\_REG}{0x000C}\label{regdesc:HPSYSTEMICMINTRAWREG}
\regfield{\rotatebox{12}{(reserved)}}{29}{3}{00000000000000000000000000000}%
\regfield{\rotatebox{12}{HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_INT\_RAW}}{1}{2}{{0}}%
\regfield{\rotatebox{12}{HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_INT\_RAW}}{1}{1}{{0}}%
\regfield{\rotatebox{12}{HP\_SYSTEM\_ICM\_DLOCK\_INT\_RAW}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:HPSYSTEMICMDLOCKINTRAW}\item [HP\_SYSTEM\_ICM\_DLOCK\_INT\_RAW] The raw interrupt status of \hyperref[tab:sysreg-int-sources]{ICM\_DLOCK\_INT}. (R/WTC/SS)
\label{fielddesc:HPSYSTEMICMSYSADDRHOLEINTRAW}\item [HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_INT\_RAW] The raw interrupt status of \hyperref[tab:sysreg-int-sources]{ICM\_SYS\_ADDRHOLE\_INT}. (R/WTC/SS)
\label{fielddesc:HPSYSTEMICMCPUADDRHOLEINTRAW}\item [HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_INT\_RAW] The raw interrupt status of \hyperref[tab:sysreg-int-sources]{ICM\_CPU\_ADDRHOLE\_INT}. (R/WTC/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{HP\_SYSTEM\_ICM\_INT\_ST\_REG}{0x0010}\label{regdesc:HPSYSTEMICMINTSTREG}
\regfield{\rotatebox{12}{(reserved)}}{29}{3}{00000000000000000000000000000}%
\regfield{\rotatebox{12}{HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_INT\_ST}}{1}{2}{{0}}%
\regfield{\rotatebox{12}{HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_INT\_ST}}{1}{1}{{0}}%
\regfield{\rotatebox{12}{HP\_SYSTEM\_ICM\_DLOCK\_INT\_ST}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:HPSYSTEMICMDLOCKINTST}\item [HP\_SYSTEM\_ICM\_DLOCK\_INT\_ST] The masked interrupt status of \hyperref[tab:sysreg-int-sources]{DLOCK\_INT}. (RO)
\label{fielddesc:HPSYSTEMICMSYSADDRHOLEINTST}\item [HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_INT\_ST] The masked interrupt status of \hyperref[tab:sysreg-int-sources]{ICM\_SYS\_ADDRHOLE\_INT}. (RO)
\label{fielddesc:HPSYSTEMICMCPUADDRHOLEINTST}\item [HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_INT\_ST] The masked interrupt status of \hyperref[tab:sysreg-int-sources]{ICM\_CPU\_ADDRHOLE\_INT}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{HP\_SYSTEM\_ICM\_INT\_ENA\_REG}{0x0014}\label{regdesc:HPSYSTEMICMINTENAREG}
\regfield{\rotatebox{12}{(reserved)}}{29}{3}{00000000000000000000000000000}%
\regfield{\rotatebox{12}{HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_INT\_ENA}}{1}{2}{{1}}%
\regfield{\rotatebox{12}{HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_INT\_ENA}}{1}{1}{{1}}%
\regfield{\rotatebox{12}{HP\_SYSTEM\_ICM\_DLOCK\_INT\_ENA}}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:HPSYSTEMICMDLOCKINTENA}\item [HP\_SYSTEM\_ICM\_DLOCK\_INT\_ENA] Write 1 to enable \hyperref[tab:sysreg-int-sources]{DLOCK\_INT} interrupt. (R/W)
\label{fielddesc:HPSYSTEMICMSYSADDRHOLEINTENA}\item [HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_INT\_ENA] Write 1 to enable \hyperref[tab:sysreg-int-sources]{ICM\_SYS\_ADDRHOLE\_INT} interrupt. (R/W)
\label{fielddesc:HPSYSTEMICMCPUADDRHOLEINTENA}\item [HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_INT\_ENA] Write 1 to enable \hyperref[tab:sysreg-int-sources]{ICM\_CPU\_ADDRHOLE\_INT} interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{HP\_SYSTEM\_ICM\_INT\_CLR\_REG}{0x0018}\label{regdesc:HPSYSTEMICMINTCLRREG}
\regfield{\rotatebox{12}{(reserved)}}{29}{3}{00000000000000000000000000000}%
\regfield{\rotatebox{12}{HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_INT\_CLR}}{1}{2}{{0}}%
\regfield{\rotatebox{12}{HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_INT\_CLR}}{1}{1}{{0}}%
\regfield{\rotatebox{12}{HP\_SYSTEM\_ICM\_DLOCK\_INT\_CLR}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:HPSYSTEMICMDLOCKINTCLR}\item [HP\_SYSTEM\_ICM\_DLOCK\_INT\_CLR] Write 1 to clear \hyperref[tab:sysreg-int-sources]{DLOCK\_INT} interrupt. (WT)
\label{fielddesc:HPSYSTEMICMSYSADDRHOLEINTCLR}\item [HP\_SYSTEM\_ICM\_SYS\_ADDRHOLE\_INT\_CLR] Write 1 to clear \hyperref[tab:sysreg-int-sources]{ICM\_SYS\_ADDRHOLE\_INT} interrupt. (WT)
\label{fielddesc:HPSYSTEMICMCPUADDRHOLEINTCLR}\item [HP\_SYSTEM\_ICM\_CPU\_ADDRHOLE\_INT\_CLR] Write 1 to clear \hyperref[tab:sysreg-int-sources]{ICM\_CPU\_ADDRHOLE\_INT} interrupt. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{HP\_SYSTEM\_ICM\_SLV\_ARB\_PRIORITY\_REG}{0x0024}\label{regdesc:HPSYSTEMICMSLVARBPRIORITYREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{HP\_SYSTEM\_ICM\_CAM\_PRIORITY}{3}{21}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_LCD\_PRIORITY}{3}{18}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_PSRAM\_MSPI\_PRIORITY}{3}{15}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_FLASH\_MSPI\_PRIORITY}{3}{12}{{0}}%
\regfield{(reserved)}{6}{6}{000000}%
\regfield{HP\_SYSTEM\_ICM\_L2MEM\_PRIORITY}{3}{3}{{0}}%
\regfield{(reserved)}{3}{0}{000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:HPSYSTEMICML2MEMPRIORITY}\item [HP\_SYSTEM\_ICM\_L2MEM\_PRIORITY] Configures the arbitration priority of L2MEM for response channels among slaves connected to SYS ICM. (R/W)
\label{fielddesc:HPSYSTEMICMFLASHMSPIPRIORITY}\item [HP\_SYSTEM\_ICM\_FLASH\_MSPI\_PRIORITY] Configures the arbitration priority of FLASH MSPI for response channels among slaves connected to SYS ICM. (R/W)
\label{fielddesc:HPSYSTEMICMPSRAMMSPIPRIORITY}\item [HP\_SYSTEM\_ICM\_PSRAM\_MSPI\_PRIORITY] Configures the arbitration priority of PSRAM MSPI for response channels among slaves connected to SYS ICM. (R/W)
\label{fielddesc:HPSYSTEMICMLCDPRIORITY}\item [HP\_SYSTEM\_ICM\_LCD\_PRIORITY] Configures the arbitration priority of MIPI\_LCD registers for response channels among slaves connected to SYS ICM. (R/W)
\label{fielddesc:HPSYSTEMICMCAMPRIORITY}\item [HP\_SYSTEM\_ICM\_CAM\_PRIORITY] Configures the arbitration priority of MIPI\_CAM registers for response channels among slaves connected to SYS ICM. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{HP\_SYSTEM\_ICM\_MST\_ARQOS\_REG0\_REG}{0x0028}\label{regdesc:HPSYSTEMICMMSTARQOSREG0REG}
\regfield{HP\_SYSTEM\_ICM\_AXI\_GDMA\_INT\_ARQOS}{4}{28}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_H264\_DMA\_M2\_ARQOS}{4}{24}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_H264\_DMA\_M1\_ARQOS}{4}{20}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_DW\_GDMA\_MST2\_ARQOS}{4}{16}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_DW\_GDMA\_MST1\_ARQOS}{4}{12}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_DMA2D\_ARQOS}{4}{8}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_CACHE\_ARQOS}{4}{4}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_CPU\_ARQOS}{4}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:HPSYSTEMICMCPUARQOS}\item [HP\_SYSTEM\_ICM\_CPU\_ARQOS] Configures the ARQoS value for CPU ICM. (R/W)
\label{fielddesc:HPSYSTEMICMCACHEARQOS}\item [HP\_SYSTEM\_ICM\_CACHE\_ARQOS] Configures the ARQoS value for CACHE. (R/W)
\label{fielddesc:HPSYSTEMICMDMA2DARQOS}\item [HP\_SYSTEM\_ICM\_DMA2D\_ARQOS] Configures the ARQoS value for DMA2D. (R/W)
\label{fielddesc:HPSYSTEMICMDWGDMAMST1ARQOS}\item [HP\_SYSTEM\_ICM\_DW\_GDMA\_MST1\_ARQOS] Configures the ARQoS value for DW-GDMA MST1. (R/W)
\label{fielddesc:HPSYSTEMICMDWGDMAMST2ARQOS}\item [HP\_SYSTEM\_ICM\_DW\_GDMA\_MST2\_ARQOS] Configures the ARQoS value for DW-GDMA MST2. (R/W)
\label{fielddesc:HPSYSTEMICMH264DMAM1ARQOS}\item [HP\_SYSTEM\_ICM\_H264\_DMA\_M1\_ARQOS] Configures the ARQoS value for H264 DMAMST1. (R/W)
\label{fielddesc:HPSYSTEMICMH264DMAM2ARQOS}\item [HP\_SYSTEM\_ICM\_H264\_DMA\_M2\_ARQOS] Configures the ARQoS value for H264 DMAMST2. (R/W)
\label{fielddesc:HPSYSTEMICMAXIGDMAINTARQOS}\item [HP\_SYSTEM\_ICM\_AXI\_GDMA\_INT\_ARQOS] Configures the ARQoS value for AXI GDMA. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{HP\_SYSTEM\_ICM\_MST\_AWQOS\_REG0\_REG}{0x0030}\label{regdesc:HPSYSTEMICMMSTAWQOSREG0REG}
\regfield{HP\_SYSTEM\_ICM\_PDMA\_INT\_AWQOS}{4}{28}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_H264\_DMA\_M2\_AWQOS}{4}{24}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_H264\_DMA\_M1\_AWQOS}{4}{20}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_GDMA\_M2\_AWQOS}{4}{16}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_GDMA\_M1\_AWQOS}{4}{12}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_DMA2D\_AWQOS}{4}{8}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_CACHE\_AWQOS}{4}{4}{{0}}%
\regfield{HP\_SYSTEM\_ICM\_CPU\_AWQOS}{4}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:HPSYSTEMICMCPUAWQOS}\item [HP\_SYSTEM\_ICM\_CPU\_AWQOS] Configures the AWQoS value for the CPU ICM. (R/W)
\label{fielddesc:HPSYSTEMICMCACHEAWQOS}\item [HP\_SYSTEM\_ICM\_CACHE\_AWQOS] Configures the AWQoS value for the CACHE. (R/W)
\label{fielddesc:HPSYSTEMICMDMA2DAWQOS}\item [HP\_SYSTEM\_ICM\_DMA2D\_AWQOS] Configures the AWQoS value for the DMA2D. (R/W)
\label{fielddesc:HPSYSTEMICMGDMAM1AWQOS}\item [HP\_SYSTEM\_ICM\_GDMA\_M1\_AWQOS] Configures the AWQoS value for the DW-GDMA MST1. (R/W)
\label{fielddesc:HPSYSTEMICMGDMAM2AWQOS}\item [HP\_SYSTEM\_ICM\_GDMA\_M2\_AWQOS] Configures the AWQoS value for the DW-GDMA MST2. (R/W)
\label{fielddesc:HPSYSTEMICMH264DMAM1AWQOS}\item [HP\_SYSTEM\_ICM\_H264\_DMA\_M1\_AWQOS] Configures the AWQoS value for the H264 DMA MST1. (R/W)
\label{fielddesc:HPSYSTEMICMH264DMAM2AWQOS}\item [HP\_SYSTEM\_ICM\_H264\_DMA\_M2\_AWQOS] Configures the AWQoS value for the H264 DMA MST2. (R/W)
\label{fielddesc:HPSYSTEMICMPDMAINTAWQOS}\item [HP\_SYSTEM\_ICM\_PDMA\_INT\_AWQOS] Configures the AWQoS value for the AXI GDMA. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{HP\_SYSTEM\_ICM\_DLOCK\_TIMEOUT\_REG}{0x0048}\label{regdesc:HPSYSTEMICMDLOCKTIMEOUTREG}
\regfield{(reserved)}{19}{13}{0000000000000000000}%
\regfield{HP\_SYSTEM\_ICM\_DLOCK\_TIMEOUT}{13}{0}{{2048}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:HPSYSTEMICMDLOCKTIMEOUT}\item [HP\_SYSTEM\_ICM\_DLOCK\_TIMEOUT] Configures the deadlock timeout threshold value. Deadlock will occur if there is no response within the configured threshold.\\
(R/W)
\end{reglist}\end{regdesc}
\end{register}