\section{Glossary}

To better illustrate the functions of GP-SPI and LP-SPI, the following terms are used in this chapter. 

\begin{longtable}[c]{ R{7cm} p{10cm} }

\textbf{Master Mode}     & GP-SPI or LP-SPI acts as an SPI master and initiates SPI transactions. \\ 
\textbf{Slave Mode}      & GP-SPI or LP-SPI acts as an SPI slave and exchanges data with its master when its CS is asserted.\\
\textbf{MISO}       & Master in, slave out, data transmission from a slave to a master.\\
\textbf{MOSI}  & Master out, slave in, data transmission from a master to a slave. \\ 
\textbf{Transaction} & One instance of a master asserting a CS line, transferring data to and from a slave, and de-asserting the CS line. Transactions are atomic, which means they can never be interrupted by another transaction.\\
\textbf{SPI Transfer} & The whole process of an SPI master exchanging data with a slave. One SPI transfer consists of one or more SPI transactions.\\
\textbf{Single Transfer} & An SPI transfer that consists of only one transaction. \\
\textbf{CPU-Controlled Transfer}& A data transfer that happens between CPU configured buffer \hyperref[regdesc:SPIW0REG]{SPI\_W0\_REG}$\sim$\hyperref[regdesc:SPIW15REG]{SPI\_W15\_REG} (\hyperref[regdesc:LPSPIW0REG]{LP\_SPI\_W0\_REG}$\sim$\hyperref[regdesc:LPSPIW15REG]{LP\_SPI\_W15\_REG}) and SPI peripherals.\\
\textbf{DMA-Controlled Transfer}& A data transfer that happens between DMA and SPI peripherals, controlled by the DMA engine.\\
\textbf{Configurable Segmented Transfer}& A data transfer controlled by DMA when GP-SPI2 works as a master. Such transfer consists of multiple transactions (segments), and each of transaction can be configured independently.\\
\textbf{Slave Segmented Transfer} & A data transfer controlled by DMA when GP-SPI works as a slave. Such transfer consists of multiple transactions (segments).\\
\textbf{Full-duplex} & The sending line and receiving line between the master and the slave are independent. Sending data and receiving data happen at the same time. \\
\textbf{Half-duplex} & Only one side, the master or the slave, sends data first, and the other side receives data. Sending data and receiving data can not happen at the same time.\\
\textbf{4-line full-duplex} & 4-line here means: clock line, CS line, and two data lines. The two data lines can be used to send or receive data simultaneously.\\
\textbf{4-line half-duplex} & 4-line here means: clock line, CS line, and two data lines. The two data lines can not be used simultaneously.\\
\textbf{3-line half-duplex} & 3-line here means: clock line, CS line, and one data line. The data line is used to transmit or receive data. \\
\textbf{1-bit SPI} & In one clock cycle, one bit can be transferred.\\
\textbf{(2-bit) Dual SPI} & In one clock cycle, two bits can be transferred. \\
\textbf{Dual Output Read} & A data mode of Dual SPI. In one clock cycle, one bit of a command, or one bit of an address, or two bits of data can be transferred.\\
\textbf{Dual I/O Read} & Another data mode of Dual SPI. In one clock cycle, one bit of a command, or two bits of an address, or two bits of data can be transferred.\\
\textbf{(4-bit) Quad SPI} & In one clock cycle, four bits can be transferred. \\
\textbf{Quad Output Read} & A data mode of Quad SPI. In one clock cycle, one bit of a command, or one bit of an address, or four bits of data can be transferred.\\
\textbf{Quad I/O Read} & Another data mode of Quad SPI. In one clock cycle, one bit of a command, or four bits of an address, or four bits of data can be transferred.\\
\textbf{QPI} & In one clock cycle, four bits of a command, or four bits of an address, or four bits of data can be transferred.\\

\textbf{(8-bit) Octal SPI} & In one clock cycle, eight bits can be transferred. \\
\textbf{Octal Output Read} & A data mode of Octal SPI. In one clock cycle, one bit of a command, or one bit of an address, or eight bits of data can be transferred.\\
\textbf{Octal I/O Read} & Another data mode of Octal SPI. In one clock cycle, one bit of a command, or eight bits of an address, or eight bits of data can be transferred.\\
\textbf{OPI} & In one clock cycle, eight bits of a command, or eight bits of an address, or eight bits of data can be transferred.\\
\textbf{SPI2} & The prefix of the signals for GP-SPI2. SPI2 bus signals are routed to GPIO pins via HP GPIO matrix or HP IO MUX.\\
\textbf{SPI3} & The prefix of the signals for GP-SPI3. SPI3 bus signals are routed to GPIO pins via HP GPIO matrix only.\\
\textbf{LP\_SPI} & The prefix of the signals for LP-SPI. LP\_SPI bus signals are routed to GPIO pins via LP GPIO matrix only.
\end{longtable}
