
   \begin{longtable}[c]{|p{0.7cm}|p{1.9cm}|p{1.9cm}|p{1.7cm}|p{1.7cm}|p{1.7cm}|p{1cm}|p{1cm}|p{1.0cm}| }
   \caption{IO MUX Pin Functions}
    \label{tab:iomuxgpio-pin-functions} \\
        \hline
        \rowcolor{lightgray}
\textbf{Pin No.} & \textbf{Pin Name} & \textbf{Function 0} & \textbf{Function 1} & \textbf{Function 2} & \textbf{Function 3} & \textbf{DRV} & \textbf{Reset} & \textbf{Notes} \\
 \hline
\endfirsthead
        \hline
        \rowcolor{lightgray}
        \textbf{Pin No.} & \textbf{Pin Name} & \textbf{Function 0} & \textbf{Function 1} & \textbf{Function 2} & \textbf{Function 3} & \textbf{DRV} & \textbf{Reset} & \textbf{Notes} \\
        \hline
        \endhead
        \endfoot
4 & XTAL\_32K\_P     & GPIO0         & GPIO0   & -          & -            & 2           & 0 & R \\ \hline
5 & XTAL\_32K\_N     & GPIO1         & GPIO1   & -          & -            & 2           & 0 & R \\ \hline
6 & GPIO2            & GPIO2         & GPIO2   & FSPIQ      & -            & 2           & 1 & R \\ \hline
8 & GPIO3            & GPIO3         & GPIO3   & -          & -            & 2           & 1 & R \\ \hline
9 & MTMS             & MTMS          & GPIO4   & FSPIHD     & -            & 2           & 1 & R \\ \hline
10 & MTDI             & MTDI          & GPIO5   & FSPIWP     & -            & 2           & 1 & R \\ \hline
12 & MTCK             & MTCK          & GPIO6   & FSPICLK    & -            & 2           & 1* & G \\ \hline
13 & MTDO             & MTDO          & GPIO7   & FSPID      & -            & 2           & 1 & G \\ \hline
14 & GPIO8            & GPIO8         & GPIO8   & -          & -            & 2           & 1 & - \\ \hline
15 & GPIO9            & GPIO9         & GPIO9   & -          & -            & 2           & 3 & - \\ \hline
16 & GPIO10          &  GPIO10       & GPIO10  & FSPICS0    & -            & 2           & 1 & G \\ \hline
18 & VDD\_SPI        &  GPIO11       & GPIO11  & -          & -            & 2           & 0 & - \\ \hline
19 & SPIHD           &  SPIHD        & GPIO12  & -          & -            & 2           & 3 & - \\ \hline
20 & SPIWP           &  SPIWP        & GPIO13  & -          & -            & 2           & 3 & - \\ \hline
21 & SPICS0          &  SPICS0       & GPIO14  & -          & -            & 2           & 3 & - \\ \hline
22 & SPICLK          &  SPICLK       & GPIO15  & -          & -            & 2           & 3 & - \\ \hline
23 & SPID            &  SPID         & GPIO16  & -          & -            & 2           & 3 & - \\ \hline
24 & SPIQ            &  SPIQ         & GPIO17  & -          & -            & 2           & 3 & - \\ \hline
25 & GPIO18          &  GPIO18       & GPIO18  & -          & -            & 3           & 0 & USB, G \\ \hline
26 & GPIO19          &  GPIO19       & GPIO19  & -          & -            & 3           & 0* & USB \\ \hline
27 & U0RXD           &  U0RXD        & GPIO20  & -          & -            & 2           & 3 & G \\ \hline
28 & U0TXD           &  U0TXD        & GPIO21  & -          & -            & 2           & 4 & - \\ \hline

    \end{longtable}
\normalsize

\textbf{Drive Strength}

``DRV" column shows the drive strength of each pin after reset:

\begin{itemize}
    \item GPIO2, GPIO3, GPIO4, GPIO5, GPIO18, GPIO19
    \begin{itemize}
        \item \textbf{0} - Drive current = \verb+~+5 mA
        \item \textbf{1} - Drive current = \verb+~+20 mA
        \item \textbf{2} - Drive current = \verb+~+10 mA
        \item \textbf{3} - Drive current = \verb+~+40 mA
    \end{itemize}
    \item Other GPIOs
    \begin{itemize}
        \item \textbf{0} - Drive current = \verb+~+5 mA
        \item \textbf{1} - Drive current = \verb+~+10 mA
        \item \textbf{2} - Drive current = \verb+~+20 mA
        \item \textbf{3} - Drive current = \verb+~+40 mA
    \end{itemize}
\end{itemize}


\textbf{Reset Configurations}

``Reset" column shows the default configuration of each pin after reset:

\begin{itemize}
\item \textbf{0} - IE = 0 (input disabled)
\item \textbf{1} - IE = 1 (input enabled)
\item \textbf{2} - IE = 1, WPD = 1 (input enabled, pull-down resistor enabled)
\item \textbf{3} - IE = 1, WPU = 1 (input enabled, pull-up resistor enabled)
\item \textbf{4} - OE = 1, WPU = 1 (output enabled, pull-up resistor enabled)
\item \textbf{0*} - IE = 0, WPU = 0. The USB pull-up value of GPIO19 is 1 by default, therefore, the pin's pull-up resistor is enabled. For more information, see the note below.
\item \textbf{1*} - If eFuse bit EFUSE\_DIS\_PAD\_JTAG = 1, the pin MTCK is left floating after reset, i.e. IE = 1. If eFuse bit EFUSE\_DIS\_PAD\_JTAG = 0, the pin MTCK is connected to internal pull-up resistor, i.e. IE = 1, WPU = 1.  
\end{itemize}

\textbf{Note:}

\begin{itemize}
\item \textbf{R} - Pins in VDD3P3\_RTC domain, and part of them have analog functions, see Table \ref{tab:iomuxgpio-iomax-pins-analog-functions}.
\item \textbf{USB} - GPIO18 and GPIO19 are USB pins. The pull-up value of the two pins are controlled by the pins' pull-up value together with USB pull-up value. If any one of the pull-up value is 1, the pin's pull-up resistor will be enabled. The pull-up resistors of USB pins are controlled by USB\_SERIAL\_JTAG\_DP\_PULLUP. 
\item \textbf{G} - These pins have glitches during power-up. See details in Table \ref{tab:glitch}.
\end{itemize}
\begin{longtable}[c]{ | l | L{3cm} | r |  }
    \caption{Power-Up Glitches on Pins}
    \label{tab:glitch}\\\hline
    \rowcolor{lightgray}
                                           && \multicolumn{1}{c|}{\textbf{Typical Time Period}} \\
    \rowcolor{lightgray}
    \multirow{-2}{*}{\textbf{Pin}}    &
    \multirow{-2}{*}{\textbf{Glitch}}  & \multicolumn{1}{c|}{\textbf{(ns)}} \\\hline
    MTCK   & Low-level glitch & 5     \\ \hline
    MTDO   & Low-level glitch & 5     \\ \hline
    GPIO10 & Low-level glitch & 5     \\ \hline
    U0RXD  & Low-level glitch & 5     \\ \hline
    GPIO18 & High-level glitch    & 50000 \\ \hline 

\end{longtable}
