\begin{register}{H}{RTC\_CNTL\_OPTIONS0\_REG}{\hexprefix{}0000}\label{regdesc:RTCCNTLOPTIONS0REG}
\regfield{RTC\_CNTL\_SW\_SYS\_RST}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_NORST}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_RST}{1}{29}{{0}}%
\regfield{(reserved)}{15}{14}{000000000000000}%
\regfield{RTC\_CNTL\_XTL\_FORCE\_PU}{1}{13}{{1}}%
\regfield{RTC\_CNTL\_XTL\_FORCE\_PD}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_BBPLL\_FORCE\_PU}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_BBPLL\_FORCE\_PD}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PU}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PD}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_BB\_I2C\_FORCE\_PU}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_BB\_I2C\_FORCE\_PD}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_SW\_PROCPU\_RST}{1}{5}{{0}}%
\regfield{(reserved)}{1}{4}{0}%
\regfield{RTC\_CNTL\_SW\_STALL\_PROCPU\_C0}{2}{2}{{0}}%
\regfield{(reserved)}{2}{0}{00}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWSTALLPROCPUC0}\item [RTC\_CNTL\_SW\_STALL\_PROCPU\_C0] When \hyperref[fielddesc:RTCCNTLSWSTALLPROCPUC1]{RTC\_CNTL\_SW\_STALL\_PROCPU\_C1} is configured to \hexprefix{}21, setting this bit to \hexprefix{}2 stalls the CPU by SW.
\label{fielddesc:RTCCNTLSWPROCPURST}\item [RTC\_CNTL\_SW\_PROCPU\_RST] Set this bit to reset the CPU by SW. (WO)
\label{fielddesc:RTCCNTLBBI2CFORCEPD}\item [RTC\_CNTL\_BB\_I2C\_FORCE\_PD] Set this bit to FPD BB\_I2C. (R/W)
\label{fielddesc:RTCCNTLBBI2CFORCEPU}\item [RTC\_CNTL\_BB\_I2C\_FORCE\_PU] Set this bit to FPU BB\_I2C. (R/W)
\label{fielddesc:RTCCNTLBBPLLI2CFORCEPD}\item [RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PD] Set this bit to FPD BB\_PLL \_I2C. (R/W)
\label{fielddesc:RTCCNTLBBPLLI2CFORCEPU}\item [RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PU] Set this bit to FPU BB\_PLL \_I2C. (R/W)
\label{fielddesc:RTCCNTLBBPLLFORCEPD}\item [RTC\_CNTL\_BBPLL\_FORCE\_PD] Set this bit to FPD BB\_PLL. (R/W)
\label{fielddesc:RTCCNTLBBPLLFORCEPU}\item [RTC\_CNTL\_BBPLL\_FORCE\_PU] Set this bit to FPU BB\_PLL. (R/W)
\label{fielddesc:RTCCNTLXTLFORCEPD}\item [RTC\_CNTL\_XTL\_FORCE\_PD] Set this bit to FPD the crystal oscillator. (R/W)
\label{fielddesc:RTCCNTLXTLFORCEPU}\item [RTC\_CNTL\_XTL\_FORCE\_PU] Set this bit to FPU the crystal oscillator. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCERST}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_RST] Set this bit to force reset the digital system in deep-sleep. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCENORST}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_NORST] Set this bit to disable force reset to digital system in deep-sleep. (R/W)
\label{fielddesc:RTCCNTLSWSYSRST}\item [RTC\_CNTL\_SW\_SYS\_RST] Set this bit to reset the system via SW. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_OPTION1\_REG}{\hexprefix{}0128}\label{regdesc:RTCCNTLOPTION1REG}
\regfield{\tiny (reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{\tiny RTC\_CNTL\_FORCE\_DOWNLOAD\_BOOT}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLFORCEDOWNLOADBOOT}\item [RTC\_CNTL\_FORCE\_DOWNLOAD\_BOOT] Set this bit to force the chip to boot from the download mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLP\_TIMER0\_REG}{\hexprefix{}0004}\label{regdesc:RTCCNTLSLPTIMER0REG}
\regfield{RTC\_CNTL\_SLP\_VAL\_LO}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPVALLO}\item [RTC\_CNTL\_SLP\_VAL\_LO] Sets the lower 32 bits of the trigger threshold for the RTC timer. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLP\_TIMER1\_REG}{\hexprefix{}0008}\label{regdesc:RTCCNTLSLPTIMER1REG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{RTC\_CNTL\_RTC\_MAIN\_TIMER\_ALARM\_EN}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_SLP\_VAL\_HI}{16}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPVALHI}\item [RTC\_CNTL\_SLP\_VAL\_HI] Sets the higher 16 bits of the trigger threshold for the RTC timer. (R/W)
\label{fielddesc:RTCCNTLRTCMAINTIMERALARMEN}\item [RTC\_CNTL\_RTC\_MAIN\_TIMER\_ALARM\_EN] Sets this bit to enable the timer alarm. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIME\_UPDATE\_REG}{\hexprefix{}000C}\label{regdesc:RTCCNTLTIMEUPDATEREG}
\regfield{RTC\_CNTL\_RTC\_TIME\_UPDATE}{1}{31}{{0}}%
\regfield{(reserved)}{1}{30}{0}%
\regfield{RTC\_CNTL\_TIMER\_SYS\_RST}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_TIMER\_XTL\_OFF}{1}{28}{{0}}%
\regfield{RTC\_CNTL\_TIMER\_SYS\_STALL}{1}{27}{{0}}%
\regfield{(reserved)}{27}{0}{000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTIMERSYSSTALL}\item [RTC\_CNTL\_TIMER\_SYS\_STALL] Selects the triggering condition for the RTC timer. (R/W)
\label{fielddesc:RTCCNTLTIMERXTLOFF}\item [RTC\_CNTL\_TIMER\_XTL\_OFF] Selects the triggering condition for the RTC timer. (R/W)
\label{fielddesc:RTCCNTLTIMERSYSRST}\item [RTC\_CNTL\_TIMER\_SYS\_RST] Selects the triggering condition for the RTC timer. (R/W)
\label{fielddesc:RTCCNTLRTCTIMEUPDATE}\item [RTC\_CNTL\_RTC\_TIME\_UPDATE] Selects the triggering condition for the RTC timer. (WO)
\end{reglist}\end{regdesc}
\end{register}

\begin{tiplisting}
For details, please refer to Table \ref{table:Update RTC TIMER VALUE}.
\end{tiplisting}

\begin{register}{H}{RTC\_CNTL\_TIME\_LOW0\_REG}{\hexprefix{}0010}\label{regdesc:RTCCNTLTIMELOW0REG}
\regfield{RTC\_CNTL\_RTC\_TIMER\_VALUE0\_LOW}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCTIMERVALUE0LOW}\item [RTC\_CNTL\_RTC\_TIMER\_VALUE0\_LOW] Stores the lower 32 bits of RTC timer 0. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIME\_HIGH0\_REG}{\hexprefix{}0014}\label{regdesc:RTCCNTLTIMEHIGH0REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{RTC\_CNTL\_RTC\_TIMER\_VALUE0\_HIGH}{16}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCTIMERVALUE0HIGH}\item [RTC\_CNTL\_RTC\_TIMER\_VALUE0\_HIGH] Stores the higher 16 bits of RTC timer 0. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STATE0\_REG}{\hexprefix{}0018}\label{regdesc:RTCCNTLSTATE0REG}
\regfield{\tiny RTC\_CNTL\_SLEEP\_EN}{1}{31}{{0}}%
\regfield{\tiny RTC\_CNTL\_SLP\_REJECT}{1}{30}{{0}}%
\regfield{\tiny RTC\_CNTL\_SLP\_WAKEUP}{1}{29}{{0}}%
\regfield{\tiny (reserved)}{1}{28}{{0}}%
\regfield{\tiny (reserved)}{26}{2}{00000000000000000000000000}%
\regfield{\tiny RTC\_CNTL\_RTC\_SLP\_REJECT\_CAUSE\_CLR}{1}{1}{{0}}%
\regfield{\tiny RTC\_CNTL\_RTC\_SW\_CPU\_INT}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSWCPUINT}\item [RTC\_CNTL\_RTC\_SW\_CPU\_INT] Sends a SW RTC interrupt to CPU. (WO)
\label{fielddesc:RTCCNTLRTCSLPREJECTCAUSECLR}\item [RTC\_CNTL\_RTC\_SLP\_REJECT\_CAUSE\_CLR] Clears the RTC reject-to-sleep cause. (WO)
\label{fielddesc:RTCCNTLSLPWAKEUP}\item [RTC\_CNTL\_SLP\_WAKEUP] Sleep wakeup bit. (R/W)
\label{fielddesc:RTCCNTLSLPREJECT}\item [RTC\_CNTL\_SLP\_REJECT] Sleep reject bit. (R/W)
\label{fielddesc:RTCCNTLSLEEPEN}\item [RTC\_CNTL\_SLEEP\_EN] Sends the chip to sleep. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIMER1\_REG}{\hexprefix{}001C}\label{regdesc:RTCCNTLTIMER1REG}
\regfield{RTC\_CNTL\_PLL\_BUF\_WAIT}{8}{24}{{40}}%
\regfield{RTC\_CNTL\_XTL\_BUF\_WAIT}{10}{14}{{80}}%
\regfield{RTC\_CNTL\_CK8M\_WAIT}{8}{6}{{\hexprefix{}10}}%
\regfield{RTC\_CNTL\_CPU\_STALL\_WAIT}{5}{1}{{1}}%
\regfield{RTC\_CNTL\_CPU\_STALL\_EN}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLCPUSTALLEN}\item [RTC\_CNTL\_CPU\_STALL\_EN] Enables the CPU stalling. (R/W)
\label{fielddesc:RTCCNTLCPUSTALLWAIT}\item [RTC\_CNTL\_CPU\_STALL\_WAIT] Sets the CPU stall waiting cycles (using the RTC fast clock). (R/W)
\label{fielddesc:RTCCNTLCK8MWAIT}\item [RTC\_CNTL\_CK8M\_WAIT] Sets the 8 MHz clock waiting cycles (using the RTC slow clock). (R/W)
\label{fielddesc:RTCCNTLXTLBUFWAIT}\item [RTC\_CNTL\_XTL\_BUF\_WAIT] Sets the XTAL waiting cycles (using the RTC slow clock). (R/W)
\label{fielddesc:RTCCNTLPLLBUFWAIT}\item [RTC\_CNTL\_PLL\_BUF\_WAIT] Sets the PLL waiting cycles (using the RTC slow clock). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIMER2\_REG}{\hexprefix{}0020}\label{regdesc:RTCCNTLTIMER2REG}
\regfield{RTC\_CNTL\_MIN\_TIME\_CK8M\_OFF}{8}{24}{{\hexprefix{}1}}%
\regfield{RTC\_CNTL\_ULPCP\_TOUCH\_START\_WAIT}{9}{15}{{\hexprefix{}10}}%
\regfield{(reserved)}{15}{0}{000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLULPCPTOUCHSTARTWAIT}\item [RTC\_CNTL\_ULPCP\_TOUCH\_START\_WAIT] Sets the waiting cycles (using the RTC slow clock) before the ULP co-processor or touch controller starts to work. (R/W)
\label{fielddesc:RTCCNTLMINTIMECK8MOFF}\item [RTC\_CNTL\_MIN\_TIME\_CK8M\_OFF] Sets the minimal cycles for  8 MHz clock (using the RTC slow clock) when powered down. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIMER5\_REG}{\hexprefix{}002C}\label{regdesc:RTCCNTLTIMER5REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{RTC\_CNTL\_MIN\_SLP\_VAL}{8}{8}{{\hexprefix{}80}}%
\regfield{(reserved)}{8}{0}{00000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLMINSLPVAL}\item [RTC\_CNTL\_MIN\_SLP\_VAL] Sets the minimal sleep cycles (using the RTC slow clock). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIME\_LOW1\_REG}{\hexprefix{}00E8}\label{regdesc:RTCCNTLTIMELOW1REG}
\regfield{RTC\_CNTL\_RTC\_TIMER\_VALUE1\_LOW}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCTIMERVALUE1LOW}\item [RTC\_CNTL\_RTC\_TIMER\_VALUE1\_LOW] Stores the lower 32 bits of RTC timer 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIME\_HIGH1\_REG}{\hexprefix{}00EC}\label{regdesc:RTCCNTLTIMEHIGH1REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{RTC\_CNTL\_RTC\_TIMER\_VALUE1\_HIGH}{16}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCTIMERVALUE1HIGH}\item [RTC\_CNTL\_RTC\_TIMER\_VALUE1\_HIGH] Stores the higher 16 bits of RTC timer. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_ANA\_CONF\_REG}{\hexprefix{}0034}\label{regdesc:RTCCNTLANACONFREG}
\regfield{(reserved)}{7}{25}{0000000}%
\regfield{RTC\_CNTL\_PLLA\_FORCE\_PU}{1}{24}{{0}}%
\regfield{RTC\_CNTL\_PLLA\_FORCE\_PD}{1}{23}{{1}}%
\regfield{RTC\_CNTL\_SAR\_I2C\_FORCE\_PU}{1}{22}{{0}}%
\regfield{RTC\_CNTL\_SAR\_I2C\_FORCE\_PD}{1}{21}{{1}}%
\regfield{RTC\_CNTL\_GLITCH\_RST\_EN}{1}{20}{{0}}%
\regfield{(reserved)}{20}{0}{00000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLGLITCHRSTEN}\item [RTC\_CNTL\_GLITCH\_RST\_EN] Set this bit to enable a reset when the system detects a glitch. (R/W)
\label{fielddesc:RTCCNTLSARI2CFORCEPD}\item [RTC\_CNTL\_SAR\_I2C\_FORCE\_PD] Set this bit to FPD the SAR\_I2C. (R/W)
\label{fielddesc:RTCCNTLSARI2CFORCEPU}\item [RTC\_CNTL\_SAR\_I2C\_FORCE\_PU] Set this bit to FPU the SAR\_I2C. (R/W)
\label{fielddesc:RTCCNTLPLLAFORCEPD}\item [RTC\_CNTL\_PLLA\_FORCE\_PD] Set this bit to FPD the PLLA. (R/W)
\label{fielddesc:RTCCNTLPLLAFORCEPU}\item [RTC\_CNTL\_PLLA\_FORCE\_PU] Set this bit to FPU the PLLA. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_REG}{\hexprefix{}0084}\label{regdesc:RTCCNTLREG}
\regfield{RTC\_CNTL\_RTC\_REGULATOR\_FORCE\_PU}{1}{31}{{1}}%
\regfield{RTC\_CNTL\_RTC\_REGULATOR\_FORCE\_PD}{1}{30}{{0}}%
\regfield{(reserved)}{2}{28}{00}%
\regfield{RTC\_CNTL\_RTC\_DBIAS\_WAK}{3}{25}{{4}}%
\regfield{RTC\_CNTL\_RTC\_DBIAS\_SLP}{3}{22}{{4}}%
\regfield{RTC\_CNTL\_SCK\_DCAP}{8}{14}{{0}}%
\regfield{RTC\_CNTL\_DIG\_DBIAS\_WAK}{3}{11}{{4}}%
\regfield{RTC\_CNTL\_DIG\_DBIAS\_SLP}{3}{8}{{4}}%
\regfield{(reserved)}{8}{0}{00000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLDIGREGDBIASSLP}\item [RTC\_CNTL\_DIG\_DBIAS\_SLP] Configures the regulation factor for the digital system voltage regulator when the CPU is in sleep state. (R/W)
\label{fielddesc:RTCCNTLDIGREGDBIASWAK}\item [RTC\_CNTL\_DIG\_DBIAS\_WAK] Configures the regulation factor for the digital system voltage regulator when the CPU is in active status. (R/W)
\label{fielddesc:RTCCNTLSCKDCAP}\item [RTC\_CNTL\_SCK\_DCAP] Configures the frequency of the RTC clocks. (R/W)
\label{fielddesc:RTCCNTLRTCDBIASSLP}\item [RTC\_CNTL\_RTC\_DBIAS\_SLP] Configures the regulation factor for the low-power voltage regulator when the CPU is in sleep status. (R/W)
\label{fielddesc:RTCCNTLRTCDBIASWAK}\item [RTC\_CNTL\_RTC\_DBIAS\_WAK] Configures the regulation factor for the low-power voltage regulator when the CPU is in active status. (R/W)
\label{fielddesc:RTCCNTLRTCREGULATORFORCEPD}\item [RTC\_CNTL\_RTC\_REGULATOR\_FORCE\_PD] Set this bit to FPD the low-power voltage regulator, which means decreasing its voltage to 0.8 V or lower. (R/W)
\label{fielddesc:RTCCNTLRTCREGULATORFORCEPU}\item [RTC\_CNTL\_RTC\_REGULATOR\_FORCE\_PU] Set this bit to FPU the low-power voltage regulator, which means increasing its voltage to higher than 0.8 V. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_PWC\_REG}{\hexprefix{}0088}\label{regdesc:RTCCNTLPWCREG}
\regfield{\tiny (reserved)}{10}{22}{0000000000}%
\regfield{\tiny RTC\_CNTL\_RTC\_PAD\_FORCE\_HOLD}{1}{21}{{0}}%
\regfield{\tiny RTC\_CNTL\_RTC\_PD\_EN}{1}{20}{{0}}%
\regfield{\tiny RTC\_CNTL\_RTC\_FORCE\_PU}{1}{19}{{0}}%
\regfield{\tiny RTC\_CNTL\_RTC\_FORCE\_PD}{1}{18}{{0}}%
\regfield{\tiny RTC\_CNTL\_RTC\_SLOWMEM\_PD\_EN}{1}{17}{{0}}%
\regfield{\tiny RTC\_CNTL\_RTC\_SLOWMEM\_FORCE\_PU}{1}{16}{{1}}%
\regfield{\tiny RTC\_CNTL\_RTC\_SLOWMEM\_FORCE\_PD}{1}{15}{{0}}%
\regfield{\tiny RTC\_CNTL\_RTC\_FASTMEM\_PD\_EN}{1}{14}{{0}}%
\regfield{\tiny RTC\_CNTL\_RTC\_FASTMEM\_FORCE\_PU}{1}{13}{{1}}%
\regfield{\tiny RTC\_CNTL\_RTC\_FASTMEM\_FORCE\_PD}{1}{12}{{0}}%
\regfield{\tiny RTC\_CNTL\_RTC\_SLOWMEM\_FORCE\_LPU}{1}{11}{{1}}%
\regfield{\tiny RTC\_CNTL\_RTC\_SLOWMEM\_FORCE\_LPD}{1}{10}{{0}}%
\regfield{\tiny RTC\_CNTL\_RTC\_SLOWMEM\_FOLW\_CPU}{1}{9}{{0}}%
\regfield{\tiny RTC\_CNTL\_RTC\_FASTMEM\_FORCE\_LPU}{1}{8}{{1}}%
\regfield{\tiny RTC\_CNTL\_RTC\_FASTMEM\_FORCE\_LPD}{1}{7}{{0}}%
\regfield{\tiny RTC\_CNTL\_RTC\_FASTMEM\_FOLW\_CPU}{1}{6}{{0}}%
\regfield{\tiny RTC\_CNTL\_RTC\_FORCE\_NOISO}{1}{5}{{1}}%
\regfield{\tiny RTC\_CNTL\_RTC\_FORCE\_ISO}{1}{4}{{0}}%
\regfield{\tiny RTC\_CNTL\_RTC\_SLOWMEM\_FORCE\_ISO}{1}{3}{{0}}%
\regfield{\tiny RTC\_CNTL\_RTC\_SLOWMEM\_FORCE\_NOISO}{1}{2}{{1}}%
\regfield{\tiny RTC\_CNTL\_RTC\_FASTMEM\_FORCE\_ISO}{1}{1}{{0}}%
\regfield{\tiny RTC\_CNTL\_RTC\_FASTMEM\_FORCE\_NOISO}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCFASTMEMFORCENOISO}\item [RTC\_CNTL\_RTC\_FASTMEM\_FORCE\_NOISO] Set this bit to disable the force isolation of the RTC fast memory. (R/W)
\label{fielddesc:RTCCNTLRTCFASTMEMFORCEISO}\item [RTC\_CNTL\_RTC\_FASTMEM\_FORCE\_ISO] Set this bit to force isolation of the RTC fast memory. (R/W)
\label{fielddesc:RTCCNTLRTCSLOWMEMFORCENOISO}\item [RTC\_CNTL\_RTC\_SLOWMEM\_FORCE\_NOISO] Set this bit to disable the force isolation of the RTC slow memory. (R/W)
\label{fielddesc:RTCCNTLRTCSLOWMEMFORCEISO}\item [RTC\_CNTL\_RTC\_SLOWMEM\_FORCE\_ISO] Set this bit to force isolation of the RTC slow memory. (R/W)
\label{fielddesc:RTCCNTLRTCFORCEISO}\item [RTC\_CNTL\_RTC\_FORCE\_ISO] Set this bit to force isolation of the RTC peripherals. (R/W)
\label{fielddesc:RTCCNTLRTCFORCENOISO}\item [RTC\_CNTL\_RTC\_FORCE\_NOISO] Set this bit to disable the force isolation of the RTC peripherals. (R/W)
\label{fielddesc:RTCCNTLRTCFASTMEMFOLWCPU}\item [RTC\_CNTL\_RTC\_FASTMEM\_FOLW\_CPU] Set this bit to FPD the RTC fast memory when the CPU is powered down. Reset this bit to FPD the RTC fast memory when the RTC main state machine is powered down. (R/W)
\label{fielddesc:RTCCNTLRTCFASTMEMFORCELPD}\item [RTC\_CNTL\_RTC\_FASTMEM\_FORCE\_LPD] Set this bit to force not retain the RTC fast memory. (R/W)
\label{fielddesc:RTCCNTLRTCFASTMEMFORCELPU}\item [RTC\_CNTL\_RTC\_FASTMEM\_FORCE\_LPU] Set this bit to force retain the RTC fast memory. (R/W)
\label{fielddesc:RTCCNTLRTCSLOWMEMFOLWCPU}\item [RTC\_CNTL\_RTC\_SLOWMEM\_FOLW\_CPU] Set this bit to FPD the RTC slow memory when the CPU is powered down. Reset this bit to FPD the RTC slow memory when the RTC main state machine is powered down. (R/W)
\label{fielddesc:RTCCNTLRTCSLOWMEMFORCELPD}\item [RTC\_CNTL\_RTC\_SLOWMEM\_FORCE\_LPD] Set this bit to force not retain the RTC slow memory. (R/W)
\label{fielddesc:RTCCNTLRTCSLOWMEMFORCELPU}\item [RTC\_CNTL\_RTC\_SLOWMEM\_FORCE\_LPU] Set this bit to force retain the RTC slow memory. (R/W)
\label{fielddesc:RTCCNTLRTCFASTMEMFORCEPD}\item [RTC\_CNTL\_RTC\_FASTMEM\_FORCE\_PD] Set this bit to FPD the RTC fast memory. (R/W)
\label{fielddesc:RTCCNTLRTCFASTMEMFORCEPU}\item [RTC\_CNTL\_RTC\_FASTMEM\_FORCE\_PU] Set this bit to FPU the RTC fast memory. (R/W)
\label{fielddesc:RTCCNTLRTCFASTMEMPDEN}\item [RTC\_CNTL\_RTC\_FASTMEM\_PD\_EN] Set this bit to enable PD for the RTC fast memory in sleep. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_PWC\_REG}{\hexprefix{}0088}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:RTCCNTLRTCSLOWMEMFORCEPD}\item [RTC\_CNTL\_RTC\_SLOWMEM\_FORCE\_PD] Set this bit to FPD the RTC slow memory. (R/W)
\label{fielddesc:RTCCNTLRTCSLOWMEMFORCEPU}\item [RTC\_CNTL\_RTC\_SLOWMEM\_FORCE\_PU] Set this bit to FPU the RTC slow memory. (R/W)
\label{fielddesc:RTCCNTLRTCSLOWMEMPDEN}\item [RTC\_CNTL\_RTC\_SLOWMEM\_PD\_EN] Set this bit to enable PD for the RTC slow memory in sleep. (R/W)
\label{fielddesc:RTCCNTLRTCFORCEPD}\item [RTC\_CNTL\_RTC\_FORCE\_PD] Set this bit to FPD the RTC peripherals. (R/W)
\label{fielddesc:RTCCNTLRTCFORCEPU}\item [RTC\_CNTL\_RTC\_FORCE\_PU] Set this bit to FPU the RTC peripherals. (R/W)
\label{fielddesc:RTCCNTLRTCPDEN}\item [RTC\_CNTL\_RTC\_PD\_EN] Set this bit to enable PD for the RTC peripherals in sleep. (R/W)
\label{fielddesc:RTCCNTLRTCPADFORCEHOLD}\item [RTC\_CNTL\_RTC\_PAD\_FORCE\_HOLD] Set this bit the force hold the RTC GPIOs. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_DIG\_PWC\_REG}{\hexprefix{}008C}\label{regdesc:RTCCNTLDIGPWCREG}
\regfield{RTC\_CNTL\_DG\_WRAP\_PD\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_WIFI\_PD\_EN}{1}{30}{{0}}%
\regfield{(reserved)}{6}{24}{000000}%
\regfield{(reserved)}{1}{23}{{0}}%
\regfield{(reserved)}{1}{22}{{1}}%
\regfield{(reserved)}{1}{21}{{0}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_PU}{1}{20}{{1}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_PD}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_WIFI\_FORCE\_PU}{1}{18}{{1}}%
\regfield{RTC\_CNTL\_WIFI\_FORCE\_PD}{1}{17}{{0}}%
\regfield{(reserved)}{12}{5}{000000000000}%
\regfield{RTC\_CNTL\_LSLP\_MEM\_FORCE\_PU}{1}{4}{{1}}%
\regfield{RTC\_CNTL\_LSLP\_MEM\_FORCE\_PD}{1}{3}{{0}}%
\regfield{(reserved)}{3}{0}{000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLLSLPMEMFORCEPD}\item [RTC\_CNTL\_LSLP\_MEM\_FORCE\_PD] Set this bit to FPD the memories in the digital system in sleep. (R/W)
\label{fielddesc:RTCCNTLLSLPMEMFORCEPU}\item [RTC\_CNTL\_LSLP\_MEM\_FORCE\_PU] Set this bit to FPU the memories in the digital system. (R/W)
\label{fielddesc:RTCCNTLWIFIFORCEPD}\item [RTC\_CNTL\_WIFI\_FORCE\_PD] Set this bit to FPD the Wi-Fi digital circuit in the digital system. (R/W)
\label{fielddesc:RTCCNTLWIFIFORCEPU}\item [RTC\_CNTL\_WIFI\_FORCE\_PU] Set this bit to FPU the Wi-Fi digital circuit in the digital system. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCEPD}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_PD] Set this bit to FPD the digital system. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCEPU}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_PU] Set this bit to FPU the digital system. (R/W)
\label{fielddesc:RTCCNTLWIFIPDEN}\item [RTC\_CNTL\_WIFI\_PD\_EN] Set this bit to enable PD for the Wi-Fi digital circuit in sleep. (R/W)
\label{fielddesc:RTCCNTLDGWRAPPDEN}\item [RTC\_CNTL\_DG\_WRAP\_PD\_EN] Set this bit to enable PD for the digital system in sleep. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_DIG\_ISO\_REG}{\hexprefix{}0090}\label{regdesc:RTCCNTLDIGISOREG}
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_NOISO}{1}{31}{{1}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_ISO}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_WIFI\_FORCE\_NOISO}{1}{29}{{1}}%
\regfield{RTC\_CNTL\_WIFI\_FORCE\_ISO}{1}{28}{{0}}%
\regfield{(reserved)}{12}{16}{000000000000}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_HOLD}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_UNHOLD}{1}{14}{{1}}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_ISO}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_NOISO}{1}{12}{{1}}%
\regfield{RTC\_CNTL\_DG\_PAD\_AUTOHOLD\_EN}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_CLR\_DG\_PAD\_AUTOHOLD}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_DG\_PAD\_AUTOHOLD}{1}{9}{{0}}%
\regfield{(reserved)}{9}{0}{000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLDGPADAUTOHOLD}\item [RTC\_CNTL\_DG\_PAD\_AUTOHOLD] Indicates the auto-hold status of the digital GPIOs. (RO)
\label{fielddesc:RTCCNTLCLRDGPADAUTOHOLD}\item [RTC\_CNTL\_CLR\_DG\_PAD\_AUTOHOLD] Set this bit to clear the auto-hold enabler for the digital GPIOs. (WO)
\label{fielddesc:RTCCNTLDGPADAUTOHOLDEN}\item [RTC\_CNTL\_DG\_PAD\_AUTOHOLD\_EN] Set this bit to allow the digital GPIOs to enter the auto-hold status. (R/W)
\label{fielddesc:RTCCNTLDGPADFORCENOISO}\item [RTC\_CNTL\_DG\_PAD\_FORCE\_NOISO] Set this bit to disable the force isolation of the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLDGPADFORCEISO}\item [RTC\_CNTL\_DG\_PAD\_FORCE\_ISO] Set this bit to force isolation of the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLDGPADFORCEUNHOLD}\item [RTC\_CNTL\_DG\_PAD\_FORCE\_UNHOLD] Set this bit the force unhold the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLDGPADFORCEHOLD}\item [RTC\_CNTL\_DG\_PAD\_FORCE\_HOLD] Set this bit the force hold the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLWIFIFORCEISO}\item [RTC\_CNTL\_WIFI\_FORCE\_ISO] Set this bit to force isolation of the Wi-Fi digital circuits. (R/W)
\label{fielddesc:RTCCNTLWIFIFORCENOISO}\item [RTC\_CNTL\_WIFI\_FORCE\_NOISO] Set this bit to disable the force isolation of the Wi-Fi digital circuits. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCEISO}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_ISO] Set this bit to force isolation of the digital system. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCENOISO}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_NOISO] Set this bit to disable the force isolation of the digital system. (R/W)
\end{reglist}\end{regdesc}
\end{register}



\begin{register}{H}{RTC\_CNTL\_LOW\_POWER\_ST\_REG}{\hexprefix{}00CC}\label{regdesc:RTCCNTLLOWPOWERSTREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{RTC\_CNTL\_MAIN\_STATE\_IN\_IDEL}{1}{27}{{0}}%
\regfield{(reserved)}{7}{20}{0000000}%
\regfield{RTC\_CNTL\_RDY\_FOR\_WAKEUP}{1}{19}{{0}}%
\regfield{(reserved)}{19}{0}{0000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRDYFORWAKEUP}\item [RTC\_CNTL\_RDY\_FOR\_WAKEUP] Indicates the RTC is ready to be triggered by any wakeup source. (RO)
\label{fielddesc:RTCCNTLMAINSTATEINIDLE}\item [RTC\_CNTL\_MAIN\_STATE\_IN\_IDLE] Indicates the RTC state.
\begin{itemize}
    \item 0: the chip can be either
\begin{itemize}
    \item in sleep modes.
    \item entering sleep modes. In this case, wait until \hyperref[fielddesc:RTCCNTLRDYFORWAKEUP]{RTC\_CNTL\_RDY\_FOR\_WAKEUP} bit is set, then you can wake up the chip.
    \item exiting sleep mode. In this case, \hyperref[fielddesc:RTCCNTLMAINSTATEINIDLE]{RTC\_CNTL\_MAIN\_STATE\_IN\_IDLE} will eventually become 1.
\end{itemize}
    \item 1: the chip is not in sleep modes (i.e. running normally).
\end{itemize}
\end{reglist}\end{regdesc}
\end{register}



\begin{register}{H}{RTC\_CNTL\_RESET\_STATE\_REG}{\hexprefix{}0038}\label{regdesc:RTCCNTLRESETSTATEREG}
\regfield{(reserved)}{18}{14}{000000000000000000}%
\regfield{RTC\_CNTL\_PROCPU\_STAT\_VECTOR\_SEL}{1}{13}{{1}}%
\regfield{(reserved)}{7}{6}{0000000}%
\regfield{RTC\_CNTL\_RESET\_CAUSE\_PROCPU}{6}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRESETCAUSEPROCPU}\item [RTC\_CNTL\_RESET\_CAUSE\_PROCPU] Stores the CPU reset cause. (RO)
\label{fielddesc:RTCCNTLPROCPUSTATVECTORSEL}\item [RTC\_CNTL\_PROCPU\_STAT\_VECTOR\_SEL] Selects the CPU static vector. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WAKEUP\_STATE\_REG}{\hexprefix{}003C}\label{regdesc:RTCCNTLWAKEUPSTATEREG}
\regfield{RTC\_CNTL\_RTC\_WAKEUP\_ENA}{17}{15}{{12}}%
\regfield{(reserved)}{15}{0}{000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCWAKEUPENA}\item [RTC\_CNTL\_RTC\_WAKEUP\_ENA] Selects the wakeup source. For details, please refer to Table \ref{table:wakeup source}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_EXT\_WAKEUP\_CONF\_REG}{\hexprefix{}0064}\label{regdesc:RTCCNTLEXTWAKEUPCONFREG}
\regfield{RTC\_CNTL\_EXT\_WAKEUP1\_LV}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_EXT\_WAKEUP0\_LV}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_WAKEUP\_FILTER}{1}{29}{{0}}%
\regfield{(reserved)}{29}{0}{00000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLGPIOWAKEUPFILTER}\item [RTC\_CNTL\_GPIO\_WAKEUP\_FILTER] Set this bit to enable the GPIO wakeup event filter. (R/W)
\label{fielddesc:RTCCNTLEXTWAKEUP0LV}\item [RTC\_CNTL\_EXT\_WAKEUP0\_LV] 0: EXT0 at low level, 1: EXT0 at high level. (R/W)
\label{fielddesc:RTCCNTLEXTWAKEUP1LV}\item [RTC\_CNTL\_EXT\_WAKEUP1\_LV] 0: EXT1 at low level, 1: EXT1 at high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLP\_REJECT\_CONF\_REG}{\hexprefix{}0068}\label{regdesc:RTCCNTLSLPREJECTCONFREG}
\regfield{RTC\_CNTL\_DEEP\_SLP\_REJECT\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_LIGHT\_SLP\_REJECT\_EN}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SLEEP\_REJECT\_ENA}{17}{13}{{0}}%
\regfield{(reserved)}{13}{0}{0000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSLEEPREJECTENA}\item [RTC\_CNTL\_RTC\_SLEEP\_REJECT\_ENA] Set this bit to enable reject-to-sleep. (R/W)
\label{fielddesc:RTCCNTLLIGHTSLPREJECTEN}\item [RTC\_CNTL\_LIGHT\_SLP\_REJECT\_EN] Set this bit to enable reject-to-light-sleep. (R/W)
\label{fielddesc:RTCCNTLDEEPSLPREJECTEN}\item [RTC\_CNTL\_DEEP\_SLP\_REJECT\_EN] Set this bit to enable reject-to-deep-sleep. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_EXT\_WAKEUP1\_REG}{\hexprefix{}00DC}\label{regdesc:RTCCNTLEXTWAKEUP1REG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{RTC\_CNTL\_EXT\_WAKEUP1\_STATUS\_CLR}{1}{22}{{0}}%
\regfield{RTC\_CNTL\_EXT\_WAKEUP1\_SEL}{22}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLEXTWAKEUP1SEL}\item [RTC\_CNTL\_EXT\_WAKEUP1\_SEL] Selects a RTC GPIO to be the EXT1 wakeup source. (R/W)
\label{fielddesc:RTCCNTLEXTWAKEUP1STATUSCLR}\item [RTC\_CNTL\_EXT\_WAKEUP1\_STATUS\_CLR] Clears the EXT1 wakeup status. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_EXT\_WAKEUP1\_STATUS\_REG}{\hexprefix{}00E0}\label{regdesc:RTCCNTLEXTWAKEUP1STATUSREG}
\regfield{(reserved)}{10}{22}{0000000000}%
\regfield{RTC\_CNTL\_EXT\_WAKEUP1\_STATUS}{22}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLEXTWAKEUP1STATUS}\item [RTC\_CNTL\_EXT\_WAKEUP1\_STATUS] Indicates the EXT1 wakeup status. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLP\_REJECT\_CAUSE\_REG}{\hexprefix{}0124}\label{regdesc:RTCCNTLSLPREJECTCAUSEREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{RTC\_CNTL\_REJECT\_CAUSE}{17}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLREJECTCAUSE}\item [RTC\_CNTL\_REJECT\_CAUSE] Stores the reject-to-sleep cause. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLP\_WAKEUP\_CAUSE\_REG}{\hexprefix{}012C}\label{regdesc:RTCCNTLSLPWAKEUPCAUSEREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{RTC\_CNTL\_WAKEUP\_CAUSE}{17}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWAKEUPCAUSE}\item [RTC\_CNTL\_WAKEUP\_CAUSE] Stores the wakeup cause. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_ENA\_RTC\_REG}{\hexprefix{}0040}\label{regdesc:RTCCNTLINTENARTCREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_ENA}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_ENA}{1}{18}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_ENA}{1}{17}{{0}}%
\regfield{RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_ENA}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SWD\_INT\_ENA}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC2\_INT\_ENA}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_INT\_ENA}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TSENS\_INT\_ENA}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC1\_INT\_ENA}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_ENA}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_ENA}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_ENA}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_ENA}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_ENA}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_RTC\_ULP\_CP\_INT\_ENA}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_ENA}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_RTC\_WDT\_INT\_ENA}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_ENA}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTENA}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA] Enables interrupts when the chip wakes up from sleep. (R/W)
\label{fielddesc:RTCCNTLSLPREJECTINTENA}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_ENA] Enables interrupts when the chip rejects to go to sleep. (R/W)
\label{fielddesc:RTCCNTLRTCWDTINTENA}\item [RTC\_CNTL\_RTC\_WDT\_INT\_ENA] Enables the RTC watchdog interrupt. (R/W)
\label{fielddesc:RTCCNTLRTCTOUCHSCANDONEINTENA}\item [RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_ENA] Enables interrupts upon the completion of a touch scanning. (R/W)
\label{fielddesc:RTCCNTLRTCULPCPINTENA}\item [RTC\_CNTL\_RTC\_ULP\_CP\_INT\_ENA] Enables the ULP co-processor interrupt. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_INT\_ENA\_RTC\_REG}{\hexprefix{}0040}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:RTCCNTLRTCTOUCHDONEINTENA}\item [RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_ENA] Enables interrupts upon the completion of a single touch. (R/W)
\label{fielddesc:RTCCNTLRTCTOUCHACTIVEINTENA}\item [RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_ENA] Enables interrupts when a touch is detected. (R/W)
\label{fielddesc:RTCCNTLRTCTOUCHINACTIVEINTENA}\item [RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_ENA] Enables interrupts when a touch is released. (R/W)
\label{fielddesc:RTCCNTLRTCBROWNOUTINTENA}\item [RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_ENA] Enables the brownout interrupt. (R/W)
\label{fielddesc:RTCCNTLRTCMAINTIMERINTENA}\item [RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_ENA] Enables the RTC main timer interrupt. (R/W)
\label{fielddesc:RTCCNTLRTCSARADC1INTENA}\item [RTC\_CNTL\_RTC\_SARADC1\_INT\_ENA] Enables the SAR ADC 1 interrupt. (R/W)
\label{fielddesc:RTCCNTLRTCTSENSINTENA}\item [RTC\_CNTL\_RTC\_TSENS\_INT\_ENA] Enables the temperature sensor interrupt. (R/W)
\label{fielddesc:RTCCNTLRTCCOCPUINTENA}\item [RTC\_CNTL\_RTC\_COCPU\_INT\_ENA] Enables the ULP-RISCV interrupt. (R/W)
\label{fielddesc:RTCCNTLRTCSARADC2INTENA}\item [RTC\_CNTL\_RTC\_SARADC2\_INT\_ENA] Enables the SAR ADC 2 interrupt. (R/W)
\label{fielddesc:RTCCNTLRTCSWDINTENA}\item [RTC\_CNTL\_RTC\_SWD\_INT\_ENA] Enables the super watchdog interrupt. (R/W)
\label{fielddesc:RTCCNTLRTCXTAL32KDEADINTENA}\item [RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_ENA] Enables interrupts when the 32 kHz crystal is dead. (R/W)
\label{fielddesc:RTCCNTLRTCCOCPUTRAPINTENA}\item [RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_ENA] Enables interrupts when the ULP-RISCV is trapped. (R/W)
\label{fielddesc:RTCCNTLRTCTOUCHTIMEOUTINTENA}\item [RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_ENA] Enables interrupts when touch sensor times out. (R/W)
\label{fielddesc:RTCCNTLRTCGLITCHDETINTENA}\item [RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_ENA] Enables interrupts when a glitch is detected. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_INT\_RAW\_RTC\_REG}{\hexprefix{}0044}\label{regdesc:RTCCNTLINTRAWRTCREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_RAW}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_RAW}{1}{18}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_RAW}{1}{17}{{0}}%
\regfield{RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_RAW}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SWD\_INT\_RAW}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC2\_INT\_RAW}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_INT\_RAW}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TSENS\_INT\_RAW}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC1\_INT\_RAW}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_RAW}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_RAW}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_RAW}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_RAW}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_RAW}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_RTC\_ULP\_CP\_INT\_RAW}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_RAW}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_RTC\_WDT\_INT\_RAW}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_RAW}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTRAW}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_RAW] Stores the raw interrupt triggered when the chip wakes up from sleep. (RO)
\label{fielddesc:RTCCNTLSLPREJECTINTRAW}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_RAW] Stores the raw interrupt triggered when the chip rejects to go to sleep. (RO)
\label{fielddesc:RTCCNTLRTCWDTINTRAW}\item [RTC\_CNTL\_RTC\_WDT\_INT\_RAW] Stores the raw RTC watchdog interrupt. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHSCANDONEINTRAW}\item [RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_RAW] Stores the raw interrupt triggered upon the completion of a touch scanning. (RO)
\label{fielddesc:RTCCNTLRTCULPCPINTRAW}\item [RTC\_CNTL\_RTC\_ULP\_CP\_INT\_RAW] Stores the raw ULP co-processor interrupt. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHDONEINTRAW}\item [RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_RAW] Stores the raw interrupt triggered upon the completion of a single touch. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHACTIVEINTRAW}\item [RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_RAW] Stores the raw interrupt triggered when a touch is detected. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHINACTIVEINTRAW}\item [RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_RAW] Stores the raw interrupt triggered when a touch is released. (RO)
\label{fielddesc:RTCCNTLRTCBROWNOUTINTRAW}\item [RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_RAW] Stores the raw brownout interrupt. (RO)
\label{fielddesc:RTCCNTLRTCMAINTIMERINTRAW}\item [RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_RAW] Stores the raw RTC main timer interrupt. (RO)
\label{fielddesc:RTCCNTLRTCSARADC1INTRAW}\item [RTC\_CNTL\_RTC\_SARADC1\_INT\_RAW] Stores the raw SAR ADC 1 interrupt. (RO)
\label{fielddesc:RTCCNTLRTCTSENSINTRAW}\item [RTC\_CNTL\_RTC\_TSENS\_INT\_RAW] Stores the raw temperature sensor interrupt. (RO)
\label{fielddesc:RTCCNTLRTCCOCPUINTRAW}\item [RTC\_CNTL\_RTC\_COCPU\_INT\_RAW] Stores the raw ULP-RISCV interrupt. (RO)
\label{fielddesc:RTCCNTLRTCSARADC2INTRAW}\item [RTC\_CNTL\_RTC\_SARADC2\_INT\_RAW] Stores the raw SAR ADC 2 interrupt. (RO)
\label{fielddesc:RTCCNTLRTCSWDINTRAW}\item [RTC\_CNTL\_RTC\_SWD\_INT\_RAW] Stores the raw super watchdog interrupt. (RO)
\label{fielddesc:RTCCNTLRTCXTAL32KDEADINTRAW}\item [RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_RAW] Stores the raw interrupt triggered when the 32 kHz crystal is dead. (RO)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_INT\_RAW\_RTC\_REG}{\hexprefix{}0044}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]


\label{fielddesc:RTCCNTLRTCCOCPUTRAPINTRAW}\item [RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_RAW] Stores the raw interrupt triggered when the ULP-RISCV is trapped. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHTIMEOUTINTRAW}\item [RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_RAW] Stores the raw interrupt triggered when touch sensor times out. (RO)
\label{fielddesc:RTCCNTLRTCGLITCHDETINTRAW}\item [RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_RAW] Stores the raw interrupt triggered when a glitch is detected. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_ST\_RTC\_REG}{\hexprefix{}0048}\label{regdesc:RTCCNTLINTSTRTCREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_ST}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_ST}{1}{18}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_ST}{1}{17}{{0}}%
\regfield{RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_ST}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SWD\_INT\_ST}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC2\_INT\_ST}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_INT\_ST}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TSENS\_INT\_ST}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC1\_INT\_ST}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_ST}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_ST}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_ST}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_ST}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_ST}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_RTC\_ULP\_CP\_INT\_ST}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_ST}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_RTC\_WDT\_INT\_ST}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_ST}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTST}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_ST] Stores the status of the interrupt triggered when the chip wakes up from sleep. (RO)
\label{fielddesc:RTCCNTLSLPREJECTINTST}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_ST] Stores the status of the interrupt triggered when the chip rejects to go to sleep. (RO)
\label{fielddesc:RTCCNTLRTCWDTINTST}\item [RTC\_CNTL\_RTC\_WDT\_INT\_ST] Stores the status of the RTC watchdog interrupt. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHSCANDONEINTST}\item [RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_ST] Stores the status of the interrupt triggered upon the completion of a touch scanning. (RO)
\label{fielddesc:RTCCNTLRTCULPCPINTST}\item [RTC\_CNTL\_RTC\_ULP\_CP\_INT\_ST] Stores the status of the ULP co-processor interrupt. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHDONEINTST}\item [RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_ST] Stores the status of the interrupt triggered upon the completion of a single touch. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHACTIVEINTST}\item [RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_ST] Stores the status of the interrupt triggered when a touch is detected. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHINACTIVEINTST}\item [RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_ST] Stores the status of the interrupt triggered when a touch is released. (RO)
\label{fielddesc:RTCCNTLRTCBROWNOUTINTST}\item [RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_ST] Stores the status of the brownout interrupt. (RO)
\label{fielddesc:RTCCNTLRTCMAINTIMERINTST}\item [RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_ST] Stores the status of the RTC main timer interrupt. (RO)
\label{fielddesc:RTCCNTLRTCSARADC1INTST}\item [RTC\_CNTL\_RTC\_SARADC1\_INT\_ST] Stores the status of the SAR ADC 1 interrupt. (RO)
\label{fielddesc:RTCCNTLRTCTSENSINTST}\item [RTC\_CNTL\_RTC\_TSENS\_INT\_ST] Stores the status of the temperature sensor interrupt. (RO)
\label{fielddesc:RTCCNTLRTCCOCPUINTST}\item [RTC\_CNTL\_RTC\_COCPU\_INT\_ST] Stores the status of the ULP-RISCV interrupt. (RO)
\label{fielddesc:RTCCNTLRTCSARADC2INTST}\item [RTC\_CNTL\_RTC\_SARADC2\_INT\_ST] Stores the status of the SAR ADC 2 interrupt. (RO)
\label{fielddesc:RTCCNTLRTCSWDINTST}\item [RTC\_CNTL\_RTC\_SWD\_INT\_ST] Stores the status of the super watchdog interrupt. (RO)
\label{fielddesc:RTCCNTLRTCXTAL32KDEADINTST}\item [RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_ST] Stores the status of the interrupt triggered when the 32 kHz crystal is dead. (RO)


\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_INT\_ST\_RTC\_REG}{\hexprefix{}0048}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:RTCCNTLRTCCOCPUTRAPINTST}\item [RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_ST] Stores the status of the interrupt triggered when the ULP-RISCV is trapped. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHTIMEOUTINTST}\item [RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_ST] Stores the status of the interrupt triggered when touch sensor times out. (RO)
\label{fielddesc:RTCCNTLRTCGLITCHDETINTST}\item [RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_ST] Stores the status of the interrupt triggered when a glitch is detected. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_CLR\_RTC\_REG}{\hexprefix{}004C}\label{regdesc:RTCCNTLINTCLRRTCREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_CLR}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_CLR}{1}{18}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_CLR}{1}{17}{{0}}%
\regfield{RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_CLR}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SWD\_INT\_CLR}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC2\_INT\_CLR}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_INT\_CLR}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TSENS\_INT\_CLR}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC1\_INT\_CLR}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_CLR}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_CLR}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_CLR}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_CLR}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_CLR}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_RTC\_ULP\_CP\_INT\_CLR}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_CLR}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_RTC\_WDT\_INT\_CLR}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_CLR}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTCLR}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_CLR] Clears the interrupt triggered when the chip wakes up from sleep. (WO)
\label{fielddesc:RTCCNTLSLPREJECTINTCLR}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_CLR] Clears the interrupt triggered when the chip rejects to go to sleep. (WO)
\label{fielddesc:RTCCNTLRTCWDTINTCLR}\item [RTC\_CNTL\_RTC\_WDT\_INT\_CLR] Clears the RTC watchdog interrupt. (WO)
\label{fielddesc:RTCCNTLRTCTOUCHSCANDONEINTCLR}\item [RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_CLR] Clears the interrupt triggered upon the completion of a touch scanning. (WO)
\label{fielddesc:RTCCNTLRTCULPCPINTCLR}\item [RTC\_CNTL\_RTC\_ULP\_CP\_INT\_CLR] Clears the ULP co-processor interrupt. (WO)
\label{fielddesc:RTCCNTLRTCTOUCHDONEINTCLR}\item [RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_CLR] Clears the interrupt triggered upon the completion of a single touch. (WO)
\label{fielddesc:RTCCNTLRTCTOUCHACTIVEINTCLR}\item [RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_CLR] Clears the interrupt triggered when a touch is detected. (WO)
\label{fielddesc:RTCCNTLRTCTOUCHINACTIVEINTCLR}\item [RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_CLR] Clears the interrupt triggered when a touch is released. (WO)
\label{fielddesc:RTCCNTLRTCBROWNOUTINTCLR}\item [RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_CLR] Clears the brownout interrupt. (WO)
\label{fielddesc:RTCCNTLRTCMAINTIMERINTCLR}\item [RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_CLR] Clears the RTC main timer interrupt. (WO)
\label{fielddesc:RTCCNTLRTCSARADC1INTCLR}\item [RTC\_CNTL\_RTC\_SARADC1\_INT\_CLR] Clears the SAR ADC 1 interrupt. (WO)
\label{fielddesc:RTCCNTLRTCTSENSINTCLR}\item [RTC\_CNTL\_RTC\_TSENS\_INT\_CLR] Clears the temperature sensor interrupt. (WO)
\label{fielddesc:RTCCNTLRTCCOCPUINTCLR}\item [RTC\_CNTL\_RTC\_COCPU\_INT\_CLR] Clears the ULP-RISCV interrupt. (WO)
\label{fielddesc:RTCCNTLRTCSARADC2INTCLR}\item [RTC\_CNTL\_RTC\_SARADC2\_INT\_CLR] Clears the SAR ADC 2 interrupt. (WO)
\label{fielddesc:RTCCNTLRTCSWDINTCLR}\item [RTC\_CNTL\_RTC\_SWD\_INT\_CLR] Clears the super watchdog interrupt. (WO)
\label{fielddesc:RTCCNTLRTCXTAL32KDEADINTCLR}\item [RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_CLR] Clears the interrupt triggered when the 32 kHz crystal is dead. (WO)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_INT\_CLR\_RTC\_REG}{\hexprefix{}004C}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]


\label{fielddesc:RTCCNTLRTCCOCPUTRAPINTCLR}\item [RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_CLR] Clears the interrupt triggered when the ULP-RISCV is trapped. (WO)
\label{fielddesc:RTCCNTLRTCTOUCHTIMEOUTINTCLR}\item [RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_CLR] Clears the interrupt triggered when touch sensor times out. (WO)
\label{fielddesc:RTCCNTLRTCGLITCHDETINTCLR}\item [RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_CLR] Clears the interrupt triggered when a glitch is detected. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE0\_REG}{\hexprefix{}0050}\label{regdesc:RTCCNTLSTORE0REG}
\regfield{RTC\_CNTL\_RTC\_SCRATCH0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSCRATCH0}\item [RTC\_CNTL\_RTC\_SCRATCH0] Reservation register 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE1\_REG}{\hexprefix{}0054}\label{regdesc:RTCCNTLSTORE1REG}
\regfield{RTC\_CNTL\_RTC\_SCRATCH1}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSCRATCH1}\item [RTC\_CNTL\_RTC\_SCRATCH1] Reservation register 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE2\_REG}{\hexprefix{}0058}\label{regdesc:RTCCNTLSTORE2REG}
\regfield{RTC\_CNTL\_RTC\_SCRATCH2}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSCRATCH2}\item [RTC\_CNTL\_RTC\_SCRATCH2] Reservation register 2. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE3\_REG}{\hexprefix{}005C}\label{regdesc:RTCCNTLSTORE3REG}
\regfield{RTC\_CNTL\_RTC\_SCRATCH3}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSCRATCH3}\item [RTC\_CNTL\_RTC\_SCRATCH3] Reservation register 3. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE4\_REG}{\hexprefix{}00BC}\label{regdesc:RTCCNTLSTORE4REG}
\regfield{RTC\_CNTL\_RTC\_SCRATCH4}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSCRATCH4}\item [RTC\_CNTL\_RTC\_SCRATCH4] Reservation register 4. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE5\_REG}{\hexprefix{}00C0}\label{regdesc:RTCCNTLSTORE5REG}
\regfield{RTC\_CNTL\_RTC\_SCRATCH5}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSCRATCH5}\item [RTC\_CNTL\_RTC\_SCRATCH5] Reservation register 5. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE6\_REG}{\hexprefix{}00C4}\label{regdesc:RTCCNTLSTORE6REG}
\regfield{RTC\_CNTL\_RTC\_SCRATCH6}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSCRATCH6}\item [RTC\_CNTL\_RTC\_SCRATCH6] Reservation register 6. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE7\_REG}{\hexprefix{}00C8}\label{regdesc:RTCCNTLSTORE7REG}
\regfield{RTC\_CNTL\_RTC\_SCRATCH7}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSCRATCH7}\item [RTC\_CNTL\_RTC\_SCRATCH7] Reservation register 7. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_EXT\_XTL\_CONF\_REG}{\hexprefix{}0060}\label{regdesc:RTCCNTLEXTXTLCONFREG}
\regfield{RTC\_CNTL\_XTL\_EXT\_CTR\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_XTL\_EXT\_CTR\_LV}{1}{30}{{0}}%
\regfield{(reserved)}{6}{24}{000000}%
\regfield{RTC\_CNTL\_RTC\_XTAL32K\_GPIO\_SEL}{1}{23}{{0}}%
\regfield{RTC\_CNTL\_RTC\_WDT\_STATE}{3}{20}{{\hexprefix{}0}}%
\regfield{(reserved)}{11}{9}{00000000000}%
\regfield{RTC\_CNTL\_ENCKINIT\_XTAL\_32K}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_XPD\_FORCE}{1}{7}{{1}}%
\regfield{RTC\_CNTL\_XTAL32K\_AUTO\_RETURN}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_AUTO\_RESTART}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_AUTO\_BACKUP}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_EXT\_CLK\_FO}{1}{3}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_WDT\_RESET}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_WDT\_CLK\_FO}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_WDT\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLXTAL32KWDTEN}\item [RTC\_CNTL\_XTAL32K\_WDT\_EN] Set this bit to enable the 32 kHz crystal watchdog. (R/W)
\label{fielddesc:RTCCNTLXTAL32KWDTCLKFO}\item [RTC\_CNTL\_XTAL32K\_WDT\_CLK\_FO] Set this bit to FPU the 32 kHz crystal watchdog clock. (R/W)
\label{fielddesc:RTCCNTLXTAL32KWDTRESET}\item [RTC\_CNTL\_XTAL32K\_WDT\_RESET] Set this bit to reset the 32 kHz crystal watchdog by SW. (R/W)
\label{fielddesc:RTCCNTLXTAL32KEXTCLKFO}\item [RTC\_CNTL\_XTAL32K\_EXT\_CLK\_FO] Set this bit to FPU the external clock of 32 kHz crystal. (R/W)
\label{fielddesc:RTCCNTLXTAL32KAUTOBACKUP}\item [RTC\_CNTL\_XTAL32K\_AUTO\_BACKUP] Set this bit to switch to the backup clock when the 32 kHz crystal is dead. (R/W)
\label{fielddesc:RTCCNTLXTAL32KAUTORESTART}\item [RTC\_CNTL\_XTAL32K\_AUTO\_RESTART] Set this bit to restart the 32 kHz crystal automatically when the 32 kHz crystal is dead. (R/W)
\label{fielddesc:RTCCNTLXTAL32KAUTORETURN}\item [RTC\_CNTL\_XTAL32K\_AUTO\_RETURN] Set this bit to switch back to 32 kHz crystal when the 32 kHz crystal is restarted. (R/W)
\label{fielddesc:RTCCNTLXTAL32KXPDFORCE}\item [RTC\_CNTL\_XTAL32K\_XPD\_FORCE] Set this bit to allow the software to FPD the 32 kHz crystal; Reset this bit to allow the FSM to FPD the 32 kHz crystal. (R/W)
\label{fielddesc:RTCCNTLENCKINITXTAL32K}\item [RTC\_CNTL\_ENCKINIT\_XTAL\_32K] Set this bit to apply an internal clock to help the 32 kHz crystal to start. (R/W)
\label{fielddesc:RTCCNTLRTCWDTSTATE}\item [RTC\_CNTL\_RTC\_WDT\_STATE] Stores the status of the 32 kHz watchdog. (RO)
\label{fielddesc:RTCCNTLRTCXTAL32KGPIOSEL}\item [RTC\_CNTL\_RTC\_XTAL32K\_GPIO\_SEL] Selects the 32 kHz crystal clock. 0: selects the external 32 kHz clock; 1: selects clock from the RTC GPIO X32P\_C. (R/W)
\label{fielddesc:RTCCNTLXTLEXTCTRLV}\item [RTC\_CNTL\_XTL\_EXT\_CTR\_LV] 0: powers down XTAL at high level; 1: powers down XTAL at low level. (R/W)
\label{fielddesc:RTCCNTLXTLEXTCTREN}\item [RTC\_CNTL\_XTL\_EXT\_CTR\_EN] Enables the GPIO to power down the crystal oscillator. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_CLK\_CONF\_REG}{\hexprefix{}0074}\label{regdesc:RTCCNTLCLKCONFREG}
\regfield{RTC\_CNTL\_ANA\_CLK\_RTC\_SEL}{2}{30}{{0}}%
\regfield{RTC\_CNTL\_FAST\_CLK\_RTC\_SEL}{1}{29}{{0}}%
\regfield{(reserved)}{2}{27}{00}%
\regfield{RTC\_CNTL\_CK8M\_FORCE\_PU}{1}{26}{{0}}%
\regfield{RTC\_CNTL\_CK8M\_FORCE\_PD}{1}{25}{{0}}%
\regfield{(reserved)}{8}{17}{00000000}%
\regfield{RTC\_CNTL\_CK8M\_FORCE\_NOGATING}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_XTAL\_FORCE\_NOGATING}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_CK8M\_DIV\_SEL}{3}{12}{{3}}%
\regfield{(reserved)}{1}{11}{0}%
\regfield{RTC\_CNTL\_DIG\_CLK8M\_EN}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_DIG\_CLK8M\_D256\_EN}{1}{9}{{1}}%
\regfield{RTC\_CNTL\_DIG\_XTAL32K\_EN}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_ENB\_CK8M\_DIV}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_ENB\_CK8M}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_CK8M\_DIV}{2}{4}{{1}}%
\regfield{RTC\_CNTL\_CK8M\_DIV\_SEL\_VLD}{1}{3}{{1}}%
\regfield{(reserved)}{3}{0}{000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLCK8MDIVSELVLD}\item [RTC\_CNTL\_CK8M\_DIV\_SEL\_VLD] Synchronizes the reg\_ck8m\_div\_sel. Note that you have to invalidate the bus before modifying the frequency divider, and then validate the new divider clock. (R/W)
\label{fielddesc:RTCCNTLCK8MDIV}\item [RTC\_CNTL\_CK8M\_DIV] Set the CK8M\_D256\_OUT divider. 00: divided by 128, 01: divided by 256, 10: divided by 512, 11: divided by 1024. (R/W)
\label{fielddesc:RTCCNTLENBCK8M}\item [RTC\_CNTL\_ENB\_CK8M] Set this bit to disable CK8M and CK8M\_D256\_OUT. (R/W)
\label{fielddesc:RTCCNTLENBCK8MDIV}\item [RTC\_CNTL\_ENB\_CK8M\_DIV] Selects the CK8M\_D256\_OUT. 1: CK8M, 0: CK8M divided by 256. (R/W)
\label{fielddesc:RTCCNTLDIGXTAL32KEN}\item [RTC\_CNTL\_DIG\_XTAL32K\_EN] Set this bit to enable CK\_XTAL\_32K clock for the digital core. (R/W)
\label{fielddesc:RTCCNTLDIGCLK8MD256EN}\item [RTC\_CNTL\_DIG\_CLK8M\_D256\_EN] Set this bit to enable CK8M\_D256\_OUT clock for the digital core. (R/W)
\label{fielddesc:RTCCNTLDIGCLK8MEN}\item [RTC\_CNTL\_DIG\_CLK8M\_EN] Set this bit to enable 8 MHz clock for the digital core. (R/W)
\label{fielddesc:RTCCNTLCK8MDIVSEL}\item [RTC\_CNTL\_CK8M\_DIV\_SEL] Stores the 8 MHz divider, which is reg\_ck8m\_div\_sel + 1. (R/W)
\label{fielddesc:RTCCNTLXTALFORCENOGATING}\item [RTC\_CNTL\_XTAL\_FORCE\_NOGATING] Set this bit to force no gating to crystal during sleep. (R/W)
\label{fielddesc:RTCCNTLCK8MFORCENOGATING}\item [RTC\_CNTL\_CK8M\_FORCE\_NOGATING] Set this bit to disable force gating to 8 MHz crystal during sleep. (R/W)
\label{fielddesc:RTCCNTLCK8MFORCEPD}\item [RTC\_CNTL\_CK8M\_FORCE\_PD] Set this bit to FPD the 8 MHz clock. (R/W)
\label{fielddesc:RTCCNTLCK8MFORCEPU}\item [RTC\_CNTL\_CK8M\_FORCE\_PU] Set this bit to FPU the 8 MHz clock. (R/W)
\label{fielddesc:RTCCNTLFASTCLKRTCSEL}\item [RTC\_CNTL\_FAST\_CLK\_RTC\_SEL] Set this bit to select the RTC fast clock. 0: XTAL\_DIV\_CLK, 1: RC\_FAST\_CLK. (R/W)
\label{fielddesc:RTCCNTLANACLKRTCSEL}\item [RTC\_CNTL\_ANA\_CLK\_RTC\_SEL] Set this bit to select the RTC slow clock. 0: RC\_SLOW\_CLK, 1: XTAL32K\_CLK, 2: RC\_FAST\_DIV\_CLK. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLOW\_CLK\_CONF\_REG}{\hexprefix{}0078}\label{regdesc:RTCCNTLSLOWCLKCONFREG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{RTC\_CNTL\_RTC\_ANA\_CLK\_DIV}{8}{23}{{0}}%
\regfield{RTC\_CNTL\_RTC\_ANA\_CLK\_DIV\_VLD}{1}{22}{{1}}%
\regfield{(reserved)}{22}{0}{0000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCANACLKDIVVLD}\item [RTC\_CNTL\_RTC\_ANA\_CLK\_DIV\_VLD] Synchronizes the reg\_rtc\_ana\_clk\_div. Note that you have to invalidate the bus before modifying the frequency divider, and then validate the new divider clock. (R/W)

\label{fielddesc:RTCCNTLRTCANACLKDIV}\item [RTC\_CNTL\_RTC\_ANA\_CLK\_DIV] Set the divider for the RTC clock. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_XTAL32K\_CLK\_FACTOR\_REG}{\hexprefix{}00F0}\label{regdesc:RTCCNTLXTAL32KCLKFACTORREG}
\regfield{RTC\_CNTL\_XTAL32K\_CLK\_FACTOR}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLXTAL32KCLKFACTOR}\item [RTC\_CNTL\_XTAL32K\_CLK\_FACTOR] Configures the divider factor for the 32 kHz crystal oscillator. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_XTAL32K\_CONF\_REG}{\hexprefix{}00F4}\label{regdesc:RTCCNTLXTAL32KCONFREG}
\regfield{RTC\_CNTL\_XTAL32K\_STABLE\_THRES}{4}{28}{{\hexprefix{}0}}%
\regfield{RTC\_CNTL\_XTAL32K\_WDT\_TIMEOUT}{8}{20}{{\hexprefix{}ff}}%
\regfield{RTC\_CNTL\_XTAL32K\_RESTART\_WAIT}{16}{4}{{\hexprefix{}00}}%
\regfield{RTC\_CNTL\_XTAL32K\_RETURN\_WAIT}{4}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLXTAL32KRETURNWAIT}\item [RTC\_CNTL\_XTAL32K\_RETURN\_WAIT] Defines the waiting cycles before returning to the normal 32 kHz crystal oscillator. (R/W)
\label{fielddesc:RTCCNTLXTAL32KRESTARTWAIT}\item [RTC\_CNTL\_XTAL32K\_RESTART\_WAIT] Defines the waiting cycles before restarting the 32 kHz crystal oscillator. (R/W)
\label{fielddesc:RTCCNTLXTAL32KWDTTIMEOUT}\item [RTC\_CNTL\_XTAL32K\_WDT\_TIMEOUT] Defines the waiting period for clock detection. If no clock is detected after this period, the 32 kHz crystal oscillator can be regarded as dead. (R/W)
\label{fielddesc:RTCCNTLXTAL32KSTABLETHRES}\item [RTC\_CNTL\_XTAL32K\_STABLE\_THRES] Defines the allowed restarting period, within which the 32 kHz crystal oscillator can be regarded as stable. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTCONFIG0\_REG}{\hexprefix{}0094}\label{regdesc:RTCCNTLWDTCONFIG0REG}
\regfield{RTC\_CNTL\_WDT\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_WDT\_STG0}{3}{28}{{\hexprefix{}0}}%
\regfield{RTC\_CNTL\_WDT\_STG1}{3}{25}{{\hexprefix{}0}}%
\regfield{RTC\_CNTL\_WDT\_STG2}{3}{22}{{\hexprefix{}0}}%
\regfield{RTC\_CNTL\_WDT\_STG3}{3}{19}{{\hexprefix{}0}}%
\regfield{RTC\_CNTL\_WDT\_CPU\_RESET\_LENGTH}{3}{16}{{\hexprefix{}1}}%
\regfield{RTC\_CNTL\_WDT\_SYS\_RESET\_LENGTH}{3}{13}{{\hexprefix{}1}}%
\regfield{RTC\_CNTL\_WDT\_FLASHBOOT\_MOD\_EN}{1}{12}{{1}}%
\regfield{RTC\_CNTL\_WDT\_PROCPU\_RESET\_EN}{1}{11}{{0}}%
\regfield{(reserved)}{1}{10}{0}%
\regfield{RTC\_CNTL\_WDT\_PAUSE\_IN\_SLP}{1}{9}{{1}}%
\regfield{(reserved)}{9}{0}{000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTPAUSEINSLP}\item [RTC\_CNTL\_WDT\_PAUSE\_IN\_SLP] Set this bit to pause the watchdog in sleep. (R/W)
\label{fielddesc:RTCCNTLWDTPROCPURESETEN}\item [RTC\_CNTL\_WDT\_PROCPU\_RESET\_EN] Set this bit to allow the watchdog to be able to reset CPU. (R/W)
\label{fielddesc:RTCCNTLWDTFLASHBOOTMODEN}\item [RTC\_CNTL\_WDT\_FLASHBOOT\_MOD\_EN] Set this bit to enable watchdog when the chip boots from flash. (R/W)
\label{fielddesc:RTCCNTLWDTSYSRESETLENGTH}\item [RTC\_CNTL\_WDT\_SYS\_RESET\_LENGTH] Sets the length of the system reset counter. (R/W)
\label{fielddesc:RTCCNTLWDTCPURESETLENGTH}\item [RTC\_CNTL\_WDT\_CPU\_RESET\_LENGTH] Sets the length of the CPU reset counter. (R/W)
\label{fielddesc:RTCCNTLWDTSTG3}\item [RTC\_CNTL\_WDT\_STG3] 1: enable at the interrupt stage, 2: enable at the CPU stage,  3: enable at the system stage, 4: enable at the system and RTC stage. (R/W)
\label{fielddesc:RTCCNTLWDTSTG2}\item [RTC\_CNTL\_WDT\_STG2] 1: enable at the interrupt stage, 2: enable at the CPU stage,  3: enable at the system stage, 4: enable at the system and RTC stage. (R/W)
\label{fielddesc:RTCCNTLWDTSTG1}\item [RTC\_CNTL\_WDT\_STG1] 1: enable at the interrupt stage, 2: enable at the CPU stage,  3: enable at the system stage, 4: enable at the system and RTC stage. (R/W)
\label{fielddesc:RTCCNTLWDTSTG0}\item [RTC\_CNTL\_WDT\_STG0] 1: enable at the interrupt stage, 2: enable at the CPU stage,  3: enable at the system stage, 4: enable at the system and RTC stage. (R/W)
\label{fielddesc:RTCCNTLWDTEN}\item [RTC\_CNTL\_WDT\_EN] Set this bit to enable the RTC watchdog. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{tiplisting}
For details, please refer to Chapter \ref{mod:xtwdt} \textit{\nameref{mod:xtwdt}}.
\end{tiplisting}


\begin{register}{H}{RTC\_CNTL\_WDTCONFIG1\_REG}{\hexprefix{}0098}\label{regdesc:RTCCNTLWDTCONFIG1REG}
\regfield{RTC\_CNTL\_WDT\_STG0\_HOLD}{32}{0}{{200000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTSTG0HOLD}\item [RTC\_CNTL\_WDT\_STG0\_HOLD] Configures the hold time of RTC watchdog at level 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTCONFIG2\_REG}{\hexprefix{}009C}\label{regdesc:RTCCNTLWDTCONFIG2REG}
\regfield{RTC\_CNTL\_WDT\_STG1\_HOLD}{32}{0}{{80000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTSTG1HOLD}\item [RTC\_CNTL\_WDT\_STG1\_HOLD] Configures the hold time of RTC watchdog at level 2. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTCONFIG3\_REG}{\hexprefix{}00A0}\label{regdesc:RTCCNTLWDTCONFIG3REG}
\regfield{RTC\_CNTL\_WDT\_STG2\_HOLD}{32}{0}{{\hexprefix{}000fff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTSTG2HOLD}\item [RTC\_CNTL\_WDT\_STG2\_HOLD] Configures the hold time of RTC watchdog at level 3. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTCONFIG4\_REG}{\hexprefix{}00A4}\label{regdesc:RTCCNTLWDTCONFIG4REG}
\regfield{RTC\_CNTL\_WDT\_STG3\_HOLD}{32}{0}{{\hexprefix{}000fff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTSTG3HOLD}\item [RTC\_CNTL\_WDT\_STG3\_HOLD] Configures the hold time of RTC watchdog at level 4. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTFEED\_REG}{\hexprefix{}00A8}\label{regdesc:RTCCNTLWDTFEEDREG}
\regfield{RTC\_CNTL\_RTC\_WDT\_FEED}{1}{31}{{0}}%
\regfield{(reserved)}{31}{0}{0000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCWDTFEED}\item [RTC\_CNTL\_RTC\_WDT\_FEED] Set this bit to feed the RTC watchdog. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTWPROTECT\_REG}{\hexprefix{}00AC}\label{regdesc:RTCCNTLWDTWPROTECTREG}
\regfield{RTC\_CNTL\_WDT\_WKEY}{32}{0}{{\hexprefix{}50d83aa1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTWKEY}\item [RTC\_CNTL\_WDT\_WKEY] If the register contains a different value than \hexprefix{}50d83aa1, write protection for the RTC watchdog (RWDT) is enabled. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SWD\_CONF\_REG}{\hexprefix{}00B0}\label{regdesc:RTCCNTLSWDCONFREG}
\regfield{RTC\_CNTL\_SWD\_AUTO\_FEED\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_SWD\_DISABLE}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_SWD\_FEED}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_SWD\_RST\_FLAG\_CLR}{1}{28}{{0}}%
\regfield{RTC\_CNTL\_SWD\_SIGNAL\_WIDTH}{10}{18}{{300}}%
\regfield{(reserved)}{16}{2}{0000000000000000}%
\regfield{RTC\_CNTL\_SWD\_FEED\_INT}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SWD\_RESET\_FLAG}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWDRESETFLAG}\item [RTC\_CNTL\_SWD\_RESET\_FLAG] Indicates the super watchdog reset flag. (RO)
\label{fielddesc:RTCCNTLSWDFEEDINT}\item [RTC\_CNTL\_SWD\_FEED\_INT] Receiving this interrupt leads to feeding the super watchdog via SW. (RO)
\label{fielddesc:RTCCNTLSWDSIGNALWIDTH}\item [RTC\_CNTL\_SWD\_SIGNAL\_WIDTH] Adjusts the signal width sent to the super watchdog. (R/W)
\label{fielddesc:RTCCNTLSWDRSTFLAGCLR}\item [RTC\_CNTL\_SWD\_RST\_FLAG\_CLR] Set to reset the super watchdog reset flag. (WO)
\label{fielddesc:RTCCNTLSWDFEED}\item [RTC\_CNTL\_SWD\_FEED] Set to feed the super watchdog via SW. (WO)
\label{fielddesc:RTCCNTLSWDDISABLE}\item [RTC\_CNTL\_SWD\_DISABLE] Set this bit to disable super watchdog. (R/W)
\label{fielddesc:RTCCNTLSWDAUTOFEEDEN}\item [RTC\_CNTL\_SWD\_AUTO\_FEED\_EN] Set this bit to enable automatic watchdog feeding upon interrupts. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SWD\_WPROTECT\_REG}{\hexprefix{}00B4}\label{regdesc:RTCCNTLSWDWPROTECTREG}
\regfield{RTC\_CNTL\_SWD\_WKEY}{32}{0}{{\hexprefix{}8f1d312a}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWDWKEY}\item [RTC\_CNTL\_SWD\_WKEY] Sets the write protection key of the super watchdog. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SW\_CPU\_STALL\_REG}{\hexprefix{}00B8}\label{regdesc:RTCCNTLSWCPUSTALLREG}
\regfield{RTC\_CNTL\_SW\_STALL\_PROCPU\_C1}{6}{26}{{0}}%
\regfield{(reserved)}{26}{0}{00000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWSTALLPROCPUC1}\item [RTC\_CNTL\_SW\_STALL\_PROCPU\_C1] When \hyperref[fielddesc:RTCCNTLSWSTALLPROCPUC0]{RTC\_CNTL\_SW\_STALL\_PROCPU\_C0} is configured to \hexprefix{}2, setting this bit to \hexprefix{}21 stalls the CPU by SW. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_PAD\_HOLD\_REG}{\hexprefix{}00D4}\label{regdesc:RTCCNTLPADHOLDREG}
\regfield{(reserved)}{10}{22}{0000000000}%
\regfield{RTC\_CNTL\_RTC\_PAD21\_HOLD}{1}{21}{{0}}%
\regfield{RTC\_CNTL\_RTC\_PAD20\_HOLD}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_RTC\_PAD19\_HOLD}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_PDAC2\_HOLD}{1}{18}{{0}}%
\regfield{RTC\_CNTL\_PDAC1\_HOLD}{1}{17}{{0}}%
\regfield{RTC\_CNTL\_X32N\_HOLD}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_X32P\_HOLD}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD14\_HOLD}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD13\_HOLD}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD12\_HOLD}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD11\_HOLD}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD10\_HOLD}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD9\_HOLD}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD8\_HOLD}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD7\_HOLD}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD6\_HOLD}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD5\_HOLD}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD4\_HOLD}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD3\_HOLD}{1}{3}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD2\_HOLD}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD1\_HOLD}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD0\_HOLD}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHPAD0HOLD}\item [RTC\_CNTL\_TOUCH\_PAD0\_HOLD] Sets the touch GPIO 0 to the holding state. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD1HOLD}\item [RTC\_CNTL\_TOUCH\_PAD1\_HOLD] Sets the touch GPIO 1 to the holding state. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD2HOLD}\item [RTC\_CNTL\_TOUCH\_PAD2\_HOLD] Sets the touch GPIO 2 to the holding state. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD3HOLD}\item [RTC\_CNTL\_TOUCH\_PAD3\_HOLD] Sets the touch GPIO 3 to the holding state. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD4HOLD}\item [RTC\_CNTL\_TOUCH\_PAD4\_HOLD] Sets the touch GPIO 4 to the holding state. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD5HOLD}\item [RTC\_CNTL\_TOUCH\_PAD5\_HOLD] Sets the touch GPIO 5 to the holding state. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD6HOLD}\item [RTC\_CNTL\_TOUCH\_PAD6\_HOLD] Sets the touch GPIO 6 to the holding state. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD7HOLD}\item [RTC\_CNTL\_TOUCH\_PAD7\_HOLD] Sets the touch GPIO 7 to the holding state. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD8HOLD}\item [RTC\_CNTL\_TOUCH\_PAD8\_HOLD] Sets the touch GPIO 8 to the holding state. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD9HOLD}\item [RTC\_CNTL\_TOUCH\_PAD9\_HOLD] Sets the touch GPIO 9 to the holding state. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD10HOLD}\item [RTC\_CNTL\_TOUCH\_PAD10\_HOLD] Sets the touch GPIO 10 to the holding state. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD11HOLD}\item [RTC\_CNTL\_TOUCH\_PAD11\_HOLD] Sets the touch GPIO 11 to the holding state. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD12HOLD}\item [RTC\_CNTL\_TOUCH\_PAD12\_HOLD] Sets the touch GPIO 12 to the holding state. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD13HOLD}\item [RTC\_CNTL\_TOUCH\_PAD13\_HOLD] Sets the touch GPIO 13 to the holding state. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD14HOLD}\item [RTC\_CNTL\_TOUCH\_PAD14\_HOLD] Sets the touch GPIO 14 to the holding state. (R/W)
\label{fielddesc:RTCCNTLX32PHOLD}\item [RTC\_CNTL\_X32P\_HOLD] Sets the x32p to the holding state. (R/W)
\label{fielddesc:RTCCNTLX32NHOLD}\item [RTC\_CNTL\_X32N\_HOLD] Sets the x32n to the holding state. (R/W)
\label{fielddesc:RTCCNTLPDAC1HOLD}\item [RTC\_CNTL\_PDAC1\_HOLD] Sets the pdac1 to the holding state. (R/W)
\label{fielddesc:RTCCNTLPDAC2HOLD}\item [RTC\_CNTL\_PDAC2\_HOLD] Sets the pdac2 to the holding state. (R/W)
\label{fielddesc:RTCCNTLRTCPAD19HOLD}\item [RTC\_CNTL\_RTC\_PAD19\_HOLD] Sets the RTG GPIO 19 to the holding state. (R/W)
\label{fielddesc:RTCCNTLRTCPAD20HOLD}\item [RTC\_CNTL\_RTC\_PAD20\_HOLD] Sets the RTG GPIO 20 to the holding state. (R/W)
\label{fielddesc:RTCCNTLRTCPAD21HOLD}\item [RTC\_CNTL\_RTC\_PAD21\_HOLD] Sets the RTG GPIO 21 to the holding state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_DIG\_PAD\_HOLD\_REG}{\hexprefix{}00D8}\label{regdesc:RTCCNTLDIGPADHOLDREG}
\regfield{RTC\_CNTL\_DIG\_PAD\_HOLD}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLDIGPADHOLD}\item [RTC\_CNTL\_DIG\_PAD\_HOLD] Set GPIO 21 to GPIO 45 to the holding state. (See bitmap to locate any GPIO). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_BROWN\_OUT\_REG}{\hexprefix{}00E4}\label{regdesc:RTCCNTLBROWNOUTREG}
\regfield{RTC\_CNTL\_RTC\_BROWN\_OUT\_DET}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_ENA}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_CNT\_CLR}{1}{29}{{0}}%
\regfield{(reserved)}{1}{28}{0}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_RST\_SEL}{1}{27}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_RST\_ENA}{1}{26}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_RST\_WAIT}{10}{16}{{\hexprefix{}3ff}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_PD\_RF\_ENA}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_CLOSE\_FLASH\_ENA}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_WAIT}{10}{4}{{\hexprefix{}2ff}}%
\regfield{(reserved)}{3}{1}{000}%
\regfield{RTC\_CNTL\_BROWN\_OUT2\_ENA}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLBROWNOUT2ENA}\item [RTC\_CNTL\_BROWN\_OUT2\_ENA] Enables the brown\_out2 to initiate a chip reset. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTINTWAIT}\item [RTC\_CNTL\_BROWN\_OUT\_INT\_WAIT] Configures the waiting cycles before sending an interrupt. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTCLOSEFLASHENA}\item [RTC\_CNTL\_BROWN\_OUT\_CLOSE\_FLASH\_ENA] Set this bit to enable PD the flash when a brown-out happens. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTPDRFENA}\item [RTC\_CNTL\_BROWN\_OUT\_PD\_RF\_ENA] Set this bit to enable PD the RF circuits when a brown-out happens. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTRSTWAIT}\item [RTC\_CNTL\_BROWN\_OUT\_RST\_WAIT] Configures the waiting cycles before the reset after a brown-out. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTRSTENA}\item [RTC\_CNTL\_BROWN\_OUT\_RST\_ENA] Enables to reset brown-out. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTRSTSEL}\item [RTC\_CNTL\_BROWN\_OUT\_RST\_SEL] Selects the reset type when a brown-out happens. 1: chip reset, 0: system reset. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTCNTCLR}\item [RTC\_CNTL\_BROWN\_OUT\_CNT\_CLR] Clears the brown-out counter. (WO)
\label{fielddesc:RTCCNTLBROWNOUTENA}\item [RTC\_CNTL\_BROWN\_OUT\_ENA] Set this bit to enable brown-out detection. (R/W)
\label{fielddesc:RTCCNTLRTCBROWNOUTDET}\item [RTC\_CNTL\_RTC\_BROWN\_OUT\_DET] Indicates the status of the brown-out signal. (RO)
\end{reglist}\end{regdesc}
\end{register}
