

\begin{register}{H}{SPI\_CMD\_REG}{0x0}\label{regdesc:SPICMDREG}
\regfield{(reserved)}{13}{19}{0000000000000}%
\regfield{SPI\_USR}{1}{18}{0}%
\regfield{(reserved)}{18}{0}{000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_USR] An SPI operation will be triggered when this bit is set. The bit will be cleared once the operation is done. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_ADDR\_REG}{0x4}\label{regdesc:SPIADDRREG}
\regfield{}{32}{0}{{0x000000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_ADDR\_REG]It stores the transmitting address when master is in half-duplex mode or QSPI mode. If the address length is bigger than 32 bits, this register stores the higher 32 bits of address value, \hyperref[regdesc:SPISLVWRSTATUSREG]{SPI\_SLV\_WR\_STATUS\_REG} stores the rest lower part of address value. If the address length is smaller than 33 bits,  this register stores all the address value. The register is in valid only when \hyperref[regdesc:SPIUSERREG]{SPI\_USR\_ADDR} bit is set to 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_CTRL\_REG}{0x8}\label{regdesc:SPICTRLREG}
\regfield{(reserved)}{5}{27}{00000}%
\regfield{SPI\_WR\_BIT\_ORDER}{1}{26}{0}%
\regfield{SPI\_RD\_BIT\_ORDER}{1}{25}{0}%
\regfield{SPI\_FREAD\_QIO}{1}{24}{0}%
\regfield{SPI\_FREAD\_DIO}{1}{23}{0}%
\regfield{(reserved)}{1}{22}{0}%
\regfield{SPI\_WP}{1}{21}{1}%
\regfield{SPI\_FREAD\_QUAD}{1}{20}{0}%
\regfield{(reserved)}{5}{15}{00000}%
\regfield{SPI\_FREAD\_DUAL}{1}{14}{0}%
\regfield{SPI\_FASTRD\_MODE}{1}{13}{1}%
\regfield{(reserved)}{13}{0}{0000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_WR\_BIT\_ORDER]This bit determines the bit order for command, address and data in transmitted signal. 1: sends LSB first; 0: sends MSB first. (R/W)
\item [SPI\_RD\_BIT\_ORDER]This bit determines the bit order for received data in received signal. 1: receives LSB first; 0: receives MSB first. (R/W)
\item [SPI\_FREAD\_QIO] This bit is used to enable four-line address writes and data reads in QSPI mode. (R/W)
\item [SPI\_FREAD\_DIO]This bit is used to enable two-line address writes and data reads in QSPI mode. (R/W)
\item [SPI\_WP] This bit determines the write-protection signal output when SPI is idle in QSPI mode. 1: output high; 0: output low. (R/W)
\item [SPI\_FREAD\_QUAD]This bit is used to enable four-line data reads in QSPI mode. (R/W)
\item [SPI\_FREAD\_DUAL]This bit is used to enable two-line data reads in QSPI mode. (R/W)
\item [SPI\_FASTRD\_MODE]Reserved.
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_CTRL1\_REG}{0xC}\label{regdesc:SPICTRL1REG}
\regfield{SPI\_CS\_HOLD\_DELAY}{4}{28}{{0x05}}%
\regfield{(reserved)}{28}{0}{0000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_CS\_HOLD\_DELAY]Reserved.
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_RD\_STATUS\_REG}{0x10}\label{regdesc:SPIRDSTATUSREG}
\regfield{SPI\_STATUS\_EXT}{8}{24}{{0x000}}%
\regfield{}{8}{16}{{0x000}}%
\regfield{SPI\_STATUS}{16}{0}{0000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_STATUS\_EXT]Reserved.
\item [SPI\_STATUS]Reserved.
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_CTRL2\_REG}{0x14}\label{regdesc:SPICTRL2REG}
\regfield{SPI\_CS\_DELAY\_NUM}{4}{28}{{0x00}}%
\regfield{SPI\_CS\_DELAY\_MODE}{2}{26}{{0x0}}%
\regfield{SPI\_MOSI\_DELAY\_NUM}{3}{23}{{0x0}}%
\regfield{SPI\_MOSI\_DELAY\_MODE}{2}{21}{{0x0}}%
\regfield{SPI\_MISO\_DELAY\_NUM}{3}{18}{{0x0}}%
\regfield{SPI\_MISO\_DELAY\_MODE}{2}{16}{{0x0}}%
\regfield{reserved}{4}{12}{{0x00}}
\regfield{reserved}{4}{8}{{0x00}}%
\regfield{SPI\_HOLD\_TIME}{4}{4}{{0x01}}%
\regfield{SPI\_SETUP\_TIME}{4}{0}{{0x01}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_CS\_DELAY\_NUM]Reserved.
\item [SPI\_CS\_DELAY\_MODE]Reserved.
\item [SPI\_MOSI\_DELAY\_NUM] It is used to configure the number of system clock cycles by which the MOSI signals are delayed. (R/W)
\item [SPI\_MOSI\_DELAY\_MODE]This register field determines the way the MOSI signals are delayed by SPI clock. (R/W) \\
After being delayed by SPI\_MOSI\_DELAY\_NUM system clocks, the MOSI signals will then be delayed by the configuration of SPI\_MOSI\_DELAY\_MODE, specifically:\\
0: no delay. \\
1: if SPI\_CK\_OUT\_EDGE or SPI\_CK\_I\_EDGE is set, the MOSI signals are delayed by half a cycle, otherwise they are delayed by one cycle.\\
2: if SPI\_CK\_OUT\_EDGE or SPI\_CK\_I\_EDGE is set, the MOSI signals are delayed by one cycle, otherwise they are delayed by half a cycle.\\
3: the MOSI signals are delayed one cycle.
\item [SPI\_MISO\_DELAY\_NUM] It is used to configure the number of system clock cycles by which the MISO signals are delayed. (R/W)
\item [SPI\_MISO\_DELAY\_MODE] This register field determines the way MISO signals are delayed by SPI clock. (R/W) \\
After being delayed by SPI\_MISO\_DELAY\_NUM system clock, the MISO signals will then be delayed by the configuration of SPI\_MISO\_DELAY\_MODE, specifically:\\
0: no delay. \\
1: if SPI\_CK\_OUT\_EDGE or SPI\_CK\_I\_EDGE is set, the MISO signals are delayed by half a cycle, otherwise they are delayed by one cycle. \\
2: if SPI\_CK\_OUT\_EDGE or SPI\_CK\_I\_EDGE is set, the MISO signals are delayed by one cycle, otherwise they are delayed by half a cycle. \\
3: the MISO signals are delayed by one cycle.
\item [SPI\_HOLD\_TIME]The number of SPI clock cycles by which CS pin signals are delayed. It is only valid when SPI\_CS\_HOLD is set to 1. (R/W)
\item [SPI\_SETUP\_TIME] It is to configure the time between the CS signal active edge and the first SPI clock edge. It is only valid in half-duplex mode or QSPI mode and when SPI\_CS\_SETUP is set to 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_CLOCK\_REG}{0x18}\label{regdesc:SPICLOCKREG}
\regfield{SPI\_CLK\_EQU\_SYSCLK}{1}{31}{1}%
\regfield{SPI\_CLKDIV\_PRE}{13}{18}{0000000000000}%
\regfield{SPI\_CLKCNT\_N}{6}{12}{{0x03}}%
\regfield{SPI\_CLKCNT\_H}{6}{6}{{0x01}}%
\regfield{SPI\_CLKCNT\_L}{6}{0}{{0x03}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_CLK\_EQU\_SYSCLK]In master mode, when this bit is set to 1, SPI output clock is equal to system clock; when set to 0, SPI output clock is divided from system clock. In slave mode, it should be set to 0. (R/W)
\item [SPI\_CLKDIV\_PRE]In master mode, it is used to configure the pre-divider value for SPI output clock. It is only valid when SPI\_CLK\_EQU\_SYSCLK is 0. In slave mode, it should be set to 0. (R/W)
\item [SPI\_CLKCNT\_N]In master mode, it is used to configure the divider for SPI output clock. It is only valid when SPI\_CLK\_EQU\_SYSCLK is 0. In slave mode, it should be set to 0. (R/W)
\item [SPI\_CLKCNT\_H] In master mode, $\textrm{SPI\_CLKCNT\_H} =\lfloor \frac{\textrm{SPI\_CLKCNT\_N+1}}{2} – 1\rfloor$. It is only valid when SPI\_CLK\_EQU\_SYSCLK is 0. In slave mode, it should be set to 0. (R/W)
\item [SPI\_CLKCNT\_L]In master mode, it is equal to SPI\_CLKCNT\_N. It is only valid when SPI\_CLK\_EQU\_SYSCLK is 0. In slave mode, it should be set to 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_USER\_REG}{0x1C}\label{regdesc:SPIUSERREG}
\regfield{SPI\_USR\_COMMAND}{1}{31}{1}%
\regfield{SPI\_USR\_ADDR}{1}{30}{0}%
\regfield{SPI\_USR\_DUMMY}{1}{29}{0}%
\regfield{SPI\_USR\_MISO}{1}{28}{0}%
\regfield{SPI\_USR\_MOSI}{1}{27}{0}%
\regfield{SPI\_USR\_DUMMY\_IDLE}{1}{26}{0}%
\regfield{SPI\_USR\_MOSI\_HIGHPART}{1}{25}{0}%
\regfield{SPI\_USR\_MISO\_HIGHPART}{1}{24}{0}%
\regfield{(reserved)}{7}{17}{0000000}%
\regfield{SPI\_SIO}{1}{16}{0}%
\regfield{SPI\_FWRITE\_QIO}{1}{15}{0}%
\regfield{SPI\_FWRITE\_DIO}{1}{14}{0}%
\regfield{SPI\_FWRITE\_QUAD}{1}{13}{0}%
\regfield{SPI\_FWRITE\_DUAL}{1}{12}{0}%
\regfield{SPI\_WR\_BYTE\_ORDER}{1}{11}{0}%
\regfield{SPI\_RD\_BYTE\_ORDER}{1}{10}{0}%
\regfield{(reserved)}{2}{8}{00}%
\regfield{SPI\_CK\_OUT\_EDGE}{1}{7}{0}%
\regfield{SPI\_CK\_I\_EDGE}{1}{6}{1}%
\regfield{SPI\_CS\_SETUP}{1}{5}{0}%
\regfield{SPI\_CS\_HOLD}{1}{4}{0}%
\regfield{(reserved)}{3}{1}{000}%
\regfield{SPI\_DOUTDIN}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_USR\_COMMAND]This bit enables the command phase of an SPI operation in SPI half-duplex mode and QSPI mode. (R/W)
\item [SPI\_USR\_ADDR]This bit enables the address phase of an SPI operation in SPI half-duplex mode and QSPI mode. (R/W)
\item [SPI\_USR\_DUMMY]This bit enables the dummy phase of an SPI operation in SPI half-duplex mode and QSPI mode. (R/W)
\item [SPI\_USR\_MISO]This bit enables the read-data phase of an SPI operation in SPI half-duplex mode and QSPI mode. (R/W)
\item [SPI\_USR\_MOSI]This bit enables the write-data phase of an SPI operation in SPI half-duplex mode and QSPI mode. (R/W)
\item [SPI\_USR\_DUMMY\_IDLE]The SPI clock signal is disabled in the dummy phase when the bit is set in SPI half-duplex mode and QSPI mode. (R/W)
\item [SPI\_USR\_MOSI\_HIGHPART]If set, MOSI data is stored in SPI\_W8\verb+ ~ +SPI\_W15 of the SPI buffer. (R/W)
\item [SPI\_USR\_MISO\_HIGHPART]If set, MISO data is stored in SPI\_W8\verb+ ~ +SPI\_W15 of the SPI buffer. (R/W)
\item [SPI\_SIO]Set this bit to enable three-line half-duplex communication. (R/W)
\item [SPI\_FWRITE\_QIO] Reserved.
\item [SPI\_FWRITE\_DIO]Reserved.
\item [SPI\_FWRITE\_QUAD]Reserved.
\item [SPI\_FWRITE\_DUAL] Reserved.
\item [SPI\_WR\_BYTE\_ORDER] This bit determines the byte order of the command, address and data in transmitted signal. 1: big-endian; 0: little-endian. (R/W)
\item [SPI\_RD\_BYTE\_ORDER]This bit determines the byte order of received data in transmitted signal. 1: big-endian; 0: little\_endian. (R/W)
\item [SPI\_CK\_OUT\_EDGE]This bit, combined with SPI\_MOSI\_DELAY\_MODE, sets the MOSI signal delay mode. It is only valid in master mode. (R/W)
\item [SPI\_CK\_I\_EDGE]In slave mode, the bit is the same as SPI\_CK\_OUT\_EDGE in master mode. It is combined with SPI\_MISO\_DELAY\_MODE. It is only valid in slave mode. (R/W)
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{SPI\_USER\_REG}{0x1C}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\item [SPI\_CS\_SETUP]Setting this bit enables a delay between CS active edge and the first clock edge, in multiples of one SPI clock cycle. In full-duplex mode and QSPI mode, setting this bit results in $(\textrm{SPI\_SETUP\_TIME}+1.5)$ SPI clock cycles delay. In full-duplex mode, there will be 1.5 SPI clock cycles delay for mode0 and mode2, and 1 SPI clock cycle delay for mode1 and mode3. (R/W)
\item [SPI\_CS\_HOLD]Setting this bit enables a delay between the end of a transmission and CS being inactive, as specified in SPI\_HOLD\_TIME. (R/W)
\item [SPI\_DOUTDIN]Set the bit to enable full-duplex communication. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{SPI\_USER1\_REG}{0x20}\label{regdesc:SPIUSER1REG}
\regfield{SPI\_USR\_ADDR\_BITLEN}{6}{26}{{23}}%
\regfield{(reserved)}{18}{8}{000000000000000000}%
\regfield{SPI\_USR\_DUMMY\_CYCLELEN}{8}{0}{{7}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_USR\_ADDR\_BITLEN]It indicates the bit length of the transmitted address minus one in half-duplex mode and QSPI mode, in multiples of one bit. It is only valid when SPI\_USR\_ADDR is set to 1. (RO)
\item [SPI\_USR\_DUMMY\_CYCLELEN]It indicates the number of SPI clock cycles for the dummy phase minus one in SPI half-duplex mode and QSPI mode. It is only valid when SPI\_USR\_DUMMY is set to 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_USER2\_REG}{0x24}\label{regdesc:SPIUSER2REG}
\regfield{SPI\_USR\_COMMAND\_BITLEN}{4}{28}{{7}}%
\regfield{(reserved)}{12}{16}{000000000000}%
\regfield{SPI\_USR\_COMMAND\_VALUE}{16}{0}{0000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_USR\_COMMAND\_BITLEN]It indicates the bit length of the command phase minus one in SPI half-duplex mode and QSPI mode. It is only valid when SPI\_USR\_COMMAND is set to 1. (R/W)
\item [SPI\_USR\_COMMAND\_VALUE] It indicates the value of the command to be transmitted in SPI half-duplex mode and QSPI mode. It is only valid when SPI\_USR\_COMMAND is set to 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_MOSI\_DLEN\_REG}{0x28}\label{regdesc:SPIMOSIDLENREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{SPI\_USR\_MOSI\_DBITLEN}{24}{0}{{0x0000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_USR\_MOSI\_DBITLEN]It indicates the length of MOSI data minus one, in multiples of one bit. It is only valid when SPI\_USR\_MOSI is set to 1 in master mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_MISO\_DLEN\_REG}{0x2C}\label{regdesc:SPIMISODLENREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{SPI\_USR\_MISO\_DBITLEN}{24}{0}{{0x0000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_USR\_MISO\_DBITLEN]It indicates the length of MISO data minus one, in multiples of one bit. It is only valid when SPI\_USR\_MISO is set to 1 in master mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_SLV\_WR\_STATUS\_REG}{0x30}\label{regdesc:SPISLVWRSTATUSREG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_SLV\_WR\_STATUS\_REG]In the slave mode this register is the status register for the master to write the slave. In the master mode, if the address length is bigger than 32 bits, \hyperref[regdesc:SPIADDRREG]{SPI\_ADDR\_REG} stores the higher 32 bits of address value, and this register stores the rest lower part of address value. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{SPI\_PIN\_REG}{0x34}\label{regdesc:SPIPINREG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{SPI\_CS\_KEEP\_ACTIVE}{1}{30}{0}%
\regfield{SPI\_CK\_IDLE\_EDGE}{1}{29}{0}%
\regfield{(reserved)}{15}{14}{000000000000000}%
\regfield{SPI\_MASTER\_CK\_SEL}{3}{11}{000}%
\regfield{(reserved)}{2}{9}{00}%
\regfield{SPI\_MASTER\_CS\_POL}{3}{6}{00000}%
\regfield{SPI\_CK\_DIS}{1}{5}{0}%
\regfield{(reserved)}{2}{3}{00}%
\regfield{SPI\_CS2\_DIS}{1}{2}{1}%
\regfield{SPI\_CS1\_DIS}{1}{1}{1}%
\regfield{SPI\_CS0\_DIS}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_CS\_KEEP\_ACTIVE] This bit is only used in master mode where when it is set, the CS signal will keep active. (R/W)
\item [SPI\_CK\_IDLE\_EDGE]  This bit is only used in master mode to configure the logicl level of SPI output clock in idle state. (R/W)\\
1: the spi\_clk line keeps high when idle;\\
0: the spi\_clk line keeps low when idle.
\item [SPI\_MASTER\_CK\_SEL]  Reserved.
\item [SPI\_MASTER\_CS\_POL]  Reserved.
\item [SPI\_CK\_DIS]  Reserved.
\item [SPI\_CS2\_DIS] This bit enables the SPI CS2 signal. 1: disables CS2; 0: enables CS2. (R/W)
\item [SPI\_CS1\_DIS] This bit enables the SPI CS1 signal. 1: disables CS1; 0: enables CS1. (R/W)
\item [SPI\_CS0\_DIS]This bit enables the SPI CS0 signal. 1: disables CS0; 0: enables CS0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_SLAVE\_REG}{0x38}\label{regdesc:SPISLAVEREG}
\regfield{SPI\_SYNC\_RESET}{1}{31}{0}%
\regfield{SPI\_SLAVE\_MODE}{1}{30}{0}%
\regfield{SPI\_SLV\_WR\_RD\_BUF\_EN}{1}{29}{0}%
\regfield{SPI\_SLV\_WR\_RD\_STA\_EN}{1}{28}{0}%
\regfield{SPI\_SLV\_CMD\_DEFINE}{1}{27}{0}%
\regfield{SPI\_TRANS\_CNT}{4}{23}{0000}%
\regfield{SPI\_SLV\_LAST\_STATE}{3}{20}{000}%
\regfield{SPI\_SLV\_LAST\_COMMAND}{3}{17}{000}%
\regfield{(reserved)}{5}{12}{00000}%
\regfield{SPI\_CS\_I\_MODE}{2}{10}{00}%
\regfield{SPI\_TRANS\_INTEN}{1}{9}{0}%
\regfield{SPI\_SLV\_WR\_STA\_INTEN}{1}{8}{0}%
\regfield{SPI\_SLV\_RD\_STA\_INTEN}{1}{7}{0}%
\regfield{SPI\_SLV\_WR\_BUF\_INTEN}{1}{6}{0}%
\regfield{SPI\_SLV\_RD\_BUF\_INTEN}{1}{5}{0}%
\regfield{SPI\_TRANS\_DONE}{1}{4}{0}%
\regfield{SPI\_SLV\_WR\_STA\_DONE}{1}{3}{0}%
\regfield{SPI\_SLV\_RD\_STA\_DONE}{1}{2}{0}%
\regfield{SPI\_SLV\_WR\_BUF\_DONE}{1}{1}{0}%
\regfield{SPI\_SLV\_RD\_BUF\_DONE}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_SYNC\_RESET] When set, it resets the latched values of the SPI clock line, CS line and data line. (R/W) 
\item [SPI\_SLAVE\_MODE]This bit is used to set the mode of the SPI device. (R/W)\\1: slave mode; \\0: master mode.
\item [SPI\_SLV\_WR\_RD\_BUF\_EN]This bit is only used in slave half-duplex mode, where when it is set, the write and read data commands are enabled.  (R/W)
\item [SPI\_SLV\_WR\_RD\_STA\_EN] This bit is only used in slave half-duplex mode, where when it is set, the write and read status commands are enabled. (R/W)
\item [SPI\_SLV\_CMD\_DEFINE] Reserved.
\item [SPI\_TRANS\_CNT]The counter for operations in both the master mode and the slave mode. (RO)
\item [SPI\_SLV\_LAST\_STATE]In slave mode, this contains the state of the SPI state machine. (RO)
\item [SPI\_SLV\_LAST\_COMMAND] Reserved.
\item [SPI\_CS\_I\_MODE]Reserved.
\item [SPI\_TRANS\_INTEN]The interrupt enable bit for the \hyperref[int:SPITRANSDONEINT]{SPI\_TRANS\_DONE\_INT} interrupt. (R/W)
\item [SPI\_SLV\_WR\_STA\_INTEN]The interrupt enable bit for the \hyperref[int:SPISLVWRSTAINT]{SPI\_SLV\_WR\_STA\_INT} interrupt. (R/W)
\item [SPI\_SLV\_RD\_STA\_INTEN]The interrupt enable bit for the \hyperref[int:SPISLVRDSTAINT]{SPI\_SLV\_RD\_STA\_INT} interrupt. (R/W)
\item [SPI\_SLV\_WR\_BUF\_INTEN]The interrupt enable bit for the \hyperref[int:SPISLVWRBUFINT]{SPI\_SLV\_WR\_BUF\_INT} interrupt. (R/W)
\item [SPI\_SLV\_RD\_BUF\_INTEN]The interrupt enable bit for the \hyperref[int:SPISLVRDBUFINT]{SPI\_SLV\_RD\_BUF\_INT} interrupt. (R/W)
\item [SPI\_TRANS\_DONE]The raw interrupt status bit for the \hyperref[int:SPITRANSDONEINT]{SPI\_TRANS\_DONE\_INT} interrupt. It is set by hardware and cleared by software. (R/W)
\item [SPI\_SLV\_WR\_STA\_DONE]The raw interrupt status bit for the \hyperref[int:SPISLVWRSTAINT]{SPI\_SLV\_WR\_STA\_INT} interrupt. It is set by hardware and cleared by software, and only applicable to slave half-duplex mode. (R/W)
\item [SPI\_SLV\_RD\_STA\_DONE]The raw interrupt status bit for the \hyperref[int:SPISLVRDSTAINT]{SPI\_SLV\_RD\_STA\_INT} interrupt. It is set by hardware and cleared by software, and only applicable to slave half-duplex mode. (R/W)
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{SPI\_SLAVE\_REG}{0x38}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page ...]

\item [SPI\_SLV\_WR\_BUF\_DONE]The raw interrupt status bit for the \hyperref[int:SPISLVWRBUFINT]{SPI\_SLV\_WR\_BUF\_INT} interrupt. It is set by hardware and cleared by software, and only applicable to slave half-duplex mode. (R/W)
\item [SPI\_SLV\_RD\_BUF\_DONE]The raw interrupt status bit for the \hyperref[int:SPISLVRDBUFINT]{SPI\_SLV\_RD\_BUF\_INT} interrupt. It is set by hardware and cleared by software, and only applicable to slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{SPI\_SLAVE1\_REG}{0x3C}\label{regdesc:SPISLAVE1REG}
\regfield{SPI\_SLV\_STATUS\_BITLEN}{5}{27}{00000}%
\regfield{SPI\_SLV\_STATUS\_FAST\_EN}{1}{26}{0}%
\regfield{SPI\_SLV\_STATUS\_READBACK}{1}{25}{1}%
\regfield{(reserved)}{9}{16}{000000000}%
\regfield{SPI\_SLV\_RD\_ADDR\_BITLEN}{6}{10}{{0x00}}%
\regfield{SPI\_SLV\_WR\_ADDR\_BITLEN}{6}{4}{{0x00}}%
\regfield{SPI\_SLV\_WRSTA\_DUMMY\_EN}{1}{3}{0}%
\regfield{SPI\_SLV\_RDSTA\_DUMMY\_EN}{1}{2}{0}%
\regfield{SPI\_SLV\_WRBUF\_DUMMY\_EN}{1}{1}{0}%
\regfield{SPI\_SLV\_RDBUF\_DUMMY\_EN}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_SLV\_STATUS\_BITLEN] It is only used in slave half-duplex mode to configure the length of the master writing into the status register. (R/W)
\item [SPI\_SLV\_STATUS\_FAST\_EN] Reserved.
\item [SPI\_SLV\_STATUS\_READBACK] Reserved.
\item [SPI\_SLV\_RD\_ADDR\_BITLEN]It indicates the address length in bits minus one for a slave-read operation. It is only valid in slave half-duplex mode. (R/W)
\item [SPI\_SLV\_WR\_ADDR\_BITLEN] It indicates the address length in bits minus one for a slave-write operation. It is only valid in slave half-duplex mode. (R/W)
\item [SPI\_SLV\_WRSTA\_DUMMY\_EN]In slave mode, this bit enables the dummy phase for write-status operations. It is only valid in slave half-duplex mode.(R/W)
\item [SPI\_SLV\_RDSTA\_DUMMY\_EN]In slave mode, this bit enables the dummy phase for read-status operations. It is only valid in slave half-duplex mode. (R/W)
\item [SPI\_SLV\_WRBUF\_DUMMY\_EN]In slave mode, this bit enables the dummy phase for write-buffer operations. It is only valid in slave half-duplex mode. (R/W)
\item [SPI\_SLV\_RDBUF\_DUMMY\_EN]In slave mode, this bit enables the dummy phase for read-buffer operations. It is only valid in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_SLAVE2\_REG}{0x40}\label{regdesc:SPISLAVE2REG}
\regfield{SPI\_SLV\_WRBUF\_DUMMY\_CYCLELEN}{8}{24}{00000000}%
\regfield{SPI\_SLV\_RDBUF\_DUMMY\_CYCLELEN}{8}{16}{{0x000}}%
\regfield{SPI\_SLV\_WRSTA\_DUMMY\_CYCLELEN}{8}{8}{{0x000}}%
\regfield{SPI\_SLV\_RDSTA\_DUMMY\_CYCLELEN}{8}{0}{{0x000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_SLV\_WRBUF\_DUMMY\_CYCLELEN] It indicates the number of SPI clock cycles minus one for the dummy phase for write-data operations. It is only valid when SPI\_SLV\_WRBUF\_DUMMY\_EN is set to 1 in slave half-duplex mode. (R/W)
\item [SPI\_SLV\_RDBUF\_DUMMY\_CYCLELEN] It indicates the number of SPI clock cycles minus one for the dummy phase for read-data operations. It is only valid when SPI\_SLV\_RDBUF\_DUMMY\_EN is set to 1 in slave half-duplex mode. (R/W)
\item [SPI\_SLV\_WRSTA\_DUMMY\_CYCLELEN] It indicates the number of SPI clock cycles minus one for the dummy phase for write-status register operations. It is only valid when SPI\_SLV\_WRSTA\_DUMMY\_EN is set to 1 in slave half-duplex mode. (R/W)
\item [SPI\_SLV\_RDSTA\_DUMMY\_CYCLELEN] It indicates the number of SPI clock cycles minus one for the dummy phase for read-status register operations. It is only valid when SPI\_SLV\_RDSTA\_DUMMY\_EN is set to 1 in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_SLAVE3\_REG}{0x44}\label{regdesc:SPISLAVE3REG}
\regfield{SPI\_SLV\_WRSTA\_CMD\_VALUE}{8}{24}{00000000}%
\regfield{SPI\_SLV\_RDSTA\_CMD\_VALUE}{8}{16}{00000000}%
\regfield{SPI\_SLV\_WRBUF\_CMD\_VALUE}{8}{8}{00000000}%
\regfield{SPI\_SLV\_RDBUF\_CMD\_VALUE}{8}{0}{00000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_SLV\_WRSTA\_CMD\_VALUE] Reserved.
\item [SPI\_SLV\_RDSTA\_CMD\_VALUE] Reserved.
\item [SPI\_SLV\_WRBUF\_CMD\_VALUE] Reserved.
\item [SPI\_SLV\_RDBUF\_CMD\_VALUE] Reserved.
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_SLV\_WRBUF\_DLEN\_REG}{0x48}\label{regdesc:SPISLVWRBUFDLENREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{SPI\_SLV\_WRBUF\_DBITLEN}{24}{0}{{0x0000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_SLV\_WRBUF\_DBITLEN] It indicates the length of written data minus one, in multiples of one bit. It is only valid in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_SLV\_RDBUF\_DLEN\_REG}{0x4C}\label{regdesc:SPISLVRDBUFDLENREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{SPI\_SLV\_RDBUF\_DBITLEN}{24}{0}{{0x0000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_SLV\_RDBUF\_DBITLEN]It indicates the length of read data minus one, in multiples of one bit. It is only valid in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_SLV\_RD\_BIT\_REG}{0x64}\label{regdesc:SPISLVRDBITREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{SPI\_SLV\_RDATA\_BIT}{24}{0}{000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_SLV\_RDATA\_BIT]It indicates the bit length of data the master reads from the slave, minus one. It is only valid in slave half-duplex mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_W\textcolor{red}{\it{n}}\_REG (\textcolor{red}{\it{n}}: 0-15)}{0x80+4*\textcolor{red}{\it{n}}}\label{regdesc:SPIWnREG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_W\textcolor{red}{\it{n}}\_REG]Data buffer. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_TX\_CRC\_REG}{0xC0}\label{regdesc:SPITXCRCREG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_TX\_CRC\_REG] Reserved.
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_EXT2\_REG}{0xF8}\label{regdesc:SPIEXT2REG}
\regfield{(reserved)}{29}{3}{00000000000000000000000000000}%
\regfield{SPI\_ST}{3}{0}{000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_ST]The current state of the SPI state machine: (RO) \\
0:  idle state\\
1:  preparation state\\
2:  send command state\\
3:  send data state\\
4:  read data state\\
5:  write data state\\
6:  wait state\\
7:  done state\\
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_CONF\_REG}{0x100}\label{regdesc:SPIDMACONFREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{SPI\_DMA\_CONTINUE}{1}{16}{0}%
\regfield{SPI\_DMA\_TX\_STOP}{1}{15}{0}%
\regfield{SPI\_DMA\_RX\_STOP}{1}{14}{0}%
\regfield{(reserved)}{1}{13}{0}%
\regfield{SPI\_OUT\_DATA\_BURST\_EN}{1}{12}{0}%
\regfield{SPI\_INDSCR\_BURST\_EN}{1}{11}{0}%
\regfield{SPI\_OUTDSCR\_BURST\_EN}{1}{10}{0}%
\regfield{SPI\_OUT\_EOF\_MODE}{1}{9}{1}%
\regfield{(reserved)}{3}{6}{000}%
\regfield{SPI\_AHBM\_RST}{1}{5}{0}%
\regfield{SPI\_AHBM\_FIFO\_RST}{1}{4}{0}%
\regfield{SPI\_OUT\_RST}{1}{3}{0}%
\regfield{SPI\_IN\_RST}{1}{2}{0}%
\regfield{(reserved)}{2}{0}{00}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_DMA\_CONTINUE]This bit enables SPI DMA continuous data TX/RX mode. (R/W)
\item [SPI\_DMA\_TX\_STOP]When in continuous TX/RX mode, setting this bit stops sending data. (R/W)
\item [SPI\_DMA\_RX\_STOP]When in continuous TX/RX mode, setting this bit stops receiving data. (R/W)
\item [SPI\_OUT\_DATA\_BURST\_EN]SPI DMA reads data from memory in burst mode. (R/W)
\item [SPI\_INDSCR\_BURST\_EN] SPI DMA reads inlink descriptor in burst mode. (R/W)
\item [SPI\_OUTDSCR\_BURST\_EN]SPI DMA reads outlink descriptor in burst mode. (R/W)
\item [SPI\_OUT\_EOF\_MODE]DMA out-EOF-flag generation mode. (R/W)\\
1: out-EOF-flag is generated when DMA has popped all data from the FIFO; \\
0: out-EOF-flag is generated when DMA has pushed all data to the FIFO.
\item [SPI\_AHBM\_RST]reset SPI DMA AHB master. (R/W)
\item [SPI\_AHBM\_FIFO\_RST] This bit is used to reset SPI DMA AHB master FIFO pointer. (R/W)
\item [SPI\_OUT\_RST]The bit is used to reset DMA out-FSM and out-data FIFO pointer. (R/W)
\item [SPI\_IN\_RST]The bit is used to reset DMA in-DSM and in-data FIFO pointer. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_OUT\_LINK\_REG}{0x104}\label{regdesc:SPIDMAOUTLINKREG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{SPI\_OUTLINK\_RESTART}{1}{30}{0}%
\regfield{SPI\_OUTLINK\_START}{1}{29}{0}%
\regfield{SPI\_OUTLINK\_STOP}{1}{28}{0}%
\regfield{(reserved)}{8}{20}{00000000}%
\regfield{SPI\_OUTLINK\_ADDR}{20}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_OUTLINK\_RESTART]Set the bit to add new outlink descriptors. (R/W)
\item [SPI\_OUTLINK\_START]Set the bit to start to use outlink descriptor. (R/W)
\item [SPI\_OUTLINK\_STOP]Set the bit to stop to use outlink descriptor. (R/W)
\item [SPI\_OUTLINK\_ADDR]The address of the first outlink descriptor. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_IN\_LINK\_REG}{0x108}\label{regdesc:SPIDMAINLINKREG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{SPI\_INLINK\_RESTART}{1}{30}{0}%
\regfield{SPI\_INLINK\_START}{1}{29}{0}%
\regfield{SPI\_INLINK\_STOP}{1}{28}{0}%
\regfield{(reserved)}{7}{21}{0000000}%
\regfield{SPI\_INLINK\_AUTO\_RET}{1}{20}{0}%
\regfield{SPI\_INLINK\_ADDR}{20}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_INLINK\_RESTART]Set the bit to add new inlink descriptors. (R/W)
\item [SPI\_INLINK\_START]Set the bit to start to use inlink descriptor. (R/W)
\item [SPI\_INLINK\_STOP]Set the bit to stop to use inlink descriptor. (R/W)
\item [SPI\_INLINK\_AUTO\_RET]when the bit is set, inlink descriptor jumps to the next descriptor when a packet is invalid. (R/W)
\item [SPI\_INLINK\_ADDR]The address of the first inlink descriptor. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_STATUS\_REG}{0x10C}\label{regdesc:SPIDMASTATUSREG}
\regfield{(reserved)}{30}{2}{000000000000000000000000000000}%
\regfield{SPI\_DMA\_TX\_EN}{1}{1}{0}%
\regfield{SPI\_DMA\_RX\_EN}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_DMA\_TX\_EN]SPI DMA write-data status bit. (RO)
\item [SPI\_DMA\_RX\_EN]SPI DMA read-data status bit. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_INT\_ENA\_REG}{0x110}\label{regdesc:SPIDMAINTENAREG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{SPI\_OUT\_TOTAL\_EOF\_INT\_ENA}{1}{8}{0}%
\regfield{SPI\_OUT\_EOF\_INT\_ENA}{1}{7}{0}%
\regfield{SPI\_OUT\_DONE\_INT\_ENA}{1}{6}{0}%
\regfield{SPI\_IN\_SUC\_EOF\_INT\_ENA}{1}{5}{0}%
\regfield{SPI\_IN\_ERR\_EOF\_INT\_ENA}{1}{4}{0}%
\regfield{SPI\_IN\_DONE\_INT\_ENA}{1}{3}{0}%
\regfield{SPI\_INLINK\_DSCR\_ERROR\_INT\_ENA}{1}{2}{0}%
\regfield{SPI\_OUTLINK\_DSCR\_ERROR\_INT\_ENA}{1}{1}{0}%
\regfield{SPI\_INLINK\_DSCR\_EMPTY\_INT\_ENA}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_OUT\_TOTAL\_EOF\_INT\_ENA]The interrupt enable bit for the \hyperref[int:SPIOUTTOTALEOFINT]{SPI\_OUT\_TOTAL\_EOF\_INT} interrupt. (R/W)
\item [SPI\_OUT\_EOF\_INT\_ENA]The interrupt enable bit for the \hyperref[int:SPIOUTEOFINT]{SPI\_OUT\_EOF\_INT} interrupt. (R/W)
\item [SPI\_OUT\_DONE\_INT\_ENA]The interrupt enable bit for the \hyperref[int:SPIOUTDONEINT]{SPI\_OUT\_DONE\_INT} interrupt. (R/W)
\item [SPI\_IN\_SUC\_EOF\_INT\_ENA]The interrupt enable bit for the \hyperref[int:SPIINSUCEOFINT]{SPI\_IN\_SUC\_EOF\_INT} interrupt. (R/W)
\item [SPI\_IN\_ERR\_EOF\_INT\_ENA]The interrupt enable bit for the \hyperref[int:SPIINERREOFINT]{SPI\_IN\_ERR\_EOF\_INT} interrupt. (R/W)
\item [SPI\_IN\_DONE\_INT\_ENA]The interrupt enable bit for the \hyperref[int:SPIINDONEINT]{SPI\_IN\_DONE\_INT} interrupt. (R/W)
\item [SPI\_INLINK\_DSCR\_ERROR\_INT\_ENA]The interrupt enable bit for the \hyperref[int:SPIINLINKDSCRERRORINT]{SPI\_INLINK\_DSCR\_ERROR\_INT} interrupt. (R/W)
\item [SPI\_OUTLINK\_DSCR\_ERROR\_INT\_ENA]The interrupt enable bit for the \hyperref[int:SPIOUTLINKDSCRERRORINT]{SPI\_OUTLINK\_DSCR\_ERROR\_INT} interrupt. (R/W)
\item [SPI\_INLINK\_DSCR\_EMPTY\_INT\_ENA]The interrupt enable bit for the \hyperref[int:SPIINLINKDSCREMPTYINT]{SPI\_INLINK\_DSCR\_EMPTY\_INT} interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_INT\_RAW\_REG}{0x114}\label{regdesc:SPIDMAINTRAWREG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{SPI\_OUT\_TOTAL\_EOF\_INT\_RAW}{1}{8}{0}%
\regfield{SPI\_OUT\_EOF\_INT\_RAW}{1}{7}{0}%
\regfield{SPI\_OUT\_DONE\_INT\_RAW}{1}{6}{0}%
\regfield{SPI\_IN\_SUC\_EOF\_INT\_RAW}{1}{5}{0}%
\regfield{SPI\_IN\_ERR\_EOF\_INT\_RAW}{1}{4}{0}%
\regfield{SPI\_IN\_DONE\_INT\_RAW}{1}{3}{0}%
\regfield{SPI\_INLINK\_DSCR\_ERROR\_INT\_RAW}{1}{2}{0}%
\regfield{SPI\_OUTLINK\_DSCR\_ERROR\_INT\_RAW}{1}{1}{0}%
\regfield{SPI\_INLINK\_DSCR\_EMPTY\_INT\_RAW}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_OUT\_TOTAL\_EOF\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:SPIOUTTOTALEOFINT]{SPI\_OUT\_TOTAL\_EOF\_INT} interrupt. (RO)
\item [SPI\_OUT\_EOF\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:SPIOUTEOFINT]{SPI\_OUT\_EOF\_INT} interrupt. (RO)
\item [SPI\_OUT\_DONE\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:SPIOUTDONEINT]{SPI\_OUT\_DONE\_INT} interrupt. (RO)
\item [SPI\_IN\_SUC\_EOF\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:SPIINSUCEOFINT]{SPI\_IN\_SUC\_EOF\_INT} interrupt. (RO)
\item [SPI\_IN\_ERR\_EOF\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:SPIINERREOFINT]{SPI\_IN\_ERR\_EOF\_INT} interrupt. (RO)
\item [SPI\_IN\_DONE\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:SPIINDONEINT]{SPI\_IN\_DONE\_INT} interrupt. (RO)
\item [SPI\_INLINK\_DSCR\_ERROR\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:SPIINLINKDSCRERRORINT]{SPI\_INLINK\_DSCR\_ERROR\_INT} interrupt. (RO)
\item [SPI\_OUTLINK\_DSCR\_ERROR\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:SPIOUTLINKDSCRERRORINT]{SPI\_OUTLINK\_DSCR\_ERROR\_INT} interrupt. (RO)
\item [SPI\_INLINK\_DSCR\_EMPTY\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:SPIINLINKDSCREMPTYINT]{SPI\_INLINK\_DSCR\_EMPTY\_INT} interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_INT\_ST\_REG}{0x118}\label{regdesc:SPIDMAINTSTREG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{SPI\_OUT\_TOTAL\_EOF\_INT\_ST}{1}{8}{0}%
\regfield{SPI\_OUT\_EOF\_INT\_ST}{1}{7}{0}%
\regfield{SPI\_OUT\_DONE\_INT\_ST}{1}{6}{0}%
\regfield{SPI\_IN\_SUC\_EOF\_INT\_ST}{1}{5}{0}%
\regfield{SPI\_IN\_ERR\_EOF\_INT\_ST}{1}{4}{0}%
\regfield{SPI\_IN\_DONE\_INT\_ST}{1}{3}{0}%
\regfield{SPI\_INLINK\_DSCR\_ERROR\_INT\_ST}{1}{2}{0}%
\regfield{SPI\_OUTLINK\_DSCR\_ERROR\_INT\_ST}{1}{1}{0}%
\regfield{SPI\_INLINK\_DSCR\_EMPTY\_INT\_ST}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_OUT\_TOTAL\_EOF\_INT\_ST]The masked interrupt status bit for the \hyperref[int:SPIOUTTOTALEOFINT]{SPI\_OUT\_TOTAL\_EOF\_INT} interrupt. (RO)
\item [SPI\_OUT\_EOF\_INT\_ST]The masked interrupt status bit for the \hyperref[int:SPIOUTEOFINT]{SPI\_OUT\_EOF\_INT} interrupt. (RO)
\item [SPI\_OUT\_DONE\_INT\_ST]The masked interrupt status bit for the
\hyperref[int:SPIOUTDONEINT]{SPI\_OUT\_DONE\_INT} interrupt. (RO)
\item [SPI\_IN\_SUC\_EOF\_INT\_ST]The masked interrupt status bit for the
\hyperref[int:SPIINSUCEOFINT]{SPI\_IN\_SUC\_EOF\_INT} interrupt. (RO)
\item [SPI\_IN\_ERR\_EOF\_INT\_ST]The masked interrupt status bit for the \hyperref[int:SPIINERREOFINT]{SPI\_IN\_ERR\_EOF\_INT} interrupt. (RO)
\item [SPI\_IN\_DONE\_INT\_ST]The masked interrupt status bit for the 
\hyperref[int:SPIINDONEINT]{SPI\_IN\_DONE\_INT} interrupt. (RO)
\item [SPI\_INLINK\_DSCR\_ERROR\_INT\_ST]The masked interrupt status bit for the 
\hyperref[int:SPIINLINKDSCRERRORINT]{SPI\_INLINK\_DSCR\_ERROR\_INT} interrupt. (RO)
\item [SPI\_OUTLINK\_DSCR\_ERROR\_INT\_ST]The masked interrupt status bit for the 
\hyperref[int:SPIOUTLINKDSCRERRORINT]{SPI\_OUTLINK\_DSCR\_ERROR\_INT} interrupt. (RO)
\item [SPI\_INLINK\_DSCR\_EMPTY\_INT\_ST]The masked interrupt status bit for the \hyperref[int:SPIINLINKDSCREMPTYINT]{SPI\_INLINK\_DSCR\_EMPTY\_INT} interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_INT\_CLR\_REG}{0x11C}\label{regdesc:SPIDMAINTCLRREG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{SPI\_OUT\_TOTAL\_EOF\_INT\_CLR}{1}{8}{0}%
\regfield{SPI\_OUT\_EOF\_INT\_CLR}{1}{7}{0}%
\regfield{SPI\_OUT\_DONE\_INT\_CLR}{1}{6}{0}%
\regfield{SPI\_IN\_SUC\_EOF\_INT\_CLR}{1}{5}{0}%
\regfield{SPI\_IN\_ERR\_EOF\_INT\_CLR}{1}{4}{0}%
\regfield{SPI\_IN\_DONE\_INT\_CLR}{1}{3}{0}%
\regfield{SPI\_INLINK\_DSCR\_ERROR\_INT\_CLR}{1}{2}{0}%
\regfield{SPI\_OUTLINK\_DSCR\_ERROR\_INT\_CLR}{1}{1}{0}%
\regfield{SPI\_INLINK\_DSCR\_EMPTY\_INT\_CLR}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_OUT\_TOTAL\_EOF\_INT\_CLR]Set this bit to clear the \hyperref[int:SPIOUTTOTALEOFINT]{SPI\_OUT\_TOTAL\_EOF\_INT} interrupt. (R/W)
\item [SPI\_OUT\_EOF\_INT\_CLR]Set this bit to clear the \hyperref[int:SPIOUTEOFINT]{SPI\_OUT\_EOF\_INT} interrupt. (R/W)
\item [SPI\_OUT\_DONE\_INT\_CLR]Set this bit to clear the \hyperref[int:SPIOUTDONEINT]{SPI\_OUT\_DONE\_INT} interrupt. (R/W)
\item [SPI\_IN\_SUC\_EOF\_INT\_CLR]Set this bit to clear the \hyperref[int:SPIINSUCEOFINT]{SPI\_IN\_SUC\_EOF\_INT} interrupt. (R/W)
\item [SPI\_IN\_ERR\_EOF\_INT\_CLR]Set this bit to clear the \hyperref[int:SPIINERREOFINT]{SPI\_IN\_ERR\_EOF\_INT} interrupt. (R/W)
\item [SPI\_IN\_DONE\_INT\_CLR]Set this bit to clear the \hyperref[int:SPIINDONEINT]{SPI\_IN\_DONE\_INT} interrupt. (R/W)
\item [SPI\_INLINK\_DSCR\_ERROR\_INT\_CLR]Set this bit to clear the \hyperref[int:SPIINLINKDSCRERRORINT]{SPI\_INLINK\_DSCR\_ERROR\_INT} interrupt. (R/W)
\item [SPI\_OUTLINK\_DSCR\_ERROR\_INT\_CLR]Set this bit to clear the \hyperref[int:SPIOUTLINKDSCRERRORINT]{SPI\_OUTLINK\_DSCR\_ERROR\_INT} interrupt. (R/W)
\item [SPI\_INLINK\_DSCR\_EMPTY\_INT\_CLR]Set this bit to clear the \hyperref[int:SPIINLINKDSCREMPTYINT]{SPI\_INLINK\_DSCR\_EMPTY\_INT} interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_IN\_ERR\_EOF\_DES\_ADDR\_REG}{0x120}\label{regdesc:SPIINERREOFDESADDRREG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_IN\_ERR\_EOF\_DES\_ADDR\_REG]The inlink descriptor address when SPI DMA encountered an error in receiving data. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_IN\_SUC\_EOF\_DES\_ADDR\_REG}{0x124}\label{regdesc:SPIINSUCEOFDESADDRREG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_IN\_SUC\_EOF\_DES\_ADDR\_REG]The last inlink descriptor address when SPI DMA encountered EOF. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_INLINK\_DSCR\_REG}{0x128}\label{regdesc:SPIINLINKDSCRREG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_INLINK\_DSCR\_REG]The address of the current inlink descriptor. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_INLINK\_DSCR\_BF0\_REG}{0x12C}\label{regdesc:SPIINLINKDSCRBF0REG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_INLINK\_DSCR\_BF0\_REG]The address of the next inlink descriptor. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_INLINK\_DSCR\_BF1\_REG}{0x130}\label{regdesc:SPIINLINKDSCRBF1REG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_INLINK\_DSCR\_BF1\_REG]The address of the next inlink data buffer. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_OUT\_EOF\_BFR\_DES\_ADDR\_REG}{0x134}\label{regdesc:SPIOUTEOFBFRDESADDRREG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_OUT\_EOF\_BFR\_DES\_ADDR\_REG]The buffer address corresponding to the outlink descriptor that produces EOF. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_OUT\_EOF\_DES\_ADDR\_REG}{0x138}\label{regdesc:SPIOUTEOFDESADDRREG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_OUT\_EOF\_DES\_ADDR\_REG]The last outlink descriptor address when SPI DMA encountered EOF. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_OUTLINK\_DSCR\_REG}{0x13C}\label{regdesc:SPIOUTLINKDSCRREG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_OUTLINK\_DSCR\_REG]The address of the current outlink descriptor. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_OUTLINK\_DSCR\_BF0\_REG}{0x140}\label{regdesc:SPIOUTLINKDSCRBF0REG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_OUTLINK\_DSCR\_BF0\_REG]The address of the next outlink descriptor. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_OUTLINK\_DSCR\_BF1\_REG}{0x144}\label{regdesc:SPIOUTLINKDSCRBF1REG}
\regfield{}{32}{0}{00000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SPI\_OUTLINK\_DSCR\_BF1\_REG]The address of the next outlink data buffer. (RO)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{SPI\_DMA\_RSTATUS\_REG}{0x148}\label{regdesc:SPIDMARSTATUSREG}
\regfield{TX\_FIFO\_EMPTY}{1}{31}{0}%
\regfield{TX\_FIFO\_FULL}{1}{30}{0}%
\regfield{(reserved)}{10}{20}{0000000000}%
\regfield{TX\_DES\_ADDRESS}{20}{0}{00000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [TX\_FIFO\_EMPTY]The SPI DMA TX FIFO is empty. (RO)
\item [TX\_FIFO\_FULL]The SPI DMA TX FIFO is full. (RO)
\item [TX\_DES\_ADDRESS] The LSB of the SPI DMA outlink descriptor address. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SPI\_DMA\_TSTATUS\_REG}{0x14C}\label{regdesc:SPIDMATSTATUSREG}
\regfield{RX\_FIFO\_EMPTY}{1}{31}{0}%
\regfield{RX\_FIFO\_FULL}{1}{30}{0}%
\regfield{(reserved)}{10}{20}{0000000000}%
\regfield{RX\_DES\_ADDRESS}{20}{0}{00000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RX\_FIFO\_EMPTY]The SPI DMA RX FIFO is empty. (RO)
\item [RX\_FIFO\_FULL]The SPI DMA RX FIFO is full. (RO)
\item [RX\_DES\_ADDRESS]The LSB of the SPI DMA inlink descriptor address. (RO)
\end{reglist}\end{regdesc}
\end{register}


