\begin{register}{H}{AXI\_DMA\_IN\_INT\_RAW\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0000+0x68*\regindex{n}}\label{regdesc:AXIDMAININTRAWCHNREG}
\regfield{(reserved)}{21}{11}{000000000000000000000}%
\regfield{AXI\_DMA\_INFIFO\_L3\_UDF\_CH\regindex{n}\_INT\_RAW}{1}{10}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L3\_OVF\_CH\regindex{n}\_INT\_RAW}{1}{9}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L2\_UDF\_CH\regindex{n}\_INT\_RAW}{1}{8}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L2\_OVF\_CH\regindex{n}\_INT\_RAW}{1}{7}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L1\_UDF\_CH\regindex{n}\_INT\_RAW}{1}{6}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L1\_OVF\_CH\regindex{n}\_INT\_RAW}{1}{5}{{0}}%
\regfield{AXI\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_RAW}{1}{4}{{0}}%
\regfield{AXI\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_RAW}{1}{3}{{0}}%
\regfield{AXI\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_RAW}{1}{2}{{0}}%
\regfield{AXI\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_RAW}{1}{1}{{0}}%
\regfield{AXI\_DMA\_IN\_DONE\_CH\regindex{n}\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINDONECHNINTRAW}\item [AXI\_DMA\_IN\_DONE\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_IN\_DONE\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AXIDMAINSUCEOFCHNINTRAW}\item [AXI\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT. For UHCI this bit turns to 1 when the last data byte pointed by one receive descriptor has been received and no data error is detected for RX channel 0. (R/WTC/SS)
\label{fielddesc:AXIDMAINERREOFCHNINTRAW}\item [AXI\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT. Valid only for UHCI. (R/WTC/SS)
\label{fielddesc:AXIDMAINDSCRERRCHNINTRAW}\item [AXI\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AXIDMAINDSCREMPTYCHNINTRAW}\item [AXI\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AXIDMAINFIFOL1OVFCHNINTRAW}\item [AXI\_DMA\_INFIFO\_L1\_OVF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_INFIFO\_L1\_OVF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AXIDMAINFIFOL1UDFCHNINTRAW}\item [AXI\_DMA\_INFIFO\_L1\_UDF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_INFIFO\_L1\_UDF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AXIDMAINFIFOL2OVFCHNINTRAW}\item [AXI\_DMA\_INFIFO\_L2\_OVF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_INFIFO\_L2\_OVF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AXIDMAINFIFOL2UDFCHNINTRAW}\item [AXI\_DMA\_INFIFO\_L2\_UDF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_INFIFO\_L2\_UDF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AXIDMAINFIFOL3OVFCHNINTRAW}\item [AXI\_DMA\_INFIFO\_L3\_OVF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_INFIFO\_L3\_OVF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AXIDMAINFIFOL3UDFCHNINTRAW}\item [AXI\_DMA\_INFIFO\_L3\_UDF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_INFIFO\_L3\_UDF\_CH\regindex{n}\_INT. (R/WTC/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_INT\_ST\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0004+0x68*\regindex{n}}\label{regdesc:AXIDMAININTSTCHNREG}
\regfield{(reserved)}{21}{11}{000000000000000000000}%
\regfield{AXI\_DMA\_INFIFO\_L3\_UDF\_CH\regindex{n}\_INT\_ST}{1}{10}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L3\_OVF\_CH\regindex{n}\_INT\_ST}{1}{9}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L2\_UDF\_CH\regindex{n}\_INT\_ST}{1}{8}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L2\_OVF\_CH\regindex{n}\_INT\_ST}{1}{7}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L1\_UDF\_CH\regindex{n}\_INT\_ST}{1}{6}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L1\_OVF\_CH\regindex{n}\_INT\_ST}{1}{5}{{0}}%
\regfield{AXI\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_ST}{1}{4}{{0}}%
\regfield{AXI\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_ST}{1}{3}{{0}}%
\regfield{AXI\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_ST}{1}{2}{{0}}%
\regfield{AXI\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_ST}{1}{1}{{0}}%
\regfield{AXI\_DMA\_IN\_DONE\_CH\regindex{n}\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINDONECHNINTST}\item [AXI\_DMA\_IN\_DONE\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_IN\_DONE\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAINSUCEOFCHNINTST}\item [AXI\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAINERREOFCHNINTST}\item [AXI\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAINDSCRERRCHNINTST}\item [AXI\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAINDSCREMPTYCHNINTST}\item [AXI\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAINFIFOL2OVFCHNINTST}\item [AXI\_DMA\_INFIFO\_L2\_OVF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_INFIFO\_L2\_OVF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAINFIFOL2UDFCHNINTST}\item [AXI\_DMA\_INFIFO\_L2\_UDF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_INFIFO\_L2\_UDF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAINFIFOL1OVFCHNINTST}\item [AXI\_DMA\_INFIFO\_L1\_OVF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_INFIFO\_L1\_OVF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAINFIFOL1UDFCHNINTST}\item [AXI\_DMA\_INFIFO\_L1\_UDF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_INFIFO\_L1\_UDF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAINFIFOL3OVFCHNINTST}\item [AXI\_DMA\_INFIFO\_L3\_OVF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_INFIFO\_L3\_OVF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAINFIFOL3UDFCHNINTST}\item [AXI\_DMA\_INFIFO\_L3\_UDF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_INFIFO\_L3\_UDF\_CH\regindex{n}\_INT. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_INT\_ENA\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0008+0x68*\regindex{n}}\label{regdesc:AXIDMAININTENACHNREG}
\regfield{(reserved)}{21}{11}{000000000000000000000}%
\regfield{AXI\_DMA\_INFIFO\_L3\_UDF\_CH\regindex{n}\_INT\_ENA}{1}{10}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L3\_OVF\_CH\regindex{n}\_INT\_ENA}{1}{9}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L2\_UDF\_CH\regindex{n}\_INT\_ENA}{1}{8}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L2\_OVF\_CH\regindex{n}\_INT\_ENA}{1}{7}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L1\_UDF\_CH\regindex{n}\_INT\_ENA}{1}{6}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L1\_OVF\_CH\regindex{n}\_INT\_ENA}{1}{5}{{0}}%
\regfield{AXI\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_ENA}{1}{4}{{0}}%
\regfield{AXI\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_ENA}{1}{3}{{0}}%
\regfield{AXI\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_ENA}{1}{2}{{0}}%
\regfield{AXI\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_ENA}{1}{1}{{0}}%
\regfield{AXI\_DMA\_IN\_DONE\_CH\regindex{n}\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINDONECHNINTENA}\item [AXI\_DMA\_IN\_DONE\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_IN\_DONE\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAINSUCEOFCHNINTENA}\item [AXI\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAINERREOFCHNINTENA}\item [AXI\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAINDSCRERRCHNINTENA}\item [AXI\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAINDSCREMPTYCHNINTENA}\item [AXI\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAINFIFOL1OVFCHNINTENA}\item [AXI\_DMA\_INFIFO\_L1\_OVF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_INFIFO\_L1\_OVF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAINFIFOL1UDFCHNINTENA}\item [AXI\_DMA\_INFIFO\_L1\_UDF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_INFIFO\_L1\_UDF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAINFIFOL2OVFCHNINTENA}\item [AXI\_DMA\_INFIFO\_L2\_OVF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_INFIFO\_L2\_OVF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAINFIFOL2UDFCHNINTENA}\item [AXI\_DMA\_INFIFO\_L2\_UDF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_INFIFO\_L2\_UDF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAINFIFOL3VFCHNINTENA}\item [AXI\_DMA\_INFIFO\_L3\_OVF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_INFIFO\_L3\_OVF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAINFIFOL3UDFCHNINTENA}\item [AXI\_DMA\_INFIFO\_L3\_UDF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_INFIFO\_L3\_UDF\_CH\regindex{n}\_INT. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_INT\_CLR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x000C+0x68*\regindex{n}}\label{regdesc:AXIDMAININTCLRCHNREG}
\regfield{(reserved)}{21}{11}{000000000000000000000}%
\regfield{AXI\_DMA\_INFIFO\_L3\_UDF\_CH\regindex{n}\_INT\_CLR}{1}{10}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L3\_OVF\_CH\regindex{n}\_INT\_CLR}{1}{9}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L2\_UDF\_CH\regindex{n}\_INT\_CLR}{1}{8}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L2\_OVF\_CH\regindex{n}\_INT\_CLR}{1}{7}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L1\_UDF\_CH\regindex{n}\_INT\_CLR}{1}{6}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L1\_OVF\_CH\regindex{n}\_INT\_CLR}{1}{5}{{0}}%
\regfield{AXI\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_CLR}{1}{4}{{0}}%
\regfield{AXI\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_CLR}{1}{3}{{0}}%
\regfield{AXI\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_CLR}{1}{2}{{0}}%
\regfield{AXI\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_CLR}{1}{1}{{0}}%
\regfield{AXI\_DMA\_IN\_DONE\_CH\regindex{n}\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINDONECHNINTCLR}\item [AXI\_DMA\_IN\_DONE\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_IN\_DONE\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAINSUCEOFCHNINTCLR}\item [AXI\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAINERREOFCHNINTCLR}\item [AXI\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAINDSCRERRCHNINTCLR}\item [AXI\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAINDSCREMPTYCHNINTCLR}\item [AXI\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAINFIFOL1OVFCHNINTCLR}\item [AXI\_DMA\_INFIFO\_L1\_OVF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_INFIFO\_L1\_OVF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAINFIFOL1UDFCHNINTCLR}\item [AXI\_DMA\_INFIFO\_L1\_UDF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_INFIFO\_L1\_UDF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAINFIFOL2OVFCHNINTCLR}\item [AXI\_DMA\_INFIFO\_L2\_OVF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_INFIFO\_L2\_OVF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAINFIFOL2UDFCHNINTCLR}\item [AXI\_DMA\_INFIFO\_L2\_UDF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_INFIFO\_L2\_UDF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAINFIFOL3OVFCHNINTCLR}\item [AXI\_DMA\_INFIFO\_L3\_OVF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_INFIFO\_L3\_OVF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAINFIFOL3UDFCHNINTCLR}\item [AXI\_DMA\_INFIFO\_L3\_UDF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_INFIFO\_L3\_UDF\_CH\regindex{n}\_INT. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_INT\_RAW\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0138+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTINTRAWCHNREG}
\iftagged{ESP32-P4-latest}{
    \regfield{(reserved)}{21}{11}{000000000000000000000}%
    \regfield{AXI\_DMA\_OUT\_LINK\_SWITCH\_CH\regindex{n}\_INT\_RAW}{1}{10}{{0}}%
}{
    \regfield{(reserved)}{22}{10}{0000000000000000000000}%
}
\regfield{AXI\_DMA\_OUTFIFO\_L3\_UDF\_CH\regindex{n}\_INT\_RAW}{1}{9}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L3\_OVF\_CH\regindex{n}\_INT\_RAW}{1}{8}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L2\_UDF\_CH\regindex{n}\_INT\_RAW}{1}{7}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L2\_OVF\_CH\regindex{n}\_INT\_RAW}{1}{6}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L1\_UDF\_CH\regindex{n}\_INT\_RAW}{1}{5}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L1\_OVF\_CH\regindex{n}\_INT\_RAW}{1}{4}{{0}}%
\regfield{AXI\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_RAW}{1}{3}{{0}}%
\regfield{AXI\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_RAW}{1}{2}{{0}}%
\regfield{AXI\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT\_RAW}{1}{1}{{0}}%
\regfield{AXI\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTDONECHNINTRAW}\item [AXI\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AXIDMAOUTEOFCHNINTRAW}\item [AXI\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AXIDMAOUTDSCRERRCHNINTRAW}\item [AXI\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AXIDMAOUTTOTALEOFCHNINTRAW}\item [AXI\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AXIDMAOUTFIFOL1OVFCHNINTRAW}\item [AXI\_DMA\_OUTFIFO\_L1\_OVF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_OUTFIFO\_L1\_OVF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AXIDMAOUTFIFOL1UDFCHNINTRAW}\item [AXI\_DMA\_OUTFIFO\_L1\_UDF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_OUTFIFO\_L1\_UDF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AXIDMAOUTFIFOL2OVFCHNINTRAW}\item [AXI\_DMA\_OUTFIFO\_L2\_OVF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_OUTFIFO\_L2\_OVF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AXIDMAOUTFIFOL2UDFCHNINTRAW}\item [AXI\_DMA\_OUTFIFO\_L2\_UDF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_OUTFIFO\_L2\_UDF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AXIDMAOUTFIFOL3OVFCHNINTRAW}\item [AXI\_DMA\_OUTFIFO\_L3\_OVF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_OUTFIFO\_L3\_OVF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AXIDMAOUTFIFOL3UDFCHNINTRAW}\item [AXI\_DMA\_OUTFIFO\_L3\_UDF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_OUTFIFO\_L3\_UDF\_CH\regindex{n}\_INT. (R/WTC/SS)
\tagged{ESP32-P4-latest}{
    \label{fielddesc:AXIDMAOUTLINKSWITCHCHNINTRAW}\item [AXI\_DMA\_OUT\_LINK\_SWITCH\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AXI\_DMA\_OUT\_LINK\_SWITCH\_CH\regindex{n}\_INT. (R/WTC/SS)
}
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_INT\_ST\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x013C+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTINTSTCHNREG}
\iftagged{ESP32-P4-latest}{
    \regfield{(reserved)}{21}{11}{000000000000000000000}%
    \regfield{AXI\_DMA\_OUT\_LINK\_SWITCH\_CH\regindex{n}\_INT\_ST}{1}{10}{{0}}%
}{
    \regfield{(reserved)}{22}{10}{0000000000000000000000}%
}
\regfield{AXI\_DMA\_OUTFIFO\_L3\_UDF\_CH\regindex{n}\_INT\_ST}{1}{9}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L3\_OVF\_CH\regindex{n}\_INT\_ST}{1}{8}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L2\_UDF\_CH\regindex{n}\_INT\_ST}{1}{7}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L2\_OVF\_CH\regindex{n}\_INT\_ST}{1}{6}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L1\_UDF\_CH\regindex{n}\_INT\_ST}{1}{5}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L1\_OVF\_CH\regindex{n}\_INT\_ST}{1}{4}{{0}}%
\regfield{AXI\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_ST}{1}{3}{{0}}%
\regfield{AXI\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_ST}{1}{2}{{0}}%
\regfield{AXI\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT\_ST}{1}{1}{{0}}%
\regfield{AXI\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTDONECHNINTST}\item [AXI\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAOUTEOFCHNINTST}\item [AXI\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAOUTDSCRERRCHNINTST}\item [AXI\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAOUTTOTALEOFCHNINTST}\item [AXI\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAOUTFIFOL1OVFCHNINTST}\item [AXI\_DMA\_OUTFIFO\_L1\_OVF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_OUTFIFO\_L1\_OVF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAOUTFIFOL1UDFCHNINTST}\item [AXI\_DMA\_OUTFIFO\_L1\_UDF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_OUTFIFO\_L1\_UDF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAOUTFIFOL2OVFCHNINTST}\item [AXI\_DMA\_OUTFIFO\_L2\_OVF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_OUTFIFO\_L2\_OVF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAOUTFIFOL2UDFCHNINTST}\item [AXI\_DMA\_OUTFIFO\_L2\_UDF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_OUTFIFO\_L2\_UDF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAOUTFIFOL3OVFCHNINTST}\item [AXI\_DMA\_OUTFIFO\_L3\_OVF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_OUTFIFO\_L3\_OVF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AXIDMAOUTFIFOL3UDFCHNINTST}\item [AXI\_DMA\_OUTFIFO\_L3\_UDF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_OUTFIFO\_L3\_UDF\_CH\regindex{n}\_INT. (RO)
\tagged{ESP32-P4-latest}{
    \label{fielddesc:AXIDMAOUTLINKSWITCHCHNINTST}\item [AXI\_DMA\_OUT\_LINK\_SWITCH\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AXI\_DMA\_OUT\_LINK\_SWITCH\_CH\regindex{n}\_INT. (RO)
}
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_INT\_ENA\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0140+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTINTENACHNREG}
\iftagged{ESP32-P4-latest}{
    \regfield{(reserved)}{21}{11}{000000000000000000000}%
    \regfield{AXI\_DMA\_OUT\_LINK\_SWITCH\_CH\regindex{n}\_INT\_ENA}{1}{10}{{0}}%
}{
    \regfield{(reserved)}{22}{10}{0000000000000000000000}%
}
\regfield{AXI\_DMA\_OUTFIFO\_L3\_UDF\_CH\regindex{n}\_INT\_ENA}{1}{9}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L3\_OVF\_CH\regindex{n}\_INT\_ENA}{1}{8}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L2\_UDF\_CH\regindex{n}\_INT\_ENA}{1}{7}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L2\_OVF\_CH\regindex{n}\_INT\_ENA}{1}{6}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L1\_UDF\_CH\regindex{n}\_INT\_ENA}{1}{5}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L1\_OVF\_CH\regindex{n}\_INT\_ENA}{1}{4}{{0}}%
\regfield{AXI\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_ENA}{1}{3}{{0}}%
\regfield{AXI\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_ENA}{1}{2}{{0}}%
\regfield{AXI\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT\_ENA}{1}{1}{{0}}%
\regfield{AXI\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTDONECHNINTENA}\item [AXI\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAOUTEOFCHNINTENA}\item [AXI\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAOUTDSCRERRCHNINTENA}\item [AXI\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAOUTTOTALEOFCHNINTENA}\item [AXI\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAOUTFIFOL1OVFCHNINTENA}\item [AXI\_DMA\_OUTFIFO\_L1\_OVF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_OUTFIFO\_L1\_OVF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAOUTFIFOL1UDFCHNINTENA}\item [AXI\_DMA\_OUTFIFO\_L1\_UDF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_OUTFIFO\_L1\_UDF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAOUTFIFOL2OVFCHNINTENA}\item [AXI\_DMA\_OUTFIFO\_L2\_OVF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_OUTFIFO\_L2\_OVF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAOUTFIFOL2UDFCHNINTENA}\item [AXI\_DMA\_OUTFIFO\_L2\_UDF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_OUTFIFO\_L2\_UDF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAOUTFIFOL3OVFCHNINTENA}\item [AXI\_DMA\_OUTFIFO\_L3\_OVF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_OUTFIFO\_L3\_OVF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AXIDMAOUTFIFOL3UDFCHNINTENA}\item [AXI\_DMA\_OUTFIFO\_L3\_UDF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_OUTFIFO\_L3\_UDF\_CH\regindex{n}\_INT. (R/W)
\tagged{ESP32-P4-latest}{
    \label{fielddesc:AXIDMAOUTLINKSWITCHCHNINTENA}\item [AXI\_DMA\_OUT\_LINK\_SWITCH\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AXI\_DMA\_OUT\_LINK\_SWITCH\_CH\regindex{n}\_INT. (RO)
}
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_INT\_CLR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0144+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTINTCLRCHNREG}
\iftagged{ESP32-P4-latest}{
    \regfield{(reserved)}{21}{11}{000000000000000000000}%
    \regfield{AXI\_DMA\_OUT\_LINK\_SWITCH\_CH\regindex{n}\_INT\_CLR}{1}{10}{{0}}%
}{
    \regfield{(reserved)}{22}{10}{0000000000000000000000}%
}
\regfield{AXI\_DMA\_OUTFIFO\_L3\_UDF\_CH\regindex{n}\_INT\_CLR}{1}{9}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L3\_OVF\_CH\regindex{n}\_INT\_CLR}{1}{8}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L2\_UDF\_CH\regindex{n}\_INT\_CLR}{1}{7}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L2\_OVF\_CH\regindex{n}\_INT\_CLR}{1}{6}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L1\_UDF\_CH\regindex{n}\_INT\_CLR}{1}{5}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L1\_OVF\_CH\regindex{n}\_INT\_CLR}{1}{4}{{0}}%
\regfield{AXI\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_CLR}{1}{3}{{0}}%
\regfield{AXI\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_CLR}{1}{2}{{0}}%
\regfield{AXI\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT\_CLR}{1}{1}{{0}}%
\regfield{AXI\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTDONECHNINTCLR}\item [AXI\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAOUTEOFCHNINTCLR}\item [AXI\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAOUTDSCRERRCHNINTCLR}\item [AXI\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAOUTTOTALEOFCHNINTCLR}\item [AXI\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAOUTFIFOL1OVFCHNINTCLR}\item [AXI\_DMA\_OUTFIFO\_L1\_OVF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_OUTFIFO\_L1\_OVF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAOUTFIFOL1UDFCHNINTCLR}\item [AXI\_DMA\_OUTFIFO\_L1\_UDF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_OUTFIFO\_L1\_UDF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAOUTFIFOL2OVFCHNINTCLR}\item [AXI\_DMA\_OUTFIFO\_L2\_OVF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_OUTFIFO\_L2\_OVF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAOUTFIFOL2UDFCHNINTCLR}\item [AXI\_DMA\_OUTFIFO\_L2\_UDF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_OUTFIFO\_L2\_UDF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAOUTFIFOL3OVFCHNINTCLR}\item [AXI\_DMA\_OUTFIFO\_L3\_OVF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_OUTFIFO\_L3\_OVF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AXIDMAOUTFIFOL3UDFCHNINTCLR}\item [AXI\_DMA\_OUTFIFO\_L3\_UDF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_OUTFIFO\_L3\_UDF\_CH\regindex{n}\_INT. (WT)
\tagged{ESP32-P4-latest}{
    \label{fielddesc:AXIDMAOUTLINKSWITCHCHNINTCLR}\item [AXI\_DMA\_OUT\_LINK\_SWITCH\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AXI\_DMA\_OUT\_LINK\_SWITCH\_CH\regindex{n}\_INT. (RO)
}
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_CONF0\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0010+0x68*\regindex{n}}\label{regdesc:AXIDMAINCONF0CHNREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{AXI\_DMA\_INDSCR\_BURST\_EN\_CH\regindex{n}}{1}{9}{{0}}%
\regfield{AXI\_DMA\_IN\_ECC\_AEC\_EN\_CH\regindex{n}}{1}{8}{{0}}%
\regfield{AXI\_DMA\_IN\_CMD\_DISABLE\_CH\regindex{n}}{1}{7}{{0}}%
\regfield{AXI\_DMA\_IN\_BURST\_SIZE\_SEL\_CH\regindex{n}}{3}{4}{{0}}%
\regfield{AXI\_DMA\_IN\_ETM\_EN\_CH\regindex{n}}{1}{3}{{0}}%
\regfield{AXI\_DMA\_MEM\_TRANS\_EN\_CH\regindex{n}}{1}{2}{{0}}%
\regfield{AXI\_DMA\_IN\_LOOP\_TEST\_CH\regindex{n}}{1}{1}{{0}}%
\regfield{AXI\_DMA\_IN\_RST\_CH\regindex{n}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINRSTCHN}\item [AXI\_DMA\_IN\_RST\_CH\regindex{n}] Write 1 and then 0 to reset RX channel \regindex{n} FSM and RX FIFO pointer.(R/W)
\label{fielddesc:AXIDMAINLOOPTESTCHN}\item [AXI\_DMA\_IN\_LOOP\_TEST\_CH\regindex{n}] Reserved. (R/W)
\label{fielddesc:AXIDMAMEMTRANSENCHN}\item [AXI\_DMA\_MEM\_TRANS\_EN\_CH\regindex{n}] Configures whether to enable memory-to-memory data transfer.\\
0: Disable\\
1: Enable\\(R/W)
\label{fielddesc:AXIDMAINETMENCHN}\item [AXI\_DMA\_IN\_ETM\_EN\_CH\regindex{n}] Configures whether to enable ETM control for RX channel \regindex{n}.\\
0: Disable\\
1: Enable\\(R/W)
\label{fielddesc:AXIDMAINBURSTSIZESELCHN}\item [AXI\_DMA\_IN\_BURST\_SIZE\_SEL\_CH\regindex{n}] Configures the burst length for RX channel \regindex{n}.\\
0: 8 bytes\\
1: 16 bytes\\
2: 32 bytes\\
3: 64 bytes\\
4: 128 bytes\\
5 \verb+~+ 7: Invalid\\ (R/W)
\label{fielddesc:AXIDMAINCMDDISABLECHN}\item [AXI\_DMA\_IN\_CMD\_DISABLE\_CH\regindex{n}] Configures whether to disable command on RX channel \regindex{n}.\\
0: Enable\\
1: Disable\\ (R/W)
\label{fielddesc:AXIDMAINECCAECENCHN}\item [AXI\_DMA\_IN\_ECC\_AEC\_EN\_CH\regindex{n}] Configures whether AXI DMA can access external memory space for ECC and AES via RX channel \regindex{n}.\\
0: Not access\\
1: Access\\ (R/W)
\label{fielddesc:AXIDMAINDSCRBURSTENCHN}\item [AXI\_DMA\_INDSCR\_BURST\_EN\_CH\regindex{n}] Configures whether to enable INCR burst transfer for RX channel \regindex{n} to read descriptors when accessing internal memory.\\
0: Disable\\
1: Enable\\(R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_CONF1\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0014+0x68*\regindex{n}}\label{regdesc:AXIDMAINCONF1CHNREG}
\regfield{(reserved)}{19}{13}{0000000000000000000}%
\regfield{AXI\_DMA\_IN\_CHECK\_OWNER\_CH\regindex{n}}{1}{12}{{0}}%
\regfield{(reserved)}{12}{0}{000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINCHECKOWNERCHN}\item [AXI\_DMA\_IN\_CHECK\_OWNER\_CH\regindex{n}] Configures whether to enable owner bit check for RX channel \regindex{n}.\\
0: Disable\\
1: Enable\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_POP\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x001C+0x68*\regindex{n}}\label{regdesc:AXIDMAINPOPCHNREG}
\regfield{(reserved)}{19}{13}{0000000000000000000}%
\regfield{AXI\_DMA\_INFIFO\_POP\_CH\regindex{n}}{1}{12}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_RDATA\_CH\regindex{n}}{12}{0}{{0x800}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINFIFORDATACHN}\item [AXI\_DMA\_INFIFO\_RDATA\_CH\regindex{n}] Represents the data popped from AXI DMA RX FIFO. (RO)
\label{fielddesc:AXIDMAINFIFOPOPCHN}\item [AXI\_DMA\_INFIFO\_POP\_CH\regindex{n}] Configures whether to pop data from AXI DMA RX FIFO.\\
0: Invalid. No effect\\
1: Pop\\ (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_LINK1\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0020+0x68*\regindex{n}}\label{regdesc:AXIDMAINLINK1CHNREG}
\regfield{(reserved)}{27}{5}{000000000000000000000000000}%
\regfield{AXI\_DMA\_INLINK\_PARK\_CH\regindex{n}}{1}{4}{{1}}%
\regfield{AXI\_DMA\_INLINK\_RESTART\_CH\regindex{n}}{1}{3}{{0}}%
\regfield{AXI\_DMA\_INLINK\_START\_CH\regindex{n}}{1}{2}{{0}}%
\regfield{AXI\_DMA\_INLINK\_STOP\_CH\regindex{n}}{1}{1}{{0}}%
\regfield{AXI\_DMA\_INLINK\_AUTO\_RET\_CH\regindex{n}}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINLINKAUTORETCHN}\item [AXI\_DMA\_INLINK\_AUTO\_RET\_CH\regindex{n}] Configures whether to return to the current receive descriptor's address when there are some errors in current receiving data.\\
0: Not return\\
1: Return\\(R/W)
\label{fielddesc:AXIDMAINLINKSTOPCHN}\item [AXI\_DMA\_INLINK\_STOP\_CH\regindex{n}] Configures whether to stop RX channel \regindex{n} from receiving data.\\
0: Invalid. No effect\\
1: Stop\\ (WT)
\label{fielddesc:AXIDMAINLINKSTARTCHN}\item [AXI\_DMA\_INLINK\_START\_CH\regindex{n}] Configures whether to enable RX channel \regindex{n} for data transfer.\\
0: Disable\\
1: Enable\\ (WT)
\label{fielddesc:AXIDMAINLINKRESTARTCHN}\item [AXI\_DMA\_INLINK\_RESTART\_CH\regindex{n}] Configures whether to restart RX channel \regindex{n} for AXI DMA transfer.\\
0: Invalid. No effect\\
1: Restart\\ (WT)
\label{fielddesc:AXIDMAINLINKPARKCHN}\item [AXI\_DMA\_INLINK\_PARK\_CH\regindex{n}] Represents the status of the receive descriptor's FSM.\\
0: Running\\
1: Idle\\ (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_LINK2\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0024+0x68*\regindex{n}}\label{regdesc:AXIDMAINLINK2CHNREG}
\regfield{AXI\_DMA\_INLINK\_ADDR\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINLINKADDRCHN}\item [AXI\_DMA\_INLINK\_ADDR\_CH\regindex{n}] Represents the first receive descriptor's address. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_CRC\_INIT\_DATA\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0048+0x68*\regindex{n}}\label{regdesc:AXIDMAINCRCINITDATACHNREG}
\regfield{AXI\_DMA\_IN\_CRC\_INIT\_DATA\_CH\regindex{n}}{32}{0}{{0xffffffff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINCRCINITDATACHN}\item [AXI\_DMA\_IN\_CRC\_INIT\_DATA\_CH\regindex{n}] Configures the CRC initial value for RX channel \regindex{n}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_RX\_CRC\_WIDTH\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x004C+0x68*\regindex{n}}\label{regdesc:AXIDMARXCRCWIDTHCHNREG}
\regfield{(reserved)}{29}{3}{00000000000000000000000000000}%
\regfield{AXI\_DMA\_RX\_CRC\_LAUTCH\_FLGA\_CH\regindex{n}}{1}{2}{{0}}%
\regfield{AXI\_DMA\_RX\_CRC\_WIDTH\_CH\regindex{n}}{2}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMARXCRCWIDTHCHN}\item [AXI\_DMA\_RX\_CRC\_WIDTH\_CH\regindex{n}] Configures the CRC result width for RX channel \regindex{n}.
0: $\leq$ 8 bits\\
1: $\leq$ 16 bits\\
2: $\leq$ 24 bits\\
3: $\leq$ 32 bits\\ (R/W)
\label{fielddesc:AXIDMARXCRCLAUTCHFLGACHN}\item [AXI\_DMA\_RX\_CRC\_LAUTCH\_FLGA\_CH\regindex{n}] Write 1 and then 0 to latch the values of AXI\_DMA\_RX\_CRC\_EN\_ADDR\_CH\regindex{n}, AXI\_DMA\_RX\_CRC\_DATA\_EN\_ADDR\_CH\regindex{n}, AXI\_DMA\_RX\_CRC\_EN\_WR\_DATA\_CH\regindex{n}, and AXI\_DMA\_RX\_CRC\_DATA\_EN\_WR\_DATA\_CH\regindex{n}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_CRC\_CLEAR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0050+0x68*\regindex{n}}\label{regdesc:AXIDMAINCRCCLEARCHNREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{AXI\_DMA\_IN\_CRC\_CLEAR\_CH\regindex{n}\_REG}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINCRCCLEARCHNREG}\item [AXI\_DMA\_IN\_CRC\_CLEAR\_CH\regindex{n}\_REG] Configures whether to clear the CRC result for RX channel \regindex{n}.\\
0: Not clear\\
1: Clear\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_CRC\_FINAL\_RESULT\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0054+0x68*\regindex{n}}\label{regdesc:AXIDMAINCRCFINALRESULTCHNREG}
\regfield{AXI\_DMA\_IN\_CRC\_FINAL\_RESULT\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINCRCFINALRESULTCHN}\item [AXI\_DMA\_IN\_CRC\_FINAL\_RESULT\_CH\regindex{n}] Represents the CRC result for RX channel \regindex{n}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_RX\_CRC\_EN\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x005C+0x68*\regindex{n}}\label{regdesc:AXIDMARXCRCENADDRCHNREG}
\regfield{AXI\_DMA\_RX\_CRC\_EN\_ADDR\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMARXCRCENADDRCHN}\item [AXI\_DMA\_RX\_CRC\_EN\_ADDR\_CH\regindex{n}] Configures at which bit of the CRC result the AXI\_DMA\_RX\_CRC\_EN\_WR\_DATA\_CH\regindex{n}\_REG register targets for TX channel \regindex{n}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_RX\_CRC\_DATA\_EN\_WR\_DATA\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0060+0x68*\regindex{n}}\label{regdesc:AXIDMARXCRCDATAENWRDATACHNREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{AXI\_DMA\_RX\_CRC\_DATA\_EN\_WR\_DATA\_CH\regindex{n}}{16}{0}{{0x00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMARXCRCDATAENWRDATACHN}\item [AXI\_DMA\_RX\_CRC\_DATA\_EN\_WR\_DATA\_CH\regindex{n}] Configures whether to include each bit of the data in the CRC calculation matrix for TX channel \regindex{n}.\\
0: Not include\\
1: Include\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_RX\_CRC\_DATA\_EN\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0064+0x68*\regindex{n}}\label{regdesc:AXIDMARXCRCDATAENADDRCHNREG}
\regfield{AXI\_DMA\_RX\_CRC\_DATA\_EN\_ADDR\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMARXCRCDATAENADDRCHN}\item [AXI\_DMA\_RX\_CRC\_DATA\_EN\_ADDR\_CH\regindex{n}] Configures at which bit of the CRC result the AXI\_DMA\_RX\_CRC\_DATA\_EN\_WR\_DATA\_CH\regindex{n}\_REG register targets for TX channel \regindex{n}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_CONF0\_CH\regindex{n}\_REG(\regindex{n}: 0-2)}{0x0148+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTCONF0CHNREG}
\regfield{(reserved)}{21}{11}{000000000000000000000}%
\regfield{AXI\_DMA\_OUTDSCR\_BURST\_EN\_CH\regindex{n}}{1}{10}{{0}}%
\regfield{AXI\_DMA\_OUT\_ECC\_AEC\_EN\_CH\regindex{n}}{1}{9}{{0}}%
\regfield{AXI\_DMA\_OUT\_CMD\_DISABLE\_CH\regindex{n}}{1}{8}{{0}}%
\regfield{AXI\_DMA\_OUT\_BURST\_SIZE\_SEL\_CH\regindex{n}}{3}{5}{{0}}%
\regfield{AXI\_DMA\_OUT\_ETM\_EN\_CH\regindex{n}}{1}{4}{{0}}%
\regfield{AXI\_DMA\_OUT\_EOF\_MODE\_CH\regindex{n}}{1}{3}{{1}}%
\regfield{AXI\_DMA\_OUT\_AUTO\_WRBACK\_CH\regindex{n}}{1}{2}{{0}}%
\regfield{AXI\_DMA\_OUT\_LOOP\_TEST\_CH\regindex{n}}{1}{1}{{0}}%
\regfield{AXI\_DMA\_OUT\_RST\_CH\regindex{n}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTRSTCHN}\item [AXI\_DMA\_OUT\_RST\_CH\regindex{n}] Configures the reset state of TX channel \regindex{n} FSM and TX FIFO pointer.\\
0: Release reset\\
1: Reset\\(R/W)
\label{fielddesc:AXIDMAOUTLOOPTESTCHN}\item [AXI\_DMA\_OUT\_LOOP\_TEST\_CH\regindex{n}] Reserved. (R/W)
\label{fielddesc:AXIDMAOUTAUTOWRBACKCHN}\item [AXI\_DMA\_OUT\_AUTO\_WRBACK\_CH\regindex{n}] Configures whether to enable automatic outlink write-back when all the data in TX FIFO has been transmitted.\\
0: Disable\\
1: Enable\\(R/W)
\label{fielddesc:AXIDMAOUTEOFMODECHN}\item [AXI\_DMA\_OUT\_EOF\_MODE\_CH\regindex{n}] Configures when to generate EOF flag.\\
0: EOF flag for TX channel \regindex{n} is generated when data to be transmitted has been pushed into FIFO in AXI DMA.\\
1: EOF flag for TX channel \regindex{n} is generated when data to be transmitted has been popped from FIFO in AXI DMA.\\ (R/W)
\label{fielddesc:AXIDMAOUTETMENCHN}\item [AXI\_DMA\_OUT\_ETM\_EN\_CH\regindex{n}] Configures whether to enable ETM control for TX channel \regindex{n}.\\
0: Disable\\
1: Enable\\( (R/W)
\label{fielddesc:AXIDMAOUTBURSTSIZESELCHN}\item [AXI\_DMA\_OUT\_BURST\_SIZE\_SEL\_CH\regindex{n}] Configures the burst length for TX channel \regindex{n}.\\
0: 8 bytes\\
1: 16 bytes\\
2: 32 bytes\\
3: 64 bytes\\
4: 128 bytes\\
5 \verb+~+ 7: Invalid\\ (R/W)
\label{fielddesc:AXIDMAOUTCMDDISABLECHN}\item [AXI\_DMA\_OUT\_CMD\_DISABLE\_CH\regindex{n}] Configures whether to disable command on TX channel \regindex{n}.\\
0: Enable\\
1: Disable\\ (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{AXI\_DMA\_OUT\_CONF0\_CH\regindex{n}\_REG(\regindex{n}: 0-2)}{0x0148+0x68*\regindex{n}}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]


\label{fielddesc:AXIDMAOUTECCAECENCHN}\item [AXI\_DMA\_OUT\_ECC\_AEC\_EN\_CH\regindex{n}] Configures whether AXI DMA can access external memory space for ECC and AES via TX channel \regindex{n}.\\
0: Not access\\
1: Access\\ (R/W)
\label{fielddesc:AXIDMAOUTDSCRBURSTENCHN}\item [AXI\_DMA\_OUTDSCR\_BURST\_EN\_CH\regindex{n}] Configures whether to enable INCR burst transfer for TX channel \regindex{n} reading descriptors when accessing internal memory.\\
0: Disable\\
1: Enable\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_CONF1\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x014C+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTCONF1CHNREG}
\regfield{(reserved)}{19}{13}{0000000000000000000}%
\regfield{AXI\_DMA\_OUT\_CHECK\_OWNER\_CH\regindex{n}}{1}{12}{{0}}%
\regfield{(reserved)}{12}{0}{000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTCHECKOWNERCHN}\item [AXI\_DMA\_OUT\_CHECK\_OWNER\_CH\regindex{n}] Configures whether to enable owner bit check for TX channel \regindex{n}.\\
0: Disable\\
1: Enable\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_PUSH\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0154+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTPUSHCHNREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{AXI\_DMA\_OUTFIFO\_PUSH\_CH\regindex{n}}{1}{9}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_WDATA\_CH\regindex{n}}{9}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTFIFOWDATACHN}\item [AXI\_DMA\_OUTFIFO\_WDATA\_CH\regindex{n}] Represents the data that need to be pushed into AXI DMA TX FIFO. (R/W)
\label{fielddesc:AXIDMAOUTFIFOPUSHCHN}\item [AXI\_DMA\_OUTFIFO\_PUSH\_CH\regindex{n}] Configures whether to push data into AXI DMA TX FIFO.\\
0: Invalid. No effect\\
1: Push\\ (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_LINK1\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0158+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTLINK1CHNREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{AXI\_DMA\_OUTLINK\_PARK\_CH\regindex{n}}{1}{3}{{1}}%
\regfield{AXI\_DMA\_OUTLINK\_RESTART\_CH\regindex{n}}{1}{2}{{0}}%
\regfield{AXI\_DMA\_OUTLINK\_START\_CH\regindex{n}}{1}{1}{{0}}%
\regfield{AXI\_DMA\_OUTLINK\_STOP\_CH\regindex{n}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTLINKSTOPCHN}\item [AXI\_DMA\_OUTLINK\_STOP\_CH\regindex{n}] Configures whether to stop TX channel \regindex{n} from transmitting data.\\
0: Invalid. No effect\\
1: Stop\\ (WT)
\label{fielddesc:AXIDMAOUTLINKSTARTCHN}\item [AXI\_DMA\_OUTLINK\_START\_CH\regindex{n}] Configures whether to enable TX channel \regindex{n} for data transfer.\\
0: Disable\\
1: Enable\\ (WT)
\label{fielddesc:AXIDMAOUTLINKRESTARTCHN}\item [AXI\_DMA\_OUTLINK\_RESTART\_CH\regindex{n}] Configures whether to restart TX channel \regindex{n} for AXI DMA transfer.\\
0: Invalid. No effect\\
1: Restart\\ (WT)
\label{fielddesc:AXIDMAOUTLINKPARKCHN}\item [AXI\_DMA\_OUTLINK\_PARK\_CH\regindex{n}] Represents the status of the transmit descriptor's FSM.\\
0: Running\\
1: Idle\\ (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_LINK2\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x015C+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTLINK2CHNREG}
\regfield{AXI\_DMA\_OUTLINK\_ADDR\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTLINKADDRCHN}\item [AXI\_DMA\_OUTLINK\_ADDR\_CH\regindex{n}] Represents the first transmit descriptor's address. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_CRC\_INIT\_DATA\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0180+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTCRCINITDATACHNREG}
\regfield{AXI\_DMA\_OUT\_CRC\_INIT\_DATA\_CH\regindex{n}}{32}{0}{{0xffffffff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTCRCINITDATACHN}\item [AXI\_DMA\_OUT\_CRC\_INIT\_DATA\_CH\regindex{n}] Configures the CRC initial value for TX channel \regindex{n}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_TX\_CRC\_WIDTH\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0184+0x68*\regindex{n}}\label{regdesc:AXIDMATXCRCWIDTHCHNREG}
\regfield{(reserved)}{29}{3}{00000000000000000000000000000}%
\regfield{AXI\_DMA\_TX\_CRC\_LAUTCH\_FLGA\_CH\regindex{n}}{1}{2}{{0}}%
\regfield{AXI\_DMA\_TX\_CRC\_WIDTH\_CH\regindex{n}}{2}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMATXCRCWIDTHCHN}\item [AXI\_DMA\_TX\_CRC\_WIDTH\_CH\regindex{n}] Configures the CRC result width for TX channel \regindex{n}.
0: $\leq$ 8 bits\\
1: $\leq$ 16 bits\\
2: $\leq$ 24 bits\\
3: $\leq$ 32 bits\\
(R/W)
\label{fielddesc:AXIDMATXCRCLAUTCHFLGACHN}\item [AXI\_DMA\_TX\_CRC\_LAUTCH\_FLGA\_CH\regindex{n}] Write 1 and then 0 to latch the values of AXI\_DMA\_TX\_CRC\_EN\_ADDR\_CH\regindex{n}, AXI\_DMA\_TX\_CRC\_DATA\_EN\_ADDR\_CH\regindex{n}, AXI\_DMA\_TX\_CRC\_EN\_WR\_DATA\_CH\regindex{n}, and AXI\_DMA\_TX\_CRC\_DATA\_EN\_WR\_DATA\_CH\regindex{n}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_CRC\_CLEAR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0188+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTCRCCLEARCHNREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{AXI\_DMA\_OUT\_CRC\_CLEAR\_CH\regindex{n}\_REG}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTCRCCLEARCHNREG}\item [AXI\_DMA\_OUT\_CRC\_CLEAR\_CH\regindex{n}\_REG] Configures whether to clear the CRC result for TX channel \regindex{n}.\\
0: Not clear\\
1: Clear\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_CRC\_FINAL\_RESULT\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x018C+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTCRCFINALRESULTCHNREG}
\regfield{AXI\_DMA\_OUT\_CRC\_FINAL\_RESULT\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTCRCFINALRESULTCHN}\item [AXI\_DMA\_OUT\_CRC\_FINAL\_RESULT\_CH\regindex{n}] Represents the CRC result for TX channel \regindex{n}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_TX\_CRC\_EN\_WR\_DATA\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0190+0x68*\regindex{n}}\label{regdesc:AXIDMATXCRCENWRDATACHNREG}
\regfield{AXI\_DMA\_TX\_CRC\_EN\_WR\_DATA\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMATXCRCENWRDATACHN}\item [AXI\_DMA\_TX\_CRC\_EN\_WR\_DATA\_CH\regindex{n}] Configures whether to include each bit of the intermediate result in the CRC calculation matrix for TX channel \regindex{n}.\\
0: Not include\\
1: Include\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_TX\_CRC\_EN\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0194+0x68*\regindex{n}}\label{regdesc:AXIDMATXCRCENADDRCHNREG}
\regfield{AXI\_DMA\_TX\_CRC\_EN\_ADDR\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMATXCRCENADDRCHN}\item [AXI\_DMA\_TX\_CRC\_EN\_ADDR\_CH\regindex{n}] Configures at which bit of the CRC result the AXI\_DMA\_TX\_CRC\_EN\_WR\_DATA\_CH\regindex{n}\_REG register targets for TX channel \regindex{n}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_TX\_CRC\_DATA\_EN\_WR\_DATA\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0198+0x68*\regindex{n}}\label{regdesc:AXIDMATXCRCDATAENWRDATACHNREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{AXI\_DMA\_TX\_CRC\_DATA\_EN\_WR\_DATA\_CH\regindex{n}}{16}{0}{{0x00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMATXCRCDATAENWRDATACHN}\item [AXI\_DMA\_TX\_CRC\_DATA\_EN\_WR\_DATA\_CH\regindex{n}] Configures whether to include each bit of the input data in the CRC calculation matrix for TX channel \regindex{n}.\\
0: Not include\\
1: Include\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_TX\_CRC\_DATA\_EN\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x019C+0x68*\regindex{n}}\label{regdesc:AXIDMATXCRCDATAENADDRCHNREG}
\regfield{AXI\_DMA\_TX\_CRC\_DATA\_EN\_ADDR\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMATXCRCDATAENADDRCHN}\item [AXI\_DMA\_TX\_CRC\_DATA\_EN\_ADDR\_CH\regindex{n}] Configures at which bit of the CRC result the AAXI\_DMA\_TX\_CRC\_DATA\_EN\_WR\_DATA\_CH\regindex{n}\_REG register targets for TX channel \regindex{n}.(R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_ARB\_TIMEOUT\_REG}{0x0270}\label{regdesc:AXIDMAARBTIMEOUTREG}
\regfield{AXI\_DMA\_ARB\_TIMEOUT\_RX}{16}{16}{{0x00}}%
\regfield{AXI\_DMA\_ARB\_TIMEOUT\_TX}{16}{0}{{0x00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAARBTIMEOUTTX}\item [AXI\_DMA\_ARB\_TIMEOUT\_TX] Configures the time slot for TX. Measurement unit: AXI bus clock cycle. (R/W)
\label{fielddesc:AXIDMAARBTIMEOUTRX}\item [AXI\_DMA\_ARB\_TIMEOUT\_RX] Configures the time slot for RX. Measurement unit: AXI bus clock cycle. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_WEIGHT\_EN\_REG}{0x0274}\label{regdesc:AXIDMAWEIGHTENREG}
\regfield{(reserved)}{30}{2}{000000000000000000000000000000}%
\regfield{AXI\_DMA\_WEIGHT\_EN\_RX}{1}{1}{{0}}%
\regfield{AXI\_DMA\_WEIGHT\_EN\_TX}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAWEIGHTENTX}\item [AXI\_DMA\_WEIGHT\_EN\_TX] Configures whether to enable weight arbitration for TX.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:AXIDMAWEIGHTENRX}\item [AXI\_DMA\_WEIGHT\_EN\_RX] Configures whether to enable weight arbitration for RX.\\
0: Disable\\
1: Enable\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_MEM\_CONF\_REG}{0x0278}\label{regdesc:AXIDMAINMEMCONFREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{AXI\_DMA\_OUT\_MEM\_FORCE\_PD}{1}{5}{{0}}%
\regfield{AXI\_DMA\_OUT\_MEM\_FORCE\_PU}{1}{4}{{0}}%
\regfield{AXI\_DMA\_OUT\_MEM\_CLK\_FORCE\_EN}{1}{3}{{0}}%
\regfield{AXI\_DMA\_IN\_MEM\_FORCE\_PD}{1}{2}{{0}}%
\regfield{AXI\_DMA\_IN\_MEM\_FORCE\_PU}{1}{1}{{0}}%
\regfield{AXI\_DMA\_IN\_MEM\_CLK\_FORCE\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINMEMCLKFORCEEN}\item [AXI\_DMA\_IN\_MEM\_CLK\_FORCE\_EN] Configures memory clock gating for RX.\\
0: Support clock only when AXI DMA accesses memory\\
1: Always force the clock on\\ (R/W)
\label{fielddesc:AXIDMAINMEMFORCEPU}\item [AXI\_DMA\_IN\_MEM\_FORCE\_PU] Configures whether to force power up memory for RX.\\
0: Not force power up\\
1: Force power up\\ (R/W)
\label{fielddesc:AXIDMAINMEMFORCEPD}\item [AXI\_DMA\_IN\_MEM\_FORCE\_PD] Configures whether to force power down memory for RX.\\
0: Not force power down\\
1: Force power down\\ (R/W)
\label{fielddesc:AXIDMAOUTMEMCLKFORCEEN}\item [AXI\_DMA\_OUT\_MEM\_CLK\_FORCE\_EN] Configures memory clock gating for TX.\\
0: Support clock only when AXI DMA accesses memory\\
1: Always force the clock on\\ (R/W)
\label{fielddesc:AXIDMAOUTMEMFORCEPU}\item [AXI\_DMA\_OUT\_MEM\_FORCE\_PU] Configures whether to force power up memory for TX.\\
0: Not force power up\\
1: Force power up\\ (R/W)
\label{fielddesc:AXIDMAOUTMEMFORCEPD}\item [AXI\_DMA\_OUT\_MEM\_FORCE\_PD] Configures whether to force power down memory for TX.\\
0: Not force power down\\
1: Force power down\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_INTR\_MEM\_START\_ADDR\_REG}{0x027C}\label{regdesc:AXIDMAINTRMEMSTARTADDRREG}
\regfield{AXI\_DMA\_ACCESS\_INTR\_MEM\_START\_ADDR}{32}{0}{{0x30100000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAACCESSINTRMEMSTARTADDR}\item [AXI\_DMA\_ACCESS\_INTR\_MEM\_START\_ADDR] Configures the start address of the accessible internal memory address space. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_INTR\_MEM\_END\_ADDR\_REG}{0x0280}\label{regdesc:AXIDMAINTRMEMENDADDRREG}
\regfield{AXI\_DMA\_ACCESS\_INTR\_MEM\_END\_ADDR}{32}{0}{{0x8fffffff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAACCESSINTRMEMENDADDR}\item [AXI\_DMA\_ACCESS\_INTR\_MEM\_END\_ADDR] Configures the end address of the accessible internal memory address space. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_EXTR\_MEM\_START\_ADDR\_REG}{0x0284}\label{regdesc:AXIDMAEXTRMEMSTARTADDRREG}
\regfield{AXI\_DMA\_ACCESS\_EXTR\_MEM\_START\_ADDR}{32}{0}{{0x30100000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAACCESSEXTRMEMSTARTADDR}\item [AXI\_DMA\_ACCESS\_EXTR\_MEM\_START\_ADDR] Configures the start address of the accessible external memory address space. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_EXTR\_MEM\_END\_ADDR\_REG}{0x0288}\label{regdesc:AXIDMAEXTRMEMENDADDRREG}
\regfield{AXI\_DMA\_ACCESS\_EXTR\_MEM\_END\_ADDR}{32}{0}{{0x8fffffff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAACCESSEXTRMEMENDADDR}\item [AXI\_DMA\_ACCESS\_EXTR\_MEM\_END\_ADDR] Configures the end address of the accessible external memory address space. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_RESET\_AVAIL\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x028C+0x4*\regindex{n}}\label{regdesc:AXIDMAINRESETAVAILCHNREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{AXI\_DMA\_IN\_RESET\_AVAIL\_CH\regindex{n}}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINRESETAVAILCHN}\item [AXI\_DMA\_IN\_RESET\_AVAIL\_CH\regindex{n}] Represents whether RX channel \regindex{n} can be reset.\\
0: Cannot be reset by software\\
1: Can be reset\\ (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_RESET\_AVAIL\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0298+0x4*\regindex{n}}\label{regdesc:AXIDMAOUTRESETAVAILCHNREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{AXI\_DMA\_OUT\_RESET\_AVAIL\_CH\regindex{n}}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTRESETAVAILCHN}\item [AXI\_DMA\_OUT\_RESET\_AVAIL\_CH\regindex{n}] Represents whether TX channel \regindex{n} can be reset.\\
0: Cannot be reset by software\\
1: Can be reset\\. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_MISC\_CONF\_REG}{0x02A8}\label{regdesc:AXIDMAMISCCONFREG}
\regfield{(reserved)}{27}{5}{000000000000000000000000000}%
\regfield{AXI\_DMA\_CLK\_EN}{1}{4}{{0}}%
\regfield{AXI\_DMA\_ARB\_PRI\_DIS}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{0}%
\regfield{AXI\_DMA\_AXIM\_RST\_RD\_INTER}{1}{1}{{0}}%
\regfield{AXI\_DMA\_AXIM\_RST\_WR\_INTER}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAAXIMRSTWRINTER}\item [AXI\_DMA\_AXIM\_RST\_WR\_INTER] Write 1 and then 0 to reset the internal AXI write FSM. (R/W)
\label{fielddesc:AXIDMAAXIMRSTRDINTER}\item [AXI\_DMA\_AXIM\_RST\_RD\_INTER] Write 1 and then 0 to reset the internal AXI read FSM. (R/W)
\label{fielddesc:AXIDMAARBPRIDIS}\item [AXI\_DMA\_ARB\_PRI\_DIS] Configures whether to disable the priority arbitration.\\
0: Enable\\
1: Disable\\ (R/W)
\label{fielddesc:AXIDMACLKEN}\item [AXI\_DMA\_CLK\_EN] Configures AXI DMA clock gating.\\
0: Support clock only when the application writes registers.\\
1: Always force the clock on for registers.\\  (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_INFIFO\_STATUS\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0018+0x68*\regindex{n}}\label{regdesc:AXIDMAINFIFOSTATUSCHNREG}
\regfield{AXI\_DMA\_IN\_BUF\_HUNGRY\_CH\regindex{n}}{1}{31}{{0}}%
\regfield{AXI\_DMA\_IN\_REMAIN\_UNDER\_8B\_CH\regindex{n}}{1}{30}{{0}}%
\regfield{AXI\_DMA\_IN\_REMAIN\_UNDER\_7B\_CH\regindex{n}}{1}{29}{{0}}%
\regfield{AXI\_DMA\_IN\_REMAIN\_UNDER\_6B\_CH\regindex{n}}{1}{28}{{0}}%
\regfield{AXI\_DMA\_IN\_REMAIN\_UNDER\_5B\_CH\regindex{n}}{1}{27}{{0}}%
\regfield{AXI\_DMA\_IN\_REMAIN\_UNDER\_4B\_CH\regindex{n}}{1}{26}{{0}}%
\regfield{AXI\_DMA\_IN\_REMAIN\_UNDER\_3B\_CH\regindex{n}}{1}{25}{{0}}%
\regfield{AXI\_DMA\_IN\_REMAIN\_UNDER\_2B\_CH\regindex{n}}{1}{24}{{0}}%
\regfield{AXI\_DMA\_IN\_REMAIN\_UNDER\_1B\_CH\regindex{n}}{1}{23}{{0}}%
\regfield{(reserved)}{5}{18}{00000}%
\regfield{AXI\_DMA\_INFIFO\_L2\_OVF\_CH\regindex{n}}{1}{17}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L2\_UDF\_CH\regindex{n}}{1}{16}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L2\_EMPTY\_CH\regindex{n}}{1}{15}{{1}}%
\regfield{AXI\_DMA\_INFIFO\_L2\_FULL\_CH\regindex{n}}{1}{14}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L1\_OVF\_CH\regindex{n}}{1}{13}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L1\_UDF\_CH\regindex{n}}{1}{12}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L1\_EMPTY\_CH\regindex{n}}{1}{11}{{1}}%
\regfield{AXI\_DMA\_INFIFO\_L1\_FULL\_CH\regindex{n}}{1}{10}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L3\_OVF\_CH\regindex{n}}{1}{9}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L3\_UDF\_CH\regindex{n}}{1}{8}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L3\_CNT\_CH\regindex{n}}{6}{2}{{0}}%
\regfield{AXI\_DMA\_INFIFO\_L3\_EMPTY\_CH\regindex{n}}{1}{1}{{1}}%
\regfield{AXI\_DMA\_INFIFO\_L3\_FULL\_CH\regindex{n}}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINFIFOL3FULLCHN}\item [AXI\_DMA\_INFIFO\_L3\_FULL\_CH\regindex{n}] Represents whether L3 RX FIFO is full.\\
0: Not Full\\
1: Full\\ (RO)
\label{fielddesc:AXIDMAINFIFOL3EMPTYCHN}\item [AXI\_DMA\_INFIFO\_L3\_EMPTY\_CH\regindex{n}] Represents whether L3 RX FIFO is empty.\\
0: Not empty\\
1: Empty\\ (RO)
\label{fielddesc:AXIDMAINFIFOL3CNTCHN}\item [AXI\_DMA\_INFIFO\_L3\_CNT\_CH\regindex{n}] Represents the number of data bytes in L3 RX FIFO for RX channel \regindex{n}. (RO)
\label{fielddesc:AXIDMAINFIFOL3UDFCHN}\item [AXI\_DMA\_INFIFO\_L3\_UDF\_CH\regindex{n}] Represents whether L3 RX FIFO underflows.\\
0: No underflow\\
1: Underflow\\ (RO)
\label{fielddesc:AXIDMAINFIFOL3OVFCHN}\item [AXI\_DMA\_INFIFO\_L3\_OVF\_CH\regindex{n}] Represents whether L3 RX FIFO overflows.\\
0: No overflow\\
1: Overflow\\ (RO)
\label{fielddesc:AXIDMAINFIFOL1FULLCHN}\item [AXI\_DMA\_INFIFO\_L1\_FULL\_CH\regindex{n}] Represents whether L1 RX FIFO is full.\\
0: Not Full\\
1: Full\\ (RO)
\label{fielddesc:AXIDMAINFIFOL1EMPTYCHN}\item [AXI\_DMA\_INFIFO\_L1\_EMPTY\_CH\regindex{n}] Represents whether L1 RX FIFO is empty.\\
0: Not empty\\
1: Empty\\ (RO)
\label{fielddesc:AXIDMAINFIFOL1UDFCHN}\item [AXI\_DMA\_INFIFO\_L1\_UDF\_CH\regindex{n}] Represents whether L1 RX FIFO underflows.\\
0: No underflow\\
1: Underflow\\ (RO)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{AXI\_DMA\_INFIFO\_STATUS\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0018+0x68*\regindex{n}}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:AXIDMAINFIFOL1OVFCHN}\item [AXI\_DMA\_INFIFO\_L1\_OVF\_CH\regindex{n}] Represents whether L1 RX FIFO overflows.\\
0: No overflow\\
1: Overflow\\ (RO)
\label{fielddesc:AXIDMAINFIFOL2FULLCHN}\item [AXI\_DMA\_INFIFO\_L2\_FULL\_CH\regindex{n}] Represents whether L2 RX FIFO is full.\\
0: Not Full\\
1: Full\\ (RO)
\label{fielddesc:AXIDMAINFIFOL2EMPTYCHN}\item [AXI\_DMA\_INFIFO\_L2\_EMPTY\_CH\regindex{n}] Represents whether L1 RX FIFO is empty.\\
0: Not empty\\
1: Empty\\ (RO)
\label{fielddesc:AXIDMAINFIFOL2UDFCHN}\item [AXI\_DMA\_INFIFO\_L2\_UDF\_CH\regindex{n}] Represents whether L2 RX FIFO underflows.\\
0: No underflow\\
1: Underflow\\ (RO)
\label{fielddesc:AXIDMAINFIFOL2OVFCHN}\item [AXI\_DMA\_INFIFO\_L2\_OVF\_CH\regindex{n}] Represents whether L2 RX FIFO overflows.\\
0: No overflow\\
1: Overflow\\ (RO)
\label{fielddesc:AXIDMAINREMAINUNDER1BCHN}\item [AXI\_DMA\_IN\_REMAIN\_UNDER\_1B\_CH\regindex{n}] Reserved.(RO)
\label{fielddesc:AXIDMAINREMAINUNDER2BCHN}\item [AXI\_DMA\_IN\_REMAIN\_UNDER\_2B\_CH\regindex{n}] Reserved.(RO)
\label{fielddesc:AXIDMAINREMAINUNDER3BCHN}\item [AXI\_DMA\_IN\_REMAIN\_UNDER\_3B\_CH\regindex{n}] Reserved.(RO)
\label{fielddesc:AXIDMAINREMAINUNDER4BCHN}\item [AXI\_DMA\_IN\_REMAIN\_UNDER\_4B\_CH\regindex{n}] Reserved.(RO)
\label{fielddesc:AXIDMAINREMAINUNDER5BCHN}\item [AXI\_DMA\_IN\_REMAIN\_UNDER\_5B\_CH\regindex{n}] Reserved.(RO)
\label{fielddesc:AXIDMAINREMAINUNDER6BCHN}\item [AXI\_DMA\_IN\_REMAIN\_UNDER\_6B\_CH\regindex{n}] Reserved.(RO)
\label{fielddesc:AXIDMAINREMAINUNDER7BCHN}\item [AXI\_DMA\_IN\_REMAIN\_UNDER\_7B\_CH\regindex{n}] Reserved.(RO)
\label{fielddesc:AXIDMAINREMAINUNDER8BCHN}\item [AXI\_DMA\_IN\_REMAIN\_UNDER\_8B\_CH\regindex{n}] Reserved.(RO)
\label{fielddesc:AXIDMAINBUFHUNGRYCHN}\item [AXI\_DMA\_IN\_BUF\_HUNGRY\_CH\regindex{n}] Reserved.(RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_STATE\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0028+0x68*\regindex{n}}\label{regdesc:AXIDMAINSTATECHNREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{AXI\_DMA\_IN\_STATE\_CH\regindex{n}}{3}{20}{{0}}%
\regfield{AXI\_DMA\_IN\_DSCR\_STATE\_CH\regindex{n}}{2}{18}{{0}}%
\regfield{AXI\_DMA\_INLINK\_DSCR\_ADDR\_CH\regindex{n}}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINLINKDSCRADDRCHN}\item [AXI\_DMA\_INLINK\_DSCR\_ADDR\_CH\regindex{n}] Represents the lower 18 bits of the next receive descriptor address that is pre-read (but not processed yet). If the current receive descriptor is the last descriptor, then this field represents the address of the current receive descriptor. (RO)
\label{fielddesc:AXIDMAINDSCRSTATECHN}\item [AXI\_DMA\_IN\_DSCR\_STATE\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:AXIDMAINSTATECHN}\item [AXI\_DMA\_IN\_STATE\_CH\regindex{n}] Reserved. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_SUC\_EOF\_DES\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x002C+0x68*\regindex{n}}\label{regdesc:AXIDMAINSUCEOFDESADDRCHNREG}
\regfield{AXI\_DMA\_IN\_SUC\_EOF\_DES\_ADDR\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINSUCEOFDESADDRCHN}\item [AXI\_DMA\_IN\_SUC\_EOF\_DES\_ADDR\_CH\regindex{n}] Represents the address of the receive descriptor when the EOF bit in this descriptor is 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_ERR\_EOF\_DES\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0030+0x68*\regindex{n}}\label{regdesc:AXIDMAINERREOFDESADDRCHNREG}
\regfield{AXI\_DMA\_IN\_ERR\_EOF\_DES\_ADDR\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINERREOFDESADDRCHN}\item [AXI\_DMA\_IN\_ERR\_EOF\_DES\_ADDR\_CH\regindex{n}] Represents the address of the receive descriptor when there are some errors in the currently received data. Valid only for UHCI. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_DSCR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0034+0x68*\regindex{n}}\label{regdesc:AXIDMAINDSCRCHNREG}
\regfield{AXI\_DMA\_INLINK\_DSCR\_CH\regindex{n}}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINLINKDSCRCHN}\item [AXI\_DMA\_INLINK\_DSCR\_CH\regindex{n}] Represents the address of the next receive descriptor x+1 pointed by the current receive descriptor that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_DSCR\_BF0\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0038+0x68*\regindex{n}}\label{regdesc:AXIDMAINDSCRBF0CHNREG}
\regfield{AXI\_DMA\_INLINK\_DSCR\_BF0\_CH\regindex{n}}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINLINKDSCRBF0CHN}\item [AXI\_DMA\_INLINK\_DSCR\_BF0\_CH\regindex{n}] Represents the address of the current receive descriptor x that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_DSCR\_BF1\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x003C+0x68*\regindex{n}}\label{regdesc:AXIDMAINDSCRBF1CHNREG}
\regfield{AXI\_DMA\_INLINK\_DSCR\_BF1\_CH\regindex{n}}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAINLINKDSCRBF1CHN}\item [AXI\_DMA\_INLINK\_DSCR\_BF1\_CH\regindex{n}] Represents the address of the previous receive descriptor x-1 that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUTFIFO\_STATUS\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0150+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTFIFOSTATUSCHNREG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{AXI\_DMA\_OUT\_REMAIN\_UNDER\_8B\_CH\regindex{n}}{1}{30}{{1}}%
\regfield{AXI\_DMA\_OUT\_REMAIN\_UNDER\_7B\_CH\regindex{n}}{1}{29}{{1}}%
\regfield{AXI\_DMA\_OUT\_REMAIN\_UNDER\_6B\_CH\regindex{n}}{1}{28}{{1}}%
\regfield{AXI\_DMA\_OUT\_REMAIN\_UNDER\_5B\_CH\regindex{n}}{1}{27}{{1}}%
\regfield{AXI\_DMA\_OUT\_REMAIN\_UNDER\_4B\_CH\regindex{n}}{1}{26}{{1}}%
\regfield{AXI\_DMA\_OUT\_REMAIN\_UNDER\_3B\_CH\regindex{n}}{1}{25}{{1}}%
\regfield{AXI\_DMA\_OUT\_REMAIN\_UNDER\_2B\_CH\regindex{n}}{1}{24}{{1}}%
\regfield{AXI\_DMA\_OUT\_REMAIN\_UNDER\_1B\_CH\regindex{n}}{1}{23}{{1}}%
\regfield{(reserved)}{5}{18}{00000}%
\regfield{AXI\_DMA\_OUTFIFO\_L2\_OVF\_CH\regindex{n}}{1}{17}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L2\_UDF\_CH\regindex{n}}{1}{16}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L2\_EMPTY\_CH\regindex{n}}{1}{15}{{1}}%
\regfield{AXI\_DMA\_OUTFIFO\_L2\_FULL\_CH\regindex{n}}{1}{14}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L1\_OVF\_CH\regindex{n}}{1}{13}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L1\_UDF\_CH\regindex{n}}{1}{12}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L1\_EMPTY\_CH\regindex{n}}{1}{11}{{1}}%
\regfield{AXI\_DMA\_OUTFIFO\_L1\_FULL\_CH\regindex{n}}{1}{10}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L3\_OVF\_CH\regindex{n}}{1}{9}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L3\_UDF\_CH\regindex{n}}{1}{8}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L3\_CNT\_CH\regindex{n}}{6}{2}{{0}}%
\regfield{AXI\_DMA\_OUTFIFO\_L3\_EMPTY\_CH\regindex{n}}{1}{1}{{1}}%
\regfield{AXI\_DMA\_OUTFIFO\_L3\_FULL\_CH\regindex{n}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTFIFOL3FULLCHN}\item [AXI\_DMA\_OUTFIFO\_L3\_FULL\_CH\regindex{n}] Represents whether L3 TX FIFO is full.\\
0: Not Full\\
1: Full\\ (RO)
\label{fielddesc:AXIDMAOUTFIFOL3EMPTYCHN}\item [AXI\_DMA\_OUTFIFO\_L3\_EMPTY\_CH\regindex{n}] Represents whether L3 TX FIFO is empty.\\
0: Not empty\\
1: Empty\\ (RO)
\label{fielddesc:AXIDMAOUTFIFOL3CNTCHN}\item [AXI\_DMA\_OUTFIFO\_L3\_CNT\_CH\regindex{n}] Represents the number of data bytes in L3 TX FIFO for TX channel \regindex{n}. (RO)
\label{fielddesc:AXIDMAOUTFIFOL3UDFCHN}\item [AXI\_DMA\_OUTFIFO\_L3\_UDF\_CH\regindex{n}] Represents whether L3 TX FIFO underflows.\\
0: No underflow\\
1: Underflow\\ (RO)
\label{fielddesc:AXIDMAOUTFIFOL3OVFCHN}\item [AXI\_DMA\_OUTFIFO\_L3\_OVF\_CH\regindex{n}] Represents whether L3 TX FIFO overflows.\\
0: No overflow\\
1: Overflow\\ (RO)
\label{fielddesc:AXIDMAOUTFIFOL1FULLCHN}\item [AXI\_DMA\_OUTFIFO\_L1\_FULL\_CH\regindex{n}] Represents whether L1 TX FIFO is full.\\
0: Not Full\\
1: Full\\ (RO)
\label{fielddesc:AXIDMAOUTFIFOL1EMPTYCHN}\item [AXI\_DMA\_OUTFIFO\_L1\_EMPTY\_CH\regindex{n}] Represents whether L1 TX FIFO is empty.\\
0: Not empty\\
1: Empty\\ (RO)
\label{fielddesc:AXIDMAOUTFIFOL1UDFCHN}\item [AXI\_DMA\_OUTFIFO\_L1\_UDF\_CH\regindex{n}] Represents whether L1 TX FIFO underflows.\\
0: No underflow\\
1: Underflow\\ (RO)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{AXI\_DMA\_OUTFIFO\_STATUS\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0150+0x68*\regindex{n}}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:AXIDMAOUTFIFOL1OVFCHN}\item [AXI\_DMA\_OUTFIFO\_L1\_OVF\_CH\regindex{n}] Represents whether L1 TX FIFO overflows.\\
0: No overflow\\
1: Overflow\\ (RO)
\label{fielddesc:AXIDMAOUTFIFOL2FULLCHN}\item [AXI\_DMA\_OUTFIFO\_L2\_FULL\_CH\regindex{n}] Represents whether L2 TX FIFO is full.\\
0: Not Full\\
1: Full\\ (RO)
\label{fielddesc:AXIDMAOUTFIFOL2EMPTYCHN}\item [AXI\_DMA\_OUTFIFO\_L2\_EMPTY\_CH\regindex{n}] Represents whether L2 TX FIFO is empty.\\
0: Not empty\\
1: Empty\\ (RO)
\label{fielddesc:AXIDMAOUTFIFOL2UDFCHN}\item [AXI\_DMA\_OUTFIFO\_L2\_UDF\_CH\regindex{n}] Represents whether L2 TX FIFO underflows.\\
0: No underflow\\
1: Underflow\\ (RO)
\label{fielddesc:AXIDMAOUTFIFOL2OVFCHN}\item [AXI\_DMA\_OUTFIFO\_L2\_OVF\_CH\regindex{n}] Represents whether L2 TX FIFO overflows.\\
0: No overflow\\
1: Overflow\\ (RO)
\label{fielddesc:AXIDMAOUTREMAINUNDER1BCHN}\item [AXI\_DMA\_OUT\_REMAIN\_UNDER\_1B\_CH\regindex{n}] Reserved.(RO)
\label{fielddesc:AXIDMAOUTREMAINUNDER2BCHN}\item [AXI\_DMA\_OUT\_REMAIN\_UNDER\_2B\_CH\regindex{n}] Reserved.(RO)
\label{fielddesc:AXIDMAOUTREMAINUNDER3BCHN}\item [AXI\_DMA\_OUT\_REMAIN\_UNDER\_3B\_CH\regindex{n}] Reserved.(RO)
\label{fielddesc:AXIDMAOUTREMAINUNDER4BCHN}\item [AXI\_DMA\_OUT\_REMAIN\_UNDER\_4B\_CH\regindex{n}] Reserved.(RO)
\label{fielddesc:AXIDMAOUTREMAINUNDER5BCHN}\item [AXI\_DMA\_OUT\_REMAIN\_UNDER\_5B\_CH\regindex{n}] Reserved.(RO)
\label{fielddesc:AXIDMAOUTREMAINUNDER6BCHN}\item [AXI\_DMA\_OUT\_REMAIN\_UNDER\_6B\_CH\regindex{n}] Reserved.(RO)
\label{fielddesc:AXIDMAOUTREMAINUNDER7BCHN}\item [AXI\_DMA\_OUT\_REMAIN\_UNDER\_7B\_CH\regindex{n}] Reserved.(RO)
\label{fielddesc:AXIDMAOUTREMAINUNDER8BCHN}\item [AXI\_DMA\_OUT\_REMAIN\_UNDER\_8B\_CH\regindex{n}] Reserved.(RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_STATE\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0160+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTSTATECHNREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{AXI\_DMA\_OUT\_STATE\_CH\regindex{n}}{3}{20}{{0}}%
\regfield{AXI\_DMA\_OUT\_DSCR\_STATE\_CH\regindex{n}}{2}{18}{{0}}%
\regfield{AXI\_DMA\_OUTLINK\_DSCR\_ADDR\_CH\regindex{n}}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTLINKDSCRADDRCHN}\item [AXI\_DMA\_OUTLINK\_DSCR\_ADDR\_CH\regindex{n}] Represents the lower 18 bits of the next transmit descriptor address that is pre-read (but not processed yet). If the current transmit descriptor is the last descriptor, then this field represents the address of the current transmit descriptor. (RO)
\label{fielddesc:AXIDMAOUTDSCRSTATECHN}\item [AXI\_DMA\_OUT\_DSCR\_STATE\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:AXIDMAOUTSTATECHN}\item [AXI\_DMA\_OUT\_STATE\_CH\regindex{n}] Reserved. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_EOF\_DES\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0164+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTEOFDESADDRCHNREG}
\regfield{AXI\_DMA\_OUT\_EOF\_DES\_ADDR\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTEOFDESADDRCHN}\item [AXI\_DMA\_OUT\_EOF\_DES\_ADDR\_CH\regindex{n}] Represents the address of the transmit descriptor when the EOF bit in this descriptor is 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_EOF\_BFR\_DES\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0168+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTEOFBFRDESADDRCHNREG}
\regfield{AXI\_DMA\_OUT\_EOF\_BFR\_DES\_ADDR\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTEOFBFRDESADDRCHN}\item [AXI\_DMA\_OUT\_EOF\_BFR\_DES\_ADDR\_CH\regindex{n}] Represents the address of the transmit descriptor before the last transmit descriptor. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_DSCR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x016C+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTDSCRCHNREG}
\regfield{AXI\_DMA\_OUTLINK\_DSCR\_CH\regindex{n}}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTLINKDSCRCHN}\item [AXI\_DMA\_OUTLINK\_DSCR\_CH\regindex{n}] Represents the address of the next transmit descriptor y+1 pointed by the current transmit descriptor that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_DSCR\_BF0\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0170+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTDSCRBF0CHNREG}
\regfield{AXI\_DMA\_OUTLINK\_DSCR\_BF0\_CH\regindex{n}}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTLINKDSCRBF0CHN}\item [AXI\_DMA\_OUTLINK\_DSCR\_BF0\_CH\regindex{n}] Represents the address of the current transmit descriptor y that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_DSCR\_BF1\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0174+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTDSCRBF1CHNREG}
\regfield{AXI\_DMA\_OUTLINK\_DSCR\_BF1\_CH\regindex{n}}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAOUTLINKDSCRBF1CHN}\item [AXI\_DMA\_OUTLINK\_DSCR\_BF1\_CH\regindex{n}] Represents the address of the previous transmit descriptor y-1 that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\tagged{ESP32-P4-latest}{
    \begin{register}{H}{AXI\_DMA\_LINK\_SWITCH\_STATE\_REG}{0x02DC}\label{regdesc:AXIDMALINKSWITCHSTATEREG}
    \regfield{(reserved)}{29}{3}{00000000000000000000000000000}%
    \regfield{AXI\_DMA\_LINK\_SWITCH\_STATE\_CH2}{1}{2}{{0}}%
    \regfield{AXI\_DMA\_LINK\_SWITCH\_STATE\_CH1}{1}{1}{{0}}%
    \regfield{AXI\_DMA\_LINK\_SWITCH\_STATE\_CH0}{1}{0}{{0}}%
    \reglabel{Reset}\regnewline%
    \begin{regdesc}\begin{reglist}
    \label{fielddesc:AXIDMALINKSWITCHSTATECHN}\item [AXI\_DMA\_LINK\_SWITCH\_STATE\_CH\regindex{n}] Configures whether to switch the linked lists read by AXI DMA. \\
    0: Not switch\\
    1: Switch\\ (R/W)
    \end{reglist}\end{regdesc}
    \end{register}
}


\begin{register}{H}{AXI\_DMA\_IN\_PRI\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0040+0x68*\regindex{n}}\label{regdesc:AXIDMAINPRICHNREG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{AXI\_DMA\_RX\_ARB\_WEIGH\_OPT\_DIR\_CH\regindex{n}}{1}{8}{{0}}%
\regfield{AXI\_DMA\_RX\_CH\_ARB\_WEIGH\_CH\regindex{n}}{4}{4}{{0x0}}%
\regfield{AXI\_DMA\_RX\_PRI\_CH\regindex{n}}{4}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMARXPRICHN}\item [AXI\_DMA\_RX\_PRI\_CH\regindex{n}] Configures the priority of RX channel \regindex{n}. The larger the value, the higher the priority. \\
Value range: 0 \verb+~+ 5. (R/W)
\label{fielddesc:AXIDMARXCHARBWEIGHCHN}\item [AXI\_DMA\_RX\_CH\_ARB\_WEIGH\_CH\regindex{n}] Configures the weight (i.e the number of tokens) of RX channel \regindex{n}.\\
Value range: 0 \verb+~+ 15. (R/W)
\label{fielddesc:AXIDMARXARBWEIGHOPTDIRCHN}\item [AXI\_DMA\_RX\_ARB\_WEIGH\_OPT\_DIR\_CH\regindex{n}] Configures whether to enable weight optimization for RX channel \regindex{n}.\\
0: Enable\\
1: Disable\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_PRI\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0178+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTPRICHNREG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{AXI\_DMA\_TX\_ARB\_WEIGH\_OPT\_DIR\_CH\regindex{n}}{1}{8}{{0}}%
\regfield{AXI\_DMA\_TX\_CH\_ARB\_WEIGH\_CH\regindex{n}}{4}{4}{{0x0}}%
\regfield{AXI\_DMA\_TX\_PRI\_CH\regindex{n}}{4}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMATXPRICHN}\item [AXI\_DMA\_TX\_PRI\_CH\regindex{n}] Configures the priority of RX channel \regindex{n}.  The larger the value, the higher the priority. \\
Value range: 0 \verb+~+ 5. (R/W)
\label{fielddesc:AXIDMATXCHARBWEIGHCHN}\item [AXI\_DMA\_TX\_CH\_ARB\_WEIGH\_CH\regindex{n}] Configures the weight (i.e the number of tokens) of TX channel \regindex{n}.\\
Value range: 0 \verb+~+ 15. (R/W)
\label{fielddesc:AXIDMATXARBWEIGHOPTDIRCHN}\item [AXI\_DMA\_TX\_ARB\_WEIGH\_OPT\_DIR\_CH\regindex{n}] Configures whether to enable weight optimization for RX channel \regindex{n}.\\
0: Enable\\
1: Disable\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_IN\_PERI\_SEL\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0044+0x68*\regindex{n}}\label{regdesc:AXIDMAINPERISELCHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{AXI\_DMA\_PERI\_IN\_SEL\_CH\regindex{n}}{6}{0}{{0x3f}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAPERIINSELCHN}\item [AXI\_DMA\_PERI\_IN\_SEL\_CH\regindex{n}] Configures the peripheral connected to RX channel \regindex{n}.\\
0: LCD\_CAM\\
1: SPI2\\
2: SPI3\\
3: PARLIO\\
4: AES\\
5: SHA\\
6 \verb+~+ 15: Dummy-6 \verb+~+ Dummy-15\\
16 \verb+~+ 63: Invalid\\
(R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_OUT\_PERI\_SEL\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x017C+0x68*\regindex{n}}\label{regdesc:AXIDMAOUTPERISELCHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{AXI\_DMA\_PERI\_OUT\_SEL\_CH\regindex{n}}{6}{0}{{0x3f}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMAPERIOUTSELCHN}\item [AXI\_DMA\_PERI\_OUT\_SEL\_CH\regindex{n}] Configures the peripheral connected to TX channel \regindex{n}.\\
0: LCD\_CAM\\
1: SPI2\\
2: SPI3\\
3: PARLIO\\
4: AES\\
5: SHA\\
6 \verb+~+ 15: Dummy-6 \verb+~+ Dummy-15\\
16 \verb+~+ 63: Invalid\\
(R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_RX\_CRC\_EN\_WR\_DATA\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0058+0x68*\regindex{n}}\label{regdesc:AXIDMARXCRCENWRDATACHNREG}
\regfield{AXI\_DMA\_RX\_CRC\_EN\_WR\_DATA\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMARXCRCENWRDATACHN}\item [AXI\_DMA\_RX\_CRC\_EN\_WR\_DATA\_CH\regindex{n}] Configures whether to include each bit of the intermediate result in the CRC calculation matrix for RX channel \regindex{n}.\\
0: Not include\\
1: Include\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AXI\_DMA\_DATE\_REG}{0x02D8}\label{regdesc:AXIDMADATEREG}
\regfield{AXI\_DMA\_DATE}{32}{0}{{0x2303140}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AXIDMADATE}\item [AXI\_DMA\_DATE] Version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}
