\begin{register}{H}{RMT\_CH\regindex{n}CONF0\_REG (\regindex{n}: 0-3)}{\hexprefix{}0010+8*\regindex{n}}\label{regdesc:RMTCHNCONF0REG}
\regfield{(reserved)}{2}{30}{00}%
\regfield{RMT\_CARRIER\_OUT\_LV\_CH\regindex{n}}{1}{29}{{1}}%
\regfield{RMT\_CARRIER\_EN\_CH\regindex{n}}{1}{28}{{1}}%
\regfield{RMT\_CARRIER\_EFF\_EN\_CH\regindex{n}}{1}{27}{{1}}%
\regfield{RMT\_MEM\_SIZE\_CH\regindex{n}}{3}{24}{{\hexprefix{}1}}%
\regfield{RMT\_IDLE\_THRES\_CH\regindex{n}}{16}{8}{{\hexprefix{}1000}}%
\regfield{RMT\_DIV\_CNT\_CH\regindex{n}}{8}{0}{{\hexprefix{}2}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTREGDIVCNTCHN}\item [RMT\_DIV\_CNT\_CH\regindex{n}] This field is used to configure clock divider for channel \regindex{n}. (R/W)
\label{fielddesc:RMTREGIDLETHRESCHN}\item [RMT\_IDLE\_THRES\_CH\regindex{n}] Receiving ends when no edge is detected on input signals for continuous clock cycles larger than this register value. (R/W)
\label{fielddesc:RMTREGMEMSIZECHN}\item [RMT\_MEM\_SIZE\_CH\regindex{n}] This field is used to configure the maximum blocks allocated to channel \regindex{n}. The valid range is from 1 \verb+~+ 4-\regindex{n}. (R/W)
\label{fielddesc:RMTREGCARRIEREFFENCHN}\item [RMT\_CARRIER\_EFF\_EN\_CH\regindex{n}] 1: Add carrier modulation on output signals only at data sending state for channel \regindex{n}. 0: Add carrier modulation on signals at all states for channel \regindex{n}. States here include idle state(ST\_IDLE), reading data from RAM (ST\_RD\_MEM), and sending data stored in RAM (ST\_SEND). Only valid when \hyperref[fielddesc:RMTREGCARRIERENCHN]{RMT\_CARRIER\_EN\_CH\regindex{n}} is set to 1. (R/W)
\label{fielddesc:RMTREGCARRIERENCHN}\item [RMT\_CARRIER\_EN\_CH\regindex{n}] This bit is used to enable carrier modulation for channel \regindex{n}. 1: Add carrier modulation on output signals. 0: No carrier modulation is added on output signals. (R/W)
\label{fielddesc:RMTREGCARRIEROUTLVCHN}\item [RMT\_CARRIER\_OUT\_LV\_CH\regindex{n}] This bit is used to configure the position of carrier wave for channel \regindex{n}.
1'h0: Add carrier wave on low-level output signals.
1'h1: Add carrier wave on high-level output signals. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_CH\regindex{n}CONF1\_REG (\regindex{n}: 0-3)}{\hexprefix{}0014+8*\regindex{n}}\label{regdesc:RMTCHNCONF1REG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RMT\_TX\_STOP\_CH\regindex{n}}{1}{20}{{0}}%
\regfield{RMT\_IDLE\_OUT\_EN\_CH\regindex{n}}{1}{19}{{0}}%
\regfield{RMT\_IDLE\_OUT\_LV\_CH\regindex{n}}{1}{18}{{0}}%
\regfield{RMT\_REF\_ALWAYS\_ON\_CH\regindex{n}}{1}{17}{{0}}%
\regfield{RMT\_CHK\_RX\_CARRIER\_EN\_CH\regindex{n}}{1}{16}{{0}}%
\regfield{RMT\_RX\_FILTER\_THRES\_CH\regindex{n}}{8}{8}{{\hexprefix{}f}}%
\regfield{RMT\_RX\_FILTER\_EN\_CH\regindex{n}}{1}{7}{{0}}%
\regfield{RMT\_TX\_CONTI\_MODE\_CH\regindex{n}}{1}{6}{{0}}%
\regfield{RMT\_MEM\_OWNER\_CH\regindex{n}}{1}{5}{{1}}%
\regfield{RMT\_APB\_MEM\_RST\_CH\regindex{n}}{1}{4}{{0}}%
\regfield{RMT\_MEM\_RD\_RST\_CH\regindex{n}}{1}{3}{{0}}%
\regfield{RMT\_MEM\_WR\_RST\_CH\regindex{n}}{1}{2}{{0}}%
\regfield{RMT\_RX\_EN\_CH\regindex{n}}{1}{1}{{0}}%
\regfield{RMT\_TX\_START\_CH\regindex{n}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTREGTXSTARTCHN}\item [RMT\_TX\_START\_CH\regindex{n}] Set this bit to start sending data on channel \regindex{n}. (R/W)
\label{fielddesc:RMTREGRXENCHN}\item [RMT\_RX\_EN\_CH\regindex{n}] Set this bit to enable receiver to receive data on channel \regindex{n}. (R/W)
\label{fielddesc:RMTREGMEMWRRSTCHN}\item [RMT\_MEM\_WR\_RST\_CH\regindex{n}] Set this bit to reset RAM write address accessed by the receiver for channel \regindex{n}. (WO)
\label{fielddesc:RMTREGMEMRDRSTCHN}\item [RMT\_MEM\_RD\_RST\_CH\regindex{n}] Set this bit to reset RAM read address accessed by the transmitter for channel \regindex{n}. (WO)
\label{fielddesc:RMTREGMEMOWNERCHN}\item [RMT\_MEM\_OWNER\_CH\regindex{n}] This bit marks the ownership of channel \regindex{n}'s RAM block.
1'h1: Receiver is using the RAM.
1'h0: Transmitter is using the RAM. (R/W)
\label{fielddesc:RMTREGTXCONTIMODECHN}\item [RMT\_TX\_CONTI\_MODE\_CH\regindex{n}] Set this bit to restart transmission in continuous mode from the first data in channel \regindex{n}. (R/W)
\label{fielddesc:RMTREGRXFILTERENCHN}\item [RMT\_RX\_FILTER\_EN\_CH\regindex{n}] Set this bit to enable the receiver's filter for channel \regindex{n}. (R/W)
\label{fielddesc:RMTREGRXFILTERTHRESCHN}\item [RMT\_RX\_FILTER\_THRES\_CH\regindex{n}] Set this field to ignore the input pulse when its width is less than RMT\_RX\_FILTER\_THRES\_CH\regindex{n} APB clock cycles in receive mode. (R/W)
\label{fielddesc:RMTREGCHKRXCARRIERENCHN}\item [RMT\_CHK\_RX\_CARRIER\_EN\_CH\regindex{n}] Set this bit to enable memory loop read mode when carrier modulation is enabled for channel \regindex{n}. (R/W)
\label{fielddesc:RMTREGREFALWAYSONCHN}\item [RMT\_REF\_ALWAYS\_ON\_CH\regindex{n}] Set this bit to select a base clock for channel \regindex{n}.
1'h1: APB\_CLK; 1'h0: REF\_TICK (R/W)
\label{fielddesc:RMTREGIDLEOUTLVCHN}\item [RMT\_IDLE\_OUT\_LV\_CH\regindex{n}] This bit configures the level of output signals in channel \regindex{n} when the transmitter is in idle state. (R/W)
\label{fielddesc:RMTREGIDLEOUTENCHN}\item [RMT\_IDLE\_OUT\_EN\_CH\regindex{n}] This is the output enable bit for channel \regindex{n} in idle state. (R/W)
\label{fielddesc:RMTREGTXSTOPCHN}\item [RMT\_TX\_STOP\_CH\regindex{n}] Set this bit to stop the transmitter of channel \regindex{n} sending data out. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_APB\_CONF\_REG}{\hexprefix{}0080}\label{regdesc:RMTAPBCONFREG}
\regfield{RMT\_CLK\_EN}{1}{31}{{0}}%
\regfield{(reserved)}{26}{5}{00000000000000000000000000}%
\regfield{RMT\_MEM\_FORCE\_PU}{1}{4}{{0}}%
\regfield{RMT\_MEM\_FORCE\_PD}{1}{3}{{0}}%
\regfield{RMT\_MEM\_CLK\_FORCE\_ON}{1}{2}{{1}}%
\regfield{RMT\_MEM\_TX\_WRAP\_EN}{1}{1}{{0}}%
\regfield{RMT\_APB\_FIFO\_MASK}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTREGAPBFIFOMASK}\item [RMT\_APB\_FIFO\_MASK] 1'h1: Access memory directly; 1'h0: Access memory via APB FIFO. (R/W)
\label{fielddesc:RMTREGMEMTXWRAPEN}\item [RMT\_MEM\_TX\_WRAP\_EN] Set this bit to enable wrap mode. (R/W)
\label{fielddesc:RMTREGMEMCLKFORCEON}\item [RMT\_MEM\_CLK\_FORCE\_ON] Set this bit to enable the clock for RAM when RMT module starts working; disable this clock when RMT stops working, to achieve low-power scheme. (R/W)
\label{fielddesc:RMTREGMEMFORCEPD}\item [RMT\_MEM\_FORCE\_PD] Set this bit to power down RMT memory. (R/W)
\label{fielddesc:RMTREGMEMFORCEPU}\item [RMT\_MEM\_FORCE\_PU] 1: Disable RAM's Light-sleep power down function. 0: power down RMT RAM when RMT is in Light-sleep mode. (R/W)
\label{fielddesc:RMTREGCLKEN}\item [RMT\_CLK\_EN] Clock gating enable bit for RMT registers to achieve low-power scheme. 1: Power up drive clock for RMT registers. 0: Power down drive clock for RMT registers. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_REF\_CNT\_RST\_REG}{\hexprefix{}0088}\label{regdesc:RMTREFCNTRSTREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{RMT\_REF\_CNT\_RST\_CH3}{1}{3}{{0}}%
\regfield{RMT\_REF\_CNT\_RST\_CH2}{1}{2}{{0}}%
\regfield{RMT\_REF\_CNT\_RST\_CH1}{1}{1}{{0}}%
\regfield{RMT\_REF\_CNT\_RST\_CH0}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTREGREFCNTRSTCHN}\item [RMT\_REF\_CNT\_RST\_CH\regindex{n}] This bit is used to reset the clock divider of channel \regindex{n}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_CH\regindex{n}\_RX\_CARRIER\_RM\_REG (\regindex{n}: 0-3)}{\hexprefix{}008C+4*\regindex{n}}\label{regdesc:RMTCHNRXCARRIERRMREG}
\regfield{RMT\_CARRIER\_HIGH\_THRES\_CH\regindex{n}}{16}{16}{{\hexprefix{}00}}%
\regfield{RMT\_CARRIER\_LOW\_THRES\_CH\regindex{n}}{16}{0}{{\hexprefix{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTREGCARRIERLOWTHRESCHN}\item [RMT\_CARRIER\_LOW\_THRES\_CH\regindex{n}] The low level period in carrier modulation mode is (RMT\_CARRIER\_LOW\_THRES\_CH\regindex{n} + 1) clock cycles for channel \regindex{n}. (R/W)
\label{fielddesc:RMTREGCARRIERHIGHTHRESCHN}\item [RMT\_CARRIER\_HIGH\_THRES\_CH\regindex{n}] The high level period in carrier modulation mode is (RMT\_CARRIER\_HIGH\_THRES\_CH\regindex{n} + 1) clock cycles for channel \regindex{n}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_CH\regindex{n}CARRIER\_DUTY\_REG (\regindex{n}: 0-3)}{\hexprefix{}0060+4*\regindex{n}}\label{regdesc:RMTCHNCARRIERDUTYREG}
\regfield{RMT\_CARRIER\_HIGH\_CH\regindex{n}}{16}{16}{{\hexprefix{}40}}%
\regfield{RMT\_CARRIER\_LOW\_CH\regindex{n}}{16}{0}{{\hexprefix{}40}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTREGCARRIERLOWCHN}\item [RMT\_CARRIER\_LOW\_CH\regindex{n}] This field is used to configure the clock cycles of carrier wave at low level for channel \regindex{n}. (R/W)
\label{fielddesc:RMTREGCARRIERHIGHCHN}\item [RMT\_CARRIER\_HIGH\_CH\regindex{n}] This field is used to configure the clock cycles of carrier wave at high level for channel \regindex{n}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_CH\regindex{n}\_TX\_LIM\_REG (\regindex{n}: 0-3)}{\hexprefix{}0070+4*\regindex{n}}\label{regdesc:RMTCHNTXLIMREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RMT\_LOOP\_COUNT\_RESET\_CH\regindex{n}}{1}{20}{{0}}%
\regfield{RMT\_TX\_LOOP\_CNT\_EN\_CH\regindex{n}}{1}{19}{{0}}%
\regfield{RMT\_TX\_LOOP\_NUM\_CH\regindex{n}}{10}{9}{{\hexprefix{}0}}%
\regfield{RMT\_TX\_LIM\_CH\regindex{n}}{9}{0}{{\hexprefix{}80}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTREGTXLIMCHN}\item [RMT\_TX\_LIM\_CH\regindex{n}] This field is used to configure the maximum entries channel \regindex{n} can send out. When \hyperref[fielddesc:RMTREGMEMSIZECHN]{RMT\_MEM\_SIZE\_CH\regindex{n}} = 1, this field can be set to any value among 0 \verb+~+ 128 (64 * 32/16 = 128); when \hyperref[fielddesc:RMTREGMEMSIZECHN]{RMT\_MEM\_SIZE\_CH\regindex{n}} > 1, this field can be set to any value among (0 \verb+~+ 128) * \hyperref[fielddesc:RMTREGMEMSIZECHN]{RMT\_MEM\_SIZE\_CH\regindex{n}}. (R/W)
\label{fielddesc:RMTREGTXLOOPNUMCHN}\item [RMT\_TX\_LOOP\_NUM\_CH\regindex{n}] This field is used to configure the maximum loop times when continuous transmission mode is enabled. (R/W)
\label{fielddesc:RMTREGTXLOOPCNTENCHN}\item [RMT\_TX\_LOOP\_CNT\_EN\_CH\regindex{n}] This bit is used to enable loop counting. (R/W)
\label{fielddesc:RMTREGLOOPCOUNTRESETCHN}\item [RMT\_LOOP\_COUNT\_RESET\_CH\regindex{n}] This bit is used to reset loop counting when continuous transmission mode is valid. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_TX\_SIM\_REG}{\hexprefix{}0084}\label{regdesc:RMTTXSIMREG}
\regfield{(reserved)}{27}{5}{000000000000000000000000000}%
\regfield{RMT\_TX\_SIM\_EN}{1}{4}{{0}}%
\regfield{RMT\_TX\_SIM\_CH3}{1}{3}{{0}}%
\regfield{RMT\_TX\_SIM\_CH2}{1}{2}{{0}}%
\regfield{RMT\_TX\_SIM\_CH1}{1}{1}{{0}}%
\regfield{RMT\_TX\_SIM\_CH0}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTREGTXSIMCHN}\item [RMT\_TX\_SIM\_CH\regindex{n}] Set this bit to enable channel \regindex{n} to start sending data simultaneously with other enabled channels. (R/W)
\label{fielddesc:RMTREGTXSIMEN}\item [RMT\_TX\_SIM\_EN] This bit is used to enable multiple channels to start sending data simultaneously. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_CH\regindex{n}STATUS\_REG (\regindex{n}: 0-3)}{\hexprefix{}0030+4*\regindex{n}}\label{regdesc:RMTCHNSTATUSREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{RMT\_APB\_MEM\_RD\_ERR\_CH\regindex{n}}{1}{27}{{0}}%
\regfield{RMT\_APB\_MEM\_WR\_ERR\_CH\regindex{n}}{1}{26}{{0}}%
\regfield{RMT\_MEM\_EMPTY\_CH\regindex{n}}{1}{25}{{0}}%
\regfield{RMT\_MEM\_FULL\_CH\regindex{n}}{1}{24}{{0}}%
\regfield{RMT\_MEM\_OWNER\_ERR\_CH\regindex{n}}{1}{23}{{0}}%
\regfield{RMT\_STATE\_CH\regindex{n}}{3}{20}{{\hexprefix{}0}}%
\regfield{(reserved)}{1}{19}{0}%
\regfield{RMT\_MEM\_RADDR\_EX\_CH\regindex{n}}{9}{10}{{\hexprefix{}0}}%
\regfield{(reserved)}{1}{9}{0}%
\regfield{RMT\_MEM\_WADDR\_EX\_CH\regindex{n}}{9}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTREGMEMWADDREXCHN}\item [RMT\_MEM\_WADDR\_EX\_CH\regindex{n}] This field records the memory address offset when receiver of channel \regindex{n} is using the RAM. (RO)
\label{fielddesc:RMTREGMEMRADDREXCHN}\item [RMT\_MEM\_RADDR\_EX\_CH\regindex{n}] This field records the memory address offset when transmitter of channel \regindex{n} is using the RAM. (RO)
\label{fielddesc:RMTREGSTATECHN}\item [RMT\_STATE\_CH\regindex{n}] This field records the FSM status of channel \regindex{n}. (RO)
\label{fielddesc:RMTREGMEMOWNERERRCHN}\item [RMT\_MEM\_OWNER\_ERR\_CH\regindex{n}] This status bit will be set when the ownership of memory block is violated. (RO)
\label{fielddesc:RMTREGMEMFULLCHN}\item [RMT\_MEM\_FULL\_CH\regindex{n}] This status bit will be set if the receiver receives more data than the memory allows. (RO)
\label{fielddesc:RMTREGMEMEMPTYCHN}\item [RMT\_MEM\_EMPTY\_CH\regindex{n}] This status bit will be set when the data to be sent is more than the memory allows and the wrap mode is disabled. (RO)
\label{fielddesc:RMTREGAPBMEMWRERRCHN}\item [RMT\_APB\_MEM\_WR\_ERR\_CH\regindex{n}] This status bit will be set if the offset address is out of memory size when channel \regindex{n} writes RAM via APB bus. (RO)
\label{fielddesc:RMTREGAPBMEMRDERRCHN}\item [RMT\_APB\_MEM\_RD\_ERR\_CH\regindex{n}] This status bit will be set if the offset address is out of memory size when channel \regindex{n} reads RAM via APB bus. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_CH\regindex{n}ADDR\_REG (\regindex{n}: 0-3)}{\hexprefix{}0040+4*\regindex{n}}\label{regdesc:RMTCHNADDRREG}
\regfield{(reserved)}{13}{19}{0000000000000}%
\regfield{RMT\_APB\_MEM\_RADDR\_CH\regindex{n}}{9}{10}{{\hexprefix{}0}}%
\regfield{(reserved)}{1}{9}{0}%
\regfield{RMT\_APB\_MEM\_WADDR\_CH\regindex{n}}{9}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTREGAPBMEMWADDRCHN}\item [RMT\_APB\_MEM\_WADDR\_CH\regindex{n}] This field records the memory address offset when channel \regindex{n} writes RAM via APB bus. (RO)
\label{fielddesc:RMTREGAPBMEMRADDRCHN}\item [RMT\_APB\_MEM\_RADDR\_CH\regindex{n}] This field records the memory address offset when channel \regindex{n} reads RAM via APB bus. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_DATE\_REG}{\hexprefix{}00FC}\label{regdesc:RMTDATEREG}
\regfield{RMT\_DATE}{32}{0}{{\hexprefix{}19072601}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTREGDATE}\item [RMT\_DATE] Version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_CH\regindex{n}DATA\_REG (\regindex{n}: 0-3)}{\hexprefix{}0000+4*\regindex{n}}\label{regdesc:RMTCHNDATAREG}
\regfield{RMT\_CH\regindex{n}\_DATA}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTCHNDATAREG}\item [RMT\_CH\regindex{n}\_DATA] This register is used to read and write data for channel \regindex{n} via APB FIFO. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_INT\_RAW\_REG}{\hexprefix{}0050}\label{regdesc:RMTINTRAWREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{RMT\_CH3\_TX\_LOOP\_INT\_RAW}{1}{19}{{0}}%
\regfield{RMT\_CH2\_TX\_LOOP\_INT\_RAW}{1}{18}{{0}}%
\regfield{RMT\_CH1\_TX\_LOOP\_INT\_RAW}{1}{17}{{0}}%
\regfield{RMT\_CH0\_TX\_LOOP\_INT\_RAW}{1}{16}{{0}}%
\regfield{RMT\_CH3\_TX\_THR\_EVENT\_INT\_RAW}{1}{15}{{0}}%
\regfield{RMT\_CH2\_TX\_THR\_EVENT\_INT\_RAW}{1}{14}{{0}}%
\regfield{RMT\_CH1\_TX\_THR\_EVENT\_INT\_RAW}{1}{13}{{0}}%
\regfield{RMT\_CH0\_TX\_THR\_EVENT\_INT\_RAW}{1}{12}{{0}}%
\regfield{RMT\_CH3\_ERR\_INT\_RAW}{1}{11}{{0}}%
\regfield{RMT\_CH3\_RX\_END\_INT\_RAW}{1}{10}{{0}}%
\regfield{RMT\_CH3\_TX\_END\_INT\_RAW}{1}{9}{{0}}%
\regfield{RMT\_CH2\_ERR\_INT\_RAW}{1}{8}{{0}}%
\regfield{RMT\_CH2\_RX\_END\_INT\_RAW}{1}{7}{{0}}%
\regfield{RMT\_CH2\_TX\_END\_INT\_RAW}{1}{6}{{0}}%
\regfield{RMT\_CH1\_ERR\_INT\_RAW}{1}{5}{{0}}%
\regfield{RMT\_CH1\_RX\_END\_INT\_RAW}{1}{4}{{0}}%
\regfield{RMT\_CH1\_TX\_END\_INT\_RAW}{1}{3}{{0}}%
\regfield{RMT\_CH0\_ERR\_INT\_RAW}{1}{2}{{0}}%
\regfield{RMT\_CH0\_RX\_END\_INT\_RAW}{1}{1}{{0}}%
\regfield{RMT\_CH0\_TX\_END\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTREGCHNTXENDINTRAW}\item [RMT\_CH\regindex{n}\_TX\_END\_INT\_RAW] The interrupt raw bit for channel \regindex{n}. Triggered when transmitting ends. (RO)
\label{fielddesc:RMTREGCHNRXENDINTRAW}\item [RMT\_CH\regindex{n}\_RX\_END\_INT\_RAW] The interrupt raw bit for channel \regindex{n}. Triggered when receiving ends. (RO)
\label{fielddesc:RMTREGCHNERRINTRAW}\item [RMT\_CH\regindex{n}\_ERR\_INT\_RAW] The interrupt raw bit for channel \regindex{n}. Triggered when error occurs. (RO)
\label{fielddesc:RMTREGCHNTXTHREVENTINTRAW}\item [RMT\_CH\regindex{n}\_TX\_THR\_EVENT\_INT\_RAW] The interrupt raw bit for channel \regindex{n}. Triggered when transmitter sends more data than configured value. (RO)
\label{fielddesc:RMTREGCHNTXLOOPINTRAW}\item [RMT\_CH\regindex{n}\_TX\_LOOP\_INT\_RAW] The interrupt raw bit for channel \regindex{n}. Triggered when loop counting reaches the configured threshold value. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_INT\_ST\_REG}{\hexprefix{}0054}\label{regdesc:RMTINTSTREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{RMT\_CH3\_TX\_LOOP\_INT\_ST}{1}{19}{{0}}%
\regfield{RMT\_CH2\_TX\_LOOP\_INT\_ST}{1}{18}{{0}}%
\regfield{RMT\_CH1\_TX\_LOOP\_INT\_ST}{1}{17}{{0}}%
\regfield{RMT\_CH0\_TX\_LOOP\_INT\_ST}{1}{16}{{0}}%
\regfield{RMT\_CH3\_TX\_THR\_EVENT\_INT\_ST}{1}{15}{{0}}%
\regfield{RMT\_CH2\_TX\_THR\_EVENT\_INT\_ST}{1}{14}{{0}}%
\regfield{RMT\_CH1\_TX\_THR\_EVENT\_INT\_ST}{1}{13}{{0}}%
\regfield{RMT\_CH0\_TX\_THR\_EVENT\_INT\_ST}{1}{12}{{0}}%
\regfield{RMT\_CH3\_ERR\_INT\_ST}{1}{11}{{0}}%
\regfield{RMT\_CH3\_RX\_END\_INT\_ST}{1}{10}{{0}}%
\regfield{RMT\_CH3\_TX\_END\_INT\_ST}{1}{9}{{0}}%
\regfield{RMT\_CH2\_ERR\_INT\_ST}{1}{8}{{0}}%
\regfield{RMT\_CH2\_RX\_END\_INT\_ST}{1}{7}{{0}}%
\regfield{RMT\_CH2\_TX\_END\_INT\_ST}{1}{6}{{0}}%
\regfield{RMT\_CH1\_ERR\_INT\_ST}{1}{5}{{0}}%
\regfield{RMT\_CH1\_RX\_END\_INT\_ST}{1}{4}{{0}}%
\regfield{RMT\_CH1\_TX\_END\_INT\_ST}{1}{3}{{0}}%
\regfield{RMT\_CH0\_ERR\_INT\_ST}{1}{2}{{0}}%
\regfield{RMT\_CH0\_RX\_END\_INT\_ST}{1}{1}{{0}}%
\regfield{RMT\_CH0\_TX\_END\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTREGCHNTXENDINTST}\item [RMT\_CH\regindex{n}\_TX\_END\_INT\_ST] The masked interrupt status bit for \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_TX\_END\_INT}. (RO)
\label{fielddesc:RMTREGCHNRXENDINTST}\item [RMT\_CH\regindex{n}\_RX\_END\_INT\_ST] The masked interrupt status bit for \hyperref[int:RMTCHnRXENDINT]{RMT\_CH\regindex{n}\_RX\_END\_INT}. (RO)
\label{fielddesc:RMTREGCHNERRINTST}\item [RMT\_CH\regindex{n}\_ERR\_INT\_ST] The masked interrupt status bit for \hyperref[int:RMTCHnERRINT]{RMT\_CH\regindex{n}\_ERR\_INT}. (RO)
\label{fielddesc:RMTREGCHNTXTHREVENTINTST}\item [RMT\_CH\regindex{n}\_TX\_THR\_EVENT\_INT\_ST] The masked interrupt status bit for \hyperref[int:RMTCHnTXTHREVENTINT]{RMT\_CH\regindex{n}\_TX\_THR\_EVENT\_INT}. (RO)
\label{fielddesc:RMTREGCHNTXLOOPINTST}\item [RMT\_CH\regindex{n}\_TX\_LOOP\_INT\_ST] The masked interrupt status bit for \hyperref[int:RMTCHnTXLOOPINT]{RMT\_CH\regindex{n}\_TX\_LOOP\_INT}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_INT\_ENA\_REG}{\hexprefix{}0058}\label{regdesc:RMTINTENAREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{RMT\_CH3\_TX\_LOOP\_INT\_ENA}{1}{19}{{0}}%
\regfield{RMT\_CH2\_TX\_LOOP\_INT\_ENA}{1}{18}{{0}}%
\regfield{RMT\_CH1\_TX\_LOOP\_INT\_ENA}{1}{17}{{0}}%
\regfield{RMT\_CH0\_TX\_LOOP\_INT\_ENA}{1}{16}{{0}}%
\regfield{RMT\_CH3\_TX\_THR\_EVENT\_INT\_ENA}{1}{15}{{0}}%
\regfield{RMT\_CH2\_TX\_THR\_EVENT\_INT\_ENA}{1}{14}{{0}}%
\regfield{RMT\_CH1\_TX\_THR\_EVENT\_INT\_ENA}{1}{13}{{0}}%
\regfield{RMT\_CH0\_TX\_THR\_EVENT\_INT\_ENA}{1}{12}{{0}}%
\regfield{RMT\_CH3\_ERR\_INT\_ENA}{1}{11}{{0}}%
\regfield{RMT\_CH3\_RX\_END\_INT\_ENA}{1}{10}{{0}}%
\regfield{RMT\_CH3\_TX\_END\_INT\_ENA}{1}{9}{{0}}%
\regfield{RMT\_CH2\_ERR\_INT\_ENA}{1}{8}{{0}}%
\regfield{RMT\_CH2\_RX\_END\_INT\_ENA}{1}{7}{{0}}%
\regfield{RMT\_CH2\_TX\_END\_INT\_ENA}{1}{6}{{0}}%
\regfield{RMT\_CH1\_ERR\_INT\_ENA}{1}{5}{{0}}%
\regfield{RMT\_CH1\_RX\_END\_INT\_ENA}{1}{4}{{0}}%
\regfield{RMT\_CH1\_TX\_END\_INT\_ENA}{1}{3}{{0}}%
\regfield{RMT\_CH0\_ERR\_INT\_ENA}{1}{2}{{0}}%
\regfield{RMT\_CH0\_RX\_END\_INT\_ENA}{1}{1}{{0}}%
\regfield{RMT\_CH0\_TX\_END\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTREGCHNTXENDINTENA}\item [RMT\_CH\regindex{n}\_TX\_END\_INT\_ENA] Interrupt enable bit for \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_TX\_END\_INT}. (R/W)
\label{fielddesc:RMTREGCHNRXENDINTENA}\item [RMT\_CH\regindex{n}\_RX\_END\_INT\_ENA] Interrupt enable bit for \hyperref[int:RMTCHnRXENDINT]{RMT\_CH\regindex{n}\_RX\_END\_INT}. (R/W)
\label{fielddesc:RMTREGCHNERRINTENA}\item [RMT\_CH\regindex{n}\_ERR\_INT\_ENA] Interrupt enable bit for \hyperref[int:RMTCHnERRINT]{RMT\_CH\regindex{n}\_ERR\_INT}. (R/W)
\label{fielddesc:RMTREGCHNTXTHREVENTINTENA}\item [RMT\_CH\regindex{n}\_TX\_THR\_EVENT\_INT\_ENA] Interrupt enable bit for \hyperref[int:RMTCHnTXTHREVENTINT]{RMT\_CH\regindex{n}\_TX\_THR\_EVENT\_INT}. (R/W)
\label{fielddesc:RMTREGCHNTXLOOPINTENA}\item [RMT\_CH\regindex{n}\_TX\_LOOP\_INT\_ENA] Interrupt enable bit for \hyperref[int:RMTCHnTXLOOPINT]{RMT\_CH\regindex{n}\_TX\_LOOP\_INT}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_INT\_CLR\_REG}{\hexprefix{}005C}\label{regdesc:RMTINTCLRREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{RMT\_CH3\_TX\_LOOP\_INT\_CLR}{1}{19}{{0}}%
\regfield{RMT\_CH2\_TX\_LOOP\_INT\_CLR}{1}{18}{{0}}%
\regfield{RMT\_CH1\_TX\_LOOP\_INT\_CLR}{1}{17}{{0}}%
\regfield{RMT\_CH0\_TX\_LOOP\_INT\_CLR}{1}{16}{{0}}%
\regfield{RMT\_CH3\_TX\_THR\_EVENT\_INT\_CLR}{1}{15}{{0}}%
\regfield{RMT\_CH2\_TX\_THR\_EVENT\_INT\_CLR}{1}{14}{{0}}%
\regfield{RMT\_CH1\_TX\_THR\_EVENT\_INT\_CLR}{1}{13}{{0}}%
\regfield{RMT\_CH0\_TX\_THR\_EVENT\_INT\_CLR}{1}{12}{{0}}%
\regfield{RMT\_CH3\_ERR\_INT\_CLR}{1}{11}{{0}}%
\regfield{RMT\_CH3\_RX\_END\_INT\_CLR}{1}{10}{{0}}%
\regfield{RMT\_CH3\_TX\_END\_INT\_CLR}{1}{9}{{0}}%
\regfield{RMT\_CH2\_ERR\_INT\_CLR}{1}{8}{{0}}%
\regfield{RMT\_CH2\_RX\_END\_INT\_CLR}{1}{7}{{0}}%
\regfield{RMT\_CH2\_TX\_END\_INT\_CLR}{1}{6}{{0}}%
\regfield{RMT\_CH1\_ERR\_INT\_CLR}{1}{5}{{0}}%
\regfield{RMT\_CH1\_RX\_END\_INT\_CLR}{1}{4}{{0}}%
\regfield{RMT\_CH1\_TX\_END\_INT\_CLR}{1}{3}{{0}}%
\regfield{RMT\_CH0\_ERR\_INT\_CLR}{1}{2}{{0}}%
\regfield{RMT\_CH0\_RX\_END\_INT\_CLR}{1}{1}{{0}}%
\regfield{RMT\_CH0\_TX\_END\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTREGCHNTXENDINTCLR}\item [RMT\_CH\regindex{n}\_TX\_END\_INT\_CLR] Set this bit to clear \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_TX\_END\_INT} interrupt. (WO)
\label{fielddesc:RMTREGCHNRXENDINTCLR}\item [RMT\_CH\regindex{n}\_RX\_END\_INT\_CLR] Set this bit to clear \hyperref[int:RMTCHnRXENDINT]{RMT\_CH\regindex{n}\_RX\_END\_INT} interrupt. (WO)
\label{fielddesc:RMTREGCHNERRINTCLR}\item [RMT\_CH\regindex{n}\_ERR\_INT\_CLR] Set this bit to clear \hyperref[int:RMTCHnERRINT]{RMT\_CH\regindex{n}\_ERR\_INT} interrupt. (WO)
\label{fielddesc:RMTREGCHNTXTHREVENTINTCLR}\item [RMT\_CH\regindex{n}\_TX\_THR\_EVENT\_INT\_CLR] Set this bit to clear \hyperref[int:RMTCHnTXTHREVENTINT]{RMT\_CH\regindex{n}\_TX\_THR\_EVENT\_INT} interrupt. (WO)
\label{fielddesc:RMTREGCHNTXLOOPINTCLR}\item [RMT\_CH\regindex{n}\_TX\_LOOP\_INT\_CLR] Set this bit to clear \hyperref[int:RMTCHnTXLOOPINT]{RMT\_CH\regindex{n}\_TX\_LOOP\_INT} interrupt. (WO)
\end{reglist}\end{regdesc}
\end{register}
