\begin{longtable}[c]{ |m{8.2cm}|r|c|r|m{9cm}| }    
\caption{Parameters in eFuse BLOCK0}
    \label{tab:efuse-block0-para}
    \\\hline
    \rowcolor{lightgray}
    \textbf{Parameters} & \textbf{\thead{Bit \\Width}} & \textbf{\thead{Accessible \\by Hardware}} & \textbf{\thead{Programming-Protection \\by \hyperref[fielddesc:EFUSEWRDIS]{EFUSE\_WR\_DIS} \\Bit Number}}
    & \textbf{Description} \\
    \endfirsthead
    
    \multicolumn{5}{c}{\bfseries \tablename\ \thetable{} -- cont'd from previous page}\\\hline
    \rowcolor{lightgray}
    \textbf{Parameters} & \textbf{\thead{Bit \\Width}} & \textbf{\thead{Accessible \\by Hardware}} & \textbf{\thead{Programming-Protection \\by \hyperref[fielddesc:EFUSEWRDIS]{EFUSE\_WR\_DIS} \\Bit Number}}
    & \textbf{Description} \\
    \endhead 
    \multicolumn{5}{r}{\textbf{Cont'd on next page}} \\
    \endfoot
    \endlastfoot
    \hline    
    \textbf{\hyperref[fielddesc:EFUSEWRDIS]{EFUSE\_WR\_DIS}}  & 32 & Y & N/A & Represents whether writing of individual eFuses is disabled. \\
    \hline
    \textbf{\hyperref[fielddesc:EFUSERDDIS]{EFUSE\_RD\_DIS}}  & 7 & Y & 0  & Represents whether users' reading from BLOCK4 \verb+~+ 10 is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEDISICACHE]{EFUSE\_DIS\_ICACHE}  &  1 & Y & 2  & Represents whether iCache is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEDISUSBJTAG]{EFUSE\_DIS\_USB\_JTAG}  & 1 & Y & 2  & Represents whether the USB-to-JTAG function is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEDISDOWNLOADICACHE]{EFUSE\_DIS\_DOWNLOAD\_ICACHE}  & 1 & Y & 2 & Represents whether iCache is disabled in Download mode.\\   
    \hline
    \hyperref[fielddesc:EFUSEDISUSBSERIALJTAG]{EFUSE\_DIS\_USB\_SERIAL\_JTAG} & 1 & Y & 2 & Represents whether the usb\_serial\_jtag peripheral is disabled.\\      
    \hline
    \hyperref[fielddesc:EFUSEDISFORCEDOWNLOAD]{EFUSE\_DIS\_FORCE\_DOWNLOAD} & 1 & Y & 2 & Represents whether the function to force the chip into Download mode is disabled.\\   
    \hline
    \hyperref[fielddesc:EFUSEDISTWAI]{EFUSE\_DIS\_TWAI} & 1 & Y & 2 & Represents whether the TWAI controller is disabled.\\  
    \hline
    \hyperref[fielddesc:EFUSEJTAGSELENABLE]{EFUSE\_JTAG\_SEL\_ENABLE} & 1 & Y & 2 & Represents whether to use JTAG directly. \\   
    \hline
    \hyperref[fielddesc:EFUSESOFTDISJTAG]{EFUSE\_SOFT\_DIS\_JTAG}  & 3 & Y & 31 & Represents whether JTAG is disabled in the soft way.\\    
    \hline
    \hyperref[fielddesc:EFUSEDISPADJTAG]{EFUSE\_DIS\_PAD\_JTAG}  & 1 & Y & 2 & Represents whether JTAG is disabled in the hard way (permanently).\\   
    \hline
    \hyperref[fielddesc:EFUSEDISDOWNLOADMANUALENCRYPT]{EFUSE\_DIS\_DOWNLOAD\_ MANUAL\_ENCRYPT}  &  1 & Y & 2 & Represents whether flash encryption is disabled in Download boot mode.\\ 
    \hline
    \hyperref[fielddesc:EFUSEUSBEXCHGPINS]{EFUSE\_USB\_EXCHG\_PINS}  & 1 & Y & 30 & Represents whether the D+ and D- pins are exchanged. \\
    \hline
    \hyperref[fielddesc:EFUSEVDDSPIASGPIO]{EFUSE\_VDD\_SPI\_AS\_GPIO}  & 1 & N & 30 & Represents whether the VDD\_SPI pin is used as a regular GPIO.
    \\    
    \hline
    \hyperref[fielddesc:EFUSEWDTDELAYSEL]{EFUSE\_WDT\_DELAY\_SEL} & 2 & Y & 3 & Represents whether RTC watchdog timeout threshold is selected. \\
    \hline
    \hyperref[fielddesc:EFUSESPIBOOTCRYPTCNT]{EFUSE\_SPI\_BOOT\_CRYPT\_CNT}  & 3 & Y & 4 & Represents whether SPI boot encryption/decryption is enabled.\\
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE0]{EFUSE\_SECURE\_BOOT\_KEY\_ REVOKE0} & 1 & N & 5 & Represents whether revoking the first Secure Boot key is enabled. \\
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE1]{EFUSE\_SECURE\_BOOT\_KEY\_ REVOKE1}  & 1 & N & 6 & Represents whether revoking the second Secure Boot key is enabled.. \\
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE2]{EFUSE\_SECURE\_BOOT\_KEY\_ REVOKE2} & 1 & N & 7 & Represents whether revoking the third Secure Boot key is enabled. \\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE0]{EFUSE\_KEY\_PURPOSE\_0}  & 4 & Y & 8 & Represents Key0 purpose, see Table \ref{tab:efuse-key-purpose}. \\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE1]{EFUSE\_KEY\_PURPOSE\_1}  & 4 & Y & 9 & Represents Key1 purpose, see Table \ref{tab:efuse-key-purpose}. \\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE2]{EFUSE\_KEY\_PURPOSE\_2}  & 4 & Y & 10 & Represents Key2 purpose, see Table  \ref{tab:efuse-key-purpose}. \\ 
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE3]{EFUSE\_KEY\_PURPOSE\_3}  & 4 & Y & 11 & Represents Key3 purpose, see Table \ref{tab:efuse-key-purpose}. \\    
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE4]{EFUSE\_KEY\_PURPOSE\_4} & 4 & Y & 12 & Represents Key4 purpose, see Table \ref{tab:efuse-key-purpose}. \\    
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE5]{EFUSE\_KEY\_PURPOSE\_5}  & 4 & Y & 13 & Represents Key5 purpose, see Table \ref{tab:efuse-key-purpose}. \\  
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTEN]{EFUSE\_SECURE\_BOOT\_EN} & 1 & N & 15 & Represents whether Secure Boot is enabled. \\ 
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTAGGRESSIVEREVOKE]{EFUSE\_SECURE\_BOOT\_AGGRESSIVE\_REVOKE}  & 1 & N & 16 & Represents whether aggressive revocation of Secure Boot is enabled. \\
    \hline
    \hyperref[fielddesc:EFUSEFLASHTPUW]{EFUSE\_FLASH\_TPUW} & 4 & N & 18 & Represents the flash waiting time after power-up. \\    
    \hline    
    \hyperref[fielddesc:EFUSEDISDOWNLOADMODE]{EFUSE\_DIS\_DOWNLOAD\_MODE}  & 1 & N & 18 & Represents whether all download modes are disabled.\\       
    \hline
    \hyperref[fielddesc:EFUSEUSBPRINTCHANNEL]{EFUSE\_USB\_PRINT\_CHANNEL}  & 1 & N & 18 & Represents whether USB printing is disabled.
    \\
    \hline 
    \hyperref[fielddesc:EFUSEDISUSBDOWNLOADMODE]{EFUSE\_DIS\_USB\_SERIAL\_JTAG\_DOWNLOAD\_MODE}  & 1 & N & 18 & Represents whether the USB-Serial-JTAG download function is disabled. \\
    \hline 
    \hyperref[fielddesc:EFUSEENABLESECURITYDOWNLOAD]{EFUSE\_ENABLE\_SECURITY\_DOWNLOAD} & 1 & N & 18 & Represents whether UART secure download mode is enabled. \\
    \hline
    \hyperref[fielddesc:EFUSEUARTPRINTCONTROL]{EFUSE\_UART\_PRINT\_CONTROL}  & 2 & N & 18 & Represents the UART boot message output mode. \\
    \hline
    \hyperref[fielddesc:EFUSEFORCESENDRESUME]{EFUSE\_FORCE\_SEND\_RESUME} & 1 & N & 18 & Represents whether ROM code is forced to send a resume command during SPI boot. \\  
    \hline
    \hyperref[fielddesc:EFUSESECUREVERSION]{EFUSE\_SECURE\_VERSION} & 16 & N & 18 & Represents the version used by ESP-IDF anti-rollback feature.\\\hline
    \hyperref[fielddesc:EFUSEERRRSTENABLE]{EFUSE\_ERR\_RST\_ENABLE} & 1 & N & 19 & Represents whether to use BLOCK0 to check error record registers.\\\hline
\end{longtable}
