\begin{register}{H}{RTC\_CNTL\_ULP\_CP\_TIMER\_REG}{\hexprefix{}00F8}\label{regdesc:RTCCNTLULPCPTIMERREG}
\regfield{RTC\_CNTL\_ULP\_CP\_SLP\_TIMER\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_ULP\_CP\_GPIO\_WAKEUP\_CLR}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_ULP\_CP\_GPIO\_WAKEUP\_ENA}{1}{29}{{0}}%
\regfield{(reserved)}{18}{11}{000000000000000000}%
\regfield{RTC\_CNTL\_ULP\_CP\_PC\_INIT}{11}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLULPCPPCINIT}\item [RTC\_CNTL\_ULP\_CP\_PC\_INIT] ULP coprocessor PC initial address. (R/W)
\label{fielddesc:RTCCNTLULPCPGPIOWAKEUPENA}\item [RTC\_CNTL\_ULP\_CP\_GPIO\_WAKEUP\_ENA] Enable the option of ULP timer woken up by RTC GPIO. (R/W) 
\label{fielddesc:RTCCNTLULPCPGPIOWAKEUPCLR}\item [RTC\_CNTL\_ULP\_CP\_GPIO\_WAKEUP\_CLR] Disable the option of ULP timer woken up by RTC GPIO. (WO)
\label{fielddesc:RTCCNTLULPCPSLPTIMEREN}\item [RTC\_CNTL\_ULP\_CP\_SLP\_TIMER\_EN] ULP coprocessor timer enable bit. 0: Disable hardware timer; 1: Enable hardware timer. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_ULP\_CP\_TIMER\_1\_REG}{\hexprefix{}0130}\label{regdesc:RTCCNTLULPCPTIMER1REG}
\regfield{RTC\_CNTL\_ULP\_CP\_TIMER\_SLP\_CYCLE}{24}{8}{{200}}%
\regfield{(reserved)}{8}{0}{00000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLULPCPTIMERSLPCYCLE}\item [RTC\_CNTL\_ULP\_CP\_TIMER\_SLP\_CYCLE] Set sleep cycles for ULP coprocessor timer. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_ULP\_CP\_CTRL\_REG}{\hexprefix{}00FC}\label{regdesc:RTCCNTLULPCPCTRLREG}
\regfield{RTC\_CNTL\_ULP\_CP\_START\_TOP}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_ULP\_CP\_FORCE\_START\_TOP}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_ULP\_CP\_RESET}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_ULP\_CP\_CLK\_FO}{1}{28}{{0}}%
\regfield{(reserved)}{28}{0}{0000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLULPCPCLKFO}\item [RTC\_CNTL\_ULP\_CP\_CLK\_FO] ULP-FSM clock force on. (R/W)
\label{fielddesc:RTCCNTLULPCPRESET}\item [RTC\_CNTL\_ULP\_CP\_RESET] ULP-FSM clock software reset. (R/W)
\label{fielddesc:RTCCNTLULPCPFORCESTARTTOP}\item [RTC\_CNTL\_ULP\_CP\_FORCE\_START\_TOP] Write 1 to start ULP-FSM by software. (R/W)
\label{fielddesc:RTCCNTLULPCPSTARTTOP}\item [RTC\_CNTL\_ULP\_CP\_START\_TOP] Write 1 to start ULP-FSM. (R/W)
\end{reglist}\end{regdesc}
\end{register}



\begin{register}{H}{RTC\_CNTL\_COCPU\_CTRL\_REG}{\hexprefix{}0100}\label{regdesc:RTCCNTLCOCPUCTRLREG}
\regfield{(reserved)}{5}{27}{00000}%
\regfield{RTC\_CNTL\_COCPU\_SW\_INT\_TRIGGER}{1}{26}{{0}}%
\regfield{RTC\_CNTL\_COCPU\_DONE}{1}{25}{{0}}%
\regfield{RTC\_CNTL\_COCPU\_DONE\_FORCE}{1}{24}{{0}}%
\regfield{RTC\_CNTL\_COCPU\_SEL}{1}{23}{{1}}%
\regfield{RTC\_CNTL\_COCPU\_SHUT\_RESET\_EN}{1}{22}{{0}}%
\regfield{RTC\_CNTL\_COCPU\_SHUT\_2\_CLK\_DIS}{8}{14}{{40}}%
\regfield{RTC\_CNTL\_COCPU\_SHUT}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_COCPU\_START\_2\_INTR\_EN}{6}{7}{{16}}%
\regfield{RTC\_CNTL\_COCPU\_START\_2\_RESET\_DIS}{6}{1}{{8}}%
\regfield{RTC\_CNTL\_COCPU\_CLK\_FO}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLCOCPUCLKFO}\item [RTC\_CNTL\_COCPU\_CLK\_FO] ULP-RISC-V clock force on. (R/W)
\label{fielddesc:RTCCNTLCOCPUSTART2RESETDIS}\item [RTC\_CNTL\_COCPU\_START\_2\_RESET\_DIS] Time from ULP-RISC-V startup to pull down reset. (R/W)
\label{fielddesc:RTCCNTLCOCPUSTART2INTREN}\item [RTC\_CNTL\_COCPU\_START\_2\_INTR\_EN] Time from ULP-RISC-V startup to send out RISCV\_START\_INT interrupt. (R/W)
\label{fielddesc:RTCCNTLCOCPUSHUT}\item [RTC\_CNTL\_COCPU\_SHUT] Shut down ULP-RISC-V. (R/W)
\label{fielddesc:RTCCNTLCOCPUSHUT2CLKDIS}\item [RTC\_CNTL\_COCPU\_SHUT\_2\_CLK\_DIS] Time from shut down ULP-RISC-V to disable clock. (R/W)
\label{fielddesc:RTCCNTLCOCPUSHUTRESETEN}\item [RTC\_CNTL\_COCPU\_SHUT\_RESET\_EN] This bit is used to reset ULP-RISC-V. (R/W)
\label{fielddesc:RTCCNTLCOCPUSEL}\item [RTC\_CNTL\_COCPU\_SEL] 0: select ULP-RISC-V; 1: select ULP-FSM. (R/W)
\label{fielddesc:RTCCNTLCOCPUDONEFORCE}\item [RTC\_CNTL\_COCPU\_DONE\_FORCE] 0: select ULP-FSM DONE signal; 1: select ULP-RISC-V DONE signal. (R/W)
\label{fielddesc:RTCCNTLCOCPUDONE}\item [RTC\_CNTL\_COCPU\_DONE] DONE signal. Write 1 to this bit, ULP-RISC-V will go to HALT and the timer starts counting. (R/W)
\label{fielddesc:RTCCNTLCOCPUSWINTTRIGGER}\item [RTC\_CNTL\_COCPU\_SW\_INT\_TRIGGER] Trigger ULP-RISC-V register interrupt. (WO)
\end{reglist}\end{regdesc}
\end{register}

