\begin{register}{H}{UART\_FIFO\_REG}{0x0000}\label{regdesc:UARTFIFOREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{UART\_RXFIFO\_RD\_BYTE}{8}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXFIFORDBYTE}\item [UART\_RXFIFO\_RD\_BYTE] Represents the data UART \regindex{n} read from FIFO.\\
Measurement unit: byte. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_TOUT\_CONF\_SYNC\_REG}{0x0064}\label{regdesc:UARTTOUTCONFSYNCREG}
\regfield{(reserved)}{20}{12}{00000000000000000000}%
\regfield{UART\_RX\_TOUT\_THRHD}{10}{2}{{0xa}}%
\regfield{(reserved)}{1}{1}{{0}}%
\regfield{UART\_RX\_TOUT\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXTOUTEN}\item [UART\_RX\_TOUT\_EN] Configures whether or not to enable UART receiver's timeout function.\\
0: Disable\\
1: Enable\\(R/W)
\label{fielddesc:UARTRXTOUTTHRHD}\item [UART\_RX\_TOUT\_THRHD] Configures the amount of time that the bus can remain idle before timeout.\\ Measurement unit: bit time (the time to transmit 1 bit). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_INT\_RAW\_REG}{0x0004}\label{regdesc:UARTINTRAWREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{UART\_WAKEUP\_INT\_RAW}{1}{19}{{0}}%
\regfield{UART\_AT\_CMD\_CHAR\_DET\_INT\_RAW}{1}{18}{{0}}%
\regfield{UART\_RS485\_CLASH\_INT\_RAW}{1}{17}{{0}}%
\regfield{UART\_RS485\_FRM\_ERR\_INT\_RAW}{1}{16}{{0}}%
\regfield{UART\_RS485\_PARITY\_ERR\_INT\_RAW}{1}{15}{{0}}%
\regfield{UART\_TX\_DONE\_INT\_RAW}{1}{14}{{0}}%
\regfield{UART\_TX\_BRK\_IDLE\_DONE\_INT\_RAW}{1}{13}{{0}}%
\regfield{UART\_TX\_BRK\_DONE\_INT\_RAW}{1}{12}{{0}}%
\regfield{UART\_GLITCH\_DET\_INT\_RAW}{1}{11}{{0}}%
\regfield{UART\_SW\_XOFF\_INT\_RAW}{1}{10}{{0}}%
\regfield{UART\_SW\_XON\_INT\_RAW}{1}{9}{{0}}%
\regfield{UART\_RXFIFO\_TOUT\_INT\_RAW}{1}{8}{{0}}%
\regfield{UART\_BRK\_DET\_INT\_RAW}{1}{7}{{0}}%
\regfield{UART\_CTS\_CHG\_INT\_RAW}{1}{6}{{0}}%
\regfield{UART\_DSR\_CHG\_INT\_RAW}{1}{5}{{0}}%
\regfield{UART\_RXFIFO\_OVF\_INT\_RAW}{1}{4}{{0}}%
\regfield{UART\_FRM\_ERR\_INT\_RAW}{1}{3}{{0}}%
\regfield{UART\_PARITY\_ERR\_INT\_RAW}{1}{2}{{0}}%
\regfield{UART\_TXFIFO\_EMPTY\_INT\_RAW}{1}{1}{{1}}%
\regfield{UART\_RXFIFO\_FULL\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXFIFOFULLINTRAW}\item [UART\_RXFIFO\_FULL\_INT\_RAW] The raw interrupt status of UART\_RXFIFO\_FULL\_INT. (R/WTC/SS)
\label{fielddesc:UARTTXFIFOEMPTYINTRAW}\item [UART\_TXFIFO\_EMPTY\_INT\_RAW] The raw interrupt status of UART\_TXFIFO\_EMPTY\_INT. (R/WTC/SS)
\label{fielddesc:UARTPARITYERRINTRAW}\item [UART\_PARITY\_ERR\_INT\_RAW] The raw interrupt status of UART\_PARITY\_ERR\_INT. (R/WTC/SS)
\label{fielddesc:UARTFRMERRINTRAW}\item [UART\_FRM\_ERR\_INT\_RAW] The raw interrupt status of UART\_FRM\_ERR\_INT. (R/WTC/SS)
\label{fielddesc:UARTRXFIFOOVFINTRAW}\item [UART\_RXFIFO\_OVF\_INT\_RAW] The raw interrupt status of UART\_RXFIFO\_OVF\_INT. (R/WTC/SS)
\label{fielddesc:UARTDSRCHGINTRAW}\item [UART\_DSR\_CHG\_INT\_RAW] The raw interrupt status of UART\_DSR\_CHG\_INT. (R/WTC/SS)
\label{fielddesc:UARTCTSCHGINTRAW}\item [UART\_CTS\_CHG\_INT\_RAW] The raw interrupt status of UART\_CTS\_CHG\_INT. (R/WTC/SS)
\label{fielddesc:UARTBRKDETINTRAW}\item [UART\_BRK\_DET\_INT\_RAW] The raw interrupt status of UART\_BRK\_DET\_INT. (R/WTC/SS)
\label{fielddesc:UARTRXFIFOTOUTINTRAW}\item [UART\_RXFIFO\_TOUT\_INT\_RAW] The raw interrupt status of UART\_RXFIFO\_TOUT\_INT. (R/WTC/SS)
\label{fielddesc:UARTSWXONINTRAW}\item [UART\_SW\_XON\_INT\_RAW] The raw interrupt status of UART\_SW\_XON\_INT. (R/WTC/SS)
\label{fielddesc:UARTSWXOFFINTRAW}\item [UART\_SW\_XOFF\_INT\_RAW] UART\_SW\_XOFF\_INT. (R/WTC/SS)
\label{fielddesc:UARTGLITCHDETINTRAW}\item [UART\_GLITCH\_DET\_INT\_RAW] The raw interrupt status of UART\_GLITCH\_DET\_INT. (R/WTC/SS)
\label{fielddesc:UARTTXBRKDONEINTRAW}\item [UART\_TX\_BRK\_DONE\_INT\_RAW] The raw interrupt status of UART\_TX\_BRK\_DONE\_INT. (R/WTC/SS)
\label{fielddesc:UARTTXBRKIDLEDONEINTRAW}\item [UART\_TX\_BRK\_IDLE\_DONE\_INT\_RAW] The raw interrupt status of UART\_TX\_BRK\_IDLE\_DONE\_INT. (R/WTC/SS)
\label{fielddesc:UARTTXDONEINTRAW}\item [UART\_TX\_DONE\_INT\_RAW] The raw interrupt status of UART\_TX\_DONE\_INT. (R/WTC/SS)
\label{fielddesc:UARTRS485PARITYERRINTRAW}\item [UART\_RS485\_PARITY\_ERR\_INT\_RAW] The raw interrupt status of UART\_RS485\_PARITY\_ERR\_INT. (R/WTC/SS)
\label{fielddesc:UARTRS485FRMERRINTRAW}\item [UART\_RS485\_FRM\_ERR\_INT\_RAW] The raw interrupt status of UART\_RS485\_FRM\_ERR\_INT. (R/WTC/SS)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{UART\_INT\_RAW\_REG}{0x0004}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:UARTRS485CLASHINTRAW}\item [UART\_RS485\_CLASH\_INT\_RAW] The raw interrupt status of UART\_RS485\_CLASH\_INT. (R/WTC/SS)
\label{fielddesc:UARTATCMDCHARDETINTRAW}\item [UART\_AT\_CMD\_CHAR\_DET\_INT\_RAW] The raw interrupt status of UART\_AT\_CMD\_CHAR\_DET\_INT. (R/WTC/SS)
\label{fielddesc:UARTWAKEUPINTRAW}\item [UART\_WAKEUP\_INT\_RAW] The raw interrupt status of UART\_WAKEUP\_INT. (R/WTC/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_INT\_ST\_REG}{0x0008}\label{regdesc:UARTINTSTREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{UART\_WAKEUP\_INT\_ST}{1}{19}{{0}}%
\regfield{UART\_AT\_CMD\_CHAR\_DET\_INT\_ST}{1}{18}{{0}}%
\regfield{UART\_RS485\_CLASH\_INT\_ST}{1}{17}{{0}}%
\regfield{UART\_RS485\_FRM\_ERR\_INT\_ST}{1}{16}{{0}}%
\regfield{UART\_RS485\_PARITY\_ERR\_INT\_ST}{1}{15}{{0}}%
\regfield{UART\_TX\_DONE\_INT\_ST}{1}{14}{{0}}%
\regfield{UART\_TX\_BRK\_IDLE\_DONE\_INT\_ST}{1}{13}{{0}}%
\regfield{UART\_TX\_BRK\_DONE\_INT\_ST}{1}{12}{{0}}%
\regfield{UART\_GLITCH\_DET\_INT\_ST}{1}{11}{{0}}%
\regfield{UART\_SW\_XOFF\_INT\_ST}{1}{10}{{0}}%
\regfield{UART\_SW\_XON\_INT\_ST}{1}{9}{{0}}%
\regfield{UART\_RXFIFO\_TOUT\_INT\_ST}{1}{8}{{0}}%
\regfield{UART\_BRK\_DET\_INT\_ST}{1}{7}{{0}}%
\regfield{UART\_CTS\_CHG\_INT\_ST}{1}{6}{{0}}%
\regfield{UART\_DSR\_CHG\_INT\_ST}{1}{5}{{0}}%
\regfield{UART\_RXFIFO\_OVF\_INT\_ST}{1}{4}{{0}}%
\regfield{UART\_FRM\_ERR\_INT\_ST}{1}{3}{{0}}%
\regfield{UART\_PARITY\_ERR\_INT\_ST}{1}{2}{{0}}%
\regfield{UART\_TXFIFO\_EMPTY\_INT\_ST}{1}{1}{{0}}%
\regfield{UART\_RXFIFO\_FULL\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXFIFOFULLINTST}\item [UART\_RXFIFO\_FULL\_INT\_ST] The masked interrupt status of UART\_RXFIFO\_FULL\_INT.(RO)
\label{fielddesc:UARTTXFIFOEMPTYINTST}\item [UART\_TXFIFO\_EMPTY\_INT\_ST] The masked interrupt status of UART\_TXFIFO\_EMPTY\_INT. (RO)
\label{fielddesc:UARTPARITYERRINTST}\item [UART\_PARITY\_ERR\_INT\_ST] The masked interrupt status of UART\_PARITY\_ERR\_INT. (RO)
\label{fielddesc:UARTFRMERRINTST}\item [UART\_FRM\_ERR\_INT\_ST] The masked interrupt status of UART\_FRM\_ERR\_INT. (RO)
\label{fielddesc:UARTRXFIFOOVFINTST}\item [UART\_RXFIFO\_OVF\_INT\_ST] The masked interrupt status of UART\_RXFIFO\_OVF\_INT. (RO)
\label{fielddesc:UARTDSRCHGINTST}\item [UART\_DSR\_CHG\_INT\_ST] The masked interrupt status of UART\_DSR\_CHG\_INT. (RO)
\label{fielddesc:UARTCTSCHGINTST}\item [UART\_CTS\_CHG\_INT\_ST] The masked interrupt status of UART\_CTS\_CHG\_INT. (RO)
\label{fielddesc:UARTBRKDETINTST}\item [UART\_BRK\_DET\_INT\_ST] The masked interrupt status of UART\_BRK\_DET\_INT. (RO)
\label{fielddesc:UARTRXFIFOTOUTINTST}\item [UART\_RXFIFO\_TOUT\_INT\_ST] The masked interrupt status of UART\_RXFIFO\_TOUT\_INT. (RO)
\label{fielddesc:UARTSWXONINTST}\item [UART\_SW\_XON\_INT\_ST] The masked interrupt status of UART\_SW\_XON\_INT. (RO)
\label{fielddesc:UARTSWXOFFINTST}\item [UART\_SW\_XOFF\_INT\_ST] The masked interrupt status of UART\_SW\_XOFF\_INT. (RO)
\label{fielddesc:UARTGLITCHDETINTST}\item [UART\_GLITCH\_DET\_INT\_ST] The masked interrupt status of UART\_GLITCH\_DET\_INT. (RO)
\label{fielddesc:UARTTXBRKDONEINTST}\item [UART\_TX\_BRK\_DONE\_INT\_ST] The masked interrupt status of UART\_TX\_BRK\_DONE\_INT. (RO)
\label{fielddesc:UARTTXBRKIDLEDONEINTST}\item [UART\_TX\_BRK\_IDLE\_DONE\_INT\_ST] The masked interrupt status of UART\_TX\_BRK\_IDLE\_DONE\_INT. (RO)
\label{fielddesc:UARTTXDONEINTST}\item [UART\_TX\_DONE\_INT\_ST] The masked interrupt status of UART\_TX\_DONE\_INT. (RO)
\label{fielddesc:UARTRS485PARITYERRINTST}\item [UART\_RS485\_PARITY\_ERR\_INT\_ST] The masked interrupt status of UART\_RS485\_PARITY\_ERR\_INT. (RO)
\label{fielddesc:UARTRS485FRMERRINTST}\item [UART\_RS485\_FRM\_ERR\_INT\_ST] The masked interrupt status of UART\_RS485\_FRM\_ERR\_INT. (RO)
\label{fielddesc:UARTRS485CLASHINTST}\item [UART\_RS485\_CLASH\_INT\_ST] The masked interrupt status of UART\_RS485\_CLASH\_INT. (RO)
\label{fielddesc:UARTATCMDCHARDETINTST}\item [UART\_AT\_CMD\_CHAR\_DET\_INT\_ST] The masked interrupt status of UART\_AT\_CMD\_CHAR\_DET\_INT. (RO)
\label{fielddesc:UARTWAKEUPINTST}\item [UART\_WAKEUP\_INT\_ST] The masked interrupt status of UART\_WAKEUP\_INT. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_INT\_ENA\_REG}{0x000C}\label{regdesc:UARTINTENAREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{UART\_WAKEUP\_INT\_ENA}{1}{19}{{0}}%
\regfield{UART\_AT\_CMD\_CHAR\_DET\_INT\_ENA}{1}{18}{{0}}%
\regfield{UART\_RS485\_CLASH\_INT\_ENA}{1}{17}{{0}}%
\regfield{UART\_RS485\_FRM\_ERR\_INT\_ENA}{1}{16}{{0}}%
\regfield{UART\_RS485\_PARITY\_ERR\_INT\_ENA}{1}{15}{{0}}%
\regfield{UART\_TX\_DONE\_INT\_ENA}{1}{14}{{0}}%
\regfield{UART\_TX\_BRK\_IDLE\_DONE\_INT\_ENA}{1}{13}{{0}}%
\regfield{UART\_TX\_BRK\_DONE\_INT\_ENA}{1}{12}{{0}}%
\regfield{UART\_GLITCH\_DET\_INT\_ENA}{1}{11}{{0}}%
\regfield{UART\_SW\_XOFF\_INT\_ENA}{1}{10}{{0}}%
\regfield{UART\_SW\_XON\_INT\_ENA}{1}{9}{{0}}%
\regfield{UART\_RXFIFO\_TOUT\_INT\_ENA}{1}{8}{{0}}%
\regfield{UART\_BRK\_DET\_INT\_ENA}{1}{7}{{0}}%
\regfield{UART\_CTS\_CHG\_INT\_ENA}{1}{6}{{0}}%
\regfield{UART\_DSR\_CHG\_INT\_ENA}{1}{5}{{0}}%
\regfield{UART\_RXFIFO\_OVF\_INT\_ENA}{1}{4}{{0}}%
\regfield{UART\_FRM\_ERR\_INT\_ENA}{1}{3}{{0}}%
\regfield{UART\_PARITY\_ERR\_INT\_ENA}{1}{2}{{0}}%
\regfield{UART\_TXFIFO\_EMPTY\_INT\_ENA}{1}{1}{{0}}%
\regfield{UART\_RXFIFO\_FULL\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXFIFOFULLINTENA}\item [UART\_RXFIFO\_FULL\_INT\_ENA] Write 1 to enable UART\_RXFIFO\_FULL\_INT. (R/W)
\label{fielddesc:UARTTXFIFOEMPTYINTENA}\item [UART\_TXFIFO\_EMPTY\_INT\_ENA] Write 1 to enable UART\_TXFIFO\_EMPTY\_INT.  (R/W)
\label{fielddesc:UARTPARITYERRINTENA}\item [UART\_PARITY\_ERR\_INT\_ENA] Write 1 to enable UART\_PARITY\_ERR\_INT. (R/W)
\label{fielddesc:UARTFRMERRINTENA}\item [UART\_FRM\_ERR\_INT\_ENA] Write 1 to enable UART\_FRM\_ERR\_INT. (R/W)
\label{fielddesc:UARTRXFIFOOVFINTENA}\item [UART\_RXFIFO\_OVF\_INT\_ENA] Write 1 to enable UART\_RXFIFO\_OVF\_INT. (R/W)
\label{fielddesc:UARTDSRCHGINTENA}\item [UART\_DSR\_CHG\_INT\_ENA] Write 1 to enable UART\_DSR\_CHG\_INT. (R/W)
\label{fielddesc:UARTCTSCHGINTENA}\item [UART\_CTS\_CHG\_INT\_ENA] Write 1 to enable UART\_CTS\_CHG\_INT. (R/W)
\label{fielddesc:UARTBRKDETINTENA}\item [UART\_BRK\_DET\_INT\_ENA] Write 1 to enable UART\_BRK\_DET\_INT. (R/W)
\label{fielddesc:UARTRXFIFOTOUTINTENA}\item [UART\_RXFIFO\_TOUT\_INT\_ENA] Write 1 to enable UART\_RXFIFO\_TOUT\_INT. (R/W)
\label{fielddesc:UARTSWXONINTENA}\item [UART\_SW\_XON\_INT\_ENA] Write 1 to enable UART\_SW\_XON\_INT.(R/W)
\label{fielddesc:UARTSWXOFFINTENA}\item [UART\_SW\_XOFF\_INT\_ENA] Write 1 to enable UART\_SW\_XOFF\_INT. (R/W)
\label{fielddesc:UARTGLITCHDETINTENA}\item [UART\_GLITCH\_DET\_INT\_ENA] Write 1 to enable UART\_GLITCH\_DET\_INT. (R/W)
\label{fielddesc:UARTTXBRKDONEINTENA}\item [UART\_TX\_BRK\_DONE\_INT\_ENA] Write 1 to enable UART\_TX\_BRK\_DONE\_INT. (R/W)
\label{fielddesc:UARTTXBRKIDLEDONEINTENA}\item [UART\_TX\_BRK\_IDLE\_DONE\_INT\_ENA] Write 1 to enable UART\_TX\_BRK\_IDLE\_DONE\_INT. (R/W)
\label{fielddesc:UARTTXDONEINTENA}\item [UART\_TX\_DONE\_INT\_ENA] Write 1 to enable UART\_TX\_DONE\_INT. (R/W)
\label{fielddesc:UARTRS485PARITYERRINTENA}\item [UART\_RS485\_PARITY\_ERR\_INT\_ENA] Write 1 to enable UART\_RS485\_PARITY\_ERR\_INT. (R/W)
\label{fielddesc:UARTRS485FRMERRINTENA}\item [UART\_RS485\_FRM\_ERR\_INT\_ENA] Write 1 to enable UART\_RS485\_FRM\_ERR\_INT. (R/W)
\label{fielddesc:UARTRS485CLASHINTENA}\item [UART\_RS485\_CLASH\_INT\_ENA] Write 1 to enable UART\_RS485\_CLASH\_INT. (R/W)
\label{fielddesc:UARTATCMDCHARDETINTENA}\item [UART\_AT\_CMD\_CHAR\_DET\_INT\_ENA] Write 1 to enable UART\_AT\_CMD\_CHAR\_DET\_INT. (R/W)
\label{fielddesc:UARTWAKEUPINTENA}\item [UART\_WAKEUP\_INT\_ENA] Write 1 to enable UART\_WAKEUP\_INT. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_INT\_CLR\_REG}{0x0010}\label{regdesc:UARTINTCLRREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{UART\_WAKEUP\_INT\_CLR}{1}{19}{{0}}%
\regfield{UART\_AT\_CMD\_CHAR\_DET\_INT\_CLR}{1}{18}{{0}}%
\regfield{UART\_RS485\_CLASH\_INT\_CLR}{1}{17}{{0}}%
\regfield{UART\_RS485\_FRM\_ERR\_INT\_CLR}{1}{16}{{0}}%
\regfield{UART\_RS485\_PARITY\_ERR\_INT\_CLR}{1}{15}{{0}}%
\regfield{UART\_TX\_DONE\_INT\_CLR}{1}{14}{{0}}%
\regfield{UART\_TX\_BRK\_IDLE\_DONE\_INT\_CLR}{1}{13}{{0}}%
\regfield{UART\_TX\_BRK\_DONE\_INT\_CLR}{1}{12}{{0}}%
\regfield{UART\_GLITCH\_DET\_INT\_CLR}{1}{11}{{0}}%
\regfield{UART\_SW\_XOFF\_INT\_CLR}{1}{10}{{0}}%
\regfield{UART\_SW\_XON\_INT\_CLR}{1}{9}{{0}}%
\regfield{UART\_RXFIFO\_TOUT\_INT\_CLR}{1}{8}{{0}}%
\regfield{UART\_BRK\_DET\_INT\_CLR}{1}{7}{{0}}%
\regfield{UART\_CTS\_CHG\_INT\_CLR}{1}{6}{{0}}%
\regfield{UART\_DSR\_CHG\_INT\_CLR}{1}{5}{{0}}%
\regfield{UART\_RXFIFO\_OVF\_INT\_CLR}{1}{4}{{0}}%
\regfield{UART\_FRM\_ERR\_INT\_CLR}{1}{3}{{0}}%
\regfield{UART\_PARITY\_ERR\_INT\_CLR}{1}{2}{{0}}%
\regfield{UART\_TXFIFO\_EMPTY\_INT\_CLR}{1}{1}{{0}}%
\regfield{UART\_RXFIFO\_FULL\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXFIFOFULLINTCLR}\item [UART\_RXFIFO\_FULL\_INT\_CLR] Write 1 to clear UART\_RXFIFO\_FULL\_INT. (WT)
\label{fielddesc:UARTTXFIFOEMPTYINTCLR}\item [UART\_TXFIFO\_EMPTY\_INT\_CLR] Write 1 to clear UART\_TXFIFO\_EMPTY\_INT. (WT)
\label{fielddesc:UARTPARITYERRINTCLR}\item [UART\_PARITY\_ERR\_INT\_CLR] Write 1 to clear UART\_PARITY\_ERR\_INT. (WT)
\label{fielddesc:UARTFRMERRINTCLR}\item [UART\_FRM\_ERR\_INT\_CLR] Write 1 to clear UART\_FRM\_ERR\_INT. (WT)
\label{fielddesc:UARTRXFIFOOVFINTCLR}\item [UART\_RXFIFO\_OVF\_INT\_CLR] Write 1 to clear UART\_RXFIFO\_OVF\_INT. (WT)
\label{fielddesc:UARTDSRCHGINTCLR}\item [UART\_DSR\_CHG\_INT\_CLR] Write 1 to clear UART\_DSR\_CHG\_INT. (WT)
\label{fielddesc:UARTCTSCHGINTCLR}\item [UART\_CTS\_CHG\_INT\_CLR] Write 1 to clear UART\_CTS\_CHG\_INT. (WT)
\label{fielddesc:UARTBRKDETINTCLR}\item [UART\_BRK\_DET\_INT\_CLR] Write 1 to clear UART\_BRK\_DET\_INT. (WT)
\label{fielddesc:UARTRXFIFOTOUTINTCLR}\item [UART\_RXFIFO\_TOUT\_INT\_CLR] Write 1 to clear UART\_RXFIFO\_TOUT\_INT. (WT)
\label{fielddesc:UARTSWXONINTCLR}\item [UART\_SW\_XON\_INT\_CLR] Write 1 to clear UART\_SW\_XON\_INT. (WT)
\label{fielddesc:UARTSWXOFFINTCLR}\item [UART\_SW\_XOFF\_INT\_CLR] Write 1 to clear UART\_SW\_XOFF\_INT. (WT)
\label{fielddesc:UARTGLITCHDETINTCLR}\item [UART\_GLITCH\_DET\_INT\_CLR] Write 1 to clear UART\_GLITCH\_DET\_INT. (WT)
\label{fielddesc:UARTTXBRKDONEINTCLR}\item [UART\_TX\_BRK\_DONE\_INT\_CLR] Write 1 to clear UART\_TX\_BRK\_DONE\_INT. (WT)
\label{fielddesc:UARTTXBRKIDLEDONEINTCLR}\item [UART\_TX\_BRK\_IDLE\_DONE\_INT\_CLR] Write 1 to clear UART\_TX\_BRK\_IDLE\_DONE\_INT. (WT)
\label{fielddesc:UARTTXDONEINTCLR}\item [UART\_TX\_DONE\_INT\_CLR] Write 1 to clear UART\_TX\_DONE\_INT. (WT)
\label{fielddesc:UARTRS485PARITYERRINTCLR}\item [UART\_RS485\_PARITY\_ERR\_INT\_CLR] Write 1 to clear UART\_RS485\_PARITY\_ERR\_INT. (WT)
\label{fielddesc:UARTRS485FRMERRINTCLR}\item [UART\_RS485\_FRM\_ERR\_INT\_CLR] Write 1 to clear UART\_RS485\_FRM\_ERR\_INT. (WT)
\label{fielddesc:UARTRS485CLASHINTCLR}\item [UART\_RS485\_CLASH\_INT\_CLR] Write 1 to clear UART\_RS485\_CLASH\_INT. (WT)
\label{fielddesc:UARTATCMDCHARDETINTCLR}\item [UART\_AT\_CMD\_CHAR\_DET\_INT\_CLR] Write 1 to clear UART\_AT\_CMD\_CHAR\_DET\_INT. (WT)
\label{fielddesc:UARTWAKEUPINTCLR}\item [UART\_WAKEUP\_INT\_CLR] Write 1 to clear UART\_WAKEUP\_INT. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_CLKDIV\_SYNC\_REG}{0x0014}\label{regdesc:UARTCLKDIVSYNCREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{UART\_CLKDIV\_FRAG}{4}{20}{{0x0}}%
\regfield{(reserved)}{8}{12}{00000000}%
\regfield{UART\_CLKDIV}{12}{0}{{0x2b6}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTCLKDIV}\item [UART\_CLKDIV] Configures the integral part of the divisor for baud rate generation. (R/W)
\label{fielddesc:UARTCLKDIVFRAG}\item [UART\_CLKDIV\_FRAG] Configures the fractional part of the divisor for baud rate generation. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_RX\_FILT\_REG}{0x0018}\label{regdesc:UARTRXFILTREG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{UART\_GLITCH\_FILT\_EN}{1}{8}{{0}}%
\regfield{UART\_GLITCH\_FILT}{8}{0}{{0x8}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTGLITCHFILT}\item [UART\_GLITCH\_FILT] Configures the width of a pulse to be filtered.\\Measurement unit: UART Core's clock cycle.\\Pulses whose width is lower than this value will be ignored. (R/W)
\label{fielddesc:UARTGLITCHFILTEN}\item [UART\_GLITCH\_FILT\_EN] Configures whether or not to enable RX signal filter.\\
0: Disable\\
1: Enable(R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_CONF0\_SYNC\_REG}{0x0020}\label{regdesc:UARTCONF0SYNCREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{UART\_TXFIFO\_RST}{1}{23}{{0}}%
\regfield{UART\_RXFIFO\_RST}{1}{22}{{0}}%
\regfield{UART\_SW\_RTS}{1}{21}{{0}}%
\regfield{UART\_MEM\_CLK\_EN}{1}{20}{{1}}%
\regfield{UART\_AUTOBAUD\_EN}{1}{19}{{0}}%
\regfield{UART\_ERR\_WR\_MASK}{1}{18}{{0}}%
\regfield{UART\_DIS\_RX\_DAT\_OVF}{1}{17}{{0}}%
\regfield{UART\_TXD\_INV}{1}{16}{{0}}%
\regfield{UART\_RXD\_INV}{1}{15}{{0}}%
\regfield{UART\_IRDA\_EN}{1}{14}{{0}}%
\regfield{UART\_TX\_FLOW\_EN}{1}{13}{{0}}%
\regfield{UART\_LOOPBACK}{1}{12}{{0}}%
\regfield{UART\_IRDA\_RX\_INV}{1}{11}{{0}}%
\regfield{UART\_IRDA\_TX\_INV}{1}{10}{{0}}%
\regfield{UART\_IRDA\_WCTL}{1}{9}{{0}}%
\regfield{UART\_IRDA\_TX\_EN}{1}{8}{{0}}%
\regfield{UART\_IRDA\_DPLX}{1}{7}{{0}}%
\regfield{UART\_TXD\_BRK}{1}{6}{{0}}%
\regfield{UART\_STOP\_BIT\_NUM}{2}{4}{{1}}%
\regfield{UART\_BIT\_NUM}{2}{2}{{3}}%
\regfield{UART\_PARITY\_EN}{1}{1}{{0}}%
\regfield{UART\_PARITY}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTPARITY}\item [UART\_PARITY] Configures the parity check mode.\\
0: Even parity\\
1: Odd parity\\(R/W)
\label{fielddesc:UARTPARITYEN}\item [UART\_PARITY\_EN] Configures whether or not to enable UART parity check.\\
0: Disable\\
1: Enable\\(R/W)
\label{fielddesc:UARTBITNUM}\item [UART\_BIT\_NUM] Configures the number of data bits.\\
0: 5 bits\\
1: 6 bits\\
2: 7 bits\\
3: 8 bits\\(R/W)
\label{fielddesc:UARTSTOPBITNUM}\item [UART\_STOP\_BIT\_NUM] Configures the number of stop bits.\\
0: Invalid. No effect\\
1: 1 bit\\
2: 1.5 bits\\
3: 2 bits\\
(R/W)
\label{fielddesc:UARTTXDBRK}\item [UART\_TXD\_BRK] Configures whether or not to send NULL characters when finishing data transmission.\\
0: Not send\\
1: Send\\(R/W)
\label{fielddesc:UARTIRDADPLX}\item [UART\_IRDA\_DPLX] Configures whether or not to enable IrDA loopback test.\\
0: Disable\\
1: Enable\\(R/W)
\label{fielddesc:UARTIRDATXEN}\item [UART\_IRDA\_TX\_EN] Configures whether or not to enable the IrDA transmitter.\\
0: Disable\\
1: Enable\\(R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{UART\_CONF0\_SYNC\_REG}{0x0020}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:UARTIRDAWCTL}\item [UART\_IRDA\_WCTL] Configures the 11th bit of the IrDA transmitter.\\
0: This bit is 0.\\
1: This bit is the same as the 10th bit.\\(R/W)
\label{fielddesc:UARTIRDATXINV}\item [UART\_IRDA\_TX\_INV] Configures whether or not to invert the level of the IrDA transmitter.\\
0: Not invert\\
1: Invert\\(R/W)
\label{fielddesc:UARTIRDARXINV}\item [UART\_IRDA\_RX\_INV] Configures whether or not to invert the level of the IrDA receiver.\\
0: Not invert\\
1: Invert\\(R/W)
\label{fielddesc:UARTLOOPBACK}\item [UART\_LOOPBACK] Configures whether or not to enable UART loopback test.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:UARTTXFLOWEN}\item [UART\_TX\_FLOW\_EN] Configures whether or not to enable flow control for the transmitter.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:UARTIRDAEN}\item [UART\_IRDA\_EN] Configures whether or not to enable IrDA protocol.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:UARTRXDINV}\item [UART\_RXD\_INV] Configures whether or not to invert the level of UART RXD signal.\\
0: Not invert\\
1: Invert\\ (R/W)
\label{fielddesc:UARTTXDINV}\item [UART\_TXD\_INV] Configures whether or not to invert the level of UART TXD signal.\\
0: Not invert\\
1: Invert\\ (R/W)
\label{fielddesc:UARTDISRXDATOVF}\item [UART\_DIS\_RX\_DAT\_OVF] Configures whether or not to disable data overflow detection for the UART receiver.\\
0: Enable\\
1: Disable\\(R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{UART\_CONF0\_SYNC\_REG}{0x0020}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:UARTERRWRMASK}\item [UART\_ERR\_WR\_MASK] Configures whether or not to store the received data with errors into FIFO.\\
0: Store\\
1: Not store\\
(R/W)
\label{fielddesc:UARTAUTOBAUDEN}\item [UART\_AUTOBAUD\_EN] Configures whether or not to enable baud rate detection.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:UARTMEMCLKEN}\item [UART\_MEM\_CLK\_EN] Configures whether or not to enable clock gating for UART memory.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:UARTSWRTS}\item [UART\_SW\_RTS] Configures the RTS signal used in software flow control.\\
0: The UART transmitter is not allowed to send data.\\
1: The UART transmitted is allowed to send data.\\(R/W)
\label{fielddesc:UARTRXFIFORST}\item [UART\_RXFIFO\_RST] Configures whether or not to reset the UART RX FIFO.\\
0: Not reset\\
1: Reset\\(R/W)
\label{fielddesc:UARTTXFIFORST}\item [UART\_TXFIFO\_RST] Configures whether or not to reset the UART TX FIFO.\\
0: Not reset\\
1: Reset\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_CONF1\_REG}{0x0024}\label{regdesc:UARTCONF1REG}
\regfield{(reserved)}{10}{22}{0000000000}%
\regfield{UART\_CLK\_EN}{1}{21}{{0}}%
\regfield{UART\_SW\_DTR}{1}{20}{{0}}%
\regfield{UART\_DTR\_INV}{1}{19}{{0}}%
\regfield{UART\_RTS\_INV}{1}{18}{{0}}%
\regfield{UART\_DSR\_INV}{1}{17}{{0}}%
\regfield{UART\_CTS\_INV}{1}{16}{{0}}%
\regfield{UART\_TXFIFO\_EMPTY\_THRHD}{8}{8}{{0x60}}%
\regfield{UART\_RXFIFO\_FULL\_THRHD}{8}{0}{{0x60}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXFIFOFULLTHRHD}\item [UART\_RXFIFO\_FULL\_THRHD] Configures the threshold for RX FIFO being full.\\Measurement unit: byte. (R/W)
\label{fielddesc:UARTTXFIFOEMPTYTHRHD}\item [UART\_TXFIFO\_EMPTY\_THRHD] Configures the threshold for TX FIFO being empty.\\Measurement unit: byte. (R/W)
\label{fielddesc:UARTCTSINV}\item [UART\_CTS\_INV] Configures whether or not to invert the level of UART CTS signal.\\
0: Not invert\\
1: Invert\\ (R/W)
\label{fielddesc:UARTDSRINV}\item [UART\_DSR\_INV] Configures whether or not to invert the level of UART DSR signal.\\
0: Not invert\\
1: Invert\\ (R/W)
\label{fielddesc:UARTRTSINV}\item [UART\_RTS\_INV] Configures whether or not to invert the level of UART RTS signal.\\
0: Not invert\\
1: Invert\\ (R/W)
\label{fielddesc:UARTDTRINV}\item [UART\_DTR\_INV] Configures whether or not to invert the level of UART DTR signal.\\
0: Not invert\\
1: Invert\\ (R/W)
\label{fielddesc:UARTSWDTR}\item [UART\_SW\_DTR] Configures the DTR signal used in software flow control.\\
0: Data to be transmitted is not ready.\\
1: Data to be transmitted is ready.\\
(R/W)
\label{fielddesc:UARTCLKEN}\item [UART\_CLK\_EN] Configures clock gating.\\
0: Support clock only when the application writes registers.\\ 
1: Always force the clock on for registers.\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_HWFC\_CONF\_SYNC\_REG}{0x002C}\label{regdesc:UARTHWFCCONFSYNCREG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{UART\_RX\_FLOW\_EN}{1}{8}{{0}}%
\regfield{UART\_RX\_FLOW\_THRHD}{8}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXFLOWTHRHD}\item [UART\_RX\_FLOW\_THRHD] Configures the maximum number of data bytes that can be received  during hardware flow control.\\Measurement unit: byte. (R/W)
\label{fielddesc:UARTRXFLOWEN}\item [UART\_RX\_FLOW\_EN] Configures whether or not to enable the UART receiver.\\
0: Disable\\
1: Enable\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_SLEEP\_CONF0\_REG}{0x0030}\label{regdesc:UARTSLEEPCONF0REG}
\regfield{UART\_WK\_CHAR4}{8}{24}{{0x0}}%
\regfield{UART\_WK\_CHAR3}{8}{16}{{0x0}}%
\regfield{UART\_WK\_CHAR2}{8}{8}{{0x0}}%
\regfield{UART\_WK\_CHAR1}{8}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTWKCHAR1}\item [UART\_WK\_CHAR1] Configures wakeup character 1. (R/W)
\label{fielddesc:UARTWKCHAR2}\item [UART\_WK\_CHAR2] Configures wakeup character 2. (R/W)
\label{fielddesc:UARTWKCHAR3}\item [UART\_WK\_CHAR3] Configures wakeup character 3. (R/W)
\label{fielddesc:UARTWKCHAR4}\item [UART\_WK\_CHAR4] Configures wakeup character 4. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_SLEEP\_CONF1\_REG}{0x0034}\label{regdesc:UARTSLEEPCONF1REG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{UART\_WK\_CHAR0}{8}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTWKCHAR0}\item [UART\_WK\_CHAR0] Configures wakeup character 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_SLEEP\_CONF2\_REG}{0x0038}\label{regdesc:UARTSLEEPCONF2REG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{UART\_WK\_MODE\_SEL}{2}{26}{{0}}%
\regfield{UART\_WK\_CHAR\_MASK}{5}{21}{{0x0}}%
\regfield{UART\_WK\_CHAR\_NUM}{3}{18}{{0x5}}%
\regfield{UART\_RX\_WAKE\_UP\_THRHD}{8}{10}{{1}}%
\regfield{UART\_ACTIVE\_THRESHOLD}{10}{0}{{0xf0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTACTIVETHRESHOLD}\item [UART\_ACTIVE\_THRESHOLD] Configures the number of RXD edge changes to wake up the chip in wakeup mode 0. (R/W)
\label{fielddesc:UARTRXWAKEUPTHRHD}\item [UART\_RX\_WAKE\_UP\_THRHD] Configures the number of received data bytes to wake up the chip in wakeup mode 1. (R/W)
\label{fielddesc:UARTWKCHARNUM}\item [UART\_WK\_CHAR\_NUM] Configures the number of wakeup characters. (R/W)
\label{fielddesc:UARTWKCHARMASK}\item [UART\_WK\_CHAR\_MASK] Configures whether or not to mask wakeup characters.\\
0: Not mask\\
1: Mask\\(R/W)
\label{fielddesc:UARTWKMODESEL}\item [UART\_WK\_MODE\_SEL] Configures which wakeup mode to select.\\
0: Mode 0\\
1: Mode 1\\
2: Mode 2\\
3: Mode 3\\(R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_SWFC\_CONF0\_SYNC\_REG}{0x003C}\label{regdesc:UARTSWFCCONF0SYNCREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{UART\_SEND\_XOFF}{1}{22}{{0}}%
\regfield{UART\_SEND\_XON}{1}{21}{{0}}%
\regfield{UART\_FORCE\_XOFF}{1}{20}{{0}}%
\regfield{UART\_FORCE\_XON}{1}{19}{{0}}%
\regfield{UART\_XONOFF\_DEL}{1}{18}{{0}}%
\regfield{UART\_SW\_FLOW\_CON\_EN}{1}{17}{{0}}%
\regfield{UART\_XON\_XOFF\_STILL\_SEND}{1}{16}{{0}}%
\regfield{UART\_XOFF\_CHAR}{8}{8}{{0x13}}%
\regfield{UART\_XON\_CHAR}{8}{0}{{0x11}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTXONCHAR}\item [UART\_XON\_CHAR] Configures the XON character for flow control. (R/W)
\label{fielddesc:UARTXOFFCHAR}\item [UART\_XOFF\_CHAR] Configures the XOFF character for flow control. (R/W)
\label{fielddesc:UARTXONXOFFSTILLSEND}\item [UART\_XON\_XOFF\_STILL\_SEND] Configures whether the UART transmitter can send XON or XOFF characters when it is disabled.\\
0: Cannot send\\
1: Can send\\ (R/W)
\label{fielddesc:UARTSWFLOWCONEN}\item [UART\_SW\_FLOW\_CON\_EN] Configures whether or not to enable software flow control.\\
0: Disable\\
1: Enable\\(R/W)
\label{fielddesc:UARTXONOFFDEL}\item [UART\_XONOFF\_DEL] Configures whether or not to remove flow control characters from the received data.\\
0: Not move\\
1: Move\\(R/W)
\label{fielddesc:UARTFORCEXON}\item [UART\_FORCE\_XON] Configures whether the transmitter continues to sending data.\\
0: Not send\\
1: Send\\(R/W)
\label{fielddesc:UARTFORCEXOFF}\item [UART\_FORCE\_XOFF] Configures whether or not to stop the transmitter from sending data.\\
0: Not stop\\
1: Stop\\(R/W)
\label{fielddesc:UARTSENDXON}\item [UART\_SEND\_XON] Configures whether or not to send XON characters.\\
0: Not send\\
1: Send\\(R/W/SS/SC)
\label{fielddesc:UARTSENDXOFF}\item [UART\_SEND\_XOFF] Configures whether or not to send XOFF characters.\\
0: Not send\\
1: Send\\(R/W/SS/SC)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_SWFC\_CONF1\_REG}{0x0040}\label{regdesc:UARTSWFCCONF1REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{UART\_XOFF\_THRESHOLD}{8}{8}{{0xe0}}%
\regfield{UART\_XON\_THRESHOLD}{8}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTXONTHRESHOLD}\item [UART\_XON\_THRESHOLD] Configures the threshold for data in RX FIFO to send XON characters in software flow control.\\Measurement unit: byte. (R/W)
\label{fielddesc:UARTXOFFTHRESHOLD}\item [UART\_XOFF\_THRESHOLD]  Configures the threshold for data in RX FIFO to send XOFF characters in software flow control.\\Measurement unit: byte. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_TXBRK\_CONF\_SYNC\_REG}{0x0044}\label{regdesc:UARTTXBRKCONFSYNCREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{UART\_TX\_BRK\_NUM}{8}{0}{{0xa}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTTXBRKNUM}\item [UART\_TX\_BRK\_NUM] Configures the number of NULL characters to be sent after finishing data transmission.\\Valid only when UART\_TXD\_BRK is 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_IDLE\_CONF\_SYNC\_REG}{0x0048}\label{regdesc:UARTIDLECONFSYNCREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{UART\_TX\_IDLE\_NUM}{10}{10}{{0x100}}%
\regfield{UART\_RX\_IDLE\_THRHD}{10}{0}{{0x100}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXIDLETHRHD}\item [UART\_RX\_IDLE\_THRHD] Configures the threshold to generate a frame end signal when the receiver takes more time to receive one data byte data.\\Measurement unit: bit time (the time to transmit 1 bit). (R/W)
\label{fielddesc:UARTTXIDLENUM}\item [UART\_TX\_IDLE\_NUM] Configures the interval between two data transfers.\\Measurement unit: bit time (the time to transmit 1 bit). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_RS485\_CONF\_SYNC\_REG}{0x004C}\label{regdesc:UARTRS485CONFSYNCREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{UART\_RS485\_TX\_DLY\_NUM}{4}{6}{{0}}%
\regfield{UART\_RS485\_RX\_DLY\_NUM}{1}{5}{{0}}%
\regfield{UART\_RS485RXBY\_TX\_EN}{1}{4}{{0}}%
\regfield{UART\_RS485TX\_RX\_EN}{1}{3}{{0}}%
\regfield{UART\_DL1\_EN}{1}{2}{{0}}%
\regfield{UART\_DL0\_EN}{1}{1}{{0}}%
\regfield{UART\_RS485\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRS485EN}\item [UART\_RS485\_EN] Configures whether or not to enable RS485 mode.\\
0: Disable\\
1: Enable\\
(R/W)
\label{fielddesc:UARTDL0EN}\item [UART\_DL0\_EN] Configures whether or not to add a turnaround delay of 1 bit before the start bit.\\
0: Not add\\
1: Add\\(R/W)
\label{fielddesc:UARTDL1EN}\item [UART\_DL1\_EN] Configures whether or not to add a turnaround delay of 1 bit after the stop bit.\\
0: Not add\\
1: Add\\(R/W)
\label{fielddesc:UARTRS485TXRXEN}\item [UART\_RS485TX\_RX\_EN] Configures whether or not to enable the receiver for data reception when the transmitter is transmitting data in RS485 mode.\\
0: Disable\\
1: Enable\\(R/W)
\label{fielddesc:UARTRS485RXBYTXEN}\item [UART\_RS485RXBY\_TX\_EN] Configures whether to enable the RS485 transmitter for data transmission when the RS485 receiver is busy.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:UARTRS485RXDLYNUM}\item [UART\_RS485\_RX\_DLY\_NUM] Configures the delay of internal data signals in the receiver.\\Measurement unit: bit time (the time to transmit 1 bit).. (R/W)
\label{fielddesc:UARTRS485TXDLYNUM}\item [UART\_RS485\_TX\_DLY\_NUM] Configures the delay of internal data signals in the transmitter.\\Measurement unit: bit time (the time to transmit 1 bit).  (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_CLK\_CONF\_REG}{0x0088}\label{regdesc:UARTCLKCONFREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{UART\_RX\_RST\_CORE}{1}{27}{{0}}%
\regfield{UART\_TX\_RST\_CORE}{1}{26}{{0}}%
\regfield{UART\_RX\_SCLK\_EN}{1}{25}{{1}}%
\regfield{UART\_TX\_SCLK\_EN}{1}{24}{{1}}%
\regfield{(reserved)}{24}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTTXSCLKEN}\item [UART\_TX\_SCLK\_EN] Configures whether or not to enable UART TX clock.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:UARTRXSCLKEN}\item [UART\_RX\_SCLK\_EN] Configures whether or not to enable UART RX clock.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:UARTTXRSTCORE}\item [UART\_TX\_RST\_CORE] Write 1 and then write 0 to reset UART TX. (R/W)
\label{fielddesc:UARTRXRSTCORE}\item [UART\_RX\_RST\_CORE] Write 1 and then write 0 to reset UART RX. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_STATUS\_REG}{0x001C}\label{regdesc:UARTSTATUSREG}
\regfield{UART\_TXD}{1}{31}{{1}}%
\regfield{UART\_RTSN}{1}{30}{{1}}%
\regfield{UART\_DTRN}{1}{29}{{1}}%
\regfield{(reserved)}{5}{24}{00000}%
\regfield{UART\_TXFIFO\_CNT}{8}{16}{{0}}%
\regfield{UART\_RXD}{1}{15}{{1}}%
\regfield{UART\_CTSN}{1}{14}{{1}}%
\regfield{UART\_DSRN}{1}{13}{{0}}%
\regfield{(reserved)}{5}{8}{00000}%
\regfield{UART\_RXFIFO\_CNT}{8}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXFIFOCNT}\item [UART\_RXFIFO\_CNT] Represents the number of valid data bytes in RX FIFO. (RO)
\label{fielddesc:UARTDSRN}\item [UART\_DSRN] Represents the level of the internal UART DSR signal. (RO)
\label{fielddesc:UARTCTSN}\item [UART\_CTSN] Represents the level of the internal UART CTS signal. (RO)
\label{fielddesc:UARTRXD}\item [UART\_RXD] Represents the  level of the internal UART RXD signal. (RO)
\label{fielddesc:UARTTXFIFOCNT}\item [UART\_TXFIFO\_CNT] Represents the number of valid data bytes in RX FIFO. (RO)
\label{fielddesc:UARTDTRN}\item [UART\_DTRN] Represents the level of the internal UART DTR signal. (RO)
\label{fielddesc:UARTRTSN}\item [UART\_RTSN] Represents the level of the internal UART RTS signal. (RO)
\label{fielddesc:UARTTXD}\item [UART\_TXD] Represents the  level of the internal UART TXD signal. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_MEM\_TX\_STATUS\_REG}{0x0068}\label{regdesc:UARTMEMTXSTATUSREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{UART\_TX\_SRAM\_RADDR}{8}{9}{{0x0}}%
\regfield{(reserved)}{1}{8}{0}%
\regfield{UART\_TX\_SRAM\_WADDR}{8}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTTXSRAMWADDR}\item [UART\_TX\_SRAM\_WADDR] Represents the offset address to write TX FIFO. (RO)
\label{fielddesc:UARTTXSRAMRADDR}\item [UART\_TX\_SRAM\_RADDR] Represents the offset address to read TX FIFO. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_MEM\_RX\_STATUS\_REG}{0x006C}\label{regdesc:UARTMEMRXSTATUSREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{UART\_RX\_SRAM\_WADDR}{8}{9}{{0x80}}%
\regfield{(reserved)}{1}{8}{0}%
\regfield{UART\_RX\_SRAM\_RADDR}{8}{0}{{0x80}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXSRAMRADDR}\item [UART\_RX\_SRAM\_RADDR] Represents the offset address to read RX FIFO. (RO)
\label{fielddesc:UARTRXSRAMWADDR}\item [UART\_RX\_SRAM\_WADDR] Represents the offset address to write RX FIFO. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_FSM\_STATUS\_REG}{0x0070}\label{regdesc:UARTFSMSTATUSREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{UART\_ST\_UTX\_OUT}{4}{4}{{0}}%
\regfield{UART\_ST\_URX\_OUT}{4}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTSTURXOUT}\item [UART\_ST\_URX\_OUT] Represents the status of the receiver. (RO)
\label{fielddesc:UARTSTUTXOUT}\item [UART\_ST\_UTX\_OUT] Represents the status of the transmitter. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_AFIFO\_STATUS\_REG}{0x0090}\label{regdesc:UARTAFIFOSTATUSREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{UART\_RX\_AFIFO\_EMPTY}{1}{3}{{1}}%
\regfield{UART\_RX\_AFIFO\_FULL}{1}{2}{{0}}%
\regfield{UART\_TX\_AFIFO\_EMPTY}{1}{1}{{1}}%
\regfield{UART\_TX\_AFIFO\_FULL}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTTXAFIFOFULL}\item [UART\_TX\_AFIFO\_FULL] Represents whether or not the APB TX asynchronous FIFO is full.\\
0: Not full\\
1: Full\\(RO)
\label{fielddesc:UARTTXAFIFOEMPTY}\item [UART\_TX\_AFIFO\_EMPTY] Represents whether or not the APB TX asynchronous FIFO is empty.\\
0: Not empty\\
1: Empty\\ (RO)
\label{fielddesc:UARTRXAFIFOFULL}\item [UART\_RX\_AFIFO\_FULL] Represents whether or not the APB RX asynchronous FIFO is full.\\
0: Not full\\
1: Full\\ (RO)
\label{fielddesc:UARTRXAFIFOEMPTY}\item [UART\_RX\_AFIFO\_EMPTY] Represents whether or not the APB RX asynchronous FIFO is empty.\\
0: Not empty\\
1: Empty\\ (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_AT\_CMD\_PRECNT\_SYNC\_REG}{0x0050}\label{regdesc:UARTATCMDPRECNTSYNCREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{UART\_PRE\_IDLE\_NUM}{16}{0}{{0x901}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTPREIDLENUM}\item [UART\_PRE\_IDLE\_NUM] Configures the idle time before the receiver receives the first AT\_CMD.\\Measurement unit: bit time (the time to transmit 1 bit). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_AT\_CMD\_POSTCNT\_SYNC\_REG}{0x0054}\label{regdesc:UARTATCMDPOSTCNTSYNCREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{UART\_POST\_IDLE\_NUM}{16}{0}{{0x901}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTPOSTIDLENUM}\item [UART\_POST\_IDLE\_NUM] Configures the interval between the last AT\_CMD and subsequent data.\\Measurement unit: bit time (the time to transmit 1 bit). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_AT\_CMD\_GAPTOUT\_SYNC\_REG}{0x0058}\label{regdesc:UARTATCMDGAPTOUTSYNCREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{UART\_RX\_GAP\_TOUT}{16}{0}{{11}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXGAPTOUT}\item [UART\_RX\_GAP\_TOUT] Configures the interval between two AT\_CMD characters.\\Measurement unit: bit time (the time to transmit 1 bit). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_AT\_CMD\_CHAR\_SYNC\_REG}{0x005C}\label{regdesc:UARTATCMDCHARSYNCREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{UART\_CHAR\_NUM}{8}{8}{{0x3}}%
\regfield{UART\_AT\_CMD\_CHAR}{8}{0}{{0x2b}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTATCMDCHAR}\item [UART\_AT\_CMD\_CHAR] Configures the AT\_CMD character. (R/W)
\label{fielddesc:UARTCHARNUM}\item [UART\_CHAR\_NUM] Configures the number of continuous AT\_CMD characters a receiver can receive. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_POSPULSE\_REG}{0x0074}\label{regdesc:UARTPOSPULSEREG}
\regfield{(reserved)}{20}{12}{00000000000000000000}%
\regfield{UART\_POSEDGE\_MIN\_CNT}{12}{0}{{0xfff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTPOSEDGEMINCNT}\item [UART\_POSEDGE\_MIN\_CNT] Represents the minimal input clock counter value between two positive edges. It is used for baud rate detection. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_NEGPULSE\_REG}{0x0078}\label{regdesc:UARTNEGPULSEREG}
\regfield{(reserved)}{20}{12}{00000000000000000000}%
\regfield{UART\_NEGEDGE\_MIN\_CNT}{12}{0}{{0xfff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTNEGEDGEMINCNT}\item [UART\_NEGEDGE\_MIN\_CNT] Represents the minimal input clock counter value between two negative edges. It is used for baud rate detection. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_LOWPULSE\_REG}{0x007C}\label{regdesc:UARTLOWPULSEREG}
\regfield{(reserved)}{20}{12}{00000000000000000000}%
\regfield{UART\_LOWPULSE\_MIN\_CNT}{12}{0}{{0xfff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTLOWPULSEMINCNT}\item [UART\_LOWPULSE\_MIN\_CNT] Represents the minimum duration time of a low-level pulse. It is used for baud rate detection.\\Measurement unit: APB\_CLK clock cycle. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_HIGHPULSE\_REG}{0x0080}\label{regdesc:UARTHIGHPULSEREG}
\regfield{(reserved)}{20}{12}{00000000000000000000}%
\regfield{UART\_HIGHPULSE\_MIN\_CNT}{12}{0}{{0xfff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTHIGHPULSEMINCNT}\item [UART\_HIGHPULSE\_MIN\_CNT] Represents  the maximum duration time for a high-level pulse. It is used for baud rate detection.\\Measurement unit: APB\_CLK clock cycle.  (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_RXD\_CNT\_REG}{0x0084}\label{regdesc:UARTRXDCNTREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{UART\_RXD\_EDGE\_CNT}{10}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXDEDGECNT}\item [UART\_RXD\_EDGE\_CNT] Represents the number of RXD edge changes. It is used for baud rate detection. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_DATE\_REG}{0x008C}\label{regdesc:UARTDATEREG}
\regfield{UART\_DATE}{32}{0}{{0x2201260}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTDATE}\item [UART\_DATE] Version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_REG\_UPDATE\_REG}{0x0098}\label{regdesc:UARTREGUPDATEREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{UART\_REG\_UPDATE}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTREGUPDATE}\item [UART\_REG\_UPDATE] Configures whether or not to synchronize registers.\\
0: Not synchronize\\
1: Synchronize\\(R/W/SC)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_ID\_REG}{0x009C}\label{regdesc:UARTIDREG}
\regfield{UART\_ID}{32}{0}{{0x000500}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTID}\item [UART\_ID] Configures the UART ID. (R/W)
\end{reglist}\end{regdesc}
\end{register}
