\begin{register}{H}{RTC\_CNTL\_RTC\_OPTIONS0\_REG}{0x{}0000}\label{regdesc:RTCCNTLRTCOPTIONS0REG}
\regfield{RTC\_CNTL\_SW\_SYS\_RST}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_NORST}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_RST}{1}{29}{{0}}%
\regfield{(reserved)}{15}{14}{000000000000000}%
\regfield{RTC\_CNTL\_XTL\_FORCE\_PU}{1}{13}{{1}}%
\regfield{RTC\_CNTL\_XTL\_FORCE\_PD}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_BBPLL\_FORCE\_PU}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_BBPLL\_FORCE\_PD}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PU}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PD}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_BB\_I2C\_FORCE\_PU}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_BB\_I2C\_FORCE\_PD}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_SW\_PROCPU\_RST}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_SW\_APPCPU\_RST}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_SW\_STALL\_PROCPU\_C0}{2}{2}{{0}}%
\regfield{RTC\_CNTL\_SW\_STALL\_APPCPU\_C0}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWSTALLAPPCPUC0}\item [RTC\_CNTL\_SW\_STALL\_APPCPU\_C0] When \hyperref[fielddesc:RTCCNTLSWSTALLPROCPUC1]{RTC\_CNTL\_SW\_STALL\_APPCPU\_C1} is configured to 0x{}21, setting this field to 0x{}2 stalls the CPU1 by SW. (R/W)
\label{fielddesc:RTCCNTLSWSTALLPROCPUC0}\item [RTC\_CNTL\_SW\_STALL\_PROCPU\_C0] When \hyperref[fielddesc:RTCCNTLSWSTALLPROCPUC1]{RTC\_CNTL\_SW\_STALL\_PROCPU\_C1} is configured to 0x{}21, setting this field to 0x{}2 stalls the CPU0 by SW. (R/W)
\label{fielddesc:RTCCNTLSWAPPCPURST}\item [RTC\_CNTL\_SW\_APPCPU\_RST] Set this bit to reset the CPU1 by SW. (WO)
\label{fielddesc:RTCCNTLSWPROCPURST}\item [RTC\_CNTL\_SW\_PROCPU\_RST] Set this bit to reset the CPU0 by SW. (WO)
\label{fielddesc:RTCCNTLBBI2CFORCEPD}\item [RTC\_CNTL\_BB\_I2C\_FORCE\_PD] Set this bit to FPD BB\_I2C. (R/W)
\label{fielddesc:RTCCNTLBBI2CFORCEPU}\item [RTC\_CNTL\_BB\_I2C\_FORCE\_PU] Set this bit to FPU BB\_I2C. (R/W)
\label{fielddesc:RTCCNTLBBPLLI2CFORCEPD}\item [RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PD] Set this bit to FPD BB\_PLL \_I2C. (R/W)
\label{fielddesc:RTCCNTLBBPLLI2CFORCEPU}\item [RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PU] Set this bit to FPU BB\_PLL \_I2C. (R/W)
\label{fielddesc:RTCCNTLBBPLLFORCEPD}\item [RTC\_CNTL\_BBPLL\_FORCE\_PD] Set this bit to FPD BB\_PLL. (R/W)
\label{fielddesc:RTCCNTLBBPLLFORCEPU}\item [RTC\_CNTL\_BBPLL\_FORCE\_PU] Set this bit to FPU BB\_PLL. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_RTC\_OPTIONS0\_REG}{0x{}0000}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:RTCCNTLXTLFORCEPD}\item [RTC\_CNTL\_XTL\_FORCE\_PD] Set this bit to FPD the crystal oscillator. (R/W)
\label{fielddesc:RTCCNTLXTLFORCEPU}\item [RTC\_CNTL\_XTL\_FORCE\_PU] Set this bit to FPU the crystal oscillator. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCERST}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_RST] Set this bit to force reset the digital system in deep-sleep. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCENORST}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_NORST] Set this bit to disable force reset to digital system in deep-sleep. (R/W)
\label{fielddesc:RTCCNTLSWSYSRST}\item [RTC\_CNTL\_SW\_SYS\_RST] Set this bit to reset the system via SW. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_SLP\_TIMER0\_REG}{0x{}0004}\label{regdesc:RTCCNTLRTCSLPTIMER0REG}
\regfield{RTC\_CNTL\_SLP\_VAL\_LO}{32}{0}{{0x{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPVALLO}\item [RTC\_CNTL\_SLP\_VAL\_LO] Sets the lower 32 bits of the trigger threshold for the RTC timer. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_SLP\_TIMER1\_REG}{0x{}0008}\label{regdesc:RTCCNTLRTCSLPTIMER1REG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{RTC\_CNTL\_RTC\_MAIN\_TIMER\_ALARM\_EN}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_SLP\_VAL\_HI}{16}{0}{{0x{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPVALHI}\item [RTC\_CNTL\_SLP\_VAL\_HI] Sets the higher 16 bits of the trigger threshold for the RTC timer. (R/W)
\label{fielddesc:RTCCNTLRTCMAINTIMERALARMEN}\item [RTC\_CNTL\_RTC\_MAIN\_TIMER\_ALARM\_EN] Sets this bit to enable the timer alarm. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_TIME\_UPDATE\_REG}{0x{}000C}\label{regdesc:RTCCNTLRTCTIMEUPDATEREG}
\regfield{RTC\_CNTL\_RTC\_TIME\_UPDATE}{1}{31}{{0}}%
\regfield{(reserved)}{1}{30}{0}%
\regfield{RTC\_CNTL\_TIMER\_SYS\_RST}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_TIMER\_XTL\_OFF}{1}{28}{{0}}%
\regfield{RTC\_CNTL\_TIMER\_SYS\_STALL}{1}{27}{{0}}%
\regfield{(reserved)}{27}{0}{000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTIMERSYSSTALL}\item [RTC\_CNTL\_TIMER\_SYS\_STALL] Selects the triggering condition for the RTC timer. See details in Table \ref{tab:lpm-Update-RTC-TIMER-VALUE}. (R/W)
\label{fielddesc:RTCCNTLTIMERXTLOFF}\item [RTC\_CNTL\_TIMER\_XTL\_OFF] Selects the triggering condition for the RTC timer. See details in Table \ref{tab:lpm-Update-RTC-TIMER-VALUE}. (R/W)
\label{fielddesc:RTCCNTLTIMERSYSRST}\item [RTC\_CNTL\_TIMER\_SYS\_RST] Selects the triggering condition for the RTC timer. See details in Table \ref{tab:lpm-Update-RTC-TIMER-VALUE}. (R/W)
\label{fielddesc:RTCCNTLRTCTIMEUPDATE}\item [RTC\_CNTL\_RTC\_TIME\_UPDATE] Selects the triggering condition for the RTC timer. See details in Table \ref{tab:lpm-Update-RTC-TIMER-VALUE}. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_TIME\_LOW0\_REG}{0x{}0010}\label{regdesc:RTCCNTLRTCTIMELOW0REG}
\regfield{RTC\_CNTL\_RTC\_TIMER\_VALUE0\_LOW}{32}{0}{{0x{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCTIMERVALUE0LOW}\item [RTC\_CNTL\_RTC\_TIMER\_VALUE0\_LOW] Stores the lower 32 bits of RTC timer 0. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_TIME\_HIGH0\_REG}{0x{}0014}\label{regdesc:RTCCNTLRTCTIMEHIGH0REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{RTC\_CNTL\_RTC\_TIMER\_VALUE0\_HIGH}{16}{0}{{0x{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCTIMERVALUE0HIGH}\item [RTC\_CNTL\_RTC\_TIMER\_VALUE0\_HIGH] Stores the higher 16 bits of RTC timer 0. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_STATE0\_REG}{0x{}0018}\label{regdesc:RTCCNTLRTCSTATE0REG}
\regfield{RTC\_CNTL\_SLEEP\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_SLP\_REJECT}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_SDIO\_ACTIVE\_IND}{1}{28}{{0}}%
\regfield{(reserved)}{5}{23}{00000}%
\regfield{RTC\_CNTL\_APB2RTC\_BRIDGE\_SEL}{1}{22}{{0}}%
\regfield{(reserved)}{20}{2}{00000000000000000000}%
\regfield{RTC\_CNTL\_RTC\_SLP\_REJECT\_CAUSE\_CLR}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SW\_CPU\_INT}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSWCPUINT}\item [RTC\_CNTL\_RTC\_SW\_CPU\_INT] Sends a SW RTC interrupt to CPU. (WO)
\label{fielddesc:RTCCNTLRTCSLPREJECTCAUSECLR}\item [RTC\_CNTL\_RTC\_SLP\_REJECT\_CAUSE\_CLR] Clears the RTC reject-to-sleep cause. (WO)
\label{fielddesc:RTCCNTLAPB2RTCBRIDGESEL}\item [RTC\_CNTL\_APB2RTC\_BRIDGE\_SEL] 1: APB to RTC using bridge, 0: APB to RTC using sync (R/W)
\label{fielddesc:RTCCNTLSDIOACTIVEIND}\item [RTC\_CNTL\_SDIO\_ACTIVE\_IND] Indicates the SDIO is active. (RO)
\label{fielddesc:RTCCNTLSLPWAKEUP}\item [RTC\_CNTL\_SLP\_WAKEUP] Indicates wakeup events. (R/W)
\label{fielddesc:RTCCNTLSLPREJECT}\item [RTC\_CNTL\_SLP\_REJECT] Indicates reject-to-sleep event. (R/W)
\label{fielddesc:RTCCNTLSLEEPEN}\item [RTC\_CNTL\_SLEEP\_EN] Sends the chip to sleep. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_TIMER1\_REG}{0x{}001C}\label{regdesc:RTCCNTLRTCTIMER1REG}
\regfield{RTC\_CNTL\_PLL\_BUF\_WAIT}{8}{24}{{40}}%
\regfield{RTC\_CNTL\_XTL\_BUF\_WAIT}{10}{14}{{80}}%
\regfield{RTC\_CNTL\_CK8M\_WAIT}{8}{6}{{0x{}10}}%
\regfield{RTC\_CNTL\_CPU\_STALL\_WAIT}{5}{1}{{1}}%
\regfield{RTC\_CNTL\_CPU\_STALL\_EN}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLCPUSTALLEN}\item [RTC\_CNTL\_CPU\_STALL\_EN] Enables CPU stalling. (R/W)
\label{fielddesc:RTCCNTLCPUSTALLWAIT}\item [RTC\_CNTL\_CPU\_STALL\_WAIT] Sets the CPU stall waiting cycle (using the RTC fast clock). (R/W)
\label{fielddesc:RTCCNTLCK8MWAIT}\item [RTC\_CNTL\_CK8M\_WAIT] Sets the FOSC waiting cycle (using the RTC slow clock). (R/W)
\label{fielddesc:RTCCNTLXTLBUFWAIT}\item [RTC\_CNTL\_XTL\_BUF\_WAIT] Sets the XTAL waiting cycle (using the RTC slow clock). (R/W)
\label{fielddesc:RTCCNTLPLLBUFWAIT}\item [RTC\_CNTL\_PLL\_BUF\_WAIT] Sets the PLL waiting cycle (using the RTC slow clock). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_TIMER2\_REG}{0x{}0020}\label{regdesc:RTCCNTLRTCTIMER2REG}
\regfield{RTC\_CNTL\_MIN\_TIME\_CK8M\_OFF}{8}{24}{{0x{}1}}%
\regfield{RTC\_CNTL\_ULPCP\_TOUCH\_START\_WAIT}{9}{15}{{0x{}10}}%
\regfield{(reserved)}{15}{0}{000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLULPCPTOUCHSTARTWAIT}\item [RTC\_CNTL\_ULPCP\_TOUCH\_START\_WAIT] Sets the waiting cycle (using the RTC slow clock) before the ULP co-processor starts to work. (R/W)
\label{fielddesc:RTCCNTLMINTIMECK8MOFF}\item [RTC\_CNTL\_MIN\_TIME\_CK8M\_OFF] Sets the minimal cycle for FOSC clock (using the RTC slow clock) when powered down. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_TIMER5\_REG}{0x{}002C}\label{regdesc:RTCCNTLRTCTIMER5REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{RTC\_CNTL\_MIN\_SLP\_VAL}{8}{8}{{0x{}80}}%
\regfield{(reserved)}{8}{0}{00000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLMINSLPVAL}\item [RTC\_CNTL\_MIN\_SLP\_VAL] Sets the minimal sleep cycles (using the RTC slow clock). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_ANA\_CONF\_REG}{0x{}0034}\label{regdesc:RTCCNTLRTCANACONFREG}
\regfield{(reserved)}{11}{21}{00000000010}%
\regfield{RTC\_CNTL\_GLITCH\_RST\_EN}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_I2C\_RESET\_POR\_FORCE\_PU}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_I2C\_RESET\_POR\_FORCE\_PD}{1}{18}{{1}}%
\regfield{(reserved)}{18}{0}{000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLI2CRESETPORFORCEPD}\item [RTC\_CNTL\_I2C\_RESET\_POR\_FORCE\_PD] Set this bit to FPD SLEEP\_I2CPOR. (R/W)
\label{fielddesc:RTCCNTLI2CRESETPORFORCEPU}\item [RTC\_CNTL\_I2C\_RESET\_POR\_FORCE\_PU] Set this bit to FPU SLEEP\_I2CPOR. (R/W)
\label{fielddesc:RTCCNTLGLITCHRSTEN}\item [RTC\_CNTL\_GLITCH\_RST\_EN] Set this bit to enable a reset when the system detects a glitch. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_RESET\_STATE\_REG}{0x{}0038}\label{regdesc:RTCCNTLRTCRESETSTATEREG}
\regfield{(reserved)}{6}{26}{000000}%
\regfield{RTC\_CNTL\_RTC\_PRO\_DRESET\_MASK}{1}{25}{{0}}%
\regfield{RTC\_CNTL\_RTC\_APP\_DRESET\_MASK}{1}{24}{{0}}%
\regfield{RTC\_CNTL\_RESET\_FLAG\_JTAG\_APPCPU\_CLR}{1}{23}{{0}}%
\regfield{RTC\_CNTL\_RESET\_FLAG\_JTAG\_PROCPU\_CLR}{1}{22}{{0}}%
\regfield{RTC\_CNTL\_RESET\_FLAG\_JTAG\_APPCPU}{1}{21}{{0}}%
\regfield{RTC\_CNTL\_RESET\_FLAG\_JTAG\_PROCPU}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_PROCPU\_OCD\_HALT\_ON\_RESET}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_APPCPU\_OCD\_HALT\_ON\_RESET}{1}{18}{{0}}%
\regfield{RTC\_CNTL\_RESET\_FLAG\_APPCPU\_CLR}{1}{17}{{0}}%
\regfield{RTC\_CNTL\_RESET\_FLAG\_PROCPU\_CLR}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_RESET\_FLAG\_APPCPU}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_RESET\_FLAG\_PROCPU}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_PROCPU\_STAT\_VECTOR\_SEL}{1}{13}{{1}}%
\regfield{RTC\_CNTL\_APPCPU\_STAT\_VECTOR\_SEL}{1}{12}{{1}}%
\regfield{RTC\_CNTL\_RESET\_CAUSE\_APPCPU}{6}{6}{{0}}%
\regfield{RTC\_CNTL\_RESET\_CAUSE\_PROCPU}{6}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRESETCAUSEPROCPU}\item [RTC\_CNTL\_RESET\_CAUSE\_PROCPU] Stores CPU0's reset cause. (RO)
\label{fielddesc:RTCCNTLRESETCAUSEAPPCPU}\item [RTC\_CNTL\_RESET\_CAUSE\_APPCPU] Stores CPU1's reset cause. (RO)
\label{fielddesc:RTCCNTLAPPCPUSTATVECTORSEL}\item [RTC\_CNTL\_APPCPU\_STAT\_VECTOR\_SEL] Selects CPU1 state vector.l (R/W)
\label{fielddesc:RTCCNTLPROCPUSTATVECTORSEL}\item [RTC\_CNTL\_PROCPU\_STAT\_VECTOR\_SEL] Selects CPU0 state vector.l (R/W)
\label{fielddesc:RTCCNTLRESETFLAGPROCPU}\item [RTC\_CNTL\_RESET\_FLAG\_PROCPU] Sets CPU0 reset flag. (RO)
\label{fielddesc:RTCCNTLRESETFLAGAPPCPU}\item [RTC\_CNTL\_RESET\_FLAG\_APPCPU] Sets CPU1 reset flag. (RO)
\label{fielddesc:RTCCNTLRESETFLAGPROCPUCLR}\item [RTC\_CNTL\_RESET\_FLAG\_PROCPU\_CLR] Set this bit to clear CPU0 reset flag. (WO)
\label{fielddesc:RTCCNTLRESETFLAGAPPCPUCLR}\item [RTC\_CNTL\_RESET\_FLAG\_APPCPU\_CLR] Set this bit to clear CPU1 reset flag. (WO)
\label{fielddesc:RTCCNTLAPPCPUOCDHALTONRESET}\item [RTC\_CNTL\_APPCPU\_OCD\_HALT\_ON\_RESET] Enables CPU1 to enter halt state after reset. (R/W)
\label{fielddesc:RTCCNTLPROCPUOCDHALTONRESET}\item [RTC\_CNTL\_PROCPU\_OCD\_HALT\_ON\_RESET] Enables CPU0 to enter halt state after reset. (R/W)
\label{fielddesc:RTCCNTLRESETFLAGJTAGPROCPU}\item [RTC\_CNTL\_RESET\_FLAG\_JTAG\_PROCPU] Sets CPU0's JTAG reset flag. (RO)
\label{fielddesc:RTCCNTLRESETFLAGJTAGAPPCPU}\item [RTC\_CNTL\_RESET\_FLAG\_JTAG\_APPCPU] Sets CPU1's JTAG reset flag. (RO)
\label{fielddesc:RTCCNTLRESETFLAGJTAGPROCPUCLR}\item [RTC\_CNTL\_RESET\_FLAG\_JTAG\_PROCPU\_CLR] Set this bit to clear CPU0 JTAG reset flag. (WO)
\label{fielddesc:RTCCNTLRESETFLAGJTAGAPPCPUCLR}\item [RTC\_CNTL\_RESET\_FLAG\_JTAG\_APPCPU\_CLR] Set this bit to clear CPU1 JTAG reset flag. (WO)
\label{fielddesc:RTCCNTLRTCAPPDRESETMASK}\item [RTC\_CNTL\_RTC\_APP\_DRESET\_MASK] Set this bit to bypass CPU1 dreset. (R/W)
\label{fielddesc:RTCCNTLRTCPRODRESETMASK}\item [RTC\_CNTL\_RTC\_PRO\_DRESET\_MASK] Set this bit to bypass CPU0 dreset. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_WAKEUP\_STATE\_REG}{0x{}003C}\label{regdesc:RTCCNTLRTCWAKEUPSTATEREG}
\regfield{RTC\_CNTL\_RTC\_WAKEUP\_ENA}{17}{15}{{12}}%
\regfield{(reserved)}{15}{0}{000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCWAKEUPENA}\item [RTC\_CNTL\_RTC\_WAKEUP\_ENA] Enables the wakeup bitmap. See details in Table \ref{tab:lpm-wakeup-source}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_ENA\_RTC\_REG}{0x{}0040}\label{regdesc:RTCCNTLINTENARTCREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_APPROACH\_LOOP\_DONE\_INT\_ENA}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_ENA}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_ENA}{1}{18}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_ENA}{1}{17}{{0}}%
\regfield{RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_ENA}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SWD\_INT\_ENA}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC2\_INT\_ENA}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_INT\_ENA}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TSENS\_INT\_ENA}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC1\_INT\_ENA}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_ENA}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_ENA}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_ENA}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_ENA}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_ENA}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_RTC\_ULP\_CP\_INT\_ENA}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_ENA}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_RTC\_WDT\_INT\_ENA}{1}{3}{{0}}%
\regfield{RTC\_CNTL\_SDIO\_IDLE\_INT\_ENA}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_ENA}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTENA}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA] Enables interrupt when the chip wakes up from sleep. (R/W)
\label{fielddesc:RTCCNTLSLPREJECTINTENA}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_ENA] Enables interrupt when the chip rejects to go to sleep. (R/W)
\label{fielddesc:RTCCNTLSDIOIDLEINTENA}\item [RTC\_CNTL\_SDIO\_IDLE\_INT\_ENA] Enables interrupt when the SDIO idles. (R/W)
\label{fielddesc:RTCCNTLRTCWDTINTENA}\item [RTC\_CNTL\_RTC\_WDT\_INT\_ENA] Enables the RTC watchdog interrupt. (R/W)
\label{fielddesc:RTCCNTLRTCTOUCHSCANDONEINTENA}\item [RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_ENA] Enables interrupt upon the completion of a touch scanning. (R/W)
\label{fielddesc:RTCCNTLRTCULPCPINTENA}\item [RTC\_CNTL\_RTC\_ULP\_CP\_INT\_ENA] Enables the ULP co-processor interrupt. (R/W)
\label{fielddesc:RTCCNTLRTCTOUCHDONEINTENA}\item [RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_ENA] Enables interrupt upon the completion of a single touch. (R/W)
\label{fielddesc:RTCCNTLRTCTOUCHACTIVEINTENA}\item [RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_ENA] Enables interrupt when a touch is detected. (R/W)
\label{fielddesc:RTCCNTLRTCTOUCHINACTIVEINTENA}\item [RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_ENA] Enables interrupt when a touch is released. (R/W)
\label{fielddesc:RTCCNTLRTCBROWNOUTINTENA}\item [RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_ENA] Enables the brown out interrupt. (R/W)


\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_INT\_ENA\_RTC\_REG}{0x{}0040}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:RTCCNTLRTCMAINTIMERINTENA}\item [RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_ENA] Enables the RTC main timer interrupt. (R/W)
\label{fielddesc:RTCCNTLRTCSARADC1INTENA}\item [RTC\_CNTL\_RTC\_SARADC1\_INT\_ENA] Enables the SAR ADC1 interrupt. (R/W)
\label{fielddesc:RTCCNTLRTCTSENSINTENA}\item [RTC\_CNTL\_RTC\_TSENS\_INT\_ENA] Enables the temperature sensor interrupt. (R/W)
\label{fielddesc:RTCCNTLRTCCOCPUINTENA}\item [RTC\_CNTL\_RTC\_COCPU\_INT\_ENA] Enables the ULP-RISCV interrupt. (R/W)
\label{fielddesc:RTCCNTLRTCSARADC2INTENA}\item [RTC\_CNTL\_RTC\_SARADC2\_INT\_ENA] Enables the SAR ADC2 interrupt. (R/W)
\label{fielddesc:RTCCNTLRTCSWDINTENA}\item [RTC\_CNTL\_RTC\_SWD\_INT\_ENA] Enables the super watchdog interrupt. (R/W)
\label{fielddesc:RTCCNTLRTCXTAL32KDEADINTENA}\item [RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_ENA] Enables interrupt when the 32 kHz crystal is dead. (R/W)
\label{fielddesc:RTCCNTLRTCCOCPUTRAPINTENA}\item [RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_ENA] Enables interrupt when the ULP-RISCV is trapped. (R/W)
\label{fielddesc:RTCCNTLRTCTOUCHTIMEOUTINTENA}\item [RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_ENA] Enables interrupt when touch sensor times out. (R/W)
\label{fielddesc:RTCCNTLRTCGLITCHDETINTENA}\item [RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_ENA] Enables interrupt when a glitch is detected. (R/W)
\label{fielddesc:RTCCNTLRTCTOUCHAPPROACHLOOPDONEINTENA}\item [RTC\_CNTL\_RTC\_TOUCH\_APPROACH\_LOOP\_DONE\_INT\_ENA] Enables interrupt upon the completion of a touch approach loop. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_RAW\_RTC\_REG}{0x{}0044}\label{regdesc:RTCCNTLINTRAWRTCREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_APPROACH\_LOOP\_DONE\_INT\_RAW}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_RAW}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_RAW}{1}{18}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_RAW}{1}{17}{{0}}%
\regfield{RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_RAW}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SWD\_INT\_RAW}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC2\_INT\_RAW}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_INT\_RAW}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TSENS\_INT\_RAW}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC1\_INT\_RAW}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_RAW}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_RAW}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_RAW}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_RAW}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_RAW}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_RTC\_ULP\_CP\_INT\_RAW}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_RAW}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_RTC\_WDT\_INT\_RAW}{1}{3}{{0}}%
\regfield{RTC\_CNTL\_SDIO\_IDLE\_INT\_RAW}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_RAW}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTRAW}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_RAW] Stores the raw interrupt triggered when the chip wakes up from sleep. (RO)
\label{fielddesc:RTCCNTLSLPREJECTINTRAW}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_RAW] Stores the raw interrupt triggered when the chip rejects to go to sleep. (RO)
\label{fielddesc:RTCCNTLSDIOIDLEINTRAW}\item [RTC\_CNTL\_SDIO\_IDLE\_INT\_RAW] Stores the raw interrupt triggered when the SDIO idles. (RO)
\label{fielddesc:RTCCNTLRTCWDTINTRAW}\item [RTC\_CNTL\_RTC\_WDT\_INT\_RAW] Stores the raw RTC watchdog interrupt. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHSCANDONEINTRAW}\item [RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_RAW] Stores the raw interrupt triggered upon the completion of a touch scanning. (RO)
\label{fielddesc:RTCCNTLRTCULPCPINTRAW}\item [RTC\_CNTL\_RTC\_ULP\_CP\_INT\_RAW] Stores the raw ULP co-processor interrupt. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHDONEINTRAW}\item [RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_RAW] Stores the raw interrupt triggered upon the completion of a single touch. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHACTIVEINTRAW}\item [RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_RAW] Stores the raw interrupt triggered when a touch is detected. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHINACTIVEINTRAW}\item [RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_RAW] Stores the raw interrupt triggered when a touch is released. (RO)
\label{fielddesc:RTCCNTLRTCBROWNOUTINTRAW}\item [RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_RAW] Stores the raw brown out interrupt. (RO)



\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_INT\_RAW\_RTC\_REG}{0x{}0044}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]


\label{fielddesc:RTCCNTLRTCMAINTIMERINTRAW}\item [RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_RAW] Stores the raw RTC main timer interrupt. (RO)
\label{fielddesc:RTCCNTLRTCSARADC1INTRAW}\item [RTC\_CNTL\_RTC\_SARADC1\_INT\_RAW] Stores the raw SAR ADC1 interrupt. (RO)
\label{fielddesc:RTCCNTLRTCTSENSINTRAW}\item [RTC\_CNTL\_RTC\_TSENS\_INT\_RAW] Stores the raw temperature sensor interrupt. (RO)
\label{fielddesc:RTCCNTLRTCCOCPUINTRAW}\item [RTC\_CNTL\_RTC\_COCPU\_INT\_RAW] Stores the raw ULP-RISCV interrupt. (RO)
\label{fielddesc:RTCCNTLRTCSARADC2INTRAW}\item [RTC\_CNTL\_RTC\_SARADC2\_INT\_RAW] Stores the raw SAR ADC2 interrupt. (RO)
\label{fielddesc:RTCCNTLRTCSWDINTRAW}\item [RTC\_CNTL\_RTC\_SWD\_INT\_RAW] Stores the raw super watchdog interrupt. (RO)
\label{fielddesc:RTCCNTLRTCXTAL32KDEADINTRAW}\item [RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_RAW] Stores the raw interrupt triggered when the 32 kHz crystal is dead. (RO)
\label{fielddesc:RTCCNTLRTCCOCPUTRAPINTRAW}\item [RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_RAW] Stores the raw interrupt triggered when the ULP-RISCV is trapped. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHTIMEOUTINTRAW}\item [RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_RAW] Stores the raw interrupt triggered when touch sensor times out. (RO)
\label{fielddesc:RTCCNTLRTCGLITCHDETINTRAW}\item [RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_RAW] Stores the raw interrupt triggered when a glitch is detected. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHAPPROACHLOOPDONEINTRAW}\item [RTC\_CNTL\_RTC\_TOUCH\_APPROACH\_LOOP\_DONE\_INT\_RAW] Stores the raw interrupt triggered upon the completion of a touch approach loop. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_ST\_RTC\_REG}{0x{}0048}\label{regdesc:RTCCNTLINTSTRTCREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_APPROACH\_LOOP\_DONE\_INT\_ST}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_ST}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_ST}{1}{18}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_ST}{1}{17}{{0}}%
\regfield{RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_ST}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SWD\_INT\_ST}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC2\_INT\_ST}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_INT\_ST}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TSENS\_INT\_ST}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC1\_INT\_ST}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_ST}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_ST}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_ST}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_ST}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_ST}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_RTC\_ULP\_CP\_INT\_ST}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_ST}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_RTC\_WDT\_INT\_ST}{1}{3}{{0}}%
\regfield{RTC\_CNTL\_SDIO\_IDLE\_INT\_ST}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_ST}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTST}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_ST] Stores the status of the interrupt triggered when the chip wakes up from sleep. (RO)
\label{fielddesc:RTCCNTLSLPREJECTINTST}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_ST] Stores the status of the interrupt triggered when the chip rejects to go to sleep. (RO)
\label{fielddesc:RTCCNTLSDIOIDLEINTST}\item [RTC\_CNTL\_SDIO\_IDLE\_INT\_ST] Stores the status of the interrupt triggered when the SDIO idles. (RO)
\label{fielddesc:RTCCNTLRTCWDTINTST}\item [RTC\_CNTL\_RTC\_WDT\_INT\_ST] Stores the status of the RTC watchdog interrupt. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHSCANDONEINTST}\item [RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_ST] Stores the status of the interrupt triggered upon the completion of a touch scanning. (RO)
\label{fielddesc:RTCCNTLRTCULPCPINTST}\item [RTC\_CNTL\_RTC\_ULP\_CP\_INT\_ST] Stores the status of the ULP co-processor interrupt. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHDONEINTST}\item [RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_ST] Stores the status of the interrupt triggered upon the completion of a single touch. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHACTIVEINTST}\item [RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_ST] Stores the status of the interrupt triggered when a touch is detected. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHINACTIVEINTST}\item [RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_ST] Stores the status of the interrupt triggered when a touch is released. (RO)
\label{fielddesc:RTCCNTLRTCBROWNOUTINTST}\item [RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_ST] Stores the status of the brown out interrupt. (RO)


\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_INT\_ST\_RTC\_REG}{0x{}0048}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]


\label{fielddesc:RTCCNTLRTCMAINTIMERINTST}\item [RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_ST] Stores the status of the RTC main timer interrupt. (RO)
\label{fielddesc:RTCCNTLRTCSARADC1INTST}\item [RTC\_CNTL\_RTC\_SARADC1\_INT\_ST] Stores the status of the SAR ADC1 interrupt. (RO)
\label{fielddesc:RTCCNTLRTCTSENSINTST}\item [RTC\_CNTL\_RTC\_TSENS\_INT\_ST] Stores the status of the temperature sensor interrupt. (RO)
\label{fielddesc:RTCCNTLRTCCOCPUINTST}\item [RTC\_CNTL\_RTC\_COCPU\_INT\_ST] Stores the status of the ULP-RISCV interrupt. (RO)
\label{fielddesc:RTCCNTLRTCSARADC2INTST}\item [RTC\_CNTL\_RTC\_SARADC2\_INT\_ST] Stores the status of the SAR ADC2 interrupt. (RO)
\label{fielddesc:RTCCNTLRTCSWDINTST}\item [RTC\_CNTL\_RTC\_SWD\_INT\_ST] Stores the status of the super watchdog interrupt. (RO)
\label{fielddesc:RTCCNTLRTCXTAL32KDEADINTST}\item [RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_ST] Stores the status of the interrupt triggered when the 32 kHz crystal is dead. (RO)
\label{fielddesc:RTCCNTLRTCCOCPUTRAPINTST}\item [RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_ST] Stores the status of the interrupt triggered when the ULP-RISCV is trapped. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHTIMEOUTINTST}\item [RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_ST] Stores the status of the interrupt triggered when touch sensor times out. (RO)
\label{fielddesc:RTCCNTLRTCGLITCHDETINTST}\item [RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_ST] Stores the status of the interrupt triggered when a glitch is detected. (RO)
\label{fielddesc:RTCCNTLRTCTOUCHAPPROACHLOOPDONEINTST}\item [RTC\_CNTL\_RTC\_TOUCH\_APPROACH\_LOOP\_DONE\_INT\_ST] Stores the status of the interrupt triggered upon the completion of a touch approach loop. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_CLR\_RTC\_REG}{0x{}004C}\label{regdesc:RTCCNTLINTCLRRTCREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_APPROACH\_LOOP\_DONE\_INT\_CLR}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_CLR}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_CLR}{1}{18}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_CLR}{1}{17}{{0}}%
\regfield{RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_CLR}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SWD\_INT\_CLR}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC2\_INT\_CLR}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_INT\_CLR}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TSENS\_INT\_CLR}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC1\_INT\_CLR}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_CLR}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_CLR}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_CLR}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_CLR}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_CLR}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_RTC\_ULP\_CP\_INT\_CLR}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_CLR}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_RTC\_WDT\_INT\_CLR}{1}{3}{{0}}%
\regfield{RTC\_CNTL\_SDIO\_IDLE\_INT\_CLR}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_CLR}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTCLR}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_CLR] Clears the interrupt triggered when the chip wakes up from sleep. (WO)
\label{fielddesc:RTCCNTLSLPREJECTINTCLR}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_CLR] Clears the interrupt triggered when the chip rejects to go to sleep. (WO)
\label{fielddesc:RTCCNTLSDIOIDLEINTCLR}\item [RTC\_CNTL\_SDIO\_IDLE\_INT\_CLR] Clears the interrupt triggered when the SDIO idles. (WO)
\label{fielddesc:RTCCNTLRTCWDTINTCLR}\item [RTC\_CNTL\_RTC\_WDT\_INT\_CLR] Clears the RTC watchdog interrupt. (WO)
\label{fielddesc:RTCCNTLRTCTOUCHSCANDONEINTCLR}\item [RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_CLR] Clears the interrupt triggered upon the completion of a touch scanning. (WO)
\label{fielddesc:RTCCNTLRTCULPCPINTCLR}\item [RTC\_CNTL\_RTC\_ULP\_CP\_INT\_CLR] Clears the ULP co-processor interrupt. (WO)
\label{fielddesc:RTCCNTLRTCTOUCHDONEINTCLR}\item [RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_CLR] Clears the interrupt triggered upon the completion of a single touch. (WO)
\label{fielddesc:RTCCNTLRTCTOUCHACTIVEINTCLR}\item [RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_CLR] Clears the interrupt triggered when a touch is detected. (WO)
\label{fielddesc:RTCCNTLRTCTOUCHINACTIVEINTCLR}\item [RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_CLR] Clears the interrupt triggered when a touch is released. (WO)
\label{fielddesc:RTCCNTLRTCBROWNOUTINTCLR}\item [RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_CLR] Clears the brown out interrupt. (WO)


\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_INT\_CLR\_RTC\_REG}{0x{}004C}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]



\label{fielddesc:RTCCNTLRTCMAINTIMERINTCLR}\item [RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_CLR] Clears the RTC main timer interrupt. (WO)
\label{fielddesc:RTCCNTLRTCSARADC1INTCLR}\item [RTC\_CNTL\_RTC\_SARADC1\_INT\_CLR] Clears the SAR ADC1 interrupt. (WO)
\label{fielddesc:RTCCNTLRTCTSENSINTCLR}\item [RTC\_CNTL\_RTC\_TSENS\_INT\_CLR] Clears the temperature sensor interrupt. (WO)
\label{fielddesc:RTCCNTLRTCCOCPUINTCLR}\item [RTC\_CNTL\_RTC\_COCPU\_INT\_CLR] Clears the ULP-RISCV interrupt. (WO)
\label{fielddesc:RTCCNTLRTCSARADC2INTCLR}\item [RTC\_CNTL\_RTC\_SARADC2\_INT\_CLR] Clears the SAR ADC2 interrupt. (WO)
\label{fielddesc:RTCCNTLRTCSWDINTCLR}\item [RTC\_CNTL\_RTC\_SWD\_INT\_CLR] Clears the super watchdog interrupt. (WO)
\label{fielddesc:RTCCNTLRTCXTAL32KDEADINTCLR}\item [RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_CLR] Clears the interrupt triggered when the 32 kHz crystal is dead. (WO)
\label{fielddesc:RTCCNTLRTCCOCPUTRAPINTCLR}\item [RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_CLR] Clears the interrupt triggered when the ULP-RISCV is trapped. (WO)
\label{fielddesc:RTCCNTLRTCTOUCHTIMEOUTINTCLR}\item [RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_CLR] Clears the interrupt triggered when touch sensor times out. (WO)
\label{fielddesc:RTCCNTLRTCGLITCHDETINTCLR}\item [RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_CLR] Clears the interrupt triggered when a glitch is detected. (WO)
\label{fielddesc:RTCCNTLRTCTOUCHAPPROACHLOOPDONEINTCLR}\item [RTC\_CNTL\_RTC\_TOUCH\_APPROACH\_LOOP\_DONE\_INT\_CLR] Clears the interrupt triggered upon the completion of a touch approach loop. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_STORE0\_REG}{0x{}0050}\label{regdesc:RTCCNTLRTCSTORE0REG}
\regfield{RTC\_CNTL\_RTC\_SCRATCH0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSCRATCH0}\item [RTC\_CNTL\_RTC\_SCRATCH0] Retention register (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_STORE1\_REG}{0x{}0054}\label{regdesc:RTCCNTLRTCSTORE1REG}
\regfield{RTC\_CNTL\_RTC\_SCRATCH1}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSCRATCH1}\item [RTC\_CNTL\_RTC\_SCRATCH1] Retention register (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_STORE2\_REG}{0x{}0058}\label{regdesc:RTCCNTLRTCSTORE2REG}
\regfield{RTC\_CNTL\_RTC\_SCRATCH2}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSCRATCH2}\item [RTC\_CNTL\_RTC\_SCRATCH2] Retention register (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_STORE3\_REG}{0x{}005C}\label{regdesc:RTCCNTLRTCSTORE3REG}
\regfield{RTC\_CNTL\_RTC\_SCRATCH3}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSCRATCH3}\item [RTC\_CNTL\_RTC\_SCRATCH3] Retention register (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_EXT\_XTL\_CONF\_REG}{0x{}0060}\label{regdesc:RTCCNTLRTCEXTXTLCONFREG}
\regfield{RTC\_CNTL\_XTL\_EXT\_CTR\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_XTL\_EXT\_CTR\_LV}{1}{30}{{0}}%
\regfield{(reserved)}{6}{24}{000000}%
\regfield{RTC\_CNTL\_RTC\_XTAL32K\_GPIO\_SEL}{1}{23}{{0}}%
\regfield{RTC\_CNTL\_RTC\_WDT\_STATE}{3}{20}{{0x{}0}}%
\regfield{RTC\_CNTL\_DAC\_XTAL\_32K}{3}{17}{{3}}%
\regfield{RTC\_CNTL\_XPD\_XTAL\_32K}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_DRES\_XTAL\_32K}{3}{13}{{3}}%
\regfield{RTC\_CNTL\_DGM\_XTAL\_32K}{3}{10}{{3}}%
\regfield{RTC\_CNTL\_DBUF\_XTAL\_32K}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_ENCKINIT\_XTAL\_32K}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_XPD\_FORCE}{1}{7}{{1}}%
\regfield{RTC\_CNTL\_XTAL32K\_AUTO\_RETURN}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_AUTO\_RESTART}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_AUTO\_BACKUP}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_EXT\_CLK\_FO}{1}{3}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_WDT\_RESET}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_WDT\_CLK\_FO}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_WDT\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLXTAL32KWDTEN}\item [RTC\_CNTL\_XTAL32K\_WDT\_EN] Set this bit to enable the 32 kHz crystal watchdog. (R/W)
\label{fielddesc:RTCCNTLXTAL32KWDTCLKFO}\item [RTC\_CNTL\_XTAL32K\_WDT\_CLK\_FO] Set this bit to FPU the 32 kHz crystal watchdog clock. (R/W)
\label{fielddesc:RTCCNTLXTAL32KWDTRESET}\item [RTC\_CNTL\_XTAL32K\_WDT\_RESET] Set this bit to reset the 32 kHz crystal watchdog by SW. (R/W)
\label{fielddesc:RTCCNTLXTAL32KEXTCLKFO}\item [RTC\_CNTL\_XTAL32K\_EXT\_CLK\_FO] Set this bit to FPU the external clock of 32 kHz crystal. (R/W)
\label{fielddesc:RTCCNTLXTAL32KAUTOBACKUP}\item [RTC\_CNTL\_XTAL32K\_AUTO\_BACKUP] Set this bit to switch to the backup clock when the 32 kHz crystal is dead. (R/W)
\label{fielddesc:RTCCNTLXTAL32KAUTORESTART}\item [RTC\_CNTL\_XTAL32K\_AUTO\_RESTART] Set this bit to restart the 32 kHz crystal automatically when the 32 kHz crystal is dead. (R/W)
\label{fielddesc:RTCCNTLXTAL32KAUTORETURN}\item [RTC\_CNTL\_XTAL32K\_AUTO\_RETURN] Set this bit to switch back to 32 kHz crystal when the 32 kHz crystal is restarted. (R/W)
\label{fielddesc:RTCCNTLXTAL32KXPDFORCE}\item [RTC\_CNTL\_XTAL32K\_XPD\_FORCE] Set 1 to allow the software to FPD the 32 kHz crystal.  Set 0 to allow the FSM to FPD the 32 kHz crystal. (R/W) (R/W)
\label{fielddesc:RTCCNTLENCKINITXTAL32K}\item [RTC\_CNTL\_ENCKINIT\_XTAL\_32K] Applies an internal clock to help the 32 kHz crystal to start. (R/W)
\label{fielddesc:RTCCNTLDBUFXTAL32K}\item [RTC\_CNTL\_DBUF\_XTAL\_32K] 0: single-end buffer 1: differential buffer (R/W)
\label{fielddesc:RTCCNTLDGMXTAL32K}\item [RTC\_CNTL\_DGM\_XTAL\_32K] xtal\_32k gm control (R/W)


\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_RTC\_EXT\_XTL\_CONF\_REG}{0x{}0060}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]


\label{fielddesc:RTCCNTLDRESXTAL32K}\item [RTC\_CNTL\_DRES\_XTAL\_32K] DRES\_XTAL\_32K (R/W)
\label{fielddesc:RTCCNTLXPDXTAL32K}\item [RTC\_CNTL\_XPD\_XTAL\_32K] XPD\_XTAL\_32K (R/W)
\label{fielddesc:RTCCNTLDACXTAL32K}\item [RTC\_CNTL\_DAC\_XTAL\_32K] DAC\_XTAL\_32K (R/W)
\label{fielddesc:RTCCNTLRTCWDTSTATE}\item [RTC\_CNTL\_RTC\_WDT\_STATE] Stores the status of the 32 kHz watchdog. (RO)
\label{fielddesc:RTCCNTLRTCXTAL32KGPIOSEL}\item [RTC\_CNTL\_RTC\_XTAL32K\_GPIO\_SEL] Selects the 32 kHz crystal clock. 0: selects the external 32 kHz clock.  1: selects clock from the RTC GPIO X32P\_C. (R/W)
\label{fielddesc:RTCCNTLXTLEXTCTRLV}\item [RTC\_CNTL\_XTL\_EXT\_CTR\_LV] 0: powers down XTAL at high level  1: powers down XTAL at low level (R/W)
\label{fielddesc:RTCCNTLXTLEXTCTREN}\item [RTC\_CNTL\_XTL\_EXT\_CTR\_EN] Enables the GPIO to power down the crystal oscillator. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_EXT\_WAKEUP\_CONF\_REG}{0x{}0064}\label{regdesc:RTCCNTLRTCEXTWAKEUPCONFREG}
\regfield{RTC\_CNTL\_EXT\_WAKEUP1\_LV}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_EXT\_WAKEUP0\_LV}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_WAKEUP\_FILTER}{1}{29}{{0}}%
\regfield{(reserved)}{29}{0}{00000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLGPIOWAKEUPFILTER}\item [RTC\_CNTL\_GPIO\_WAKEUP\_FILTER] Set this bit to enable the GPIO wakeup event filter. (R/W)
\label{fielddesc:RTCCNTLEXTWAKEUP0LV}\item [RTC\_CNTL\_EXT\_WAKEUP0\_LV] 0: external wakeup 0 at low level     1: external wakeup 0 at high level (R/W)
\label{fielddesc:RTCCNTLEXTWAKEUP1LV}\item [RTC\_CNTL\_EXT\_WAKEUP1\_LV] 0: external wakeup 1 at low level     1: external wakeup 1 at high level (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_SLP\_REJECT\_CONF\_REG}{0x{}0068}\label{regdesc:RTCCNTLRTCSLPREJECTCONFREG}
\regfield{RTC\_CNTL\_DEEP\_SLP\_REJECT\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_LIGHT\_SLP\_REJECT\_EN}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SLEEP\_REJECT\_ENA}{18}{12}{{0}}%
\regfield{(reserved)}{12}{0}{000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSLEEPREJECTENA}\item [RTC\_CNTL\_RTC\_SLEEP\_REJECT\_ENA] Set this bit to enable reject-to-sleep. (R/W)
\label{fielddesc:RTCCNTLLIGHTSLPREJECTEN}\item [RTC\_CNTL\_LIGHT\_SLP\_REJECT\_EN] Set this bit to enable reject-to-light-sleep. (R/W)
\label{fielddesc:RTCCNTLDEEPSLPREJECTEN}\item [RTC\_CNTL\_DEEP\_SLP\_REJECT\_EN] Set this bit to enable reject-to-deep-sleep. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_CLK\_CONF\_REG}{0x{}0074}\label{regdesc:RTCCNTLRTCCLKCONFREG}
\regfield{RTC\_CNTL\_ANA\_CLK\_RTC\_SEL}{2}{30}{{0}}%
\regfield{RTC\_CNTL\_FAST\_CLK\_RTC\_SEL}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_XTAL\_GLOBAL\_FORCE\_NOGATING}{1}{28}{{1}}%
\regfield{RTC\_CNTL\_XTAL\_GLOBAL\_FORCE\_GATING}{1}{27}{{0}}%
\regfield{RTC\_CNTL\_CK8M\_FORCE\_PU}{1}{26}{{0}}%
\regfield{RTC\_CNTL\_CK8M\_FORCE\_PD}{1}{25}{{0}}%
\regfield{RTC\_CNTL\_CK8M\_DFREQ}{8}{17}{{172}}%
\regfield{RTC\_CNTL\_CK8M\_FORCE\_NOGATING}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_XTAL\_FORCE\_NOGATING}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_CK8M\_DIV\_SEL}{3}{12}{{3}}%
\regfield{(reserved)}{1}{11}{0}%
\regfield{RTC\_CNTL\_DIG\_CLK8M\_EN}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_DIG\_CLK8M\_D256\_EN}{1}{9}{{1}}%
\regfield{RTC\_CNTL\_DIG\_XTAL32K\_EN}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_ENB\_CK8M\_DIV}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_ENB\_CK8M}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_CK8M\_DIV}{2}{4}{{1}}%
\regfield{RTC\_CNTL\_CK8M\_DIV\_SEL\_VLD}{1}{3}{{1}}%
\regfield{RTC\_CNTL\_EFUSE\_CLK\_FORCE\_NOGATING}{1}{2}{{1}}%
\regfield{RTC\_CNTL\_EFUSE\_CLK\_FORCE\_GATING}{1}{1}{{0}}%
\regfield{(reserved)}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLEFUSECLKFORCEGATING}\item [RTC\_CNTL\_EFUSE\_CLK\_FORCE\_GATING] Set this bit to force eFuse gating. (R/W)
\label{fielddesc:RTCCNTLEFUSECLKFORCENOGATING}\item [RTC\_CNTL\_EFUSE\_CLK\_FORCE\_NOGATING] Set this bit to force no eFuse gating. (R/W)
\label{fielddesc:RTCCNTLCK8MDIVSELVLD}\item [RTC\_CNTL\_CK8M\_DIV\_SEL\_VLD] Synchronizes the reg\_ck8m\_div\_sel. Not that you have to invalidate the bus before switching clock, and validate the new clock. (R/W)
\label{fielddesc:RTCCNTLCK8MDIV}\item [RTC\_CNTL\_CK8M\_DIV] Set the CK8M\_D256\_OUT divider. 00: divided by 128   01: divided by 256   10: divided by 512  11: divided by 1024. (R/W)
\label{fielddesc:RTCCNTLENBCK8M}\item [RTC\_CNTL\_ENB\_CK8M] Set this bit to disable CK8M and CK8M\_D256\_OUT. (R/W)
\label{fielddesc:RTCCNTLENBCK8MDIV}\item [RTC\_CNTL\_ENB\_CK8M\_DIV] Selects the CK8M\_D256\_OUT. 1: CK8M 0: CK8M divided by 256. (R/W)
\label{fielddesc:RTCCNTLDIGXTAL32KEN}\item [RTC\_CNTL\_DIG\_XTAL32K\_EN] Set this bit to enable CK\_XTAL\_32K clock for the digital core. (R/W)
\label{fielddesc:RTCCNTLDIGCLK8MD256EN}\item [RTC\_CNTL\_DIG\_CLK8M\_D256\_EN] Set this bit to enable CK8M\_D256\_OUT clock for the digital core. (R/W)
\label{fielddesc:RTCCNTLDIGCLK8MEN}\item [RTC\_CNTL\_DIG\_CLK8M\_EN] Set this bit to enable 8 MHz clock for the digital core. (R/W)
\label{fielddesc:RTCCNTLCK8MDIVSEL}\item [RTC\_CNTL\_CK8M\_DIV\_SEL] Stores the 8 MHz divider, which is reg\_ck8m\_div\_sel + 1 (R/W)
\label{fielddesc:RTCCNTLXTALFORCENOGATING}\item [RTC\_CNTL\_XTAL\_FORCE\_NOGATING] Set this bit to force no gating to crystal during sleep (R/W)
\label{fielddesc:RTCCNTLCK8MFORCENOGATING}\item [RTC\_CNTL\_CK8M\_FORCE\_NOGATING] Set this bit to disable force gating to 8 MHz crystal during sleep. (R/W)


\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_RTC\_CLK\_CONF\_REG}{0x{}0074}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]


\label{fielddesc:RTCCNTLCK8MDFREQ}\item [RTC\_CNTL\_CK8M\_DFREQ] CK8M\_DFREQ (R/W)
\label{fielddesc:RTCCNTLCK8MFORCEPD}\item [RTC\_CNTL\_CK8M\_FORCE\_PD] Set this bit to FPD the RC\_FAST\_CLK clock. (R/W)
\label{fielddesc:RTCCNTLCK8MFORCEPU}\item [RTC\_CNTL\_CK8M\_FORCE\_PU] Set this bit to FPU the RC\_FAST\_CLK clock. (R/W)
\label{fielddesc:RTCCNTLXTALGLOBALFORCEGATING}\item [RTC\_CNTL\_XTAL\_GLOBAL\_FORCE\_GATING] Set this bit to force gating xtal. (R/W)
\label{fielddesc:RTCCNTLXTALGLOBALFORCENOGATING}\item [RTC\_CNTL\_XTAL\_GLOBAL\_FORCE\_NOGATING]  Set this bit to force no gating xtal. (R/W)
\label{fielddesc:RTCCNTLFASTCLKRTCSEL}\item [RTC\_CNTL\_FAST\_CLK\_RTC\_SEL] Set this bit to select the RTC fast clock. 0: XTAL\_DIV\_CLK, 1: RC\_FAST\_CLK div n. (R/W)
\label{fielddesc:RTCCNTLANACLKRTCSEL}\item [RTC\_CNTL\_ANA\_CLK\_RTC\_SEL] Set this bit to select the RTC slow clock. 0: RC\_SLOW\_CLK  1: XTAL32K\_CLK 2: RC\_FAST\_DIV\_CLK. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_SLOW\_CLK\_CONF\_REG}{0x{}0078}\label{regdesc:RTCCNTLRTCSLOWCLKCONFREG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{RTC\_CNTL\_RTC\_ANA\_CLK\_DIV}{8}{23}{{0}}%
\regfield{RTC\_CNTL\_RTC\_ANA\_CLK\_DIV\_VLD}{1}{22}{{1}}%
\regfield{(reserved)}{22}{0}{0000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCANACLKDIVVLD}\item [RTC\_CNTL\_RTC\_ANA\_CLK\_DIV\_VLD] Synchronizes the reg\_rtc\_ana\_clk\_div bus. Note that you have to invalidate the bus before switching clock, and validate the new clock. (R/W)
\label{fielddesc:RTCCNTLRTCANACLKDIV}\item [RTC\_CNTL\_RTC\_ANA\_CLK\_DIV] Set the RC\_SLOW\_CLK divider. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_RTC\_SDIO\_CONF\_REG}{0x{}007C}\label{regdesc:RTCCNTLRTCSDIOCONFREG}
\regfield{RTC\_CNTL\_XPD\_SDIO\_REG}{1}{31}{{0}}%
\regfield{(reserved)}{7}{24}{0000000}%
\regfield{RTC\_CNTL\_SDIO\_TIEH}{1}{23}{{1}}%
\regfield{RTC\_CNTL\_SDIO\_FORCE}{1}{22}{{0}}%
\regfield{RTC\_CNTL\_SDIO\_REG\_PD\_EN}{1}{21}{{1}}%
\regfield{(reserved)}{21}{0}{000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSDIOREGPDEN}\item [RTC\_CNTL\_SDIO\_REG\_PD\_EN] Set this bit to power down SDIO\_REG when chip is in light sleep and deep sleep. This field is only valid when \hyperref[fielddesc:RTCCNTLSDIOFORCE]{RTC\_CNTL\_SDIO\_FORCE} = 0.  (R/W)
\label{fielddesc:RTCCNTLSDIOFORCE}\item [RTC\_CNTL\_SDIO\_FORCE] Set this bit to allow software t1: use SW option to control SDIO\_REG. Clear this bit to allow the state machine to control SDIO\_REG. (R/W)
\label{fielddesc:RTCCNTLSDIOTIEH}\item [RTC\_CNTL\_SDIO\_TIEH] Configure the SDIO\_TIEH via software. This field is only valid when \hyperref[fielddesc:RTCCNTLSDIOFORCE]{RTC\_CNTL\_SDIO\_FORCE} = 1. (R/W)
\label{fielddesc:RTCCNTLXPDSDIOREG}\item [RTC\_CNTL\_XPD\_SDIO\_REG] Set this bit to power on flash regulator. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_REG}{0x{}0084}\label{regdesc:RTCCNTLRTCREG}
\regfield{RTC\_CNTL\_RTC\_REGULATOR\_FORCE\_PU}{1}{31}{{1}}%
\regfield{RTC\_CNTL\_RTC\_REGULATOR\_FORCE\_PD}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_RTC\_DBOOST\_FORCE\_PU}{1}{29}{{1}}%
\regfield{RTC\_CNTL\_RTC\_DBOOST\_FORCE\_PD}{1}{28}{{0}}%
\regfield{(reserved)}{6}{22}{000000}%
\regfield{RTC\_CNTL\_SCK\_DCAP}{8}{14}{{0}}%
\regfield{(reserved)}{6}{8}{000000}%
\regfield{RTC\_CNTL\_DIG\_REG\_CAL\_EN}{1}{7}{{0}}%
\regfield{(reserved)}{7}{0}{0000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLDIGREGCALEN}\item [RTC\_CNTL\_DIG\_REG\_CAL\_EN] Set this bit to enable calibration for the digital regulator. (R/W)
\label{fielddesc:RTCCNTLSCKDCAP}\item [RTC\_CNTL\_SCK\_DCAP] Configures the frequency of the RTC clocks. (R/W)
\label{fielddesc:RTCCNTLRTCDBOOSTFORCEPD}\item [RTC\_CNTL\_RTC\_DBOOST\_FORCE\_PD] Set this bit to FPD the RTC\_DBOOST (R/W)
\label{fielddesc:RTCCNTLRTCDBOOSTFORCEPU}\item [RTC\_CNTL\_RTC\_DBOOST\_FORCE\_PU] Set this bit to FPU the RTC\_DBOOST (R/W)
\label{fielddesc:RTCCNTLRTCREGULATORFORCEPD}\item [RTC\_CNTL\_RTC\_REGULATOR\_FORCE\_PD] Set this bit to FPD the RTC\_REG, which means decreasing its voltage to 0.8 V or lower. (R/W)
\label{fielddesc:RTCCNTLRTCREGULATORFORCEPU}\item [RTC\_CNTL\_RTC\_REGULATOR\_FORCE\_PU] Set this bit to FPU the RTC\_REG. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_PWC\_REG}{0x{}0088}\label{regdesc:RTCCNTLRTCPWCREG}
\regfield{(reserved)}{10}{22}{0000000000}%
\regfield{RTC\_CNTL\_RTC\_PAD\_FORCE\_HOLD}{1}{21}{{0}}%
\regfield{RTC\_CNTL\_RTC\_PD\_EN}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_RTC\_FORCE\_PU}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_RTC\_FORCE\_PD}{1}{18}{{0}}%
\regfield{(reserved)}{6}{12}{000000}%
\regfield{RTC\_CNTL\_RTC\_SLOWMEM\_FORCE\_LPU}{1}{11}{{1}}%
\regfield{RTC\_CNTL\_RTC\_SLOWMEM\_FORCE\_LPD}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SLOWMEM\_FOLW\_CPU}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_RTC\_FASTMEM\_FORCE\_LPU}{1}{8}{{1}}%
\regfield{RTC\_CNTL\_RTC\_FASTMEM\_FORCE\_LPD}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_RTC\_FASTMEM\_FOLW\_CPU}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_RTC\_FORCE\_NOISO}{1}{5}{{1}}%
\regfield{RTC\_CNTL\_RTC\_FORCE\_ISO}{1}{4}{{0}}%
\regfield{(reserved)}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{{1}}%
\regfield{(reserved)}{1}{1}{{0}}%
\regfield{(reserved)}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCFORCEISO}\item [RTC\_CNTL\_RTC\_FORCE\_ISO] Set this bit to force isolate the RTC peripherals. (R/W)
\label{fielddesc:RTCCNTLRTCFORCENOISO}\item [RTC\_CNTL\_RTC\_FORCE\_NOISO] Set this bit to disable the force isolation to the RTC peripherals. (R/W)
\label{fielddesc:RTCCNTLRTCFASTMEMFOLWCPU}\item [RTC\_CNTL\_RTC\_FASTMEM\_FOLW\_CPU] Set 1 to FPD the RTC slow memory when the CPU is powered down.  Set 0 to FPD the RTC slow memory when the RTC main state machine is powered down. (R/W)
\label{fielddesc:RTCCNTLRTCFASTMEMFORCELPD}\item [RTC\_CNTL\_RTC\_FASTMEM\_FORCE\_LPD] Set this bit to force not retain the RTC fast memory. (R/W)
\label{fielddesc:RTCCNTLRTCFASTMEMFORCELPU}\item [RTC\_CNTL\_RTC\_FASTMEM\_FORCE\_LPU] Set this bit to force retain the RTC fast memory. (R/W)
\label{fielddesc:RTCCNTLRTCSLOWMEMFOLWCPU}\item [RTC\_CNTL\_RTC\_SLOWMEM\_FOLW\_CPU] 1: RTC memory  PD following CPU, 0: RTC memory PD following RTC state machine (R/W)
\label{fielddesc:RTCCNTLRTCSLOWMEMFORCELPD}\item [RTC\_CNTL\_RTC\_SLOWMEM\_FORCE\_LPD] Set this bit to force not retain the RTC slow memory. (R/W)
\label{fielddesc:RTCCNTLRTCSLOWMEMFORCELPU}\item [RTC\_CNTL\_RTC\_SLOWMEM\_FORCE\_LPU] Set this bit to force retain the RTC slow memory. (R/W)
\label{fielddesc:RTCCNTLRTCFORCEPD}\item [RTC\_CNTL\_RTC\_FORCE\_PD] Set this bit to FPD the RTC peripherals. (R/W)
\label{fielddesc:RTCCNTLRTCFORCEPU}\item [RTC\_CNTL\_RTC\_FORCE\_PU] Set this bit to FPU the RTC peripherals. (R/W)
\label{fielddesc:RTCCNTLRTCPDEN}\item [RTC\_CNTL\_RTC\_PD\_EN] Set this bit to enable PD for the RTC peripherals in sleep. (R/W)
\label{fielddesc:RTCCNTLRTCPADFORCEHOLD}\item [RTC\_CNTL\_RTC\_PAD\_FORCE\_HOLD] Set this bit the force hold the RTC GPIOs. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_DIG\_PWC\_REG}{0x{}0090}\label{regdesc:RTCCNTLDIGPWCREG}
\regfield{RTC\_CNTL\_DG\_WRAP\_PD\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_WIFI\_PD\_EN}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_CPU\_TOP\_PD\_EN}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_DG\_PERI\_PD\_EN}{1}{28}{{0}}%
\regfield{(reserved)}{5}{23}{00000}%
\regfield{RTC\_CNTL\_CPU\_TOP\_FORCE\_PU}{1}{22}{{1}}%
\regfield{RTC\_CNTL\_CPU\_TOP\_FORCE\_PD}{1}{21}{{0}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_PU}{1}{20}{{1}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_PD}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_WIFI\_FORCE\_PU}{1}{18}{{1}}%
\regfield{RTC\_CNTL\_WIFI\_FORCE\_PD}{1}{17}{{0}}%
\regfield{(reserved)}{2}{15}{00}%
\regfield{RTC\_CNTL\_DG\_PERI\_FORCE\_PU}{1}{14}{{1}}%
\regfield{RTC\_CNTL\_DG\_PERI\_FORCE\_PD}{1}{13}{{0}}%
\regfield{(reserved)}{8}{5}{00000000}%
\regfield{RTC\_CNTL\_LSLP\_MEM\_FORCE\_PU}{1}{4}{{1}}%
\regfield{RTC\_CNTL\_LSLP\_MEM\_FORCE\_PD}{1}{3}{{0}}%
\regfield{(reserved)}{3}{0}{000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLLSLPMEMFORCEPD}\item [RTC\_CNTL\_LSLP\_MEM\_FORCE\_PD] Set this bit to FPD the memories in the digital system in sleep. (R/W)
\label{fielddesc:RTCCNTLLSLPMEMFORCEPU}\item [RTC\_CNTL\_LSLP\_MEM\_FORCE\_PU] Set this bit to FPU the memories in the digital system. (R/W)
\label{fielddesc:RTCCNTLDGPERIFORCEPD}\item [RTC\_CNTL\_DG\_PERI\_FORCE\_PD] Set this bit to FPD PD periphrals. (R/W)
\label{fielddesc:RTCCNTLDGPERIFORCEPU}\item [RTC\_CNTL\_DG\_PERI\_FORCE\_PU] Set this bit to FPU PD periphrals. (R/W)
\label{fielddesc:RTCCNTLWIFIFORCEPD}\item [RTC\_CNTL\_WIFI\_FORCE\_PD] Set this bit to FPD Wi-Fi. (R/W)
\label{fielddesc:RTCCNTLWIFIFORCEPU}\item [RTC\_CNTL\_WIFI\_FORCE\_PU] Set this bit to FPU Wi-Fi. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCEPD}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_PD] Set this bit to FPD the digital core. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCEPU}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_PU] Set this bit to FPU the digital core. (R/W)
\label{fielddesc:RTCCNTLCPUTOPFORCEPD}\item [RTC\_CNTL\_CPU\_TOP\_FORCE\_PD] Set this bit to FPD the CPU. (R/W)
\label{fielddesc:RTCCNTLCPUTOPFORCEPU}\item [RTC\_CNTL\_CPU\_TOP\_FORCE\_PU] Set this bit to FPU the CPU. (R/W)
\label{fielddesc:RTCCNTLDGPERIPDEN}\item [RTC\_CNTL\_DG\_PERI\_PD\_EN] Set this bit to enable PD for the PD peripherals in sleep. (R/W)
\label{fielddesc:RTCCNTLCPUTOPPDEN}\item [RTC\_CNTL\_CPU\_TOP\_PD\_EN] Set this bit to enable PD for the CPU in sleep. (R/W)
\label{fielddesc:RTCCNTLWIFIPDEN}\item [RTC\_CNTL\_WIFI\_PD\_EN] Set this bit to enable PD for the Wi-Fi circuit in sleep. (R/W)
\label{fielddesc:RTCCNTLDGWRAPPDEN}\item [RTC\_CNTL\_DG\_WRAP\_PD\_EN] Set this bit to enable PD for the digital system in sleep. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_DIG\_ISO\_REG}{0x{}0094}\label{regdesc:RTCCNTLDIGISOREG}
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_NOISO}{1}{31}{{1}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_ISO}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_WIFI\_FORCE\_NOISO}{1}{29}{{1}}%
\regfield{RTC\_CNTL\_WIFI\_FORCE\_ISO}{1}{28}{{0}}%
\regfield{RTC\_CNTL\_CPU\_TOP\_FORCE\_NOISO}{1}{27}{{1}}%
\regfield{RTC\_CNTL\_CPU\_TOP\_FORCE\_ISO}{1}{26}{{0}}%
\regfield{RTC\_CNTL\_DG\_PERI\_FORCE\_NOISO}{1}{25}{{1}}%
\regfield{RTC\_CNTL\_DG\_PERI\_FORCE\_ISO}{1}{24}{{0}}%
\regfield{(reserved)}{8}{16}{00000000}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_HOLD}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_UNHOLD}{1}{14}{{1}}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_ISO}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_NOISO}{1}{12}{{1}}%
\regfield{RTC\_CNTL\_DG\_PAD\_AUTOHOLD\_EN}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_CLR\_DG\_PAD\_AUTOHOLD}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_DG\_PAD\_AUTOHOLD}{1}{9}{{0}}%
\regfield{(reserved)}{9}{0}{000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLDGPADAUTOHOLD}\item [RTC\_CNTL\_DG\_PAD\_AUTOHOLD] Indicates the auto-hold status of the digital GPIOs. (RO)
\label{fielddesc:RTCCNTLCLRDGPADAUTOHOLD}\item [RTC\_CNTL\_CLR\_DG\_PAD\_AUTOHOLD] Ste this bit to clear the auto-hold enabler for the digital GPIOs. (WO)
\label{fielddesc:RTCCNTLDGPADAUTOHOLDEN}\item [RTC\_CNTL\_DG\_PAD\_AUTOHOLD\_EN] Set this bit to allow the digital GPIOs to enter the autohold status. (R/W)
\label{fielddesc:RTCCNTLDGPADFORCENOISO}\item [RTC\_CNTL\_DG\_PAD\_FORCE\_NOISO] Set this bit to disable the force isolation to the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLDGPADFORCEISO}\item [RTC\_CNTL\_DG\_PAD\_FORCE\_ISO] Set this bit to force isolate the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLDGPADFORCEUNHOLD}\item [RTC\_CNTL\_DG\_PAD\_FORCE\_UNHOLD] Set this bit the force unhold the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLDGPADFORCEHOLD}\item [RTC\_CNTL\_DG\_PAD\_FORCE\_HOLD] Set this bit the force hold the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLDGPERIFORCEISO}\item [RTC\_CNTL\_DG\_PERI\_FORCE\_ISO] Set this bit to force isolate the digital peripherals. (R/W)
\label{fielddesc:RTCCNTLDGPERIFORCENOISO}\item [RTC\_CNTL\_DG\_PERI\_FORCE\_NOISO] Set this bit to disable the force isolation to the digital peripherals. (R/W)
\label{fielddesc:RTCCNTLCPUTOPFORCEISO}\item [RTC\_CNTL\_CPU\_TOP\_FORCE\_ISO] Set this bit to force isolate the CPU. (R/W)
\label{fielddesc:RTCCNTLCPUTOPFORCENOISO}\item [RTC\_CNTL\_CPU\_TOP\_FORCE\_NOISO] Set this bit to disable the force isolation to the CPU. (R/W)
\label{fielddesc:RTCCNTLWIFIFORCEISO}\item [RTC\_CNTL\_WIFI\_FORCE\_ISO] Set this bit to force isolate the Wi-Fi circuits. (R/W)
\label{fielddesc:RTCCNTLWIFIFORCENOISO}\item [RTC\_CNTL\_WIFI\_FORCE\_NOISO] Set this bit to disable the force isolation to the Wi-Fi circuits. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCEISO}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_ISO] Set this bit to force isolate the digital system. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCENOISO}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_NOISO] Set this bit to disable the force isolation to the digital system. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_WDTCONFIG0\_REG}{0x{}0098}\label{regdesc:RTCCNTLRTCWDTCONFIG0REG}
\regfield{RTC\_CNTL\_WDT\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_WDT\_STG0}{3}{28}{{0x{}0}}%
\regfield{RTC\_CNTL\_WDT\_STG1}{3}{25}{{0x{}0}}%
\regfield{RTC\_CNTL\_WDT\_STG2}{3}{22}{{0x{}0}}%
\regfield{RTC\_CNTL\_WDT\_STG3}{3}{19}{{0x{}0}}%
\regfield{RTC\_CNTL\_WDT\_CPU\_RESET\_LENGTH}{3}{16}{{0x{}1}}%
\regfield{RTC\_CNTL\_WDT\_SYS\_RESET\_LENGTH}{3}{13}{{0x{}1}}%
\regfield{RTC\_CNTL\_WDT\_FLASHBOOT\_MOD\_EN}{1}{12}{{1}}%
\regfield{RTC\_CNTL\_WDT\_PROCPU\_RESET\_EN}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_WDT\_APPCPU\_RESET\_EN}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_WDT\_PAUSE\_IN\_SLP}{1}{9}{{1}}%
\regfield{(reserved)}{9}{0}{000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTPAUSEINSLP}\item [RTC\_CNTL\_WDT\_PAUSE\_IN\_SLP] Set this bit to pause the watchdog in sleep. (R/W)
\label{fielddesc:RTCCNTLWDTAPPCPURESETEN}\item [RTC\_CNTL\_WDT\_APPCPU\_RESET\_EN] enable WDT reset APP CPU (R/W)
\label{fielddesc:RTCCNTLWDTPROCPURESETEN}\item [RTC\_CNTL\_WDT\_PROCPU\_RESET\_EN] Set this bit to allow the watchdog to be able to reset CPU. (R/W)
\label{fielddesc:RTCCNTLWDTFLASHBOOTMODEN}\item [RTC\_CNTL\_WDT\_FLASHBOOT\_MOD\_EN] Set this bit to enable watchdog when the chip boots from flash. (R/W)
\label{fielddesc:RTCCNTLWDTSYSRESETLENGTH}\item [RTC\_CNTL\_WDT\_SYS\_RESET\_LENGTH] Sets the length of the system reset counter. (R/W)
\label{fielddesc:RTCCNTLWDTCPURESETLENGTH}\item [RTC\_CNTL\_WDT\_CPU\_RESET\_LENGTH] Sets the length of the CPU reset counter. (R/W)
\label{fielddesc:RTCCNTLWDTSTG3}\item [RTC\_CNTL\_WDT\_STG3] 1: enable at the interrupt stage 2: enable at the CPU stage  3: enable at the system stage 4: enable at the system and RTC stage. (R/W)
\label{fielddesc:RTCCNTLWDTSTG2}\item [RTC\_CNTL\_WDT\_STG2] 1: enable at the interrupt stage 2: enable at the CPU stage  3: enable at the system stage 4: enable at the system and RTC stage. (R/W)
\label{fielddesc:RTCCNTLWDTSTG1}\item [RTC\_CNTL\_WDT\_STG1] 1: enable at the interrupt stage 2: enable at the CPU stage  3: enable at the system stage 4: enable at the system and RTC stage. (R/W)
\label{fielddesc:RTCCNTLWDTSTG0}\item [RTC\_CNTL\_WDT\_STG0] 1: enable at the interrupt stage 2: enable at the CPU stage  3: enable at the system stage 4: enable at the system and RTC stage. (R/W)
\label{fielddesc:RTCCNTLWDTEN}\item [RTC\_CNTL\_WDT\_EN] Set this bit to enable the RTC watchdog. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_WDTCONFIG1\_REG}{0x{}009C}\label{regdesc:RTCCNTLRTCWDTCONFIG1REG}
\regfield{RTC\_CNTL\_WDT\_STG0\_HOLD}{32}{0}{{200000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTSTG0HOLD}\item [RTC\_CNTL\_WDT\_STG0\_HOLD] Configures the hold time of RTC watchdog at level 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_WDTCONFIG2\_REG}{0x{}00A0}\label{regdesc:RTCCNTLRTCWDTCONFIG2REG}
\regfield{RTC\_CNTL\_WDT\_STG1\_HOLD}{32}{0}{{80000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTSTG1HOLD}\item [RTC\_CNTL\_WDT\_STG1\_HOLD] Configures the hold time of RTC watchdog at level 2. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_WDTCONFIG3\_REG}{0x{}00A4}\label{regdesc:RTCCNTLRTCWDTCONFIG3REG}
\regfield{RTC\_CNTL\_WDT\_STG2\_HOLD}{32}{0}{{0x{}000fff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTSTG2HOLD}\item [RTC\_CNTL\_WDT\_STG2\_HOLD] Configures the hold time of RTC watchdog at level 3. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_WDTCONFIG4\_REG}{0x{}00A8}\label{regdesc:RTCCNTLRTCWDTCONFIG4REG}
\regfield{RTC\_CNTL\_WDT\_STG3\_HOLD}{32}{0}{{0x{}000fff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTSTG3HOLD}\item [RTC\_CNTL\_WDT\_STG3\_HOLD] Configures the hold time of RTC watchdog at level 4. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_WDTFEED\_REG}{0x{}00AC}\label{regdesc:RTCCNTLRTCWDTFEEDREG}
\regfield{RTC\_CNTL\_RTC\_WDT\_FEED}{1}{31}{{0}}%
\regfield{(reserved)}{31}{0}{0000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCWDTFEED}\item [RTC\_CNTL\_RTC\_WDT\_FEED] Set 1 to feed the RTC watchdog. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_WDTWPROTECT\_REG}{0x{}00B0}\label{regdesc:RTCCNTLRTCWDTWPROTECTREG}
\regfield{RTC\_CNTL\_WDT\_WKEY}{32}{0}{{0x{}50d83aa1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTWKEY}\item [RTC\_CNTL\_WDT\_WKEY] If the register contains a different value than 0x{}50d83aa1, write protection for the RTC watchdog (RWDT) is enabled. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_SWD\_CONF\_REG}{0x{}00B4}\label{regdesc:RTCCNTLRTCSWDCONFREG}
\regfield{RTC\_CNTL\_SWD\_AUTO\_FEED\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_SWD\_DISABLE}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_SWD\_FEED}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_SWD\_RST\_FLAG\_CLR}{1}{28}{{0}}%
\regfield{RTC\_CNTL\_SWD\_SIGNAL\_WIDTH}{10}{18}{{300}}%
\regfield{RTC\_CNTL\_SWD\_BYPASS\_RST}{1}{17}{{0}}%
\regfield{(reserved)}{15}{2}{000000000000000}%
\regfield{RTC\_CNTL\_SWD\_FEED\_INT}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SWD\_RESET\_FLAG}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWDRESETFLAG}\item [RTC\_CNTL\_SWD\_RESET\_FLAG] Indicates the super watchdog reset flag. (RO)
\label{fielddesc:RTCCNTLSWDFEEDINT}\item [RTC\_CNTL\_SWD\_FEED\_INT] Receiving this interrupt leads to feeding the super watchdog via SW. (RO)
\label{fielddesc:RTCCNTLSWDBYPASSRST}\item [RTC\_CNTL\_SWD\_BYPASS\_RST] Set this bit to enable super watchdog reset. (R/W)
\label{fielddesc:RTCCNTLSWDSIGNALWIDTH}\item [RTC\_CNTL\_SWD\_SIGNAL\_WIDTH] Adjusts the signal width sent to the super watchdog. (R/W)
\label{fielddesc:RTCCNTLSWDRSTFLAGCLR}\item [RTC\_CNTL\_SWD\_RST\_FLAG\_CLR] Set to reset the super watchdog reset flag. (WO)
\label{fielddesc:RTCCNTLSWDFEED}\item [RTC\_CNTL\_SWD\_FEED] Set to feed the super watchdog via SW. (WO)
\label{fielddesc:RTCCNTLSWDDISABLE}\item [RTC\_CNTL\_SWD\_DISABLE] Set this bit to disable super watchdog. (R/W)
\label{fielddesc:RTCCNTLSWDAUTOFEEDEN}\item [RTC\_CNTL\_SWD\_AUTO\_FEED\_EN] Set this bit to enable automatic watchdog feeding upon interrupts. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_SWD\_WPROTECT\_REG}{0x{}00B8}\label{regdesc:RTCCNTLRTCSWDWPROTECTREG}
\regfield{RTC\_CNTL\_SWD\_WKEY}{32}{0}{{0x{}8f1d312a}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWDWKEY}\item [RTC\_CNTL\_SWD\_WKEY] Sets the write protection key of the super watchdog. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_SW\_CPU\_STALL\_REG}{0x{}00BC}\label{regdesc:RTCCNTLRTCSWCPUSTALLREG}
\regfield{RTC\_CNTL\_SW\_STALL\_PROCPU\_C1}{6}{26}{{0}}%
\regfield{RTC\_CNTL\_SW\_STALL\_APPCPU\_C1}{6}{20}{{0}}%
\regfield{(reserved)}{20}{0}{00000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWSTALLAPPCPUC1}\item [RTC\_CNTL\_SW\_STALL\_APPCPU\_C1] Set this bit to allow the SW to be able to send the CPU0 into stalling. (R/W)
\label{fielddesc:RTCCNTLSWSTALLPROCPUC1}\item [RTC\_CNTL\_SW\_STALL\_PROCPU\_C1] Set this bit to allow the SW to be able to send the CPU1 into stalling. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_STORE4\_REG}{0x{}00C0}\label{regdesc:RTCCNTLRTCSTORE4REG}
\regfield{RTC\_CNTL\_RTC\_SCRATCH4}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSCRATCH4}\item [RTC\_CNTL\_RTC\_SCRATCH4] Retention register 4. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_STORE5\_REG}{0x{}00C4}\label{regdesc:RTCCNTLRTCSTORE5REG}
\regfield{RTC\_CNTL\_RTC\_SCRATCH5}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSCRATCH5}\item [RTC\_CNTL\_RTC\_SCRATCH5] Retention register 5. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_STORE6\_REG}{0x{}00C8}\label{regdesc:RTCCNTLRTCSTORE6REG}
\regfield{RTC\_CNTL\_RTC\_SCRATCH6}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSCRATCH6}\item [RTC\_CNTL\_RTC\_SCRATCH6] Retention register 6. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_STORE7\_REG}{0x{}00CC}\label{regdesc:RTCCNTLRTCSTORE7REG}
\regfield{RTC\_CNTL\_RTC\_SCRATCH7}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCSCRATCH7}\item [RTC\_CNTL\_RTC\_SCRATCH7] Retention register 7. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_LOW\_POWER\_ST\_REG}{0x{}00D0}\label{regdesc:RTCCNTLRTCLOWPOWERSTREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{RTC\_CNTL\_MAIN\_STATE\_IN\_IDEL}{1}{27}{{0}}%
\regfield{(reserved)}{7}{20}{0000000}%
\regfield{RTC\_CNTL\_RTC\_RDY\_FOR\_WAKEUP}{1}{19}{{0}}%
\regfield{(reserved)}{19}{0}{0000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCRDYFORWAKEUP}\item [RTC\_CNTL\_RTC\_RDY\_FOR\_WAKEUP] Indicates the RTC is ready to be triggered by any wakeup source. (RO)
\label{fielddesc:RTCCNTLMAINSTATEINIDLE}\item [RTC\_CNTL\_MAIN\_STATE\_IN\_IDLE] Indicates the RTC state.
\begin{itemize}
    \item 0: the chip can be either
\begin{itemize}
    \item in sleep modes.
    \item entering sleep modes. In this case, wait until \hyperref[fielddesc:RTCCNTLRTCRDYFORWAKEUP]{RTC\_CNTL\_RTC\_RDY\_FOR\_WAKEUP} bit is set, then you can wake up the chip.
    \item exiting sleep mode. In this case, \hyperref[fielddesc:RTCCNTLMAINSTATEINIDLE]{RTC\_CNTL\_MAIN\_STATE\_IN\_IDLE} will eventually become 1.
\end{itemize}
    \item 1: the chip is not in sleep modes (i.e., running normally).
\end{itemize}
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_PAD\_HOLD\_REG}{0x{}00D8}\label{regdesc:RTCCNTLRTCPADHOLDREG}
\regfield{(reserved)}{10}{22}{0000000000}%
\regfield{RTC\_CNTL\_RTC\_PAD21\_HOLD}{1}{21}{{0}}%
\regfield{RTC\_CNTL\_RTC\_PAD20\_HOLD}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_RTC\_PAD19\_HOLD}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_PDAC2\_HOLD}{1}{18}{{0}}%
\regfield{RTC\_CNTL\_PDAC1\_HOLD}{1}{17}{{0}}%
\regfield{RTC\_CNTL\_X32N\_HOLD}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_X32P\_HOLD}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD14\_HOLD}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD13\_HOLD}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD12\_HOLD}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD11\_HOLD}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD10\_HOLD}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD9\_HOLD}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD8\_HOLD}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD7\_HOLD}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD6\_HOLD}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD5\_HOLD}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD4\_HOLD}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD3\_HOLD}{1}{3}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD2\_HOLD}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD1\_HOLD}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_TOUCH\_PAD0\_HOLD}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTOUCHPAD0HOLD}\item [RTC\_CNTL\_TOUCH\_PAD0\_HOLD] Sets the touch GPIO 0 to hold. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD1HOLD}\item [RTC\_CNTL\_TOUCH\_PAD1\_HOLD] Sets the touch GPIO 1 to hold. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD2HOLD}\item [RTC\_CNTL\_TOUCH\_PAD2\_HOLD] Sets the touch GPIO 2 to hold. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD3HOLD}\item [RTC\_CNTL\_TOUCH\_PAD3\_HOLD] Sets the touch GPIO 3 to hold. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD4HOLD}\item [RTC\_CNTL\_TOUCH\_PAD4\_HOLD] Sets the touch GPIO 4 to hold. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD5HOLD}\item [RTC\_CNTL\_TOUCH\_PAD5\_HOLD] Sets the touch GPIO 5 to hold. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD6HOLD}\item [RTC\_CNTL\_TOUCH\_PAD6\_HOLD] Sets the touch GPIO 6 to hold. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD7HOLD}\item [RTC\_CNTL\_TOUCH\_PAD7\_HOLD] Sets the touch GPIO 7 to hold. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD8HOLD}\item [RTC\_CNTL\_TOUCH\_PAD8\_HOLD] Sets the touch GPIO 8 to hold. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD9HOLD}\item [RTC\_CNTL\_TOUCH\_PAD9\_HOLD] Sets the touch GPIO 9 to hold. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD10HOLD}\item [RTC\_CNTL\_TOUCH\_PAD10\_HOLD] Sets the touch GPIO 10 to hold. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD11HOLD}\item [RTC\_CNTL\_TOUCH\_PAD11\_HOLD] Sets the touch GPIO 11 to hold. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD12HOLD}\item [RTC\_CNTL\_TOUCH\_PAD12\_HOLD] Sets the touch GPIO 12 to hold. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_RTC\_PAD\_HOLD\_REG}{0x{}00D8}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]


\label{fielddesc:RTCCNTLTOUCHPAD13HOLD}\item [RTC\_CNTL\_TOUCH\_PAD13\_HOLD] Sets the touch GPIO 13 to hold. (R/W)
\label{fielddesc:RTCCNTLTOUCHPAD14HOLD}\item [RTC\_CNTL\_TOUCH\_PAD14\_HOLD] Sets the touch GPIO 14 to hold. (R/W)
\label{fielddesc:RTCCNTLX32PHOLD}\item [RTC\_CNTL\_X32P\_HOLD] Sets the x32p to hold. (R/W)
\label{fielddesc:RTCCNTLX32NHOLD}\item [RTC\_CNTL\_X32N\_HOLD] Sets the x32n to hold. (R/W)
\label{fielddesc:RTCCNTLPDAC1HOLD}\item [RTC\_CNTL\_PDAC1\_HOLD] Sets the pdac1 to hold. (R/W)
\label{fielddesc:RTCCNTLPDAC2HOLD}\item [RTC\_CNTL\_PDAC2\_HOLD] Sets the pdac2 to hold. (R/W)
\label{fielddesc:RTCCNTLRTCPAD19HOLD}\item [RTC\_CNTL\_RTC\_PAD19\_HOLD] Sets the RTG GPIO 19 to hold. (R/W)
\label{fielddesc:RTCCNTLRTCPAD20HOLD}\item [RTC\_CNTL\_RTC\_PAD20\_HOLD] Sets the RTG GPIO 20 to hold. (R/W)
\label{fielddesc:RTCCNTLRTCPAD21HOLD}\item [RTC\_CNTL\_RTC\_PAD21\_HOLD] Sets the RTG GPIO 21 to hold. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_DIG\_PAD\_HOLD\_REG}{0x{}00DC}\label{regdesc:RTCCNTLDIGPADHOLDREG}
\regfield{RTC\_CNTL\_DIG\_PAD\_HOLD}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLDIGPADHOLD}\item [RTC\_CNTL\_DIG\_PAD\_HOLD] Set GPIO 21 to GPIO 45 to hold. (See bitmap to locate any GPIO). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_EXT\_WAKEUP1\_REG}{0x{}00E0}\label{regdesc:RTCCNTLRTCEXTWAKEUP1REG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{RTC\_CNTL\_EXT\_WAKEUP1\_STATUS\_CLR}{1}{22}{{0}}%
\regfield{RTC\_CNTL\_EXT\_WAKEUP1\_SEL}{22}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLEXTWAKEUP1SEL}\item [RTC\_CNTL\_EXT\_WAKEUP1\_SEL] Selects a RTC GPIO to be the EXT1 wakeup source. (R/W)
\label{fielddesc:RTCCNTLEXTWAKEUP1STATUSCLR}\item [RTC\_CNTL\_EXT\_WAKEUP1\_STATUS\_CLR] Clears the EXT1 wakeup status. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_EXT\_WAKEUP1\_STATUS\_REG}{0x{}00E4}\label{regdesc:RTCCNTLRTCEXTWAKEUP1STATUSREG}
\regfield{(reserved)}{10}{22}{0000000000}%
\regfield{RTC\_CNTL\_EXT\_WAKEUP1\_STATUS}{22}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLEXTWAKEUP1STATUS}\item [RTC\_CNTL\_EXT\_WAKEUP1\_STATUS] Indicates the EXT1 wakeup status. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_BROWN\_OUT\_REG}{0x{}00E8}\label{regdesc:RTCCNTLRTCBROWNOUTREG}
\regfield{RTC\_CNTL\_RTC\_BROWN\_OUT\_DET}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_ENA}{1}{30}{{1}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_CNT\_CLR}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_ANA\_RST\_EN}{1}{28}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_RST\_SEL}{1}{27}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_RST\_ENA}{1}{26}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_RST\_WAIT}{10}{16}{{0x{}3ff}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_PD\_RF\_ENA}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_CLOSE\_FLASH\_ENA}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_WAIT}{10}{4}{{0x{}1}}%
\regfield{(reserved)}{4}{0}{0000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLBROWNOUTINTWAIT}\item [RTC\_CNTL\_BROWN\_OUT\_INT\_WAIT] Configures the waiting cycle before sending an interrupt. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTCLOSEFLASHENA}\item [RTC\_CNTL\_BROWN\_OUT\_CLOSE\_FLASH\_ENA] Set this bit to enable PD the flash when a brown-out happens. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTPDRFENA}\item [RTC\_CNTL\_BROWN\_OUT\_PD\_RF\_ENA] Set this bit to enable PD the RF circuits when a brown-out happens. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTRSTWAIT}\item [RTC\_CNTL\_BROWN\_OUT\_RST\_WAIT] Configures the waiting cycle before the reset after a brown-out. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTRSTENA}\item [RTC\_CNTL\_BROWN\_OUT\_RST\_ENA] Enables to reset brown-out. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTRSTSEL}\item [RTC\_CNTL\_BROWN\_OUT\_RST\_SEL] Selects the reset type when a brown-out happens. 1: Chip reset  0: System reset. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTANARSTEN}\item [RTC\_CNTL\_BROWN\_OUT\_ANA\_RST\_EN] Enables brown-out detector reset. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTCNTCLR}\item [RTC\_CNTL\_BROWN\_OUT\_CNT\_CLR] Clears the brown-out counter. (WO)
\label{fielddesc:RTCCNTLBROWNOUTENA}\item [RTC\_CNTL\_BROWN\_OUT\_ENA] Set this bit to enable brown-out detection. (R/W)
\label{fielddesc:RTCCNTLRTCBROWNOUTDET}\item [RTC\_CNTL\_RTC\_BROWN\_OUT\_DET] Indicates the status of the brown-out signal. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_TIME\_LOW1\_REG}{0x{}00EC}\label{regdesc:RTCCNTLRTCTIMELOW1REG}
\regfield{RTC\_CNTL\_RTC\_TIMER\_VALUE1\_LOW}{32}{0}{{0x{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCTIMERVALUE1LOW}\item [RTC\_CNTL\_RTC\_TIMER\_VALUE1\_LOW] Stores the lower 32 bits of RTC timer 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_TIME\_HIGH1\_REG}{0x{}00F0}\label{regdesc:RTCCNTLRTCTIMEHIGH1REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{RTC\_CNTL\_RTC\_TIMER\_VALUE1\_HIGH}{16}{0}{{0x{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCTIMERVALUE1HIGH}\item [RTC\_CNTL\_RTC\_TIMER\_VALUE1\_HIGH] Stores the higher 16 bits of RTC timer 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_XTAL32K\_CLK\_FACTOR\_REG}{0x{}00F4}\label{regdesc:RTCCNTLRTCXTAL32KCLKFACTORREG}
\regfield{RTC\_CNTL\_XTAL32K\_CLK\_FACTOR}{32}{0}{{0x{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLXTAL32KCLKFACTOR}\item [RTC\_CNTL\_XTAL32K\_CLK\_FACTOR] Configures the divider factor for the 32 kHz crystal oscillator. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_XTAL32K\_CONF\_REG}{0x{}00F8}\label{regdesc:RTCCNTLRTCXTAL32KCONFREG}
\regfield{RTC\_CNTL\_XTAL32K\_STABLE\_THRES}{4}{28}{{0x{}0}}%
\regfield{RTC\_CNTL\_XTAL32K\_WDT\_TIMEOUT}{8}{20}{{0x{}ff}}%
\regfield{RTC\_CNTL\_XTAL32K\_RESTART\_WAIT}{16}{4}{{0x{}00}}%
\regfield{RTC\_CNTL\_XTAL32K\_RETURN\_WAIT}{4}{0}{{0x{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLXTAL32KRETURNWAIT}\item [RTC\_CNTL\_XTAL32K\_RETURN\_WAIT] Defines the waiting cycles before returning to the normal 32 kHz crystal oscillator. (R/W)
\label{fielddesc:RTCCNTLXTAL32KRESTARTWAIT}\item [RTC\_CNTL\_XTAL32K\_RESTART\_WAIT] Defines the maximum waiting cycle before restarting the 32 kHz crystal oscillator. (R/W)
\label{fielddesc:RTCCNTLXTAL32KWDTTIMEOUT}\item [RTC\_CNTL\_XTAL32K\_WDT\_TIMEOUT] Defines the maximum waiting period for clock detection. If no clock is detected after this period, the 32 kHz crystal oscillator can be regarded as dead. (R/W)
\label{fielddesc:RTCCNTLXTAL32KSTABLETHRES}\item [RTC\_CNTL\_XTAL32K\_STABLE\_THRES] Defines the maximum allowed restarting period, within which the 32 kHz crystal oscillator can be regarded as stable. (R/W)
\end{reglist}\end{regdesc}
\end{register}



\begin{register}{H}{RTC\_CNTL\_RTC\_USB\_CONF\_REG}{0x{}0120}\label{regdesc:RTCCNTLRTCUSBCONFREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_SW\_HW\_USB\_PHY\_SEL}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_SW\_USB\_PHY\_SEL}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_IO\_MUX\_RESET\_DISABLE}{1}{18}{{0}}%
\regfield{RTC\_CNTL\_USB\_RESET\_DISABLE}{1}{17}{{0}}%
\regfield{RTC\_CNTL\_USB\_TX\_EN\_OVERRIDE}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_USB\_TX\_EN}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_USB\_TXP}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_USB\_TXM}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_USB\_PAD\_ENABLE}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_USB\_PAD\_ENABLE\_OVERRIDE}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_USB\_PULLUP\_VALUE}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_USB\_DM\_PULLDOWN}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_USB\_DM\_PULLUP}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_USB\_DP\_PULLDOWN}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_USB\_DP\_PULLUP}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_USB\_PAD\_PULL\_OVERRIDE}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_USB\_VREF\_OVERRIDE}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_USB\_VREFL}{2}{2}{{0}}%
\regfield{RTC\_CNTL\_USB\_VREFH}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLUSBVREFH}\item [RTC\_CNTL\_USB\_VREFH] Controls the internal USB transceiver single-end input high threshold (1.76 V to 2 V, step 80 mV). This field is valid when \hyperref[fielddesc:RTCCNTLUSBVREFOVERRIDE]{RTC\_CNTL\_USB\_VREF\_OVERRIDE} is set. (R/W)
\label{fielddesc:RTCCNTLUSBVREFL}\item [RTC\_CNTL\_USB\_VREFL] Controls the internal USB transceiver single-end input low threshold (0.8 V to 1.04 V, step 80 mV). This field is valid when \hyperref[fielddesc:RTCCNTLUSBVREFOVERRIDE]{RTC\_CNTL\_USB\_VREF\_OVERRIDE} is set.  (R/W)
\label{fielddesc:RTCCNTLUSBVREFOVERRIDE}\item [RTC\_CNTL\_USB\_VREF\_OVERRIDE] Set this bit to enable controlling the internal USB transceiver's input voltage threshold via software. (R/W)
\label{fielddesc:RTCCNTLUSBPADPULLOVERRIDE}\item [RTC\_CNTL\_USB\_PAD\_PULL\_OVERRIDE] Set this bit to enable software controlling the internal USB transceiver's USB D+/D- pull-up and pull-down resistor via software. (R/W)
\label{fielddesc:RTCCNTLUSBDPPULLUP}\item [RTC\_CNTL\_USB\_DP\_PULLUP] Set this bit to enable USB+ pull-up resistor. This field is valid when \hyperref[fielddesc:RTCCNTLUSBPADPULLOVERRIDE]{RTC\_CNTL\_USB\_PAD\_PULL\_OVERRIDE} is set. (R/W)
\label{fielddesc:RTCCNTLUSBDPPULLDOWN}\item [RTC\_CNTL\_USB\_DP\_PULLDOWN] Set this bit to enable USB+ pull-down resistor. This field is valid when \hyperref[fielddesc:RTCCNTLUSBPADPULLOVERRIDE]{RTC\_CNTL\_USB\_PAD\_PULL\_OVERRIDE} is set. (R/W)
\label{fielddesc:RTCCNTLUSBDMPULLUP}\item [RTC\_CNTL\_USB\_DM\_PULLUP] Set this bit to enable USB- pull-up resistor. This field is valid when \hyperref[fielddesc:RTCCNTLUSBPADPULLOVERRIDE]{RTC\_CNTL\_USB\_PAD\_PULL\_OVERRIDE} is set. (R/W)
\label{fielddesc:RTCCNTLUSBDMPULLDOWN}\item [RTC\_CNTL\_USB\_DM\_PULLDOWN] Set this bit to enable USB- pull-down resistor. This field is valid when \hyperref[fielddesc:RTCCNTLUSBPADPULLOVERRIDE]{RTC\_CNTL\_USB\_PAD\_PULL\_OVERRIDE} is set. (R/W)
\label{fielddesc:RTCCNTLUSBPULLUPVALUE}\item [RTC\_CNTL\_USB\_PULLUP\_VALUE] Controls the pull-up value. 0: typical value is 2.4 kΩ; 1: typical value is 1.2 kΩ. This field is valid when \hyperref[fielddesc:RTCCNTLUSBPADPULLOVERRIDE]{RTC\_CNTL\_USB\_PAD\_PULL\_OVERRIDE} is set. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_RTC\_USB\_CONF\_REG}{0x{}0120}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]


\label{fielddesc:RTCCNTLUSBPADENABLEOVERRIDE}\item [RTC\_CNTL\_USB\_PAD\_ENABLE\_OVERRIDE] Set this bit to enable controlling the internal USB transceiver's function via software. (R/W)
\label{fielddesc:RTCCNTLUSBPADENABLE}\item [RTC\_CNTL\_USB\_PAD\_ENABLE] Set this bit to enable the USB transceiver function. This field is valid when \hyperref[fielddesc:RTCCNTLUSBPADENABLE]{RTC\_CNTL\_USB\_PAD\_ENABLE\_OVERRIDE} is set. (R/W)
\label{fielddesc:RTCCNTLUSBTXM}\item [RTC\_CNTL\_USB\_TXM] Configures the USB D- tx value in test mode. This field is valid when \hyperref[fielddesc:RTCCNTLUSBTXENOVERRIDE]{RTC\_CNTL\_USB\_TX\_EN\_OVERRIDE} is set.(R/W)
\label{fielddesc:RTCCNTLUSBTXP}\item [RTC\_CNTL\_USB\_TXP] Configures the USB D+ tx value in test mode. This field is valid when \hyperref[fielddesc:RTCCNTLUSBTXENOVERRIDE]{RTC\_CNTL\_USB\_TX\_EN\_OVERRIDE} is set.(R/W)
\label{fielddesc:RTCCNTLUSBTXEN}\item [RTC\_CNTL\_USB\_TX\_EN] Setting to 1 enables USB TX, setting to 0 enables USB RX. Only valid when \hyperref[fielddesc:RTCCNTLUSBTXENOVERRIDE]{RTC\_CNTL\_USB\_TX\_EN\_OVERRIDE} is 1. (R/W)
\label{fielddesc:RTCCNTLUSBTXENOVERRIDE}\item [RTC\_CNTL\_USB\_TX\_EN\_OVERRIDE] Set this bit to enable controlling the internal USB transceiver Tx in test mode via software. (R/W)
\label{fielddesc:RTCCNTLUSBRESETDISABLE}\item [RTC\_CNTL\_USB\_RESET\_DISABLE] Set this bit to disable reset USB OTG. (R/W)
\label{fielddesc:RTCCNTLIOMUXRESETDISABLE}\item [RTC\_CNTL\_IO\_MUX\_RESET\_DISABLE] Set this bit to disable reset IO MUX and GPIO Matrix. (R/W)
\label{fielddesc:RTCCNTLSWUSBPHYSEL}\item [RTC\_CNTL\_SW\_USB\_PHY\_SEL] Set this bit to allow USB OTG to use the internal USB transceiver. Clear this bit to allow USB-Serial-JTAG to use the internal USB transceiver. This field is valid when \hyperref[fielddesc:RTCCNTLSWHWUSBPHYSEL]{RTC\_CNTL\_SW\_HW\_USB\_PHY\_SEL} is set. (R/W)
\label{fielddesc:RTCCNTLSWHWUSBPHYSEL}\item [RTC\_CNTL\_SW\_HW\_USB\_PHY\_SEL] Set this bit to control the internal USB transceiver selection via software (\hyperref[fielddesc:RTCCNTLSWUSBPHYSEL]{RTC\_CNTL\_SW\_USB\_PHY\_SEL}). Clear this bit to control the the internal USB transceiver selection via hardware (eFuse). (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_RTC\_SLP\_REJECT\_CAUSE\_REG}{0x{}0128}\label{regdesc:RTCCNTLRTCSLPREJECTCAUSEREG}
\regfield{(reserved)}{14}{18}{00000000000000}%
\regfield{RTC\_CNTL\_REJECT\_CAUSE}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLREJECTCAUSE}\item [RTC\_CNTL\_REJECT\_CAUSE] Stores the reject-to-sleep cause. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_OPTION1\_REG}{0x{}012C}\label{regdesc:RTCCNTLRTCOPTION1REG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{RTC\_CNTL\_FORCE\_DOWNLOAD\_BOOT}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLFORCEDOWNLOADBOOT}\item [RTC\_CNTL\_FORCE\_DOWNLOAD\_BOOT] Set this bit to force chip enters download boot by sw. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_SLP\_WAKEUP\_CAUSE\_REG}{0x{}0130}\label{regdesc:RTCCNTLRTCSLPWAKEUPCAUSEREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{RTC\_CNTL\_WAKEUP\_CAUSE}{17}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWAKEUPCAUSE}\item [RTC\_CNTL\_WAKEUP\_CAUSE] Stores the wakeup cause. (RO)
\end{reglist}\end{regdesc}
\end{register}



\begin{register}{H}{RTC\_CNTL\_INT\_ENA\_RTC\_W1TS\_REG}{0x{}0138}\label{regdesc:RTCCNTLINTENARTCW1TSREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_APPROACH\_LOOP\_DONE\_INT\_ENA\_W1TS}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_ENA\_W1TS}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_ENA\_W1TS}{1}{18}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_ENA\_W1TS}{1}{17}{{0}}%
\regfield{RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_ENA\_W1TS}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SWD\_INT\_ENA\_W1TS}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC2\_INT\_ENA\_W1TS}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_INT\_ENA\_W1TS}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TSENS\_INT\_ENA\_W1TS}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC1\_INT\_ENA\_W1TS}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_ENA\_W1TS}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_ENA\_W1TS}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_ENA\_W1TS}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_ENA\_W1TS}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_ENA\_W1TS}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_RTC\_ULP\_CP\_INT\_ENA\_W1TS}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_ENA\_W1TS}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_RTC\_WDT\_INT\_ENA\_W1TS}{1}{3}{{0}}%
\regfield{RTC\_CNTL\_SDIO\_IDLE\_INT\_ENA\_W1TS}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_ENA\_W1TS}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA\_W1TS}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTENAW1TS}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA\_W1TS] Enables interrupt when the chip wakes up from sleep. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLSLPWAKEUPINTENA]{RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLSLPREJECTINTENAW1TS}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_ENA\_W1TS] Enables interrupt when the chip rejects to go to sleep. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLSLPREJECTINTENA]{RTC\_CNTL\_SLP\_REJECT\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLSDIOIDLEINTENAW1TS}\item [RTC\_CNTL\_SDIO\_IDLE\_INT\_ENA\_W1TS] Enables interrupt when the SDIO idles. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLSDIOIDLEINTENA]{RTC\_CNTL\_SDIO\_IDLE\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLRTCWDTINTENAW1TS}\item [RTC\_CNTL\_RTC\_WDT\_INT\_ENA\_W1TS] Enables the RTC watchdog interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCWDTINTENA]{RTC\_CNTL\_RTC\_WDT\_INT\_ENA} field will be set to 1. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCTOUCHSCANDONEINTENAW1TS}\item [RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_ENA\_W1TS] Enables interrupt upon the completion of a touch scanning. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCTOUCHSCANDONEINTENA]{RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLRTCULPCPINTENAW1TS}\item [RTC\_CNTL\_RTC\_ULP\_CP\_INT\_ENA\_W1TS] Enables the ULP co-processor interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCULPCPINTENA]{RTC\_CNTL\_RTC\_ULP\_CP\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLRTCTOUCHDONEINTENAW1TS}\item [RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_ENA\_W1TS] Enables interrupt upon the completion of a single touch. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCTOUCHDONEINTENA]{RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLRTCTOUCHACTIVEINTENAW1TS}\item [RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_ENA\_W1TS] Enables interrupt when a touch is detected. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCTOUCHACTIVEINTENA]{RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLRTCTOUCHINACTIVEINTENAW1TS}\item [RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_ENA\_W1TS] Enables interrupt when a touch is released. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCTOUCHACTIVEINTENA]{RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_ENA} field will be set to 1. (WO)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_INT\_ENA\_RTC\_W1TS\_REG}{0x{}0138}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]


\label{fielddesc:RTCCNTLRTCBROWNOUTINTENAW1TS}\item [RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_ENA\_W1TS] Enables the brown out interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCBROWNOUTINTENA]{RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLRTCMAINTIMERINTENAW1TS}\item [RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_ENA\_W1TS] Enables the RTC main timer interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCMAINTIMERINTENA]{RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLRTCSARADC1INTENAW1TS}\item [RTC\_CNTL\_RTC\_SARADC1\_INT\_ENA\_W1TS] Enables the SAR ADC1 interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCSARADC1INTENA]{RTC\_CNTL\_RTC\_SARADC1\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLRTCTSENSINTENAW1TS}\item [RTC\_CNTL\_RTC\_TSENS\_INT\_ENA\_W1TS] Enables the temperature sensor interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCTSENSINTENA]{RTC\_CNTL\_RTC\_TSENS\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLRTCCOCPUINTENAW1TS}\item [RTC\_CNTL\_RTC\_COCPU\_INT\_ENA\_W1TS] Enables the ULP-RISCV interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCCOCPUINTENA]{RTC\_CNTL\_RTC\_COCPU\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLRTCSARADC2INTENAW1TS}\item [RTC\_CNTL\_RTC\_SARADC2\_INT\_ENA\_W1TS] Enables the SAR ADC2 interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCSARADC2INTENA]{RTC\_CNTL\_RTC\_SARADC2\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLRTCSWDINTENAW1TS}\item [RTC\_CNTL\_RTC\_SWD\_INT\_ENA\_W1TS] Enables the super watchdog interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCSWDINTENA]{RTC\_CNTL\_RTC\_SWD\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLRTCXTAL32KDEADINTENAW1TS}\item [RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_ENA\_W1TS] Enables interrupt when the 32 kHz crystal is dead. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCXTAL32KDEADINTENA]{RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLRTCCOCPUTRAPINTENAW1TS}\item [RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_ENA\_W1TS] Enables interrupt when the ULP-RISCV is trapped. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCCOCPUTRAPINTENA]{RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLRTCTOUCHTIMEOUTINTENAW1TS}\item [RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_ENA\_W1TS] Enables interrupt when touch sensor times out. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCTOUCHTIMEOUTINTENA]{RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLRTCGLITCHDETINTENAW1TS}\item [RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_ENA\_W1TS] Enables interrupt when a glitch is detected. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCGLITCHDETINTENA]{RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_ENA} field will be set to 1. (WO)
\label{fielddesc:RTCCNTLRTCTOUCHAPPROACHLOOPDONEINTENAW1TS}\item [RTC\_CNTL\_RTC\_TOUCH\_APPROACH\_LOOP\_DONE\_INT\_ENA\_W1TS] Enables interrupt upon the completion of a touch approach loop. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCTOUCHAPPROACHLOOPDONEINTENA]{RTC\_CNTL\_RTC\_TOUCH\_APPROACH\_LOOP\_DONE\_INT\_ENA} field will be set to 1. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_ENA\_RTC\_W1TC\_REG}{0x{}013C}\label{regdesc:RTCCNTLINTENARTCW1TCREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_APPROACH\_LOOP\_DONE\_INT\_ENA\_W1TC}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_ENA\_W1TC}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_ENA\_W1TC}{1}{18}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_ENA\_W1TC}{1}{17}{{0}}%
\regfield{RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_ENA\_W1TC}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SWD\_INT\_ENA\_W1TC}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC2\_INT\_ENA\_W1TC}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_RTC\_COCPU\_INT\_ENA\_W1TC}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TSENS\_INT\_ENA\_W1TC}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_RTC\_SARADC1\_INT\_ENA\_W1TC}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_ENA\_W1TC}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_ENA\_W1TC}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_ENA\_W1TC}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_ENA\_W1TC}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_ENA\_W1TC}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_RTC\_ULP\_CP\_INT\_ENA\_W1TC}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_ENA\_W1TC}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_RTC\_WDT\_INT\_ENA\_W1TC}{1}{3}{{0}}%
\regfield{RTC\_CNTL\_SDIO\_IDLE\_INT\_ENA\_W1TC}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_ENA\_W1TC}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA\_W1TC}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\raggedright \label{fielddesc:RTCCNTLSLPWAKEUPINTENAW1TC}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA\_W1TC] Clears the interrupt triggered when the chip wakes up from sleep. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLSLPWAKEUPINTCLR]{RTC\_CNTL\_SLP\_WAKEUP\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLSLPREJECTINTENAW1TC}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_ENA\_W1TC] Clears the interrupt triggered when the chip rejects to go to sleep. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLSLPREJECTINTCLR]{RTC\_CNTL\_SLP\_REJECT\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLSDIOIDLEINTENAW1TC}\item [RTC\_CNTL\_SDIO\_IDLE\_INT\_ENA\_W1TC] Clears the interrupt triggered when the SDIO idles. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLSDIOIDLEINTCLR]{RTC\_CNTL\_SDIO\_IDLE\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCWDTINTENAW1TC}\item [RTC\_CNTL\_RTC\_WDT\_INT\_ENA\_W1TC] Clears the RTC watchdog interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCWDTINTCLR]{RTC\_CNTL\_RTC\_WDT\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCTOUCHSCANDONEINTENAW1TC}\item [RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_ENA\_W1TC] Clears the interrupt triggered upon the completion of a touch scanning. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCTOUCHSCANDONEINTCLR]{RTC\_CNTL\_RTC\_TOUCH\_SCAN\_DONE\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCULPCPINTENAW1TC}\item [RTC\_CNTL\_RTC\_ULP\_CP\_INT\_ENA\_W1TC] Clears the ULP co-processor interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCULPCPINTCLR]{RTC\_CNTL\_RTC\_ULP\_CP\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCTOUCHDONEINTENAW1TC}\item [RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_ENA\_W1TC] Clears the interrupt triggered upon the completion of a single touch. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCTOUCHDONEINTCLR]{RTC\_CNTL\_RTC\_TOUCH\_DONE\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCTOUCHACTIVEINTENAW1TC}\item [RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_ENA\_W1TC] Clears the interrupt triggered when a touch is detected. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCTOUCHACTIVEINTCLR]{RTC\_CNTL\_RTC\_TOUCH\_ACTIVE\_INT\_CLR} field will be cleared. (WO)


\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_INT\_ENA\_RTC\_W1TC\_REG}{0x{}013C}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\raggedright \label{fielddesc:RTCCNTLRTCTOUCHINACTIVEINTENAW1TC}\item [RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_ENA\_W1TC] Clears the interrupt triggered when a touch is released. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCTOUCHINACTIVEINTCLR]{RTC\_CNTL\_RTC\_TOUCH\_INACTIVE\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCBROWNOUTINTENAW1TC}\item [RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_ENA\_W1TC] Clears the brown out interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCBROWNOUTINTCLR]{RTC\_CNTL\_RTC\_BROWN\_OUT\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCMAINTIMERINTENAW1TC}\item [RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_ENA\_W1TC] Clears the RTC main timer interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCMAINTIMERINTCLR]{RTC\_CNTL\_RTC\_MAIN\_TIMER\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCSARADC1INTENAW1TC}\item [RTC\_CNTL\_RTC\_SARADC1\_INT\_ENA\_W1TC] Clears the SAR ADC1 interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCSARADC1INTCLR]{RTC\_CNTL\_RTC\_SARADC1\_INT\_ENA\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCTSENSINTENAW1TC}\item [RTC\_CNTL\_RTC\_TSENS\_INT\_ENA\_W1TC] Clears the temperature sensor interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCTSENSINTCLR]{RTC\_CNTL\_RTC\_TSENS\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCCOCPUINTENAW1TC}\item [RTC\_CNTL\_RTC\_COCPU\_INT\_ENA\_W1TC] Clears the ULP-RISCV interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCCOCPUINTCLR]{RTC\_CNTL\_RTC\_COCPU\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCSARADC2INTENAW1TC}\item [RTC\_CNTL\_RTC\_SARADC2\_INT\_ENA\_W1TC] Clears the SAR ADC2 interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCSARADC2INTCLR]{RTC\_CNTL\_RTC\_SARADC2\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCSWDINTENAW1TC}\item [RTC\_CNTL\_RTC\_SWD\_INT\_ENA\_W1TC] Clears the super watchdog interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCSWDINTCLR]{RTC\_CNTL\_RTC\_SWD\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCXTAL32KDEADINTENAW1TC}\item [RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_ENA\_W1TC] Clears the interrupt triggered when the 32 kHz crystal is dead. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCXTAL32KDEADINTCLR]{RTC\_CNTL\_RTC\_XTAL32K\_DEAD\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCCOCPUTRAPINTENAW1TC}\item [RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_ENA\_W1TC] Clears the interrupt triggered when the ULP-RISCV is trapped. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCCOCPUTRAPINTCLR]{RTC\_CNTL\_RTC\_COCPU\_TRAP\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCTOUCHTIMEOUTINTENAW1TC}\item [RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_ENA\_W1TC] Clears the interrupt triggered when touch sensor times out. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCTOUCHTIMEOUTINTCLR]{RTC\_CNTL\_RTC\_TOUCH\_TIMEOUT\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCGLITCHDETINTENAW1TC}\item [RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_ENA\_W1TC] Clears the interrupt triggered when a glitch is detected. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCGLITCHDETINTCLR]{RTC\_CNTL\_RTC\_GLITCH\_DET\_INT\_CLR} field will be cleared. (WO)
\raggedright \label{fielddesc:RTCCNTLRTCTOUCHAPPROACHLOOPDONEINTENAW1TC}\item [RTC\_CNTL\_RTC\_TOUCH\_APPROACH\_LOOP\_DONE\_INT\_ENA\_W1TC] Clears the interrupt triggered upon the completion of a touch approach loop. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLRTCTOUCHAPPROACHLOOPDONEINTCLR]{RTC\_CNTL\_RTC\_TOUCH\_APPROACH\_LOOP\_DONE\_INT\_CLR} field will be cleared. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RETENTION\_CTRL\_REG}{0x{}0140}\label{regdesc:RTCCNTLRETENTIONCTRLREG}
\regfield{RTC\_CNTL\_RETENTION\_WAIT}{7}{25}{{20}}%
\regfield{RTC\_CNTL\_RETENTION\_EN}{1}{24}{{0}}%
\regfield{RTC\_CNTL\_RETENTION\_CLKOFF\_WAIT}{4}{20}{{3}}%
\regfield{RTC\_CNTL\_RETENTION\_DONE\_WAIT}{3}{17}{{2}}%
\regfield{(reserved)}{1}{16}{0}%
\regfield{RTC\_CNTL\_RETENTION\_TARGET}{2}{14}{{0}}%
\regfield{(reserved)}{14}{0}{00000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRETENTIONTARGET}\item [RTC\_CNTL\_RETENTION\_TARGET] Configures retention target: cpu and/or tag (R/W)
\label{fielddesc:RTCCNTLRETENTIONDONEWAIT}\item [RTC\_CNTL\_RETENTION\_DONE\_WAIT] Configures the waiting cycle before retention done (R/W)
\label{fielddesc:RTCCNTLRETENTIONCLKOFFWAIT}\item [RTC\_CNTL\_RETENTION\_CLKOFF\_WAIT] Configures the waiting cycle before clk\_off. (R/W)
\label{fielddesc:RTCCNTLRETENTIONEN}\item [RTC\_CNTL\_RETENTION\_EN] Set this bit to enable retention. (R/W)
\label{fielddesc:RTCCNTLRETENTIONWAIT}\item [RTC\_CNTL\_RETENTION\_WAIT] Configures the waiting cycles for retention operation. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RTC\_FIB\_SEL\_REG}{0x{}0148}\label{regdesc:RTCCNTLRTCFIBSELREG}
\regfield{(reserved)}{29}{3}{00000000000000000000000000000}%
\regfield{RTC\_CNTL\_RTC\_FIB\_SEL}{3}{0}{{7}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCFIBSEL}\item [RTC\_CNTL\_RTC\_FIB\_SEL] Configures the brownout detector. (R/W)
\end{reglist}\end{regdesc}
\end{register}
