
\begin{register}{H}{tselect}{0x7A0}\label{regdesc:TSELECT}
\regfield{(reserved)}{29}{2}{{0x00000000}}%
\regfield{tselect}{2}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:TSELECT}\item [tselect] Configures the index (0-3) of the selected trigger unit. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{tdata1}{0x7A1}\label{regdesc:TDATA1}
\regfield{type}{4}{28}{{0x2}}%
\regfield{dmode}{1}{27}{{0}}%
\regfield{data}{27}{0}{{0x3e00000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:TDATA1TYPE}\item [type] Represents the trigger type. This field is reserved since only match type (0x2) triggers are supported. (RO)
\label{fielddesc:TDATA1DMODE}\item [dmode] This is set to 1 if a trigger is being used by the debugger.\\
0: Both Debug and M mode can write the tdata1 and tdata2 registers at the selected tselect.\\
1: Only Debug Mode can write the tdata1 and tdata2 registers at the selected tselect. Writes from other modes are ignored.\\
Note: Only writable from debug mode.\\
(R/W)
\label{fielddesc:TDATA1DATA}\item [data] Configures the abstract tdata1 content. This will always be interpreted as fields of \hyperref[regdesc:MCONTROL]{mcontrol} since only match type (0x2) triggers are supported. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{tdata2}{0x7A2}\label{regdesc:TDATA2}
\regfield{tdata2}{32}{0}{{0x00000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:TDATA2}\item [tdata2] Configures the abstract tdata2 content. This will always be interpreted as \hyperref[regdesc:MADDRESS]{maddress} since only match type (0x2) triggers are supported. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{tcontrol}{0x7A5}\label{regdesc:TCONTROL}
\regfield{(reserved)}{24}{8}{{0x000000}}%
\regfield{mpte}{1}{7}{{0}}%
\regfield{(reserved)}{6}{1}{{0x00}}%
\regfield{mte}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:TCONTROLMPTE}\item [mpte] Configures whether to enable the machine mode previous trigger.\\
When CPU is taking a machine mode trap, the value of \hyperref[fielddesc:TCONTROLMTE]{mte} is automatically pushed into this.\\
When CPU is executing MRET, its value is popped back into \hyperref[fielddesc:TCONTROLMTE]{mte}, so this becomes 0.\\
(R/W)
\label{fielddesc:TCONTROLMTE}\item [mte] Configures whether to enable the machine mode trigger.\\
When CPU is taking a machine mode trap, its value is automatically pushed into \hyperref[fielddesc:TCONTROLMPTE]{mpte}, so this becomes 0 and triggers with \hyperref[fielddesc:MCONTROLACTION]{action}=0 are disabled globally.\\
When CPU is executing MRET, the value of \hyperref[fielddesc:TCONTROLMPTE]{mpte} is automatically popped back into this.\\
(R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{mcontrol}{0x7A1}\label{regdesc:MCONTROL}
\regfield{(reserved)}{4}{28}{{0x2}}%
\regfield{dmode}{1}{27}{{0}}%
\regfield{(reserved)}{6}{21}{{0x1f}}%
\regfield{hit}{1}{20}{{0}}%
\regfield{(reserved)}{4}{16}{{0}}%
\regfield{action}{4}{12}{{0}}%
\regfield{(reserved)}{1}{11}{{0}}%
\regfield{match}{4}{7}{{0}}%
\regfield{m}{1}{6}{{0}}%
\regfield{(reserved)}{2}{4}{{0}}%
\regfield{u}{1}{3}{{0}}%
\regfield{execute}{1}{2}{{0}}%
\regfield{store}{1}{1}{{0}}%
\regfield{load}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MCONTROLDMODE}\item [dmode] Same as \hyperref[fielddesc:TDATA1DMODE]{dmode} in \hyperref[regdesc:TDATA1]{tdata1}. (RW *)
\label{fielddesc:MCONTROLHIT}\item [hit] This is found to be 1 if the selected trigger had fired previously. This bit is to be cleared manually. (R/W) 
\label{fielddesc:MCONTROLACTION}\item [action] Configures the selected trigger to perform one of the available actions when firing. Valid options are:\\
0x0: cause breakpoint exception.\\
0x1: enter debug mode (only valid when dmode = 1)\\
Note: Writing an invalid value will set this to the default value 0x0.\\
(R/W)
\label{fielddesc:MCONTROLMATCH}\item [match] Configures the selected trigger to perform one of the available matching operations on a data/instruction address. Valid options are:\\
0x0: exact byte match, i.e., address corresponding to one of the bytes in an access must match the value of \hyperref[regdesc:MADDRESS]{maddress} exactly.\\
0x1: NAPOT match, i.e., at least one of the bytes of an access must lie in the NAPOT region specified in \hyperref[regdesc:MADDRESS]{maddress}.\\
Note: Writing a larger value will clip it to the largest possible value 0x1.\\
(R/W)
\label{fielddesc:MCONTROLM}\item [m] Set this for enabling selected trigger to operate in machine mode. (R/W)
\label{fielddesc:MCONTROLU}\item [u] Set this for enabling selected trigger to operate in user mode. (R/W)
\label{fielddesc:MCONTROLEXECUTE}\item [execute] Set this for configuring the selected trigger to fire right before an instruction with matching virtual address is executed by the CPU. (R/W)
\label{fielddesc:MCONTROLSTORE}\item [store] Set this for configuring the selected trigger to fire right before a store operation with matching data address is executed by the CPU. (R/W)
\label{fielddesc:MCONTROLLOAD}\item [load] Set this for configuring the selected trigger to fire right before a load operation with matching data address is executed by the CPU. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{maddress}{0x7A2}\label{regdesc:MADDRESS}
\regfield{maddress}{32}{0}{{0x00000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:MADDRESS}\item [maddress] Configures the address used by the selected trigger when performing match operation. This is decoded as NAPOT when \hyperref[fielddesc:MCONTROLMATCH]{match}=1 in \hyperref[regdesc:MCONTROL]{mcontrol}. (R/W)
\end{reglist}\end{regdesc}
\end{register}
