\begin{register}{H}{USB\_SERIAL\_JTAG\_EP1\_REG}{0x0000}\label{regdesc:USBSERIALJTAGEP1REG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{USB\_SERIAL\_JTAG\_RDWR\_BYTE}{8}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGRDWRBYTE}\item [USB\_SERIAL\_JTAG\_RDWR\_BYTE] Write and read byte data to/from UART Tx/Rx FIFO through this field. When USB\_SERIAL\_JTAG\_SERIAL\_IN\_EMPTY\_INT is set  then user can write data (up to 64 bytes) into UART Tx FIFO. When USB\_SERIAL\_JTAG\_SERIAL\_OUT\_RECV\_PKT\_INT is set, user can check USB\_SERIAL\_JTAG\_OUT\_EP1\_WR\_ADDR and USB\_SERIAL\_JTAG\_OUT\_EP1\_RD\_ADDR to know how many data is received, then read that amount of data from UART Rx FIFO. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_CONF0\_REG}{0x0018}\label{regdesc:USBSERIALJTAGCONF0REG}
\regfield{(reserved)}{17}{15}{00000000000000000}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_USB\_PAD\_ENABLE}}{1}{14}{{1}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_PULLUP\_VALUE}}{1}{13}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_DM\_PULLDOWN}}{1}{12}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_DM\_PULLUP}}{1}{11}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_DP\_PULLDOWN}}{1}{10}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_DP\_PULLUP}}{1}{9}{{1}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_PAD\_PULL\_OVERRIDE}}{1}{8}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_VREF\_OVERRIDE}}{1}{7}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_VREFH}}{2}{5}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_VREFL}}{2}{3}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_EXCHG\_PINS}}{1}{2}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_EXCHG\_PINS\_OVERRIDE}}{1}{1}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_PHY\_SEL}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGPHYSEL}\item [USB\_SERIAL\_JTAG\_PHY\_SEL] Select internal/external PHY. 1'b0: internal PHY, 1'b1: external PHY. (R/W)
\label{fielddesc:USBSERIALJTAGEXCHGPINSOVERRIDE}\item [USB\_SERIAL\_JTAG\_EXCHG\_PINS\_OVERRIDE] Enable software control USB D+ D- exchange. (R/W)
\label{fielddesc:USBSERIALJTAGEXCHGPINS}\item [USB\_SERIAL\_JTAG\_EXCHG\_PINS] USB D+ D- exchange (R/W)
\label{fielddesc:USBSERIALJTAGVREFL}\item [USB\_SERIAL\_JTAG\_VREFL] Control single-end input high threshold. 1.76 V to 2 V, step 80 mV. (R/W)
\label{fielddesc:USBSERIALJTAGVREFH}\item [USB\_SERIAL\_JTAG\_VREFH] Control single-end input low threshold. 0.8 V to 1.04 V, step 80 mV. (R/W)
\label{fielddesc:USBSERIALJTAGVREFOVERRIDE}\item [USB\_SERIAL\_JTAG\_VREF\_OVERRIDE] Enable software control input threshold. (R/W)
\label{fielddesc:USBSERIALJTAGPADPULLOVERRIDE}\item [USB\_SERIAL\_JTAG\_PAD\_PULL\_OVERRIDE] Enable software control USB D+ D- pull-up pull-down. (R/W)
\label{fielddesc:USBSERIALJTAGDPPULLUP}\item [USB\_SERIAL\_JTAG\_DP\_PULLUP] Control USB D+ pull-up. (R/W)
\label{fielddesc:USBSERIALJTAGDPPULLDOWN}\item [USB\_SERIAL\_JTAG\_DP\_PULLDOWN] Control USB D+ pull-down. (R/W)
\label{fielddesc:USBSERIALJTAGDMPULLUP}\item [USB\_SERIAL\_JTAG\_DM\_PULLUP] Control USB D- pull-up. (R/W)
\label{fielddesc:USBSERIALJTAGDMPULLDOWN}\item [USB\_SERIAL\_JTAG\_DM\_PULLDOWN] Control USB D- pull-down. (R/W)
\label{fielddesc:USBSERIALJTAGPULLUPVALUE}\item [USB\_SERIAL\_JTAG\_PULLUP\_VALUE] Control pull-up value. 0: 2.2 K; 1: 1.1 K. (R/W)
\label{fielddesc:USBSERIALJTAGUSBPADENABLE}\item [USB\_SERIAL\_JTAG\_USB\_PAD\_ENABLE] Enable USB pad function. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_TEST\_REG}{0x001C}\label{regdesc:USBSERIALJTAGTESTREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{USB\_SERIAL\_JTAG\_TEST\_TX\_DM}{1}{3}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_TEST\_TX\_DP}{1}{2}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_TEST\_USB\_OE}{1}{1}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_TEST\_ENABLE}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGTESTENABLE}\item [USB\_SERIAL\_JTAG\_TEST\_ENABLE] Enable test of the USB pad. (R/W)
\label{fielddesc:USBSERIALJTAGTESTUSBOE}\item [USB\_SERIAL\_JTAG\_TEST\_USB\_OE] USB pad output enable in test. (R/W)
\label{fielddesc:USBSERIALJTAGTESTTXDP}\item [USB\_SERIAL\_JTAG\_TEST\_TX\_DP] USB D+ tx value in test. (R/W)
\label{fielddesc:USBSERIALJTAGTESTTXDM}\item [USB\_SERIAL\_JTAG\_TEST\_TX\_DM] USB D- tx value in test. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_MISC\_CONF\_REG}{0x0044}\label{regdesc:USBSERIALJTAGMISCCONFREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{USB\_SERIAL\_JTAG\_CLK\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGCLKEN}\item [USB\_SERIAL\_JTAG\_CLK\_EN] 1'h1: Force clock on for register. 1'h0: Support clock only when application writes registers. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_MEM\_CONF\_REG}{0x0048}\label{regdesc:USBSERIALJTAGMEMCONFREG}
\regfield{(reserved)}{30}{2}{000000000000000000000000000000}%
\regfield{USB\_SERIAL\_JTAG\_USB\_MEM\_CLK\_EN}{1}{1}{{1}}%
\regfield{USB\_SERIAL\_JTAG\_USB\_MEM\_PD}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGUSBMEMPD}\item [USB\_SERIAL\_JTAG\_USB\_MEM\_PD] Set to power down USB memory. (R/W)
\label{fielddesc:USBSERIALJTAGUSBMEMCLKEN}\item [USB\_SERIAL\_JTAG\_USB\_MEM\_CLK\_EN] Set to force clock-on for USB memory. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_EP1\_CONF\_REG}{0x0004}\label{regdesc:USBSERIALJTAGEP1CONFREG}
\regfield{\rotatebox{15}{(reserved)}}{29}{3}{00000000000000000000000000000}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_SERIAL\_OUT\_EP\_DATA\_AVAIL}}{1}{2}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_SERIAL\_IN\_EP\_DATA\_FREE}}{1}{1}{{1}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_WR\_DONE}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGWRDONE}\item [USB\_SERIAL\_JTAG\_WR\_DONE] Set this bit to indicate writing byte data to UART Tx FIFO is done.  This bit then stays 0 until data in UART Tx FIFO is read by the USB Host. (WT)
\label{fielddesc:USBSERIALJTAGSERIALINEPDATAFREE}\item [USB\_SERIAL\_JTAG\_SERIAL\_IN\_EP\_DATA\_FREE] 1'b1: Indicate UART Tx FIFO is not full and data can be written into in. After writing USB\_SERIAL\_JTAG\_WR\_DONE, this will be 1'b0 until the data is sent to the USB Host. (RO)
\label{fielddesc:USBSERIALJTAGSERIALOUTEPDATAAVAIL}\item [USB\_SERIAL\_JTAG\_SERIAL\_OUT\_EP\_DATA\_AVAIL] 1'b1: Indicate there is data in UART Rx FIFO. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_JFIFO\_ST\_REG}{0x0020}\label{regdesc:USBSERIALJTAGJFIFOSTREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{USB\_SERIAL\_JTAG\_OUT\_FIFO\_RESET}{1}{9}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_IN\_FIFO\_RESET}{1}{8}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_OUT\_FIFO\_FULL}{1}{7}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_OUT\_FIFO\_EMPTY}{1}{6}{{1}}%
\regfield{USB\_SERIAL\_JTAG\_OUT\_FIFO\_CNT}{2}{4}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_IN\_FIFO\_FULL}{1}{3}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_IN\_FIFO\_EMPTY}{1}{2}{{1}}%
\regfield{USB\_SERIAL\_JTAG\_IN\_FIFO\_CNT}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGINFIFOCNT}\item [USB\_SERIAL\_JTAG\_IN\_FIFO\_CNT] JTAG in FIFO counter. (RO)
\label{fielddesc:USBSERIALJTAGINFIFOEMPTY}\item [USB\_SERIAL\_JTAG\_IN\_FIFO\_EMPTY] Set to indicate JTAG in FIFO is empty. (RO)
\label{fielddesc:USBSERIALJTAGINFIFOFULL}\item [USB\_SERIAL\_JTAG\_IN\_FIFO\_FULL] Set to indicate JTAG in FIFO is full. (RO)
\label{fielddesc:USBSERIALJTAGOUTFIFOCNT}\item [USB\_SERIAL\_JTAG\_OUT\_FIFO\_CNT] JTAT out FIFO counter. (RO)
\label{fielddesc:USBSERIALJTAGOUTFIFOEMPTY}\item [USB\_SERIAL\_JTAG\_OUT\_FIFO\_EMPTY] Set to indicate JTAG out FIFO is empty. (RO)
\label{fielddesc:USBSERIALJTAGOUTFIFOFULL}\item [USB\_SERIAL\_JTAG\_OUT\_FIFO\_FULL] Set to indicate JTAG out FIFO is full. (RO)
\label{fielddesc:USBSERIALJTAGINFIFORESET}\item [USB\_SERIAL\_JTAG\_IN\_FIFO\_RESET] Write 1 to reset JTAG in FIFO. (R/W)
\label{fielddesc:USBSERIALJTAGOUTFIFORESET}\item [USB\_SERIAL\_JTAG\_OUT\_FIFO\_RESET] Write 1 to reset JTAG out FIFO. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_FRAM\_NUM\_REG}{0x0024}\label{regdesc:USBSERIALJTAGFRAMNUMREG}
\regfield{(reserved)}{21}{11}{000000000000000000000}%
\regfield{USB\_SERIAL\_JTAG\_SOF\_FRAME\_INDEX}{11}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGSOFFRAMEINDEX}\item [USB\_SERIAL\_JTAG\_SOF\_FRAME\_INDEX] Frame index of received SOF frame. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_IN\_EP0\_ST\_REG}{0x0028}\label{regdesc:USBSERIALJTAGINEP0STREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{USB\_SERIAL\_JTAG\_IN\_EP0\_RD\_ADDR}{7}{9}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_IN\_EP0\_WR\_ADDR}{7}{2}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_IN\_EP0\_STATE}{2}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGINEP0STATE}\item [USB\_SERIAL\_JTAG\_IN\_EP0\_STATE] State of IN Endpoint 0. (RO)
\label{fielddesc:USBSERIALJTAGINEP0WRADDR}\item [USB\_SERIAL\_JTAG\_IN\_EP0\_WR\_ADDR] Write data address of IN endpoint 0. (RO)
\label{fielddesc:USBSERIALJTAGINEP0RDADDR}\item [USB\_SERIAL\_JTAG\_IN\_EP0\_RD\_ADDR] Read data address of IN endpoint 0. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_IN\_EP1\_ST\_REG}{0x002C}\label{regdesc:USBSERIALJTAGINEP1STREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{USB\_SERIAL\_JTAG\_IN\_EP1\_RD\_ADDR}{7}{9}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_IN\_EP1\_WR\_ADDR}{7}{2}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_IN\_EP1\_STATE}{2}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGINEP1STATE}\item [USB\_SERIAL\_JTAG\_IN\_EP1\_STATE] State of IN Endpoint 1. (RO)
\label{fielddesc:USBSERIALJTAGINEP1WRADDR}\item [USB\_SERIAL\_JTAG\_IN\_EP1\_WR\_ADDR] Write data address of IN endpoint 1. (RO)
\label{fielddesc:USBSERIALJTAGINEP1RDADDR}\item [USB\_SERIAL\_JTAG\_IN\_EP1\_RD\_ADDR] Read data address of IN endpoint 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_IN\_EP2\_ST\_REG}{0x0030}\label{regdesc:USBSERIALJTAGINEP2STREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{USB\_SERIAL\_JTAG\_IN\_EP2\_RD\_ADDR}{7}{9}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_IN\_EP2\_WR\_ADDR}{7}{2}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_IN\_EP2\_STATE}{2}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGINEP2STATE}\item [USB\_SERIAL\_JTAG\_IN\_EP2\_STATE] State of IN Endpoint 2. (RO)
\label{fielddesc:USBSERIALJTAGINEP2WRADDR}\item [USB\_SERIAL\_JTAG\_IN\_EP2\_WR\_ADDR] Write data address of IN endpoint 2. (RO)
\label{fielddesc:USBSERIALJTAGINEP2RDADDR}\item [USB\_SERIAL\_JTAG\_IN\_EP2\_RD\_ADDR] Read data address of IN endpoint 2. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_IN\_EP3\_ST\_REG}{0x0034}\label{regdesc:USBSERIALJTAGINEP3STREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{USB\_SERIAL\_JTAG\_IN\_EP3\_RD\_ADDR}{7}{9}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_IN\_EP3\_WR\_ADDR}{7}{2}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_IN\_EP3\_STATE}{2}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGINEP3STATE}\item [USB\_SERIAL\_JTAG\_IN\_EP3\_STATE] State of IN Endpoint 3. (RO)
\label{fielddesc:USBSERIALJTAGINEP3WRADDR}\item [USB\_SERIAL\_JTAG\_IN\_EP3\_WR\_ADDR] Write data address of IN endpoint 3. (RO)
\label{fielddesc:USBSERIALJTAGINEP3RDADDR}\item [USB\_SERIAL\_JTAG\_IN\_EP3\_RD\_ADDR] Read data address of IN endpoint 3. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_OUT\_EP0\_ST\_REG}{0x0038}\label{regdesc:USBSERIALJTAGOUTEP0STREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{USB\_SERIAL\_JTAG\_OUT\_EP0\_RD\_ADDR}{7}{9}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_OUT\_EP0\_WR\_ADDR}{7}{2}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_OUT\_EP0\_STATE}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGOUTEP0STATE}\item [USB\_SERIAL\_JTAG\_OUT\_EP0\_STATE] State of OUT Endpoint 0. (RO)
\label{fielddesc:USBSERIALJTAGOUTEP0WRADDR}\item [USB\_SERIAL\_JTAG\_OUT\_EP0\_WR\_ADDR] Write data address of OUT Endpoint 0. When USB\_SERIAL\_JTAG\_SERIAL\_OUT\_RECV\_PKT\_INT is detected, there are USB\_SERIAL\_JTAG\_OUT\_EP0\_WR\_ADDR - 2 bytes of data in OUT EP0. (RO)
\label{fielddesc:USBSERIALJTAGOUTEP0RDADDR}\item [USB\_SERIAL\_JTAG\_OUT\_EP0\_RD\_ADDR] Read data address of OUT endpoint 0. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_OUT\_EP1\_ST\_REG}{0x003C}\label{regdesc:USBSERIALJTAGOUTEP1STREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{USB\_SERIAL\_JTAG\_OUT\_EP1\_REC\_DATA\_CNT}{7}{16}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_OUT\_EP1\_RD\_ADDR}{7}{9}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_OUT\_EP1\_WR\_ADDR}{7}{2}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_OUT\_EP1\_STATE}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGOUTEP1STATE}\item [USB\_SERIAL\_JTAG\_OUT\_EP1\_STATE] State of OUT Endpoint 1. (RO)
\label{fielddesc:USBSERIALJTAGOUTEP1WRADDR}\item [USB\_SERIAL\_JTAG\_OUT\_EP1\_WR\_ADDR] Write data address of OUT Endpoint 1. When USB\_SERIAL\_JTAG\_SERIAL\_OUT\_RECV\_PKT\_INT is detected, there are USB\_SERIAL\_JTAG\_OUT\_EP1\_WR\_ADDR - 2 bytes of data in OUT EP1. (RO)
\label{fielddesc:USBSERIALJTAGOUTEP1RDADDR}\item [USB\_SERIAL\_JTAG\_OUT\_EP1\_RD\_ADDR] Read data address of OUT endpoint 1. (RO)
\label{fielddesc:USBSERIALJTAGOUTEP1RECDATACNT}\item [USB\_SERIAL\_JTAG\_OUT\_EP1\_REC\_DATA\_CNT] Data count in OUT Endpoint 1 when one packet is received. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_OUT\_EP2\_ST\_REG}{0x0040}\label{regdesc:USBSERIALJTAGOUTEP2STREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{USB\_SERIAL\_JTAG\_OUT\_EP2\_RD\_ADDR}{7}{9}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_OUT\_EP2\_WR\_ADDR}{7}{2}{{0}}%
\regfield{USB\_SERIAL\_JTAG\_OUT\_EP2\_STATE}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGOUTEP2STATE}\item [USB\_SERIAL\_JTAG\_OUT\_EP2\_STATE] State of OUT Endpoint 2. (RO)
\label{fielddesc:USBSERIALJTAGOUTEP2WRADDR}\item [USB\_SERIAL\_JTAG\_OUT\_EP2\_WR\_ADDR] Write data address of OUT endpoint 2. When USB\_SERIAL\_JTAG\_SERIAL\_OUT\_RECV\_PKT\_INT is detected, there are USB\_SERIAL\_JTAG\_OUT\_EP2\_WR\_ADDR - 2 bytes of data in OUT EP2. (RO)
\label{fielddesc:USBSERIALJTAGOUTEP2RDADDR}\item [USB\_SERIAL\_JTAG\_OUT\_EP2\_RD\_ADDR] Read data address of OUT endpoint 2. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_INT\_RAW\_REG}{0x0008}\label{regdesc:USBSERIALJTAGINTRAWREG}
\regfield{\rotatebox{15}{(reserved)}}{20}{12}{00000000000000000000}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_OUT\_EP2\_ZERO\_PAYLOAD\_INT\_RAW}}{1}{11}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_OUT\_EP1\_ZERO\_PAYLOAD\_INT\_RAW}}{1}{10}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_USB\_BUS\_RESET\_INT\_RAW}}{1}{9}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_IN\_TOKEN\_REC\_IN\_EP1\_INT\_RAW}}{1}{8}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_STUFF\_ERR\_INT\_RAW}}{1}{7}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_CRC16\_ERR\_INT\_RAW}}{1}{6}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_CRC5\_ERR\_INT\_RAW}}{1}{5}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_PID\_ERR\_INT\_RAW}}{1}{4}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_SERIAL\_IN\_EMPTY\_INT\_RAW}}{1}{3}{{1}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_SERIAL\_OUT\_RECV\_PKT\_INT\_RAW}}{1}{2}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_SOF\_INT\_RAW}}{1}{1}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_JTAG\_IN\_FLUSH\_INT\_RAW}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGJTAGINFLUSHINTRAW}\item [USB\_SERIAL\_JTAG\_JTAG\_IN\_FLUSH\_INT\_RAW] The raw interrupt bit turns to high level when a flush command is received for IN endpoint 2 of JTAG. (R/WTC/SS)
\label{fielddesc:USBSERIALJTAGSOFINTRAW}\item [USB\_SERIAL\_JTAG\_SOF\_INT\_RAW] The raw interrupt bit turns to high level when a SOF frame is received. (R/WTC/SS)
\label{fielddesc:USBSERIALJTAGSERIALOUTRECVPKTINTRAW}\item [USB\_SERIAL\_JTAG\_SERIAL\_OUT\_RECV\_PKT\_INT\_RAW] The raw interrupt bit turns to high level when the Serial Port OUT Endpoint received one packet. (R/WTC/SS)
\label{fielddesc:USBSERIALJTAGSERIALINEMPTYINTRAW}\item [USB\_SERIAL\_JTAG\_SERIAL\_IN\_EMPTY\_INT\_RAW] The raw interrupt bit turns to high level when the Serial Port IN Endpoint is empty. (R/WTC/SS)
\label{fielddesc:USBSERIALJTAGPIDERRINTRAW}\item [USB\_SERIAL\_JTAG\_PID\_ERR\_INT\_RAW] The raw interrupt bit turns to high level when a PID error is detected. (R/WTC/SS)
\label{fielddesc:USBSERIALJTAGCRC5ERRINTRAW}\item [USB\_SERIAL\_JTAG\_CRC5\_ERR\_INT\_RAW] The raw interrupt bit turns to high level when a CRC5 error is detected. (R/WTC/SS)
\label{fielddesc:USBSERIALJTAGCRC16ERRINTRAW}\item [USB\_SERIAL\_JTAG\_CRC16\_ERR\_INT\_RAW] The raw interrupt bit turns to high level when a CRC16 error is detected. (R/WTC/SS)
\label{fielddesc:USBSERIALJTAGSTUFFERRINTRAW}\item [USB\_SERIAL\_JTAG\_STUFF\_ERR\_INT\_RAW] The raw interrupt bit turns to high level when a bit stuffing error is detected. (R/WTC/SS)
\label{fielddesc:USBSERIALJTAGINTOKENRECINEP1INTRAW}\item [USB\_SERIAL\_JTAG\_IN\_TOKEN\_REC\_IN\_EP1\_INT\_RAW] The raw interrupt bit turns to high level when an IN token for IN endpoint 1 is received. (R/WTC/SS)
\label{fielddesc:USBSERIALJTAGUSBBUSRESETINTRAW}\item [USB\_SERIAL\_JTAG\_USB\_BUS\_RESET\_INT\_RAW] The raw interrupt bit turns to high level when a USB bus reset is detected. (R/WTC/SS)
\label{fielddesc:USBSERIALJTAGOUTEP1ZEROPAYLOADINTRAW}\item [USB\_SERIAL\_JTAG\_OUT\_EP1\_ZERO\_PAYLOAD\_INT\_RAW] The raw interrupt bit turns to high level when OUT endpoint 1 received packet with zero payload. (R/WTC/SS)
\label{fielddesc:USBSERIALJTAGOUTEP2ZEROPAYLOADINTRAW}\item [USB\_SERIAL\_JTAG\_OUT\_EP2\_ZERO\_PAYLOAD\_INT\_RAW] The raw interrupt bit turns to high level when OUT endpoint 2 received packet with zero payload. (R/WTC/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_INT\_ST\_REG}{0x000C}\label{regdesc:USBSERIALJTAGINTSTREG}
\regfield{\rotatebox{15}{(reserved)}}{20}{12}{00000000000000000000}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_OUT\_EP2\_ZERO\_PAYLOAD\_INT\_ST}}{1}{11}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_OUT\_EP1\_ZERO\_PAYLOAD\_INT\_ST}}{1}{10}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_USB\_BUS\_RESET\_INT\_ST}}{1}{9}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_IN\_TOKEN\_REC\_IN\_EP1\_INT\_ST}}{1}{8}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_STUFF\_ERR\_INT\_ST}}{1}{7}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_CRC16\_ERR\_INT\_ST}}{1}{6}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_CRC5\_ERR\_INT\_ST}}{1}{5}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_PID\_ERR\_INT\_ST}}{1}{4}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_SERIAL\_IN\_EMPTY\_INT\_ST}}{1}{3}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_SERIAL\_OUT\_RECV\_PKT\_INT\_ST}}{1}{2}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_SOF\_INT\_ST}}{1}{1}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_JTAG\_IN\_FLUSH\_INT\_ST}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGJTAGINFLUSHINTST}\item [USB\_SERIAL\_JTAG\_JTAG\_IN\_FLUSH\_INT\_ST] The raw interrupt status bit for the USB\_SERIAL\_JTAG\_JTAG\_IN\_FLUSH\_INT interrupt. (RO)
\label{fielddesc:USBSERIALJTAGSOFINTST}\item [USB\_SERIAL\_JTAG\_SOF\_INT\_ST] The raw interrupt status bit for the USB\_SERIAL\_JTAG\_SOF\_INT interrupt. (RO)
\label{fielddesc:USBSERIALJTAGSERIALOUTRECVPKTINTST}\item [USB\_SERIAL\_JTAG\_SERIAL\_OUT\_RECV\_PKT\_INT\_ST] The raw interrupt status bit for the USB\_SERIAL\_JTAG\_SERIAL\_OUT\_RECV\_PKT\_INT interrupt. (RO)
\label{fielddesc:USBSERIALJTAGSERIALINEMPTYINTST}\item [USB\_SERIAL\_JTAG\_SERIAL\_IN\_EMPTY\_INT\_ST] The raw interrupt status bit for the USB\_SERIAL\_JTAG\_SERIAL\_IN\_EMPTY\_INT interrupt. (RO)
\label{fielddesc:USBSERIALJTAGPIDERRINTST}\item [USB\_SERIAL\_JTAG\_PID\_ERR\_INT\_ST] The raw interrupt status bit for the USB\_SERIAL\_JTAG\_PID\_ERR\_INT interrupt. (RO)
\label{fielddesc:USBSERIALJTAGCRC5ERRINTST}\item [USB\_SERIAL\_JTAG\_CRC5\_ERR\_INT\_ST] The raw interrupt status bit for the USB\_SERIAL\_JTAG\_CRC5\_ERR\_INT interrupt. (RO)
\label{fielddesc:USBSERIALJTAGCRC16ERRINTST}\item [USB\_SERIAL\_JTAG\_CRC16\_ERR\_INT\_ST] The raw interrupt status bit for the USB\_SERIAL\_JTAG\_CRC16\_ERR\_INT interrupt. (RO)
\label{fielddesc:USBSERIALJTAGSTUFFERRINTST}\item [USB\_SERIAL\_JTAG\_STUFF\_ERR\_INT\_ST] The raw interrupt status bit for the USB\_SERIAL\_JTAG\_STUFF\_ERR\_INT interrupt. (RO)
\label{fielddesc:USBSERIALJTAGINTOKENRECINEP1INTST}\item [USB\_SERIAL\_JTAG\_IN\_TOKEN\_REC\_IN\_EP1\_INT\_ST] The raw interrupt status bit for the USB\_SERIAL\_JTAG\_IN\_TOKEN\_REC\_IN\_EP1\_INT interrupt. (RO)
\label{fielddesc:USBSERIALJTAGUSBBUSRESETINTST}\item [USB\_SERIAL\_JTAG\_USB\_BUS\_RESET\_INT\_ST] The raw interrupt status bit for the USB\_SERIAL\_JTAG\_USB\_BUS\_RESET\_INT interrupt. (RO)
\label{fielddesc:USBSERIALJTAGOUTEP1ZEROPAYLOADINTST}\item [USB\_SERIAL\_JTAG\_OUT\_EP1\_ZERO\_PAYLOAD\_INT\_ST] The raw interrupt status bit for the USB\_SERIAL\_JTAG\_OUT\_EP1\_ZERO\_PAYLOAD\_INT interrupt. (RO)
\label{fielddesc:USBSERIALJTAGOUTEP2ZEROPAYLOADINTST}\item [USB\_SERIAL\_JTAG\_OUT\_EP2\_ZERO\_PAYLOAD\_INT\_ST] The raw interrupt status bit for the USB\_SERIAL\_JTAG\_OUT\_EP2\_ZERO\_PAYLOAD\_INT interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_INT\_ENA\_REG}{0x0010}\label{regdesc:USBSERIALJTAGINTENAREG}
\regfield{\rotatebox{15}{(reserved)}}{20}{12}{00000000000000000000}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_OUT\_EP2\_ZERO\_PAYLOAD\_INT\_ENA}}{1}{11}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_OUT\_EP1\_ZERO\_PAYLOAD\_INT\_ENA}}{1}{10}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_USB\_BUS\_RESET\_INT\_ENA}}{1}{9}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_IN\_TOKEN\_REC\_IN\_EP1\_INT\_ENA}}{1}{8}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_STUFF\_ERR\_INT\_ENA}}{1}{7}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_CRC16\_ERR\_INT\_ENA}}{1}{6}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_CRC5\_ERR\_INT\_ENA}}{1}{5}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_PID\_ERR\_INT\_ENA}}{1}{4}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_SERIAL\_IN\_EMPTY\_INT\_ENA}}{1}{3}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_SERIAL\_OUT\_RECV\_PKT\_INT\_ENA}}{1}{2}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_SOF\_INT\_ENA}}{1}{1}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_JTAG\_IN\_FLUSH\_INT\_ENA}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGJTAGINFLUSHINTENA}\item [USB\_SERIAL\_JTAG\_JTAG\_IN\_FLUSH\_INT\_ENA] The interrupt enable bit for the USB\_SERIAL\_JTAG\_JTAG\_IN\_FLUSH\_INT interrupt. (R/W)
\label{fielddesc:USBSERIALJTAGSOFINTENA}\item [USB\_SERIAL\_JTAG\_SOF\_INT\_ENA] The interrupt enable bit for the USB\_SERIAL\_JTAG\_SOF\_INT interrupt. (R/W)
\label{fielddesc:USBSERIALJTAGSERIALOUTRECVPKTINTENA}\item [USB\_SERIAL\_JTAG\_SERIAL\_OUT\_RECV\_PKT\_INT\_ENA] The interrupt enable bit for the USB\_SERIAL\_JTAG\_SERIAL\_OUT\_RECV\_PKT\_INT interrupt. (R/W)
\label{fielddesc:USBSERIALJTAGSERIALINEMPTYINTENA}\item [USB\_SERIAL\_JTAG\_SERIAL\_IN\_EMPTY\_INT\_ENA] The interrupt enable bit for the USB\_SERIAL\_JTAG\_SERIAL\_IN\_EMPTY\_INT interrupt. (R/W)
\label{fielddesc:USBSERIALJTAGPIDERRINTENA}\item [USB\_SERIAL\_JTAG\_PID\_ERR\_INT\_ENA] The interrupt enable bit for the USB\_SERIAL\_JTAG\_PID\_ERR\_INT interrupt. (R/W)
\label{fielddesc:USBSERIALJTAGCRC5ERRINTENA}\item [USB\_SERIAL\_JTAG\_CRC5\_ERR\_INT\_ENA] The interrupt enable bit for the USB\_SERIAL\_JTAG\_CRC5\_ERR\_INT interrupt. (R/W)
\label{fielddesc:USBSERIALJTAGCRC16ERRINTENA}\item [USB\_SERIAL\_JTAG\_CRC16\_ERR\_INT\_ENA] The interrupt enable bit for the USB\_SERIAL\_JTAG\_CRC16\_ERR\_INT interrupt. (R/W)
\label{fielddesc:USBSERIALJTAGSTUFFERRINTENA}\item [USB\_SERIAL\_JTAG\_STUFF\_ERR\_INT\_ENA] The interrupt enable bit for the USB\_SERIAL\_JTAG\_STUFF\_ERR\_INT interrupt. (R/W)
\label{fielddesc:USBSERIALJTAGINTOKENRECINEP1INTENA}\item [USB\_SERIAL\_JTAG\_IN\_TOKEN\_REC\_IN\_EP1\_INT\_ENA] The interrupt enable bit for the USB\_SERIAL\_JTAG\_IN\_TOKEN\_REC\_IN\_EP1\_INT interrupt. (R/W)
\label{fielddesc:USBSERIALJTAGUSBBUSRESETINTENA}\item [USB\_SERIAL\_JTAG\_USB\_BUS\_RESET\_INT\_ENA] The interrupt enable bit for the USB\_SERIAL\_JTAG\_USB\_BUS\_RESET\_INT interrupt. (R/W)
\label{fielddesc:USBSERIALJTAGOUTEP1ZEROPAYLOADINTENA}\item [USB\_SERIAL\_JTAG\_OUT\_EP1\_ZERO\_PAYLOAD\_INT\_ENA] The interrupt enable bit for the USB\_SERIAL\_JTAG\_OUT\_EP1\_ZERO\_PAYLOAD\_INT interrupt. (R/W)
\label{fielddesc:USBSERIALJTAGOUTEP2ZEROPAYLOADINTENA}\item [USB\_SERIAL\_JTAG\_OUT\_EP2\_ZERO\_PAYLOAD\_INT\_ENA] The interrupt enable bit for the USB\_SERIAL\_JTAG\_OUT\_EP2\_ZERO\_PAYLOAD\_INT interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_INT\_CLR\_REG}{0x0014}\label{regdesc:USBSERIALJTAGINTCLRREG}
\regfield{\rotatebox{15}{(reserved)}}{20}{12}{00000000000000000000}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_OUT\_EP2\_ZERO\_PAYLOAD\_INT\_CLR}}{1}{11}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_OUT\_EP1\_ZERO\_PAYLOAD\_INT\_CLR}}{1}{10}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_USB\_BUS\_RESET\_INT\_CLR}}{1}{9}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_IN\_TOKEN\_REC\_IN\_EP1\_INT\_CLR}}{1}{8}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_STUFF\_ERR\_INT\_CLR}}{1}{7}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_CRC16\_ERR\_INT\_CLR}}{1}{6}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_CRC5\_ERR\_INT\_CLR}}{1}{5}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_PID\_ERR\_INT\_CLR}}{1}{4}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_SERIAL\_IN\_EMPTY\_INT\_CLR}}{1}{3}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_SERIAL\_OUT\_RECV\_PKT\_INT\_CLR}}{1}{2}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_SOF\_INT\_CLR}}{1}{1}{{0}}%
\regfield{\rotatebox{15}{USB\_SERIAL\_JTAG\_JTAG\_IN\_FLUSH\_INT\_CLR}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGJTAGINFLUSHINTCLR}\item [USB\_SERIAL\_JTAG\_JTAG\_IN\_FLUSH\_INT\_CLR] Set this bit to clear the USB\_SERIAL\_JTAG\_JTAG\_IN\_FLUSH\_INT interrupt. (WT)
\label{fielddesc:USBSERIALJTAGSOFINTCLR}\item [USB\_SERIAL\_JTAG\_SOF\_INT\_CLR] Set this bit to clear the USB\_SERIAL\_JTAG\_JTAG\_SOF\_INT interrupt. (WT)
\label{fielddesc:USBSERIALJTAGSERIALOUTRECVPKTINTCLR}\item [USB\_SERIAL\_JTAG\_SERIAL\_OUT\_RECV\_PKT\_INT\_CLR] Set this bit to clear the USB\_SERIAL\_JTAG\_SERIAL\_OUT\_RECV\_PKT\_INT interrupt. (WT)
\label{fielddesc:USBSERIALJTAGSERIALINEMPTYINTCLR}\item [USB\_SERIAL\_JTAG\_SERIAL\_IN\_EMPTY\_INT\_CLR] Set this bit to clear the USB\_SERIAL\_JTAG\_SERIAL\_IN\_EMPTY\_INT interrupt. (WT)
\label{fielddesc:USBSERIALJTAGPIDERRINTCLR}\item [USB\_SERIAL\_JTAG\_PID\_ERR\_INT\_CLR] Set this bit to clear the USB\_SERIAL\_JTAG\_PID\_ERR\_INT interrupt. (WT)
\label{fielddesc:USBSERIALJTAGCRC5ERRINTCLR}\item [USB\_SERIAL\_JTAG\_CRC5\_ERR\_INT\_CLR] Set this bit to clear the USB\_SERIAL\_JTAG\_CRC5\_ERR\_INT interrupt. (WT)
\label{fielddesc:USBSERIALJTAGCRC16ERRINTCLR}\item [USB\_SERIAL\_JTAG\_CRC16\_ERR\_INT\_CLR] Set this bit to clear the USB\_SERIAL\_JTAG\_CRC16\_ERR\_INT interrupt. (WT)
\label{fielddesc:USBSERIALJTAGSTUFFERRINTCLR}\item [USB\_SERIAL\_JTAG\_STUFF\_ERR\_INT\_CLR] Set this bit to clear the USB\_SERIAL\_JTAG\_STUFF\_ERR\_INT interrupt. (WT)
\label{fielddesc:USBSERIALJTAGINTOKENRECINEP1INTCLR}\item [USB\_SERIAL\_JTAG\_IN\_TOKEN\_REC\_IN\_EP1\_INT\_CLR] Set this bit to clear the USB\_SERIAL\_JTAG\_IN\_TOKEN\_IN\_EP1\_INT interrupt. (WT)
\label{fielddesc:USBSERIALJTAGUSBBUSRESETINTCLR}\item [USB\_SERIAL\_JTAG\_USB\_BUS\_RESET\_INT\_CLR] Set this bit to clear the USB\_SERIAL\_JTAG\_USB\_BUS\_RESET\_INT interrupt. (WT)
\label{fielddesc:USBSERIALJTAGOUTEP1ZEROPAYLOADINTCLR}\item [USB\_SERIAL\_JTAG\_OUT\_EP1\_ZERO\_PAYLOAD\_INT\_CLR] Set this bit to clear the USB\_SERIAL\_JTAG\_OUT\_EP1\_ZERO\_PAYLOAD\_INT interrupt. (WT)
\label{fielddesc:USBSERIALJTAGOUTEP2ZEROPAYLOADINTCLR}\item [USB\_SERIAL\_JTAG\_OUT\_EP2\_ZERO\_PAYLOAD\_INT\_CLR] Set this bit to clear the USB\_SERIAL\_JTAG\_OUT\_EP2\_ZERO\_PAYLOAD\_INT interrupt. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{USB\_SERIAL\_JTAG\_DATE\_REG}{0x0080}\label{regdesc:USBSERIALJTAGDATEREG}
\regfield{USB\_SERIAL\_JTAG\_DATE}{32}{0}{{0x2007300}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:USBSERIALJTAGDATE}\item [USB\_SERIAL\_JTAG\_DATE] Version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}
