\begin{longtable}[c]{|l|m{11cm}|}
    \caption{Shift Instructions}
    \label{tab:pie-shift-instructions}\\
    \hline
    \rowcolor{lightgray}
    \textbf{Instructions} & \textbf{Description} \\\hline
    \endfirsthead
    \rowcolor{lightgray}
    \textbf{Instructions} & \textbf{Description} \\\hline
    \endhead
    \endfoot
    
    \hyperref[instruction:EESRCQ]{EE.SRC.Q} & Perform logical right-shift on the spliced 16-byte data, and the shift value is determined by the SAR\_BYTE register.
    \\\hline
    \hyperref[instruction:EESRCQQUP]{EE.SRC.Q.QUP} & Perform logical right-shift on the spliced 16-byte data, and the shift value is determined by the SAR\_BYTE register. Meanwhile, the higher 8-byte data is saved.
    \\\hline
    \hyperref[instruction:EESRCQLDXP]{EE.SRC.Q.LD.XP} & Perform logical right-shift on the spliced 16-byte data, and the shift value is determined by the SAR\_BYTE register. At the same time, read 16-byte data from memory and add a register value to the read address.
    \\\hline
    \hyperref[instruction:EESRCQLDIP]{EE.SRC.Q.LD.IP} & Perform logical right-shift on the spliced 16-byte data, and the shift value is determined by the SAR\_BYTE register. At the same time, read 16-byte data from memory and add an immediate number to the read address.
    \\\hline
    \hyperref[instruction:EESLCI2Q]{EE.SLCI.2Q} & Perform logical left-shift on the spliced 16-byte data, and the shift value is determined by the immediate value.
    \\\hline
    \hyperref[instruction:EESLCXXP2Q]{EE.SLCXXP.2Q} & Perform logical left-shift on the spliced 16-byte data, and the shift value is determined by the value in the AR register.
    \\\hline
    \hyperref[instruction:EESRCI2Q]{EE.SRCI.2Q} & Perform logical right-shift on the spliced 16-byte data, and the shift value is determined by the immediate value.
    \\\hline
    \hyperref[instruction:EESRCXXP2Q]{EE.SRCXXP.2Q} & Perform logical right-shift on the spliced 16-byte data, and the shift value is determined by the value in the AR register.
    \\\hline
    \hyperref[instruction:EESRCQ128STINCP]{EE.SRCQ.128.ST.INCP} & Perform logical right-shift on the spliced 16-byte data, which will be written to memory after the shift.
    \\\hline
    \hyperref[instruction:EEVSR32]{EE.VSR.32} & Perform vector arithmetic right-shift on the 4-byte data.
    \\\hline
    \hyperref[instruction:EEVSL32]{EE.VSL.32} & Perform vector arithmetic left-shift on the 4-byte data.
    \\\hline
\end{longtable}