\begin{longtable}[c]{|l|m{11cm}|}
    \caption{Comparison Instructions}
    \label{tab:pie-comparison-instructions}\\
    \hline
    \rowcolor{lightgray}
    \textbf{Instructions} & \textbf{Description} \\\hline
    \endfirsthead
    \rowcolor{lightgray}
    \textbf{Instructions} & \textbf{Description} \\\hline
    \endhead
    \endfoot
    
    \hyperref[instruction:EEVMAXS8]{EE.VMAX.S[8/16/32]} & Take the larger value between the two 1-byte/2-byte/4-byte values.
    \\\hline
    \hyperref[instruction:EEVMAXS8LDINCP]{EE.VMAX.S[8/16/32].LD.INCP} & Take the larger value between the two 1-byte/2-byte/4-byte values, and read 16-byte data from memory at the same time.
    \\\hline
    \hyperref[instruction:EEVMAXS8STINCP]{EE.VMAX.S[8/16/32].ST.INCP} & Take the larger value between the two 1-byte/2-byte/4-byte values, and write 16-byte data to memory at the same time.
    \\\hline
    \hyperref[instruction:EEVMINS8]{EE.VMIN.S[8/16/32]} & Take the smaller value between the two 1-byte/2-byte/4-byte values.
    \\\hline
    \hyperref[instruction:EEVMINS8LDINCP]{EE.VMIN.S[8/16/32].LD.INCP} & Take the smaller value between the two 1-byte/2-byte/4-byte values, and read 16-byte data from memory at the same time.
    \\\hline
    \hyperref[instruction:EEVMINS8STINCP]{EE.VMIN.S[8/16/32].ST.INCP} & Take the smaller value between the two 1-byte/2-byte/4-byte values, and write 16-byte data to memory at the same time.
    \\\hline
    \hyperref[instruction:EEVCMPEQS8]{EE.VCMP.EQ.S[8/16/32]} & Compare two 1-byte/2-byte/4-byte values, set all bits to 1 when the two values are equal, or set all bits to 0 when they are not equal.
    \\\hline
    \hyperref[instruction:EEVCMPLTS8]{EE.VCMP.LT.S[8/16/32]} & Compare two 1-byte/2-byte/4-byte values, set all bits to 1 when the former value is smaller than the latter one, or set them to 0 otherwise.
    \\\hline
    \hyperref[instruction:EEVCMPGTS8]{EE.VCMP.GT.S[8/16/32]} & Compare two 1-byte/2-byte/4-byte values, set all bits to 1 when the former value is larger than the latter one, or set them to 0 otherwise.
    \\\hline
\end{longtable}