\begin{longtable}[c]{|l|m{9cm}|}
    \caption{Vector Multiplication Accumulation Instructions}
    \label{tab:pie-mula-instructions}\\
    \hline
    \rowcolor{lightgray}
    \textbf{Instructions} & \textbf{Description} \\\hline
    \endfirsthead
    \rowcolor{lightgray}
    \textbf{Instructions} & \textbf{Description} \\\hline
    \endhead
    \endfoot
    
    \hyperref[instruction:EEVMULASU8ACCX]{EE.VMULAS.[U/S][8/16].ACCX} & Perform vector multiplication accumulation to signed/unsigned data in 1-byte/2-byte segment, and store the result to the ACCX register temporarily.
    \\\hline
    \hyperref[instruction:EEVMULASU8ACCXLDIP]{EE.VMULAS.[U/S][8/16].ACCX.LD.IP} & Perform vector multiplication accumulation to signed/unsigned data in 1-byte/2-byte segment, and store the result to the ACCX register temporarily, then read 16-byte data from memory. Add immediate to address register.
    \\\hline
    \hyperref[instruction:EEVMULASU8ACCXLDXP]{EE.VMULAS.[U/S][8/16].ACCX.LD.XP} & Perform vector multiplication accumulation to signed/unsigned data in 1-byte/2-byte segment, and store the result to the ACCX register temporarily, then read 16-byte data from memory. Add the value of AR register to address register.
    \\\hline
    \hyperref[instruction:EEVMULASU8ACCXLDIPQUP]{EE.VMULAS.[U/S][8/16].ACCX.LD.IP.QUP} & Perform vector multiplication accumulation to signed/unsigned data in 1-byte/2-byte segment, and store the result to the ACCX register temporarily. Then read 16-byte data from memory and output a 16-byte aligned data. Add immediate to address register.
    \\\hline
    \hyperref[instruction:EEVMULASU8ACCXLDXPQUP]{EE.VMULAS.[U/S][8/16].ACCX.LD.XP.QUP} & Perform vector multiplication accumulation to signed/unsigned data in 1-byte/2-byte segment, and store the result to the ACCX register temporarily. Then read 16-byte data from memory and output a 16-byte aligned data. Add the value of AR register to address register.
    \\\hline
    \hyperref[instruction:EEVMULASU8QACC]{EE.VMULAS.[U/S][8/16].QACC} & Perform vector multiplication operation on signed/unsigned data in 1-byte/2-byte segment, and accumulate the results to corresponding bit segments in QACC\_H and QACC\_L registers.
    \\\hline
    \hyperref[instruction:EEVMULASU8QACCLDIP]{EE.VMULAS.[U/S][8/16].QACC.LD.IP} & Perform vector multiplication operation on signed/unsigned data in 1-byte/2-byte segment, and accumulate the results to corresponding bit segments in QACC\_H and QACC\_L registers, then read 16-byte data from memory. Add immediate to address register.
    \\\hline
    \hyperref[instruction:EEVMULASU8QACCLDXP]{EE.VMULAS.[U/S][8/16].QACC.LD.XP} & Perform vector multiplication operation on signed/unsigned data in 1-byte/2-byte segment, and accumulate the results to corresponding bit segments in QACC\_H and QACC\_L registers, then read 16-byte data from memory. Add the value of AR register to address register.
    \\\hline
    \hyperref[instruction:EEVMULASU8QACCLDBCINCP]{EE.VMULAS.[U/S][8/16].QACC.LDBC.INCP} & Perform vector multiplication operation on signed/unsigned data in 1-byte/2-byte segment, and accumulate the results to corresponding bit segments in QACC\_H and QACC\_L registers. Then read 1-byte/2-byte data from memory and broadcast it to the 128-bit QR register. Add 16 to address register.
    \\\hline
    \hyperref[instruction:EEVMULASU8QACCLDIPQUP]{EE.VMULAS.[U/S][8/16].QACC.LD.IP.QUP} & Perform vector multiplication operation on signed/unsigned data in 1-byte/2-byte segment, and accumulate the results to the corresponding bit segments in QACC\_H and QACC\_L registers. At the same time, read 16-byte data from memory and output a 16-byte aligned data. Add immediate to address register.
    \\\hline
    \hyperref[instruction:EEVMULASU8QACCLDXPQUP]{EE.VMULAS.[U/S][8/16].QACC.LD.XP.QUP} & Perform vector multiplication operation on signed/unsigned data in 1-byte/2-byte segment, and accumulate the results to the corresponding bit segments in QACC\_H and QACC\_L registers. At the same time, read 16-byte data from memory and output a 16-byte aligned data. Add the value of AR register to address register.
    \\\hline
    \hyperref[instruction:EEVMULASU8QACCLDBCINCPQUP]{EE.VMULAS.[U/S][8/16].QACC.LDBC.INCP.QUP} & Perform vector multiplication operation on signed/unsigned data in 1-byte/2-byte segment, and accumulate the results to the corresponding bit segments in QACC\_H and QACC\_L registers. At the same time, read 1-byte/2-byte data from memory and broadcast it to the 128-bit QR register, then output a 16-byte aligned data. Add 16 to address register.
    \\\hline
\end{longtable}