\begin{longtable}[c]{|l|m{11cm}|}
    \caption{Data Exchange Instructions}
    \label{tab:pie-data-exchange-instructions}\\
    \hline
    \rowcolor{lightgray}
        \textbf{Instructions} & \textbf{Description} \\\hline
    \endfirsthead
    \rowcolor{lightgray}
    \textbf{Instructions} & \textbf{Description} \\\hline
    \endhead
    \endfoot

    \hyperref[instruction:MVQR]{MV.QR} & Move the value from the source QR register to the target QR register.
    \\\hline
    \hyperref[instruction:EEMOVI32A]{EE.MOVI.32.A} & Assign a piece of 32-bit data from the QR register to the AR register.
    \\\hline
    \hyperref[instruction:EEMOVI32Q]{EE.MOVI.32.Q} & Assign the data stored in the AR register to a piece of 32-bit data space in the QR register.
    \\\hline
    \hyperref[instruction:EEVZIP8]{EE.VZIP.[8/16/32]} & Encoding the two QR registers in 1-byte/2-byte/4-byte unit.
    \\\hline
    \hyperref[instruction:EEVUNZIP8]{EE.VUNZIP.[8/16/32]} & Decoding the two QR registers in 1-byte/2-byte/4-byte unit.
    \\\hline
    \hyperref[instruction:EEZEROQ]{EE.ZERO.Q} & Clear a specified QR register.
    \\\hline
    \hyperref[instruction:EEZEROQACC]{EE.ZERO.QACC} & Clear QACC\_H and QACC\_L registers.
    \\\hline
    \hyperref[instruction:EEZEROACCX]{EE.ZERO.ACCX} & Clear a specified ACCX register.
    \\\hline
    \hyperref[instruction:EEMOVS8QACC]{EE.MOV.S8.QACC} & Slice the QR register by 1-byte, and sign-extend it to 20-bit data, then assign this value to QACC\_H and QACC\_L registers.
    \\\hline
    \hyperref[instruction:EEMOVS16QACC]{EE.MOV.S16.QACC} & Slice the QR register by 2-byte, and sign-extend it to 40-bit data, then assign this value to QACC\_H and QACC\_L registers.
    \\\hline
    \hyperref[instruction:EEMOVU8QACC]{EE.MOV.U8.QACC} & Slice the QR register by 1-byte, and zero-extend it to 20-bit, then assign this value to QACC\_H and QACC\_L registers.
    \\\hline
    \hyperref[instruction:EEMOVU16QACC]{EE.MOV.U16.QACC} & Slice the QR register by 2-byte, and zero-extend it to 40-bit data, then assign this value to QACC\_H and QACC\_L registers.
    \\\hline
\end{longtable}