\begin{longtable}[c]{|l|m{12cm}|}
    \caption{Read Instructions}
    \label{tab:pie-load-instructions}\\
    \hline
    \rowcolor{lightgray}
    \textbf{Instructions} & \textbf{Description} \\\hline
    \endfirsthead
    \rowcolor{lightgray}
    \textbf{Instructions} & \textbf{Description} \\\hline
    \endhead
    \endfoot
    
    \hyperref[instruction:LDQR]{LD.QR} & Load 16-byte data to QR.
    \\\hline
    \hyperref[instruction:EEVLD128XP]{EE.VLD.128.XP} & Read the 16-byte data, then add the value stored in the AR register to the access address.
    \\\hline
    \hyperref[instruction:EEVLD128IP]{EE.VLD.128.IP} & Read the 16-byte data, then add the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EEVLDH64XP]{EE.VLD.[H/L].64.XP} & Read the 8-byte data, then add the value stored in the AR register to the access address.
    \\\hline
    \hyperref[instruction:EEVLDH64IP]{EE.VLD.[H/L].64.IP} & Read the 8-byte data, then add the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EEVLDBC8]{EE.VLDBC.[8/16/32]} & Read the 1-byte/2-byte/4-byte data.
    \\\hline
    \hyperref[instruction:EEVLDBC8XP]{EE.VLDBC.[8/16/32].XP} & Read the 1-byte/2-byte/4-byte data, then add the value stored in the AR register to the access address.
    \\\hline
    \hyperref[instruction:EEVLDBC8IP]{EE.VLDBC.[8/16/32].IP} & Read the 1-byte/2-byte/4-byte data, then add the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EEVLDHBC16INCP]{EE.VLDHBC.16.INCP} & Read the 16-byte data, then add 16 to the access address.
    \\\hline
    \hyperref[instruction:EELDF64XP]{EE.LDF.[64/128].XP} & Read the 8-byte/16-byte data, then add the value stored in the AR register to the access address.
    \\\hline
    \hyperref[instruction:EELDF64IP]{EE.LDF.[64/128].IP} & Read the 8-byte/16-byte data, then add the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EELD128USARXP]{EE.LD.128.USAR.XP} & Read the 16-byte data, then add the value stored in the AR register to the access address.
    \\\hline
    \hyperref[instruction:EELD128USARIP]{EE.LD.128.USAR.IP} & Read the 16-byte data, then add the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EELDQAU8128XP]{EE.LDQA.U8.128.[XP/IP]} & Read the 16-byte data and slice it by 1-byte, and zero-extend it to 20-bit data, which then will be written to register QACC\_H and QACC\_L, and finally add the value stored in the AR register or the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EELDQAU16128XP]{EE.LDQA.U16.128.XP} & Read the 16-byte data and slice it by 2-byte, and zero-extend it to 40-bit data, which then will be written to register QACC\_H and QACC\_L, and finally add the value stored in the AR register or the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EELDQAS8128XP]{EE.LDQA.S8.128.XP} & Read the 16-byte data and slice it by 1-byte, then sign-extend it to 20-bit data, which then will be written to register QACC\_H and QACC\_L, and finally add the value stored in the AR register or the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EELDQAS16128XP]{EE.LDQA.S16.128.XP} & Read the 16-byte data and slice it by 1-byte, then sign-extend it to 40-bit data, which then will be written to register QACC\_H and QACC\_L, and finally add the value stored in the AR register or the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EELDQACCHH32IP]{EE.LD.QACC\_[H/L].H.32.IP} & Read the 4-byte data, then add the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EELDQACCHL128IP]{EE.LD.QACC\_[H/L].L.128.IP} & Read the 16-byte data, then add the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EELDACCXIP]{EE.LD.ACCX.IP} & Read the 8-byte data, then add the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EELDUASTATEIP]{EE.LD.UA\_STATE.IP} & Read the 16-byte data, then add the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EELDXQ32]{EE.LDXQ.32} & Update access address first, then read the 4-byte data.
    \\\hline
\end{longtable}