\begin{longtable}[c]{|l|m{11cm}|}
    \caption{Write Instructions}
    \label{tab:pie-store-instructions}\\
    \hline
    \rowcolor{lightgray}
        \textbf{Instructions} & \textbf{Description} \\\hline
    \endfirsthead
    \rowcolor{lightgray}
    \textbf{Instructions} & \textbf{Description} \\\hline
    \endhead
    \endfoot
    
    \hyperref[instruction:STQR]{ST.QR} & Store 16-byte from QR to memory.
    \\\hline
    \hyperref[instruction:EEVST128XP]{EE.VST.128.XP} & Write the 16-byte data to memory, then add the value stored in the AR register to the access address.
    \\\hline
    \hyperref[instruction:EEVST128IP]{EE.VST.128.IP} & Write the 16-byte data to memory, then add the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EEVSTH64XP]{EE.VST.[H/L].64.XP} & Write the 8-byte data to memory, then add the value stored in the AR register to the access address.
    \\\hline
    \hyperref[instruction:EEVSTH64IP]{EE.VST.[H/L].64.IP} & Write the 8-byte data to memory, then add the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EESTF64XP]{EE.STF.[64/128].XP} & Write the 8-byte/16-byte data to memory, then add the value stored in the AR register to the access address.
    \\\hline
    \hyperref[instruction:EESTF64IP]{EE.STF.[64/128].IP} & Write the 8-byte/16-byte data to memory, then add the immediate value to the access address.
    \\\hline 
    \hyperref[instruction:EESTQACCHH32IP]{EE.ST.QACC\_[H/L].H.32.IP} & Write the 4-byte data to memory, then add the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EESTQACCHL128IP]{EE.ST.QACC\_[H/L].L.128.IP} & Write the 16-byte data to memory, then add the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EESTACCXIP]{EE.ST.ACCX.IP} & Zero-extend the value in the ACCX register to 8-byte data and write it to memory, then add the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EESTUASTATEIP]{EE.ST.UA\_STATE.IP} & Write the 16-byte data to memory, then add the immediate value to the access address.
    \\\hline
    \hyperref[instruction:EESTXQ32]{EE.STXQ.32} & Update the access address first, then write the 4-byte data to memory.
    \\\hline
\end{longtable}