\begin{register}{H}{SENS\_SAR\_READ\_CTRL\_REG}{0x0000}\label{regdesc:SENSSARREADCTRLREG}
\regfield{(reserved)}{3}{29}{000}%
\regfield{SENS\_SAR1\_DATA\_INV}{1}{28}{0}%
\regfield{SENS\_SAR1\_DIG\_FORCE}{1}{27}{0}%
\regfield{(reserved)}{9}{18}{000000000}%
\regfield{SENS\_SAR1\_SAMPLE\_BIT}{2}{16}{{3}}%
\regfield{SENS\_SAR1\_SAMPLE\_CYCLE}{8}{8}{{9}}%
\regfield{SENS\_SAR1\_CLK\_DIV}{8}{0}{{2}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_SAR1\_DATA\_INV]Invert SAR ADC1 data. (R/W)
\item [SENS\_SAR1\_DIG\_FORCE]1: SAR ADC1 controlled by DIG ADC1 CTR, 0: SAR ADC1 controlled by RTC ADC1 CTRL. (R/W)
\item [SENS\_SAR1\_SAMPLE\_BIT]Bit width of SAR ADC1, 00: for 9-bit, 01: for 10-bit, 10: for 11-bit, 11: for 12-bit. (R/W)
\item [SENS\_SAR1\_SAMPLE\_CYCLE]Sample cycles for SAR ADC1. (R/W)
\item [SENS\_SAR1\_CLK\_DIV]Clock divider. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_ULP\_CP\_SLEEP\_CYC0\_REG}{0x0018}\label{regdesc:SENSULPCPSLEEPCYC0REG}
\regfield{}{32}{0}{{200}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_ULP\_CP\_SLEEP\_CYC0\_REG]Sleep cycles for ULP coprocessor timer. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_START\_FORCE\_REG}{0x002c}\label{regdesc:SENSSARSTARTFORCEREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{SENS\_SAR1\_STOP}{1}{23}{0}%
\regfield{SENS\_SAR2\_STOP}{1}{22}{0}%
\regfield{SENS\_PC\_INIT}{11}{11}{00000000000}%
\regfield{(reserved)}{1}{10}{0}%
\regfield{SENS\_ULP\_CP\_START\_TOP}{1}{9}{0}%
\regfield{SENS\_ULP\_CP\_FORCE\_START\_TOP}{1}{8}{0}%
\regfield{SENS\_SAR2\_PWDET\_CCT}{3}{5}{000}%
\regfield{SENS\_SAR2\_EN\_TEST}{1}{4}{0}%
\regfield{SENS\_SAR2\_BIT\_WIDTH}{2}{2}{11}%
\regfield{SENS\_SAR1\_BIT\_WIDTH}{2}{0}{11}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_SAR1\_STOP]Stop SAR ADC1 conversion. (R/W)
\item [SENS\_SAR2\_STOP]Stop SAR ADC2 conversion. (R/W)
\item [SENS\_PC\_INIT]Initialized PC for ULP coprocessor. (R/W)
\item [SENS\_ULP\_CP\_START\_TOP]Write 1 to start ULP coprocessor; it is active only when reg\_ulp\_cp\_force\_start\_top = 1. (R/W)
\item [SENS\_ULP\_CP\_FORCE\_START\_TOP]1: ULP coprocessor is started by SW, 0: ULP coprocessor is started by timer. (R/W)
\item [SENS\_SAR2\_PWDET\_CCT]SAR2\_PWDET\_CCT, PA power detector capacitance tuning.  (R/W)
\item [SENS\_SAR2\_EN\_TEST]SAR2\_EN\_TEST is active only when reg\_sar2\_dig\_force = 0. (R/W)
\item [SENS\_SAR2\_BIT\_WIDTH]\label{SENSSAR2BITWIDTH}Bit width of SAR ADC2, 00: 9 bits, 01: 10 bits, 10: 11 bits, 11: 12 bits. (R/W)
\item [SENS\_SAR1\_BIT\_WIDTH]\label{SENSSAR1BITWIDTH}Bit width of SAR ADC1, 00: 9 bits, 01: 10 bits, 10: 11 bits, 11: 12 bits.  (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_ATTEN1\_REG}{0x0034}\label{regdesc:SENSSARATTEN1REG}
\regfield{}{32}{0}{{0x0FFFFFFFF}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_SAR\_ATTEN1\_REG]2-bit attenuation for each pad, 11: 1 dB, 10: 6 dB, 01: 3 dB, 00: 0 dB, [1:0] is used for ADC1\_CH0, [3:2] is used for ADC1\_CH1, etc. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_ATTEN2\_REG}{0x0038}\label{regdesc:SENSSARATTEN2REG}
\regfield{}{32}{0}{{0x0FFFFFFFF}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_SAR\_ATTEN2\_REG]2-bit attenuation for each pad, 11: 1 dB, 10: 6 dB, 01: 3 dB, 00: 0 dB, [1:0] is used for ADC2\_CH0, [3:2] is used for ADC2\_CH1, etc (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{SENS\_SAR\_MEAS\_START1\_REG}{0x0054}\label{regdesc:SENSSARMEASSTART1REG}
\regfield{SENS\_SAR1\_EN\_PAD\_FORCE}{1}{31}{0}%
\regfield{SENS\_SAR1\_EN\_PAD}{12}{19}{000000000000}%
\regfield{SENS\_MEAS1\_START\_FORCE}{1}{18}{0}%
\regfield{SENS\_MEAS1\_START\_SAR}{1}{17}{0}%
\regfield{SENS\_MEAS1\_DONE\_SAR}{1}{16}{0}%
\regfield{SENS\_MEAS1\_DATA\_SAR}{16}{0}{0000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_SAR1\_EN\_PAD\_FORCE]1: SAR ADC1 pad enable bitmap is controlled by SW, 0: SAR ADC1 pad enable bitmap is controlled by ULP coprocessor. (R/W)
\item [SENS\_SAR1\_EN\_PAD]SAR ADC1 pad enable bitmap; active only when reg\_sar1\_en\_pad\_force = 1. (R/W)
\item [SENS\_MEAS1\_START\_FORCE]1: SAR ADC1 controller (in RTC) is started by SW, 0: SAR ADC1 controller is started by ULP coprocessor. (R/W)
\item [SENS\_MEAS1\_START\_SAR]SAR ADC1 controller (in RTC) starts conversion; active only when reg\_meas1\_start\_force = 1. (R/W)
\item [SENS\_MEAS1\_DONE\_SAR]SAR ADC1 conversion-done indication. (RO)
\item [SENS\_MEAS1\_DATA\_SAR]SAR ADC1 data. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_TOUCH\_CTRL1\_REG}{0x0058}\label{regdesc:SENSSARTOUCHCTRL1REG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{(reserved)}{1}{27}{0}%
\regfield{(reserved)}{1}{26}{0}%
\regfield{SENS\_TOUCH\_OUT\_1EN}{1}{25}{1}%
\regfield{SENS\_TOUCH\_OUT\_SEL}{1}{24}{0}%
\regfield{SENS\_TOUCH\_XPD\_WAIT}{8}{16}{{0x004}}%
\regfield{SENS\_TOUCH\_MEAS\_DELAY}{16}{0}{{0x01000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_TOUCH\_OUT\_1EN]1: wakeup interrupt is generated if SET1 is touched, 0: wakeup interrupt is generated only if both SET1 \& SET2 are touched. (R/W)
\item [SENS\_TOUCH\_OUT\_SEL]1: the touch pad is considered touched when the value of the counter is greater than the threshold, 0: the touch pad is considered touched when the value of the counter is less than the threshold. (R/W)
\item [SENS\_TOUCH\_XPD\_WAIT]The waiting time (in 8 MHz cycles) between TOUCH\_START and TOUCH\_XPD. (R/W)
\item [SENS\_TOUCH\_MEAS\_DELAY]The measurement's duration (in 8 MHz cycles). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_TOUCH\_THRES1\_REG}{0x005c}\label{regdesc:SENSSARTOUCHTHRES1REG}
\regfield{SENS\_TOUCH\_OUT\_TH0}{16}{16}{{0x00000}}%
\regfield{SENS\_TOUCH\_OUT\_TH1}{16}{0}{{0x00000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_TOUCH\_OUT\_TH0]The threshold for touch pad 0. (R/W)
\item [SENS\_TOUCH\_OUT\_TH1]The threshold for touch pad 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_TOUCH\_THRES2\_REG}{0x0060}\label{regdesc:SENSSARTOUCHTHRES2REG}
\regfield{SENS\_TOUCH\_OUT\_TH2}{16}{16}{{0x00000}}%
\regfield{SENS\_TOUCH\_OUT\_TH3}{16}{0}{{0x00000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_TOUCH\_OUT\_TH2]The threshold for touch pad 2. (R/W)
\item [SENS\_TOUCH\_OUT\_TH3]The threshold for touch pad 3. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_TOUCH\_THRES3\_REG}{0x0064}\label{regdesc:SENSSARTOUCHTHRES3REG}
\regfield{SENS\_TOUCH\_OUT\_TH4}{16}{16}{{0x00000}}%
\regfield{SENS\_TOUCH\_OUT\_TH5}{16}{0}{{0x00000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_TOUCH\_OUT\_TH4]The threshold for touch pad 4. (R/W)
\item [SENS\_TOUCH\_OUT\_TH5]The threshold for touch pad 5. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_TOUCH\_THRES4\_REG}{0x0068}\label{regdesc:SENSSARTOUCHTHRES4REG}
\regfield{SENS\_TOUCH\_OUT\_TH6}{16}{16}{{0x00000}}%
\regfield{SENS\_TOUCH\_OUT\_TH7}{16}{0}{{0x00000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_TOUCH\_OUT\_TH6]The threshold for touch pad 6. (R/W)
\item [SENS\_TOUCH\_OUT\_TH7]The threshold for touch pad 7. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_TOUCH\_THRES5\_REG}{0x006c}\label{regdesc:SENSSARTOUCHTHRES5REG}
\regfield{SENS\_TOUCH\_OUT\_TH8}{16}{16}{{0x00000}}%
\regfield{SENS\_TOUCH\_OUT\_TH9}{16}{0}{{0x00000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_TOUCH\_OUT\_TH8]The threshold for touch pad 8. (R/W)
\item [SENS\_TOUCH\_OUT\_TH9]The threshold for touch pad 9. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_TOUCH\_OUT1\_REG}{0x0070}\label{regdesc:SENSSARTOUCHOUT1REG}
\regfield{SENS\_TOUCH\_MEAS\_OUT0}{16}{16}{{0x00000}}%
\regfield{SENS\_TOUCH\_MEAS\_OUT1}{16}{0}{{0x00000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_TOUCH\_MEAS\_OUT0]The counter for touch pad 0. (RO)
\item [SENS\_TOUCH\_MEAS\_OUT1]The counter for touch pad 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_TOUCH\_OUT2\_REG}{0x0074}\label{regdesc:SENSSARTOUCHOUT2REG}
\regfield{SENS\_TOUCH\_MEAS\_OUT2}{16}{16}{{0x00000}}%
\regfield{SENS\_TOUCH\_MEAS\_OUT3}{16}{0}{{0x00000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_TOUCH\_MEAS\_OUT2]The counter for touch pad 2. (RO)
\item [SENS\_TOUCH\_MEAS\_OUT3]The counter for touch pad 3. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_TOUCH\_OUT3\_REG}{0x0078}\label{regdesc:SENSSARTOUCHOUT3REG}
\regfield{SENS\_TOUCH\_MEAS\_OUT4}{16}{16}{{0x00000}}%
\regfield{SENS\_TOUCH\_MEAS\_OUT5}{16}{0}{{0x00000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_TOUCH\_MEAS\_OUT4]The counter for touch pad 4. (RO)
\item [SENS\_TOUCH\_MEAS\_OUT5]The counter for touch pad 5. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_TOUCH\_OUT4\_REG}{0x007c}\label{regdesc:SENSSARTOUCHOUT4REG}
\regfield{SENS\_TOUCH\_MEAS\_OUT6}{16}{16}{{0x00000}}%
\regfield{SENS\_TOUCH\_MEAS\_OUT7}{16}{0}{{0x00000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_TOUCH\_MEAS\_OUT6]The counter for touch pad 6. (RO)
\item [SENS\_TOUCH\_MEAS\_OUT7]The counter for touch pad 7. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_TOUCH\_OUT5\_REG}{0x0080}\label{regdesc:SENSSARTOUCHOUT5REG}
\regfield{SENS\_TOUCH\_MEAS\_OUT8}{16}{16}{{0x00000}}%
\regfield{SENS\_TOUCH\_MEAS\_OUT9}{16}{0}{{0x00000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_TOUCH\_MEAS\_OUT8]The counter for touch pad 8. (RO)
\item [SENS\_TOUCH\_MEAS\_OUT9]The counter for touch pad 9. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_TOUCH\_CTRL2\_REG}{0x0084}\label{regdesc:SENSSARTOUCHCTRL2REG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{SENS\_TOUCH\_MEAS\_EN\_CLR}{1}{30}{0}%
\regfield{SENS\_TOUCH\_SLEEP\_CYCLES}{16}{14}{{0x00100}}%
\regfield{SENS\_TOUCH\_START\_FORCE}{1}{13}{0}%
\regfield{SENS\_TOUCH\_START\_EN}{1}{12}{0}%
\regfield{SENS\_TOUCH\_START\_FSM\_EN}{1}{11}{1}%
\regfield{SENS\_TOUCH\_MEAS\_DONE}{1}{10}{0}%
\regfield{SENS\_TOUCH\_MEAS\_EN}{10}{0}{{0x000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_TOUCH\_MEAS\_EN\_CLR]Set to clear reg\_touch\_meas\_en. (WO)
\item [SENS\_TOUCH\_SLEEP\_CYCLES]Sleep cycles for timer. (R/W)
\item [SENS\_TOUCH\_START\_FORCE]1: starts the Touch FSM via software; 0: starts the Touch FSM via timer. (R/W)
\item [SENS\_TOUCH\_START\_EN]1: starts the Touch FSM; this is valid when reg\_touch\_start\_force is set. (R/W)
\item [SENS\_TOUCH\_START\_FSM\_EN]1: TOUCH\_START \& TOUCH\_XPD are controlled by the Touch FSM; 0: TOUCH\_START \& TOUCH\_XPD are controlled by registers. (R/W)
\item [SENS\_TOUCH\_MEAS\_DONE]Set to 1 by FSM, indicating that touch measurement is done. (RO)
\item [SENS\_TOUCH\_MEAS\_EN]10-bit register indicating which pads are touched. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_TOUCH\_ENABLE\_REG}{0x008c}\label{regdesc:SENSSARTOUCHENABLEREG}
\regfield{(reserved)}{2}{30}{00}%
\regfield{SENS\_TOUCH\_PAD\_OUTEN1}{10}{20}{{0x3FF}}%
\regfield{SENS\_TOUCH\_PAD\_OUTEN2}{10}{10}{{0x3FF}}%
\regfield{SENS\_TOUCH\_PAD\_WORKEN}{10}{0}{{0x3FF}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_TOUCH\_PAD\_OUTEN1]Bitmap defining SET1 for generating a wakeup interrupt; SET1 is considered touched if at least one of the touch pads in SET1 is touched. (R/W)
\item [SENS\_TOUCH\_PAD\_OUTEN2]Bitmap defining SET2 for generating a wakeup interrupt; SET2 is considered touched if at least one of the touch pads in SET2 is touched. (R/W)
\item [SENS\_TOUCH\_PAD\_WORKEN]Bitmap defining the working set during measurement. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_READ\_CTRL2\_REG}{0x0090}\label{regdesc:SENSSARREADCTRL2REG}
\regfield{(reserved)}{2}{30}{00}%
\regfield{SENS\_SAR2\_DATA\_INV}{1}{29}{0}%
\regfield{SENS\_SAR2\_DIG\_FORCE}{1}{28}{0}%
\regfield{(reserved)}{10}{18}{0000000000}%
\regfield{SENS\_SAR2\_SAMPLE\_BIT}{2}{16}{{3}}%
\regfield{SENS\_SAR2\_SAMPLE\_CYCLE}{8}{8}{{9}}%
\regfield{SENS\_SAR2\_CLK\_DIV}{8}{0}{{2}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_SAR2\_DATA\_INV]Invert SAR ADC2 data. (R/W)
\item [SENS\_SAR2\_DIG\_FORCE]1: SAR ADC2 controlled by DIG ADC2 CTRL or PWDET CTRL, 0: SAR ADC2 controlled by RTC ADC2 CTRL (R/W)
\item [SENS\_SAR2\_SAMPLE\_BIT]Bit width of SAR ADC2, 00: for 9-bit, 01: for 10-bit, 10: for 11-bit, 11: for 12-bit. (R/W)
\item [SENS\_SAR2\_SAMPLE\_CYCLE]Sample cycles of SAR ADC2. (R/W)
\item [SENS\_SAR2\_CLK\_DIV]Clock divider. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_MEAS\_START2\_REG}{0x0094}\label{regdesc:SENSSARMEASSTART2REG}
\regfield{SENS\_SAR2\_EN\_PAD\_FORCE}{1}{31}{0}%
\regfield{SENS\_SAR2\_EN\_PAD}{12}{19}{000000000000}%
\regfield{SENS\_MEAS2\_START\_FORCE}{1}{18}{0}%
\regfield{SENS\_MEAS2\_START\_SAR}{1}{17}{0}%
\regfield{SENS\_MEAS2\_DONE\_SAR}{1}{16}{0}%
\regfield{SENS\_MEAS2\_DATA\_SAR}{16}{0}{0000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_SAR2\_EN\_PAD\_FORCE]1: SAR ADC2 pad enable bitmap is controlled by SW, 0: SAR ADC2 pad enable bitmap is controlled by ULP coprocessor. (R/W)
\item [SENS\_SAR2\_EN\_PAD]SAR ADC2 pad enable bitmap; active only when reg\_sar2\_en\_pad\_force = 1. (R/W)
\item [SENS\_MEAS2\_START\_FORCE]1: SAR ADC2 controller (in RTC) is started by SW, 0: SAR ADC2 controller is started by ULP coprocessor. (R/W)
\item [SENS\_MEAS2\_START\_SAR]SAR ADC2 controller (in RTC) starts conversion; active only when reg\_meas2\_start\_force = 1. (R/W)
\item [SENS\_MEAS2\_DONE\_SAR]SAR ADC2-conversion-done indication. (RO)
\item [SENS\_MEAS2\_DATA\_SAR]SAR ADC2 data. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_DAC\_CTRL1\_REG}{0x0098}\label{regdesc:SENSSARDACCTRL1REG}
\regfield{(reserved)}{6}{26}{000000}%
\regfield{SENS\_DAC\_CLK\_INV}{1}{25}{0}%
\regfield{SENS\_DAC\_CLK\_FORCE\_HIGH}{1}{24}{0}%
\regfield{SENS\_DAC\_CLK\_FORCE\_LOW}{1}{23}{0}%
\regfield{SENS\_DAC\_DIG\_FORCE}{1}{22}{0}%
\regfield{(reserved)}{5}{17}{00000}%
\regfield{SENS\_SW\_TONE\_EN}{1}{16}{0}%
\regfield{SENS\_SW\_FSTEP}{16}{0}{0000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_DAC\_CLK\_INV]1: inverts PDAC\_CLK, 0: no inversion. (R/W)
\item [SENS\_DAC\_CLK\_FORCE\_HIGH] forces PDAC\_CLK to be 1. (R/W)
\item [SENS\_DAC\_CLK\_FORCE\_LOW] forces PDAC\_CLK to be 0. (R/W)
\item [SENS\_DAC\_DIG\_FORCE]1: DAC1 \& DAC2 use DMA, 0: DAC1 \& DAC2 do not use DMA. (R/W)
\item [SENS\_SW\_TONE\_EN]1: enable CW generator, 0: disable CW generator. (R/W)
\item [SENS\_SW\_FSTEP]Frequency step for CW generator; can be used to adjust the frequency. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_DAC\_CTRL2\_REG}{0x009c}\label{regdesc:SENSSARDACCTRL2REG}
\regfield{(reserved)}{6}{26}{000000}%
\regfield{SENS\_DAC\_CW\_EN2}{1}{25}{1}%
\regfield{SENS\_DAC\_CW\_EN1}{1}{24}{1}%
\regfield{SENS\_DAC\_INV2}{2}{22}{00}%
\regfield{SENS\_DAC\_INV1}{2}{20}{00}%
\regfield{SENS\_DAC\_SCALE2}{2}{18}{00}%
\regfield{SENS\_DAC\_SCALE1}{2}{16}{00}%
\regfield{SENS\_DAC\_DC2}{8}{8}{00000000}%
\regfield{SENS\_DAC\_DC1}{8}{0}{00000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [SENS\_DAC\_CW\_EN2]1: selects CW generator as source for PDAC2\_DAC[7:0], 0: selects register reg\_pdac2\_dac[7:0] as source for PDAC2\_DAC[7:0].  (R/W)
\item [SENS\_DAC\_CW\_EN1]1: selects CW generator as source for PDAC1\_DAC[7:0], 0: selects register reg\_pdac1\_dac[7:0] as source for PDAC1\_DAC[7:0]. (R/W)
\item [SENS\_DAC\_INV2]DAC2, 00: does not invert any bits, 01: inverts all bits, 10: inverts MSB, 11: inverts all bits except for MSB. (R/W)
\item [SENS\_DAC\_INV1]DAC1, 00: does not invert any bits, 01: inverts all bits, 10: inverts MSB, 11: inverts all bits except for MSB. (R/W)
\item [SENS\_DAC\_SCALE2]DAC2, 00: no scale; 01: scale to 1/2; 10: scale to 1/4; 11: scale to 1/8. (R/W)
\item [SENS\_DAC\_SCALE1]DAC1, 00: no scale; 01: scale to 1/2; 10: scale to 1/4; 11: scale to 1/8. (R/W)
\item [SENS\_DAC\_DC2]DC offset for DAC2 CW generator. (R/W)
\item [SENS\_DAC\_DC1]DC offset for DAC1 CW generator. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{SENS\_SAR\_MEAS\_CTRL2\_REG}{0x3FF488A0}\label{regdesc:SENSSARMEASCTRL2REG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{SENS\_SAR1\_DAC\_XPD\_FSM}{4}{0}{{3}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SENSSAR1DACXPDFSM}\item [SENS\_SAR1\_DAC\_XPD\_FSM] Control of DAC. \\
0: Power up DAC by FSM. \\
2: Disable DAC. \\
3: Power up DAC by software. \\(R/W)
\end{reglist}\end{regdesc}
\end{register}
