\begin{register}{H}{CP\_DMA\_INT\_RAW\_REG}{\hexprefix{}0000}\label{regdesc:CPDMAINTRAWREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{CP\_DMA\_OUT\_TOTAL\_EOF\_INT\_RAW}{1}{7}{{0}}%
\regfield{CP\_DMA\_IN\_DSCR\_EMPTY\_INT\_RAW}{1}{6}{{0}}%
\regfield{CP\_DMA\_OUT\_DSCR\_ERR\_INT\_RAW}{1}{5}{{0}}%
\regfield{CP\_DMA\_IN\_DSCR\_ERR\_INT\_RAW}{1}{4}{{0}}%
\regfield{CP\_DMA\_OUT\_EOF\_INT\_RAW}{1}{3}{{0}}%
\regfield{CP\_DMA\_OUT\_DONE\_INT\_RAW}{1}{2}{{0}}%
\regfield{CP\_DMA\_IN\_SUC\_EOF\_INT\_RAW}{1}{1}{{0}}%
\regfield{CP\_DMA\_IN\_DONE\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CPDMAINDONEINTRAW}\item [CP\_DMA\_IN\_DONE\_INT\_RAW] This is the interrupt raw bit. Triggered when the last data of frame is received or the receive buffer is full indicated by receive descriptor. (RO)
\label{fielddesc:CPDMAINSUCEOFINTRAW}\item [CP\_DMA\_IN\_SUC\_EOF\_INT\_RAW] This is the interrupt raw bit. Triggered when the last data of one frame is received. (RO)
\label{fielddesc:CPDMAOUTDONEINTRAW}\item [CP\_DMA\_OUT\_DONE\_INT\_RAW] This is the interrupt raw bit. Triggered when all data indicated by one transmit descriptor has been pushed into TX FIFO. (RO)
\label{fielddesc:CPDMAOUTEOFINTRAW}\item [CP\_DMA\_OUT\_EOF\_INT\_RAW] This is the interrupt raw bit. Triggered when the last data with EOF flag has been pushed into TX FIFO. (RO)
\label{fielddesc:CPDMAINDSCRERRINTRAW}\item [CP\_DMA\_IN\_DSCR\_ERR\_INT\_RAW] This is the interrupt raw bit. Triggered when detecting receive descriptor error, including owner error, the second and third word error of receive descriptor. (RO)
\label{fielddesc:CPDMAOUTDSCRERRINTRAW}\item [CP\_DMA\_OUT\_DSCR\_ERR\_INT\_RAW] This is the interrupt raw bit. Triggered when detecting transmit descriptor error, including owner error, the second and third word error of transmit descriptor. (RO)
\label{fielddesc:CPDMAINDSCREMPTYINTRAW}\item [CP\_DMA\_IN\_DSCR\_EMPTY\_INT\_RAW] This is the interrupt raw bit. Triggered when receiving data is completed and no more receive descriptor. (RO)
\label{fielddesc:CPDMAOUTTOTALEOFINTRAW}\item [CP\_DMA\_OUT\_TOTAL\_EOF\_INT\_RAW] This is the interrupt raw bit. Triggered when data corresponding to all transmit descriptors and the last descriptor with valid EOF is transmitted out. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CP\_DMA\_INT\_ST\_REG}{\hexprefix{}0004}\label{regdesc:CPDMAINTSTREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{CP\_DMA\_OUT\_TOTAL\_EOF\_INT\_ST}{1}{7}{{0}}%
\regfield{CP\_DMA\_IN\_DSCR\_EMPTY\_INT\_ST}{1}{6}{{0}}%
\regfield{CP\_DMA\_OUT\_DSCR\_ERR\_INT\_ST}{1}{5}{{0}}%
\regfield{CP\_DMA\_IN\_DSCR\_ERR\_INT\_ST}{1}{4}{{0}}%
\regfield{CP\_DMA\_OUT\_EOF\_INT\_ST}{1}{3}{{0}}%
\regfield{CP\_DMA\_OUT\_DONE\_INT\_ST}{1}{2}{{0}}%
\regfield{CP\_DMA\_IN\_SUC\_EOF\_INT\_ST}{1}{1}{{0}}%
\regfield{CP\_DMA\_IN\_DONE\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CPDMAINDONEINTST}\item [CP\_DMA\_IN\_DONE\_INT\_ST] This is the masked interrupt bit for CP\_DMA\_IN\_DONE\_INT interrupt when CP\_DMA\_IN\_DONE\_INT\_ENA is set. (RO)
\label{fielddesc:CPDMAINSUCEOFINTST}\item [CP\_DMA\_IN\_SUC\_EOF\_INT\_ST] This is the masked interrupt bit for CP\_DMA\_IN\_SUC\_EOF\_INT interrupt when CP\_DMA\_IN\_SUC\_EOF\_INT\_ENA is set. (RO)
\label{fielddesc:CPDMAOUTDONEINTST}\item [CP\_DMA\_OUT\_DONE\_INT\_ST] This is the masked interrupt bit for CP\_DMA\_OUT\_DONE\_INT interrupt when CP\_DMA\_OUT\_DONE\_INT\_ENA is set. (RO)
\label{fielddesc:CPDMAOUTEOFINTST}\item [CP\_DMA\_OUT\_EOF\_INT\_ST] This is the masked interrupt bit for CP\_DMA\_OUT\_EOF\_INT interrupt when CP\_DMA\_OUT\_EOF\_INT\_ENA is set. (RO)
\label{fielddesc:CPDMAINDSCRERRINTST}\item [CP\_DMA\_IN\_DSCR\_ERR\_INT\_ST] This is the masked interrupt bit for CP\_DMA\_IN\_DSCR\_ERR\_INT interrupt when CP\_DMA\_IN\_DSCR\_ERR\_INT\_ENA is set. (RO)
\label{fielddesc:CPDMAOUTDSCRERRINTST}\item [CP\_DMA\_OUT\_DSCR\_ERR\_INT\_ST] This is the masked interrupt bit for CP\_DMA\_OUT\_DSCR\_ERR\_INT interrupt when CP\_DMA\_OUT\_DSCR\_ERR\_INT\_ENA is set. (RO)
\label{fielddesc:CPDMAINDSCREMPTYINTST}\item [CP\_DMA\_IN\_DSCR\_EMPTY\_INT\_ST] This is the masked interrupt bit for CP\_DMA\_IN\_DSCR\_EMPTY\_INT interrupt when CP\_DMA\_IN\_DSCR\_EMPTY\_INT\_ENA is set. (RO)
\label{fielddesc:CPDMAOUTTOTALEOFINTST}\item [CP\_DMA\_OUT\_TOTAL\_EOF\_INT\_ST] This is the masked interrupt bit for CP\_DMA\_OUT\_TOTAL\_EOF\_INT interrupt when CP\_DMA\_OUT\_TOTAL\_EOF\_INT\_ENA is set. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CP\_DMA\_INT\_ENA\_REG}{\hexprefix{}0008}\label{regdesc:CPDMAINTENAREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{CP\_DMA\_OUT\_TOTAL\_EOF\_INT\_ENA}{1}{7}{{0}}%
\regfield{CP\_DMA\_IN\_DSCR\_EMPTY\_INT\_ENA}{1}{6}{{0}}%
\regfield{CP\_DMA\_OUT\_DSCR\_ERR\_INT\_ENA}{1}{5}{{0}}%
\regfield{CP\_DMA\_IN\_DSCR\_ERR\_INT\_ENA}{1}{4}{{0}}%
\regfield{CP\_DMA\_OUT\_EOF\_INT\_ENA}{1}{3}{{0}}%
\regfield{CP\_DMA\_OUT\_DONE\_INT\_ENA}{1}{2}{{0}}%
\regfield{CP\_DMA\_IN\_SUC\_EOF\_INT\_ENA}{1}{1}{{0}}%
\regfield{CP\_DMA\_IN\_DONE\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CPDMAINDONEINTENA}\item [CP\_DMA\_IN\_DONE\_INT\_ENA] This is the interrupt enable bit for CP\_DMA\_IN\_DONE\_INT interrupt. (R/W)
\label{fielddesc:CPDMAINSUCEOFINTENA}\item [CP\_DMA\_IN\_SUC\_EOF\_INT\_ENA] This is the interrupt enable bit for CP\_DMA\_IN\_SUC\_EOF\_INT interrupt. (R/W)
\label{fielddesc:CPDMAOUTDONEINTENA}\item [CP\_DMA\_OUT\_DONE\_INT\_ENA] This is the interrupt enable bit for CP\_DMA\_OUT\_DONE\_INT interrupt. (R/W)
\label{fielddesc:CPDMAOUTEOFINTENA}\item [CP\_DMA\_OUT\_EOF\_INT\_ENA] This is the interrupt enable bit for CP\_DMA\_OUT\_EOF\_INT interrupt. (R/W)
\label{fielddesc:CPDMAINDSCRERRINTENA}\item [CP\_DMA\_IN\_DSCR\_ERR\_INT\_ENA] This is the interrupt enable bit for CP\_DMA\_IN\_DSCR\_ERR\_INT interrupt. (R/W)
\label{fielddesc:CPDMAOUTDSCRERRINTENA}\item [CP\_DMA\_OUT\_DSCR\_ERR\_INT\_ENA] This is the interrupt enable bit for CP\_DMA\_OUT\_DSCR\_ERR\_INT interrupt. (R/W)
\label{fielddesc:CPDMAINDSCREMPTYINTENA}\item [CP\_DMA\_IN\_DSCR\_EMPTY\_INT\_ENA] This is the interrupt enable bit for CP\_DMA\_IN\_DSCR\_EMPTY\_INT interrupt. (R/W)
\label{fielddesc:CPDMAOUTTOTALEOFINTENA}\item [CP\_DMA\_OUT\_TOTAL\_EOF\_INT\_ENA] This is the interrupt enable bit for CP\_DMA\_OUT\_TOTAL\_EOF\_INT interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CP\_DMA\_INT\_CLR\_REG}{\hexprefix{}000C}\label{regdesc:CPDMAINTCLRREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{CP\_DMA\_OUT\_TOTAL\_EOF\_INT\_CLR}{1}{7}{{0}}%
\regfield{CP\_DMA\_IN\_DSCR\_EMPTY\_INT\_CLR}{1}{6}{{0}}%
\regfield{CP\_DMA\_OUT\_DSCR\_ERR\_INT\_CLR}{1}{5}{{0}}%
\regfield{CP\_DMA\_IN\_DSCR\_ERR\_INT\_CLR}{1}{4}{{0}}%
\regfield{CP\_DMA\_OUT\_EOF\_INT\_CLR}{1}{3}{{0}}%
\regfield{CP\_DMA\_OUT\_DONE\_INT\_CLR}{1}{2}{{0}}%
\regfield{CP\_DMA\_IN\_SUC\_EOF\_INT\_CLR}{1}{1}{{0}}%
\regfield{CP\_DMA\_IN\_DONE\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CPDMAINDONEINTCLR}\item [CP\_DMA\_IN\_DONE\_INT\_CLR] Set this bit to clear CP\_DMA\_IN\_DONE\_INT INTERRUPT. (WO)
\label{fielddesc:CPDMAINSUCEOFINTCLR}\item [CP\_DMA\_IN\_SUC\_EOF\_INT\_CLR] Set this bit to clear CP\_DMA\_IN\_SUC\_EOF\_INT interrupt. (WO)
\label{fielddesc:CPDMAOUTDONEINTCLR}\item [CP\_DMA\_OUT\_DONE\_INT\_CLR] Set this bit to clear CP\_DMA\_OUT\_DONE\_INT interrupt. (WO)
\label{fielddesc:CPDMAOUTEOFINTCLR}\item [CP\_DMA\_OUT\_EOF\_INT\_CLR] Set this bit to clear CP\_DMA\_OUT\_EOF\_INT interrupt. (WO)
\label{fielddesc:CPDMAINDSCRERRINTCLR}\item [CP\_DMA\_IN\_DSCR\_ERR\_INT\_CLR] Set this bit to clear CP\_DMA\_IN\_DSCR\_ERR\_INT interrupt. (WO)
\label{fielddesc:CPDMAOUTDSCRERRINTCLR}\item [CP\_DMA\_OUT\_DSCR\_ERR\_INT\_CLR] Set this bit to clear CP\_DMA\_OUT\_DSCR\_ERR\_INT interrupt. (WO)
\label{fielddesc:CPDMAINDSCREMPTYINTCLR}\item [CP\_DMA\_IN\_DSCR\_EMPTY\_INT\_CLR] Set this bit to clear CP\_DMA\_IN\_DSCR\_EMPTY\_INT interrupt. (WO)
\label{fielddesc:CPDMAOUTTOTALEOFINTCLR}\item [CP\_DMA\_OUT\_TOTAL\_EOF\_INT\_CLR] Set this bit to clear CP\_DMA\_OUT\_TOTAL\_EOF\_INT interrupt. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CP\_DMA\_OUT\_LINK\_REG}{\hexprefix{}0010}\label{regdesc:CPDMAOUTLINKREG}
\regfield{CP\_DMA\_OUTLINK\_PARK}{1}{31}{{0}}%
\regfield{CP\_DMA\_OUTLINK\_RESTART}{1}{30}{{0}}%
\regfield{CP\_DMA\_OUTLINK\_START}{1}{29}{{0}}%
\regfield{CP\_DMA\_OUTLINK\_STOP}{1}{28}{{0}}%
\regfield{(reserved)}{8}{20}{00000000}%
\regfield{CP\_DMA\_OUTLINK\_ADDR}{20}{0}{{\hexprefix{}000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CPDMAOUTLINKADDR}\item [CP\_DMA\_OUTLINK\_ADDR] This register is used to specify the least significant 20 bits of the first transmit descriptor's address. (R/W)
\label{fielddesc:CPDMAOUTLINKSTOP}\item [CP\_DMA\_OUTLINK\_STOP] Set this bit to stop DMA from reading transmit descriptors after finishing the current data transaction. (R/W)
\label{fielddesc:CPDMAOUTLINKSTART}\item [CP\_DMA\_OUTLINK\_START] Set this bit to start a new transmit descriptor. (R/W)
\label{fielddesc:CPDMAOUTLINKRESTART}\item [CP\_DMA\_OUTLINK\_RESTART] Set this bit to restart the transmit descriptor from the last address. (R/W)
\label{fielddesc:CPDMAOUTLINKPARK}\item [CP\_DMA\_OUTLINK\_PARK] 1: the transmit descriptor's FSM is in idle state.
0: the transmit descriptor's FSM is working. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CP\_DMA\_IN\_LINK\_REG}{\hexprefix{}0014}\label{regdesc:CPDMAINLINKREG}
\regfield{CP\_DMA\_INLINK\_PARK}{1}{31}{{0}}%
\regfield{CP\_DMA\_INLINK\_RESTART}{1}{30}{{0}}%
\regfield{CP\_DMA\_INLINK\_START}{1}{29}{{0}}%
\regfield{CP\_DMA\_INLINK\_STOP}{1}{28}{{0}}%
\regfield{(reserved)}{8}{20}{00000000}%
\regfield{CP\_DMA\_INLINK\_ADDR}{20}{0}{{\hexprefix{}000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CPDMAINLINKADDR}\item [CP\_DMA\_INLINK\_ADDR] This register is used to specify the least significant 20 bits of the first receive descriptor's address. (R/W)
\label{fielddesc:CPDMAINLINKSTOP}\item [CP\_DMA\_INLINK\_STOP] Set this bit to stop DMA from reading receive descriptors after finishing the current data transaction. (R/W)
\label{fielddesc:CPDMAINLINKSTART}\item [CP\_DMA\_INLINK\_START] Set this bit to enable DMA to read receive descriptors. (R/W)
\label{fielddesc:CPDMAINLINKRESTART}\item [CP\_DMA\_INLINK\_RESTART] Set this bit to restart new receive descriptors. (R/W)
\label{fielddesc:CPDMAINLINKPARK}\item [CP\_DMA\_INLINK\_PARK] 1: the receive descriptor's FSM is in idle state.
0: the receive descriptor's FSM is working. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CP\_DMA\_CONF\_REG}{\hexprefix{}003C}\label{regdesc:CPDMACONFREG}
\regfield{CP\_DMA\_CLK\_EN}{1}{31}{{0}}%
\regfield{(reserved)}{23}{8}{00000000000000000000000}%
\regfield{CP\_DMA\_CHECK\_OWNER}{1}{7}{{0}}%
\regfield{CP\_DMA\_OUT\_AUTO\_WRBACK}{1}{6}{{0}}%
\regfield{CP\_DMA\_IN\_OWNER}{1}{5}{{0}}%
\regfield{CP\_DMA\_OUT\_OWNER}{1}{4}{{0}}%
\regfield{CP\_DMA\_FIFO\_RST}{1}{3}{{0}}%
\regfield{CP\_DMA\_CMDFIFO\_RST}{1}{2}{{0}}%
\regfield{CP\_DMA\_OUT\_RST}{1}{1}{{0}}%
\regfield{CP\_DMA\_IN\_RST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CPDMAINRST}\item [CP\_DMA\_IN\_RST] Set this bit to reset in DMA FSM. (R/W)
\label{fielddesc:CPDMAOUTRST}\item [CP\_DMA\_OUT\_RST] Set this bit to reset out DMA FSM. (R/W)
\label{fielddesc:CPDMACMDFIFORST}\item [CP\_DMA\_CMDFIFO\_RST] Set this bit to reset in\_cmd FIFO and out\_cmd FIFO. (R/W)
\label{fielddesc:CPDMAFIFORST}\item [CP\_DMA\_FIFO\_RST] Set this bit to reset data in RX FIFO. (R/W)
\label{fielddesc:CPDMAOUTOWNER}\item [CP\_DMA\_OUT\_OWNER] This is used to configure the owner bit in transmit descriptor. This is effective only when you set CP\_DMA\_OUT\_AUTO\_WRBACK. (R/W)
\label{fielddesc:CPDMAINOWNER}\item [CP\_DMA\_IN\_OWNER] This is used to configure the owner bit in receive descriptor. (R/W)
\label{fielddesc:CPDMAOUTAUTOWRBACK}\item [CP\_DMA\_OUT\_AUTO\_WRBACK] This bit is used to write back out descriptor when hardware has already used this descriptor. (R/W)
\label{fielddesc:CPDMACHECKOWNER}\item [CP\_DMA\_CHECK\_OWNER] Set this bit to enable owner bit check in descriptor. (R/W)
\label{fielddesc:CPDMACLKEN}\item [CP\_DMA\_CLK\_EN] 1'b1: Force clock on for register. 1'b0: Support clock only when application writes registers. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CP\_DMA\_OUT\_EOF\_DES\_ADDR\_REG}{\hexprefix{}0018}\label{regdesc:CPDMAOUTEOFDESADDRREG}
\regfield{CP\_DMA\_OUT\_EOF\_DES\_ADDR}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CPDMAOUTEOFDESADDR}\item [CP\_DMA\_OUT\_EOF\_DES\_ADDR] This register stores the address of the transmit descriptor when the EOF bit in this descriptor is 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CP\_DMA\_IN\_EOF\_DES\_ADDR\_REG}{\hexprefix{}001C}\label{regdesc:CPDMAINEOFDESADDRREG}
\regfield{CP\_DMA\_IN\_SUC\_EOF\_DES\_ADDR}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CPDMAINSUCEOFDESADDR}\item [CP\_DMA\_IN\_SUC\_EOF\_DES\_ADDR] This register stores the address of the receive descriptor when received successful EOF. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CP\_DMA\_OUT\_EOF\_BFR\_DES\_ADDR\_REG}{\hexprefix{}0020}\label{regdesc:CPDMAOUTEOFBFRDESADDRREG}
\regfield{CP\_DMA\_OUT\_EOF\_BFR\_DES\_ADDR}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CPDMAOUTEOFBFRDESADDR}\item [CP\_DMA\_OUT\_EOF\_BFR\_DES\_ADDR] This register stores the address of the transmit descriptor before the last transmit descriptor. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CP\_DMA\_INLINK\_DSCR\_REG}{\hexprefix{}0024}\label{regdesc:CPDMAINLINKDSCRREG}
\regfield{CP\_DMA\_INLINK\_DSCR}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CPDMAINLINKDSCR}\item [CP\_DMA\_INLINK\_DSCR] Represents the address of the next receive descriptor x+1 pointed by the current receive descriptor that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CP\_DMA\_INLINK\_DSCR\_BF0\_REG}{\hexprefix{}0028}\label{regdesc:CPDMAINLINKDSCRBF0REG}
\regfield{CP\_DMA\_INLINK\_DSCR\_BF0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CPDMAINLINKDSCRBF0}\item [CP\_DMA\_INLINK\_DSCR\_BF0] Represents the address of the current receive descriptor x that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CP\_DMA\_OUTLINK\_DSCR\_REG}{\hexprefix{}0030}\label{regdesc:CPDMAOUTLINKDSCRREG}
\regfield{CP\_DMA\_OUTLINK\_DSCR}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CPDMAOUTLINKDSCR}\item [CP\_DMA\_OUTLINK\_DSCR] Represents the address of the next transmit descriptor y+1 pointed by the current transmit descriptor that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CP\_DMA\_OUTLINK\_DSCR\_BF0\_REG}{\hexprefix{}0034}\label{regdesc:CPDMAOUTLINKDSCRBF0REG}
\regfield{CP\_DMA\_OUTLINK\_DSCR\_BF0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CPDMAOUTLINKDSCRBF0}\item [CP\_DMA\_OUTLINK\_DSCR\_BF0] Represents the address of the current transmit descriptor y that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CP\_DMA\_IN\_ST\_REG}{\hexprefix{}0040}\label{regdesc:CPDMAINSTREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{CP\_DMA\_FIFO\_EMPTY}{1}{23}{{0}}%
\regfield{CP\_DMA\_IN\_STATE}{3}{20}{{0}}%
\regfield{CP\_DMA\_IN\_DSCR\_STATE}{2}{18}{{0}}%
\regfield{CP\_DMA\_INLINK\_DSCR\_ADDR}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CPDMAINLINKDSCRADDR}\item [CP\_DMA\_INLINK\_DSCR\_ADDR] This register stores the lower 18 bits of the next receive descriptor address that is pre-read (but not processed yet). If the current receive descriptor is the last descriptor, then this field represents the address of the current receive descriptor. (RO)
\label{fielddesc:CPDMAINDSCRSTATE}\item [CP\_DMA\_IN\_DSCR\_STATE] Reserved. (RO)
\label{fielddesc:CPDMAINSTATE}\item [CP\_DMA\_IN\_STATE] Reserved. (RO)
\label{fielddesc:CPDMAFIFOEMPTY}\item [CP\_DMA\_FIFO\_EMPTY] Copy DMA FIFO empty signal. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CP\_DMA\_OUT\_ST\_REG}{\hexprefix{}0044}\label{regdesc:CPDMAOUTSTREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{CP\_DMA\_FIFO\_FULL}{1}{23}{{0}}%
\regfield{CP\_DMA\_OUT\_STATE}{3}{20}{{0}}%
\regfield{CP\_DMA\_OUT\_DSCR\_STATE}{2}{18}{{0}}%
\regfield{CP\_DMA\_OUTLINK\_DSCR\_ADDR}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CPDMAOUTLINKDSCRADDR}\item [CP\_DMA\_OUTLINK\_DSCR\_ADDR] This register stores the lower 18 bits of the next transmit descriptor address that is pre-read (but not processed yet). If the current transmit descriptor is the last descriptor, then this field represents the address of the current transmit descriptor. (RO)
\label{fielddesc:CPDMAOUTDSCRSTATE}\item [CP\_DMA\_OUT\_DSCR\_STATE] Reserved. (RO)
\label{fielddesc:CPDMAOUTSTATE}\item [CP\_DMA\_OUT\_STATE] Reserved. (RO)
\label{fielddesc:CPDMAFIFOFULL}\item [CP\_DMA\_FIFO\_FULL] Copy DMA FIFO full signal. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CP\_DMA\_DATE\_REG}{\hexprefix{}00FC}\label{regdesc:CPDMADATEREG}
\regfield{CP\_DMA\_DMA\_DATE}{32}{0}{{\hexprefix{}18082000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CPDMADMADATE}\item [CP\_DMA\_DMA\_DATE] This is the version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}

