\begin{register}{H}{CRYPTO\_DMA\_CONF0\_REG}{\hexprefix{}0000}\label{regdesc:CRYPTODMACONF0REG}
\regfield{(reserved)}{19}{13}{0000000000000000000}%
\regfield{CRYPTO\_DMA\_MEM\_TRANS\_EN}{1}{12}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_DATA\_BURST\_EN}{1}{11}{{0}}%
\regfield{CRYPTO\_DMA\_INDSCR\_BURST\_EN}{1}{10}{{0}}%
\regfield{CRYPTO\_DMA\_OUTDSCR\_BURST\_EN}{1}{9}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_EOF\_MODE}{1}{8}{{1}}%
\regfield{CRYPTO\_DMA\_OUT\_NO\_RESTART\_CLR}{1}{7}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_AUTO\_WRBACK}{1}{6}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_LOOP\_TEST}{1}{5}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_LOOP\_TEST}{1}{4}{{0}}%
\regfield{CRYPTO\_DMA\_AHBM\_RST}{1}{3}{{0}}%
\regfield{CRYPTO\_DMA\_AHBM\_FIFO\_RST}{1}{2}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_RST}{1}{1}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_RST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAINRST}\item [CRYPTO\_DMA\_IN\_RST] This bit is used to reset crypto DMA in FSM and RX FIFO pointer. (R/W)
\label{fielddesc:CRYPTODMAOUTRST}\item [CRYPTO\_DMA\_OUT\_RST] This bit is used to reset crypto DMA out FSM and TX FIFO pointer. (R/W)
\label{fielddesc:CRYPTODMAAHBMFIFORST}\item [CRYPTO\_DMA\_AHBM\_FIFO\_RST] This bit is used to reset crypto DMA AHB master FIFO pointer. (R/W)
\label{fielddesc:CRYPTODMAAHBMRST}\item [CRYPTO\_DMA\_AHBM\_RST] Reset crypto DMA AHB master. (R/W)
\label{fielddesc:CRYPTODMAINLOOPTEST}\item [CRYPTO\_DMA\_IN\_LOOP\_TEST] Reserved (R/W)
\label{fielddesc:CRYPTODMAOUTLOOPTEST}\item [CRYPTO\_DMA\_OUT\_LOOP\_TEST] Reserved (R/W)
\label{fielddesc:CRYPTODMAOUTAUTOWRBACK}\item [CRYPTO\_DMA\_OUT\_AUTO\_WRBACK] Set this bit to enable automatic outlink-writeback when all the data in TX Buffer has been transmitted. (R/W)
\label{fielddesc:CRYPTODMAOUTNORESTARTCLR}\item [CRYPTO\_DMA\_OUT\_NO\_RESTART\_CLR] Reserved (R/W)
\label{fielddesc:CRYPTODMAOUTEOFMODE}\item [CRYPTO\_DMA\_OUT\_EOF\_MODE] Out EOF flag generation mode of TX FIFO. 1: EOF flag of TX is generated when the last data with EOF would be transmitted has been popped from FIFO of Crypto DMA; 0: EOF flag is generated when the last data with EOF would be transmitted has been pushed into FIFO of Crypto DMA. (R/W)
\label{fielddesc:CRYPTODMAOUTDSCRBURSTEN}\item [CRYPTO\_DMA\_OUTDSCR\_BURST\_EN] Set this bit to enable INCR burst transfer when TX FIFO reads descriptor from internal RAM. (R/W)
\label{fielddesc:CRYPTODMAINDSCRBURSTEN}\item [CRYPTO\_DMA\_INDSCR\_BURST\_EN] Set this bit to enable INCR burst transfer when RX FIFO reads descriptor from internal RAM. (R/W)
\label{fielddesc:CRYPTODMAOUTDATABURSTEN}\item [CRYPTO\_DMA\_OUT\_DATA\_BURST\_EN] Set this bit to enable INCR burst transfer when TX FIFO reads data from internal RAM. (R/W)
\label{fielddesc:CRYPTODMAMEMTRANSEN}\item [CRYPTO\_DMA\_MEM\_TRANS\_EN] Set this bit to enable automatic transmitting data from memory to memory via DMA. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_OUT\_LINK\_REG}{\hexprefix{}0024}\label{regdesc:CRYPTODMAOUTLINKREG}
\regfield{CRYPTO\_DMA\_OUTLINK\_PARK}{1}{31}{{0}}%
\regfield{CRYPTO\_DMA\_OUTLINK\_RESTART}{1}{30}{{0}}%
\regfield{CRYPTO\_DMA\_OUTLINK\_START}{1}{29}{{0}}%
\regfield{CRYPTO\_DMA\_OUTLINK\_STOP}{1}{28}{{0}}%
\regfield{(reserved)}{8}{20}{00000000}%
\regfield{CRYPTO\_DMA\_OUTLINK\_ADDR}{20}{0}{{\hexprefix{}000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAOUTLINKADDR}\item [CRYPTO\_DMA\_OUTLINK\_ADDR] This register stores the 20 least significant bits of the first transmit descriptor's address. (R/W)
\label{fielddesc:CRYPTODMAOUTLINKSTOP}\item [CRYPTO\_DMA\_OUTLINK\_STOP] Set this bit to stop DMA from reading transmit descriptors after finishing the current data transaction. (R/W)
\label{fielddesc:CRYPTODMAOUTLINKSTART}\item [CRYPTO\_DMA\_OUTLINK\_START] Set this bit to enable DMA to read transmit descriptors. (R/W)
\label{fielddesc:CRYPTODMAOUTLINKRESTART}\item [CRYPTO\_DMA\_OUTLINK\_RESTART] Set this bit to restart a new outlink from the last address. (R/W)
\label{fielddesc:CRYPTODMAOUTLINKPARK}\item [CRYPTO\_DMA\_OUTLINK\_PARK] 1: the transmit descriptor's FSM is in idle state.  0: the transmit descriptor's FSM is working. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_IN\_LINK\_REG}{\hexprefix{}0028}\label{regdesc:CRYPTODMAINLINKREG}
\regfield{CRYPTO\_DMA\_INLINK\_PARK}{1}{31}{{0}}%
\regfield{CRYPTO\_DMA\_INLINK\_RESTART}{1}{30}{{0}}%
\regfield{CRYPTO\_DMA\_INLINK\_START}{1}{29}{{0}}%
\regfield{CRYPTO\_DMA\_INLINK\_STOP}{1}{28}{{0}}%
\regfield{(reserved)}{7}{21}{0000000}%
\regfield{CRYPTO\_DMA\_INLINK\_AUTO\_RET}{1}{20}{{1}}%
\regfield{CRYPTO\_DMA\_INLINK\_ADDR}{20}{0}{{\hexprefix{}000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAINLINKADDR}\item [CRYPTO\_DMA\_INLINK\_ADDR] This register stores the 20 least significant bits of the first receive descriptor's address. (R/W)
\label{fielddesc:CRYPTODMAINLINKAUTORET}\item [CRYPTO\_DMA\_INLINK\_AUTO\_RET] Reserved (R/W)
\label{fielddesc:CRYPTODMAINLINKSTOP}\item [CRYPTO\_DMA\_INLINK\_STOP] Set this bit to stop DMA from reading receive descriptors after finishing the current data transaction. (R/W)
\label{fielddesc:CRYPTODMAINLINKSTART}\item [CRYPTO\_DMA\_INLINK\_START] Set this bit to enable DMA to read receive descriptors. (R/W)
\label{fielddesc:CRYPTODMAINLINKRESTART}\item [CRYPTO\_DMA\_INLINK\_RESTART] Set this bit to mount a new receive descriptor. (R/W)
\label{fielddesc:CRYPTODMAINLINKPARK}\item [CRYPTO\_DMA\_INLINK\_PARK] 1: the receive descriptor's FSM is in idle state.  0: the receive descriptor's FSM is working. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_CONF1\_REG}{\hexprefix{}002C}\label{regdesc:CRYPTODMACONF1REG}
\regfield{(reserved)}{17}{15}{00000000000000000}%
\regfield{CRYPTO\_DMA\_EXT\_MEM\_BK\_SIZE}{2}{13}{{0}}%
\regfield{CRYPTO\_DMA\_CHECK\_OWNER}{1}{12}{{0}}%
\regfield{CRYPTO\_DMA\_INFIFO\_FULL\_THRS}{12}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAINFIFOFULLTHRS}\item [CRYPTO\_DMA\_INFIFO\_FULL\_THRS] This register is used to generate the CRYPTO\_DMA\_INFIFO\_FULL\_WM\_INT interrupt when the byte number is up to the value of the register. (R/W)
\label{fielddesc:CRYPTODMACHECKOWNER}\item [CRYPTO\_DMA\_CHECK\_OWNER] Set this bit to enable checking the owner attribute of the link descriptor. (R/W)
\label{fielddesc:CRYPTODMAEXTMEMBKSIZE}\item [CRYPTO\_DMA\_EXT\_MEM\_BK\_SIZE] DMA access external memory block size. 0: 16 bytes;      1: 32 bytes;    2:64 bytes;      3:Reserved. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_AHB\_TEST\_REG}{\hexprefix{}0048}\label{regdesc:CRYPTODMAAHBTESTREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{CRYPTO\_DMA\_AHB\_TESTADDR}{2}{4}{{0}}%
\regfield{(reserved)}{1}{3}{0}%
\regfield{CRYPTO\_DMA\_AHB\_TESTMODE}{3}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAAHBTESTMODE}\item [CRYPTO\_DMA\_AHB\_TESTMODE] Reserved (R/W)
\label{fielddesc:CRYPTODMAAHBTESTADDR}\item [CRYPTO\_DMA\_AHB\_TESTADDR] Reserved (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_AES\_SHA\_SELECT\_REG}{\hexprefix{}0064}\label{regdesc:CRYPTODMAAESSHASELECTREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{CRYPTO\_DMA\_AES\_SHA\_SELECT}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAAESSHASELECT}\item [CRYPTO\_DMA\_AES\_SHA\_SELECT] Select one between AES and SHA to use DMA.  0: AES. 1:SHA. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_PD\_CONF\_REG}{\hexprefix{}0068}\label{regdesc:CRYPTODMAPDCONFREG}
\regfield{(reserved)}{25}{7}{0000000000000000000000000}%
\regfield{CRYPTO\_DMA\_RAM\_CLK\_FO}{1}{6}{{0}}%
\regfield{CRYPTO\_DMA\_RAM\_FORCE\_PU}{1}{5}{{1}}%
\regfield{CRYPTO\_DMA\_RAM\_FORCE\_PD}{1}{4}{{0}}%
\regfield{(reserved)}{4}{0}{0000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMARAMFORCEPD}\item [CRYPTO\_DMA\_RAM\_FORCE\_PD] Force power down signal to RAM. 0: force RAM power up; 1: only when CRYPTO\_DMA\_RAM\_FORCE\_PU is 0, power down RAM. (R/W)
\label{fielddesc:CRYPTODMARAMFORCEPU}\item [CRYPTO\_DMA\_RAM\_FORCE\_PU] Force power up signal to RAM. 0: only when CRYPTO\_DMA\_RAM\_FORCE\_PD is 1, power down RAM; 1: force RAM power up. (R/W)
\label{fielddesc:CRYPTODMARAMCLKFO}\item [CRYPTO\_DMA\_RAM\_CLK\_FO] 1: Force to open the clock and bypass the gate-clock when accessing the RAM in DMA. 0: A gate-clock will be used when accessing the RAM in DMA. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_DATE\_REG}{\hexprefix{}00FC}\label{regdesc:CRYPTODMADATEREG}
\regfield{CRYPTO\_DMA\_DATE}{32}{0}{{\hexprefix{}19050700}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMADATE}\item [CRYPTO\_DMA\_DATE] This is the version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_INT\_RAW\_REG}{\hexprefix{}0004}\label{regdesc:CRYPTODMAINTRAWREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{CRYPTO\_DMA\_INFIFO\_FULL\_WM\_INT\_RAW}{1}{9}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_TOTAL\_EOF\_INT\_RAW}{1}{8}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_DSCR\_EMPTY\_INT\_RAW}{1}{7}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_DSCR\_ERR\_INT\_RAW}{1}{6}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_DSCR\_ERR\_INT\_RAW}{1}{5}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_EOF\_INT\_RAW}{1}{4}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_DONE\_INT\_RAW}{1}{3}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_ERR\_EOF\_INT\_RAW}{1}{2}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_SUC\_EOF\_INT\_RAW}{1}{1}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_DONE\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAINDONEINTRAW}\item [CRYPTO\_DMA\_IN\_DONE\_INT\_RAW] The raw interrupt status. Set when the last data of one frame is received or the receive buffer is full indicated by receive descriptor. (RO)
\label{fielddesc:CRYPTODMAINSUCEOFINTRAW}\item [CRYPTO\_DMA\_IN\_SUC\_EOF\_INT\_RAW] The raw interrupt status. Set when the last data of one frame is received by Crypto DMA RX FIFO. (RO)
\label{fielddesc:CRYPTODMAINERREOFINTRAW}\item [CRYPTO\_DMA\_IN\_ERR\_EOF\_INT\_RAW] Reserved (RO)
\label{fielddesc:CRYPTODMAOUTDONEINTRAW}\item [CRYPTO\_DMA\_OUT\_DONE\_INT\_RAW] The raw interrupt status. Set when all data indicated by one transmit descriptor has been pushed into TX FIFO. (RO)
\label{fielddesc:CRYPTODMAOUTEOFINTRAW}\item [CRYPTO\_DMA\_OUT\_EOF\_INT\_RAW] The raw interrupt status. Set when Out EOF flag is generated. (RO)
\label{fielddesc:CRYPTODMAINDSCRERRINTRAW}\item [CRYPTO\_DMA\_IN\_DSCR\_ERR\_INT\_RAW] The raw interrupt status. Set when detecting receive descriptor error, including owner error, the second and third word error of receive descriptor. (RO)
\label{fielddesc:CRYPTODMAOUTDSCRERRINTRAW}\item [CRYPTO\_DMA\_OUT\_DSCR\_ERR\_INT\_RAW] The raw interrupt status. Set when detecting transmit descriptor error, including owner error, the second and third word error of transmit descriptor. (RO)
\label{fielddesc:CRYPTODMAINDSCREMPTYINTRAW}\item [CRYPTO\_DMA\_IN\_DSCR\_EMPTY\_INT\_RAW] The raw interrupt status. Set when receiving data is completed and no more receive descriptor. (RO)
\label{fielddesc:CRYPTODMAOUTTOTALEOFINTRAW}\item [CRYPTO\_DMA\_OUT\_TOTAL\_EOF\_INT\_RAW] The raw interrupt status. Set when data corresponding to all transmit descriptor and the last descriptor with valid EOF is transmitted out. (RO)
\label{fielddesc:CRYPTODMAINFIFOFULLWMINTRAW}\item [CRYPTO\_DMA\_INFIFO\_FULL\_WM\_INT\_RAW] The raw interrupt status. Set when received data byte number is up to threshold configured by CRYPTO\_DMA\_INFIFO\_FULL\_THRS in RX FIFO. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_INT\_ST\_REG}{\hexprefix{}0008}\label{regdesc:CRYPTODMAINTSTREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{CRYPTO\_DMA\_INFIFO\_FULL\_WM\_INT\_ST}{1}{9}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_TOTAL\_EOF\_INT\_ST}{1}{8}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_DSCR\_EMPTY\_INT\_ST}{1}{7}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_DSCR\_ERR\_INT\_ST}{1}{6}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_DSCR\_ERR\_INT\_ST}{1}{5}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_EOF\_INT\_ST}{1}{4}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_DONE\_INT\_ST}{1}{3}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_ERR\_EOF\_INT\_ST}{1}{2}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_SUC\_EOF\_INT\_ST}{1}{1}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_DONE\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAINDONEINTST}\item [CRYPTO\_DMA\_IN\_DONE\_INT\_ST] The masked interrupt status bit for the CRYPTO\_DMA\_IN\_DONE\_INT interrupt. (RO)
\label{fielddesc:CRYPTODMAINSUCEOFINTST}\item [CRYPTO\_DMA\_IN\_SUC\_EOF\_INT\_ST] The masked interrupt status bit for the CRYPTO\_DMA\_IN\_SUC\_EOF\_INT interrupt. (RO)
\label{fielddesc:CRYPTODMAINERREOFINTST}\item [CRYPTO\_DMA\_IN\_ERR\_EOF\_INT\_ST] Reserved (RO)
\label{fielddesc:CRYPTODMAOUTDONEINTST}\item [CRYPTO\_DMA\_OUT\_DONE\_INT\_ST] The masked interrupt status bit for the CRYPTO\_DMA\_OUT\_DONE\_INT interrupt. (RO)
\label{fielddesc:CRYPTODMAOUTEOFINTST}\item [CRYPTO\_DMA\_OUT\_EOF\_INT\_ST] The masked interrupt status bit for the CRYPTO\_DMA\_OUT\_EOF\_INT interrupt. (RO)
\label{fielddesc:CRYPTODMAINDSCRERRINTST}\item [CRYPTO\_DMA\_IN\_DSCR\_ERR\_INT\_ST] The masked interrupt status bit for the CRYPTO\_DMA\_IN\_DSCR\_ERR\_INT interrupt. (RO)
\label{fielddesc:CRYPTODMAOUTDSCRERRINTST}\item [CRYPTO\_DMA\_OUT\_DSCR\_ERR\_INT\_ST] The masked interrupt status bit for the CRYPTO\_DMA\_OUT\_DSCR\_ERR\_INT interrupt. (RO)
\label{fielddesc:CRYPTODMAINDSCREMPTYINTST}\item [CRYPTO\_DMA\_IN\_DSCR\_EMPTY\_INT\_ST] The masked interrupt status bit for the CRYPTO\_DMA\_IN\_DSCR\_EMPTY\_INT interrupt. (RO)
\label{fielddesc:CRYPTODMAOUTTOTALEOFINTST}\item [CRYPTO\_DMA\_OUT\_TOTAL\_EOF\_INT\_ST] The masked interrupt status bit for the CRYPTO\_DMA\_OUT\_TOTAL\_EOF\_INT interrupt. (RO)
\label{fielddesc:CRYPTODMAINFIFOFULLWMINTST}\item [CRYPTO\_DMA\_INFIFO\_FULL\_WM\_INT\_ST] The masked interrupt status bit for the CRYPTO\_DMA\_INFIFO\_FULL\_WM\_INT interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_INT\_ENA\_REG}{\hexprefix{}000C}\label{regdesc:CRYPTODMAINTENAREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{CRYPTO\_DMA\_INFIFO\_FULL\_WM\_INT\_ENA}{1}{9}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_TOTAL\_EOF\_INT\_ENA}{1}{8}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_DSCR\_EMPTY\_INT\_ENA}{1}{7}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_DSCR\_ERR\_INT\_ENA}{1}{6}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_DSCR\_ERR\_INT\_ENA}{1}{5}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_EOF\_INT\_ENA}{1}{4}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_DONE\_INT\_ENA}{1}{3}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_ERR\_EOF\_INT\_ENA}{1}{2}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_SUC\_EOF\_INT\_ENA}{1}{1}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_DONE\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAINDONEINTENA}\item [CRYPTO\_DMA\_IN\_DONE\_INT\_ENA] The interrupt enable bit for the CRYPTO\_DMA\_IN\_DONE\_INT interrupt. (R/W)
\label{fielddesc:CRYPTODMAINSUCEOFINTENA}\item [CRYPTO\_DMA\_IN\_SUC\_EOF\_INT\_ENA] The interrupt enable bit for the CRYPTO\_DMA\_IN\_SUC\_EOF\_INT interrupt. (R/W)
\label{fielddesc:CRYPTODMAINERREOFINTENA}\item [CRYPTO\_DMA\_IN\_ERR\_EOF\_INT\_ENA] Reserved (R/W)
\label{fielddesc:CRYPTODMAOUTDONEINTENA}\item [CRYPTO\_DMA\_OUT\_DONE\_INT\_ENA] The interrupt enable bit for the CRYPTO\_DMA\_OUT\_DONE\_INT interrupt. (R/W)
\label{fielddesc:CRYPTODMAOUTEOFINTENA}\item [CRYPTO\_DMA\_OUT\_EOF\_INT\_ENA] The interrupt enable bit for the CRYPTO\_DMA\_OUT\_EOF\_INT interrupt. (R/W)
\label{fielddesc:CRYPTODMAINDSCRERRINTENA}\item [CRYPTO\_DMA\_IN\_DSCR\_ERR\_INT\_ENA] The interrupt enable bit for the CRYPTO\_DMA\_IN\_DSCR\_ERR\_INT interrupt. (R/W)
\label{fielddesc:CRYPTODMAOUTDSCRERRINTENA}\item [CRYPTO\_DMA\_OUT\_DSCR\_ERR\_INT\_ENA] The interrupt enable bit for the CRYPTO\_DMA\_OUT\_DSCR\_ERR\_INT interrupt. (R/W)
\label{fielddesc:CRYPTODMAINDSCREMPTYINTENA}\item [CRYPTO\_DMA\_IN\_DSCR\_EMPTY\_INT\_ENA] The interrupt enable bit for the CRYPTO\_DMA\_IN\_DSCR\_EMPTY\_INT interrupt. (R/W)
\label{fielddesc:CRYPTODMAOUTTOTALEOFINTENA}\item [CRYPTO\_DMA\_OUT\_TOTAL\_EOF\_INT\_ENA] The interrupt enable bit for the CRYPTO\_DMA\_OUT\_TOTAL\_EOF\_INT interrupt. (R/W)
\label{fielddesc:CRYPTODMAINFIFOFULLWMINTENA}\item [CRYPTO\_DMA\_INFIFO\_FULL\_WM\_INT\_ENA] The interrupt enable bit for the CRYPTO\_DMA\_INFIFO\_FULL\_WM\_INT interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_INT\_CLR\_REG}{\hexprefix{}0010}\label{regdesc:CRYPTODMAINTCLRREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{CRYPTO\_DMA\_INFIFO\_FULL\_WM\_INT\_CLR}{1}{9}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_TOTAL\_EOF\_INT\_CLR}{1}{8}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_DSCR\_EMPTY\_INT\_CLR}{1}{7}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_DSCR\_ERR\_INT\_CLR}{1}{6}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_DSCR\_ERR\_INT\_CLR}{1}{5}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_EOF\_INT\_CLR}{1}{4}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_DONE\_INT\_CLR}{1}{3}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_ERR\_EOF\_INT\_CLR}{1}{2}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_SUC\_EOF\_INT\_CLR}{1}{1}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_DONE\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAINDONEINTCLR}\item [CRYPTO\_DMA\_IN\_DONE\_INT\_CLR] Set this bit to clear the CRYPTO\_DMA\_IN\_DONE\_INT interrupt. (WO)
\label{fielddesc:CRYPTODMAINSUCEOFINTCLR}\item [CRYPTO\_DMA\_IN\_SUC\_EOF\_INT\_CLR] Set this bit to clear the CRYPTO\_DMA\_IN\_SUC\_EOF\_INT interrupt. (WO)
\label{fielddesc:CRYPTODMAINERREOFINTCLR}\item [CRYPTO\_DMA\_IN\_ERR\_EOF\_INT\_CLR] Reserved (WO)
\label{fielddesc:CRYPTODMAOUTDONEINTCLR}\item [CRYPTO\_DMA\_OUT\_DONE\_INT\_CLR] Set this bit to clear the CRYPTO\_DMA\_OUT\_DONE\_INT interrupt. (WO)
\label{fielddesc:CRYPTODMAOUTEOFINTCLR}\item [CRYPTO\_DMA\_OUT\_EOF\_INT\_CLR] Set this bit to clear the CRYPTO\_DMA\_OUT\_EOF\_INT interrupt. (WO)
\label{fielddesc:CRYPTODMAINDSCRERRINTCLR}\item [CRYPTO\_DMA\_IN\_DSCR\_ERR\_INT\_CLR] Set this bit to clear the CRYPTO\_DMA\_IN\_DSCR\_ERR\_INT interrupt. (WO)
\label{fielddesc:CRYPTODMAOUTDSCRERRINTCLR}\item [CRYPTO\_DMA\_OUT\_DSCR\_ERR\_INT\_CLR] Set this bit to clear the CRYPTO\_DMA\_OUT\_DSCR\_ERR\_INT interrupt. (WO)
\label{fielddesc:CRYPTODMAINDSCREMPTYINTCLR}\item [CRYPTO\_DMA\_IN\_DSCR\_EMPTY\_INT\_CLR] Set this bit to clear the CRYPTO\_DMA\_IN\_DSCR\_EMPTY\_INT interrupt. (WO)
\label{fielddesc:CRYPTODMAOUTTOTALEOFINTCLR}\item [CRYPTO\_DMA\_OUT\_TOTAL\_EOF\_INT\_CLR] Set this bit to clear the CRYPTO\_DMA\_OUT\_TOTAL\_EOF\_INT interrupt. (WO)
\label{fielddesc:CRYPTODMAINFIFOFULLWMINTCLR}\item [CRYPTO\_DMA\_INFIFO\_FULL\_WM\_INT\_CLR] Set this bit to clear the CRYPTO\_DMA\_INFIFO\_FULL\_WM\_INT interrupt. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_OUT\_STATUS\_REG}{\hexprefix{}0014}\label{regdesc:CRYPTODMAOUTSTATUSREG}
\regfield{(reserved)}{30}{2}{000000000000000000000000000000}%
\regfield{CRYPTO\_DMA\_OUT\_EMPTY}{1}{1}{{1}}%
\regfield{CRYPTO\_DMA\_OUT\_FULL}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAOUTFULL}\item [CRYPTO\_DMA\_OUT\_FULL] 1: DMA TX FIFO is full. (RO)
\label{fielddesc:CRYPTODMAOUTEMPTY}\item [CRYPTO\_DMA\_OUT\_EMPTY] 1: DMA TX FIFO is empty. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_IN\_STATUS\_REG}{\hexprefix{}001C}\label{regdesc:CRYPTODMAINSTATUSREG}
\regfield{(reserved)}{30}{2}{000000000000000000000000000000}%
\regfield{CRYPTO\_DMA\_IN\_EMPTY}{1}{1}{{1}}%
\regfield{CRYPTO\_DMA\_IN\_FULL}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAINFULL}\item [CRYPTO\_DMA\_IN\_FULL] 1: DMA RX FIFO is full. (RO)
\label{fielddesc:CRYPTODMAINEMPTY}\item [CRYPTO\_DMA\_IN\_EMPTY] 1: DMA RX FIFO is empty. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_STATE0\_REG}{\hexprefix{}0030}\label{regdesc:CRYPTODMASTATE0REG}
\regfield{(reserved)}{5}{27}{00000}%
\regfield{CRYPTO\_DMA\_INFIFO\_CNT\_DEBUG}{4}{23}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_STATE}{3}{20}{{0}}%
\regfield{CRYPTO\_DMA\_IN\_DSCR\_STATE}{2}{18}{{0}}%
\regfield{CRYPTO\_DMA\_INLINK\_DSCR\_ADDR}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAINLINKDSCRADDR}\item [CRYPTO\_DMA\_INLINK\_DSCR\_ADDR] This register stores the lower 18 bits of the next receive descriptor address that is pre-read (but not processed yet). If the current receive descriptor is the last descriptor, then this field represents the address of the current receive descriptor. (RO)
\label{fielddesc:CRYPTODMAINDSCRSTATE}\item [CRYPTO\_DMA\_IN\_DSCR\_STATE] Reserved (RO)
\label{fielddesc:CRYPTODMAINSTATE}\item [CRYPTO\_DMA\_IN\_STATE] Reserved (RO)
\label{fielddesc:CRYPTODMAINFIFOCNTDEBUG}\item [CRYPTO\_DMA\_INFIFO\_CNT\_DEBUG] This register stores the byte number of the data in the receive descriptor's FIFO. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_STATE1\_REG}{\hexprefix{}0034}\label{regdesc:CRYPTODMASTATE1REG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{CRYPTO\_DMA\_OUTFIFO\_CNT}{5}{23}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_STATE}{3}{20}{{0}}%
\regfield{CRYPTO\_DMA\_OUT\_DSCR\_STATE}{2}{18}{{0}}%
\regfield{CRYPTO\_DMA\_OUTLINK\_DSCR\_ADDR}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAOUTLINKDSCRADDR}\item [CRYPTO\_DMA\_OUTLINK\_DSCR\_ADDR] This register stores the lower 18 bits of the next transmit descriptor address that is pre-read (but not processed yet). If the current transmit descriptor is the last descriptor, then this field represents the address of the current transmit descriptor. (RO)
\label{fielddesc:CRYPTODMAOUTDSCRSTATE}\item [CRYPTO\_DMA\_OUT\_DSCR\_STATE] Reserved (RO)
\label{fielddesc:CRYPTODMAOUTSTATE}\item [CRYPTO\_DMA\_OUT\_STATE] Reserved (RO)
\label{fielddesc:CRYPTODMAOUTFIFOCNT}\item [CRYPTO\_DMA\_OUTFIFO\_CNT] This register stores the byte number of the data in the transmit descriptor's FIFO. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_OUT\_EOF\_DES\_ADDR\_REG}{\hexprefix{}0038}\label{regdesc:CRYPTODMAOUTEOFDESADDRREG}
\regfield{CRYPTO\_DMA\_OUT\_EOF\_DES\_ADDR}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAOUTEOFDESADDR}\item [CRYPTO\_DMA\_OUT\_EOF\_DES\_ADDR] This register stores the address of the transmit descriptor when the EOF bit in this descriptor is 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_IN\_SUC\_EOF\_DES\_ADDR\_REG}{\hexprefix{}003C}\label{regdesc:CRYPTODMAINSUCEOFDESADDRREG}
\regfield{CRYPTO\_DMA\_IN\_SUC\_EOF\_DES\_ADDR}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAINSUCEOFDESADDR}\item [CRYPTO\_DMA\_IN\_SUC\_EOF\_DES\_ADDR] This register stores the address of the receive descriptor when received successful EOF. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_IN\_ERR\_EOF\_DES\_ADDR\_REG}{\hexprefix{}0040}\label{regdesc:CRYPTODMAINERREOFDESADDRREG}
\regfield{CRYPTO\_DMA\_IN\_ERR\_EOF\_DES\_ADDR}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAINERREOFDESADDR}\item [CRYPTO\_DMA\_IN\_ERR\_EOF\_DES\_ADDR] This register stores the address of the receive descriptor when there are some errors in this descriptor. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_OUT\_EOF\_BFR\_DES\_ADDR\_REG}{\hexprefix{}0044}\label{regdesc:CRYPTODMAOUTEOFBFRDESADDRREG}
\regfield{CRYPTO\_DMA\_OUT\_EOF\_BFR\_DES\_ADDR}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAOUTEOFBFRDESADDR}\item [CRYPTO\_DMA\_OUT\_EOF\_BFR\_DES\_ADDR] This register stores the address of the transmit descriptor before the last transmit descriptor. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_IN\_DSCR\_REG}{\hexprefix{}004C}\label{regdesc:CRYPTODMAINDSCRREG}
\regfield{CRYPTO\_DMA\_INLINK\_DSCR}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAINLINKDSCR}\item [CRYPTO\_DMA\_INLINK\_DSCR] Represents the address of the next receive descriptor x+1 pointed by the current receive descriptor that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_IN\_DSCR\_BF0\_REG}{\hexprefix{}0050}\label{regdesc:CRYPTODMAINDSCRBF0REG}
\regfield{CRYPTO\_DMA\_INLINK\_DSCR\_BF0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAINLINKDSCRBF0}\item [CRYPTO\_DMA\_INLINK\_DSCR\_BF0] Represents the address of the current receive descriptor x that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_OUT\_DSCR\_REG}{\hexprefix{}0058}\label{regdesc:CRYPTODMAOUTDSCRREG}
\regfield{CRYPTO\_DMA\_OUTLINK\_DSCR}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAOUTLINKDSCR}\item [CRYPTO\_DMA\_OUTLINK\_DSCR] Represents the address of the next transmit descriptor y+1 pointed by the current transmit descriptor that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{CRYPTO\_DMA\_OUT\_DSCR\_BF0\_REG}{\hexprefix{}005C}\label{regdesc:CRYPTODMAOUTDSCRBF0REG}
\regfield{CRYPTO\_DMA\_OUTLINK\_DSCR\_BF0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:CRYPTODMAOUTLINKDSCRBF0}\item [CRYPTO\_DMA\_OUTLINK\_DSCR\_BF0] Represents the address of the current transmit descriptor y that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}

