\begin{register}{H}{AHB\_DMA\_IN\_INT\_RAW\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0000+0x10*\regindex{n}}\label{regdesc:AHBDMAININTRAWCHNREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{AHB\_DMA\_IN\_RESP\_ERR\_CH\regindex{n}\_INT\_RAW}{1}{7}{{0}}%
\regfield{AHB\_DMA\_INFIFO\_UDF\_CH\regindex{n}\_INT\_RAW}{1}{6}{{0}}%
\regfield{AHB\_DMA\_INFIFO\_OVF\_CH\regindex{n}\_INT\_RAW}{1}{5}{{0}}%
\regfield{AHB\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_RAW}{1}{4}{{0}}%
\regfield{AHB\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_RAW}{1}{3}{{0}}%
\regfield{AHB\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_RAW}{1}{2}{{0}}%
\regfield{AHB\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_RAW}{1}{1}{{0}}%
\regfield{AHB\_DMA\_IN\_DONE\_CH\regindex{n}\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAINDONECHNINTRAW}\item [AHB\_DMA\_IN\_DONE\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AHB\_DMA\_IN\_DONE\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AHBDMAINSUCEOFCHNINTRAW}\item [AHB\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AHB\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT. For UHCI, this bit turns to 1 when the last data byte pointed by one receive descriptor has been received and no data error is detected for RX channel \regindex{n}. (R/WTC/SS)
\label{fielddesc:AHBDMAINERREOFCHNINTRAW}\item [AHB\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AHB\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT. Valid only for UHCI. (R/WTC/SS)
\label{fielddesc:AHBDMAINDSCRERRCHNINTRAW}\item [AHB\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AHB\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AHBDMAINDSCREMPTYCHNINTRAW}\item [AHB\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AHB\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AHBDMAINFIFOOVFCHNINTRAW}\item [AHB\_DMA\_INFIFO\_OVF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AHB\_DMA\_INFIFO\_OVF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AHBDMAINFIFOUDFCHNINTRAW}\item [AHB\_DMA\_INFIFO\_UDF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AHB\_DMA\_INFIFO\_UDF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AHBDMAINAHBINFRESPERRCHNINTRAW}\item [AHB\_DMA\_IN\_RESP\_ERR\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AHB\_DMA\_IN\_RESP\_ERR\_CH\regindex{n}\_INT. (R/WTC/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_IN\_INT\_ST\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0004+0x10*\regindex{n}}\label{regdesc:AHBDMAININTSTCHNREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{AHB\_DMA\_IN\_RESP\_ERR\_CH\regindex{n}\_INT\_ST}{1}{7}{{0}}%
\regfield{AHB\_DMA\_INFIFO\_UDF\_CH\regindex{n}\_INT\_ST}{1}{6}{{0}}%
\regfield{AHB\_DMA\_INFIFO\_OVF\_CH\regindex{n}\_INT\_ST}{1}{5}{{0}}%
\regfield{AHB\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_ST}{1}{4}{{0}}%
\regfield{AHB\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_ST}{1}{3}{{0}}%
\regfield{AHB\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_ST}{1}{2}{{0}}%
\regfield{AHB\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_ST}{1}{1}{{0}}%
\regfield{AHB\_DMA\_IN\_DONE\_CH\regindex{n}\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAINDONECHNINTST}\item [AHB\_DMA\_IN\_DONE\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AHB\_DMA\_IN\_DONE\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AHBDMAINSUCEOFCHNINTST}\item [AHB\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AHB\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AHBDMAINERREOFCHNINTST}\item [AHB\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AHB\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AHBDMAINDSCRERRCHNINTST}\item [AHB\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AHB\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AHBDMAINDSCREMPTYCHNINTST}\item [AHB\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AHB\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AHBDMAINFIFOOVFCHNINTST}\item [AHB\_DMA\_INFIFO\_OVF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AHB\_DMA\_INFIFO\_OVF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AHBDMAINFIFOUDFCHNINTST}\item [AHB\_DMA\_INFIFO\_UDF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AHB\_DMA\_INFIFO\_UDF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AHBDMAINAHBINFRESPERRCHNINTST}\item [AHB\_DMA\_IN\_RESP\_ERR\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AHB\_DMA\_IN\_RESP\_ERR\_CH\regindex{n}\_INT. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_IN\_INT\_ENA\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0008+0x10*\regindex{n}}\label{regdesc:AHBDMAININTENACHNREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{AHB\_DMA\_IN\_RESP\_ERR\_CH\regindex{n}\_INT\_ENA}{1}{7}{{0}}%
\regfield{AHB\_DMA\_INFIFO\_UDF\_CH\regindex{n}\_INT\_ENA}{1}{6}{{0}}%
\regfield{AHB\_DMA\_INFIFO\_OVF\_CH\regindex{n}\_INT\_ENA}{1}{5}{{0}}%
\regfield{AHB\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_ENA}{1}{4}{{0}}%
\regfield{AHB\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_ENA}{1}{3}{{0}}%
\regfield{AHB\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_ENA}{1}{2}{{0}}%
\regfield{AHB\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_ENA}{1}{1}{{0}}%
\regfield{AHB\_DMA\_IN\_DONE\_CH\regindex{n}\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAINDONECHNINTENA}\item [AHB\_DMA\_IN\_DONE\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AHB\_DMA\_IN\_DONE\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AHBDMAINSUCEOFCHNINTENA}\item [AHB\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AHB\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AHBDMAINERREOFCHNINTENA}\item [AHB\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AHB\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AHBDMAINDSCRERRCHNINTENA}\item [AHB\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AHB\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AHBDMAINDSCREMPTYCHNINTENA}\item [AHB\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AHB\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AHBDMAINFIFOOVFCHNINTENA}\item [AHB\_DMA\_INFIFO\_OVF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AHB\_DMA\_INFIFO\_OVF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AHBDMAINFIFOUDFCHNINTENA}\item [AHB\_DMA\_INFIFO\_UDF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AHB\_DMA\_INFIFO\_UDF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AHBDMAINAHBINFRESPERRCHNINTENA}\item [AHB\_DMA\_IN\_RESP\_ERR\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AHB\_DMA\_IN\_RESP\_ERR\_CH\regindex{n}\_INT. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_IN\_INT\_CLR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x000C+0x10*\regindex{n}}\label{regdesc:AHBDMAININTCLRCHNREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{AHB\_DMA\_IN\_RESP\_ERR\_CH\regindex{n}\_INT\_CLR}{1}{7}{{0}}%
\regfield{AHB\_DMA\_INFIFO\_UDF\_CH\regindex{n}\_INT\_CLR}{1}{6}{{0}}%
\regfield{AHB\_DMA\_INFIFO\_OVF\_CH\regindex{n}\_INT\_CLR}{1}{5}{{0}}%
\regfield{AHB\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_CLR}{1}{4}{{0}}%
\regfield{AHB\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_CLR}{1}{3}{{0}}%
\regfield{AHB\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_CLR}{1}{2}{{0}}%
\regfield{AHB\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_CLR}{1}{1}{{0}}%
\regfield{AHB\_DMA\_IN\_DONE\_CH\regindex{n}\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAINDONECHNINTCLR}\item [AHB\_DMA\_IN\_DONE\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AHB\_DMA\_IN\_DONE\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AHBDMAINSUCEOFCHNINTCLR}\item [AHB\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AHB\_DMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AHBDMAINERREOFCHNINTCLR}\item [AHB\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AHB\_DMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AHBDMAINDSCRERRCHNINTCLR}\item [AHB\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AHB\_DMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AHBDMAINDSCREMPTYCHNINTCLR}\item [AHB\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AHB\_DMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AHBDMAINFIFOOVFCHNINTCLR}\item [AHB\_DMA\_INFIFO\_OVF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AHB\_DMA\_INFIFO\_OVF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AHBDMAINFIFOUDFCHNINTCLR}\item [AHB\_DMA\_INFIFO\_UDF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AHB\_DMA\_INFIFO\_UDF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AHBDMAINAHBINFRESPERRCHNINTCLR}\item [AHB\_DMA\_IN\_RESP\_ERR\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AHB\_DMA\_IN\_RESP\_ERR\_CH\regindex{n}\_INT. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_INT\_RAW\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0030+0x10*\regindex{n}}\label{regdesc:AHBDMAOUTINTRAWCHNREG}
\regfield{(reserved)}{25}{7}{0000000000000000000000000}%
\regfield{AHB\_DMA\_OUT\_RESP\_ERR\_CH\regindex{n}\_INT\_RAW}{1}{6}{{0}}%
\regfield{AHB\_DMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT\_RAW}{1}{5}{{0}}%
\regfield{AHB\_DMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT\_RAW}{1}{4}{{0}}%
\regfield{AHB\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_RAW}{1}{3}{{0}}%
\regfield{AHB\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_RAW}{1}{2}{{0}}%
\regfield{AHB\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT\_RAW}{1}{1}{{0}}%
\regfield{AHB\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAOUTDONECHNINTRAW}\item [AHB\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AHB\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AHBDMAOUTEOFCHNINTRAW}\item [AHB\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AHB\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AHBDMAOUTDSCRERRCHNINTRAW}\item [AHB\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AHB\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AHBDMAOUTTOTALEOFCHNINTRAW}\item [AHB\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AHB\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AHBDMAOUTFIFOOVFCHNINTRAW}\item [AHB\_DMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AHB\_DMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AHBDMAOUTFIFOUDFCHNINTRAW}\item [AHB\_DMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AHB\_DMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:AHBDMAOUTRESPERRINTRAW}\item [AHB\_DMA\_OUT\_RESP\_ERR\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of AHB\_DMA\_OUT\_RESP\_ERR\_CH\regindex{n}\_INT. (R/WTC/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_INT\_ST\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0034+0x10*\regindex{n}}\label{regdesc:AHBDMAOUTINTSTCHNREG}
\regfield{(reserved)}{25}{7}{0000000000000000000000000}%
\regfield{AHB\_DMA\_OUT\_RESP\_ERR\_CH\regindex{n}\_INT\_ST}{1}{6}{{0}}%
\regfield{AHB\_DMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT\_ST}{1}{5}{{0}}%
\regfield{AHB\_DMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT\_ST}{1}{4}{{0}}%
\regfield{AHB\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_ST}{1}{3}{{0}}%
\regfield{AHB\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_ST}{1}{2}{{0}}%
\regfield{AHB\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT\_ST}{1}{1}{{0}}%
\regfield{AHB\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAOUTDONECHNINTST}\item [AHB\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AHB\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AHBDMAOUTEOFCHNINTST}\item [AHB\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AHB\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AHBDMAOUTDSCRERRCHNINTST}\item [AHB\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AHB\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AHBDMAOUTTOTALEOFCHNINTST}\item [AHB\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AHB\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AHBDMAOUTFIFOOVFCHNINTST}\item [AHB\_DMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AHB\_DMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AHBDMAOUTFIFOUDFCHNINTST}\item [AHB\_DMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AHB\_DMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:AHBDMAOUTRESPERRINTST}\item [AHB\_DMA\_OUT\_RESP\_ERR\_CH\regindex{n}\_INT\_ST] The masked interrupt status of AHB\_DMA\_OUT\_RESP\_ERR\_CH\regindex{n}\_INT. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_INT\_ENA\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0038+0x10*\regindex{n}}\label{regdesc:AHBDMAOUTINTENACHNREG}
\regfield{(reserved)}{25}{7}{0000000000000000000000000}%
\regfield{AHB\_DMA\_OUT\_RESP\_ERR\_CH\regindex{n}\_INT\_ENA}{1}{6}{{0}}%
\regfield{AHB\_DMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT\_ENA}{1}{5}{{0}}%
\regfield{AHB\_DMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT\_ENA}{1}{4}{{0}}%
\regfield{AHB\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_ENA}{1}{3}{{0}}%
\regfield{AHB\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_ENA}{1}{2}{{0}}%
\regfield{AHB\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT\_ENA}{1}{1}{{0}}%
\regfield{AHB\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAOUTDONECHNINTENA}\item [AHB\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AHB\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AHBDMAOUTEOFCHNINTENA}\item [AHB\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AHB\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AHBDMAOUTDSCRERRCHNINTENA}\item [AHB\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AHB\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AHBDMAOUTTOTALEOFCHNINTENA}\item [AHB\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AHB\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AHBDMAOUTFIFOOVFCHNINTENA}\item [AHB\_DMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AHB\_DMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AHBDMAOUTFIFOUDFCHNINTENA}\item [AHB\_DMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AHB\_DMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:AHBDMAOUTRESPERRINTENA}\item [AHB\_DMA\_OUT\_RESP\_ERR\_CH\regindex{n}\_INT\_ENA] Write 1 to enable AHB\_DMA\_OUT\_RESP\_ERR\_CH\regindex{n}\_INT. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_INT\_CLR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x003C+0x10*\regindex{n}}\label{regdesc:AHBDMAOUTINTCLRCHNREG}
\regfield{(reserved)}{25}{7}{0000000000000000000000000}%
\regfield{AHB\_DMA\_OUT\_RESP\_ERR\_CH\regindex{n}\_INT\_CLR}{1}{6}{{0}}%
\regfield{AHB\_DMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT\_CLR}{1}{5}{{0}}%
\regfield{AHB\_DMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT\_CLR}{1}{4}{{0}}%
\regfield{AHB\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_CLR}{1}{3}{{0}}%
\regfield{AHB\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_CLR}{1}{2}{{0}}%
\regfield{AHB\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT\_CLR}{1}{1}{{0}}%
\regfield{AHB\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAOUTDONECHNINTCLR}\item [AHB\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AHB\_DMA\_OUT\_DONE\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AHBDMAOUTEOFCHNINTCLR}\item [AHB\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AHB\_DMA\_OUT\_EOF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AHBDMAOUTDSCRERRCHNINTCLR}\item [AHB\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AHB\_DMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AHBDMAOUTTOTALEOFCHNINTCLR}\item [AHB\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AHB\_DMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AHBDMAOUTFIFOOVFCHNINTCLR}\item [AHB\_DMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AHB\_DMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AHBDMAOUTFIFOUDFCHNINTCLR}\item [AHB\_DMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AHB\_DMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:AHBDMAOUTRESPERRINTCLR}\item [AHB\_DMA\_OUT\_RESP\_ERR\_CH\regindex{n}\_INT\_CLR] Write 1 to clear AHB\_DMA\_OUT\_RESP\_ERR\_CH\regindex{n}\_INT. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_AHB\_TEST\_REG}{0x0060}\label{regdesc:AHBDMAAHBTESTREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{AHB\_DMA\_AHB\_TESTADDR}{2}{4}{{0}}%
\regfield{(reserved)}{1}{3}{0}%
\regfield{AHB\_DMA\_AHB\_TESTMODE}{3}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAAHBTESTMODE}\item [AHB\_DMA\_AHB\_TESTMODE] Reserved. (R/W)
\label{fielddesc:AHBDMAAHBTESTADDR}\item [AHB\_DMA\_AHB\_TESTADDR] Reserved. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_MISC\_CONF\_REG}{0x0064}\label{regdesc:AHBDMAMISCCONFREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{AHB\_DMA\_CLK\_EN}{1}{3}{{0}}%
\regfield{AHB\_DMA\_ARB\_PRI\_DIS}{1}{2}{{0}}%
\regfield{(reserved)}{1}{1}{0}%
\regfield{AHB\_DMA\_AHBM\_RST\_INTER}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAAHBMRSTINTER}\item [AHB\_DMA\_AHBM\_RST\_INTER] Write 1 and then 0 to reset the internal AHB FSM. (R/W)
\label{fielddesc:AHBDMAARBPRIDIS}\item [AHB\_DMA\_ARB\_PRI\_DIS] Configures whether to disable the priority arbitration.\\
0: Enable\\
1: Disable\\ (R/W)
\label{fielddesc:AHBDMACLKEN}\item [AHB\_DMA\_CLK\_EN] Configures AHB DMA clock gating.\\
0: Support clock only when the application writes registers\\
1: Always force the clock on for registers\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_IN\_CONF0\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0070+0xC0*\regindex{n}}\label{regdesc:AHBDMAINCONF0CHNREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{AHB\_DMA\_IN\_DATA\_BURST\_MODE\_SEL\_CH\regindex{n}}{2}{6}{{0}}%
\regfield{AHB\_DMA\_IN\_ETM\_EN\_CH\regindex{n}}{1}{5}{{0}}%
\regfield{AHB\_DMA\_MEM\_TRANS\_EN\_CH\regindex{n}}{1}{4}{{0}}%
\regfield{(reserved)}{1}{3}{0}%
\regfield{AHB\_DMA\_INDSCR\_BURST\_EN\_CH\regindex{n}}{1}{2}{{0}}%
\regfield{AHB\_DMA\_IN\_LOOP\_TEST\_CH\regindex{n}}{1}{1}{{0}}%
\regfield{AHB\_DMA\_IN\_RST\_CH\regindex{n}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAINRSTCHN}\item [AHB\_DMA\_IN\_RST\_CH\regindex{n}] Write 1 and then 0 to reset RX channel \regindex{n} FSM and RX FIFO pointer. (R/W)
\label{fielddesc:AHBDMAINLOOPTESTCHN}\item [AHB\_DMA\_IN\_LOOP\_TEST\_CH\regindex{n}] Configures the owner bit value for inlink write-back. (R/W)
\label{fielddesc:AHBDMAINDSCRBURSTENCHN}\item [AHB\_DMA\_INDSCR\_BURST\_EN\_CH\regindex{n}] Configures whether to enable INCR burst transfer for RX channel \regindex{n} to read descriptors.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:AHBDMAMEMTRANSENCHN}\item [AHB\_DMA\_MEM\_TRANS\_EN\_CH\regindex{n}] Configures whether to enable memory-to-memory data transfer.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:AHBDMAINETMENCHN}\item [AHB\_DMA\_IN\_ETM\_EN\_CH\regindex{n}] Configures whether to enable ETM control for RX channel\regindex{n}.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:AHBDMAINDATABURSTMODESELCHN}\item [AHB\_DMA\_IN\_DATA\_BURST\_MODE\_SEL\_CH\regindex{n}] Configures maximum burst length for RX channel\regindex{n}.\\0: SINGLE\\ 1: INCR4\\ 2: INCR8\\ 3: Reserved\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_IN\_CONF1\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0074+0xC0*\regindex{n}}\label{regdesc:AHBDMAINCONF1CHNREG}
\regfield{(reserved)}{19}{13}{0000000000000000000}%
\regfield{AHB\_DMA\_IN\_CHECK\_OWNER\_CH\regindex{n}}{1}{12}{{0}}%
\regfield{(reserved)}{12}{0}{000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAINCHECKOWNERCHN}\item [AHB\_DMA\_IN\_CHECK\_OWNER\_CH\regindex{n}] Configures whether to enable owner bit check for RX channel \regindex{n}.\\
0: Disable\\
1: Enable\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_IN\_POP\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x007C+0xC0*\regindex{n}}\label{regdesc:AHBDMAINPOPCHNREG}
\regfield{(reserved)}{19}{13}{0000000000000000000}%
\regfield{AHB\_DMA\_INFIFO\_POP\_CH\regindex{n}}{1}{12}{{0}}%
\regfield{AHB\_DMA\_INFIFO\_RDATA\_CH\regindex{n}}{12}{0}{{0x800}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAINFIFORDATACHN}\item [AHB\_DMA\_INFIFO\_RDATA\_CH\regindex{n}] Represents the data popped from AHB DMA RX FIFO. (RO)
\label{fielddesc:AHBDMAINFIFOPOPCHN}\item [AHB\_DMA\_INFIFO\_POP\_CH\regindex{n}] Configures whether to pop data from AHB DMA RX FIFO.\\
0: Invalid. No effect\\
1: Pop\\ (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_IN\_LINK\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0080+0xC0*\regindex{n}}\label{regdesc:AHBDMAINLINKCHNREG}
\regfield{(reserved)}{27}{5}{000000000000000000000000000}%
\regfield{AHB\_DMA\_INLINK\_PARK\_CH\regindex{n}}{1}{4}{{1}}%
\regfield{AHB\_DMA\_INLINK\_RESTART\_CH\regindex{n}}{1}{3}{{0}}%
\regfield{AHB\_DMA\_INLINK\_START\_CH\regindex{n}}{1}{2}{{0}}%
\regfield{AHB\_DMA\_INLINK\_STOP\_CH\regindex{n}}{1}{1}{{0}}%
\regfield{AHB\_DMA\_INLINK\_AUTO\_RET\_CH\regindex{n}}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAINLINKAUTORETCHN}\item [AHB\_DMA\_INLINK\_AUTO\_RET\_CH\regindex{n}] Configures whether to return to the current receive descriptor's address when there are some errors in current receiving data.\\
0: Not return\\
1: Return\\ (R/W)
\label{fielddesc:AHBDMAINLINKSTOPCHN}\item [AHB\_DMA\_INLINK\_STOP\_CH\regindex{n}] Configures whether to stop RX channel \regindex{n} from receiving data.\\
0: Invalid. No effect\\
1: Stop\\ (WT)
\label{fielddesc:AHBDMAINLINKSTARTCHN}\item [AHB\_DMA\_INLINK\_START\_CH\regindex{n}] Configures whether to enable RX channel \regindex{n} for data transfer.\\
0: Disable\\
1: Enable\\ (WT)
\label{fielddesc:AHBDMAINLINKRESTARTCHN}\item [AHB\_DMA\_INLINK\_RESTART\_CH\regindex{n}] Configures whether to restart RX channel \regindex{n} for AHB DMA transfer.\\
0: Invalid. No effect\\
1: Restart\\ (WT)
\label{fielddesc:AHBDMAINLINKPARKCHN}\item [AHB\_DMA\_INLINK\_PARK\_CH\regindex{n}] Represents the status of the receive descriptor's FSM.\\
0: Running\\
1: Idle\\ (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_CONF0\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00D0+0xC0*(\regindex{n}-1)}\label{regdesc:AHBDMAOUTCONF0CHNREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{AHB\_DMA\_OUT\_DATA\_BURST\_MODE\_SEL\_CH\regindex{n}}{2}{8}{{0}}%
\regfield{(reserved)}{1}{7}{0}%
\regfield{AHB\_DMA\_OUT\_ETM\_EN\_CH\regindex{n}}{1}{6}{{0}}%
\regfield{(reserved)}{1}{5}{0}%
\regfield{AHB\_DMA\_OUTDSCR\_BURST\_EN\_CH\regindex{n}}{1}{4}{{0}}%
\regfield{AHB\_DMA\_OUT\_EOF\_MODE\_CH\regindex{n}}{1}{3}{{1}}%
\regfield{AHB\_DMA\_OUT\_AUTO\_WRBACK\_CH\regindex{n}}{1}{2}{{0}}%
\regfield{AHB\_DMA\_OUT\_LOOP\_TEST\_CH\regindex{n}}{1}{1}{{0}}%
\regfield{AHB\_DMA\_OUT\_RST\_CH\regindex{n}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAOUTRSTCHN}\item [AHB\_DMA\_OUT\_RST\_CH\regindex{n}] Configures the reset state of TX channel \regindex{n} FSM and TX FIFO pointer.\\
0: Release reset\\
1: Reset\\ (R/W)
\label{fielddesc:AHBDMAOUTLOOPTESTCHN}\item [AHB\_DMA\_OUT\_LOOP\_TEST\_CH\regindex{n}] Configures the owner bit value for outlink write-back. (R/W)
\label{fielddesc:AHBDMAOUTAUTOWRBACKCHN}\item [AHB\_DMA\_OUT\_AUTO\_WRBACK\_CH\regindex{n}] Configures whether to enable automatic outlink write-back when all the data in TX FIFO has been transmitted.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:AHBDMAOUTEOFMODECHN}\item [AHB\_DMA\_OUT\_EOF\_MODE\_CH\regindex{n}] Configures when to generate EOF flag.\\
0: EOF flag for TX channel \regindex{n} is generated when data to be transmitted has been pushed into FIFO in AHB DMA.\\
1: EOF flag for TX channel \regindex{n} is generated when data to be transmitted has been popped from FIFO in AHB DMA.\\ (R/W)
\label{fielddesc:AHBDMAOUTDSCRBURSTENCHN}\item [AHB\_DMA\_OUTDSCR\_BURST\_EN\_CH\regindex{n}] Configures whether to enable INCR burst transfer for TX channel \regindex{n} reading descriptors.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:AHBDMAOUTETMENCHN}\item [AHB\_DMA\_OUT\_ETM\_EN\_CH\regindex{n}] Configures whether to enable ETM control for TX channel \regindex{n}.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:AHBDMAOUTDATABURSTMODESELCHN}\item [AHB\_DMA\_OUT\_DATA\_BURST\_MODE\_SEL\_CH\regindex{n}] Configures maximum burst length for TX channel\regindex{n}.\\0: SINGLE\\ 1: INCR4\\ 2: INCR8\\ 3: Reserved\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_CONF1\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00D4+0xC0*\regindex{n}}\label{regdesc:AHBDMAOUTCONF1CHNREG}
\regfield{(reserved)}{19}{13}{0000000000000000000}%
\regfield{AHB\_DMA\_OUT\_CHECK\_OWNER\_CH\regindex{n}}{1}{12}{{0}}%
\regfield{(reserved)}{12}{0}{000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAOUTCHECKOWNERCHN}\item [AHB\_DMA\_OUT\_CHECK\_OWNER\_CH\regindex{n}] Configures whether to enable owner bit check for TX channel \regindex{n}.\\
0: Disable\\
1: Enable\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_PUSH\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00DC+0xC0*\regindex{n}}\label{regdesc:AHBDMAOUTPUSHCHNREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{AHB\_DMA\_OUTFIFO\_PUSH\_CH\regindex{n}}{1}{9}{{0}}%
\regfield{AHB\_DMA\_OUTFIFO\_WDATA\_CH\regindex{n}}{9}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAOUTFIFOWDATACHN}\item [AHB\_DMA\_OUTFIFO\_WDATA\_CH\regindex{n}] Represents the data that need to be pushed into AHB DMA TX FIFO. (R/W)
\label{fielddesc:AHBDMAOUTFIFOPUSHCHN}\item [AHB\_DMA\_OUTFIFO\_PUSH\_CH\regindex{n}] Configures whether to push data into AHB DMA TX FIFO.\\
0: Invalid. No effect\\
1: Push\\ (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_LINK\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00E0+0xC0*\regindex{n}}\label{regdesc:AHBDMAOUTLINKCHNREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{AHB\_DMA\_OUTLINK\_PARK\_CH\regindex{n}}{1}{3}{{1}}%
\regfield{AHB\_DMA\_OUTLINK\_RESTART\_CH\regindex{n}}{1}{2}{{0}}%
\regfield{AHB\_DMA\_OUTLINK\_START\_CH\regindex{n}}{1}{1}{{0}}%
\regfield{AHB\_DMA\_OUTLINK\_STOP\_CH\regindex{n}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAOUTLINKSTOPCHN}\item [AHB\_DMA\_OUTLINK\_STOP\_CH\regindex{n}] Configures whether to stop TX channel \regindex{n} from transmitting data.\\
0: Invalid. No effect\\
1: Stop\\ (WT)
\label{fielddesc:AHBDMAOUTLINKSTARTCHN}\item [AHB\_DMA\_OUTLINK\_START\_CH\regindex{n}] Configures whether to enable TX channel \regindex{n} for data transfer.\\
0: Disable\\
1: Enable\\ (WT)
\label{fielddesc:AHBDMAOUTLINKRESTARTCHN}\item [AHB\_DMA\_OUTLINK\_RESTART\_CH\regindex{n}] Configures whether to restart TX channel \regindex{n} for AHB DMA transfer.\\
0: Invalid. No effect\\
1: Restart\\ (WT)
\label{fielddesc:AHBDMAOUTLINKPARKCHN}\item [AHB\_DMA\_OUTLINK\_PARK\_CH\regindex{n}] Represents the status of the transmit descriptor's FSM.\\
0: Running\\
1: Idle\\ (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_TX\_CH\_ARB\_WEIGH\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x02DC+0x28*\regindex{n}}\label{regdesc:AHBDMATXCHARBWEIGHCHNREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{AHB\_DMA\_TX\_CH\_ARB\_WEIGH\_CH\regindex{n}}{4}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMATXCHARBWEIGHCHN}\item [AHB\_DMA\_TX\_CH\_ARB\_WEIGH\_CH\regindex{n}] Configures the weight (i.e the number of tokens) of TX channel\regindex{n}. \\Value range: 0 \verb+~+ 15. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_TX\_ARB\_WEIGH\_OPT\_DIR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x02E0+0x28*\regindex{n}}\label{regdesc:AHBDMATXARBWEIGHOPTDIRCHNREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{\rotatebox{20}{AHB\_DMA\_TX\_ARB\_WEIGH\_OPT\_DIR\_CH\regindex{n}}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMATXARBWEIGHOPTDIRCHN}\item [AHB\_DMA\_TX\_ARB\_WEIGH\_OPT\_DIR\_CH\regindex{n}] Configures whether to enable weight optimization for TX channel \regindex{n}.\\
0: Disable\\
1: Enable\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_RX\_CH\_ARB\_WEIGH\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0354+0x28*\regindex{n}}\label{regdesc:AHBDMARXCHARBWEIGHCHNREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{AHB\_DMA\_RX\_CH\_ARB\_WEIGH\_CH\regindex{n}}{4}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMARXCHARBWEIGHCHN}\item [AHB\_DMA\_RX\_CH\_ARB\_WEIGH\_CH\regindex{n}] Configures the weight (i.e the number of tokens) of RX channel\regindex{n}. \\Value range: 0 \verb+~+ 15. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_RX\_ARB\_WEIGH\_OPT\_DIR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0358+0x28*\regindex{n}}\label{regdesc:AHBDMARXARBWEIGHOPTDIRCHNREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{\rotatebox{20}{AHB\_DMA\_RX\_ARB\_WEIGH\_OPT\_DIR\_CH\regindex{n}}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMARXARBWEIGHOPTDIRCHN}\item [AHB\_DMA\_RX\_ARB\_WEIGH\_OPT\_DIR\_CH\regindex{n}] Configures whether to enable weight optimization for RX channel \regindex{n}.\\
0: Disable\\
1: Enable\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_IN\_LINK\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x03AC+0x4*\regindex{n}}\label{regdesc:AHBDMAINLINKADDRCHNREG}
\regfield{AHB\_DMA\_INLINK\_ADDR\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAINLINKADDRCHN}\item [AHB\_DMA\_INLINK\_ADDR\_CH\regindex{n}] Represents the first receive descriptor's address. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_LINK\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x03B8+0x4*\regindex{n}}\label{regdesc:AHBDMAOUTLINKADDRCHNREG}
\regfield{AHB\_DMA\_OUTLINK\_ADDR\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAOUTLINKADDRCHN}\item [AHB\_DMA\_OUTLINK\_ADDR\_CH\regindex{n}] Represents the first transmit descriptor's address. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_INTR\_MEM\_START\_ADDR\_REG}{0x03C4}\label{regdesc:AHBDMAINTRMEMSTARTADDRREG}
\regfield{AHB\_DMA\_ACCESS\_INTR\_MEM\_START\_ADDR}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAACCESSINTRMEMSTARTADDR}\item [AHB\_DMA\_ACCESS\_INTR\_MEM\_START\_ADDR] Configures the start address of accessible address space. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_INTR\_MEM\_END\_ADDR\_REG}{0x03C8}\label{regdesc:AHBDMAINTRMEMENDADDRREG}
\regfield{AHB\_DMA\_ACCESS\_INTR\_MEM\_END\_ADDR}{32}{0}{{0xffffffff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAACCESSINTRMEMENDADDR}\item [AHB\_DMA\_ACCESS\_INTR\_MEM\_END\_ADDR] Configures the end address of accessible address space. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_ARB\_TIMEOUT\_REG}{0x03DC}\label{regdesc:AHBDMAARBTIMEOUTREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{AHB\_DMA\_ARB\_TIMEOUT}{16}{0}{{0x00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAARBTIMEOUT}\item [AHB\_DMA\_ARB\_TIMEOUT] Configures the time slot of weight arbitration. Measurement unit: AHB bus clock cycle. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_WEIGHT\_EN\_REG}{0x0400}\label{regdesc:AHBDMAWEIGHTENREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{AHB\_DMA\_WEIGHT\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAWEIGHTEN}\item [AHB\_DMA\_WEIGHT\_EN] Configures whether to enable weight arbitration.\\
0: Disable\\
1: Enable\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_DATE\_REG}{0x0068}\label{regdesc:AHBDMADATEREG}
\regfield{AHB\_DMA\_DATE}{32}{0}{{0x2311290}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMADATE}\item [AHB\_DMA\_DATE] Version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_INFIFO\_STATUS\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0078+0xC0*\regindex{n}}\label{regdesc:AHBDMAINFIFOSTATUSCHNREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{AHB\_DMA\_IN\_BUF\_HUNGRY\_CH\regindex{n}}{1}{27}{{0}}%
\regfield{AHB\_DMA\_IN\_REMAIN\_UNDER\_4B\_CH\regindex{n}}{1}{26}{{1}}%
\regfield{AHB\_DMA\_IN\_REMAIN\_UNDER\_3B\_CH\regindex{n}}{1}{25}{{1}}%
\regfield{AHB\_DMA\_IN\_REMAIN\_UNDER\_2B\_CH\regindex{n}}{1}{24}{{1}}%
\regfield{AHB\_DMA\_IN\_REMAIN\_UNDER\_1B\_CH\regindex{n}}{1}{23}{{1}}%
\regfield{(reserved)}{8}{15}{00000000}%
\regfield{AHB\_DMA\_INFIFO\_CNT\_CH\regindex{n}}{7}{8}{{0}}%
\regfield{(reserved)}{6}{2}{000000}%
\regfield{AHB\_DMA\_INFIFO\_EMPTY\_CH\regindex{n}}{1}{1}{{1}}%
\regfield{AHB\_DMA\_INFIFO\_FULL\_CH\regindex{n}}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAINFIFOFULLCHN}\item [AHB\_DMA\_INFIFO\_FULL\_CH\regindex{n}] Represents whether L1 RX FIFO is full.\\
0: Not Full\\
1: Full\\ (RO)
\label{fielddesc:AHBDMAINFIFOEMPTYCHN}\item [AHB\_DMA\_INFIFO\_EMPTY\_CH\regindex{n}] Represents whether L1 RX FIFO is empty.\\
0: Not empty\\
1: Empty\\ (RO)
\label{fielddesc:AHBDMAINFIFOCNTCHN}\item [AHB\_DMA\_INFIFO\_CNT\_CH\regindex{n}] Represents the number of data bytes in L1 RX FIFO for RX channel \regindex{n}. (RO)
\label{fielddesc:AHBDMAINREMAINUNDER1BCHN}\item [AHB\_DMA\_IN\_REMAIN\_UNDER\_1B\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:AHBDMAINREMAINUNDER2BCHN}\item [AHB\_DMA\_IN\_REMAIN\_UNDER\_2B\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:AHBDMAINREMAINUNDER3BCHN}\item [AHB\_DMA\_IN\_REMAIN\_UNDER\_3B\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:AHBDMAINREMAINUNDER4BCHN}\item [AHB\_DMA\_IN\_REMAIN\_UNDER\_4B\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:AHBDMAINBUFHUNGRYCHN}\item [AHB\_DMA\_IN\_BUF\_HUNGRY\_CH\regindex{n}] Reserved. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_IN\_STATE\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0084+0xC0*\regindex{n}}\label{regdesc:AHBDMAINSTATECHNREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{AHB\_DMA\_IN\_STATE\_CH\regindex{n}}{3}{20}{{0}}%
\regfield{AHB\_DMA\_IN\_DSCR\_STATE\_CH\regindex{n}}{2}{18}{{0}}%
\regfield{AHB\_DMA\_INLINK\_DSCR\_ADDR\_CH\regindex{n}}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAINLINKDSCRADDRCHN}\item [AHB\_DMA\_INLINK\_DSCR\_ADDR\_CH\regindex{n}] Represents the lower 18 bits of the next receive descriptor address that is pre-read (but not processed yet). If the current receive descriptor is the last descriptor, then this field represents the address of the current receive descriptor. (RO)
\label{fielddesc:AHBDMAINDSCRSTATECHN}\item [AHB\_DMA\_IN\_DSCR\_STATE\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:AHBDMAINSTATECHN}\item [AHB\_DMA\_IN\_STATE\_CH\regindex{n}] Reserved. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_IN\_SUC\_EOF\_DES\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0088+0xC0*\regindex{n}}\label{regdesc:AHBDMAINSUCEOFDESADDRCHNREG}
\regfield{AHB\_DMA\_IN\_SUC\_EOF\_DES\_ADDR\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAINSUCEOFDESADDRCHN}\item [AHB\_DMA\_IN\_SUC\_EOF\_DES\_ADDR\_CH\regindex{n}] Represents the address of the receive descriptor when the EOF bit in this descriptor is 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_IN\_ERR\_EOF\_DES\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x008C+0xC0*\regindex{n}}\label{regdesc:AHBDMAINERREOFDESADDRCHNREG}
\regfield{AHB\_DMA\_IN\_ERR\_EOF\_DES\_ADDR\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAINERREOFDESADDRCHN}\item [AHB\_DMA\_IN\_ERR\_EOF\_DES\_ADDR\_CH\regindex{n}] Represents the address of the receive descriptor when there are some errors in the currently received data. Valid only for UHCI. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_IN\_DSCR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0090+0xC0*\regindex{n}}\label{regdesc:AHBDMAINDSCRCHNREG}
\regfield{AHB\_DMA\_INLINK\_DSCR\_CH\regindex{n}}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAINLINKDSCRCHN}\item [AHB\_DMA\_INLINK\_DSCR\_CH\regindex{n}] Represents the address of the next receive descriptor x+1 pointed by the current receive descriptor that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_IN\_DSCR\_BF0\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0094+0xC0*\regindex{n}}\label{regdesc:AHBDMAINDSCRBF0CHNREG}
\regfield{AHB\_DMA\_INLINK\_DSCR\_BF0\_CH\regindex{n}}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAINLINKDSCRBF0CHN}\item [AHB\_DMA\_INLINK\_DSCR\_BF0\_CH\regindex{n}] Represents the address of the current receive descriptor x that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_IN\_DSCR\_BF1\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0098+0xC0*\regindex{n}}\label{regdesc:AHBDMAINDSCRBF1CHNREG}
\regfield{AHB\_DMA\_INLINK\_DSCR\_BF1\_CH\regindex{n}}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAINLINKDSCRBF1CHN}\item [AHB\_DMA\_INLINK\_DSCR\_BF1\_CH\regindex{n}] Represents the address of the previous receive descriptor x-1 that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUTFIFO\_STATUS\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00D8+0xC0*\regindex{n}}\label{regdesc:AHBDMAOUTFIFOSTATUSCHNREG}
\regfield{(reserved)}{5}{27}{00000}%
\regfield{AHB\_DMA\_OUT\_REMAIN\_UNDER\_4B\_CH\regindex{n}}{1}{26}{{1}}%
\regfield{AHB\_DMA\_OUT\_REMAIN\_UNDER\_3B\_CH\regindex{n}}{1}{25}{{1}}%
\regfield{AHB\_DMA\_OUT\_REMAIN\_UNDER\_2B\_CH\regindex{n}}{1}{24}{{1}}%
\regfield{AHB\_DMA\_OUT\_REMAIN\_UNDER\_1B\_CH\regindex{n}}{1}{23}{{1}}%
\regfield{(reserved)}{8}{15}{00000000}%
\regfield{AHB\_DMA\_OUTFIFO\_CNT\_CH\regindex{n}}{7}{8}{{0}}%
\regfield{(reserved)}{6}{2}{000000}%
\regfield{AHB\_DMA\_OUTFIFO\_EMPTY\_CH\regindex{n}}{1}{1}{{1}}%
\regfield{AHB\_DMA\_OUTFIFO\_FULL\_CH\regindex{n}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAOUTFIFOFULLCHN}\item [AHB\_DMA\_OUTFIFO\_FULL\_CH\regindex{n}] Represents whether L1 TX FIFO is full.\\
0: Not Full\\
1: Full\\ (RO)
\label{fielddesc:AHBDMAOUTFIFOEMPTYCHN}\item [AHB\_DMA\_OUTFIFO\_EMPTY\_CH\regindex{n}] Represents whether L1 TX FIFO is empty.\\
0: Not empty\\
1: Empty\\ (RO)
\label{fielddesc:AHBDMAOUTFIFOCNTCHN}\item [AHB\_DMA\_OUTFIFO\_CNT\_CH\regindex{n}] Represents the number of data bytes in L1 TX FIFO for TX channel \regindex{n}. (RO)
\label{fielddesc:AHBDMAOUTREMAINUNDER1BCHN}\item [AHB\_DMA\_OUT\_REMAIN\_UNDER\_1B\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:AHBDMAOUTREMAINUNDER2BCHN}\item [AHB\_DMA\_OUT\_REMAIN\_UNDER\_2B\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:AHBDMAOUTREMAINUNDER3BCHN}\item [AHB\_DMA\_OUT\_REMAIN\_UNDER\_3B\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:AHBDMAOUTREMAINUNDER4BCHN}\item [AHB\_DMA\_OUT\_REMAIN\_UNDER\_4B\_CH\regindex{n}] Reserved. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_STATE\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00E4+0xC0*\regindex{n}}\label{regdesc:AHBDMAOUTSTATECHNREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{AHB\_DMA\_OUT\_STATE\_CH\regindex{n}}{3}{20}{{0}}%
\regfield{AHB\_DMA\_OUT\_DSCR\_STATE\_CH\regindex{n}}{2}{18}{{0}}%
\regfield{AHB\_DMA\_OUTLINK\_DSCR\_ADDR\_CH\regindex{n}}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAOUTLINKDSCRADDRCHN}\item [AHB\_DMA\_OUTLINK\_DSCR\_ADDR\_CH\regindex{n}] Represents the lower 18 bits of the next transmit descriptor address that is pre-read (but not processed yet). If the current transmit descriptor is the last descriptor, then this field represents the address of the current transmit descriptor. (RO)
\label{fielddesc:AHBDMAOUTDSCRSTATECHN}\item [AHB\_DMA\_OUT\_DSCR\_STATE\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:AHBDMAOUTSTATECHN}\item [AHB\_DMA\_OUT\_STATE\_CH\regindex{n}] Reserved. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_EOF\_DES\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00E8+0xC0*\regindex{n}}\label{regdesc:AHBDMAOUTEOFDESADDRCHNREG}
\regfield{AHB\_DMA\_OUT\_EOF\_DES\_ADDR\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAOUTEOFDESADDRCHN}\item [AHB\_DMA\_OUT\_EOF\_DES\_ADDR\_CH\regindex{n}] Represents the address of the transmit descriptor when the EOF bit in this descriptor is 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_EOF\_BFR\_DES\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00EC+0xC0*\regindex{n}}\label{regdesc:AHBDMAOUTEOFBFRDESADDRCHNREG}
\regfield{AHB\_DMA\_OUT\_EOF\_BFR\_DES\_ADDR\_CH\regindex{n}}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAOUTEOFBFRDESADDRCHN}\item [AHB\_DMA\_OUT\_EOF\_BFR\_DES\_ADDR\_CH\regindex{n}] Represents the address of the transmit descriptor before the last transmit descriptor. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_DSCR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00F0+0xC0*\regindex{n}}\label{regdesc:AHBDMAOUTDSCRCHNREG}
\regfield{AHB\_DMA\_OUTLINK\_DSCR\_CH\regindex{n}}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAOUTLINKDSCRCHN}\item [AHB\_DMA\_OUTLINK\_DSCR\_CH\regindex{n}] Represents the address of the next transmit descriptor y+1 pointed by the current transmit descriptor that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_DSCR\_BF0\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00F4+0xC0*\regindex{n}}\label{regdesc:AHBDMAOUTDSCRBF0CHNREG}
\regfield{AHB\_DMA\_OUTLINK\_DSCR\_BF0\_CH\regindex{n}}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAOUTLINKDSCRBF0CHN}\item [AHB\_DMA\_OUTLINK\_DSCR\_BF0\_CH\regindex{n}] Represents the address of the current transmit descriptor y that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_DSCR\_BF1\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00F8+0xC0*\regindex{n}}\label{regdesc:AHBDMAOUTDSCRBF1CHNREG}
\regfield{AHB\_DMA\_OUTLINK\_DSCR\_BF1\_CH\regindex{n}}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAOUTLINKDSCRBF1CHN}\item [AHB\_DMA\_OUTLINK\_DSCR\_BF1\_CH\regindex{n}] Represents the address of the previous transmit descriptor y-1 that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_IN\_PRI\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x009C+0xC0*\regindex{n}}\label{regdesc:AHBDMAINPRICHNREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{AHB\_DMA\_RX\_PRI\_CH\regindex{n}}{4}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMARXPRICHN}\item [AHB\_DMA\_RX\_PRI\_CH\regindex{n}] Configures the priority of RX channel \regindex{n}. The larger the value, the higher the priority. \\
Value range: 0  \verb+~+  5 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_PRI\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00FC+0xC0*\regindex{n}}\label{regdesc:AHBDMAOUTPRICHNREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{AHB\_DMA\_TX\_PRI\_CH\regindex{n}}{4}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMATXPRICHN}\item [AHB\_DMA\_TX\_PRI\_CH\regindex{n}] Configures the priority of TX channel \regindex{n}. The larger the value, the higher the priority. \\
Value range: 0  \verb+~+  5 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_IN\_PERI\_SEL\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00A0+0xC0*\regindex{n}}\label{regdesc:AHBDMAINPERISELCHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{AHB\_DMA\_PERI\_IN\_SEL\_CH\regindex{n}}{6}{0}{{0x3f}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAPERIINSELCHN}\item [AHB\_DMA\_PERI\_IN\_SEL\_CH\regindex{n}] Configures the peripheral connected to RX channel \regindex{n}.\\
0: Dummy\\ 1: GP-SPI\\ 2: UHCI\\ 3: I2S\\ 4: Dummy\\ 5: Dummy\\ 6: AES\\ 7: SHA\\ 8: ADC\\ 9: PARLIO\\ 10: Dummy\\ 11 \verb+~+ 15: Dummy\\
16 \verb+~+ 63: Invalid\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_PERI\_SEL\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0100+0xC0*\regindex{n}}\label{regdesc:AHBDMAOUTPERISELCHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{AHB\_DMA\_PERI\_OUT\_SEL\_CH\regindex{n}}{6}{0}{{0x3f}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAPERIOUTSELCHN}\item [AHB\_DMA\_PERI\_OUT\_SEL\_CH\regindex{n}] Configures the peripheral connected to TX channel \regindex{n}.\\
0: Dummy\\ 1: GP-SPI\\ 2: UHCI\\ 3: I2S\\ 4: Dummy\\ 5: Dummy\\ 6: AES\\ 7: SHA\\ 8: ADC\\ 9: PARLIO\\ 10: Dummy\\ 11 \verb+~+ 15: Dummy\\
16  \verb+~+  63: Invalid\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_MODULE\_CLK\_EN\_REG} {0x0404}\label{regdesc:AHBDMAMODULECLKENREG}
\regfield{(reserved)}{3}{29}{000}%
\regfield{AHB\_DMA\_AHBINF\_CLK\_EN}{1}{28}{{0x0}}%
\regfield{AHB\_DMA\_CMD\_ARB\_CLK\_EN}{1}{27}{{0x0}}%
\regfield{(reserved)}{12}{15}{000000000000}%
\regfield{AHB\_DMA\_IN\_CTRL\_CLK\_EN}{3}{12}{{0x7}}%
\regfield{AHB\_DMA\_IN\_DSCR\_CLK\_EN}{3}{9}{{0x7}}%
\regfield{AHB\_DMA\_OUT\_CTRL\_CLK\_EN}{3}{6}{{0x7}}%
\regfield{AHB\_DMA\_OUT\_DSCR\_CLK\_EN}{3}{3}{{0x7}}%
\regfield{AHB\_DMA\_AHB\_APB\_SYNC\_CLK\_EN}{3}{0}{{0x7}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAAHBAPBSYNCCLKEN}\item [AHB\_DMA\_AHB\_APB\_SYNC\_CLK\_EN] Configures whether to forcibly enable the clock for the GDMA register configuration synchronization module.\\
Bit 0 corresponds to TX and RX channel 0, bit 1 corresponds to channel TX and RX 1, and so on.\\
0: Not forcibly enable\\
1: Forcibly enable\\ (R/W)
\label{fielddesc:AHBDMAOUTDSCRCLKEN}\item [AHB\_DMA\_OUT\_DSCR\_CLK\_EN] Configures whether to forcibly enable the clock for the GDMA TX descriptor processing module.\\
Bit 0 corresponds to TX channel 0, bit 1 corresponds to TX channel 1, and so on.\\
0: Not forcibly enable\\
1: Forcibly enable\\ (R/W)
\label{fielddesc:AHBDMAOUTCTRLCLKEN}\item [AHB\_DMA\_OUT\_CTRL\_CLK\_EN] Configures whether to forcibly enable the clock for the GDMA TX data processing module.\\
Bit 0 corresponds to TX channel 0, bit 1 corresponds to TX channel 1, and so on.\\
0: Not forcibly enable\\
1: Forcibly enable\\ (R/W)
\label{fielddesc:AHBDMAINDSCRCLKEN}\item [AHB\_DMA\_IN\_DSCR\_CLK\_EN] Configures whether to forcibly enable the clock for the GDMA RX descriptor processing module.\\
Bit 0 corresponds to RX channel 0, bit 1 corresponds to TX channel 1, and so on.\\
0: Not forcibly enable\\
1: Forcibly enable\\ (R/W)
\label{fielddesc:AHBDMAINCTRLCLKEN}\item [AHB\_DMA\_IN\_CTRL\_CLK\_EN] Configures whether to forcibly enable the clock for the GDMA RX data processing module.\\
Bit 0 corresponds to RX channel 0, bit 1 corresponds to TX channel 1, and so on.\\
0: Not forcibly enable\\
1: Forcibly enable\\ (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{AHB\_DMA\_MODULE\_CLK\_EN\_REG} {0x0404}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:AHBDMACMDARBCLKEN}\item [AHB\_DMA\_CMD\_ARB\_CLK\_EN] Configures whether to forcibly enable the clock for the GDMA arbitration module.\\
0: Not forcibly enable\\
1: Forcibly enable\\ (R/W)
\label{fielddesc:AHBDMAAHBINFCLKEN}\item [AHB\_DMA\_AHBINF\_CLK\_EN] Configures whether to forcibly enable the clock for the GDMA bus interface processing module.\\
0: Not forcibly enable\\
1: Forcibly enable\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_AHBINF\_RESP\_ERR\_STATUS0\_REG} {0x0408}\label{regdesc:AHBDMAAHBINFRESPERRSTATUS0REG}
\regfield{AHB\_DMA\_AHBINF\_RESP\_ERR\_ADDR}{32}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAAHBINFRESPERRADDR}\item [AHB\_DMA\_AHBINF\_RESP\_ERR\_ADDR] Represents the address of the current AHB bus transfer that triggers an error response. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_AHBINF\_RESP\_ERR\_STATUS1\_REG} {0x040C}\label{regdesc:AHBDMAAHBINFRESPERRSTATUS1REG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{AHB\_DMA\_AHBINF\_RESP\_ERR\_CH\_ID}{3}{5}{{0x0}}%
\regfield{AHB\_DMA\_AHBINF\_RESP\_ERR\_ID}{4}{1}{{0xF}}%
\regfield{AHB\_DMA\_AHBINF\_RESP\_ERR\_WR}{1}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAAHBINFRESPERRCHID}\item [AHB\_DMA\_AHBINF\_RESP\_ERR\_CH\_ID] Represents the channel ID of the transfer that triggers the AHB bus error response.\\
Bits[0:1]: Channel number. Value range: 0 \verb+~+ 2\\
Bit[2]: Channel direction.
0: RX\\
1: TX\\ (RO)
\label{fielddesc:AHBDMAAHBINFRESPERRID}\item [AHB\_DMA\_AHBINF\_RESP\_ERR\_ID] Represents the ID of the transfer that triggers the AHB bus error response.\\
1: Transfer between GP-SPI and memory\\
2: Transfer between UHCI and memory\\
3: Transfer between I2S and memory\\
6: Transfer between AES and memory\\
7: Transfer between SHA and memory\\
8: Transfer between ADC and memory\\
9: Transfer between PARLIO and memory\\
10: Memory-to-memory transfer on channel 0\\
11: Memory-to-memory transfer on channel 1\\
12: Memory-to-memory transfer on channel 2\\
Other values are invalid\\
(RO)
\label{fielddesc:AHBDMAAHBINFRESPERRWR}\item [AHB\_DMA\_AHBINF\_RESP\_ERR\_WR] Represents the type of the transfer that triggered the AHB bus error response received by the GDMA.\\
0: Read\\
1: Write\\ (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_IN\_DONE\_DES\_ADDR\_CH\regindex{n}\_REG(\regindex{n}: 0-2)}{0x0410+0x08*\regindex{n}}\label{regdesc:AHBDMAINDONEDESADDRCHNREG}
\regfield{AHB\_DMA\_IN\_DONE\_DES\_ADDR\_CH\regindex{n}}{32}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAINDONEDESADDRCHNREG}\item [AHB\_DMA\_IN\_DONE\_DES\_ADDR\_CH\regindex{n}] Represents the address of the descriptor corresponding to the completed RX transfer. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{AHB\_DMA\_OUT\_DONE\_DES\_ADDR\_CH\regindex{n}\_REG(\regindex{n}: 0-2)}{0x0414+0x08*\regindex{n}}\label{regdesc:AHBDMAOUTDONEDESADDRCHNREG}
\regfield{AHB\_DMA\_OUT\_DONE\_DES\_ADDR\_CH\regindex{n}}{32}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:AHBDMAOUTDONEDESADDRCHNREG}\item [AHB\_DMA\_OUT\_DONE\_DES\_ADDR\_CH\regindex{n}] Represents the address of the descriptor corresponding to the completed TX transfer. (RO)
\end{reglist}\end{regdesc}
\end{register}
