\begin{longtable}[l]{ |m{8.2cm}|r|c|r|m{9cm}| }
\caption{Parameters in eFuse BLOCK0}
    \label{tab:efuse-block0-para}
    \\\hline
    \rowcolor{lightgray}
    \textbf{Parameters} & \textbf{\thead{Bit \\Width}} & \textbf{\thead{\hyperref[sec:para-hw-modules]{Hardware Use}}} & \textbf{\thead{Write Protection \\by \hyperref[fielddesc:EFUSEWRDIS]{EFUSE\_WR\_DIS} \\Bit Number}}
    & \textbf{Description} \\
    \endfirsthead
    \multicolumn{5}{c}{\bfseries \tablename\ \thetable{} -- cont'd from previous page}\\\hline
    \rowcolor{lightgray}
    \textbf{Parameters} & \textbf{\thead{Bit \\Width}} & \textbf{\thead{\hyperref[sec:para-hw-modules]{Hardware Use}}} & \textbf{\thead{Write Protection \\by \hyperref[fielddesc:EFUSEWRDIS]{EFUSE\_WR\_DIS} \\Bit Number}}
    & \textbf{Description} \\
    \endhead
    \multicolumn{5}{r}{\textbf{Cont'd on next page}} \\
    \endfoot
    \endlastfoot
    \hline
    \textbf{\hyperref[fielddesc:EFUSEWRDIS]{EFUSE\_WR\_DIS}}  & 32 & Y & N/A & Represents whether writing of eFuse bits by eFuse controller is disabled.\\
    \hline
    \textbf{\hyperref[fielddesc:EFUSERDDIS]{EFUSE\_RD\_DIS}}  & 7 & Y & 0  & Represents whether reading data from BLOCK4 \verb+~+ 10 in eFuse memory by users is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEDISICACHE]{EFUSE\_DIS\_ICACHE}  &  1 & Y & 2  & Represents whether instruction cache is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEDISUSBJTAG]{EFUSE\_DIS\_USB\_JTAG}  & 1 & Y & 2  & Represents whether the USB-to-JTAG function in the USB module is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEPOWERGLITCHEN]{EFUSE\_POWERGLITCH\_EN}  & 1 & Y & 2 & Represents whether to enable the power glitch detection function\\
    \hline
    \hyperref[fielddesc:EFUSEDISFORCEDOWNLOAD]{EFUSE\_DIS\_FORCE\_DOWNLOAD} & 1 & Y & 2 & Represents whether the function to force the chip into Download mode is disabled.\\
    \hline
    \hyperref[fielddesc:EFUSESPIDOWNLOADMSPIDIS]{EFUSE\_SPI\_DOWNLOAD\_MSPI\_DIS} & 1 & Y & 17 & Represents whether the SPI0 controller is disabled in boot\_mode\_download. \\
    \hline
    \hyperref[fielddesc:EFUSEDISCAN]{EFUSE\_DIS\_CAN} & 1 & Y & 2 & Represents whether the TWAI controller is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEJTAGSELENABLE]{EFUSE\_JTAG\_SEL\_ENABLE} & 1 & Y & 2 & Represents whether the selection of a JTAG signal source through the strapping value of GPIO15 is enabled when both \hyperref[fielddesc:EFUSEDISPADJTAG]{EFUSE\_DIS\_PAD\_JTAG} and \hyperref[fielddesc:EFUSEDISUSBJTAG]{EFUSE\_DIS\_USB\_JTAG} are configured to 0.\\
    \hline
    \hyperref[fielddesc:EFUSESOFTDISJTAG]{EFUSE\_SOFT\_DIS\_JTAG} & 3 & Y & 31 & Represents whether JTAG is disabled in the soft way.\\
    \hline
    \hyperref[fielddesc:EFUSEDISPADJTAG]{EFUSE\_DIS\_PAD\_JTAG} & 1 & Y & 2 & Represents whether JTAG is disabled in the hard way (permanently). \\
    \hline
    \hyperref[fielddesc:EFUSEDISDOWNLOADMANUALENCRYPT]{EFUSE\_DIS\_DOWNLOAD\_MANUAL\_ENCRYPT} &  1 & Y & 2 & Represents whether flash encryption is disabled (except in SPI boot mode).\\
    \hline
    \hyperref[fielddesc:EFUSEUSBEXCHGPINS]{EFUSE\_USB\_EXCHG\_PINS} & 1 & Y & 30 & Represents whether the D+ and D- pins are exchanged. \\
    \hline
    \hyperref[fielddesc:EFUSEVDDSPIASGPIO]{EFUSE\_VDD\_SPI\_AS\_GPIO} & 1 & Y & 30 & Represents whether the VDD\_SPI pin is used as a regular GPIO. \\
    \hline
    \hyperref[fielddesc:EFUSEWDTDELAYSEL]{EFUSE\_WDT\_DELAY\_SEL} & 2 & Y & 3 & Represents whether RTC watchdog timeout threshold is selected at startup.\\
    \hline
    \hyperref[fielddesc:EFUSESPIBOOTCRYPTCNT]{EFUSE\_SPI\_BOOT\_CRYPT\_CNT} & 3 & Y & 4 & Represents whether SPI boot encryption/decryption is enabled.\\
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE0]{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE0} & 1 & N & 5 & Represents whether revoking the first Secure Boot key is enabled.\\
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE1]{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE1} & 1 & N & 6 & Represents whether revoking the second Secure Boot key is enabled.\\
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTKEYREVOKE2]{EFUSE\_SECURE\_BOOT\_KEY\_REVOKE2} & 1 & N & 7 & Represents whether revoking the third Secure Boot key is enabled.\\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE0]{EFUSE\_KEY\_PURPOSE\_0} & 4 & Y & 8 & {Represents Key0 purpose. See Table \ref{tab:efuse-key-purpose}.} \\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE1]{EFUSE\_KEY\_PURPOSE\_1} & 4 & Y & 9 & {Represents Key1 purpose. See Table \ref{tab:efuse-key-purpose}.} \\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE2]{EFUSE\_KEY\_PURPOSE\_2} & 4 & Y & 10 & {Represents Key2 purpose. See Table \ref{tab:efuse-key-purpose}.} \\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE3]{EFUSE\_KEY\_PURPOSE\_3} & 4 & Y & 11 & {Represents Key3 purpose. See Table \ref{tab:efuse-key-purpose}.} \\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE4]{EFUSE\_KEY\_PURPOSE\_4} & 4 & Y & 12 & {Represents Key4 purpose. See Table \ref{tab:efuse-key-purpose}.} \\
    \hline
    \hyperref[fielddesc:EFUSEKEYPURPOSE5]{EFUSE\_KEY\_PURPOSE\_5} & 4 & Y & 13 & {Represents Key5 purpose. See Table \ref{tab:efuse-key-purpose}.} \\
    \hline
    \hyperref[fielddesc:EFUSESECDPALEVEL]{EFUSE\_SEC\_DPA\_LEVEL} & 2 & Y & 14 & Represents the security level of anti-DPA (differential power analysis) attack. \\
    \hline
    \hyperref[fielddesc:EFUSECRYPTDPAENABLE]{EFUSE\_CRYPT\_DPA\_ENABLE} & 1 & Y & 15 & Represents whether defense against DPA attack is enabled. \\
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTEN]{EFUSE\_SECURE\_BOOT\_EN} & 1 & N & 16 & Represents whether Secure Boot is enabled or disabled. \\
    \hline
    \hyperref[fielddesc:EFUSESECUREBOOTAGGRESSIVEREVOKE]{EFUSE\_SECURE\_BOOT\_AGGRESSIVE\_REVOKE} & 1 & N & 16 & Represents whether aggressive revocation of Secure Boot is enabled. \\
    \hline
    \hyperref[fielddesc:EFUSEFLASHTPUW]{EFUSE\_FLASH\_TPUW} & 4 & N & 18 & Represents the flash waiting time after power-up.\\
    \hline
    \hyperref[fielddesc:EFUSEDISDOWNLOADMODE]{EFUSE\_DIS\_DOWNLOAD\_MODE} & 1 & N & 18 & Represents whether all download modes are disabled.\\
    \hline
    \hyperref[fielddesc:EFUSEDISDIRECTBOOT]{EFUSE\_DIS\_DIRECT\_BOOT} & 1 & N & 18 & Represents whether direct boot mode is disabled.\\
    \hline
    \hyperref[fielddesc:EFUSEDISUSBPRINT]{EFUSE\_DIS\_USB\_PRINT} & 1 & N & 18 & Represents whether print from USB-Serial-JTAG during ROM boot is disabled.\\
    \hline
    \hyperref[fielddesc:EFUSEDISUSBSERIALJTAGDOWNLOADMODE]{EFUSE\_DIS\_USB\_SERIAL\_JTAG\_DOWNLOAD\_MODE} & 1 & N & 18 & Represents whether the USB-Serial-JTAG download function is disabled. \\
    \hline
    \hyperref[fielddesc:EFUSEENABLESECURITYDOWNLOAD]{EFUSE\_ENABLE\_SECURITY\_DOWNLOAD} & 1 & N & 18 & Represents whether security download is enabled. \\
    \hline
    \hyperref[fielddesc:EFUSEUARTPRINTCONTROL]{EFUSE\_UART\_PRINT\_CONTROL} & 2 & N & 18 & Represents the type of UART printing.\\
    \hline
    \hyperref[fielddesc:EFUSEFORCESENDRESUME]{EFUSE\_FORCE\_SEND\_RESUME} & 1 & N & 18 & Represents whether ROM code is forced to send a resume command during SPI boot. \\
    \hline
    \hyperref[fielddesc:EFUSESECUREVERSION]{EFUSE\_SECURE\_VERSION} & 16 & N & 18 & Represents the version used by ESP-IDF anti-rollback feature. \\\hline
    \hyperref[fielddesc:EFUSESECUREBOOTDISABLEFASTWAKE]{EFUSE\_SECURE\_BOOT\_DISABLE\_FAST\_WAKE} & 1 & N & 18 & Represents whether FAST VERIFY ON WAKE is disabled or enabled when Secure Boot is enabled.\\\hline
    \hyperref[fielddesc:EFUSEHYSENPAD0]{EFUSE\_HYS\_EN\_PAD0} & 6 & Y & 19 & Represents whether to enable the hysteresis function of pad 0-5\\\hline
    \hyperref[fielddesc:EFUSEHYSENPAD1]{EFUSE\_HYS\_EN\_PAD1} & 22 & Y & 19 & Represents whether to enable the hysteresis function of pad 6-27\\\hline
\end{longtable}