\begin{longtable}[c]{|l|l|m{11cm}|}
    \caption{UTMI+ OTG Interface 
    \label{tab:usbotg-utmi-otg-interface}} \\
    
    \hline
    \rowcolor{lightgray}
    Signal Name & I/O & Description \\
    \hline
    \endfirsthead
    \hline
    \rowcolor{lightgray}
    Signal Name & I/O & Description \\ 
    \hline
    \endhead
    \endfoot
    usb\_otg\_iddig\_in  & I & Mini A/B Plug Indicator. Indicates whether the connected plug is mini-A or mini-B. Valid only when usb\_otg\_idpullup is sampled asserted.\newline 0: Mini-A connected\newline 1: Mini-B connected \\
    \hline
    usb\_otg\_avalid\_in & I & A-Peripheral Session Valid. Indicates if the voltage Vbus is at a valid level for an A-peripheral session. The comparator thresholds are:\newline 0: Vbus \textless 0.8 V\newline 1: Vbus = 0.2 V to 2.0 V \\
    \hline
    usb\_otg\_bvalid\_in & I & B-Peripheral Session Valid. Indicates if the voltage Vbus is at a valid level for a B-peripheral session. The comparator thresholds are:\newline 0: Vbus \textless 0.8 V\newline 1: Vbus = 0.8 V to 4 V \\
    \hline
    usb\_otg\_vbusvalid\_in & I & Vbus Valid. Indicates if the voltage Vbus is valid for A/B-device/peripheral operation. The comparator thresholds are:\newline 0: Vbus \textless 4.4 V\newline 1: Vbus \textgreater 4.75 V \\
    \hline
    usb\_srp\_sessend\_in & I & B-device Session End. Indicates if the voltage Vbus is below the B-device Session End threshold. The comparator thresholds are:\newline 0: Vbus \textgreater 0.8 V\newline 1: Vbus \textless 0.2 V \\
    \hline
    usb\_otg\_idpullup & O & \begin{tabular}[c]{@{}l@{}}Analog ID input Sample Enable. Enables sampling the analog ID line.\\ 0: ID pin sampling disabled\\ 1: ID pin sampling enabled\end{tabular} \\
    \hline
    usb\_otg\_dppulldown & O & D+ Pull-down Resistor Enable. Enables the 15 k$\Omega$ pull-down resistor on the D+ line. \\
    \hline
    usb\_otg\_dmpulldown & O & D- Pull-down Resistor Enable. Enables the 15 k$\Omega$ pull-down resistor on the D- line. \\
    \hline
    usb\_otg\_drvvbus & O & Drive Vbus. Enables driving Vbus to 5 V.\newline 0: Do not drive Vbus\newline 1: Drive Vbus \\
    \hline
    usb\_srp\_chrgvbus & O & Vbus Input Charge Enable. Directs the PHY to charge Vbus.\newline 0: Do not charge Vbus through a resistor\newline 1: Charge Vbus through a resistor (must be active for at least 30 ms) \\
    \hline
    usb\_srp\_dischrgvbus & O & Vbus Input Discharge Enable. Directs the PHY to discharge Vbus.\newline 0: Do not discharge Vbus through a resistor.\newline 1: Discharge Vbus through a resistor (must be active for at least 50 ms). \\
    \hline
\end{longtable}
