\begin{register}{H}{SYSTEM\_CPU\_PERI\_CLK\_EN\_REG}{0x0000}\label{regdesc:SYSTEMCPUPERICLKENREG}
\regfield{(reserved)}{24}{7}{0000000000000000000000000}%
\regfield{SYSTEM\_CLK\_EN\_ASSIST\_DEBUG}{1}{6}{{0}}%
\regfield{(reserved)}{6}{0}{000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMCLKENASSISTDEBUG}\item [SYSTEM\_CLK\_EN\_ASSIST\_DEBUG] Set this bit to enable the ASSIST\_DEBUG clock. Please see Chapter \ref{mod:dbgassist}
\textit{\nameref{mod:dbgassist}} for more information about ASSIST\_DEBUG. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_CPU\_PERI\_RST\_EN\_REG}{0x0004}\label{regdesc:SYSTEMCPUPERIRSTENREG}
\regfield{(reserved)}{24}{8}{0000000000000000000000000}%
\regfield{SYSTEM\_RST\_EN\_ASSIST\_DEBUG}{1}{6}{{1}}%
\regfield{(reserved)}{6}{0}{000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMRSTENASSISTDEBUG}\item [SYSTEM\_RST\_EN\_ASSIST\_DEBUG] Set this bit to reset the ASSIST\_DEBUG clock. Please see Chapter \ref{mod:dbgassist}
\textit{\nameref{mod:dbgassist}} for more information about ASSIST\_DEBUG. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{SYSTEM\_PERIP\_CLK\_EN0\_REG}{0x0010}\label{regdesc:SYSTEMPERIPCLKEN0REG}
\regfield{(reserved)}{1}{31}{{1}}%
\regfield{SYSTEM\_ADC2\_ARB\_CLK\_EN}{1}{30}{{1}}%
\regfield{SYSTEM\_SYSTIMER\_CLK\_EN}{1}{29}{{1}}%
\regfield{SYSTEM\_APB\_SARADC\_CLK\_EN}{1}{28}{{1}}%
\regfield{SYSTEM\_SPI3\_DMA\_CLK\_EN}{1}{27}{{1}}%
\regfield{(reserved)}{2}{25}{00}%
\regfield{SYSTEM\_UART\_MEM\_CLK\_EN}{1}{24}{{1}}%
\regfield{SYSTEM\_USB\_DEVICE\_CLK\_EN}{1}{23}{{1}}%
\regfield{(reserved)}{1}{22}{{1}}%
\regfield{SYSTEM\_I2S0\_CLK\_EN}{1}{21}{{0}}%
\regfield{(reserved)}{1}{20}{{0}}%
\regfield{SYSTEM\_CAN\_CLK\_EN}{1}{19}{{0}}%
\regfield{(reserved)}{3}{16}{001}%
\regfield{SYSTEM\_TIMERGROUP1\_CLK\_EN}{1}{15}{{1}}%
\regfield{(reserved)}{1}{14}{{1}}%
\regfield{SYSTEM\_TIMERGROUP\_CLK\_EN}{1}{13}{{1}}%
\regfield{(reserved)}{1}{12}{{0}}%
\regfield{SYSTEM\_LEDC\_CLK\_EN}{1}{11}{{0}}%
\regfield{(reserved)}{1}{10}{{0}}%
\regfield{SYSTEM\_RMT\_CLK\_EN}{1}{9}{{0}}%
\regfield{SYSTEM\_UHCI0\_CLK\_EN}{1}{8}{{0}}%
\regfield{SYSTEM\_EXT0\_CLK\_EN}{1}{7}{{0}}%
\regfield{SYSTEM\_SPI2\_CLK\_EN}{1}{6}{{1}}%
\regfield{SYSTEM\_UART1\_CLK\_EN}{1}{5}{{1}}%
\regfield{(reserved)}{1}{4}{{0}}%
\regfield{(reserved)}{1}{3}{{1}}%
\regfield{SYSTEM\_UART\_CLK\_EN}{1}{2}{{1}}%
\regfield{SYSTEM\_SPI01\_CLK\_EN}{1}{1}{{1}}%
\regfield{SYSTEM\_TIMERS\_CLK\_EN}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMTIMERSCLKEN}\item [SYSTEM\_TIMERS\_CLK\_EN] Set this bit to enable TIMERS clock. (R/W)
\label{fielddesc:SYSTEMSPI01CLKEN}\item [SYSTEM\_SPI01\_CLK\_EN] Set this bit to enable SPI0 / SPI1 clock. (R/W)
\label{fielddesc:SYSTEMUARTCLKEN}\item [SYSTEM\_UART\_CLK\_EN] Set this bit to enable UART clock. (R/W)
\label{fielddesc:SYSTEMUART1CLKEN}\item [SYSTEM\_UART1\_CLK\_EN] Set this bit to enable UART1 clock. (R/W)
\label{fielddesc:SYSTEMSPI2CLKEN}\item [SYSTEM\_SPI2\_CLK\_EN] Set this bit to enable SPI2 clock. (R/W)
\label{fielddesc:SYSTEMEXT0CLKEN}\item [SYSTEM\_EXT0\_CLK\_EN] Set this bit to enable I2C\_EXT0 clock. (R/W)
\label{fielddesc:SYSTEMUHCI0CLKEN}\item [SYSTEM\_UHCI0\_CLK\_EN] Set this bit to enable UHCI0 clock. (R/W)
\label{fielddesc:SYSTEMRMTCLKEN}\item [SYSTEM\_RMT\_CLK\_EN] Set this bit to enable RMT clock. (R/W)
\label{fielddesc:SYSTEMLEDCCLKEN}\item [SYSTEM\_LEDC\_CLK\_EN] Set this bit to enable LEDC clock. (R/W)
\label{fielddesc:SYSTEMTIMERGROUPCLKEN}\item [SYSTEM\_TIMERGROUP\_CLK\_EN] Set this bit to enable TIMER GROUP clock. (R/W)
\label{fielddesc:SYSTEMTIMERGROUP1CLKEN}\item [SYSTEM\_TIMERGROUP1\_CLK\_EN] Set this bit to enable TIMERGROUP1 clock. (R/W)
\label{fielddesc:SYSTEMCANCLKEN}\item [SYSTEM\_CAN\_CLK\_EN] Set this bit to enable TWAI clock. (R/W)
\label{fielddesc:SYSTEMI2S0CLKEN}\item [SYSTEM\_I2S0\_CLK\_EN] Set this bit to enable I2S clock. (R/W)
\label{fielddesc:SYSTEMUSBDEVICECLKEN}\item [SYSTEM\_USB\_DEVICE\_CLK\_EN] Set this bit to enable USB DEVICE clock. (R/W)
\label{fielddesc:SYSTEMUARTMEMCLKEN}\item [SYSTEM\_UART\_MEM\_CLK\_EN] Set this bit to enable UART\_MEM clock. (R/W)
\label{fielddesc:SYSTEMSPI3DMACLKEN}\item [SYSTEM\_SPI3\_DMA\_CLK\_EN] Set this bit to enable SPI3 DMA clock. (R/W)
\label{fielddesc:SYSTEMAPBSARADCCLKEN}\item [SYSTEM\_APB\_SARADC\_CLK\_EN] Set this bit to enable APB\_SARADC clock. (R/W)
\label{fielddesc:SYSTEMSYSTIMERCLKEN}\item [SYSTEM\_SYSTIMER\_CLK\_EN] Set this bit to enable SYSTEMTIMER clock. (R/W)
\label{fielddesc:SYSTEMADC2ARBCLKEN}\item [SYSTEM\_ADC2\_ARB\_CLK\_EN] Set this bit to enable ADC2\_ARB clock. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_PERIP\_CLK\_EN1\_REG}{0x0014}\label{regdesc:SYSTEMPERIPCLKEN1REG}
\regfield{(reserved)}{21}{11}{000000000000000000000}%
\regfield{SYSTEM\_TSENS\_CLK\_EN}{1}{10}{{0}}%
\regfield{(reserved)}{3}{7}{100}%
\regfield{SYSTEM\_DMA\_CLK\_EN}{1}{6}{{0}}%
\regfield{SYSTEM\_CRYPTO\_HMAC\_CLK\_EN}{1}{5}{{0}}%
\regfield{SYSTEM\_CRYPTO\_DS\_CLK\_EN}{1}{4}{{0}}%
\regfield{SYSTEM\_CRYPTO\_RSA\_CLK\_EN}{1}{3}{{0}}%
\regfield{SYSTEM\_CRYPTO\_SHA\_CLK\_EN}{1}{2}{{0}}%
\regfield{SYSTEM\_CRYPTO\_AES\_CLK\_EN}{1}{1}{{0}}%
\regfield{(reserved)}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMCRYPTOAESCLKEN}\item [SYSTEM\_CRYPTO\_AES\_CLK\_EN] Set this bit to enable AES clock. (R/W)
\label{fielddesc:SYSTEMCRYPTOSHACLKEN}\item [SYSTEM\_CRYPTO\_SHA\_CLK\_EN] Set this bit to enable SHA clock. (R/W)
\label{fielddesc:SYSTEMCRYPTORSACLKEN}\item [SYSTEM\_CRYPTO\_RSA\_CLK\_EN] Set this bit to enable RSA clock. (R/W)
\label{fielddesc:SYSTEMCRYPTODSCLKEN}\item [SYSTEM\_CRYPTO\_DS\_CLK\_EN] Set this bit to enable the RSA\_DS clock. (R/W)
\label{fielddesc:SYSTEMCRYPTOHMACCLKEN}\item [SYSTEM\_CRYPTO\_HMAC\_CLK\_EN] Set this bit to enable HMAC clock. (R/W)
\label{fielddesc:SYSTEMDMACLKEN}\item [SYSTEM\_DMA\_CLK\_EN] Set this bit to enable DMA clock. (R/W)
\label{fielddesc:SYSTEMTSENSCLKEN}\item [SYSTEM\_TSENS\_CLK\_EN] Set this bit to enable TSENS clock. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_PERIP\_RST\_EN0\_REG}{0x0018}\label{regdesc:SYSTEMPERIPRSTEN0REG}
\regfield{(reserved)}{1}{31}{{0}}%
\regfield{SYSTEM\_ADC2\_ARB\_RST}{1}{30}{{0}}%
\regfield{SYSTEM\_SYSTIMER\_RST}{1}{29}{{0}}%
\regfield{SYSTEM\_APB\_SARADC\_RST}{1}{28}{{0}}%
\regfield{SYSTEM\_SPI3\_DMA\_RST}{1}{27}{{0}}%
\regfield{(reserved)}{2}{25}{00}%
\regfield{SYSTEM\_UART\_MEM\_RST}{1}{24}{{0}}%
\regfield{SYSTEM\_USB\_DEVICE\_RST}{1}{23}{{0}}%
\regfield{(reserved)}{1}{22}{{0}}%
\regfield{SYSTEM\_I2S0\_RST}{1}{21}{{0}}%
\regfield{(reserved)}{1}{20}{{0}}%
\regfield{SYSTEM\_CAN\_RST}{1}{19}{{0}}%
\regfield{(reserved)}{3}{16}{000}%
\regfield{SYSTEM\_TIMERGROUP1\_RST}{1}{15}{{0}}%
\regfield{(reserved)}{1}{14}{{0}}%
\regfield{SYSTEM\_TIMERGROUP\_RST}{1}{13}{{0}}%
\regfield{(reserved)}{1}{12}{{0}}%
\regfield{SYSTEM\_LEDC\_RST}{1}{11}{{0}}%
\regfield{(reserved)}{1}{10}{{0}}%
\regfield{SYSTEM\_RMT\_RST}{1}{9}{{0}}%
\regfield{SYSTEM\_UHCI0\_RST}{1}{8}{{0}}%
\regfield{SYSTEM\_EXT0\_RST}{1}{7}{{0}}%
\regfield{SYSTEM\_SPI2\_RST}{1}{6}{{0}}%
\regfield{SYSTEM\_UART1\_RST}{1}{5}{{0}}%
\regfield{(reserved)}{1}{4}{{0}}%
\regfield{(reserved)}{1}{3}{{0}}%
\regfield{SYSTEM\_UART\_RST}{1}{2}{{0}}%
\regfield{SYSTEM\_SPI01\_RST}{1}{1}{{0}}%
\regfield{SYSTEM\_TIMERS\_RST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMTIMERSRST}\item [SYSTEM\_TIMERS\_RST] Set this bit to reset TIMERS. (R/W)
\label{fielddesc:SYSTEMSPI01RST}\item [SYSTEM\_SPI01\_RST] Set this bit to reset SPI0 / SPI1. (R/W)
\label{fielddesc:SYSTEMUARTRST}\item [SYSTEM\_UART\_RST] Set this bit to reset UART. (R/W)
\label{fielddesc:SYSTEMUART1RST}\item [SYSTEM\_UART1\_RST] Set this bit to reset UART1. (R/W)
\label{fielddesc:SYSTEMSPI2RST}\item [SYSTEM\_SPI2\_RST] Set this bit to reset SPI2. (R/W)
\label{fielddesc:SYSTEMEXT0RST}\item [SYSTEM\_EXT0\_RST] Set this bit to reset I2C\_EXT0. (R/W)
\label{fielddesc:SYSTEMUHCI0RST}\item [SYSTEM\_UHCI0\_RST] Set this bit to reset UHCI0. (R/W)
\label{fielddesc:SYSTEMRMTRST}\item [SYSTEM\_RMT\_RST] Set this bit to reset RMT. (R/W)
\label{fielddesc:SYSTEMLEDCRST}\item [SYSTEM\_LEDC\_RST] Set this bit to reset LEDC. (R/W)
\label{fielddesc:SYSTEMTIMERGROUPRST}\item [SYSTEM\_TIMERGROUP\_RST] Set this bit to reset TIMERGROUP. (R/W)
\label{fielddesc:SYSTEMTIMERGROUP1RST}\item [SYSTEM\_TIMERGROUP1\_RST] Set this bit to reset TIMERGROUP1. (R/W)
\label{fielddesc:SYSTEMCANRST}\item [SYSTEM\_CAN\_RST] Set this bit to reset CAN. (R/W)
\label{fielddesc:SYSTEMI2S0RST}\item [SYSTEM\_I2S0\_RST] Set this bit to reset I2S. (R/W)
\label{fielddesc:SYSTEMUSBDEVICERST}\item [SYSTEM\_USB\_DEVICE\_RST] Set this bit to reset USB DEVICE. (R/W)
\label{fielddesc:SYSTEMUARTMEMRST}\item [SYSTEM\_UART\_MEM\_RST] Set this bit to reset UART\_MEM. (R/W)
\label{fielddesc:SYSTEMSPI3DMARST}\item [SYSTEM\_SPI3\_DMA\_RST] Set this bit to reset SPI3. (R/W)
\label{fielddesc:SYSTEMAPBSARADCRST}\item [SYSTEM\_APB\_SARADC\_RST] Set this bit to reset APB\_SARADC. (R/W)
\label{fielddesc:SYSTEMSYSTIMERRST}\item [SYSTEM\_SYSTIMER\_RST] Set this bit to reset SYSTIMER. (R/W)
\label{fielddesc:SYSTEMADC2ARBRST}\item [SYSTEM\_ADC2\_ARB\_RST] Set this bit to reset ADC2\_ARB. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_PERIP\_RST\_EN1\_REG}{0x001C}\label{regdesc:SYSTEMPERIPRSTEN1REG}
\regfield{(reserved)}{21}{11}{000000000000000000000}%
\regfield{SYSTEM\_TSENS\_RST}{1}{10}{{0}}%
\regfield{(reserved)}{3}{7}{011}%
\regfield{SYSTEM\_DMA\_RST}{1}{6}{{1}}%
\regfield{SYSTEM\_CRYPTO\_HMAC\_RST}{1}{5}{{1}}%
\regfield{SYSTEM\_CRYPTO\_DS\_RST}{1}{4}{{1}}%
\regfield{SYSTEM\_CRYPTO\_RSA\_RST}{1}{3}{{1}}%
\regfield{SYSTEM\_CRYPTO\_SHA\_RST}{1}{2}{{1}}%
\regfield{SYSTEM\_CRYPTO\_AES\_RST}{1}{1}{{1}}%
\regfield{(reserved)}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMCRYPTOAESRST}\item [SYSTEM\_CRYPTO\_AES\_RST] Set this bit to reset CRYPTO\_AES. (R/W)
\label{fielddesc:SYSTEMCRYPTOSHARST}\item [SYSTEM\_CRYPTO\_SHA\_RST] Set this bit to reset CRYPTO\_SHA. (R/W)
\label{fielddesc:SYSTEMCRYPTORSARST}\item [SYSTEM\_CRYPTO\_RSA\_RST] Set this bit to reset CRYPTO\_RSA. (R/W)
\label{fielddesc:SYSTEMCRYPTODSRST}\item [SYSTEM\_CRYPTO\_DS\_RST] Set this bit to reset the RSA\_DS peripheral. (R/W)
\label{fielddesc:SYSTEMCRYPTOHMACRST}\item [SYSTEM\_CRYPTO\_HMAC\_RST] Set this bit to reset CRYPTO\_HMAC. (R/W)
\label{fielddesc:SYSTEMDMARST}\item [SYSTEM\_DMA\_RST] Set this bit to reset DMA. (R/W)
\label{fielddesc:SYSTEMTSENSRST}\item [SYSTEM\_TSENS\_RST] Set this bit to reset TSENS. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{SYSTEM\_CACHE\_CONTROL\_REG}{0x0040}\label{regdesc:SYSTEMCACHECONTROLREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{SYSTEM\_DCACHE\_RESET}{1}{3}{{0}}%
\regfield{SYSTEM\_DCACHE\_CLK\_ON}{1}{2}{{1}}%
\regfield{SYSTEM\_ICACHE\_RESET}{1}{1}{{0}}%
\regfield{SYSTEM\_ICACHE\_CLK\_ON}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMICACHECLKON}\item [SYSTEM\_ICACHE\_CLK\_ON] Set this bit to enable i-cache clock. (R/W)
\label{fielddesc:SYSTEMICACHERESET}\item [SYSTEM\_ICACHE\_RESET] Set this bit to reset i-cache. (R/W)
\label{fielddesc:SYSTEMDCACHECLKON}\item [SYSTEM\_DCACHE\_CLK\_ON] Set this bit to enable d-cache clock. (R/W)
\label{fielddesc:SYSTEMDCACHERESET}\item [SYSTEM\_DCACHE\_RESET] Set this bit to reset d-cache. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_CPU\_PER\_CONF\_REG}{0x0008}\label{regdesc:SYSTEMCPUPERCONFREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{SYSTEM\_CPU\_WAITI\_DELAY\_NUM}{4}{4}{{0x0}}%
\regfield{SYSTEM\_CPU\_WAIT\_MODE\_FORCE\_ON}{1}{3}{{1}}%
\regfield{SYSTEM\_PLL\_FREQ\_SEL}{1}{2}{{1}}%
\regfield{SYSTEM\_CPUPERIOD\_SEL}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMCPUPERIODSEL}\item [SYSTEM\_CPUPERIOD\_SEL] Set this field to select the CPU clock frequency. For details, please refer to Table \ref{tab:resclk-periph-clks} in Chapter \ref{mod:resclk} \textit{\nameref{mod:resclk}}.(R/W)
\label{fielddesc:SYSTEMPLLFREQSEL}\item [SYSTEM\_PLL\_FREQ\_SEL] Set this bit to select the PLL clock frequency. For details, please refer to Table \ref{tab:resclk-periph-clks} in Chapter \ref{mod:resclk} \textit{\nameref{mod:resclk}}. (R/W)
\label{fielddesc:SYSTEMCPUWAITMODEFORCEON}\item [SYSTEM\_CPU\_WAIT\_MODE\_FORCE\_ON] Set this bit to force on the clock gate of CPU wait mode. Usually, after executing the WFI instruction, CPU enters the wait mode, during which the clock gate of CPU is turned off until any interrupts occur. In this way, power consumption is saved. However, if this bit is set, the clock gate of CPU is always on and will not be turned off by the WFI instruction. (R/W)
\label{fielddesc:SYSTEMCPUWAITIDELAYNUM}\item [SYSTEM\_CPU\_WAITI\_DELAY\_NUM] Sets the number of delay cycles to turn off the CPU clock gate after the CPU enters the wait mode because of a WFI instruction. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_BT\_LPCK\_DIV\_FRAC\_REG}{0x0024}\label{regdesc:SYSTEMBTLPCKDIVFRACREG}
\regfield{(reserved)}{3}{29}{000}%
\regfield{SYSTEM\_LPCLK\_RTC\_EN}{1}{28}{{0}}%
\regfield{SYSTEM\_LPCLK\_SEL\_XTAL32K}{1}{27}{{0}}%
\regfield{SYSTEM\_LPCLK\_SEL\_XTAL}{1}{26}{{0}}%
\regfield{SYSTEM\_LPCLK\_SEL\_8M}{1}{25}{{1}}%
\regfield{SYSTEM\_LPCLK\_SEL\_RTC\_SLOW}{1}{24}{{0}}%
\regfield{(reserved)}{24}{0}{{}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMLPCLKSELRTCSLOW}\item [SYSTEM\_LPCLK\_SEL\_RTC\_SLOW] Set this bit to select RTC\_SLOW\_CLK as the low-power clock. (R/W)
\label{fielddesc:SYSTEMLPCLKSEL8M}\item [SYSTEM\_LPCLK\_SEL\_8M] Set this bit to select RC\_FAST\_CLK div n clock as the low-power clock. (R/W)
\label{fielddesc:SYSTEMLPCLKSELXTAL}\item [SYSTEM\_LPCLK\_SEL\_XTAL] Set this bit to select XTAL clock as the low-power clock. (R/W)
\label{fielddesc:SYSTEMLPCLKSELXTAL32K}\item [SYSTEM\_LPCLK\_SEL\_XTAL32K] Set this bit to select xtal32k clock as the low-power clock. (R/W)
\label{fielddesc:SYSTEMLPCLKRTCEN}\item [SYSTEM\_LPCLK\_RTC\_EN] Set this bit to enable the LOW\_POWER\_CLK clock. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_SYSCLK\_CONF\_REG}{0x0058}\label{regdesc:SYSTEMSYSCLKCONFREG}
\regfield{(reserved)}{13}{19}{0000000000000}%
\regfield{SYSTEM\_CLK\_XTAL\_FREQ}{7}{12}{{0}}%
\regfield{SYSTEM\_SOC\_CLK\_SEL}{2}{10}{{0}}%
\regfield{SYSTEM\_PRE\_DIV\_CNT}{10}{0}{{0x1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMPREDIVCNT}\item [SYSTEM\_PRE\_DIV\_CNT] This field is used to set the count of prescaler of XTAL\_CLK. For details, please refer to Table \ref{tab:resclk-periph-clks} in Chapter \ref{mod:resclk} \textit{\nameref{mod:resclk}}. (R/W)
\label{fielddesc:SYSTEMSOCCLKSEL}\item [SYSTEM\_SOC\_CLK\_SEL] This field is used to select SOC clock. For details, please refer to Table \ref{tab:resclk-cpu-clk-src} in Chapter \ref{mod:resclk} \textit{\nameref{mod:resclk}}. (R/W)
\label{fielddesc:SYSTEMCLKXTALFREQ}\item [SYSTEM\_CLK\_XTAL\_FREQ] This field is used to read XTAL frequency in MHz. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_RTC\_FASTMEM\_CONFIG\_REG}{0x0048}\label{regdesc:SYSTEMRTCFASTMEMCONFIGREG}
\regfield{SYSTEM\_RTC\_MEM\_CRC\_FINISH}{1}{31}{{0}}%
\regfield{SYSTEM\_RTC\_MEM\_CRC\_LEN}{11}{20}{{0x7ff}}%
\regfield{SYSTEM\_RTC\_MEM\_CRC\_ADDR}{11}{9}{{0x0}}%
\regfield{SYSTEM\_RTC\_MEM\_CRC\_START}{1}{8}{{0}}%
\regfield{(reserved)}{8}{0}{00000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMRTCMEMCRCSTART}\item [SYSTEM\_RTC\_MEM\_CRC\_START] Set this bit to start the CRC of RTC memory. (R/W)
\label{fielddesc:SYSTEMRTCMEMCRCADDR}\item [SYSTEM\_RTC\_MEM\_CRC\_ADDR] This field is used to set address of RTC memory for CRC. (R/W)
\label{fielddesc:SYSTEMRTCMEMCRCLEN}\item [SYSTEM\_RTC\_MEM\_CRC\_LEN] This field is used to set length of RTC memory for CRC based on start address. (R/W)
\label{fielddesc:SYSTEMRTCMEMCRCFINISH}\item [SYSTEM\_RTC\_MEM\_CRC\_FINISH] This bit stores the status of RTC memory CRC. High level means finished while low level means not finished. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_RTC\_FASTMEM\_CRC\_REG}{0x004C}\label{regdesc:SYSTEMRTCFASTMEMCRCREG}
\regfield{SYSTEM\_RTC\_MEM\_CRC\_RES}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMRTCMEMCRCRES}\item [SYSTEM\_RTC\_MEM\_CRC\_RES] This field stores the CRC result of RTC memory. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_CPU\_INTR\_FROM\_CPU\_0\_REG}{0x0028}\label{regdesc:SYSTEMCPUINTRFROMCPU0REG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{SYSTEM\_CPU\_INTR\_FROM\_CPU\_0}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMCPUINTRFROMCPU0}\item [SYSTEM\_CPU\_INTR\_FROM\_CPU\_0] Set this bit to generate CPU interrupt 0. This bit needs to be reset by software in the ISR process. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_CPU\_INTR\_FROM\_CPU\_1\_REG}{0x002C}\label{regdesc:SYSTEMCPUINTRFROMCPU1REG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{SYSTEM\_CPU\_INTR\_FROM\_CPU\_1}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMCPUINTRFROMCPU1}\item [SYSTEM\_CPU\_INTR\_FROM\_CPU\_1] Set this bit to generate CPU interrupt 1. This bit needs to be reset by software in the ISR process. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_CPU\_INTR\_FROM\_CPU\_2\_REG}{0x0030}\label{regdesc:SYSTEMCPUINTRFROMCPU2REG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{SYSTEM\_CPU\_INTR\_FROM\_CPU\_2}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMCPUINTRFROMCPU2}\item [SYSTEM\_CPU\_INTR\_FROM\_CPU\_2] Set this bit to generate CPU interrupt 2. This bit needs to be reset by software in the ISR process. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_CPU\_INTR\_FROM\_CPU\_3\_REG}{0x0034}\label{regdesc:SYSTEMCPUINTRFROMCPU3REG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{SYSTEM\_CPU\_INTR\_FROM\_CPU\_3}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMCPUINTRFROMCPU3}\item [SYSTEM\_CPU\_INTR\_FROM\_CPU\_3] Set this bit to generate CPU interrupt 3. This bit needs to be reset by software in the ISR process. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_RSA\_PD\_CTRL\_REG}{0x0038}\label{regdesc:SYSTEMRSAPDCTRLREG}
\regfield{(reserved)}{29}{3}{00000000000000000000000000000}%
\regfield{SYSTEM\_RSA\_MEM\_FORCE\_PD}{1}{2}{{0}}%
\regfield{SYSTEM\_RSA\_MEM\_FORCE\_PU}{1}{1}{{0}}%
\regfield{SYSTEM\_RSA\_MEM\_PD}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMRSAMEMPD}\item [SYSTEM\_RSA\_MEM\_PD] Set this bit to send the RSA memory into retention state. This bit has the lowest priority, meaning it can be masked by the \hyperref[fielddesc:SYSTEMRSAMEMFORCEPU]{SYSTEM\_RSA\_MEM\_FORCE\_PU} field. When the RSA\_DS peripheral occupies the RSA accelerator, this bit is invalid. (R/W)
\label{fielddesc:SYSTEMRSAMEMFORCEPU}\item [SYSTEM\_RSA\_MEM\_FORCE\_PU] Set this bit to force the RSA memory to work as normal when the chip enters light sleep. This bit has the second highest priority, meaning it overrides the \hyperref[fielddesc:SYSTEMRSAMEMPD]{SYSTEM\_RSA\_MEM\_PD} field. (R/W)
\label{fielddesc:SYSTEMRSAMEMFORCEPD}\item [SYSTEM\_RSA\_MEM\_FORCE\_PD] Set this bit to send the RSA memory into retention state. This bit has the highest priority, meaning it sends the RSA memory into retention state regardless of the \hyperref[fielddesc:SYSTEMRSAMEMFORCEPU]{SYSTEM\_RSA\_MEM\_FORCE\_PU} field. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_EXTERNAL\_DEVICE\_ENCRYPT\_DECRYPT\_CONTROL\_REG}{0x0044}\label{regdesc:SYSTEMEXTERNALDEVICEENCRYPTDECRYPTCONTROLREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{\tiny{SYSTEM\_ENABLE\_DOWNLOAD\_MANUAL\_ENCRYPT}}{1}{3}{{0}}%
\regfield{\tiny{SYSTEM\_ENABLE\_DOWNLOAD\_G0CB\_DECRYPT}}{1}{2}{{0}}%
\regfield{\tiny{SYSTEM\_ENABLE\_DOWNLOAD\_DB\_ENCRYPT}}{1}{1}{{0}}%
\regfield{\tiny{SYSTEM\_ENABLE\_SPI\_MANUAL\_ENCRYPT}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMENABLESPIMANUALENCRYPT}\item [SYSTEM\_ENABLE\_SPI\_MANUAL\_ENCRYPT] Set this bit to enable Manual Encryption under SPI Boot mode. (R/W)
\label{fielddesc:SYSTEMENABLEDOWNLOADDBENCRYPT}\item [SYSTEM\_ENABLE\_DOWNLOAD\_DB\_ENCRYPT] Set this bit to enable Auto Encryption under Download Boot mode. (R/W)
\label{fielddesc:SYSTEMENABLEDOWNLOADG0CBDECRYPT}\item [SYSTEM\_ENABLE\_DOWNLOAD\_G0CB\_DECRYPT] Set this bit to enable Auto Decryption under Download Boot mode. (R/W)
\label{fielddesc:SYSTEMENABLEDOWNLOADMANUALENCRYPT}\item [SYSTEM\_ENABLE\_DOWNLOAD\_MANUAL\_ENCRYPT] Set this bit to enable Manual Encryption under Download Boot mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_CLOCK\_GATE\_REG}{0x0054}\label{regdesc:SYSTEMCLOCKGATEREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{SYSTEM\_CLK\_EN}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMCLKEN}\item [SYSTEM\_CLK\_EN] Set this bit to enable the system clock. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SYSTEM\_DATE\_REG}{0x0FFC}\label{regdesc:SYSTEMDATEREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{SYSTEM\_DATE}{28}{0}{{0x2007150}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SYSTEMDATE}\item [SYSTEM\_DATE] Version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}
