\begin{register}{H}{APB\_SARADC\_CTRL\_REG}{\hexprefix{}0000}\label{regdesc:APBSARADCCTRLREG}
\regfield{APB\_SARADC\_WAIT\_ARB\_CYCLE}{2}{30}{{1}}%
\regfield{(reserved)}{1}{29}{0}%
\regfield{APB\_SARADC\_XPD\_SAR\_FORCE}{2}{27}{{0}}%
\regfield{(reserved)}{1}{26}{{0}}%
\regfield{APB\_SARADC\_DATA\_SAR\_SEL}{1}{25}{{0}}%
\regfield{APB\_SARADC\_SAR2\_PATT\_P\_CLEAR}{1}{24}{{0}}%
\regfield{APB\_SARADC\_SAR1\_PATT\_P\_CLEAR}{1}{23}{{0}}%
\regfield{APB\_SARADC\_SAR2\_PATT\_LEN}{4}{19}{{15}}%
\regfield{APB\_SARADC\_SAR1\_PATT\_LEN}{4}{15}{{15}}%
\regfield{APB\_SARADC\_SAR\_CLK\_DIV}{8}{7}{{4}}%
\regfield{APB\_SARADC\_SAR\_CLK\_GATED}{1}{6}{{1}}%
\regfield{APB\_SARADC\_SAR\_SEL}{1}{5}{{0}}%
\regfield{APB\_SARADC\_WORK\_MODE}{2}{3}{{0}}%
\regfield{(reserved)}{1}{2}{0}%
\regfield{APB\_SARADC\_START}{1}{1}{{0}}%
\regfield{APB\_SARADC\_START\_FORCE}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCSTARTFORCE}\item [APB\_SARADC\_START\_FORCE] 0: select FSM to start SAR ADC. 1: select software to start SAR ADC. (R/W)
\label{fielddesc:APBSARADCSTART}\item [APB\_SARADC\_START] Start SAR ADC by software. (R/W)
\label{fielddesc:APBSARADCWORKMODE}\item [APB\_SARADC\_WORK\_MODE] 0: single-channel scan mode. 1: double-channel scan mode. 2: alternate-channel scan mode. (R/W)
\label{fielddesc:APBSARADCSARSEL}\item [APB\_SARADC\_SAR\_SEL] 0: select SAR ADC1. 1: select SAR ADC2, only work for single-channel scan mode. (R/W)
\label{fielddesc:APBSARADCSARCLKGATED}\item [APB\_SARADC\_SAR\_CLK\_GATED] SAR clock gate enable bit. (R/W)
\label{fielddesc:APBSARADCSARCLKDIV}\item [APB\_SARADC\_SAR\_CLK\_DIV] SAR clock divider. (R/W)
\label{fielddesc:APBSARADCSAR1PATTLEN}\item [APB\_SARADC\_SAR1\_PATT\_LEN] 0 \verb+~+ 15 means length 1 \verb+~+ 16. (R/W)
\label{fielddesc:APBSARADCSAR2PATTLEN}\item [APB\_SARADC\_SAR2\_PATT\_LEN] 0 \verb+~+ 15 means length 1 \verb+~+ 16. (R/W)
\label{fielddesc:APBSARADCSAR1PATTPCLEAR}\item [APB\_SARADC\_SAR1\_PATT\_P\_CLEAR] Clear the pointer of pattern table for DIG ADC1 CTRL. (R/W)
\label{fielddesc:APBSARADCSAR2PATTPCLEAR}\item [APB\_SARADC\_SAR2\_PATT\_P\_CLEAR] Clear the pointer of pattern table for DIG ADC2 CTRL. (R/W)
\label{fielddesc:APBSARADCDATASARSEL}\item [APB\_SARADC\_DATA\_SAR\_SEL] 1: sar\_sel will be coded to the MSB of the 16-bit output data, in this case the resolution should not be larger than 11 bits. (R/W)
\label{fielddesc:APBSARADCXPDSARFORCE}\item [APB\_SARADC\_XPD\_SAR\_FORCE] Force option to xpd sar blocks. (R/W)
\label{fielddesc:APBSARADCWAITARBCYCLE}\item [APB\_SARADC\_WAIT\_ARB\_CYCLE] Wait arbit signal stable after sar\_done. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_CTRL2\_REG}{\hexprefix{}0004}\label{regdesc:APBSARADCCTRL2REG}
\regfield{(reserved)}{7}{25}{0000000}%
\regfield{APB\_SARADC\_TIMER\_EN}{1}{24}{{0}}%
\regfield{APB\_SARADC\_TIMER\_TARGET}{12}{12}{{10}}%
\regfield{(reserved)}{1}{11}{{0}}%
\regfield{APB\_SARADC\_SAR2\_INV}{1}{10}{{0}}%
\regfield{APB\_SARADC\_SAR1\_INV}{1}{9}{{0}}%
\regfield{APB\_SARADC\_MAX\_MEAS\_NUM}{8}{1}{{255}}%
\regfield{APB\_SARADC\_MEAS\_NUM\_LIMIT}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCMEASNUMLIMIT}\item [APB\_SARADC\_MEAS\_NUM\_LIMIT] Enable limit times of SAR ADC sample. (R/W)
\label{fielddesc:APBSARADCMAXMEASNUM}\item [APB\_SARADC\_MAX\_MEAS\_NUM] Set maximum conversion number. (R/W)
\label{fielddesc:APBSARADCSAR1INV}\item [APB\_SARADC\_SAR1\_INV] 1: data to DIG ADC1 CTRL is inverted, otherwise not. (R/W)
\label{fielddesc:APBSARADCSAR2INV}\item [APB\_SARADC\_SAR2\_INV] 1: data to DIG ADC2 CTRL is inverted, otherwise not. (R/W)
\label{fielddesc:APBSARADCTIMERTARGET}\item [APB\_SARADC\_TIMER\_TARGET] Set SAR ADC timer target. (R/W)
\label{fielddesc:APBSARADCTIMEREN}\item [APB\_SARADC\_TIMER\_EN] Enable SAR ADC timer trigger. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_CLKM\_CONF\_REG}{\hexprefix{}005C}\label{regdesc:APBSARADCCLKMCONFREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{APB\_SARADC\_CLK\_SEL}{2}{21}{{0}}%
\regfield{(reserved)}{1}{20}{0}%
\regfield{APB\_SARADC\_CLKM\_DIV\_A}{6}{14}{{\hexprefix{}0}}%
\regfield{APB\_SARADC\_CLKM\_DIV\_B}{6}{8}{{\hexprefix{}0}}%
\regfield{APB\_SARADC\_CLKM\_DIV\_NUM}{8}{0}{{4}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCCLKMDIVNUM}\item [APB\_SARADC\_CLKM\_DIV\_NUM] Integral DIG\_ADC clock divider value (R/W)
\label{fielddesc:APBSARADCCLKMDIVB}\item [APB\_SARADC\_CLKM\_DIV\_B] Fractional clock divider numerator value (R/W)
\label{fielddesc:APBSARADCCLKMDIVA}\item [APB\_SARADC\_CLKM\_DIV\_A] Fractional clock divider denominator value (R/W)
\label{fielddesc:APBSARADCCLKSEL}\item [APB\_SARADC\_CLK\_SEL] 1: select APLL. 2: select APB\_CLK. Other values: disable clock. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_SAR1\_PATT\_TAB1\_REG}{\hexprefix{}0018}\label{regdesc:APBSARADCSAR1PATTTAB1REG}
\regfield{APB\_SARADC\_SAR1\_PATT\_TAB1}{32}{0}{{\hexprefix{}f0f0f0f}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCSAR1PATTTAB1}\item [APB\_SARADC\_SAR1\_PATT\_TAB1] Item 0 \verb+~+ 3 for pattern table 1 (each item one byte). (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{APB\_SARADC\_SAR1\_PATT\_TAB2\_REG}{\hexprefix{}001C}\label{regdesc:APBSARADCSAR1PATTTAB2REG}
\regfield{APB\_SARADC\_SAR1\_PATT\_TAB2}{32}{0}{{\hexprefix{}f0f0f0f}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCSAR1PATTTAB2}\item [APB\_SARADC\_SAR1\_PATT\_TAB2] Item 4 \verb+~+ 7 for pattern table 1 (each item one byte). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_SAR1\_PATT\_TAB3\_REG}{\hexprefix{}0020}\label{regdesc:APBSARADCSAR1PATTTAB3REG}
\regfield{APB\_SARADC\_SAR1\_PATT\_TAB3}{32}{0}{{\hexprefix{}f0f0f0f}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCSAR1PATTTAB3}\item [APB\_SARADC\_SAR1\_PATT\_TAB3] Item 8 \verb+~+ 11 for pattern table 1 (each item one byte). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_SAR1\_PATT\_TAB4\_REG}{\hexprefix{}0024}\label{regdesc:APBSARADCSAR1PATTTAB4REG}
\regfield{APB\_SARADC\_SAR1\_PATT\_TAB4}{32}{0}{{\hexprefix{}f0f0f0f}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCSAR1PATTTAB4}\item [APB\_SARADC\_SAR1\_PATT\_TAB4] Item 12 \verb+~+ 15 for pattern table 1 (each item one byte). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_SAR2\_PATT\_TAB1\_REG}{\hexprefix{}0028}\label{regdesc:APBSARADCSAR2PATTTAB1REG}
\regfield{APB\_SARADC\_SAR2\_PATT\_TAB1}{32}{0}{{\hexprefix{}f0f0f0f}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCSAR2PATTTAB1}\item [APB\_SARADC\_SAR2\_PATT\_TAB1] Item 0 \verb+~+ 3 for pattern table 2 (each item one byte). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_SAR2\_PATT\_TAB2\_REG}{\hexprefix{}002C}\label{regdesc:APBSARADCSAR2PATTTAB2REG}
\regfield{APB\_SARADC\_SAR2\_PATT\_TAB2}{32}{0}{{\hexprefix{}f0f0f0f}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCSAR2PATTTAB2}\item [APB\_SARADC\_SAR2\_PATT\_TAB2] Item 4 \verb+~+ 7 for pattern table 2 (each item one byte). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_SAR2\_PATT\_TAB3\_REG}{\hexprefix{}0030}\label{regdesc:APBSARADCSAR2PATTTAB3REG}
\regfield{APB\_SARADC\_SAR2\_PATT\_TAB3}{32}{0}{{\hexprefix{}f0f0f0f}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCSAR2PATTTAB3}\item [APB\_SARADC\_SAR2\_PATT\_TAB3] Item 8 \verb+~+ 11 for pattern table 2 (each item one byte). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_SAR2\_PATT\_TAB4\_REG}{\hexprefix{}0034}\label{regdesc:APBSARADCSAR2PATTTAB4REG}
\regfield{APB\_SARADC\_SAR2\_PATT\_TAB4}{32}{0}{{\hexprefix{}f0f0f0f}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCSAR2PATTTAB4}\item [APB\_SARADC\_SAR2\_PATT\_TAB4] Item 12 \verb+~+ 15 for pattern table 2 (each item one byte). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_ARB\_CTRL\_REG}{\hexprefix{}0038}\label{regdesc:APBSARADCARBCTRLREG}
\regfield{(reserved)}{19}{13}{0000000000000000000}%
\regfield{APB\_SARADC\_ADC\_ARB\_FIX\_PRIORITY}{1}{12}{{0}}%
\regfield{APB\_SARADC\_ADC\_ARB\_WIFI\_PRIORITY}{2}{10}{{2}}%
\regfield{APB\_SARADC\_ADC\_ARB\_RTC\_PRIORITY}{2}{8}{{1}}%
\regfield{APB\_SARADC\_ADC\_ARB\_APB\_PRIORITY}{2}{6}{{0}}%
\regfield{APB\_SARADC\_ADC\_ARB\_GRANT\_FORCE}{1}{5}{{0}}%
\regfield{APB\_SARADC\_ADC\_ARB\_WIFI\_FORCE}{1}{4}{{0}}%
\regfield{APB\_SARADC\_ADC\_ARB\_RTC\_FORCE}{1}{3}{{0}}%
\regfield{APB\_SARADC\_ADC\_ARB\_APB\_FORCE}{1}{2}{{0}}%
\regfield{(reserved)}{2}{0}{00}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCADCARBAPBFORCE}\item [APB\_SARADC\_ADC\_ARB\_APB\_FORCE] ADC2 arbiter forces to enable DIG ADC2 CTRL. (R/W)
\label{fielddesc:APBSARADCADCARBRTCFORCE}\item [APB\_SARADC\_ADC\_ARB\_RTC\_FORCE] ADC2 arbiter forces to enable RTC ADC2 CTRL. (R/W)
\label{fielddesc:APBSARADCADCARBWIFIFORCE}\item [APB\_SARADC\_ADC\_ARB\_WIFI\_FORCE] ADC2 arbiter forces to enable PWDET/PKDET CTRL. (R/W)
\label{fielddesc:APBSARADCADCARBGRANTFORCE}\item [APB\_SARADC\_ADC\_ARB\_GRANT\_FORCE] ADC2 arbiter force grant. (R/W)
\label{fielddesc:APBSARADCADCARBAPBPRIORITY}\item [APB\_SARADC\_ADC\_ARB\_APB\_PRIORITY] Set DIG ADC2 CTRL priority. (R/W)
\label{fielddesc:APBSARADCADCARBRTCPRIORITY}\item [APB\_SARADC\_ADC\_ARB\_RTC\_PRIORITY] Set RTC ADC2 CTRL priority. (R/W)
\label{fielddesc:APBSARADCADCARBWIFIPRIORITY}\item [APB\_SARADC\_ADC\_ARB\_WIFI\_PRIORITY] Set PWDET/PKDET CTRL priority. (R/W)
\label{fielddesc:APBSARADCADCARBFIXPRIORITY}\item [APB\_SARADC\_ADC\_ARB\_FIX\_PRIORITY] ADC2 arbiter uses fixed priority. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_FILTER\_CTRL\_REG}{\hexprefix{}003C}\label{regdesc:APBSARADCFILTERCTRLREG}
\regfield{APB\_SARADC\_ADC1\_FILTER\_EN}{1}{31}{{0}}%
\regfield{APB\_SARADC\_ADC2\_FILTER\_EN}{1}{30}{{0}}%
\regfield{APB\_SARADC\_ADC1\_FILTER\_FACTOR}{7}{23}{{64}}%
\regfield{APB\_SARADC\_ADC2\_FILTER\_FACTOR}{7}{16}{{64}}%
\regfield{(reserved)}{14}{2}{00000000000000}%
\regfield{APB\_SARADC\_ADC1\_FILTER\_RESET}{1}{1}{{0}}%
\regfield{APB\_SARADC\_ADC2\_FILTER\_RESET}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCADC2FILTERRESET}\item [APB\_SARADC\_ADC2\_FILTER\_RESET] Reset ADC2 filter. (R/W)
\label{fielddesc:APBSARADCADC1FILTERRESET}\item [APB\_SARADC\_ADC1\_FILTER\_RESET] Reset ADC1 filter. (R/W)
\label{fielddesc:APBSARADCADC2FILTERFACTOR}\item [APB\_SARADC\_ADC2\_FILTER\_FACTOR] Set filter factor for DIG ADC2 CRTL. (R/W)
\label{fielddesc:APBSARADCADC1FILTERFACTOR}\item [APB\_SARADC\_ADC1\_FILTER\_FACTOR] Set filter factor for DIG ADC1 CRTL. (R/W)
\label{fielddesc:APBSARADCADC2FILTEREN}\item [APB\_SARADC\_ADC2\_FILTER\_EN] Enable DIG ADC2 CRTL filter. (R/W)
\label{fielddesc:APBSARADCADC1FILTEREN}\item [APB\_SARADC\_ADC1\_FILTER\_EN] Enable DIG ADC1 CRTL filter. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_FILTER\_STATUS\_REG}{\hexprefix{}0040}\label{regdesc:APBSARADCFILTERSTATUSREG}
\regfield{APB\_SARADC\_ADC1\_FILTER\_DATA}{16}{16}{{0}}%
\regfield{APB\_SARADC\_ADC2\_FILTER\_DATA}{16}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCADC2FILTERDATA}\item [APB\_SARADC\_ADC2\_FILTER\_DATA] ADC2 filter data. (RO)
\label{fielddesc:APBSARADCADC1FILTERDATA}\item [APB\_SARADC\_ADC1\_FILTER\_DATA] ADC1 filter data. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_THRES\_CTRL\_REG}{\hexprefix{}0044}\label{regdesc:APBSARADCTHRESCTRLREG}
\regfield{APB\_SARADC\_ADC1\_THRES\_EN}{1}{31}{{0}}%
\regfield{APB\_SARADC\_ADC2\_THRES\_EN}{1}{30}{{0}}%
\regfield{APB\_SARADC\_ADC1\_THRES}{13}{17}{{0}}%
\regfield{APB\_SARADC\_ADC2\_THRES}{13}{4}{{0}}%
\regfield{APB\_SARADC\_ADC1\_THRES\_MODE}{1}{3}{{0}}%
\regfield{APB\_SARADC\_ADC2\_THRES\_MODE}{1}{2}{{0}}%
\regfield{(reserved)}{1}{1}{0}%
\regfield{APB\_SARADC\_CLK\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCCLKEN}\item [APB\_SARADC\_CLK\_EN] Clock gate enable. (R/W)
\label{fielddesc:APBSARADCADC2THRESMODE}\item [APB\_SARADC\_ADC2\_THRES\_MODE] 1: ADC\_DATA > = threshold, generate interrupt. 0: ADC\_DATA < threshold, generate interrupt. (R/W)
\label{fielddesc:APBSARADCADC1THRESMODE}\item [APB\_SARADC\_ADC1\_THRES\_MODE] 1: ADC\_DATA > = threshold, generate interrupt. 0: ADC\_DATA < threshold, generate interrupt. (R/W)
\label{fielddesc:APBSARADCADC2THRES}\item [APB\_SARADC\_ADC2\_THRES] ADC2 threshold. (R/W)
\label{fielddesc:APBSARADCADC1THRES}\item [APB\_SARADC\_ADC1\_THRES] ADC1 threshold. (R/W)
\label{fielddesc:APBSARADCADC2THRESEN}\item [APB\_SARADC\_ADC2\_THRES\_EN] Enable ADC2 threshold monitor. (R/W)
\label{fielddesc:APBSARADCADC1THRESEN}\item [APB\_SARADC\_ADC1\_THRES\_EN] Enable ADC1 threshold monitor. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_INT\_ENA\_REG}{\hexprefix{}0048}\label{regdesc:APBSARADCINTENAREG}
\regfield{APB\_SARADC\_ADC1\_DONE\_INT\_ENA}{1}{31}{{0}}%
\regfield{APB\_SARADC\_ADC2\_DONE\_INT\_ENA}{1}{30}{{0}}%
\regfield{APB\_SARADC\_ADC1\_THRES\_INT\_ENA}{1}{29}{{0}}%
\regfield{APB\_SARADC\_ADC2\_THRES\_INT\_ENA}{1}{28}{{0}}%
\regfield{(reserved)}{28}{0}{0000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCADC2THRESINTENA}\item [APB\_SARADC\_ADC2\_THRES\_INT\_ENA] Enable bit of \hyperref[interreupt:SARADCTHRESINT2]{APB\_SARADC\_ADC2\_THRES\_INT} interrupt. (R/W)
\label{fielddesc:APBSARADCADC1THRESINTENA}\item [APB\_SARADC\_ADC1\_THRES\_INT\_ENA] Enable bit of \hyperref[interreupt:SARADCTHRESINT1]{APB\_SARADC\_ADC1\_THRES\_INT} interrupt. (R/W)
\label{fielddesc:APBSARADCADC2DONEINTENA}\item [APB\_SARADC\_ADC2\_DONE\_INT\_ENA] Enable bit of \hyperref[interreupt:SARADCDONEINT2]{APB\_SARADC\_ADC2\_DONE\_INT} interrupt. (R/W)
\label{fielddesc:APBSARADCADC1DONEINTENA}\item [APB\_SARADC\_ADC1\_DONE\_INT\_ENA] Enable bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_ADC1\_DONE\_INT} interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_INT\_RAW\_REG}{\hexprefix{}004C}\label{regdesc:APBSARADCINTRAWREG}
\regfield{APB\_SARADC\_ADC1\_DONE\_INT\_RAW}{1}{31}{{0}}%
\regfield{APB\_SARADC\_ADC2\_DONE\_INT\_RAW}{1}{30}{{0}}%
\regfield{APB\_SARADC\_ADC1\_THRES\_INT\_RAW}{1}{29}{{0}}%
\regfield{APB\_SARADC\_ADC2\_THRES\_INT\_RAW}{1}{28}{{0}}%
\regfield{(reserved)}{28}{0}{0000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCADC2THRESINTRAW}\item [APB\_SARADC\_ADC2\_THRES\_INT\_RAW] Raw bit of \hyperref[interreupt:SARADCTHRESINT2]{APB\_SARADC\_ADC2\_THRES\_INT} interrupt. (RO)
\label{fielddesc:APBSARADCADC1THRESINTRAW}\item [APB\_SARADC\_ADC1\_THRES\_INT\_RAW] Raw bit of \hyperref[interreupt:SARADCTHRESINT1]{APB\_SARADC\_ADC1\_THRES\_INT} interrupt. (RO)
\label{fielddesc:APBSARADCADC2DONEINTRAW}\item [APB\_SARADC\_ADC2\_DONE\_INT\_RAW] Raw bit of \hyperref[interreupt:SARADCDONEINT2]{APB\_SARADC\_ADC2\_DONE\_INT} interrupt. (RO)
\label{fielddesc:APBSARADCADC1DONEINTRAW}\item [APB\_SARADC\_ADC1\_DONE\_INT\_RAW] Raw bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_ADC1\_DONE\_INT} interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_INT\_ST\_REG}{\hexprefix{}0050}\label{regdesc:APBSARADCINTSTREG}
\regfield{APB\_SARADC\_ADC1\_DONE\_INT\_ST}{1}{31}{{0}}%
\regfield{APB\_SARADC\_ADC2\_DONE\_INT\_ST}{1}{30}{{0}}%
\regfield{APB\_SARADC\_ADC1\_THRES\_INT\_ST}{1}{29}{{0}}%
\regfield{APB\_SARADC\_ADC2\_THRES\_INT\_ST}{1}{28}{{0}}%
\regfield{(reserved)}{28}{0}{0000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCADC2THRESINTST}\item [APB\_SARADC\_ADC2\_THRES\_INT\_ST] Status of \hyperref[interreupt:SARADCTHRESINT2]{APB\_SARADC\_ADC2\_THRES\_INT} interrupt. (RO)
\label{fielddesc:APBSARADCADC1THRESINTST}\item [APB\_SARADC\_ADC1\_THRES\_INT\_ST] Status of \hyperref[interreupt:SARADCTHRESINT1]{APB\_SARADC\_ADC1\_THRES\_INT} interrupt. (RO)
\label{fielddesc:APBSARADCADC2DONEINTST}\item [APB\_SARADC\_ADC2\_DONE\_INT\_ST] Status of \hyperref[interreupt:SARADCDONEINT2]{APB\_SARADC\_ADC2\_DONE\_INT} interrupt. (RO)
\label{fielddesc:APBSARADCADC1DONEINTST}\item [APB\_SARADC\_ADC1\_DONE\_INT\_ST] Status of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_ADC1\_DONE\_INT} interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_INT\_CLR\_REG}{\hexprefix{}0054}\label{regdesc:APBSARADCINTCLRREG}
\regfield{APB\_SARADC\_ADC1\_DONE\_INT\_CLR}{1}{31}{{0}}%
\regfield{APB\_SARADC\_ADC2\_DONE\_INT\_CLR}{1}{30}{{0}}%
\regfield{APB\_SARADC\_ADC1\_THRES\_INT\_CLR}{1}{29}{{0}}%
\regfield{APB\_SARADC\_ADC2\_THRES\_INT\_CLR}{1}{28}{{0}}%
\regfield{(reserved)}{28}{0}{0000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCADC2THRESINTCLR}\item [APB\_SARADC\_ADC2\_THRES\_INT\_CLR] Clear bit of \hyperref[interreupt:SARADCTHRESINT2]{APB\_SARADC\_ADC2\_THRES\_INT} interrupt. (WO)
\label{fielddesc:APBSARADCADC1THRESINTCLR}\item [APB\_SARADC\_ADC1\_THRES\_INT\_CLR] Clear bit of \hyperref[interreupt:SARADCTHRESINT1]{APB\_SARADC\_ADC1\_THRES\_INT} interrupt. (WO)
\label{fielddesc:APBSARADCADC2DONEINTCLR}\item [APB\_SARADC\_ADC2\_DONE\_INT\_CLR] Clear bit of \hyperref[interreupt:SARADCDONEINT2]{APB\_SARADC\_ADC2\_DONE\_INT} interrupt. (WO)
\label{fielddesc:APBSARADCADC1DONEINTCLR}\item [APB\_SARADC\_ADC1\_DONE\_INT\_CLR] Clear bit of \hyperref[interreupt:SARADCDONEINT1]{APB\_SARADC\_ADC1\_DONE\_INT} interrupt. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_DMA\_CONF\_REG}{\hexprefix{}0058}\label{regdesc:APBSARADCDMACONFREG}
\regfield{APB\_SARADC\_APB\_ADC\_TRANS}{1}{31}{{0}}%
\regfield{APB\_SARADC\_APB\_ADC\_RESET\_FSM}{1}{30}{{0}}%
\regfield{(reserved)}{14}{16}{00000000000000}%
\regfield{APB\_SARADC\_APB\_ADC\_EOF\_NUM}{16}{0}{{255}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCAPBADCEOFNUM}\item [APB\_SARADC\_APB\_ADC\_EOF\_NUM] Generate dma\_in\_suc\_eof when sample cnt = spi\_eof\_num. (R/W)
\label{fielddesc:APBSARADCAPBADCRESETFSM}\item [APB\_SARADC\_APB\_ADC\_RESET\_FSM] Reset DIG ADC CTRL status. (R/W)
\label{fielddesc:APBSARADCAPBADCTRANS}\item [APB\_SARADC\_APB\_ADC\_TRANS] Set this bit, DIG ADC CTRL uses SPI DMA. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_APB\_DAC\_CTRL\_REG}{\hexprefix{}0060}\label{regdesc:APBSARADCAPBDACCTRLREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{APB\_SARADC\_APB\_DAC\_RST}{1}{16}{{0}}%
\regfield{APB\_SARADC\_DAC\_RESET\_FIFO}{1}{15}{{0}}%
\regfield{APB\_SARADC\_APB\_DAC\_TRANS}{1}{14}{{0}}%
\regfield{APB\_SARADC\_APB\_DAC\_ALTER\_MODE}{1}{13}{{1}}%
\regfield{APB\_SARADC\_DAC\_TIMER\_EN}{1}{12}{{0}}%
\regfield{APB\_SARADC\_DAC\_TIMER\_TARGET}{12}{0}{{100}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCDACTIMERTARGET}\item [APB\_SARADC\_DAC\_TIMER\_TARGET] Set DAC timer target. (R/W)
\label{fielddesc:APBSARADCDACTIMEREN}\item [APB\_SARADC\_DAC\_TIMER\_EN] Enable read dac data. (R/W)
\label{fielddesc:APBSARADCAPBDACALTERMODE}\item [APB\_SARADC\_APB\_DAC\_ALTER\_MODE] Enable DAC alter mode. (R/W)
\label{fielddesc:APBSARADCAPBDACTRANS}\item [APB\_SARADC\_APB\_DAC\_TRANS] Enable DMA\_DAC. (R/W)
\label{fielddesc:APBSARADCDACRESETFIFO}\item [APB\_SARADC\_DAC\_RESET\_FIFO] Reset DIG DAC FIFO. (R/W)
\label{fielddesc:APBSARADCAPBDACRST}\item [APB\_SARADC\_APB\_DAC\_RST] Reset DIG DAC by software. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{APB\_SARADC\_APB\_CTRL\_DATE\_REG}{\hexprefix{}03FC}\label{regdesc:APBSARADCAPBCTRLDATEREG}
\regfield{APB\_SARADC\_APB\_CTRL\_DATE}{32}{0}{{\hexprefix{}1907162}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:APBSARADCAPBCTRLDATE}\item [APB\_SARADC\_APB\_CTRL\_DATE] Version control register (R/W)
\end{reglist}\end{regdesc}
\end{register}
