\begin{register}{H}{SENS\_SAR\_READER1\_CTRL\_REG}{\hexprefix{}0000}\label{regdesc:SENSSARREADER1CTRLREG}
\regfield{(reserved)}{2}{30}{00}%
\regfield{SENS\_SAR1\_INT\_EN}{1}{29}{{1}}%
\regfield{SENS\_SAR1\_DATA\_INV}{1}{28}{{0}}%
\regfield{(reserved)}{20}{8}{00000000000000000000}%
\regfield{SENS\_SAR1\_CLK\_DIV}{8}{0}{{2}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SENSSAR1CLKDIV}\item [SENS\_SAR1\_CLK\_DIV] Clock divider. (R/W)
\label{fielddesc:SENSSAR1DATAINV}\item [SENS\_SAR1\_DATA\_INV] Invert SAR ADC1 data. (R/W)
\label{fielddesc:SENSSAR1INTEN}\item [SENS\_SAR1\_INT\_EN] Enable SAR ADC1 to send out interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_MEAS1\_CTRL1\_REG}{\hexprefix{}0008}\label{regdesc:SENSSARMEAS1CTRL1REG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{SENS\_RTC\_SARADC\_CLKGATE\_EN}{1}{23}{{0}}%
\regfield{SENS\_RTC\_SARADC\_RESET}{1}{22}{{0}}%
\regfield{(reserved)}{22}{0}{0000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SENSRTCSARADCRESET}\item [SENS\_RTC\_SARADC\_RESET] SAR ADC software reset. (R/W)
\label{fielddesc:SENSRTCSARADCCLKGATEEN}\item [SENS\_RTC\_SARADC\_CLKGATE\_EN] Enable bit of SAR ADC clock gate. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_MEAS1\_CTRL2\_REG}{\hexprefix{}000C}\label{regdesc:SENSSARMEAS1CTRL2REG}
\regfield{SENS\_SAR1\_EN\_PAD\_FORCE}{1}{31}{{0}}%
\regfield{SENS\_SAR1\_EN\_PAD}{12}{19}{{0}}%
\regfield{SENS\_MEAS1\_START\_FORCE}{1}{18}{{0}}%
\regfield{SENS\_MEAS1\_START\_SAR}{1}{17}{{0}}%
\regfield{SENS\_MEAS1\_DONE\_SAR}{1}{16}{{0}}%
\regfield{SENS\_MEAS1\_DATA\_SAR}{16}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SENSMEAS1DATASAR}\item [SENS\_MEAS1\_DATA\_SAR] SAR ADC1 data. (RO)
\label{fielddesc:SENSMEAS1DONESAR}\item [SENS\_MEAS1\_DONE\_SAR] Indicate SAR ADC1 conversion is done. (RO)
\label{fielddesc:SENSMEAS1STARTSAR}\item [SENS\_MEAS1\_START\_SAR] SAR ADC1 controller (in RTC) starts conversion, active only when SENS\_MEAS1\_START\_FORCE = 1. (R/W)
\label{fielddesc:SENSMEAS1STARTFORCE}\item [SENS\_MEAS1\_START\_FORCE] 1: SAR ADC1 controller (in RTC) is started by software. 0: SAR ADC1 controller is started by ULP coprocessor. (R/W)
\label{fielddesc:SENSSAR1ENPAD}\item [SENS\_SAR1\_EN\_PAD] SAR ADC1 pad enable bitmap, active only when SENS\_SAR1\_EN\_PAD\_FORCE = 1. (R/W)
\label{fielddesc:SENSSAR1ENPADFORCE}\item [SENS\_SAR1\_EN\_PAD\_FORCE] 1: SAR ADC1 pad enable bitmap is controlled by software. 0: SAR ADC1 pad enable bitmap is controlled by ULP coprocessor. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_MEAS1\_MUX\_REG}{\hexprefix{}0010}\label{regdesc:SENSSARMEAS1MUXREG}
\regfield{SENS\_SAR1\_DIG\_FORCE}{1}{31}{{0}}%
\regfield{(reserved)}{31}{0}{0000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SENSSAR1DIGFORCE}\item [SENS\_SAR1\_DIG\_FORCE] 1: SAR ADC1 controlled by DIG ADC1 CTRL. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_ATTEN1\_REG}{\hexprefix{}0014}\label{regdesc:SENSSARATTEN1REG}
\regfield{SENS\_SAR1\_ATTEN}{32}{0}{{\hexprefix{}ffffffff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SENSSAR1ATTEN}\item [SENS\_SAR1\_ATTEN] 2-bit attenuation for each pad. [1:0] is used for channel 0, [3:2] is used for channel 1, etc. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_ATTEN2\_REG}{\hexprefix{}0038}\label{regdesc:SENSSARATTEN2REG}
\regfield{SENS\_SAR2\_ATTEN}{32}{0}{{\hexprefix{}ffffffff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SENSSAR2ATTEN}\item [SENS\_SAR2\_ATTEN] 2-bit attenuation for each pad. [1:0] is used for channel 0, [3:2] is used for channel 1, etc. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{SENS\_SAR\_AMP\_CTRL3\_REG}{\hexprefix{}0020}\label{regdesc:SENSSARAMPCTRL3REG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{SENS\_SAR1\_DAC\_XPD\_FSM}{4}{0}{{3}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SENSSAR1DACXPDFSM}\item [SENS\_SAR1\_DAC\_XPD\_FSM] Control of DAC. 4'b0010: disable DAC. 4'b0000: power up DAC by FSM. 4'b0011: power up DAC by software. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{SENS\_SAR\_READER2\_CTRL\_REG}{\hexprefix{}0024}\label{regdesc:SENSSARREADER2CTRLREG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{SENS\_SAR2\_INT\_EN}{1}{30}{{1}}%
\regfield{SENS\_SAR2\_DATA\_INV}{1}{29}{{0}}%
\regfield{(reserved)}{11}{18}{00000000000}%
\regfield{SENS\_SAR2\_WAIT\_ARB\_CYCLE}{2}{16}{{1}}%
\regfield{(reserved)}{8}{8}{00000000}%
\regfield{SENS\_SAR2\_CLK\_DIV}{8}{0}{{2}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SENSSAR2CLKDIV}\item [SENS\_SAR2\_CLK\_DIV] Clock divider. (R/W)
\label{fielddesc:SENSSAR2WAITARBCYCLE}\item [SENS\_SAR2\_WAIT\_ARB\_CYCLE] Wait arbiter stable after sar\_done. (R/W)
\label{fielddesc:SENSSAR2DATAINV}\item [SENS\_SAR2\_DATA\_INV] Invert SAR ADC2 data. (R/W)
\label{fielddesc:SENSSAR2INTEN}\item [SENS\_SAR2\_INT\_EN] Enable SAR ADC2 to send out interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}



\begin{register}{H}{SENS\_SAR\_MEAS2\_CTRL2\_REG}{\hexprefix{}0030}\label{regdesc:SENSSARMEAS2CTRL2REG}
\regfield{SENS\_SAR2\_EN\_PAD\_FORCE}{1}{31}{{0}}%
\regfield{SENS\_SAR2\_EN\_PAD}{12}{19}{{0}}%
\regfield{SENS\_MEAS2\_START\_FORCE}{1}{18}{{0}}%
\regfield{SENS\_MEAS2\_START\_SAR}{1}{17}{{0}}%
\regfield{SENS\_MEAS2\_DONE\_SAR}{1}{16}{{0}}%
\regfield{SENS\_MEAS2\_DATA\_SAR}{16}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SENSMEAS2DATASAR}\item [SENS\_MEAS2\_DATA\_SAR] SAR ADC2 data. (RO)
\label{fielddesc:SENSMEAS2DONESAR}\item [SENS\_MEAS2\_DONE\_SAR] Indicate SAR ADC2 conversion is done. (RO)
\label{fielddesc:SENSMEAS2STARTSAR}\item [SENS\_MEAS2\_START\_SAR] SAR ADC2 controller (in RTC) starts conversion, active only when SENS\_MEAS2\_START\_FORCE = 1. (R/W)
\label{fielddesc:SENSMEAS2STARTFORCE}\item [SENS\_MEAS2\_START\_FORCE] 1: SAR ADC2 controller (in RTC) is started by software.  0: SAR ADC2 controller is started by ULP coprocessor. (R/W)
\label{fielddesc:SENSSAR2ENPAD}\item [SENS\_SAR2\_EN\_PAD] SAR ADC2 pad enable bitmap, active    only    whenSENS\_SAR2\_EN\_PAD\_FORCE = 1. (R/W)
\label{fielddesc:SENSSAR2ENPADFORCE}\item [SENS\_SAR2\_EN\_PAD\_FORCE] 1: SAR ADC2 pad enable bitmap is controlled by software. 0: SAR ADC2 pad enable bitmap is controlled by ULP coprocessor.  (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_MEAS2\_MUX\_REG}{\hexprefix{}0034}\label{regdesc:SENSSARMEAS2MUXREG}
\regfield{SENS\_SAR2\_RTC\_FORCE}{1}{31}{{0}}%
\regfield{SENS\_SAR2\_PWDET\_CCT}{3}{28}{{0}}%
\regfield{(reserved)}{28}{0}{0000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SENSSAR2PWDETCCT}\item [SENS\_SAR2\_PWDET\_CCT] SAR2\_PWDET\_CCT, PA power detector capacitance tuning. (R/W)
\label{fielddesc:SENSSAR2RTCFORCE}\item [SENS\_SAR2\_RTC\_FORCE] In sleep, force to use RTC to control ADC. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_TSENS\_CTRL\_REG}{\hexprefix{}0050}\label{regdesc:SENSSARTSENSCTRLREG}
\regfield{(reserved)}{7}{25}{0000000}%
\regfield{SENS\_TSENS\_DUMP\_OUT}{1}{24}{{0}}%
\regfield{SENS\_TSENS\_POWER\_UP\_FORCE}{1}{23}{{0}}%
\regfield{SENS\_TSENS\_POWER\_UP}{1}{22}{{0}}%
\regfield{SENS\_TSENS\_CLK\_DIV}{8}{14}{{6}}%
\regfield{SENS\_TSENS\_IN\_INV}{1}{13}{{0}}%
\regfield{SENS\_TSENS\_INT\_EN}{1}{12}{{1}}%
\regfield{(reserved)}{3}{9}{000}%
\regfield{SENS\_TSENS\_READY}{1}{8}{{0}}%
\regfield{SENS\_TSENS\_OUT}{8}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SENSTSENSOUT}\item [SENS\_TSENS\_OUT] Temperature sensor data out. (RO)
\label{fielddesc:SENSTSENSREADY}\item [SENS\_TSENS\_READY] Indicate temperature sensor out ready. (RO)
\label{fielddesc:SENSTSENSINTEN}\item [SENS\_TSENS\_INT\_EN] Enable temperature sensor to send out interrupt. (R/W)
\label{fielddesc:SENSTSENSININV}\item [SENS\_TSENS\_IN\_INV] Invert temperature sensor data. (R/W)
\label{fielddesc:SENSTSENSCLKDIV}\item [SENS\_TSENS\_CLK\_DIV] Temperature sensor clock divider. (R/W)
\label{fielddesc:SENSTSENSPOWERUP}\item [SENS\_TSENS\_POWER\_UP] Temperature sensor power up. (R/W)
\label{fielddesc:SENSTSENSPOWERUPFORCE}\item [SENS\_TSENS\_POWER\_UP\_FORCE] 1: dump out and power up controlled by software. 0: by FSM. (R/W)
\label{fielddesc:SENSTSENSDUMPOUT}\item [SENS\_TSENS\_DUMP\_OUT] Temperature sensor dump out only active when SENS\_TSENS\_POWER\_UP\_FORCE = 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_TSENS\_CTRL2\_REG}{\hexprefix{}0054}\label{regdesc:SENSSARTSENSCTRL2REG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{SENS\_TSENS\_RESET}{1}{16}{{0}}%
\regfield{SENS\_TSENS\_CLKGATE\_EN}{1}{15}{{0}}%
\regfield{(reserved)}{15}{0}{000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SENSTSENSCLKGATEEN}\item [SENS\_TSENS\_CLKGATE\_EN] Enable temperature sensor clock. (R/W)
\label{fielddesc:SENSTSENSRESET}\item [SENS\_TSENS\_RESET] Reset temperature sensor. (R/W)
\end{reglist}\end{regdesc}
\end{register}



\begin{register}{H}{SENS\_SAR\_DAC\_CTRL1\_REG}{\hexprefix{}011C}\label{regdesc:SENSSARDACCTRL1REG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{SENS\_DAC\_CLKGATE\_EN}{1}{27}{{0}}%
\regfield{SENS\_DAC\_RESET}{1}{26}{{0}}%
\regfield{SENS\_DAC\_CLK\_INV}{1}{25}{{0}}%
\regfield{SENS\_DAC\_CLK\_FORCE\_HIGH}{1}{24}{{0}}%
\regfield{SENS\_DAC\_CLK\_FORCE\_LOW}{1}{23}{{0}}%
\regfield{SENS\_DAC\_DIG\_FORCE}{1}{22}{{0}}%
\regfield{(reserved)}{5}{17}{00000}%
\regfield{SENS\_SW\_TONE\_EN}{1}{16}{{0}}%
\regfield{SENS\_SW\_FSTEP}{16}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SENSSWFSTEP}\item [SENS\_SW\_FSTEP] Frequency step for CW generator can be used to adjust the frequency. (R/W)
\label{fielddesc:SENSSWTONEEN}\item [SENS\_SW\_TONE\_EN] 0: disable CW generator. 1: enable CW generator. (R/W)
\label{fielddesc:SENSDACDIGFORCE}\item [SENS\_DAC\_DIG\_FORCE] 0: DAC1 and DAC2 do not use DMA. 1: DAC1 and DAC2 use DMA. (R/W)
\label{fielddesc:SENSDACCLKFORCELOW}\item [SENS\_DAC\_CLK\_FORCE\_LOW] 1: force PDAC\_CLK to low. (R/W)
\label{fielddesc:SENSDACCLKFORCEHIGH}\item [SENS\_DAC\_CLK\_FORCE\_HIGH] 1: force PDAC\_CLK to high. (R/W)
\label{fielddesc:SENSDACCLKINV}\item [SENS\_DAC\_CLK\_INV] 1: invert PDAC\_CLK. (R/W)
\label{fielddesc:SENSDACRESET}\item [SENS\_DAC\_RESET] Reset DAC by software. (R/W)
\label{fielddesc:SENSDACCLKGATEEN}\item [SENS\_DAC\_CLKGATE\_EN] DAC clock gate enable bit. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_DAC\_CTRL2\_REG}{\hexprefix{}0120}\label{regdesc:SENSSARDACCTRL2REG}
\regfield{(reserved)}{6}{26}{000000}%
\regfield{SENS\_DAC\_CW\_EN2}{1}{25}{{1}}%
\regfield{SENS\_DAC\_CW\_EN1}{1}{24}{{1}}%
\regfield{SENS\_DAC\_INV2}{2}{22}{{0}}%
\regfield{SENS\_DAC\_INV1}{2}{20}{{0}}%
\regfield{SENS\_DAC\_SCALE2}{2}{18}{{0}}%
\regfield{SENS\_DAC\_SCALE1}{2}{16}{{0}}%
\regfield{SENS\_DAC\_DC2}{8}{8}{{0}}%
\regfield{SENS\_DAC\_DC1}{8}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SENSDACDC1}\item [SENS\_DAC\_DC1] DC offset for DAC1 CW generator. (R/W)
\label{fielddesc:SENSDACDC2}\item [SENS\_DAC\_DC2] DC offset for DAC2 CW generator. (R/W)
\label{fielddesc:SENSDACSCALE1}\item [SENS\_DAC\_SCALE1] DAC1 scaling. 00: no scale. 01: scale to 1/2. 10: scale to 1/4. 11: scale to 1/8. (R/W)
\label{fielddesc:SENSDACSCALE2}\item [SENS\_DAC\_SCALE2] DAC2 scaling. 00: no scale. 01: scale to 1/2. 10: scale to 1/4. 11: scale to 1/8. (R/W)
\label{fielddesc:SENSDACINV1}\item [SENS\_DAC\_INV1] Invert DAC1. 00: do not invert any bits. 01: invert all bits. 10: invert MSB. 11: invert all bits except MSB. (R/W)
\label{fielddesc:SENSDACINV2}\item [SENS\_DAC\_INV2] Invert DAC2. 00: do not invert any bits. 01: invert all bits. 10: invert MSB. 11: invert all bits except MSB. (R/W)
\label{fielddesc:SENSDACCWEN1}\item [SENS\_DAC\_CW\_EN1] 1: select CW generator as source for PDAC1\_DAC. 0: select register RTCIO\_PDAC1\_DAC as source for PDAC1\_DAC. (R/W)
\label{fielddesc:SENSDACCWEN2}\item [SENS\_DAC\_CW\_EN2] 1: select CW generator as source for PDAC2\_DAC. 0: select register RTCIO\_PDAC2\_DAC as source for PDAC2\_DAC. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{SENS\_SAR\_IO\_MUX\_CONF\_REG}{\hexprefix{}0144}\label{regdesc:SENSSARIOMUXCONFREG}
\regfield{SENS\_IOMUX\_CLK\_GATE\_EN}{1}{31}{{0}}%
\regfield{SENS\_IOMUX\_RESET}{1}{30}{{0}}%
\regfield{(reserved)}{30}{0}{000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:SENSIOMUXRESET}\item [SENS\_IOMUX\_RESET] Reset IO MUX by software (R/W)
\label{fielddesc:SENSIOMUXCLKGATEEN}\item [SENS\_IOMUX\_CLK\_GATE\_EN] IO MUX clock gate enable bit (R/W)
\end{reglist}\end{regdesc}
\end{register}
