\begin{register}{H}{LP\_I2S\_VAD\_CONF\_REG}{0x0000}\label{regdesc:LPI2SVADCONFREG}
\regfield{(reserved)}{29}{3}{00000000000000000000000000000}%
\regfield{LP\_I2S\_VAD\_FORCE\_START}{1}{2}{{0}}%
\regfield{LP\_I2S\_VAD\_RESET}{1}{1}{{0}}%
\regfield{LP\_I2S\_VAD\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPI2SVADEN}\item [LP\_I2S\_VAD\_EN] Configures whether to enable the automatic operation mode.\\0: Disable\\1: Enable\\(R/W)
\label{fielddesc:LPI2SVADRESET}\item [LP\_I2S\_VAD\_RESET] Configures whether to reset the VAD module.\\0: Not reset\\1: Reset\\(WT)
\label{fielddesc:LPI2SVADFORCESTART}\item [LP\_I2S\_VAD\_FORCE\_START] Configures whether to trigger the manual operation on one frame of data.\\0: Not trigger\\1: Trigger\\(WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_I2S\_VAD\_RESULT\_REG}{0x0004}\label{regdesc:LPI2SVADRESULTREG}
\regfield{(reserved)}{30}{2}{000000000000000000000000000000}%
\regfield{LP\_I2S\_ENERGY\_ENOUGH}{1}{1}{{0}}%
\regfield{LP\_I2S\_VAD\_FLAG}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPI2SVADFLAG}\item [LP\_I2S\_VAD\_FLAG] Represents the voice activity status. For details, see Section \ref{sec:vad-param-config}. (RO)
\label{fielddesc:LPI2SENERGYENOUGH}\item [LP\_I2S\_ENERGY\_ENOUGH] Represents whether the current frame passes the energy threshold check. For details, see Section \ref{sec:vad-param-config}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_I2S\_VAD\_PARAM0\_REG}{0x0080}\label{regdesc:LPI2SVADPARAM0REG}
\regfield{(reserved)}{7}{25}{0000000}%
\regfield{LP\_I2S\_PARAM\_INIT\_FRAME\_NUM}{9}{16}{{200}}%
\regfield{LP\_I2S\_PARAM\_MIN\_ENERGY}{16}{0}{{5000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPI2SPARAMMINENERGY}\item [LP\_I2S\_PARAM\_MIN\_ENERGY] Configures the energy threshold. For details, see Section \ref{sec:vad-param-config}. (R/W)
\label{fielddesc:LPI2SPARAMINITFRAMENUM}\item [LP\_I2S\_PARAM\_INIT\_FRAME\_NUM] Configures the number of initial frames. For details, see Section \ref{sec:vad-param-config}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LP\_I2S\_VAD\_PARAM1\_REG}{0x0084}\label{regdesc:LPI2SVADPARAM1REG}
\regfield{LP\_I2S\_PARAM\_SKIP\_BAND\_ENERGY}{1}{31}{{0}}%
\regfield{(reserved)}{7}{24}{{0x0}}%
\regfield{LP\_I2S\_PARAM\_HANGOVER\_SILENT}{8}{16}{{30}}%
\regfield{LP\_I2S\_PARAM\_HANGOVER\_SPEECH}{5}{11}{{3}}%
\regfield{LP\_I2S\_PARAM\_MAX\_SPEECH\_COUNT}{7}{4}{{100}}%
\regfield{LP\_I2S\_PARAM\_MIN\_SPEECH\_COUNT}{4}{0}{{3}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPI2SPARAMMINSPEECHCOUNT}\item [LP\_I2S\_PARAM\_MIN\_SPEECH\_COUNT] Configures the transition between voice activity status. For details, see Section \ref{sec:vad-param-config}. (R/W)
\label{fielddesc:LPI2SPARAMMAXSPEECHCOUNT}\item [LP\_I2S\_PARAM\_MAX\_SPEECH\_COUNT] Configures the transition between voice activity status. For details, see Section \ref{sec:vad-param-config}. (R/W)
\label{fielddesc:LPI2SPARAMHANGOVERSPEECH}\item [LP\_I2S\_PARAM\_HANGOVER\_SPEECH] Configures the transition between voice activity status. For details, see Section \ref{sec:vad-param-config}. (R/W)
\label{fielddesc:LPI2SPARAMHANGOVERSILENT}\item [LP\_I2S\_PARAM\_HANGOVER\_SILENT] Configures the transition between voice activity status. For details, see Section \ref{sec:vad-param-config}. (R/W)
\label{fielddesc:LPI2SPARAMSKIPBANDENERGY}\item [LP\_I2S\_PARAM\_SKIP\_BAND\_ENERGY] Configures the transition between voice activity status. For details, see Section \ref{sec:vad-param-config}. (R/W)
\end{reglist}\end{regdesc}
\end{register}



\begin{register}{H}{LP\_I2S\_VAD\_OB0\_REG}{0x00B0}\label{regdesc:LPI2SVADOB0REG}
\regfield{(reserved)}{16}{16}{0x0}%
\regfield{LP\_I2S\_SILENT\_COUNT\_OB}{8}{8}{{0x0}}%
\regfield{LP\_I2S\_SPEECH\_COUNT\_OB}{8}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LPI2SSPEECHCOUNTOB}\item [LP\_I2S\_SPEECH\_COUNT\_OB] Represents the count value of the voice frame counter, speech\_count. For details, see Section \ref{sec:vad-param-config}. (RO)
\label{fielddesc:LPI2SSILENTCOUNTOB}\item [LP\_I2S\_SILENT\_COUNT\_OB] Represents the count value of the non-voice frame counter, silent\_count. For details, see Section \ref{sec:vad-param-config}. (RO)
\end{reglist}\end{regdesc}
\end{register}

