\begin{longtable}{ |m{6cm} |m{7.2cm} | m{1.3cm} |m{1cm} | }
\hline\rowcolor{lightgray}
Name & Description &  Address & Access \\ \hline
\endhead
\multicolumn{4}{|l|}{\textbf{Control Registers}} \\ \hline

\hyperref[regdesc:PMSPROIRAM00REG]{PMS\_PRO\_IRAM0\_0\_REG} & IBUS permission control register 0. & \hexprefix{}0010 & R/W \\ \hline
\hyperref[regdesc:PMSPRODRAM00REG]{PMS\_PRO\_DRAM0\_0\_REG} & DBUS permission control register 0. & \hexprefix{}0028 & R/W \\ \hline
\hyperref[regdesc:PMSPRODPORT0REG]{PMS\_PRO\_DPORT\_0\_REG} & PeriBus1 permission control register 0. & \hexprefix{}003C & R/W \\ \hline
\hyperref[regdesc:PMSPROAHB0REG]{PMS\_PRO\_AHB\_0\_REG} & PeriBus2 permission control register 0. & \hexprefix{}005C & R/W \\ \hline
\hyperref[regdesc:PMSPROTRACE0REG]{PMS\_PRO\_TRACE\_0\_REG} & Trace memory permission control register 0. & \hexprefix{}0070 & R/W \\ \hline
\hyperref[regdesc:PMSPROCACHE0REG]{PMS\_PRO\_CACHE\_0\_REG} & Cache permission control register 0. & \hexprefix{}0078 & R/W \\ \hline
\hyperref[regdesc:PMSDMAAPBI0REG]{PMS\_DMA\_APB\_I\_0\_REG} & Internal DMA permission control register 0. & \hexprefix{}008C & R/W \\ \hline
\hyperref[regdesc:PMSDMARXI0REG]{PMS\_DMA\_RX\_I\_0\_REG} & RX Copy DMA permission control register 0. & \hexprefix{}009C & R/W \\ \hline
\hyperref[regdesc:PMSDMATXI0REG]{PMS\_DMA\_TX\_I\_0\_REG} & TX Copy DMA permission control register 0. & \hexprefix{}00AC & R/W \\ \hline
\hyperref[regdesc:PMSCACHESOURCE0REG]{PMS\_CACHE\_SOURCE\_0\_REG} & Cache access permission control register 0. & \hexprefix{}00C4 & R/W \\ \hline
\hyperref[regdesc:PMSAPBPERIPHERAL0REG]{PMS\_APB\_PERIPHERAL\_0\_REG} & Peripheral access permission control register 0. & \hexprefix{}00CC & R/W \\ \hline
\hyperref[regdesc:PMSOCCUPY0REG]{PMS\_OCCUPY\_0\_REG} & Occupy permission control register 0. & \hexprefix{}00D4 & R/W \\ \hline
\hyperref[regdesc:PMSCACHETAGACCESS0REG]{PMS\_CACHE\_TAG\_ACCESS\_0\_REG} & Cache tag permission control register 0. & \hexprefix{}00E4 & R/W \\ \hline
\hyperref[regdesc:PMSCACHEMMUACCESS0REG]{PMS\_CACHE\_MMU\_ACCESS\_0\_REG} & Cache MMU permission control register 0. & \hexprefix{}00EC & R/W \\ \hline
\hyperref[regdesc:PMSCLOCKGATEREGREG]{PMS\_CLOCK\_GATE\_REG\_REG} & Clock gate register of permission control. & \hexprefix{}0104 & R/W \\ \hline
\multicolumn{4}{|l|}{\textbf{Configuration Registers}} \\ \hline

\hyperref[regdesc:PMSPROIRAM01REG]{PMS\_PRO\_IRAM0\_1\_REG} & IBUS permission control register 1. & \hexprefix{}0014 & R/W \\ \hline
\hyperref[regdesc:PMSPROIRAM02REG]{PMS\_PRO\_IRAM0\_2\_REG} & IBUS permission control register 2. & \hexprefix{}0018 & R/W \\ \hline
\hyperref[regdesc:PMSPROIRAM03REG]{PMS\_PRO\_IRAM0\_3\_REG} & IBUS permission control register 3. & \hexprefix{}001C & R/W \\ \hline
\hyperref[regdesc:PMSPRODRAM01REG]{PMS\_PRO\_DRAM0\_1\_REG} & DBUS permission control register 1. & \hexprefix{}002C & R/W \\ \hline
\hyperref[regdesc:PMSPRODRAM02REG]{PMS\_PRO\_DRAM0\_2\_REG} & DBUS permission control register 2. & \hexprefix{}0030 & R/W \\ \hline
\hyperref[regdesc:PMSPRODPORT1REG]{PMS\_PRO\_DPORT\_1\_REG} & PeriBus1 permission control register 1. & \hexprefix{}0040 & R/W \\ \hline
\hyperref[regdesc:PMSPRODPORT2REG]{PMS\_PRO\_DPORT\_2\_REG} & PeriBus1 permission control register 2. & \hexprefix{}0044 & R/W \\ \hline
\hyperref[regdesc:PMSPRODPORT3REG]{PMS\_PRO\_DPORT\_3\_REG} & PeriBus1 permission control register 3. & \hexprefix{}0048 & R/W \\ \hline
\hyperref[regdesc:PMSPRODPORT4REG]{PMS\_PRO\_DPORT\_4\_REG} & PeriBus1 permission control register 4. & \hexprefix{}004C & R/W \\ \hline
\hyperref[regdesc:PMSPRODPORT5REG]{PMS\_PRO\_DPORT\_5\_REG} & PeriBus1 permission control register 5. & \hexprefix{}0050 & R/W \\ \hline
\hyperref[regdesc:PMSPROAHB1REG]{PMS\_PRO\_AHB\_1\_REG} & PeriBus2 permission control register 1. & \hexprefix{}0060 & R/W \\ \hline
\hyperref[regdesc:PMSPROAHB2REG]{PMS\_PRO\_AHB\_2\_REG} & PeriBus2 permission control register 2. & \hexprefix{}0064 & R/W \\ \hline
\hyperref[regdesc:PMSPROTRACE1REG]{PMS\_PRO\_TRACE\_1\_REG} & Trace memory permission control register 1. & \hexprefix{}0074 & R/W \\ \hline
\hyperref[regdesc:PMSPROCACHE1REG]{PMS\_PRO\_CACHE\_1\_REG} & Cache permission control register 1. & \hexprefix{}007C & R/W \\ \hline
\hyperref[regdesc:PMSDMAAPBI1REG]{PMS\_DMA\_APB\_I\_1\_REG} & Internal DMA permission control register 1. & \hexprefix{}0090 & R/W \\ \hline
\hyperref[regdesc:PMSDMARXI1REG]{PMS\_DMA\_RX\_I\_1\_REG} & RX Copy DMA permission control register 1. & \hexprefix{}00A0 & R/W \\ \hline
\hyperref[regdesc:PMSDMATXI1REG]{PMS\_DMA\_TX\_I\_1\_REG} & TX Copy DMA permission control register 1. & \hexprefix{}00B0 & R/W \\ \hline
\hyperref[regdesc:PMSAPBPERIPHERAL1REG]{PMS\_APB\_PERIPHERAL\_1\_REG} & Peripheral access permission control register 1. & \hexprefix{}00D0 & R/W \\ \hline
\hyperref[regdesc:PMSOCCUPY1REG]{PMS\_OCCUPY\_1\_REG} & Occupy permission control register 1. & \hexprefix{}00D8 & R/W \\ \hline

\hyperref[regdesc:PMSOCCUPY3REG]{PMS\_OCCUPY\_3\_REG} & Occupy permission control register 3. & \hexprefix{}00E0 & R/W \\ \hline
\hyperref[regdesc:PMSCACHETAGACCESS1REG]{PMS\_CACHE\_TAG\_ACCESS\_1\_REG} & Cache tag permission control register 1. & \hexprefix{}00E8 & R/W \\ \hline
\hyperref[regdesc:PMSCACHEMMUACCESS1REG]{PMS\_CACHE\_MMU\_ACCESS\_1\_REG} & Cache MMU permission control register 1. & \hexprefix{}00F0 & R/W \\ \hline
\multicolumn{4}{|l|}{\textbf{Interrupt Registers}} \\ \hline
\hyperref[regdesc:PMSPROIRAM04REG]{PMS\_PRO\_IRAM0\_4\_REG} & IBUS permission control register 4. & \hexprefix{}0020 & varies \\ \hline
\hyperref[regdesc:PMSPROIRAM05REG]{PMS\_PRO\_IRAM0\_5\_REG} & IBUS status register. & \hexprefix{}0024 & RO \\ \hline
\hyperref[regdesc:PMSPRODRAM03REG]{PMS\_PRO\_DRAM0\_3\_REG} & DBUS permission control register 3. & \hexprefix{}0034 & varies \\ \hline
\hyperref[regdesc:PMSPRODRAM04REG]{PMS\_PRO\_DRAM0\_4\_REG} & DBUS status register. & \hexprefix{}0038 & RO \\ \hline
\hyperref[regdesc:PMSPRODPORT6REG]{PMS\_PRO\_DPORT\_6\_REG} & PeriBus1 permission control register 6. & \hexprefix{}0054 & varies \\ \hline
\hyperref[regdesc:PMSPRODPORT7REG]{PMS\_PRO\_DPORT\_7\_REG} & PeriBus1 status register. & \hexprefix{}0058 & RO \\ \hline
\hyperref[regdesc:PMSPROAHB3REG]{PMS\_PRO\_AHB\_3\_REG} & PeriBus2 permission control register 3. & \hexprefix{}0068 & varies \\ \hline
\hyperref[regdesc:PMSPROAHB4REG]{PMS\_PRO\_AHB\_4\_REG} & PeriBus2 status register. & \hexprefix{}006C & RO \\ \hline
\hyperref[regdesc:PMSPROCACHE2REG]{PMS\_PRO\_CACHE\_2\_REG} & Cache permission control register 2. & \hexprefix{}0080 & varies \\ \hline
\hyperref[regdesc:PMSPROCACHE3REG]{PMS\_PRO\_CACHE\_3\_REG} & Icache status register. & \hexprefix{}0084 & RO \\ \hline
\hyperref[regdesc:PMSPROCACHE4REG]{PMS\_PRO\_CACHE\_4\_REG} & Dcache status register. & \hexprefix{}0088 & RO \\ \hline
\hyperref[regdesc:PMSDMAAPBI2REG]{PMS\_DMA\_APB\_I\_2\_REG} & Internal DMA permission control register 2. & \hexprefix{}0094 & varies \\ \hline
\hyperref[regdesc:PMSDMAAPBI3REG]{PMS\_DMA\_APB\_I\_3\_REG} & Internal DMA status register. & \hexprefix{}0098 & RO \\ \hline
\hyperref[regdesc:PMSDMARXI2REG]{PMS\_DMA\_RX\_I\_2\_REG} & RX Copy DMA permission control register 2. & \hexprefix{}00A4 & varies \\ \hline
\hyperref[regdesc:PMSDMARXI3REG]{PMS\_DMA\_RX\_I\_3\_REG} & RX Copy DMA status register. & \hexprefix{}00A8 & RO \\ \hline
\hyperref[regdesc:PMSDMATXI2REG]{PMS\_DMA\_TX\_I\_2\_REG} & TX Copy DMA permission control register 2. & \hexprefix{}00B4 & varies \\ \hline
\hyperref[regdesc:PMSDMATXI3REG]{PMS\_DMA\_TX\_I\_3\_REG} & TX Copy DMA status register. & \hexprefix{}00B8 & RO \\ \hline
\hyperref[regdesc:PMSAPBPERIPHERALINTRREG]{PMS\_APB\_PERIPHERAL\_INTR\_REG} & PeriBus2 permission control register. & \hexprefix{}00F4 & varies \\ \hline
\hyperref[regdesc:PMSAPBPERIPHERALSTATUSREG]{PMS\_APB\_PERIPHERAL\_STATUS\_REG} & PeriBus2 peripheral access status register. & \hexprefix{}00F8 & RO \\ \hline
\hyperref[regdesc:PMSCPUPERIPHERALINTRREG]{PMS\_CPU\_PERIPHERAL\_INTR\_REG} & PeriBus1 permission control register. & \hexprefix{}00FC & varies \\ \hline
\hyperref[regdesc:PMSCPUPERIPHERALSTATUSREG]{PMS\_CPU\_PERIPHERAL\_STATUS\_REG} & PeriBus1 peripheral access status register. & \hexprefix{}0100 & RO \\ \hline
\multicolumn{4}{|l|}{\textbf{Version Control Register}} \\ \hline
\hyperref[regdesc:PMSDATEREG]{PMS\_DATE} & Version control register. & \hexprefix{}0FFC & R/W \\ \hline
\end{longtable}
