\begin{register}{H}{RTC\_CNTL\_OPTIONS0\_REG}{0x0000}\label{regdesc:RTCCNTLOPTIONS0REG}
\regfield{RTC\_CNTL\_SW\_SYS\_RST}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_NORST}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_RST}{1}{29}{{0}}%
\regfield{(reserved)}{15}{14}{000000000000000}%
\regfield{RTC\_CNTL\_XTL\_FORCE\_PU}{1}{13}{{1}}%
\regfield{RTC\_CNTL\_XTL\_FORCE\_PD}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_BBPLL\_FORCE\_PU}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_BBPLL\_FORCE\_PD}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PU}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PD}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_BB\_I2C\_FORCE\_PU}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_BB\_I2C\_FORCE\_PD}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_SW\_PROCPU\_RST}{1}{5}{{0}}%
\regfield{(reserved)}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_SW\_STALL\_PROCPU\_C0}{2}{2}{{0}}%
\regfield{(reserved)}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWSTALLPROCPUC0}\item [RTC\_CNTL\_SW\_STALL\_PROCPU\_C0] When \hyperref[fielddesc:RTCCNTLSWSTALLPROCPUC1]{RTC\_CNTL\_SW\_STALL\_PROCPU\_C1} is configured to 0x21, setting this bit to 0x2 stalls the CPU by SW. (R/W)
\label{fielddesc:RTCCNTLSWPROCPURST}\item [RTC\_CNTL\_SW\_PROCPU\_RST] Set this bit to reset the CPU by SW. (WO)
\label{fielddesc:RTCCNTLBBI2CFORCEPD}\item [RTC\_CNTL\_BB\_I2C\_FORCE\_PD] Set this bit to FPD BB\_I2C. (R/W)
\label{fielddesc:RTCCNTLBBI2CFORCEPU}\item [RTC\_CNTL\_BB\_I2C\_FORCE\_PU] Set this bit to FPU BB\_I2C. (R/W)
\label{fielddesc:RTCCNTLBBPLLI2CFORCEPD}\item [RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PD] Set this bit to FPD BB\_PLL\_I2C. (R/W)
\label{fielddesc:RTCCNTLBBPLLI2CFORCEPU}\item [RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PU] Set this bit to FPU BB\_PLL\_I2C. (R/W)
\label{fielddesc:RTCCNTLBBPLLFORCEPD}\item [RTC\_CNTL\_BBPLL\_FORCE\_PD] Set this bit to FPD BB\_PLL. (R/W)
\label{fielddesc:RTCCNTLBBPLLFORCEPU}\item [RTC\_CNTL\_BBPLL\_FORCE\_PU] Set this bit to FPU BB\_PLL. (R/W)
\label{fielddesc:RTCCNTLXTLFORCEPD}\item [RTC\_CNTL\_XTL\_FORCE\_PD] Set this bit to FPD the crystal oscillator. (R/W)
\label{fielddesc:RTCCNTLXTLFORCEPU}\item [RTC\_CNTL\_XTL\_FORCE\_PU] Set this bit to FPU the crystal oscillator. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCERST}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_RST] Set this bit to force reset the digital system in deep-sleep. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCENORST}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_NORST] Set this bit to disable force reset to digital system in deep-sleep. (R/W)
\label{fielddesc:RTCCNTLSWSYSRST}\item [RTC\_CNTL\_SW\_SYS\_RST] Set this bit to reset the system via SW. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLP\_TIMER0\_REG}{0x0004}\label{regdesc:RTCCNTLSLPTIMER0REG}
\regfield{RTC\_CNTL\_SLP\_VAL\_LO}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPVALLO}\item [RTC\_CNTL\_SLP\_VAL\_LO] Sets the lower 32 bits of the trigger threshold for the RTC timer. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLP\_TIMER1\_REG}{0x0008}\label{regdesc:RTCCNTLSLPTIMER1REG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_ALARM\_EN}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_SLP\_VAL\_HI}{16}{0}{{0x00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPVALHI}\item [RTC\_CNTL\_SLP\_VAL\_HI] Sets the higher 16 bits of the trigger threshold for the RTC timer. (R/W)
\label{fielddesc:RTCCNTLMAINTIMERALARMEN}\item [RTC\_CNTL\_MAIN\_TIMER\_ALARM\_EN] Sets this bit to enable the timer alarm. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIME\_UPDATE\_REG}{0x000C}\label{regdesc:RTCCNTLTIMEUPDATEREG}
\regfield{RTC\_CNTL\_TIME\_UPDATE}{1}{31}{{0}}%
\regfield{(reserved)}{1}{30}{0}%
\regfield{RTC\_CNTL\_TIMER\_SYS\_RST}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_TIMER\_XTL\_OFF}{1}{28}{{0}}%
\regfield{RTC\_CNTL\_TIMER\_SYS\_STALL}{1}{27}{{0}}%
\regfield{(reserved)}{27}{0}{000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTIMERSYSSTALL}\item [RTC\_CNTL\_TIMER\_SYS\_STALL] Selects the triggering condition for the RTC timer. (R/W)
\label{fielddesc:RTCCNTLTIMERXTLOFF}\item [RTC\_CNTL\_TIMER\_XTL\_OFF] Selects the triggering condition for the RTC timer. (R/W)
\label{fielddesc:RTCCNTLTIMERSYSRST}\item [RTC\_CNTL\_TIMER\_SYS\_RST] Selects the triggering condition for the RTC timer. (R/W)
\label{fielddesc:RTCCNTLTIMEUPDATE}\item [RTC\_CNTL\_TIME\_UPDATE] Selects the triggering condition for the RTC timer. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIME\_LOW0\_REG}{0x0010}\label{regdesc:RTCCNTLTIMELOW0REG}
\regfield{RTC\_CNTL\_TIMER\_VALUE0\_LOW}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTIMERVALUE0LOW}\item [RTC\_CNTL\_TIMER\_VALUE0\_LOW] Stores the lower 32 bits of RTC timer 0. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIME\_HIGH0\_REG}{0x0014}\label{regdesc:RTCCNTLTIMEHIGH0REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{RTC\_CNTL\_TIMER\_VALUE0\_HIGH}{16}{0}{{0x00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTIMERVALUE0HIGH}\item [RTC\_CNTL\_TIMER\_VALUE0\_HIGH] Stores the higher 16 bits of RTC timer 0. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STATE0\_REG}{0x0018}\label{regdesc:RTCCNTLSTATE0REG}
\regfield{RTC\_CNTL\_SLEEP\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_SLP\_REJECT}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP}{1}{29}{{0}}%
\regfield{(reserved)}{5}{23}{00000}%
\regfield{RTC\_CNTL\_APB2RTC\_BRIDGE\_SEL}{1}{22}{{0}}%
\regfield{(reserved)}{20}{2}{00000000000000000000}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_CAUSE\_CLR}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SW\_CPU\_INT}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWCPUINT}\item [RTC\_CNTL\_SW\_CPU\_INT] Sends a SW RTC interrupt to CPU. (WO)
\label{fielddesc:RTCCNTLSLPREJECTCAUSECLR}\item [RTC\_CNTL\_SLP\_REJECT\_CAUSE\_CLR] Clears the RTC reject-to-sleep cause. (WO)
\label{fielddesc:RTCCNTLAPB2RTCBRIDGESEL}\item [RTC\_CNTL\_APB2RTC\_BRIDGE\_SEL] 1: APB to RTC using bridge (R/W)
\label{fielddesc:RTCCNTLSLPWAKEUP}\item [RTC\_CNTL\_SLP\_WAKEUP] Sleep wakeup bit. (R/W)
\label{fielddesc:RTCCNTLSLPREJECT}\item [RTC\_CNTL\_SLP\_REJECT] Sleep reject bit. (R/W)
\label{fielddesc:RTCCNTLSLEEPEN}\item [RTC\_CNTL\_SLEEP\_EN] Sends the chip to sleep. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIMER1\_REG}{0x001C}\label{regdesc:RTCCNTLTIMER1REG}
\regfield{RTC\_CNTL\_PLL\_BUF\_WAIT}{8}{24}{{40}}%
\regfield{RTC\_CNTL\_XTL\_BUF\_WAIT}{10}{14}{{80}}%
\regfield{RTC\_CNTL\_FOSC\_WAIT}{8}{6}{{0x10}}%
\regfield{RTC\_CNTL\_CPU\_STALL\_WAIT}{5}{1}{{1}}%
\regfield{RTC\_CNTL\_CPU\_STALL\_EN}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLCPUSTALLEN}\item [RTC\_CNTL\_CPU\_STALL\_EN] Enables the CPU stalling. (R/W)
\label{fielddesc:RTCCNTLCPUSTALLWAIT}\item [RTC\_CNTL\_CPU\_STALL\_WAIT] Sets the CPU stall waiting cycles (using the RTC fast clock). (R/W)
\label{fielddesc:RTCCNTLFOSCWAIT}\item [RTC\_CNTL\_FOSC\_WAIT] Sets the FOSC clock waiting cycles (using the RTC slow clock). (R/W)
\label{fielddesc:RTCCNTLXTLBUFWAIT}\item [RTC\_CNTL\_XTL\_BUF\_WAIT] Sets the XTAL waiting cycles (using the RTC slow clock). (R/W)
\label{fielddesc:RTCCNTLPLLBUFWAIT}\item [RTC\_CNTL\_PLL\_BUF\_WAIT] Sets the PLL waiting cycles (using the RTC slow clock). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIMER2\_REG}{0x0020}\label{regdesc:RTCCNTLTIMER2REG}
\regfield{RTC\_CNTL\_MIN\_TIME\_FOSC\_OFF}{8}{24}{{0x1}}%
\regfield{(reserved)}{24}{0}{000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLMINTIMEFOSCOFF}\item [RTC\_CNTL\_MIN\_TIME\_FOSC\_OFF] Sets the minimal cycles for FOSC clock (using the RTC slow clock) when powered down. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_TIMER5\_REG}{0x002C}\label{regdesc:RTCCNTLTIMER5REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{RTC\_CNTL\_MIN\_SLP\_VAL}{8}{8}{{0x80}}%
\regfield{(reserved)}{8}{0}{00000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLMINSLPVAL}\item [RTC\_CNTL\_MIN\_SLP\_VAL] Sets the minimal sleep cycles (using the RTC slow clock). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_ANA\_CONF\_REG}{0x0034}\label{regdesc:RTCCNTLANACONFREG}
\regfield{RTC\_CNTL\_PLL\_I2C\_PU}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_CKGEN\_I2C\_PU}{1}{30}{{0}}%
\regfield{(reserved)}{1}{29}{0}%
\regfield{RTC\_CNTL\_RFRX\_PBUS\_PU}{1}{28}{{0}}%
\regfield{RTC\_CNTL\_TXRF\_I2C\_PU}{1}{27}{{0}}%
\regfield{(reserved)}{1}{26}{{0}}%
\regfield{(reserved)}{1}{25}{0}%
\regfield{(reserved)}{1}{24}{{0}}%
\regfield{(reserved)}{1}{23}{{1}}%
\regfield{RTC\_CNTL\_SAR\_I2C\_PU}{1}{22}{{1}}%
\regfield{(reserved)}{1}{21}{0}%
\regfield{RTC\_CNTL\_GLITCH\_RST\_EN}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_RESET\_POR\_FORCE\_PU}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_RESET\_POR\_FORCE\_PD}{1}{18}{{1}}%
\regfield{(reserved)}{18}{0}{000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRESETPORFORCEPD}\item [RTC\_CNTL\_RESET\_POR\_FORCE\_PD] Set this bit to force not bypass I2C power-on reset. (R/W)
\label{fielddesc:RTCCNTLRESETPORFORCEPU}\item [RTC\_CNTL\_RESET\_POR\_FORCE\_PU] Set this bit to force bypass I2C power-on reset. (R/W)
\label{fielddesc:RTCCNTLGLITCHRSTEN}\item [RTC\_CNTL\_GLITCH\_RST\_EN] Set this bit to enable reset when the system detects a glitch. (R/W)
\label{fielddesc:RTCCNTLSARI2CPU}\item [RTC\_CNTL\_SAR\_I2C\_PU] Set this bit to FPU the SAR\_I2C. (R/W)
\label{fielddesc:RTCCNTLTXRFI2CPU}\item [RTC\_CNTL\_TXRF\_I2C\_PU] Set this bit to PU TXRF\_I2C. (R/W)
\label{fielddesc:RTCCNTLRFRXPBUSPU}\item [RTC\_CNTL\_RFRX\_PBUS\_PU] Set this bit to PU RFRX\_PBUS. (R/W)
\label{fielddesc:RTCCNTLCKGENI2CPU}\item [RTC\_CNTL\_CKGEN\_I2C\_PU] Set this bit to PU CKGEN\_I2C. (R/W)
\label{fielddesc:RTCCNTLPLLI2CPU}\item [RTC\_CNTL\_PLL\_I2C\_PU] Set this bit to PU PLL I2C. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RESET\_STATE\_REG}{0x0038}\label{regdesc:RTCCNTLRESETSTATEREG}
\regfield{(reserved)}{6}{26}{000000}%
\regfield{RTC\_CNTL\_DRESET\_MASK\_PROCPU}{1}{25}{{0}}%
\regfield{(reserved)}{1}{24}{{0}}%
\regfield{(reserved)}{1}{23}{{0}}%
\regfield{RTC\_CNTL\_JTAG\_RESET\_FLAG\_CLR\_PROCPU}{1}{22}{{0}}%
\regfield{(reserved)}{1}{21}{{0}}%
\regfield{RTC\_CNTL\_JTAG\_RESET\_FLAG\_PROCPU}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_OCD\_HALT\_ON\_RESET\_PROCPU}{1}{19}{{0}}%
\regfield{(reserved)}{1}{18}{{0}}%
\regfield{(reserved)}{1}{17}{{0}}%
\regfield{RTC\_CNTL\_ALL\_RESET\_FLAG\_CLR\_PROCPU}{1}{16}{{0}}%
\regfield{(reserved)}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_ALL\_RESET\_FLAG\_PROCPU}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_STAT\_VECTOR\_SEL\_PROCPU}{1}{13}{{1}}%
\regfield{(reserved)}{1}{12}{{1}}%
\regfield{(reserved)}{6}{6}{{0}}%
\regfield{RTC\_CNTL\_RESET\_CAUSE\_PROCPU}{6}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRESETCAUSEPROCPU}\item [RTC\_CNTL\_RESET\_CAUSE\_PROCPU] Stores the CPU reset cause. (RO)
\label{fielddesc:RTCCNTLSTATVECTORSELPROCPU}\item [RTC\_CNTL\_STAT\_VECTOR\_SEL\_PROCPU] Selects the CPU static vector. (R/W)
\label{fielddesc:RTCCNTLALLRESETFLAGPROCPU}\item [RTC\_CNTL\_ALL\_RESET\_FLAG\_PROCPU] Indicates the CPU reset flag. (RO)
\label{fielddesc:RTCCNTLALLRESETFLAGCLRPROCPU}\item [RTC\_CNTL\_ALL\_RESET\_FLAG\_CLR\_PROCPU] Clears the CPU reset flag. (WO)
\label{fielddesc:RTCCNTLOCDHALTONRESETPROCPU}\item [RTC\_CNTL\_OCD\_HALT\_ON\_RESET\_PROCPU] Set this bit to send CPU into halt state upon CPU reset. (R/W)
\label{fielddesc:RTCCNTLJTAGRESETFLAGPROCPU}\item [RTC\_CNTL\_JTAG\_RESET\_FLAG\_PROCPU] Indicates the JTAG reset flag. (RO)
\label{fielddesc:RTCCNTLJTAGRESETFLAGCLRPROCPU}\item [RTC\_CNTL\_JTAG\_RESET\_FLAG\_CLR\_PROCPU] Sets the JTAG reset flag. (WO)
\label{fielddesc:RTCCNTLDRESETMASKPROCPU}\item [RTC\_CNTL\_DRESET\_MASK\_PROCPU] Set this bit to bybass D-reset. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_WAKEUP\_STATE\_REG}{0x003C}\label{regdesc:RTCCNTLWAKEUPSTATEREG}
\regfield{RTC\_CNTL\_WAKEUP\_ENA}{17}{15}{{12}}%
\regfield{(reserved)}{15}{0}{000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWAKEUPENA}\item [RTC\_CNTL\_WAKEUP\_ENA] Selects the wakeup source. For details, please refer to Table \ref{tab:lpm-wakeup-source}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_ENA\_RTC\_REG}{0x0040}\label{regdesc:RTCCNTLINTENARTCREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_BBPLL\_CAL\_INT\_ENA}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_GLITCH\_DET\_INT\_ENA}{1}{19}{{0}}%
\regfield{(reserved)}{2}{17}{00}%
\regfield{RTC\_CNTL\_XTAL32K\_DEAD\_INT\_ENA}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_SWD\_INT\_ENA}{1}{15}{{0}}%
\regfield{(reserved)}{4}{11}{0000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_INT\_ENA}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_ENA}{1}{9}{{0}}%
\regfield{(reserved)}{5}{4}{00000}%
\regfield{RTC\_CNTL\_WDT\_INT\_ENA}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{0}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_ENA}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTENA}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA] Enables interrupts when chip wakes up from sleep. (R/W)
\label{fielddesc:RTCCNTLSLPREJECTINTENA}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_ENA] Enables interrupts when chip rejects to go to sleep. (R/W)
\label{fielddesc:RTCCNTLWDTINTENA}\item [RTC\_CNTL\_WDT\_INT\_ENA] Enables the RTC watchdog interrupt. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTINTENA}\item [RTC\_CNTL\_BROWN\_OUT\_INT\_ENA] Enables the brown-out interrupt. (R/W)
\label{fielddesc:RTCCNTLMAINTIMERINTENA}\item [RTC\_CNTL\_MAIN\_TIMER\_INT\_ENA] Enables the RTC timer interrupt. (R/W)
\label{fielddesc:RTCCNTLSWDINTENA}\item [RTC\_CNTL\_SWD\_INT\_ENA] Enables the super watchdog interrupt. (R/W)
\label{fielddesc:RTCCNTLXTAL32KDEADINTENA}\item [RTC\_CNTL\_XTAL32K\_DEAD\_INT\_ENA] Enables interrupts when the XTAL32K is dead. (R/W)
\label{fielddesc:RTCCNTLGLITCHDETINTENA}\item [RTC\_CNTL\_GLITCH\_DET\_INT\_ENA] Enables interrupts when a glitch is detected. (R/W)
\label{fielddesc:RTCCNTLBBPLLCALINTENA}\item [RTC\_CNTL\_BBPLL\_CAL\_INT\_ENA] Enables interrupts upon the ending of a bb\_pll call. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_INT\_RAW\_RTC\_REG}{0x0044}\label{regdesc:RTCCNTLINTRAWRTCREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_BBPLL\_CAL\_INT\_RAW}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_GLITCH\_DET\_INT\_RAW}{1}{19}{{0}}%
\regfield{(reserved)}{2}{17}{00}%
\regfield{RTC\_CNTL\_XTAL32K\_DEAD\_INT\_RAW}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_SWD\_INT\_RAW}{1}{15}{{0}}%
\regfield{(reserved)}{4}{11}{0000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_INT\_RAW}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_RAW}{1}{9}{{0}}%
\regfield{(reserved)}{5}{4}{00000}%
\regfield{RTC\_CNTL\_WDT\_INT\_RAW}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{0}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_RAW}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTRAW}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_RAW] Stores the raw interrupt triggered when the chip wakes up from sleep. (RO)
\label{fielddesc:RTCCNTLSLPREJECTINTRAW}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_RAW] Stores the raw interrupt triggered when the chip rejects to go to sleep. (RO)
\label{fielddesc:RTCCNTLWDTINTRAW}\item [RTC\_CNTL\_WDT\_INT\_RAW] Stores the raw watchdog interrupt. (RO)
\label{fielddesc:RTCCNTLBROWNOUTINTRAW}\item [RTC\_CNTL\_BROWN\_OUT\_INT\_RAW]  Stores the raw brownout interrupt. (RO)
\label{fielddesc:RTCCNTLMAINTIMERINTRAW}\item [RTC\_CNTL\_MAIN\_TIMER\_INT\_RAW] Stores the raw RTC main timer interrupt. (RO)
\label{fielddesc:RTCCNTLSWDINTRAW}\item [RTC\_CNTL\_SWD\_INT\_RAW] Stores the raw super watchdog interrupt. (RO)
\label{fielddesc:RTCCNTLXTAL32KDEADINTRAW}\item [RTC\_CNTL\_XTAL32K\_DEAD\_INT\_RAW] Stores the raw interrupt triggered when the XTAL32K is dead. (RO)
\label{fielddesc:RTCCNTLGLITCHDETINTRAW}\item [RTC\_CNTL\_GLITCH\_DET\_INT\_RAW] Stores the raw interrupt triggered when a glitch is detected. (RO)
\label{fielddesc:RTCCNTLBBPLLCALINTRAW}\item [RTC\_CNTL\_BBPLL\_CAL\_INT\_RAW] Stores the raw interrupt upon the ending of a bb\_pll call. (RO)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_INT\_ST\_RTC\_REG}{0x0048}\label{regdesc:RTCCNTLINTSTRTCREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_BBPLL\_CAL\_INT\_ST}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_GLITCH\_DET\_INT\_ST}{1}{19}{{0}}%
\regfield{(reserved)}{2}{17}{00}%
\regfield{RTC\_CNTL\_XTAL32K\_DEAD\_INT\_ST}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_SWD\_INT\_ST}{1}{15}{{0}}%
\regfield{(reserved)}{4}{11}{0000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_INT\_ST}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_ST}{1}{9}{{0}}%
\regfield{(reserved)}{5}{4}{00000}%
\regfield{RTC\_CNTL\_WDT\_INT\_ST}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{0}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_ST}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTST}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_ST] Stores the status of the interrupt triggered when the chip wakes up from sleep. (RO)
\label{fielddesc:RTCCNTLSLPREJECTINTST}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_ST] Stores the status of the interrupt triggered when the chip rejects to go to sleep. (RO)
\label{fielddesc:RTCCNTLWDTINTST}\item [RTC\_CNTL\_WDT\_INT\_ST] Stores the status of the RTC watchdog interrupt. (RO)
\label{fielddesc:RTCCNTLBROWNOUTINTST}\item [RTC\_CNTL\_BROWN\_OUT\_INT\_ST] Stores the status of the brownout interrupt. (RO)
\label{fielddesc:RTCCNTLMAINTIMERINTST}\item [RTC\_CNTL\_MAIN\_TIMER\_INT\_ST] Stores the status of the RTC main timer interrupt. (RO)
\label{fielddesc:RTCCNTLSWDINTST}\item [RTC\_CNTL\_SWD\_INT\_ST] Stores the status of the super watchdog interrupt. (RO)
\label{fielddesc:RTCCNTLXTAL32KDEADINTST}\item [RTC\_CNTL\_XTAL32K\_DEAD\_INT\_ST] Stores the status of the interrupt triggered when the XTAL32K is dead. (RO)
\label{fielddesc:RTCCNTLGLITCHDETINTST}\item [RTC\_CNTL\_GLITCH\_DET\_INT\_ST] Stores the status of the interrupt triggered when a glitch is detected. (RO)
\label{fielddesc:RTCCNTLBBPLLCALINTST}\item [RTC\_CNTL\_BBPLL\_CAL\_INT\_ST] Stores the status of the interrupt triggered upon the ending of a bbpll call. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_CLR\_RTC\_REG}{0x004C}\label{regdesc:RTCCNTLINTCLRRTCREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_BBPLL\_CAL\_INT\_CLR}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_GLITCH\_DET\_INT\_CLR}{1}{19}{{0}}%
\regfield{(reserved)}{2}{17}{00}%
\regfield{RTC\_CNTL\_XTAL32K\_DEAD\_INT\_CLR}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_SWD\_INT\_CLR}{1}{15}{{0}}%
\regfield{(reserved)}{4}{11}{0000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_INT\_CLR}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_CLR}{1}{9}{{0}}%
\regfield{(reserved)}{5}{4}{00000}%
\regfield{RTC\_CNTL\_WDT\_INT\_CLR}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{0}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_CLR}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTCLR}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_CLR] Clears the interrupt triggered when the chip wakes up from sleep. (WO)
\label{fielddesc:RTCCNTLSLPREJECTINTCLR}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_CLR] Clears the interrupt triggered when the chip rejects to go to sleep. (WO)
\label{fielddesc:RTCCNTLWDTINTCLR}\item [RTC\_CNTL\_WDT\_INT\_CLR] Clears the RTC watchdog interrupt. (WO)
\label{fielddesc:RTCCNTLBROWNOUTINTCLR}\item [RTC\_CNTL\_BROWN\_OUT\_INT\_CLR] Clears the brownout interrupt. (WO)
\label{fielddesc:RTCCNTLMAINTIMERINTCLR}\item [RTC\_CNTL\_MAIN\_TIMER\_INT\_CLR] Clears the RTC main timer interrupt. (WO)
\label{fielddesc:RTCCNTLSWDINTCLR}\item [RTC\_CNTL\_SWD\_INT\_CLR] Clears the super watchdog interrupt. (WO)
\label{fielddesc:RTCCNTLXTAL32KDEADINTCLR}\item [RTC\_CNTL\_XTAL32K\_DEAD\_INT\_CLR] Clears the RTC watchdog interrupt. (WO)
\label{fielddesc:RTCCNTLGLITCHDETINTCLR}\item [RTC\_CNTL\_GLITCH\_DET\_INT\_CLR] Clears the interrupt triggered when a glitch is detected. (WO)
\label{fielddesc:RTCCNTLBBPLLCALINTCLR}\item [RTC\_CNTL\_BBPLL\_CAL\_INT\_CLR] Clears the interrupt triggered upon the ending of a bbpll call. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE0\_REG}{0x0050}\label{regdesc:RTCCNTLSTORE0REG}
\regfield{RTC\_CNTL\_SCRATCH0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSCRATCH0}\item [RTC\_CNTL\_SCRATCH0] Reservation register 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE1\_REG}{0x0054}\label{regdesc:RTCCNTLSTORE1REG}
\regfield{RTC\_CNTL\_SCRATCH1}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSCRATCH1}\item [RTC\_CNTL\_SCRATCH1] Reservation register 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE2\_REG}{0x0058}\label{regdesc:RTCCNTLSTORE2REG}
\regfield{RTC\_CNTL\_SCRATCH2}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSCRATCH2}\item [RTC\_CNTL\_SCRATCH2] Reservation register 2. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE3\_REG}{0x005C}\label{regdesc:RTCCNTLSTORE3REG}
\regfield{RTC\_CNTL\_SCRATCH3}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSCRATCH3}\item [RTC\_CNTL\_SCRATCH3] Reservation register 3. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_EXT\_XTL\_CONF\_REG}{0x0060}\label{regdesc:RTCCNTLEXTXTLCONFREG}
\regfield{(reserved)}{1}{31}{{0}}%
\regfield{(reserved)}{1}{30}{{0}}%
\regfield{(reserved)}{6}{24}{000000}%
\regfield{RTC\_CNTL\_XTAL32K\_GPIO\_SEL}{1}{23}{{0}}%
\regfield{RTC\_CNTL\_WDT\_STATE}{3}{20}{{0x0}}%
\regfield{RTC\_CNTL\_DAC\_XTAL\_32K}{3}{17}{{3}}%
\regfield{RTC\_CNTL\_XPD\_XTAL\_32K}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_DRES\_XTAL\_32K}{3}{13}{{3}}%
\regfield{RTC\_CNTL\_DGM\_XTAL\_32K}{3}{10}{{3}}%
\regfield{RTC\_CNTL\_DBUF\_XTAL\_32K}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_ENCKINIT\_XTAL\_32K}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_XPD\_FORCE}{1}{7}{{1}}%
\regfield{RTC\_CNTL\_XTAL32K\_AUTO\_RETURN}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_AUTO\_RESTART}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_AUTO\_BACKUP}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_EXT\_CLK\_FO}{1}{3}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_WDT\_RESET}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_WDT\_CLK\_FO}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_XTAL32K\_WDT\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLXTAL32KWDTEN}\item [RTC\_CNTL\_XTAL32K\_WDT\_EN] Set this bit to enable the XTAL32K watchdog. (R/W)
\label{fielddesc:RTCCNTLXTAL32KWDTCLKFO}\item [RTC\_CNTL\_XTAL32K\_WDT\_CLK\_FO] Set this bit to FPU the XTAL32K watchdog clock. (R/W)
\label{fielddesc:RTCCNTLXTAL32KWDTRESET}\item [RTC\_CNTL\_XTAL32K\_WDT\_RESET] Set this bit to reset the XTAL32K watchdog by SW. (R/W)
\label{fielddesc:RTCCNTLXTAL32KEXTCLKFO}\item [RTC\_CNTL\_XTAL32K\_EXT\_CLK\_FO] Set this bit to FPU the external clock of XTAL32K. (R/W)
\label{fielddesc:RTCCNTLXTAL32KAUTOBACKUP}\item [RTC\_CNTL\_XTAL32K\_AUTO\_BACKUP] Set this bit to switch to the backup clock when the XTAL32K is dead. (R/W)
\label{fielddesc:RTCCNTLXTAL32KAUTORESTART}\item [RTC\_CNTL\_XTAL32K\_AUTO\_RESTART] Set this bit to restart the XTAL32K automatically when the XTAL32K is dead. (R/W)
\label{fielddesc:RTCCNTLXTAL32KAUTORETURN}\item [RTC\_CNTL\_XTAL32K\_AUTO\_RETURN] Set this bit to switch back to XTAL32K when the XTAL32K is restarted. (R/W)
\label{fielddesc:RTCCNTLXTAL32KXPDFORCE}\item [RTC\_CNTL\_XTAL32K\_XPD\_FORCE] Set this bit to allow the software to FPD the XTAL32K; Reset this bit to allow the FSM to FPD the XTAL32K. (R/W)
\label{fielddesc:RTCCNTLENCKINITXTAL32K}\item [RTC\_CNTL\_ENCKINIT\_XTAL\_32K] Set this bit to apply an internal clock to help the XTAL32K to start. (R/W)
\label{fielddesc:RTCCNTLDBUFXTAL32K}\item [RTC\_CNTL\_DBUF\_XTAL\_32K] 0: single-end buffer 1: differential buffer. (R/W)
\label{fielddesc:RTCCNTLDGMXTAL32K}\item [RTC\_CNTL\_DGM\_XTAL\_32K] Configures the xtal\_32k gm control. (R/W)
\label{fielddesc:RTCCNTLDRESXTAL32K}\item [RTC\_CNTL\_DRES\_XTAL\_32K] Configures DRES\_XTAL\_32K. (R/W)
\label{fielddesc:RTCCNTLXPDXTAL32K}\item [RTC\_CNTL\_XPD\_XTAL\_32K] Configures XPD\_XTAL\_32K. (R/W)
\label{fielddesc:RTCCNTLDACXTAL32K}\item [RTC\_CNTL\_DAC\_XTAL\_32K] Configures DAC\_XTAL\_32K. (R/W)
\label{fielddesc:RTCCNTLWDTSTATE}\item [RTC\_CNTL\_WDT\_STATE] Indicates the 32 kHz watchdog timer state. (RO)
\label{fielddesc:RTCCNTLXTAL32KGPIOSEL}\item [RTC\_CNTL\_XTAL32K\_GPIO\_SEL] Set this bit to select the XTAL32K. Clear this bit to select external XTAL32K. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_EXT\_WAKEUP\_CONF\_REG}{0x0064}\label{regdesc:RTCCNTLEXTWAKEUPCONFREG}
\regfield{RTC\_CNTL\_GPIO\_WAKEUP\_FILTER}{1}{31}{{0}}%
\regfield{(reserved)}{31}{0}{0000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLGPIOWAKEUPFILTER}\item [RTC\_CNTL\_GPIO\_WAKEUP\_FILTER] Set this bit to enable the GPIO wakeup event filter. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLP\_REJECT\_CONF\_REG}{0x0068}\label{regdesc:RTCCNTLSLPREJECTCONFREG}
\regfield{RTC\_CNTL\_DEEP\_SLP\_REJECT\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_LIGHT\_SLP\_REJECT\_EN}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_SLEEP\_REJECT\_ENA}{18}{12}{{0}}%
\regfield{(reserved)}{12}{0}{000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLEEPREJECTENA}\item [RTC\_CNTL\_SLEEP\_REJECT\_ENA] Set this bit to enable reject-to-sleep. (R/W)
\label{fielddesc:RTCCNTLLIGHTSLPREJECTEN}\item [RTC\_CNTL\_LIGHT\_SLP\_REJECT\_EN] Set this bit to enable reject-to-light-sleep. (R/W)
\label{fielddesc:RTCCNTLDEEPSLPREJECTEN}\item [RTC\_CNTL\_DEEP\_SLP\_REJECT\_EN] Set this bit to enable reject-to-deep-sleep. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_CLK\_CONF\_REG}{0x0070}\label{regdesc:RTCCNTLCLKCONFREG}
\regfield{RTC\_CNTL\_ANA\_CLK\_RTC\_SEL}{2}{30}{{0}}%
\regfield{RTC\_CNTL\_FAST\_CLK\_RTC\_SEL}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_XTAL\_GLOBAL\_FORCE\_NOGATING}{1}{28}{{1}}%
\regfield{RTC\_CNTL\_XTAL\_GLOBAL\_FORCE\_GATING}{1}{27}{{0}}%
\regfield{RTC\_CNTL\_FOSC\_FORCE\_PU}{1}{26}{{0}}%
\regfield{RTC\_CNTL\_FOSC\_FORCE\_PD}{1}{25}{{0}}%
\regfield{RTC\_CNTL\_FOSC\_DFREQ}{8}{17}{{172}}%
\regfield{RTC\_CNTL\_FOSC\_FORCE\_NOGATING}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_XTAL\_FORCE\_NOGATING}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_FOSC\_DIV\_SEL}{3}{12}{{3}}%
\regfield{(reserved)}{1}{11}{0}%
\regfield{RTC\_CNTL\_DIG\_FOSC\_EN}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_DIG\_FOSC\_D256\_EN}{1}{9}{{1}}%
\regfield{RTC\_CNTL\_DIG\_XTAL32K\_EN}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_ENB\_FOSC\_DIV}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_ENB\_FOSC}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_FOSC\_DIV}{2}{4}{{1}}%
\regfield{RTC\_CNTL\_FOSC\_DIV\_SEL\_VLD}{1}{3}{{1}}%
\regfield{RTC\_CNTL\_EFUSE\_CLK\_FORCE\_NOGATING}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_EFUSE\_CLK\_FORCE\_GATING}{1}{1}{{0}}%
\regfield{(reserved)}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLEFUSECLKFORCEGATING}\item [RTC\_CNTL\_EFUSE\_CLK\_FORCE\_GATING] Set this bit to FPU the eFuse clock gating. (R/W)
\label{fielddesc:RTCCNTLEFUSECLKFORCENOGATING}\item [RTC\_CNTL\_EFUSE\_CLK\_FORCE\_NOGATING] Set this bit to FPD the eFuse clock gating. (R/W)
\label{fielddesc:RTCCNTLFOSCDIVSELVLD}\item [RTC\_CNTL\_FOSC\_DIV\_SEL\_VLD] Synchronizes reg\_fosc\_div\_sel. Note that you have to invalidate the bus before modifying the frequency divider, then validate the new divider clock. (R/W)
\label{fielddesc:RTCCNTLFOSCDIV}\item [RTC\_CNTL\_FOSC\_DIV] Set the FOSC\_D256\_OUT divider. 00: divided by 128, 01: divided by 256, 10: divided by 512, 11: divided by 1024. (R/W)
\label{fielddesc:RTCCNTLENBFOSC}\item [RTC\_CNTL\_ENB\_FOSC] Set this bit to disable FOSC and FOSC\_D256\_OUT. (R/W)
\label{fielddesc:RTCCNTLENBFOSCDIV}\item [RTC\_CNTL\_ENB\_FOSC\_DIV] Selects the FOSC\_D256\_OUT. 1: FOSC, 0: FOSC divided by 256. (R/W)
\label{fielddesc:RTCCNTLDIGXTAL32KEN}\item [RTC\_CNTL\_DIG\_XTAL32K\_EN] Set this bit to enable CK\_XTAL\_32K clock for the digital system. (R/W)
\label{fielddesc:RTCCNTLDIGFOSED256EN}\item [RTC\_CNTL\_DIG\_FOSC\_D256\_EN] Set this bit to enable FOSC\_D256\_OUT clock for the digital system. (R/W)
\label{fielddesc:RTCCNTLDIGFOSCEN}\item [RTC\_CNTL\_DIG\_FOSC\_EN] Set this bit to enable FOSC for the digital system. (R/W)
\label{fielddesc:RTCCNTLFOSCDIVSEL}\item [RTC\_CNTL\_FOSC\_DIV\_SEL] Stores the FOSC divider, which is reg\_FOSC\_div\_sel + 1. (R/W)
\label{fielddesc:RTCCNTLXTALFORCENOGATING}\item [RTC\_CNTL\_XTAL\_FORCE\_NOGATING] Set this bit to force no gating to crystal during sleep. (R/W)
\label{fielddesc:RTCCNTLFOSCFORCENOGATING}\item [RTC\_CNTL\_FOSC\_FORCE\_NOGATING] Set this bit to disable force gating to crystal during sleep. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_CLK\_CONF\_REG}{0x0070}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]


\label{fielddesc:RTCCNTLFOSCDFREQ}\item [RTC\_CNTL\_FOSC\_DFREQ] Configures the FOSC frequency. (R/W)
\label{fielddesc:RTCCNTLFOSCFORCEPD}\item [RTC\_CNTL\_FOSC\_FORCE\_PD] Set this bit to FPD FOSC. (R/W)
\label{fielddesc:RTCCNTLFOSCFORCEPU}\item [RTC\_CNTL\_FOSC\_FORCE\_PU] Set this bit to FPU FOSC. (R/W)
\label{fielddesc:RTCCNTLXTALGLOBALFORCEGATING}\item [RTC\_CNTL\_XTAL\_GLOBAL\_FORCE\_GATING] Set this bit to force enable XTAL clock gating. (R/W)
\label{fielddesc:RTCCNTLXTALGLOBALFORCENOGATING}\item [RTC\_CNTL\_XTAL\_GLOBAL\_FORCE\_NOGATING] Set this bit to force bypass the XTAL clock  gating. (R/W)
\label{fielddesc:RTCCNTLFASTCLKRTCSEL}\item [RTC\_CNTL\_FAST\_CLK\_RTC\_SEL] Selects the RTC fast clock. 0: XTAL\_DIV\_CLK, 1: RC\_FAST\_CLK div n. (R/W)
\label{fielddesc:RTCCNTLANACLKRTCSEL}\item [RTC\_CNTL\_ANA\_CLK\_RTC\_SEL] Selects the RTC slow clock. 0: RC\_SLOW\_CLK, 1: XTAL32K\_CLK, 2: RC\_FAST\_DIV\_CLK. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_SLOW\_CLK\_CONF\_REG}{0x0074}\label{regdesc:RTCCNTLSLOWCLKCONFREG}
\regfield{(reserved)}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_ANA\_CLK\_DIV}{8}{23}{{0}}%
\regfield{RTC\_CNTL\_ANA\_CLK\_DIV\_VLD}{1}{22}{{1}}%
\regfield{(reserved)}{22}{0}{0000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLANACLKDIVVLD}\item [RTC\_CNTL\_ANA\_CLK\_DIV\_VLD] Synchronizes the reg\_fosc\_div\_sel. Note that you have to invalidate the bus before modifying the frequency divider, and then validate the new divider clock. (R/W)
\label{fielddesc:RTCCNTLANACLKDIV}\item [RTC\_CNTL\_ANA\_CLK\_DIV] Configures the divider for the RTC clock. (R/W)4
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_REG}{0x0080}\label{regdesc:RTCCNTLREG}
\regfield{RTC\_CNTL\_REGULATOR\_FORCE\_PU}{1}{31}{{1}}%
\regfield{RTC\_CNTL\_REGULATOR\_FORCE\_PD}{1}{30}{{0}}%
\regfield{(reserved)}{1}{29}{{1}}%
\regfield{(reserved)}{1}{28}{{0}}%
\regfield{(reserved)}{6}{22}{000000}%
\regfield{RTC\_CNTL\_SCK\_DCAP}{8}{14}{{0}}%
\regfield{(reserved)}{6}{8}{000000}%
\regfield{RTC\_CNTL\_DIG\_REG\_CAL\_EN}{1}{7}{{0}}%
\regfield{(reserved)}{7}{0}{0000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLDIGREGCALEN}\item [RTC\_CNTL\_DIG\_REG\_CAL\_EN] Set this bit to enable digital regulator calibration by software. (R/W)
\label{fielddesc:RTCCNTLSCKDCAP}\item [RTC\_CNTL\_SCK\_DCAP] Configures the RC\_SLOW\_CLK frequency. (R/W)
\label{fielddesc:RTCCNTLREGULATORFORCEPD}\item [RTC\_CNTL\_REGULATOR\_FORCE\_PD] Set this bit to FPD the low-power voltage regulator, which means decreasing its voltage to 0.8 V or lower. (R/W)
\label{fielddesc:RTCCNTLREGULATORFORCEPU}\item [RTC\_CNTL\_REGULATOR\_FORCE\_PU] Set this bit to FPU the low-power voltage regulator, which means increasing its voltage to higher than 0.8 V. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_PWC\_REG}{0x0084}\label{regdesc:RTCCNTLPWCREG}
\regfield{(reserved)}{10}{22}{0000000000}%
\regfield{RTC\_CNTL\_PAD\_FORCE\_HOLD}{1}{21}{{0}}%
\regfield{(reserved)}{21}{0}{000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLPADFORCEHOLD}\item [RTC\_CNTL\_PAD\_FORCE\_HOLD] Set this bit to force RTC pad into hold state. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_DIG\_PWC\_REG}{0x0088}\label{regdesc:RTCCNTLDIGPWCREG}
\regfield{RTC\_CNTL\_DG\_WRAP\_PD\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_WIFI\_PD\_EN}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_CPU\_TOP\_PD\_EN}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_DG\_PERI\_PD\_EN}{1}{28}{{0}}%
\regfield{(reserved)}{1}{27}{{0}}%
\regfield{(reserved)}{4}{23}{0000}%
\regfield{RTC\_CNTL\_CPU\_TOP\_FORCE\_PU}{1}{22}{{1}}%
\regfield{RTC\_CNTL\_CPU\_TOP\_FORCE\_PD}{1}{21}{{0}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_PU}{1}{20}{{1}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_PD}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_WIFI\_FORCE\_PU}{1}{18}{{1}}%
\regfield{RTC\_CNTL\_WIFI\_FORCE\_PD}{1}{17}{{0}}%
\regfield{RTC\_CNTL\_FASTMEM\_FORCE\_LPU}{1}{16}{{1}}%
\regfield{RTC\_CNTL\_FASTMEM\_FORCE\_LPD}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_DG\_PERI\_FORCE\_PU}{1}{14}{{1}}%
\regfield{RTC\_CNTL\_DG\_PERI\_FORCE\_PD}{1}{13}{{0}}%
\regfield{(reserved)}{1}{12}{{1}}%
\regfield{(reserved)}{1}{11}{{0}}%
\regfield{(reserved)}{6}{5}{000000}%
\regfield{RTC\_CNTL\_LSLP\_MEM\_FORCE\_PU}{1}{4}{{1}}%
\regfield{RTC\_CNTL\_LSLP\_MEM\_FORCE\_PD}{1}{3}{{0}}%
\regfield{RTC\_CNTL\_VDD\_SPI\_PWR\_FORCE}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_VDD\_SPI\_PWR\_DRV}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLVDDSPIPWRDRV}\item [RTC\_CNTL\_VDD\_SPI\_PWR\_DRV] Configures the vdd\_spi's drive intensity. (R/W)
\label{fielddesc:RTCCNTLVDDSPIPWRFORCE}\item [RTC\_CNTL\_VDD\_SPI\_PWR\_FORCE] Set this bit to allow software to configure vdd\_spi's drive intensity. (R/W)
\label{fielddesc:RTCCNTLLSLPMEMFORCEPD}\item [RTC\_CNTL\_LSLP\_MEM\_FORCE\_PD] Set this bit to force the memories in the digital system not to enter retention mode in sleep. (R/W)
\label{fielddesc:RTCCNTLLSLPMEMFORCEPU}\item [RTC\_CNTL\_LSLP\_MEM\_FORCE\_PU] Set this bit to force the memories in the digital system into retention mode in sleep. (R/W)
\label{fielddesc:RTCCNTLDGPERIFORCEPD}\item [RTC\_CNTL\_DG\_PERI\_FORCE\_PD] Set this bit to FPD the digital peripherals. (R/W)
\label{fielddesc:RTCCNTLDGPERIFORCEPU}\item [RTC\_CNTL\_DG\_PERI\_FORCE\_PU] Set this bit to FPU the digital peripherals. (R/W)
\label{fielddesc:RTCCNTLFASTMEMFORCELPD}\item [RTC\_CNTL\_FASTMEM\_FORCE\_LPD] Set this bit to force the fast memory not to enter retention mode in sleep. (R/W)
\label{fielddesc:RTCCNTLFASTMEMFORCELPU}\item [RTC\_CNTL\_FASTMEM\_FORCE\_LPU] Set this bit to force the fast memory into retention mode in sleep. (R/W)
\label{fielddesc:RTCCNTLWIFIFORCEPD}\item [RTC\_CNTL\_WIFI\_FORCE\_PD] Set this bit to FPD wireless. (R/W)
\label{fielddesc:RTCCNTLWIFIFORCEPU}\item [RTC\_CNTL\_WIFI\_FORCE\_PU] Set this bit to FPU wireless. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCEPD}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_PD] Set this bit to FPD the digital system. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCEPU}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_PU] Set this bit to FPU the digital system. (R/W)
\label{fielddesc:RTCCNTLCPUTOPFORCEPD}\item [RTC\_CNTL\_CPU\_TOP\_FORCE\_PD] Set this bit to FPD the CPU. (R/W)
\label{fielddesc:RTCCNTLCPUTOPFORCEPU}\item [RTC\_CNTL\_CPU\_TOP\_FORCE\_PU] Set this bit to FPU the CPU. (R/W)
\label{fielddesc:RTCCNTLDGPERIPDEN}\item [RTC\_CNTL\_DG\_PERI\_PD\_EN] Set this bit to enable FPD digital peripherals in sleep. (R/W)
\label{fielddesc:RTCCNTLCPUTOPPDEN}\item [RTC\_CNTL\_CPU\_TOP\_PD\_EN] Set this bit to enable FPD CPU in sleep. (R/W)
\label{fielddesc:RTCCNTLWIFIPDEN}\item [RTC\_CNTL\_WIFI\_PD\_EN] Set this bit to enable FPD wireless in sleep. (R/W)
\label{fielddesc:RTCCNTLDGWRAPPDEN}\item [RTC\_CNTL\_DG\_WRAP\_PD\_EN] Set this bit to enable FPD digital system in sleep. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_DIG\_ISO\_REG}{0x008C}\label{regdesc:RTCCNTLDIGISOREG}
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_NOISO}{1}{31}{{1}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_ISO}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_WIFI\_FORCE\_NOISO}{1}{29}{{1}}%
\regfield{RTC\_CNTL\_WIFI\_FORCE\_ISO}{1}{28}{{0}}%
\regfield{RTC\_CNTL\_CPU\_TOP\_FORCE\_NOISO}{1}{27}{{1}}%
\regfield{RTC\_CNTL\_CPU\_TOP\_FORCE\_ISO}{1}{26}{{0}}%
\regfield{RTC\_CNTL\_DG\_PERI\_FORCE\_NOISO}{1}{25}{{1}}%
\regfield{RTC\_CNTL\_DG\_PERI\_FORCE\_ISO}{1}{24}{{0}}%
\regfield{(reserved)}{1}{23}{{1}}%
\regfield{(reserved)}{1}{22}{{0}}%
\regfield{(reserved)}{6}{16}{000000}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_HOLD}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_UNHOLD}{1}{14}{{1}}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_ISO}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_NOISO}{1}{12}{{1}}%
\regfield{RTC\_CNTL\_DG\_PAD\_AUTOHOLD\_EN}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_CLR\_DG\_PAD\_AUTOHOLD}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_DG\_PAD\_AUTOHOLD}{1}{9}{{0}}%
\regfield{(reserved)}{9}{0}{000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLDGPADAUTOHOLD}\item [RTC\_CNTL\_DG\_PAD\_AUTOHOLD] Indicates the auto-hold status of the digital GPIOs. (RO)
\label{fielddesc:RTCCNTLCLRDGPADAUTOHOLD}\item [RTC\_CNTL\_CLR\_DG\_PAD\_AUTOHOLD] Set this bit to clear the auto-hold enabler for the digital GPIOs. (WO)
\label{fielddesc:RTCCNTLDGPADAUTOHOLDEN}\item [RTC\_CNTL\_DG\_PAD\_AUTOHOLD\_EN] Set this bit to allow the digital GPIOs to enter the auto-hold status. (R/W)
\label{fielddesc:RTCCNTLDGPADFORCENOISO}\item [RTC\_CNTL\_DG\_PAD\_FORCE\_NOISO] Set this bit to disable the force isolation of the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLDGPADFORCEISO}\item [RTC\_CNTL\_DG\_PAD\_FORCE\_ISO] Set this bit to force isolation of the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLDGPADFORCEUNHOLD}\item [RTC\_CNTL\_DG\_PAD\_FORCE\_UNHOLD] Set this bit the force unhold the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLDGPADFORCEHOLD}\item [RTC\_CNTL\_DG\_PAD\_FORCE\_HOLD] Set this bit the force hold the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLDGPERIFORCEISO}\item [RTC\_CNTL\_DG\_PERI\_FORCE\_ISO] Set this bit to force isolation of the digital peripherals. (R/W)
\label{fielddesc:RTCCNTLDGPERIFORCENOISO}\item [RTC\_CNTL\_DG\_PERI\_FORCE\_NOISO] Set this bit to disable the force isolation of the digital peripherals. (R/W)
\label{fielddesc:RTCCNTLCPUTOPFORCEISO}\item [RTC\_CNTL\_CPU\_TOP\_FORCE\_ISO] Set this bit to force hold the CPU. (R/W)
\label{fielddesc:RTCCNTLCPUTOPFORCENOISO}\item [RTC\_CNTL\_CPU\_TOP\_FORCE\_NOISO]  Set this bit to force unhold the CPU. (R/W)
\label{fielddesc:RTCCNTLWIFIFORCEISO}\item [RTC\_CNTL\_WIFI\_FORCE\_ISO] Set this bit to force isolation of the wireless circuits. (R/W)
\label{fielddesc:RTCCNTLWIFIFORCENOISO}\item [RTC\_CNTL\_WIFI\_FORCE\_NOISO] Set this bit to disable the force isolation of the wireless circuits. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCEISO}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_ISO] Set this bit to force isolation of the digital system. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCENOISO}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_NOISO] Set this bit to disable the force isolation of the digital system. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTCONFIG0\_REG}{0x0090}\label{regdesc:RTCCNTLWDTCONFIG0REG}
\regfield{RTC\_CNTL\_WDT\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_WDT\_STG0}{3}{28}{{0x0}}%
\regfield{RTC\_CNTL\_WDT\_STG1}{3}{25}{{0x0}}%
\regfield{RTC\_CNTL\_WDT\_STG2}{3}{22}{{0x0}}%
\regfield{RTC\_CNTL\_WDT\_STG3}{3}{19}{{0x0}}%
\regfield{RTC\_CNTL\_WDT\_CPU\_RESET\_LENGTH}{3}{16}{{0x1}}%
\regfield{RTC\_CNTL\_WDT\_SYS\_RESET\_LENGTH}{3}{13}{{0x1}}%
\regfield{RTC\_CNTL\_WDT\_FLASHBOOT\_MOD\_EN}{1}{12}{{1}}%
\regfield{RTC\_CNTL\_WDT\_PROCPU\_RESET\_EN}{1}{11}{{0}}%
\regfield{(reserved)}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_WDT\_PAUSE\_IN\_SLP}{1}{9}{{1}}%
\regfield{(reserved)}{9}{0}{000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTPAUSEINSLP}\item [RTC\_CNTL\_WDT\_PAUSE\_IN\_SLP] Set this bit to pause the watchdog in sleep. (R/W)
\label{fielddesc:RTCCNTLWDTPROCPURESETEN}\item [RTC\_CNTL\_WDT\_PROCPU\_RESET\_EN] enable WDT reset CPU (R/W)
\label{fielddesc:RTCCNTLWDTFLASHBOOTMODEN}\item [RTC\_CNTL\_WDT\_FLASHBOOT\_MOD\_EN] Set this bit to enable watchdog when the chip boots from flash. (R/W)
\label{fielddesc:RTCCNTLWDTSYSRESETLENGTH}\item [RTC\_CNTL\_WDT\_SYS\_RESET\_LENGTH] Sets the length of the system reset counter. (R/W)
\label{fielddesc:RTCCNTLWDTCPURESETLENGTH}\item [RTC\_CNTL\_WDT\_CPU\_RESET\_LENGTH] Sets the length of the CPU reset counter. (R/W)
\label{fielddesc:RTCCNTLWDTSTG3}\item [RTC\_CNTL\_WDT\_STG3] 1: enable at the interrupt stage, 2: enable at the CPU stage,  3: enable at the system stage, 4: enable at the system and RTC stage. (R/W)
\label{fielddesc:RTCCNTLWDTSTG2}\item [RTC\_CNTL\_WDT\_STG2] 1: enable at the interrupt stage, 2: enable at the CPU stage,  3: enable at the system stage, 4: enable at the system and RTC stage. (R/W)
\label{fielddesc:RTCCNTLWDTSTG1}\item [RTC\_CNTL\_WDT\_STG1] 1: enable at the interrupt stage, 2: enable at the CPU stage,  3: enable at the system stage, 4: enable at the system and RTC stage. (R/W)
\label{fielddesc:RTCCNTLWDTSTG0}\item [RTC\_CNTL\_WDT\_STG0] 1: enable at the interrupt stage, 2: enable at the CPU stage,  3: enable at the system stage, 4: enable at the system and RTC stage. (R/W)
\label{fielddesc:RTCCNTLWDTEN}\item [RTC\_CNTL\_WDT\_EN] Set this bit to enable the RTC watchdog. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTCONFIG1\_REG}{0x0094}\label{regdesc:RTCCNTLWDTCONFIG1REG}
\regfield{RTC\_CNTL\_WDT\_STG0\_HOLD}{32}{0}{{200000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTSTG0HOLD}\item [RTC\_CNTL\_WDT\_STG0\_HOLD] Configures the hold time of RTC watchdog at level 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTCONFIG2\_REG}{0x0098}\label{regdesc:RTCCNTLWDTCONFIG2REG}
\regfield{RTC\_CNTL\_WDT\_STG1\_HOLD}{32}{0}{{80000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTSTG1HOLD}\item [RTC\_CNTL\_WDT\_STG1\_HOLD] Configures the hold time of RTC watchdog at level 2. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTCONFIG3\_REG}{0x009C}\label{regdesc:RTCCNTLWDTCONFIG3REG}
\regfield{RTC\_CNTL\_WDT\_STG2\_HOLD}{32}{0}{{0x000fff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTSTG2HOLD}\item [RTC\_CNTL\_WDT\_STG2\_HOLD] Configures the hold time of RTC watchdog at level 3. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTCONFIG4\_REG}{0x00A0}\label{regdesc:RTCCNTLWDTCONFIG4REG}
\regfield{RTC\_CNTL\_WDT\_STG3\_HOLD}{32}{0}{{0x000fff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTSTG3HOLD}\item [RTC\_CNTL\_WDT\_STG3\_HOLD] Configures the hold time of RTC watchdog at level 4. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTFEED\_REG}{0x00A4}\label{regdesc:RTCCNTLWDTFEEDREG}
\regfield{RTC\_CNTL\_WDT\_FEED}{1}{31}{{0}}%
\regfield{(reserved)}{31}{0}{0000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTFEED}\item [RTC\_CNTL\_WDT\_FEED] Set this bit to feed the RTC watchdog. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTWPROTECT\_REG}{0x00A8}\label{regdesc:RTCCNTLWDTWPROTECTREG}
\regfield{RTC\_CNTL\_WDT\_WKEY}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTWKEY}\item [RTC\_CNTL\_WDT\_WKEY] If the register contains a different value than 0x50d83aa1, write protection for the RTC watchdog (RWDT) is enabled. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SWD\_CONF\_REG}{0x00AC}\label{regdesc:RTCCNTLSWDCONFREG}
\regfield{RTC\_CNTL\_SWD\_AUTO\_FEED\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_SWD\_DISABLE}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_SWD\_FEED}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_SWD\_RST\_FLAG\_CLR}{1}{28}{{0}}%
\regfield{RTC\_CNTL\_SWD\_SIGNAL\_WIDTH}{10}{18}{{300}}%
\regfield{RTC\_CNTL\_SWD\_BYPASS\_RST}{1}{17}{{0}}%
\regfield{(reserved)}{15}{2}{000000000000000}%
\regfield{RTC\_CNTL\_SWD\_FEED\_INT}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SWD\_RESET\_FLAG}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWDRESETFLAG}\item [RTC\_CNTL\_SWD\_RESET\_FLAG] Indicates the super watchdog reset flag. (RO)
\label{fielddesc:RTCCNTLSWDFEEDINT}\item [RTC\_CNTL\_SWD\_FEED\_INT] Receiving this interrupt leads to feeding the super watchdog via SW. (RO)
\label{fielddesc:RTCCNTLSWDBYPASSRST}\item [RTC\_CNTL\_SWD\_BYPASS\_RST] Set this bit to bypass super watchdog reset. (R/W)
\label{fielddesc:RTCCNTLSWDSIGNALWIDTH}\item [RTC\_CNTL\_SWD\_SIGNAL\_WIDTH] Adjusts the signal width sent to the super watchdog. (R/W)
\label{fielddesc:RTCCNTLSWDRSTFLAGCLR}\item [RTC\_CNTL\_SWD\_RST\_FLAG\_CLR] Set to reset the super watchdog reset flag. (WO)
\label{fielddesc:RTCCNTLSWDFEED}\item [RTC\_CNTL\_SWD\_FEED] Set to feed the super watchdog via SW. (WO)
\label{fielddesc:RTCCNTLSWDDISABLE}\item [RTC\_CNTL\_SWD\_DISABLE] Set this bit to disable super watchdog. (R/W)
\label{fielddesc:RTCCNTLSWDAUTOFEEDEN}\item [RTC\_CNTL\_SWD\_AUTO\_FEED\_EN] Set this bit to enable automatic watchdog feeding upon interrupts. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SWD\_WPROTECT\_REG}{0x00B0}\label{regdesc:RTCCNTLSWDWPROTECTREG}
\regfield{RTC\_CNTL\_SWD\_WKEY}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWDWKEY}\item [RTC\_CNTL\_SWD\_WKEY] Sets the write protection key of the super watchdog. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SW\_CPU\_STALL\_REG}{0x00B4}\label{regdesc:RTCCNTLSWCPUSTALLREG}
\regfield{RTC\_CNTL\_SW\_STALL\_PROCPU\_C1}{6}{26}{{0}}%
\regfield{(reserved)}{6}{20}{{0}}%
\regfield{(reserved)}{20}{0}{00000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWSTALLPROCPUC1}\item [RTC\_CNTL\_SW\_STALL\_PROCPU\_C1] When \hyperref[fielddesc:RTCCNTLSWSTALLPROCPUC0]{RTC\_CNTL\_SW\_STALL\_PROCPU\_C0} is configured to 0x2, setting this bit to 0x21 stalls the CPU by SW. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_STORE4\_REG}{0x00B8}\label{regdesc:RTCCNTLSTORE4REG}
\regfield{RTC\_CNTL\_SCRATCH4}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSCRATCH4}\item [RTC\_CNTL\_SCRATCH4] Reservation register 4. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE5\_REG}{0x00BC}\label{regdesc:RTCCNTLSTORE5REG}
\regfield{RTC\_CNTL\_SCRATCH5}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSCRATCH5}\item [RTC\_CNTL\_SCRATCH5] Reservation register 5. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE6\_REG}{0x00C0}\label{regdesc:RTCCNTLSTORE6REG}
\regfield{RTC\_CNTL\_SCRATCH6}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSCRATCH6}\item [RTC\_CNTL\_SCRATCH6] Reservation register 6. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE7\_REG}{0x00C4}\label{regdesc:RTCCNTLSTORE7REG}
\regfield{RTC\_CNTL\_SCRATCH7}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSCRATCH7}\item [RTC\_CNTL\_SCRATCH7] Reservation register 7. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_LOW\_POWER\_ST\_REG}{0x00C8}\label{regdesc:RTCCNTLLOWPOWERSTREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{RTC\_CNTL\_MAIN\_STATE\_IN\_IDLE}{1}{27}{{0}}%
\regfield{(reserved)}{7}{20}{0000000}%
\regfield{RTC\_CNTL\_RDY\_FOR\_WAKEUP}{1}{19}{{0}}%
\regfield{(reserved)}{19}{0}{0000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRDYFORWAKEUP}\item [RTC\_CNTL\_RDY\_FOR\_WAKEUP] Indicates the RTC is ready to be triggered by any wakeup source. (RO)
\label{fielddesc:RTCCNTLMAINSTATEINIDLE}\item [RTC\_CNTL\_MAIN\_STATE\_IN\_IDLE] Indicates the RTC state.
\begin{itemize}
    \item 0: the chip can be either
\begin{itemize}
    \item in sleep modes.
    \item entering sleep modes. In this case, wait until \hyperref[fielddesc:RTCCNTLRDYFORWAKEUP]{RTC\_CNTL\_RDY\_FOR\_WAKEUP} bit is set, then you can wake up the chip.
    \item exiting sleep mode. In this case, \hyperref[fielddesc:RTCCNTLMAINSTATEINIDLE]{RTC\_CNTL\_MAIN\_STATE\_IN\_IDLE} will eventually become 1.
\end{itemize}
    \item 1: the chip is not in sleep modes (i.e. running normally).
\end{itemize}
(RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_PAD\_HOLD\_REG}{0x00D0}\label{regdesc:RTCCNTLPADHOLDREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{RTC\_CNTL\_GPIO\_PIN5\_HOLD}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN4\_HOLD}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN3\_HOLD}{1}{3}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN2\_HOLD}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN1\_HOLD}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN0\_HOLD}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLGPIOPIN0HOLD}\item [RTC\_CNTL\_GPIO\_PIN0\_HOLD] Sets the GPIO 0 to the holding state. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN1HOLD}\item [RTC\_CNTL\_GPIO\_PIN1\_HOLD] Sets the GPIO 1 to the holding state. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN2HOLD}\item [RTC\_CNTL\_GPIO\_PIN2\_HOLD] Sets the GPIO 2 to the holding state. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN3HOLD}\item [RTC\_CNTL\_GPIO\_PIN3\_HOLD] Sets the GPIO 3 to the holding state. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN4HOLD}\item [RTC\_CNTL\_GPIO\_PIN4\_HOLD] Sets the GPIO 4 to the holding state. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN5HOLD}\item [RTC\_CNTL\_GPIO\_PIN5\_HOLD] Sets the GPIO 5 to the holding state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_DIG\_PAD\_HOLD\_REG}{0x00D4}\label{regdesc:RTCCNTLDIGPADHOLDREG}
\regfield{RTC\_CNTL\_DIG\_PAD\_HOLD}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLDIGPADHOLD}\item [RTC\_CNTL\_DIG\_PAD\_HOLD] Set GPIO 6 to GPIO 21 to the holding state. (See bitmap to locate any GPIO). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_BROWN\_OUT\_REG}{0x00D8}\label{regdesc:RTCCNTLBROWNOUTREG}
\regfield{RTC\_CNTL\_BROWN\_OUT\_DET}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_ENA}{1}{30}{{1}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_CNT\_CLR}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_ANA\_RST\_EN}{1}{28}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_RST\_SEL}{1}{27}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_RST\_ENA}{1}{26}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_RST\_WAIT}{10}{16}{{0x3ff}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_PD\_RF\_ENA}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_CLOSE\_FLASH\_ENA}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_WAIT}{10}{4}{{0x1}}%
\regfield{(reserved)}{4}{0}{0000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLBROWNOUTINTWAIT}\item [RTC\_CNTL\_BROWN\_OUT\_INT\_WAIT] Configures the waiting cycles before sending an interrupt. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTCLOSEFLASHENA}\item [RTC\_CNTL\_BROWN\_OUT\_CLOSE\_FLASH\_ENA] Set this bit to enable PD the flash when a brown-out happens. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTPDRFENA}\item [RTC\_CNTL\_BROWN\_OUT\_PD\_RF\_ENA] Set this bit to enable PD the RF circuits when a brown-out happens. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTRSTWAIT}\item [RTC\_CNTL\_BROWN\_OUT\_RST\_WAIT] Configures the waiting cycles before the reset after a brown-out. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTRSTENA}\item [RTC\_CNTL\_BROWN\_OUT\_RST\_ENA] Enables to reset brown-out. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTRSTSEL}\item [RTC\_CNTL\_BROWN\_OUT\_RST\_SEL] Selects the reset type when a brown-out happens. 1: chip reset, 0: system reset. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTANARSTEN}\item [RTC\_CNTL\_BROWN\_OUT\_ANA\_RST\_EN] Enables to reset brown-out. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTCNTCLR}\item [RTC\_CNTL\_BROWN\_OUT\_CNT\_CLR] Clears the brown-out counter. (WO)
\label{fielddesc:RTCCNTLBROWNOUTENA}\item [RTC\_CNTL\_BROWN\_OUT\_ENA] Set this bit to enable brown-out detection. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTDET}\item [RTC\_CNTL\_BROWN\_OUT\_DET] Indicates the status of the brown-out signal. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIME\_LOW1\_REG}{0x00DC}\label{regdesc:RTCCNTLTIMELOW1REG}
\regfield{RTC\_CNTL\_TIMER\_VALUE1\_LOW}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTIMERVALUE1LOW}\item [RTC\_CNTL\_TIMER\_VALUE1\_LOW] Stores the lower 32 bits of RTC timer 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIME\_HIGH1\_REG}{0x00E0}\label{regdesc:RTCCNTLTIMEHIGH1REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{RTC\_CNTL\_TIMER\_VALUE1\_HIGH}{16}{0}{{0x00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTIMERVALUE1HIGH}\item [RTC\_CNTL\_TIMER\_VALUE1\_HIGH] Stores the higher 16 bits of RTC timer. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_XTAL32K\_CLK\_FACTOR\_REG}{0x00E4}\label{regdesc:RTCCNTLXTAL32KCLKFACTORREG}
\regfield{RTC\_CNTL\_XTAL32K\_CLK\_FACTOR}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLXTAL32KCLKFACTOR}\item [RTC\_CNTL\_XTAL32K\_CLK\_FACTOR] Configures the divider factor for the XTAL32K oscillator. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_XTAL32K\_CONF\_REG}{0x00E8}\label{regdesc:RTCCNTLXTAL32KCONFREG}
\regfield{RTC\_CNTL\_XTAL32K\_STABLE\_THRES}{4}{28}{{0x0}}%
\regfield{RTC\_CNTL\_XTAL32K\_WDT\_TIMEOUT}{8}{20}{{0xff}}%
\regfield{RTC\_CNTL\_XTAL32K\_RESTART\_WAIT}{16}{4}{{0x00}}%
\regfield{RTC\_CNTL\_XTAL32K\_RETURN\_WAIT}{4}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLXTAL32KRETURNWAIT}\item [RTC\_CNTL\_XTAL32K\_RETURN\_WAIT] Defines the waiting cycles before returning to the normal XTAL32K oscillator. (R/W)
\label{fielddesc:RTCCNTLXTAL32KRESTARTWAIT}\item [RTC\_CNTL\_XTAL32K\_RESTART\_WAIT] Defines the waiting cycles before restarting the XTAL32K oscillator. (R/W)
\label{fielddesc:RTCCNTLXTAL32KWDTTIMEOUT}\item [RTC\_CNTL\_XTAL32K\_WDT\_TIMEOUT] Defines the waiting period for clock detection. If no clock is detected after this period, the XTAL32K oscillator can be regarded as dead. (R/W)
\label{fielddesc:RTCCNTLXTAL32KSTABLETHRES}\item [RTC\_CNTL\_XTAL32K\_STABLE\_THRES] Defines the allowed restarting period, within which the XTAL32K oscillator can be regarded as stable.  (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_USB\_CONF\_REG}{0x00EC}\label{regdesc:RTCCNTLUSBCONFREG}
\regfield{(reserved)}{13}{19}{0000000000000}%
\regfield{RTC\_CNTL\_IO\_MUX\_RESET\_DISABLE}{1}{18}{{0}}%
\regfield{(reserved)}{18}{0}{000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLIOMUXRESETDISABLE}\item [RTC\_CNTL\_IO\_MUX\_RESET\_DISABLE] Set this bit to disable io\_mux reset. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLP\_REJECT\_CAUSE\_REG}{0x00F0}\label{regdesc:RTCCNTLSLPREJECTCAUSEREG}
\regfield{(reserved)}{14}{18}{00000000000000}%
\regfield{RTC\_CNTL\_REJECT\_CAUSE}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLREJECTCAUSE}\item [RTC\_CNTL\_REJECT\_CAUSE] Stores the reject-to-sleep cause. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_OPTION1\_REG}{0x00F4}\label{regdesc:RTCCNTLOPTION1REG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{RTC\_CNTL\_FORCE\_DOWNLOAD\_BOOT}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLFORCEDOWNLOADBOOT}\item [RTC\_CNTL\_FORCE\_DOWNLOAD\_BOOT] Set this bit to force the chip to boot from the download mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLP\_WAKEUP\_CAUSE\_REG}{0x00F8}\label{regdesc:RTCCNTLSLPWAKEUPCAUSEREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{RTC\_CNTL\_WAKEUP\_CAUSE}{17}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWAKEUPCAUSE}\item [RTC\_CNTL\_WAKEUP\_CAUSE] Stores the wakeup cause.  (RO)
\end{reglist}\end{regdesc}
\end{register}



\begin{register}{H}{RTC\_CNTL\_INT\_ENA\_RTC\_W1TS\_REG}{0x0100}\label{regdesc:RTCCNTLINTENARTCW1TSREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_BBPLL\_CAL\_INT\_ENA\_W1TS}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_GLITCH\_DET\_INT\_ENA\_W1TS}{1}{19}{{0}}%
\regfield{(reserved)}{2}{17}{00}%
\regfield{RTC\_CNTL\_XTAL32K\_DEAD\_INT\_ENA\_W1TS}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_SWD\_INT\_ENA\_W1TS}{1}{15}{{0}}%
\regfield{(reserved)}{4}{11}{0000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_INT\_ENA\_W1TS}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_ENA\_W1TS}{1}{9}{{0}}%
\regfield{(reserved)}{5}{4}{00000}%
\regfield{RTC\_CNTL\_WDT\_INT\_ENA\_W1TS}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{0}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_ENA\_W1TS}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA\_W1TS}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTENAW1TS}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA\_W1TS] Enables interrupts when the chip wakes up from sleep by writing 1 to set (W1TS). (WO)
\label{fielddesc:RTCCNTLSLPREJECTINTENAW1TS}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_ENA\_W1TS] Enables interrupts when the chip rejects to go to sleep by writing 1 to set (W1TS). (WO)
\label{fielddesc:RTCCNTLWDTINTENAW1TS}\item [RTC\_CNTL\_WDT\_INT\_ENA\_W1TS] Enables the RTC watchdog interrupt by writing 1 to set (W1TS). (WO)
\label{fielddesc:RTCCNTLBROWNOUTINTENAW1TS}\item [RTC\_CNTL\_BROWN\_OUT\_INT\_ENA\_W1TS] Enables the brownout interrupt by writing 1 to set. (WO)
\label{fielddesc:RTCCNTLMAINTIMERINTENAW1TS}\item [RTC\_CNTL\_MAIN\_TIMER\_INT\_ENA\_W1TS] Enables the RTC main timer interrupt by writing 1 to set (W1TS). (WO)
\label{fielddesc:RTCCNTLSWDINTENAW1TS}\item [RTC\_CNTL\_SWD\_INT\_ENA\_W1TS] Enables the super watchdog interrupt by writing 1 to set (W1TS). (WO)
\label{fielddesc:RTCCNTLXTAL32KDEADINTENAW1TS}\item [RTC\_CNTL\_XTAL32K\_DEAD\_INT\_ENA\_W1TS]Enables interrupts when the XTAL32K is dead by writing 1 to set (W1TS). (WO)
\label{fielddesc:RTCCNTLGLITCHDETINTENAW1TS}\item [RTC\_CNTL\_GLITCH\_DET\_INT\_ENA\_W1TS] Enables interrupts when a glitch is detected by writing 1 to set (W1TS). (WO)
\label{fielddesc:RTCCNTLBBPLLCALINTENAW1TS}\item [RTC\_CNTL\_BBPLL\_CAL\_INT\_ENA\_W1TS] Enables interrupts upon the ending of a bb\_pll call by writing 1 to set (W1TS). (WO)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_INT\_ENA\_RTC\_W1TC\_REG}{0x0104}\label{regdesc:RTCCNTLINTENARTCW1TCREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_BBPLL\_CAL\_INT\_ENA\_W1TC}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_GLITCH\_DET\_INT\_ENA\_W1TC}{1}{19}{{0}}%
\regfield{(reserved)}{2}{17}{00}%
\regfield{RTC\_CNTL\_XTAL32K\_DEAD\_INT\_ENA\_W1TC}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_SWD\_INT\_ENA\_W1TC}{1}{15}{{0}}%
\regfield{(reserved)}{4}{11}{0000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_INT\_ENA\_W1TC}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_ENA\_W1TC}{1}{9}{{0}}%
\regfield{(reserved)}{5}{4}{00000}%
\regfield{RTC\_CNTL\_WDT\_INT\_ENA\_W1TC}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{0}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_ENA\_W1TC}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA\_W1TC}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTENAW1TC}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA\_W1TC] Clear the interrupt enable bit when the chip wakes up from sleep by writing 1 to clear. (W1TC).  (WO)
\label{fielddesc:RTCCNTLSLPREJECTINTENAW1TC}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_ENA\_W1TC] Clear the interrupt enable bit when the chip rejects to go to sleep by writing 1 to clear (W1TC). (WO)
\label{fielddesc:RTCCNTLWDTINTENAW1TC}\item [RTC\_CNTL\_WDT\_INT\_ENA\_W1TC] Clear the RTC watchdog interrupt enable bit by writing 1 to clear (W1TC). (WO)
\label{fielddesc:RTCCNTLBROWNOUTINTENAW1TC}\item [RTC\_CNTL\_BROWN\_OUT\_INT\_ENA\_W1TC] Clear the brownout interrupt enable bit by writing 1 to clear (W1TC). (WO)
\label{fielddesc:RTCCNTLMAINTIMERINTENAW1TC}\item [RTC\_CNTL\_MAIN\_TIMER\_INT\_ENA\_W1TC] Clear the RTC timer interrupt enable bit by writing 1 to clear. (W1TC). (WO)
\label{fielddesc:RTCCNTLSWDINTENAW1TC}\item [RTC\_CNTL\_SWD\_INT\_ENA\_W1TC] Clear the super watchdog interrupt enable bit by writing 1 to clear (W1TC). (WO)
\label{fielddesc:RTCCNTLXTAL32KDEADINTENAW1TC}\item [RTC\_CNTL\_XTAL32K\_DEAD\_INT\_ENA\_W1TC] Clear the interrupt enable bit when the XTAL32K is dead by writing 1 to clear (W1TC). (WO)
\label{fielddesc:RTCCNTLGLITCHDETINTENAW1TC}\item [RTC\_CNTL\_GLITCH\_DET\_INT\_ENA\_W1TC] Clear the interrupt enable bit when a glitch is detected by writing 1 to clear (W1TC). (WO)
\label{fielddesc:RTCCNTLBBPLLCALINTENAW1TC}\item [RTC\_CNTL\_BBPLL\_CAL\_INT\_ENA\_W1TC] Clear the interrupt enable bit upon the ending of a bb\_pll call by writing 1 to clear (W1TC).(WO)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_RETENTION\_CTRL\_REG}{0x0108}\label{regdesc:RTCCNTLRETENTIONCTRLREG}
\regfield{(reserved)}{5}{27}{{20}}%
\regfield{RTC\_CNTL\_RETENTION\_EN}{1}{26}{{0}}%
\regfield{(reserved)}{4}{22}{{3}}%
\regfield{(reserved)}{3}{19}{{2}}%
\regfield{RTC\_CNTL\_RETENTION\_CLK\_SEL}{1}{18}{{0}}%
\regfield{(reserved)}{18}{0}{000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRETENTIONCLKSEL}\item [RTC\_CNTL\_RETENTION\_CLK\_SEL] Selects the retention clock. 0: RC\_FAST\_CLK; 1: XTAL\_CLK. (R/W)
\label{fielddesc:RTCCNTLRETENTIONEN}\item [RTC\_CNTL\_RETENTION\_EN] Set to enable the CPU retention in light sleep. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_GPIO\_WAKEUP\_REG}{0x0110}\label{regdesc:RTCCNTLGPIOWAKEUPREG}
\regfield{RTC\_CNTL\_GPIO\_PIN0\_WAKEUP\_ENABLE}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN1\_WAKEUP\_ENABLE}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN2\_WAKEUP\_ENABLE}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN3\_WAKEUP\_ENABLE}{1}{28}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN4\_WAKEUP\_ENABLE}{1}{27}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN5\_WAKEUP\_ENABLE}{1}{26}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN0\_INT\_TYPE}{3}{23}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN1\_INT\_TYPE}{3}{20}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN2\_INT\_TYPE}{3}{17}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN3\_INT\_TYPE}{3}{14}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN4\_INT\_TYPE}{3}{11}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN5\_INT\_TYPE}{3}{8}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN\_CLK\_GATE}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_WAKEUP\_STATUS\_CLR}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_WAKEUP\_STATUS}{6}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLGPIOWAKEUPSTATUS}\item [RTC\_CNTL\_GPIO\_WAKEUP\_STATUS] Indicates the RTC GPIO that woke up the chip, with Bit0 to Bit5 representing RTC GPIO 0 to RTC GPIO 5, respectively. For example, 010000 indicates it is the RTC GPIO 4 that woke up the chip. (RO)
\label{fielddesc:RTCCNTLGPIOWAKEUPSTATUSCLR}\item [RTC\_CNTL\_GPIO\_WAKEUP\_STATUS\_CLR] Clears the RTC GPIO wakeup flag. (R/W)
\label{fielddesc:RTCCNTLGPIOPINCLKGATE}\item [RTC\_CNTL\_GPIO\_PIN\_CLK\_GATE] Enables the RTC GPIO clock gate. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN5INTTYPE}\item [RTC\_CNTL\_GPIO\_PIN5\_INT\_TYPE] Configures RTC GPIO 5 wakeup type.\\
0: disable wakeup by RTC GPIO\\
1: wake up the chip upon the rising edge\\
2: wake up the chip upon the failing edge\\
3: wake up the chip upon the rising edge or the failing edge\\
4: wake up the chip upon low level\\
5: wake up the chip upon high level\\
(R/W)
\label{fielddesc:RTCCNTLGPIOPIN4INTTYPE}\item [RTC\_CNTL\_GPIO\_PIN4\_INT\_TYPE] Configures RTC GPIO 4 wakeup type.\\
0: disable wakeup by RTC GPIO\\
1: wake up the chip upon the rising edge\\
2: wake up the chip upon the failing edge\\
3: wake up the chip upon the rising edge or the failing edge\\
4: wake up the chip upon low level\\
5: wake up the chip upon high level\\
(R/W)
\label{fielddesc:RTCCNTLGPIOPIN3INTTYPE}\item [RTC\_CNTL\_GPIO\_PIN3\_INT\_TYPE] Configures RTC GPIO 3 wakeup type.\\
0: disable wakeup by RTC GPIO\\
1: wake up the chip upon the rising edge\\
2: wake up the chip upon the failing edge\\
3: wake up the chip upon the rising edge or the failing edge\\
4: wake up the chip upon low level\\
5: wake up the chip upon high level\\
(R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_GPIO\_WAKEUP\_REG}{0x0110}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:RTCCNTLGPIOPIN2INTTYPE}\item [RTC\_CNTL\_GPIO\_PIN2\_INT\_TYPE] Configures RTC GPIO 2 wakeup type.\\
0: disable wakeup by RTC GPIO\\
1: wake up the chip upon the rising edge\\
2: wake up the chip upon the failing edge\\
3: wake up the chip upon the rising edge or the failing edge\\
4: wake up the chip upon low level\\
5: wake up the chip upon high level\\
(R/W)
\label{fielddesc:RTCCNTLGPIOPIN1INTTYPE}\item [RTC\_CNTL\_GPIO\_PIN1\_INT\_TYPE] Configures RTC GPIO 1 wakeup type.\\
0: disable wakeup by RTC GPIO\\
1: wake up the chip upon the rising edge\\
2: wake up the chip upon the failing edge\\
3: wake up the chip upon the rising edge or the failing edge\\
4: wake up the chip upon low level\\
5: wake up the chip upon high level\\
(R/W)
\label{fielddesc:RTCCNTLGPIOPIN0INTTYPE}\item [RTC\_CNTL\_GPIO\_PIN0\_INT\_TYPE] Configures RTC GPIO 0 wakeup type. \\
0: disable wakeup by RTC GPIO\\
1: wake up the chip upon the rising edge\\
2: wake up the chip upon the failing edge\\
3: wake up the chip upon the rising edge or the failing edge\\
4: wake up the chip upon low level\\
5: wake up the chip upon high level\\
(R/W)
\label{fielddesc:RTCCNTLGPIOPIN5WAKEUPENABLE}\item [RTC\_CNTL\_GPIO\_PIN5\_WAKEUP\_ENABLE] Enables wakeup from RTC GPIO 5. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN4WAKEUPENABLE}\item [RTC\_CNTL\_GPIO\_PIN4\_WAKEUP\_ENABLE] Enables wakeup from RTC GPIO 4. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN3WAKEUPENABLE}\item [RTC\_CNTL\_GPIO\_PIN3\_WAKEUP\_ENABLE] Enables wakeup from RTC GPIO 3. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN2WAKEUPENABLE}\item [RTC\_CNTL\_GPIO\_PIN2\_WAKEUP\_ENABLE] Enables wakeup from RTC GPIO 2. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN1WAKEUPENABLE}\item [RTC\_CNTL\_GPIO\_PIN1\_WAKEUP\_ENABLE] Enables wakeup from RTC GPIO 1. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN0WAKEUPENABLE}\item [RTC\_CNTL\_GPIO\_PIN0\_WAKEUP\_ENABLE] Enables wakeup from RTC GPIO 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SENSOR\_CTRL\_REG}{0x011C}\label{regdesc:RTCCNTLSENSORCTRLREG}
\regfield{RTC\_CNTL\_FORCE\_XPD\_SAR}{2}{30}{{0}}%
\regfield{(reserved)}{3}{27}{{0}}%
\regfield{(reserved)}{27}{0}{000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLFORCEXPDSAR}\item [RTC\_CNTL\_FORCE\_XPD\_SAR] Set this field to FPU SAR ADC. (R/W)
\end{reglist}\end{regdesc}
\end{register}
