The addresses in parenthesis besides register names are the register addresses relative to the Low-power Management (RTC) base address provided in Table \ref{table:Peripheral_Address_Mapping} \textit{Peripheral Address Mapping} in Chapter \ref{mod:sysmem} \textit{\nameref{mod:sysmem}}. The absolute register addresses are listed in Section \ref{sec:lowpowm-reg-summ} \textit{\nameref{sec:lowpowm-reg-summ}}.

\raggedright

\begin{register}{H}{RTC\_CNTL\_OPTIONS0\_REG}{0x0000}\label{regdesc:RTCCNTLOPTIONS0REG}
\regfield{RTC\_CNTL\_SW\_SYS\_RST}{1}{31}{0}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_NORST}{1}{30}{0}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_RST}{1}{29}{0}%
\regfield{(reserved)}{6}{23}{000000}%
\regfield{RTC\_CNTL\_BIAS\_CORE\_FORCE\_PU}{1}{22}{1}%
\regfield{RTC\_CNTL\_BIAS\_CORE\_FORCE\_PD}{1}{21}{0}%
\regfield{RTC\_CNTL\_BIAS\_CORE\_FOLW\_8M}{1}{20}{0}%
\regfield{RTC\_CNTL\_BIAS\_I2C\_FORCE\_PU}{1}{19}{1}%
\regfield{RTC\_CNTL\_BIAS\_I2C\_FORCE\_PD}{1}{18}{0}%
\regfield{RTC\_CNTL\_BIAS\_I2C\_FOLW\_8M}{1}{17}{0}%
\regfield{RTC\_CNTL\_BIAS\_FORCE\_NOSLEEP}{1}{16}{1}%
\regfield{RTC\_CNTL\_BIAS\_FORCE\_SLEEP}{1}{15}{0}%
\regfield{RTC\_CNTL\_BIAS\_SLEEP\_FOLW\_8M}{1}{14}{0}%
\regfield{RTC\_CNTL\_XTL\_FORCE\_PU}{1}{13}{1}%
\regfield{RTC\_CNTL\_XTL\_FORCE\_PD}{1}{12}{0}%
\regfield{RTC\_CNTL\_BBPLL\_FORCE\_PU}{1}{11}{0}%
\regfield{RTC\_CNTL\_BBPLL\_FORCE\_PD}{1}{10}{0}%
\regfield{RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PU}{1}{9}{0}%
\regfield{RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PD}{1}{8}{0}%
\regfield{RTC\_CNTL\_BB\_I2C\_FORCE\_PU}{1}{7}{0}%
\regfield{RTC\_CNTL\_BB\_I2C\_FORCE\_PD}{1}{6}{0}%
\regfield{RTC\_CNTL\_SW\_PROCPU\_RST}{1}{5}{0}%
\regfield{RTC\_CNTL\_SW\_APPCPU\_RST}{1}{4}{0}%
\regfield{RTC\_CNTL\_SW\_STALL\_PROCPU\_C0}{2}{2}{00}%
\regfield{RTC\_CNTL\_SW\_STALL\_APPCPU\_C0}{2}{0}{00}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_SW\_SYS\_RST]\label{fielddesc:RTCCNTLSWSYSRST} SW system reset. (WO)
\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_NORST]The digital core forces no reset in deep sleep. (R/W)
\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_RST]The digital core can force a reset in deep sleep. (R/W)
\item [RTC\_CNTL\_BIAS\_CORE\_FORCE\_PU]BIAS\_CORE force power up. (R/W)
\item [RTC\_CNTL\_BIAS\_CORE\_FORCE\_PD]BIAS\_CORE force power down. (R/W)
\item [RTC\_CNTL\_BIAS\_CORE\_FOLW\_8M]BIAS\_CORE follow CK8M. (R/W)
\item [RTC\_CNTL\_BIAS\_I2C\_FORCE\_PU]BIAS\_I2C force power up. (R/W)
\item [RTC\_CNTL\_BIAS\_I2C\_FORCE\_PD]BIAS\_I2C force power down. (R/W)
\item [RTC\_CNTL\_BIAS\_I2C\_FOLW\_8M]BIAS\_I2C follow CK8M. (R/W)
\item [RTC\_CNTL\_BIAS\_FORCE\_NOSLEEP]BIAS\_SLEEP force no sleep. (R/W)
\item [RTC\_CNTL\_BIAS\_FORCE\_SLEEP]BIAS\_SLEEP force sleep. (R/W)
\item [RTC\_CNTL\_BIAS\_SLEEP\_FOLW\_8M]BIAS\_SLEEP follow CK8M. (R/W)
\item [RTC\_CNTL\_XTL\_FORCE\_PU]Crystal force power up. (R/W)
\item [RTC\_CNTL\_XTL\_FORCE\_PD]Crystal force power down. (R/W)
\item [RTC\_CNTL\_BBPLL\_FORCE\_PU]BB\_PLL force power up. (R/W)
\item [RTC\_CNTL\_BBPLL\_FORCE\_PD]BB\_PLL force power down. (R/W)
\item [RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PU]BB\_PLL\_I2C force power up. (R/W)
\item [RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PD]BB\_PLL \_I2C force power down. (R/W)
\item [RTC\_CNTL\_BB\_I2C\_FORCE\_PU]BB\_I2C force power up. (R/W)
\item [RTC\_CNTL\_BB\_I2C\_FORCE\_PD]BB\_I2C force power down. (R/W)
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_OPTIONS0\_REG}{0x0000}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\item [RTC\_CNTL\_SW\_PROCPU\_RST]PRO\_CPU SW reset. (WO)
\item [RTC\_CNTL\_SW\_APPCPU\_RST]\label{fielddesc:RTCCNTLSWAPPCPURST} APP\_CPU SW reset. (WO)
\item [RTC\_CNTL\_SW\_STALL\_PROCPU\_C0] described under \hyperref[regdesc:RTCCNTLSWCPUSTALLREG]{RTC\_CNTL\_SW\_CPU\_STALL\_REG}. (R/W)
\item [RTC\_CNTL\_SW\_STALL\_APPCPU\_C0] described under  \hyperref[regdesc:RTCCNTLSWCPUSTALLREG]{RTC\_CNTL\_SW\_CPU\_STALL\_REG}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLP\_TIMER0\_REG}{0x0004}\label{regdesc:RTCCNTLSLPTIMER0REG}
\regfield{}{32}{0}{{0x000000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_SLP\_TIMER0\_REG]RTC sleep timer low 32 bits. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLP\_TIMER1\_REG}{0x0008}\label{regdesc:RTCCNTLSLPTIMER1REG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_ALARM\_EN}{1}{16}{0}%
\regfield{RTC\_CNTL\_SLP\_VAL\_HI}{16}{0}{{0x00000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_MAIN\_TIMER\_ALARM\_EN]Timer alarm enable bit. (R/W)
\item [RTC\_CNTL\_SLP\_VAL\_HI]RTC sleep timer high 16 bits. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIME\_UPDATE\_REG}{0x000C}\label{regdesc:RTCCNTLTIMEUPDATEREG}
\regfield{RTC\_CNTL\_TIME\_UPDATE}{1}{31}{0}%
\regfield{RTC\_CNTL\_TIME\_VALID}{1}{30}{0}%
\regfield{(reserved)}{30}{0}{000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_TIME\_UPDATE]Set 1: to update register with RTC timer. (WO)
\item [RTC\_CNTL\_TIME\_VALID] Indicates that the register is updated. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIME0\_REG}{0x0010}\label{regdesc:RTCCNTLTIME0REG}
\regfield{}{32}{0}{{0x000000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_TIME0\_REG]RTC timer low 32 bits. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIME1\_REG}{0x0014}\label{regdesc:RTCCNTLTIME1REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{RTC\_CNTL\_TIME\_HI}{16}{0}{{0x00000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_TIME\_HI]RTC timer high 16 bits. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STATE0\_REG}{0x0018}\label{regdesc:RTCCNTLSTATE0REG}
\regfield{RTC\_CNTL\_SLEEP\_EN}{1}{31}{0}%
\regfield{RTC\_CNTL\_SLP\_REJECT}{1}{30}{0}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP}{1}{29}{0}%
\regfield{RTC\_CNTL\_SDIO\_ACTIVE\_IND}{1}{28}{0}%
\regfield{(reserved)}{3}{25}{000}%
\regfield{RTC\_CNTL\_ULP\_CP\_SLP\_TIMER\_EN}{1}{24}{0}%
\regfield{RTC\_CNTL\_TOUCH\_SLP\_TIMER\_EN}{1}{23}{0}%
\regfield{(reserved)}{23}{0}{00000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_SLEEP\_EN]Sleep enable bit. (R/W)
\item [RTC\_CNTL\_SLP\_REJECT]Sleep reject bit. (R/W)
\item [RTC\_CNTL\_SLP\_WAKEUP]Sleep wake-up bit. (R/W)
\item [RTC\_CNTL\_SDIO\_ACTIVE\_IND]SDIO active indication. (RO)
\item [RTC\_CNTL\_ULP\_CP\_SLP\_TIMER\_EN]ULP coprocessor timer enable bit. (R/W)
\item [RTC\_CNTL\_TOUCH\_SLP\_TIMER\_EN]Touch timer enable bit. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIMER1\_REG}{0x001C}\label{regdesc:RTCCNTLTIMER1REG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{RTC\_CNTL\_CPU\_STALL\_EN}{1}{0}{1}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_CPU\_STALL\_EN]CPU stall enable bit. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIMER2\_REG}{0x0020}\label{regdesc:RTCCNTLTIMER2REG}
\regfield{RTC\_CNTL\_MIN\_TIME\_CK8M\_OFF}{8}{24}{{0x001}}%
\regfield{RTC\_CNTL\_ULPCP\_TOUCH\_START\_WAIT}{9}{15}{{0x010}}%
\regfield{(reserved)}{15}{0}{000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_MIN\_TIME\_CK8M\_OFF]Minimal amount of cycles in RTC\_SLOW\_CLK to power down CK8M. (R/W)
\item [RTC\_CNTL\_ULPCP\_TOUCH\_START\_WAIT]\label{RTCCNTLULPCPTOUCHSTARTWAIT} Awaited cycles in RTC\_SLOW\_CLK before\\
ULP coprocessor/touch controller starts working. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIMER5\_REG}{0x002C}\label{regdesc:RTCCNTLTIMER5REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{RTC\_CNTL\_MIN\_SLP\_VAL}{8}{8}{{0x080}}%
\regfield{(reserved)}{8}{0}{00000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_MIN\_SLP\_VAL]Minimal amount of sleep cycles in RTC\_SLOW\_CLK. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_ANA\_CONF\_REG}{0x0030}\label{regdesc:RTCCNTLANACONFREG}
\regfield{RTC\_CNTL\_PLL\_I2C\_PU}{1}{31}{0}%
\regfield{RTC\_CNTL\_CKGEN\_I2C\_PU}{1}{30}{0}%
\regfield{(reserved)}{1}{29}{0}%
\regfield{RTC\_CNTL\_RFRX\_PBUS\_PU}{1}{28}{0}%
\regfield{RTC\_CNTL\_TXRF\_I2C\_PU}{1}{27}{0}%
\regfield{RTC\_CNTL\_PVTMON\_PU}{1}{26}{0}%
\regfield{(reserved)}{1}{25}{0}%
\regfield{RTC\_CNTL\_PLLA\_FORCE\_PU}{1}{24}{0}%
\regfield{RTC\_CNTL\_PLLA\_FORCE\_PD}{1}{23}{1}%
\regfield{(reserved)}{23}{0}{00000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_PLL\_I2C\_PU]1: PLL\_I2C power up,  otherwise power down. (R/W)
\item [RTC\_CNTL\_CKGEN\_I2C\_PU]1: CKGEN\_I2C power up,  otherwise power down. (R/W)
\item [RTC\_CNTL\_RFRX\_PBUS\_PU]1: RFRX\_PBUS power up,  otherwise power down. (R/W)
\item [RTC\_CNTL\_TXRF\_I2C\_PU]1: TXRF\_I2C power up,  otherwise power down. (R/W)
\item [RTC\_CNTL\_PVTMON\_PU]1: PVTMON power up,  otherwise power down. (R/W)
\item [RTC\_CNTL\_PLLA\_FORCE\_PU]PLLA force power up. (R/W)
\item [RTC\_CNTL\_PLLA\_FORCE\_PD]PLLA force power down. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_RESET\_STATE\_REG}{0x0034}\label{regdesc:RTCCNTLRESETSTATEREG}
\regfield{(reserved)}{18}{14}{000000000000000000}%
\regfield{RTC\_CNTL\_PROCPU\_STAT\_VECTOR\_SEL}{1}{13}{1}%
\regfield{RTC\_CNTL\_APPCPU\_STAT\_VECTOR\_SEL}{1}{12}{1}%
\regfield{RTC\_CNTL\_RESET\_CAUSE\_APPCPU}{6}{6}{xxxxxx}%
\regfield{RTC\_CNTL\_RESET\_CAUSE\_PROCPU}{6}{0}{xxxxxx}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_PROCPU\_STAT\_VECTOR\_SEL]PRO\_CPU state vector selection. (R/W)
\item [RTC\_CNTL\_APPCPU\_STAT\_VECTOR\_SEL]APP\_CPU state vector selection. (R/W)
\item [RTC\_CNTL\_RESET\_CAUSE\_APPCPU]\label{regdesc:RTCCNTLRESETCAUSEAPPCPU} Reset cause for APP\_CPU. (RO)
\item [RTC\_CNTL\_RESET\_CAUSE\_PROCPU]\label{fielddesc:RTCCNTLRESETCAUSEPROCPU} Reset cause for PRO\_CPU. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WAKEUP\_STATE\_REG}{0x0038}\label{regdesc:RTCCNTLWAKEUPSTATEREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{RTC\_CNTL\_GPIO\_WAKEUP\_FILTER}{1}{22}{0}%
\regfield{RTC\_CNTL\_WAKEUP\_ENA}{11}{11}{00000001100}%
\regfield{RTC\_CNTL\_WAKEUP\_CAUSE}{11}{0}{{0x000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_GPIO\_WAKEUP\_FILTER]Enable filter for GPIO wake-up event. (R/W)
\item [RTC\_CNTL\_WAKEUP\_ENA]Wake-up enable bitmap. (R/W)
\item [RTC\_CNTL\_WAKEUP\_CAUSE]Wake-up cause. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_ENA\_REG}{0x003C}\label{regdesc:RTCCNTLINTENAREG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_INT\_ENA}{1}{8}{0}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_ENA}{1}{7}{0}%
\regfield{RTC\_CNTL\_TOUCH\_INT\_ENA}{1}{6}{0}%
\regfield{RTC\_CNTL\_ULP\_CP\_INT\_ENA}{1}{5}{0}%
\regfield{RTC\_CNTL\_TIME\_VALID\_INT\_ENA}{1}{4}{0}%
\regfield{RTC\_CNTL\_WDT\_INT\_ENA}{1}{3}{0}%
\regfield{RTC\_CNTL\_SDIO\_IDLE\_INT\_ENA}{1}{2}{0}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_ENA}{1}{1}{0}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_MAIN\_TIMER\_INT\_ENA]The interrupt enable bit for the RTC\_CNTL\_MAIN\_TIMER\_INT interrupt. (R/W)
\item [RTC\_CNTL\_BROWN\_OUT\_INT\_ENA]The interrupt enable bit for the\\ RTC\_CNTL\_BROWN\_OUT\_INT interrupt. (R/W)
\item [RTC\_CNTL\_TOUCH\_INT\_ENA]The interrupt enable bit for the RTC\_CNTL\_TOUCH\_INT interrupt. (R/W)
\item [RTC\_CNTL\_ULP\_CP\_INT\_ENA]The interrupt enable bit for the RTC\_CNTL\_ULP\_CP\_INT interrupt. (R/W)
\item [RTC\_CNTL\_TIME\_VALID\_INT\_ENA]The interrupt enable bit for the RTC\_CNTL\_TIME\_VALID\_INT interrupt. (R/W)
\item [RTC\_CNTL\_WDT\_INT\_ENA]The interrupt enable bit for the RTC\_CNTL\_WDT\_INT interrupt. (R/W)
\item [RTC\_CNTL\_SDIO\_IDLE\_INT\_ENA]The interrupt enable bit for the RTC\_CNTL\_SDIO\_IDLE\_INT interrupt. (R/W)
\item [RTC\_CNTL\_SLP\_REJECT\_INT\_ENA]The interrupt enable bit for the RTC\_CNTL\_SLP\_REJECT\_INT interrupt. (R/W)
\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA]The interrupt enable bit for the\\ RTC\_CNTL\_SLP\_WAKEUP\_INT interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_RAW\_REG}{0x0040}\label{regdesc:RTCCNTLINTRAWREG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_INT\_RAW}{1}{8}{0}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_RAW}{1}{7}{0}%
\regfield{RTC\_CNTL\_TOUCH\_INT\_RAW}{1}{6}{0}%
\regfield{RTC\_CNTL\_ULP\_CP\_INT\_RAW}{1}{5}{0}%
\regfield{RTC\_CNTL\_TIME\_VALID\_INT\_RAW}{1}{4}{0}%
\regfield{RTC\_CNTL\_WDT\_INT\_RAW}{1}{3}{0}%
\regfield{RTC\_CNTL\_SDIO\_IDLE\_INT\_RAW}{1}{2}{0}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_RAW}{1}{1}{0}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_RAW}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_MAIN\_TIMER\_INT\_RAW]The raw interrupt status bit for the\\ RTC\_CNTL\_MAIN\_TIMER\_INT interrupt. (RO)
\item [RTC\_CNTL\_BROWN\_OUT\_INT\_RAW]The raw interrupt status bit for the\\ RTC\_CNTL\_BROWN\_OUT\_INT interrupt. (RO)
\item [RTC\_CNTL\_TOUCH\_INT\_RAW]The raw interrupt status bit for the RTC\_CNTL\_TOUCH\_INT interrupt. (RO)
\item [RTC\_CNTL\_ULP\_CP\_INT\_RAW]The raw interrupt status bit for the RTC\_CNTL\_ULP\_CP\_INT interrupt. (RO)
\item [RTC\_CNTL\_TIME\_VALID\_INT\_RAW]The raw interrupt status bit for the\\ RTC\_CNTL\_TIME\_VALID\_INT interrupt. (RO)
\item [RTC\_CNTL\_WDT\_INT\_RAW]The raw interrupt status bit for the RTC\_CNTL\_WDT\_INT interrupt. (RO)
\item [RTC\_CNTL\_SDIO\_IDLE\_INT\_RAW]The raw interrupt status bit for the RTC\_CNTL\_SDIO\_IDLE\_INT interrupt. (RO)
\item [RTC\_CNTL\_SLP\_REJECT\_INT\_RAW]The raw interrupt status bit for the\\ RTC\_CNTL\_SLP\_REJECT\_INT interrupt. (RO)
\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_RAW]The raw interrupt status bit for the\\ RTC\_CNTL\_SLP\_WAKEUP\_INT interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_ST\_REG}{0x0044}\label{regdesc:RTCCNTLINTSTREG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_INT\_ST}{1}{8}{0}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_ST}{1}{7}{0}%
\regfield{RTC\_CNTL\_TOUCH\_INT\_ST}{1}{6}{0}%
\regfield{RTC\_CNTL\_SAR\_INT\_ST}{1}{5}{0}%
\regfield{RTC\_CNTL\_TIME\_VALID\_INT\_ST}{1}{4}{0}%
\regfield{RTC\_CNTL\_WDT\_INT\_ST}{1}{3}{0}%
\regfield{RTC\_CNTL\_SDIO\_IDLE\_INT\_ST}{1}{2}{0}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_ST}{1}{1}{0}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_ST}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_MAIN\_TIMER\_INT\_ST]The masked interrupt status bit for the\\ RTC\_CNTL\_MAIN\_TIMER\_INT interrupt. (RO)
\item [RTC\_CNTL\_BROWN\_OUT\_INT\_ST]The masked interrupt status bit for the\\ RTC\_CNTL\_BROWN\_OUT\_INT interrupt. (RO)
\item [RTC\_CNTL\_TOUCH\_INT\_ST]The masked interrupt status bit for the RTC\_CNTL\_TOUCH\_INT interrupt. (RO)
\item [RTC\_CNTL\_SAR\_INT\_ST]The masked interrupt status bit for the RTC\_CNTL\_SAR\_INT interrupt. (RO)
\item [RTC\_CNTL\_TIME\_VALID\_INT\_ST]The masked interrupt status bit for the\\ RTC\_CNTL\_TIME\_VALID\_INT interrupt. (RO)
\item [RTC\_CNTL\_WDT\_INT\_ST]The masked interrupt status bit for the RTC\_CNTL\_WDT\_INT interrupt. (RO)
\item [RTC\_CNTL\_SDIO\_IDLE\_INT\_ST]The masked interrupt status bit for the\\ RTC\_CNTL\_SDIO\_IDLE\_INT interrupt. (RO)
\item [RTC\_CNTL\_SLP\_REJECT\_INT\_ST]The masked interrupt status bit for the\\ RTC\_CNTL\_SLP\_REJECT\_INT interrupt. (RO)
\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_ST]The masked interrupt status bit for the\\ RTC\_CNTL\_SLP\_WAKEUP\_INT interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_CLR\_REG}{0x0048}\label{regdesc:RTCCNTLINTCLRREG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_INT\_CLR}{1}{8}{0}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_CLR}{1}{7}{0}%
\regfield{RTC\_CNTL\_TOUCH\_INT\_CLR}{1}{6}{0}%
\regfield{RTC\_CNTL\_SAR\_INT\_CLR}{1}{5}{0}%
\regfield{RTC\_CNTL\_TIME\_VALID\_INT\_CLR}{1}{4}{0}%
\regfield{RTC\_CNTL\_WDT\_INT\_CLR}{1}{3}{0}%
\regfield{RTC\_CNTL\_SDIO\_IDLE\_INT\_CLR}{1}{2}{0}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_CLR}{1}{1}{0}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_CLR}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_MAIN\_TIMER\_INT\_CLR]Set this bit to clear the RTC\_CNTL\_MAIN\_TIMER\_INT interrupt. (WO)
\item [RTC\_CNTL\_BROWN\_OUT\_INT\_CLR]Set this bit to clear the RTC\_CNTL\_BROWN\_OUT\_INT interrupt. (WO)
\item [RTC\_CNTL\_TOUCH\_INT\_CLR]Set this bit to clear the RTC\_CNTL\_TOUCH\_INT interrupt. (WO)
\item [RTC\_CNTL\_SAR\_INT\_CLR]Set this bit to clear the RTC\_CNTL\_SAR\_INT interrupt. (WO)
\item [RTC\_CNTL\_TIME\_VALID\_INT\_CLR]Set this bit to clear the RTC\_CNTL\_TIME\_VALID\_INT interrupt. (WO)
\item [RTC\_CNTL\_WDT\_INT\_CLR]Set this bit to clear the RTC\_CNTL\_WDT\_INT interrupt. (WO)
\item [RTC\_CNTL\_SDIO\_IDLE\_INT\_CLR]Set this bit to clear the RTC\_CNTL\_SDIO\_IDLE\_INT interrupt. (WO)
\item [RTC\_CNTL\_SLP\_REJECT\_INT\_CLR]Set this bit to clear the RTC\_CNTL\_SLP\_REJECT\_INT interrupt. (WO)
\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_CLR]Set this bit to clear the RTC\_CNTL\_SLP\_WAKEUP\_INT interrupt. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE\textcolor{red}{\it{n}}\_REG (\textcolor{red}{\it{n}}: 0-3)}{0x004C+4*\textcolor{red}{\it{n}}}\label{regdesc:RTCCNTLSTOREnREG}
\regfield{}{32}{0}{xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_STORE\textcolor{red}{\it{n}}\_REG]32-bit general-purpose retention register. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_LOW\_POWER\_ST\_REG}{0x00C0}\label{regdesc:RTCCNTLLOWPOWERSTREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{RTC\_CNTL\_MAIN\_STATE\_IN\_IDEL}{1}{27}{{0}}%
\regfield{(reserved)}{7}{20}{0000000}%
\regfield{RTC\_CNTL\_RTC\_RDY\_FOR\_WAKEUP}{1}{19}{{0}}%
\regfield{(reserved)}{19}{0}{0000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCRDYFORWAKEUP}\item [RTC\_CNTL\_RTC\_RDY\_FOR\_WAKEUP] The value 1 indicates the RTC is ready to be triggered by any wakeup source. (RO)
\label{fielddesc:RTCCNTLMAINSTATEINIDLE}\item [RTC\_CNTL\_MAIN\_STATE\_IN\_IDLE] Indicates the RTC state.
\begin{itemize}
    \item 0: the chip can be either
\begin{itemize}
    \item in sleep modes.
    \item entering sleep modes. In this case, wait until \hyperref[fielddesc:RTCCNTLRTCRDYFORWAKEUP]{RTC\_CNTL\_RTC\_RDY\_FOR\_WAKEUP} bit is set, then you can wake up the chip.
    \item exiting sleep mode. In this case, \hyperref[fielddesc:RTCCNTLMAINSTATEINIDLE]{RTC\_CNTL\_MAIN\_STATE\_IN\_IDLE} will eventually become 1.
\end{itemize}
    \item 1: the chip is not in sleep modes (i.e. running normally).
\end{itemize}
(RO)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_EXT\_XTL\_CONF\_REG}{0x005C}\label{regdesc:RTCCNTLEXTXTLCONFREG}
\regfield{RTC\_CNTL\_XTL\_EXT\_CTR\_EN}{1}{31}{0}%
\regfield{RTC\_CNTL\_XTL\_EXT\_CTR\_LV}{1}{30}{0}%
\regfield{(reserved)}{30}{0}{000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_XTL\_EXT\_CTR\_EN]Enable control XTAL with external pads. (R/W)
\label{regdesc:RTCCNTLXTEXTCTRLV} \item [RTC\_CNTL\_XTL\_EXT\_CTR\_LV]0: power down XTAL at high level, 1: power down XTAL at low level. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_EXT\_WAKEUP\_CONF\_REG}{0x0060}\label{regdesc:RTCCNTLEXTWAKEUPCONFREG}
\regfield{RTC\_CNTL\_EXT\_WAKEUP1\_LV}{1}{31}{0}%
\regfield{RTC\_CNTL\_EXT\_WAKEUP0\_LV}{1}{30}{0}%
\regfield{(reserved)}{30}{0}{000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_EXT\_WAKEUP1\_LV]0: external wake-up at low level, 1: external wake-up at high level. (R/W)
\item [RTC\_CNTL\_EXT\_WAKEUP0\_LV]0: external wake-up at low level, 1: external wake-up at high level. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_SLP\_REJECT\_CONF\_REG}{0x0064}\label{regdesc:RTCCNTLSLPREJECTCONFREG}
\regfield{RTC\_CNTL\_REJECT\_CAUSE}{4}{28}{0000}%
\regfield{RTC\_CNTL\_DEEP\_SLP\_REJECT\_EN}{1}{27}{0}%
\regfield{RTC\_CNTL\_LIGHT\_SLP\_REJECT\_EN}{1}{26}{0}%
\regfield{RTC\_CNTL\_SDIO\_REJECT\_EN}{1}{25}{0}%
\regfield{RTC\_CNTL\_GPIO\_REJECT\_EN}{1}{24}{0}%
\regfield{(reserved)}{24}{0}{000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_REJECT\_CAUSE]Sleep reject cause. 2: GPIO; 3: SDIO. (RO)
\item [RTC\_CNTL\_DEEP\_SLP\_REJECT\_EN]Enable reject for deep sleep. (R/W)
\item [RTC\_CNTL\_LIGHT\_SLP\_REJECT\_EN]Enable reject for light sleep. (R/W)
\item [RTC\_CNTL\_SDIO\_REJECT\_EN]Enable SDIO reject. (R/W)
\item [RTC\_CNTL\_GPIO\_REJECT\_EN]Enable GPIO reject. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_CPU\_PERIOD\_CONF\_REG}{0x0068}\label{regdesc:RTCCNTLCPUPERIODCONFREG}
\regfield{RTC\_CNTL\_RTC\_CPUPERIOD\_SEL}{2}{30}{00}%
\regfield{RTC\_CNTL\_CPUSEL\_CONF}{1}{29}{0}%
\regfield{(reserved)}{29}{0}{00000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_RTC\_CPUPERIOD\_SEL]CPU period selection. (R/W)
\item [RTC\_CNTL\_CPUSEL\_CONF]CPU selection option. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_CLK\_CONF\_REG}{0x0070}\label{regdesc:RTCCNTLCLKCONFREG}
\regfield{RTC\_CNTL\_ANA\_CLK\_RTC\_SEL}{2}{30}{{0}}%
\regfield{RTC\_CNTL\_RTC\_FAST\_CLK\_SEL}{1}{29}{0}%
\regfield{RTC\_CNTL\_SOC\_CLK\_SEL}{2}{27}{{0}}%
\regfield{RTC\_CNTL\_CK8M\_FORCE\_PU}{1}{26}{0}%
\regfield{RTC\_CNTL\_CK8M\_FORCE\_PD}{1}{25}{0}%
\regfield{RTC\_CNTL\_CK8M\_DFREQ}{8}{17}{{0}}%
\regfield{(reserved)}{2}{15}{00}%
\regfield{RTC\_CNTL\_CK8M\_DIV\_SEL}{3}{12}{{2}}%
\regfield{(reserved)}{1}{11}{0}%
\regfield{RTC\_CNTL\_DIG\_CLK8M\_EN}{1}{10}{0}%
\regfield{RTC\_CNTL\_DIG\_CLK8M\_D256\_EN}{1}{9}{1}%
\regfield{RTC\_CNTL\_DIG\_XTAL32K\_EN}{1}{8}{0}%
\regfield{RTC\_CNTL\_ENB\_CK8M\_DIV}{1}{7}{0}%
\regfield{RTC\_CNTL\_ENB\_CK8M}{1}{6}{0}%
\regfield{RTC\_CNTL\_CK8M\_DIV}{2}{4}{01}%
\regfield{(reserved)}{4}{0}{0000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLANACLKRTCSEL}\item [RTC\_CNTL\_ANA\_CLK\_RTC\_SEL]RTC\_SLOW\_CLK sel. 0: RC\_SLOW\_CLK, 1: XTL32K\_CLK,\\ 2: RC\_FAST\_DIV\_CLK. (R/W)
\label{fielddesc:RTCCNTLFASTCLKSEL}\item [RTC\_CNTL\_RTC\_FAST\_CLK\_SEL]RTC\_FAST\_CLK sel. 0: XTAL div 4, 1: CK8M. (R/W)
\label{regdesc:RTCCNTLSOCCLKSEL} \item [RTC\_CNTL\_SOC\_CLK\_SEL] SoC clock selection. 0: XTAL, 1: PLL, 2: CK8M, 3: APLL. (R/W)
\item [RTC\_CNTL\_CK8M\_FORCE\_PU]CK8M force power up. (R/W)
\item [RTC\_CNTL\_CK8M\_FORCE\_PD]CK8M force power down. (R/W)
\item [RTC\_CNTL\_CK8M\_DFREQ]CK8M\_DFREQ. (R/W)
\item [RTC\_CNTL\_CK8M\_DIV\_SEL]Divider = reg\_rtc\_cntl\_ck8m\_div\_sel + 1. (R/W)
\item [RTC\_CNTL\_DIG\_CLK8M\_EN]Enable CK8M for digital core (no relation to RTC core). (R/W)
\item [RTC\_CNTL\_DIG\_CLK8M\_D256\_EN]Enable RC\_FAST\_DIV\_CLK for digital core (no relation to RTC core). (R/W)
\item [RTC\_CNTL\_DIG\_XTAL32K\_EN]Enable XTL32K\_CLK for digital core (no relation to RTC core). (R/W)
\item [RTC\_CNTL\_ENB\_CK8M\_DIV]1: RC\_FAST\_DIV\_CLK is actually CK8M, 0: RC\_FAST\_DIV\_CLK is CK8M divided by 256. (R/W)
\item [RTC\_CNTL\_ENB\_CK8M]Disable CK8M and RC\_FAST\_DIV\_CLK. (R/W)
\item [RTC\_CNTL\_CK8M\_DIV] RC\_FAST\_DIV\_CLK divider. 00: div128, 01: div256, 10: div512, 11: div1024. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SDIO\_CONF\_REG}{0x0074}\label{regdesc:RTCCNTLSDIOCONFREG}
\regfield{RTC\_CNTL\_XPD\_SDIO\_VREG}{1}{31}{0}%
\regfield{RTC\_CNTL\_DREFH\_SDIO}{2}{29}{00}%
\regfield{RTC\_CNTL\_DREFM\_SDIO}{2}{27}{00}%
\regfield{RTC\_CNTL\_DREFL\_SDIO}{2}{25}{01}%
\regfield{RTC\_CNTL\_REG1P8\_READY}{1}{24}{0}%
\regfield{RTC\_CNTL\_SDIO\_TIEH}{1}{23}{1}%
\regfield{RTC\_CNTL\_SDIO\_FORCE}{1}{22}{0}%
\regfield{RTC\_CNTL\_SDIO\_VREG\_PD\_EN}{1}{21}{1}%
\regfield{(reserved)}{21}{0}{000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_XPD\_SDIO\_VREG]SW option for XPD\_SDIO\_VREG; active only when\\ reg\_rtc\_cntl\_sdio\_force == 1. (R/W)
\label{fielddesc:RTCCNTLDREFHSDIO}\item [RTC\_CNTL\_DREFH\_SDIO]SW option for DREFH\_SDIO; active only when reg\_rtc\_cntl\_sdio\_force == 1. (R/W)
\label{fielddesc:RTCCNTLDREFMSDIO}\item [RTC\_CNTL\_DREFM\_SDIO]SW option for DREFM\_SDIO; active only when reg\_rtc\_cntl\_sdio\_force == 1. (R/W)
\label{fielddesc:RTCCNTLDREFLSDIO}\item [RTC\_CNTL\_DREFL\_SDIO]SW option for DREFL\_SDIO; active only when reg\_rtc\_cntl\_sdio\_force == 1. (R/W)
\item [RTC\_CNTL\_REG1P8\_READY]Read-only register for REG1P8\_READY. (RO)
\item [RTC\_CNTL\_SDIO\_TIEH]SW option for SDIO\_TIEH; active only when reg\_rtc\_cntl\_sdio\_force == 1. (R/W)
\item [RTC\_CNTL\_SDIO\_FORCE]1: use SW option to control SDIO\_VREG; 0: use state machine to control SDIO\_VREG. (R/W)
\item [RTC\_CNTL\_SDIO\_VREG\_PD\_EN]Power down SDIO\_VREG in sleep; active only when\\ reg\_rtc\_cntl\_sdio\_force == 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_VREG\_REG}{0x007C}\label{regdesc:RTCCNTLVREGREG}
\regfield{RTC\_CNTL\_VREG\_FORCE\_PU}{1}{31}{1}%
\regfield{RTC\_CNTL\_VREG\_FORCE\_PD}{1}{30}{0}%
\regfield{RTC\_CNTL\_DBOOST\_FORCE\_PU}{1}{29}{1}%
\regfield{RTC\_CNTL\_DBOOST\_FORCE\_PD}{1}{28}{0}%
\regfield{RTC\_CNTL\_DBIAS\_WAK}{3}{25}{{4}}%
\regfield{RTC\_CNTL\_DBIAS\_SLP}{3}{22}{{4}}%
\regfield{RTC\_CNTL\_SCK\_DCAP}{8}{14}{{0}}%
\regfield{RTC\_CNTL\_DIG\_VREG\_DBIAS\_WAK}{3}{11}{{4}}%
\regfield{RTC\_CNTL\_DIG\_VREG\_DBIAS\_SLP}{3}{8}{{4}}%
\regfield{(reserved)}{8}{0}{00000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLVREGFORCEPU}\item [RTC\_CNTL\_VREG\_FORCE\_PU]RTC voltage regulator - force power up. (R/W)
\label{fielddesc:RTCCNTLVREGFORCEPD}\item [RTC\_CNTL\_VREG\_FORCE\_PD]RTC voltage regulator - force power down (in this case power down means decreasing the voltage to 0.8 V or lower). (R/W)
\item [RTC\_CNTL\_DBOOST\_FORCE\_PU]RTC\_DBOOST force power up. (R/W)
\item [RTC\_CNTL\_DBOOST\_FORCE\_PD]RTC\_DBOOST force power down. (R/W)
\label{fielddesc:RTCCNTLDBIASWAK}\item [RTC\_CNTL\_DBIAS\_WAK]RTC\_DBIAS during wake-up. (R/W)
\item [RTC\_CNTL\_DBIAS\_SLP]RTC\_DBIAS during sleep. (R/W)
\item [RTC\_CNTL\_SCK\_DCAP]Used to adjust the frequency of RTC slow clock. (R/W)
\label{fielddesc:RTCCNTLDIGVREGDBIASWAK}\item [RTC\_CNTL\_DIG\_VREG\_DBIAS\_WAK]Digital voltage regulator DBIAS during wake-up. (R/W)
\label{fielddesc:RTCCNTLDIGVREGDBIASSLP}\item [RTC\_CNTL\_DIG\_VREG\_DBIAS\_SLP]Digital voltage regulator DBIAS during sleep. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_PWC\_REG}{0x0080}\label{regdesc:RTCCNTLPWCREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_PD\_EN}{1}{20}{0}%
\regfield{RTC\_CNTL\_FORCE\_PU}{1}{19}{0}%
\regfield{RTC\_CNTL\_FORCE\_PD}{1}{18}{0}%
\regfield{RTC\_CNTL\_SLOWMEM\_PD\_EN}{1}{17}{0}%
\regfield{RTC\_CNTL\_SLOWMEM\_FORCE\_PU}{1}{16}{1}%
\regfield{RTC\_CNTL\_SLOWMEM\_FORCE\_PD}{1}{15}{0}%
\regfield{RTC\_CNTL\_FASTMEM\_PD\_EN}{1}{14}{0}%
\regfield{RTC\_CNTL\_FASTMEM\_FORCE\_PU}{1}{13}{1}%
\regfield{RTC\_CNTL\_FASTMEM\_FORCE\_PD}{1}{12}{0}%
\regfield{RTC\_CNTL\_SLOWMEM\_FORCE\_LPU}{1}{11}{1}%
\regfield{RTC\_CNTL\_SLOWMEM\_FORCE\_LPD}{1}{10}{0}%
\regfield{RTC\_CNTL\_SLOWMEM\_FOLW\_CPU}{1}{9}{0}%
\regfield{RTC\_CNTL\_FASTMEM\_FORCE\_LPU}{1}{8}{1}%
\regfield{RTC\_CNTL\_FASTMEM\_FORCE\_LPD}{1}{7}{0}%
\regfield{RTC\_CNTL\_FASTMEM\_FOLW\_CPU}{1}{6}{0}%
\regfield{RTC\_CNTL\_FORCE\_NOISO}{1}{5}{1}%
\regfield{RTC\_CNTL\_FORCE\_ISO}{1}{4}{0}%
\regfield{RTC\_CNTL\_SLOWMEM\_FORCE\_ISO}{1}{3}{0}%
\regfield{RTC\_CNTL\_SLOWMEM\_FORCE\_NOISO}{1}{2}{1}%
\regfield{RTC\_CNTL\_FASTMEM\_FORCE\_ISO}{1}{1}{0}%
\regfield{RTC\_CNTL\_FASTMEM\_FORCE\_NOISO}{1}{0}{1}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_PD\_EN]Enable power down rtc\_peri in sleep. (R/W)
\item [RTC\_CNTL\_FORCE\_PU]rtc\_peri force power up. (R/W)
\item [RTC\_CNTL\_FORCE\_PD]rtc\_peri force power down. (R/W)
\item [RTC\_CNTL\_SLOWMEM\_PD\_EN]Enable power down RTC memory in sleep. (R/W)
\item [RTC\_CNTL\_SLOWMEM\_FORCE\_PU]RTC memory force power up. (R/W)
\item [RTC\_CNTL\_SLOWMEM\_FORCE\_PD]RTC memory force power down. (R/W)
\item [RTC\_CNTL\_FASTMEM\_PD\_EN]Enable power down fast RTC memory in sleep. (R/W)
\item [RTC\_CNTL\_FASTMEM\_FORCE\_PU]Fast RTC memory force power up. (R/W)
\item [RTC\_CNTL\_FASTMEM\_FORCE\_PD]Fast RTC memory force power down. (R/W)
\item [RTC\_CNTL\_SLOWMEM\_FORCE\_LPU]RTC memory force power up in low-power mode. (R/W)
\item [RTC\_CNTL\_SLOWMEM\_FORCE\_LPD]RTC memory force power down in low-power mode. (R/W)
\item [RTC\_CNTL\_SLOWMEM\_FOLW\_CPU]1: RTC memory low-power mode PD following CPU; 0: RTC memory low-power mode PD following RTC state machine. (R/W)
\item [RTC\_CNTL\_FASTMEM\_FORCE\_LPU]Fast RTC memory force power up in low-power mode. (R/W)
\item [RTC\_CNTL\_FASTMEM\_FORCE\_LPD]Fast RTC memory force power down in low-power mode. (R/W)
\item [RTC\_CNTL\_FASTMEM\_FOLW\_CPU]1: Fast RTC memory low-power mode PD following CPU; 0: fast RTC memory low-power mode PD following RTC state machine. (R/W)
\item [RTC\_CNTL\_FORCE\_NOISO]rtc\_peri force no isolation. (R/W)
\item [RTC\_CNTL\_FORCE\_ISO]rtc\_peri force isolation. (R/W)
\item [RTC\_CNTL\_SLOWMEM\_FORCE\_ISO]RTC memory force isolation. (R/W)
\item [RTC\_CNTL\_SLOWMEM\_FORCE\_NOISO]RTC memory force no isolation. (R/W)
\item [RTC\_CNTL\_FASTMEM\_FORCE\_ISO]Fast RTC memory force isolation. (R/W)
\item [RTC\_CNTL\_FASTMEM\_FORCE\_NOISO]Fast RTC memory force no isolation. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_DIG\_PWC\_REG}{0x0084}\label{regdesc:RTCCNTLDIGPWCREG}
\regfield{RTC\_CNTL\_DG\_WRAP\_PD\_EN}{1}{31}{x}%
\regfield{RTC\_CNTL\_WIFI\_PD\_EN}{1}{30}{x}%
\regfield{RTC\_CNTL\_INTER\_RAM4\_PD\_EN}{1}{29}{x}%
\regfield{RTC\_CNTL\_INTER\_RAM3\_PD\_EN}{1}{28}{x}%
\regfield{RTC\_CNTL\_INTER\_RAM2\_PD\_EN}{1}{27}{x}%
\regfield{RTC\_CNTL\_INTER\_RAM1\_PD\_EN}{1}{26}{x}%
\regfield{RTC\_CNTL\_INTER\_RAM0\_PD\_EN}{1}{25}{x}%
\regfield{RTC\_CNTL\_ROM0\_PD\_EN}{1}{24}{x}%
\regfield{(reserved)}{3}{21}{000}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_PU}{1}{20}{1}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_PD}{1}{19}{0}%
\regfield{RTC\_CNTL\_WIFI\_FORCE\_PU}{1}{18}{1}%
\regfield{RTC\_CNTL\_WIFI\_FORCE\_PD}{1}{17}{0}%
\regfield{RTC\_CNTL\_INTER\_RAM4\_FORCE\_PU}{1}{16}{1}%
\regfield{RTC\_CNTL\_INTER\_RAM4\_FORCE\_PD}{1}{15}{0}%
\regfield{RTC\_CNTL\_INTER\_RAM3\_FORCE\_PU}{1}{14}{1}%
\regfield{RTC\_CNTL\_INTER\_RAM3\_FORCE\_PD}{1}{13}{0}%
\regfield{RTC\_CNTL\_INTER\_RAM2\_FORCE\_PU}{1}{12}{1}%
\regfield{RTC\_CNTL\_INTER\_RAM2\_FORCE\_PD}{1}{11}{0}%
\regfield{RTC\_CNTL\_INTER\_RAM1\_FORCE\_PU}{1}{10}{1}%
\regfield{RTC\_CNTL\_INTER\_RAM1\_FORCE\_PD}{1}{9}{0}%
\regfield{RTC\_CNTL\_INTER\_RAM0\_FORCE\_PU}{1}{8}{1}%
\regfield{RTC\_CNTL\_INTER\_RAM0\_FORCE\_PD}{1}{7}{0}%
\regfield{RTC\_CNTL\_ROM0\_FORCE\_PU}{1}{6}{1}%
\regfield{RTC\_CNTL\_ROM0\_FORCE\_PD}{1}{5}{0}%
\regfield{RTC\_CNTL\_LSLP\_MEM\_FORCE\_PU}{1}{4}{1}%
\regfield{RTC\_CNTL\_LSLP\_MEM\_FORCE\_PD}{1}{3}{0}%
\regfield{(reserved)}{3}{0}{000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_DG\_WRAP\_PD\_EN]Enable power down digital core in sleep mode. (R/W)
\item [RTC\_CNTL\_WIFI\_PD\_EN]Enable power down Wi-Fi in sleep. (R/W)
\item [RTC\_CNTL\_INTER\_RAM4\_PD\_EN]Enable power down internal SRAM 4 in sleep mode. (R/W)
\item [RTC\_CNTL\_INTER\_RAM3\_PD\_EN]Enable power down internal SRAM 3 in sleep mode. (R/W)
\item [RTC\_CNTL\_INTER\_RAM2\_PD\_EN]Enable power down internal SRAM 2 in sleep mode. (R/W)
\item [RTC\_CNTL\_INTER\_RAM1\_PD\_EN]Enable power down internal SRAM 1 in sleep mode. (R/W)
\item [RTC\_CNTL\_INTER\_RAM0\_PD\_EN]Enable power down internal SRAM 0 in sleep mode. (R/W)
\item [RTC\_CNTL\_ROM0\_PD\_EN]Enable power down ROM in sleep mode. (R/W)
\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_PU]Digital core force power up. (R/W)
\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_PD]Digital core force power down. (R/W)
\item [RTC\_CNTL\_WIFI\_FORCE\_PU]Wi-Fi force power up. (R/W)
\item [RTC\_CNTL\_WIFI\_FORCE\_PD]Wi-Fi force power down. (R/W)
\item [RTC\_CNTL\_INTER\_RAM4\_FORCE\_PU]Internal SRAM 4 force power up. (R/W)
\item [RTC\_CNTL\_INTER\_RAM4\_FORCE\_PD]Internal SRAM 4 force power down. (R/W)
\item [RTC\_CNTL\_INTER\_RAM3\_FORCE\_PU]Internal SRAM 3 force power up. (R/W)
\item [RTC\_CNTL\_INTER\_RAM3\_FORCE\_PD]Internal SRAM 3 force power down. (R/W)
\item [RTC\_CNTL\_INTER\_RAM2\_FORCE\_PU]Internal SRAM 2 force power up. (R/W)
\item [RTC\_CNTL\_INTER\_RAM2\_FORCE\_PD]Internal SRAM 2 force power down. (R/W)
\item [RTC\_CNTL\_INTER\_RAM1\_FORCE\_PU]Internal SRAM 1 force power up. (R/W)
\item [RTC\_CNTL\_INTER\_RAM1\_FORCE\_PD]Internal SRAM 1 force power down. (R/W)
\item [RTC\_CNTL\_INTER\_RAM0\_FORCE\_PU]Internal SRAM 0 force power up. (R/W)
\item [RTC\_CNTL\_INTER\_RAM0\_FORCE\_PD]Internal SRAM 0 force power down. (R/W)
\item [RTC\_CNTL\_ROM0\_FORCE\_PU]ROM force power up. (R/W)
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_DIG\_PWC\_REG}{0x0084}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\item [RTC\_CNTL\_ROM0\_FORCE\_PD]ROM force power down. (R/W)
\item [RTC\_CNTL\_LSLP\_MEM\_FORCE\_PU]Memories in digital core force power up in sleep mode. (R/W)
\item [RTC\_CNTL\_LSLP\_MEM\_FORCE\_PD]Memories in digital core force power down in sleep mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_DIG\_ISO\_REG}{0x0088}\label{regdesc:RTCCNTLDIGISOREG}
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_NOISO}{1}{31}{1}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_ISO}{1}{30}{0}%
\regfield{RTC\_CNTL\_WIFI\_FORCE\_NOISO}{1}{29}{1}%
\regfield{RTC\_CNTL\_WIFI\_FORCE\_ISO}{1}{28}{0}%
\regfield{RTC\_CNTL\_INTER\_RAM4\_FORCE\_NOISO}{1}{27}{1}%
\regfield{RTC\_CNTL\_INTER\_RAM4\_FORCE\_ISO}{1}{26}{0}%
\regfield{RTC\_CNTL\_INTER\_RAM3\_FORCE\_NOISO}{1}{25}{1}%
\regfield{RTC\_CNTL\_INTER\_RAM3\_FORCE\_ISO}{1}{24}{0}%
\regfield{RTC\_CNTL\_INTER\_RAM2\_FORCE\_NOISO}{1}{23}{1}%
\regfield{RTC\_CNTL\_INTER\_RAM2\_FORCE\_ISO}{1}{22}{0}%
\regfield{RTC\_CNTL\_INTER\_RAM1\_FORCE\_NOISO}{1}{21}{1}%
\regfield{RTC\_CNTL\_INTER\_RAM1\_FORCE\_ISO}{1}{20}{0}%
\regfield{RTC\_CNTL\_INTER\_RAM0\_FORCE\_NOISO}{1}{19}{1}%
\regfield{RTC\_CNTL\_INTER\_RAM0\_FORCE\_ISO}{1}{18}{0}%
\regfield{RTC\_CNTL\_ROM0\_FORCE\_NOISO}{1}{17}{1}%
\regfield{RTC\_CNTL\_ROM0\_FORCE\_ISO}{1}{16}{0}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_HOLD}{1}{15}{0}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_UNHOLD}{1}{14}{1}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_ISO}{1}{13}{0}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_NOISO}{1}{12}{1}%
\regfield{RTC\_CNTL\_REG\_RTC\_CNTL\_DG\_PAD\_AUTOHOLD\_EN}{1}{11}{0}%
\regfield{RTC\_CNTL\_CLR\_REG\_RTC\_CNTL\_DG\_PAD\_AUTOHOLD}{1}{10}{0}%
\regfield{RTC\_CNTL\_DG\_PAD\_AUTOHOLD}{1}{9}{0}%
\regfield{(reserved)}{9}{0}{000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_NOISO]Digital core force no isolation. (R/W)
\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_ISO]Digital core force isolation. (R/W)
\item [RTC\_CNTL\_WIFI\_FORCE\_NOISO]Wi-Fi force no isolation. (R/W)
\item [RTC\_CNTL\_WIFI\_FORCE\_ISO]Wi-Fi force isolation. (R/W)
\item [RTC\_CNTL\_INTER\_RAM4\_FORCE\_NOISO]Internal SRAM 4 force no isolation. (R/W)
\item [RTC\_CNTL\_INTER\_RAM4\_FORCE\_ISO]Internal SRAM 4 force isolation. (R/W)
\item [RTC\_CNTL\_INTER\_RAM3\_FORCE\_NOISO]Internal SRAM 3 force no isolation. (R/W)
\item [RTC\_CNTL\_INTER\_RAM3\_FORCE\_ISO]Internal SRAM 3 force isolation. (R/W)
\item [RTC\_CNTL\_INTER\_RAM2\_FORCE\_NOISO]Internal SRAM 2 force no isolation. (R/W)
\item [RTC\_CNTL\_INTER\_RAM2\_FORCE\_ISO]Internal SRAM 2 force isolation. (R/W)
\item [RTC\_CNTL\_INTER\_RAM1\_FORCE\_NOISO]Internal SRAM 1 force no isolation. (R/W)
\item [RTC\_CNTL\_INTER\_RAM1\_FORCE\_ISO]Internal SRAM 1 force isolation. (R/W)
\item [RTC\_CNTL\_INTER\_RAM0\_FORCE\_NOISO]Internal SRAM 0 force no isolation. (R/W)
\item [RTC\_CNTL\_INTER\_RAM0\_FORCE\_ISO]Internal SRAM 0 force isolation. (R/W)
\item [RTC\_CNTL\_ROM0\_FORCE\_NOISO]ROM force no isolation. (R/W)
\item [RTC\_CNTL\_ROM0\_FORCE\_ISO]ROM force isolation. (R/W)
\item [RTC\_CNTL\_DG\_PAD\_FORCE\_HOLD]Digital pad force hold. (R/W)
\item [RTC\_CNTL\_DG\_PAD\_FORCE\_UNHOLD]Digital pad force un-hold. (R/W)
\item [RTC\_CNTL\_DG\_PAD\_FORCE\_ISO]Digital pad force isolation. (R/W)
\item [RTC\_CNTL\_DG\_PAD\_FORCE\_NOISO]Digital pad force no isolation. (R/W)
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_DIG\_ISO\_REG}{0x0088}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\item [RTC\_CNTL\_REG\_RTC\_CNTL\_DG\_PAD\_AUTOHOLD\_EN]Digital pad enable auto-hold. (R/W)
\item [RTC\_CNTL\_CLR\_REG\_RTC\_CNTL\_DG\_PAD\_AUTOHOLD]Write-only register clears digital pad auto-hold. (WO)
\item [RTC\_CNTL\_DG\_PAD\_AUTOHOLD]Read-only register indicates digital pad auto-hold status. (RO)
\end{reglist}\end{regdesc}
\end{register}



\begin{register}{H}{RTC\_CNTL\_WDTCONFIG0\_REG}{0x008C}\label{regdesc:RTCCNTLWDTCONFIG0REG}
\regfield{RTC\_CNTL\_WDT\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_WDT\_STG0}{3}{28}{{0}}%
\regfield{RTC\_CNTL\_WDT\_STG1}{3}{25}{{0}}%
\regfield{RTC\_CNTL\_WDT\_STG2}{3}{22}{0}%
\regfield{RTC\_CNTL\_WDT\_STG3}{3}{19}{{0}}%
\regfield{reserved}{1}{18}{{0}}%
\regfield{reserved}{1}{17}{{0}}%
\regfield{RTC\_CNTL\_WDT\_CPU\_RESET\_LENGTH}{3}{14}{{1}}%
\regfield{RTC\_CNTL\_WDT\_SYS\_RESET\_LENGTH}{3}{11}{{1}}%
\regfield{RTC\_CNTL\_WDT\_FLASHBOOT\_MOD\_EN}{1}{10}{{1}}%
\regfield{RTC\_CNTL\_WDT\_PROCPU\_RESET\_EN}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_WDT\_APPCPU\_RESET\_EN}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_WDT\_PAUSE\_IN\_SLP}{1}{7}{{1}}%
\regfield{reserved}{7}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_WDT\_PAUSE\_IN\_SLP] Pause RTC WDT in sleep. (R/W)
\item [RTC\_CNTL\_WDT\_APPCPU\_RESET\_EN] RTC WDT reset APP\_CPU enable. (R/W)
\item [RTC\_CNTL\_WDT\_PROCPU\_RESET\_EN] RTC WDT reset PRO\_CPU enable. (R/W)
\item [RTC\_CNTL\_WDT\_FLASHBOOT\_MOD\_EN] Enable RTC WDT in flash boot. (R/W)
\item [RTC\_CNTL\_WDT\_SYS\_RESET\_LENGTH] System reset counter length, unit: RTC\_SLOW\_CLK cycle. The value can be 0 \verb+~+ 7. (R/W)
\item [RTC\_CNTL\_WDT\_CPU\_RESET\_LENGTH] CPU reset counter length, unit: RTC\_SLOW\_CLK cycle. The value can be 0 \verb+~+ 7. (R/W)
\item [RTC\_CNTL\_WDT\_STG3] 1: interrupt stage enable, 2: CPU reset stage enable, 3: system reset stage enable, 4: RTC reset stage enable. (R/W)

\item [RTC\_CNTL\_WDT\_STG2] 1: interrupt stage enable, 2: CPU reset stage enable, 3: system reset stage enable, 4: RTC reset stage enable. (R/W)

\item [RTC\_CNTL\_WDT\_STG1] 1: interrupt stage enable, 2: CPU reset stage enable, 3: system reset stage enable, 4: RTC reset stage enable. (R/W)

\item [RTC\_CNTL\_WDT\_STG0] 1: interrupt stage enable, 2: CPU reset stage enable, 3: system reset stage enable, 4: RTC reset stage enable. (R/W)
\item [RTC\_CNTL\_WDT\_EN] Enable RTC WDT. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTCONFIG\textcolor{red}{\it{n}}\_REG (\textcolor{red}{\it{n}}: 1-4)}{0x008C+4*\textcolor{red}{\it{n}}}\label{regdesc:RTCCNTLWDTCONFIGnREG}
\regfield{}{32}{0}{{0x000000FFF}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_WDTCONFIG\textcolor{red}{\it{n}}\_REG] Hold cycles for WDT stage \textcolor{red}{\it{n}}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTFEED\_REG}{0x00A0}\label{regdesc:RTCCNTLWDTFEEDREG}
\regfield{RTC\_CNTL\_WDT\_FEED}{1}{31}{0}%
\regfield{(reserved)}{31}{0}{0000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_WDT\_FEED]SW feeds WDT. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTWPROTECT\_REG}{0x00A4}\label{regdesc:RTCCNTLWDTWPROTECTREG}
\regfield{}{32}{0}{{0x050D83AA1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_WDTWPROTECT\_REG] If the register contains a different value than 0x50d83aa1, write protection for the RTC watchdog (RWDT) is enabled. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_SW\_CPU\_STALL\_REG}{0x00AC}\label{regdesc:RTCCNTLSWCPUSTALLREG}
\regfield{RTC\_CNTL\_SW\_STALL\_PROCPU\_C1}{6}{26}{000000}%
\regfield{RTC\_CNTL\_SW\_STALL\_APPCPU\_C1}{6}{20}{000000}%
\regfield{(reserved)}{20}{0}{00000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_SW\_STALL\_PROCPU\_C1]{reg\_rtc\_cntl\_sw\_stall\_procpu\_c1[5:0],  reg\_rtc\_cntl\_sw\_stall\_procpu\_c0[1:0]} == 0x86 (100001 10) will stall PRO\_CPU, see also \hyperref[regdesc:RTCCNTLOPTIONS0REG]{RTC\_CNTL\_OPTIONS0\_REG}. (R/W)
\item [RTC\_CNTL\_SW\_STALL\_APPCPU\_C1]{reg\_rtc\_cntl\_sw\_stall\_appcpu\_c1[5:0],  reg\_rtc\_cntl\_sw\_stall\_appcpu\_c0[1:0]} == 0x86 (100001 10) will stall APP\_CPU, see also \hyperref[regdesc:RTCCNTLOPTIONS0REG]{RTC\_CNTL\_OPTIONS0\_REG}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE\textcolor{red}{\it{n}}\_REG (\textcolor{red}{\it{n}}: 4-7)}{0x00B0+4*(\textcolor{red}{\it{n}}-4)}\label{regdesc:RTCCNTLSTORE1nREG}
\regfield{}{32}{0}{xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_STORE\textcolor{red}{\it{n}}\_REG]32-bit general-purpose retention register. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_HOLD\_FORCE\_REG}{0x00C8}\label{regdesc:RTCCNTLHOLDFORCEREG}
\regfield{(reserved)}{14}{18}{00000000000000}%
\regfield{RTC\_CNTL\_X32N\_HOLD\_FORCE}{1}{17}{0}%
\regfield{RTC\_CNTL\_X32P\_HOLD\_FORCE}{1}{16}{0}%
\regfield{RTC\_CNTL\_TOUCH\_PAD7\_HOLD\_FORCE}{1}{15}{0}%
\regfield{RTC\_CNTL\_TOUCH\_PAD6\_HOLD\_FORCE}{1}{14}{0}%
\regfield{RTC\_CNTL\_TOUCH\_PAD5\_HOLD\_FORCE}{1}{13}{0}%
\regfield{RTC\_CNTL\_TOUCH\_PAD4\_HOLD\_FORCE}{1}{12}{0}%
\regfield{RTC\_CNTL\_TOUCH\_PAD3\_HOLD\_FORCE}{1}{11}{0}%
\regfield{RTC\_CNTL\_TOUCH\_PAD2\_HOLD\_FORCE}{1}{10}{0}%
\regfield{RTC\_CNTL\_TOUCH\_PAD1\_HOLD\_FORCE}{1}{9}{0}%
\regfield{RTC\_CNTL\_TOUCH\_PAD0\_HOLD\_FORCE}{1}{8}{0}%
\regfield{RTC\_CNTL\_SENSE4\_HOLD\_FORCE}{1}{7}{0}%
\regfield{RTC\_CNTL\_SENSE3\_HOLD\_FORCE}{1}{6}{0}%
\regfield{RTC\_CNTL\_SENSE2\_HOLD\_FORCE}{1}{5}{0}%
\regfield{RTC\_CNTL\_SENSE1\_HOLD\_FORCE}{1}{4}{0}%
\regfield{RTC\_CNTL\_PDAC2\_HOLD\_FORCE}{1}{3}{0}%
\regfield{RTC\_CNTL\_PDAC1\_HOLD\_FORCE}{1}{2}{0}%
\regfield{RTC\_CNTL\_ADC2\_HOLD\_FORCE}{1}{1}{0}%
\regfield{RTC\_CNTL\_ADC1\_HOLD\_FORCE}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_X32N\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\item [RTC\_CNTL\_X32P\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\item [RTC\_CNTL\_TOUCH\_PAD7\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\item [RTC\_CNTL\_TOUCH\_PAD6\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\item [RTC\_CNTL\_TOUCH\_PAD5\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\item [RTC\_CNTL\_TOUCH\_PAD4\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\item [RTC\_CNTL\_TOUCH\_PAD3\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\item [RTC\_CNTL\_TOUCH\_PAD2\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\item [RTC\_CNTL\_TOUCH\_PAD1\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\item [RTC\_CNTL\_TOUCH\_PAD0\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\item [RTC\_CNTL\_SENSE4\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\item [RTC\_CNTL\_SENSE3\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\item [RTC\_CNTL\_SENSE2\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\item [RTC\_CNTL\_SENSE1\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\item [RTC\_CNTL\_PDAC2\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\item [RTC\_CNTL\_PDAC1\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\item [RTC\_CNTL\_ADC2\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\item [RTC\_CNTL\_ADC1\_HOLD\_FORCE]Set to preserve pad’s state during hibernation. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_EXT\_WAKEUP1\_REG}{0x00CC}\label{regdesc:RTCCNTLEXTWAKEUP1REG}
\regfield{(reserved)}{13}{19}{0000000000000}%
\regfield{RTC\_CNTL\_EXT\_WAKEUP1\_STATUS\_CLR}{1}{18}{0}%
\regfield{RTC\_CNTL\_EXT\_WAKEUP1\_SEL}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_EXT\_WAKEUP1\_STATUS\_CLR]Clear external wakeup1 status. (WO)
\item [RTC\_CNTL\_EXT\_WAKEUP1\_SEL]Bitmap to select RTC pads for external wakeup1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_EXT\_WAKEUP1\_STATUS\_REG}{0x00D0}\label{regdesc:RTCCNTLEXTWAKEUP1STATUSREG}
\regfield{(reserved)}{14}{18}{00000000000000}%
\regfield{RTC\_CNTL\_EXT\_WAKEUP1\_STATUS}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_EXT\_WAKEUP1\_STATUS] EXT1 wakeup source status. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_BROWN\_OUT\_REG}{0x00D4}\label{regdesc:RTCCNTLBROWNOUTREG}
\regfield{RTC\_CNTL\_BROWN\_OUT\_DET}{1}{31}{0}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_ENA}{1}{30}{0}%
\regfield{RTC\_CNTL\_DBROWN\_OUT\_THRES}{3}{27}{{0x2}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_RST\_ENA}{1}{26}{0}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_RST\_WAIT}{10}{16}{{0x3FF}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_PD\_RF\_ENA}{1}{15}{0}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_CLOSE\_FLASH\_ENA}{1}{14}{0}%
\regfield{(reserved)}{14}{0}{00000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [RTC\_CNTL\_BROWN\_OUT\_DET]Brownout detect. (RO)
\item [RTC\_CNTL\_BROWN\_OUT\_ENA]Enables brownout. (R/W)
\item [RTC\_CNTL\_DBROWN\_OUT\_THRES]\label{RTCCNTLDBROWNOUTTHRES}Brownout threshold. The brownout detector will reset the chip when the supply voltage is approximately below this level. Note that there may be some variation of brownout voltage level between each ESP32 chip. 0: 2.43 V ± 0.05; 1: 2.48 V ± 0.05; 2: 2.58 V ± 0.05; 3: 2.62 V ± 0.05; 4: 2.67 V ± 0.05; 5: 2.70 V ± 0.05; 6: 2.77 V ± 0.05; 7: 2.80 V ± 0.05. (R/W)
\item [RTC\_CNTL\_BROWN\_OUT\_RST\_ENA]Enables brownout reset. (R/W)
\item [RTC\_CNTL\_BROWN\_OUT\_RST\_WAIT]Brownout reset wait cycles. (R/W)
\item [RTC\_CNTL\_BROWN\_OUT\_PD\_RF\_ENA]Enables power down RF when brownout happens. (R/W)
\item [RTC\_CNTL\_BROWN\_OUT\_CLOSE\_FLASH\_ENA]\label{RTCCNTLBROWNOUTCLOSEFLASHENA}Sends suspend command to flash when brownout happens. (R/W)
\end{reglist}\end{regdesc}
\end{register}
