\begin{register}{H}{LCD\_CAM\_LCD\_CLOCK\_REG}{0x{}0000}\label{regdesc:LCDCAMLCDCLOCKREG}
\regfield{LCD\_CAM\_CLK\_EN}{1}{31}{{0}}%
\regfield{LCD\_CAM\_LCD\_CLK\_SEL}{2}{29}{{0}}%
\regfield{LCD\_CAM\_LCD\_CLKM\_DIV\_A}{6}{23}{{0x{}0}}%
\regfield{LCD\_CAM\_LCD\_CLKM\_DIV\_B}{6}{17}{{0x{}0}}%
\regfield{LCD\_CAM\_LCD\_CLKM\_DIV\_NUM}{8}{9}{{4}}%
\regfield{LCD\_CAM\_LCD\_CK\_OUT\_EDGE}{1}{8}{{0}}%
\regfield{LCD\_CAM\_LCD\_CK\_IDLE\_EDGE}{1}{7}{{0}}%
\regfield{LCD\_CAM\_LCD\_CLK\_EQU\_SYSCLK}{1}{6}{{1}}%
\regfield{LCD\_CAM\_LCD\_CLKCNT\_N}{6}{0}{{0x{}3}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMLCDCLKCNTN}\item [LCD\_CAM\_LCD\_CLKCNT\_N] f$_{LCD\_PCLK}$
 = f$_{LCD\_CLK}$/(\hyperref[fielddesc:LCDCAMLCDCLKCNTN]{LCD\_CAM\_LCD\_CLKCNT\_N} + 1) when \hyperref[fielddesc:LCDCAMLCDCLKEQUSYSCLK]{LCD\_CAM\_LCD\_CLK\_EQU\_SYSCLK} is 0. Note: this field must not be configured to 0. (R/W)

\label{fielddesc:LCDCAMLCDCLKEQUSYSCLK}\item [LCD\_CAM\_LCD\_CLK\_EQU\_SYSCLK] 1: f$_{LCD\_PCLK}$
= f$_{LCD\_CLK}$. 0: f$_{LCD\_PCLK}$
 = f$_{LCD\_CLK}$/(\hyperref[fielddesc:LCDCAMLCDCLKCNTN]{LCD\_CAM\_LCD\_CLKCNT\_N} + 1). (R/W)

\label{fielddesc:LCDCAMLCDCKIDLEEDGE}\item [LCD\_CAM\_LCD\_CK\_IDLE\_EDGE] 1: LCD\_PCLK line is high in idle. 0: LCD\_PCLK line is low in idle. (R/W)
\label{fielddesc:LCDCAMLCDCKOUTEDGE}\item [LCD\_CAM\_LCD\_CK\_OUT\_EDGE] 1: LCD\_PCLK is high in the first half clock cycle. 0: LCD\_PCLK is low in the first half clock cycle. (R/W)
\label{fielddesc:LCDCAMLCDCLKMDIVNUM}\item [LCD\_CAM\_LCD\_CLKM\_DIV\_NUM] Integral LCD clock divider value. (R/W)
\label{fielddesc:LCDCAMLCDCLKMDIVB}\item [LCD\_CAM\_LCD\_CLKM\_DIV\_B] Fractional clock divider numerator value. (R/W)
\label{fielddesc:LCDCAMLCDCLKMDIVA}\item [LCD\_CAM\_LCD\_CLKM\_DIV\_A] Fractional clock divider denominator value. (R/W)
\label{fielddesc:LCDCAMLCDCLKSEL}\item [LCD\_CAM\_LCD\_CLK\_SEL] Select LCD module source clock. 0: clock source is disabled. 1: XTAL\_CLK. 2: PLL\_D2\_CLK. 3: PLL\_F160M\_CLK. (R/W)
\label{fielddesc:LCDCAMCLKEN}\item [LCD\_CAM\_CLK\_EN] Set this bit to force enable the clock for all configuration registers. Clock gate is not used. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LCD\_CAM\_LCD\_RGB\_YUV\_REG}{0x{}0010}\label{regdesc:LCDCAMLCDRGBYUVREG}
\regfield{LCD\_CAM\_LCD\_CONV\_BYPASS}{1}{31}{{0}}%
\regfield{LCD\_CAM\_LCD\_CONV\_TRANS\_MODE}{1}{30}{{0}}%
\regfield{LCD\_CAM\_LCD\_CONV\_MODE\_8BITS\_ON}{1}{29}{{0}}%
\regfield{LCD\_CAM\_LCD\_CONV\_DATA\_IN\_MODE}{1}{28}{{0}}%
\regfield{LCD\_CAM\_LCD\_CONV\_DATA\_OUT\_MODE}{1}{27}{{0}}%
\regfield{LCD\_CAM\_LCD\_CONV\_PROTOCOL\_MODE}{1}{26}{{0}}%
\regfield{LCD\_CAM\_LCD\_CONV\_YUV\_MODE}{2}{24}{{0}}%
\regfield{LCD\_CAM\_LCD\_CONV\_YUV2YUV\_MODE}{2}{22}{{3}}%
\regfield{(reserved)}{1}{21}{{0}}%
\regfield{LCD\_CAM\_LCD\_CONV\_8BITS\_DATA\_INV}{1}{20}{{0}}%
\regfield{(reserved)}{20}{0}{00000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMLCDCONV8BITSDATAINV}\item [LCD\_CAM\_LCD\_CONV\_8BITS\_DATA\_INV] Swap every two 8-bit input data. 1: Enabled. 0: Disabled. (R/W)
\label{fielddesc:LCDCAMLCDCONVYUV2YUVMODE}\item [LCD\_CAM\_LCD\_CONV\_YUV2YUV\_MODE] In YUV-to-YUV mode, 0: data is converted to YUV422 format. 1: data is converted to YUV420 format. 2: data is converted to YUV411 format. 3: disabled. To enable YUV-to-YUV mode, \hyperref[fielddesc:LCDCAMLCDCONVTRANSMODE]{LCD\_CAM\_LCD\_CONV\_TRANS\_MODE} must be set to 1. (R/W)
\label{fielddesc:LCDCAMLCDCONVYUVMODE}\item [LCD\_CAM\_LCD\_CONV\_YUV\_MODE] In YUV-to-YUV mode and YUV-to-RGB mode, LCD\_CAM\_LCD\_CONV\_YUV\_MODE decides the YUV mode of input data. 0: input data is in YUV422 format. 1: input data is in YUV420 format. 2: input data is in YUV411 format. In RGB-to-YUV mode, 0: data is converted to YUV422 format. 1: data is converted to YUV420 format. 2: data is converted to YUV411 format. (R/W)
\label{fielddesc:LCDCAMLCDCONVPROTOCOLMODE}\item [LCD\_CAM\_LCD\_CONV\_PROTOCOL\_MODE] 0: BT601. 1: BT709. (R/W)
\label{fielddesc:LCDCAMLCDCONVDATAOUTMODE}\item [LCD\_CAM\_LCD\_CONV\_DATA\_OUT\_MODE] Configure color range for output data. 0: limited color range. 1: full color range. (R/W)
\label{fielddesc:LCDCAMLCDCONVDATAINMODE}\item [LCD\_CAM\_LCD\_CONV\_DATA\_IN\_MODE] Configure color range for input data. 0: limited color range. 1: full color range. (R/W)
\label{fielddesc:LCDCAMLCDCONVMODE8BITSON}\item [LCD\_CAM\_LCD\_CONV\_MODE\_8BITS\_ON] 0: 16-bit mode. 1: 8-bit mode. (R/W)
\label{fielddesc:LCDCAMLCDCONVTRANSMODE}\item [LCD\_CAM\_LCD\_CONV\_TRANS\_MODE] 0: converted to RGB format. 1: converted to YUV format. (R/W)
\label{fielddesc:LCDCAMLCDCONVBYPASS}\item [LCD\_CAM\_LCD\_CONV\_BYPASS] 0: Bypass converter. 1: Enable converter. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LCD\_CAM\_LCD\_USER\_REG}{0x{}0014}\label{regdesc:LCDCAMLCDUSERREG}
\regfield{LCD\_CAM\_LCD\_CMD\_2\_CYCLE\_EN}{1}{31}{{0}}%
\regfield{LCD\_CAM\_LCD\_DUMMY\_CYCLELEN}{2}{29}{{0}}%
\regfield{LCD\_CAM\_LCD\_RESET}{1}{28}{{0}}%
\regfield{LCD\_CAM\_LCD\_START}{1}{27}{{0}}%
\regfield{LCD\_CAM\_LCD\_CMD}{1}{26}{{0}}%
\regfield{LCD\_CAM\_LCD\_DUMMY}{1}{25}{{0}}%
\regfield{LCD\_CAM\_LCD\_DOUT}{1}{24}{{0}}%
\regfield{LCD\_CAM\_LCD\_2BYTE\_EN}{1}{23}{{0}}%
\regfield{LCD\_CAM\_LCD\_BYTE\_ORDER}{1}{22}{{0}}%
\regfield{LCD\_CAM\_LCD\_BIT\_ORDER}{1}{21}{{0}}%
\regfield{LCD\_CAM\_LCD\_UPDATE}{1}{20}{{0}}%
\regfield{LCD\_CAM\_LCD\_8BITS\_ORDER}{1}{19}{{0}}%
\regfield{(reserved)}{5}{14}{00000}%
\regfield{LCD\_CAM\_LCD\_ALWAYS\_OUT\_EN}{1}{13}{{0}}%
\regfield{LCD\_CAM\_LCD\_DOUT\_CYCLELEN}{13}{0}{{0x{}01}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMLCDDOUTCYCLELEN}\item [LCD\_CAM\_LCD\_DOUT\_CYCLELEN] Configure the cycles for DOUT phase of LCD module. The cycles =  this value + 1. (R/W)
\label{fielddesc:LCDCAMLCDALWAYSOUTEN}\item [LCD\_CAM\_LCD\_ALWAYS\_OUT\_EN] LCD continues outputting data when LCD is in DOUT phase, till \hyperref[fielddesc:LCDCAMLCDSTART]{LCD\_CAM\_LCD\_START} is cleared or \hyperref[fielddesc:LCDCAMLCDRESET]{LCD\_CAM\_LCD\_RESET} is set. (R/W)
\label{fielddesc:LCDCAMLCD8BITSORDER}\item [LCD\_CAM\_LCD\_8BITS\_ORDER] 1: Swap every two data bytes, valid in 8-bit mode. 0: Do not swap. (R/W)
\label{fielddesc:LCDCAMLCDUPDATE}\item [LCD\_CAM\_LCD\_UPDATE] 1: Update LCD registers. This bit is cleared by hardware. 0: Do not care. (R/W)
\label{fielddesc:LCDCAMLCDBITORDER}\item [LCD\_CAM\_LCD\_BIT\_ORDER] 1: Change data bit order. Change LCD\_DATA\_out[7:0] to LCD\_DATA\_out[0:7] in 8-bit mode, and bits[15:0] to bits[0:15] in 16-bit mode. 0: Do not change. (R/W)
\label{fielddesc:LCDCAMLCDBYTEORDER}\item [LCD\_CAM\_LCD\_BYTE\_ORDER] 1: Invert data byte order, only valid in 16-bit mode. 0: Do not invert. (R/W)
\label{fielddesc:LCDCAMLCD2BYTEEN}\item [LCD\_CAM\_LCD\_2BYTE\_EN] 1: The width of output LCD data is 16 bits. 0: The width of output LCD data is 8 bits. (R/W)
\label{fielddesc:LCDCAMLCDDOUT}\item [LCD\_CAM\_LCD\_DOUT] 1: Be able to send data out in LCD sequence when LCD starts. 0: Disable. (R/W)
\label{fielddesc:LCDCAMLCDDUMMY}\item [LCD\_CAM\_LCD\_DUMMY] 1: Enable DUMMY phase in LCD sequence when LCD starts. 0: Disable. (R/W)
\label{fielddesc:LCDCAMLCDCMD}\item [LCD\_CAM\_LCD\_CMD] 1: Be able to send command in LCD sequence when LCD starts. 0: Disable. (R/W)
\label{fielddesc:LCDCAMLCDSTART}\item [LCD\_CAM\_LCD\_START] LCD starts sending data enable signal, valid in high level. (R/W)
\label{fielddesc:LCDCAMLCDRESET}\item [LCD\_CAM\_LCD\_RESET] Reset LCD module. (WO)
\label{fielddesc:LCDCAMLCDDUMMYCYCLELEN}\item [LCD\_CAM\_LCD\_DUMMY\_CYCLELEN] Configure DUMMY cycles. DUMMY cycles = this value + 1. (R/W)
\label{fielddesc:LCDCAMLCDCMD2CYCLEEN}\item [LCD\_CAM\_LCD\_CMD\_2\_CYCLE\_EN] The cycle length of command phase. 1: 2 cycles. 0: 1 cycle. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LCD\_CAM\_LCD\_MISC\_REG}{0x{}0018}\label{regdesc:LCDCAMLCDMISCREG}
\regfield{LCD\_CAM\_LCD\_CD\_IDLE\_EDGE}{1}{31}{{0}}%
\regfield{LCD\_CAM\_LCD\_CD\_CMD\_SET}{1}{30}{{0}}%
\regfield{LCD\_CAM\_LCD\_CD\_DUMMY\_SET}{1}{29}{{0}}%
\regfield{LCD\_CAM\_LCD\_CD\_DATA\_SET}{1}{28}{{0}}%
\regfield{LCD\_CAM\_LCD\_AFIFO\_RESET}{1}{27}{{0}}%
\regfield{LCD\_CAM\_LCD\_BK\_EN}{1}{26}{{0}}%
\regfield{LCD\_CAM\_LCD\_NEXT\_FRAME\_EN}{1}{25}{{0}}%
\regfield{LCD\_CAM\_LCD\_VBK\_CYCLELEN}{13}{12}{{0x{}00}}%
\regfield{LCD\_CAM\_LCD\_VFK\_CYCLELEN}{6}{6}{{0x{}3}}%
\regfield{LCD\_CAM\_LCD\_AFIFO\_THRESHOLD\_NUM}{5}{1}{{11}}%
\regfield{(reserved)}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMLCDAFIFOTHRESHOLDNUM}\item [LCD\_CAM\_LCD\_AFIFO\_THRESHOLD\_NUM] Set the threshold for Async Tx FIFO full event. (R/W)
\label{fielddesc:LCDCAMLCDVFKCYCLELEN}\item [LCD\_CAM\_LCD\_VFK\_CYCLELEN] Configure the setup cycles in LCD non-RGB mode. Setup cycles expected = this value + 1. (R/W)
\label{fielddesc:LCDCAMLCDVBKCYCLELEN}\item [LCD\_CAM\_LCD\_VBK\_CYCLELEN] Configure the hold time cycles in LCD non-RGB mode. Hold cycles expected = this value + 1. (R/W)
\label{fielddesc:LCDCAMLCDNEXTFRAMEEN}\item [LCD\_CAM\_LCD\_NEXT\_FRAME\_EN] 1: Send the next frame data when the current frame is sent out. 0: LCD stops when the current frame is sent out. (R/W)
\label{fielddesc:LCDCAMLCDBKEN}\item [LCD\_CAM\_LCD\_BK\_EN] 1: Enable blank region when LCD sends data out. 0: No blank region. (R/W)
\label{fielddesc:LCDCAMLCDAFIFORESET}\item [LCD\_CAM\_LCD\_AFIFO\_RESET] Async Tx FIFO reset signal. (WO)
\label{fielddesc:LCDCAMLCDCDDATASET}\item [LCD\_CAM\_LCD\_CD\_DATA\_SET] 1: LCD\_CD = !\hyperref[fielddesc:LCDCAMLCDCDIDLEEDGE]{LCD\_CAM\_LCD\_CD\_IDLE\_EDGE} when LCD is in DOUT phase. 0: LCD\_CD = \hyperref[fielddesc:LCDCAMLCDCDIDLEEDGE]{LCD\_CAM\_LCD\_CD\_IDLE\_EDGE}. (R/W)
\label{fielddesc:LCDCAMLCDCDDUMMYSET}\item [LCD\_CAM\_LCD\_CD\_DUMMY\_SET] 1: LCD\_CD = !\hyperref[fielddesc:LCDCAMLCDCDIDLEEDGE]{LCD\_CAM\_LCD\_CD\_IDLE\_EDGE} when LCD is in DUMMY phase. 0: LCD\_CD = \hyperref[fielddesc:LCDCAMLCDCDIDLEEDGE]{LCD\_CAM\_LCD\_CD\_IDLE\_EDGE}. (R/W)
\label{fielddesc:LCDCAMLCDCDCMDSET}\item [LCD\_CAM\_LCD\_CD\_CMD\_SET] 1: LCD\_CD = !\hyperref[fielddesc:LCDCAMLCDCDIDLEEDGE]{LCD\_CAM\_LCD\_CD\_IDLE\_EDGE} when LCD is in CMD phase. 0: LCD\_CD = \hyperref[fielddesc:LCDCAMLCDCDIDLEEDGE]{LCD\_CAM\_LCD\_CD\_IDLE\_EDGE}. (R/W)
\label{fielddesc:LCDCAMLCDCDIDLEEDGE}\item [LCD\_CAM\_LCD\_CD\_IDLE\_EDGE] The default value of LCD\_CD. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LCD\_CAM\_LCD\_CTRL\_REG}{0x{}001C}\label{regdesc:LCDCAMLCDCTRLREG}
\regfield{LCD\_CAM\_LCD\_RGB\_MODE\_EN}{1}{31}{{0}}%
\regfield{LCD\_CAM\_LCD\_VT\_HEIGHT}{10}{21}{{0}}%
\regfield{LCD\_CAM\_LCD\_VA\_HEIGHT}{10}{11}{{0}}%
\regfield{LCD\_CAM\_LCD\_HB\_FRONT}{11}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMLCDHBFRONT}\item [LCD\_CAM\_LCD\_HB\_FRONT] Configures the value of (\hyperref[fielddesc:LCDCAMLCDHSYNCPOSITION]{HSYNC\_POSITION} + \hyperref[fielddesc:LCDCAMLCDHSYNCWIDTH]{HSYNC\_WIDTH} + horizontal back porch). (R/W)
\label{fielddesc:LCDCAMLCDVAHEIGHT}\item [LCD\_CAM\_LCD\_VA\_HEIGHT] It is the vertical active height of a frame. (R/W)
\label{fielddesc:LCDCAMLCDVTHEIGHT}\item [LCD\_CAM\_LCD\_VT\_HEIGHT] It is the vertical total height of a frame. (R/W)
\label{fielddesc:LCDCAMLCDRGBMODEEN}\item [LCD\_CAM\_LCD\_RGB\_MODE\_EN] 1: Enable RGB mode, and input VSYNC, HSYNC, and DE signals. 0: Disable. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LCD\_CAM\_LCD\_CTRL1\_REG}{0x{}0020}\label{regdesc:LCDCAMLCDCTRL1REG}
\regfield{LCD\_CAM\_LCD\_HT\_WIDTH}{12}{20}{{0}}%
\regfield{LCD\_CAM\_LCD\_HA\_WIDTH}{12}{8}{{0}}%
\regfield{LCD\_CAM\_LCD\_VB\_FRONT}{8}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMLCDVBFRONT}\item [LCD\_CAM\_LCD\_VB\_FRONT] Configures the value of (\hyperref[fielddesc:LCDCAMLCDVSYNCWIDTH]{VSYNC\_WIDTH} + vertical back porch). (R/W)
\label{fielddesc:LCDCAMLCDHAWIDTH}\item [LCD\_CAM\_LCD\_HA\_WIDTH] It is the horizontal active width of a frame. (R/W)
\label{fielddesc:LCDCAMLCDHTWIDTH}\item [LCD\_CAM\_LCD\_HT\_WIDTH] It is the horizontal total width of a frame. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LCD\_CAM\_LCD\_CTRL2\_REG}{0x{}0024}\label{regdesc:LCDCAMLCDCTRL2REG}
\regfield{LCD\_CAM\_LCD\_HSYNC\_POSITION}{8}{24}{{0}}%
\regfield{LCD\_CAM\_LCD\_HSYNC\_IDLE\_POL}{1}{23}{{0}}%
\regfield{LCD\_CAM\_LCD\_HSYNC\_WIDTH}{7}{16}{{1}}%
\regfield{(reserved)}{6}{10}{000000}%
\regfield{LCD\_CAM\_LCD\_HS\_BLANK\_EN}{1}{9}{{0}}%
\regfield{LCD\_CAM\_LCD\_DE\_IDLE\_POL}{1}{8}{{0}}%
\regfield{LCD\_CAM\_LCD\_VSYNC\_IDLE\_POL}{1}{7}{{0}}%
\regfield{LCD\_CAM\_LCD\_VSYNC\_WIDTH}{7}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMLCDVSYNCWIDTH}\item [LCD\_CAM\_LCD\_VSYNC\_WIDTH] It is the width of LCD\_VSYNC active pulse in a line. (R/W)
\label{fielddesc:LCDCAMLCDVSYNCIDLEPOL}\item [LCD\_CAM\_LCD\_VSYNC\_IDLE\_POL] It is the idle value of LCD\_VSYNC. (R/W)
\label{fielddesc:LCDCAMLCDDEIDLEPOL}\item [LCD\_CAM\_LCD\_DE\_IDLE\_POL] It is the idle value of LCD\_DE. (R/W)
\label{fielddesc:LCDCAMLCDHSBLANKEN}\item [LCD\_CAM\_LCD\_HS\_BLANK\_EN] 1: The pulse of LCD\_HSYNC is out in vertical blanking lines in RGB mode. 0: LCD\_HSYNC pulse is valid only in active region lines in RGB mode. (R/W)
\label{fielddesc:LCDCAMLCDHSYNCWIDTH}\item [LCD\_CAM\_LCD\_HSYNC\_WIDTH] Configures the width of LCD\_HSYNC active pulse. Expected width = this value +1. (R/W)
\label{fielddesc:LCDCAMLCDHSYNCIDLEPOL}\item [LCD\_CAM\_LCD\_HSYNC\_IDLE\_POL] It is the idle value of LCD\_HSYNC. (R/W)
\label{fielddesc:LCDCAMLCDHSYNCPOSITION}\item [LCD\_CAM\_LCD\_HSYNC\_POSITION] Configures the position of LCD\_HSYNC active pulse. Expected position = this value + 1. Unit is a pixel. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LCD\_CAM\_LCD\_CMD\_VAL\_REG}{0x{}0028}\label{regdesc:LCDCAMLCDCMDVALREG}
\regfield{LCD\_CAM\_LCD\_CMD\_VALUE}{32}{0}{{0x{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMLCDCMDVALUE}\item [LCD\_CAM\_LCD\_CMD\_VALUE] The LCD write command value. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LCD\_CAM\_LCD\_DLY\_MODE\_REG}{0x{}0030}\label{regdesc:LCDCAMLCDDLYMODEREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{LCD\_CAM\_LCD\_VSYNC\_MODE}{2}{6}{{0x{}0}}%
\regfield{LCD\_CAM\_LCD\_HSYNC\_MODE}{2}{4}{{0x{}0}}%
\regfield{LCD\_CAM\_LCD\_DE\_MODE}{2}{2}{{0x{}0}}%
\regfield{LCD\_CAM\_LCD\_CD\_MODE}{2}{0}{{0x{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMLCDCDMODE}\item [LCD\_CAM\_LCD\_CD\_MODE] The output LCD\_CD is delayed by module clock LCD\_CLK. 0: output without delay. 1: delayed by the rising edge of LCD\_CLK. 2: delayed by the falling edge of LCD\_CLK. (R/W)
\label{fielddesc:LCDCAMLCDDEMODE}\item [LCD\_CAM\_LCD\_DE\_MODE] The output LCD\_DE is delayed by module clock LCD\_CLK. 0: output without delay. 1: delayed by the rising edge of LCD\_CLK. 2: delayed by the falling edge of LCD\_CLK. (R/W)
\label{fielddesc:LCDCAMLCDHSYNCMODE}\item [LCD\_CAM\_LCD\_HSYNC\_MODE] The output LCD\_HSYNC is delayed by module clock LCD\_CLK. 0: output without delay. 1: delayed by the rising edge of LCD\_CLK. 2: delayed by the falling edge of LCD\_CLK. (R/W)
\label{fielddesc:LCDCAMLCDVSYNCMODE}\item [LCD\_CAM\_LCD\_VSYNC\_MODE] The output LCD\_VSYNC is delayed by module clock LCD\_CLK. 0: output without delay. 1: delayed by the rising edge of LCD\_CLK. 2: delay by the falling edge of LCD\_CLK. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LCD\_CAM\_LCD\_DATA\_DOUT\_MODE\_REG}{0x{}0038}\label{regdesc:LCDCAMLCDDATADOUTMODEREG}
\regfield{LCD\_CAM\_DOUT15\_MODE}{2}{30}{{0x{}0}}%
\regfield{LCD\_CAM\_DOUT14\_MODE}{2}{28}{{0x{}0}}%
\regfield{LCD\_CAM\_DOUT13\_MODE}{2}{26}{{0x{}0}}%
\regfield{LCD\_CAM\_DOUT12\_MODE}{2}{24}{{0x{}0}}%
\regfield{LCD\_CAM\_DOUT11\_MODE}{2}{22}{{0x{}0}}%
\regfield{LCD\_CAM\_DOUT10\_MODE}{2}{20}{{0x{}0}}%
\regfield{LCD\_CAM\_DOUT9\_MODE}{2}{18}{{0x{}0}}%
\regfield{LCD\_CAM\_DOUT8\_MODE}{2}{16}{{0x{}0}}%
\regfield{LCD\_CAM\_DOUT7\_MODE}{2}{14}{{0x{}0}}%
\regfield{LCD\_CAM\_DOUT6\_MODE}{2}{12}{{0x{}0}}%
\regfield{LCD\_CAM\_DOUT5\_MODE}{2}{10}{{0x{}0}}%
\regfield{LCD\_CAM\_DOUT4\_MODE}{2}{8}{{0x{}0}}%
\regfield{LCD\_CAM\_DOUT3\_MODE}{2}{6}{{0x{}0}}%
\regfield{LCD\_CAM\_DOUT2\_MODE}{2}{4}{{0x{}0}}%
\regfield{LCD\_CAM\_DOUT1\_MODE}{2}{2}{{0x{}0}}%
\regfield{LCD\_CAM\_DOUT0\_MODE}{2}{0}{{0x{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMDOUT0MODE}\item [LCD\_CAM\_DOUT\regindex{n}\_MODE (\regindex{n} = 0 - 15)] The output data bit \regindex{n} is delayed by module clock LCD\_CLK. 0: output without delay. 1: delayed by the rising edge of LCD\_CLK. 2: delayed by the falling edge of LCD\_CLK. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LCD\_CAM\_CAM\_CTRL\_REG}{0x{}0004}\label{regdesc:LCDCAMCAMCTRLREG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{LCD\_CAM\_CAM\_CLK\_SEL}{2}{29}{{0}}%
\regfield{LCD\_CAM\_CAM\_CLKM\_DIV\_A}{6}{23}{{0x{}0}}%
\regfield{LCD\_CAM\_CAM\_CLKM\_DIV\_B}{6}{17}{{0x{}0}}%
\regfield{LCD\_CAM\_CAM\_CLKM\_DIV\_NUM}{8}{9}{{4}}%
\regfield{LCD\_CAM\_CAM\_VS\_EOF\_EN}{1}{8}{{0}}%
\regfield{LCD\_CAM\_CAM\_LINE\_INT\_EN}{1}{7}{{0}}%
\regfield{LCD\_CAM\_CAM\_BIT\_ORDER}{1}{6}{{0}}%
\regfield{LCD\_CAM\_CAM\_BYTE\_ORDER}{1}{5}{{0}}%
\regfield{LCD\_CAM\_CAM\_UPDATE}{1}{4}{{0}}%
\regfield{LCD\_CAM\_CAM\_VSYNC\_FILTER\_THRES}{3}{1}{{0x{}0}}%
\regfield{LCD\_CAM\_CAM\_STOP\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMCAMSTOPEN}\item [LCD\_CAM\_CAM\_STOP\_EN] Camera stop enable signal, 1: camera stops when GDMA Rx FIFO is full. 0: Do not stop. (R/W)
\label{fielddesc:LCDCAMCAMVSYNCFILTERTHRES}\item [LCD\_CAM\_CAM\_VSYNC\_FILTER\_THRES] Filter threshold value for CAM\_VSYNC signal. (R/W)
\label{fielddesc:LCDCAMCAMUPDATE}\item [LCD\_CAM\_CAM\_UPDATE] 1: Update camera registers. This bit is cleared by hardware. 0: Do not care. (R/W)
\label{fielddesc:LCDCAMCAMBYTEORDER}\item [LCD\_CAM\_CAM\_BYTE\_ORDER] 1: Invert data byte order, only valid in 16-bit mode. 0: Do not change. (R/W)
\label{fielddesc:LCDCAMCAMBITORDER}\item [LCD\_CAM\_CAM\_BIT\_ORDER] 1: Change data bit order, change CAM\_DATA\_in[7:0] to CAM\_DATA\_in[0:7] in 8-bit mode, and bits[15:0] to bits[0:15] in 16-bit mode.  0: Do not change. (R/W)
\label{fielddesc:LCDCAMCAMLINEINTEN}\item [LCD\_CAM\_CAM\_LINE\_INT\_EN] 1: Enable to generate \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_CAM\_HS\_INT}. 0: Disable. (R/W)
\label{fielddesc:LCDCAMCAMVSEOFEN}\item [LCD\_CAM\_CAM\_VS\_EOF\_EN] 1: Enable CAM\_VSYNC to generate in\_suc\_eof. 0: in\_suc\_eof is controlled by \hyperref[fielddesc:LCDCAMCAMRECDATABYTELEN]{LCD\_CAM\_CAM\_REC\_DATA\_BYTELEN}. (R/W)
\label{fielddesc:LCDCAMCAMCLKMDIVNUM}\item [LCD\_CAM\_CAM\_CLKM\_DIV\_NUM] Integral camera clock divider value. (R/W)
\label{fielddesc:LCDCAMCAMCLKMDIVB}\item [LCD\_CAM\_CAM\_CLKM\_DIV\_B] Fractional clock divider numerator value. (R/W)
\label{fielddesc:LCDCAMCAMCLKMDIVA}\item [LCD\_CAM\_CAM\_CLKM\_DIV\_A] Fractional clock divider denominator value. (R/W)
\label{fielddesc:LCDCAMCAMCLKSEL}\item [LCD\_CAM\_CAM\_CLK\_SEL] Select camera module source clock. 0: Clock source is disabled. 1: XTAL\_CLK. 2: PLL\_D2\_CLK. 3: PLL\_F160M\_CLK. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LCD\_CAM\_CAM\_CTRL1\_REG}{0x{}0008}\label{regdesc:LCDCAMCAMCTRL1REG}
\regfield{LCD\_CAM\_CAM\_AFIFO\_RESET}{1}{31}{{0}}%
\regfield{LCD\_CAM\_CAM\_RESET}{1}{30}{{0}}%
\regfield{LCD\_CAM\_CAM\_START}{1}{29}{{0}}%
\regfield{LCD\_CAM\_CAM\_VH\_DE\_MODE\_EN}{1}{28}{{0}}%
\regfield{LCD\_CAM\_CAM\_VSYNC\_INV}{1}{27}{{0}}%
\regfield{LCD\_CAM\_CAM\_HSYNC\_INV}{1}{26}{{0}}%
\regfield{LCD\_CAM\_CAM\_DE\_INV}{1}{25}{{0}}%
\regfield{LCD\_CAM\_CAM\_2BYTE\_EN}{1}{24}{{0}}%
\regfield{LCD\_CAM\_CAM\_VSYNC\_FILTER\_EN}{1}{23}{{0}}%
\regfield{LCD\_CAM\_CAM\_CLK\_INV}{1}{22}{{0}}%
\regfield{LCD\_CAM\_CAM\_LINE\_INT\_NUM}{6}{16}{{0x{}0}}%
\regfield{LCD\_CAM\_CAM\_REC\_DATA\_BYTELEN}{16}{0}{{0x{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMCAMRECDATABYTELEN}\item [LCD\_CAM\_CAM\_REC\_DATA\_BYTELEN] Configure camera received data byte length. When the length of received data reaches this value + 1, GDMA in\_suc\_eof\_int is triggered. (R/W)
\label{fielddesc:LCDCAMCAMLINEINTNUM}\item [LCD\_CAM\_CAM\_LINE\_INT\_NUM] Configure line number. When the number of received lines reaches this value + 1, \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_CAM\_HS\_INT} is triggered. (R/W)
\label{fielddesc:LCDCAMCAMCLKINV}\item [LCD\_CAM\_CAM\_CLK\_INV] 1: Invert the input signal CAM\_PCLK. 0: Do not invert. (R/W)
\label{fielddesc:LCDCAMCAMVSYNCFILTEREN}\item [LCD\_CAM\_CAM\_VSYNC\_FILTER\_EN] 1: Enable CAM\_VSYNC filter function. 0: Bypass. (R/W)
\label{fielddesc:LCDCAMCAM2BYTEEN}\item [LCD\_CAM\_CAM\_2BYTE\_EN] 1: The width of input data is 16 bits. 0: The width of input data is 8 bits. (R/W)
\label{fielddesc:LCDCAMCAMDEINV}\item [LCD\_CAM\_CAM\_DE\_INV] CAM\_DE invert enable signal, valid in high level. (R/W)
\label{fielddesc:LCDCAMCAMHSYNCINV}\item [LCD\_CAM\_CAM\_HSYNC\_INV] CAM\_HSYNC invert enable signal, valid in high level. (R/W)
\label{fielddesc:LCDCAMCAMVSYNCINV}\item [LCD\_CAM\_CAM\_VSYNC\_INV] CAM\_VSYNC invert enable signal, valid in high level. (R/W)
\label{fielddesc:LCDCAMCAMVHDEMODEEN}\item [LCD\_CAM\_CAM\_VH\_DE\_MODE\_EN] 1: Input control signals are CAM\_DE and CAM\_HSYNC. CAM\_VSYNC is 1. 0: Input control signals are CAM\_DE and CAM\_VSYNC. CAM\_HSYNC and CAM\_DE are all 1 at the the same time. (R/W)
\label{fielddesc:LCDCAMCAMSTART}\item [LCD\_CAM\_CAM\_START] Camera module start signal. (R/W)
\label{fielddesc:LCDCAMCAMRESET}\item [LCD\_CAM\_CAM\_RESET] Camera module reset signal. (WO)
\label{fielddesc:LCDCAMCAMAFIFORESET}\item [LCD\_CAM\_CAM\_AFIFO\_RESET] Camera Async Rx FIFO reset signal. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LCD\_CAM\_CAM\_RGB\_YUV\_REG}{0x{}000C}\label{regdesc:LCDCAMCAMRGBYUVREG}
\regfield{LCD\_CAM\_CAM\_CONV\_BYPASS}{1}{31}{{0}}%
\regfield{LCD\_CAM\_CAM\_CONV\_TRANS\_MODE}{1}{30}{{0}}%
\regfield{LCD\_CAM\_CAM\_CONV\_MODE\_8BITS\_ON}{1}{29}{{0}}%
\regfield{LCD\_CAM\_CAM\_CONV\_DATA\_IN\_MODE}{1}{28}{{0}}%
\regfield{LCD\_CAM\_CAM\_CONV\_DATA\_OUT\_MODE}{1}{27}{{0}}%
\regfield{LCD\_CAM\_CAM\_CONV\_PROTOCOL\_MODE}{1}{26}{{0}}%
\regfield{LCD\_CAM\_CAM\_CONV\_YUV\_MODE}{2}{24}{{0}}%
\regfield{LCD\_CAM\_CAM\_CONV\_YUV2YUV\_MODE}{2}{22}{{3}}%
\regfield{LCD\_CAM\_CAM\_CONV\_8BITS\_DATA\_INV}{1}{21}{{0}}%
\regfield{(reserved)}{21}{0}{000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMCAMCONV8BITSDATAINV}\item [LCD\_CAM\_CAM\_CONV\_8BITS\_DATA\_INV] Swap every two 8-bit input data. 1: Enabled. 0: Disabled. (R/W)
\label{fielddesc:LCDCAMCAMCONVYUV2YUVMODE}\item [LCD\_CAM\_CAM\_CONV\_YUV2YUV\_MODE] In YUV-to-YUV mode, 0: data is converted to YUV422 format. 1: data is converted to YUV420 format. 2: data is converted to YUV411 format. 3: disabled. To enable YUV-to-YUV mode, \hyperref[fielddesc:LCDCAMCAMCONVTRANSMODE]{LCD\_CAM\_CAM\_CONV\_TRANS\_MODE} must be set to 1. (R/W)
\label{fielddesc:LCDCAMCAMCONVYUVMODE}\item [LCD\_CAM\_CAM\_CONV\_YUV\_MODE] In YUV-to-YUV mode and YUV-to-RGB mode, LCD\_CAM\_CAM\_CONV\_YUV\_MODE decides the YUV mode of input data. 0: input data is in YUV422 format. 1: input data is in YUV420 format. 2: input data is in YUV411 format. In RGB-to-YUV mode, 0: data is converted to YUV422 format. 1: data is converted to YUV420 format. 2: data is converted to YUV411 format. (R/W)
\label{fielddesc:LCDCAMCAMCONVPROTOCOLMODE}\item [LCD\_CAM\_CAM\_CONV\_PROTOCOL\_MODE] 0: BT601. 1: BT709. (R/W)
\label{fielddesc:LCDCAMCAMCONVDATAOUTMODE}\item [LCD\_CAM\_CAM\_CONV\_DATA\_OUT\_MODE] Configure color range for output data. 0: limited color range. 1: full color range.  (R/W)
\label{fielddesc:LCDCAMCAMCONVDATAINMODE}\item [LCD\_CAM\_CAM\_CONV\_DATA\_IN\_MODE] Configure color range for input data. 0: limited color range. 1: full color range.  (R/W)
\label{fielddesc:LCDCAMCAMCONVMODE8BITSON}\item [LCD\_CAM\_CAM\_CONV\_MODE\_8BITS\_ON] 0: 16-bit mode. 1: 8-bit mode. (R/W)
\label{fielddesc:LCDCAMCAMCONVTRANSMODE}\item [LCD\_CAM\_CAM\_CONV\_TRANS\_MODE] 0: converted to RGB format. 1: converted to YUV format. (R/W)
\label{fielddesc:LCDCAMCAMCONVBYPASS}\item [LCD\_CAM\_CAM\_CONV\_BYPASS] 0: Bypass converter. 1: Enable converter. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LCD\_CAM\_LC\_DMA\_INT\_ENA\_REG}{0x{}0064}\label{regdesc:LCDCAMLCDMAINTENAREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{LCD\_CAM\_CAM\_HS\_INT\_ENA}{1}{3}{{0}}%
\regfield{LCD\_CAM\_CAM\_VSYNC\_INT\_ENA}{1}{2}{{0}}%
\regfield{LCD\_CAM\_LCD\_TRANS\_DONE\_INT\_ENA}{1}{1}{{0}}%
\regfield{LCD\_CAM\_LCD\_VSYNC\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMLCDVSYNCINTENA}\item [LCD\_CAM\_LCD\_VSYNC\_INT\_ENA] The enable bit for \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_LCD\_VSYNC\_INT} interrupt. (R/W)
\label{fielddesc:LCDCAMLCDTRANSDONEINTENA}\item [LCD\_CAM\_LCD\_TRANS\_DONE\_INT\_ENA] The enable bit for \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_LCD\_TRANS\_DONE\_INT} interrupt. (R/W)
\label{fielddesc:LCDCAMCAMVSYNCINTENA}\item [LCD\_CAM\_CAM\_VSYNC\_INT\_ENA] The enable bit for \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_CAM\_VSYNC\_INT} interrupt. (R/W)
\label{fielddesc:LCDCAMCAMHSINTENA}\item [LCD\_CAM\_CAM\_HS\_INT\_ENA] The enable bit for \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_CAM\_HS\_INT} interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LCD\_CAM\_LC\_DMA\_INT\_RAW\_REG}{0x{}0068}\label{regdesc:LCDCAMLCDMAINTRAWREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{LCD\_CAM\_CAM\_HS\_INT\_RAW}{1}{3}{{0}}%
\regfield{LCD\_CAM\_CAM\_VSYNC\_INT\_RAW}{1}{2}{{0}}%
\regfield{LCD\_CAM\_LCD\_TRANS\_DONE\_INT\_RAW}{1}{1}{{0}}%
\regfield{LCD\_CAM\_LCD\_VSYNC\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMLCDVSYNCINTRAW}\item [LCD\_CAM\_LCD\_VSYNC\_INT\_RAW] The raw bit for \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_LCD\_VSYNC\_INT} interrupt. (RO)
\label{fielddesc:LCDCAMLCDTRANSDONEINTRAW}\item [LCD\_CAM\_LCD\_TRANS\_DONE\_INT\_RAW] The raw bit for \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_LCD\_TRANS\_DONE\_INT} interrupt. (RO)
\label{fielddesc:LCDCAMCAMVSYNCINTRAW}\item [LCD\_CAM\_CAM\_VSYNC\_INT\_RAW] The raw bit for \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_CAM\_VSYNC\_INT} interrupt. (RO)
\label{fielddesc:LCDCAMCAMHSINTRAW}\item [LCD\_CAM\_CAM\_HS\_INT\_RAW] The raw bit for \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_CAM\_HS\_INT} interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LCD\_CAM\_LC\_DMA\_INT\_ST\_REG}{0x{}006C}\label{regdesc:LCDCAMLCDMAINTSTREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{LCD\_CAM\_CAM\_HS\_INT\_ST}{1}{3}{{0}}%
\regfield{LCD\_CAM\_CAM\_VSYNC\_INT\_ST}{1}{2}{{0}}%
\regfield{LCD\_CAM\_LCD\_TRANS\_DONE\_INT\_ST}{1}{1}{{0}}%
\regfield{LCD\_CAM\_LCD\_VSYNC\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMLCDVSYNCINTST}\item [LCD\_CAM\_LCD\_VSYNC\_INT\_ST] The status bit for \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_LCD\_VSYNC\_INT} interrupt. (RO)
\label{fielddesc:LCDCAMLCDTRANSDONEINTST}\item [LCD\_CAM\_LCD\_TRANS\_DONE\_INT\_ST] The status bit for \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_LCD\_TRANS\_DONE\_INT} interrupt. (RO)
\label{fielddesc:LCDCAMCAMVSYNCINTST}\item [LCD\_CAM\_CAM\_VSYNC\_INT\_ST] The status bit for \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_CAM\_VSYNC\_INT} interrupt. (RO)
\label{fielddesc:LCDCAMCAMHSINTST}\item [LCD\_CAM\_CAM\_HS\_INT\_ST] The status bit for \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_CAM\_HS\_INT} interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LCD\_CAM\_LC\_DMA\_INT\_CLR\_REG}{0x{}0070}\label{regdesc:LCDCAMLCDMAINTCLRREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{LCD\_CAM\_CAM\_HS\_INT\_CLR}{1}{3}{{0}}%
\regfield{LCD\_CAM\_CAM\_VSYNC\_INT\_CLR}{1}{2}{{0}}%
\regfield{LCD\_CAM\_LCD\_TRANS\_DONE\_INT\_CLR}{1}{1}{{0}}%
\regfield{LCD\_CAM\_LCD\_VSYNC\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMLCDVSYNCINTCLR}\item [LCD\_CAM\_LCD\_VSYNC\_INT\_CLR] The clear bit for \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_LCD\_VSYNC\_INT} interrupt. (WO)
\label{fielddesc:LCDCAMLCDTRANSDONEINTCLR}\item [LCD\_CAM\_LCD\_TRANS\_DONE\_INT\_CLR] The clear bit for \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_LCD\_TRANS\_DONE\_INT} interrupt. (WO)
\label{fielddesc:LCDCAMCAMVSYNCINTCLR}\item [LCD\_CAM\_CAM\_VSYNC\_INT\_CLR] The clear bit for \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_CAM\_VSYNC\_INT} interrupt. (WO)
\label{fielddesc:LCDCAMCAMHSINTCLR}\item [LCD\_CAM\_CAM\_HS\_INT\_CLR] The clear bit for \hyperref[int:LCDCAMCAMHSINT]{LCD\_CAM\_CAM\_HS\_INT} interrupt. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{LCD\_CAM\_LC\_REG\_DATE\_REG}{0x{}00FC}\label{regdesc:LCDCAMLCREGDATEREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{LCD\_CAM\_LC\_DATE}{28}{0}{{0x{}2003020}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:LCDCAMLCDATE}\item [LCD\_CAM\_LC\_DATE] Version control register (R/W)
\end{reglist}\end{regdesc}
\end{register}


