\begin{register}{H}{PCNT\_U\textit{\textcolor{red}{\it{n}}}\_CONF0\_REG (\textcolor{red}{\it{n}}: 0-7)}{0x0+0x0C*\textcolor{red}{\it{n}}}\label{regdesc:PCNTUnCONF0REG}
\regfield{PCNT\_CH1\_LCTRL\_MODE\_U\textcolor{red}{\it{n}}}{2}{30}{{0}}%
\regfield{PCNT\_CH1\_HCTRL\_MODE\_U\textcolor{red}{\it{n}}}{2}{28}{{0}}%
\regfield{PCNT\_CH1\_POS\_MODE\_U\textcolor{red}{\it{n}}}{2}{26}{{0}}%
\regfield{PCNT\_CH1\_NEG\_MODE\_U\textcolor{red}{\it{n}}}{2}{24}{{0}}%
\regfield{PCNT\_CH0\_LCTRL\_MODE\_U\textcolor{red}{\it{n}}}{2}{22}{{0}}%
\regfield{PCNT\_CH0\_HCTRL\_MODE\_U\textcolor{red}{\it{n}}}{2}{20}{{0}}%
\regfield{PCNT\_CH0\_POS\_MODE\_U\textcolor{red}{\it{n}}}{2}{18}{{0}}%
\regfield{PCNT\_CH0\_NEG\_MODE\_U\textcolor{red}{\it{n}}}{2}{16}{{0}}%
\regfield{PCNT\_THR\_THRES1\_EN\_U\textcolor{red}{\it{n}}}{1}{15}{0}%
\regfield{PCNT\_THR\_THRES0\_EN\_U\textcolor{red}{\it{n}}}{1}{14}{0}%
\regfield{PCNT\_THR\_L\_LIM\_EN\_U\textcolor{red}{\it{n}}}{1}{13}{1}%
\regfield{PCNT\_THR\_H\_LIM\_EN\_U\textcolor{red}{\it{n}}}{1}{12}{1}%
\regfield{PCNT\_THR\_ZERO\_EN\_U\textcolor{red}{\it{n}}}{1}{11}{1}%
\regfield{PCNT\_FILTER\_EN\_U\textcolor{red}{\it{n}}}{1}{10}{1}%
\regfield{PCNT\_FILTER\_THRES\_U\textcolor{red}{\it{n}}}{10}{0}{{0x010}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [PCNT\_CH1\_LCTRL\_MODE\_U\textcolor{red}{\it{n}}]This register configures how the CH1\_POS\_MODE/CH1\_NEG\_MODE settings will be modified when the control signal is low. (R/W) 0: No modification; 1: Invert behaviour (increase ->  decrease, decrease ->  increase); 2, 3: Inhibit counter modification
\item [PCNT\_CH1\_HCTRL\_MODE\_U\textcolor{red}{\it{n}}]This register configures how the CH1\_POS\_MODE/CH1\_NEG\_MODE settings will be modified when the control signal is high. (R/W) 0: No modification; 1: Invert behaviour (increase ->  decrease, decrease ->  increase); 2, 3: Inhibit counter modification
\item [PCNT\_CH1\_POS\_MODE\_U\textcolor{red}{\it{n}}]This register sets the behaviour when the signal input of channel 1 detects a positive edge. (R/W) 1: Increment the counter; 2: Decrement the counter; 0, 3: No effect on counter
\item [PCNT\_CH1\_NEG\_MODE\_U\textcolor{red}{\it{n}}]This register sets the behaviour when the signal input of channel 1 detects a negative edge. (R/W) 1: Increment the counter; 2: Decrement the counter; 0, 3: No effect on counter
\item [PCNT\_CH0\_LCTRL\_MODE\_U\textcolor{red}{\it{n}}]This register configures how the CH0\_POS\_MODE/CH0\_NEG\_MODE settings will be modified when the control signal is low. (R/W) 0: No modification; 1: Invert behaviour (increase ->  decrease, decrease ->  increase); 2, 3: Inhibit counter modification
\item [PCNT\_CH0\_HCTRL\_MODE\_U\textcolor{red}{\it{n}}]This register configures how the CH0\_POS\_MODE/CH0\_NEG\_MODE settings will be modified when the control signal is high. (R/W) 0: No modification; 1: Invert behaviour (increase ->  decrease, decrease ->  increase); 2, 3: Inhibit counter modification
\item [PCNT\_CH0\_POS\_MODE\_U\textcolor{red}{\it{n}}]This register sets the behaviour when the signal input of channel 0 detects a positive edge. (R/W) 1: Increase the counter; 2: Decrease the counter; 0, 3: No effect on counter
\item [PCNT\_CH0\_NEG\_MODE\_U\textcolor{red}{\it{n}}]This register sets the behaviour when the signal input of channel 0 detects a negative edge. (R/W) 1: Increase the counter; 2: Decrease the counter; 0, 3: No effect on counter
\item [PCNT\_THR\_THRES1\_EN\_U\textcolor{red}{\it{n}}]This is the enable bit for unit \textcolor{red}{\it{n}}'s thres1 comparator. (R/W)
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{PCNT\_U\textit{\textcolor{red}{\it{n}}}\_CONF0\_REG (\textcolor{red}{\it{n}}: 0-7)}{0x0+0x0C*\textcolor{red}{\it{n}}}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\item [PCNT\_THR\_THRES0\_EN\_U\textcolor{red}{\it{n}}]This is the enable bit for unit \textcolor{red}{\it{n}}'s thres0 comparator. (R/W)
\item [PCNT\_THR\_L\_LIM\_EN\_U\textcolor{red}{\it{n}}]This is the enable bit for unit \textcolor{red}{\it{n}}'s thr\_l\_lim comparator. (R/W)
\item [PCNT\_THR\_H\_LIM\_EN\_U\textcolor{red}{\it{n}}]This is the enable bit for unit \textcolor{red}{\it{n}}'s thr\_h\_lim comparator. (R/W)
\item [PCNT\_THR\_ZERO\_EN\_U\textcolor{red}{\it{n}}]This is the enable bit for unit \textcolor{red}{\it{n}}'s zero comparator. (R/W)
\item [PCNT\_FILTER\_EN\_U\textcolor{red}{\it{n}}]This is the enable bit for unit \textcolor{red}{\it{n}}'s input filter. (R/W)
\item [PCNT\_FILTER\_THRES\_U\textcolor{red}{\it{n}}]This sets the maximum threshold, in APB\_CLK cycles, for the filter. Any pulses lasting shorter than this will be ignored when the filter is enabled. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{PCNT\_U\textit{\textcolor{red}{\it{n}}}\_CONF1\_REG (\textcolor{red}{\it{n}}: 0-7)}{0x4+0x0C*\textcolor{red}{\it{n}}}\label{regdesc:PCNTUnCONF1REG}
\regfield{PCNT\_CNT\_THRES1\_U\textcolor{red}{\it{n}}}{16}{16}{{0x000}}%
\regfield{PCNT\_CNT\_THRES0\_U\textcolor{red}{\it{n}}}{16}{0}{{0x000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [PCNT\_CNT\_THRES1\_U\textcolor{red}{\it{n}}]This register is used to configure the thres1 value for unit \textcolor{red}{\it{n}}. (R/W)
\item [PCNT\_CNT\_THRES0\_U\textcolor{red}{\it{n}}]This register is used to configure the thres0 value for unit \textcolor{red}{\it{n}}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{PCNT\_U\textit{\textcolor{red}{\it{n}}}\_CONF2\_REG (\textcolor{red}{\it{n}}: 0-7)}{0x8+0x0C*\textcolor{red}{\it{n}}}\label{regdesc:PCNTUnCONF2REG}
\regfield{PCNT\_CNT\_L\_LIM\_U\textcolor{red}{\it{n}}}{16}{16}{{0x000}}%
\regfield{PCNT\_CNT\_H\_LIM\_U\textcolor{red}{\it{n}}}{16}{0}{{0x000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [PCNT\_CNT\_L\_LIM\_U\textcolor{red}{\it{n}}]This register is used to configure the thr\_l\_lim value for unit \textcolor{red}{\it{n}}. (R/W)
\item [PCNT\_CNT\_H\_LIM\_U\textcolor{red}{\it{n}}]This register is used to configure the thr\_h\_lim value for unit \textcolor{red}{\it{n}}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{PCNT\_U\textit{\textcolor{red}{\it{n}}}\_CNT\_REG (\textcolor{red}{\it{n}}: 0-7)}{0x60+0x04*\textcolor{red}{\it{n}}}\label{regdesc:PCNTUnCNTREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{PCNT\_PLUS\_CNT\_U\textcolor{red}{\it{n}}}{16}{0}{{0x00000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [PCNT\_PLUS\_CNT\_U\textcolor{red}{\it{n}}]This register stores the current pulse count value for unit \textcolor{red}{\it{n}}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{PCNT\_INT\_RAW\_REG}{0x0080}\label{regdesc:PCNTINTRAWREG}
\regfield{(reserved)}{24}{8}{{0x0000000}}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U7\_INT\_RAW}{1}{7}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U6\_INT\_RAW}{1}{6}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U5\_INT\_RAW}{1}{5}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U4\_INT\_RAW}{1}{4}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U3\_INT\_RAW}{1}{3}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U2\_INT\_RAW}{1}{2}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U1\_INT\_RAW}{1}{1}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U0\_INT\_RAW}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [PCNT\_CNT\_THR\_EVENT\_U\textcolor{red}{\it{n}}\_INT\_RAW]The raw interrupt status bit for the \hyperref[int:PCNTCNTTHREVENTUnINT]{PCNT\_CNT\_THR\_EVENT\_U\textcolor{red}{\it{n}}\_INT} interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{PCNT\_INT\_ST\_REG}{0x0084}\label{regdesc:PCNTINTSTREG}
\regfield{(reserved)}{24}{8}{{0x0000000}}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U7\_INT\_ST}{1}{7}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U6\_INT\_ST}{1}{6}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U5\_INT\_ST}{1}{5}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U4\_INT\_ST}{1}{4}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U3\_INT\_ST}{1}{3}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U2\_INT\_ST}{1}{2}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U1\_INT\_ST}{1}{1}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U0\_INT\_ST}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [PCNT\_CNT\_THR\_EVENT\_U\textcolor{red}{\it{n}}\_INT\_ST]The masked interrupt status bit for the \hyperref[int:PCNTCNTTHREVENTUnINT]{PCNT\_CNT\_THR\_EVENT\_U\textcolor{red}{\it{n}}\_INT} interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{PCNT\_INT\_ENA\_REG}{0x0088}\label{regdesc:PCNTINTENAREG}
\regfield{(reserved)}{24}{8}{{0x0000000}}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U7\_INT\_ENA}{1}{7}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U6\_INT\_ENA}{1}{6}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U5\_INT\_ENA}{1}{5}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U4\_INT\_ENA}{1}{4}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U3\_INT\_ENA}{1}{3}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U2\_INT\_ENA}{1}{2}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U1\_INT\_ENA}{1}{1}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U0\_INT\_ENA}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [PCNT\_CNT\_THR\_EVENT\_U\textcolor{red}{\it{n}}\_INT\_ENA]The interrupt enable bit for the \hyperref[int:PCNTCNTTHREVENTUnINT]{PCNT\_CNT\_THR\_EVENT\_U\textcolor{red}{\it{n}}\_INT} interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{PCNT\_INT\_CLR\_REG}{0x008c}\label{regdesc:PCNTINTCLRREG}
\regfield{(reserved)}{24}{8}{{0x0000000}}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U7\_INT\_CLR}{1}{7}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U6\_INT\_CLR}{1}{6}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U5\_INT\_CLR}{1}{5}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U4\_INT\_CLR}{1}{4}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U3\_INT\_CLR}{1}{3}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U2\_INT\_CLR}{1}{2}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U1\_INT\_CLR}{1}{1}{0}%
\regfield{PCNT\_CNT\_THR\_EVENT\_U0\_INT\_CLR}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [PCNT\_CNT\_THR\_EVENT\_U\textcolor{red}{\it{n}}\_INT\_CLR]Set this bit to clear the \hyperref[int:PCNTCNTTHREVENTUnINT]{PCNT\_CNT\_THR\_EVENT\_U\textcolor{red}{\it{n}}\_INT} interrupt. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{PCNT\_CTRL\_REG}{0x00b0}\label{regdesc:PCNTCTRLREG}
\regfield{(reserved)}{15}{17}{{0x0000}}%
\regfield{PCNT\_CLK\_EN}{1}{16}{0}%
\regfield{PCNT\_CNT\_PAUSE\_U7}{1}{15}{0}%
\regfield{PCNT\_PLUS\_CNT\_RST\_U7}{1}{14}{1}%
\regfield{PCNT\_CNT\_PAUSE\_U6}{1}{13}{0}%
\regfield{PCNT\_PLUS\_CNT\_RST\_U6}{1}{12}{1}%
\regfield{PCNT\_CNT\_PAUSE\_U5}{1}{11}{0}%
\regfield{PCNT\_PLUS\_CNT\_RST\_U5}{1}{10}{1}%
\regfield{PCNT\_CNT\_PAUSE\_U4}{1}{9}{0}%
\regfield{PCNT\_PLUS\_CNT\_RST\_U4}{1}{8}{1}%
\regfield{PCNT\_CNT\_PAUSE\_U3}{1}{7}{0}%
\regfield{PCNT\_PLUS\_CNT\_RST\_U3}{1}{6}{1}%
\regfield{PCNT\_CNT\_PAUSE\_U2}{1}{5}{0}%
\regfield{PCNT\_PLUS\_CNT\_RST\_U2}{1}{4}{1}%
\regfield{PCNT\_CNT\_PAUSE\_U1}{1}{3}{0}%
\regfield{PCNT\_PLUS\_CNT\_RST\_U1}{1}{2}{1}%
\regfield{PCNT\_CNT\_PAUSE\_U0}{1}{1}{0}%
\regfield{PCNT\_PLUS\_CNT\_RST\_U0}{1}{0}{1}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [PCNT\_CLK\_EN] Configures register clock gating.\\
0: Support clock only when the application writes registers.\\
1: Always force the clock on for registers.\\ (R/W)
\item [PCNT\_CNT\_PAUSE\_U\textcolor{red}{\it{n}}]Set this bit to freeze unit \textcolor{red}{\it{n}}'s counter. (R/W)
\item [PCNT\_PLUS\_CNT\_RST\_U\textcolor{red}{\it{n}}]Set this bit to clear unit \textcolor{red}{\it{n}}'s counter. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{PCNT\_U\textit{\textcolor{red}{\it{n}}}\_STATUS\_REG (\textit{\textcolor{red}{\it{n}}}: 0-7)}{0x90+0x0C*\textit{\textcolor{red}{\it{n}}}}\label{regdesc:PCNTUnSTATUSREG}
\regfield{(reserved)}{25}{7}{0000000000000000000000000}%
\regfield{PCNT\_THR\_ZERO\_LAT\_U\textcolor{red}{\it{n}}}{1}{6}{{0}}%
\regfield{PCNT\_THR\_H\_LIM\_LAT\_U\textcolor{red}{\it{n}}}{1}{5}{{0}}%
\regfield{PCNT\_THR\_L\_LIM\_LAT\_U\textcolor{red}{\it{n}}}{1}{4}{{0}}%
\regfield{PCNT\_THR\_THRES0\_LAT\_U\textcolor{red}{\it{n}}}{1}{3}{{0}}%
\regfield{PCNT\_THR\_THRES1\_LAT\_U\textcolor{red}{\it{n}}}{1}{2}{{0}}%
\regfield{PCNT\_THR\_ZERO\_MODE\_U\textcolor{red}{\it{n}}}{2}{0}{{00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\item [PCNT\_THR\_ZERO\_LAT\_U\textcolor{red}{\it{n}}] The last interrupt happened on counter for unit \textcolor{red}{\it{n}} reaching 0.  (RO)
\item [PCNT\_THR\_H\_LIM\_LAT\_U\textcolor{red}{\it{n}}] The last interrupt happened on counter for unit \textcolor{red}{\it{n}} reaching thr\_h\_lim. (RO)
\item [PCNT\_THR\_L\_LIM\_LAT\_U\textcolor{red}{\it{n}}] The last interrupt happened on counter for unit \textcolor{red}{\it{n}} reaching thr\_l\_lim. (RO)
\item [PCNT\_THR\_THRES0\_LAT\_U\textcolor{red}{\it{n}}] The last interrupt happened on counter for unit \textcolor{red}{\it{n}} reaching thres0. (RO)
\item [PCNT\_THR\_THRES1\_LAT\_U\textcolor{red}{\it{n}}] The last interrupt happened on counter for unit \textcolor{red}{\it{n}} reaching thres1. (RO)
\item [PCNT\_THR\_ZERO\_MODE\_U\textcolor{red}{\it{n}}] This register stores the current status of the counter. 0: counting value is +0 (the counter values are represented by signed binary numbers); 1: counting value is -0; 2: counting value is negative; 3: counting value is positive. (RO)

\end{reglist}\end{regdesc}
\end{register}

