\begin{register}{H}{UART\_FIFO\_REG}{\hexprefix{}0000}\label{regdesc:UARTFIFOREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{UART\_RXFIFO\_RD\_BYTE}{8}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXFIFORDBYTE}\item [UART\_RXFIFO\_RD\_BYTE] UART \regindex{n} accesses FIFO via this register. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_MEM\_CONF\_REG}{\hexprefix{}005C}\label{regdesc:UARTMEMCONFREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{UART\_MEM\_FORCE\_PU}{1}{27}{{0}}%
\regfield{UART\_MEM\_FORCE\_PD}{1}{26}{{0}}%
\regfield{UART\_RX\_TOUT\_THRHD}{10}{16}{{\hexprefix{}a}}%
\regfield{UART\_RX\_FLOW\_THRHD}{9}{7}{{\hexprefix{}0}}%
\regfield{UART\_TX\_SIZE}{3}{4}{{\hexprefix{}1}}%
\regfield{UART\_RX\_SIZE}{3}{1}{{1}}%
\regfield{(reserved)}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXSIZE}\item [UART\_RX\_SIZE] This register is used to configure the amount of RAM allocated for RX FIFO. The default number is 128 bytes. (R/W)
\label{fielddesc:UARTTXSIZE}\item [UART\_TX\_SIZE] This register is used to configure the amount of RAM allocated for TX FIFO. The default number is 128 bytes. (R/W)
\label{fielddesc:UARTRXFLOWTHRHD}\item [UART\_RX\_FLOW\_THRHD] This register is used to configure the maximum amount of data bytes that can be received when hardware flow control works. (R/W)
\label{fielddesc:UARTRXTOUTTHRHD}\item [UART\_RX\_TOUT\_THRHD] This register is used to configure the threshold time that the receiver takes to receive one byte, in the unit of bit time (the time it takes to transfer one bit).
The UART\_RXFIFO\_TOUT\_INT interrupt will be triggered when the receiver takes more time to receive one byte with UART RX\_TOUT\_EN set to 1. (R/W)
\label{fielddesc:UARTMEMFORCEPD}\item [UART\_MEM\_FORCE\_PD] Set this bit to force power down UART RAM. (R/W)
\label{fielddesc:UARTMEMFORCEPU}\item [UART\_MEM\_FORCE\_PU] Set this bit to force power up UART RAM. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_INT\_RAW\_REG}{\hexprefix{}0004}\label{regdesc:UARTINTRAWREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{UART\_WAKEUP\_INT\_RAW}{1}{19}{{0}}%
\regfield{UART\_AT\_CMD\_CHAR\_DET\_INT\_RAW}{1}{18}{{0}}%
\regfield{UART\_RS485\_CLASH\_INT\_RAW}{1}{17}{{0}}%
\regfield{UART\_RS485\_FRM\_ERR\_INT\_RAW}{1}{16}{{0}}%
\regfield{UART\_RS485\_PARITY\_ERR\_INT\_RAW}{1}{15}{{0}}%
\regfield{UART\_TX\_DONE\_INT\_RAW}{1}{14}{{0}}%
\regfield{UART\_TX\_BRK\_IDLE\_DONE\_INT\_RAW}{1}{13}{{0}}%
\regfield{UART\_TX\_BRK\_DONE\_INT\_RAW}{1}{12}{{0}}%
\regfield{UART\_GLITCH\_DET\_INT\_RAW}{1}{11}{{0}}%
\regfield{UART\_SW\_XOFF\_INT\_RAW}{1}{10}{{0}}%
\regfield{UART\_SW\_XON\_INT\_RAW}{1}{9}{{0}}%
\regfield{UART\_RXFIFO\_TOUT\_INT\_RAW}{1}{8}{{0}}%
\regfield{UART\_BRK\_DET\_INT\_RAW}{1}{7}{{0}}%
\regfield{UART\_CTS\_CHG\_INT\_RAW}{1}{6}{{0}}%
\regfield{UART\_DSR\_CHG\_INT\_RAW}{1}{5}{{0}}%
\regfield{UART\_RXFIFO\_OVF\_INT\_RAW}{1}{4}{{0}}%
\regfield{UART\_FRM\_ERR\_INT\_RAW}{1}{3}{{0}}%
\regfield{UART\_PARITY\_ERR\_INT\_RAW}{1}{2}{{0}}%
\regfield{UART\_TXFIFO\_EMPTY\_INT\_RAW}{1}{1}{{0}}%
\regfield{UART\_RXFIFO\_FULL\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXFIFOFULLINTRAW}\item [UART\_RXFIFO\_FULL\_INT\_RAW] This interrupt raw bit turns to high level when the receiver receives more data than what UART\_RXFIFO\_FULL\_THRHD specifies. (RO)
\label{fielddesc:UARTTXFIFOEMPTYINTRAW}\item [UART\_TXFIFO\_EMPTY\_INT\_RAW] This interrupt raw bit turns to high level when the amount of data in TX FIFO is less than what UART\_TXFIFO\_EMPTY\_THRHD specifies. (RO)
\label{fielddesc:UARTPARITYERRINTRAW}\item [UART\_PARITY\_ERR\_INT\_RAW] This interrupt raw bit turns to high level when the receiver detects a parity error in the data. (RO)
\label{fielddesc:UARTFRMERRINTRAW}\item [UART\_FRM\_ERR\_INT\_RAW] This interrupt raw bit turns to high level when the receiver detects a data frame error. (RO)
\label{fielddesc:UARTRXFIFOOVFINTRAW}\item [UART\_RXFIFO\_OVF\_INT\_RAW] This interrupt raw bit turns to high level when the receiver receives more data than the capacity of RX FIFO. (RO)
\label{fielddesc:UARTDSRCHGINTRAW}\item [UART\_DSR\_CHG\_INT\_RAW] This interrupt raw bit turns to high level when the receiver detects the edge change of DSRn signal. (RO)
\label{fielddesc:UARTCTSCHGINTRAW}\item [UART\_CTS\_CHG\_INT\_RAW] This interrupt raw bit turns to high level when the receiver detects the edge change of CTSn signal. (RO)
\label{fielddesc:UARTBRKDETINTRAW}\item [UART\_BRK\_DET\_INT\_RAW] This interrupt raw bit turns to high level when the receiver detects a 0 after the stop bit. (RO)
\label{fielddesc:UARTRXFIFOTOUTINTRAW}\item [UART\_RXFIFO\_TOUT\_INT\_RAW] This interrupt raw bit turns to high level when the receiver takes more time than UART\_RX\_TOUT\_THRHD to receive a byte. (RO)
\label{fielddesc:UARTSWXONINTRAW}\item [UART\_SW\_XON\_INT\_RAW] This interrupt raw bit turns to high level when the receiver receives an XON character and UART\_SW\_FLOW\_CON\_EN is set to 1. (RO)
\label{fielddesc:UARTSWXOFFINTRAW}\item [UART\_SW\_XOFF\_INT\_RAW] This interrupt raw bit turns to high level when the receiver receives an XOFF character and UART\_SW\_FLOW\_CON\_EN is set to 1. (RO)
\label{fielddesc:UARTGLITCHDETINTRAW}\item [UART\_GLITCH\_DET\_INT\_RAW] This interrupt raw bit turns to high level when the receiver detects a glitch in the middle of a start bit. (RO)
\label{fielddesc:UARTTXBRKDONEINTRAW}\item [UART\_TX\_BRK\_DONE\_INT\_RAW] This interrupt raw bit turns to high level when the transmitter completes  sending  NULL characters, after all data in TX FIFO are sent. (RO)
\label{fielddesc:UARTTXBRKIDLEDONEINTRAW}\item [UART\_TX\_BRK\_IDLE\_DONE\_INT\_RAW] This interrupt raw bit turns to high level when the transmitter has kept the shortest duration after sending the  last data. (RO)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{UART\_INT\_RAW\_REG}{\hexprefix{}0004}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:UARTTXDONEINTRAW}\item [UART\_TX\_DONE\_INT\_RAW] This interrupt raw bit turns to high level when the transmitter has sent out all data in FIFO. (RO)
\label{fielddesc:UARTRS485PARITYERRINTRAW}\item [UART\_RS485\_PARITY\_ERR\_INT\_RAW] This interrupt raw bit turns to high level when the receiver detects a parity error from the echo of the transmitter in RS485 mode. (RO)
\label{fielddesc:UARTRS485FRMERRINTRAW}\item [UART\_RS485\_FRM\_ERR\_INT\_RAW] This interrupt raw bit turns to high level when the receiver detects a data frame error from the echo of the transmitter in RS485 mode. (RO)
\label{fielddesc:UARTRS485CLASHINTRAW}\item [UART\_RS485\_CLASH\_INT\_RAW] This interrupt raw bit turns to high level when a collision is detected between the transmitter and the receiver in RS485 mode. (RO)
\label{fielddesc:UARTATCMDCHARDETINTRAW}\item [UART\_AT\_CMD\_CHAR\_DET\_INT\_RAW] This interrupt raw bit turns to high level when the receiver detects the configured UART\_AT\_CMD CHAR. (RO)
\label{fielddesc:UARTWAKEUPINTRAW}\item [UART\_WAKEUP\_INT\_RAW] This interrupt raw bit turns to high level when input RXD edge changes more times than what (UART\_ACTIVE\_THRESHOLD + 3) specifies in Light-sleep mode. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_INT\_ST\_REG}{\hexprefix{}0008}\label{regdesc:UARTINTSTREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{UART\_WAKEUP\_INT\_ST}{1}{19}{{0}}%
\regfield{UART\_AT\_CMD\_CHAR\_DET\_INT\_ST}{1}{18}{{0}}%
\regfield{UART\_RS485\_CLASH\_INT\_ST}{1}{17}{{0}}%
\regfield{UART\_RS485\_FRM\_ERR\_INT\_ST}{1}{16}{{0}}%
\regfield{UART\_RS485\_PARITY\_ERR\_INT\_ST}{1}{15}{{0}}%
\regfield{UART\_TX\_DONE\_INT\_ST}{1}{14}{{0}}%
\regfield{UART\_TX\_BRK\_IDLE\_DONE\_INT\_ST}{1}{13}{{0}}%
\regfield{UART\_TX\_BRK\_DONE\_INT\_ST}{1}{12}{{0}}%
\regfield{UART\_GLITCH\_DET\_INT\_ST}{1}{11}{{0}}%
\regfield{UART\_SW\_XOFF\_INT\_ST}{1}{10}{{0}}%
\regfield{UART\_SW\_XON\_INT\_ST}{1}{9}{{0}}%
\regfield{UART\_RXFIFO\_TOUT\_INT\_ST}{1}{8}{{0}}%
\regfield{UART\_BRK\_DET\_INT\_ST}{1}{7}{{0}}%
\regfield{UART\_CTS\_CHG\_INT\_ST}{1}{6}{{0}}%
\regfield{UART\_DSR\_CHG\_INT\_ST}{1}{5}{{0}}%
\regfield{UART\_RXFIFO\_OVF\_INT\_ST}{1}{4}{{0}}%
\regfield{UART\_FRM\_ERR\_INT\_ST}{1}{3}{{0}}%
\regfield{UART\_PARITY\_ERR\_INT\_ST}{1}{2}{{0}}%
\regfield{UART\_TXFIFO\_EMPTY\_INT\_ST}{1}{1}{{0}}%
\regfield{UART\_RXFIFO\_FULL\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXFIFOFULLINTST}\item [UART\_RXFIFO\_FULL\_INT\_ST] This is the status bit for UART\_RXFIFO\_FULL\_INT when UART\_RXFIFO\_FULL\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTTXFIFOEMPTYINTST}\item [UART\_TXFIFO\_EMPTY\_INT\_ST] This is the status bit for UART\_TXFIFO\_EMPTY\_INT when UART\_TXFIFO\_EMPTY\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTPARITYERRINTST}\item [UART\_PARITY\_ERR\_INT\_ST] This is the status bit for UART\_PARITY\_ERR\_INT when UART\_PARITY\_ERR\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTFRMERRINTST}\item [UART\_FRM\_ERR\_INT\_ST] This is the status bit for UART\_FRM\_ERR\_INT when UART\_FRM\_ERR\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTRXFIFOOVFINTST}\item [UART\_RXFIFO\_OVF\_INT\_ST] This is the status bit for UART\_RXFIFO\_OVF\_INT when UART\_RXFIFO\_OVF\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTDSRCHGINTST}\item [UART\_DSR\_CHG\_INT\_ST] This is the status bit for UART\_DSR\_CHG\_INT when UART\_DSR\_CHG\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTCTSCHGINTST}\item [UART\_CTS\_CHG\_INT\_ST] This is the status bit for UART\_CTS\_CHG\_INT when UART\_CTS\_CHG\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTBRKDETINTST}\item [UART\_BRK\_DET\_INT\_ST] This is the status bit for UART\_BRK\_DET\_INT when UART\_BRK\_DET\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTRXFIFOTOUTINTST}\item [UART\_RXFIFO\_TOUT\_INT\_ST] This is the status bit for UART\_RXFIFO\_TOUT\_INT when UART\_RXFIFO\_TOUT\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTSWXONINTST}\item [UART\_SW\_XON\_INT\_ST] This is the status bit for UART\_SW\_XON\_INT when UART\_SW\_XON\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTSWXOFFINTST}\item [UART\_SW\_XOFF\_INT\_ST] This is the status bit for UART\_SW\_XOFF\_INT when UART\_SW\_XOFF\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTGLITCHDETINTST}\item [UART\_GLITCH\_DET\_INT\_ST] This is the status bit for UART\_GLITCH\_DET\_INT when UART\_GLITCH\_DET\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTTXBRKDONEINTST}\item [UART\_TX\_BRK\_DONE\_INT\_ST] This is the status bit for UART\_TX\_BRK\_DONE\_INT when UART\_TX\_BRK\_DONE\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTTXBRKIDLEDONEINTST}\item [UART\_TX\_BRK\_IDLE\_DONE\_INT\_ST] This is the status bit for UART\_TX\_BRK\_IDLE\_DONE\_INT when UART\_TX\_BRK\_IDLE\_DONE\_INT\_ENA is set to 1. (RO)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{UART\_INT\_ST\_REG}{\hexprefix{}0008}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:UARTTXDONEINTST}\item [UART\_TX\_DONE\_INT\_ST] This is the status bit for UART\_TX\_DONE\_INT when UART\_TX\_DONE\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTRS485PARITYERRINTST}\item [UART\_RS485\_PARITY\_ERR\_INT\_ST] This is the status bit for UART\_RS485\_PARITY\_ERR\_INT when UART\_RS485\_PARITY\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTRS485FRMERRINTST}\item [UART\_RS485\_FRM\_ERR\_INT\_ST] This is the status bit for UART\_RS485\_FRM\_ERR\_INT when UART\_RS485\_FRM\_ERR\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTRS485CLASHINTST}\item [UART\_RS485\_CLASH\_INT\_ST] This is the status bit for UART\_RS485\_CLASH\_INT when UART\_RS485\_CLASH\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTATCMDCHARDETINTST}\item [UART\_AT\_CMD\_CHAR\_DET\_INT\_ST] This is the status bit for UART\_AT\_CMD\_CHAR\_DET\_INT when UART\_AT\_CMD\_CHAR\_DET\_INT\_ENA is set to 1. (RO)
\label{fielddesc:UARTWAKEUPINTST}\item [UART\_WAKEUP\_INT\_ST] This is the status bit for UART\_WAKEUP\_INT when UART\_WAKEUP\_INT\_ENA is set to 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_INT\_ENA\_REG}{\hexprefix{}000C}\label{regdesc:UARTINTENAREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{UART\_WAKEUP\_INT\_ENA}{1}{19}{{0}}%
\regfield{UART\_AT\_CMD\_CHAR\_DET\_INT\_ENA}{1}{18}{{0}}%
\regfield{UART\_RS485\_CLASH\_INT\_ENA}{1}{17}{{0}}%
\regfield{UART\_RS485\_FRM\_ERR\_INT\_ENA}{1}{16}{{0}}%
\regfield{UART\_RS485\_PARITY\_ERR\_INT\_ENA}{1}{15}{{0}}%
\regfield{UART\_TX\_DONE\_INT\_ENA}{1}{14}{{0}}%
\regfield{UART\_TX\_BRK\_IDLE\_DONE\_INT\_ENA}{1}{13}{{0}}%
\regfield{UART\_TX\_BRK\_DONE\_INT\_ENA}{1}{12}{{0}}%
\regfield{UART\_GLITCH\_DET\_INT\_ENA}{1}{11}{{0}}%
\regfield{UART\_SW\_XOFF\_INT\_ENA}{1}{10}{{0}}%
\regfield{UART\_SW\_XON\_INT\_ENA}{1}{9}{{0}}%
\regfield{UART\_RXFIFO\_TOUT\_INT\_ENA}{1}{8}{{0}}%
\regfield{UART\_BRK\_DET\_INT\_ENA}{1}{7}{{0}}%
\regfield{UART\_CTS\_CHG\_INT\_ENA}{1}{6}{{0}}%
\regfield{UART\_DSR\_CHG\_INT\_ENA}{1}{5}{{0}}%
\regfield{UART\_RXFIFO\_OVF\_INT\_ENA}{1}{4}{{0}}%
\regfield{UART\_FRM\_ERR\_INT\_ENA}{1}{3}{{0}}%
\regfield{UART\_PARITY\_ERR\_INT\_ENA}{1}{2}{{0}}%
\regfield{UART\_TXFIFO\_EMPTY\_INT\_ENA}{1}{1}{{0}}%
\regfield{UART\_RXFIFO\_FULL\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXFIFOFULLINTENA}\item [UART\_RXFIFO\_FULL\_INT\_ENA] This is the enable bit for UART\_RXFIFO\_FULL\_INT. (R/W)
\label{fielddesc:UARTTXFIFOEMPTYINTENA}\item [UART\_TXFIFO\_EMPTY\_INT\_ENA] This is the enable bit for UART\_TXFIFO\_EMPTY\_INT. (R/W)
\label{fielddesc:UARTPARITYERRINTENA}\item [UART\_PARITY\_ERR\_INT\_ENA] This is the enable bit for UART\_PARITY\_ERR\_INT. (R/W)
\label{fielddesc:UARTFRMERRINTENA}\item [UART\_FRM\_ERR\_INT\_ENA] This is the enable bit for UART\_FRM\_ERR\_INT. (R/W)
\label{fielddesc:UARTRXFIFOOVFINTENA}\item [UART\_RXFIFO\_OVF\_INT\_ENA] This is the enable bit for UART\_RXFIFO\_OVF\_INT. (R/W)
\label{fielddesc:UARTDSRCHGINTENA}\item [UART\_DSR\_CHG\_INT\_ENA] This is the enable bit for UART\_DSR\_CHG\_INT. (R/W)
\label{fielddesc:UARTCTSCHGINTENA}\item [UART\_CTS\_CHG\_INT\_ENA] This is the enable bit for UART\_CTS\_CHG\_INT. (R/W)
\label{fielddesc:UARTBRKDETINTENA}\item [UART\_BRK\_DET\_INT\_ENA] This is the enable bit for UART\_BRK\_DET\_INT. (R/W)
\label{fielddesc:UARTRXFIFOTOUTINTENA}\item [UART\_RXFIFO\_TOUT\_INT\_ENA] This is the enable bit for UART\_RXFIFO\_TOUT\_INT. (R/W)
\label{fielddesc:UARTSWXONINTENA}\item [UART\_SW\_XON\_INT\_ENA] This is the enable bit for UART\_SW\_XON\_INT. (R/W)
\label{fielddesc:UARTSWXOFFINTENA}\item [UART\_SW\_XOFF\_INT\_ENA] This is the enable bit for UART\_SW\_XOFF\_INT. (R/W)
\label{fielddesc:UARTGLITCHDETINTENA}\item [UART\_GLITCH\_DET\_INT\_ENA] This is the enable bit for UART\_GLITCH\_DET\_INT. (R/W)
\label{fielddesc:UARTTXBRKDONEINTENA}\item [UART\_TX\_BRK\_DONE\_INT\_ENA] This is the enable bit for UART\_TX\_BRK\_DONE\_INT. (R/W)
\label{fielddesc:UARTTXBRKIDLEDONEINTENA}\item [UART\_TX\_BRK\_IDLE\_DONE\_INT\_ENA] This is the enable bit for UART\_TX\_BRK\_IDLE\_DONE\_INT. (R/W)
\label{fielddesc:UARTTXDONEINTENA}\item [UART\_TX\_DONE\_INT\_ENA] This is the enable bit for UART\_TX\_DONE\_INT. (R/W)
\label{fielddesc:UARTRS485PARITYERRINTENA}\item [UART\_RS485\_PARITY\_ERR\_INT\_ENA] This is the enable bit for UART\_RS485\_PARITY\_ERR\_INT. (R/W)
\label{fielddesc:UARTRS485FRMERRINTENA}\item [UART\_RS485\_FRM\_ERR\_INT\_ENA] This is the enable bit for UART\_RS485\_PARITY\_ERR\_INT. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{UART\_INT\_ENA\_REG}{\hexprefix{}000C}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:UARTRS485CLASHINTENA}\item [UART\_RS485\_CLASH\_INT\_ENA] This is the enable bit for UART\_RS485\_CLASH\_INT. (R/W)
\label{fielddesc:UARTATCMDCHARDETINTENA}\item [UART\_AT\_CMD\_CHAR\_DET\_INT\_ENA] This is the enable bit for UART\_AT\_CMD\_CHAR\_DET\_INT. (R/W)
\label{fielddesc:UARTWAKEUPINTENA}\item [UART\_WAKEUP\_INT\_ENA] This is the enable bit for UART\_WAKEUP\_INT. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_INT\_CLR\_REG}{\hexprefix{}0010}\label{regdesc:UARTINTCLRREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{UART\_WAKEUP\_INT\_CLR}{1}{19}{{0}}%
\regfield{UART\_AT\_CMD\_CHAR\_DET\_INT\_CLR}{1}{18}{{0}}%
\regfield{UART\_RS485\_CLASH\_INT\_CLR}{1}{17}{{0}}%
\regfield{UART\_RS485\_FRM\_ERR\_INT\_CLR}{1}{16}{{0}}%
\regfield{UART\_RS485\_PARITY\_ERR\_INT\_CLR}{1}{15}{{0}}%
\regfield{UART\_TX\_DONE\_INT\_CLR}{1}{14}{{0}}%
\regfield{UART\_TX\_BRK\_IDLE\_DONE\_INT\_CLR}{1}{13}{{0}}%
\regfield{UART\_TX\_BRK\_DONE\_INT\_CLR}{1}{12}{{0}}%
\regfield{UART\_GLITCH\_DET\_INT\_CLR}{1}{11}{{0}}%
\regfield{UART\_SW\_XOFF\_INT\_CLR}{1}{10}{{0}}%
\regfield{UART\_SW\_XON\_INT\_CLR}{1}{9}{{0}}%
\regfield{UART\_RXFIFO\_TOUT\_INT\_CLR}{1}{8}{{0}}%
\regfield{UART\_BRK\_DET\_INT\_CLR}{1}{7}{{0}}%
\regfield{UART\_CTS\_CHG\_INT\_CLR}{1}{6}{{0}}%
\regfield{UART\_DSR\_CHG\_INT\_CLR}{1}{5}{{0}}%
\regfield{UART\_RXFIFO\_OVF\_INT\_CLR}{1}{4}{{0}}%
\regfield{UART\_FRM\_ERR\_INT\_CLR}{1}{3}{{0}}%
\regfield{UART\_PARITY\_ERR\_INT\_CLR}{1}{2}{{0}}%
\regfield{UART\_TXFIFO\_EMPTY\_INT\_CLR}{1}{1}{{0}}%
\regfield{UART\_RXFIFO\_FULL\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXFIFOFULLINTCLR}\item [UART\_RXFIFO\_FULL\_INT\_CLR] Set this bit to clear UART\_THE RXFIFO\_FULL\_INT interrupt. (WO)
\label{fielddesc:UARTTXFIFOEMPTYINTCLR}\item [UART\_TXFIFO\_EMPTY\_INT\_CLR] Set this bit to clear UART\_TXFIFO\_EMPTY\_INT interrupt. (WO)
\label{fielddesc:UARTPARITYERRINTCLR}\item [UART\_PARITY\_ERR\_INT\_CLR] Set this bit to clear UART\_PARITY\_ERR\_INT interrupt. (WO)
\label{fielddesc:UARTFRMERRINTCLR}\item [UART\_FRM\_ERR\_INT\_CLR] Set this bit to clear UART\_FRM\_ERR\_INT interrupt. (WO)
\label{fielddesc:UARTRXFIFOOVFINTCLR}\item [UART\_RXFIFO\_OVF\_INT\_CLR] Set this bit to clear UART\_UART\_RXFIFO\_OVF\_INT interrupt. (WO)
\label{fielddesc:UARTDSRCHGINTCLR}\item [UART\_DSR\_CHG\_INT\_CLR] Set this bit to clear UART\_DSR\_CHG\_INT interrupt. (WO)
\label{fielddesc:UARTCTSCHGINTCLR}\item [UART\_CTS\_CHG\_INT\_CLR] Set this bit to clear UART\_CTS\_CHG\_INT interrupt. (WO)
\label{fielddesc:UARTBRKDETINTCLR}\item [UART\_BRK\_DET\_INT\_CLR] Set this bit to clear UART\_BRK\_DET\_INT interrupt. (WO)
\label{fielddesc:UARTRXFIFOTOUTINTCLR}\item [UART\_RXFIFO\_TOUT\_INT\_CLR] Set this bit to clear UART\_RXFIFO\_TOUT\_INT interrupt. (WO)
\label{fielddesc:UARTSWXONINTCLR}\item [UART\_SW\_XON\_INT\_CLR] Set this bit to clear UART\_SW\_XON\_INT interrupt. (WO)
\label{fielddesc:UARTSWXOFFINTCLR}\item [UART\_SW\_XOFF\_INT\_CLR] Set this bit to clear UART\_SW\_XOFF\_INT interrupt. (WO)
\label{fielddesc:UARTGLITCHDETINTCLR}\item [UART\_GLITCH\_DET\_INT\_CLR] Set this bit to clear UART\_GLITCH\_DET\_INT interrupt. (WO)
\label{fielddesc:UARTTXBRKDONEINTCLR}\item [UART\_TX\_BRK\_DONE\_INT\_CLR] Set this bit to clear UART\_TX\_BRK\_DONE\_INT interrupt. (WO)
\label{fielddesc:UARTTXBRKIDLEDONEINTCLR}\item [UART\_TX\_BRK\_IDLE\_DONE\_INT\_CLR] Set this bit to clear UART\_TX\_BRK\_IDLE\_DONE\_INT interrupt. (WO)
\label{fielddesc:UARTTXDONEINTCLR}\item [UART\_TX\_DONE\_INT\_CLR] Set this bit to clear UART\_TX\_DONE\_INT interrupt. (WO)
\label{fielddesc:UARTRS485PARITYERRINTCLR}\item [UART\_RS485\_PARITY\_ERR\_INT\_CLR] Set this bit to clear UART\_RS485\_PARITY\_ERR\_INT interrupt. (WO)
\label{fielddesc:UARTRS485FRMERRINTCLR}\item [UART\_RS485\_FRM\_ERR\_INT\_CLR] Set this bit to clear UART\_RS485\_FRM\_ERR\_INT interrupt. (WO)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{UART\_INT\_CLR\_REG}{\hexprefix{}0010}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:UARTRS485CLASHINTCLR}\item [UART\_RS485\_CLASH\_INT\_CLR] Set this bit to clear UART\_RS485\_CLASH\_INT interrupt. (WO)
\label{fielddesc:UARTATCMDCHARDETINTCLR}\item [UART\_AT\_CMD\_CHAR\_DET\_INT\_CLR] Set this bit to clear UART\_AT\_CMD\_CHAR\_DET\_INT interrupt. (WO)
\label{fielddesc:UARTWAKEUPINTCLR}\item [UART\_WAKEUP\_INT\_CLR] Set this bit to clear UART\_WAKEUP\_INT interrupt. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_CLKDIV\_REG}{\hexprefix{}0014}\label{regdesc:UARTCLKDIVREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{UART\_CLKDIV\_FRAG}{4}{20}{{\hexprefix{}0}}%
\regfield{UART\_CLKDIV}{20}{0}{{\hexprefix{}2b6}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTCLKDIV}\item [UART\_CLKDIV] The integral part of the frequency divisor. (R/W)
\label{fielddesc:UARTCLKDIVFRAG}\item [UART\_CLKDIV\_FRAG] The fractional part of the frequency divisor. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_CONF0\_REG}{\hexprefix{}0020}\label{regdesc:UARTCONF0REG}
\regfield{(reserved)}{3}{29}{000}%
\regfield{UART\_MEM\_CLK\_EN}{1}{28}{{1}}%
\regfield{UART\_TICK\_REF\_ALWAYS\_ON}{1}{27}{{1}}%
\regfield{(reserved)}{2}{25}{00}%
\regfield{UART\_DTR\_INV}{1}{24}{{0}}%
\regfield{UART\_RTS\_INV}{1}{23}{{0}}%
\regfield{UART\_TXD\_INV}{1}{22}{{0}}%
\regfield{UART\_DSR\_INV}{1}{21}{{0}}%
\regfield{UART\_CTS\_INV}{1}{20}{{0}}%
\regfield{UART\_RXD\_INV}{1}{19}{{0}}%
\regfield{UART\_TXFIFO\_RST}{1}{18}{{0}}%
\regfield{UART\_RXFIFO\_RST}{1}{17}{{0}}%
\regfield{UART\_IRDA\_EN}{1}{16}{{0}}%
\regfield{UART\_TX\_FLOW\_EN}{1}{15}{{0}}%
\regfield{UART\_LOOPBACK}{1}{14}{{0}}%
\regfield{UART\_IRDA\_RX\_INV}{1}{13}{{0}}%
\regfield{UART\_IRDA\_TX\_INV}{1}{12}{{0}}%
\regfield{UART\_IRDA\_WCTL}{1}{11}{{0}}%
\regfield{UART\_IRDA\_TX\_EN}{1}{10}{{0}}%
\regfield{UART\_IRDA\_DPLX}{1}{9}{{0}}%
\regfield{UART\_TXD\_BRK}{1}{8}{{0}}%
\regfield{UART\_SW\_DTR}{1}{7}{{0}}%
\regfield{UART\_SW\_RTS}{1}{6}{{0}}%
\regfield{UART\_STOP\_BIT\_NUM}{2}{4}{{1}}%
\regfield{UART\_BIT\_NUM}{2}{2}{{3}}%
\regfield{UART\_PARITY\_EN}{1}{1}{{0}}%
\regfield{UART\_PARITY}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTPARITY}\item [UART\_PARITY] This register is used to configure the parity check mode.
0: even. : odd. (R/W)
\label{fielddesc:UARTPARITYEN}\item [UART\_PARITY\_EN] Set this bit to enable UART parity check. (R/W)
\label{fielddesc:UARTBITNUM}\item [UART\_BIT\_NUM] This register is used to set the length of data.
0: 5 bits. 1: 6 bits. 2: 7 bits. 3: 8 bits. (R/W)
\label{fielddesc:UARTSTOPBITNUM}\item [UART\_STOP\_BIT\_NUM] This register is used to set the length of stop bit.\\
0: Invalid. No effect\\
1: 1 bit\\
2: 1.5 bits\\
3: 2 bits\\ (R/W)
\label{fielddesc:UARTSWRTS}\item [UART\_SW\_RTS] This register is used to configure the software RTS signal which is used in software flow control. (R/W)
\label{fielddesc:UARTSWDTR}\item [UART\_SW\_DTR] This register is used to configure the software DTR signal which is used in software flow control. (R/W)
\label{fielddesc:UARTTXDBRK}\item [UART\_TXD\_BRK] Set this bit to enable the transmitter to send NULL characterswhen the process of sending data is done. (R/W)
\label{fielddesc:UARTIRDADPLX}\item [UART\_IRDA\_DPLX] Set this bit to enable IrDA loopback mode. (R/W)
\label{fielddesc:UARTIRDATXEN}\item [UART\_IRDA\_TX\_EN] This is the start enable bit for IrDA transmitter. (R/W)
\label{fielddesc:UARTIRDAWCTL}\item [UART\_IRDA\_WCTL] 1: The IrDA transmitter's 11th bit is the same as 10th bit. 0: Set IrDA transmitter's 11th bit to 0. (R/W)
\label{fielddesc:UARTIRDATXINV}\item [UART\_IRDA\_TX\_INV] Set this bit to invert the level of IrDA transmitter. (R/W)
\label{fielddesc:UARTIRDARXINV}\item [UART\_IRDA\_RX\_INV] Set this bit to invert the level of IrDA receiver. (R/W)
\label{fielddesc:UARTLOOPBACK}\item [UART\_LOOPBACK] Set this bit to enable UART loopback test mode. (R/W)
\label{fielddesc:UARTTXFLOWEN}\item [UART\_TX\_FLOW\_EN] Set this bit to enable flow control function for the transmitter. (R/W)
\label{fielddesc:UARTIRDAEN}\item [UART\_IRDA\_EN] Set this bit to enable IrDA protocol. (R/W)
\label{fielddesc:UARTRXFIFORST}\item [UART\_RXFIFO\_RST] Set this bit to reset the UART RX FIFO. (R/W)
\label{fielddesc:UARTTXFIFORST}\item [UART\_TXFIFO\_RST] Set this bit to reset the UART TX FIFO. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{UART\_CONF0\_REG}{\hexprefix{}0020}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:UARTRXDINV}\item [UART\_RXD\_INV] Set this bit to invert the level of UART RXD signal. (R/W)
\label{fielddesc:UARTCTSINV}\item [UART\_CTS\_INV] Set this bit to invert the level of UART CTS signal. (R/W)
\label{fielddesc:UARTDSRINV}\item [UART\_DSR\_INV] Set this bit to invert the level of UART DSR signal. (R/W)
\label{fielddesc:UARTTXDINV}\item [UART\_TXD\_INV] Set this bit to invert the level of UART TXD signal. (R/W)
\label{fielddesc:UARTRTSINV}\item [UART\_RTS\_INV] Set this bit to invert the level of UART RTS signal. (R/W)
\label{fielddesc:UARTDTRINV}\item [UART\_DTR\_INV] Set this bit to invert the level of UART DTR signal. (R/W)
\label{fielddesc:UARTTICKREFALWAYSON}\item [UART\_TICK\_REF\_ALWAYS\_ON] This register is used to select the clock.
1: APB\_CLK.
0: REF\_TICK. (R/W)
\label{fielddesc:UARTMEMCLKEN}\item [UART\_MEM\_CLK\_EN] The signal to enable UART RAM clock gating.
1: UART RAM powers on, the data of which can be read and written.
0: UART RAM powers down. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_CONF1\_REG}{\hexprefix{}0024}\label{regdesc:UARTCONF1REG}
\regfield{UART\_RX\_TOUT\_EN}{1}{31}{{0}}%
\regfield{UART\_RX\_FLOW\_EN}{1}{30}{{0}}%
\regfield{UART\_RX\_TOUT\_FLOW\_DIS}{1}{29}{{0}}%
\regfield{(reserved)}{11}{18}{00000000000}%
\regfield{UART\_TXFIFO\_EMPTY\_THRHD}{9}{9}{{\hexprefix{}60}}%
\regfield{UART\_RXFIFO\_FULL\_THRHD}{9}{0}{{\hexprefix{}60}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXFIFOFULLTHRHD}\item [UART\_RXFIFO\_FULL\_THRHD] An UART\_RXFIFO\_FULL\_INT interrupt is generated when the receiver receives more data than this register's value. (R/W)
\label{fielddesc:UARTTXFIFOEMPTYTHRHD}\item [UART\_TXFIFO\_EMPTY\_THRHD] An UART\_TXFIFO\_EMPTY\_INT interrupt is generated when the number of data bytes in TX FIFO is less than this register's value. (R/W)
\label{fielddesc:UARTRXTOUTFLOWDIS}\item [UART\_RX\_TOUT\_FLOW\_DIS] Set this bit to stop accumulating idle\_cnt when hardware flow control works. (R/W)
\label{fielddesc:UARTRXFLOWEN}\item [UART\_RX\_FLOW\_EN] This is the flow enable bit for UART receiver.
1: Choose software flow control with configuring sw\_rts signal. 0: Disable software flow control. (R/W)
\label{fielddesc:UARTRXTOUTEN}\item [UART\_RX\_TOUT\_EN] This is the enable bit for UART receiver's timeout function. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_FLOW\_CONF\_REG}{\hexprefix{}0034}\label{regdesc:UARTFLOWCONFREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{UART\_SEND\_XOFF}{1}{5}{{0}}%
\regfield{UART\_SEND\_XON}{1}{4}{{0}}%
\regfield{UART\_FORCE\_XOFF}{1}{3}{{0}}%
\regfield{UART\_FORCE\_XON}{1}{2}{{0}}%
\regfield{UART\_XONOFF\_DEL}{1}{1}{{0}}%
\regfield{UART\_SW\_FLOW\_CON\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTSWFLOWCONEN}\item [UART\_SW\_FLOW\_CON\_EN] Set this bit to enable software flow control. When UART receives flow control characters XON or XOFF, which can be configured by UART\_XON\_CHAR or UART\_XOFF\_CHAR respectively, UART\_SW\_XON\_INT or UART\_SW\_XOFF\_INT interrupts can be triggered if enabled.  (R/W)
\label{fielddesc:UARTXONOFFDEL}\item [UART\_XONOFF\_DEL] Set this bit to remove flow control characters from the received data. (R/W)
\label{fielddesc:UARTFORCEXON}\item [UART\_FORCE\_XON] Set this bit to force the transmitter to send data. (R/W)
\label{fielddesc:UARTFORCEXOFF}\item [UART\_FORCE\_XOFF] Set this bit to stop the  transmitter from sending data. (R/W)
\label{fielddesc:UARTSENDXON}\item [UART\_SEND\_XON] Set this bit to send an XON character. This bit is cleared by hardware automatically. (R/W)
\label{fielddesc:UARTSENDXOFF}\item [UART\_SEND\_XOFF] Set this bit to send an XOFF character. This bit is cleared by hardware automatically. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_SLEEP\_CONF\_REG}{\hexprefix{}0038}\label{regdesc:UARTSLEEPCONFREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{UART\_ACTIVE\_THRESHOLD}{10}{0}{{\hexprefix{}f0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTACTIVETHRESHOLD}\item [UART\_ACTIVE\_THRESHOLD] The UART is activated from Light-sleep mode when the input RXD edge changes more times than this register's value plus 3. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_SWFC\_CONF0\_REG}{\hexprefix{}003C}\label{regdesc:UARTSWFCCONF0REG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{UART\_XOFF\_CHAR}{8}{9}{{\hexprefix{}13}}%
\regfield{UART\_XOFF\_THRESHOLD}{9}{0}{{\hexprefix{}e0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTXOFFTHRESHOLD}\item [UART\_XOFF\_THRESHOLD] When the number of data bytes in RX FIFO is more than this register's value with UART\_SW\_FLOW\_CON\_EN set to 1, the transmitter sends an XOFF character. (R/W)
\label{fielddesc:UARTXOFFCHAR}\item [UART\_XOFF\_CHAR] This register stores the XOFF flow control character. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_SWFC\_CONF1\_REG}{\hexprefix{}0040}\label{regdesc:UARTSWFCCONF1REG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{UART\_XON\_CHAR}{8}{9}{{\hexprefix{}11}}%
\regfield{UART\_XON\_THRESHOLD}{9}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTXONTHRESHOLD}\item [UART\_XON\_THRESHOLD] When the number of data bytes in RX FIFO is less than this register's value with UART\_SW\_FLOW\_CON\_EN set to 1, the transmitter sends an XON character. (R/W)
\label{fielddesc:UARTXONCHAR}\item [UART\_XON\_CHAR] This register stores the XON flow control character. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_IDLE\_CONF\_REG}{\hexprefix{}0044}\label{regdesc:UARTIDLECONFREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{UART\_TX\_BRK\_NUM}{8}{20}{{\hexprefix{}a}}%
\regfield{UART\_TX\_IDLE\_NUM}{10}{10}{{\hexprefix{}100}}%
\regfield{UART\_RX\_IDLE\_THRHD}{10}{0}{{\hexprefix{}100}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXIDLETHRHD}\item [UART\_RX\_IDLE\_THRHD] A frame end signal is generated when the receiver takes more time to receive one byte data than this register's value, in the unit of bit time (the time it takes to transfer one bit). (R/W)
\label{fielddesc:UARTTXIDLENUM}\item [UART\_TX\_IDLE\_NUM] This register is used to configure the duration time between transfers, in the unit of bit time (the time it takes to transfer one bit). (R/W)
\label{fielddesc:UARTTXBRKNUM}\item [UART\_TX\_BRK\_NUM] This register is used to configure the number of 0 to be sent after the process of sending data is done. It is active when UART\_TXD\_BRK is set to 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_RS485\_CONF\_REG}{\hexprefix{}0048}\label{regdesc:UARTRS485CONFREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{UART\_RS485\_TX\_DLY\_NUM}{4}{6}{{\hexprefix{}0}}%
\regfield{UART\_RS485\_RX\_DLY\_NUM}{1}{5}{{0}}%
\regfield{UART\_RS485RXBY\_TX\_EN}{1}{4}{{0}}%
\regfield{UART\_RS485TX\_RX\_EN}{1}{3}{{0}}%
\regfield{UART\_DL1\_EN}{1}{2}{{0}}%
\regfield{UART\_DL0\_EN}{1}{1}{{0}}%
\regfield{UART\_RS485\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRS485EN}\item [UART\_RS485\_EN] Set this bit to choose RS485 mode. (R/W)
\label{fielddesc:UARTDL0EN}\item [UART\_DL0\_EN] Set this bit to delay the stop bit by 1 bit. (R/W)
\label{fielddesc:UARTDL1EN}\item [UART\_DL1\_EN] Set this bit to delay the stop bit by 1 bit. (R/W)
\label{fielddesc:UARTRS485TXRXEN}\item [UART\_RS485TX\_RX\_EN] Set this bit to enable the receiver could receive data when the the transmitter is transmitting data in RS485 mode. (R/W)
\label{fielddesc:UARTRS485RXBYTXEN}\item [UART\_RS485RXBY\_TX\_EN] 1: enable RS485 transmitter to send data when RS485 receiver line is busy.
0: RS485 transmitter should not send data when its the receiver is busy. (R/W)
\label{fielddesc:UARTRS485RXDLYNUM}\item [UART\_RS485\_RX\_DLY\_NUM] This register is used to delay the receiver's internal data signal. (R/W)
\label{fielddesc:UARTRS485TXDLYNUM}\item [UART\_RS485\_TX\_DLY\_NUM] This register is used to delay the transmitter's internal data signal. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_AUTOBAUD\_REG}{\hexprefix{}0018}\label{regdesc:UARTAUTOBAUDREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{UART\_GLITCH\_FILT}{8}{8}{{\hexprefix{}10}}%
\regfield{(reserved)}{7}{1}{0000000}%
\regfield{UART\_AUTOBAUD\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTAUTOBAUDEN}\item [UART\_AUTOBAUD\_EN] This is the enable bit for baud rate detection. (R/W)
\label{fielddesc:UARTGLITCHFILT}\item [UART\_GLITCH\_FILT] When input pulse width is lower than this value, the pulse is ignored.
This register is used in autobaud detection. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_LOWPULSE\_REG}{\hexprefix{}0028}\label{regdesc:UARTLOWPULSEREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{UART\_LOWPULSE\_MIN\_CNT}{20}{0}{{\hexprefix{}fffff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTLOWPULSEMINCNT}\item [UART\_LOWPULSE\_MIN\_CNT] This register stores the value of the minimum duration time of the low level pulse. It is used in baud rate detection. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_HIGHPULSE\_REG}{\hexprefix{}002C}\label{regdesc:UARTHIGHPULSEREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{UART\_HIGHPULSE\_MIN\_CNT}{20}{0}{{\hexprefix{}fffff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTHIGHPULSEMINCNT}\item [UART\_HIGHPULSE\_MIN\_CNT] This register stores  the value of the maximum duration time for the high level pulse. It is used in baud rate detection. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_RXD\_CNT\_REG}{\hexprefix{}0030}\label{regdesc:UARTRXDCNTREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{UART\_RXD\_EDGE\_CNT}{10}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXDEDGECNT}\item [UART\_RXD\_EDGE\_CNT] This register stores the count of RXD edge change. It is used in baud rate detection. As baud rate registers UART\_REG\_LOWPULSE\_MIN\_CNT, UART\_REG\_HIGHPULSE\_MIN\_CNT, UART\_REG\_POSEDGE\_MIN\_CNT, and UART\_REG\_NEGEDGE\_MIN\_CNT always record the minimal value, UART\_REG\_RXD\_EDGE\_CNT indicates the statistic number of RXD edge to find out the minimal value for these baud rate registers. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_POSPULSE\_REG}{\hexprefix{}006C}\label{regdesc:UARTPOSPULSEREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{UART\_POSEDGE\_MIN\_CNT}{20}{0}{{\hexprefix{}fffff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTPOSEDGEMINCNT}\item [UART\_POSEDGE\_MIN\_CNT] This register stores the minimal input clock count between two positive edges. It is used in baud rate detection. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_NEGPULSE\_REG}{\hexprefix{}0070}\label{regdesc:UARTNEGPULSEREG}
\regfield{(reserved)}{12}{20}{000000000000}%
\regfield{UART\_NEGEDGE\_MIN\_CNT}{20}{0}{{\hexprefix{}fffff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTNEGEDGEMINCNT}\item [UART\_NEGEDGE\_MIN\_CNT] This register stores the minimal input clock count between two negative edges. It is used in baud rate detection. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_STATUS\_REG}{\hexprefix{}001C}\label{regdesc:UARTSTATUSREG}
\regfield{UART\_TXD}{1}{31}{{\hexprefix{}0}}%
\regfield{UART\_RTSN}{1}{30}{{0}}%
\regfield{UART\_DTRN}{1}{29}{{0}}%
\regfield{(reserved)}{3}{26}{000}%
\regfield{UART\_TXFIFO\_CNT}{10}{16}{{\hexprefix{}0}}%
\regfield{UART\_RXD}{1}{15}{{0}}%
\regfield{UART\_CTSN}{1}{14}{{0}}%
\regfield{UART\_DSRN}{1}{13}{{0}}%
\regfield{(reserved)}{3}{10}{000}%
\regfield{UART\_RXFIFO\_CNT}{10}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXFIFOCNT}\item [UART\_RXFIFO\_CNT] Stores the number of valid data bytes in RX FIFO. (RO)
\label{fielddesc:UARTDSRN}\item [UART\_DSRN] This register represents the level of the internal UART DSR signal. (RO)
\label{fielddesc:UARTCTSN}\item [UART\_CTSN] This register represents the level of the internal UART CTS signal. (RO)
\label{fielddesc:UARTRXD}\item [UART\_RXD] This register represents the  level of the internal UART RXD signal. (RO)
\label{fielddesc:UARTTXFIFOCNT}\item [UART\_TXFIFO\_CNT] Stores the number of data bytes in TX FIFO. (RO)
\label{fielddesc:UARTDTRN}\item [UART\_DTRN] This bit represents the level of the internal UART DTR signal. (RO)
\label{fielddesc:UARTRTSN}\item [UART\_RTSN] This bit represents the level of the internal UART RTS signal. (RO)
\label{fielddesc:UARTTXD}\item [UART\_TXD] This bit represents the  level of the internal UART TXD signal. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_MEM\_TX\_STATUS\_REG}{\hexprefix{}0060}\label{regdesc:UARTMEMTXSTATUSREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{UART\_TX\_RADDR}{10}{11}{{\hexprefix{}0}}%
\regfield{(reserved)}{1}{10}{0}%
\regfield{UART\_APB\_TX\_WADDR}{10}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTAPBTXWADDR}\item [UART\_APB\_TX\_WADDR] This register stores the offset address in TX FIFO when software writes TX FIFO via APB. (RO)
\label{fielddesc:UARTTXRADDR}\item [UART\_TX\_RADDR] This register stores the offset address in TX FIFO when TX FSM reads data via Tx\_FIFO\_Ctrl. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_MEM\_RX\_STATUS\_REG}{\hexprefix{}0064}\label{regdesc:UARTMEMRXSTATUSREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{UART\_RX\_WADDR}{10}{11}{{\hexprefix{}0}}%
\regfield{(reserved)}{1}{10}{0}%
\regfield{UART\_APB\_RX\_RADDR}{10}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTAPBRXRADDR}\item [UART\_APB\_RX\_RADDR] This register stores the offset address in RX\_FIFO when software reads data from RX FIFO via APB. (RO)
\label{fielddesc:UARTRXWADDR}\item [UART\_RX\_WADDR] This register stores the offset address in RX FIFO when Rx\_FIFO\_Ctrl writes RX FIFO. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_FSM\_STATUS\_REG}{\hexprefix{}0068}\label{regdesc:UARTFSMSTATUSREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{UART\_ST\_UTX\_OUT}{4}{4}{{\hexprefix{}0}}%
\regfield{UART\_ST\_URX\_OUT}{4}{0}{{\hexprefix{}0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTSTURXOUT}\item [UART\_ST\_URX\_OUT] This is the status register of the receiver. (RO)
\label{fielddesc:UARTSTUTXOUT}\item [UART\_ST\_UTX\_OUT] This is the status register of the transmitter. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_AT\_CMD\_PRECNT\_REG}{\hexprefix{}004C}\label{regdesc:UARTATCMDPRECNTREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{UART\_PRE\_IDLE\_NUM}{16}{0}{{\hexprefix{}901}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTPREIDLENUM}\item [UART\_PRE\_IDLE\_NUM] This register is used to configure the idle duration time before the first AT\_CMD is received by the receiver.
It will not take the next data received as AT\_CMD character when the duration is less than this register's value. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_AT\_CMD\_POSTCNT\_REG}{\hexprefix{}0050}\label{regdesc:UARTATCMDPOSTCNTREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{UART\_POST\_IDLE\_NUM}{16}{0}{{\hexprefix{}901}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTPOSTIDLENUM}\item [UART\_POST\_IDLE\_NUM] This register is used to configure the duration time between the last AT\_CMD and the next data.
It will not take the previous data as AT\_CMD character when the duration is less than this register's value. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_AT\_CMD\_GAPTOUT\_REG}{\hexprefix{}0054}\label{regdesc:UARTATCMDGAPTOUTREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{UART\_RX\_GAP\_TOUT}{16}{0}{{11}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTRXGAPTOUT}\item [UART\_RX\_GAP\_TOUT] This register is used to configure the duration time between the AT\_CMD characters.
It will not take the data as continuous AT\_CMD characters when the duration time is less than this register's value. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_AT\_CMD\_CHAR\_REG}{\hexprefix{}0058}\label{regdesc:UARTATCMDCHARREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{UART\_CHAR\_NUM}{8}{8}{{\hexprefix{}3}}%
\regfield{UART\_AT\_CMD\_CHAR}{8}{0}{{\hexprefix{}2b}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTATCMDCHAR}\item [UART\_AT\_CMD\_CHAR] This register is used to configure the content of AT\_CMD character. (R/W)
\label{fielddesc:UARTCHARNUM}\item [UART\_CHAR\_NUM] This register is used to configure the number of continuous AT\_CMD characters received by the receiver. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{UART\_DATE\_REG}{\hexprefix{}0074}\label{regdesc:UARTDATEREG}
\regfield{UART\_DATE}{32}{0}{{\hexprefix{}18082800}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:UARTDATE}\item [UART\_DATE] This is the version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}
