\begin{longtable}[c]{|p{7.5cm}|p{7.5cm}|}
  \caption{IN and OUT Transactions in Slave Mode}
  \label{tab:usbotghs-in-and-out-transaction}  
  \\\hline
  \rowcolor{lightgray}
  \textbf{Host Mode} & \textbf{Device Mode} \\\hline
  \hline
\endfirsthead
\hline
\rowcolor{lightgray}
  \textbf{Host Mode} & \textbf{Device Mode} \\\hline
\hline
\endhead
\hline
\endfoot
\hline
\endlastfoot
 \multicolumn{2}{|l|}{OUT Transactions} \\\hline
 \begin{enumerate}
     \item Software specifies the size of the data packet and the number of data packets (1 data packet) in the USB\_HCTSIZ\regindex{n}\_REG register, enables the channel, then copies the packet’s data payload into the TX FIFO.
     \item When the last DWORD of the data payload has been pushed, the controller core will automatically write a request into the appropriate request queue.
     \item If the transaction is successful, the USB\_XFERCOMPL interrupt will be generated. If the transaction is unsuccessful, an error interrupt, e.g., USB\_H\_NACK\regindex{n} will occur.
 \end{enumerate}
  & 
 \begin{enumerate}
     \item Software specifies the expected size of the data packet (1 MPS) and the number of data packets (1 data packet) in the USB\_DOEPTSIZ\regindex{n}\_REG register. Once the endpoint is enabled, it will wait for the host to transmit a packet to it.
     \item The received packet will be pushed into the RX FIFO along with a packet status entry.
     \item If the transaction is unsuccessful, e.g., due to a full RX FIFO, the endpoint will automatically NAK the incoming packet.
 \end{enumerate}
 \\\hline
  \multicolumn{2}{|l|}{IN Transactions} \\\hline
 \begin{enumerate}
     \item Software specifies the expected size of the data packet and the number of packets (1 data packet) in the USB\_HCTSIZ\regindex{n}\_REG register, then enables the channel.
     \item The controller core will automatically write a request into the appropriate request queue.
     \item If the transaction is successful, the received data along with a status entry should be written to the RX FIFO. If the transaction is unsuccessful, an error interrupt, e.g., USB\_H\_NACK\regindex{n} will occur.
 \end{enumerate}
 &
 \begin{enumerate}
     \item Software specifies the size of the data packet and the number of data packets (1 data packet) in the USB\_DIEPTSIZ\regindex{n}\_REG register. Once the endpoint is enabled, it will wait for the host to read the packet.
     \item When the packet has been transmitted, the USB\_XFERCOMPL interrupt will be generated.
 \end{enumerate}
 \\\hline
\end{longtable}