\begin{register}{H}{RTC\_CNTL\_OPTIONS0\_REG}{0x0000}\label{regdesc:RTCCNTLOPTIONS0REG}
\regfield{RTC\_CNTL\_SW\_SYS\_RST}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_NORST}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_RST}{1}{29}{{0}}%
\regfield{(reserved)}{15}{14}{000000000000000}%
\regfield{RTC\_CNTL\_XTL\_FORCE\_PU}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_XTL\_FORCE\_PD}{1}{12}{{0}}%
\regfield{RTC\_CNTL\_BBPLL\_FORCE\_PU}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_BBPLL\_FORCE\_PD}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PU}{1}{9}{{0}}%
\regfield{RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PD}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_BB\_I2C\_FORCE\_PU}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_BB\_I2C\_FORCE\_PD}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_SW\_PROCPU\_RST}{1}{5}{{0}}%
\regfield{(reserved)}{1}{4}{0}%
\regfield{RTC\_CNTL\_SW\_STALL\_PROCPU\_C0}{2}{2}{{0x0}}%
\regfield{(reserved)}{2}{0}{00}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWSTALLPROCPUC0}\item [RTC\_CNTL\_SW\_STALL\_PROCPU\_C0] Write 0x2 to stall the CPU by SW. Valid only when \hyperref[fielddesc:RTCCNTLSWSTALLPROCPUC1]{RTC\_CNTL\_SW\_STALL\_PROCPU\_C1} is configured to 0x21. (R/W)
\label{fielddesc:RTCCNTLSWPROCPURST}\item [RTC\_CNTL\_SW\_PROCPU\_RST] Write 1 to reset the CPU by SW. (WO)
\label{fielddesc:RTCCNTLBBI2CFORCEPD}\item [RTC\_CNTL\_BB\_I2C\_FORCE\_PD] Write 1 to FPD BB\_I2C. (R/W)
\label{fielddesc:RTCCNTLBBI2CFORCEPU}\item [RTC\_CNTL\_BB\_I2C\_FORCE\_PU] Write 1 to FPU BB\_I2C. (R/W)
\label{fielddesc:RTCCNTLBBPLLI2CFORCEPD}\item [RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PD] Write 1 to FPD BB\_PLL\_I2C. (R/W)
\label{fielddesc:RTCCNTLBBPLLI2CFORCEPU}\item [RTC\_CNTL\_BBPLL\_I2C\_FORCE\_PU] Write 1 to FPU BB\_PLL\_I2C. (R/W)
\label{fielddesc:RTCCNTLBBPLLFORCEPD}\item [RTC\_CNTL\_BBPLL\_FORCE\_PD] Write 1 to FPD BB\_PLL. (R/W)
\label{fielddesc:RTCCNTLBBPLLFORCEPU}\item [RTC\_CNTL\_BBPLL\_FORCE\_PU] Write 1 to FPU BB\_PLL. (R/W)
\label{fielddesc:RTCCNTLXTLFORCEPD}\item [RTC\_CNTL\_XTL\_FORCE\_PD] Write 1 to FPD the XTAL\_CLK. (R/W)
\label{fielddesc:RTCCNTLXTLFORCEPU}\item [RTC\_CNTL\_XTL\_FORCE\_PU] Write 1 to FPU the XTAL\_CLK. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCERST}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_RST] Write 1 to force reset the digital system in deep-sleep. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCENORST}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_NORST] Write 1 to disable force reset to the digital system in deep-sleep. (R/W)
\label{fielddesc:RTCCNTLSWSYSRST}\item [RTC\_CNTL\_SW\_SYS\_RST] Write 1 to reset the digital power category via SW. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLP\_TIMER0\_REG}{0x0004}\label{regdesc:RTCCNTLSLPTIMER0REG}
\regfield{RTC\_CNTL\_SLP\_VAL\_LO}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPVALLO}\item [RTC\_CNTL\_SLP\_VAL\_LO] Configures the lower 32 bits of the trigger threshold for the RTC timer. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLP\_TIMER1\_REG}{0x0008}\label{regdesc:RTCCNTLSLPTIMER1REG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_ALARM\_EN}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_SLP\_VAL\_HI}{16}{0}{{0x00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPVALHI}\item [RTC\_CNTL\_SLP\_VAL\_HI] Configures the higher 16 bits of the trigger threshold for the RTC timer. (R/W)
\label{fielddesc:RTCCNTLMAINTIMERALARMEN}\item [RTC\_CNTL\_MAIN\_TIMER\_ALARM\_EN] Write 1 to enable the timer alarm. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIME\_UPDATE\_REG}{0x000C}\label{regdesc:RTCCNTLTIMEUPDATEREG}
\regfield{RTC\_CNTL\_TIME\_UPDATE}{1}{31}{{0}}%
\regfield{(reserved)}{1}{30}{0}%
\regfield{RTC\_CNTL\_TIMER\_SYS\_RST}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_TIMER\_XTL\_OFF}{1}{28}{{0}}%
\regfield{RTC\_CNTL\_TIMER\_SYS\_STALL}{1}{27}{{0}}%
\regfield{(reserved)}{27}{0}{000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTIMERSYSSTALL}\item [RTC\_CNTL\_TIMER\_SYS\_STALL] Write 1 to enable recording digital system stall time. (R/W)
\label{fielddesc:RTCCNTLTIMERXTLOFF}\item [RTC\_CNTL\_TIMER\_XTL\_OFF] Write 1 to enable recording XTAL\_CLK OFF time. (R/W)
\label{fielddesc:RTCCNTLTIMERSYSRST}\item [RTC\_CNTL\_TIMER\_SYS\_RST] Write 1 to enable recording digital system reset time. (R/W)
\label{fielddesc:RTCCNTLTIMEUPDATE}\item [RTC\_CNTL\_TIME\_UPDATE] Write 1 to update register with RTC timer. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_TIME\_LOW0\_REG}{0x0010}\label{regdesc:RTCCNTLTIMELOW0REG}
\regfield{RTC\_CNTL\_TIMER\_VALUE0\_LOW}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTIMERVALUE0LOW}\item [RTC\_CNTL\_TIMER\_VALUE0\_LOW] Represents the lower 32 bits of RTC timer 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIME\_HIGH0\_REG}{0x0014}\label{regdesc:RTCCNTLTIMEHIGH0REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{RTC\_CNTL\_TIMER\_VALUE0\_HIGH}{16}{0}{{0x00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTIMERVALUE0HIGH}\item [RTC\_CNTL\_TIMER\_VALUE0\_HIGH] Represents the higher 16 bits of RTC timer 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STATE0\_REG}{0x0018}\label{regdesc:RTCCNTLSTATE0REG}
\regfield{RTC\_CNTL\_SLEEP\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_SLP\_REJECT}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_SDIO\_ACTIVE\_IND}{1}{28}{{0}}%
\regfield{(reserved)}{5}{23}{00000}%
\regfield{RTC\_CNTL\_APB2RTC\_BRIDGE\_SEL}{1}{22}{{0}}%
\regfield{(reserved)}{20}{2}{00000000000000000000}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_CAUSE\_CLR}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SW\_CPU\_INT}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWCPUINT}\item [RTC\_CNTL\_SW\_CPU\_INT] Write 1 to send a SW RTC interrupt to CPU. (R/W)
\label{fielddesc:RTCCNTLSLPREJECTCAUSECLR}\item [RTC\_CNTL\_SLP\_REJECT\_CAUSE\_CLR] Write 1 to clear the RTC reject-to-sleep cause. (R/W)
\label{fielddesc:RTCCNTLAPB2RTCBRIDGESEL}\item [RTC\_CNTL\_APB2RTC\_BRIDGE\_SEL] Configures the APB to RTC option. \\
0x0: APB to RTC using sync\\
0x1: APB to RTC using bridge\\
 (R/W)
\label{fielddesc:RTCCNTLSDIOACTIVEIND}\item [RTC\_CNTL\_SDIO\_ACTIVE\_IND] Represents the SDIO is active. (R/W)
\label{fielddesc:RTCCNTLSLPWAKEUP}\item [RTC\_CNTL\_SLP\_WAKEUP] Represents wakeup events. (R/W)
\label{fielddesc:RTCCNTLSLPREJECT}\item [RTC\_CNTL\_SLP\_REJECT] Represents reject-to-sleep events. (R/W)
\label{fielddesc:RTCCNTLSLEEPEN}\item [RTC\_CNTL\_SLEEP\_EN] Write 1 to send the chip to sleep. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIMER1\_REG}{0x001C}\label{regdesc:RTCCNTLTIMER1REG}
\regfield{RTC\_CNTL\_PLL\_BUF\_WAIT}{8}{24}{{40}}%
\regfield{RTC\_CNTL\_XTL\_BUF\_WAIT}{10}{14}{{80}}%
\regfield{RTC\_CNTL\_FOSC\_WAIT}{8}{6}{{0x10}}%
\regfield{RTC\_CNTL\_CPU\_STALL\_WAIT}{5}{1}{{1}}%
\regfield{RTC\_CNTL\_CPU\_STALL\_EN}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLCPUSTALLEN}\item [RTC\_CNTL\_CPU\_STALL\_EN] Write 1 to enable CPU stalling. (R/W)
\label{fielddesc:RTCCNTLCPUSTALLWAIT}\item [RTC\_CNTL\_CPU\_STALL\_WAIT] Configures CPU stall wait cycles using  RTC\_FAST\_CLK. (R/W)
\label{fielddesc:RTCCNTLFOSCWAIT}\item [RTC\_CNTL\_FOSC\_WAIT] Configures the RC\_FAST\_CLK wait cycles using RTC\_SLOW\_CLK. (R/W)
\label{fielddesc:RTCCNTLXTLBUFWAIT}\item [RTC\_CNTL\_XTL\_BUF\_WAIT] Configures XTAL\_CLK wait cycles using RTC\_SLOW\_CLK. (R/W)
\label{fielddesc:RTCCNTLPLLBUFWAIT}\item [RTC\_CNTL\_PLL\_BUF\_WAIT] Configures the PLL\_CLK wait cycles using RTC\_SLOW\_CLK. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIMER2\_REG}{0x0020}\label{regdesc:RTCCNTLTIMER2REG}
\regfield{RTC\_CNTL\_MIN\_TIME\_FOSC\_OFF}{8}{24}{{0x1}}%
\regfield{(reserved)}{24}{0}{000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\raggedright\label{fielddesc:RTCCNTLMINTIMEFOSCOFF}\item [RTC\_CNTL\_MIN\_TIME\_FOSC\_OFF] Configures the minimal cycle for RC\_FAST\_CLK (using RTC\_SLOW\_CLK) when powered down. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_ANA\_CONF\_REG}{0x002C}\label{regdesc:RTCCNTLANACONFREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{RTC\_CNTL\_SAR\_I2C\_PU}{1}{22}{{1}}%
\regfield{(reserved)}{2}{20}{00}%
\regfield{RTC\_CNTL\_I2C\_RESET\_POR\_FORCE\_PU}{1}{19}{{0}}%
\regfield{RTC\_CNTL\_I2C\_RESET\_POR\_FORCE\_PD}{1}{18}{{1}}%
\regfield{(reserved)}{18}{0}{000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLI2CRESETPORFORCEPD}\item [RTC\_CNTL\_I2C\_RESET\_POR\_FORCE\_PD] Write 1 to force not bypass I2C power-on reset. (R/W)
\label{fielddesc:RTCCNTLI2CRESETPORFORCEPU}\item [RTC\_CNTL\_I2C\_RESET\_POR\_FORCE\_PU] Write 1 to force bypass I2C power-on reset. (R/W)
\label{fielddesc:RTCCNTLSARI2CPU}\item [RTC\_CNTL\_SAR\_I2C\_PU] Write 1 to FPU the SAR\_I2C. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WAKEUP\_STATE\_REG}{0x0034}\label{regdesc:RTCCNTLWAKEUPSTATEREG}
\regfield{RTC\_CNTL\_WAKEUP\_ENA}{17}{15}{{12}}%
\regfield{(reserved)}{15}{0}{000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWAKEUPENA}\item [RTC\_CNTL\_WAKEUP\_ENA] Configures the wakeup source. For details, please refer to Table \ref{tab:lpm-wakeup-source}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE0\_REG}{0x0048}\label{regdesc:RTCCNTLSTORE0REG}
\regfield{RTC\_CNTL\_SCRATCH0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSCRATCH0}\item [RTC\_CNTL\_SCRATCH0] Reservation register 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE1\_REG}{0x004C}\label{regdesc:RTCCNTLSTORE1REG}
\regfield{RTC\_CNTL\_SCRATCH1}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSCRATCH1}\item [RTC\_CNTL\_SCRATCH1] Reservation register 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE2\_REG}{0x0050}\label{regdesc:RTCCNTLSTORE2REG}
\regfield{RTC\_CNTL\_SCRATCH2}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSCRATCH2}\item [RTC\_CNTL\_SCRATCH2] Reservation register 2. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE3\_REG}{0x0054}\label{regdesc:RTCCNTLSTORE3REG}
\regfield{RTC\_CNTL\_SCRATCH3}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSCRATCH3}\item [RTC\_CNTL\_SCRATCH3] Reservation register 3. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_EXT\_WAKEUP\_CONF\_REG}{0x005C}\label{regdesc:RTCCNTLEXTWAKEUPCONFREG}
\regfield{RTC\_CNTL\_GPIO\_WAKEUP\_FILTER}{1}{31}{{0}}%
\regfield{(reserved)}{31}{0}{0000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLGPIOWAKEUPFILTER}\item [RTC\_CNTL\_GPIO\_WAKEUP\_FILTER] Write 1 to enable the GPIO wakeup event filter. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLP\_REJECT\_CONF\_REG}{0x0060}\label{regdesc:RTCCNTLSLPREJECTCONFREG}
\regfield{RTC\_CNTL\_DEEP\_SLP\_REJECT\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_LIGHT\_SLP\_REJECT\_EN}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_SLEEP\_REJECT\_ENA}{18}{12}{{0}}%
\regfield{(reserved)}{12}{0}{000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLEEPREJECTENA}\item [RTC\_CNTL\_SLEEP\_REJECT\_ENA] Write 1 to enable reject-to-sleep. (R/W)
\label{fielddesc:RTCCNTLLIGHTSLPREJECTEN}\item [RTC\_CNTL\_LIGHT\_SLP\_REJECT\_EN] Write 1 to enable reject-to-light-sleep. (R/W)
\label{fielddesc:RTCCNTLDEEPSLPREJECTEN}\item [RTC\_CNTL\_DEEP\_SLP\_REJECT\_EN] Write 1 to enable reject-to-deep-sleep. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_CLK\_CONF\_REG}{0x0068}\label{regdesc:RTCCNTLCLKCONFREG}
\regfield{RTC\_CNTL\_ANA\_CLK\_RTC\_SEL}{2}{30}{{0}}%
\regfield{RTC\_CNTL\_FAST\_CLK\_RTC\_SEL}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_XTAL\_GLOBAL\_FORCE\_NOGATING}{1}{28}{{1}}%
\regfield{RTC\_CNTL\_XTAL\_GLOBAL\_FORCE\_GATING}{1}{27}{{0}}%
\regfield{RTC\_CNTL\_FOSC\_FORCE\_PU}{1}{26}{{0}}%
\regfield{RTC\_CNTL\_FOSC\_FORCE\_PD}{1}{25}{{0}}%
\regfield{RTC\_CNTL\_FOSC\_DFREQ}{8}{17}{{172}}%
\regfield{RTC\_CNTL\_FOSC\_FORCE\_NOGATING}{1}{16}{{0}}%
\regfield{RTC\_CNTL\_XTAL\_FORCE\_NOGATING}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_FOSC\_DIV\_SEL}{3}{12}{{3}}%
\regfield{(reserved)}{1}{11}{0}%
\regfield{RTC\_CNTL\_DIG\_CLK8M\_EN}{1}{10}{{0}}%
\regfield{(reserved)}{1}{9}{{1}}%
\regfield{(reserved)}{1}{8}{{0}}%
\regfield{RTC\_CNTL\_ENB\_FOSC\_DIV}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_ENB\_FOSC}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_FOSC\_DIV}{2}{4}{{1}}%
\regfield{RTC\_CNTL\_FOSC\_DIV\_SEL\_VLD}{1}{3}{{1}}%
\regfield{RTC\_CNTL\_EFUSE\_CLK\_FORCE\_NOGATING}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_EFUSE\_CLK\_FORCE\_GATING}{1}{1}{{0}}%
\regfield{(reserved)}{1}{0}{0}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLEFUSECLKFORCEGATING}\item [RTC\_CNTL\_EFUSE\_CLK\_FORCE\_GATING] Write 1 to FPU the eFuse clock gating. (R/W)
\label{fielddesc:RTCCNTLEFUSECLKFORCENOGATING}\item [RTC\_CNTL\_EFUSE\_CLK\_FORCE\_NOGATING] Write 1 to FPD the eFuse clock gating. (R/W)
\label{fielddesc:RTCCNTLFOSCDIVSELVLD}\item [RTC\_CNTL\_FOSC\_DIV\_SEL\_VLD] Write 1 to synchronize \hyperref[fielddesc:RTCCNTLFOSCDIVSEL]{RTC\_CNTL\_FOSC\_DIV\_SEL}. Note that you have to invalidate the bus before modifying the frequency divider, then validate the new divider clock. (R/W)
\label{fielddesc:RTCCNTLFOSCDIV}\item [RTC\_CNTL\_FOSC\_DIV] Configures the RC\_FAST\_DIV\_CLK divider.\\
0x0: divided by 128\\
0x1: divided by 256\\
0x2: divided by 512\\
0x3: divided by 1024\\
 (R/W)
\label{fielddesc:RTCCNTLENBFOSC}\item [RTC\_CNTL\_ENB\_FOSC] Write 1 to disable RC\_FAST\_CLK and RC\_FAST\_DIV\_CLK. (R/W)
\label{fielddesc:RTCCNTLENBFOSCDIV}\item [RTC\_CNTL\_ENB\_FOSC\_DIV] Configures the RC\_FAST\_CLK divider.\\
0x0: RC\_FAST\_CLK divided by 256\\
0x1: RC\_FAST\_CLK\\
 (R/W)
\label{fielddesc:RTCCNTLDIGCLK8MEN}\item [RTC\_CNTL\_DIG\_FOSC\_EN] Write 1 to enable RC\_FAST\_CLK for the digital system. (R/W)
\label{fielddesc:RTCCNTLFOSCDIVSEL}\item [RTC\_CNTL\_FOSC\_DIV\_SEL] Represents the RC\_FAST\_CLK divider, which is \hyperref[fielddesc:RTCCNTLFOSCDIVSEL]{RTC\_CNTL\_FOSC\_DIV\_SEL} + 1. (R/W)
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_CLK\_CONF\_REG}{0x0068}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:RTCCNTLXTALFORCENOGATING}\item [RTC\_CNTL\_XTAL\_FORCE\_NOGATING] Write 1 to force no gating to XTAL\_CLK during sleep. (R/W)
\label{fielddesc:RTCCNTLFOSCFORCENOGATING}\item [RTC\_CNTL\_FOSC\_FORCE\_NOGATING] Write 1 to disable force gating to XTAL\_CLK during sleep. (R/W)
\label{fielddesc:RTCCNTLFOSCDFREQ}\item [RTC\_CNTL\_FOSC\_DFREQ] Configures the  RC\_FAST\_CLK frequency. (R/W)
\label{fielddesc:RTCCNTLFOSCFORCEPD}\item [RTC\_CNTL\_FOSC\_FORCE\_PD] Write 1 to FPD RC\_FAST\_CLK. (R/W)
\label{fielddesc:RTCCNTLFOSCFORCEPU}\item [RTC\_CNTL\_FOSC\_FORCE\_PU] Write 1 to FPU RC\_FAST\_CLK. (R/W)
\label{fielddesc:RTCCNTLXTALGLOBALFORCEGATING}\item [RTC\_CNTL\_XTAL\_GLOBAL\_FORCE\_GATING] Write 1 to force enable XTAL\_CLK clock gating. (R/W)
\label{fielddesc:RTCCNTLXTALGLOBALFORCENOGATING}\item [RTC\_CNTL\_XTAL\_GLOBAL\_FORCE\_NOGATING] Write 1 to force bypass the XTAL\_CLK clock gating. (R/W)
\label{fielddesc:RTCCNTLFASTCLKRTCSEL}\item [RTC\_CNTL\_FAST\_CLK\_RTC\_SEL] Configures the RTC\_FAST\_CLK.\\
0x0: XTAL\_DIV\_CLK\\
0x1: FOSC\_DIV\\
 (R/W)
\label{fielddesc:RTCCNTLANACLKRTCSEL}\item [RTC\_CNTL\_ANA\_CLK\_RTC\_SEL] Configures the RTC\_SLOW\_CLK. \\
0x0: RC\_SLOW\_CLK\\
0x1: OSC\_SLOW\_CLK\\
0x2: RC\_FAST\_DIV\_CLK\\
0x3: Reserved\\
 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_REG}{0x0074}\label{regdesc:RTCCNTLREG}
\regfield{RTC\_CNTL\_REGULATOR\_FORCE\_PU}{1}{31}{{1}}%
\regfield{RTC\_CNTL\_REGULATOR\_FORCE\_PD}{1}{30}{{0}}%
\regfield{(reserved)}{8}{22}{00000000}%
\regfield{RTC\_CNTL\_SCK\_DCAP}{8}{14}{{0}}%
\regfield{(reserved)}{6}{8}{000000}%
\regfield{RTC\_CNTL\_DIG\_REG\_CAL\_EN}{1}{7}{{0}}%
\regfield{(reserved)}{7}{0}{0000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLDIGREGCALEN}\item [RTC\_CNTL\_DIG\_REG\_CAL\_EN] Write 1 to enable digital regulator calibration by SW. (R/W)
\label{fielddesc:RTCCNTLSCKDCAP}\item [RTC\_CNTL\_SCK\_DCAP] Configures the RC\_SLOW\_CLK frequency. (R/W)
\label{fielddesc:RTCCNTLREGULATORFORCEPD}\item [RTC\_CNTL\_REGULATOR\_FORCE\_PD] Write 1 to FPD the low-power voltage regulator, which means decreasing its voltage to 0.8 V or lower. (R/W)
\label{fielddesc:RTCCNTLREGULATORFORCEPU}\item [RTC\_CNTL\_REGULATOR\_FORCE\_PU] Write 1 to FPU the low-power voltage regulator, which means increasing its voltage to higher than 0.8 V. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_PWC\_REG}{0x0078}\label{regdesc:RTCCNTLPWCREG}
\regfield{(reserved)}{10}{22}{0000000000}%
\regfield{RTC\_CNTL\_PAD\_FORCE\_HOLD}{1}{21}{{0}}%
\regfield{(reserved)}{21}{0}{000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLPADFORCEHOLD}\item [RTC\_CNTL\_PAD\_FORCE\_HOLD] Write 1 to force RTC pad into hold state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_DIG\_PWC\_REG}{0x007C}\label{regdesc:RTCCNTLDIGPWCREG}
\regfield{RTC\_CNTL\_DG\_WRAP\_PD\_EN}{1}{31}{{0}}%
\regfield{(reserved)}{10}{21}{0000000000}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_PU}{1}{20}{{1}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_PD}{1}{19}{{0}}%
\regfield{(reserved)}{15}{4}{000000000000000}%
\regfield{RTC\_CNTL\_VDD\_SPI\_PD\_EN}{1}{3}{{0}}%
\regfield{RTC\_CNTL\_VDD\_SPI\_PWR\_FORCE}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_VDD\_SPI\_PWR\_DRV}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLVDDSPIPWRDRV}\item [RTC\_CNTL\_VDD\_SPI\_PWR\_DRV] Configures the vdd\_spi's drive intensity. (R/W)
\label{fielddesc:RTCCNTLVDDSPIPWRFORCE}\item [RTC\_CNTL\_VDD\_SPI\_PWR\_FORCE] Write 1 to allow software to configure vdd\_spi's drive intensity. (R/W)
\label{fielddesc:RTCCNTLVDDSPIPDEN}\item [RTC\_CNTL\_VDD\_SPI\_PD\_EN] Write 1 to power down VDD\_SPI in sleep. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCEPD}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_PD] Write 1 to FPD the digital system. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCEPU}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_PU] Write 1 to FPU the digital system. (R/W)
\label{fielddesc:RTCCNTLDGWRAPPDEN}\item [RTC\_CNTL\_DG\_WRAP\_PD\_EN] Write 1 to enable FPD digital system in sleep. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_DIG\_ISO\_REG}{0x0080}\label{regdesc:RTCCNTLDIGISOREG}
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_NOISO}{1}{31}{{1}}%
\regfield{RTC\_CNTL\_DG\_WRAP\_FORCE\_ISO}{1}{30}{{0}}%
\regfield{(reserved)}{14}{16}{00000000000000}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_HOLD}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_UNHOLD}{1}{14}{{1}}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_ISO}{1}{13}{{0}}%
\regfield{RTC\_CNTL\_DG\_PAD\_FORCE\_NOISO}{1}{12}{{1}}%
\regfield{RTC\_CNTL\_DG\_PAD\_AUTOHOLD\_EN}{1}{11}{{0}}%
\regfield{RTC\_CNTL\_CLR\_DG\_PAD\_AUTOHOLD}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_DG\_PAD\_AUTOHOLD}{1}{9}{{0}}%
\regfield{(reserved)}{9}{0}{000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLDGPADAUTOHOLD}\item [RTC\_CNTL\_DG\_PAD\_AUTOHOLD] Indicates the auto-hold status of the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLCLRDGPADAUTOHOLD}\item [RTC\_CNTL\_CLR\_DG\_PAD\_AUTOHOLD] Write 1 to clear the auto-hold enabler for the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLDGPADAUTOHOLDEN}\item [RTC\_CNTL\_DG\_PAD\_AUTOHOLD\_EN] Write 1 to allow the digital GPIOs to enter the auto-hold status. (R/W)
\label{fielddesc:RTCCNTLDGPADFORCENOISO}\item [RTC\_CNTL\_DG\_PAD\_FORCE\_NOISO] Write 1 to disable the force isolation of the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLDGPADFORCEISO}\item [RTC\_CNTL\_DG\_PAD\_FORCE\_ISO] Write 1 to force isolation of the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLDGPADFORCEUNHOLD}\item [RTC\_CNTL\_DG\_PAD\_FORCE\_UNHOLD] Write 1 the force unhold the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLDGPADFORCEHOLD}\item [RTC\_CNTL\_DG\_PAD\_FORCE\_HOLD] Write 1 the force hold the digital GPIOs. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCEISO}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_ISO] Write 1 to force isolation of the digital system. (R/W)
\label{fielddesc:RTCCNTLDGWRAPFORCENOISO}\item [RTC\_CNTL\_DG\_WRAP\_FORCE\_NOISO] Write 1 to disable the force isolation of the digital system. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTCONFIG0\_REG}{0x0084}\label{regdesc:RTCCNTLWDTCONFIG0REG}
\regfield{RTC\_CNTL\_WDT\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_WDT\_STG0}{3}{28}{{0x0}}%
\regfield{RTC\_CNTL\_WDT\_STG1}{3}{25}{{0x0}}%
\regfield{RTC\_CNTL\_WDT\_STG2}{3}{22}{{0x0}}%
\regfield{RTC\_CNTL\_WDT\_STG3}{3}{19}{{0x0}}%
\regfield{RTC\_CNTL\_WDT\_CPU\_RESET\_LENGTH}{3}{16}{{0x1}}%
\regfield{RTC\_CNTL\_WDT\_SYS\_RESET\_LENGTH}{3}{13}{{0x1}}%
\regfield{RTC\_CNTL\_WDT\_FLASHBOOT\_MOD\_EN}{1}{12}{{1}}%
\regfield{RTC\_CNTL\_WDT\_PROCPU\_RESET\_EN}{1}{11}{{0}}%
\regfield{(reserved)}{1}{10}{0}%
\regfield{RTC\_CNTL\_WDT\_PAUSE\_IN\_SLP}{1}{9}{{1}}%
\regfield{(reserved)}{9}{0}{000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTPAUSEINSLP}\item [RTC\_CNTL\_WDT\_PAUSE\_IN\_SLP] Write 1 to pause the watchdog in sleep. (R/W)
\label{fielddesc:RTCCNTLWDTPROCPURESETEN}\item [RTC\_CNTL\_WDT\_PROCPU\_RESET\_EN] Write 1 to enable RTC WDT to reset CPU. (R/W)
\label{fielddesc:RTCCNTLWDTFLASHBOOTMODEN}\item [RTC\_CNTL\_WDT\_FLASHBOOT\_MOD\_EN] Write 1 to enable watchdog when the chip boots from flash. (R/W)
\label{fielddesc:RTCCNTLWDTSYSRESETLENGTH}\item [RTC\_CNTL\_WDT\_SYS\_RESET\_LENGTH] Configures the length of the digital system reset counter. (R/W)
\label{fielddesc:RTCCNTLWDTCPURESETLENGTH}\item [RTC\_CNTL\_WDT\_CPU\_RESET\_LENGTH] Configures the length of the CPU reset counter. (R/W)
\label{fielddesc:RTCCNTLWDTSTG3}\item [RTC\_CNTL\_WDT\_STG3] Configures the timeout action for RTC watchdog timer at stage 3.\\
0x1: triggers an interrupt\\
0x2: resets the CPU core\\
0x3: resets the digital system excluding RTC\\
0x4: resets the digital system including RTC\\
 (R/W)
\label{fielddesc:RTCCNTLWDTSTG2}\item [RTC\_CNTL\_WDT\_STG2] Configures the timeout action for RTC watchdog timer at stage 2.\\
0x1: triggers an interrupt\\
0x2: resets the CPU core\\
0x3: resets the digital system excluding RTC\\
0x4: resets the digital system including RTC\\
 (R/W)


\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}
\addtocounter{Regfloat}{-1}
\begin{register}{H}{RTC\_CNTL\_WDTCONFIG0\_REG}{0x0084}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:RTCCNTLWDTSTG1}\item [RTC\_CNTL\_WDT\_STG1] Configures the timeout action for RTC watchdog timer at stage 1.\\
0x1: triggers an interrupt\\
0x2: resets the CPU core\\
0x3: resets the digital system excluding RTC\\
0x4: resets the digital system including RTC\\
 (R/W)
\label{fielddesc:RTCCNTLWDTSTG0}\item [RTC\_CNTL\_WDT\_STG0] Configures the timeout action for RTC watchdog timer at stage 0.\\
0x1: triggers an interrupt\\
0x2: resets the CPU core\\
0x3: resets the digital system excluding RTC\\
0x4: resets the digital system including RTC\\
 (R/W)
\label{fielddesc:RTCCNTLWDTEN}\item [RTC\_CNTL\_WDT\_EN] Write 1 to enable the RTC watchdog. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTCONFIG1\_REG}{0x0088}\label{regdesc:RTCCNTLWDTCONFIG1REG}
\regfield{RTC\_CNTL\_WDT\_STG0\_HOLD}{32}{0}{{200000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTSTG0HOLD}\item [RTC\_CNTL\_WDT\_STG0\_HOLD] Configures the hold time of RTC watchdog in stage 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTCONFIG2\_REG}{0x008C}\label{regdesc:RTCCNTLWDTCONFIG2REG}
\regfield{RTC\_CNTL\_WDT\_STG1\_HOLD}{32}{0}{{80000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTSTG1HOLD}\item [RTC\_CNTL\_WDT\_STG1\_HOLD] Configures the hold time of RTC watchdog in stage 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTCONFIG3\_REG}{0x0090}\label{regdesc:RTCCNTLWDTCONFIG3REG}
\regfield{RTC\_CNTL\_WDT\_STG2\_HOLD}{32}{0}{{0x000fff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTSTG2HOLD}\item [RTC\_CNTL\_WDT\_STG2\_HOLD] Configures the hold time of RTC watchdog in stage 2. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTCONFIG4\_REG}{0x0094}\label{regdesc:RTCCNTLWDTCONFIG4REG}
\regfield{RTC\_CNTL\_WDT\_STG3\_HOLD}{32}{0}{{0x000fff}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTSTG3HOLD}\item [RTC\_CNTL\_WDT\_STG3\_HOLD] Configures the hold time of RTC watchdog in stage 3. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTFEED\_REG}{0x0098}\label{regdesc:RTCCNTLWDTFEEDREG}
\regfield{RTC\_CNTL\_WDT\_FEED}{1}{31}{{0}}%
\regfield{(reserved)}{31}{0}{0000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTFEED}\item [RTC\_CNTL\_WDT\_FEED] Write 1 to feed the RTC watchdog. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_WDTWPROTECT\_REG}{0x009C}\label{regdesc:RTCCNTLWDTWPROTECTREG}
\regfield{RTC\_CNTL\_WDT\_WKEY}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWDTWKEY}\item [RTC\_CNTL\_WDT\_WKEY] If the register contains a different value than 0x50d83aa1, write protection for the RTC watchdog (RWDT) is enabled. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SWD\_CONF\_REG}{0x00A0}\label{regdesc:RTCCNTLSWDCONFREG}
\regfield{RTC\_CNTL\_SWD\_AUTO\_FEED\_EN}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_SWD\_DISABLE}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_SWD\_FEED}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_SWD\_RST\_FLAG\_CLR}{1}{28}{{0}}%
\regfield{RTC\_CNTL\_SWD\_SIGNAL\_WIDTH}{10}{18}{{300}}%
\regfield{RTC\_CNTL\_SWD\_BYPASS\_RST}{1}{17}{{0}}%
\regfield{(reserved)}{15}{2}{000000000000000}%
\regfield{RTC\_CNTL\_SWD\_FEED\_INT}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SWD\_RESET\_FLAG}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWDRESETFLAG}\item [RTC\_CNTL\_SWD\_RESET\_FLAG] Represents the super watchdog reset flag. (R/W)
\label{fielddesc:RTCCNTLSWDFEEDINT}\item [RTC\_CNTL\_SWD\_FEED\_INT] Represents super watchdog will be fed via SW. (R/W)
\label{fielddesc:RTCCNTLSWDBYPASSRST}\item [RTC\_CNTL\_SWD\_BYPASS\_RST] Write 1 to bypass super watchdog reset. (R/W)
\label{fielddesc:RTCCNTLSWDSIGNALWIDTH}\item [RTC\_CNTL\_SWD\_SIGNAL\_WIDTH] Configures the signal width sent to the super watchdog. (R/W)
\label{fielddesc:RTCCNTLSWDRSTFLAGCLR}\item [RTC\_CNTL\_SWD\_RST\_FLAG\_CLR] Write 1 to reset the super watchdog reset flag. (R/W)
\label{fielddesc:RTCCNTLSWDFEED}\item [RTC\_CNTL\_SWD\_FEED] Write 1 to feed the super watchdog via SW. (R/W)
\label{fielddesc:RTCCNTLSWDDISABLE}\item [RTC\_CNTL\_SWD\_DISABLE] Write 1 to disable super watchdog. (R/W)
\label{fielddesc:RTCCNTLSWDAUTOFEEDEN}\item [RTC\_CNTL\_SWD\_AUTO\_FEED\_EN] Write 1 to enable automatic watchdog feeding upon interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SWD\_WPROTECT\_REG}{0x00A4}\label{regdesc:RTCCNTLSWDWPROTECTREG}
\regfield{RTC\_CNTL\_SWD\_WKEY}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWDWKEY}\item [RTC\_CNTL\_SWD\_WKEY] Configures the write protection key of the super watchdog. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SW\_CPU\_STALL\_REG}{0x00A8}\label{regdesc:RTCCNTLSWCPUSTALLREG}
\regfield{RTC\_CNTL\_SW\_STALL\_PROCPU\_C1}{6}{26}{{0}}%
\regfield{(reserved)}{26}{0}{00000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSWSTALLPROCPUC1}\item [RTC\_CNTL\_SW\_STALL\_PROCPU\_C1] Write 0x21 to stall the CPU by SW. Valid only when \hyperref[fielddesc:RTCCNTLSWSTALLPROCPUC0]{RTC\_CNTL\_SW\_STALL\_PROCPU\_C0} is configured to 0x2. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE4\_REG}{0x00AC}\label{regdesc:RTCCNTLSTORE4REG}
\regfield{RTC\_CNTL\_SCRATCH4}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSCRATCH4}\item [RTC\_CNTL\_SCRATCH4] Reservation register 4. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE5\_REG}{0x00B0}\label{regdesc:RTCCNTLSTORE5REG}
\regfield{RTC\_CNTL\_SCRATCH5}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSCRATCH5}\item [RTC\_CNTL\_SCRATCH5] Reservation register 5. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE6\_REG}{0x00B4}\label{regdesc:RTCCNTLSTORE6REG}
\regfield{RTC\_CNTL\_SCRATCH6}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSCRATCH6}\item [RTC\_CNTL\_SCRATCH6] Reservation register 6. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_STORE7\_REG}{0x00B8}\label{regdesc:RTCCNTLSTORE7REG}
\regfield{RTC\_CNTL\_SCRATCH7}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSCRATCH7}\item [RTC\_CNTL\_SCRATCH7] Reservation register 7. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_LOW\_POWER\_ST\_REG}{0x00BC}\label{regdesc:RTCCNTLLOWPOWERSTREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{RTC\_CNTL\_MAIN\_STATE\_IN\_IDEL}{1}{27}{{0}}%
\regfield{(reserved)}{7}{20}{0000000}%
\regfield{RTC\_CNTL\_RDY\_FOR\_WAKEUP}{1}{19}{{0}}%
\regfield{(reserved)}{19}{0}{0000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRDYFORWAKEUP}\item [RTC\_CNTL\_RDY\_FOR\_WAKEUP] Indicates the RTC is ready to be triggered by any wakeup source. (RO)
\label{fielddesc:RTCCNTLMAINSTATEINIDLE}\item [RTC\_CNTL\_MAIN\_STATE\_IN\_IDLE] Indicates the RTC state.
\begin{itemize}
    \item 0: the chip can be either
\begin{itemize}
    \item in sleep modes.
    \item entering sleep modes. In this case, wait until \hyperref[fielddesc:RTCCNTLRDYFORWAKEUP]{RTC\_CNTL\_RDY\_FOR\_WAKEUP} bit is set, then you can wake up the chip.
    \item exiting sleep mode. In this case, \hyperref[fielddesc:RTCCNTLMAINSTATEINIDLE]{RTC\_CNTL\_MAIN\_STATE\_IN\_IDLE} will eventually become 1.
\end{itemize}
    \item 1: the chip is not in sleep modes (i.e. running normally).
\end{itemize}
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_PAD\_HOLD\_REG}{0x00C4}\label{regdesc:RTCCNTLPADHOLDREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{RTC\_CNTL\_GPIO\_PIN5\_HOLD}{1}{5}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN4\_HOLD}{1}{4}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN3\_HOLD}{1}{3}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN2\_HOLD}{1}{2}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN1\_HOLD}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN0\_HOLD}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLGPIOPIN0HOLD}\item [RTC\_CNTL\_GPIO\_PIN0\_HOLD] Sets the GPIO 0 to the holding state. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN1HOLD}\item [RTC\_CNTL\_GPIO\_PIN1\_HOLD] Sets the GPIO 1 to the holding state. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN2HOLD}\item [RTC\_CNTL\_GPIO\_PIN2\_HOLD] Sets the GPIO 2 to the holding state. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN3HOLD}\item [RTC\_CNTL\_GPIO\_PIN3\_HOLD] Sets the GPIO 3 to the holding state. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN4HOLD}\item [RTC\_CNTL\_GPIO\_PIN4\_HOLD] Sets the GPIO 4 to the holding state. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN5HOLD}\item [RTC\_CNTL\_GPIO\_PIN5\_HOLD] Sets the GPIO 5 to the holding state. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_DIG\_PAD\_HOLD\_REG}{0x00C8}\label{regdesc:RTCCNTLDIGPADHOLDREG}
\regfield{RTC\_CNTL\_DIG\_PAD\_HOLD}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLDIGPADHOLD}\item [RTC\_CNTL\_DIG\_PAD\_HOLD] Set GPIO 6 to GPIO 20 to the holding state. (See bitmap to locate any GPIO). (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_BROWN\_OUT\_REG}{0x00CC}\label{regdesc:RTCCNTLBROWNOUTREG}
\regfield{RTC\_CNTL\_BROWN\_OUT\_DET}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_ENA}{1}{30}{{1}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_CNT\_CLR}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_ANA\_RST\_EN}{1}{28}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_RST\_SEL}{1}{27}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_RST\_ENA}{1}{26}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_RST\_WAIT}{10}{16}{{0x3ff}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_PD\_RF\_ENA}{1}{15}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_CLOSE\_FLASH\_ENA}{1}{14}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_WAIT}{10}{4}{{0x1}}%
\regfield{(reserved)}{4}{0}{0000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLBROWNOUTINTWAIT}\item [RTC\_CNTL\_BROWN\_OUT\_INT\_WAIT] Configures the waiting cycles before sending an interrupt. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTCLOSEFLASHENA}\item [RTC\_CNTL\_BROWN\_OUT\_CLOSE\_FLASH\_ENA] Write 1 to enable PD the flash when a brownout happens. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTPDRFENA}\item [RTC\_CNTL\_BROWN\_OUT\_PD\_RF\_ENA] Write 1 to enable PD the RF circuits when a brownout happens. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTRSTWAIT}\item [RTC\_CNTL\_BROWN\_OUT\_RST\_WAIT] Configures the waiting cycles before the reset after a brown-out. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTRSTENA}\item [RTC\_CNTL\_BROWN\_OUT\_RST\_ENA] Write 1 to reset brown-out. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTRSTSEL}\item [RTC\_CNTL\_BROWN\_OUT\_RST\_SEL] Configures the reset type when a brownout happens in mode0. \\
0x0: system reset\\
0x1: chip reset\\
 (R/W)
\label{fielddesc:RTCCNTLBROWNOUTANARSTEN}\item [RTC\_CNTL\_BROWN\_OUT\_ANA\_RST\_EN] Write 1 to enable brownout detection mode1. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTCNTCLR}\item [RTC\_CNTL\_BROWN\_OUT\_CNT\_CLR] Write 1 to clear the brownout counter. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTENA}\item [RTC\_CNTL\_BROWN\_OUT\_ENA] Write 1 to enable brownout detection mode0. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTDET}\item [RTC\_CNTL\_BROWN\_OUT\_DET] Represents the status of the brownout signal. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIME\_LOW1\_REG}{0x00D0}\label{regdesc:RTCCNTLTIMELOW1REG}
\regfield{RTC\_CNTL\_TIMER\_VALUE1\_LOW}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTIMERVALUE1LOW}\item [RTC\_CNTL\_TIMER\_VALUE1\_LOW] Represents the lower 32 bits of RTC timer 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_TIME\_HIGH1\_REG}{0x00D4}\label{regdesc:RTCCNTLTIMEHIGH1REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{RTC\_CNTL\_TIMER\_VALUE1\_HIGH}{16}{0}{{0x00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLTIMERVALUE1HIGH}\item [RTC\_CNTL\_TIMER\_VALUE1\_HIGH] Represents the higher 16 bits of RTC timer 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_USB\_CONF\_REG}{0x00D8}\label{regdesc:RTCCNTLUSBCONFREG}
\regfield{(reserved)}{13}{19}{0000000000000}%
\regfield{RTC\_CNTL\_IO\_MUX\_RESET\_DISABLE}{1}{18}{{0}}%
\regfield{(reserved)}{18}{0}{000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLIOMUXRESETDISABLE}\item [RTC\_CNTL\_IO\_MUX\_RESET\_DISABLE] Write 1 to disable io\_mux reset. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLP\_REJECT\_CAUSE\_REG}{0x00DC}\label{regdesc:RTCCNTLSLPREJECTCAUSEREG}
\regfield{(reserved)}{14}{18}{00000000000000}%
\regfield{RTC\_CNTL\_REJECT\_CAUSE}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLREJECTCAUSE}\item [RTC\_CNTL\_REJECT\_CAUSE] Represents the reject-to-sleep cause. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_OPTION1\_REG}{0x00E0}\label{regdesc:RTCCNTLOPTION1REG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{\scriptsize RTC\_CNTL\_FORCE\_DOWNLOAD\_BOOT}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLFORCEDOWNLOADBOOT}\item [RTC\_CNTL\_FORCE\_DOWNLOAD\_BOOT] Write 1 to force the chip to boot from the download mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_SLP\_WAKEUP\_CAUSE\_REG}{0x00E4}\label{regdesc:RTCCNTLSLPWAKEUPCAUSEREG}
\regfield{(reserved)}{15}{17}{000000000000000}%
\regfield{RTC\_CNTL\_WAKEUP\_CAUSE}{17}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLWAKEUPCAUSE}\item [RTC\_CNTL\_WAKEUP\_CAUSE] Represents the wakeup cause. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_CNTL\_GPIO\_WAKEUP\_REG}{0x00FC}\label{regdesc:RTCCNTLCNTLGPIOWAKEUPREG}
\regfield{RTC\_CNTL\_GPIO\_PIN0\_WAKEUP\_ENABLE}{1}{31}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN1\_WAKEUP\_ENABLE}{1}{30}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN2\_WAKEUP\_ENABLE}{1}{29}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN3\_WAKEUP\_ENABLE}{1}{28}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN4\_WAKEUP\_ENABLE}{1}{27}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN5\_WAKEUP\_ENABLE}{1}{26}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN0\_INT\_TYPE}{3}{23}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN1\_INT\_TYPE}{3}{20}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN2\_INT\_TYPE}{3}{17}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN3\_INT\_TYPE}{3}{14}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN4\_INT\_TYPE}{3}{11}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN5\_INT\_TYPE}{3}{8}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_PIN\_CLK\_GATE}{1}{7}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_WAKEUP\_STATUS\_CLR}{1}{6}{{0}}%
\regfield{RTC\_CNTL\_GPIO\_WAKEUP\_STATUS}{6}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLGPIOWAKEUPSTATUS}\item [RTC\_CNTL\_GPIO\_WAKEUP\_STATUS] Write 1 to set the RTC GPIO wakeup flag. (R/W)
\label{fielddesc:RTCCNTLGPIOWAKEUPSTATUSCLR}\item [RTC\_CNTL\_GPIO\_WAKEUP\_STATUS\_CLR] Write 1 to clear the RTC GPIO flag. (R/W)
\label{fielddesc:RTCCNTLGPIOPINCLKGATE}\item [RTC\_CNTL\_GPIO\_PIN\_CLK\_GATE] Write 1 to enable the RTC GPIO clock gating. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN5INTTYPE}\item [RTC\_CNTL\_GPIO\_PIN5\_INT\_TYPE] Configures GPIO 5 wakeup type. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN4INTTYPE}\item [RTC\_CNTL\_GPIO\_PIN4\_INT\_TYPE] Configures GPIO 4 wakeup type. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN3INTTYPE}\item [RTC\_CNTL\_GPIO\_PIN3\_INT\_TYPE] Configures GPIO 3 wakeup type. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN2INTTYPE}\item [RTC\_CNTL\_GPIO\_PIN2\_INT\_TYPE] Configures GPIO 2 wakeup type. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN1INTTYPE}\item [RTC\_CNTL\_GPIO\_PIN1\_INT\_TYPE] Configures GPIO 1 wakeup type. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN0INTTYPE}\item [RTC\_CNTL\_GPIO\_PIN0\_INT\_TYPE] Configures GPIO 0 wakeup type. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN5WAKEUPENABLE}\item [RTC\_CNTL\_GPIO\_PIN5\_WAKEUP\_ENABLE] Write 1 to enable wakeup from RTC GPIO 5. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN4WAKEUPENABLE}\item [RTC\_CNTL\_GPIO\_PIN4\_WAKEUP\_ENABLE] Write 1 to enable wakeup from RTC GPIO 4. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN3WAKEUPENABLE}\item [RTC\_CNTL\_GPIO\_PIN3\_WAKEUP\_ENABLE] Write 1 to enable wakeup from RTC GPIO 3. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN2WAKEUPENABLE}\item [RTC\_CNTL\_GPIO\_PIN2\_WAKEUP\_ENABLE] Write 1 to enable wakeup from RTC GPIO 2. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN1WAKEUPENABLE}\item [RTC\_CNTL\_GPIO\_PIN1\_WAKEUP\_ENABLE] Write 1 to enable wakeup from RTC GPIO 1. (R/W)
\label{fielddesc:RTCCNTLGPIOPIN0WAKEUPENABLE}\item [RTC\_CNTL\_GPIO\_PIN0\_WAKEUP\_ENABLE] Write 1 to enable wakeup from RTC GPIO 0. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_CNTL\_SENSOR\_CTRL\_REG}{0x0108}\label{regdesc:RTCCNTLCNTLSENSORCTRLREG}
\regfield{RTC\_CNTL\_FORCE\_XPD\_SAR}{2}{30}{{0}}%
\regfield{(reserved)}{30}{0}{000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLFORCEXPDSAR}\item [RTC\_CNTL\_FORCE\_XPD\_SAR] Set this field to FPU SAR ADC. (R/W)
\end{reglist}\end{regdesc}
\end{register}



\begin{register}{H}{RTC\_CNTL\_RESET\_STATE\_REG}{0x0030}\label{regdesc:RTCCNTLRESETSTATEREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_DRESET\_MASK\_PROCPU}{1}{20}{{0}}%
\regfield{RTC\_CNTL\_OCD\_HALT\_ON\_RESET\_PROCPU}{1}{19}{{0}}%
\regfield{(reserved)}{5}{14}{00000}%
\regfield{(reserved)}{1}{13}{{1}}%
\regfield{(reserved)}{7}{6}{0000000}%
\regfield{RTC\_CNTL\_RESET\_CAUSE\_PROCPU}{6}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRESETCAUSEPROCPU}\item [RTC\_CNTL\_RESET\_CAUSE\_PROCPU] Represents the CPU reset cause. (R/W)
\label{fielddesc:RTCCNTLOCDHALTONRESETPROCPU}\item [RTC\_CNTL\_OCD\_HALT\_ON\_RESET\_PROCPU] Write 1 to send CPU into halt state upon CPU reset. (R/W)
\label{fielddesc:RTCCNTLDRESETMASKPROCPU}\item [RTC\_CNTL\_DRESET\_MASK\_PROCPU] Write 1 to bybass D-reset. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{RTC\_CNTL\_INT\_ENA\_RTC\_REG}{0x0038}\label{regdesc:RTCCNTLINTENARTCREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_BBPLL\_CAL\_INT\_ENA}{1}{20}{{0}}%
\regfield{(reserved)}{4}{16}{0000}%
\regfield{RTC\_CNTL\_SWD\_INT\_ENA}{1}{15}{{0}}%
\regfield{(reserved)}{4}{11}{0000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_INT\_ENA}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_ENA}{1}{9}{{0}}%
\regfield{(reserved)}{5}{4}{00000}%
\regfield{RTC\_CNTL\_WDT\_INT\_ENA}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{0}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_ENA}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTENA}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA] Write 1 to enable interrupt when chip wakes up from sleep. (R/W)
\label{fielddesc:RTCCNTLSLPREJECTINTENA}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_ENA] Write 1 to enable interrupt when chip rejects to go to sleep. (R/W)
\label{fielddesc:RTCCNTLWDTINTENA}\item [RTC\_CNTL\_WDT\_INT\_ENA] Write 1 to enable RTC WDT interrupt. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTINTENA}\item [RTC\_CNTL\_BROWN\_OUT\_INT\_ENA] Write 1 to enable the brownout interrupt. (R/W)
\label{fielddesc:RTCCNTLMAINTIMERINTENA}\item [RTC\_CNTL\_MAIN\_TIMER\_INT\_ENA] Write 1 to enable the RTC timer interrupt. (R/W)
\label{fielddesc:RTCCNTLSWDINTENA}\item [RTC\_CNTL\_SWD\_INT\_ENA] Write 1 to enable the super watchdog interrupt. (R/W)
\label{fielddesc:RTCCNTLBBPLLCALINTENA}\item [RTC\_CNTL\_BBPLL\_CAL\_INT\_ENA] Write 1 to enable interrupt upon the ending of a BB\_PLL call. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_RAW\_RTC\_REG}{0x003C}\label{regdesc:RTCCNTLINTRAWRTCREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_BBPLL\_CAL\_INT\_RAW}{1}{20}{{0}}%
\regfield{(reserved)}{4}{16}{0000}%
\regfield{RTC\_CNTL\_SWD\_INT\_RAW}{1}{15}{{0}}%
\regfield{(reserved)}{4}{11}{0000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_INT\_RAW}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_RAW}{1}{9}{{0}}%
\regfield{(reserved)}{5}{4}{00000}%
\regfield{RTC\_CNTL\_WDT\_INT\_RAW}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{0}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_RAW}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTRAW}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_RAW] Represents the raw interrupt triggered when the chip wakes up from sleep. (R/W)
\label{fielddesc:RTCCNTLSLPREJECTINTRAW}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_RAW] Represents the raw interrupt triggered when the chip rejects to go to sleep. (R/W)
\label{fielddesc:RTCCNTLWDTINTRAW}\item [RTC\_CNTL\_WDT\_INT\_RAW] Represents the raw watchdog interrupt. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTINTRAW}\item [RTC\_CNTL\_BROWN\_OUT\_INT\_RAW] Represents the raw brownout interrupt. (R/W)
\label{fielddesc:RTCCNTLMAINTIMERINTRAW}\item [RTC\_CNTL\_MAIN\_TIMER\_INT\_RAW] Represents the raw RTC main timer interrupt. (R/W)
\label{fielddesc:RTCCNTLSWDINTRAW}\item [RTC\_CNTL\_SWD\_INT\_RAW] Represents the raw super watchdog interrupt. (R/W)
\label{fielddesc:RTCCNTLBBPLLCALINTRAW}\item [RTC\_CNTL\_BBPLL\_CAL\_INT\_RAW] Represents the raw interrupt upon the ending of a BB\_PLL call. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_ST\_RTC\_REG}{0x0040}\label{regdesc:RTCCNTLINTSTRTCREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_BBPLL\_CAL\_INT\_ST}{1}{20}{{0}}%
\regfield{(reserved)}{4}{16}{0000}%
\regfield{RTC\_CNTL\_SWD\_INT\_ST}{1}{15}{{0}}%
\regfield{(reserved)}{4}{11}{0000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_INT\_ST}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_ST}{1}{9}{{0}}%
\regfield{(reserved)}{5}{4}{00000}%
\regfield{RTC\_CNTL\_WDT\_INT\_ST}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{0}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_ST}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTST}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_ST] Represents the status of the interrupt triggered when the chip wakes up from sleep. (R/W)
\label{fielddesc:RTCCNTLSLPREJECTINTST}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_ST] Represents the status of the interrupt triggered when the chip rejects to go to sleep. (R/W)
\label{fielddesc:RTCCNTLWDTINTST}\item [RTC\_CNTL\_WDT\_INT\_ST] Represents the status of the RTC watchdog interrupt. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTINTST}\item [RTC\_CNTL\_BROWN\_OUT\_INT\_ST] Represents the status of the brownout interrupt. (R/W)
\label{fielddesc:RTCCNTLMAINTIMERINTST}\item [RTC\_CNTL\_MAIN\_TIMER\_INT\_ST] Represents the status of the RTC main timer interrupt. (R/W)
\label{fielddesc:RTCCNTLSWDINTST}\item [RTC\_CNTL\_SWD\_INT\_ST] Represents the status of the super watchdog interrupt. (R/W)
\label{fielddesc:RTCCNTLBBPLLCALINTST}\item [RTC\_CNTL\_BBPLL\_CAL\_INT\_ST] Represents the status of the interrupt triggered upon the ending of a BB\_PLL call. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_CLR\_RTC\_REG}{0x0044}\label{regdesc:RTCCNTLINTCLRRTCREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_BBPLL\_CAL\_INT\_CLR}{1}{20}{{0}}%
\regfield{(reserved)}{4}{16}{0000}%
\regfield{RTC\_CNTL\_SWD\_INT\_CLR}{1}{15}{{0}}%
\regfield{(reserved)}{4}{11}{0000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_INT\_CLR}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_CLR}{1}{9}{{0}}%
\regfield{(reserved)}{5}{4}{00000}%
\regfield{RTC\_CNTL\_WDT\_INT\_CLR}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{0}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_CLR}{1}{1}{{0}}%
\regfield{RTC\_CNTL\_SLP\_WAKEUP\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTCLR}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_CLR] Write 1 to clear the interrupt triggered when the chip wakes up from sleep. (R/W)
\label{fielddesc:RTCCNTLSLPREJECTINTCLR}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_CLR] Write 1 to clear the interrupt triggered when the chip rejects to go to sleep. (R/W)
\label{fielddesc:RTCCNTLWDTINTCLR}\item [RTC\_CNTL\_WDT\_INT\_CLR] Write 1 to clear the RTC watchdog interrupt. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTINTCLR}\item [RTC\_CNTL\_BROWN\_OUT\_INT\_CLR] Write 1 to clear the brownout interrupt. (R/W)
\label{fielddesc:RTCCNTLMAINTIMERINTCLR}\item [RTC\_CNTL\_MAIN\_TIMER\_INT\_CLR] Write 1 to clear the RTC main timer interrupt. (R/W)
\label{fielddesc:RTCCNTLSWDINTCLR}\item [RTC\_CNTL\_SWD\_INT\_CLR] Write 1 to clear the super watch dog interrupt state. (R/W)
\label{fielddesc:RTCCNTLBBPLLCALINTCLR}\item [RTC\_CNTL\_BBPLL\_CAL\_INT\_CLR] Write 1 to clear the interrupt triggered upon the ending of a BB\_PLL call. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_ENA\_RTC\_W1TS\_REG}{0x00EC}\label{regdesc:RTCCNTLINTENARTCW1TSREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_BBPLL\_CAL\_INT\_ENA\_W1TS}{1}{20}{{0}}%
\regfield{(reserved)}{4}{16}{0000}%
\regfield{RTC\_CNTL\_SWD\_INT\_ENA\_W1TS}{1}{15}{{0}}%
\regfield{(reserved)}{4}{11}{0000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_INT\_ENA\_W1TS}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_ENA\_W1TS}{1}{9}{{0}}%
\regfield{(reserved)}{5}{4}{00000}%
\regfield{RTC\_CNTL\_WDT\_INT\_ENA\_W1TS}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{0}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_ENA\_W1TS}{1}{1}{{0}}%
\regfield{\scriptsize RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA\_W1TS}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTENAW1TS}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA\_W1TS] Write 1 to enable interrupt when the chip wakes up from sleep. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLSLPWAKEUPINTENA]{RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA} field will be set to 1. (R/W)
\label{fielddesc:RTCCNTLSLPREJECTINTENAW1TS}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_ENA\_W1TS] Write 1 to enable interrupt when the chip rejects to go to sleep. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLSLPREJECTINTENA]{RTC\_CNTL\_SLP\_REJECT\_INT\_ENA} field will be set to 1. (R/W)
\label{fielddesc:RTCCNTLWDTINTENAW1TS}\item [RTC\_CNTL\_WDT\_INT\_ENA\_W1TS] Write 1 to enable the RTC watchdog interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLWDTINTENA]{RTC\_CNTL\_WDT\_INT\_ENA} field will be set to 1. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTINTENAW1TS}\item [RTC\_CNTL\_BROWN\_OUT\_INT\_ENA\_W1TS] Write 1 to enable the brownout interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLBROWNOUTINTENA]{RTC\_CNTL\_BROWN\_OUT\_INT\_ENA} field will be set to 1. (R/W)
\label{fielddesc:RTCCNTLMAINTIMERINTENAW1TS}\item [RTC\_CNTL\_MAIN\_TIMER\_INT\_ENA\_W1TS] Write 1 to enable the RTC main timer interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLMAINTIMERINTENA]{RTC\_CNTL\_MAIN\_TIMER\_INT\_ENA} field will be set to 1. (R/W)
\label{fielddesc:RTCCNTLSWDINTENAW1TS}\item [RTC\_CNTL\_SWD\_INT\_ENA\_W1TS] Write 1 to enable the super watchdog interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLSWDINTENA]{RTC\_CNTL\_SWD\_INT\_ENA} field will be set to 1. (R/W)
\label{fielddesc:RTCCNTLBBPLLCALINTENAW1TS}\item [RTC\_CNTL\_BBPLL\_CAL\_INT\_ENA\_W1TS] Write 1 to enable interrupt upon the ending of a BB\_PLL call. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLBBPLLCALINTENA]{RTC\_CNTL\_BBPLL\_CAL\_INT\_ENA} field will be set to 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_INT\_ENA\_RTC\_W1TC\_REG}{0x00F0}\label{regdesc:RTCCNTLINTENARTCW1TCREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{RTC\_CNTL\_BBPLL\_CAL\_INT\_ENA\_W1TC}{1}{20}{{0}}%
\regfield{(reserved)}{4}{16}{0000}%
\regfield{RTC\_CNTL\_SWD\_INT\_ENA\_W1TC}{1}{15}{{0}}%
\regfield{(reserved)}{4}{11}{0000}%
\regfield{RTC\_CNTL\_MAIN\_TIMER\_INT\_ENA\_W1TC}{1}{10}{{0}}%
\regfield{RTC\_CNTL\_BROWN\_OUT\_INT\_ENA\_W1TC}{1}{9}{{0}}%
\regfield{(reserved)}{5}{4}{00000}%
\regfield{RTC\_CNTL\_WDT\_INT\_ENA\_W1TC}{1}{3}{{0}}%
\regfield{(reserved)}{1}{2}{0}%
\regfield{RTC\_CNTL\_SLP\_REJECT\_INT\_ENA\_W1TC}{1}{1}{{0}}%
\regfield{\scriptsize RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA\_W1TC}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLSLPWAKEUPINTENAW1TC}\item [RTC\_CNTL\_SLP\_WAKEUP\_INT\_ENA\_W1TC] Write 1 to disable interrupt when the chip wakes up from sleep. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLSLPWAKEUPINTCLR]{RTC\_CNTL\_SLP\_WAKEUP\_INT\_CLR} field will be cleared. (R/W)
\label{fielddesc:RTCCNTLSLPREJECTINTENAW1TC}\item [RTC\_CNTL\_SLP\_REJECT\_INT\_ENA\_W1TC] Write 1 to disable interrupt when the chip rejects to go to sleep. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLSLPREJECTINTCLR]{RTC\_CNTL\_SLP\_REJECT\_INT\_CLR} field will be cleared. (R/W)
\label{fielddesc:RTCCNTLWDTINTENAW1TC}\item [RTC\_CNTL\_WDT\_INT\_ENA\_W1TC] Write 1 to disable the RTC watchdog interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLWDTINTCLR]{RTC\_CNTL\_WDT\_INT\_CLR} field will be cleared. (R/W)
\label{fielddesc:RTCCNTLBROWNOUTINTENAW1TC}\item [RTC\_CNTL\_BROWN\_OUT\_INT\_ENA\_W1TC] Write 1 to disable the brownout interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLBROWNOUTINTCLR]{RTC\_CNTL\_BROWN\_OUT\_INT\_CLR} field will be cleared. (R/W)
\label{fielddesc:RTCCNTLMAINTIMERINTENAW1TC}\item [RTC\_CNTL\_MAIN\_TIMER\_INT\_ENA\_W1TC] Write 1 to disable the RTC timer interrupt. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLMAINTIMERINTCLR]{RTC\_CNTL\_MAIN\_TIMER\_INT\_CLR} field will be cleared. (R/W)
\label{fielddesc:RTCCNTLSWDINTENAW1TC}\item [RTC\_CNTL\_SWD\_INT\_ENA\_W1TC] Write 1 to disable the super watchdog interrupt enable bit. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLSWDINTCLR]{RTC\_CNTL\_SWD\_INT\_CLR} field will be cleared. (R/W)
\label{fielddesc:RTCCNTLBBPLLCALINTENAW1TC}\item [RTC\_CNTL\_BBPLL\_CAL\_INT\_ENA\_W1TC] Write 1 to disable the interrupt upon the ending of a BB\_PLL call. If the value 1 is written to this bit, the \hyperref[fielddesc:RTCCNTLBBPLLCALINTCLR]{RTC\_CNTL\_BBPLL\_CAL\_INT\_CLR} field will be cleared. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RTC\_CNTL\_FIB\_SEL\_REG}{0x00F8}\label{regdesc:RTCCNTLFIBSELREG}
\regfield{(reserved)}{29}{3}{00000000000000000000000000000}%
\regfield{RTC\_CNTL\_RTC\_FIB\_SEL}{3}{0}{{7}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RTCCNTLRTCFIBSEL}\item [RTC\_CNTL\_RTC\_FIB\_SEL] Configures the brownout detector. (R/W)
\end{reglist}\end{regdesc}
\end{register}
