\begin{longtable}[c]{ |p{3cm}|p{4cm}|p{8cm}| }
\caption{Word DES0 of SD/MMC GDMA Linked List} \label{tab:sdhost-DES0}\\
\hline
\rowcolor{lightgray}
Bits &Name & Description \\
\hline
\endfirsthead
\hline
\rowcolor{lightgray}
Bits &Name & Description  \\
\hline
\endhead
\endfoot
\multirow{4}{*}{31} & \multirow{4}{*}{OWNER} & When set, this bit indicates that the descriptor is owned by the DMA Controller. When reset, it indicates that the descriptor is owned by the Host. The DMA clears this bit when it completes the data transfer.\\\hline
\multirow{11}{*}{30} & \multirow{11}{*}{CES (Card Error Summary)} & These error bits indicate the status of the transition to or from the card. \\
 & & The following bits are also present in SDHOST\_RINTSTS\_REG, which indicates their digital logic OR gate.
 \begin{itemize}
     \item{EBE: End Bit Error}
     \item{RTO: Response Time out}
     \item{RCRC: Response CRC}
     \item{SBE: Start Bit Error}
     \item{DRTO: Data Read Timeout}
     \item{DCRC: Data CRC for Receive}
     \item{RE: Response Error}
 \end{itemize}\vspace{-1.5em}
 \\\hline
29:6 & Reserved & Reserved	\\\hline
\multirow{4}{*}{5} &\multirow{4}{*}{ER (End of Ring)} & When set, this bit indicates that the descriptor list has reached its final descriptor. The DMA Controller then returns to the base address of the list, creating a Descriptor Chain. \\\hline
\multirow{3}{*}{4} &\multirow{3}{*}{\makecell[l]{CH\\ (Second Address Chained)}} & When set, this bit indicates that the second address in the descriptor is the Next Descriptor address. When this bit is set, BS2 (DES1[25:13]) should be all zeros. \\\hline
\multirow{4}{*}{3} & \multirow{4}{*}{FD (First Descriptor)}& When set, this bit indicates that this descriptor contains the first buffer of the data. If the size of the first buffer is 0, the Next Descriptor contains the beginning of the data. \\\hline
\multirow{7}{*}{2} & \multirow{7}{*}{LD (Last Descriptor)}&  This bit is associated with the last block of a DMA transfer. When set, the bit indicates that the buffers pointed by this descriptor are the last buffers of the data. After this descriptor is completed, the remaining byte count is 0. In other words, after the descriptor with the LD bit set is completed, the remaining byte count should be 0.\\\hline
\multirow{3}{*}{1}&\multirow{3}{*}{\makecell[l]{DIC (Disable Interrupt\\ on Completion)}}& When set, this bit will prevent the setting of the TI/RI bit of the DMA Status Register (IDSTS) for the data that ends in the buffer pointed by this descriptor. \\\hline
0 & Reserved& Reserved \\\hline
\end{longtable}