\begin{register}{H}{GDMA\_IN\_INT\_RAW\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0000+0x10*\regindex{n}}\label{regdesc:GDMAININTRAWCHNREG}
\regfield{(reserved)}{25}{7}{0000000000000000000000000}%
\regfield{GDMA\_INFIFO\_UDF\_CH0\_INT\_RAW}{1}{6}{{0}}%
\regfield{GDMA\_INFIFO\_OVF\_CH0\_INT\_RAW}{1}{5}{{0}}%
\regfield{GDMA\_IN\_DSCR\_EMPTY\_CH0\_INT\_RAW}{1}{4}{{0}}%
\regfield{GDMA\_IN\_DSCR\_ERR\_CH0\_INT\_RAW}{1}{3}{{0}}%
\regfield{GDMA\_IN\_ERR\_EOF\_CH0\_INT\_RAW}{1}{2}{{0}}%
\regfield{GDMA\_IN\_SUC\_EOF\_CH0\_INT\_RAW}{1}{1}{{0}}%
\regfield{GDMA\_IN\_DONE\_CH0\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAINDONECHNINTRAW}\item [GDMA\_IN\_DONE\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of GDMA\_IN\_DONE\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:GDMAINSUCEOFCHNINTRAW}\item [GDMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of GDMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT. For UHCI this bit turns to 1 when the last data byte pointed by one receive descriptor has been received and no data error is detected for RX channel 0. (R/WTC/SS)
\label{fielddesc:GDMAINERREOFCHNINTRAW}\item [GDMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of GDMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT. Valid only for UHCI or PARLIO. (R/WTC/SS)
\label{fielddesc:GDMAINDSCRERRCHNINTRAW}\item [GDMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of GDMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:GDMAINDSCREMPTYCHNINTRAW}\item [GDMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of GDMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:GDMAINFIFOOVFCHNINTRAW}\item [GDMA\_INFIFO\_OVF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of GDMA\_INFIFO\_OVF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:GDMAINFIFOUDFCHNINTRAW}\item [GDMA\_INFIFO\_UDF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of GDMA\_INFIFO\_UDF\_CH\regindex{n}\_INT. (R/WTC/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_INT\_ST\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0004+0x10*\regindex{n}}\label{regdesc:GDMAININTSTCHNREG}
\regfield{(reserved)}{25}{7}{0000000000000000000000000}%
\regfield{GDMA\_INFIFO\_UDF\_CH0\_INT\_ST}{1}{6}{{0}}%
\regfield{GDMA\_INFIFO\_OVF\_CH0\_INT\_ST}{1}{5}{{0}}%
\regfield{GDMA\_IN\_DSCR\_EMPTY\_CH0\_INT\_ST}{1}{4}{{0}}%
\regfield{GDMA\_IN\_DSCR\_ERR\_CH0\_INT\_ST}{1}{3}{{0}}%
\regfield{GDMA\_IN\_ERR\_EOF\_CH0\_INT\_ST}{1}{2}{{0}}%
\regfield{GDMA\_IN\_SUC\_EOF\_CH0\_INT\_ST}{1}{1}{{0}}%
\regfield{GDMA\_IN\_DONE\_CH0\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAINDONECHNINTST}\item [GDMA\_IN\_DONE\_CH\regindex{n}\_INT\_ST] The masked interrupt status of GDMA\_IN\_DONE\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:GDMAINSUCEOFCHNINTST}\item [GDMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of GDMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:GDMAINERREOFCHNINTST}\item [GDMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of GDMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:GDMAINDSCRERRCHNINTST}\item [GDMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_ST] The masked interrupt status of GDMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:GDMAINDSCREMPTYCHNINTST}\item [GDMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_ST] The masked interrupt status of GDMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:GDMAINFIFOOVFCHNINTST}\item [GDMA\_INFIFO\_OVF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of GDMA\_INFIFO\_OVF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:GDMAINFIFOUDFCHNINTST}\item [GDMA\_INFIFO\_UDF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of GDMA\_INFIFO\_UDF\_CH\regindex{n}\_INT. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_INT\_ENA\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0008+0x10*\regindex{n}}\label{regdesc:GDMAININTENACHNREG}
\regfield{(reserved)}{25}{7}{0000000000000000000000000}%
\regfield{GDMA\_INFIFO\_UDF\_CH0\_INT\_ENA}{1}{6}{{0}}%
\regfield{GDMA\_INFIFO\_OVF\_CH0\_INT\_ENA}{1}{5}{{0}}%
\regfield{GDMA\_IN\_DSCR\_EMPTY\_CH0\_INT\_ENA}{1}{4}{{0}}%
\regfield{GDMA\_IN\_DSCR\_ERR\_CH0\_INT\_ENA}{1}{3}{{0}}%
\regfield{GDMA\_IN\_ERR\_EOF\_CH0\_INT\_ENA}{1}{2}{{0}}%
\regfield{GDMA\_IN\_SUC\_EOF\_CH0\_INT\_ENA}{1}{1}{{0}}%
\regfield{GDMA\_IN\_DONE\_CH0\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAINDONECHNINTENA}\item [GDMA\_IN\_DONE\_CH\regindex{n}\_INT\_ENA] Write 1 to enable GDMA\_IN\_DONE\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:GDMAINSUCEOFCHNINTENA}\item [GDMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable GDMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:GDMAINERREOFCHNINTENA}\item [GDMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable GDMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:GDMAINDSCRERRCHNINTENA}\item [GDMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_ENA] Write 1 to enable GDMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:GDMAINDSCREMPTYCHNINTENA}\item [GDMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_ENA] Write 1 to enable GDMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:GDMAINFIFOOVFCHNINTENA}\item [GDMA\_INFIFO\_OVF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable GDMA\_INFIFO\_OVF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:GDMAINFIFOUDFCHNINTENA}\item [GDMA\_INFIFO\_UDF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable GDMA\_INFIFO\_UDF\_CH\regindex{n}\_INT. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_INT\_CLR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x000C+0x10*\regindex{n}}\label{regdesc:GDMAININTCLRCHNREG}
\regfield{(reserved)}{25}{7}{0000000000000000000000000}%
\regfield{GDMA\_INFIFO\_UDF\_CH0\_INT\_CLR}{1}{6}{{0}}%
\regfield{GDMA\_INFIFO\_OVF\_CH0\_INT\_CLR}{1}{5}{{0}}%
\regfield{GDMA\_IN\_DSCR\_EMPTY\_CH0\_INT\_CLR}{1}{4}{{0}}%
\regfield{GDMA\_IN\_DSCR\_ERR\_CH0\_INT\_CLR}{1}{3}{{0}}%
\regfield{GDMA\_IN\_ERR\_EOF\_CH0\_INT\_CLR}{1}{2}{{0}}%
\regfield{GDMA\_IN\_SUC\_EOF\_CH0\_INT\_CLR}{1}{1}{{0}}%
\regfield{GDMA\_IN\_DONE\_CH0\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAINDONECHNINTCLR}\item [GDMA\_IN\_DONE\_CH\regindex{n}\_INT\_CLR] Write 1 to clear GDMA\_IN\_DONE\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:GDMAINSUCEOFCHNINTCLR}\item [GDMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear GDMA\_IN\_SUC\_EOF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:GDMAINERREOFCHNINTCLR}\item [GDMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear GDMA\_IN\_ERR\_EOF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:GDMAINDSCRERRCHNINTCLR}\item [GDMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT\_CLR] Write 1 to clear GDMA\_IN\_DSCR\_ERR\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:GDMAINDSCREMPTYCHNINTCLR}\item [GDMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT\_CLR] Write 1 to clear GDMA\_IN\_DSCR\_EMPTY\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:GDMAINFIFOOVFCHNINTCLR}\item [GDMA\_INFIFO\_OVF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear GDMA\_INFIFO\_OVF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:GDMAINFIFOUDFCHNINTCLR}\item [GDMA\_INFIFO\_UDF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear GDMA\_INFIFO\_UDF\_CH\regindex{n}\_INT. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_INT\_RAW\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0030+0x10*\regindex{n}}\label{regdesc:GDMAOUTINTRAWCHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{GDMA\_OUTFIFO\_UDF\_CH0\_INT\_RAW}{1}{5}{{0}}%
\regfield{GDMA\_OUTFIFO\_OVF\_CH0\_INT\_RAW}{1}{4}{{0}}%
\regfield{GDMA\_OUT\_TOTAL\_EOF\_CH0\_INT\_RAW}{1}{3}{{0}}%
\regfield{GDMA\_OUT\_DSCR\_ERR\_CH0\_INT\_RAW}{1}{2}{{0}}%
\regfield{GDMA\_OUT\_EOF\_CH0\_INT\_RAW}{1}{1}{{0}}%
\regfield{GDMA\_OUT\_DONE\_CH0\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAOUTDONECHNINTRAW}\item [GDMA\_OUT\_DONE\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of GDMA\_OUT\_DONE\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:GDMAOUTEOFCHNINTRAW}\item [GDMA\_OUT\_EOF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of GDMA\_OUT\_EOF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:GDMAOUTDSCRERRCHNINTRAW}\item [GDMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of GDMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:GDMAOUTTOTALEOFCHNINTRAW}\item [GDMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of GDMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:GDMAOUTFIFOOVFCHNINTRAW}\item [GDMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of GDMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT. (R/WTC/SS)
\label{fielddesc:GDMAOUTFIFOUDFCHNINTRAW}\item [GDMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT\_RAW] The raw interrupt status of GDMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT. (R/WTC/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_INT\_ST\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0034+0x10*\regindex{n}}\label{regdesc:GDMAOUTINTSTCHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{GDMA\_OUTFIFO\_UDF\_CH0\_INT\_ST}{1}{5}{{0}}%
\regfield{GDMA\_OUTFIFO\_OVF\_CH0\_INT\_ST}{1}{4}{{0}}%
\regfield{GDMA\_OUT\_TOTAL\_EOF\_CH0\_INT\_ST}{1}{3}{{0}}%
\regfield{GDMA\_OUT\_DSCR\_ERR\_CH0\_INT\_ST}{1}{2}{{0}}%
\regfield{GDMA\_OUT\_EOF\_CH0\_INT\_ST}{1}{1}{{0}}%
\regfield{GDMA\_OUT\_DONE\_CH0\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAOUTDONECHNINTST}\item [GDMA\_OUT\_DONE\_CH\regindex{n}\_INT\_ST] The masked interrupt status of GDMA\_OUT\_DONE\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:GDMAOUTEOFCHNINTST}\item [GDMA\_OUT\_EOF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of GDMA\_OUT\_EOF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:GDMAOUTDSCRERRCHNINTST}\item [GDMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_ST] The masked interrupt status of GDMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:GDMAOUTTOTALEOFCHNINTST}\item [GDMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of GDMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:GDMAOUTFIFOOVFCHNINTST}\item [GDMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of GDMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT. (RO)
\label{fielddesc:GDMAOUTFIFOUDFCHNINTST}\item [GDMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT\_ST] The masked interrupt status of GDMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_INT\_ENA\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0038+0x10*\regindex{n}}\label{regdesc:GDMAOUTINTENACHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{GDMA\_OUTFIFO\_UDF\_CH0\_INT\_ENA}{1}{5}{{0}}%
\regfield{GDMA\_OUTFIFO\_OVF\_CH0\_INT\_ENA}{1}{4}{{0}}%
\regfield{GDMA\_OUT\_TOTAL\_EOF\_CH0\_INT\_ENA}{1}{3}{{0}}%
\regfield{GDMA\_OUT\_DSCR\_ERR\_CH0\_INT\_ENA}{1}{2}{{0}}%
\regfield{GDMA\_OUT\_EOF\_CH0\_INT\_ENA}{1}{1}{{0}}%
\regfield{GDMA\_OUT\_DONE\_CH0\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAOUTDONECHNINTENA}\item [GDMA\_OUT\_DONE\_CH\regindex{n}\_INT\_ENA] Write 1 to enable GDMA\_OUT\_DONE\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:GDMAOUTEOFCHNINTENA}\item [GDMA\_OUT\_EOF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable GDMA\_OUT\_EOF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:GDMAOUTDSCRERRCHNINTENA}\item [GDMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_ENA] Write 1 to enable GDMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:GDMAOUTTOTALEOFCHNINTENA}\item [GDMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable GDMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:GDMAOUTFIFOOVFCHNINTENA}\item [GDMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable GDMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT. (R/W)
\label{fielddesc:GDMAOUTFIFOUDFCHNINTENA}\item [GDMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT\_ENA] Write 1 to enable GDMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_INT\_CLR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x003C+0x10*\regindex{n}}\label{regdesc:GDMAOUTINTCLRCHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{GDMA\_OUTFIFO\_UDF\_CH0\_INT\_CLR}{1}{5}{{0}}%
\regfield{GDMA\_OUTFIFO\_OVF\_CH0\_INT\_CLR}{1}{4}{{0}}%
\regfield{GDMA\_OUT\_TOTAL\_EOF\_CH0\_INT\_CLR}{1}{3}{{0}}%
\regfield{GDMA\_OUT\_DSCR\_ERR\_CH0\_INT\_CLR}{1}{2}{{0}}%
\regfield{GDMA\_OUT\_EOF\_CH0\_INT\_CLR}{1}{1}{{0}}%
\regfield{GDMA\_OUT\_DONE\_CH0\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAOUTDONECHNINTCLR}\item [GDMA\_OUT\_DONE\_CH\regindex{n}\_INT\_CLR] Write 1 to clear GDMA\_OUT\_DONE\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:GDMAOUTEOFCHNINTCLR}\item [GDMA\_OUT\_EOF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear GDMA\_OUT\_EOF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:GDMAOUTDSCRERRCHNINTCLR}\item [GDMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT\_CLR] Write 1 to clear GDMA\_OUT\_DSCR\_ERR\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:GDMAOUTTOTALEOFCHNINTCLR}\item [GDMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear GDMA\_OUT\_TOTAL\_EOF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:GDMAOUTFIFOOVFCHNINTCLR}\item [GDMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear GDMA\_OUTFIFO\_OVF\_CH\regindex{n}\_INT. (WT)
\label{fielddesc:GDMAOUTFIFOUDFCHNINTCLR}\item [GDMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT\_CLR] Write 1 to clear GDMA\_OUTFIFO\_UDF\_CH\regindex{n}\_INT. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_AHB\_TEST\_REG}{0x0060}\label{regdesc:GDMAAHBTESTREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{GDMA\_AHB\_TESTADDR}{2}{4}{{0}}%
\regfield{(reserved)}{1}{3}{0}%
\regfield{GDMA\_AHB\_TESTMODE}{3}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAAHBTESTMODE}\item [GDMA\_AHB\_TESTMODE] Reserved. (R/W)
\label{fielddesc:GDMAAHBTESTADDR}\item [GDMA\_AHB\_TESTADDR] Reserved. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_MISC\_CONF\_REG}{0x0064}\label{regdesc:GDMAMISCCONFREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{GDMA\_CLK\_EN}{1}{3}{{0}}%
\regfield{GDMA\_ARB\_PRI\_DIS}{1}{2}{{0}}%
\regfield{(reserved)}{1}{1}{0}%
\regfield{GDMA\_AHBM\_RST\_INTER}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAAHBMRSTINTER}\item [GDMA\_AHBM\_RST\_INTER] Write 1 and then 0 to reset the internal AHB FSM. (R/W)
\label{fielddesc:GDMAARBPRIDIS}\item [GDMA\_ARB\_PRI\_DIS] Configures whether or not to disable the fixed-priority channel arbitration.\\
0: Enable\\
1: Disable\\(R/W)
\label{fielddesc:GDMACLKEN}\item [GDMA\_CLK\_EN] Configures clock gating.\\
0: Support clock only when the application writes registers.\\ 
1: Always force the clock on for registers.\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_CONF0\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0070+0xC0*\regindex{n}}\label{regdesc:GDMAINCONF0CHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{GDMA\_IN\_ETM\_EN\_CH0}{1}{5}{{0}}%
\regfield{GDMA\_MEM\_TRANS\_EN\_CH0}{1}{4}{{0}}%
\regfield{GDMA\_IN\_DATA\_BURST\_EN\_CH0}{1}{3}{{0}}%
\regfield{GDMA\_INDSCR\_BURST\_EN\_CH0}{1}{2}{{0}}%
\regfield{GDMA\_IN\_LOOP\_TEST\_CH0}{1}{1}{{0}}%
\regfield{GDMA\_IN\_RST\_CH0}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAINRSTCHN}\item [GDMA\_IN\_RST\_CH\regindex{n}] Write 1 and then 0 to reset GDMA channel 0 RX FSM and RX FIFO pointer.(R/W)
\label{fielddesc:GDMAINLOOPTESTCHN}\item [GDMA\_IN\_LOOP\_TEST\_CH\regindex{n}] Reserved. (R/W)
\label{fielddesc:GDMAINDSCRBURSTENCHN}\item [GDMA\_INDSCR\_BURST\_EN\_CH\regindex{n}] Configures whether or not to enable INCR burst transfer for RX channel \regindex{n} to read descriptors.\\
0: Disable\\
1: Enable\\(R/W)
\label{fielddesc:GDMAINDATABURSTENCHN}\item [GDMA\_IN\_DATA\_BURST\_EN\_CH\regindex{n}] Configures whether or not to enable INCR burst transfer for RX channel \regindex{n}.\\
0: Disable\\
1: Enable\\(R/W)
\label{fielddesc:GDMAMEMTRANSENCHN}\item [GDMA\_MEM\_TRANS\_EN\_CH\regindex{n}] Configures whether or not to enable memory-to-memory data transfer.\\
0: Disable\\
1: Enable\\(R/W)
\label{fielddesc:GDMAINETMENCHN}\item [GDMA\_IN\_ETM\_EN\_CH\regindex{n}] Configures whether or not to enable ETM control for RX channel\regindex{n}.\\
0: Disable\\
1: Enable\\(R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_CONF1\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0074+0xC0*\regindex{n}}\label{regdesc:GDMAINCONF1CHNREG}
\regfield{(reserved)}{19}{13}{0000000000000000000}%
\regfield{GDMA\_IN\_CHECK\_OWNER\_CH0}{1}{12}{{0}}%
\regfield{(reserved)}{12}{0}{000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAINCHECKOWNERCHN}\item [GDMA\_IN\_CHECK\_OWNER\_CH\regindex{n}] Configures whether or not to enable owner bit check for RX channel \regindex{n}.\\
0: Disable\\
1: Enable\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_POP\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x007C+0xC0*\regindex{n}}\label{regdesc:GDMAINPOPCHNREG}
\regfield{(reserved)}{19}{13}{0000000000000000000}%
\regfield{GDMA\_INFIFO\_POP\_CH0}{1}{12}{{0}}%
\regfield{GDMA\_INFIFO\_RDATA\_CH0}{12}{0}{{0x800}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAINFIFORDATACHN}\item [GDMA\_INFIFO\_RDATA\_CH\regindex{n}] Represents the data popped from GDMA FIFO. (RO)
\label{fielddesc:GDMAINFIFOPOPCHN}\item [GDMA\_INFIFO\_POP\_CH\regindex{n}] Configures whether to pop data from GDMA FIFO.\\
0: Invalid. No effect\\
1: Pop\\ (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_LINK\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0080+0xC0*\regindex{n}}\label{regdesc:GDMAINLINKCHNREG}
\regfield{(reserved)}{7}{25}{0000000}%
\regfield{GDMA\_INLINK\_PARK\_CH0}{1}{24}{{1}}%
\regfield{GDMA\_INLINK\_RESTART\_CH0}{1}{23}{{0}}%
\regfield{GDMA\_INLINK\_START\_CH0}{1}{22}{{0}}%
\regfield{GDMA\_INLINK\_STOP\_CH0}{1}{21}{{0}}%
\regfield{GDMA\_INLINK\_AUTO\_RET\_CH0}{1}{20}{{1}}%
\regfield{GDMA\_INLINK\_ADDR\_CH0}{20}{0}{{0x000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAINLINKADDRCHN}\item [GDMA\_INLINK\_ADDR\_CH\regindex{n}] Represents the lower 20 bits of the first receive descriptor's address. (R/W)
\label{fielddesc:GDMAINLINKAUTORETCHN}\item [GDMA\_INLINK\_AUTO\_RET\_CH\regindex{n}] Configures whether or not to return to the current receive descriptor's address when there are some errors in current receiving data.\\
0: Not return\\
1: Return\\(R/W)
\label{fielddesc:GDMAINLINKSTOPCHN}\item [GDMA\_INLINK\_STOP\_CH\regindex{n}] Configures whether to stop GDMA's RX channel \regindex{n} from receiving data.\\
0: Invalid. No effect\\
1: Stop\\ (WT)
\label{fielddesc:GDMAINLINKSTARTCHN}\item [GDMA\_INLINK\_START\_CH\regindex{n}] Configures whether or not to enable GDMA's RX channel \regindex{n} for data transfer.\\
0: Disable\\
1: Enable\\ (WT)
\label{fielddesc:GDMAINLINKRESTARTCHN}\item [GDMA\_INLINK\_RESTART\_CH\regindex{n}] Configures whether or not to restart RX channel \regindex{n} for GDMA transfer.\\
0: Invalid. No effect\\
1: Restart\\ (WT)
\label{fielddesc:GDMAINLINKPARKCHN}\item [GDMA\_INLINK\_PARK\_CH\regindex{n}] Represents the status of the receive descriptor's FSM.\\
0: Running\\
1: Idle\\ (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_CONF0\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00D0+0xC0*\regindex{n}}\label{regdesc:GDMAOUTCONF0CHNREG}
\regfield{(reserved)}{25}{7}{0000000000000000000000000}%
\regfield{GDMA\_OUT\_ETM\_EN\_CH\regindex{n}}{1}{6}{{0}}%
\regfield{GDMA\_OUT\_DATA\_BURST\_EN\_CH\regindex{n}}{1}{5}{{0}}%
\regfield{GDMA\_OUTDSCR\_BURST\_EN\_CH\regindex{n}}{1}{4}{{0}}%
\regfield{GDMA\_OUT\_EOF\_MODE\_CH\regindex{n}}{1}{3}{{1}}%
\regfield{GDMA\_OUT\_AUTO\_WRBACK\_CH\regindex{n}}{1}{2}{{0}}%
\regfield{GDMA\_OUT\_LOOP\_TEST\_CH\regindex{n}}{1}{1}{{0}}%
\regfield{GDMA\_OUT\_RST\_CH\regindex{n}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAOUTRSTCHN}\item [GDMA\_OUT\_RST\_CH\regindex{n}] Configures the reset state of GDMA channel \regindex{n} TX FSM and TX FIFO pointer.\\
0: Release reset\\
1: Reset\\(R/W)
\label{fielddesc:GDMAOUTLOOPTESTCHN}\item [GDMA\_OUT\_LOOP\_TEST\_CH\regindex{n}] Reserved. (R/W)
\label{fielddesc:GDMAOUTAUTOWRBACKCHN}\item [GDMA\_OUT\_AUTO\_WRBACK\_CH\regindex{n}] Configures whether or not to enable automatic outlink write-back when all the data in TX FIFO has been transmitted.\\
0: Disable\\
1: Enable\\(R/W)
\label{fielddesc:GDMAOUTEOFMODECHN}\item [GDMA\_OUT\_EOF\_MODE\_CH\regindex{n}] Configures when to generate EOF flag.\\
0: EOF flag for TX channel \regindex{n} is generated when data to be transmitted has been pushed into FIFO in GDMA.\\ 
1: EOF flag for TX channel \regindex{n} is generated when data to be transmitted has been popped from FIFO in GDMA.\\ (R/W)
\label{fielddesc:GDMAOUTDSCRBURSTENCHN}\item [GDMA\_OUTDSCR\_BURST\_EN\_CH\regindex{n}] Configures whether or not to enable INCR burst transfer for TX channel \regindex{n} reading descriptors.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:GDMAOUTDATABURSTENCHN}\item [GDMA\_OUT\_DATA\_BURST\_EN\_CH\regindex{n}] Configures whether or not to enable INCR burst transfer for TX channel \regindex{n}.\\
0: Disable\\
1: Enable\\ (R/W)
\label{fielddesc:GDMAOUTETMENCHN}\item [GDMA\_OUT\_ETM\_EN\_CH\regindex{n}] Configures whether or not to enable ETM control for TX channel \regindex{n}.\\
0: Disable\\
1: Enable\\( (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_CONF1\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00D4+0xC0*\regindex{n}}\label{regdesc:GDMAOUTCONF1CHNREG}
\regfield{(reserved)}{19}{13}{0000000000000000000}%
\regfield{GDMA\_OUT\_CHECK\_OWNER\_CH0}{1}{12}{{0}}%
\regfield{(reserved)}{12}{0}{000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAOUTCHECKOWNERCHN}\item [GDMA\_OUT\_CHECK\_OWNER\_CH\regindex{n}] Configures whether or not to enable owner bit check for TX channel \regindex{n}.\\
0: Disable\\
1: Enable\\ (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_PUSH\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00DC+0xC0*\regindex{n}}\label{regdesc:GDMAOUTPUSHCHNREG}
\regfield{(reserved)}{22}{10}{0000000000000000000000}%
\regfield{GDMA\_OUTFIFO\_PUSH\_CH0}{1}{9}{{0}}%
\regfield{GDMA\_OUTFIFO\_WDATA\_CH0}{9}{0}{{0x0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAOUTFIFOWDATACHN}\item [GDMA\_OUTFIFO\_WDATA\_CH\regindex{n}] Represents the data that need to be pushed into GDMA FIFO. (R/W)
\label{fielddesc:GDMAOUTFIFOPUSHCHN}\item [GDMA\_OUTFIFO\_PUSH\_CH\regindex{n}] Configures whether to push data into GDMA FIFO.\\
0: Invalid. No effect\\
1: Push\\ (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_LINK\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00E0+0xC0*\regindex{n}}\label{regdesc:GDMAOUTLINKCHNREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{GDMA\_OUTLINK\_PARK\_CH0}{1}{23}{{1}}%
\regfield{GDMA\_OUTLINK\_RESTART\_CH0}{1}{22}{{0}}%
\regfield{GDMA\_OUTLINK\_START\_CH0}{1}{21}{{0}}%
\regfield{GDMA\_OUTLINK\_STOP\_CH0}{1}{20}{{0}}%
\regfield{GDMA\_OUTLINK\_ADDR\_CH0}{20}{0}{{0x000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAOUTLINKADDRCHN}\item [GDMA\_OUTLINK\_ADDR\_CH\regindex{n}] Represents the lower 20 bits of the first transmit descriptor's address. (R/W)
\label{fielddesc:GDMAOUTLINKSTOPCHN}\item [GDMA\_OUTLINK\_STOP\_CH\regindex{n}] Configures whether to stop GDMA's TX channel \regindex{n} from transmitting data.\\
0: Invalid. No effect\\
1: Stop\\ (WT)
\label{fielddesc:GDMAOUTLINKSTARTCHN}\item [GDMA\_OUTLINK\_START\_CH\regindex{n}] Configures whether or not to enable GDMA's TX channel \regindex{n} for data transfer.\\
0: Disable\\
1: Enable\\ (WT)
\label{fielddesc:GDMAOUTLINKRESTARTCHN}\item [GDMA\_OUTLINK\_RESTART\_CH\regindex{n}] Configures whether to restart TX channel \regindex{n} for GDMA transfer.\\
0: Invalid. No effect\\
1: Restart\\ (WT)
\label{fielddesc:GDMAOUTLINKPARKCHN}\item [GDMA\_OUTLINK\_PARK\_CH\regindex{n}] Represents the status of the transmit descriptor's FSM.\\
0: Running\\
1: Idle\\ (RO)
\end{reglist}\end{regdesc}
\end{register}



\begin{register}{H}{GDMA\_DATE\_REG}{0x0068}\label{regdesc:GDMADATEREG}
\regfield{GDMA\_DATE}{32}{0}{{0x2202250}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMADATE}\item [GDMA\_DATE] Version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_INFIFO\_STATUS\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0078+0xC0*\regindex{n}}\label{regdesc:GDMAINFIFOSTATUSCHNREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{GDMA\_IN\_BUF\_HUNGRY\_CH0}{1}{27}{{0}}%
\regfield{GDMA\_IN\_REMAIN\_UNDER\_4B\_CH0}{1}{26}{{1}}%
\regfield{GDMA\_IN\_REMAIN\_UNDER\_3B\_CH0}{1}{25}{{1}}%
\regfield{GDMA\_IN\_REMAIN\_UNDER\_2B\_CH0}{1}{24}{{1}}%
\regfield{GDMA\_IN\_REMAIN\_UNDER\_1B\_CH0}{1}{23}{{1}}%
\regfield{(reserved)}{15}{8}{000000000000000}%
\regfield{GDMA\_INFIFO\_CNT\_CH0}{6}{2}{{0}}%
\regfield{GDMA\_INFIFO\_EMPTY\_CH0}{1}{1}{{1}}%
\regfield{GDMA\_INFIFO\_FULL\_CH0}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAINFIFOFULLCHN}\item [GDMA\_INFIFO\_FULL\_CH\regindex{n}] Represents whether or not L1 RX FIFO is full.\\
0: Not Full\\
1: Full\\(RO)
\label{fielddesc:GDMAINFIFOEMPTYCHN}\item [GDMA\_INFIFO\_EMPTY\_CH\regindex{n}] Represents whether or not  L1 RX FIFO is empty.\\
0: Not empty\\
1: Empty\\ (RO)
\label{fielddesc:GDMAINFIFOCNTCHN}\item [GDMA\_INFIFO\_CNT\_CH\regindex{n}] Represents the number of data bytes in L1 RX FIFO for RX channel \regindex{n}. (RO)
\label{fielddesc:GDMAINREMAINUNDER1BCHN}\item [GDMA\_IN\_REMAIN\_UNDER\_1B\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:GDMAINREMAINUNDER2BCHN}\item [GDMA\_IN\_REMAIN\_UNDER\_2B\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:GDMAINREMAINUNDER3BCHN}\item [GDMA\_IN\_REMAIN\_UNDER\_3B\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:GDMAINREMAINUNDER4BCHN}\item [GDMA\_IN\_REMAIN\_UNDER\_4B\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:GDMAINBUFHUNGRYCHN}\item [GDMA\_IN\_BUF\_HUNGRY\_CH\regindex{n}] Reserved. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_STATE\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0084+0xC0*\regindex{n}}\label{regdesc:GDMAINSTATECHNREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{GDMA\_IN\_STATE\_CH0}{3}{20}{{0}}%
\regfield{GDMA\_IN\_DSCR\_STATE\_CH0}{2}{18}{{0}}%
\regfield{GDMA\_INLINK\_DSCR\_ADDR\_CH0}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAINLINKDSCRADDRCHN}\item [GDMA\_INLINK\_DSCR\_ADDR\_CH\regindex{n}] Represents the lower 18 bits of the address of the next receive descriptor that is pre-read (but not processed yet). If the current receive descriptor is the last descriptor, then this field represents the address of the current receive descriptor. (RO)
\label{fielddesc:GDMAINDSCRSTATECHN}\item [GDMA\_IN\_DSCR\_STATE\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:GDMAINSTATECHN}\item [GDMA\_IN\_STATE\_CH\regindex{n}] Reserved. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_SUC\_EOF\_DES\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0088+0xC0*\regindex{n}}\label{regdesc:GDMAINSUCEOFDESADDRCHNREG}
\regfield{GDMA\_IN\_SUC\_EOF\_DES\_ADDR\_CH0}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAINSUCEOFDESADDRCHN}\item [GDMA\_IN\_SUC\_EOF\_DES\_ADDR\_CH\regindex{n}] Represents the address of the receive descriptor when the EOF bit in this descriptor is 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_ERR\_EOF\_DES\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x008C+0xC0*\regindex{n}}\label{regdesc:GDMAINERREOFDESADDRCHNREG}
\regfield{GDMA\_IN\_ERR\_EOF\_DES\_ADDR\_CH0}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAINERREOFDESADDRCHN}\item [GDMA\_IN\_ERR\_EOF\_DES\_ADDR\_CH\regindex{n}] Represents the address of the receive descriptor when there are some errors in the currently received data. Valid only for UHCI or PARLIO. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_DSCR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0090+0xC0*\regindex{n}}\label{regdesc:GDMAINDSCRCHNREG}
\regfield{GDMA\_INLINK\_DSCR\_CH0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAINLINKDSCRCHN}\item [GDMA\_INLINK\_DSCR\_CH\regindex{n}] Represents the address of the next receive descriptor x+1 pointed by the current receive descriptor that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_DSCR\_BF0\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0094+0xC0*\regindex{n}}\label{regdesc:GDMAINDSCRBF0CHNREG}
\regfield{GDMA\_INLINK\_DSCR\_BF0\_CH0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAINLINKDSCRBF0CHN}\item [GDMA\_INLINK\_DSCR\_BF0\_CH\regindex{n}] Represents the address of the current receive descriptor x that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_DSCR\_BF1\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0098+0xC0*\regindex{n}}\label{regdesc:GDMAINDSCRBF1CHNREG}
\regfield{GDMA\_INLINK\_DSCR\_BF1\_CH0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAINLINKDSCRBF1CHN}\item [GDMA\_INLINK\_DSCR\_BF1\_CH\regindex{n}] Represents the address of the previous receive descriptor x-1 that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUTFIFO\_STATUS\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00D8+0xC0*\regindex{n}}\label{regdesc:GDMAOUTFIFOSTATUSCHNREG}
\regfield{(reserved)}{5}{27}{00000}%
\regfield{GDMA\_OUT\_REMAIN\_UNDER\_4B\_CH0}{1}{26}{{1}}%
\regfield{GDMA\_OUT\_REMAIN\_UNDER\_3B\_CH0}{1}{25}{{1}}%
\regfield{GDMA\_OUT\_REMAIN\_UNDER\_2B\_CH0}{1}{24}{{1}}%
\regfield{GDMA\_OUT\_REMAIN\_UNDER\_1B\_CH0}{1}{23}{{1}}%
\regfield{(reserved)}{15}{8}{000000000000000}%
\regfield{GDMA\_OUTFIFO\_CNT\_CH0}{6}{2}{{0}}%
\regfield{GDMA\_OUTFIFO\_EMPTY\_CH0}{1}{1}{{1}}%
\regfield{GDMA\_OUTFIFO\_FULL\_CH0}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAOUTFIFOFULLCHN}\item [GDMA\_OUTFIFO\_FULL\_CH\regindex{n}] Represents whether or not L1 TX FIFO is full.\\
0: Not Full\\
1: Full\\ (RO)
\label{fielddesc:GDMAOUTFIFOEMPTYCHN}\item [GDMA\_OUTFIFO\_EMPTY\_CH\regindex{n}] Represents whether or not L1 TX FIFO is empty.\\
0: Not empty\\
1: Empty\\ (RO)
\label{fielddesc:GDMAOUTFIFOCNTCHN}\item [GDMA\_OUTFIFO\_CNT\_CH\regindex{n}] Represents the number of data bytes in L1 TX FIFO for TX channel \regindex{n}. (RO)
\label{fielddesc:GDMAOUTREMAINUNDER1BCHN}\item [GDMA\_OUT\_REMAIN\_UNDER\_1B\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:GDMAOUTREMAINUNDER2BCHN}\item [GDMA\_OUT\_REMAIN\_UNDER\_2B\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:GDMAOUTREMAINUNDER3BCHN}\item [GDMA\_OUT\_REMAIN\_UNDER\_3B\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:GDMAOUTREMAINUNDER4BCHN}\item [GDMA\_OUT\_REMAIN\_UNDER\_4B\_CH\regindex{n}] Reserved. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_STATE\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00E4+0xC0*\regindex{n}}\label{regdesc:GDMAOUTSTATECHNREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{GDMA\_OUT\_STATE\_CH0}{3}{20}{{0}}%
\regfield{GDMA\_OUT\_DSCR\_STATE\_CH0}{2}{18}{{0}}%
\regfield{GDMA\_OUTLINK\_DSCR\_ADDR\_CH0}{18}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAOUTLINKDSCRADDRCHN}\item [GDMA\_OUTLINK\_DSCR\_ADDR\_CH\regindex{n}] Represents the lower 18 bits of the address of the next transmit descriptor that is pre-read (but not processed yet). If the current transmit descriptor is the last descriptor, then this field represents the address of the current transmit descriptor. (RO)
\label{fielddesc:GDMAOUTDSCRSTATECHN}\item [GDMA\_OUT\_DSCR\_STATE\_CH\regindex{n}] Reserved. (RO)
\label{fielddesc:GDMAOUTSTATECHN}\item [GDMA\_OUT\_STATE\_CH\regindex{n}] Reserved. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_EOF\_DES\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00E8+0xC0*\regindex{n}}\label{regdesc:GDMAOUTEOFDESADDRCHNREG}
\regfield{GDMA\_OUT\_EOF\_DES\_ADDR\_CH0}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAOUTEOFDESADDRCHN}\item [GDMA\_OUT\_EOF\_DES\_ADDR\_CH\regindex{n}] Represents the address of the transmit descriptor when the EOF bit in this descriptor is 1. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_EOF\_BFR\_DES\_ADDR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00EC+0xC0*\regindex{n}}\label{regdesc:GDMAOUTEOFBFRDESADDRCHNREG}
\regfield{GDMA\_OUT\_EOF\_BFR\_DES\_ADDR\_CH0}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAOUTEOFBFRDESADDRCHN}\item [GDMA\_OUT\_EOF\_BFR\_DES\_ADDR\_CH\regindex{n}] Represents the address of the transmit descriptor before the last transmit descriptor. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_DSCR\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00F0+0xC0*\regindex{n}}\label{regdesc:GDMAOUTDSCRCHNREG}
\regfield{GDMA\_OUTLINK\_DSCR\_CH0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAOUTLINKDSCRCHN}\item [GDMA\_OUTLINK\_DSCR\_CH\regindex{n}] Represents the address of the next transmit descriptor y+1 pointed by the current transmit descriptor that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_DSCR\_BF0\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00F4+0xC0*\regindex{n}}\label{regdesc:GDMAOUTDSCRBF0CHNREG}
\regfield{GDMA\_OUTLINK\_DSCR\_BF0\_CH0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAOUTLINKDSCRBF0CHN}\item [GDMA\_OUTLINK\_DSCR\_BF0\_CH\regindex{n}] Represents the address of the current transmit descriptor y that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_DSCR\_BF1\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00F8+0xC0*\regindex{n}}\label{regdesc:GDMAOUTDSCRBF1CHNREG}
\regfield{GDMA\_OUTLINK\_DSCR\_BF1\_CH0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAOUTLINKDSCRBF1CHN}\item [GDMA\_OUTLINK\_DSCR\_BF1\_CH\regindex{n}] Represents the address of the previous transmit descriptor y-1 that is pre-read. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_PRI\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x009C+0xC0*\regindex{n}}\label{regdesc:GDMAINPRICHNREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{GDMA\_RX\_PRI\_CH0}{4}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMARXPRICHN}\item [GDMA\_RX\_PRI\_CH\regindex{n}] Configures the priority of RX channel \regindex{n}.\\
Value range: 0 \verb+~+ 9\\
The larger of the value, the higher of the priority. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_PRI\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00FC+0xC0*\regindex{n}}\label{regdesc:GDMAOUTPRICHNREG}
\regfield{(reserved)}{28}{4}{0000000000000000000000000000}%
\regfield{GDMA\_TX\_PRI\_CH0}{4}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMATXPRICHN}\item [GDMA\_TX\_PRI\_CH\regindex{n}] Configures the priority of TX channel \regindex{n}.\\
Value range: 0 \verb+~+ 9\\
The larger of the value, the higher of the priority. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_IN\_PERI\_SEL\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x00A0+0xC0*\regindex{n}}\label{regdesc:GDMAINPERISELCHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{GDMA\_PERI\_IN\_SEL\_CH0}{6}{0}{{0x3f}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAPERIINSELCHN}\item [GDMA\_PERI\_IN\_SEL\_CH\regindex{n}] Configures the peripheral connected to RX channel \regindex{n}.\\
0: SPI2\\
1: Dummy-1\\
2: UHCI\\
3: I2S\\
4: Dummy-4\\
5: Dummy-5\\
6: AES\\
7: SHA\\
8: ADC\\
9: Parallel IO\\
10 \verb+~+ 15: Dummy-10  \verb+~+  15\\
16 \verb+~+ 63: Invalid.\\
(R/W)

\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{GDMA\_OUT\_PERI\_SEL\_CH\regindex{n}\_REG (\regindex{n}: 0-2)}{0x0100+0xC0*\regindex{n}}\label{regdesc:GDMAOUTPERISELCHNREG}
\regfield{(reserved)}{26}{6}{00000000000000000000000000}%
\regfield{GDMA\_PERI\_OUT\_SEL\_CH0}{6}{0}{{0x3f}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:GDMAPERIOUTSELCHN}\item [GDMA\_PERI\_OUT\_SEL\_CH\regindex{n}] Configures the peripheral connected to TX channel \regindex{n}.\\
0: SPI2\\
1: Dummy-1\\
2: UHCI\\
3: I2S\\
4: Dummy-4\\
5: Dummy-5\\
6: AES\\
7: SHA\\
8: ADC\\
9: Parallel IO\\
10 \verb+~+  15: Dummy-10  \verb+~+  15\\
16 \verb+~+ 63: Invalid.\\
(R/W)
\end{reglist}\end{regdesc}
\end{register}


