\begin{register}{H}{I2S\_CONF\_REG}{\hexprefix{}0008}\label{regdesc:I2SCONFREG}
\regfield{(reserved)}{2}{30}{00}%
\regfield{I2S\_RX\_RESET\_ST}{1}{29}{{0}}%
\regfield{I2S\_RX\_BIG\_ENDIAN}{1}{28}{{0}}%
\regfield{I2S\_TX\_BIG\_ENDIAN}{1}{27}{{0}}%
\regfield{I2S\_PRE\_REQ\_EN}{1}{26}{{0}}%
\regfield{I2S\_RX\_DMA\_EQUAL}{1}{25}{{0}}%
\regfield{I2S\_TX\_DMA\_EQUAL}{1}{24}{{0}}%
\regfield{I2S\_TX\_RESET\_ST}{1}{23}{{0}}%
\regfield{I2S\_RX\_FIFO\_RESET\_ST}{1}{22}{{0}}%
\regfield{I2S\_TX\_FIFO\_RESET\_ST}{1}{21}{{0}}%
\regfield{I2S\_SIG\_LOOPBACK}{1}{20}{{0}}%
\regfield{(reserved)}{1}{19}{{1}}%
\regfield{(reserved)}{1}{18}{{1}}%
\regfield{I2S\_RX\_MSB\_RIGHT}{1}{17}{{0}}%
\regfield{I2S\_TX\_MSB\_RIGHT}{1}{16}{{0}}%
\regfield{I2S\_RX\_MONO}{1}{15}{{0}}%
\regfield{I2S\_TX\_MONO}{1}{14}{{0}}%
\regfield{I2S\_RX\_SHORT\_SYNC}{1}{13}{{0}}%
\regfield{I2S\_TX\_SHORT\_SYNC}{1}{12}{{0}}%
\regfield{I2S\_RX\_MSB\_SHIFT}{1}{11}{{0}}%
\regfield{I2S\_TX\_MSB\_SHIFT}{1}{10}{{0}}%
\regfield{I2S\_RX\_RIGHT\_FIRST}{1}{9}{{1}}%
\regfield{I2S\_TX\_RIGHT\_FIRST}{1}{8}{{1}}%
\regfield{I2S\_RX\_SLAVE\_MOD}{1}{7}{{0}}%
\regfield{I2S\_TX\_SLAVE\_MOD}{1}{6}{{0}}%
\regfield{I2S\_RX\_START}{1}{5}{{0}}%
\regfield{I2S\_TX\_START}{1}{4}{{0}}%
\regfield{I2S\_RX\_FIFO\_RESET}{1}{3}{{0}}%
\regfield{I2S\_TX\_FIFO\_RESET}{1}{2}{{0}}%
\regfield{I2S\_RX\_RESET}{1}{1}{{0}}%
\regfield{I2S\_TX\_RESET}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2STXRESET}\item [I2S\_TX\_RESET] Set this bit to reset transmitter. (WO)
\label{fielddesc:I2SRXRESET}\item [I2S\_RX\_RESET] Set this bit to reset receiver. (WO)
\label{fielddesc:I2STXFIFORESET}\item [I2S\_TX\_FIFO\_RESET] Set this bit to reset TX FIFO. (WO)
\label{fielddesc:I2SRXFIFORESET}\item [I2S\_RX\_FIFO\_RESET] Set this bit to reset RX FIFO. (WO)
\label{fielddesc:I2STXSTART}\item [I2S\_TX\_START] Set this bit to start transmitting data. (R/W)
\label{fielddesc:I2SRXSTART}\item [I2S\_RX\_START] Set this bit to start receiving data. (R/W)
\label{fielddesc:I2STXSLAVEMOD}\item [I2S\_TX\_SLAVE\_MOD] Set this bit to enable slave transmitter mode. (R/W)
\label{fielddesc:I2SRXSLAVEMOD}\item [I2S\_RX\_SLAVE\_MOD] Set this bit to enable slave receiver mode. (R/W)
\label{fielddesc:I2STXRIGHTFIRST}\item [I2S\_TX\_RIGHT\_FIRST] Set this bit to transmit right channel data first. (R/W)
\label{fielddesc:I2SRXRIGHTFIRST}\item [I2S\_RX\_RIGHT\_FIRST] Set this bit to receive right channel data first. (R/W)
\label{fielddesc:I2STXMSBSHIFT}\item [I2S\_TX\_MSB\_SHIFT] Set this bit to enable transmitter in Phillips standard mode. (R/W)
\label{fielddesc:I2SRXMSBSHIFT}\item [I2S\_RX\_MSB\_SHIFT] Set this bit to enable receiver in Phillips standard mode. (R/W)
\label{fielddesc:I2STXSHORTSYNC}\item [I2S\_TX\_SHORT\_SYNC] Set this bit to enable transmitter in PCM standard mode. (R/W)
\label{fielddesc:I2SRXSHORTSYNC}\item [I2S\_RX\_SHORT\_SYNC] Set this bit to enable receiver in PCM standard mode. (R/W)
\label{fielddesc:I2STXMONO}\item [I2S\_TX\_MONO] Set this bit to enable transmitter in mono mode. (R/W)
\label{fielddesc:I2SRXMONO}\item [I2S\_RX\_MONO] Set this bit to enable receiver in mono mode. (R/W)
\label{fielddesc:I2STXMSBRIGHT}\item [I2S\_TX\_MSB\_RIGHT] Set this bit to place right channel data at the MSB in TX FIFO. (R/W)
\label{fielddesc:I2SRXMSBRIGHT}\item [I2S\_RX\_MSB\_RIGHT] Set this bit to place right channel data at the MSB in RX FIFO. (R/W)
\label{fielddesc:I2SSIGLOOPBACK}\item [I2S\_SIG\_LOOPBACK] Enable signal loopback mode with transmitter module and receiver module sharing the same WS and BCK signals. (R/W)
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{I2S\_CONF\_REG}{\hexprefix{}0008}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\label{fielddesc:I2STXFIFORESETST}\item [I2S\_TX\_FIFO\_RESET\_ST] I2S TX FIFO reset status. 1: I2S\_TX\_FIFO\_RESET is not completed. 0: I2S\_TX\_FIFO\_RESET is completed. (RO)
\label{fielddesc:I2SRXFIFORESETST}\item [I2S\_RX\_FIFO\_RESET\_ST] I2S RX FIFO reset status. 1: I2S\_RX\_FIFO\_RESET is not completed. 0: I2S\_RX\_FIFO\_RESET is completed. (RO)
\label{fielddesc:I2STXRESETST}\item [I2S\_TX\_RESET\_ST] I2S TX reset status. 1: I2S\_TX\_RESET is not completed. 0: I2S\_TX\_RESET is completed. (RO)
\label{fielddesc:I2STXDMAEQUAL}\item [I2S\_TX\_DMA\_EQUAL] 1: Data in left channel is equal to data in right channel. 0: Data in left channel is not equal to data in right channel. (R/W)
\label{fielddesc:I2SRXDMAEQUAL}\item [I2S\_RX\_DMA\_EQUAL] 1: Data in left channel is equal to data in right channel. 0: Data in left channel is not equal to data in right channel. (R/W)
\label{fielddesc:I2SPREREQEN}\item [I2S\_PRE\_REQ\_EN] Set this bit to enable I2S to prepare data earlier. (R/W)
\label{fielddesc:I2STXBIGENDIAN}\item [I2S\_TX\_BIG\_ENDIAN] I2S TX byte endianness. (R/W)
\label{fielddesc:I2SRXBIGENDIAN}\item [I2S\_RX\_BIG\_ENDIAN] I2S RX byte endianness. (R/W)
\label{fielddesc:I2SRXRESETST}\item [I2S\_RX\_RESET\_ST] I2S RX reset status. 1: I2S\_RX\_RESET is not completed. 0: I2S\_RX\_RESET is completed. (RO)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{I2S\_FIFO\_CONF\_REG}{\hexprefix{}0020}\label{regdesc:I2SFIFOCONFREG}
\regfield{(reserved)}{11}{21}{00000000000}%
\regfield{I2S\_RX\_FIFO\_MOD\_FORCE\_EN}{1}{20}{{0}}%
\regfield{I2S\_TX\_FIFO\_MOD\_FORCE\_EN}{1}{19}{{0}}%
\regfield{I2S\_RX\_FIFO\_MOD}{3}{16}{{0}}%
\regfield{I2S\_TX\_FIFO\_MOD}{3}{13}{{0}}%
\regfield{I2S\_DSCR\_EN}{1}{12}{{1}}%
\regfield{I2S\_RX\_DATA\_NUM}{6}{6}{{32}}%
\regfield{I2S\_RX\_DATA\_NUM}{6}{0}{{32}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SRXDATANUM}\item [I2S\_RX\_DATA\_NUM] I2S\_RX\_TAKE\_DATA\_INT is triggered when the left and right channel data number in RX FIFO is larger than the value of I2S\_RX\_DATA\_NUM[5:0]. (RX FIFO is almost full threshold.)
\label{fielddesc:I2STXDATANUM}\item [I2S\_TX\_DATA\_NUM] I2S\_TX\_PUT\_DATA\_INT is triggered when the left and right channel data number in TX FIFO is smaller than the value of I2S\_TX\_DATA\_NUM[5:0]. (TX FIFO is almost empty threshold.)
\label{fielddesc:I2SDSCREN}\item [I2S\_DSCR\_EN] Set this bit to enable I2S DMA mode. (R/W)
\label{fielddesc:I2STXFIFOMOD}\item [I2S\_TX\_FIFO\_MOD] Configures TX FIFO mode.\\
0: 8/16 bit dual channel mode\\
1: 8/16 bit mono mode\\
2: 24/32 bit dual channel mode\\
3: 24/32 bit mono mode\\
4-7: reserved\\
To configure the TX FIFO mode, configurations of other registers are required, such as \hyperref[fielddesc:I2STXBITSMOD]{I2S\_TX\_BITS\_MOD} to choose bit width, \hyperref[fielddesc:I2STXCHANMOD]{I2S\_TX\_CHAN\_MOD} to choose dual channel or mono mode, etc. For details please see Section \ref{sec:i2s-conf-tx-mode}.\\ 
(R/W)
\label{fielddesc:I2SRXFIFOMOD}\item [I2S\_RX\_FIFO\_MOD] Configures RX FIFO mode.\\
0: 8/16 bit dual channel mode\\
1: 8/16 bit mono mode\\
2: 24/32 bit dual channel mode\\
3: 24/32 bit mono mode\\
4-7: reserved\\
To configure the RX FIFO mode, configurations of other registers are required, such as  \hyperref[fielddesc:I2SRXBITSMOD]{I2S\_RX\_BITS\_MOD} to choose bit width, \hyperref[fielddesc:I2SRXCHANMOD]{I2S\_RX\_CHAN\_MOD} to choose dual channel or mono mode, etc. For details please see Section \ref{sec:i2s-conf-rx-mode}.\\
(R/W)
\label{fielddesc:I2STXFIFOMODFORCEEN}\item [I2S\_TX\_FIFO\_MOD\_FORCE\_EN] This field must be set to 1. (R/W)
\label{fielddesc:I2SRXFIFOMODFORCEEN}\item [I2S\_RX\_FIFO\_MOD\_FORCE\_EN] This field must be set to 1. (R/W)
\end{reglist}\end{regdesc}
\end{register}



\begin{register}{H}{I2S\_CONF\_SIGLE\_DATA\_REG}{\hexprefix{}0028}\label{regdesc:I2SCONFSIGLEDATAREG}
\regfield{I2S\_SIGLE\_DATA}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SSIGLEDATA}\item [I2S\_SIGLE\_DATA] The right channel or left channel transmits constant value stored in this register according to I2S\_TX\_CHAN\_MOD and I2S\_TX\_MSB\_RIGHT. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_CONF\_CHAN\_REG}{\hexprefix{}002C}\label{regdesc:I2SCONFCHANREG}
\regfield{(reserved)}{27}{5}{000000000000000000000000000}%
\regfield{I2S\_RX\_CHAN\_MOD}{2}{3}{{0}}%
\regfield{I2S\_TX\_CHAN\_MOD}{3}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2STXCHANMOD}\item [I2S\_TX\_CHAN\_MOD] I2S transmitter channel mode configuration bits. (R/W)
\label{fielddesc:I2SRXCHANMOD}\item [I2S\_RX\_CHAN\_MOD] I2S receiver channel mode configuration bits. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_LC\_HUNG\_CONF\_REG}{\hexprefix{}0074}\label{regdesc:I2SLCHUNGCONFREG}
\regfield{(reserved)}{20}{12}{00000000000000000000}%
\regfield{I2S\_LC\_FIFO\_TIMEOUT\_ENA}{1}{11}{{1}}%
\regfield{I2S\_LC\_FIFO\_TIMEOUT\_SHIFT}{3}{8}{{0}}%
\regfield{I2S\_LC\_FIFO\_TIMEOUT}{8}{0}{{\hexprefix{}10}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SLCFIFOTIMEOUT}\item [I2S\_LC\_FIFO\_TIMEOUT] I2S\_TX\_HUNG\_INT interrupt or I2S\_RX\_HUNG\_INT interrupt will be triggered when FIFO hung counter is equal to this value. (R/W)
\label{fielddesc:I2SLCFIFOTIMEOUTSHIFT}\item [I2S\_LC\_FIFO\_TIMEOUT\_SHIFT] The bits are used to set the tick counter threshold. The tick counter is clocked by CLK\_APB. The tick counter threshold is 88000/2$^{I2S\_LC\_FIFO\_TIMEOUT\_SHIFT}$. The tick counter is reset when it reaches the threshold. (R/W)
\label{fielddesc:I2SLCFIFOTIMEOUTENA}\item [I2S\_LC\_FIFO\_TIMEOUT\_ENA] The enable bit for FIFO timeout. (R/W)
\end{reglist}\end{regdesc}
\end{register}



\begin{register}{H}{I2S\_CONF1 \_REG}{\hexprefix{}00A0}\label{regdesc:I2SCONF1 REG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{I2S\_TX\_STOP\_EN}{1}{8}{{0}}%
\regfield{(reserved)}{8}{0}{00000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2STXSTOPEN}\item [I2S\_TX\_STOP\_EN] Set this bit to stop the output of BCK signal and WS signal when TX FIFO is empty. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_PD\_CONF\_REG}{\hexprefix{}00A4}\label{regdesc:I2SPDCONFREG}
\regfield{(reserved)}{25}{7}{0000000000000000000000000}%
\regfield{I2S\_DMA\_RAM\_CLK\_FO}{1}{6}{{0}}%
\regfield{I2S\_DMA\_RAM\_FORCE\_PU}{1}{5}{{1}}%
\regfield{I2S\_DMA\_RAM\_FORCE\_PD}{1}{4}{{0}}%
\regfield{I2S\_PLC\_MEM\_FORCE\_PU}{1}{3}{{1}}%
\regfield{I2S\_PLC\_MEM\_FORCE\_PD}{1}{2}{{0}}%
\regfield{I2S\_FIFO\_FORCE\_PU}{1}{1}{{1}}%
\regfield{I2S\_FIFO\_FORCE\_PD}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SFIFOFORCEPD}\item [I2S\_FIFO\_FORCE\_PD] Force FIFO power-down. (R/W)
\label{fielddesc:I2SFIFOFORCEPU}\item [I2S\_FIFO\_FORCE\_PU] Force FIFO power-up. (R/W)
\label{fielddesc:I2SPLCMEMFORCEPD}\item [I2S\_PLC\_MEM\_FORCE\_PD] Force I2S memory power-down. (R/W)
\label{fielddesc:I2SPLCMEMFORCEPU}\item [I2S\_PLC\_MEM\_FORCE\_PU] Force I2S memory power-up. (R/W)
\label{fielddesc:I2SDMARAMFORCEPD}\item [I2S\_DMA\_RAM\_FORCE\_PD] Force DMA FIFO power-down. (R/W)
\label{fielddesc:I2SDMARAMFORCEPU}\item [I2S\_DMA\_RAM\_FORCE\_PU] Force DMA FIFO power-up. (R/W)
\label{fielddesc:I2SDMARAMCLKFO}\item [I2S\_DMA\_RAM\_CLK\_FO] Set this bit to force on DMA RAM clock. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_CONF2\_REG}{\hexprefix{}00A8}\label{regdesc:I2SCONF2REG}
\regfield{(reserved)}{18}{14}{000000000000000000}%
\regfield{I2S\_VSYNC\_FILTER\_THRES}{3}{11}{{0}}%
\regfield{I2S\_VSYNC\_FILTER\_EN}{1}{10}{{0}}%
\regfield{I2S\_CAM\_CLK\_LOOPBACK}{1}{9}{{0}}%
\regfield{I2S\_CAM\_SYNC\_FIFO\_RESET}{1}{8}{{0}}%
\regfield{I2S\_INTER\_VALID\_EN}{1}{7}{{0}}%
\regfield{(reserved)}{1}{6}{{0}}%
\regfield{I2S\_LCD\_EN}{1}{5}{{0}}%
\regfield{(reserved)}{2}{3}{00}%
\regfield{I2S\_LCD\_TX\_SDX2\_EN}{1}{2}{{0}}%
\regfield{I2S\_LCD\_TX\_WRX2\_EN}{1}{1}{{0}}%
\regfield{I2S\_CAMERA\_EN}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SCAMERAEN}\item [I2S\_CAMERA\_EN] Set this bit to enable camera mode. (R/W)
\label{fielddesc:I2SLCDTXWRX2EN}\item [I2S\_LCD\_TX\_WRX2\_EN] LCD WR double for one datum. (R/W)
\label{fielddesc:I2SLCDTXSDX2EN}\item [I2S\_LCD\_TX\_SDX2\_EN] Set this bit to duplicate data pairs (Frame Form 2) in LCD mode. (R/W)
\label{fielddesc:I2SLCDEN}\item [I2S\_LCD\_EN] Set this bit to enable LCD mode. (R/W)
\label{fielddesc:I2SINTERVALIDEN}\item [I2S\_INTER\_VALID\_EN] Set this bit to enable camera VGA reducing-resolution mode: only receive two consecutive cycle data in four consecutive clocks. (R/W)
\label{fielddesc:I2SCAMSYNCFIFORESET}\item [I2S\_CAM\_SYNC\_FIFO\_RESET] Set this bit to reset FIFO in camera mode. (R/W)
\label{fielddesc:I2SCAMCLKLOOPBACK}\item [I2S\_CAM\_CLK\_LOOPBACK] Set this bit to loopback PCLK from I2S0I\_WS\_out. (R/W)
\label{fielddesc:I2SVSYNCFILTEREN}\item [I2S\_VSYNC\_FILTER\_EN] Set this bit to enable I2S VSYNC filter function. (R/W)
\label{fielddesc:I2SVSYNCFILTERTHRES}\item [I2S\_VSYNC\_FILTER\_THRES] Configure the I2S VSYNC filter threshold value. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_INT\_RAW\_REG}{\hexprefix{}000C}\label{regdesc:I2SINTRAWREG}
\regfield{(reserved)}{14}{18}{00000000000000}%
\regfield{I2S\_V\_SYNC\_INT\_RAW}{1}{17}{{0}}%
\regfield{I2S\_OUT\_TOTAL\_EOF\_INT\_RAW}{1}{16}{{0}}%
\regfield{I2S\_IN\_DSCR\_EMPTY\_INT\_RAW}{1}{15}{{0}}%
\regfield{I2S\_OUT\_DSCR\_ERR\_INT\_RAW}{1}{14}{{0}}%
\regfield{I2S\_IN\_DSCR\_ERR\_INT\_RAW}{1}{13}{{0}}%
\regfield{I2S\_OUT\_EOF\_INT\_RAW}{1}{12}{{0}}%
\regfield{I2S\_OUT\_DONE\_INT\_RAW}{1}{11}{{0}}%
\regfield{(reserved)}{1}{10}{0}%
\regfield{I2S\_IN\_SUC\_EOF\_INT\_RAW}{1}{9}{{0}}%
\regfield{I2S\_IN\_DONE\_INT\_RAW}{1}{8}{{0}}%
\regfield{I2S\_TX\_HUNG\_INT\_RAW}{1}{7}{{0}}%
\regfield{I2S\_RX\_HUNG\_INT\_RAW}{1}{6}{{0}}%
\regfield{I2S\_TX\_REMPTY\_INT\_RAW}{1}{5}{{0}}%
\regfield{I2S\_TX\_WFULL\_INT\_RAW}{1}{4}{{0}}%
\regfield{I2S\_RX\_REMPTY\_INT\_RAW}{1}{3}{{0}}%
\regfield{I2S\_RX\_WFULL\_INT\_RAW}{1}{2}{{0}}%
\regfield{I2S\_TX\_PUT\_DATA\_INT\_RAW}{1}{1}{{0}}%
\regfield{I2S\_RX\_TAKE\_DATA\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SRXTAKEDATAINTRAW}\item [I2S\_RX\_TAKE\_DATA\_INT\_RAW] The raw interrupt status bit for \hyperref[int:I2SRXTAKEDATAINT]{I2S\_RX\_TAKE\_DATA\_INT} interrupt. (RO)
\label{fielddesc:I2STXPUTDATAINTRAW}\item [I2S\_TX\_PUT\_DATA\_INT\_RAW] The raw interrupt status bit for \hyperref[int:I2STXPUTDATAINT]{I2S\_TX\_PUT\_DATA\_INT} interrupt. (RO)
\label{fielddesc:I2SRXWFULLINTRAW}\item [I2S\_RX\_WFULL\_INT\_RAW] The raw interrupt status bit for \hyperref[int:I2SRXWFULLINT]{I2S\_RX\_WFULL\_INT} interrupt. (RO)
\label{fielddesc:I2SRXREMPTYINTRAW}\item [I2S\_RX\_REMPTY\_INT\_RAW] The raw interrupt status bit for \hyperref[int:I2SRXREMPTYINT]{I2S\_RX\_REMPTY\_INT} interrupt (RO)
\label{fielddesc:I2STXWFULLINTRAW}\item [I2S\_TX\_WFULL\_INT\_RAW] The raw interrupt status bit for \hyperref[int:I2STXWFULLINT]{I2S\_TX\_WFULL\_INT} interrupt. (RO)
\label{fielddesc:I2STXREMPTYINTRAW}\item [I2S\_TX\_REMPTY\_INT\_RAW] The raw interrupt status bit for \hyperref[int:I2STXREMPTYINT]{I2S\_TX\_REMPTY\_INT} interrupt. (RO)
\label{fielddesc:I2SRXHUNGINTRAW}\item [I2S\_RX\_HUNG\_INT\_RAW] The raw interrupt status bit for \hyperref[int:I2SRXHUNGINT]{I2S\_RX\_HUNG\_INT} interrupt. (RO)
\label{fielddesc:I2STXHUNGINTRAW}\item [I2S\_TX\_HUNG\_INT\_RAW] The raw interrupt status bit for \hyperref[int:I2STXHUNGINT]{I2S\_TX\_HUNG\_INT} interrupt. (RO)
\label{fielddesc:I2SINDONEINTRAW}\item [I2S\_IN\_DONE\_INT\_RAW] The raw interrupt status bit  for \hyperref[int:I2SINDONEINT]{I2S\_IN\_DONE\_INT} interrupt. (RO)
\label{fielddesc:I2SINSUCEOFINTRAW}\item [I2S\_IN\_SUC\_EOF\_INT\_RAW] The raw interrupt status bit for \hyperref[int:I2SINSUCEOFINT]{I2S\_IN\_SUC\_EOF\_INT} interrupt. (RO)
\label{fielddesc:I2SOUTDONEINTRAW}\item [I2S\_OUT\_DONE\_INT\_RAW] The raw interrupt status bit for \hyperref[int:I2SOUTDONEINT]{I2S\_OUT\_DONE\_INT} interrupt. (RO)
\label{fielddesc:I2SOUTEOFINTRAW}\item [I2S\_OUT\_EOF\_INT\_RAW] The raw interrupt status bit for \hyperref[int:I2SOUTEOFINT]{I2S\_OUT\_EOF\_INT} interrupt. (RO)
\label{fielddesc:I2SINDSCRERRINTRAW}\item [I2S\_IN\_DSCR\_ERR\_INT\_RAW] The raw interrupt status bit for \hyperref[int:I2SINDSCRERRINT]{I2S\_IN\_DSCR\_ERR\_INT} interrupt. (RO)
\label{fielddesc:I2SOUTDSCRERRINTRAW}\item [I2S\_OUT\_DSCR\_ERR\_INT\_RAW] The raw interrupt status bit for \hyperref[int:I2SOUTDSCRERRINT]{I2S\_OUT\_DSCR\_ERR\_INT} interrupt. (RO)
\label{fielddesc:I2SINDSCREMPTYINTRAW}\item [I2S\_IN\_DSCR\_EMPTY\_INT\_RAW] The raw interrupt status bit for \hyperref[int:I2SINDSCREMPTYINT]{I2S\_IN\_DSCR\_EMPTY\_INT} interrupt. (RO)
\label{fielddesc:I2SOUTTOTALEOFINTRAW}\item [I2S\_OUT\_TOTAL\_EOF\_INT\_RAW] The raw interrupt status bit for \hyperref[int:I2SOUTTOTALEOFINT]{I2S\_OUT\_TOTAL\_EOF\_INT} interrupt. (RO)
\label{fielddesc:I2SVSYNCINTRAW}\item [I2S\_V\_SYNC\_INT\_RAW] The raw interrupt status bit for \hyperref[int:I2SVSYNCINT]{I2S\_V\_SYNC\_INT} interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_INT\_ST\_REG}{\hexprefix{}0010}\label{regdesc:I2SINTSTREG}
\regfield{(reserved)}{14}{18}{00000000000000}%
\regfield{I2S\_V\_SYNC\_INT\_ST}{1}{17}{{0}}%
\regfield{I2S\_OUT\_TOTAL\_EOF\_INT\_ST}{1}{16}{{0}}%
\regfield{I2S\_IN\_DSCR\_EMPTY\_INT\_ST}{1}{15}{{0}}%
\regfield{I2S\_OUT\_DSCR\_ERR\_INT\_ST}{1}{14}{{0}}%
\regfield{I2S\_IN\_DSCR\_ERR\_INT\_ST}{1}{13}{{0}}%
\regfield{I2S\_OUT\_EOF\_INT\_ST}{1}{12}{{0}}%
\regfield{I2S\_OUT\_DONE\_INT\_ST}{1}{11}{{0}}%
\regfield{(reserved)}{1}{10}{0}%
\regfield{I2S\_IN\_SUC\_EOF\_INT\_ST}{1}{9}{{0}}%
\regfield{I2S\_IN\_DONE\_INT\_ST}{1}{8}{{0}}%
\regfield{I2S\_TX\_HUNG\_INT\_ST}{1}{7}{{0}}%
\regfield{I2S\_RX\_HUNG\_INT\_ST}{1}{6}{{0}}%
\regfield{I2S\_TX\_REMPTY\_INT\_ST}{1}{5}{{0}}%
\regfield{I2S\_TX\_WFULL\_INT\_ST}{1}{4}{{0}}%
\regfield{I2S\_RX\_REMPTY\_INT\_ST}{1}{3}{{0}}%
\regfield{I2S\_RX\_WFULL\_INT\_ST}{1}{2}{{0}}%
\regfield{I2S\_TX\_PUT\_DATA\_INT\_ST}{1}{1}{{0}}%
\regfield{I2S\_RX\_TAKE\_DATA\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SRXTAKEDATAINTST}\item [I2S\_RX\_TAKE\_DATA\_INT\_ST] The masked interrupt status bit for \hyperref[int:I2SRXTAKEDATAINT]{I2S\_RX\_TAKE\_DATA\_INT} interrupt. (RO)
\label{fielddesc:I2STXPUTDATAINTST}\item [I2S\_TX\_PUT\_DATA\_INT\_ST] The masked interrupt status bit for \hyperref[int:I2STXPUTDATAINT]{I2S\_TX\_PUT\_DATA\_INT} interrupt. (RO)
\label{fielddesc:I2SRXWFULLINTST}\item [I2S\_RX\_WFULL\_INT\_ST] The masked interrupt status bit for \hyperref[int:I2SRXWFULLINT]{I2S\_RX\_WFULL\_INT} interrupt (RO)
\label{fielddesc:I2SRXREMPTYINTST}\item [I2S\_RX\_REMPTY\_INT\_ST] The masked interrupt status bit for \hyperref[int:I2SRXREMPTYINT]{I2S\_RX\_REMPTY\_INT} interrupt. (RO)
\label{fielddesc:I2STXWFULLINTST}\item [I2S\_TX\_WFULL\_INT\_ST] The masked interrupt status bit for \hyperref[int:I2STXWFULLINT]{I2S\_TX\_WFULL\_INT} interrupt. (RO)
\label{fielddesc:I2STXREMPTYINTST}\item [I2S\_TX\_REMPTY\_INT\_ST] The masked interrupt status bit for \hyperref[int:I2STXREMPTYINT]{I2S\_TX\_REMPTY\_INT} interrupt. (RO)
\label{fielddesc:I2SRXHUNGINTST}\item [I2S\_RX\_HUNG\_INT\_ST] The masked interrupt status bit for \hyperref[int:I2SRXHUNGINT]{I2S\_RX\_HUNG\_INT} interrupt. (RO)
\label{fielddesc:I2STXHUNGINTST}\item [I2S\_TX\_HUNG\_INT\_ST] The masked interrupt status bit for \hyperref[int:I2STXHUNGINT]{I2S\_TX\_HUNG\_INT} interrupt. (RO)
\label{fielddesc:I2SINDONEINTST}\item [I2S\_IN\_DONE\_INT\_ST] The masked interrupt status bit for \hyperref[int:I2SINDONEINT]{I2S\_IN\_DONE\_INT} interrupt. (RO)
\label{fielddesc:I2SINSUCEOFINTST}\item [I2S\_IN\_SUC\_EOF\_INT\_ST] The masked interrupt status bit for \hyperref[int:I2SINSUCEOFINT]{I2S\_IN\_SUC\_EOF\_INT} interrupt. (RO)
\label{fielddesc:I2SOUTDONEINTST}\item [I2S\_OUT\_DONE\_INT\_ST] The masked interrupt status bit for \hyperref[int:I2SOUTDONEINT]{I2S\_OUT\_DONE\_INT} interrupt. (RO)
\label{fielddesc:I2SOUTEOFINTST}\item [I2S\_OUT\_EOF\_INT\_ST] The masked interrupt status bit for \hyperref[int:I2SOUTEOFINT]{I2S\_OUT\_EOF\_INT} interrupt. (RO)
\label{fielddesc:I2SINDSCRERRINTST}\item [I2S\_IN\_DSCR\_ERR\_INT\_ST] The masked interrupt status bit for \hyperref[int:I2SINDSCRERRINT]{I2S\_IN\_DSCR\_ERR\_INT} interrupt. (RO)
\label{fielddesc:I2SOUTDSCRERRINTST}\item [I2S\_OUT\_DSCR\_ERR\_INT\_ST] The masked interrupt status bit for \hyperref[int:I2SOUTDSCRERRINT]{I2S\_OUT\_DSCR\_ERR\_INT} interrupt. (RO)
\label{fielddesc:I2SINDSCREMPTYINTST}\item [I2S\_IN\_DSCR\_EMPTY\_INT\_ST] The masked interrupt status bit for \hyperref[int:I2SINDSCREMPTYINT]{I2S\_IN\_DSCR\_EMPTY\_INT} interrupt. (RO)
\label{fielddesc:I2SOUTTOTALEOFINTST}\item [I2S\_OUT\_TOTAL\_EOF\_INT\_ST] The masked interrupt status bit for \hyperref[int:I2SOUTTOTALEOFINT]{I2S\_OUT\_TOTAL\_EOF\_INT} interrupt. (RO)
\label{fielddesc:I2SVSYNCINTST}\item [I2S\_V\_SYNC\_INT\_ST] The masked interrupt status bit for \hyperref[int:I2SVSYNCINT]{I2S\_V\_SYNC\_INT} interrupt. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_INT\_ENA\_REG}{\hexprefix{}0014}\label{regdesc:I2SINTENAREG}
\regfield{(reserved)}{14}{18}{00000000000000}%
\regfield{I2S\_V\_SYNC\_INT\_ENA}{1}{17}{{0}}%
\regfield{I2S\_OUT\_TOTAL\_EOF\_INT\_ENA}{1}{16}{{0}}%
\regfield{I2S\_IN\_DSCR\_EMPTY\_INT\_ENA}{1}{15}{{0}}%
\regfield{I2S\_OUT\_DSCR\_ERR\_INT\_ENA}{1}{14}{{0}}%
\regfield{I2S\_IN\_DSCR\_ERR\_INT\_ENA}{1}{13}{{0}}%
\regfield{I2S\_OUT\_EOF\_INT\_ENA}{1}{12}{{0}}%
\regfield{I2S\_OUT\_DONE\_INT\_ENA}{1}{11}{{0}}%
\regfield{(reserved)}{1}{10}{0}%
\regfield{I2S\_IN\_SUC\_EOF\_INT\_ENA}{1}{9}{{0}}%
\regfield{I2S\_IN\_DONE\_INT\_ENA}{1}{8}{{0}}%
\regfield{I2S\_TX\_HUNG\_INT\_ENA}{1}{7}{{0}}%
\regfield{I2S\_RX\_HUNG\_INT\_ENA}{1}{6}{{0}}%
\regfield{I2S\_TX\_REMPTY\_INT\_ENA}{1}{5}{{0}}%
\regfield{I2S\_TX\_WFULL\_INT\_ENA}{1}{4}{{0}}%
\regfield{I2S\_RX\_REMPTY\_INT\_ENA}{1}{3}{{0}}%
\regfield{I2S\_RX\_WFULL\_INT\_ENA}{1}{2}{{0}}%
\regfield{I2S\_TX\_PUT\_DATA\_INT\_ENA}{1}{1}{{0}}%
\regfield{I2S\_RX\_TAKE\_DATA\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SRXTAKEDATAINTENA}\item [I2S\_RX\_TAKE\_DATA\_INT\_ENA] The interrupt enable bit for \hyperref[int:I2SRXTAKEDATAINT]{I2S\_RX\_TAKE\_DATA\_INT} interrupt. (R/W)
\label{fielddesc:I2STXPUTDATAINTENA}\item [I2S\_TX\_PUT\_DATA\_INT\_ENA] The interrupt enable bit for \hyperref[int:I2STXPUTDATAINT]{I2S\_TX\_PUT\_DATA\_INT} interrupt. (R/W)
\label{fielddesc:I2SRXWFULLINTENA}\item [I2S\_RX\_WFULL\_INT\_ENA] The interrupt enable bit for the \hyperref[int:I2SRXWFULLINT]{I2S\_RX\_WFULL\_INT} interrupt. (R/W)
\label{fielddesc:I2SRXREMPTYINTENA}\item [I2S\_RX\_REMPTY\_INT\_ENA] The interrupt enable bit for \hyperref[int:I2SRXREMPTYINT]{I2S\_RX\_REMPTY\_INT} interrupt. (R/W)
\label{fielddesc:I2STXWFULLINTENA}\item [I2S\_TX\_WFULL\_INT\_ENA] The interrupt enable bit for \hyperref[int:I2STXWFULLINT]{I2S\_TX\_WFULL\_INT} interrupt. (R/W)
\label{fielddesc:I2STXREMPTYINTENA}\item [I2S\_TX\_REMPTY\_INT\_ENA] The interrupt enable bit for \hyperref[int:I2STXREMPTYINT]{I2S\_TX\_REMPTY\_INT} interrupt. (R/W)
\label{fielddesc:I2SRXHUNGINTENA}\item [I2S\_RX\_HUNG\_INT\_ENA] The interrupt enable bit for the \hyperref[int:I2SRXHUNGINT]{I2S\_RX\_HUNG\_INT} interrupt. (R/W)
\label{fielddesc:I2STXHUNGINTENA}\item [I2S\_TX\_HUNG\_INT\_ENA] The interrupt enable bit for \hyperref[int:I2STXHUNGINT]{I2S\_TX\_HUNG\_INT} interrupt. (R/W)
\label{fielddesc:I2SINDONEINTENA}\item [I2S\_IN\_DONE\_INT\_ENA] The interrupt enable bit for \hyperref[int:I2SINDONEINT]{I2S\_IN\_DONE\_INT} interrupt. (R/W)
\label{fielddesc:I2SINSUCEOFINTENA}\item [I2S\_IN\_SUC\_EOF\_INT\_ENA] The interrupt enable bit for \hyperref[int:I2SINSUCEOFINT]{I2S\_IN\_SUC\_EOF\_INT} interrupt. (R/W)
\label{fielddesc:I2SOUTDONEINTENA}\item [I2S\_OUT\_DONE\_INT\_ENA] The interrupt enable bit for \hyperref[int:I2SOUTDONEINT]{I2S\_OUT\_DONE\_INT} interrupt. (R/W)
\label{fielddesc:I2SOUTEOFINTENA}\item [I2S\_OUT\_EOF\_INT\_ENA] The interrupt enable bit for \hyperref[int:I2SOUTEOFINT]{I2S\_OUT\_EOF\_INT} interrupt. (R/W)
\label{fielddesc:I2SINDSCRERRINTENA}\item [I2S\_IN\_DSCR\_ERR\_INT\_ENA] The interrupt enable bit for \hyperref[int:I2SINDSCRERRINT]{I2S\_IN\_DSCR\_ERR\_INT} interrupt. (R/W)
\label{fielddesc:I2SOUTDSCRERRINTENA}\item [I2S\_OUT\_DSCR\_ERR\_INT\_ENA] The interrupt enable bit for \hyperref[int:I2SOUTDSCRERRINT]{I2S\_OUT\_DSCR\_ERR\_INT} interrupt. (R/W)
\label{fielddesc:I2SINDSCREMPTYINTENA}\item [I2S\_IN\_DSCR\_EMPTY\_INT\_ENA] The interrupt enable bit for \hyperref[int:I2SINDSCREMPTYINT]{I2S\_IN\_DSCR\_EMPTY\_INT} interrupt. (R/W)
\label{fielddesc:I2SOUTTOTALEOFINTENA}\item [I2S\_OUT\_TOTAL\_EOF\_INT\_ENA] The interrupt enable bit for \hyperref[int:I2SOUTTOTALEOFINT]{I2S\_OUT\_TOTAL\_EOF\_INT} interrupt. (R/W)
\label{fielddesc:I2SVSYNCINTENA}\item [I2S\_V\_SYNC\_INT\_ENA] The interrupt enable bit for \hyperref[int:I2SVSYNCINT]{I2S\_V\_SYNC\_INT} interrupt. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_INT\_CLR\_REG}{\hexprefix{}0018}\label{regdesc:I2SINTCLRREG}
\regfield{(reserved)}{14}{18}{00000000000000}%
\regfield{I2S\_V\_SYNC\_INT\_CLR}{1}{17}{{0}}%
\regfield{I2S\_OUT\_TOTAL\_EOF\_INT\_CLR}{1}{16}{{0}}%
\regfield{I2S\_IN\_DSCR\_EMPTY\_INT\_CLR}{1}{15}{{0}}%
\regfield{I2S\_OUT\_DSCR\_ERR\_INT\_CLR}{1}{14}{{0}}%
\regfield{I2S\_IN\_DSCR\_ERR\_INT\_CLR}{1}{13}{{0}}%
\regfield{I2S\_OUT\_EOF\_INT\_CLR}{1}{12}{{0}}%
\regfield{I2S\_OUT\_DONE\_INT\_CLR}{1}{11}{{0}}%
\regfield{(reserved)}{1}{10}{0}%
\regfield{I2S\_IN\_SUC\_EOF\_INT\_CLR}{1}{9}{{0}}%
\regfield{I2S\_IN\_DONE\_INT\_CLR}{1}{8}{{0}}%
\regfield{I2S\_TX\_HUNG\_INT\_CLR}{1}{7}{{0}}%
\regfield{I2S\_RX\_HUNG\_INT\_CLR}{1}{6}{{0}}%
\regfield{I2S\_TX\_REMPTY\_INT\_CLR}{1}{5}{{0}}%
\regfield{I2S\_TX\_WFULL\_INT\_CLR}{1}{4}{{0}}%
\regfield{I2S\_RX\_REMPTY\_INT\_CLR}{1}{3}{{0}}%
\regfield{I2S\_RX\_WFULL\_INT\_CLR}{1}{2}{{0}}%
\regfield{I2S\_PUT\_DATA\_INT\_CLR}{1}{1}{{0}}%
\regfield{I2S\_TAKE\_DATA\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2STAKEDATAINTCLR}\item [I2S\_TAKE\_DATA\_INT\_CLR] Set this bit to clear \hyperref[int:I2SRXTAKEDATAINT]{I2S\_RX\_TAKE\_DATA\_INT} interrupt. (WO)
\label{fielddesc:I2SPUTDATAINTCLR}\item [I2S\_PUT\_DATA\_INT\_CLR] Set this bit to clear \hyperref[int:I2STXPUTDATAINT]{I2S\_TX\_PUT\_DATA\_INT} interrupt. (WO)
\label{fielddesc:I2SRXWFULLINTCLR}\item [I2S\_RX\_WFULL\_INT\_CLR] Set this bit to clear \hyperref[int:I2SRXWFULLINT]{I2S\_RX\_WFULL\_INT} interrupt. (WO)
\label{fielddesc:I2SRXREMPTYINTCLR}\item [I2S\_RX\_REMPTY\_INT\_CLR] Set this bit to clear \hyperref[int:I2SRXREMPTYINT]{I2S\_RX\_REMPTY\_INT} interrupt. (WO)
\label{fielddesc:I2STXWFULLINTCLR}\item [I2S\_TX\_WFULL\_INT\_CLR] Set this bit to clear \hyperref[int:I2STXWFULLINT]{I2S\_TX\_WFULL\_INT} interrupt. (WO)
\label{fielddesc:I2STXREMPTYINTCLR}\item [I2S\_TX\_REMPTY\_INT\_CLR] Set this bit to clear \hyperref[int:I2STXREMPTYINT]{I2S\_TX\_REMPTY\_INT} interrupt. (WO)
\label{fielddesc:I2SRXHUNGINTCLR}\item [I2S\_RX\_HUNG\_INT\_CLR] Set this bit to clear \hyperref[int:I2SRXHUNGINT]{I2S\_RX\_HUNG\_INT} interrupt. (WO)
\label{fielddesc:I2STXHUNGINTCLR}\item [I2S\_TX\_HUNG\_INT\_CLR] Set this bit to clear \hyperref[int:I2STXHUNGINT]{I2S\_TX\_HUNG\_INT} interrupt. (WO)
\label{fielddesc:I2SINDONEINTCLR}\item [I2S\_IN\_DONE\_INT\_CLR] Set this bit to clear \hyperref[int:I2SINDONEINT]{I2S\_IN\_DONE\_INT} interrupt. (WO)
\label{fielddesc:I2SINSUCEOFINTCLR}\item [I2S\_IN\_SUC\_EOF\_INT\_CLR] Set this bit to clear \hyperref[int:I2SINSUCEOFINT]{I2S\_IN\_SUC\_EOF\_INT} interrupt. (WO)
\label{fielddesc:I2SOUTDONEINTCLR}\item [I2S\_OUT\_DONE\_INT\_CLR] Set this bit to clear \hyperref[int:I2SOUTDONEINT]{I2S\_OUT\_DONE\_INT} interrupt. (WO)
\label{fielddesc:I2SOUTEOFINTCLR}\item [I2S\_OUT\_EOF\_INT\_CLR] Set this bit to clear \hyperref[int:I2SOUTEOFINT]{I2S\_OUT\_EOF\_INT} interrupt. (WO)
\label{fielddesc:I2SINDSCRERRINTCLR}\item [I2S\_IN\_DSCR\_ERR\_INT\_CLR] Set this bit to clear \hyperref[int:I2SINDSCRERRINT]{I2S\_IN\_DSCR\_ERR\_INT} interrupt. (WO)
\label{fielddesc:I2SOUTDSCRERRINTCLR}\item [I2S\_OUT\_DSCR\_ERR\_INT\_CLR] Set this bit to clear \hyperref[int:I2SOUTDSCRERRINT]{I2S\_OUT\_DSCR\_ERR\_INT} interrupt. (WO)
\label{fielddesc:I2SINDSCREMPTYINTCLR}\item [I2S\_IN\_DSCR\_EMPTY\_INT\_CLR] Set this bit to clear \hyperref[int:I2SINDSCREMPTYINT]{I2S\_IN\_DSCR\_EMPTY\_INT} interrupt. (WO)
\label{fielddesc:I2SOUTTOTALEOFINTCLR}\item [I2S\_OUT\_TOTAL\_EOF\_INT\_CLR] Set this bit to clear \hyperref[int:I2SOUTTOTALEOFINT]{I2S\_OUT\_TOTAL\_EOF\_INT} interrupt. (WO)
\label{fielddesc:I2SVSYNCINTCLR}\item [I2S\_V\_SYNC\_INT\_CLR] Set this bit to clear \hyperref[int:I2SVSYNCINT]{I2S\_V\_SYNC\_INT} interrupt. (WO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_TIMING\_REG}{\hexprefix{}001C}\label{regdesc:I2STIMINGREG}
\regfield{(reserved)}{7}{25}{0000000}%
\regfield{I2S\_TX\_BCK\_IN\_INV}{1}{24}{{0}}%
\regfield{I2S\_DATA\_ENABLE\_DELAY}{2}{22}{{0}}%
\regfield{I2S\_RX\_DSYNC\_SW}{1}{21}{{0}}%
\regfield{I2S\_TX\_DSYNC\_SW}{1}{20}{{0}}%
\regfield{I2S\_RX\_BCK\_OUT\_DELAY}{2}{18}{{0}}%
\regfield{I2S\_RX\_WS\_OUT\_DELAY}{2}{16}{{0}}%
\regfield{I2S\_TX\_SD\_OUT\_DELAY}{2}{14}{{0}}%
\regfield{I2S\_TX\_WS\_OUT\_DELAY}{2}{12}{{0}}%
\regfield{I2S\_TX\_BCK\_OUT\_DELAY}{2}{10}{{0}}%
\regfield{I2S\_RX\_SD\_IN\_DELAY}{2}{8}{{0}}%
\regfield{I2S\_RX\_WS\_IN\_DELAY}{2}{6}{{0}}%
\regfield{I2S\_RX\_BCK\_IN\_DELAY}{2}{4}{{0}}%
\regfield{I2S\_TX\_WS\_IN\_DELAY}{2}{2}{{0}}%
\regfield{I2S\_TX\_BCK\_IN\_DELAY}{2}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2STXBCKINDELAY}\item [I2S\_TX\_BCK\_IN\_DELAY] Number of delay cycles for BCK signal into the transmitter based on I2S0\_CLK. (R/W)
\begin{itemize}
    \item 0: delayed by 1.5 cycles
    \item 1: delayed by 2.5 cycles
    \item 2: delayed by 3.5 cycles
    \item 3: delayed by 4.5 cycles
\end{itemize}
\label{fielddesc:I2STXWSINDELAY}\item [I2S\_TX\_WS\_IN\_DELAY] Number of delay cycles for WS signal into the transmitter based on I2S0\_CLK. (R/W)
\begin{itemize}
    \item 0: delayed by 1.5 cycles
    \item 1: delayed by 2.5 cycles
    \item 2: delayed by 3.5 cycles
    \item 3: delayed by 4.5 cycles
\end{itemize}
\label{fielddesc:I2SRXBCKINDELAY}\item [I2S\_RX\_BCK\_IN\_DELAY] Number of delay cycles for BCK signal into the receiver based on I2S0\_CLK. (R/W)
\begin{itemize}
    \item 0: delayed by 1.5 cycles
    \item 1: delayed by 2.5 cycles
    \item 2: delayed by 3.5 cycles
    \item 3: delayed by 4.5 cycles
\end{itemize}
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{I2S\_TIMING\_REG}{\hexprefix{}001C}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\label{fielddesc:I2SRXWSINDELAY}\item [I2S\_RX\_WS\_IN\_DELAY] Number of delay cycles for WS signal into the receiver based on I2S0\_CLK. (R/W)
\begin{itemize}
    \item 0: delayed by 1.5 cycles
    \item 1: delayed by 2.5 cycles
    \item 2: delayed by 3.5 cycles
    \item 3: delayed by 4.5 cycles
\end{itemize}
\label{fielddesc:I2SRXSDINDELAY}\item [I2S\_RX\_SD\_IN\_DELAY] Number of delay cycles for SD signal into the receiver based on I2S0\_CLK. (R/W)
\begin{itemize}
    \item 0: delayed by 1.5 cycles
    \item 1: delayed by 2.5 cycles
    \item 2: delayed by 3.5 cycles
    \item 3: delayed by 4.5 cycles
\end{itemize}
\label{fielddesc:I2STXBCKOUTDELAY}\item [I2S\_TX\_BCK\_OUT\_DELAY] Number of delay cycles for BCK signal out of the transmitter based on I2S0\_CLK. (R/W)
 \begin{itemize}
     \item 0: delayed by 0 cycles
     \item 1: delayed by 1 cycles
     \item 2: delayed by 2 cycles
     \item 3: delayed by 3 cycles
 \end{itemize}
\label{fielddesc:I2STXWSOUTDELAY}\item [I2S\_TX\_WS\_OUT\_DELAY] Number of delay cycles for WS signal out of the transmitter based on I2S0\_CLK. (R/W)
\begin{itemize}
    \item 0: delayed by 0 cycles
    \item 1: delayed by 1 cycles
    \item 2: delayed by 2 cycles
    \item 3: delayed by 3 cycles
\end{itemize}
\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{I2S\_TIMING\_REG}{\hexprefix{}001C}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]
\label{fielddesc:I2STXSDOUTDELAY}\item [I2S\_TX\_SD\_OUT\_DELAY] Number of delay cycles for SD signal out of the transmitter based on I2S0\_CLK. (R/W)
\begin{itemize}
    \item 0: delayed by 0 cycles
    \item 1: delayed by 1 cycles
    \item 2: delayed by 2 cycles
    \item 3: delayed by 3 cycles
\end{itemize}
\label{fielddesc:I2SRXWSOUTDELAY}\item [I2S\_RX\_WS\_OUT\_DELAY] Number of delay cycles for WS signal out of the receiver based on I2S0\_CLK. (R/W)
\begin{itemize}
    \item 0: delayed by 0 cycles
    \item 1: delayed by 1 cycles
    \item 2: delayed by 2 cycles
    \item 3: delayed by 3 cycles
\end{itemize}
\label{fielddesc:I2SRXBCKOUTDELAY}\item [I2S\_RX\_BCK\_OUT\_DELAY] Number of delay cycles for BCK signal out of the receiver based on I2S0\_CLK. (R/W)
\begin{itemize}
    \item 0: delayed by 0 cycles
    \item 1: delayed by 1 cycles
    \item 2: delayed by 2 cycles
    \item 3: delayed by 3 cycles
\end{itemize}
\label{fielddesc:I2STXDSYNCSW}\item [I2S\_TX\_DSYNC\_SW] Set this bit to synchronize signals into the transmitter by two flip-flop synchronizer. (R/W)
\begin{itemize}
    \item 0: the signals will be firstly clocked by rising clock edge , then clocked by falling clock edge.
    \item 1: the signals will be firstly clocked by falling clock edge, then clocked by rising clock edge.
\end{itemize}

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{I2S\_TIMING\_REG}{\hexprefix{}001C}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:I2SRXDSYNCSW}\item [I2S\_RX\_DSYNC\_SW] Set this bit to synchronize signals into the receiver by two flip-flop synchronizer. (R/W)
\begin{itemize}
    \item 0: the signals will be clocked by rising clock edge firstly, then clocked by falling clock edge.
    \item 1: the signals will be clocked by falling clock edge firstly, then clocked by rising clock edge.
\end{itemize}
\label{fielddesc:I2SDATAENABLEDELAY}\item [I2S\_DATA\_ENABLE\_DELAY] Number of delay cycles for data valid flag based on I2S0\_CLK. (R/W)
\begin{itemize}
    \item 0: delayed by 1.5 cycles
    \item 1: delayed by 2.5 cycles
    \item 2: delayed by 3.5 cycles
    \item 3: delayed by 4.5 cycles
\end{itemize}
\label{fielddesc:I2STXBCKININV}\item [I2S\_TX\_BCK\_IN\_INV] Set this bit to invert BCK signal input to the slave transmitter. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_RXEOF\_NUM\_REG}{\hexprefix{}0024}\label{regdesc:I2SRXEOFNUMREG}
\regfield{I2S\_RX\_EOF\_NUM}{32}{0}{{64}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SRXEOFNUM}\item [I2S\_RX\_EOF\_NUM] The length of data to be received. It will trigger I2S\_IN\_SUC\_EOF\_INT. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_OUT\_LINK\_REG}{\hexprefix{}0030}\label{regdesc:I2SOUTLINKREG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{I2S\_OUTLINK\_RESTART}{1}{30}{{0}}%
\regfield{I2S\_OUTLINK\_START}{1}{29}{{0}}%
\regfield{I2S\_OUTLINK\_STOP}{1}{28}{{0}}%
\regfield{(reserved)}{8}{20}{00000000}%
\regfield{I2S\_OUTLINK\_ADDR}{20}{0}{{\hexprefix{}000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SOUTLINKADDR}\item [I2S\_OUTLINK\_ADDR] The address of first outlink descriptor (R/W)
\label{fielddesc:I2SOUTLINKSTOP}\item [I2S\_OUTLINK\_STOP] Set this bit to stop outlink descriptor. (R/W)
\label{fielddesc:I2SOUTLINKSTART}\item [I2S\_OUTLINK\_START] Set this bit to start outlink descriptor. (R/W)
\label{fielddesc:I2SOUTLINKRESTART}\item [I2S\_OUTLINK\_RESTART] Set this bit to restart outlink descriptor. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_IN\_LINK\_REG}{\hexprefix{}0034}\label{regdesc:I2SINLINKREG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{I2S\_INLINK\_RESTART}{1}{30}{{0}}%
\regfield{I2S\_INLINK\_START}{1}{29}{{0}}%
\regfield{I2S\_INLINK\_STOP}{1}{28}{{0}}%
\regfield{(reserved)}{8}{20}{00000000}%
\regfield{I2S\_INLINK\_ADDR}{20}{0}{{\hexprefix{}000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SINLINKADDR}\item [I2S\_INLINK\_ADDR] The address of first inlink descriptor (R/W)
\label{fielddesc:I2SINLINKSTOP}\item [I2S\_INLINK\_STOP] Set this bit to stop inlink descriptor. (R/W)
\label{fielddesc:I2SINLINKSTART}\item [I2S\_INLINK\_START] Set this bit to start inlink descriptor. (R/W)
\label{fielddesc:I2SINLINKRESTART}\item [I2S\_INLINK\_RESTART] Set this bit to restart inlink descriptor. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_OUT\_EOF\_DES\_ADDR\_REG}{\hexprefix{}0038}\label{regdesc:I2SOUTEOFDESADDRREG}
\regfield{I2S\_OUT\_EOF\_DES\_ADDR}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SOUTEOFDESADDR}\item [I2S\_OUT\_EOF\_DES\_ADDR] The address of outlink descriptor that produces EOF (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_IN\_EOF\_DES\_ADDR\_REG}{\hexprefix{}003C}\label{regdesc:I2SINEOFDESADDRREG}
\regfield{I2S\_IN\_SUC\_EOF\_DES\_ADDR}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SINSUCEOFDESADDR}\item [I2S\_IN\_SUC\_EOF\_DES\_ADDR] The address of inlink descriptor that produces EOF (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_OUT\_EOF\_BFR\_DES\_ADDR\_REG}{\hexprefix{}0040}\label{regdesc:I2SOUTEOFBFRDESADDRREG}
\regfield{I2S\_OUT\_EOF\_BFR\_DES\_ADDR}{32}{0}{{\hexprefix{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SOUTEOFBFRDESADDR}\item [I2S\_OUT\_EOF\_BFR\_DES\_ADDR] The address of buffer relative to the outlink descriptor that produces EOF (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_INLINK\_DSCR\_REG}{\hexprefix{}0048}\label{regdesc:I2SINLINKDSCRREG}
\regfield{I2S\_INLINK\_DSCR}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SINLINKDSCR}\item [I2S\_INLINK\_DSCR] The address of current inlink descriptor (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_INLINK\_DSCR\_BF0\_REG}{\hexprefix{}004C}\label{regdesc:I2SINLINKDSCRBF0REG}
\regfield{I2S\_INLINK\_DSCR\_BF0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SINLINKDSCRBF0}\item [I2S\_INLINK\_DSCR\_BF0] The address of next inlink descriptor (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_INLINK\_DSCR\_BF1\_REG}{\hexprefix{}0050}\label{regdesc:I2SINLINKDSCRBF1REG}
\regfield{I2S\_INLINK\_DSCR\_BF1}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SINLINKDSCRBF1}\item [I2S\_INLINK\_DSCR\_BF1] The address of next inlink data buffer (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_OUTLINK\_DSCR\_REG}{\hexprefix{}0054}\label{regdesc:I2SOUTLINKDSCRREG}
\regfield{I2S\_OUTLINK\_DSCR}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SOUTLINKDSCR}\item [I2S\_OUTLINK\_DSCR] The address of current outlink descriptor (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_OUTLINK\_DSCR\_BF0\_REG}{\hexprefix{}0058}\label{regdesc:I2SOUTLINKDSCRBF0REG}
\regfield{I2S\_OUTLINK\_DSCR\_BF0}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SOUTLINKDSCRBF0}\item [I2S\_OUTLINK\_DSCR\_BF0] The address of next outlink descriptor (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_OUTLINK\_DSCR\_BF1\_REG}{\hexprefix{}005C}\label{regdesc:I2SOUTLINKDSCRBF1REG}
\regfield{I2S\_OUTLINK\_DSCR\_BF1}{32}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SOUTLINKDSCRBF1}\item [I2S\_OUTLINK\_DSCR\_BF1] The address of next outlink data buffer (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_LC\_CONF\_REG}{\hexprefix{}0060}\label{regdesc:I2SLCCONFREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{I2S\_EXT\_MEM\_BK\_SIZE}{2}{14}{{0}}%
\regfield{I2S\_MEM\_TRANS\_EN}{1}{13}{{0}}%
\regfield{I2S\_CHECK\_OWNER}{1}{12}{{0}}%
\regfield{I2S\_OUT\_DATA\_BURST\_EN}{1}{11}{{0}}%
\regfield{I2S\_INDSCR\_BURST\_EN}{1}{10}{{0}}%
\regfield{I2S\_OUTDSCR\_BURST\_EN}{1}{9}{{0}}%
\regfield{I2S\_OUT\_EOF\_MODE}{1}{8}{{1}}%
\regfield{(reserved)}{1}{7}{0}%
\regfield{I2S\_OUT\_AUTO\_WRBACK}{1}{6}{{0}}%
\regfield{I2S\_IN\_LOOP\_TEST}{1}{5}{{0}}%
\regfield{I2S\_OUT\_LOOP\_TEST}{1}{4}{{0}}%
\regfield{I2S\_AHBM\_RST}{1}{3}{{0}}%
\regfield{I2S\_AHBM\_FIFO\_RST}{1}{2}{{0}}%
\regfield{I2S\_OUT\_RST}{1}{1}{{0}}%
\regfield{I2S\_IN\_RST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SINRST}\item [I2S\_IN\_RST] Set this bit to reset in-DMA FSM. Set this bit before the DMA configuration. (R/W)
\label{fielddesc:I2SOUTRST}\item [I2S\_OUT\_RST] Set this bit to reset out-DMA FSM. Set this bit before the DMA configuration. (R/W)
\label{fielddesc:I2SAHBMFIFORST}\item [I2S\_AHBM\_FIFO\_RST] Set this bit to reset AHB interface cmdFIFO of DMA. Set this bit before the DMA configuration. (R/W)
\label{fielddesc:I2SAHBMRST}\item [I2S\_AHBM\_RST] Set this bit to reset AHB interface of DMA. Set this bit before the DMA configuration. (R/W)
\label{fielddesc:I2SOUTLOOPTEST}\item [I2S\_OUT\_LOOP\_TEST] Set this bit to loop test inlink. (R/W)
\label{fielddesc:I2SINLOOPTEST}\item [I2S\_IN\_LOOP\_TEST] Set this bit to loop test outlink. (R/W)
\label{fielddesc:I2SOUTAUTOWRBACK}\item [I2S\_OUT\_AUTO\_WRBACK] Set this bit to enable outlink-written-back automatically when out buffer is transmitted done. (R/W)
\label{fielddesc:I2SOUTEOFMODE}\item [I2S\_OUT\_EOF\_MODE] DMA out EOF flag generation mode. 1: When DMA has popped all data from the FIFO. 0: When AHB has pushed all data to the FIFO. (R/W)
\label{fielddesc:I2SOUTDSCRBURSTEN}\item [I2S\_OUTDSCR\_BURST\_EN] DMA outlink descriptor transfer mode configuration bit. 1: Prepare outlink descriptor with burst mode. 0: Prepare outlink descriptor with byte mode. (R/W)
\label{fielddesc:I2SINDSCRBURSTEN}\item [I2S\_INDSCR\_BURST\_EN] DMA inlink descriptor transfer mode configuration bit. 1: Prepare inlink descriptor with burst mode. 0: Prepare inlink descriptor with byte mode. (R/W)
\label{fielddesc:I2SOUTDATABURSTEN}\item [I2S\_OUT\_DATA\_BURST\_EN] Transmitter data transfer mode configuration bit. 1: Prepare out data with burst mode. 0: Prepare out data with byte mode. (R/W)
\label{fielddesc:I2SCHECKOWNER}\item [I2S\_CHECK\_OWNER] Set this bit to enable check owner bit by hardware. (R/W)
\label{fielddesc:I2SMEMTRANSEN}\item [I2S\_MEM\_TRANS\_EN] Reserved. (R/W)
\label{fielddesc:I2SEXTMEMBKSIZE}\item [I2S\_EXT\_MEM\_BK\_SIZE] DMA access external memory block size. 0: 16 bytes. 1: 32 bytes. 2: 64 bytes. 3: reserved. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_LC\_STATE0\_REG}{\hexprefix{}006C}\label{regdesc:I2SLCSTATE0REG}
\regfield{I2S\_OUT\_EMPTY}{1}{31}{{0}}%
\regfield{I2S\_OUT\_FULL}{1}{30}{{0}}%
\regfield{I2S\_OUTFIFO\_CNT}{7}{23}{{0}}%
\regfield{I2S\_OUT\_STATE}{3}{20}{{0}}%
\regfield{I2S\_OUT\_DSCR\_STATE}{2}{18}{{0}}%
\regfield{I2S\_OUTLINK\_DSCR\_ADDR}{18}{0}{{\hexprefix{}000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SOUTLINKDSCRADDR}\item [I2S\_OUTLINK\_DSCR\_ADDR] I2S DMA out descriptor address. (RO)
\label{fielddesc:I2SOUTDSCRSTATE}\item [I2S\_OUT\_DSCR\_STATE] I2S DMA out descriptor state. (RO)
\label{fielddesc:I2SOUTSTATE}\item [I2S\_OUT\_STATE] I2S DMA out data state. (RO)
\label{fielddesc:I2SOUTFIFOCNT}\item [I2S\_OUTFIFO\_CNT] The remains of I2S DMA outfifo data. (RO)
\label{fielddesc:I2SOUTFULL}\item [I2S\_OUT\_FULL] I2S DMA outfifo is full. (RO)
\label{fielddesc:I2SOUTEMPTY}\item [I2S\_OUT\_EMPTY] I2S DMA outfifo is empty. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_LC\_STATE1\_REG}{\hexprefix{}0070}\label{regdesc:I2SLCSTATE1REG}
\regfield{I2S\_IN\_EMPTY}{1}{31}{{0}}%
\regfield{I2S\_IN\_FULL}{1}{30}{{0}}%
\regfield{I2S\_INFIFO\_CNT\_DEBUG}{7}{23}{{0}}%
\regfield{I2S\_IN\_STATE}{3}{20}{{0}}%
\regfield{I2S\_IN\_DSCR\_STATE}{2}{18}{{0}}%
\regfield{I2S\_INLINK\_DSCR\_ADDR}{18}{0}{{\hexprefix{}000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SINLINKDSCRADDR}\item [I2S\_INLINK\_DSCR\_ADDR] I2S DMA in descriptor address. (RO)
\label{fielddesc:I2SINDSCRSTATE}\item [I2S\_IN\_DSCR\_STATE] I2S DMA in descriptor state. (RO)
\label{fielddesc:I2SINSTATE}\item [I2S\_IN\_STATE] I2S DMA in data state. (RO)
\label{fielddesc:I2SINFIFOCNTDEBUG}\item [I2S\_INFIFO\_CNT\_DEBUG] The remains of I2S DMA infifo data. (RO)
\label{fielddesc:I2SINFULL}\item [I2S\_IN\_FULL] I2S DMA infifo is full. (RO)
\label{fielddesc:I2SINEMPTY}\item [I2S\_IN\_EMPTY] I2S DMA infifo is empty. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_STATE\_REG}{\hexprefix{}00BC}\label{regdesc:I2SSTATEREG}
\regfield{(reserved)}{31}{1}{0000000000000000000000000000000}%
\regfield{I2S\_TX\_IDLE}{1}{0}{{1}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2STXIDLE}\item [I2S\_TX\_IDLE] 1: I2S TX is in idle state. 0: I2S TX is at work. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_CLKM\_CONF\_REG}{\hexprefix{}00AC}\label{regdesc:I2SCLKMCONFREG}
\regfield{(reserved)}{9}{23}{000000000}%
\regfield{I2S\_CLK\_SEL}{2}{21}{{0}}%
\regfield{I2S\_CLK\_EN}{1}{20}{{0}}%
\regfield{I2S\_CLKM\_DIV\_A}{6}{14}{{\hexprefix{}0}}%
\regfield{I2S\_CLKM\_DIV\_B}{6}{8}{{\hexprefix{}0}}%
\regfield{I2S\_CLKM\_DIV\_NUM}{8}{0}{{4}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SCLKMDIVNUM}\item [I2S\_CLKM\_DIV\_NUM] Integral I2S clock divider value (R/W)
\label{fielddesc:I2SCLKMDIVB}\item [I2S\_CLKM\_DIV\_B] Fractional clock divider numerator value (R/W)
\label{fielddesc:I2SCLKMDIVA}\item [I2S\_CLKM\_DIV\_A] Fractional clock divider denominator value (R/W)
\label{fielddesc:I2SCLKEN}\item [I2S\_CLK\_EN] Set this bit to enable clock gate (R/W)
\label{fielddesc:I2SCLKSEL}\item [I2S\_CLK\_SEL] Set this bit to select I2S module clock source. 0: No clock. 1: APLL\_CLK. 2: PLL\_160M\_CLK. 3: No clock. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{I2S\_SAMPLE\_RATE\_CONF\_REG}{\hexprefix{}00B0}\label{regdesc:I2SSAMPLERATECONFREG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{I2S\_RX\_BITS\_MOD}{6}{18}{{16}}%
\regfield{I2S\_TX\_BITS\_MOD}{6}{12}{{16}}%
\regfield{I2S\_RX\_BCK\_DIV\_NUM}{6}{6}{{6}}%
\regfield{I2S\_TX\_BCK\_DIV\_NUM}{6}{0}{{6}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2STXBCKDIVNUM}\item [I2S\_TX\_BCK\_DIV\_NUM] Bit clock configuration bits in transmitter mode. (R/W)
\label{fielddesc:I2SRXBCKDIVNUM}\item [I2S\_RX\_BCK\_DIV\_NUM] Bit clock configuration bits in receiver mode. (R/W)
\label{fielddesc:I2STXBITSMOD}\item [I2S\_TX\_BITS\_MOD] Set the bits to configure bit length of I2S transmitter channel, the value of which can only be 8, 16, 24 and 32.   (R/W)
\label{fielddesc:I2SRXBITSMOD}\item [I2S\_RX\_BITS\_MOD] Set the bits to configure bit length of I2S receiver channel,  the value of which can only be 8, 16, 24 and 32. (R/W)
\end{reglist}\end{regdesc}
\end{register}

\begin{register}{H}{I2S\_DATE\_REG}{\hexprefix{}00FC}\label{regdesc:I2SDATEREG}
\regfield{I2S\_DATE}{32}{0}{{\hexprefix{}19052500}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:I2SDATE}\item [I2S\_DATE] Version control register (R/W)
\end{reglist}\end{regdesc}
\end{register}
