\documentclass[openany, 10pt]{book}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Find  10-readme-for-trm-repo.tex at:        %%%
%%% https://www.overleaf.com/read/bwdjvfjksvjy/ %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% >>> R?: marks a repo project setting number or important notice
\usepackage{chip-spec-settings}

\usepackage{preamble-trm-repo}

% >>> R2: In file below, comment out the modules already included into
% this project to avoid warnings for multiple label definitions <<<
\myexternaldocument{temp-labels-en}

\raggedright
\raggedbottom

% Keep commented out!
% >>> Only uncomment to generate the list of added hypertargets <<<


\begin{document}


\selectlanguage{english}
\setenglishformatting

\input{titlepage}
\clearpage
\input{preface__EN}
\clearpage
\input{glance__EN}

\tableofcontents
\clearpage
\listoftables
\clearpage
\listoffigures

% >>> R3: List all todo notes from the current project? <<<
% 'Yes' - uncomment the lines below; 'No' - comment out
% Don't forget to deactivate before publishing
%\todototoc
%\listoftodos
%{\let\clearpage\relax \listofdonetodos}


% Included modules
% Uncomment to include


%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Module Group: System %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\part{Microprocessor and Master}

% Note: Updates may be necessary based on the specific SoC. For instance, Xtensa-based SoCs lack CPU descriptions, and certain SoCs may omit processor instruction extensions.

This part covers the essential processing elements of the system, diving into the ESP-RISC-V CPU and GDMA Controller (GDMA). Details include CPU instruction extensions and controllers for Direct Memory Access (DMA).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% (A) Microprocessor and Master %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subfileinclude{01-RISCVCPU__EN}
\subfileinclude{02-DMA__EN}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% (B) Memory Organization %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{Memory Organization}

This part provides insights into the system's memory structure, discussing system memory and eFuse, offering a framework for understanding memory-related subsystems.

\subfileinclude{03-SYSMEM__EN}
\subfileinclude{04-EFUSE__EN}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% (C) System Component %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\part{System Component}

% Note: Tailor the description based on the specific components present in the SoC.

Encompassing a range of system-level functionalities, this part describes components related to system boot, clocks, GPIO, timers, watchdogs, interrupt handling, low-power management, system registers, and debug assistant.

\subfileinclude{06-IOMUXGPIO__EN}
\subfileinclude{07-RESCLK__EN}
\subfileinclude{08-BOOTCTRL__EN}
\subfileinclude{09-INTERRUPT__EN}
\subfileinclude{10-LOWPOWM__EN}
\subfileinclude{11-SYSTIMER__EN}
\subfileinclude{12-TIMG__EN}
\subfileinclude{13-WDT__EN}
\subfileinclude{14-SYSREG__EN}
\subfileinclude{15-DBGASSIST__EN}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% (D) Cryptography/Security Component %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{Cryptography/Security Component}

Dedicated to security features, this part explores cryptographic accelerators like SHA and ECC. It also covers external Memory Encryption and Decryption and random number generation, showcasing the SoC's capabilities in cryptography and secure data processing.

\subfileinclude{16-ECC__EN}
\subfileinclude{17-SHA__EN}
\subfileinclude{18-EXTMEMENCR__EN}
\subfileinclude{19-RNG__EN}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Module Group: Peripherals %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% (E) Connectivity Interface %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{Connectivity Interface}

% Note: Update the description based on the actual components implemented in the SoC, e.g., some SoCs do not have RMT.

This part addresses the connectivity aspects of the system, describing components related to various communication interfaces like I2C, SPI, UART, and LEDPWM.

\subfileinclude{21-UART__EN}
\subfileinclude{22-SPI__EN}
\subfileinclude{23-I2C__EN}
\subfileinclude{24-LEDPWM__EN}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% (G) On-Chip Sensors and Analog Signal Processing %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{Analog Signal Processing}

% Note: Tailor the description based on the actual components implemented in the SoC.

This part describes components related to analog-to-digital conversion, on-chip sensors, and features such as temperature sensing, demonstrating the system's capabilities in handling analog signals.

\subfileinclude{25-SENSOR__EN}

%%%%%%%%%%%%%%%%
%%% Appendix %%%
%%%%%%%%%%%%%%%%

\part{Appendix}\label{appendix}

This part contains the following information starting from the next page:

\begin{itemize}
    \item \hyperref[sec:resources]{\textit{Related Documentation and Resources}}
    \item \hyperref[glossary]{\textit{Glossary}}
    \item \hyperref[programming-reserved-field]{\textit{Programming Reserved Register Field}}
    \item \hyperref[interrupt-config-registers]{\textit{Interrupt Configuration Registers}}
    \item \hyperref[revision-history]{\textit{Revision History}}
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Related Documentation and Resources %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\input{resources__EN}

\clearpage
\input{glossary__EN}

\clearpage
\input{programming-reserved-field__EN}

\clearpage
\input{interrupt_config_registers__EN}

\clearpage
\input{revision-history__EN}

\clearpage
\input{disclaimer-copyright__EN}

\end{document}
