\begin{register}{H}{RMT\_CH\regindex{n}DATA\_REG (\regindex{n}: 0-3)}{0x{}0000+0x{}4*\regindex{n}}\label{regdesc:RMTCHNDATAREG}
\regfield{RMT\_CH\regindex{n}DATA}{32}{0}{{0x{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTCHNDATA}\item [RMT\_CH\regindex{n}DATA] Read and write data for channel \regindex{n} via APB FIFO. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_CH\regindex{m}DATA\_REG (\regindex{m} = 4, 5, 6, 7)}{0x{}0010, 0x{}0014, 0x{}0018, 0x{}001C }\label{regdesc:RMTCHMDATAREG}
\regfield{RMT\_CH\regindex{m}DATA}{32}{0}{{0x{}000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTCHMDATA}\item [RMT\_CH\regindex{m}DATA] Read and write data for channel \regindex{m} via APB FIFO. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_CH\regindex{n}CONF0\_REG (\regindex{n}: 0-3)}{0x{}0020+0x{}4*\regindex{n}}\label{regdesc:RMTCHNCONF0REG}
\regfield{(reserved)}{6}{26}{0000000}%
\regfield{RMT\_DMA\_ACCESS\_EN\_CH\regindex{3}(reserved for \regindex{n}:0-2)}{1}{25}{{0}}%
\regfield{RMT\_CONF\_UPDATE\_CH\regindex{n}}{1}{24}{{0}}%
\regfield{(reserved)}{1}{23}{0}%
\regfield{RMT\_CARRIER\_OUT\_LV\_CH\regindex{n}}{1}{22}{{1}}%
\regfield{RMT\_CARRIER\_EN\_CH\regindex{n}}{1}{21}{{1}}%
\regfield{RMT\_CARRIER\_EFF\_EN\_CH\regindex{n}}{1}{20}{{1}}%
\regfield{RMT\_MEM\_SIZE\_CH\regindex{n}}{4}{16}{{0x{}1}}%
\regfield{RMT\_DIV\_CNT\_CH\regindex{n}}{8}{8}{{0x{}2}}%
\regfield{RMT\_TX\_STOP\_CH\regindex{n}}{1}{7}{{0}}%
\regfield{RMT\_IDLE\_OUT\_EN\_CH\regindex{n}}{1}{6}{{0}}%
\regfield{RMT\_IDLE\_OUT\_LV\_CH\regindex{n}}{1}{5}{{0}}%
\regfield{RMT\_MEM\_TX\_WRAP\_EN\_CH\regindex{n}}{1}{4}{{0}}%
\regfield{RMT\_TX\_CONTI\_MODE\_CH\regindex{n}}{1}{3}{{0}}%
\regfield{RMT\_APB\_MEM\_RST\_CH\regindex{n}}{1}{2}{{0}}%
\regfield{RMT\_MEM\_RD\_RST\_CH\regindex{n}}{1}{1}{{0}}%
\regfield{RMT\_TX\_START\_CH\regindex{n}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTTXSTARTCHN}\item [RMT\_TX\_START\_CH\regindex{n}] Set this bit to start sending data in channel \regindex{n}. (WT)
\label{fielddesc:RMTMEMRDRSTCHN}\item [RMT\_MEM\_RD\_RST\_CH\regindex{n}] Set this bit to reset RAM read address accessed by the transmitter of channel \regindex{n}. (WT)
\label{fielddesc:RMTAPBMEMRSTCHN}\item [RMT\_APB\_MEM\_RST\_CH\regindex{n}] Set this bit to reset RAM W/R address for channel \regindex{n} when accessed by APB FIFO. (WT)
\label{fielddesc:RMTTXCONTIMODECHN}\item [RMT\_TX\_CONTI\_MODE\_CH\regindex{n}] 
Set this bit to enable continuous TX mode for channel \regindex{n}. (R/W)

In this mode, the transmitter starts its transmission from the first data, and in the following transmission:
\begin{itemize}
    \item if an end-marker is encountered, the transmitter starts transmitting data from the first data again;
    \item if no end-marker is encountered, the transmitter starts transmitting the first data again when the last data is transmitted.
\end{itemize}

\label{fielddesc:RMTMEMTXWRAPENCHN}\item [RMT\_MEM\_TX\_WRAP\_EN\_CH\regindex{n}] 
Set this bit to enable wrap TX mode for channel \regindex{n}. In this mode, if the TX data size is larger than the channel's RAM block size, the transmitter continues transmitting the first data again to the last data in loops. (R/W)
\label{fielddesc:RMTIDLEOUTLVCHN}\item [RMT\_IDLE\_OUT\_LV\_CH\regindex{n}] This bit configures the level of output signal for channel \regindex{n} when the transmitter is in idle state. (R/W)
\label{fielddesc:RMTIDLEOUTENCHN}\item [RMT\_IDLE\_OUT\_EN\_CH\regindex{n}] This is the output enable-bit for channel \regindex{n} in idle state. 0: the output level in idle state is determined by the level field of an end-marker. 1: the output level in idle state is determined by \hyperref[fielddesc:RMTIDLEOUTLVCHN]{RMT\_IDLE\_OUT\_LV\_CH\regindex{n}}. (R/W)
\label{fielddesc:RMTTXSTOPCHN}\item [RMT\_TX\_STOP\_CH\regindex{n}] Set this bit to stop the transmitter of channel \regindex{n} sending data out. (R/W/SC)
\label{fielddesc:RMTDIVCNTCHN}\item [RMT\_DIV\_CNT\_CH\regindex{n}] This field is used to configure the divider for clock of channel \regindex{n}. (R/W)
\label{fielddesc:RMTMEMSIZECHN}\item [RMT\_MEM\_SIZE\_CH\regindex{n}] This field is used to configure the maximum number of memory blocks allocated to channel \regindex{n}. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{RMT\_CH\regindex{n}CONF0\_REG (\regindex{n}: 0-3)}{0x{}0020+0x{}4*\regindex{n}}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:RMTCARRIEREFFENCHN}\item [RMT\_CARRIER\_EFF\_EN\_CH\regindex{n}] 1: Add carrier modulation on the output signal only at data-sending state for channel \regindex{n}. 0: Add carrier modulation on the output signal at data-sending state and idle state for channel \regindex{n}. Only valid when \hyperref[fielddesc:RMTCARRIERENCHN]{RMT\_CARRIER\_EN\_CH\regindex{n}} is 1. (R/W)
\label{fielddesc:RMTCARRIERENCHN}\item [RMT\_CARRIER\_EN\_CH\regindex{n}] This is the carrier modulation enable-bit for channel \regindex{n}. 1: Add carrier modulation on the output signal. 0: No carrier modulation is added on output signal. (R/W)
\label{fielddesc:RMTCARRIEROUTLVCHN}\item [RMT\_CARRIER\_OUT\_LV\_CH\regindex{n}] This bit is used to configure the position of carrier wave for channel \regindex{n}. (R/W)

1'h0: add carrier wave on low level.

1'h1: add carrier wave on high level. 
\label{fielddesc:RMTCONFUPDATECHN}\item [RMT\_CONF\_UPDATE\_CH\regindex{n}] Synchronization bit for channel \regindex{n} (WT)

\label{fielddesc:RMTDMAACCESSENCH3}\item
[RMT\_DMA\_ACCESS\_EN\_CH3 (Reserved for channel 0 - 2)] DMA access enable bit for channel 3. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_CH\regindex{m}CONF0\_REG (\regindex{m} = 4, 5, 6, 7)}{0x{}0030, 0x{}0038, 0x{}0040, 0x{}0048}\label{regdesc:RMTCHMCONF0REG}
\regfield{(reserved)}{2}{30}{00}%
\regfield{RMT\_CARRIER\_OUT\_LV\_CH\regindex{m}}{1}{29}{{1}}%
\regfield{RMT\_CARRIER\_EN\_CH\regindex{m}}{1}{28}{{1}}%
\regfield{RMT\_MEM\_SIZE\_CH\regindex{m}}{4}{24}{{0x{}1}}%
\regfield{RMT\_DMA\_ACCESS\_EN\_CH\regindex{7}(reserved for \regindex{m}:4-6)}{1}{23}{{0}}%
\regfield{RMT\_IDLE\_THRES\_CH\regindex{m}}{15}{8}{{0x{}7fff}}%
\regfield{RMT\_DIV\_CNT\_CH\regindex{m}}{8}{0}{{0x{}2}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTDIVCNTCHM}\item [RMT\_DIV\_CNT\_CH\regindex{m}] This field is used to configure the clock divider of channel \regindex{m}. (R/W)
\label{fielddesc:RMTIDLETHRESCHM}\item [RMT\_IDLE\_THRES\_CH\regindex{m}] This field is used to configure RX threshold. When no edge is detected on the input signal for continuous clock cycles longer than this field value, the receiver stops receiving data. (R/W)
\label{fielddesc:RMTDMAACCESSENCH7}\item
[RMT\_DMA\_ACCESS\_EN\_CH7 (Reserved for channel 4 - 6)] DMA access enable bit for channel 7. (R/W)
\label{fielddesc:RMTMEMSIZECHM}\item [RMT\_MEM\_SIZE\_CH\regindex{m}] This field is used to configure the maximum number of memory blocks allocated to channel \regindex{m}. (R/W)
\label{fielddesc:RMTCARRIERENCHM}\item [RMT\_CARRIER\_EN\_CH\regindex{m}] This is the carrier demodulation enable-bit for channel \regindex{m}. 1: enable carrier demodulation for input signal. 0: disable carrier modulation for input signal. (R/W)
\label{fielddesc:RMTCARRIEROUTLVCHM}\item [RMT\_CARRIER\_OUT\_LV\_CH\regindex{m}] This bit is used to configure the position of carrier demodulation for channel \regindex{m}. (R/W)

1'h0: demodulate low-level carrier wave.

1'h1: demodulate high-level carrier wave. 
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_CH\regindex{m}CONF1\_REG (\regindex{m} = 4, 5, 6, 7)}{0x{}0034, 0x{}003C, 0x{}0044, 0x{}004C}\label{regdesc:RMTCHMCONF1REG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{RMT\_CONF\_UPDATE\_CH\regindex{m}}{1}{15}{{0}}%
\regfield{(reserved)}{1}{14}{0}%
\regfield{RMT\_MEM\_RX\_WRAP\_EN\_CH\regindex{m}}{1}{13}{{0}}%
\regfield{RMT\_RX\_FILTER\_THRES\_CH\regindex{m}}{8}{5}{{0x{}f}}%
\regfield{RMT\_RX\_FILTER\_EN\_CH\regindex{m}}{1}{4}{{0}}%
\regfield{RMT\_MEM\_OWNER\_CH\regindex{m}}{1}{3}{{1}}%
\regfield{RMT\_APB\_MEM\_RST\_CH\regindex{m}}{1}{2}{{0}}%
\regfield{RMT\_MEM\_WR\_RST\_CH\regindex{m}}{1}{1}{{0}}%
\regfield{RMT\_RX\_EN\_CH\regindex{m}}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTRXENCHM}\item [RMT\_RX\_EN\_CH\regindex{m}] Set this bit to enable the receiver to start receiving data on channel \regindex{m}. (R/W)
\label{fielddesc:RMTMEMWRRSTCHM}\item [RMT\_MEM\_WR\_RST\_CH\regindex{m}] Set this bit to reset RAM write address accessed by the receiver for channel \regindex{m}. (WT)
\label{fielddesc:RMTAPBMEMRSTCHM}\item [RMT\_APB\_MEM\_RST\_CH\regindex{m}] Set this bit to reset RAM W/R address accessed by APB FIFO for channel \regindex{m}. (WT)
\label{fielddesc:RMTMEMOWNERCHM}\item [RMT\_MEM\_OWNER\_CH\regindex{m}] This bit marks the ownership of channel \regindex{m}'s RAM block. (R/W/SC)

1'h1: Receiver is using the RAM. 

1'h0: APB bus is using the RAM. 
\label{fielddesc:RMTRXFILTERENCHM}\item [RMT\_RX\_FILTER\_EN\_CH\regindex{m}] Set this bit to enable the receiver's filter for channel \regindex{m}. (R/W)
\label{fielddesc:RMTRXFILTERTHRESCHM}\item [RMT\_RX\_FILTER\_THRES\_CH\regindex{m}] When receiving data, the receiver ignores the input pulse when its width is shorter than this register value in units of rmt\_sclk cycles. (R/W)
\label{fielddesc:RMTMEMRXWRAPENCHM}\item [RMT\_MEM\_RX\_WRAP\_EN\_CH\regindex{m}] Set this bit to enable wrap RX mode for channel \regindex{m}. In this mode, if the RX data size is larger than channel \regindex{m} 's RAM block size, the receiver stores the RX data from the first address to the last address in loops. (R/W)
\label{fielddesc:RMTCONFUPDATECHM}\item [RMT\_CONF\_UPDATE\_CH\regindex{m}] Synchronization bit for channel \regindex{m}. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_CH\regindex{m}\_RX\_CARRIER\_RM\_REG (\regindex{m} = 4, 5, 6, 7)}{0x{}0090, 0x{}0094, 0x{}0098, 0x{}009C}\label{regdesc:RMTCHMRXCARRIERRMREG}
\regfield{RMT\_CARRIER\_HIGH\_THRES\_CH\regindex{m}}{16}{16}{{0x{}00}}%
\regfield{RMT\_CARRIER\_LOW\_THRES\_CH\regindex{m}}{16}{0}{{0x{}00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTCARRIERLOWTHRESCHM}\item [RMT\_CARRIER\_LOW\_THRES\_CH\regindex{m}]  The low level period in a carrier modulation mode is (RMT\_CARRIER\_LOW\_THRES\_CH\regindex{m} + 1) for channel \regindex{m}. (R/W)
\label{fielddesc:RMTCARRIERHIGHTHRESCHM}\item [RMT\_CARRIER\_HIGH\_THRES\_CH\regindex{m}] The high level period in a carrier modulation mode is (RMT\_CARRIER\_HIGH\_THRES\_CH\regindex{m} + 1) for channel \regindex{m}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_SYS\_CONF\_REG}{0x{}00C0}\label{regdesc:RMTSYSCONFREG}
\regfield{RMT\_CLK\_EN}{1}{31}{{0}}%
\regfield{(reserved)}{4}{27}{0000}%
\regfield{RMT\_SCLK\_ACTIVE}{1}{26}{{1}}%
\regfield{RMT\_SCLK\_SEL}{2}{24}{{0x{}1}}%
\regfield{RMT\_SCLK\_DIV\_B}{6}{18}{{0x{}0}}%
\regfield{RMT\_SCLK\_DIV\_A}{6}{12}{{0x{}0}}%
\regfield{RMT\_SCLK\_DIV\_NUM}{8}{4}{{0x{}1}}%
\regfield{RMT\_MEM\_FORCE\_PU}{1}{3}{{0}}%
\regfield{RMT\_MEM\_FORCE\_PD}{1}{2}{{0}}%
\regfield{RMT\_MEM\_CLK\_FORCE\_ON}{1}{1}{{0}}%
\regfield{RMT\_APB\_FIFO\_MASK}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTAPBFIFOMASK}\item [RMT\_APB\_FIFO\_MASK] 1'h1: Access memory directly (NONFIFO mode). 1'h0: Access memory by FIFO (FIFO mode). (R/W)
\label{fielddesc:RMTMEMCLKFORCEON}\item [RMT\_MEM\_CLK\_FORCE\_ON] Set this bit to enable the clock for RMT memory. (R/W)
\label{fielddesc:RMTMEMFORCEPD}\item [RMT\_MEM\_FORCE\_PD] Set this bit to power down RMT memory. (R/W)
\label{fielddesc:RMTMEMFORCEPU}\item [RMT\_MEM\_FORCE\_PU] 1: Disable the power-down function of RMT memory in Light-sleep. 0: Power down RMT memory when RMT is in Light-sleep mode. (R/W)
\label{fielddesc:RMTSCLKDIVNUM}\item [RMT\_SCLK\_DIV\_NUM] The integral part of the fractional divider. (R/W)
\label{fielddesc:RMTSCLKDIVA}\item [RMT\_SCLK\_DIV\_A] The numerator of the fractional part of the fractional divider. (R/W)
\label{fielddesc:RMTSCLKDIVB}\item [RMT\_SCLK\_DIV\_B] The denominator of the fractional part of the fractional divider. (R/W)
\label{fielddesc:RMTSCLKSEL}\item [RMT\_SCLK\_SEL] Choose the clock source of rmt\_sclk. 1: APB\_CLK; 2: RC\_FAST\_CLK; 3: XTAL\_CLK. (R/W)
\label{fielddesc:RMTSCLKACTIVE}\item [RMT\_SCLK\_ACTIVE] rmt\_sclk switch. (R/W)
\label{fielddesc:RMTCLKEN}\item [RMT\_CLK\_EN] The enable signal of RMT register clock gate. 1: Power up the drive clock of registers. 0: Power down the drive clock of registers. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_REF\_CNT\_RST\_REG}{0x{}00C8}\label{regdesc:RMTREFCNTRSTREG}
\regfield{(reserved)}{24}{8}{000000000000000000000000}%
\regfield{RMT\_REF\_CNT\_RST\_CH7}{1}{7}{{0}}%
\regfield{RMT\_REF\_CNT\_RST\_CH6}{1}{6}{{0}}%
\regfield{RMT\_REF\_CNT\_RST\_CH5}{1}{5}{{0}}%
\regfield{RMT\_REF\_CNT\_RST\_CH4}{1}{4}{{0}}%
\regfield{RMT\_REF\_CNT\_RST\_CH3}{1}{3}{{0}}%
\regfield{RMT\_REF\_CNT\_RST\_CH2}{1}{2}{{0}}%
\regfield{RMT\_REF\_CNT\_RST\_CH1}{1}{1}{{0}}%
\regfield{RMT\_REF\_CNT\_RST\_CH0}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTREFCNTRSTCHN}\item [RMT\_REF\_CNT\_RST\_CH\regindex{n}(\regindex{n} = 0, 1, 2, 3)] This bit is used to reset the clock divider of channel \regindex{n}. (WT)
\label{fielddesc:RMTREFCNTRSTCHM}\item [RMT\_REF\_CNT\_RST\_CH\regindex{m} (\regindex{m} = 4, 5, 6, 7)] This bit is used to reset the clock divider of channel \regindex{m}. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_CH\regindex{n}STATUS\_REG (\regindex{n}: 0-3)}{0x{}0050+0x{}4*\regindex{n}}\label{regdesc:RMTCHNSTATUSREG}
\regfield{(reserved)}{5}{27}{00000}%
\regfield{RMT\_APB\_MEM\_WR\_ERR\_CH\regindex{n}}{1}{26}{{0}}%
\regfield{RMT\_MEM\_EMPTY\_CH\regindex{n}}{1}{25}{{0}}%
\regfield{RMT\_STATE\_CH\regindex{n}}{3}{22}{{0}}%
\regfield{(reserved)}{1}{21}{0}%
\regfield{RMT\_APB\_MEM\_WADDR\_CH\regindex{n}}{10}{11}{{0}}%
\regfield{(reserved)}{1}{10}{0}%
\regfield{RMT\_MEM\_RADDR\_EX\_CH\regindex{n}}{10}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTMEMRADDREXCHN}\item [RMT\_MEM\_RADDR\_EX\_CH\regindex{n}] This field records the memory address offset when transmitter of channel \regindex{n} is using the RAM. (RO)
\label{fielddesc:RMTAPBMEMWADDRCHN}\item [RMT\_APB\_MEM\_WADDR\_CH\regindex{n}] This field records the memory address offset when writes RAM over APB bus. (RO)
\label{fielddesc:RMTSTATECHN}\item [RMT\_STATE\_CH\regindex{n}] This field records the FSM status of channel \regindex{n}. (RO)
\label{fielddesc:RMTMEMEMPTYCHN}\item [RMT\_MEM\_EMPTY\_CH\regindex{n}] This status bit will be set when the TX data size is larger than the memory size and the wrap TX mode is disabled. (RO)
\label{fielddesc:RMTAPBMEMWRERRCHN}\item [RMT\_APB\_MEM\_WR\_ERR\_CH\regindex{n}] This status bit will be set if the offset address is out of memory size (overflows) when writes via APB bus. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_CH\regindex{m}STATUS\_REG (\regindex{m} = 4, 5, 6, 7)}{0x{}0060, 0x{}0064, 0x{}0068, 0x{}006C}\label{regdesc:RMTCHMSTATUSREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{RMT\_APB\_MEM\_RD\_ERR\_CH\regindex{m}}{1}{27}{{0}}%
\regfield{RMT\_MEM\_FULL\_CH\regindex{m}}{1}{26}{{0}}%
\regfield{RMT\_MEM\_OWNER\_ERR\_CH\regindex{m}}{1}{25}{{0}}%
\regfield{RMT\_STATE\_CH\regindex{m}}{3}{22}{{0}}%
\regfield{(reserved)}{1}{21}{0}%
\regfield{RMT\_APB\_MEM\_RADDR\_CH\regindex{m}}{10}{11}{{0x{}c0}}%
\regfield{(reserved)}{1}{10}{0}%
\regfield{RMT\_MEM\_WADDR\_EX\_CH\regindex{m}}{10}{0}{{0x{}c0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTMEMWADDREXCHM}\item [RMT\_MEM\_WADDR\_EX\_CH\regindex{m}] This field records the memory address offset when receiver of channel \regindex{m} is using the RAM. (RO) 
\label{fielddesc:RMTAPBMEMRADDRCHM}\item [RMT\_APB\_MEM\_RADDR\_CH\regindex{m}] This field records the memory address offset when reads RAM over APB bus. (RO)
\label{fielddesc:RMTSTATECHM}\item [RMT\_STATE\_CH\regindex{m}] This field records the FSM status of channel \regindex{m}. (RO)
\label{fielddesc:RMTMEMOWNERERRCHM}\item [RMT\_MEM\_OWNER\_ERR\_CH\regindex{m}] This status bit will be set when the ownership of memory block is wrong. (RO)
\label{fielddesc:RMTMEMFULLCHM}\item [RMT\_MEM\_FULL\_CH\regindex{m}] This status bit will be set if the receiver receives more data than the memory can fit. (RO)
\label{fielddesc:RMTAPBMEMRDERRCHM}\item [RMT\_APB\_MEM\_RD\_ERR\_CH\regindex{m}] This status bit will be set if the offset address is out of memory size (overflows) when reads RAM via APB bus. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_INT\_RAW\_REG}{0x{}0070}\label{regdesc:RMTINTRAWREG}
\regfield{(reserved)}{2}{30}{00}%
\regfield{RMT\_CH7\_DMA\_ACCESS\_FAIL\_INT\_RAW}{1}{29}{{0}}%
\regfield{RMT\_CH3\_DMA\_ACCESS\_FAIL\_INT\_RAW}{1}{28}{{0}}%
\regfield{RMT\_CH7\_RX\_THR\_EVENT\_INT\_RAW}{1}{27}{{0}}%
\regfield{RMT\_CH6\_RX\_THR\_EVENT\_INT\_RAW}{1}{26}{{0}}%
\regfield{RMT\_CH5\_RX\_THR\_EVENT\_INT\_RAW}{1}{25}{{0}}%
\regfield{RMT\_CH4\_RX\_THR\_EVENT\_INT\_RAW}{1}{24}{{0}}%
\regfield{RMT\_CH7\_ERR\_INT\_RAW}{1}{23}{{0}}%
\regfield{RMT\_CH6\_ERR\_INT\_RAW}{1}{22}{{0}}%
\regfield{RMT\_CH5\_ERR\_INT\_RAW}{1}{21}{{0}}%
\regfield{RMT\_CH4\_ERR\_INT\_RAW}{1}{20}{{0}}%
\regfield{RMT\_CH7\_RX\_END\_INT\_RAW}{1}{19}{{0}}%
\regfield{RMT\_CH6\_RX\_END\_INT\_RAW}{1}{18}{{0}}%
\regfield{RMT\_CH5\_RX\_END\_INT\_RAW}{1}{17}{{0}}%
\regfield{RMT\_CH4\_RX\_END\_INT\_RAW}{1}{16}{{0}}%
\regfield{RMT\_CH3\_TX\_LOOP\_INT\_RAW}{1}{15}{{0}}%
\regfield{RMT\_CH2\_TX\_LOOP\_INT\_RAW}{1}{14}{{0}}%
\regfield{RMT\_CH1\_TX\_LOOP\_INT\_RAW}{1}{13}{{0}}%
\regfield{RMT\_CH0\_TX\_LOOP\_INT\_RAW}{1}{12}{{0}}%
\regfield{RMT\_CH3\_TX\_THR\_EVENT\_INT\_RAW}{1}{11}{{0}}%
\regfield{RMT\_CH2\_TX\_THR\_EVENT\_INT\_RAW}{1}{10}{{0}}%
\regfield{RMT\_CH1\_TX\_THR\_EVENT\_INT\_RAW}{1}{9}{{0}}%
\regfield{RMT\_CH0\_TX\_THR\_EVENT\_INT\_RAW}{1}{8}{{0}}%
\regfield{RMT\_CH3\_ERR\_INT\_RAW}{1}{7}{{0}}%
\regfield{RMT\_CH2\_ERR\_INT\_RAW}{1}{6}{{0}}%
\regfield{RMT\_CH1\_ERR\_INT\_RAW}{1}{5}{{0}}%
\regfield{RMT\_CH0\_ERR\_INT\_RAW}{1}{4}{{0}}%
\regfield{RMT\_CH3\_TX\_END\_INT\_RAW}{1}{3}{{0}}%
\regfield{RMT\_CH2\_TX\_END\_INT\_RAW}{1}{2}{{0}}%
\regfield{RMT\_CH1\_TX\_END\_INT\_RAW}{1}{1}{{0}}%
\regfield{RMT\_CH0\_TX\_END\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTCHNTXENDINTRAW}\item [RMT\_CH\regindex{n}\_TX\_END\_INT\_RAW (\regindex{n} = 0-3)] The interrupt raw bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_TX\_END\_INT}. (R/WTC/SS)
\label{fielddesc:RMTCHNERRINTRAW}\item [RMT\_CH\regindex{n}\_ERR\_INT\_RAW (\regindex{n} = 0-3)] The interrupt raw bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_ERR\_INT}. (R/WTC/SS)
\label{fielddesc:RMTCHNTXTHREVENTINTRAW}\item [RMT\_CH\regindex{n}\_TX\_THR\_EVENT\_INT\_RAW (\regindex{n} = 0-3)] The interrupt raw bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_TX\_THR\_EVENT\_INT} (R/WTC/SS)
\label{fielddesc:RMTCHNTXLOOPINTRAW}\item [RMT\_CH\regindex{n}\_TX\_LOOP\_INT\_RAW (\regindex{n} = 0-3)] The interrupt raw bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_TX\_LOOP\_INT}. (R/WTC/SS)
\label{fielddesc:RMTCHMRXENDINTRAW}\item [RMT\_CH\regindex{m}\_RX\_END\_INT\_RAW(\regindex{m} = 4-7)] The interrupt raw bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{m}\_RX\_END\_INT}. (R/WTC/SS)
\label{fielddesc:RMTCHMERRINTRAW}\item [RMT\_CH\regindex{m}\_ERR\_INT\_RAW (\regindex{m} = 4-7)] The interrupt raw bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{m}\_ERR\_INT}. (R/WTC/SS)
\label{fielddesc:RMTCHMRXTHREVENTINTRAW}\item [RMT\_CH\regindex{m}\_RX\_THR\_EVENT\_INT\_RAW(\regindex{m} = 4-7)] The interrupt raw bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{m}\_RX\_THR\_EVENT\_INT}. (R/WTC/SS)
\label{fielddesc:RMTCHNDMAACCESSFAILINTRAW}\item [RMT\_CH3\_DMA\_ACCESS\_FAIL\_INT\_RAW] The interrupt raw bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH3\_DMA\_ACCESS\_FAIL\_INT}. (R/WTC/SS)
\label{fielddesc:RMTCHMDMAACCESSFAILINTRAW}\item [RMT\_CH7\_DMA\_ACCESS\_FAIL\_INT\_RAW] The interrupt raw bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH7\_DMA\_ACCESS\_FAIL\_INT}. (R/WTC/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_INT\_ST\_REG}{0x{}0074}\label{regdesc:RMTINTSTREG}
\regfield{(reserved)}{2}{30}{00}%
\regfield{RMT\_CH7\_DMA\_ACCESS\_FAIL\_INT\_ST}{1}{29}{{0}}%
\regfield{RMT\_CH3\_DMA\_ACCESS\_FAIL\_INT\_ST}{1}{28}{{0}}%
\regfield{RMT\_CH7\_RX\_THR\_EVENT\_INT\_ST}{1}{27}{{0}}%
\regfield{RMT\_CH6\_RX\_THR\_EVENT\_INT\_ST}{1}{26}{{0}}%
\regfield{RMT\_CH5\_RX\_THR\_EVENT\_INT\_ST}{1}{25}{{0}}%
\regfield{RMT\_CH4\_RX\_THR\_EVENT\_INT\_ST}{1}{24}{{0}}%
\regfield{RMT\_CH7\_ERR\_INT\_ST}{1}{23}{{0}}%
\regfield{RMT\_CH6\_ERR\_INT\_ST}{1}{22}{{0}}%
\regfield{RMT\_CH5\_ERR\_INT\_ST}{1}{21}{{0}}%
\regfield{RMT\_CH4\_ERR\_INT\_ST}{1}{20}{{0}}%
\regfield{RMT\_CH7\_RX\_END\_INT\_ST}{1}{19}{{0}}%
\regfield{RMT\_CH6\_RX\_END\_INT\_ST}{1}{18}{{0}}%
\regfield{RMT\_CH5\_RX\_END\_INT\_ST}{1}{17}{{0}}%
\regfield{RMT\_CH4\_RX\_END\_INT\_ST}{1}{16}{{0}}%
\regfield{RMT\_CH3\_TX\_LOOP\_INT\_ST}{1}{15}{{0}}%
\regfield{RMT\_CH2\_TX\_LOOP\_INT\_ST}{1}{14}{{0}}%
\regfield{RMT\_CH1\_TX\_LOOP\_INT\_ST}{1}{13}{{0}}%
\regfield{RMT\_CH0\_TX\_LOOP\_INT\_ST}{1}{12}{{0}}%
\regfield{RMT\_CH3\_TX\_THR\_EVENT\_INT\_ST}{1}{11}{{0}}%
\regfield{RMT\_CH2\_TX\_THR\_EVENT\_INT\_ST}{1}{10}{{0}}%
\regfield{RMT\_CH1\_TX\_THR\_EVENT\_INT\_ST}{1}{9}{{0}}%
\regfield{RMT\_CH0\_TX\_THR\_EVENT\_INT\_ST}{1}{8}{{0}}%
\regfield{RMT\_CH3\_ERR\_INT\_ST}{1}{7}{{0}}%
\regfield{RMT\_CH2\_ERR\_INT\_ST}{1}{6}{{0}}%
\regfield{RMT\_CH1\_ERR\_INT\_ST}{1}{5}{{0}}%
\regfield{RMT\_CH0\_ERR\_INT\_ST}{1}{4}{{0}}%
\regfield{RMT\_CH3\_TX\_END\_INT\_ST}{1}{3}{{0}}%
\regfield{RMT\_CH2\_TX\_END\_INT\_ST}{1}{2}{{0}}%
\regfield{RMT\_CH1\_TX\_END\_INT\_ST}{1}{1}{{0}}%
\regfield{RMT\_CH0\_TX\_END\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTCHNTXENDINTST}\item [RMT\_CH\regindex{n}\_TX\_END\_INT\_ST (\regindex{n} = 0-3)] The masked interrupt status bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_TX\_END\_INT}. (RO)
\label{fielddesc:RMTCHNERRINTST}\item [RMT\_CH\regindex{n}\_ERR\_INT\_ST (\regindex{n} = 0-3)] The masked interrupt status bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_ERR\_INT}. (RO)
\label{fielddesc:RMTCHNTXTHREVENTINTST}\item [RMT\_CH\regindex{n}\_TX\_THR\_EVENT\_INT\_ST (\regindex{n} = 0-3)] The masked interrupt status bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_TX\_THR\_EVENT\_INT}. (RO)
\label{fielddesc:RMTCHNTXLOOPINTST}\item [RMT\_CH\regindex{n}\_TX\_LOOP\_INT\_ST (\regindex{n} = 0-3)] The masked interrupt status bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_TX\_LOOP\_INT}. (RO)
\label{fielddesc:RMTCHMRXENDINTST}\item [RMT\_CH\regindex{m}\_RX\_END\_INT\_ST (\regindex{m} = 4-7)] The masked interrupt status bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{m}\_RX\_END\_INT}. (RO)
\label{fielddesc:RMTCHMERRINTST}\item [RMT\_CH\regindex{m}\_ERR\_INT\_ST (\regindex{m} = 4-7)] The masked interrupt status bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{m}\_ERR\_INT}. (RO)
\label{fielddesc:RMTCHMRXTHREVENTINTST}\item [RMT\_CH\regindex{m}\_RX\_THR\_EVENT\_INT\_ST (\regindex{m} = 4-7)] The masked interrupt status bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{m}\_RX\_THR\_EVENT\_INT}. (RO)
\label{fielddesc:RMTCHNDMAACCESSFAILINTST}\item [RMT\_CH3\_DMA\_ACCESS\_FAIL\_INT\_ST] The masked interrupt status bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH3\_DMA\_ACCESS\_FAIL\_INT}. (RO)
\label{fielddesc:RMTCHMDMAACCESSFAILINTST}\item [RMT\_CH7\_DMA\_ACCESS\_FAIL\_INT\_ST] The masked interrupt status bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH7\_DMA\_ACCESS\_FAIL\_INT}. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_INT\_ENA\_REG}{0x{}0078}\label{regdesc:RMTINTENAREG}
\regfield{(reserved)}{2}{30}{00}%
\regfield{RMT\_CH7\_DMA\_ACCESS\_FAIL\_INT\_ENA}{1}{29}{{0}}%
\regfield{RMT\_CH3\_DMA\_ACCESS\_FAIL\_INT\_ENA}{1}{28}{{0}}%
\regfield{RMT\_CH7\_RX\_THR\_EVENT\_INT\_ENA}{1}{27}{{0}}%
\regfield{RMT\_CH6\_RX\_THR\_EVENT\_INT\_ENA}{1}{26}{{0}}%
\regfield{RMT\_CH5\_RX\_THR\_EVENT\_INT\_ENA}{1}{25}{{0}}%
\regfield{RMT\_CH4\_RX\_THR\_EVENT\_INT\_ENA}{1}{24}{{0}}%
\regfield{RMT\_CH7\_ERR\_INT\_ENA}{1}{23}{{0}}%
\regfield{RMT\_CH6\_ERR\_INT\_ENA}{1}{22}{{0}}%
\regfield{RMT\_CH5\_ERR\_INT\_ENA}{1}{21}{{0}}%
\regfield{RMT\_CH4\_ERR\_INT\_ENA}{1}{20}{{0}}%
\regfield{RMT\_CH7\_RX\_END\_INT\_ENA}{1}{19}{{0}}%
\regfield{RMT\_CH6\_RX\_END\_INT\_ENA}{1}{18}{{0}}%
\regfield{RMT\_CH5\_RX\_END\_INT\_ENA}{1}{17}{{0}}%
\regfield{RMT\_CH4\_RX\_END\_INT\_ENA}{1}{16}{{0}}%
\regfield{RMT\_CH3\_TX\_LOOP\_INT\_ENA}{1}{15}{{0}}%
\regfield{RMT\_CH2\_TX\_LOOP\_INT\_ENA}{1}{14}{{0}}%
\regfield{RMT\_CH1\_TX\_LOOP\_INT\_ENA}{1}{13}{{0}}%
\regfield{RMT\_CH0\_TX\_LOOP\_INT\_ENA}{1}{12}{{0}}%
\regfield{RMT\_CH3\_TX\_THR\_EVENT\_INT\_ENA}{1}{11}{{0}}%
\regfield{RMT\_CH2\_TX\_THR\_EVENT\_INT\_ENA}{1}{10}{{0}}%
\regfield{RMT\_CH1\_TX\_THR\_EVENT\_INT\_ENA}{1}{9}{{0}}%
\regfield{RMT\_CH0\_TX\_THR\_EVENT\_INT\_ENA}{1}{8}{{0}}%
\regfield{RMT\_CH3\_ERR\_INT\_ENA}{1}{7}{{0}}%
\regfield{RMT\_CH2\_ERR\_INT\_ENA}{1}{6}{{0}}%
\regfield{RMT\_CH1\_ERR\_INT\_ENA}{1}{5}{{0}}%
\regfield{RMT\_CH0\_ERR\_INT\_ENA}{1}{4}{{0}}%
\regfield{RMT\_CH3\_TX\_END\_INT\_ENA}{1}{3}{{0}}%
\regfield{RMT\_CH2\_TX\_END\_INT\_ENA}{1}{2}{{0}}%
\regfield{RMT\_CH1\_TX\_END\_INT\_ENA}{1}{1}{{0}}%
\regfield{RMT\_CH0\_TX\_END\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTCHNTXENDINTENA}\item [RMT\_CH\regindex{n}\_TX\_END\_INT\_ENA (\regindex{n} = 0-3)] The interrupt enable bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_TX\_END\_INT}. (R/W)
\label{fielddesc:RMTCHNERRINTENA}\item [RMT\_CH\regindex{n}\_ERR\_INT\_ENA (\regindex{n} = 0-3)] The interrupt enable bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_ERR\_INT}. (R/W)
\label{fielddesc:RMTCHNTXTHREVENTINTENA}\item [RMT\_CH\regindex{n}\_TX\_THR\_EVENT\_INT\_ENA (\regindex{n} = 0-3)] The interrupt enable bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_TX\_THR\_EVENT\_INT}. (R/W)
\label{fielddesc:RMTCHNTXLOOPINTENA}\item [RMT\_CH\regindex{n}\_TX\_LOOP\_INT\_ENA (\regindex{n} = 0-3)] The interrupt enable bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_TX\_LOOP\_INT}. (R/W)
\label{fielddesc:RMTCHMRXENDINTENA}\item [RMT\_CH\regindex{m}\_RX\_END\_INT\_ENA (\regindex{m} = 4-7)] The interrupt enable bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{m}\_RX\_END\_INT}. (R/W)
\label{fielddesc:RMTCHMERRINTENA}\item [RMT\_CH\regindex{m}\_ERR\_INT\_ENA (\regindex{m} = 4-7)] The interrupt enable bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{m}\_ERR\_INT}. (R/W)
\label{fielddesc:RMTCHMRXTHREVENTINTENA}\item [RMT\_CH\regindex{m}\_RX\_THR\_EVENT\_INT\_ENA (\regindex{m} = 4-7)] The interrupt enable bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{m}\_RX\_THR\_EVENT\_INT}. (R/W)
\label{fielddesc:RMTCHNDMAACCESSFAILINTENA}\item [RMT\_CH3\_DMA\_ACCESS\_FAIL\_INT\_ENA] The interrupt enable bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH3\_DMA\_ACCESS\_FAIL\_INT}. (R/W)
\label{fielddesc:RMTCHMDMAACCESSFAILINTENA}\item [RMT\_CH7\_DMA\_ACCESS\_FAIL\_INT\_ENA] The interrupt enable bit of \hyperref[int:RMTCHnTXENDINT]{RMT\_CH7\_DMA\_ACCESS\_FAIL\_INT}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_INT\_CLR\_REG}{0x{}007C}\label{regdesc:RMTINTCLRREG}
\regfield{(reserved)}{2}{30}{00}%
\regfield{RMT\_CH7\_DMA\_ACCESS\_FAIL\_INT\_CLR}{1}{29}{{0}}%
\regfield{RMT\_CH3\_DMA\_ACCESS\_FAIL\_INT\_CLR}{1}{28}{{0}}%
\regfield{RMT\_CH7\_RX\_THR\_EVENT\_INT\_CLR}{1}{27}{{0}}%
\regfield{RMT\_CH6\_RX\_THR\_EVENT\_INT\_CLR}{1}{26}{{0}}%
\regfield{RMT\_CH5\_RX\_THR\_EVENT\_INT\_CLR}{1}{25}{{0}}%
\regfield{RMT\_CH4\_RX\_THR\_EVENT\_INT\_CLR}{1}{24}{{0}}%
\regfield{RMT\_CH7\_ERR\_INT\_CLR}{1}{23}{{0}}%
\regfield{RMT\_CH6\_ERR\_INT\_CLR}{1}{22}{{0}}%
\regfield{RMT\_CH5\_ERR\_INT\_CLR}{1}{21}{{0}}%
\regfield{RMT\_CH4\_ERR\_INT\_CLR}{1}{20}{{0}}%
\regfield{RMT\_CH7\_RX\_END\_INT\_CLR}{1}{19}{{0}}%
\regfield{RMT\_CH6\_RX\_END\_INT\_CLR}{1}{18}{{0}}%
\regfield{RMT\_CH5\_RX\_END\_INT\_CLR}{1}{17}{{0}}%
\regfield{RMT\_CH4\_RX\_END\_INT\_CLR}{1}{16}{{0}}%
\regfield{RMT\_CH3\_TX\_LOOP\_INT\_CLR}{1}{15}{{0}}%
\regfield{RMT\_CH2\_TX\_LOOP\_INT\_CLR}{1}{14}{{0}}%
\regfield{RMT\_CH1\_TX\_LOOP\_INT\_CLR}{1}{13}{{0}}%
\regfield{RMT\_CH0\_TX\_LOOP\_INT\_CLR}{1}{12}{{0}}%
\regfield{RMT\_CH3\_TX\_THR\_EVENT\_INT\_CLR}{1}{11}{{0}}%
\regfield{RMT\_CH2\_TX\_THR\_EVENT\_INT\_CLR}{1}{10}{{0}}%
\regfield{RMT\_CH1\_TX\_THR\_EVENT\_INT\_CLR}{1}{9}{{0}}%
\regfield{RMT\_CH0\_TX\_THR\_EVENT\_INT\_CLR}{1}{8}{{0}}%
\regfield{RMT\_CH3\_ERR\_INT\_CLR}{1}{7}{{0}}%
\regfield{RMT\_CH2\_ERR\_INT\_CLR}{1}{6}{{0}}%
\regfield{RMT\_CH1\_ERR\_INT\_CLR}{1}{5}{{0}}%
\regfield{RMT\_CH0\_ERR\_INT\_CLR}{1}{4}{{0}}%
\regfield{RMT\_CH3\_TX\_END\_INT\_CLR}{1}{3}{{0}}%
\regfield{RMT\_CH2\_TX\_END\_INT\_CLR}{1}{2}{{0}}%
\regfield{RMT\_CH1\_TX\_END\_INT\_CLR}{1}{1}{{0}}%
\regfield{RMT\_CH0\_TX\_END\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTCHNTXENDINTCLR}\item [RMT\_CH\regindex{n}\_TX\_END\_INT\_CLR (\regindex{n} = 0-3)] Set this bit to clear \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_TX\_END\_INT} interrupt. (WT)
\label{fielddesc:RMTCHNERRINTCLR}\item [RMT\_CH\regindex{n}\_ERR\_INT\_CLR (\regindex{n} = 0-3)] Set this bit to clear \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_ERR\_INT} interrupt. (WT)
\label{fielddesc:RMTCHNTXTHREVENTINTCLR}\item [RMT\_CH\regindex{n}\_TX\_THR\_EVENT\_INT\_CLR (\regindex{n} = 0-3)] Set this bit to clear \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_TX\_THR\_EVENT\_INT} interrupt. (WT)
\label{fielddesc:RMTCHNTXLOOPINTCLR}\item [RMT\_CH\regindex{n}\_TX\_LOOP\_INT\_CLR (\regindex{n} = 0-3)] Set this bit to clear \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{n}\_TX\_LOOP\_INT} interrupt. (WT)
\label{fielddesc:RMTCHMRXENDINTCLR}\item [RMT\_CH\regindex{m}\_RX\_END\_INT\_CLR (\regindex{m} = 4-7)] Set this bit to clear \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{m}\_RX\_END\_INT} interrupt. (WT)
\label{fielddesc:RMTCHMERRINTCLR}\item [RMT\_CH\regindex{m}\_ERR\_INT\_CLR (\regindex{m} = 4-7)] Set this bit to clear \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{m}\_ERR\_INT} interrupt. (WT)
\label{fielddesc:RMTCHMRXTHREVENTINTCLR}\item [RMT\_CH\regindex{m}\_RX\_THR\_EVENT\_INT\_CLR (\regindex{m} = 4-7)] Set this bit to clear \hyperref[int:RMTCHnTXENDINT]{RMT\_CH\regindex{m}\_RX\_THR\_EVENT\_INT} interrupt. (WT)
\label{fielddesc:RMTCHNDMAACCESSFAILINTCLR}\item [RMT\_CH3\_DMA\_ACCESS\_FAIL\_INT\_CLR] Set this bit to clear \hyperref[int:RMTCHnTXENDINT]{RMT\_CH3\_DMA\_ACCESS\_FAIL\_INT} interrupt. (WT)
\label{fielddesc:RMTCHMDMAACCESSFAILINTCLR}\item [RMT\_CH7\_DMA\_ACCESS\_FAIL\_INT\_CLR] Set this bit to clear \hyperref[int:RMTCHnTXENDINT]{RMT\_CH7\_DMA\_ACCESS\_FAIL\_INT} interrupt. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_CH\regindex{n}CARRIER\_DUTY\_REG (\regindex{n}: 0-3)}{0x{}0080+0x{}4*\regindex{n}}\label{regdesc:RMTCHNCARRIERDUTYREG}
\regfield{RMT\_CARRIER\_HIGH\_CH\regindex{n}}{16}{16}{{0x{}40}}%
\regfield{RMT\_CARRIER\_LOW\_CH\regindex{n}}{16}{0}{{0x{}40}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTCARRIERLOWCHN}\item [RMT\_CARRIER\_LOW\_CH\regindex{n}] This field is used to configure carrier wave's low level clock period for channel \regindex{n}. (R/W)
\label{fielddesc:RMTCARRIERHIGHCHN}\item [RMT\_CARRIER\_HIGH\_CH\regindex{n}] This field is used to configure carrier wave's high level clock period for channel \regindex{n}. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_CH\regindex{n}\_TX\_LIM\_REG (\regindex{n}: 0-3)}{0x{}00A0+0x{}4*\regindex{n}}\label{regdesc:RMTCHNTXLIMREG}
\regfield{(reserved)}{10}{22}{0000000000}%
\regfield{RMT\_LOOP\_STOP\_EN\_CH\regindex{n}}{1}{21}{{0}}%
\regfield{RMT\_LOOP\_COUNT\_RESET\_CH\regindex{n}}{1}{20}{{0}}%
\regfield{RMT\_TX\_LOOP\_CNT\_EN\_CH\regindex{n}}{1}{19}{{0}}%
\regfield{RMT\_TX\_LOOP\_NUM\_CH\regindex{n}}{10}{9}{{0}}%
\regfield{RMT\_TX\_LIM\_CH\regindex{n}}{9}{0}{{0x{}80}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTTXLIMCHN}\item [RMT\_TX\_LIM\_CH\regindex{n}] This field is used to configure the maximum entries that channel \regindex{n} can send out. (R/W)
\label{fielddesc:RMTTXLOOPNUMCHN}\item [RMT\_TX\_LOOP\_NUM\_CH\regindex{n}] This field is used to configure the maximum loop count when continuous TX mode is enabled. (R/W)
\label{fielddesc:RMTTXLOOPCNTENCHN}\item [RMT\_TX\_LOOP\_CNT\_EN\_CH\regindex{n}] This bit is the enable bit for loop counting. (R/W)
\label{fielddesc:RMTLOOPCOUNTRESETCHN}\item [RMT\_LOOP\_COUNT\_RESET\_CH\regindex{n}] This bit is used to reset the loop count when continuous TX mode is enabled. (WT)
\label{fielddesc:RMTLOOPSTOPENCHN}\item [RMT\_LOOP\_STOP\_EN\_CH\regindex{n}] Set this bit, if the loop counting reaches the value set in RMT\_TX\_LOOP\_CNT\_EN\_CH\regindex{n}, continuous TX mode will be stopped. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_TX\_SIM\_REG}{0x{}00C4}\label{regdesc:RMTTXSIMREG}
\regfield{(reserved)}{27}{5}{000000000000000000000000000}%
\regfield{RMT\_TX\_SIM\_EN}{1}{4}{{0}}%
\regfield{RMT\_TX\_SIM\_CH3}{1}{3}{{0}}%
\regfield{RMT\_TX\_SIM\_CH2}{1}{2}{{0}}%
\regfield{RMT\_TX\_SIM\_CH1}{1}{1}{{0}}%
\regfield{RMT\_TX\_SIM\_CH0}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTTXSIMCHN}\item [RMT\_TX\_SIM\_CH\regindex{n} (\regindex{n} = 0-3)] Set this bit to enable channel \regindex{n} to start sending data simultaneously with other enabled channels. (R/W)
\label{fielddesc:RMTTXSIMEN}\item [RMT\_TX\_SIM\_EN] This bit is used to enable multiple channels to start sending data simultaneously. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_CH\regindex{m}\_RX\_LIM\_REG (\regindex{m} = 4, 5, 6, 7)}{0x{}00B0, 0x{}00B4, 0x{}00B8, 0x{}00BC}\label{regdesc:RMTCHMRXLIMREG}
\regfield{(reserved)}{23}{9}{00000000000000000000000}%
\regfield{RMT\_CH\regindex{m}\_RX\_LIM\_REG}{9}{0}{{0x{}80}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTCHMRXLIMREG}\item [RMT\_CH\regindex{m}\_RX\_LIM\_REG] This field is used to configure the maximum entries that channel \regindex{m} can receive. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{RMT\_DATE\_REG}{0x{}00CC}\label{regdesc:RMTDATEREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{RMT\_DATE}{28}{0}{{0x{}2101181}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:RMTDATE}\item [RMT\_DATE] Version control register. (R/W)
\end{reglist}\end{regdesc}
\end{register}


