\begin{register}{H}{JPEG\_CONFIG\_REG}{0x0000}\label{regdesc:JPEGCONFIGREG}
\regfield{JPEG\_MODE}{1}{31}{{0}}%
\regfield{(reserved)}{2}{29}{{00}}%
\regfield{JPEG\_PAUSE\_EN}{1}{28}{{0}}%
\regfield{JPEG\_TAILER\_EN}{1}{27}{{0}}%
\regfield{JPEG\_PIXEL\_REV}{1}{26}{{0}}%
\regfield{JPEG\_FIFO\_RST}{1}{25}{{0}}%
\regfield{JPEG\_SOFT\_RST}{1}{24}{{0}}%
\regfield{JPEG\_DECODE\_TIMEOUT\_TASK\_SEL}{1}{23}{{0}}%
\regfield{JPEG\_DECODE\_TIMEOUT\_THRES}{6}{17}{{32}}%
\regfield{JPEG\_MEM\_CLK\_FORCE\_ON}{1}{16}{{0}}%
\regfield{JPEG\_DHT\_FIFO\_EN}{1}{15}{{1}}%
\regfield{JPEG\_COLOR\_SPACE}{2}{13}{{0}}%
\regfield{JPEG\_CQNR\_TBL\_SEL}{2}{11}{{1}}%
\regfield{JPEG\_LQNR\_TBL\_SEL}{2}{9}{{0}}%
\regfield{JPEG\_QNR\_FIFO\_EN}{1}{8}{{1}}%
\regfield{JPEG\_DEBUG\_DIRECT\_OUT\_EN}{1}{7}{{0}}%
\regfield{JPEG\_DMA\_LINKLIST\_MODE}{1}{6}{{1}}%
\regfield{JPEG\_SAMPLE\_SEL}{2}{4}{{1}}%
\regfield{JPEG\_FF\_CHECK\_EN}{1}{3}{{1}}%
\regfield{JPEG\_QNR\_PRECISION}{1}{2}{{0}}%
\regfield{JPEG\_JPEG\_START}{1}{1}{{0}}%
\regfield{JPEG\_FSM\_RST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGFSMRST}\item [JPEG\_FSM\_RST] Configures whether or not to reset the state machine of JPEG Codec.\\
0: Invalid. No effect\\
1: Reset the state machine\\
(WT)
\label{fielddesc:JPEGJPEGSTART}\item [JPEG\_JPEG\_START] Configures whether or not to start compressing a new image.\\
0: Invalid. No effect\\
1: Start compressing a new image\\
(WT)
\label{fielddesc:JPEGQNRPRECISION}\item [JPEG\_QNR\_PRECISION] Configures the quantization coefficient table precision for the encoder.\\
0: 8-bit precision\\
1: 16-bit precision\\
(R/W)
\label{fielddesc:JPEGFFCHECKEN}\item [JPEG\_FF\_CHECK\_EN] Configures whether or not to add ``0x00" after ``0xFF".\\
0: Not add\\
1: Add\\
(R/W)
\label{fielddesc:JPEGSAMPLESEL}\item [JPEG\_SAMPLE\_SEL] Configures the format of the image to be compressed.\\
0: YUV444\\
1: YUV422\\
2: YUV420\\
3: Invalid. No effect\\
(R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{JPEG\_CONFIG\_REG}{0x0000}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]


\label{fielddesc:JPEGDMALINKLISTMODE}\item [JPEG\_DMA\_LINKLIST\_MODE] Represents 2D DMA linked list mode.\\
0: Invalid. No effect\\
1: 2D DMA uses linked lists to configure\\ (RO)
\label{fielddesc:JPEGDEBUGDIRECTOUTEN}\item [JPEG\_DEBUG\_DIRECT\_OUT\_EN] Configures whether out not to enable debug mode for encoder.\\
0: Disable debug mode, the encoder will work in normal mode\\
1: Enable debug mode, the input image will be directly output by the encoder\\
(R/W)
\label{fielddesc:JPEGQNRFIFOEN}\item [JPEG\_QNR\_FIFO\_EN] Configures whether or not to enable FIFO mode when configuring quantization coefficient tables.\\
0: Disable. Use non-FIFO mode\\
1: Enable\\
(R/W)
\label{fielddesc:JPEGLQNRTBLSEL}\item [JPEG\_LQNR\_TBL\_SEL] Configures the luminance quantization table ID for the encoder. (R/W)
\label{fielddesc:JPEGCQNRTBLSEL}\item [JPEG\_CQNR\_TBL\_SEL] Configures the chrominance quantization table ID for the encoder. (R/W)
\label{fielddesc:JPEGCOLORSPACE}\item [JPEG\_COLOR\_SPACE] Configures the original image's color space.\\
0: RGB888\\
1: YUV422\\
2: RGB565\\
3: GRAY\\
(R/W)
\label{fielddesc:JPEGDHTFIFOEN}\item [JPEG\_DHT\_FIFO\_EN] Configures whether or not to enable FIFO mode when configuring Huffman tables.\\
0: Disable. Use non-FIFO mode\\
1: Enable\\
Note that to read Huffman tables only non-FIFO mode is supported.\\
(R/W)
\label{fielddesc:JPEGMEMCLKFORCEON}\item [JPEG\_MEM\_CLK\_FORCE\_ON] Configures whether or not to force on memory's clock gate.\\
0: Not force on\\
1: Force on\\
(R/W)
\label{fielddesc:JPEGDECODETIMEOUTTHRES}\item [JPEG\_DECODE\_TIMEOUT\_THRES] Configures decode timeout period to trigger \hyperref[fielddesc:JPEGDECODETIMEOUTINTRAW]{JPEG\_DECODE\_TIMEOUT\_INT\_RAW}. The clock cycles of timeout period = $ 2 ^ {JPEG\_DECODE\_TIMEOUT\_THRES} - 1 $.  (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{JPEG\_CONFIG\_REG}{0x0000}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:JPEGDECODETIMEOUTTASKSEL}\item [JPEG\_DECODE\_TIMEOUT\_TASK\_SEL] Configures the reset mode upon the decoder timeout.\\
0: Software uses reset to abort the decoding process\\
1: Hardware automatically aborts decoding process\\
(R/W)
\label{fielddesc:JPEGSOFTRST}\item [JPEG\_SOFT\_RST] Configures whether or not to apply soft reset to the JPEG Codec.\\
0: Release the soft reset\\
1: Apply soft reset to the JPEG Codec (the register configuration value will not be reset)\\
(R/W)
\label{fielddesc:JPEGFIFORST}\item [JPEG\_FIFO\_RST] Configures whether or not to apply FIFO reset to the JPEG Codec.\\
0: Release the FIFO reset\\
1: Apply FIFO reset to the JPEG Codec\\
(R/W)
\label{fielddesc:JPEGPIXELREV}\item [JPEG\_PIXEL\_REV] Configures whether or not to reverse the original image's pixel order.\\
0: Not reverse\\
1: Reverse\\
(R/W)
\label{fielddesc:JPEGTAILEREN}\item [JPEG\_TAILER\_EN] Configures whether or not to add EOI marker ``0xFFD9" at the end of bitstream.\\
0: Not add\\
1: Add\\
(R/W)
\label{fielddesc:JPEGPAUSEEN}\item [JPEG\_PAUSE\_EN] Configures whether or not to pause the JPEG Codec.\\
0: Not pause\\
1: Pause\\ (R/W)
\label{fielddesc:JPEGMODE}\item [JPEG\_MODE] Configures if the JPEG Codec is working as an encoder or a decoder.\\
0: Encoder\\
1: Decoder\\
(R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_DQT\_INFO\_REG}{0x0004}\label{regdesc:JPEGDQTINFOREG}
\regfield{JPEG\_T3\_DQT\_INFO}{8}{24}{{3}}%
\regfield{JPEG\_T2\_DQT\_INFO}{8}{16}{{2}}%
\regfield{JPEG\_T1\_DQT\_INFO}{8}{8}{{1}}%
\regfield{JPEG\_T0\_DQT\_INFO}{8}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGT0DQTINFO}\item [JPEG\_T0\_DQT\_INFO] Configures quantization coefficient table0's precision and ID for decoder.\\
Bit[7:4]: Configures precision\\
Bit[3:0]: Configures ID\\
(R/W)
\label{fielddesc:JPEGT1DQTINFO}\item [JPEG\_T1\_DQT\_INFO] Configures quantization coefficient table1's precision and ID for decoder. See details in \hyperref[fielddesc:JPEGT0DQTINFO]{JPEG\_T0\_DQT\_INFO}. (R/W)\\
\label{fielddesc:JPEGT2DQTINFO}\item [JPEG\_T2\_DQT\_INFO] Configures quantization coefficient table2's precision and ID for decoder. See details in \hyperref[fielddesc:JPEGT0DQTINFO]{JPEG\_T0\_DQT\_INFO}. (R/W)\\
\label{fielddesc:JPEGT3DQTINFO}\item [JPEG\_T3\_DQT\_INFO] Configures quantization coefficient table3's precision and ID for decoder. See details in \hyperref[fielddesc:JPEGT0DQTINFO]{JPEG\_T0\_DQT\_INFO}. (R/W)\\
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_PIC\_SIZE\_REG}{0x0008}\label{regdesc:JPEGPICSIZEREG}
\regfield{JPEG\_HA}{16}{16}{{640}}%
\regfield{JPEG\_VA}{16}{0}{{480}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGVA}\item [JPEG\_VA] Configures the image's height. \\
When JPEG Codec works as an encoder, the maximum configurable bits is 14.\\
When JPEG Codec works as a decoder, the maximum configurable bits is 16.\\
 (R/W)
\label{fielddesc:JPEGHA}\item [JPEG\_HA] Configures the image's width. \\
When JPEG Codec works as an encoder, the maximum configurable bits is 14.\\
When JPEG Codec works as a decoder, the maximum configurable bits is 16.\\
 (R/W)
\end{reglist}\end{regdesc}
\end{register}


\tagged{ESP32-P4-latest}{
    \begin{register}{H}{JPEG\_EXTD\_CONFIG\_REG}{0x000C}\label{regdesc:JPEGEXTDCONFIGREG}
    \regfield{(reserved)}{30}{2}{000000000000000000000000000000}%
    \regfield{JPEG\_EXTD\_COLOR\_SPACE}{1}{1}{{0}}%
    \regfield{JPEG\_EXTD\_COLOR\_SPACE\_EN}{1}{0}{{0}}%
    \reglabel{Reset}\regnewline%
    \begin{regdesc}\begin{reglist}
    \label{fielddesc:JPEGEXTDCOLORSPACEEN}\item [JPEG\_EXTD\_COLOR\_SPACE\_EN] Configure whether to enable extended color space conversion options.\\
    0: Disable\\
    1: Enable\\ (R/W)
    \label{fielddesc:JPEGEXTDCOLORSPACE}\item [JPEG\_EXTD\_COLOR\_SPACE] Configure the extended color space format to be converted. Valid when JPEG\_EXTD\_COLOR\_SPACE\_EN configured to 1.\\
    0: YUV444\\
    1: YUV420\\ (R/W)
    \end{reglist}\end{regdesc}
    \end{register}
}


\begin{register}{H}{JPEG\_T0QNR\_REG}{0x0010}\label{regdesc:JPEGT0QNRREG}
\regfield{JPEG\_T0\_QNR\_VAL}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGT0QNRVAL}\item [JPEG\_T0\_QNR\_VAL] Configures the quantization coefficients of the quantization table 0 in FIFO mode. (HRO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_T1QNR\_REG}{0x0014}\label{regdesc:JPEGT1QNRREG}
\regfield{JPEG\_T1\_QNR\_VAL}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGT1QNRVAL}\item [JPEG\_T1\_QNR\_VAL] Configures the quantization coefficients of the quantization table 1 in FIFO mode. (HRO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_T2QNR\_REG}{0x0018}\label{regdesc:JPEGT2QNRREG}
\regfield{JPEG\_T2\_QNR\_VAL}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGT2QNRVAL}\item [JPEG\_T2\_QNR\_VAL] Configures the quantization coefficients of the quantization table 2 in FIFO mode. (HRO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_T3QNR\_REG}{0x001C}\label{regdesc:JPEGT3QNRREG}
\regfield{JPEG\_T3\_QNR\_VAL}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGT3QNRVAL}\item [JPEG\_T3\_QNR\_VAL] Configures the quantization coefficients of the quantization table 3 in FIFO mode. (HRO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_DECODE\_CONF\_REG}{0x0020}\label{regdesc:JPEGDECODECONFREG}
\regfield{(reserved)}{1}{31}{0}%
\regfield{JPEG\_DEZIGZAG\_READY\_CTL}{1}{30}{{1}}%
\regfield{JPEG\_MULTI\_SCAN\_ERR\_CHECK}{1}{29}{{0}}%
\regfield{JPEG\_RST\_CHECK\_BYTE\_NUM}{2}{27}{{3}}%
\regfield{JPEG\_SOS\_CHECK\_BYTE\_NUM}{2}{25}{{3}}%
\regfield{JPEG\_SW\_DHT\_EN}{1}{24}{{1}}%
\regfield{JPEG\_COMPONENT\_NUM}{8}{16}{{3}}%
\regfield{JPEG\_RESTART\_INTERVAL}{16}{0}{{0x00}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGRESTARTINTERVAL}\item [JPEG\_RESTART\_INTERVAL] Configures the RST interval in DRI segment when decoding. (R/W)
\label{fielddesc:JPEGCOMPONENTNUM}\item [JPEG\_COMPONENT\_NUM] Configures the number of chrominance components in the image when decoding. (R/W)
\label{fielddesc:JPEGSWDHTEN}\item [JPEG\_SW\_DHT\_EN] Represents the Huffman table configured by the software for the decoder. The value is always 1. (RO)
\label{fielddesc:JPEGSOSCHECKBYTENUM}\item [JPEG\_SOS\_CHECK\_BYTE\_NUM] Configures the byte number to check the next SOS marker in the multi-scan image after one scan is decoded down. The actual check number is \hyperref[fielddesc:JPEGSOSCHECKBYTENUM]{JPEG\_SOS\_CHECK\_BYTE\_NUM} + 1 (R/W)
\label{fielddesc:JPEGRSTCHECKBYTENUM}\item [JPEG\_RST\_CHECK\_BYTE\_NUM] Configures the byte number to check the next RST marker after one RST interval is decoded down. The actual check number is \hyperref[fielddesc:JPEGRSTCHECKBYTENUM]{JPEG\_RST\_CHECK\_BYTE\_NUM} + 1. (R/W)
\label{fielddesc:JPEGMULTISCANERRCHECK}\item [JPEG\_MULTI\_SCAN\_ERR\_CHECK] Reserved for decoder and should not be configured. (R/W)
\label{fielddesc:JPEGDEZIGZAGREADYCTL}\item [JPEG\_DEZIGZAG\_READY\_CTL] Reserved for decoder and should not be configured. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_C0\_REG}{0x0024}\label{regdesc:JPEGC0REG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{JPEG\_C0\_ID}{8}{16}{{0}}%
\regfield{JPEG\_C0\_X\_FACTOR}{4}{12}{{1}}%
\regfield{JPEG\_C0\_Y\_FACTOR}{4}{8}{{1}}%
\regfield{JPEG\_C0\_DQT\_TBL\_SEL}{8}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGC0DQTTBLSEL}\item [JPEG\_C0\_DQT\_TBL\_SEL] Configures
 the selected quantization coefficient table ID for component0 in decoder mode. (R/W)
\label{fielddesc:JPEGC0YFACTOR}\item [JPEG\_C0\_Y\_FACTOR] Configures the vertical sampling factor of component0 in decoder mode. (R/W)
\label{fielddesc:JPEGC0xFACTOR}\item [JPEG\_C0\_X\_FACTOR] Configures the horizontal sampling factor of component0 in decoder mode. (R/W)
\label{fielddesc:JPEGC0ID}\item [JPEG\_C0\_ID] Configures the ID of component0 in decoder mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_C1\_REG}{0x0028}\label{regdesc:JPEGC1REG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{JPEG\_C1\_ID}{8}{16}{{0}}%
\regfield{JPEG\_C1\_X\_FACTOR}{4}{12}{{1}}%
\regfield{JPEG\_C1\_Y\_FACTOR}{4}{8}{{1}}%
\regfield{JPEG\_C1\_DQT\_TBL\_SEL}{8}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGC1DQTTBLSEL}\item [JPEG\_C1\_DQT\_TBL\_SEL] Configures
 the selected quantization coefficient table ID for component1 in decoder mode. (R/W)
\label{fielddesc:JPEGC1YFACTOR}\item [JPEG\_C1\_Y\_FACTOR] Configures the vertical sampling factor of component1 in decoder mode. (R/W)
\label{fielddesc:JPEGC1XFACTOR}\item [JPEG\_C1\_X\_FACTOR] Configures the horizontal sampling factor of component1 in decoder mode. (R/W)
\label{fielddesc:JPEGC1ID}\item [JPEG\_C1\_ID] Configures the ID of component1 in decoder mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_C2\_REG}{0x002C}\label{regdesc:JPEGC2REG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{JPEG\_C2\_ID}{8}{16}{{0}}%
\regfield{JPEG\_C2\_X\_FACTOR}{4}{12}{{1}}%
\regfield{JPEG\_C2\_Y\_FACTOR}{4}{8}{{1}}%
\regfield{JPEG\_C2\_DQT\_TBL\_SEL}{8}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGC2DQTTBLSEL}\item [JPEG\_C2\_DQT\_TBL\_SEL] Configures
 the selected quantization coefficient table ID for component2 in decoder mode. (R/W)
\label{fielddesc:JPEGC2YFACTOR}\item [JPEG\_C2\_Y\_FACTOR] Configures the vertical sampling factor of component2 in decoder mode. (R/W)
\label{fielddesc:JPEGC2XFACTOR}\item [JPEG\_C2\_X\_FACTOR] Configures the horizontal sampling factor of component2 in decoder mode. (R/W)
\label{fielddesc:JPEGC2ID}\item [JPEG\_C2\_ID] Configures the ID of component2 in decoder mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_C3\_REG}{0x0030}\label{regdesc:JPEGC3REG}
\regfield{(reserved)}{8}{24}{00000000}%
\regfield{JPEG\_C3\_ID}{8}{16}{{0}}%
\regfield{JPEG\_C3\_X\_FACTOR}{4}{12}{{1}}%
\regfield{JPEG\_C3\_Y\_FACTOR}{4}{8}{{1}}%
\regfield{JPEG\_C3\_DQT\_TBL\_SEL}{8}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGC3DQTTBLSEL}\item [JPEG\_C3\_DQT\_TBL\_SEL] Configures
 the selected quantization coefficient table ID for component3 in decoder mode. (R/W)
\label{fielddesc:JPEGC3YFACTOR}\item [JPEG\_C3\_Y\_FACTOR] Configures the vertical sampling factor of component3 in decoder mode. (R/W)
\label{fielddesc:JPEGC3XFACTOR}\item [JPEG\_C3\_X\_FACTOR] Configures the horizontal sampling factor of component3 in decoder mode. (R/W)
\label{fielddesc:JPEGC3ID}\item [JPEG\_C3\_ID] Configures the ID of component3 in decoder mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_DHT\_INFO\_REG}{0x0034}\label{regdesc:JPEGDHTINFOREG}
\regfield{(reserved)}{16}{16}{0000000000000000}%
\regfield{JPEG\_AC1\_DHT\_ID}{4}{12}{{1}}%
\regfield{JPEG\_AC0\_DHT\_ID}{4}{8}{{0}}%
\regfield{JPEG\_DC1\_DHT\_ID}{4}{4}{{1}}%
\regfield{JPEG\_DC0\_DHT\_ID}{4}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGDC0DHTID}\item [JPEG\_DC0\_DHT\_ID] Configures the ID of DC0 Huffman table in decoder mode. (R/W)
\label{fielddesc:JPEGDC1DHTID}\item [JPEG\_DC1\_DHT\_ID] Configures the ID of DC1 Huffman table in decoder mode. (R/W)
\label{fielddesc:JPEGAC0DHTID}\item [JPEG\_AC0\_DHT\_ID] Configures the ID of AC0 Huffman table in decoder mode. (R/W)
\label{fielddesc:JPEGAC1DHTID}\item [JPEG\_AC1\_DHT\_ID] Configures the ID of AC1 Huffman table in decoder mode. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_INT\_RAW\_REG}{0x0038}\label{regdesc:JPEGINTRAWREG}
\regfield{(reserved)}{7}{25}{0000000}%
\regfield{JPEG\_DECODE\_TIMEOUT\_INT\_RAW}{1}{24}{{0}}%
\regfield{JPEG\_UNDET\_INT\_RAW}{1}{23}{{0}}%
\regfield{JPEG\_MARKER\_ERR\_OTHER\_SCAN\_INT\_RAW}{1}{22}{{0}}%
\regfield{JPEG\_MARKER\_ERR\_FST\_SCAN\_INT\_RAW}{1}{21}{{0}}%
\regfield{JPEG\_SOS\_UNMATCH\_ERR\_INT\_RAW}{1}{20}{{0}}%
\regfield{JPEG\_DE\_FRAME\_EOF\_LACK\_INT\_RAW}{1}{19}{{0}}%
\regfield{JPEG\_DE\_FRAME\_EOF\_ERR\_INT\_RAW}{1}{18}{{0}}%
\regfield{JPEG\_EN\_FRAME\_EOF\_LACK\_INT\_RAW}{1}{17}{{0}}%
\regfield{JPEG\_EN\_FRAME\_EOF\_ERR\_INT\_RAW}{1}{16}{{0}}%
\regfield{JPEG\_UXP\_DET\_INT\_RAW}{1}{15}{{0}}%
\regfield{JPEG\_SCAN\_CHECK\_POS\_ERR\_INT\_RAW}{1}{14}{{0}}%
\regfield{JPEG\_SCAN\_CHECK\_NONE\_ERR\_INT\_RAW}{1}{13}{{0}}%
\regfield{JPEG\_BS\_LAST\_BLOCK\_EOF\_INT\_RAW}{1}{12}{{0}}%
\regfield{JPEG\_DCT\_DONE\_INT\_RAW}{1}{11}{{0}}%
\regfield{JPEG\_SR\_COLOR\_MODE\_ERR\_INT\_RAW}{1}{10}{{0}}%
\regfield{JPEG\_OUT\_EOF\_INT\_RAW}{1}{9}{{0}}%
\regfield{JPEG\_RST\_CHECK\_POS\_ERR\_INT\_RAW}{1}{8}{{0}}%
\regfield{JPEG\_RST\_CHECK\_NONE\_ERR\_INT\_RAW}{1}{7}{{0}}%
\regfield{JPEG\_RST\_UXP\_ERR\_INT\_RAW}{1}{6}{{0}}%
\regfield{JPEG\_C\_DQT\_ID\_ERR\_INT\_RAW}{1}{5}{{0}}%
\regfield{JPEG\_C\_DHT\_AC\_ID\_ERR\_INT\_RAW}{1}{4}{{0}}%
\regfield{JPEG\_C\_DHT\_DC\_ID\_ERR\_INT\_RAW}{1}{3}{{0}}%
\regfield{JPEG\_CID\_ERR\_INT\_RAW}{1}{2}{{0}}%
\regfield{JPEG\_RLE\_PARALLEL\_ERR\_INT\_RAW}{1}{1}{{0}}%
\regfield{JPEG\_DONE\_INT\_RAW}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGDONEINTRAW}\item [JPEG\_DONE\_INT\_RAW] The raw status of JPEG\_DONE\_INT. (R/WTC/SS)
\label{fielddesc:JPEGRLEPARALLELERRINTRAW}\item [JPEG\_RLE\_PARALLEL\_ERR\_INT\_RAW] The raw status of JPEG\_RLE\_PARALLEL\_ERR\_INT.
 (R/WTC/SS)
\label{fielddesc:JPEGCIDERRINTRAW}\item [JPEG\_CID\_ERR\_INT\_RAW] The raw status of JPEG\_CID\_ERR\_INT. (R/WTC/SS)
\label{fielddesc:JPEGCDHTDCIDERRINTRAW}\item [JPEG\_C\_DHT\_DC\_ID\_ERR\_INT\_RAW] The raw status of JPEG\_C\_DHT\_DC\_ID\_ERR\_INT. (R/WTC/SS)
\label{fielddesc:JPEGCDHTACIDERRINTRAW}\item [JPEG\_C\_DHT\_AC\_ID\_ERR\_INT\_RAW] The raw status of JPEG\_C\_DHT\_AC\_ID\_ERR\_INT. (R/WTC/SS)
\label{fielddesc:JPEGCDQTIDERRINTRAW}\item [JPEG\_C\_DQT\_ID\_ERR\_INT\_RAW] The raw status of JPEG\_C\_DQT\_ID\_ERR\_INT. (R/WTC/SS)
\label{fielddesc:JPEGRSTUXPERRINTRAW}\item [JPEG\_RST\_UXP\_ERR\_INT\_RAW] The raw status of JPEG\_RST\_UXP\_ERR\_INT. (R/WTC/SS)
\label{fielddesc:JPEGRSTCHECKNONEERRINTRAW}\item [JPEG\_RST\_CHECK\_NONE\_ERR\_INT\_RAW] The raw status of JPEG\_RST\_CHECK\_NONE\_ERR\_INT. (R/WTC/SS)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{JPEG\_INT\_RAW\_REG}{0x0038}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:JPEGRSTCHECKPOSERRINTRAW}\item [JPEG\_RST\_CHECK\_POS\_ERR\_INT\_RAW] The raw status of JPEG\_RST\_CHECK\_POS\_ERR\_INT. (R/WTC/SS)
\label{fielddesc:JPEGOUTEOFINTRAW}\item [JPEG\_OUT\_EOF\_INT\_RAW] The raw status of JPEG\_OUT\_EOF\_INT. (R/WTC/SS)
\label{fielddesc:JPEGSRCOLORMODEERRINTRAW}\item [JPEG\_SR\_COLOR\_MODE\_ERR\_INT\_RAW] The raw status of JPEG\_SR\_COLOR\_MODE\_ERR\_INT. This interrupt is invalid. (R/WTC/SS)
\label{fielddesc:JPEGDCTDONEINTRAW}\item [JPEG\_DCT\_DONE\_INT\_RAW] The raw status of JPEG\_DCT\_DONE\_INT. (R/WTC/SS)
\label{fielddesc:JPEGBSLASTBLOCKEOFINTRAW}\item [JPEG\_BS\_LAST\_BLOCK\_EOF\_INT\_RAW] The raw status of JPEG\_BS\_LAST\_BLOCK\_EOF\_INT. (R/WTC/SS)
\label{fielddesc:JPEGSCANCHECKNONEERRINTRAW}\item [JPEG\_SCAN\_CHECK\_NONE\_ERR\_INT\_RAW] The raw status of JPEG\_SCAN\_CHECK\_NONE\_ERR\_INT. (R/WTC/SS)
\label{fielddesc:JPEGSCANCHECKPOSERRINTRAW}\item [JPEG\_SCAN\_CHECK\_POS\_ERR\_INT\_RAW] The raw status of JPEG\_SCAN\_CHECK\_POS\_ERR\_INT. (R/WTC/SS)
\label{fielddesc:JPEGUXPDETINTRAW}\item [JPEG\_UXP\_DET\_INT\_RAW] The raw status of JPEG\_UXP\_DET\_INT. (R/WTC/SS)
\label{fielddesc:JPEGENFRAMEEOFERRINTRAW}\item [JPEG\_EN\_FRAME\_EOF\_ERR\_INT\_RAW] The raw status of JPEG\_EN\_FRAME\_EOF\_ERR\_INT. (R/WTC/SS)
\label{fielddesc:JPEGENFRAMEEOFLACKINTRAW}\item [JPEG\_EN\_FRAME\_EOF\_LACK\_INT\_RAW] The raw status of JPEG\_EN\_FRAME\_EOF\_LACK\_INT. (R/WTC/SS)
\label{fielddesc:JPEGDEFRAMEEOFERRINTRAW}\item [JPEG\_DE\_FRAME\_EOF\_ERR\_INT\_RAW] The raw status of JPEG\_DE\_FRAME\_EOF\_ERR\_INT. (R/WTC/SS)
\label{fielddesc:JPEGDEFRAMEEOFLACKINTRAW}\item [JPEG\_DE\_FRAME\_EOF\_LACK\_INT\_RAW] The raw status of JPEG\_DE\_FRAME\_EOF\_LACK\_INT. (R/WTC/SS)
\label{fielddesc:JPEGSOSUNMATCHERRINTRAW}\item [JPEG\_SOS\_UNMATCH\_ERR\_INT\_RAW] The raw status of JPEG\_SOS\_UNMATCH\_ERR\_INT. (R/WTC/SS)
\label{fielddesc:JPEGMARKERERRFSTSCANINTRAW}\item [JPEG\_MARKER\_ERR\_FST\_SCAN\_INT\_RAW] The raw status of JPEG\_MARKER\_ERR\_FST\_SCAN\_INT. (R/WTC/SS)
\label{fielddesc:JPEGMARKERERROTHERSCANINTRAW}\item [JPEG\_MARKER\_ERR\_OTHER\_SCAN\_INT\_RAW] The raw status of JPEG\_MARKER\_ERR\_OTHER\_SCAN\_INT. (R/WTC/SS)
\label{fielddesc:JPEGUNDETINTRAW}\item [JPEG\_UNDET\_INT\_RAW] The raw status of JPEG\_UNDET\_INT. (R/WTC/SS)
\label{fielddesc:JPEGDECODETIMEOUTINTRAW}\item [JPEG\_DECODE\_TIMEOUT\_INT\_RAW] The raw status of JPEG\_DECODE\_TIMEOUT\_INT. (R/WTC/SS)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_INT\_ENA\_REG}{0x003C}\label{regdesc:JPEGINTENAREG}
\regfield{(reserved)}{7}{25}{0000000}%
\regfield{JPEG\_DECODE\_TIMEOUT\_INT\_ENA}{1}{24}{{0}}%
\regfield{JPEG\_UNDET\_INT\_ENA}{1}{23}{{0}}%
\regfield{JPEG\_MARKER\_ERR\_OTHER\_SCAN\_INT\_ENA}{1}{22}{{0}}%
\regfield{JPEG\_MARKER\_ERR\_FST\_SCAN\_INT\_ENA}{1}{21}{{0}}%
\regfield{JPEG\_SOS\_UNMATCH\_ERR\_INT\_ENA}{1}{20}{{0}}%
\regfield{JPEG\_DE\_FRAME\_EOF\_LACK\_INT\_ENA}{1}{19}{{0}}%
\regfield{JPEG\_DE\_FRAME\_EOF\_ERR\_INT\_ENA}{1}{18}{{0}}%
\regfield{JPEG\_EN\_FRAME\_EOF\_LACK\_INT\_ENA}{1}{17}{{0}}%
\regfield{JPEG\_EN\_FRAME\_EOF\_ERR\_INT\_ENA}{1}{16}{{0}}%
\regfield{JPEG\_UXP\_DET\_INT\_ENA}{1}{15}{{0}}%
\regfield{JPEG\_SCAN\_CHECK\_POS\_ERR\_INT\_ENA}{1}{14}{{0}}%
\regfield{JPEG\_SCAN\_CHECK\_NONE\_ERR\_INT\_ENA}{1}{13}{{0}}%
\regfield{JPEG\_BS\_LAST\_BLOCK\_EOF\_INT\_ENA}{1}{12}{{0}}%
\regfield{JPEG\_DCT\_DONE\_INT\_ENA}{1}{11}{{0}}%
\regfield{JPEG\_SR\_COLOR\_MODE\_ERR\_INT\_ENA}{1}{10}{{0}}%
\regfield{JPEG\_OUT\_EOF\_INT\_ENA}{1}{9}{{0}}%
\regfield{JPEG\_RST\_CHECK\_POS\_ERR\_INT\_ENA}{1}{8}{{0}}%
\regfield{JPEG\_RST\_CHECK\_NONE\_ERR\_INT\_ENA}{1}{7}{{0}}%
\regfield{JPEG\_RST\_UXP\_ERR\_INT\_ENA}{1}{6}{{0}}%
\regfield{JPEG\_C\_DQT\_ID\_ERR\_INT\_ENA}{1}{5}{{0}}%
\regfield{JPEG\_C\_DHT\_AC\_ID\_ERR\_INT\_ENA}{1}{4}{{0}}%
\regfield{JPEG\_C\_DHT\_DC\_ID\_ERR\_INT\_ENA}{1}{3}{{0}}%
\regfield{JPEG\_CID\_ERR\_INT\_ENA}{1}{2}{{0}}%
\regfield{JPEG\_RLE\_PARALLEL\_ERR\_INT\_ENA}{1}{1}{{0}}%
\regfield{JPEG\_DONE\_INT\_ENA}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGDONEINTENA}\item [JPEG\_DONE\_INT\_ENA] Write 1 to enable JPEG\_DONE\_INT\_ENA. (R/W)
\label{fielddesc:JPEGRLEPARALLELERRINTENA}\item [JPEG\_RLE\_PARALLEL\_ERR\_INT\_ENA] Write 1 to enable JPEG\_RLE\_PARALLEL\_ERR\_INT. (R/W)
\label{fielddesc:JPEGCIDERRINTENA}\item [JPEG\_CID\_ERR\_INT\_ENA] Write 1 to enable JPEG\_CID\_ERR\_INT. (R/W)
\label{fielddesc:JPEGCDHTDCIDERRINTENA}\item [JPEG\_C\_DHT\_DC\_ID\_ERR\_INT\_ENA] Write 1 to enable JPEG\_C\_DHT\_DC\_ID\_ERR\_INT. (R/W)
\label{fielddesc:JPEGCDHTACIDERRINTENA}\item [JPEG\_C\_DHT\_AC\_ID\_ERR\_INT\_ENA] Write 1 to enable JPEG\_C\_DHT\_AC\_ID\_ERR\_INT. (R/W)
\label{fielddesc:JPEGCDQTIDERRINTENA}\item [JPEG\_C\_DQT\_ID\_ERR\_INT\_ENA] Write 1 to enable JPEG\_C\_DQT\_ID\_ERR\_INT. (R/W)
\label{fielddesc:JPEGRSTUXPERRINTENA}\item [JPEG\_RST\_UXP\_ERR\_INT\_ENA] Write 1 to enable JPEG\_RST\_UXP\_ERR\_INT. (R/W)
\label{fielddesc:JPEGRSTCHECKNONEERRINTENA}\item [JPEG\_RST\_CHECK\_NONE\_ERR\_INT\_ENA] Write 1 to enable JPEG\_RST\_CHECK\_NONE\_ERR\_INT. (R/W)
\label{fielddesc:JPEGRSTCHECKPOSERRINTENA}\item [JPEG\_RST\_CHECK\_POS\_ERR\_INT\_ENA] Write 1 to enable JPEG\_RST\_CHECK\_POS\_ERR\_INT. (R/W)
\label{fielddesc:JPEGOUTEOFINTENA}\item [JPEG\_OUT\_EOF\_INT\_ENA] Write 1 to enable JPEG\_OUT\_EOF\_INT. (R/W)
\label{fielddesc:JPEGSRCOLORMODEERRINTENA}\item [JPEG\_SR\_COLOR\_MODE\_ERR\_INT\_ENA] Write 1 to enable JPEG\_SR\_COLOR\_MODE\_ERR\_INT. (R/W)
\label{fielddesc:JPEGDCTDONEINTENA}\item [JPEG\_DCT\_DONE\_INT\_ENA] Write 1 to enable JPEG\_DCT\_DONE\_INT. (R/W)
\label{fielddesc:JPEGBSLASTBLOCKEOFINTENA}\item [JPEG\_BS\_LAST\_BLOCK\_EOF\_INT\_ENA] Write 1 to enable JPEG\_BS\_LAST\_BLOCK\_EOF\_INT. (R/W)
\label{fielddesc:JPEGSCANCHECKNONEERRINTENA}\item [JPEG\_SCAN\_CHECK\_NONE\_ERR\_INT\_ENA] Write 1 to enable JPEG\_SCAN\_CHECK\_NONE\_ERR\_INT. (R/W)
\label{fielddesc:JPEGSCANCHECKPOSERRINTENA}\item [JPEG\_SCAN\_CHECK\_POS\_ERR\_INT\_ENA] Write 1 to enable JPEG\_SCAN\_CHECK\_POS\_ERR\_INT. (R/W)
\label{fielddesc:JPEGUXPDETINTENA}\item [JPEG\_UXP\_DET\_INT\_ENA] Write 1 to enable JPEG\_UXP\_DET\_INT. (R/W)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{JPEG\_INT\_ENA\_REG}{0x003C}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:JPEGENFRAMEEOFERRINTENA}\item [JPEG\_EN\_FRAME\_EOF\_ERR\_INT\_ENA] Write 1 to enable JPEG\_EN\_FRAME\_EOF\_ERR\_INT. (R/W)
\label{fielddesc:JPEGENFRAMEEOFLACKINTENA}\item [JPEG\_EN\_FRAME\_EOF\_LACK\_INT\_ENA] Write 1 to enable JPEG\_EN\_FRAME\_EOF\_LACK\_INT. (R/W)
\label{fielddesc:JPEGDEFRAMEEOFERRINTENA}\item [JPEG\_DE\_FRAME\_EOF\_ERR\_INT\_ENA] Write 1 to enable JPEG\_DE\_FRAME\_EOF\_ERR\_INT. (R/W)
\label{fielddesc:JPEGDEFRAMEEOFLACKINTENA}\item [JPEG\_DE\_FRAME\_EOF\_LACK\_INT\_ENA] Write 1 to enable JPEG\_DE\_FRAME\_EOF\_LACK\_INT. (R/W)
\label{fielddesc:JPEGSOSUNMATCHERRINTENA}\item [JPEG\_SOS\_UNMATCH\_ERR\_INT\_ENA] Write 1 to enable JPEG\_SOS\_UNMATCH\_ERR\_INT. (R/W)
\label{fielddesc:JPEGMARKERERRFSTSCANINTENA}\item [JPEG\_MARKER\_ERR\_FST\_SCAN\_INT\_ENA] Write 1 to enable JPEG\_MARKER\_ERR\_FST\_SCAN\_INT. (R/W)
\label{fielddesc:JPEGMARKERERROTHERSCANINTENA}\item [JPEG\_MARKER\_ERR\_OTHER\_SCAN\_INT\_ENA] Write 1 to enable JPEG\_MARKER\_ERR\_OTHER\_SCAN\_INT. (R/W)
\label{fielddesc:JPEGUNDETINTENA}\item [JPEG\_UNDET\_INT\_ENA] Write 1 to enable JPEG\_UNDET\_INT. (R/W)
\label{fielddesc:JPEGDECODETIMEOUTINTENA}\item [JPEG\_DECODE\_TIMEOUT\_INT\_ENA] Write 1 to enable JPEG\_DECODE\_TIMEOUT\_INT. (R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_INT\_ST\_REG}{0x0040}\label{regdesc:JPEGINTSTREG}
\regfield{(reserved)}{7}{25}{0000000}%
\regfield{JPEG\_DECODE\_TIMEOUT\_INT\_ST}{1}{24}{{0}}%
\regfield{JPEG\_UNDET\_INT\_ST}{1}{23}{{0}}%
\regfield{JPEG\_MARKER\_ERR\_OTHER\_SCAN\_INT\_ST}{1}{22}{{0}}%
\regfield{JPEG\_MARKER\_ERR\_FST\_SCAN\_INT\_ST}{1}{21}{{0}}%
\regfield{JPEG\_SOS\_UNMATCH\_ERR\_INT\_ST}{1}{20}{{0}}%
\regfield{JPEG\_DE\_FRAME\_EOF\_LACK\_INT\_ST}{1}{19}{{0}}%
\regfield{JPEG\_DE\_FRAME\_EOF\_ERR\_INT\_ST}{1}{18}{{0}}%
\regfield{JPEG\_EN\_FRAME\_EOF\_LACK\_INT\_ST}{1}{17}{{0}}%
\regfield{JPEG\_EN\_FRAME\_EOF\_ERR\_INT\_ST}{1}{16}{{0}}%
\regfield{JPEG\_UXP\_DET\_INT\_ST}{1}{15}{{0}}%
\regfield{JPEG\_SCAN\_CHECK\_POS\_ERR\_INT\_ST}{1}{14}{{0}}%
\regfield{JPEG\_SCAN\_CHECK\_NONE\_ERR\_INT\_ST}{1}{13}{{0}}%
\regfield{JPEG\_BS\_LAST\_BLOCK\_EOF\_INT\_ST}{1}{12}{{0}}%
\regfield{JPEG\_DCT\_DONE\_INT\_ST}{1}{11}{{0}}%
\regfield{JPEG\_SR\_COLOR\_MODE\_ERR\_INT\_ST}{1}{10}{{0}}%
\regfield{JPEG\_OUT\_EOF\_INT\_ST}{1}{9}{{0}}%
\regfield{JPEG\_RST\_CHECK\_POS\_ERR\_INT\_ST}{1}{8}{{0}}%
\regfield{JPEG\_RST\_CHECK\_NONE\_ERR\_INT\_ST}{1}{7}{{0}}%
\regfield{JPEG\_RST\_UXP\_ERR\_INT\_ST}{1}{6}{{0}}%
\regfield{JPEG\_C\_DQT\_ID\_ERR\_INT\_ST}{1}{5}{{0}}%
\regfield{JPEG\_C\_DHT\_AC\_ID\_ERR\_INT\_ST}{1}{4}{{0}}%
\regfield{JPEG\_C\_DHT\_DC\_ID\_ERR\_INT\_ST}{1}{3}{{0}}%
\regfield{JPEG\_CID\_ERR\_INT\_ST}{1}{2}{{0}}%
\regfield{JPEG\_RLE\_PARALLEL\_ERR\_INT\_ST}{1}{1}{{0}}%
\regfield{JPEG\_DONE\_INT\_ST}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGDONEINTST}\item [JPEG\_DONE\_INT\_ST] The masked interrupt status of JPEG\_DONE\_INT. (RO)
\label{fielddesc:JPEGRLEPARALLELERRINTST}\item [JPEG\_RLE\_PARALLEL\_ERR\_INT\_ST] The masked interrupt status of JPEG\_RLE\_PARALLEL\_ERR\_INT. (RO)
\label{fielddesc:JPEGCIDERRINTST}\item [JPEG\_CID\_ERR\_INT\_ST] The masked interrupt status of JPEG\_CID\_ERR\_INT. (RO)
\label{fielddesc:JPEGCDHTDCIDERRINTST}\item [JPEG\_C\_DHT\_DC\_ID\_ERR\_INT\_ST] The masked interrupt status of JPEG\_C\_DHT\_DC\_ID\_ERR\_INT. (RO)
\label{fielddesc:JPEGCDHTACIDERRINTST}\item [JPEG\_C\_DHT\_AC\_ID\_ERR\_INT\_ST] The masked interrupt status of JPEG\_C\_DHT\_AC\_ID\_ERR\_INT. (RO)
\label{fielddesc:JPEGCDQTIDERRINTST}\item [JPEG\_C\_DQT\_ID\_ERR\_INT\_ST] The masked interrupt status of JPEG\_C\_DQT\_ID\_ERR\_INT. (RO)
\label{fielddesc:JPEGRSTUXPERRINTST}\item [JPEG\_RST\_UXP\_ERR\_INT\_ST] The masked interrupt status of JPEG\_RST\_UXP\_ERR\_INT. (RO)
\label{fielddesc:JPEGRSTCHECKNONEERRINTST}\item [JPEG\_RST\_CHECK\_NONE\_ERR\_INT\_ST] The masked interrupt status of JPEG\_RST\_CHECK\_NONE\_ERR\_INT. (RO)
\label{fielddesc:JPEGRSTCHECKPOSERRINTST}\item [JPEG\_RST\_CHECK\_POS\_ERR\_INT\_ST] The masked interrupt status of JPEG\_RST\_CHECK\_POS\_ERR\_INT. (RO)
\label{fielddesc:JPEGOUTEOFINTST}\item [JPEG\_OUT\_EOF\_INT\_ST] The masked interrupt status of JPEG\_OUT\_EOF\_INT. (RO)
\label{fielddesc:JPEGSRCOLORMODEERRINTST}\item [JPEG\_SR\_COLOR\_MODE\_ERR\_INT\_ST] The masked interrupt status of JPEG\_SR\_COLOR\_MODE\_ERR\_INT. (RO)
\label{fielddesc:JPEGDCTDONEINTST}\item [JPEG\_DCT\_DONE\_INT\_ST] The masked interrupt status of JPEG\_DCT\_DONE\_INT. (RO)
\label{fielddesc:JPEGBSLASTBLOCKEOFINTST}\item [JPEG\_BS\_LAST\_BLOCK\_EOF\_INT\_ST] The masked interrupt status of JPEG\_BS\_LAST\_BLOCK\_EOF\_INT. (RO)
\label{fielddesc:JPEGSCANCHECKNONEERRINTST}\item [JPEG\_SCAN\_CHECK\_NONE\_ERR\_INT\_ST] The masked interrupt status of JPEG\_SCAN\_CHECK\_NONE\_ERR\_INT. (RO)
\label{fielddesc:JPEGSCANCHECKPOSERRINTST}\item [JPEG\_SCAN\_CHECK\_POS\_ERR\_INT\_ST] The masked interrupt status of JPEG\_SCAN\_CHECK\_POS\_ERR\_INT. (RO)
\label{fielddesc:JPEGUXPDETINTST}\item [JPEG\_UXP\_DET\_INT\_ST] The masked interrupt status of JPEG\_UXP\_DET\_INT. (RO)

\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{JPEG\_INT\_ST\_REG}{0x0040}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]

\label{fielddesc:JPEGENFRAMEEOFERRINTST}\item [JPEG\_EN\_FRAME\_EOF\_ERR\_INT\_ST] The masked interrupt status of JPEG\_EN\_FRAME\_EOF\_ERR\_INT. (RO)
\label{fielddesc:JPEGENFRAMEEOFLACKINTST}\item [JPEG\_EN\_FRAME\_EOF\_LACK\_INT\_ST] The masked interrupt status of JPEG\_EN\_FRAME\_EOF\_LACK\_INT. (RO)
\label{fielddesc:JPEGDEFRAMEEOFERRINTST}\item [JPEG\_DE\_FRAME\_EOF\_ERR\_INT\_ST] The masked interrupt status of JPEG\_DE\_FRAME\_EOF\_ERR\_INT. (RO)
\label{fielddesc:JPEGDEFRAMEEOFLACKINTST}\item [JPEG\_DE\_FRAME\_EOF\_LACK\_INT\_ST] The masked interrupt status of JPEG\_DE\_FRAME\_EOF\_LACK\_INT. (RO)
\label{fielddesc:JPEGSOSUNMATCHERRINTST}\item [JPEG\_SOS\_UNMATCH\_ERR\_INT\_ST] The masked interrupt status of JPEG\_SOS\_UNMATCH\_ERR\_INT. (RO)
\label{fielddesc:JPEGMARKERERRFSTSCANINTST}\item [JPEG\_MARKER\_ERR\_FST\_SCAN\_INT\_ST] The masked interrupt status of JPEG\_MARKER\_ERR\_FST\_SCAN\_INT. (RO)
\label{fielddesc:JPEGMARKERERROTHERSCANINTST}\item [JPEG\_MARKER\_ERR\_OTHER\_SCAN\_INT\_ST] The masked interrupt status of JPEG\_MARKER\_ERR\_OTHER\_SCAN\_INT. (RO)
\label{fielddesc:JPEGUNDETINTST}\item [JPEG\_UNDET\_INT\_ST] The masked interrupt status of JPEG\_UNDET\_INT. (RO)
\label{fielddesc:JPEGDECODETIMEOUTINTST}\item [JPEG\_DECODE\_TIMEOUT\_INT\_ST] The masked interrupt status of JPEG\_DECODE\_TIMEOUT\_INT. (RO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_INT\_CLR\_REG}{0x0044}\label{regdesc:JPEGINTCLRREG}
\regfield{(reserved)}{7}{25}{0000000}%
\regfield{JPEG\_DECODE\_TIMEOUT\_INT\_CLR}{1}{24}{{0}}%
\regfield{JPEG\_UNDET\_INT\_CLR}{1}{23}{{0}}%
\regfield{JPEG\_MARKER\_ERR\_OTHER\_SCAN\_INT\_CLR}{1}{22}{{0}}%
\regfield{JPEG\_MARKER\_ERR\_FST\_SCAN\_INT\_CLR}{1}{21}{{0}}%
\regfield{JPEG\_SOS\_UNMATCH\_ERR\_INT\_CLR}{1}{20}{{0}}%
\regfield{JPEG\_DE\_FRAME\_EOF\_LACK\_INT\_CLR}{1}{19}{{0}}%
\regfield{JPEG\_DE\_FRAME\_EOF\_ERR\_INT\_CLR}{1}{18}{{0}}%
\regfield{JPEG\_EN\_FRAME\_EOF\_LACK\_INT\_CLR}{1}{17}{{0}}%
\regfield{JPEG\_EN\_FRAME\_EOF\_ERR\_INT\_CLR}{1}{16}{{0}}%
\regfield{JPEG\_UXP\_DET\_INT\_CLR}{1}{15}{{0}}%
\regfield{JPEG\_SCAN\_CHECK\_POS\_ERR\_INT\_CLR}{1}{14}{{0}}%
\regfield{JPEG\_SCAN\_CHECK\_NONE\_ERR\_INT\_CLR}{1}{13}{{0}}%
\regfield{JPEG\_BS\_LAST\_BLOCK\_EOF\_INT\_CLR}{1}{12}{{0}}%
\regfield{JPEG\_DCT\_DONE\_INT\_CLR}{1}{11}{{0}}%
\regfield{JPEG\_SR\_COLOR\_MODE\_ERR\_INT\_CLR}{1}{10}{{0}}%
\regfield{JPEG\_OUT\_EOF\_INT\_CLR}{1}{9}{{0}}%
\regfield{JPEG\_RST\_CHECK\_POS\_ERR\_INT\_CLR}{1}{8}{{0}}%
\regfield{JPEG\_RST\_CHECK\_NONE\_ERR\_INT\_CLR}{1}{7}{{0}}%
\regfield{JPEG\_RST\_UXP\_ERR\_INT\_CLR}{1}{6}{{0}}%
\regfield{JPEG\_C\_DQT\_ID\_ERR\_INT\_CLR}{1}{5}{{0}}%
\regfield{JPEG\_C\_DHT\_AC\_ID\_ERR\_INT\_CLR}{1}{4}{{0}}%
\regfield{JPEG\_C\_DHT\_DC\_ID\_ERR\_INT\_CLR}{1}{3}{{0}}%
\regfield{JPEG\_CID\_ERR\_INT\_CLR}{1}{2}{{0}}%
\regfield{JPEG\_RLE\_PARALLEL\_ERR\_INT\_CLR}{1}{1}{{0}}%
\regfield{JPEG\_DONE\_INT\_CLR}{1}{0}{{0}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGDONEINTCLR}\item [JPEG\_DONE\_INT\_CLR] Write 1 to clear JPEG\_DONE\_INT. (WT)
\label{fielddesc:JPEGRLEPARALLELERRINTCLR}\item [JPEG\_RLE\_PARALLEL\_ERR\_INT\_CLR] Write 1 to clear JPEG\_RLE\_PARALLEL\_ERR\_INT. (WT)
\label{fielddesc:JPEGCIDERRINTCLR}\item [JPEG\_CID\_ERR\_INT\_CLR] Write 1 to clear JPEG\_CID\_ERR\_INT. (WT)
\label{fielddesc:JPEGCDHTDCIDERRINTCLR}\item [JPEG\_C\_DHT\_DC\_ID\_ERR\_INT\_CLR] Write 1 to clear JPEG\_C\_DHT\_DC\_ID\_ERR\_INT. (WT)
\label{fielddesc:JPEGCDHTACIDERRINTCLR}\item [JPEG\_C\_DHT\_AC\_ID\_ERR\_INT\_CLR] Write 1 to clear JPEG\_C\_DHT\_AC\_ID\_ERR\_INT. (WT)
\label{fielddesc:JPEGCDQTIDERRINTCLR}\item [JPEG\_C\_DQT\_ID\_ERR\_INT\_CLR] Write 1 to clear JPEG\_C\_DQT\_ID\_ERR\_INT. (WT)
\label{fielddesc:JPEGRSTUXPERRINTCLR}\item [JPEG\_RST\_UXP\_ERR\_INT\_CLR] Write 1 to clear JPEG\_RST\_UXP\_ERR\_INT. (WT)
\label{fielddesc:JPEGRSTCHECKNONEERRINTCLR}\item [JPEG\_RST\_CHECK\_NONE\_ERR\_INT\_CLR] Write 1 to clear JPEG\_RST\_CHECK\_NONE\_ERR\_INT. (WT)
\label{fielddesc:JPEGRSTCHECKPOSERRINTCLR}\item [JPEG\_RST\_CHECK\_POS\_ERR\_INT\_CLR] Write 1 to clear JPEG\_RST\_CHECK\_POS\_ERR\_INT. (WT)
\label{fielddesc:JPEGOUTEOFINTCLR}\item [JPEG\_OUT\_EOF\_INT\_CLR] Write 1 to clear JPEG\_OUT\_EOF\_INT. (WT)
\label{fielddesc:JPEGSRCOLORMODEERRINTCLR}\item [JPEG\_SR\_COLOR\_MODE\_ERR\_INT\_CLR] Write 1 to clear JPEG\_SR\_COLOR\_MODE\_ERR\_INT. (WT)
\label{fielddesc:JPEGDCTDONEINTCLR}\item [JPEG\_DCT\_DONE\_INT\_CLR] Write 1 to clear JPEG\_DCT\_DONE\_INT. (WT)
\label{fielddesc:JPEGBSLASTBLOCKEOFINTCLR}\item [JPEG\_BS\_LAST\_BLOCK\_EOF\_INT\_CLR] Write 1 to clear JPEG\_BS\_LAST\_BLOCK\_EOF\_INT. (WT)
\label{fielddesc:JPEGSCANCHECKNONEERRINTCLR}\item [JPEG\_SCAN\_CHECK\_NONE\_ERR\_INT\_CLR] Write 1 to clear JPEG\_SCAN\_CHECK\_NONE\_ERR\_INT. (WT)
\label{fielddesc:JPEGSCANCHECKPOSERRINTCLR}\item [JPEG\_SCAN\_CHECK\_POS\_ERR\_INT\_CLR] Write 1 to clear JPEG\_SCAN\_CHECK\_POS\_ERR\_INT. (WT)


\item [Continued on the next page...]
\end{reglist}\end{regdesc}
\end{register}

\addtocounter{Regfloat}{-1}
\begin{register}{H}{JPEG\_INT\_CLR\_REG}{0x0044}
\begin{regdesc}\begin{reglist}
\item [Continued from the previous page...]


\label{fielddesc:JPEGUXPDETINTCLR}\item [JPEG\_UXP\_DET\_INT\_CLR] Write 1 to clear JPEG\_UXP\_DET\_INT. (WT)
\label{fielddesc:JPEGENFRAMEEOFERRINTCLR}\item [JPEG\_EN\_FRAME\_EOF\_ERR\_INT\_CLR] Write 1 to clear JPEG\_EN\_FRAME\_EOF\_ERR\_INT. (WT)
\label{fielddesc:JPEGENFRAMEEOFLACKINTCLR}\item [JPEG\_EN\_FRAME\_EOF\_LACK\_INT\_CLR] Write 1 to clear JPEG\_EN\_FRAME\_EOF\_LACK\_INT. (WT)
\label{fielddesc:JPEGDEFRAMEEOFERRINTCLR}\item [JPEG\_DE\_FRAME\_EOF\_ERR\_INT\_CLR] Write 1 to clear JPEG\_DE\_FRAME\_EOF\_ERR\_INT. (WT)
\label{fielddesc:JPEGDEFRAMEEOFLACKINTCLR}\item [JPEG\_DE\_FRAME\_EOF\_LACK\_INT\_CLR] Write 1 to clear JPEG\_DE\_FRAME\_EOF\_LACK\_INT. (WT)
\label{fielddesc:JPEGSOSUNMATCHERRINTCLR}\item [JPEG\_SOS\_UNMATCH\_ERR\_INT\_CLR] Write 1 to clear JPEG\_SOS\_UNMATCH\_ERR\_INT. (WT)
\label{fielddesc:JPEGMARKERERRFSTSCANINTCLR}\item [JPEG\_MARKER\_ERR\_FST\_SCAN\_INT\_CLR] Write 1 to clear JPEG\_MARKER\_ERR\_FST\_SCAN\_INT. (WT)
\label{fielddesc:JPEGMARKERERROTHERSCANINTCLR}\item [JPEG\_MARKER\_ERR\_OTHER\_SCAN\_INT\_CLR] Write 1 to clear JPEG\_MARKER\_ERR\_OTHER\_SCAN\_INT. (WT)
\label{fielddesc:JPEGUNDETINTCLR}\item [JPEG\_UNDET\_INT\_CLR] Write 1 to clear JPEG\_UNDET\_INT. (WT)
\label{fielddesc:JPEGDECODETIMEOUTINTCLR}\item [JPEG\_DECODE\_TIMEOUT\_INT\_CLR] Write 1 to clear JPEG\_DECODE\_TIMEOUT\_INT. (WT)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_DHT\_TOTLEN\_DC0\_REG}{0x0058}\label{regdesc:JPEGDHTTOTLENDC0REG}
\regfield{JPEG\_DHT\_TOTLEN\_DC0}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGDHTTOTLENDC0}\item [JPEG\_DHT\_TOTLEN\_DC0] Configures the number of codeword with a codeword length of 1 to 16 bits for DC0 Huffman table in FIFO mode. (HRO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_DHT\_VAl\_DC0\_REG}{0x005C}\label{regdesc:JPEGDHTVALDC0REG}
\regfield{JPEG\_DHT\_VAL\_DC0}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGDHTVALDC0}\item [JPEG\_DHT\_VAL\_DC0] Configures the symbols corresponding to the decoded codeword for DC0 Huffman table in FIFO mode. (HRO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_DHT\_TOTLEN\_AC0\_REG}{0x0060}\label{regdesc:JPEGDHTTOTLENAC0REG}
\regfield{JPEG\_DHT\_TOTLEN\_AC0}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGDHTTOTLENAC0}\item [JPEG\_DHT\_TOTLEN\_AC0] Configures the number of codeword with a codeword length of 1 to 16 bits for AC0 Huffman table in FIFO mode. (HRO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_DHT\_VAl\_AC0\_REG}{0x0064}\label{regdesc:JPEGDHTVALAC0REG}
\regfield{JPEG\_DHT\_VAL\_AC0}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGDHTVALAC0}\item [JPEG\_DHT\_VAL\_AC0] Configures the symbols corresponding to the decoded codeword for AC0 Huffman table in FIFO mode. (HRO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_DHT\_TOTLEN\_DC1\_REG}{0x0068}\label{regdesc:JPEGDHTTOTLENDC1REG}
\regfield{JPEG\_DHT\_TOTLEN\_DC1}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGDHTTOTLENDC1}\item [JPEG\_DHT\_TOTLEN\_DC1] Configures the number of codeword with a codeword length of 1 to 16 bits for DC1 Huffman table in FIFO mode. (HRO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_DHT\_VAl\_DC1\_REG}{0x006C}\label{regdesc:JPEGDHTVALDC1REG}
\regfield{JPEG\_DHT\_VAL\_DC1}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGDHTVALDC1}\item [JPEG\_DHT\_VAL\_DC1] Configures the symbols corresponding to the decoded codeword for DC1 Huffman table in FIFO mode. (HRO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_DHT\_TOTLEN\_AC1\_REG}{0x0070}\label{regdesc:JPEGDHTTOTLENAC1REG}
\regfield{JPEG\_DHT\_TOTLEN\_AC1}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGDHTTOTLENAC1}\item [JPEG\_DHT\_TOTLEN\_AC1] Configures the number of codeword with a codeword length of 1 to 16 bits for AC1 Huffman table in FIFO mode. (HRO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_DHT\_VAl\_AC1\_REG}{0x0074}\label{regdesc:JPEGDHTVALAC1REG}
\regfield{JPEG\_DHT\_VAL\_AC1}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGDHTVALAC1}\item [JPEG\_DHT\_VAL\_AC1] Configures the symbols corresponding to the decoded codeword for AC1 Huffman table in FIFO mode. (HRO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_DHT\_CODEMIN\_DC0\_REG}{0x0078}\label{regdesc:JPEGDHTCODEMINDC0REG}
\regfield{JPEG\_DHT\_CODEMIN\_DC0}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGDHTCODEMINDC0}\item [JPEG\_DHT\_CODEMIN\_DC0] Configures the minimum codeword with a codeword length of 1 to 16 bits for DC0 Huffman table in FIFO mode. The codeword should be left shifted to the MSB position of a 16-bit word. (HRO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_DHT\_CODEMIN\_AC0\_REG}{0x007C}\label{regdesc:JPEGDHTCODEMINAC0REG}
\regfield{JPEG\_DHT\_CODEMIN\_AC0}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGDHTCODEMINAC0}\item [JPEG\_DHT\_CODEMIN\_AC0] Configures the minimum codeword with a codeword length of 1 to 16 bits for AC0 Huffman table in FIFO mode. The codeword should be left shifted to the MSB position of a 16-bit word. (HRO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_DHT\_CODEMIN\_DC1\_REG}{0x0080}\label{regdesc:JPEGDHTCODEMINDC1REG}
\regfield{JPEG\_DHT\_CODEMIN\_DC1}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGDHTCODEMINDC1}\item [JPEG\_DHT\_CODEMIN\_DC1] Configures the minimum codeword with a codeword length of 1 to 16 bits for DC1 Huffman table in FIFO mode. The codeword should be left shifted to the MSB position of a 16-bit word. (HRO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_DHT\_CODEMIN\_AC1\_REG}{0x0084}\label{regdesc:JPEGDHTCODEMINAC1REG}
\regfield{JPEG\_DHT\_CODEMIN\_AC1}{32}{0}{{0x000000}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGDHTCODEMINAC1}\item [JPEG\_DHT\_CODEMIN\_AC1] Configures the minimum codeword with a codeword length of 1 to 16 bits for AC1 Huffman table in FIFO mode. The codeword should be left shifted to the MSB position of a 16-bit word. (HRO)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_SYS\_REG}{0x00F8}\label{regdesc:JPEGSYSREG}
\regfield{JPEG\_CLK\_EN}{1}{31}{{0}}%
\regfield{(reserved)}{31}{0}{0000000000000000000000000000000}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGCLKEN}\item [JPEG\_CLK\_EN] Configures whether or not to force open register clock gate.\\
0: Open the clock gate only when the application writes registers\\
1: Force open the clock gate for register\\
(R/W)
\end{reglist}\end{regdesc}
\end{register}


\begin{register}{H}{JPEG\_VERSION\_REG}{0x00FC}\label{regdesc:JPEGVERSIONREG}
\regfield{(reserved)}{4}{28}{0000}%
\regfield{JPEG\_JPEG\_VER}{28}{0}{{0x2111190}}%
\reglabel{Reset}\regnewline%
\begin{regdesc}\begin{reglist}
\label{fielddesc:JPEGJPEGVER}\item [JPEG\_JPEG\_VER] Version control. (R/W)
\end{reglist}\end{regdesc}
\end{register}
